### 2018-12-14 vesicle_code/docs/adhesion/adhesion.tex
added paper to repo

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.1 distribution.
%   Version 4.1r of REVTeX, August 2010
%
%   Copyright (c) 2009, 2010 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
%reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
preprint,
%showpacs,preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-1}

\usepackage[titletoc]{appendix}
\usepackage{todonotes}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{stmaryrd}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

%\usepackage[showframe,%Uncomment any one of the following lines to test 
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}

\renewcommand{\AA}{\mathcal{A}}
\newcommand{\BB}{\mathcal{B}}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\ff}{\mathbf{f}}
\newcommand{\nn}{\mathbf{n}}
\renewcommand{\tt}{\mathbf{t}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbb{R}}
\renewcommand{\ss}{\mathbf{s}}
\renewcommand{\SS}{\mathcal{S}}
\newcommand{\TT}{\mathcal{T}}
\newcommand{\uu}{\mathbf{u}}
\newcommand{\WW}{\mathcal{W}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\xxi}{\boldsymbol{\xi}}
\newcommand{\yy}{\mathbf{y}}

\begin{document}

\preprint{APS/123-QED}

\title{Hydrodynamics of two vesicles interacting via a Van der Waals potential}% Force line breaks with \\
%\thanks{A footnote to the article title}%

\author{Bryan Quaife}
 \email{bquaife@fsu.edu}
 \altaffiliation[]{Department of Scientific Computing \\ Florida State University}
\author{Shravan Veerapaneni}%
 \email{shravan@umich.edu}
\altaffiliation{%
 Department of Mathematics \\
University of Michigan, Ann Arbor
}%
\author{Yuan-Nan Young}%
 \email{yyoung@njit.edu}
\altaffiliation{%
 Department of Mathematical Sciences \\
 New Jersey Institute of Technology
}%

%\collaboration{MUSO Collaboration}%\noaffiliation

%\author{Charlie Author}
% \homepage{http://www.Second.institution.edu/~Charlie.Author}
%\affiliation{
% Second institution and/or address\\
% This line break forced% with \\
%}%
%\affiliation{
% Third institution, the second for Charlie Author
%}%
%\author{Delta Author}
%\affiliation{%
% Authors' institution and/or address\\
% This line break forced with \textbackslash\textbackslash
%}%
%
%\collaboration{CLEO Collaboration}%\noaffiliation

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}
An article usually includes an abstract, a concise summary of the work
covered at length in the main body of the article. 
\begin{description}
\item[Usage]
Secondary publications and information retrieval purposes.
\item[PACS numbers]
May be entered using the \verb+\pacs{#1}+ command.
\item[Structure]
You may use the \texttt{description} environment to structure your abstract;
use the optional argument of the \verb+\item+ command to give the category of each item. 
\end{description}
\end{abstract}

\pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
                             % Classification Scheme.
%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle

%\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Vesicles (self-enclosed phopolipid bilayer membranes) have been widely utilized
as simple cell mimics in biomedical and material engineering \cite{}. The ever expanding applications of vesicles have encouraged extensive investigations on vesicle hydrodynamics
and electrohydrodynamics: Theoretical investigations are often limited to small-deformation of a nearly spherical (circular) vesicle in 3D (2D) \cite{Barthes-BieselRallison1981_JFM,Misbah2006_PRL,Vlahovska2007_PRE,Finken2008_EPL}. Various numerical schemes have been designed and deployed to simulate the dynamics of many vesicles \cite{BagchiJohoson2005_JBE,Biben2005_EJP,Veerapaneni2009_JCP,SeolHuKimLai2016_JCP}.  Careful experiments on vesicles under different flowing conditions or forcing configurations have been carried out \cite{MaderVitkova2006_EurPhysJE, Abkarian2008_SoftMatt}. In a vesicle suspension under 
a hydrodynamic flow or an external field (such as an electric field) 
the interactions between
vesicles play a crucial role in determining the collective dynamics of
vesicle suspension. For example, boundary integral simulations show that
vesicles may align to form chains along the external electric field,
enhancing the suspension viscosity in the direction of alignment.
In numerical simulations, it is often assumed that vesicles do not get closer than a few nano meters, where the
Van der Waals interaction between lipid bilayers becomes important \cite{EvansMetcalfe1984_BJ,Book_PhysicalBasisCellAdhesion,Book_IntermolecularSurfaceForces}.
For giant unilamellar vesicles (GUVs) this assumption is reasonable, however for vesicles of size $\sim 100$ nm the van der Waals
interactions between vesicles are important and may significantly affect their shape in the absence of any external forcing \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}. In this paper we use boundary integral simulations to investigate
how such Van der Waals interactions between sub-micron vesicles may affect their hydrodynamics and consequently the rheology 
of their suspension in the dilute limit.

Due to the nature of amphiphilic molecules (a dipole in the hydrophilic head), the adhesive interaction of a amphiphilic bilayer membrane 
with either a solid (such as a glass substrate or a nano particle) or another bilayer 
plays a central role in many biomedical, biological and biophysical processes.
Vesicle adhesion is an essential step for membrane fusion/fission in many
processes such as, e.g., endocytosis and exocytosis, that is, the
transport of small vesicles through large membrane surfaces. 
Adhesion between a vesicle and a substrate has been extensively studied, with 
more computations and experiments for the equilibrium shapes \cite{Seifert1990_PRA,ShiFengGao2006_ActaMechSin,LinFreund2007_IntJSolidsStructures} than analysis and simulation of
the dynamic adhesion process \cite{BlountMiksisDavis2013_PRSa}.
Adhesion between bilayer membranes was first experimentally observed by Evans and Metcalfe, who measured 
the reduction in the free energy per unit area of membrane-membrane contact formation due to the Van der Waals' attraction. For a membrane-membrane
separation distance of $\sim 3$ nano meters, they estimated that the Hamaker constant $\sim 5.8\times 10^{-14}$ ergs \cite{EvansMetcalfe1984_BJ}, which corresponds to an adhesion energy density $\sim 1$ mJ/m$^2$. The ratio of adhesion energy per unit area to the bending energy (bending rigidity of lipid bilayer membranes $\sim 10^{-19}$ J) gives a measure of vesicle deformation in the presence of adhesion \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}. In this work we focus on regimes where the ratio is of order unity, between the weak adhesion (ratio $\ll 1$) and strong adhesion (ratio $\gg 1$) regimes \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}. 
In this regime the membrane deformation may increase the ``contact area'' between two vesicles and enhance the adhesion effects \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}. The equilibration of vesicle membranes under adhesion in these regimes have been well studied and documented (\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir} and references therein). However it is not clear how in such regime the adhesion couples to the vesicle hydrodynamics? Our work in this paper aims to address this question with quantitative characterization in terms of physical parameters.

Hydrodynamics of a single vesicle in Stokes flow has been extensively investigated. In a planar shear flow, the vesicle hydrodynamics is characterized by
excess area (reduced volume), viscosity contrast between interior and exterior fluids, and shear rate of the imposed far-field fluid flow. In addition a vesicle
with a rigid particle inside is also investigated as a biological mimic of a 
eukaryotic cell with a nucleus that occupies nearly half of the intracellular volume \cite{Veerapaneni2011_PRL}. Small-deformation analysis shows that
a vesicle tank-treads in a planar shear flow for low viscosity contrast and shear rate. At high viscosity contrast the tank-tread (TT) dynamics transitions to tumbling (TB) \cite{Misbah2006_PRL,Vlahovska2007_PRE} ,
and this leads to a transition in effective shear viscosity in the vesicle suspension \cite{Misbah2006_PRL,Vitkova2008_BJ} that is also validated
by direct numerical simulations \cite{GhigliottiBibenMisbah2010_JFM} and experiments \cite{KantslerSegreSteinberg2008_EPL,ZabuskySegreDeschamps2011_PoF}.
Between TT and TB vesicle hydrodynamics, a breathing (tremble) is also observed \cite{Misbah2006_PRL,KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2011_JFM,SpannZhaoShaqfeh2014_PoF} to affect the effective shear viscosity in a 
different way.
%
In an extensional flow (planar or uniaxial), vesicle shape dynamics
depends sensitively on the vesicle reduced volume  and the elastic capillary number \cite{KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2013_JFM,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}: Asymmetric shape and oscillatory undulation of the vesicle membrane are two examples of the complex vesicle hydrodynamics in an extensional flow.

In a quiescent environment, sub-micron size vesicles are found to form a doublet due to their Van der Waals' attractive interactions \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}. Due to the strong Van der Waals' adhesive force, the vesicles are far
from spherical shape and the membrane is almost flat in the ``contact" region. Gires {\it et al.} used small-deformation analysis to investigate the hydrodynamic
interactions between two vesicles in a planar shear flow with a long separation distance \cite{GiresDankerMisbah2012_PRE}. They found that the vesicle interaction could be either attractive or repulsive depending on the organization of the two vesicles relative to the shear flow. To the best of authors' knowledge,
the effects of close-range vesicle adhesion on their hydrodynamics under an external flow have not been studied and quantified. The goal of this work is to use
state-of-the-art boundary integral simulations to numerically investigate the dynamics of two vesicles in both planar shear flow and extensional flow for a wide range of vesicle shapes and adhesive strength and distance.

Boundary integral equations (BIEs) have a unique advantage that all the
unknowns are on the boundary of the domain.  Therefore, resolving
complex and dynamic geometries is straightforward.  Moreover, by using
appropriate quadrature rules, high-order or spectral accuracy is
obtained.  Finally, even though the resulting linear systems that need
to be solved are dense, they can be solved with optimal complexity by
using fast summation methods.  \todo[inline]{Time stepping}

This paper is organized as follows.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing Equations}
We consider suspensions of locally inextensible vesicles in an unbounded
two-dimensional viscous fluid.  For simplicity, we assume the fluid
viscosity both inside and outside the vesicles is constant, but our
method can be easily adjusted to account for a viscosity contrast.
Individual vesicles are denoted as $\gamma_j$, and they are
parameterized in arclength as $\xx_j(s,t)$.  The union of all vesicles
is denoted by $\gamma$.  Given a background velocity $\uu_\infty$, the
governing equations are
\begin{equation*}
\begin{aligned}
  \mu \Delta \uu = \nabla p, \quad &\xx \in \RR^2,
    &&\mbox{\em conservation of momentum} \\
  \nabla \cdot \uu = 0, \quad &\xx \in \RR^2, 
    &&\mbox{\em conservation of mass} \\
  \uu \rightarrow \uu_\infty, \quad &\|\xx\| \rightarrow \infty,
    &&\mbox{\em far-field condition} \\
  \uu(\xx,t) = \dot{\xx}, \quad &\xx \in \gamma,
    &&\mbox{\em velocity continuity} \\
  \xx_s \cdot \uu_s =0, \quad &\xx \in \gamma,
    &&\mbox{\em vesicle inextensibility} \\
  \llbracket T \rrbracket \nn = \xxi, \quad &\xx \in \gamma,
    &&\mbox{\em non-zero traction jump}
\end{aligned}
\end{equation*}
where $\xxi$ is the traction jump that depends on a bending, stretching,
and adhesion.  The bending term is $\BB \xx = -\kappa_b \xx_{ssss}$,
where $\kappa_b$ is the bending modulus, and this term comes from the
Helfrich energy.  For the numerical examples, we set $\kappa_b = 1$ and
use a Hamaker constants ranging from $0.1$ to $1$.  The stretching term
is $\TT \sigma  = (\sigma \xx_s)_s$, where $\sigma$ is the tension.  The
resistance to bending and stretching are standard assumptions of
vesicles.  In this work, we include an adhesive term, $\AA \xx$, that we
now describe.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Adhesion Model}
The adhesion model of Sukumaran and Seifert~\cite{suk-sei2001,
RamachandranAndersonLealIsraelachvili2010_Langmuir} considers adhesion
between a single three-dimensional vesicle and a solid wall at $z=0$.
\todo[inline]{Need a cartoon picture in here.  Some kind of version of
the one I had for my SIAM Life Sciences Talk}
Their model uses the adhesion potential
\begin{align*}
  \phi(z) = \sigma\left(\frac{\delta}{z}\right)^2 \left[ 
    \left(\frac{\delta}{z}\right)^2 - 2 \right],
\end{align*}
where $z$ is the distance between the solid wall and the vesicle,
$\sigma$ is the Hamaker constant, and $\delta$ is the adhesion length
scale.  We generalize this model to an unbounded suspension of vesicles.
We assume that the adhesion force applies between all pairs of points on
different vesicles, so we are interested in Hamaker constants that are
appropriate for lipid-lipid interactions. In
Appendix~\ref{sec:appendixA}, the adhesive force at a point $\xx$ on
vesicle $j$ is shown to be
\begin{align}
  \AA\xx:=-4 \sigma \delta^2\sum_{\substack{k=1 \\ k \neq j}}^M 
  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^2} 
  \left(\delta^2 - \|\xx - \yy\|^2 \right) ds_\yy.
  \label{eqn:adhesionForce}
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Integral Equation Formulation}
Because the fluid equations are linear and elliptic, an integral
equation formulation is possible.  This has several advantages,
including that only the vesicle interfaces require discretization.  We
start by defining the Stokes single-layer potential
\begin{align}
  \SS[\ff](\xx) &= \frac{1}{4\pi\mu} \int_\gamma \left(
    -\log \rho + \frac{\rr \otimes \rr}{\rho^2} \right) 
    \ff(\yy) ds_\yy, \quad \xx \in \RR^2.
  \label{eqn:SLP}
\end{align}
The traction jump of the velocity $\uu(\xx) = \SS[\ff](\xx)$ is the
density function $\ff$, so the fluid velocity is $\xx \in \RR^2$ is
\begin{align*}
  \uu(\xx) = \uu_{\infty}(\xx) + \SS[\xxi](\xx).
\end{align*}
The traction jump is given by three terms: the bending, tension, and
adhesion.  Therefore
\begin{align*}
  \xxi = -\kappa_b \xx_{ssss} + (\sigma \xx_s)_s + \AA \xx.
\end{align*}
Applying the no-slip boundary condition on each vesicle, the governing
equations are
\begin{align*}
  &\dot{\xx} = \uu_{\infty}(\xx) + \SS[\xxi](\xx), \\
  &\xx_s \cdot \uu_s = 0, \\
  &\xxi = -\kappa_b \xx_{ssss} + (\sigma \xx_s)_s + \AA\xx.
\end{align*}
Defining the bending operator as $\BB[\xx](\ff) = -\kappa_b \ff_{ssss}$,
and the tension operator $\TT[\xx](\sigma) = (\sigma \xx_s)_s$, the
no-slip boundary condition can be written as
\begin{align*}
  \pderiv{\xx}{t} = \SS \BB \xx + \SS \TT \sigma + \SS \AA \xx.
\end{align*}
We apply the IMEX-Euler method 
\begin{align*}
  \frac{\xx^{N+1} - \xx^N}{\Delta t} = \SS^N \BB^N \xx^{N+1} + 
  \SS^N \TT^N \sigma^{N+1} + \SS^N \AA^N \xx^N,
\end{align*}
that treats both the bending and tension terms
semi-implicitly~\cite{qua-bir2014}. Note that the adhesive term is
treated explicitly.  Therefore, a single time step requires solving
\begin{align}
  \xx^{N+1} - \Delta t \SS^N \BB^N \xx^{N+1} - 
    \Delta t \SS^N \TT^N \sigma^{N+1} = \xx^N + 
    \Delta t \SS^N \AA^N \xx^N,
  \label{eqn:IMEXEuler}
\end{align}
along with the inextensibility constraint that is discretized as
\begin{align*}
  \xx_s^{N} \cdot \xx_{s}^{N+1} = 1.
\end{align*}
We discretize the vesicles at a set of collocation points, compute the
bending and tension terms with Fourier differentiation, and apply
Alpert quadrature to the logarithmically singular single-layer potential
$\SS$~\cite{alp1999}.  The source and target points of the adhesion
force never coincide since they are always on different vesicles, so the
adhesion force~\eqref{eqn:adhesionForce} is computed with the spectrally
accurate trapezoid rule~\cite{tre-wei2014}.  To control the error and
achieve higher-order accuracy in time, we apply a time adaptive spectral
deferred correction method~\cite{qua-bir2016}.  The SDC method is able
to achieve second-order accuracy by iteratively applying the first-order
method~\eqref{eqn:IMEXEuler}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Shear and Normal Stresses}
Consider a single vesicle $\gamma$ and a target point $\xx$ in the fluid
bulk.  In addition to the velocity $\uu$, we are also interested in
computing the shear stress and normal stresses of each vesicle.
Therefore, we must compute the total stress tensor
\begin{align*}
  T = - p I + \nabla \uu + \nabla \uu^T
\end{align*}
of the single-layer potential~\eqref{eqn:SLP}.  Given a traction jump
$\xxi$ across a vesicle $\gamma$, the velocity, pressure, and stress
tensor at a target point $\xx$ are in the bulk
\begin{align*}
  \uu(\xx) &= \SS_\uu[\xxi](\xx) = \frac{1}{4\pi\mu}\int_{\gamma} \left( 
    -\log \rho + \frac{\rr \otimes \rr}{\rho^2} \right) 
    \xxi ds_\yy, \\
    p(\xx) &= \SS_p[\xxi](\xx) = \frac{1}{2\pi} \int_{\gamma} 
    \frac{\rr \cdot \xxi}{\rho^2} ds_\yy, \\
    T(\xx) &= \SS_T[\xxi](\xx) = -\frac{1}{\pi}\int_{\gamma}
      \frac{\rr \cdot \xxi}{\rho^2} 
      \frac{\rr \otimes \rr}{\rho^2} ds_\yy.
\end{align*}
We require the stress tensor on the vesicle, and the layer potential for
$\SS_T$ has a jump as $\xx$ approaches $\gamma$.  Accounting for the
jump, the stress tensor at $\xx \in \gamma$ is
\begin{align*}
  T(\xx) = \frac{1}{2}(\nn \otimes \xxi) + \frac{1}{2} \left(
    \tt \otimes \left[
    \begin{array}{cc}
      2 t_x t_y & t_y^2 - t_x^2 \\
      t_y^2 - t_x^2 & -2 t_x t_y
    \end{array}
    \right] \xxi \right) + 
  \SS_T[\xxi](\xx).
\end{align*}
With the stress tensor computed for $\xx \in \gamma$, we can compute the
shear stress and normal stress
\begin{align*}
  \tau^\tt = (T \nn) \cdot \tt, \qquad
  \tau^\nn = (T \nn) \cdot \nn.
\end{align*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a quiescent flow} 
\label{sec:qflow}

\subsection{Effects of the adhesion parameters}
\label{subsec:qflow_adhesion_parameters} 
Here we investigate the dynamics and steady state configuration of two
identical vesicles placed next to each other in a quiescent flow.  For a
large reduced area, the two vesicles move toward each other until the
membrane flattens in the adhesion region, as shown in
Figures~\ref{fig:qflow01} and~\ref{fig:qflow02}.  The color coding along
the membrane denotes the membrane tension, which is the lowest in the
adhesion region.

\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.125]{figs/Nrelax2Ves02-rA0p96adR0p4.png}
\caption{Two vesicles interacting with each other via a vdW potential at different strengths in a quiescent viscous fluid. The color coding is the tension along the vesicle.}
\label{fig:qflow01}
\end{figure}

\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.25]{figs/Nrelax2Ves02composite-draining.pdf}
\caption{Adhesion of two vesicles in a quiescent flow.  Only one vesicle
  is illustrated, and the second is a mirror image.  Left panel: The
  steady state configuration for different vdW interaction distances.
  The color coding is the tension along the vesicle.  Right panel:
  Vesicle configurations at different times for different vdW strengths.
  The top plot has the weakest vdW strength and the bottom plot has the
  strongest vdW strength.}
\label{fig:qflow02} 
\end{figure}

% \begin{figure}
% \includegraphics[keepaspectratio=true,scale=0.4]{figs/relax2Ves01g-draining01a.eps}
% \caption{Adhesion dynamics of two vesicles with $\delta = 0.3$. From $t=0.3$ to $t=40$, the time interval $\delta t = 0.3$ between every two neighboring dash-dotted curves.}
% \label{fig:qflow_g-draining01a}
% \end{figure}

% \begin{figure}
% \includegraphics[keepaspectratio=true,scale=0.4]{figs/relax2Ves01j-draining01a.eps}
% \caption{Adhesion dynamics of two vesicles with $\delta = 0.6$. From $t=0.1$ to $t=40$, the time interval $\delta t = 0.1$ between every two neighboring dash-dotted curves.}
% \label{fig:qflow_g-draining01a}
% \end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Effects of reduced area}
\label{sec:qflow_reduced_area} 
Figure~\ref{fig:qflow_reduced_area}

\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.5]{figs/nrelax2Ves02o_rA.png}
\caption{The effect of the reduced area on adhering vesicles in a
quiescent flow.  The parameters of the vdW potential are $\delta = 0.2$
and $\sigma = 0.5$.}
\label{fig:qflow_reduced_area}
\end{figure}

% \begin{figure}
% \includegraphics[keepaspectratio=true,scale=0.4]{figs/relax2Ves01usa.eps}
% \caption{Adhesion dynamics of two vesicles with $\delta = 0.4$ and $\sigma=0.2$. From $t=0.06$ to $t=100$, the time interval $\delta t = 0.06$ between every two neighboring dash-dotted curves.}
% \label{fig:qflow_u-draining}
% \end{figure}

% \begin{figure}
% \includegraphics[keepaspectratio=true,scale=0.4]{figs/relax2Ves01zsa.eps}
% \caption{Adhesion dynamics of two vesicles with $\delta = 0.4$ and $\sigma=0.2$. From $t=1$ to $t=100$, the time interval $\delta t = 1$ 
% between every two neighboring dash-dotted curves.}
% \label{fig:qflow_z-draining}
% \end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in an extensional flow} 
\label{sec:eflow} 
We consider two vesicles suspended in the extensional flow $\uu =
\chi(-x,y)$, where $\chi$ is the extensional rate.  The vesicles are
initially place symmetrically on the $y$ axis so that the background
velocity drives the vesicles towards one another.  We vary the reduced
area and the two vdW parameters and characterize the possible steady
state configurations.  For all the simulations, the length of the
vesicles are fixed, while the area is changed to achieve the desired
reduced area.

\begin{figure}[htp]
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep1.pdf}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep2.pdf}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep3.pdf}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep4.pdf}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep5.pdf}
  \caption{Two vesicles in an extensional flow.  The reduced area is
  $0.40$, the adhesion strength is $1.0$, and the adhesion length scale
is $0.8$, background flow strength is $\chi = 10^{-2}$.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep1.pdf}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep2.pdf}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep3.pdf}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep4.pdf}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep5.pdf}
  \caption{Two vesicles in an extensional flow.  The reduced area is
  $0.90$, the adhesion strength is $1.0$, and the adhesion length scale
is $0.8$, background flow strength is $\chi = 10^{-2}$.}
\end{figure}

\todo[inline]{Phase diagram of different shapes that can be formed}
\todo[inline]{Vary the reduced area, adhesion strength, and adhesion
length scale?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a shear flow}
\label{sec:sflow} 
We consider two vesicles suspended in the shear flow $\uu = \chi(y,0)$,
where $\chi$ is the shear rate.  The vesicles are placed on the $y$ axis
so that the background velocity drives the vesicles towards one another.
In the absence of adhesion, once the vesicles are sufficiently close,
they are deflected to opposite sides of the $y$ axis, and the result is
that the distance between the vesicles goes to infinity.  However, in
the presence of adhesion, is it possible that the adhesive force keeps
the vesicles from separating, resulting in the formation of a {\em
doublet}~\cite{}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Formation of doublets}
\label{sec:sflow_doublet_formation} 
The formation of the doublet depends on four main parameters: the
vesicles' reduced area, the adhesion length scale $\delta$, the adhesion
strength $\sigma$, and the shear rate $\chi$.
Figure~\ref{fig:doublet090} shows the configuration of two vesicles that
have formed a doublet at several instances in time.  The double
structure affects the rheological properties of the flow; in particular,
it increases the effect viscosity as discussed in Section~\ref{}.  In
Figure~\ref{fig:sflow_phase_diagram} (left), we show the minimum
distance between the two vesicles as a function of time for various
adhesion strengths.  The adhesion strength corresponding to the red
curves is less than a critical strength $\sigma_c$ for a doublet to
form.  In contrast, for larger adhesive strengths, doublets are formed
(blue curves).

\begin{figure}[htp]
  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep01.pdf}
  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep02.pdf}
  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep03.pdf}
  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep04.pdf}
  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep05.pdf}
  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep06.pdf}
  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep07.pdf}
  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep08.pdf}
  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep09.pdf}
  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep10.pdf}
  \caption{\label{fig:doublet090} The formation of a doublet in a shear
  flow.  The reduced area is $0.90$, the adhesion strength is $0.7$, the
adhesion length scale is $0.4$, and the shear rate is $\chi=1$.}
\end{figure}

\begin{figure}
  \todo[inline]{Fix and finish right figure}
  \includegraphics[height=0.4\textwidth]{figs/shear_adR4em1Chi1e0_ra-090.pdf}
  \includegraphics[height=0.4\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
  \caption{{\em Left}: Distance between a pair of vesicles in a planar
    shear flow with shear rate $\chi=1$ and adhesion length scale
    $\delta = 0.4$.   The different lines correspond to a linear spacing
    of adhesion strengths ranging from $\sigma=0.1$ and $\sigma=1.0$.
    {\em Right}: Phase diagram of vesicle hydrodynamics in a shear flow.
    At a fixed reduced area $\triangle A=0.90$ and $\delta =0.4$,  the
    critical vdW potential strength $\sigma$ for binding of two vesicles
    in a shear flow depends on the shear rate $\chi$.
  \label{fig:sflow_phase_diagram}}
\end{figure}

%Figures~\ref{fig:sflow_phase_diagram},
%~\ref{fig:sflow_1frames}, and~\ref{fig:sflow_2frames}
%\begin{figure}
%\includegraphics[keepaspectratio=true,scale=0.41]{figs/shear2Ves01a-iD12a.eps}
%\includegraphics[keepaspectratio=true,scale=0.415]{Nshear02_adS_ShearRate01.png}
%% \includegraphics[keepaspectratio=true,scale=0.40]{figs/Nshear02_adS_rA01.png}
%\caption{(a) Dynamics of a pair of vesicles in a planar shear flow with shear rate $\dot\gamma=1$ and vdW length $\delta = 0.4$. (b) Phase diagram of vesicle hydrodynamics in a shear flow. At a fixed reduced area $\triangle A=0.95$ and $\delta =0.4$,  the critical vdW potential strength $\sigma$ for binding of two vesicles in a shear flow depends on the shear rate $\dot\gamma$.}
%\label{fig:sflow_phase_diagram}
%\end{figure}

\begin{figure}
%\includegraphics[keepaspectratio=true,scale=0.215]{figs/shear2Ves03na_frame412.png}
%\includegraphics[keepaspectratio=true,scale=0.215]{figs/shear2Ves03na_frame2565.png}
%\includegraphics[keepaspectratio=true,scale=0.215]{figs/shear2Ves03na_frame3611.png}
%\includegraphics[keepaspectratio=true,scale=0.215]{figs/shear2Ves03na_frame4075.png}
%\includegraphics[keepaspectratio=true,scale=0.215]{figs/shear2Ves03na_frame6501.png}
%\includegraphics[keepaspectratio=true,scale=0.215]{figs/shear2Ves03na_frame6640.png}
\caption{Dynamics of a vesicle doublet in a shear flow with $\delta = 0.4$, $\sigma = 0.7$ and $\triangle A=0.95$.}
\label{fig:sflow_1frames}
\end{figure}

\begin{figure}
%\includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03qa_frame12630.png}
%\includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03qa_frame15128.png}
%\includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03qa_frame18399.png}
%\includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03qa_frame18801.png}
%\includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03qa_frame19018.png}
%\includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03qa_frame21547.png}
\caption{Dynamics of a vesicle doublet in a shear flow with $\delta = 0.4$, $\sigma = 1.0$ and $\triangle A=0.95$.}
\label{fig:sflow_2frames}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Effects of reduced area}
%\label{sec:sflow_reduced_area} 
%Figure~\ref{fig:sflow_ra_D12} and~\ref{fig:sflow_shearVes11frames}
%
%\begin{figure}
%\includegraphics[keepaspectratio=true,scale=0.405]{figs/shear2Ves10-11D12a.eps}
%\includegraphics[keepaspectratio=true,scale=0.405]{figs/shear2Ves10-11tau.png}
%\caption{Dynamics of two vesicles in a shear flow with the adhesion length $\delta = 0.4$ and several varying adhesion strength $\sigma$. Tolerance in length error is $10^{-3}$ and number of points is $256$ on each vesicle.}
%\label{fig:sflow_ra_D12}
%\end{figure}
%
% \begin{figure}
% \includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03etol1em3_frame6026.png}
% \includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03etol1em3_frame6144.png}
% \includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03etol1em3_frame6704.png}\\
% \includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03etol1em3_frame6945.png}
% \includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03etol1em3_frame7463.png}
% \includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03etol1em3_frame7986.png}
% \caption{Dynamics of a vesicle doublet in a shear flow with $\delta = 0.4$, $\sigma = 0.1$ and $\triangle A=0.95$.}
% \label{fig:sflow_shearVes03eframes}
% \end{figure}
%
%\begin{figure}
%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame2287.png}
%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame2927.png}
%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame3855.png}
%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame4072.png}
%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame4108.png}
%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame4281.png}
%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame4676.png}
%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame5001.png}
%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame5070.png}
%\caption{Dynamics of a vesicle doublet in a shear flow with $\delta = 0.4$, $\sigma = 0.1$ and $\triangle A=0.5$.}
%\label{fig:sflow_shearVes11frames}
%\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Effective viscosity of a doublet}
\todo[inline]{Effect of effective viscosity with respect to the reduced
area and adhesion model}
\todo[inline]{Compare a single vesicle as per Misbah with doublets}
\todo[inline]{Bryan can start this section}

Here we investigate rheology of suspensions by computing the effective
viscosity. The effective viscosity is defined as the viscosity of a
homogeneous Newtonian fluid with the same energy dissipation per
macroscopic element of fluid.  In a simple shear flow, the ambient
velocity field is given by $\uu(\xx) = (\chi y,0)$, where $\chi$ is the
shear rate.  In dilute suspensions, the interaction between vesicles can
be ignored, and the intrinsic viscosity is
\begin{align*}
  [\mu]:= \frac{\mu_{\mathrm{eff}} - \mu_0}{\phi \mu_0} = 
  \frac{1}{\chi \mu_0 T} \int_{T_i}^{T_e} 
  \langle \sigma_{12} \rangle dt,
\end{align*}
where
\begin{align*}
  \langle \sigma \rangle = \frac{1}{|\omega|} \int_{\gamma}
    \xxi \otimes \xx ds.
\end{align*}
Here, $[\mu]$ is the intrinsic viscosity, $|phi$ is the area fraction of
vesicles, $\sigma$ is the stress due to the vesicles, and $\langle \cdot
\rangle$ is the spatial average.  For dilute suspensions of rigid
bodies, the intrinsic viscosity was derived by Eienstein~\cite{}, and it
is given by
\begin{align*}
  something.
\end{align*}
For vesicles, the intrinsic viscosity was derived by Misbah~\cite{}, and
it is given by
\begin{align*}
  something.
\end{align*}

When adhesion is present, the formation of doublets has a significant
effect on the effective viscosity.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\todo[inline]{Concluding remarks}

Future work includes three dimensional simulations, viscosity contrast,
confined suspensions, and dense suspensions.

Recently Liu {\it et al.} \cite{LiuChuNewbyRead2018_bioRxiv} used immersed boundary simulations to show that, 
at a separation distance of tens of nanometers,
the thin film between the two membranes facilitate the coupling between membranes via strong hydrodynamic interactions. In particular they demonstrate
numerically that the fluctuation in one membrane is highly correlated to the other membrane without any physical contact. It is not clear how thermal fluctuations may affect the hydrodynamics of vesicles under adhesion. For example, does the fluctuating hydrodynamics in the thin film between two vesicles enhance adhesion to keep vesicles bound under linear flows?

\begin{appendices}
\section{Adhesion Force}
\label{sec:appendixA}
Consider a suspension of two vesicles $\gamma_1$ and $\gamma_2$
parameterized as $\xx_1(s)$ and $\xx_2(s)$, respectively, with $s \in
[0,1]$.  Here $s$ is the arclength, and we have assumed, without loss of
generality, that both vesicles have length one.  We use the van der
Waals potential
\begin{align*}
  \phi(z) = \sigma\left(\frac{\delta}{z}\right)^2 \left[ 
    \left(\frac{\delta}{z}\right)^2 - 2 \right],
\end{align*}
where $z$ is the distance between two points.  Then, we define the total
adhesive energy on $\gamma_1$ to be
\begin{align*}
  U_1 = \int_{\gamma_1} \int_{\gamma_2} \phi(\|\xx_1 - \xx_2\|) 
    ds_{\xx_2} ds_{\xx_1}
\end{align*}
Perturbing $\xx_1$ to $\tilde{\xx}_1 = \xx_1 +  \delta \xx_1$, results
in a new vesicle $\tilde{\gamma}_1$, and the perturbed adhesive energy
is
\begin{align*}
  \widetilde{U}_1 = \int_{\tilde{\gamma}_1} \int_{\gamma_2}
  \phi(\|\tilde{\xx}_1 - \xx_2\|) ds_{\xx_2} ds_{\tilde{\xx}_1},
\end{align*}
and the change in the energy is
\begin{align*}
  \delta U_1 = \int_{\tilde{\gamma}_1} \int_{\gamma_2}
  \phi(\|\tilde{\xx}_1 - \xx_2\|) ds_{\xx_2} ds_{\tilde{\xx}_1} - 
  \int_{\gamma_1} \int_{\gamma_2} \phi(\|\xx_1 - \xx_2\|) 
  ds_{\xx_2} ds_{\xx_1}.
\end{align*}

We now decompose the perturbation into normal and tangential components
as $\delta \xx_1 = \epsilon \yy(s) = \epsilon(u\tt + v\nn)$. The
perturbed arclength term, to leading order, is
\begin{align*}
  \|\tilde{\xx}'_1\| \approx 1 + \epsilon(u_s + \nu\kappa),
\end{align*}
where $\kappa$ is the curvature.  To leading order, inextensible
perturbations satisfy $u_s + \kappa v = 0$, so the arclength term of
$\gamma_1$ and $\tilde{\gamma}_1$ are identical to leading order.
Therefore,
\begin{align*}
  \delta U_1 &= \int_{\gamma_1} \int_{\gamma_2} \left(
  \phi(\|\xx_1 + \epsilon \yy  - \xx_2\|) - \phi(\|\xx_1 - \xx_2\|)
  \right) ds_{\xx_2} ds_{\xx_1} \\
  &\approx \epsilon \int_{\gamma_1} \int_{\gamma_2}
  \nabla \phi (\|\xx_1 - \xx_2\|) \cdot \yy ds_{\xx_2} ds_{\xx_1}
\end{align*}
and the adhesive force applied by vesicle 2 on vesicle 1 is
\begin{align*}
  \int_{\gamma_2}\nabla \phi(\|\xx_1 - \xx_2\|)ds_{\xx_2} = 
  -4 \sigma \delta^2 \int_{\gamma_2}
  \frac{\xx_1 - \xx_2}{\|\xx_1 - \xx_2\|^2} 
  \left(\delta^2 - \|\xx_1 - \xx_2\|^2 \right) ds_{\xx_2}.
\end{align*}
A similar expression holds for the adhesive force applied by vesicle 1
on vesicle 2, and equation~\eqref{eqn:adhesionForce} gives the adhesive
force for a suspension of $M$ vesicles.

\section{Small Deformation Limit}
\label{sec:appendixB}
\todo[inline]{Used to validate the code/results}

\end{appendices}

\bibliography{refs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{\label{sec:level2}Second-level heading: Formatting}
%
%This file may be formatted in either the \texttt{preprint} or
%\texttt{reprint} style. \texttt{reprint} format mimics final journal output. 
%Either format may be used for submission purposes. \texttt{letter} sized paper should
%be used when submitting to APS journals.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsubsection{Wide text (A level-3 head)}
%The \texttt{widetext} environment will make the text the width of the
%full page, as on page~\pageref{eq:wideeq}. (Note the use the
%\verb+\pageref{#1}+ command to refer to the page number.) 
%\paragraph{Note (Fourth-level head is run in)}
%The width-changing commands only take effect in two-column formatting. 
%There is no effect if text is in a single column.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{\label{sec:citeref}Citations and References}
%
%
%
%A citation in text uses the command \verb+\cite{#1}+ or
%\verb+\onlinecite{#1}+ and refers to an entry in the bibliography. 
%An entry in the bibliography is a reference to another document.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsubsection{Citations}

%Because REV\TeX\ uses the \verb+natbib+ package of Patrick Daly, 
%the entire repertoire of commands in that package are available for your document;
%see the \verb+natbib+ documentation for further details. Please note that
%REV\TeX\ requires version 8.31a or later of \verb+natbib+.
%
%\paragraph{Syntax}
%The argument of \verb+\cite+ may be a single \emph{key}, 
%or may consist of a comma-separated list of keys.
%The citation \emph{key} may contain 
%letters, numbers, the dash (-) character, or the period (.) character. 
%New with natbib 8.3 is an extension to the syntax that allows for 
%a star (*) form and two optional arguments on the citation key itself.
%The syntax of the \verb+\cite+ command is thus (informally stated)
%\begin{quotation}\flushleft\leftskip1em
%\verb+\cite+ \verb+{+ \emph{key} \verb+}+, or\\
%\verb+\cite+ \verb+{+ \emph{optarg+key} \verb+}+, or\\
%\verb+\cite+ \verb+{+ \emph{optarg+key} \verb+,+ \emph{optarg+key}\ldots \verb+}+,
%\end{quotation}\noindent
%where \emph{optarg+key} signifies 
%\begin{quotation}\flushleft\leftskip1em
%\emph{key}, or\\
%\texttt{*}\emph{key}, or\\
%\texttt{[}\emph{pre}\texttt{]}\emph{key}, or\\
%\texttt{[}\emph{pre}\texttt{]}\texttt{[}\emph{post}\texttt{]}\emph{key}, or even\\
%\texttt{*}\texttt{[}\emph{pre}\texttt{]}\texttt{[}\emph{post}\texttt{]}\emph{key}.
%\end{quotation}\noindent
%where \emph{pre} and \emph{post} is whatever text you wish to place 
%at the beginning and end, respectively, of the bibliographic reference
%(see Ref.~[\onlinecite{witten2001}] and the two under Ref.~[\onlinecite{feyn54}]).
%(Keep in mind that no automatic space or punctuation is applied.)
%It is highly recommended that you put the entire \emph{pre} or \emph{post} portion 
%within its own set of braces, for example: 
%\verb+\cite+ \verb+{+ \texttt{[} \verb+{+\emph{text}\verb+}+\texttt{]}\emph{key}\verb+}+.
%The extra set of braces will keep \LaTeX\ out of trouble if your \emph{text} contains the comma (,) character.
%
%The star (*) modifier to the \emph{key} signifies that the reference is to be 
%merged with the previous reference into a single bibliographic entry, 
%a common idiom in APS and AIP articles (see below, Ref.~[\onlinecite{epr}]). 
%When references are merged in this way, they are separated by a semicolon instead of 
%the period (full stop) that would otherwise appear.
%
%\paragraph{Eliding repeated information}
%When a reference is merged, some of its fields may be elided: for example, 
%when the author matches that of the previous reference, it is omitted. 
%If both author and journal match, both are omitted.
%If the journal matches, but the author does not, the journal is replaced by \emph{ibid.},
%as exemplified by Ref.~[\onlinecite{epr}]. 
%These rules embody common editorial practice in APS and AIP journals and will only
%be in effect if the markup features of the APS and AIP Bib\TeX\ styles is employed.
%
%\paragraph{The options of the cite command itself}
%Please note that optional arguments to the \emph{key} change the reference in the bibliography, 
%not the citation in the body of the document. 
%For the latter, use the optional arguments of the \verb+\cite+ command itself:
%\verb+\cite+ \texttt{*}\allowbreak
%\texttt{[}\emph{pre-cite}\texttt{]}\allowbreak
%\texttt{[}\emph{post-cite}\texttt{]}\allowbreak
%\verb+{+\emph{key-list}\verb+}+.

\end{document}
%
% ****** End of file apssamp.tex ******

### 2018-12-14 vesicle_code/examples/shear2Ves.m

@@ -3,10 +3,10 @@ clear all; clc
 fprintf('Two elliptical vesicles in a shear flow.\n');
 
 % Physics parameters
-prams.N = 128;               % points per vesicle
+prams.N = 64;               % points per vesicle
 prams.nv = 2;               % number of vesicles
 prams.T = 100;               % time horizon (two tumbling)
-prams.m = 2000;             % number of time steps
+prams.m = 200;             % number of time steps
 prams.kappa = [1e-1 1e-1];         % bending coefficient
 prams.viscCant = [1 1];         % viscosity contrast
 options.farField = 'shear'; % background velocity
@@ -28,7 +28,7 @@ prams.errorTol = 1;
 options.correctShape = false;
 options.adhesion = true;
 prams.adRange = 4e-1;
-prams.adStrength = 0.7;
+prams.adStrength = 1;
 
 % TIME ADAPTIVITY (parameters for new implementation)
 options.timeAdap = true;
@@ -65,7 +65,7 @@ oc = curve;
 centerx = [-1.5 1.5];
 centery = zeros(1,2);
 ang = pi/2*ones(2,1);
-ra = 0.50;
+ra = 0.65;
 scale = 1/2*sqrt(ra);
 X = oc.initConfig(prams.N,'nv',prams.nv,...
     'reducedArea',ra,...

### 2018-12-17 vesicle_code/docs/adhesion/adhesion.tex
adding new images

@@
 \begin{figure}[htp]
-  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep01.pdf}
-  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep02.pdf}
-  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep03.pdf}
-  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep04.pdf}
-  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep05.pdf}
-  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep06.pdf}
-  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep07.pdf}
-  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep08.pdf}
-  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep09.pdf}
-  \includegraphics[width=0.19\textwidth]{figs/shear_adR4em1adS7em1Chi1e0_ra090_timestep10.pdf}
+  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image01.png}
+  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image02.png}
+  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image03.png}
+  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image04.png}
+  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image05.png}
+  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image06.png}
+  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image07.png}
+  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image08.png}
   \caption{\label{fig:doublet090} The formation of a doublet in a shear
-  flow.  The reduced area is $0.90$, the adhesion strength is $0.7$, the
-adhesion length scale is $0.4$, and the shear rate is $\chi=1$.}
+  flow.  The reduced area is $0.90$, the Hamaker contsant is $\sigma=0.7$, the
+adhesion length scale is $\delta = 0.4$, and the shear rate is $\chi=0.5$.}
 \end{figure}
@@
 \begin{figure}
-  \todo[inline]{Fix and finish right figure}
   \includegraphics[height=0.4\textwidth]{figs/shear_adR4em1Chi1e0_ra-090.pdf}

### 2018-12-18 vesicle_code/docs/adhesion/adhesion.tex
adding new figure

@@
 \end{align*}
+\begin{figure}[htp]
+  \includegraphics[scale=1]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
+  \caption{\label{fig:shearIntrinsicViscosity} The intrinsic viscosity
+  of a tank treading vesicle (blue) and a doublet (red).  The shear rate
+is $\chi = 0.5$, the Hamaker constant is $\sigma = 0.7$, and the
+adhesion length scale is $\delta = 0.4$.  The length of the vesicles at
+each of the reduced areas is fixed, while the area changes with
+differing reduced areas.}
+\end{figure}
 

### 2018-12-18 vesicle_code/examples/output/makeImages.m

@@ -4,11 +4,6 @@ set(0,'DefaultAxesFontSize',22)
 irate = 10; % controls the speed of the visualization
 
 if 0
-  file = 'shear1VesData.bin';
-  ax = [-8 8 -5 5];
-  options.confined = false;
-end
-if 0
 %  file = 'extensional2VesData.bin';
   file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR1em1adS1e0_ra040/extensional2VesData.bin';
   ax = [-4 4 -2 2];
@@ -25,8 +20,7 @@ if 0
   options.confined = false;
 end
 if 0
-%  file = 'relaxation2VesData.bin';
-  file = '~/projects/brinkman/vesicle_code/results/shear2Ves/adR5em1adS1em1Chi1e0_ra090/shear2VesData.bin';
+  file = 'relaxation2VesData.bin';
 %  file = '~/presentations/2018/lifeSciences2018/results/relaxation/RA65_Range8_Strength2/relaxation2VesData.bin';
   ax = [-2 2 -3 3];
   options.confined = false;
@@ -41,9 +35,14 @@ if 0
   ax = [-2 2 -2 2];
   options.confined = false;
 end
+if 0
+  file = 'shear1VesAData.bin.run1';
+  ax = [-8 8 -5 5];
+  options.confined = false;
+end
 if 1
-%  file = 'shear2VesEData.bin.run2';
-  file = '~/projects/brinkman/vesicle_code/results/shear2Ves/adR4em1adS4em1Chi5em1_ra090/shear2VesData.bin';
+  file = 'shear2VesCData.bin.run1';
+%  file = '~/projects/brinkman/vesicle_code/results/shear2Ves/adR4em1adS7em1Chi5em1_ra090/shear2VesData.bin';
   ax = [-10 10 -3 3];
   options.confined = false;
 end
@@ -76,9 +75,10 @@ for k = istart:irate:iend
   vec1 = [xx(:,:);xx(1,:)];
   vec2 = [yy(:,:);yy(1,:)];
   if 1
+    clf
     plot(vec1,vec2,'r','linewidth',3)
-%    hold on
-%    plot(vec1(1,:),vec2(1,:),'b.','markersize',20)
+    hold on;
+    plot(vec1(1,:),vec2(1,:),'b.','markersize',20)
     if options.confined
       vec1 = [wallx(:,:);wallx(1,:)];
       vec2 = [wally(:,:);wally(1,:)];

### 2018-12-18 vesicle_code/docs/adhesion/adhesion.tex
worked on shear example

@@
 
+\newpage % so that the figures are more organized writing the paper
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\todo[inline]{Phase diagram of different shapes that can be formed}
-\todo[inline]{Vary the reduced area, adhesion strength, and adhesion
-length scale?}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Formation of doublets}
-\label{sec:sflow_doublet_formation} 
 The formation of the doublet depends on four main parameters: the
@@
 Figure~\ref{fig:doublet090} shows the configuration of two vesicles that
-have formed a doublet at several instances in time.  The double
-structure affects the rheological properties of the flow; in particular,
-it increases the effect viscosity as discussed in Section~\ref{}.  In
+have formed a doublet at several instances in time.  In
 Figure~\ref{fig:sflow_phase_diagram} (left), we show the minimum
@@
   \caption{{\em Left}: Distance between a pair of vesicles in a planar
-    shear flow with shear rate $\chi=1$ and adhesion length scale
+    shear flow with shear rate $\chi=0.5$ and adhesion length scale
     $\delta = 0.4$.   The different lines correspond to a linear spacing
@@
 
-\begin{figure}
-%\includegraphics[keepaspectratio=true,scale=0.215]{figs/shear2Ves03na_frame412.png}
-%\includegraphics[keepaspectratio=true,scale=0.215]{figs/shear2Ves03na_frame2565.png}
-%\includegraphics[keepaspectratio=true,scale=0.215]{figs/shear2Ves03na_frame3611.png}
-%\includegraphics[keepaspectratio=true,scale=0.215]{figs/shear2Ves03na_frame4075.png}
-%\includegraphics[keepaspectratio=true,scale=0.215]{figs/shear2Ves03na_frame6501.png}
-%\includegraphics[keepaspectratio=true,scale=0.215]{figs/shear2Ves03na_frame6640.png}
-\caption{Dynamics of a vesicle doublet in a shear flow with $\delta = 0.4$, $\sigma = 0.7$ and $\triangle A=0.95$.}
-\label{fig:sflow_1frames}
-\end{figure}
-
-\begin{figure}
-%\includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03qa_frame12630.png}
-%\includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03qa_frame15128.png}
-%\includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03qa_frame18399.png}
-%\includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03qa_frame18801.png}
-%\includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03qa_frame19018.png}
-%\includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03qa_frame21547.png}
-\caption{Dynamics of a vesicle doublet in a shear flow with $\delta = 0.4$, $\sigma = 1.0$ and $\triangle A=0.95$.}
-\label{fig:sflow_2frames}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Effects of reduced area}
-%\label{sec:sflow_reduced_area} 
-%Figure~\ref{fig:sflow_ra_D12} and~\ref{fig:sflow_shearVes11frames}
-%
-%\begin{figure}
-%\includegraphics[keepaspectratio=true,scale=0.405]{figs/shear2Ves10-11D12a.eps}
-%\includegraphics[keepaspectratio=true,scale=0.405]{figs/shear2Ves10-11tau.png}
-%\caption{Dynamics of two vesicles in a shear flow with the adhesion length $\delta = 0.4$ and several varying adhesion strength $\sigma$.
-Tolerance in length error is $10^{-3}$ and number of points is $256$ on each vesicle.}
-%\label{fig:sflow_ra_D12}
-%\end{figure}
-%
-% \begin{figure}
-% \includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03etol1em3_frame6026.png}
-% \includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03etol1em3_frame6144.png}
-% \includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03etol1em3_frame6704.png}\\
-% \includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03etol1em3_frame6945.png}
-% \includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03etol1em3_frame7463.png}
-% \includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03etol1em3_frame7986.png}
-% \caption{Dynamics of a vesicle doublet in a shear flow with $\delta = 0.4$, $\sigma = 0.1$ and $\triangle A=0.95$.}
-% \label{fig:sflow_shearVes03eframes}
-% \end{figure}
-%
-%\begin{figure}
-%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame2287.png}
-%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame2927.png}
-%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame3855.png}
-%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame4072.png}
-%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame4108.png}
-%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame4281.png}
-%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame4676.png}
-%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame5001.png}
-%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame5070.png}
-%\caption{Dynamics of a vesicle doublet in a shear flow with $\delta = 0.4$, $\sigma = 0.1$ and $\triangle A=0.5$.}
-%\label{fig:sflow_shearVes11frames}
-%\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Effective viscosity of a doublet}
-\todo[inline]{Effect of effective viscosity with respect to the reduced
-area and adhesion model}
-\todo[inline]{Compare a single vesicle as per Misbah with doublets}
-\todo[inline]{Bryan can start this section}
-
-Here we investigate rheology of suspensions by computing the effective
-viscosity. The effective viscosity is defined as the viscosity of a
-homogeneous Newtonian fluid with the same energy dissipation per
-macroscopic element of fluid.  In a simple shear flow, the ambient
-velocity field is given by $\uu(\xx) = (\chi y,0)$, where $\chi$ is the
-shear rate.  In dilute suspensions, the interaction between vesicles can
-be ignored, and the intrinsic viscosity is
+We investigate rheology of suspensions by computing the effective
+viscosity of a doublet and compare it to the effective viscosity of a
+single tank-treading vesicle. The effective viscosity is defined as the
+viscosity of a homogeneous Newtonian fluid with the same energy
+dissipation per macroscopic element of fluid.  In a simple shear flow,
+the ambient velocity field is given by $\uu(\xx) = \chi(y,0)$, where
+$\chi$ is the shear rate, and the intrinsic viscosity is
 \begin{align*}
@@
 vesicles, $\sigma$ is the stress due to the vesicles, and $\langle \cdot
-\rangle$ is the spatial average.  For dilute suspensions of rigid
-bodies, the intrinsic viscosity was derived by Eienstein~\cite{}, and it
-is given by
-\begin{align*}
-  something.
-\end{align*}
-For vesicles, the intrinsic viscosity was derived by Misbah~\cite{}, and
-it is given by
-\begin{align*}
-  something.
-\end{align*}
+\rangle$ is the spatial average.
+
 \begin{figure}[htp]
@@
 \end{figure}
-
-When adhesion is present, the formation of doublets has a significant
-effect on the effective viscosity.
 

### 2018-12-18 vesicle_code/examples/output/makeImages.m

@@ -1,11 +1,11 @@
 addpath ../../src
 set(0,'DefaultAxesFontSize',22)
 
-irate = 10; % controls the speed of the visualization
+irate = 100; % controls the speed of the visualization
 
-if 0
+if 1
 %  file = 'extensional2VesData.bin';
-  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR1em1adS1e0_ra040/extensional2VesData.bin';
+  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR2em1adS1e0_ra040/extensional2VesData.bin';
   ax = [-4 4 -2 2];
   options.confined = false;
 end
@@ -40,7 +40,7 @@ if 0
   ax = [-8 8 -5 5];
   options.confined = false;
 end
-if 1
+if 0
   file = 'shear2VesCData.bin.run1';
 %  file = '~/projects/brinkman/vesicle_code/results/shear2Ves/adR4em1adS7em1Chi5em1_ra090/shear2VesData.bin';
   ax = [-10 10 -3 3];

### 2018-12-25 vesicle_code/docs/adhesion/adhesion.tex
fixed bug in adhesion energy term

@@
 \end{align*}
-Here, $[\mu]$ is the intrinsic viscosity, $|phi$ is the area fraction of
+Here, $[\mu]$ is the intrinsic viscosity, $\phi$ is the area fraction of
 vesicles, $\sigma$ is the stress due to the vesicles, and $\langle \cdot
@@
 \end{figure}
+\todo[inline]{Do the smaller reduced area doublets since the intrinsic
+viscosity seemed to increase as the reduced area was decresed further}
+\todo[inline]{Decompose the red curve as the intrinsic viscosity due to
+adhesion and due to the bending/tension}
 
@@
   -4 \sigma \delta^2 \int_{\gamma_2}
-  \frac{\xx_1 - \xx_2}{\|\xx_1 - \xx_2\|^2} 
+  \frac{\xx_1 - \xx_2}{\|\xx_1 - \xx_2\|^6} 
   \left(\delta^2 - \|\xx_1 - \xx_2\|^2 \right) ds_{\xx_2}.

### 2018-12-28 vesicle_code/docs/adhesion/adhesion.tex
starting extensional section

@@
 \chi(-x,y)$, where $\chi$ is the extensional rate.  The vesicles are
-initially place symmetrically on the $y$ axis so that the background
-velocity drives the vesicles towards one another.  We vary the reduced
-area and the two vdW parameters and characterize the possible steady
-state configurations.  For all the simulations, the length of the
+initially placed symmetrically on the $x$ axis in a quiescent flow
+($\chi = 0$).  Once they reach steady-state, the extensional background
+flow is started.  We use this example to characterize the required
+extensional rate to overcome the adhesive forces at for vesicles with
+different reduced areas.  For all the simulations, the length of the
 vesicles are fixed, while the area is changed to achieve the desired
@@
 
-\begin{figure}[htp]
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep1.pdf}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep2.pdf}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep3.pdf}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep4.pdf}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep5.pdf}
-  \caption{Two vesicles in an extensional flow.  The reduced area is
-  $0.40$, the adhesion strength is $1.0$, and the adhesion length scale
-is $0.8$, background flow strength is $\chi = 10^{-2}$.}
-\end{figure}
+%We consider two vesicles suspended in the extensional flow $\uu =
+%\chi(-x,y)$, where $\chi$ is the extensional rate.  The vesicles are
+%initially place symmetrically on the $y$ axis so that the background
+%velocity drives the vesicles towards one another.  We vary the reduced
+%area and the two vdW parameters and characterize the possible steady
+%state configurations.  For all the simulations, the length of the
+%vesicles are fixed, while the area is changed to achieve the desired
+%reduced area.
+%
+%\begin{figure}[htp]
+%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep1.pdf}
+%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep2.pdf}
+%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep3.pdf}
+%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep4.pdf}
+%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep5.pdf}
+%  \caption{Two vesicles in an extensional flow.  The reduced area is
+%  $0.40$, the adhesion strength is $1.0$, and the adhesion length scale
+%is $0.8$, background flow strength is $\chi = 10^{-2}$.}
+%\end{figure}
+%
+%\begin{figure}[htp]
+%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep1.pdf}
+%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep2.pdf}
+%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep3.pdf}
+%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep4.pdf}
+%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep5.pdf}
+%  \caption{Two vesicles in an extensional flow.  The reduced area is
+%  $0.90$, the adhesion strength is $1.0$, and the adhesion length scale
+%is $0.8$, background flow strength is $\chi = 10^{-2}$.}
+%\end{figure}
 
-\begin{figure}[htp]
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep1.pdf}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep2.pdf}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep3.pdf}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep4.pdf}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep5.pdf}
-  \caption{Two vesicles in an extensional flow.  The reduced area is
-  $0.90$, the adhesion strength is $1.0$, and the adhesion length scale
-is $0.8$, background flow strength is $\chi = 10^{-2}$.}
-\end{figure}
-
+\newpage % so that the figures are more organized writing the paper
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Recently Liu {\it et al.} \cite{LiuChuNewbyRead2018_bioRxiv} used immersed boundary simulations to show that, 
-at a separation distance of tens of nanometers,
-the thin film between the two membranes facilitate the coupling between membranes via strong hydrodynamic interactions. In particular they demonstrate
-numerically that the fluctuation in one membrane is highly correlated to the other membrane without any physical contact.
-It is not clear how thermal fluctuations may affect the hydrodynamics of vesicles under adhesion.
-For example, does the fluctuating hydrodynamics in the thin film between two vesicles enhance adhesion to keep vesicles bound under linear flows?
+Recently Liu {\it et al.} \cite{LiuChuNewbyRead2018_bioRxiv} used
+immersed boundary simulations to show that, at a separation distance of
+tens of nanometers, the thin film between the two membranes facilitate
+the coupling between membranes via strong hydrodynamic interactions. In
+particular they demonstrate numerically that the fluctuation in one
+membrane is highly correlated to the other membrane without any physical
+contact. It is not clear how thermal fluctuations may affect the
+hydrodynamics of vesicles under adhesion. For example, does the
+fluctuating hydrodynamics in the thin film between two vesicles enhance
+adhesion to keep vesicles bound under linear flows?
 

### 2018-12-28 vesicle_code/examples/output/makeImages.m

@@ -1,11 +1,11 @@
 addpath ../../src
 set(0,'DefaultAxesFontSize',22)
 
-irate = 100; % controls the speed of the visualization
+irate = 10; % controls the speed of the visualization
 
 if 1
   file = 'extensional2VesData.bin';
-%  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi1em1_ra080/extensional2VesData.bin';
+  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi5em2_ra080/extensional2VesData.bin';
   ax = [-4 4 -5 5];
   options.confined = false;
 end

### 2018-12-28 vesicle_code/docs/adhesion/adhesion.tex
adding extensional results

@@
 
+\begin{figure}[htp]
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image01.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image02.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image03.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image04.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image05.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image06.png}
+  \caption{Two vesicles in an extensional flow.  The reduced area is
+  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
+is $0.4$, extensional rate is $\chi = 0.05$.}
+\end{figure}
+
+\begin{figure}[htp]
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi9em2_ra080_image01.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi9em2_ra080_image02.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi9em2_ra080_image03.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi9em2_ra080_image04.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi9em2_ra080_image05.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi9em2_ra080_image06.png}
+  \caption{Two vesicles in an extensional flow.  The reduced area is
+  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
+is $0.4$, extensional rate is $\chi = 0.09$.}
+\end{figure}
+
+\begin{figure}[htp]
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image06.png}
+  \caption{Two vesicles in an extensional flow.  The reduced area is
+  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
+is $0.4$, extensional rate is $\chi = 0.1$.}
+\end{figure}
+
+\begin{figure}[htp]
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image01.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image02.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image03.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image04.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image05.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image06.png}
+  \caption{Two vesicles in an extensional flow.  The reduced area is
+  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
+is $0.4$, extensional rate is $\chi = 0.11$.}
+\end{figure}
+
 %We consider two vesicles suspended in the extensional flow $\uu =

### 2018-12-28 vesicle_code/examples/output/makeImages.m

@@ -5,7 +5,7 @@ irate = 10; % controls the speed of the visualization
 
 if 1
   file = 'extensional2VesData.bin';
-  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi5em2_ra080/extensional2VesData.bin';
+%  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi5em2_ra080/extensional2VesData.bin';
   ax = [-4 4 -5 5];
   options.confined = false;
 end

### 2018-12-28 vesicle_code/docs/adhesion/adhesion.tex
changes on relaxation, introduction, and refs

--- 2018-12-25 vesicle_code/docs/adhesion/adhesion.tex
@@
 \section{Introduction}
-Vesicles (self-enclosed phopolipid bilayer membranes) have been widely utilized
-as simple cell mimics in biomedical and material engineering \cite{}. The ever expanding applications of vesicles have encouraged extensive investigations on vesicle hydrodynamics
-and electrohydrodynamics: Theoretical investigations are often limited to small-deformation of a nearly spherical (circular) vesicle in 3D (2D) \cite{Barthes-BieselRallison1981_JFM,Misbah2006_PRL,Vlahovska2007_PRE,Finken2008_EPL}.
-Various numerical schemes have been designed and deployed to simulate the dynamics of many vesicles \cite{BagchiJohoson2005_JBE,Biben2005_EJP,Veerapaneni2009_JCP,SeolHuKimLai2016_JCP}.
-Careful experiments on vesicles under different flowing conditions or forcing configurations have been carried out \cite{MaderVitkova2006_EurPhysJE, Abkarian2008_SoftMatt}.
+Vesicles (self-enclosed phopholipid bilayer membranes) have been widely utilized
+as simple model membranes for cell mimics in biomedical and material engineering \cite{}. 
+%
+The ever expanding applications of vesicles have encouraged extensive investigations on vesicle hydrodynamics
+and electrohydrodynamics.
+Theoretical investigations are conducted to study the small-deformation or spheroidal dynamics of a nearly spherical (circular) vesicle in a fluid flow or under an external forcing \cite{Barthes-BieselRallison1981_JFM,Misbah2006_PRL,Vlahovska2007_PRE,Finken2008_EPL,ZhangZahnTanLin2013_PoF,Nganguia2013_PRE}.
+Various numerical schemes have been designed and deployed to simulate the hydrodynamics of many vesicles \cite{BagchiJohoson2005_JBE,Biben2005_EJP,Veerapaneni2009_JCP,SeolHuKimLai2016_JCP}.  
+Experiments are performed to study vesicle hydrodynamics under various flowing conditions or forcing configurations \cite{MaderVitkova2006_EurPhysJE, Abkarian2008_SoftMatt,DahlNarsimhanGouveia2016_SoftMatt}.
 In a vesicle suspension under
@@
 enhancing the suspension viscosity in the direction of alignment.
-In numerical simulations, it is often assumed that vesicles do not get closer than a few nano meters, where the
-Van der Waals interaction between lipid bilayers becomes important \cite{EvansMetcalfe1984_BJ,Book_PhysicalBasisCellAdhesion,Book_IntermolecularSurfaceForces}.
-For giant unilamellar vesicles (GUVs) this assumption is reasonable, however for vesicles of size $\sim 100$ nm the van der Waals
-interactions between vesicles are important and may significantly affect their shape in the absence of any external forcing \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.
-In this paper we use boundary integral simulations to investigate
-how such Van der Waals interactions between sub-micron vesicles may affect their hydrodynamics and consequently the rheology 
-of their suspension in the dilute limit.
+In numerical simulations of vesicle suspension, it is often assumed that lubrication layer between vesicle membranes act to keep
+membrane-membrane interaction (such as Van der Waals interaction) negligible \cite{BagchiJohoson2005_JBE,Veerapaneni2009_JCP}.
 
-Due to the nature of amphiphilic molecules (a dipole in the hydrophilic head), the adhesive interaction of a amphiphilic bilayer membrane 
-with either a solid (such as a glass substrate or a nano particle) or another bilayer 
-plays a central role in many biomedical, biological and biophysical processes.
-Vesicle adhesion is an essential step for membrane fusion/fission in many
-processes such as, e.g., endocytosis and exocytosis, that is, the
-transport of small vesicles through large membrane surfaces. 
+However the amphiphilic natures of lipid molecules (a hydrophobic tail and a hydrophilic head with an electric dipole) complicate the
+interactions between a lipid bilayer membrane and a solid (such as a glass substrate or a nano particle) or another bilayer membrane \cite{EvansMetcalfe1984_BJ,Book_PhysicalBasisCellAdhesion,Book_IntermolecularSurfaceForces}.
+Studies confirmed that such interaction potential inevitably consists of a long-range attraction component and a short-range repulsion component 
+\cite{Book_IntermolecularSurfaceForces}. Such interactions leads to adhesion at the separation distance that minimizes the
+interaction potential \cite{Book_IntermolecularSurfaceForces}, and are essential in many biomedical, biological and biophysical processes.
+For example, vesicle adhesion
+is essential for membrane fusion/fission in endocytosis and exocytosis, the transport of small
+vesicles through membrane surfaces.
+
+%
 Adhesion between a vesicle and a substrate has been extensively studied, with 
@@
 
-\subsection{Effects of the adhesion parameters}
+When two vesicles move towards each other under a constant force $F$ without any external fluid flow, the height  $(h)$ of the lubrication film between two vesicles follows the
+draining dynamics \cite{RamachandranLeal2010_PoF}
+\begin{equation}
+\label{eq:dhdt}
+\frac{d h}{dt} \sim \frac{K_a^{2/3} F^{1/3}}{\mu R_0^{10/3}} h^3,
+\end{equation}
+where $K_a$ is the area expansion modulus, $\mu$ is the viscosity of exterior fluid, $R_0$ is the radius of the undeformed vesicle.
+When $F$ is a constant (independent of separation distance $h$ and/or time $t$), the above scaling can give variation of $h$ versus $t$ by integrating the above equation
+\begin{equation}
+t \sim \frac{\mu R_0^{10/3}}{K_a^{2/3} F^{1/3}}\frac{1}{2 h^2} \bigg|^{h(t)}_{h(0)},
+\end{equation}
+where $h(0)$ is the vesicle separation at $t=0$.
+We note that $F< (>) 0$ for an attractive  (repulsive) force and consequently $h(t)$ decreases (increases) from  the initial separation distance $h(0)$. 
+When the force is attractive, $h$ decreases monotonically and $t$ in the above
+equation is the
+draining time that diverges as $h\rightarrow 0$.
+%Similarly $F>0$ for a repulsive force and consequently $h(t) > h(0)$.
+
+When the force on each vesicle is a function of separation distance $h$ of the form (with an integer $m\ge 2$)
+\begin{equation}
+\label{eq:Fh}
+F(h) \sim \sigma \frac{\delta^m}{h^{m+1}}\left(\left(\frac{\delta}{h}\right)^2-1\right),
+\end{equation}
+attraction is dominant at ``large" scales ($h > \delta$) while repulsion is dominant at ``small" scales ($h<\delta$).
+Integration of equation~\ref{eq:dhdt} with the above $F(h)$ gives the relationship between $t$ and $h$.
+In this case the relationship involves an integral of a function of dimensionless $\bar{h} \equiv h/\delta$:
+\begin{align}
+t\frac{K_a^{2/3}}{\mu R_0^{10/3}}& = \int^{h(t)}_{h(0)}-\frac{dh}{h^3 F^{1/3}} = -\frac{1}{\sigma^{1/3}\delta^{5/3}}\int^{\bar{h}(t)}_{\bar{h}(0)}\frac{d \bar{h}}{\bar{h}^{(8-m)/3}(\bar{h}^2-1)^{1/3}},
+\end{align}
+\begin{equation}
+\label{eq:teq_scaling}
+t\sim \frac{\mu R_0^{10/3}}{K_a^{2/3}}\frac{1}{\sigma^{1/3}\delta^{5/3}}.
+\end{equation}
+Equation~\ref{eq:teq_scaling} tells us that both adhesion strength $\sigma$ and the separation distance $\delta$ affect
+the time it takes for a pair of vesicles to reach equilibrium under adhesion force $F$ in equation~\ref{eq:Fh}.  In particular, the equilibration time $t$ 
+is proportional to both (1) the separation distance $\delta^{-5/3}$ (thus $t\rightarrow \infty$ as $\delta\rightarrow 0$), and (2) the adhesion strength $\sigma^{-1/3}$ 
+(as in constant forcing case \cite{RamachandranLeal2010_PoF}).  From the above analysis we also expect that the scaling of $t$ with respect to $\delta$ depends on the
+adhesion potential, while the scaling with respect to adhesion strength is independent of the specific form of the potential.
+
+\begin{figure}
+\includegraphics[keepaspectratio=true,scale=0.4]{figs/Dec13a_time_scaling01.eps}
+\includegraphics[keepaspectratio=true,scale=0.4]{figs/Dec13a_time_scaling02.eps}
+\caption{Scaling of the time it takes for two vesicles to reach equilibrium: (a) scaling with respect to $\delta$ with $\sigma=0.1$, and (b) scaling
+with respect to $\sigma$ with $\delta = 0.4$. Arrows indicate the time by when the equilibrium is reached within $1\%$.}
+\label{fig:qflow00}
+\end{figure}
+
+To test the scaling of the equilibration time $t$ with respect to $\sigma$ and $\delta$, we simulate the vesicle adhesion dynamics in a quiescent flow.
+Starting with two vesicles at a distance of twice the radius at $t=0$, the long-range attraction pulls the vesicles together. Figure~\ref{fig:qflow00}(a) plots
+the scaled adhesion energy versus time with $\sigma=0.1$ and three values of $\delta$ as labeled. 
+Adhesion energy reaches minimum at equilibrium, and the scaled $E_{adh}$ evolves towards zero at equilibrium. 
+The arrow indicate the times when the scaled adhesion energy
+reaches within $1\%$ of equilibrium: $t\sim 96$ for $\delta=0.2$, $t\sim 45$ for $\delta = 0.3$, and $t\sim 30$ for $\delta=0.4$:
+\begin{align}
+\frac{t_{\delta=0.2}}{t_{\delta=0.4}} \sim \frac{96}{30}=3.2 &\Longleftrightarrow \left(\frac{0.4}{0.2}\right)^{5/3}\sim 3.17,\\
+\frac{t_{\delta=0.2}}{t_{\delta=0.3}} \sim \frac{96}{45}=2.1 &\Longleftrightarrow \left(\frac{0.3}{0.2}\right)^{5/3}\sim 2.
+\end{align}
+
+The scaling with respect to adhesion strength $\sigma$ is illustrated in figure~\ref{fig:qflow00}(b), where $\delta = 0.4$ and $\sigma$ varies from $0.1$ to $0.5$ as labeled.
+Again the arrows indicate the times when the equilibrium is reached within $1\%$:
+\begin{align}
+\frac{t_{\sigma=0.1}}{t_{\sigma=0.5}} \sim \frac{34}{20} = 1.71 &\Longleftrightarrow \left(\frac{0.5}{0.1}\right)^{1/3}\sim 1.71.
+\end{align}
+From the above results we conclude that the scaling in equation~\ref{eq:teq_scaling} captures the adhesion dynamics of two vesicles that interact with each other via the adhesion force in equation~\ref{eq:Fh}.
+
+\subsection{Effects of the adhesion parameters on equilibrium}
 \label{subsec:qflow_adhesion_parameters} 
@@
 \end{align*}
-Here, $[\mu]$ is the intrinsic viscosity, $\phi$ is the area fraction of
+Here, $[\mu]$ is the intrinsic viscosity, $|phi$ is the area fraction of
 vesicles, $\sigma$ is the stress due to the vesicles, and $\langle \cdot
@@
 \end{figure}
-\todo[inline]{Do the smaller reduced area doublets since the intrinsic
-viscosity seemed to increase as the reduced area was decresed further}
-\todo[inline]{Decompose the red curve as the intrinsic viscosity due to
-adhesion and due to the bending/tension}
 
@@
   -4 \sigma \delta^2 \int_{\gamma_2}
-  \frac{\xx_1 - \xx_2}{\|\xx_1 - \xx_2\|^6} 
+  \frac{\xx_1 - \xx_2}{\|\xx_1 - \xx_2\|^2} 
   \left(\delta^2 - \|\xx_1 - \xx_2\|^2 \right) ds_{\xx_2}.
@@
 
-\bibliography{refs}
+\bibliography{refs,refs_yny}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-12-28 vesicle_code/docs/adhesion/adhesion.tex

@@
 \begin{figure}[htp]
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep1.pdf}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep2.pdf}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep3.pdf}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep4.pdf}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep5.pdf}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image01.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image02.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image03.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image04.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image05.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image06.png}
   \caption{Two vesicles in an extensional flow.  The reduced area is
-  $0.40$, the adhesion strength is $1.0$, and the adhesion length scale
-is $0.8$, background flow strength is $\chi = 10^{-2}$.}
+  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
+is $0.4$, extensional rate is $\chi = 0.05$.}
 \end{figure}
@@
 \begin{figure}[htp]
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep1.pdf}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep2.pdf}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep3.pdf}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep4.pdf}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep5.pdf}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi9em2_ra080_image01.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi9em2_ra080_image02.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi9em2_ra080_image03.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi9em2_ra080_image04.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi9em2_ra080_image05.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi9em2_ra080_image06.png}
   \caption{Two vesicles in an extensional flow.  The reduced area is
-  $0.90$, the adhesion strength is $1.0$, and the adhesion length scale
-is $0.8$, background flow strength is $\chi = 10^{-2}$.}
+  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
+is $0.4$, extensional rate is $\chi = 0.09$.}
 \end{figure}
 
+\begin{figure}[htp]
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image06.png}
+  \caption{Two vesicles in an extensional flow.  The reduced area is
+  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
+is $0.4$, extensional rate is $\chi = 0.1$.}
+\end{figure}
+
+\begin{figure}[htp]
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image01.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image02.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image03.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image04.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image05.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image06.png}
+  \caption{Two vesicles in an extensional flow.  The reduced area is
+  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
+is $0.4$, extensional rate is $\chi = 0.11$.}
+\end{figure}
+
+%We consider two vesicles suspended in the extensional flow $\uu =
+%\chi(-x,y)$, where $\chi$ is the extensional rate.  The vesicles are
+%initially place symmetrically on the $y$ axis so that the background
+%velocity drives the vesicles towards one another.  We vary the reduced
+%area and the two vdW parameters and characterize the possible steady
+%state configurations.  For all the simulations, the length of the
+%vesicles are fixed, while the area is changed to achieve the desired
+%reduced area.
+%
+%\begin{figure}[htp]
+%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep1.pdf}
+%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep2.pdf}
+%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep3.pdf}
+%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep4.pdf}
+%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep5.pdf}
+%  \caption{Two vesicles in an extensional flow.  The reduced area is
+%  $0.40$, the adhesion strength is $1.0$, and the adhesion length scale
+%is $0.8$, background flow strength is $\chi = 10^{-2}$.}
+%\end{figure}
+%
+%\begin{figure}[htp]
+%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep1.pdf}
+%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep2.pdf}
+%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep3.pdf}
+%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep4.pdf}
+%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep5.pdf}
+%  \caption{Two vesicles in an extensional flow.  The reduced area is
+%  $0.90$, the adhesion strength is $1.0$, and the adhesion length scale
+%is $0.8$, background flow strength is $\chi = 10^{-2}$.}
+%\end{figure}
+
+\newpage % so that the figures are more organized writing the paper
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-12-29 vesicle_code/docs/adhesion/adhesion.tex
removed yuan's reference file

@@
 
-When two vesicles move towards each other under a constant force $F$ without any external fluid flow, the height  $(h)$ of the lubrication film between two vesicles follows the
+When two vesicles move towards (or away from) each other under a constant force $F$ without any external fluid flow, the height  $(h)$ of the thin liquid film between two vesicles follows the
 draining dynamics \cite{RamachandranLeal2010_PoF}
@@
 where $K_a$ is the area expansion modulus, $\mu$ is the viscosity of exterior fluid, $R_0$ is the radius of the undeformed vesicle.
-When $F$ is a constant (independent of separation distance $h$ and/or time $t$), the above scaling can give variation of $h$ versus $t$ by integrating the above equation
+For the case of a constant forcing $F$ (independent of separation distance $h$ and time $t$), equation~\ref{eq:dhdt} can be easily integrated to give
+a relation between film thickness $h$ and time $t$:
 \begin{equation}
@@
 where $h(0)$ is the vesicle separation at $t=0$.
-We note that $F< (>) 0$ for an attractive  (repulsive) force and consequently $h(t)$ decreases (increases) from  the initial separation distance $h(0)$. 
+We note that $F< (>) 0$ for an attractive  (repulsive) interaction between two vesicles,  and consequently $h(t)$ decreases (increases) from  the initial separation distance $h(0)$. 
 When the force is attractive, $h$ decreases monotonically and $t$ in the above
@@
 the time it takes for a pair of vesicles to reach equilibrium under adhesion force $F$ in equation~\ref{eq:Fh}.  In particular, the equilibration time $t$ 
-is proportional to both (1) the separation distance $\delta^{-5/3}$ (thus $t\rightarrow \infty$ as $\delta\rightarrow 0$), and (2) the adhesion strength $\sigma^{-1/3}$ 
+is proportional to (1) the separation distance $\delta^{-5/3}$ (thus $t\rightarrow \infty$ as $\delta\rightarrow 0$), and (2) the adhesion strength $\sigma^{-1/3}$ 
 (as in constant forcing case \cite{RamachandranLeal2010_PoF}).  From the above analysis we also expect that the scaling of $t$ with respect to $\delta$ depends on the
@@
 
-\subsection{Effects of the adhesion parameters on equilibrium}
+\subsection{Effects of the adhesion parameters on equilibrium configuration of a vesicle pair}
 \label{subsec:qflow_adhesion_parameters} 
-Here we investigate the dynamics and steady state configuration of two
-identical vesicles placed next to each other in a quiescent flow.  For a
-large reduced area, the two vesicles move toward each other until the
-membrane flattens in the adhesion region, as shown in
-Figures~\ref{fig:qflow01} and~\ref{fig:qflow02}.  The color coding along
-the membrane denotes the membrane tension, which is the lowest in the
-adhesion region.
+In the simulations of a pair of 2d vesicles interacting with each other via the adhesion force in equation~\ref{eq:Fh} 
+two vesicles are placed (not too far apart for numerical convenience) in a quiescent flow. Long-range attraction pulls two vesicles together as they deform until their
+separation distance is close to $\delta$ (where $F$ vanishes). 
+\begin{figure}
+\includegraphics[keepaspectratio=true,scale=0.25]{figs/Dec18_vesicle_shape_vs_rA_00.jpeg}
+\caption{Equilibrium shapes of wo vesicles under adhesive  interactions with adhesion strength $\sigma=0.5$ and separation distance $\delta=0.2$. 
+Vesicle reduced area $\Delta A=0.95$, $0.75$ and $0.6$ as labeled.
+ The color coding is the tension along the vesicle.}
+\label{fig:Dec18_vesicle_shape}
+\end{figure}
+
+Figure~\ref{fig:Dec18_vesicle_shape}(a) shows the equilibrium shapes of vesicles with
+three values of reduced area: $\Delta A=0.95$, $0.75$ and $0.6$ with $\sigma=5$ and $\delta = 0.2$.
+The equilibrium vesicle shape for $\Delta A=0.95$ is the circular cap with a flatten contact region. 
+This is similar to the observed shapes of two vesicles under strong adhesive interaction in \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.
+
+When vesicles are more deflated with a reduced area  $\Delta A = 0.75$, the equilibrium vesicle shape is elongated with a bigger contact region.
+As the reduced area decreases further, we observe undulation of the elongated equilibrium vesicle shape on the non-contact side while the contact region remains flat. 
+The color coding along each curve is for the tension of vesicle membrane.
+We observe that the membrane tension in the contact region is very negative, indicating a dominant compression of membrane when the adhesion force is strong to keep the vesicles bound together.
 
 \begin{figure}
-\includegraphics[keepaspectratio=true,scale=0.125]{figs/Nrelax2Ves02-rA0p96adR0p4.png}
-\caption{Two vesicles interacting with each other via a vdW potential at different strengths in a quiescent viscous fluid. The color coding is the tension along the vesicle.}
-\label{fig:qflow01}
+\includegraphics[keepaspectratio=true,scale=0.125]{figs/Dec18_Eb_vs_rA_adR0p2_adS502.jpeg}
+\includegraphics[keepaspectratio=true,scale=0.125]{figs/Dec18_Eadh_vs_rA_adR0p2_adS502.jpeg}
+\includegraphics[keepaspectratio=true,scale=0.125]{figs/Dec18_EbEadh_vs_rA_adR0p2_adS502.jpeg}
+\caption{Total bending energy (panel (a)), adhesion energy (panel (b)) and the sum of two energies (panel (c)) plotted against reduced area $\Delta A$.}
+\label{fig:Dec18_vesicle_equilibrium1}
 \end{figure}
+Figure~\ref{fig:Dec18_vesicle_equilibrium1}(a) shows the total bending energy as a function of reduced area. The smaller the reduced area, the more vesicle area is available
+for deformation and thus the bending energy is higher. Figure~\ref{fig:Dec18_vesicle_equilibrium1}(b) shows the total adhesion energy as a function of reduced area. We note
+that the total adhesion energy is more negative as reduced area decreases.
+The sum of two energies is plotted in figure~\ref{fig:Dec18_vesicle_equilibrium1}(c), where a local minimum in the total energy is
+found around $\Delta A =0.8$.
 
 \begin{figure}
-\includegraphics[keepaspectratio=true,scale=0.25]{figs/Nrelax2Ves02composite-draining.pdf}
-\caption{Adhesion of two vesicles in a quiescent flow.  Only one vesicle
-  is illustrated, and the second is a mirror image.  Left panel: The
-  steady state configuration for different vdW interaction distances.
-  The color coding is the tension along the vesicle.  Right panel:
-  Vesicle configurations at different times for different vdW strengths.
-  The top plot has the weakest vdW strength and the bottom plot has the
-  strongest vdW strength.}
-\label{fig:qflow02} 
+\includegraphics[keepaspectratio=true,scale=0.18]{figs/Dec18_Eb_vs_sigma_rA0p9502.jpeg}
+\includegraphics[keepaspectratio=true,scale=0.18]{figs/Dec18_Eadh_vs_sigma_rA0p9502.jpeg}
+\caption{Total bending energy (a) and adhesion energy (b) versus the adhesion strength $\sigma$ 
+for two vesicles with reduced area $\Delta A=0.95$, separation distance $\delta = 0.2$ (triangles), $0.3$ (crosses)
+and $0.4$ (circles). }
+\label{fig:Dec18_equilibrium} 
 \end{figure}
+%
+Figure~\ref{fig:Dec18_equilibrium} is an example of how the adhesion strength $\sigma$ and separation distance $\delta$ affect the equilibrium configuration of two vesicles under adhesive interactions.
+For both vesicles the reduced area $\Delta A=0.95$ and the bending rigidity is $1$.
+In figure~\ref{fig:Dec18_equilibrium}(a) 
+the total bending energy at equilibrium is plotted against $\sigma$ for three values of separation distance $\delta$.
+We observe that for $\Delta A=0.95$ the equilibrium vesicle shape does not vary much with the adhesion strength $\sigma$, while the total adhesion energy in figure~\ref{fig:Dec18_equilibrium}(b) varies linearly
+with $\sigma$.
 
-% \begin{figure}
-% \includegraphics[keepaspectratio=true,scale=0.4]{figs/relax2Ves01g-draining01a.eps}
-% \caption{Adhesion dynamics of two vesicles with $\delta = 0.3$. From $t=0.3$ to $t=40$, the time interval $\delta t = 0.3$ between every two neighboring dash-dotted curves.}
-% \label{fig:qflow_g-draining01a}
-% \end{figure}
-
-% \begin{figure}
-% \includegraphics[keepaspectratio=true,scale=0.4]{figs/relax2Ves01j-draining01a.eps}
-% \caption{Adhesion dynamics of two vesicles with $\delta = 0.6$. From $t=0.1$ to $t=40$, the time interval $\delta t = 0.1$ between every two neighboring dash-dotted curves.}
-% \label{fig:qflow_g-draining01a}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Effects of reduced area}
-\label{sec:qflow_reduced_area} 
-Figure~\ref{fig:qflow_reduced_area}
-
-\begin{figure}
-\includegraphics[keepaspectratio=true,scale=0.5]{figs/nrelax2Ves02o_rA.png}
-\caption{The effect of the reduced area on adhering vesicles in a
-quiescent flow.  The parameters of the vdW potential are $\delta = 0.2$
-and $\sigma = 0.5$.}
-\label{fig:qflow_reduced_area}
-\end{figure}
-
-% \begin{figure}
-% \includegraphics[keepaspectratio=true,scale=0.4]{figs/relax2Ves01usa.eps}
-% \caption{Adhesion dynamics of two vesicles with $\delta = 0.4$ and $\sigma=0.2$. From $t=0.06$ to $t=100$, the time interval $\delta t = 0.06$ between every two neighboring dash-dotted curves.}
-% \label{fig:qflow_u-draining}
-% \end{figure}
-
-% \begin{figure}
-% \includegraphics[keepaspectratio=true,scale=0.4]{figs/relax2Ves01zsa.eps}
-% \caption{Adhesion dynamics of two vesicles with $\delta = 0.4$ and $\sigma=0.2$. From $t=1$ to $t=100$, the time interval $\delta t = 1$ 
-% between every two neighboring dash-dotted curves.}
-% \label{fig:qflow_z-draining}
-% \end{figure}
+%% \begin{figure}
+%% \includegraphics[keepaspectratio=true,scale=0.4]{figs/relax2Ves01g-draining01a.eps}
+%% \caption{Adhesion dynamics of two vesicles with $\delta = 0.3$. From $t=0.3$ to $t=40$, the time interval $\delta t = 0.3$ between every two neighboring dash-dotted curves.}
+%% \label{fig:qflow_g-draining01a}
+%% \end{figure}
+%
+%% \begin{figure}
+%% \includegraphics[keepaspectratio=true,scale=0.4]{figs/relax2Ves01j-draining01a.eps}
+%% \caption{Adhesion dynamics of two vesicles with $\delta = 0.6$. From $t=0.1$ to $t=40$, the time interval $\delta t = 0.1$ between every two neighboring dash-dotted curves.}
+%% \label{fig:qflow_g-draining01a}
+%% \end{figure}
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Effects of reduced area}
+%\label{sec:qflow_reduced_area} 
+%Figure~\ref{fig:qflow_reduced_area}
+%
+%\begin{figure}
+%\includegraphics[keepaspectratio=true,scale=0.5]{figs/nrelax2Ves02o_rA.png}
+%\caption{The effect of the reduced area on adhering vesicles in a
+%quiescent flow.  The parameters of the vdW potential are $\delta = 0.2$
+%and $\sigma = 0.5$.}
+%\label{fig:qflow_reduced_area}
+%\end{figure}
+%
+%% \begin{figure}
+%% \includegraphics[keepaspectratio=true,scale=0.4]{figs/relax2Ves01usa.eps}
+%% \caption{Adhesion dynamics of two vesicles with $\delta = 0.4$ and $\sigma=0.2$. From $t=0.06$ to $t=100$, the time interval $\delta t = 0.06$ between every two neighboring dash-dotted curves.}
+%% \label{fig:qflow_u-draining}
+%% \end{figure}
+%
+%% \begin{figure}
+%% \includegraphics[keepaspectratio=true,scale=0.4]{figs/relax2Ves01zsa.eps}
+%% \caption{Adhesion dynamics of two vesicles with $\delta = 0.4$ and $\sigma=0.2$. From $t=1$ to $t=100$, the time interval $\delta t = 1$ 
+%% between every two neighboring dash-dotted curves.}
+%% \label{fig:qflow_z-draining}
+%% \end{figure}
 
@@
 
-\bibliography{refs,refs_yny}
+\bibliography{refs}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-12-29 vesicle_code/docs/adhesion/adhesion.tex
revised figures added

@@
 and electrohydrodynamics.
-Theoretical investigations are conducted to study the small-deformation or spheroidal dynamics of a nearly spherical (circular) vesicle in a fluid flow or under an external forcing \cite{Barthes-BieselRallison1981_JFM,Misbah2006_PRL,Vlahovska2007_PRE,Finken2008_EPL,ZhangZahnTanLin2013_PoF,Nganguia2013_PRE}.
+Theoretical investigations are conducted to study the small-deformation or spheroidal dynamics of a nearly spherical  3D (or nearly circular 2D) vesicle in a fluid flow or under an external forcing \cite{Barthes-BieselRallison1981_JFM,Misbah2006_PRL,Vlahovska2007_PRE,Finken2008_EPL,ZhangZahnTanLin2013_PoF,Nganguia2013_PRE}.
 Various numerical schemes have been designed and deployed to simulate the hydrodynamics of many vesicles \cite{BagchiJohoson2005_JBE,Biben2005_EJP,Veerapaneni2009_JCP,SeolHuKimLai2016_JCP}.  
@@
 \label{subsec:qflow_adhesion_parameters} 
-In the simulations of a pair of 2d vesicles interacting with each other via the adhesion force in equation~\ref{eq:Fh} 
-two vesicles are placed (not too far apart for numerical convenience) in a quiescent flow. Long-range attraction pulls two vesicles together as they deform until their
-separation distance is close to $\delta$ (where $F$ vanishes). 
+In the simulations of a pair of 2d vesicles interacting with each other via the adhesion force in equation~\ref{eq:Fh},
+two vesicles are initially placed not too far apart  from each other for numerical convenience. 
+Without any external forcing such as an imposed electric field or a fluid flow in the far-field, the long-range attraction pulls two vesicles together until their
+separation distance is close to $\delta$ (where $F$ vanishes).  Depending on the adhesion strength relative to the membrane bending rigidity, the vesicle may deform significantly in the contact
+region while still maintain nearly spherical shape on the opposite side to the contact region \cite{EvansMetcalfe1984_BJ,Book_PhysicalBasisCellAdhesion,Book_IntermolecularSurfaceForces,RamachandranAndersonLealIsraelachvili2010_Langmuir}.
 \begin{figure}
-\includegraphics[keepaspectratio=true,scale=0.25]{figs/Dec18_vesicle_shape_vs_rA_00.jpeg}
-\caption{Equilibrium shapes of wo vesicles under adhesive  interactions with adhesion strength $\sigma=0.5$ and separation distance $\delta=0.2$. 
+\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_00.jpeg}
+\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
+\caption{Two vesicles of length $\pi$ with $\kappa=1$, $\sigma=5$ and $\delta=0.2$.
+(a) Equilibrium shapes of two vesicles under adhesive  interactions with adhesion strength $\sigma=0.5$ and separation distance $\delta=0.2$. 
 Vesicle reduced area $\Delta A=0.95$, $0.75$ and $0.6$ as labeled.
- The color coding is the tension along the vesicle.}
+ The color coding is the tension along the vesicle. (b) Membrane shapes in the contact region.}
 \label{fig:Dec18_vesicle_shape}
@@
 \begin{figure}
-\includegraphics[keepaspectratio=true,scale=0.125]{figs/Dec18_Eb_vs_rA_adR0p2_adS502.jpeg}
-\includegraphics[keepaspectratio=true,scale=0.125]{figs/Dec18_Eadh_vs_rA_adR0p2_adS502.jpeg}
-\includegraphics[keepaspectratio=true,scale=0.125]{figs/Dec18_EbEadh_vs_rA_adR0p2_adS502.jpeg}
-\caption{Total bending energy (panel (a)), adhesion energy (panel (b)) and the sum of two energies (panel (c)) plotted against reduced area $\Delta A$.}
+\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_Ebleft_Eadhright_vs_rA_adR0p2_adS502.jpeg}
+\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_EbEadh_vs_rA_adR0p2_adS502.jpeg}
+\caption{Two vesicles of length $\pi$ with $\kappa=1$, $\sigma=5$ and $\delta=0.2$. 
+(a) Total bending energy (solid curve) and adhesion energy (dash-dotted curve) plotted against
+the reduced area $\Delta A$. (b) Sum of two energies plotted against reduced area $\Delta A$.}
 \label{fig:Dec18_vesicle_equilibrium1}

### 2019-01-07 vesicle_code/docs/adhesion/adhesion.tex
put in a few todos that ashley pointed out

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\todo[inline]{$\sigma$ is overdefined as the Hamacher constant, and the
+tension, and possibly the stress}
+
 \section{Introduction}
@@
 \end{align}
+\todo[inline]{Define $\rr$ and other variables in
+equation~\eqref{eqn:SLP}}
 The traction jump of the velocity $\uu(\xx) = \SS[\ff](\xx)$ is the
@@
 \begin{figure}[htp]
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image01.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image02.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image03.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image04.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image05.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image06.png}
+  \caption{Two vesicles in an extensional flow.  The reduced area is
+  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
+is $0.4$, extensional rate is $\chi = 0.03$.}
+\end{figure}
+
+\begin{figure}[htp]
   \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image01.png}
@@
   \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image04.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image05.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi9em2_ra080_image05.png}
   \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image06.png}
@@
 is $0.4$, extensional rate is $\chi = 0.05$.}
-\end{figure}
-
-\begin{figure}[htp]
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi9em2_ra080_image01.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi9em2_ra080_image02.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi9em2_ra080_image03.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi9em2_ra080_image04.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi9em2_ra080_image05.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi9em2_ra080_image06.png}
-  \caption{Two vesicles in an extensional flow.  The reduced area is
-  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
-is $0.4$, extensional rate is $\chi = 0.09$.}
 \end{figure}

### 2019-01-07 vesicle_code/docs/adhesion/adhesion.tex
fixed extensional snapshot figures

@@
   \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image04.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi9em2_ra080_image05.png}
+  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image05.png}
   \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image06.png}
@@
   $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
-is $0.4$, extensional rate is $\chi = 0.1$.}
+is $0.4$, extensional rate is $\chi = 0.1$.  After time $t=400$, the
+  vesicles extensional rate has overcome the adhesive force, and the
+  vesicles continue to separate.}
 \end{figure}

### 2019-01-09 vesicle_code/docs/adhesion/adhesion.tex
intro

@@
 %
-\documentclass[%
+\documentclass[aps,prl,twocolumn,showpacs,amsmath,amssymb]{revtex4-1}
+
+%\documentclass[%
 %reprint,
@@
 %frontmatterverbose, 
-preprint,
+%preprint,
 %showpacs,preprintnumbers,
@@
 %bibnotes,
- amsmath,amssymb,
- aps,
+ %amsmath,amssymb,
+ %aps,
 %pra,
@@
 %floatfix,
-]{revtex4-1}
+%]{revtex4-1}
 
@@
 
-\title{Hydrodynamics of two vesicles interacting via a Van der Waals potential}% Force line breaks with \\
+\title{Vesicle-vesicle adhesion in linear flows: dynamics and rheology}% Force line breaks with \\
 %\thanks{A footnote to the article title}%
@@
 \begin{abstract}
-An article usually includes an abstract, a concise summary of the work
-covered at length in the main body of the article. 
-\begin{description}
-\item[Usage]
-Secondary publications and information retrieval purposes.
-\item[PACS numbers]
-May be entered using the \verb+\pacs{#1}+ command.
-\item[Structure]
-You may use the \texttt{description} environment to structure your abstract;
-use the optional argument of the \verb+\item+ command to give the category of each item. 
-\end{description}
+
+%\begin{description}
+%\item[Usage]
+%Secondary publications and information retrieval purposes.
+%\item[PACS numbers]
+%May be entered using the \verb+\pacs{#1}+ command.
+%\item[Structure]
+%You may use the \texttt{description} environment to structure your abstract;
+%use the optional argument of the \verb+\item+ command to give the category of each item. 
+%\end{description}
 \end{abstract}
@@
 \section{Introduction}
-Vesicles (self-enclosed phopholipid bilayer membranes) have been widely utilized
-as simple model membranes for cell mimics in biomedical and material engineering \cite{}. 
+Vesicles (closed fluid-filled phospholipid bilayer membranes) have been widely utilized
+as biological cell mimics in biophysics and material engineering \cite{}. 
 %
-The ever expanding applications of vesicles have encouraged extensive investigations on vesicle hydrodynamics
-and electrohydrodynamics.
-Theoretical investigations are conducted to study the small-deformation or spheroidal dynamics of a nearly spherical  3D (or nearly circular 2D) vesicle in a fluid flow or under an external forcing \cite{Barthes-BieselRallison1981_JFM,Misbah2006_PRL,Vlahovska2007_PRE,Finken2008_EPL,ZhangZahnTanLin2013_PoF,Nganguia2013_PRE}.
-Various numerical schemes have been designed and deployed to simulate the hydrodynamics of many vesicles \cite{BagchiJohoson2005_JBE,Biben2005_EJP,Veerapaneni2009_JCP,SeolHuKimLai2016_JCP}.  
-Experiments are performed to study vesicle hydrodynamics under various flowing conditions or forcing configurations \cite{MaderVitkova2006_EurPhysJE, Abkarian2008_SoftMatt,DahlNarsimhanGouveia2016_SoftMatt}.
-In a vesicle suspension under
-a hydrodynamic flow or an external field (such as an electric field) 
-the interactions between
-vesicles play a crucial role in determining the collective dynamics of
-vesicle suspension. For example, boundary integral simulations show that
-vesicles may align to form chains along the external electric field,
-enhancing the suspension viscosity in the direction of alignment.
-In numerical simulations of vesicle suspension, it is often assumed that lubrication layer between vesicle membranes act to keep
-membrane-membrane interaction (such as Van der Waals interaction) negligible \cite{BagchiJohoson2005_JBE,Veerapaneni2009_JCP}.
+The ever expanding applications have encouraged detailed experimental, theoretical and numerical investigations of vesicle hydrodynamics
+in applied flow, electric and magnetic fields.
+Theoretical investigations often take the form of small-deformation analysis or spheroidal dynamics of a nearly-spherical vesicle (or nearly-circular in two dimensions) subjected to an applied flow or under an external forcing \cite{Barthes-BieselRallison1981_JFM,Misbah2006_PRL,Vlahovska2007_PRE,Finken2008_EPL,ZhangZahnTanLin2013_PoF,Nganguia2013_PRE}.
+On the other hand, various numerical methods have been developed for simulating the transient hydrodynamics of vesicle suspensions  \cite{BagchiJohoson2005_JBE,Biben2005_EJP,Veerapaneni2009_JCP,SeolHuKimLai2016_JCP}.
+%Experiments are performed to study vesicle hydrodynamics under various flowing conditions or forcing configurations \cite{MaderVitkova2006_EurPhysJE, Abkarian2008_SoftMatt,DahlNarsimhanGouveia2016_SoftMatt}.
+Collective vesicle hydrodynamics naturally is dictated by the individual vesicle-vesicle interactions;  for example, 
+it was shown recently that vesicles may align to form chains along the direction of the externally applied DC electric field with ensuing consequences to suspension rheology \cite{wu2018pairwise}.
 
-However the amphiphilic natures of lipid molecules (a hydrophobic tail and a hydrophilic head with an electric dipole) complicate the
-interactions between a lipid bilayer membrane and a solid (such as a glass substrate or a nano particle) or another bilayer membrane \cite{EvansMetcalfe1984_BJ,Book_PhysicalBasisCellAdhesion,Book_IntermolecularSurfaceForces}.
+In numerical simulations of vesicle suspensions, it is often assumed that the lubrication layer between vesicle membranes acts to keep the 
+membrane-membrane interaction, such as the van der Waals type interaction, negligible.
+However the amphiphilic natures of lipid molecules (a hydrophobic tail and a hydrophilic head with an electric dipole) complicate the interactions between a lipid bilayer membrane and a solid (such as a glass substrate or a nano particle) or another bilayer membrane \cite{EvansMetcalfe1984_BJ,Book_PhysicalBasisCellAdhesion,Book_IntermolecularSurfaceForces}.
 Studies confirmed that such interaction potential inevitably consists of a long-range attraction component and a short-range repulsion component 
@@
 interaction potential \cite{Book_IntermolecularSurfaceForces}, and are essential in many biomedical, biological and biophysical processes.
-For example, vesicle adhesion
-is essential for membrane fusion/fission in endocytosis and exocytosis, the transport of small
+For example, vesicle adhesion is essential for membrane fusion/fission in endocytosis and exocytosis, the transport of small
 vesicles through membrane surfaces.
@@
 %
-Adhesion between a vesicle and a substrate has been extensively studied, with 
-more computations and experiments for the equilibrium shapes \cite{Seifert1990_PRA,ShiFengGao2006_ActaMechSin,LinFreund2007_IntJSolidsStructures} than analysis and simulation of
-the dynamic adhesion process \cite{BlountMiksisDavis2013_PRSa}.
-Adhesion between bilayer membranes was first experimentally observed by Evans and Metcalfe, who measured 
+Adhesion between a vesicle and a substrate has been extensively studied, primarily focused on analyzing the static equilibrium shapes \cite{Seifert1990_PRA, ShiFengGao2006_ActaMechSin, LinFreund2007_IntJSolidsStructures, das2008adhesion, zhang2009phase} than the the transient adhesion process; exceptions include \cite{cantat1999lift, suk-sei2001, BlountMiksisDavis2013_PRSa}.
+Adhesion between bilayer membranes was first experimentally observed by Evans and Metcalfe \cite{EvansMetcalfe1984_BJ}, who measured 
 the reduction in the free energy per unit area of membrane-membrane contact formation due to the Van der Waals' attraction. For a membrane-membrane
-separation distance of $\sim 3$ nano meters, they estimated that the Hamaker constant $\sim 5.8\times 10^{-14}$ ergs \cite{EvansMetcalfe1984_BJ}, which corresponds to an adhesion energy density $\sim 1$ mJ/m$^2$.
+separation distance of $\sim 3$ nm, they estimated that the Hamaker constant is approximately $5.8\times 10^{-14}$ ergs, which corresponds to an adhesion energy density around $1$ mJ/m$^2$.
 The ratio of adhesion energy per unit area to the bending energy (bending rigidity of lipid bilayer membranes $\sim 10^{-19}$ J) gives a measure of vesicle deformation in the presence of adhesion \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.
-In this work we focus on regimes where the ratio is of order unity, between the weak adhesion (ratio $\ll 1$) and strong adhesion (ratio $\gg 1$) regimes \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.
-In this regime the membrane deformation may increase the ``contact area'' between two vesicles and enhance the adhesion effects \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.
-The equilibration of vesicle membranes under adhesion in these regimes have been well studied and documented (\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir} and references therein).
-However it is not clear how in such regime the adhesion couples to the vesicle hydrodynamics?
+In this work we focus on regimes where the ratio is of order unity, between the weak adhesion (ratio $\ll 1$) and strong adhesion (ratio $\gg 1$) regimes.
+In this regime the membrane deformation may increase the ``contact area'' between two vesicles and enhance the adhesion effects.
+The equilibration of vesicle membranes under adhesion in these regimes have been well studied and documented (see \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir} and references therein).
+However it is unclear how the adhesion couples to the vesicle hydrodynamics in such regime.
 Our work in this paper aims to address this question with quantitative characterization in terms of physical parameters.
 
-Hydrodynamics of a single vesicle in Stokes flow has been extensively investigated. In a planar shear flow, the vesicle hydrodynamics is characterized by
-excess area (reduced volume), viscosity contrast between interior and exterior fluids, and shear rate of the imposed far-field fluid flow. In addition a vesicle
-with a rigid particle inside is also investigated as a biological mimic of a 
-eukaryotic cell with a nucleus that occupies nearly half of the intracellular volume \cite{Veerapaneni2011_PRL}. Small-deformation analysis shows that
-a vesicle tank-treads in a planar shear flow for low viscosity contrast and shear rate.
+%Hydrodynamics of a single vesicle in Stokes flow has been extensively investigated. In a planar shear flow, the vesicle hydrodynamics is characterized by
+%excess area (reduced volume), viscosity contrast between interior and exterior fluids, and shear rate of the imposed far-field fluid flow. In addition a vesicle
+%with a rigid particle inside is also investigated as a biological mimic of a 
+%eukaryotic cell with a nucleus that occupies nearly half of the intracellular volume \cite{Veerapaneni2011_PRL}. Small-deformation analysis shows that
+%a vesicle tank-treads in a planar shear flow for low viscosity contrast and shear rate.
 At high viscosity contrast the tank-tread (TT) dynamics transitions to tumbling (TB) \cite{Misbah2006_PRL,Vlahovska2007_PRE} ,
-and this leads to a transition in effective shear viscosity in the vesicle suspension \cite{Misbah2006_PRL,Vitkova2008_BJ} that is also validated
-by direct numerical simulations \cite{GhigliottiBibenMisbah2010_JFM} and experiments \cite{KantslerSegreSteinberg2008_EPL,ZabuskySegreDeschamps2011_PoF}.
-Between TT and TB vesicle hydrodynamics, a breathing (tremble) is also observed \cite{Misbah2006_PRL,KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2011_JFM,SpannZhaoShaqfeh2014_PoF} to affect the effective shear viscosity in a
-different way.
+%and this leads to a transition in effective shear viscosity in the vesicle suspension \cite{Misbah2006_PRL,Vitkova2008_BJ} that is also validated
+%by direct numerical simulations \cite{GhigliottiBibenMisbah2010_JFM} and experiments \cite{KantslerSegreSteinberg2008_EPL,ZabuskySegreDeschamps2011_PoF}.
+%Between TT and TB vesicle hydrodynamics, a breathing (tremble) is also observed \cite{Misbah2006_PRL,KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2011_JFM,SpannZhaoShaqfeh2014_PoF} to affect the effective shear viscosity in a
+%different way.
 %
-In an extensional flow (planar or uniaxial), vesicle shape dynamics
-depends sensitively on the vesicle reduced volume  and the elastic capillary number \cite{KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2013_JFM,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}: Asymmetric shape and oscillatory undulation of the vesicle membrane are two examples of the complex vesicle hydrodynamics in an extensional flow.
+%In an extensional flow (planar or uniaxial), vesicle shape dynamics
+%depends sensitively on the vesicle reduced volume  and the elastic capillary number \cite{KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2013_JFM,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}: Asymmetric shape and oscillatory undulation of the vesicle membrane are two examples of the complex vesicle hydrodynamics in an extensional flow.
 
 In a quiescent environment, sub-micron size vesicles are found to form a doublet due to their Van der Waals' attractive interactions \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.
-Due to the strong Van der Waals' adhesive force, the vesicles are far
-from spherical shape and the membrane is almost flat in the ``contact" region. Gires {\it et al.} used small-deformation analysis to investigate the hydrodynamic
+Due to the strong Van der Waals' adhesive force, the vesicles are far from spherical shape and the membrane is almost flat in the ``contact" region.
+Gires {\it et al.} used small-deformation analysis to investigate the hydrodynamic
 interactions between two vesicles in a planar shear flow with a long separation distance \cite{GiresDankerMisbah2012_PRE}.
@@
 
-Boundary integral equations (BIEs) have a unique advantage that all the
-unknowns are on the boundary of the domain.  Therefore, resolving
-complex and dynamic geometries is straightforward.  Moreover, by using
-appropriate quadrature rules, high-order or spectral accuracy is
-obtained.  Finally, even though the resulting linear systems that need
-to be solved are dense, they can be solved with optimal complexity by
-using fast summation methods.  \todo[inline]{Time stepping}
+Boundary integral equation (BIE) approaches are well-suited for solving the low Re flow problems considered here as they lead to reduction in dimensionality and 
+achieve high-order accuracy even for moving geometry problems. When the vesicles adhere, one major issue for BIE solvers is to resolve the vesicle-vesicle hydrodynamic forces which become 
+{\em nearly singular}.
+In this work, we use the recently developed spectrally-accurate algorithm of \cite{barnett2015spectrally} for overcoming this problem.
+To overcome the numerical stiffness induced by the membrane bending forces,
+we extend the adaptive time-stepping scheme developed in \cite{quaife2016adaptive} to our setting.
 
@@
 \subsection{Adhesion Model}
-The adhesion model of Sukumaran and Seifert~\cite{suk-sei2001,
-RamachandranAndersonLealIsraelachvili2010_Langmuir} considers adhesion
+The adhesion model of Sukumaran and Seifert~\cite{suk-sei2001} considers adhesion
 between a single three-dimensional vesicle and a solid wall at $z=0$.

### 2019-01-09 vesicle_code/docs/adhesion/adhesion.tex
changes to extensional

--- 2019-01-07 vesicle_code/docs/adhesion/adhesion.tex
@@
 initially placed symmetrically on the $x$ axis in a quiescent flow
-($\chi = 0$).  Once they reach steady-state, the extensional background
-flow is started.  We use this example to characterize the required
-extensional rate to overcome the adhesive forces at for vesicles with
-different reduced areas.  For all the simulations, the length of the
-vesicles are fixed, while the area is changed to achieve the desired
-reduced area.
+($\chi = 0$).  Once they reach steady-state doublet, the extensional
+background flow is started.  We use this example to characterize the
+required extensional rate to overcome the adhesive forces of the
+doublet.  In particular, we investigate the effect of the reduced area.
+For all the simulations, the length of the vesicles are fixed, while the
+area is changed to achieve the desired reduced area.
+
+We observe three different vesicle configurations that depend on the
+reduced area and extensional rate.  First, the doublet is not broken and
+the individual vesicles long axis is parallel to the contracting
+direction (Figure~\ref{fig:extensional1}).  Second, the doublet is not
+broken, but it tilts to some inclination angle that is not parallel to
+either of the contracting or separation directions
+(Figure~\ref{fig:extensional3}).  Finally, if the extensional rate is
+sufficiently large, the doublet is broken and the vesicles tend to
+$(0,\pm \infty)$.
 
@@
   \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image06.png}
-  \caption{Two vesicles in an extensional flow.  The reduced area is
-  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
-is $0.4$, extensional rate is $\chi = 0.03$.}
+  \caption{\label{fig:extensional1} Two vesicles in an extensional flow.
+  The reduced area is $0.8$, the adhesion strength is $0.7$, and the
+  adhesion length scale is $0.4$, extensional rate is $\chi = 0.03$.}
 \end{figure}
@@
   \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image06.png}
-  \caption{Two vesicles in an extensional flow.  The reduced area is
-  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
-is $0.4$, extensional rate is $\chi = 0.05$.}
+  \caption{\label{fig:extensional2} Two vesicles in an extensional flow.
+  The reduced area is $0.8$, the adhesion strength is $0.7$, and the
+  adhesion length scale is $0.4$, extensional rate is $\chi = 0.05$.}
 \end{figure}
@@
   \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image06.png}
-  \caption{Two vesicles in an extensional flow.  The reduced area is
-  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
-is $0.4$, extensional rate is $\chi = 0.1$.  After time $t=400$, the
-  vesicles extensional rate has overcome the adhesive force, and the
-  vesicles continue to separate.}
+  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
+  The reduced area is $0.8$, the adhesion strength is $0.7$, and the
+  adhesion length scale is $0.4$, extensional rate is $\chi = 0.1$.
+  After time $t=400$, the vesicles extensional rate has overcome the
+  adhesive force, and the vesicles continue to separate.}
 \end{figure}

### 2019-01-09 vesicle_code/src/capsules.m

@@ -138,23 +138,32 @@ function adh = adhesionTerm(o,Wconst,d0)
 adh = zeros(2*o.N,o.nv);
 for k = 1:o.nv
   notk = [(1:k-1) (k+1:o.nv)];
+  % all vesicles except self
   adhesive_x = o.X(1:o.N,notk);
   adhesive_y = o.X(o.N+1:2*o.N,notk);
   ds = o.sa(:,notk)*2*pi/o.N;
+  % x and y coordinates and arclength of the adhesion source points
   
   for j = 1:o.N
     dist2 = (o.X(j,k) - adhesive_x).^2 + ...
         (o.X(j+o.N,k) - adhesive_y).^2;
-%    Dw = -Wconst * 4*d0^2.*(d0^2 - dist2)./dist2.^(2.5);
+    % distance squared
     Dw = -Wconst*4*d0^2.*(d0^2 - dist2)./dist2.^3;
+    % common term in the vector that is integrated in the adhesion model
 
     adh(j,k) = sum(sum(-Dw .* (o.X(j,k) - adhesive_x).*ds));
+    % adhesive force in the x direction
     adh(j+o.N,k) = sum(sum(-Dw .* (o.X(j+o.N,k) - adhesive_y).*ds));
+    % adhesive force in the y direction
   end
 
 end
 
 end % adhesionTerm
+
+
+
+
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 function [Ben,Ten,Div] = computeDerivs(o)

### 2019-01-09 vesicle_code/docs/adhesion/adhesion.tex
put in extensional doublet work

@@
 
-\newpage % so that the figures are more organized writing the paper
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{figure}[htp]
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image01.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image02.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image03.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image04.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image05.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image06.png}
+  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image01.png}
+  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image02.png}
+  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image03.png}
+  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image04.png}
+  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image05.png}
+  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image06.png}
   \caption{\label{fig:extensional1} Two vesicles in an extensional flow.
@@
 \begin{figure}[htp]
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image01.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image02.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image03.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image04.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image05.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image06.png}
+  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image01.png}
+  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image02.png}
+  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image03.png}
+  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image04.png}
+  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image05.png}
+  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image06.png}
   \caption{\label{fig:extensional2} Two vesicles in an extensional flow.
@@
 \begin{figure}[htp]
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image06.png}
+  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
+  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
+  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
+  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
+  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
+  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image06.png}
   \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
@@
 
+Whether the doublet is broken or not and the inclination angle of the
+doublet depends on the extensional rate and the vesicles' reduced area.
+A phase diagram of the steady-state configuration is in
+Figure~\ref{fig:extensionalPhaseDiagram}.  Final configurations that
+remain symmetric to the flow (Figure~\ref{fig:extensional1} are
+indicated by red dots, tilt to some inclination angle
+(Figure~\ref{fig:extensional2} are indicated by blue dots, and that
+separate (Figure~\ref{fig:extensional3}) are indicated by green dots.
+
 \begin{figure}[htp]
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image01.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image02.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image03.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image04.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image05.png}
-  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image06.png}
-  \caption{Two vesicles in an extensional flow.  The reduced area is
-  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
-is $0.4$, extensional rate is $\chi = 0.11$.}
+  \includegraphics[width=0.5\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
+  \caption{\label{fig:extensionalPhaseDiagram} Phase diagram of vesicle
+  hydrodynamics in an extensional flow.  At a fixed Hamaker constant
+  $\sigma=0.7$ and adhesion length scale $\delta=0.4$, doublets may
+  either remain symmetric to the flow (red marks), or tilt to some
+  inclination angle (blue dots), or the extensional rate, $\chi$, may
+  overcome the adhesive force (green dots).}
 \end{figure}
 
-%We consider two vesicles suspended in the extensional flow $\uu =
-%\chi(-x,y)$, where $\chi$ is the extensional rate.  The vesicles are
-%initially place symmetrically on the $y$ axis so that the background
-%velocity drives the vesicles towards one another.  We vary the reduced
-%area and the two vdW parameters and characterize the possible steady
-%state configurations.  For all the simulations, the length of the
-%vesicles are fixed, while the area is changed to achieve the desired
-%reduced area.
-%
-%\begin{figure}[htp]
-%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep1.pdf}
-%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep2.pdf}
-%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep3.pdf}
-%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep4.pdf}
-%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep5.pdf}
-%  \caption{Two vesicles in an extensional flow.  The reduced area is
-%  $0.40$, the adhesion strength is $1.0$, and the adhesion length scale
-%is $0.8$, background flow strength is $\chi = 10^{-2}$.}
-%\end{figure}
-%
-%\begin{figure}[htp]
-%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep1.pdf}
-%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep2.pdf}
-%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep3.pdf}
-%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep4.pdf}
-%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep5.pdf}
-%  \caption{Two vesicles in an extensional flow.  The reduced area is
-%  $0.90$, the adhesion strength is $1.0$, and the adhesion length scale
-%is $0.8$, background flow strength is $\chi = 10^{-2}$.}
-%\end{figure}
-
-\newpage % so that the figures are more organized writing the paper
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-01-09 vesicle_code/examples/output/makeImages.m

@@ -5,7 +5,7 @@ irate = 10; % controls the speed of the visualization
 
 if 1
 %  file = 'extensional2VesJData.bin';
-  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi1em1_ra075/extensional2VesData.bin';
+  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi7em2_ra075/extensional2VesData.bin';
   ax = [-4 4 -5 5];
   options.confined = false;
 end

### 2019-01-09 vesicle_code/docs/adhesion/adhesion.tex
updated fig 11
remove small-deformation
updated title

@@
 %
-\documentclass[aps,prl,twocolumn,showpacs,amsmath,amssymb]{revtex4-1}
+\documentclass[aps,prl,showpacs,amsmath,amssymb]{revtex4-1}
 
@@
 
-\title{Vesicle-vesicle adhesion in linear flows: dynamics and rheology}% Force line breaks with \\
+\title{Hydrodynamics and rheology of adhesive vesicle doublets}
+% Force line breaks with \\
 %\thanks{A footnote to the article title}%
@@
   \AA\xx:=-4 \sigma \delta^2\sum_{\substack{k=1 \\ k \neq j}}^M 
-  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^2} 
+  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^6} 
   \left(\delta^2 - \|\xx - \yy\|^2 \right) ds_\yy.
@@
 differing reduced areas.}
+  \todo[inline]{Make black marks larger and reference that they come
+  from Ghigliotti, Biben, Misbah 2010 JFM}
 \end{figure}
@@
 
-\section{Small Deformation Limit}
-\label{sec:appendixB}
-\todo[inline]{Used to validate the code/results}
+%\section{Small Deformation Analysis on a Single Vesicle in Linear Shear Flow}
+%\label{sec:appendixB}
+%\todo[inline]{Used to validate the code/results}
+%Hydrodynamics of a single vesicle in Stokes flow has been extensively investigated. 
+%In a planar shear flow, the vesicle hydrodynamics is characterized by
+%excess area (reduced volume), viscosity contrast between interior and exterior fluids, and shear rate of the imposed far-field fluid flow. 
+%%In addition a vesicle with a rigid particle inside is also investigated as a biological mimic of a 
+%%eukaryotic cell with a nucleus that occupies nearly half of the intracellular volume \cite{Veerapaneni2011_PRL}. 
+%Small-deformation analysis shows that
+%a vesicle tank-treads in a planar shear flow for low viscosity contrast and shear rate.
+At high viscosity contrast the tank-tread (TT) dynamics transitions to tumbling (TB) \cite{Misbah2006_PRL,Vlahovska2007_PRE} ,
+%and this leads to a transition in effective shear viscosity in the vesicle suspension \cite{Misbah2006_PRL,Vitkova2008_BJ} that is also validated
+%by direct numerical simulations \cite{GhigliottiBibenMisbah2010_JFM} and experiments \cite{KantslerSegreSteinberg2008_EPL,ZabuskySegreDeschamps2011_PoF}.
+%Between TT and TB vesicle hydrodynamics, a breathing (tremble) is also observed \cite{Misbah2006_PRL,KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2011_JFM,SpannZhaoShaqfeh2014_PoF} to affect the effective shear viscosity in a
+%different way.
+%Some of these theoretical results have inspired detailed comparison of rheology of a dilute vesicle suspension between direct numerical simulations and experiments.
+%Here we follow the small-deformation analysis by Finken {\it et al.} to derive the effective shear viscosity of a dilute suspension of TT vesicle in a planar shear flow.
+%The main results in the derivation carried out in the Mathematica run script (supplementary material) are summarized here.
+%For the homogeneous membrane tension of an inextensible two-dimensional vesicle (with an excess length $\triangle$) under a planar shear flow we found
+%\begin{equation}
+%\sigma_0 = -\frac{5}{2} + 
+%\end{equation}
+%
+%The effective shear viscosity of a single TT vesicle in a planar shear flow has been 
+%
+% studied and comparison between numerical simulations, small-deformation theory and experiments has been made.
+%Following the asymptotic analysis by Finken {\it et al.} \cite{Finken2008_EPL} we 
+%In an extensional flow (planar or uniaxial), vesicle shape dynamics
+%depends sensitively on the vesicle reduced volume  and the elastic capillary number \cite{KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2013_JFM,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}: Asymmetric shape and oscillatory undulation of the vesicle membrane are two examples of the complex vesicle hydrodynamics in an extensional flow.
 

### 2019-01-10 vesicle_code/docs/adhesion/adhesion.tex
worked on shear example

@@
 
+In the left plot of Figure~\ref{fig:shearIntrinsicViscosity}, we compare
+the intrinsic viscosity of a single tank treading vesicle to a doublet.
+To validate our simulations, we superimpose (black marks) the intrinsic
+viscosity calculated by Ghigliotti et
+al.~\cite{GhigliottiBibenMisbah2010_JFM}.  The presence of the doublet
+significant increases the intrinsic viscosity at all reduced areas.  To
+further characterize the effect of adhesion, in the right plot of
+Figure~\ref{fig:shearIntrinsicViscosity} we decompose the intrinsic
+viscosity into the contributions from the bending and tension, and the
+contribution from the adhesion.  We see that the effect of the adhesion
+on the intrinsic viscosity is largest for vesicles with small reduced
+areas.
+
 \begin{figure}[htp]
-  \includegraphics[scale=1]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
-  \caption{\label{fig:shearIntrinsicViscosity} The intrinsic viscosity
-  of a tank treading vesicle (blue) and a doublet (red).  The shear rate
-is $\chi = 0.5$, the Hamaker constant is $\sigma = 0.7$, and the
-adhesion length scale is $\delta = 0.4$.  The length of the vesicles at
-each of the reduced areas is fixed, while the area changes with
-differing reduced areas.}
-  \todo[inline]{Make black marks larger and reference that they come
-  from Ghigliotti, Biben, Misbah 2010 JFM}
+  \centering
+  \includegraphics[width=0.45\textwidth]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
+  \includegraphics[width=0.45\textwidth]{figs/doublet_decomp.pdf}
+  \caption{\label{fig:shearIntrinsicViscosity} {\em Left}: The intrinsic
+  viscosity of a tank treading vesicle (blue) and a doublet (red).  The
+  shear rate is $\chi = 0.5$, the Hamaker constant is $\sigma = 0.7$,
+  and the adhesion length scale is $\delta = 0.4$.  The length of the
+  vesicles at each of the reduced areas is fixed, while the area changes
+  with differing reduced areas.  The black marks denote intrinsic
+  viscosity values computed by Ghigliotti et
+  al.~\cite{GhigliottiBibenMisbah2010_JFM} (cf.~Figure 5).  {\em Right}:
+  The decomposition of the intrinsic viscosity into the contributions
+  for the bending and tension of the vesicles, and the contribution from
+  the vesicle adhesion.}
 \end{figure}
-\todo[inline]{Do the smaller reduced area doublets since the intrinsic
-viscosity seemed to increase as the reduced area was decresed further}
-\todo[inline]{Decompose the red curve as the intrinsic viscosity due to
-adhesion and due to the bending/tension}
 

### 2019-01-10 vesicle_code/docs/adhesion/adhesion.tex
touched up figure 11

@@
     -\log \rho + \frac{\rr \otimes \rr}{\rho^2} \right) 
-    \ff(\yy) ds_\yy, \quad \xx \in \RR^2.
+    \ff(\yy) ds_\yy, \quad \xx \in \RR^2,
   \label{eqn:SLP}
 \end{align}
-\todo[inline]{Define $\rr$ and other variables in
-equation~\eqref{eqn:SLP}}
-The traction jump of the velocity $\uu(\xx) = \SS[\ff](\xx)$ is the
-density function $\ff$, so the fluid velocity is $\xx \in \RR^2$ is
+where $\rr = \xx - \yy$ and $\rho = \|\rr\|$.  The traction jump of the
+velocity $\uu(\xx) = \SS[\ff](\xx)$ is the density function $\ff$, so
+the fluid velocity is $\xx \in \RR^2$ is
 \begin{align*}
@@
 al.~\cite{GhigliottiBibenMisbah2010_JFM}.  The presence of the doublet
-significant increases the intrinsic viscosity at all reduced areas.  To
-further characterize the effect of adhesion, in the right plot of
-Figure~\ref{fig:shearIntrinsicViscosity} we decompose the intrinsic
-viscosity into the contributions from the bending and tension, and the
-contribution from the adhesion.  We see that the effect of the adhesion
-on the intrinsic viscosity is largest for vesicles with small reduced
-areas.
+significantly increases the intrinsic viscosity at all the reduced
+areas.  To further characterize the effect of adhesion, in the right
+plot of Figure~\ref{fig:shearIntrinsicViscosity} we decompose the
+intrinsic viscosity into the contributions from the bending and tension
+(blue), and the contribution from the adhesion (red).  We also
+superimpose twice the intrinsic viscosity of a single tank treading
+vesicle (dashed curve) to demonstrate that the bending and tension of
+the doublet behaves similarly, but not identically, to a dilute
+suspensions of non-adhering tank-treading vesicles.  We see that the
+effect of the adhesion on the intrinsic viscosity is largest for
+vesicles with small reduced areas.
 
@@
   The decomposition of the intrinsic viscosity into the contributions
-  for the bending and tension of the vesicles, and the contribution from
-  the vesicle adhesion.}
+  for the bending and tension (blue) of the vesicles, and the
+  contribution from the vesicle adhesion (red).  Also included is twice
+  the intrinsic viscosity of a single tank-treading vesicle.}
 \end{figure}

### 2019-01-11 vesicle_code/docs/adhesion/adhesion.tex
worked on extensional example

@@
 In this work we focus on regimes where the ratio is of order unity, between the weak adhesion (ratio $\ll 1$) and strong adhesion (ratio $\gg 1$) regimes.
-In this regime the membrane deformation may increase the ``contact area'' between two vesicles and enhance the adhesion effects.
-The equilibration of vesicle membranes under adhesion in these regimes have been well studied and documented (see \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir} and references therein).
-However it is unclear how the adhesion couples to the vesicle hydrodynamics in such regime.
-Our work in this paper aims to address this question with quantitative characterization in terms of physical parameters.
+In this regime the membrane deformation may increase the ``contact
+area'' between two vesicles and enhance the adhesion effects. The
+equilibration of vesicle membranes under adhesion in these regimes have
+been well studied and documented
+(see~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir} and
+references therein). However it is unclear how the adhesion couples to
+the vesicle hydrodynamics in such regime.  Our work in this paper aims
+to address this question with quantitative characterization in terms of
+physical parameters.
 
@@
 
-In a quiescent environment, sub-micron size vesicles are found to form a doublet due to their Van der Waals' attractive interactions \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.
-Due to the strong Van der Waals' adhesive force, the vesicles are far from spherical shape and the membrane is almost flat in the ``contact" region.
-Gires {\it et al.} used small-deformation analysis to investigate the hydrodynamic
-interactions between two vesicles in a planar shear flow with a long separation distance \cite{GiresDankerMisbah2012_PRE}.
-They found that the vesicle interaction could be either attractive or repulsive depending on the organization of the two vesicles relative to the shear flow.
-To the best of authors' knowledge,
-the effects of close-range vesicle adhesion on their hydrodynamics under an external flow have not been studied and quantified. The goal of this work is to use
-state-of-the-art boundary integral simulations to numerically investigate the dynamics of two vesicles in both planar shear flow and extensional flow for a wide range of vesicle shapes and adhesive strength and distance.
+In a quiescent environment, sub-micron size vesicles are found to form a
+doublet due to their Van der Waals' attractive
+interactions~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.
+Due to the strong Van der Waals' adhesive force, the vesicles are far
+from spherical shape and the membrane is almost flat in the ``contact"
+region. Gires {\it et al.} used small-deformation analysis to
+investigate the hydrodynamic interactions between two vesicles in a
+planar shear flow with a long separation distance
+\cite{GiresDankerMisbah2012_PRE}. They found that the vesicle
+interaction could be either attractive or repulsive depending on the
+organization of the two vesicles relative to the shear flow. To the best
+of authors' knowledge, the effects of close-range vesicle adhesion on
+their hydrodynamics under an external flow have not been studied and
+quantified. The goal of this work is to use state-of-the-art boundary
+integral simulations to numerically investigate the dynamics of two
+vesicles in both planar shear flow and extensional flow for a wide range
+of vesicle shapes and adhesive strength and distance.
 
@@
 
+In Figure~\ref{fig:extensionalInclinationAngle}, we plot the inclination
+angle of a doublet formed by two vesicles of reduced area $0.70$ at four
+different extensional rates.
+
+\begin{figure}[htp]
+  \includegraphics[width=0.45\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
+  \todo[inline]{need a plot describing what the inclination angle
+  is}
+  \caption{\label{fig:extensionalInclinationAngle} The inclination angle
+  of a doublet formed by vesicles of reduced area $0.70$ submerged in an
+  extensional flow with an extensional rate of $\chi$.}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-01-13 vesicle_code/docs/adhesion/adhesion.tex
added some new images and worked on extensional

@@
 \begin{figure}[htp]
-  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image01.png}
-  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image02.png}
-  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image03.png}
-  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image04.png}
-  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image05.png}
-  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image06.png}
+  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
+  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
+  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
+  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
+  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}
   \caption{\label{fig:extensional1} Two vesicles in an extensional flow.
-  The reduced area is $0.8$, the adhesion strength is $0.7$, and the
-  adhesion length scale is $0.4$, extensional rate is $\chi = 0.03$.}
+  The reduced area is $0.7$, the adhesion strength is $0.7$, and the
+  adhesion length scale is $0.4$, extensional rate is $\chi = 0.02$.
+  The doublet tilts to an inclination angle.
+  }
 \end{figure}
@@
 \begin{figure}[htp]
-  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image01.png}
-  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image02.png}
-  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image03.png}
-  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image04.png}
-  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image05.png}
-  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image06.png}
+  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
+  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
+  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
+  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
+  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
   \caption{\label{fig:extensional2} Two vesicles in an extensional flow.
-  The reduced area is $0.8$, the adhesion strength is $0.7$, and the
-  adhesion length scale is $0.4$, extensional rate is $\chi = 0.05$.}
+  The reduced area is $0.7$, the adhesion strength is $0.7$, and the
+  adhesion length scale is $0.4$, extensional rate is $\chi = 0.07$.
+  The doublet tilts to an inclination angle.}
 \end{figure}
@@
 \begin{figure}[htp]
-  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
-  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
-  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
-  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
-  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
-  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image06.png}
+  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
+  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
+  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
+  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
+  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
   \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
-  The reduced area is $0.8$, the adhesion strength is $0.7$, and the
-  adhesion length scale is $0.4$, extensional rate is $\chi = 0.1$.
-  After time $t=400$, the vesicles extensional rate has overcome the
-  adhesive force, and the vesicles continue to separate.}
+  The reduced area is $0.7$, the adhesion strength is $0.7$, and the
+  adhesion length scale is $0.4$, extensional rate is $\chi = 0.1$.  The
+  vesicles extensional rate has overcome the adhesive force, and the
+  vesicles doublet is broken.}
 \end{figure}
@@
 \begin{figure}[htp]
-  \includegraphics[width=0.45\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
-  \todo[inline]{need a plot describing what the inclination angle
-  is}
-  \caption{\label{fig:extensionalInclinationAngle} The inclination angle
-  of a doublet formed by vesicles of reduced area $0.70$ submerged in an
-  extensional flow with an extensional rate of $\chi$.}
+  \centering
+  \includegraphics[height=0.4\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
+  \hfill
+  \includegraphics[height=0.4\textwidth]{figs/angleDefinition.pdf}
+  \caption{\label{fig:extensionalInclinationAngle} {\em Left}: The
+  inclination angle of a doublet formed by vesicles of reduced area
+  $0.70$ submerged in an extensional flow with an extensional rate of
+  $\chi$. {\em Right}: The definition of the inclination angle.  An
+  inclination angle of $\pi$ indicates a doublet whose long axis is
+  parallel to the converging direction, while an inclination angle of
+  $\pi/2$ indicates a doublet whose short axis is parallel to the
+  converging direction.}
 \end{figure}

### 2019-01-13 vesicle_code/examples/output/makeImages.m

@@ -1,11 +1,11 @@
 addpath ../../src
 set(0,'DefaultAxesFontSize',22)
 
-irate = 10; % controls the speed of the visualization
+irate = 30; % controls the speed of the visualization
 
 if 1
-%  file = 'extensional2VesData.bin';
-  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi2em2_ra070/extensional2VesData.bin';
+  file = 'extensional2VesGData.bin';
+  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi1em1_ra080/extensional2VesData.bin';
   ax = [-4 4 -5 5];
   options.confined = false;
 end
@@ -78,7 +78,7 @@ for k = istart:irate:iend
     clf
     plot(vec1,vec2,'r','linewidth',3)
     hold on;
-    plot(vec1(1:N/8:end,:),vec2(1:N/8:end,:),'b.','markersize',20)
+%    plot(vec1(1:N/8:end,:),vec2(1:N/8:end,:),'b.','markersize',20)
     if options.confined
       vec1 = [wallx(:,:);wallx(1,:)];
       vec2 = [wally(:,:);wally(1,:)];

### 2019-01-14 vesicle_code/docs/adhesion/adhesion.tex
some changes on e-flow and adhesion force

@@
 %
-\documentclass[aps,prl,showpacs,amsmath,amssymb]{revtex4-1}
+\documentclass[aps,prl,showpacs,amsmath,amssymb,superscriptaddress]{revtex4-1}
 
@@
 \author{Bryan Quaife}
- \email{bquaife@fsu.edu}
- \altaffiliation[]{Department of Scientific Computing \\ Florida State University}
+\affiliation{Department of Scientific Computing, Florida State University, Tallahassee, Florida, USA}
+% \email{bquaife@fsu.edu}
+% \altaffiliation[]{Department of Scientific Computing \\ Florida State University}
 \author{Shravan Veerapaneni}%
- \email{shravan@umich.edu}
-\altaffiliation{%
- Department of Mathematics \\
-University of Michigan, Ann Arbor
-}%
-\author{Yuan-Nan Young}%
- \email{yyoung@njit.edu}
-\altaffiliation{%
- Department of Mathematical Sciences \\
- New Jersey Institute of Technology
-}%
+% \email{shravan@umich.edu}
+\affiliation{Department of Mathematics, University of Michigan, Ann Arbor, Michigan, USA}%
+\author{Y.-N. Young}%
+ \email[Corresponding author: ]{yyoung@njit.edu}
+\affiliation{Department of Mathematical Sciences, Newark, NJ, USA}%
 
@@
 the one I had for my SIAM Life Sciences Talk}
-Their model uses the adhesion potential
-\begin{align*}
-  \phi(z) = \sigma\left(\frac{\delta}{z}\right)^2 \left[ 
-    \left(\frac{\delta}{z}\right)^2 - 2 \right],
-\end{align*}
+The adhesion potential in their model is of the functional form in equation~\ref{eq:adhesion_potential} with $(m,n) = (4,2)$:
+\begin{align}
+\label{eq:adhesion_potential}
+  \phi(z) = \sigma \left[ 
+    \left(\frac{\delta}{z}\right)^m - \frac{m}{n} \left(\frac{\delta}{z}\right)^n \right],
+\end{align}
 where $z$ is the distance between the solid wall and the vesicle,
@@
 \begin{align}
-  \AA\xx:=-4 \sigma \delta^2\sum_{\substack{k=1 \\ k \neq j}}^M 
-  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^6} 
-  \left(\delta^2 - \|\xx - \yy\|^2 \right) ds_\yy.
+  \AA\xx:=-\sigma m \delta^{n+1}\sum_{\substack{k=1 \\ k \neq j}}^M 
+  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+1}} 
+  \left(\delta^{m-n} - \|\xx - \yy\|^{m-n} \right) ds_\yy.
   \label{eqn:adhesionForce}
 \end{align}
+
+%\begin{align}
+%  \AA\xx:=-4 \sigma \delta^2\sum_{\substack{k=1 \\ k \neq j}}^M 
+%  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^6} 
+%  \left(\delta^2 - \|\xx - \yy\|^2 \right) ds_\yy.
+%  \label{eqn:adhesionForce}
+%\end{align}
+
+The exponents $(m,n)$ depend on the geometry of the two objects under adhesion \cite{Book_IntermolecularSurfaceForces}: $(m,n)=(4,2)$ corresponds to two
+flat, planar surfaces interacting with each under a long-range attraction and a short-range repulsion. On the other hand, $(m,n) = (12,6)$ corresponds to the L-J potential between
+two molecules. The adhesion potential in  the integral of equation~\ref{eqn:adhesionForce} is between two small patches of lipid bilayer membrane. Thus we argue that
+a reasonable choice for $(m,n)$ is between $(m,n) = (4,2)$ and $(m,n) = (12,6)$.
 
@@
 \label{sec:eflow} 
+The hydrodynamics of a single vesicle in an 
+extensional flow has revealed novel nonlinear vesicle dynamics not found for a viscous drop \cite{KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2013_JFM,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}.
+The stagnation point (zero-velocity point) in an extensional flow is a saddle point where two laminar streams converge along an axis and then diverge in a
+different direction. 
+With an active control algorithm to fix the position of the stagnation point by adjusting the streaming flow strength with a feedback loop \cite{Johnson-Chavarria2011_EMJ},
+a particle can be trapped at the stagnation point for long time scales to facilitate
+image acquisition or other detailed measures such as PIV of flow inside/around the particle.
+To explore the application of such fluid trap to measure the adhesion strength between two bound vesicle membranes, we propose the following thought experiment.
+
+We begin from two vesicles forming a doublet under an adhesion potential in a quiescent flow as in \S~\ref{sec:qflow}. 
+Once a doublet forms and reaches an equilibrium configuration, we turn on 
+the fluid trap with the stagnation point placed at the center of the vesicle doublet.
+For simplification we assume that each vesicle in the doublet has the same reduced area, membrane area, and bending stiffness.
+At low extensional rate, we expect the vesicle doublet to stay bound at the fluid trap stagnation point.
+On the other hand, the vesicle doublet may become unstable and eventually separate at a high extensional rate.
+Thus we expect there to exist a critical extensional rate above which the vesicle doublet cannot stay bound under a given adhesion potential.
+The dependence of the critical extensional rate on the adhesion potential and the mechanical vesicle properties thus provides a means to probe the physics of membrane adhesion.
+
 We consider two vesicles suspended in the extensional flow $\uu =
@@
 \begin{align*}
-  \phi(z) = \sigma\left(\frac{\delta}{z}\right)^2 \left[ 
-    \left(\frac{\delta}{z}\right)^2 - 2 \right],
+  \phi(z) = \sigma \left[ 
+    \left(\frac{\delta}{z}\right)^m - \frac{m}{n}\left(\frac{\delta}{z}\right)^n \right],
 \end{align*}
@@
 Perturbing $\xx_1$ to $\tilde{\xx}_1 = \xx_1 +  \delta \xx_1$, results
-in a new vesicle $\tilde{\gamma}_1$, and the perturbed adhesive energy
-is
+in a new vesicle $\tilde{\gamma}_1$, and the perturbed adhesive energy is
 \begin{align*}
@@
 and the adhesive force applied by vesicle 2 on vesicle 1 is
+\begin{align}
+ \int_{\gamma_2}\nabla \phi(\|\xx_1 - \xx_2\|)ds_{\xx_2} = -m \sigma\delta^{n+1}
+   \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+1}} 
+  \left(\delta^{m-n} - \|\xx - \yy\|^{m-n} \right) ds_\yy.
+  \end{align}
+When $(m,n) = (4,2)$, the above express becomes
 \begin{align*}

### 2019-01-14 vesicle_code/docs/adhesion/adhesion.tex
some more from yn
added some todos

@@
 \todo[inline]{$\sigma$ is overdefined as the Hamacher constant, and the
-tension, and possibly the stress}
+tension, and possibly the stress.  Replace Hamacher constant with $H$.}
+
+\todo[inline]{In the xtensional flow, put a plus sign after the 0.
+Indicate the flow with arrows.  Do the same for the shear and Figure 9
+(right).}
 

### 2019-01-14 vesicle_code/docs/adhesion/adhesion.tex
changes in intro and misc by yny

@@
 %
-\documentclass[aps,prl,showpacs,amsmath,amssymb,superscriptaddress]{revtex4-1}
+\documentclass[aps,prb,showpacs,amsmath,amssymb,superscriptaddress]{revtex4-1}
 
@@
 %Experiments are performed to study vesicle hydrodynamics under various flowing conditions or forcing configurations \cite{MaderVitkova2006_EurPhysJE, Abkarian2008_SoftMatt,DahlNarsimhanGouveia2016_SoftMatt}.
-Collective vesicle hydrodynamics naturally is dictated by the individual vesicle-vesicle interactions;  for example, 
-it was shown recently that vesicles may align to form chains along the direction of the externally applied DC electric field with ensuing consequences to suspension rheology \cite{wu2018pairwise}.
-
-In numerical simulations of vesicle suspensions, it is often assumed that the lubrication layer between vesicle membranes acts to keep the 
-membrane-membrane interaction, such as the van der Waals type interaction, negligible.
-However the amphiphilic natures of lipid molecules (a hydrophobic tail and a hydrophilic head with an electric dipole) complicate the interactions between a lipid bilayer membrane and a solid (such as a glass substrate or a nano particle) or another bilayer membrane \cite{EvansMetcalfe1984_BJ,Book_PhysicalBasisCellAdhesion,Book_IntermolecularSurfaceForces}.
+
+Hydrodynamics of a single vesicle in Stokes flow has been extensively investigated. In a planar shear flow, the vesicle hydrodynamics is characterized by
+excess area (reduced volume), viscosity contrast between interior and exterior fluids, and shear rate of the imposed far-field fluid flow. In addition a vesicle
+with a rigid particle inside is also investigated as a biological mimic of a 
+eukaryotic cell with a nucleus that occupies nearly half of the intracellular volume \cite{Veerapaneni2011_PRL}. Small-deformation analysis shows that
+a vesicle tank-treads in a planar shear flow for low viscosity contrast and shear rate.
+At high viscosity contrast the tank-tread (TT) dynamics transitions to tumbling (TB) \cite{Misbah2006_PRL,Vlahovska2007_PRE},
+and this leads to a transition in effective shear viscosity in the vesicle suspension \cite{Misbah2006_PRL,Vitkova2008_BJ} that is also validated
+by direct numerical simulations \cite{GhigliottiBibenMisbah2010_JFM} and experiments \cite{KantslerSegreSteinberg2008_EPL,ZabuskySegreDeschamps2011_PoF}.
+Between TT and TB vesicle hydrodynamics, a breathing (tremble) is also observed \cite{Misbah2006_PRL,KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2011_JFM,SpannZhaoShaqfeh2014_PoF} to affect the effective shear viscosity in a
+different way.
+In an extensional flow (planar or uniaxial), vesicle shape dynamics
+depends sensitively on the vesicle reduced volume  and the elastic capillary number \cite{KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2013_JFM,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}: Asymmetric shape and oscillatory undulation of the vesicle membrane are two examples of the complex vesicle hydrodynamics in an extensional flow.
+
+Collective dynamics of vesicless naturally is dictated by the individual vesicle-vesicle interactions.
+%
+% for example, 
+%it was shown recently that vesicles may align to form chains along the direction of the externally applied DC electric field with ensuing consequences to suspension rheology \cite{wu2018pairwise}.
+%
+In numerical simulations of vesicle suspensions, it is often assumed that the liquid film between vesicles acts to keep the
+membrane-membrane interaction, such as the van der Waals type adhesive interaction, negligible.
+However the amphiphilic natures of lipid molecules (a hydrophobic tail and a hydrophilic head with an electric dipole) complicate the interactions between a lipid bilayer membrane and 
+another bilayer membrane \cite{EvansMetcalfe1984_BJ,Book_PhysicalBasisCellAdhesion,Book_IntermolecularSurfaceForces} or
+a solid (such as a glass substrate or a nano particle).
 Studies confirmed that such interaction potential inevitably consists of a long-range attraction component and a short-range repulsion component 
-\cite{Book_IntermolecularSurfaceForces}. Such interactions leads to adhesion at the separation distance that minimizes the
-interaction potential \cite{Book_IntermolecularSurfaceForces}, and are essential in many biomedical, biological and biophysical processes.
+\cite{Book_IntermolecularSurfaceForces}, and the combination of the two gives rise to adhesion at the separation distance that minimizes the
+interaction potential \cite{Book_IntermolecularSurfaceForces}. Such adhesive potentials are essential in many biomedical, biological and biophysical processes.
 For example, vesicle adhesion is essential for membrane fusion/fission in endocytosis and exocytosis, the transport of small
@@
 
-This paper is organized as follows.
+This paper is organized as follows. In \S~\ref{sec:ge} we formulate our model for vesicle hydrodynamics with adhesive interactions  between membranes of distinct vesicles. 
+We simulate the adhesion process of two vesicles in a quiescent flow in \S~\ref{sec:qflow}, where we also present a simple model to estimate how long it takes for two nearby
+vesicles to reach an equilibrium configuration under adhesion. In \S~\ref{sec:eflow} we numerically investigate the hydrodynamics of a vesicle doublet in a fluid trap where the
+stagnation point is actively controlled to be at the center of the vesicle doublet. From these results we propose a novel application of the microfluidic fluid trap to probe the 
+adhesion strength between lipid bilayer membranes in solutions. In \S~\ref{sec:sflow} we investigate how two vesicles may  form a doublet as they move
+toward each other under a planar shear flow.  We map out the parameter regions for bound/unbound vesicles under a planar shear flow, and we also investigate the effects of
+adhesive interactions on the rheological properties of a dilute suspension of vesicle doublets. 
+Finally in \S~\ref{sec:conclusions} we discuss the implications of our results and point out a few
+potential future directions.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Governing Equations}
+\section{Governing Equations \label{sec:ge}}
 We consider suspensions of locally inextensible vesicles in an unbounded
@@
 \begin{align}
-  \AA\xx:=-\sigma m \delta^{n+1}\sum_{\substack{k=1 \\ k \neq j}}^M 
-  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+1}} 
+  \AA\xx:=-\sigma m \delta^{n}\sum_{\substack{k=1 \\ k \neq j}}^M 
+  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+2}} 
   \left(\delta^{m-n} - \|\xx - \yy\|^{m-n} \right) ds_\yy.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
+\section{Conclusions\label{sec:conclusions}}
 \todo[inline]{Concluding remarks}
@@
 \begin{align}
- \int_{\gamma_2}\nabla \phi(\|\xx_1 - \xx_2\|)ds_{\xx_2} = -m \sigma\delta^{n+1}
-   \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+1}} 
+ \int_{\gamma_2}\nabla \phi(\|\xx_1 - \xx_2\|)ds_{\xx_2} = -m \sigma\delta^{n}
+   \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+2}} 
   \left(\delta^{m-n} - \|\xx - \yy\|^{m-n} \right) ds_\yy.

### 2019-01-14 vesicle_code/docs/adhesion/adhesion.tex
started some small latex changes

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\todo[inline]{$\sigma$ is overdefined as the Hamacher constant, and the
-tension, and possibly the stress.  Replace Hamacher constant with $H$.}
-
-\todo[inline]{In the xtensional flow, put a plus sign after the 0.
+\todo[inline]{In the extensional flow, put a plus sign after the 0.
 Indicate the flow with arrows.  Do the same for the shear and Figure 9
@@
 %
-The ever expanding applications have encouraged detailed experimental, theoretical and numerical investigations of vesicle hydrodynamics
-in applied flow, electric and magnetic fields.
-Theoretical investigations often take the form of small-deformation analysis or spheroidal dynamics of a nearly-spherical vesicle (or nearly-circular in two dimensions) subjected to an applied flow or under an external forcing \cite{Barthes-BieselRallison1981_JFM,Misbah2006_PRL,Vlahovska2007_PRE,Finken2008_EPL,ZhangZahnTanLin2013_PoF,Nganguia2013_PRE}.
-On the other hand, various numerical methods have been developed for simulating the transient hydrodynamics of vesicle suspensions  \cite{BagchiJohoson2005_JBE,Biben2005_EJP,Veerapaneni2009_JCP,SeolHuKimLai2016_JCP}.
+The ever expanding applications have encouraged detailed experimental,
+theoretical and numerical investigations of vesicle hydrodynamics in
+applied flow, electric and magnetic fields. Theoretical investigations
+often take the form of small-deformation analysis or spheroidal dynamics
+of a nearly-spherical vesicle (or nearly-circular in two dimensions)
+subjected to an applied flow or under an external
+forcing~\cite{Barthes-BieselRallison1981_JFM,Misbah2006_PRL,Vlahovska2007_PRE,Finken2008_EPL,ZhangZahnTanLin2013_PoF,Nganguia2013_PRE}.
+On the other hand, various numerical methods have been developed for
+simulating the transient hydrodynamics of vesicle
+suspensions~\cite{BagchiJohoson2005_JBE,Biben2005_EJP,Veerapaneni2009_JCP,SeolHuKimLai2016_JCP}.  
 %Experiments are performed to study vesicle hydrodynamics under various flowing conditions or forcing configurations \cite{MaderVitkova2006_EurPhysJE, Abkarian2008_SoftMatt,DahlNarsimhanGouveia2016_SoftMatt}.
 
-Hydrodynamics of a single vesicle in Stokes flow has been extensively investigated. In a planar shear flow, the vesicle hydrodynamics is characterized by
-excess area (reduced volume), viscosity contrast between interior and exterior fluids, and shear rate of the imposed far-field fluid flow. In addition a vesicle
-with a rigid particle inside is also investigated as a biological mimic of a 
-eukaryotic cell with a nucleus that occupies nearly half of the intracellular volume \cite{Veerapaneni2011_PRL}. Small-deformation analysis shows that
-a vesicle tank-treads in a planar shear flow for low viscosity contrast and shear rate.
-At high viscosity contrast the tank-tread (TT) dynamics transitions to tumbling (TB) \cite{Misbah2006_PRL,Vlahovska2007_PRE},
-and this leads to a transition in effective shear viscosity in the vesicle suspension \cite{Misbah2006_PRL,Vitkova2008_BJ} that is also validated
-by direct numerical simulations \cite{GhigliottiBibenMisbah2010_JFM} and experiments \cite{KantslerSegreSteinberg2008_EPL,ZabuskySegreDeschamps2011_PoF}.
-Between TT and TB vesicle hydrodynamics, a breathing (tremble) is also observed \cite{Misbah2006_PRL,KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2011_JFM,SpannZhaoShaqfeh2014_PoF} to affect the effective shear viscosity in a
-different way.
-In an extensional flow (planar or uniaxial), vesicle shape dynamics
-depends sensitively on the vesicle reduced volume  and the elastic capillary number \cite{KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2013_JFM,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}: Asymmetric shape and oscillatory undulation of the vesicle membrane are two examples of the complex vesicle hydrodynamics in an extensional flow.
-
-Collective dynamics of vesicless naturally is dictated by the individual vesicle-vesicle interactions.
+Hydrodynamics of a single vesicle in Stokes flow has been extensively
+investigated. In a planar shear flow, the vesicle hydrodynamics is
+characterized by excess area (reduced volume), viscosity contrast
+between interior and exterior fluids, and shear rate of the imposed
+far-field fluid flow. In addition a vesicle with a rigid particle inside
+is also investigated as a biological mimic of a eukaryotic cell with a
+nucleus that occupies nearly half of the intracellular
+volume~\cite{Veerapaneni2011_PRL}. Small-deformation analysis shows that
+a vesicle tank-treads in a planar shear flow for low viscosity contrast
+and shear rate. At high viscosity contrast the tank-tread (TT) dynamics
+transitions to tumbling (TB)~\cite{Misbah2006_PRL,Vlahovska2007_PRE},
+and this leads to a transition in effective shear viscosity in the
+vesicle suspension~\cite{Misbah2006_PRL,Vitkova2008_BJ} that is also
+validated by direct numerical
+simulations~\cite{GhigliottiBibenMisbah2010_JFM} and
+experiments~\cite{KantslerSegreSteinberg2008_EPL,ZabuskySegreDeschamps2011_PoF}.
+Between TT and TB vesicle hydrodynamics, a breathing (tremble) is also
+observed~\cite{Misbah2006_PRL,KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2011_JFM,SpannZhaoShaqfeh2014_PoF}
+to affect the effective shear viscosity in a different way.  In an
+extensional flow (planar or uniaxial), vesicle shape dynamics depends
+sensitively on the vesicle reduced volume  and the elastic capillary
+number~\cite{KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2013_JFM,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}:
+Asymmetric shape and oscillatory undulation of the vesicle membrane are
+two examples of the complex vesicle hydrodynamics in an extensional
+flow.
+
+Collective dynamics of vesicles naturally is dictated by the individual vesicle-vesicle interactions.
 %
@@
 %
-In numerical simulations of vesicle suspensions, it is often assumed that the liquid film between vesicles acts to keep the
-membrane-membrane interaction, such as the van der Waals type adhesive interaction, negligible.
-However the amphiphilic natures of lipid molecules (a hydrophobic tail and a hydrophilic head with an electric dipole) complicate the interactions between a lipid bilayer membrane and 
-another bilayer membrane \cite{EvansMetcalfe1984_BJ,Book_PhysicalBasisCellAdhesion,Book_IntermolecularSurfaceForces} or
-a solid (such as a glass substrate or a nano particle).
-Studies confirmed that such interaction potential inevitably consists of a long-range attraction component and a short-range repulsion component 
-\cite{Book_IntermolecularSurfaceForces}, and the combination of the two gives rise to adhesion at the separation distance that minimizes the
-interaction potential \cite{Book_IntermolecularSurfaceForces}. Such adhesive potentials are essential in many biomedical, biological and biophysical processes.
-For example, vesicle adhesion is essential for membrane fusion/fission in endocytosis and exocytosis, the transport of small
+In numerical simulations of vesicle suspensions, it is often assumed
+that the liquid film between vesicles acts to keep the membrane-membrane
+interaction, such as the van der Waals type adhesive interaction,
+negligible.  However the amphiphilic natures of lipid molecules (a
+hydrophobic tail and a hydrophilic head with an electric dipole)
+complicate the interactions between a lipid bilayer membrane and another
+bilayer
+membrane~\cite{EvansMetcalfe1984_BJ,Book_PhysicalBasisCellAdhesion,Book_IntermolecularSurfaceForces}
+or a solid (such as a glass substrate or a nano particle).  Studies
+confirmed that such interaction potential inevitably consists of a
+long-range attraction component and a short-range repulsion
+component~\cite{Book_IntermolecularSurfaceForces}, and the combination
+of the two gives rise to adhesion at the separation distance that
+minimizes the interaction
+potential~\cite{Book_IntermolecularSurfaceForces}. Such adhesive
+potentials are essential in many biomedical, biological and biophysical
+processes.  For example, vesicle adhesion is essential for membrane
+fusion/fission in endocytosis and exocytosis, the transport of small
 vesicles through membrane surfaces.
@@
 %
-Adhesion between a vesicle and a substrate has been extensively studied, primarily focused on analyzing the static equilibrium shapes \cite{Seifert1990_PRA, ShiFengGao2006_ActaMechSin, LinFreund2007_IntJSolidsStructures, das2008adhesion, zhang2009phase} than the the transient adhesion process; exceptions include \cite{cantat1999lift, suk-sei2001, BlountMiksisDavis2013_PRSa}.
-Adhesion between bilayer membranes was first experimentally observed by Evans and Metcalfe \cite{EvansMetcalfe1984_BJ}, who measured 
-the reduction in the free energy per unit area of membrane-membrane contact formation due to the Van der Waals' attraction. For a membrane-membrane
-separation distance of $\sim 3$ nm, they estimated that the Hamaker constant is approximately $5.8\times 10^{-14}$ ergs, which corresponds to an adhesion energy density around $1$ mJ/m$^2$.
-The ratio of adhesion energy per unit area to the bending energy (bending rigidity of lipid bilayer membranes $\sim 10^{-19}$ J) gives a measure of vesicle deformation in the presence of adhesion \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.
-In this work we focus on regimes where the ratio is of order unity, between the weak adhesion (ratio $\ll 1$) and strong adhesion (ratio $\gg 1$) regimes.
-In this regime the membrane deformation may increase the ``contact
-area'' between two vesicles and enhance the adhesion effects. The
-equilibration of vesicle membranes under adhesion in these regimes have
-been well studied and documented
+Adhesion between a vesicle and a substrate has been extensively studied,
+primarily focused on analyzing the static equilibrium
+shapes~\cite{Seifert1990_PRA, ShiFengGao2006_ActaMechSin,
+LinFreund2007_IntJSolidsStructures, das2008adhesion, zhang2009phase}
+than the transient adhesion process; exceptions
+include~\cite{cantat1999lift, suk-sei2001, BlountMiksisDavis2013_PRSa}.
+Adhesion between bilayer membranes was first experimentally observed by
+Evans and Metcalfe~\cite{EvansMetcalfe1984_BJ}, who measured the
+reduction in the free energy per unit area of membrane-membrane contact
+formation due to the Van der Waals' attraction. For a membrane-membrane
+separation distance of $\sim 3$ nm, they estimated that the Hamaker
+constant is approximately $5.8\times 10^{-14}$ ergs, which corresponds
+to an adhesion energy density around $1$ mJ/m$^2$. The ratio of adhesion
+energy per unit area to the bending energy (bending rigidity of lipid
+bilayer membranes $\sim 10^{-19}$ J) gives a measure of vesicle
+deformation in the presence of
+adhesion~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}. In
+this work we focus on regimes where the ratio is of order unity, between
+the weak adhesion (ratio $\ll 1$) and strong adhesion (ratio $\gg 1$)
+regimes.  In this regime the membrane deformation may increase the
+``contact area'' between two vesicles and enhance the adhesion effects.
+The equilibration of vesicle membranes under adhesion in these regimes
+have been well studied and documented
 (see~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir} and
@@
 investigate the hydrodynamic interactions between two vesicles in a
-planar shear flow with a long separation distance
-\cite{GiresDankerMisbah2012_PRE}. They found that the vesicle
+planar shear flow with a long separation
+distance~\cite{GiresDankerMisbah2012_PRE}. They found that the vesicle
 interaction could be either attractive or repulsive depending on the
@@
 
-Boundary integral equation (BIE) approaches are well-suited for solving the low Re flow problems considered here as they lead to reduction in dimensionality and 
-achieve high-order accuracy even for moving geometry problems. When the vesicles adhere, one major issue for BIE solvers is to resolve the vesicle-vesicle hydrodynamic forces which become 
-{\em nearly singular}.
-In this work, we use the recently developed spectrally-accurate algorithm of \cite{barnett2015spectrally} for overcoming this problem.
-To overcome the numerical stiffness induced by the membrane bending forces,
-we extend the adaptive time-stepping scheme developed in \cite{quaife2016adaptive} to our setting.
-
-This paper is organized as follows. In \S~\ref{sec:ge} we formulate our model for vesicle hydrodynamics with adhesive interactions  between membranes of distinct vesicles. 
-We simulate the adhesion process of two vesicles in a quiescent flow in \S~\ref{sec:qflow}, where we also present a simple model to estimate how long it takes for two nearby
-vesicles to reach an equilibrium configuration under adhesion. In \S~\ref{sec:eflow} we numerically investigate the hydrodynamics of a vesicle doublet in a fluid trap where the
-stagnation point is actively controlled to be at the center of the vesicle doublet. From these results we propose a novel application of the microfluidic fluid trap to probe the 
-adhesion strength between lipid bilayer membranes in solutions. In \S~\ref{sec:sflow} we investigate how two vesicles may  form a doublet as they move
-toward each other under a planar shear flow.  We map out the parameter regions for bound/unbound vesicles under a planar shear flow, and we also investigate the effects of
-adhesive interactions on the rheological properties of a dilute suspension of vesicle doublets. 
-Finally in \S~\ref{sec:conclusions} we discuss the implications of our results and point out a few
-potential future directions.
+Boundary integral equation (BIE) approaches are well-suited for solving
+the low Re flow problems considered here as they lead to reduction in
+dimensionality and achieve high-order accuracy even for moving geometry
+problems. When the vesicles adhere, one major issue for BIE solvers is
+to resolve the vesicle-vesicle hydrodynamic forces which become {\em
+nearly singular}. In this work, we use the recently developed
+spectrally-accurate algorithm of~\cite{barnett2015spectrally} for
+overcoming this problem. To overcome the numerical stiffness induced by
+the membrane bending forces, we extend the adaptive time-stepping scheme
+developed in~\cite{quaife2016adaptive} to our setting.
+
+This paper is organized as follows. In \S~\ref{sec:ge} we formulate our
+model for vesicle hydrodynamics with adhesive interactions  between
+membranes of distinct vesicles.  We simulate the adhesion process of two
+vesicles in a quiescent flow in \S~\ref{sec:qflow}, where we also
+present a simple model to estimate how long it takes for two nearby
+vesicles to reach an equilibrium configuration under adhesion. In
+\S~\ref{sec:eflow} we numerically investigate the hydrodynamics of a
+vesicle doublet in a fluid trap where the stagnation point is actively
+controlled to be at the center of the vesicle doublet. From these
+results we propose a novel application of the microfluidic fluid trap to
+probe the adhesion strength between lipid bilayer membranes in
+solutions. In \S~\ref{sec:sflow} we investigate how two vesicles may
+form a doublet as they move toward each other under a planar shear flow.
+We map out the parameter regions for bound/unbound vesicles under a
+planar shear flow, and we also investigate the effects of adhesive
+interactions on the rheological properties of a dilute suspension of
+vesicle doublets.  Finally in \S~\ref{sec:conclusions} we discuss the
+implications of our results and point out a few potential future
+directions.
 
@@
 \todo[inline]{Need a cartoon picture in here.  Some kind of version of
-the one I had for my SIAM Life Sciences Talk}
-The adhesion potential in their model is of the functional form in equation~\ref{eq:adhesion_potential} with $(m,n) = (4,2)$:
+the one I had for my SIAM Life Sciences Talk} The adhesion potential in
+their model is of the functional form in
+equation~\eqref{eq:adhesion_potential} with $(m,n) = (4,2)$:
 \begin{align}
 \label{eq:adhesion_potential}
-  \phi(z) = \sigma \left[ 
+  \phi(z) = H \left[ 
     \left(\frac{\delta}{z}\right)^m - \frac{m}{n} \left(\frac{\delta}{z}\right)^n \right],
@@
 where $z$ is the distance between the solid wall and the vesicle,
-$\sigma$ is the Hamaker constant, and $\delta$ is the adhesion length
+$H$ is the Hamaker constant, and $\delta$ is the adhesion length
 scale.  We generalize this model to an unbounded suspension of vesicles.
@@
 \begin{align}
-  \AA\xx:=-\sigma m \delta^{n}\sum_{\substack{k=1 \\ k \neq j}}^M 
+  \AA\xx:=-H m \delta^{n}\sum_{\substack{k=1 \\ k \neq j}}^M 
   \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+2}} 
@@
 %\begin{align}
-%  \AA\xx:=-4 \sigma \delta^2\sum_{\substack{k=1 \\ k \neq j}}^M 
+%  \AA\xx:=-4 H \delta^2\sum_{\substack{k=1 \\ k \neq j}}^M 
 %  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^6} 
@@
 
-The exponents $(m,n)$ depend on the geometry of the two objects under adhesion \cite{Book_IntermolecularSurfaceForces}: $(m,n)=(4,2)$ corresponds to two
-flat, planar surfaces interacting with each under a long-range attraction and a short-range repulsion. On the other hand, $(m,n) = (12,6)$ corresponds to the L-J potential between
-two molecules. The adhesion potential in  the integral of equation~\ref{eqn:adhesionForce} is between two small patches of lipid bilayer membrane. Thus we argue that
-a reasonable choice for $(m,n)$ is between $(m,n) = (4,2)$ and $(m,n) = (12,6)$.
+The exponents $(m,n)$ depend on the geometry of the two objects under
+adhesion~\cite{Book_IntermolecularSurfaceForces}: $(m,n)=(4,2)$
+corresponds to two flat, planar surfaces interacting with each under a
+long-range attraction and a short-range repulsion. On the other hand,
+$(m,n) = (12,6)$ corresponds to the L-J potential between two molecules.
+The adhesion potential in  the integral of
+equation~\eqref{eqn:adhesionForce} is between two small patches of lipid
+bilayer membrane. Thus we argue that a reasonable choice for $(m,n)$ is
+between $(m,n) = (4,2)$ and $(m,n) = (12,6)$.
 
@@
 
-When two vesicles move towards (or away from) each other under a constant force $F$ without any external fluid flow, the height  $(h)$ of the thin liquid film between two vesicles follows the
-draining dynamics \cite{RamachandranLeal2010_PoF}
+When two vesicles move towards (or away from) each other under a
+constant force $F$ without any external fluid flow, the height $(h)$ of
+the thin liquid film between two vesicles follows the draining
+dynamics~\cite{RamachandranLeal2010_PoF}
 \begin{equation}
@@
 \end{equation}
-where $K_a$ is the area expansion modulus, $\mu$ is the viscosity of exterior fluid, $R_0$ is the radius of the undeformed vesicle.
-For the case of a constant forcing $F$ (independent of separation distance $h$ and time $t$), equation~\ref{eq:dhdt} can be easily integrated to give
+where $K_a$ is the area expansion modulus, $\mu$ is the viscosity of
+exterior fluid, $R_0$ is the radius of the undeformed vesicle.  For the
+case of a constant forcing $F$ (independent of separation distance $h$
+and time $t$), equation~\eqref{eq:dhdt} can be easily integrated to give
 a relation between film thickness $h$ and time $t$:
@@
 where $h(0)$ is the vesicle separation at $t=0$.
-We note that $F< (>) 0$ for an attractive  (repulsive) interaction between two vesicles,  and consequently $h(t)$ decreases (increases) from  the initial separation distance $h(0)$. 
-When the force is attractive, $h$ decreases monotonically and $t$ in the above
-equation is the
-draining time that diverges as $h\rightarrow 0$.
+We note that $F< (>) 0$ for an attractive  (repulsive) interaction
+between two vesicles,  and consequently $h(t)$ decreases (increases)
+from  the initial separation distance $h(0)$.  When the force is
+attractive, $h$ decreases monotonically and $t$ in the above equation is
+the draining time that diverges as $h\rightarrow 0$.
 %Similarly $F>0$ for a repulsive force and consequently $h(t) > h(0)$.
@@
 \label{eq:Fh}
-F(h) \sim \sigma \frac{\delta^m}{h^{m+1}}\left(\left(\frac{\delta}{h}\right)^2-1\right),
+F(h) \sim H \frac{\delta^m}{h^{m+1}}\left(\left(\frac{\delta}{h}\right)^2-1\right),
 \end{equation}
-attraction is dominant at ``large" scales ($h > \delta$) while repulsion is dominant at ``small" scales ($h<\delta$).
-Integration of equation~\ref{eq:dhdt} with the above $F(h)$ gives the relationship between $t$ and $h$.
-In this case the relationship involves an integral of a function of dimensionless $\bar{h} \equiv h/\delta$:
+attraction is dominant at ``large" scales ($h > \delta$) while repulsion
+is dominant at ``small" scales ($h<\delta$).  Integration of
+equation~\eqref{eq:dhdt} with the above $F(h)$ gives the relationship
+between $t$ and $h$.  In this case the relationship involves an integral
+of a function of dimensionless $\bar{h} \equiv h/\delta$:
 \begin{align}
-t\frac{K_a^{2/3}}{\mu R_0^{10/3}}& = \int^{h(t)}_{h(0)}-\frac{dh}{h^3 F^{1/3}} = -\frac{1}{\sigma^{1/3}\delta^{5/3}}\int^{\bar{h}(t)}_{\bar{h}(0)}\frac{d \bar{h}}{\bar{h}^{(8-m)/3}(\bar{h}^2-1)^{1/3}},
+t\frac{K_a^{2/3}}{\mu R_0^{10/3}}& = \int^{h(t)}_{h(0)}-\frac{dh}{h^3
+  F^{1/3}} = -\frac{1}{H^{1/3}\delta^{5/3}}\int^{\bar{h}(t)}_{\bar{h}(0)}\frac{d \bar{h}}{\bar{h}^{(8-m)/3}(\bar{h}^2-1)^{1/3}},
 \end{align}
@@
 \label{eq:teq_scaling}
-t\sim \frac{\mu R_0^{10/3}}{K_a^{2/3}}\frac{1}{\sigma^{1/3}\delta^{5/3}}.
+t\sim \frac{\mu R_0^{10/3}}{K_a^{2/3}}\frac{1}{H^{1/3}\delta^{5/3}}.
 \end{equation}
-Equation~\ref{eq:teq_scaling} tells us that both adhesion strength $\sigma$ and the separation distance $\delta$ affect
-the time it takes for a pair of vesicles to reach equilibrium under adhesion force $F$ in equation~\ref{eq:Fh}.  In particular, the equilibration time $t$ 
-is proportional to (1) the separation distance $\delta^{-5/3}$ (thus $t\rightarrow \infty$ as $\delta\rightarrow 0$), and (2) the adhesion strength $\sigma^{-1/3}$ 
-(as in constant forcing case \cite{RamachandranLeal2010_PoF}).  From the above analysis we also expect that the scaling of $t$ with respect to $\delta$ depends on the
-adhesion potential, while the scaling with respect to adhesion strength is independent of the specific form of the potential.
+Equation~\eqref{eq:teq_scaling} tells us that both adhesion strength $H$
+and the separation distance $\delta$ affect the time it takes for a pair
+of vesicles to reach equilibrium under adhesion force $F$ in
+equation~\eqref{eq:Fh}.  In particular, the equilibration time $t$ is
+proportional to (1) the separation distance $\delta^{-5/3}$ (thus
+$t\rightarrow \infty$ as $\delta\rightarrow 0$), and (2) the adhesion
+strength $H^{-1/3}$ (as in constant forcing
+case~\cite{RamachandranLeal2010_PoF}).  From the above analysis we also
+expect that the scaling of $t$ with respect to $\delta$ depends on the
+adhesion potential, while the scaling with respect to adhesion strength
+is independent of the specific form of the potential.
 
@@
 \includegraphics[keepaspectratio=true,scale=0.4]{figs/Dec13a_time_scaling02.eps}
-\caption{Scaling of the time it takes for two vesicles to reach equilibrium: (a) scaling with respect to $\delta$ with $\sigma=0.1$, and (b) scaling
-with respect to $\sigma$ with $\delta = 0.4$. Arrows indicate the time by when the equilibrium is reached within $1\%$.}
-\label{fig:qflow00}
+\caption{\label{fig:qflow00} Scaling of the time it takes for two
+  vesicles to reach equilibrium. {\em Left}: Scaling with respect to
+  $\delta$ with $H=0.1$.  {\em Right}: Scaling with respect to $H$ with
+  $\delta = 0.4$. Arrows indicate the time by when the equilibrium is
+  reached within $1\%$.}
 \end{figure}
 
-To test the scaling of the equilibration time $t$ with respect to $\sigma$ and $\delta$, we simulate the vesicle adhesion dynamics in a quiescent flow.
-Starting with two vesicles at a distance of twice the radius at $t=0$, the long-range attraction pulls the vesicles together. Figure~\ref{fig:qflow00}(a) plots
-the scaled adhesion energy versus time with $\sigma=0.1$ and three values of $\delta$ as labeled. 
-Adhesion energy reaches minimum at equilibrium, and the scaled $E_{adh}$ evolves towards zero at equilibrium. 
-The arrow indicate the times when the scaled adhesion energy
-reaches within $1\%$ of equilibrium: $t\sim 96$ for $\delta=0.2$, $t\sim 45$ for $\delta = 0.3$, and $t\sim 30$ for $\delta=0.4$:
+To test the scaling of the equilibration time $t$ with respect to $H$
+and $\delta$, we simulate the vesicle adhesion dynamics in a quiescent
+flow.  Starting with two vesicles at a distance of twice the radius at
+$t=0$, the long-range attraction pulls the vesicles together.
+Figure~\ref{fig:qflow00}(a) plots the scaled adhesion energy versus time
+with $H=0.1$ and three values of $\delta$ as labeled.  Adhesion energy
+reaches minimum at equilibrium, and the scaled $E_{adh}$ evolves towards
+zero at equilibrium.  The arrow indicate the times when the scaled
+adhesion energy reaches within $1\%$ of equilibrium: $t\sim 96$ for
+$\delta=0.2$, $t\sim 45$ for $\delta = 0.3$, and $t\sim 30$ for
+$\delta=0.4$:
 \begin{align}
@@
 
-The scaling with respect to adhesion strength $\sigma$ is illustrated in figure~\ref{fig:qflow00}(b), where $\delta = 0.4$ and $\sigma$ varies from $0.1$ to $0.5$ as labeled.
-Again the arrows indicate the times when the equilibrium is reached within $1\%$:
+The scaling with respect to adhesion strength $H$ is illustrated in
+Figure~\ref{fig:qflow00}(b), where $\delta = 0.4$ and $H$ varies from
+$0.1$ to $0.5$ as labeled.  Again the arrows indicate the times when the
+equilibrium is reached within $1\%$:
 \begin{align}
-\frac{t_{\sigma=0.1}}{t_{\sigma=0.5}} \sim \frac{34}{20} = 1.71 &\Longleftrightarrow \left(\frac{0.5}{0.1}\right)^{1/3}\sim 1.71.
+\frac{t_{H=0.1}}{t_{H=0.5}} \sim \frac{34}{20} = 1.71 &\Longleftrightarrow \left(\frac{0.5}{0.1}\right)^{1/3}\sim 1.71.
 \end{align}
-From the above results we conclude that the scaling in equation~\ref{eq:teq_scaling} captures the adhesion dynamics of two vesicles that interact with each other via the adhesion force in equation~\ref{eq:Fh}.
+From the above results we conclude that the scaling in
+equation~\eqref{eq:teq_scaling} captures the adhesion dynamics of two
+vesicles that interact with each other via the adhesion force in
+equation~\eqref{eq:Fh}.
 
@@
 \label{subsec:qflow_adhesion_parameters} 
-In the simulations of a pair of 2d vesicles interacting with each other via the adhesion force in equation~\ref{eq:Fh},
-two vesicles are initially placed not too far apart  from each other for numerical convenience. 
-Without any external forcing such as an imposed electric field or a fluid flow in the far-field, the long-range attraction pulls two vesicles together until their
-separation distance is close to $\delta$ (where $F$ vanishes).  Depending on the adhesion strength relative to the membrane bending rigidity, the vesicle may deform significantly in the contact
-region while still maintain nearly spherical shape on the opposite side to the contact region \cite{EvansMetcalfe1984_BJ,Book_PhysicalBasisCellAdhesion,Book_IntermolecularSurfaceForces,RamachandranAndersonLealIsraelachvili2010_Langmuir}.
+In the simulations of a pair of 2d vesicles interacting with each other
+via the adhesion force in equation~\eqref{eq:Fh}, two vesicles are
+initially placed not too far apart  from each other for numerical
+convenience.  Without any external forcing such as an imposed electric
+field or a fluid flow in the far-field, the long-range attraction pulls
+two vesicles together until their separation distance is close to
+$\delta$ (where $F$ vanishes).  Depending on the adhesion strength
+relative to the membrane bending rigidity, the vesicle may deform
+significantly in the contact region while still maintain nearly
+spherical shape on the opposite side to the contact
+region~\cite{EvansMetcalfe1984_BJ, Book_PhysicalBasisCellAdhesion,
+Book_IntermolecularSurfaceForces,
+RamachandranAndersonLealIsraelachvili2010_Langmuir}.
 \begin{figure}
@@
 \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
-\caption{Two vesicles of length $\pi$ with $\kappa=1$, $\sigma=5$ and $\delta=0.2$.
-(a) Equilibrium shapes of two vesicles under adhesive  interactions with adhesion strength $\sigma=0.5$ and separation distance $\delta=0.2$. 
-Vesicle reduced area $\Delta A=0.95$, $0.75$ and $0.6$ as labeled.
- The color coding is the tension along the vesicle. (b) Membrane shapes in the contact region.}
+\caption{Two vesicles of length $\pi$ with $\kappa=1$, $H=5$ and
+  $\delta=0.2$.  (a) Equilibrium shapes of two vesicles under adhesive
+  interactions with adhesion strength $H=0.5$ and separation distance
+  $\delta=0.2$.  Vesicle reduced area $\Delta A=0.95$, $0.75$ and $0.6$
+  as labeled.  The color coding is the tension along the vesicle. (b)
+  Membrane shapes in the contact region.}
 \label{fig:Dec18_vesicle_shape}
@@
 
-Figure~\ref{fig:Dec18_vesicle_shape}(a) shows the equilibrium shapes of vesicles with
-three values of reduced area: $\Delta A=0.95$, $0.75$ and $0.6$ with $\sigma=5$ and $\delta = 0.2$.
-The equilibrium vesicle shape for $\Delta A=0.95$ is the circular cap with a flatten contact region. 
-This is similar to the observed shapes of two vesicles under strong adhesive interaction in \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.
+Figure~\ref{fig:Dec18_vesicle_shape}(a) shows the equilibrium shapes of
+vesicles with three values of reduced area: $\Delta A=0.95$, $0.75$ and
+$0.6$ with $H=5$ \todo[inline]{Is this really the Hamacher constant?
+It's not 0.5?} and $\delta = 0.2$.  The equilibrium vesicle shape for
+$\Delta A=0.95$ is the circular cap with a flatten contact region.  This
+is similar to the observed shapes of two vesicles under strong adhesive
+interaction
+in~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.
 
@@
 \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_EbEadh_vs_rA_adR0p2_adS502.jpeg}
-\caption{Two vesicles of length $\pi$ with $\kappa=1$, $\sigma=5$ and $\delta=0.2$. 
+\caption{Two vesicles of length $\pi$ with $\kappa=1$, $H=5$ and $\delta=0.2$. 
 (a) Total bending energy (solid curve) and adhesion energy (dash-dotted curve) plotted against
@@
 \end{figure}
-Figure~\ref{fig:Dec18_vesicle_equilibrium1}(a) shows the total bending energy as a function of reduced area. The smaller the reduced area, the more vesicle area is available
-for deformation and thus the bending energy is higher. Figure~\ref{fig:Dec18_vesicle_equilibrium1}(b) shows the total adhesion energy as a function of reduced area. We note
-that the total adhesion energy is more negative as reduced area decreases.
-The sum of two energies is plotted in figure~\ref{fig:Dec18_vesicle_equilibrium1}(c), where a local minimum in the total energy is
-found around $\Delta A =0.8$.
+Figure~\ref{fig:Dec18_vesicle_equilibrium1}(a) shows the total bending
+energy as a function of reduced area. The smaller the reduced area, the
+more vesicle area is available for deformation and thus the bending
+energy is higher. Figure~\ref{fig:Dec18_vesicle_equilibrium1}(b) shows
+the total adhesion energy as a function of reduced area. We note that
+the total adhesion energy is more negative as reduced area decreases.
+The sum of two energies is plotted in
+Figure~\ref{fig:Dec18_vesicle_equilibrium1}(c), where a local minimum in
+the total energy is found around $\Delta A =0.8$.
 
@@
 \includegraphics[keepaspectratio=true,scale=0.18]{figs/Dec18_Eadh_vs_sigma_rA0p9502.jpeg}
-\caption{Total bending energy (a) and adhesion energy (b) versus the adhesion strength $\sigma$ 
+\caption{Total bending energy (a) and adhesion energy (b) versus the
+  adhesion strength $H$ 
 for two vesicles with reduced area $\Delta A=0.95$, separation distance $\delta = 0.2$ (triangles), $0.3$ (crosses)
@@
 %
-Figure~\ref{fig:Dec18_equilibrium} is an example of how the adhesion strength $\sigma$ and separation distance $\delta$ affect the equilibrium configuration of two vesicles under adhesive interactions.
-For both vesicles the reduced area $\Delta A=0.95$ and the bending rigidity is $1$.
-In figure~\ref{fig:Dec18_equilibrium}(a) 
-the total bending energy at equilibrium is plotted against $\sigma$ for three values of separation distance $\delta$.
-We observe that for $\Delta A=0.95$ the equilibrium vesicle shape does not vary much with the adhesion strength $\sigma$, while the total adhesion energy in figure~\ref{fig:Dec18_equilibrium}(b) varies linearly
-with $\sigma$.
+Figure~\ref{fig:Dec18_equilibrium} is an example of how the adhesion
+strength $H$ and separation distance $\delta$ affect the equilibrium
+configuration of two vesicles under adhesive interactions.  For both
+vesicles the reduced area $\Delta A=0.95$ and the bending rigidity is
+$1$.  In Figure~\ref{fig:Dec18_equilibrium}(a) the total bending energy
+at equilibrium is plotted against $H$ for three values of separation
+distance $\delta$.  We observe that for $\Delta A=0.95$ the equilibrium
+vesicle shape does not vary much with the adhesion strength $H$, while
+the total adhesion energy in Figure~\ref{fig:Dec18_equilibrium}(b)
+varies linearly with $H$.
 
@@
 \label{sec:eflow} 
-The hydrodynamics of a single vesicle in an 
-extensional flow has revealed novel nonlinear vesicle dynamics not found for a viscous drop \cite{KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2013_JFM,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}.
-The stagnation point (zero-velocity point) in an extensional flow is a saddle point where two laminar streams converge along an axis and then diverge in a
-different direction. 
-With an active control algorithm to fix the position of the stagnation point by adjusting the streaming flow strength with a feedback loop \cite{Johnson-Chavarria2011_EMJ},
-a particle can be trapped at the stagnation point for long time scales to facilitate
-image acquisition or other detailed measures such as PIV of flow inside/around the particle.
-To explore the application of such fluid trap to measure the adhesion strength between two bound vesicle membranes, we propose the following thought experiment.
-
-We begin from two vesicles forming a doublet under an adhesion potential in a quiescent flow as in \S~\ref{sec:qflow}. 
-Once a doublet forms and reaches an equilibrium configuration, we turn on 
-the fluid trap with the stagnation point placed at the center of the vesicle doublet.
-For simplification we assume that each vesicle in the doublet has the same reduced area, membrane area, and bending stiffness.
-At low extensional rate, we expect the vesicle doublet to stay bound at the fluid trap stagnation point.
-On the other hand, the vesicle doublet may become unstable and eventually separate at a high extensional rate.
-Thus we expect there to exist a critical extensional rate above which the vesicle doublet cannot stay bound under a given adhesion potential.
-The dependence of the critical extensional rate on the adhesion potential and the mechanical vesicle properties thus provides a means to probe the physics of membrane adhesion.
+The hydrodynamics of a single vesicle in an extensional flow has
+revealed novel nonlinear vesicle dynamics not found for a viscous drop
+\cite{KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2013_JFM,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}.
+The stagnation point (zero-velocity point) in an extensional flow is a
+saddle point where two laminar streams converge along an axis and then
+diverge in a different direction.  With an active control algorithm to
+fix the position of the stagnation point by adjusting the streaming flow
+strength with a feedback loop~\cite{Johnson-Chavarria2011_EMJ}, a
+particle can be trapped at the stagnation point for long time scales to
+facilitate image acquisition or other detailed measures such as PIV of
+flow inside/around the particle.  To explore the application of such
+fluid trap to measure the adhesion strength between two bound vesicle
+membranes, we propose the following thought experiment.
+
+We begin from two vesicles forming a doublet under an adhesion potential
+in a quiescent flow as in \S~\ref{sec:qflow}.  Once a doublet forms and
+reaches an equilibrium configuration, we turn on the fluid trap with the
+stagnation point placed at the center of the vesicle doublet.  For
+simplification we assume that each vesicle in the doublet has the same
+reduced area, membrane area, and bending stiffness.  At low extensional
+rate, we expect the vesicle doublet to stay bound at the fluid trap
+stagnation point.  On the other hand, the vesicle doublet may become
+unstable and eventually separate at a high extensional rate.  Thus we
+expect there to exist a critical extensional rate above which the
+vesicle doublet cannot stay bound under a given adhesion potential.  The
+dependence of the critical extensional rate on the adhesion potential
+and the mechanical vesicle properties thus provides a means to probe the
+physics of membrane adhesion.
 
@@
   hydrodynamics in an extensional flow.  At a fixed Hamaker constant
-  $\sigma=0.7$ and adhesion length scale $\delta=0.4$, doublets may
-  either remain symmetric to the flow (red marks), or tilt to some
-  inclination angle (blue dots), or the extensional rate, $\chi$, may
-  overcome the adhesive force (green dots).}
+  $H=0.7$ and adhesion length scale $\delta=0.4$, doublets may either
+  remain symmetric to the flow (red marks), or tilt to some inclination
+  angle (blue dots), or the extensional rate, $\chi$, may overcome the
+  adhesive force (green dots).}
 \end{figure}
@@
 vesicles' reduced area, the adhesion length scale $\delta$, the adhesion
-strength $\sigma$, and the shear rate $\chi$.
-Figure~\ref{fig:doublet090} shows the configuration of two vesicles that
-have formed a doublet at several instances in time.  In
-Figure~\ref{fig:sflow_phase_diagram} (left), we show the minimum
-distance between the two vesicles as a function of time for various
-adhesion strengths.  The adhesion strength corresponding to the red
-curves is less than a critical strength $\sigma_c$ for a doublet to
-form.  In contrast, for larger adhesive strengths, doublets are formed
-(blue curves).
+strength $H$, and the shear rate $\chi$.  Figure~\ref{fig:doublet090}
+shows the configuration of two vesicles that have formed a doublet at
+several instances in time.  In Figure~\ref{fig:sflow_phase_diagram}
+(left), we show the minimum distance between the two vesicles as a
+function of time for various adhesion strengths.  The adhesion strength
+corresponding to the red curves is less than a critical strength $H_c$
+for a doublet to form.  In contrast, for larger adhesive strengths,
+doublets are formed (blue curves).
 
@@
   \caption{\label{fig:doublet090} The formation of a doublet in a shear
-  flow.  The reduced area is $0.90$, the Hamaker contsant is $\sigma=0.7$, the
-adhesion length scale is $\delta = 0.4$, and the shear rate is $\chi=0.5$.}
+  flow.  The reduced area is $0.90$, the Hamaker constant is $H=0.7$,
+  the adhesion length scale is $\delta = 0.4$, and the shear rate is
+  $\chi=0.5$.}
 \end{figure}
@@
   $\delta = 0.4$.   The different lines correspond to a linear spacing
-    of adhesion strengths ranging from $\sigma=0.1$ and $\sigma=1.0$.
-    {\em Right}: Phase diagram of vesicle hydrodynamics in a shear flow.
-    At a fixed reduced area $\triangle A=0.90$ and $\delta =0.4$,  the
-    critical vdW potential strength $\sigma$ for binding of two vesicles
-  in a shear flow depends on the shear rate $\chi$.
+  of adhesion strengths ranging from $H=0.1$ and $H=1.0$.  {\em Right}:
+  Phase diagram of vesicle hydrodynamics in a shear flow.  At a fixed
+  reduced area $\triangle A=0.90$ and $\delta =0.4$,  the critical vdW
+  potential strength $H$ for binding of two vesicles in a shear flow
+  depends on the shear rate $\chi$.
 \label{fig:sflow_phase_diagram}}
@@
 \rangle$ is the spatial average.
+\todo[inline]{Stress $\sigma$ is also used for tension}
 
@@
   viscosity of a tank treading vesicle (blue) and a doublet (red).  The
-  shear rate is $\chi = 0.5$, the Hamaker constant is $\sigma = 0.7$,
+  shear rate is $\chi = 0.5$, the Hamaker constant is $H = 0.7$,
   and the adhesion length scale is $\delta = 0.4$.  The length of the
@@
 
-Recently Liu {\it et al.} \cite{LiuChuNewbyRead2018_bioRxiv} used
+Recently Liu {\em et al.}~\cite{LiuChuNewbyRead2018_bioRxiv} used
 immersed boundary simulations to show that, at a separation distance of
@@
 \begin{align*}
-  \phi(z) = \sigma \left[ 
+  \phi(z) = H \left[ 
     \left(\frac{\delta}{z}\right)^m - \frac{m}{n}\left(\frac{\delta}{z}\right)^n \right],
@@
 \begin{align}
- \int_{\gamma_2}\nabla \phi(\|\xx_1 - \xx_2\|)ds_{\xx_2} = -m \sigma\delta^{n}
+ \int_{\gamma_2}\nabla \phi(\|\xx_1 - \xx_2\|)ds_{\xx_2} = -m   H\delta^{n}
    \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+2}} 
@@
   \int_{\gamma_2}\nabla \phi(\|\xx_1 - \xx_2\|)ds_{\xx_2} = 
-  -4 \sigma \delta^2 \int_{\gamma_2}
+  -4 H \delta^2 \int_{\gamma_2}
   \frac{\xx_1 - \xx_2}{\|\xx_1 - \xx_2\|^6} 

### 2019-01-15 vesicle_code/docs/adhesion/adhesion.tex
fixed some latex fomratting issues.

@@
 %
-\documentclass[aps,prb,showpacs,amsmath,amssymb,superscriptaddress]{revtex4-1}
+%\documentclass[aps,prb,showpacs,amsmath,amssymb,superscriptaddress]{revtex4-1}
+\documentclass[prf,superscriptaddress,showpacs]{revtex4-1}
 
@@
 
+\usepackage{amsmath,amssymb}
 \usepackage[titletoc]{appendix}
@@
 % \email{bquaife@fsu.edu}
-% \altaffiliation[]{Department of Scientific Computing \\ Florida State University}
 \author{Shravan Veerapaneni}%
@@
 \affiliation{Department of Mathematics, University of Michigan, Ann Arbor, Michigan, USA}%
-\author{Y.-N. Young}%
+\author{Y.-N.~Young}%
  \email[Corresponding author: ]{yyoung@njit.edu}
 \affiliation{Department of Mathematical Sciences, Newark, NJ, USA}%
-
-%\collaboration{MUSO Collaboration}%\noaffiliation
-
-%\author{Charlie Author}
-% \homepage{http://www.Second.institution.edu/~Charlie.Author}
-%\affiliation{
-% Second institution and/or address\\
-% This line break forced% with \\
-%}%
-%\affiliation{
-% Third institution, the second for Charlie Author
-%}%
-%\author{Delta Author}
-%\affiliation{%
-% Authors' institution and/or address\\
-% This line break forced with \textbackslash\textbackslash
-%}%
-%
-%\collaboration{CLEO Collaboration}%\noaffiliation
 
@@
 \section{Introduction}
-Vesicles (closed fluid-filled phospholipid bilayer membranes) have been widely utilized
-as biological cell mimics in biophysics and material engineering \cite{}. 
-%
-The ever expanding applications have encouraged detailed experimental,
-theoretical and numerical investigations of vesicle hydrodynamics in
-applied flow, electric and magnetic fields. Theoretical investigations
-often take the form of small-deformation analysis or spheroidal dynamics
-of a nearly-spherical vesicle (or nearly-circular in two dimensions)
-subjected to an applied flow or under an external
-forcing~\cite{Barthes-BieselRallison1981_JFM,Misbah2006_PRL,Vlahovska2007_PRE,Finken2008_EPL,ZhangZahnTanLin2013_PoF,Nganguia2013_PRE}.
-On the other hand, various numerical methods have been developed for
-simulating the transient hydrodynamics of vesicle
-suspensions~\cite{BagchiJohoson2005_JBE,Biben2005_EJP,Veerapaneni2009_JCP,SeolHuKimLai2016_JCP}.  
+Vesicles (closed fluid-filled phospholipid bilayer membranes) have been
+widely utilized as biological cell mimics in biophysics and material
+engineering \cite{}.  The ever expanding applications have encouraged
+detailed experimental, theoretical and numerical investigations of
+vesicle hydrodynamics in applied flow, electric and magnetic fields.
+Theoretical investigations often take the form of small-deformation
+analysis or spheroidal dynamics of a nearly-spherical vesicle (or
+nearly-circular in two dimensions) subjected to an applied flow or under
+an external forcing~\cite{Barthes-BieselRallison1981_JFM,
+Misbah2006_PRL, Vlahovska2007_PRE, Finken2008_EPL,
+ZhangZahnTanLin2013_PoF, Nganguia2013_PRE}.  On the other hand, various
+numerical methods have been developed for simulating the transient
+hydrodynamics of vesicle suspensions~\cite{BagchiJohoson2005_JBE,
+Biben2005_EJP, Veerapaneni2009_JCP, SeolHuKimLai2016_JCP}.  
 %Experiments are performed to study vesicle hydrodynamics under various flowing conditions or forcing configurations \cite{MaderVitkova2006_EurPhysJE, Abkarian2008_SoftMatt,DahlNarsimhanGouveia2016_SoftMatt}.
@@
 and shear rate. At high viscosity contrast the tank-tread (TT) dynamics
-transitions to tumbling (TB)~\cite{Misbah2006_PRL,Vlahovska2007_PRE},
+transitions to tumbling (TB)~\cite{Misbah2006_PRL, Vlahovska2007_PRE},
 and this leads to a transition in effective shear viscosity in the
@@
 simulations~\cite{GhigliottiBibenMisbah2010_JFM} and
-experiments~\cite{KantslerSegreSteinberg2008_EPL,ZabuskySegreDeschamps2011_PoF}.
-Between TT and TB vesicle hydrodynamics, a breathing (tremble) is also
-observed~\cite{Misbah2006_PRL,KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2011_JFM,SpannZhaoShaqfeh2014_PoF}
-to affect the effective shear viscosity in a different way.  In an
-extensional flow (planar or uniaxial), vesicle shape dynamics depends
-sensitively on the vesicle reduced volume  and the elastic capillary
-number~\cite{KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2013_JFM,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}:
-Asymmetric shape and oscillatory undulation of the vesicle membrane are
-two examples of the complex vesicle hydrodynamics in an extensional
-flow.
-
-Collective dynamics of vesicles naturally is dictated by the individual vesicle-vesicle interactions.
+experiments~\cite{KantslerSegreSteinberg2008_EPL,
+ZabuskySegreDeschamps2011_PoF}.  Between TT and TB vesicle
+hydrodynamics, a breathing (tremble) is also
+observed~\cite{Misbah2006_PRL,KantslerSegreSteinberg2008_PRL,
+ZhaoShaqfeh2011_JFM, SpannZhaoShaqfeh2014_PoF} to affect the effective
+shear viscosity in a different way.  In an extensional flow (planar or
+uniaxial), vesicle shape dynamics depends sensitively on the vesicle
+reduced volume  and the elastic capillary
+number~\cite{KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
+Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}: Asymmetric shape
+and oscillatory undulation of the vesicle membrane are two examples of
+the complex vesicle hydrodynamics in an extensional flow.
+
 %
@@
 %
-In numerical simulations of vesicle suspensions, it is often assumed
-that the liquid film between vesicles acts to keep the membrane-membrane
-interaction, such as the van der Waals type adhesive interaction,
-negligible.  However the amphiphilic natures of lipid molecules (a
-hydrophobic tail and a hydrophilic head with an electric dipole)
-complicate the interactions between a lipid bilayer membrane and another
-bilayer
-membrane~\cite{EvansMetcalfe1984_BJ,Book_PhysicalBasisCellAdhesion,Book_IntermolecularSurfaceForces}
-or a solid (such as a glass substrate or a nano particle).  Studies
-confirmed that such interaction potential inevitably consists of a
-long-range attraction component and a short-range repulsion
-component~\cite{Book_IntermolecularSurfaceForces}, and the combination
-of the two gives rise to adhesion at the separation distance that
-minimizes the interaction
+Collective dynamics of vesicles naturally is dictated by the individual
+vesicle-vesicle interactions.  In numerical simulations of vesicle
+suspensions, it is often assumed that the liquid film between vesicles
+acts to keep the membrane-membrane interaction, such as the van der
+Waals type adhesive interaction, negligible.  However the amphiphilic
+natures of lipid molecules (a hydrophobic tail and a hydrophilic head
+with an electric dipole) complicate the interactions between a lipid
+bilayer membrane and another bilayer
+membrane~\cite{EvansMetcalfe1984_BJ, Book_PhysicalBasisCellAdhesion,
+Book_IntermolecularSurfaceForces} or a solid (such as a glass substrate
+or a nano particle).  Studies confirmed that such interaction potential
+inevitably consists of a long-range attraction component and a
+short-range repulsion component~\cite{Book_IntermolecularSurfaceForces},
+and the combination of the two gives rise to adhesion at the separation
+distance that minimizes the interaction
 potential~\cite{Book_IntermolecularSurfaceForces}. Such adhesive
@@
 
-%
 Adhesion between a vesicle and a substrate has been extensively studied,
@@
 
-This paper is organized as follows. In \S~\ref{sec:ge} we formulate our
-model for vesicle hydrodynamics with adhesive interactions  between
+This paper is organized as follows. In Section~\ref{sec:ge} we formulate
+our model for vesicle hydrodynamics with adhesive interactions  between
 membranes of distinct vesicles.  We simulate the adhesion process of two
-vesicles in a quiescent flow in \S~\ref{sec:qflow}, where we also
+vesicles in a quiescent flow in Section~\ref{sec:qflow}, where we also
 present a simple model to estimate how long it takes for two nearby
 vesicles to reach an equilibrium configuration under adhesion. In
-\S~\ref{sec:eflow} we numerically investigate the hydrodynamics of a
-vesicle doublet in a fluid trap where the stagnation point is actively
+Section~\ref{sec:eflow} we numerically investigate the hydrodynamics of
+a vesicle doublet in a fluid trap where the stagnation point is actively
 controlled to be at the center of the vesicle doublet. From these
@@
 probe the adhesion strength between lipid bilayer membranes in
-solutions. In \S~\ref{sec:sflow} we investigate how two vesicles may
-form a doublet as they move toward each other under a planar shear flow.
-We map out the parameter regions for bound/unbound vesicles under a
-planar shear flow, and we also investigate the effects of adhesive
+solutions. In Section~\ref{sec:sflow} we investigate how two vesicles
+may form a doublet as they move toward each other under a planar shear
+flow.  We map out the parameter regions for bound/unbound vesicles under
+a planar shear flow, and we also investigate the effects of adhesive
 interactions on the rheological properties of a dilute suspension of
-vesicle doublets.  Finally in \S~\ref{sec:conclusions} we discuss the
-implications of our results and point out a few potential future
+vesicle doublets.  Finally in Section~\ref{sec:conclusions} we discuss
+the implications of our results and point out a few potential future
 directions.
@@
 \subsection{Adhesion Model}
-The adhesion model of Sukumaran and Seifert~\cite{suk-sei2001} considers adhesion
-between a single three-dimensional vesicle and a solid wall at $z=0$.
-\todo[inline]{Need a cartoon picture in here.  Some kind of version of
-the one I had for my SIAM Life Sciences Talk} The adhesion potential in
-their model is of the functional form in
+The adhesion model of Sukumaran and Seifert~\cite{suk-sei2001} considers
+adhesion between a single three-dimensional vesicle and a solid wall at
+$z=0$.  \todo[inline]{Need a cartoon picture in here.  Some kind of
+version of the one I had for my SIAM Life Sciences Talk} The adhesion
+potential in their model is of the functional form in
 equation~\eqref{eq:adhesion_potential} with $(m,n) = (4,2)$:
@@
 that treats both the bending and tension terms
-semi-implicitly~\cite{qua-bir2014}. Note that the adhesive term is
+semi-implicitly~\cite{quaife2016adaptive}. Note that the adhesive term is
 treated explicitly.  Therefore, a single time step requires solving
@@
 achieve higher-order accuracy in time, we apply a time adaptive spectral
-deferred correction method~\cite{qua-bir2016}.  The SDC method is able
-to achieve second-order accuracy by iteratively applying the first-order
-method~\eqref{eqn:IMEXEuler}.
+deferred correction method~\cite{quaife2016adaptive}.  The SDC method is
+able to achieve second-order accuracy by iteratively applying the
+first-order method~\eqref{eqn:IMEXEuler}.
 
@@
 dynamics~\cite{RamachandranLeal2010_PoF}
-\begin{equation}
+\begin{align}
 \label{eq:dhdt}
 \frac{d h}{dt} \sim \frac{K_a^{2/3} F^{1/3}}{\mu R_0^{10/3}} h^3,
-\end{equation}
+\end{align}
 where $K_a$ is the area expansion modulus, $\mu$ is the viscosity of
@@
 a relation between film thickness $h$ and time $t$:
-\begin{equation}
+\begin{align*}
 t \sim \frac{\mu R_0^{10/3}}{K_a^{2/3} F^{1/3}}\frac{1}{2 h^2} \bigg|^{h(t)}_{h(0)},
-\end{equation}
+\end{align*}
 where $h(0)$ is the vesicle separation at $t=0$.
@@
 When the force on each vesicle is a function of separation distance $h$ of the form (with an integer $m\ge 2$)
-\begin{equation}
+\begin{align}
 \label{eq:Fh}
 F(h) \sim H \frac{\delta^m}{h^{m+1}}\left(\left(\frac{\delta}{h}\right)^2-1\right),
-\end{equation}
+\end{align}
 attraction is dominant at ``large" scales ($h > \delta$) while repulsion
@@
 of a function of dimensionless $\bar{h} \equiv h/\delta$:
-\begin{align}
+\begin{align*}
 t\frac{K_a^{2/3}}{\mu R_0^{10/3}}& = \int^{h(t)}_{h(0)}-\frac{dh}{h^3
   F^{1/3}} = -\frac{1}{H^{1/3}\delta^{5/3}}\int^{\bar{h}(t)}_{\bar{h}(0)}\frac{d \bar{h}}{\bar{h}^{(8-m)/3}(\bar{h}^2-1)^{1/3}},
-\end{align}
-\begin{equation}
+\end{align*}
+\begin{align}
 \label{eq:teq_scaling}
 t\sim \frac{\mu R_0^{10/3}}{K_a^{2/3}}\frac{1}{H^{1/3}\delta^{5/3}}.
-\end{equation}
+\end{align}
 Equation~\eqref{eq:teq_scaling} tells us that both adhesion strength $H$
@@
 $\delta=0.4$:
-\begin{align}
+\begin{align*}
 \frac{t_{\delta=0.2}}{t_{\delta=0.4}} \sim \frac{96}{30}=3.2 &\Longleftrightarrow \left(\frac{0.4}{0.2}\right)^{5/3}\sim 3.17,\\
 \frac{t_{\delta=0.2}}{t_{\delta=0.3}} \sim \frac{96}{45}=2.1 &\Longleftrightarrow \left(\frac{0.3}{0.2}\right)^{5/3}\sim 2.
-\end{align}
+\end{align*}
 
@@
 equilibrium is reached within $1\%$:
-\begin{align}
+\begin{align*}
 \frac{t_{H=0.1}}{t_{H=0.5}} \sim \frac{34}{20} = 1.71 &\Longleftrightarrow \left(\frac{0.5}{0.1}\right)^{1/3}\sim 1.71.
-\end{align}
+\end{align*}
 From the above results we conclude that the scaling in
@@
 revealed novel nonlinear vesicle dynamics not found for a viscous drop
-\cite{KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2013_JFM,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}.
-The stagnation point (zero-velocity point) in an extensional flow is a
-saddle point where two laminar streams converge along an axis and then
-diverge in a different direction.  With an active control algorithm to
-fix the position of the stagnation point by adjusting the streaming flow
+\cite{KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
+Narsimhan2014_JFM,  DahlNarsimhanGouveia2016_SoftMatt}.  The stagnation
+point (zero-velocity point) in an extensional flow is a saddle point
+where two laminar streams converge along an axis and then diverge in a
+different direction.  With an active control algorithm to fix the
+position of the stagnation point by adjusting the streaming flow
 strength with a feedback loop~\cite{Johnson-Chavarria2011_EMJ}, a
@@
 We begin from two vesicles forming a doublet under an adhesion potential
-in a quiescent flow as in \S~\ref{sec:qflow}.  Once a doublet forms and
-reaches an equilibrium configuration, we turn on the fluid trap with the
-stagnation point placed at the center of the vesicle doublet.  For
+in a quiescent flow as in Section~\ref{sec:qflow}.  Once a doublet forms
+and reaches an equilibrium configuration, we turn on the fluid trap with
+the stagnation point placed at the center of the vesicle doublet.  For
 simplification we assume that each vesicle in the doublet has the same
@@
 and the adhesive force applied by vesicle 2 on vesicle 1 is
-\begin{align}
+\begin{align*}
  \int_{\gamma_2}\nabla \phi(\|\xx_1 - \xx_2\|)ds_{\xx_2} = -m   H\delta^{n}
@@
   \left(\delta^{m-n} - \|\xx - \yy\|^{m-n} \right) ds_\yy.
-  \end{align}
+  \end{align*}
 When $(m,n) = (4,2)$, the above express becomes

### 2019-01-15 vesicle_code/docs/adhesion/adhesion.tex
fixed some figures

@@
 facilitate image acquisition or other detailed measures such as PIV of
-flow inside/around the particle.  To explore the application of such
-fluid trap to measure the adhesion strength between two bound vesicle
+flow inside and around the particle.  To explore the application of such
+a fluid trap to measure the adhesion strength between two bound vesicle
 membranes, we propose the following thought experiment.
@@
 
+\todo[inline]{Start rewriting from here}
 We consider two vesicles suspended in the extensional flow $\uu =

### 2019-01-15 vesicle_code/examples/output/makeImages.m

@@ -4,8 +4,8 @@ set(0,'DefaultAxesFontSize',22)
 irate = 30; % controls the speed of the visualization
 
 if 1
-  file = 'extensional2VesGData.bin';
-  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi1em1_ra080/extensional2VesData.bin';
+  file = 'extensional2VesAData.bin';
+%  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi7em2_ra090_largerTol/extensional2VesData.bin';
   ax = [-4 4 -5 5];
   options.confined = false;
 end

### 2019-01-15 vesicle_code/docs/adhesion/adhesion.tex
worked on extensional example

@@
 vesicles with three values of reduced area: $\Delta A=0.95$, $0.75$ and
-$0.6$ with $H=5$ \todo[inline]{Is this really the Hamacher constant?
+$0.6$ with $H=5$ \todo[inline]{Is this really the Hamaker constant?
 It's not 0.5?} and $\delta = 0.2$.  The equilibrium vesicle shape for
@@
 Narsimhan2014_JFM,  DahlNarsimhanGouveia2016_SoftMatt}.  The stagnation
-point (zero-velocity point) in an extensional flow is a saddle point
-where two laminar streams converge along an axis and then diverge in a
-different direction.  With an active control algorithm to fix the
-position of the stagnation point by adjusting the streaming flow
-strength with a feedback loop~\cite{Johnson-Chavarria2011_EMJ}, a
+point (zero-velocity point) in an extensional flow, $\uu =\chi(-x,y) $,
+is a saddle point where two laminar streams converge along an axis and
+then diverge in a different direction.  With an active control algorithm
+to fix the position of the stagnation point by adjusting the streaming
+flow strength with a feedback loop~\cite{Johnson-Chavarria2011_EMJ}, a
 particle can be trapped at the stagnation point for long time scales to
@@
 We begin from two vesicles forming a doublet under an adhesion potential
-in a quiescent flow as in Section~\ref{sec:qflow}.  Once a doublet forms
-and reaches an equilibrium configuration, we turn on the fluid trap with
-the stagnation point placed at the center of the vesicle doublet.  For
-simplification we assume that each vesicle in the doublet has the same
-reduced area, membrane area, and bending stiffness.  At low extensional
-rate, we expect the vesicle doublet to stay bound at the fluid trap
-stagnation point.  On the other hand, the vesicle doublet may become
-unstable and eventually separate at a high extensional rate.  Thus we
-expect there to exist a critical extensional rate above which the
-vesicle doublet cannot stay bound under a given adhesion potential.  The
-dependence of the critical extensional rate on the adhesion potential
-and the mechanical vesicle properties thus provides a means to probe the
-physics of membrane adhesion.
-
-\todo[inline]{Start rewriting from here}
-We consider two vesicles suspended in the extensional flow $\uu =
-\chi(-x,y)$, where $\chi$ is the extensional rate.  The vesicles are
-initially placed symmetrically on the $x$ axis in a quiescent flow
-($\chi = 0$).  Once they reach steady-state doublet, the extensional
-background flow is started.  We use this example to characterize the
-required extensional rate to overcome the adhesive forces of the
-doublet.  In particular, we investigate the effect of the reduced area.
-For all the simulations, the length of the vesicles are fixed, while the
-area is changed to achieve the desired reduced area.
-
-We observe three different vesicle configurations that depend on the
-reduced area and extensional rate.  First, the doublet is not broken and
-the individual vesicles long axis is parallel to the contracting
-direction (Figure~\ref{fig:extensional1}).  Second, the doublet is not
-broken, but it tilts to some inclination angle that is not parallel to
-either of the contracting or separation directions
-(Figure~\ref{fig:extensional3}).  Finally, if the extensional rate is
-sufficiently large, the doublet is broken and the vesicles tend to
-$(0,\pm \infty)$.
+in a quiescent flow as described in Section~\ref{sec:qflow}.  Once a
+doublet forms and reaches an equilibrium configuration, we turn on the
+fluid trap with the stagnation point placed at the center of the vesicle
+doublet.  For simplification we assume that each vesicle in the doublet
+has the same reduced area, membrane area, and bending stiffness.  At low
+extensional rate, $\chi$, we expect the vesicle doublet to stay bound at
+the fluid trap stagnation point.  On the other hand, the vesicle doublet
+may become unstable and eventually separate at higher extensional rates.
+Thus we expect there to exist a critical extensional rate above which
+the vesicle doublet cannot stay bound under a given adhesion potential.
+The dependence of the critical extensional rate on the adhesion
+potential and the mechanical vesicle properties thus provides a means to
+probe the physics of membrane adhesion.
+
+We consider six pairs of vesicles with reduced areas 0.70, 0.75, 0.80,
+0.85, 0.90, and 0.95, and we use extensional rates between $10^{-2}$ and
+$10^{-1}$.  For all the simulations, the length of the vesicles are
+fixed, while the area is changed to achieve the desired reduced area.
+Since the stagnation point can be controlled in an experimental
+setting~\cite{Johnson-Chavarria2011_EMJ}, we translate the vesicles at
+each time step so that the stagnation point occurs exactly in the middle
+of the two vesicles.  With this adjustment, the doublet can not migrate
+towards $(0,\pm \infty)$; instead, for all time, each vesicle is
+centered at $\pm(x_0,y_0)$ for some $(x_0,y_0)$.
+
+As expected, we observe two different regimes---the extensional rate is
+sufficiently small that the doublet structure is not broken, and the
+extensional rate is sufficiently large that the doublet is broken.  In
+Figure~\ref{fig:extensionalPhaseDiagram}.
+
+\begin{figure}[htp]
+  \includegraphics[width=0.5\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
+  \caption{\label{fig:extensionalPhaseDiagram} Phase diagram of vesicle
+  hydrodynamics in an extensional flow.  At a fixed Hamaker constant
+  $H=0.7$ and adhesion length scale $\delta=0.4$.  For small extensional
+  rates, the doublet structure is not broken (blue marks), while at
+  large extensional rates, the doublet is broken (red marks).}
+\end{figure}
+
+In Figures~\ref{fig:extensional1}--\ref{fig:extensional3}, we show
+snapshots of two vesicles of reduced area $0.70$ in an extensional flow
+with three different extensional rates.  Interestingly, when the
+extensional rate does not overcome the adhesion rate, the doublet does
+not remain parallel to the stagnation point, but instead tilts to an
+inclination angle (Figures~\ref{fig:extensional1}
+and~\ref{fig:extensional2}.  We include a plot of the inclination angle
+as a function of time for varying extensional rates (left plot of
+Figure~\ref{fig:extensionalInclinationAngle}).  The inclination angle is
+defined defined in with respect to the diverging direction (right plot
+of Figure~\ref{fig:extensionalInclinationAngle}).  When the doublet is
+broken at reduced area $0.70$, the extensional rate is sufficiently
+large to align the long axis of the vesicle with the diverging direction
+and then the vesicles separate.  However, for larger reduced areas, the
+separation dynamics is different.  Instead, the vesicles tilt to an
+inclination angle and then separate (Figure~\ref{fig:extensional4}).
 
@@
   \caption{\label{fig:extensional1} Two vesicles in an extensional flow.
-  The reduced area is $0.7$, the adhesion strength is $0.7$, and the
-  adhesion length scale is $0.4$, extensional rate is $\chi = 0.02$.
-  The doublet tilts to an inclination angle.
+  The reduced area is $0.7$, the Hamaker constant is $H = 0.7$, and the
+  adhesion length scale is $\delta = 0.4$, extensional rate is $\chi =
+  0.02$.  The doublet tilts to an inclination angle.
   }
@@
   \caption{\label{fig:extensional2} Two vesicles in an extensional flow.
-  The reduced area is $0.7$, the adhesion strength is $0.7$, and the
-  adhesion length scale is $0.4$, extensional rate is $\chi = 0.07$.
-  The doublet tilts to an inclination angle.}
+  The reduced area is $0.7$, the Hamaker constant is $H = 0.7$, and the
+  adhesion length scale is $\delta = 0.4$, extensional rate is $\chi =
+  0.07$.  The doublet tilts to an inclination angle.}
 \end{figure}
@@
   \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
-  The reduced area is $0.7$, the adhesion strength is $0.7$, and the
-  adhesion length scale is $0.4$, extensional rate is $\chi = 0.1$.  The
-  vesicles extensional rate has overcome the adhesive force, and the
-  vesicles doublet is broken.}
-\end{figure}
-
-Whether the doublet is broken or not and the inclination angle of the
-doublet depends on the extensional rate and the vesicles' reduced area.
-A phase diagram of the steady-state configuration is in
-Figure~\ref{fig:extensionalPhaseDiagram}.  Final configurations that
-remain symmetric to the flow (Figure~\ref{fig:extensional1} are
-indicated by red dots, tilt to some inclination angle
-(Figure~\ref{fig:extensional2} are indicated by blue dots, and that
-separate (Figure~\ref{fig:extensional3}) are indicated by green dots.
+  The reduced area is $0.7$, the Hamaker constant is $H = 0.7$, and the
+  adhesion length scale is $\delta = 0.4$, extensional rate is $\chi =
+  0.1$.  The vesicles extensional rate has overcome the adhesive force,
+  and the vesicles doublet is broken.}
+\end{figure}
 
 \begin{figure}[htp]
-  \includegraphics[width=0.5\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
-  \caption{\label{fig:extensionalPhaseDiagram} Phase diagram of vesicle
-  hydrodynamics in an extensional flow.  At a fixed Hamaker constant
-  $H=0.7$ and adhesion length scale $\delta=0.4$, doublets may either
-  remain symmetric to the flow (red marks), or tilt to some inclination
-  angle (blue dots), or the extensional rate, $\chi$, may overcome the
-  adhesive force (green dots).}
-\end{figure}
-
-In Figure~\ref{fig:extensionalInclinationAngle}, we plot the inclination
-angle of a doublet formed by two vesicles of reduced area $0.70$ at four
-different extensional rates.
+  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
+  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
+  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
+  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
+  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
+  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
+  The reduced area is $0.8$, the Hamaker constant is $H = 0.7$, and the
+  adhesion length scale is $\delta0.4$, extensional rate is $\chi =
+  0.1$.  Initially, the doublet tilts to an inclination angle, and then
+  the extensional rate overcomes the adhesive force and the doublet is
+  broken.}
+\end{figure}
+
+\todo[inline]{Plot of the final inclination angle of doublets that
+survive the extensional rate}
 
 \begin{figure}[htp]
+  \begin{minipage}{0.6\textwidth}
     \centering
-  \includegraphics[height=0.4\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
+    \includegraphics[width=\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
+  \end{minipage}
   \hfill
-  \includegraphics[height=0.4\textwidth]{figs/angleDefinition.pdf}
+  \begin{minipage}{0.33\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{figs/angleDefinition.pdf}
+  \end{minipage}
   \caption{\label{fig:extensionalInclinationAngle} {\em Left}: The
@@
   $\chi=0.5$.}
+  \todo[inline]{Superimpose the background velocity on the leftmost plot
+  to indicate the shearing motion}
 \end{figure}

### 2019-01-17 vesicle_code/docs/adhesion/adhesion.tex
some changes from yn

@@
 include~\cite{cantat1999lift, suk-sei2001, BlountMiksisDavis2013_PRSa}.
+%
+% The short-range adhesive potential of a lipid bilayer membrane
+% inevitably involves the membrane change redistribution and the membrane potential
+% 
+%  in relation the screening of charges in the electric double layer (EDL) right next to the
+% membrane \cite{Book_IntermolecularSurfaceForces,LiraDimova}.
+% When two vesicles are in close vicinity of each other within the electric double layer,  
+% In this work we do not consider the electrostatic of two lipid bilayer membranes.
+% 
 Adhesion between bilayer membranes was first experimentally observed by
@@
 $(m,n) = (12,6)$ corresponds to the L-J potential between two molecules.
-The adhesion potential in  the integral of
+In our case,  the adhesion potential in  the integral of
 equation~\eqref{eqn:adhesionForce} is between two small patches of lipid
-bilayer membrane. Thus we argue that a reasonable choice for $(m,n)$ is
-between $(m,n) = (4,2)$ and $(m,n) = (12,6)$.
+bilayer membrane (because the lipid molecules are coarse-grained in the continuum modeling).
+Thus a reasonable choice for $(m,n)$ between two coarse-grained membrane patches
+ would be between those for two planar surfaces and two point molecules.
+
+ Large value of $m$ corresponds to a sharp increase in repulsion force as two objects are within the separation distance $\delta$.
+ This poses great challenges for simulations as the numerical time-marching can be very stiff (i.e., very small time step) for large $m$. 
+ The adaptive time-stepping BIE scheme makes it possible to simulate vesicle adhesive dynamics with specified numerical precision for reasonable computation time.
+ We explore several combinations of $(m,n)$ in the simulations 
+ of two vesicles forming a doublet in a quiescent flow, 
+ and found very little difference in both the dynamic evolution and equilibrium configuration between $(m,n)=(8,6)$ and $(m,n)=(4,2)$.
+
+ %
+%
+% Thus we argue that a reasonable choice for $(m,n)$ is
+%between $(m,n) = (4,2)$ and $(m,n) = (12,6)$.
 
@@
 \label{eq:Fh}
-F(h) \sim H \frac{\delta^m}{h^{m+1}}\left(\left(\frac{\delta}{h}\right)^2-1\right),
+F(h) \sim H \frac{\delta^m}{h^{m+1}}\left(\left(\frac{\delta}{h}\right)^{m-n}-1\right),
 \end{align}
@@
 t\frac{K_a^{2/3}}{\mu R_0^{10/3}}& = \int^{h(t)}_{h(0)}-\frac{dh}{h^3
-  F^{1/3}} = -\frac{1}{H^{1/3}\delta^{5/3}}\int^{\bar{h}(t)}_{\bar{h}(0)}\frac{d \bar{h}}{\bar{h}^{(8-m)/3}(\bar{h}^2-1)^{1/3}},
+  F^{1/3}} = -\frac{1}{H^{1/3}\delta^{5/3}}\int^{\bar{h}(t)}_{\bar{h}(0)}\frac{d \bar{h}}{\bar{h}^{(8-m)/3}(\bar{h}^{m-n}-1)^{1/3}},
 \end{align*}

### 2019-01-17 vesicle_code/docs/adhesion/adhesion.tex
more changes from yn

@@
 
- Large value of $m$ corresponds to a sharp increase in repulsion force as two objects are within the separation distance $\delta$.
+ Large value of $m$ corresponds to a sharp increase in the repulsion force as two objects are within the separation distance $\delta$.
  This poses great challenges for simulations as the numerical time-marching can be very stiff (i.e., very small time step) for large $m$. 
@@
  We explore several combinations of $(m,n)$ in the simulations 
- of two vesicles forming a doublet in a quiescent flow, 
- and found very little difference in both the dynamic evolution and equilibrium configuration between $(m,n)=(8,6)$ and $(m,n)=(4,2)$.
+ of two vesicles forming a doublet in a quiescent flow.
+ We found very little difference in both the dynamic evolution and equilibrium configuration between $(m,n)=(8,6)$ and $(m,n)=(4,2)$.
 
@@
 \todo[inline]{Concluding remarks}
+In this work we use boundary integral formulation with adaptive time-stepping  to simulate hydrodynamics of two vesicles with adhesive interactions.
+In a quiescent flow,  two vesicles move towards each other under a long-range attraction when they are in close vicinity of each other.
+We use a lubrication theory to estimate the time it takes to reach the separation distance, and found the theoretical scaling to be in good agreement with numerical results.  
+Once two membranes are within separation distance $\delta$, the adhesive force turns repulsive and the membranes flatten to form a contact region.
+Our simulations show that the membranes in the contact region are actually curved with end points at the shortest distance. 
+Once a vesicle doublet forms, we examine the dependence of membrane bending and adhesion energies on reduced area, Hamakar constant and separation distance.
+
+Next we conduct a numerical experiment where a vesicle doublet is placed at the center of a fluid trap, which in microfluidic laboratory 
+can be actively controlled so that fluid trap center is effectively a stagnation point in an extensional flow characterized by a extensional flow rate.
+At low flow rate, we find the doublet to rotate ninety degrees to align with the flow such that 
+the long axis of the doublet is along the divergent axis and the convergent stream is pushing the two vesicles
+together. As the flow rate increases the vesicle doublet rotates less and we observe tank-treading like motion of both vesicles in the doublet.
+When the flow rate reaches above the critical value, the diverging flow pulls the vesicles apart before the doublet has time to rotate to remain intact.
+These results indicate that it is possible to use the fluid trap to separate a vesicle doublet under adhesion, and thus provide a means to
+probe the adhesion strength between membranes. {\color{red} For adhesion energy blahblahblah, an extensional flow rate sososo is required to separate the doublet from our
+simulations. IS THIS PLAUSIBLE?}
+We hope that our simulations might inspire microfluidic experiments.
+
+We also examine how adhesive interaction may lead to formation of a vesicle doublet dynamically in flowing conditions.
+We simulate two vesicles approaching each other in a planar shear flow, and examine how their adhesive interactions lead to doublet formation.
+Once a doublet forms, the two vesicle membranes rotate around each other as they deform dynamically. The usual tank-treading motion of a vesicle under shear flow is not 
+observed in each of the two vesicles. We also compute the effective shear viscosity of a dilute suspension of vesicle doublets, and found that membrane adhesion contribution
+increases with decreasing reduced area because deflated vesicles (low reduced area) deform more easily and more membranes in the contact region.
+
+In our formulation we did not include any electrostatic interactions between membranes under adhesion. When the electrostatic interaction is important, an electro-osmotic pressure
+in the thin film is found to be responsible for the observed membrane undulation \cite{LiraDimova}.
 
@@
 adhesion to keep vesicles bound under linear flows?
+
+\acknowledgments
+
+YNY would like to acknowledge helpful discussions with 
+The authors acknowledge support from NSF-DMS 1614863 and 1412789 (YNY).
 

### 2019-01-18 vesicle_code/docs/adhesion/adhesion.tex
rearranged some figs

@@
 \begin{figure}[htp]
-  \includegraphics[width=0.5\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
-  \caption{\label{fig:extensionalPhaseDiagram} Phase diagram of vesicle
-  hydrodynamics in an extensional flow.  At a fixed Hamaker constant
-  $H=0.7$ and adhesion length scale $\delta=0.4$.  For small extensional
-  rates, the doublet structure is not broken (blue marks), while at
-  large extensional rates, the doublet is broken (red marks).}
+  \begin{minipage}{0.6\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
+  \end{minipage}
+  \hfill
+  \begin{minipage}{0.33\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{figs/angleDefinition.pdf}
+  \end{minipage}
+  \caption{\label{fig:extensionalPhaseDiagram} {\em Left}:Phase diagram
+  of vesicle hydrodynamics in an extensional flow.  At a fixed Hamaker
+  constant $H=0.7$ and adhesion length scale $\delta=0.4$.  For small
+  extensional rates, the doublet structure is not broken (blue marks),
+  while at large extensional rates, the doublet is broken (red marks).
+  {\em Right}: The definition of the inclination angle.  An inclination
+  angle of $\pi$ indicates a doublet whose long axis is parallel to the
+  converging direction, while an inclination angle of $\pi/2$ indicates
+  a doublet whose short axis is parallel to the converging direction.}
 \end{figure}
@@
 
-\todo[inline]{Plot of the final inclination angle of doublets that
-survive the extensional rate}
-
 \begin{figure}[htp]
-  \begin{minipage}{0.6\textwidth}
+  \begin{minipage}{0.45\textwidth}
   \centering
@@
   \hfill
-  \begin{minipage}{0.33\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{figs/angleDefinition.pdf}
+  \begin{minipage}{0.45\textwidth}
+    \todo[inline]{Plot of the final inclination angle of doublets that
+    survive the extensional rate}
   \end{minipage}
@@
   $0.70$ submerged in an extensional flow with an extensional rate of
-  $\chi$. {\em Right}: The definition of the inclination angle.  An
-  inclination angle of $\pi$ indicates a doublet whose long axis is
-  parallel to the converging direction, while an inclination angle of
-  $\pi/2$ indicates a doublet whose short axis is parallel to the
-  converging direction.}
+  $\chi$.}
 \end{figure}

### 2019-01-18 vesicle_code/docs/adhesion/adhesion.tex
added a few lines and need for time adaptivity

@@
 adhesion force~\eqref{eqn:adhesionForce} is computed with the spectrally
-accurate trapezoid rule~\cite{tre-wei2014}.  To control the error and
-achieve higher-order accuracy in time, we apply a time adaptive spectral
-deferred correction method~\cite{quaife2016adaptive}.  The SDC method is
-able to achieve second-order accuracy by iteratively applying the
-first-order method~\eqref{eqn:IMEXEuler}.
+accurate trapezoid rule~\cite{tre-wei2014}.
+
+The dynamics of a doublet undergoes many different time scales over time
+horizons that are sufficiently large to characterize the formation of a
+doublet and its rheological properties.  Therefore, time adaptivity is
+crucial so that a user-specified tolerance is achieved with using a
+guess-and-check procedure to find an appropriately small fixed time step
+size.  To control the error and achieve higher-order accuracy in time,
+we apply a time adaptive spectral deferred correction
+method~\cite{quaife2016adaptive}.  The SDC method is able to achieve
+second-order accuracy by iteratively applying the first-order
+method~\eqref{eqn:IMEXEuler}.
 

### 2019-01-18 vesicle_code/docs/adhesion/adhesion.tex
small changes to paper

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\todo[inline]{In the extensional flow, put a plus sign after the 0.
-Indicate the flow with arrows.  Do the same for the shear and Figure 9
-(right).}
 
@@
   converging direction, while an inclination angle of $\pi/2$ indicates
-  a doublet whose short axis is parallel to the converging direction.}
+  a doublet whose short axis is parallel to the converging direction.
+  The square mark is a stagnation point while the round point is located
+  at the center of the vesicle.}
 \end{figure}
@@
 \begin{figure}[htp]
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}
   \caption{\label{fig:extensional1} Two vesicles in an extensional flow.
@@
   adhesion length scale is $\delta = 0.4$, extensional rate is $\chi =
-  0.02$.  The doublet tilts to an inclination angle.
-  }
+  0.02$.  The center of the vesicle, denoted with a black square, is a
+  stagnation point.}
 \end{figure}
@@
 \begin{figure}[htp]
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
   \caption{\label{fig:extensional2} Two vesicles in an extensional flow.
@@
   adhesion length scale is $\delta = 0.4$, extensional rate is $\chi =
-  0.07$.  The doublet tilts to an inclination angle.}
+  0.07$.  The center of the vesicle, denoted with a black square, is a
+  stagnation point.}
 \end{figure}
@@
 \begin{figure}[htp]
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
   \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
@@
   adhesion length scale is $\delta = 0.4$, extensional rate is $\chi =
-  0.1$.  The vesicles extensional rate has overcome the adhesive force,
-  and the vesicles doublet is broken.}
+  0.1$.  The center of the vesicle, denoted with a black square, is a
+  stagnation point.}
 \end{figure}
@@
 \begin{figure}[htp]
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
-  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
   \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
   The reduced area is $0.8$, the Hamaker constant is $H = 0.7$, and the
-  adhesion length scale is $\delta0.4$, extensional rate is $\chi =
+  adhesion length scale is $\delta = 0.4$, extensional rate is $\chi =
   0.1$.  Initially, the doublet tilts to an inclination angle, and then
   the extensional rate overcomes the adhesive force and the doublet is
-  broken.}
+  broken.  The center of the vesicle, denoted with a black square, is a
+  stagnation point.}
 \end{figure}
@@
 \end{figure}
+\todo[inline]{Indicate the shear flow in the right most plot.}
 

### 2019-01-18 vesicle_code/examples/output/makeImages.m

@@ -5,7 +5,7 @@ irate = 25; % controls the speed of the visualization
 
 if 1
   file = 'extensional2VesBData.bin';
-%  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi1em1_ra070/extensional2VesData.bin';
+  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi9em2_ra070_longT/extensional2VesData.bin';
   ax = [-4 4 -5 5];
   options.confined = false;
 end

### 2019-01-21 vesicle_code/docs/adhesion/adhesion.tex
added a cartoon figure

@@
 adhesion between a single three-dimensional vesicle and a solid wall at
-$z=0$.  \todo[inline]{Need a cartoon picture in here.  Some kind of
-version of the one I had for my SIAM Life Sciences Talk} The adhesion
-potential in their model is of the functional form in
-equation~\eqref{eq:adhesion_potential} with $(m,n) = (4,2)$:
+$z=0$.  The adhesion potential in their model is of the functional form
+in equation~\eqref{eq:adhesion_potential} with $(m,n) = (4,2)$:
 \begin{align}
@@
 \end{align}
-
-%\begin{align}
-%  \AA\xx:=-4 H \delta^2\sum_{\substack{k=1 \\ k \neq j}}^M 
-%  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^6} 
-%  \left(\delta^2 - \|\xx - \yy\|^2 \right) ds_\yy.
-%  \label{eqn:adhesionForce}
-%\end{align}
+The adhesion model is illustrated in Figure~\ref{fig:adhesionModel}.
+
+\begin{figure}[htp]
+  \begin{minipage}{0.48\textwidth}
+    \centering
+    \includegraphics[height=6cm]{figs/adhesionPotential.pdf}
+  \end{minipage}
+  \hfill
+  \begin{minipage}{0.48\textwidth}
+    \centering
+    \includegraphics[height=6cm]{figs/configCartoon.pdf}
+  \end{minipage}
+  \caption{\label{fig:adhesionModel} {\em Left}: The adhesion potential
+  $\phi(z)$ in Equation~\eqref{eq:adhesion_potential}.  Distances in the
+  green region are repulsive and distances in the blue region are
+  attractive.  {\em Right}: The resulting adhesive force of a single
+  vesicle of a doublet using Equation~\eqref{eqn:adhesionForce}.  The
+  point marked in with a red dot is repelled by the green region and
+  attracted to the blue region.  The net forces are plotted with the
+  black arrows.}
+\end{figure}
 

### 2019-01-23 vesicle_code/docs/adhesion/adhesion.tex
updated figure 1

@@
   \caption{\label{fig:adhesionModel} {\em Left}: The adhesion potential
-  $\phi(z)$ in Equation~\eqref{eq:adhesion_potential}.  Distances in the
-  green region are repulsive and distances in the blue region are
+  $\phi(z)$ in Equation~\eqref{eq:adhesion_potential}.  Distances less
+  than $\delta$ are repulsive and distances greater than $\delta$ are 
   attractive.  {\em Right}: The resulting adhesive force of a single
   vesicle of a doublet using Equation~\eqref{eqn:adhesionForce}.  The
-  point marked in with a red dot is repelled by the green region and
-  attracted to the blue region.  The net forces are plotted with the
-  black arrows.}
+  point marked with a blue dot is repelled by the region of the vesicle
+  denoted with a thick line, and attracted to the remainder of the
+  vesicle.  The blue region is repelled to the right vesicle and the red
+  region is attracted by the vesicle.}
 \end{figure}

### 2019-01-25 vesicle_code/docs/adhesion/adhesion.tex
fixed up figure 1

@@
 \begin{figure}[htp]
-  \begin{minipage}{0.48\textwidth}
+  \begin{minipage}{0.31\textwidth}
     \centering
-    \includegraphics[height=6cm]{figs/adhesionPotential.pdf}
+    \includegraphics[height=5cm,trim={0cm 0cm 2cm 0cm},clip]{figs/adhesionPotential.pdf}
   \end{minipage}
   \hfill
-  \begin{minipage}{0.48\textwidth}
+  \begin{minipage}{0.31\textwidth}
     \centering
-    \includegraphics[height=6cm]{figs/configCartoon.pdf}
+    \includegraphics[height=5cm]{figs/configCartoon.pdf}
+  \end{minipage}
+  \hfill
+  \begin{minipage}{0.31\textwidth}
+    \centering
+    \includegraphics[height=5cm,trim={3cm 0cm 2cm 0cm},clip]{figs/Adhesion_Force.png}
   \end{minipage}
@@
 vesicles with three values of reduced area: $\Delta A=0.95$, $0.75$ and
-$0.6$ with $H=5$ \todo[inline]{Is this really the Hamaker constant?
-It's not 0.5?} and $\delta = 0.2$.  The equilibrium vesicle shape for
+$0.6$ with $H=5$ and $\delta = 0.2$.  The equilibrium vesicle shape for
 $\Delta A=0.95$ is the circular cap with a flatten contact region.  This
@@
 \begin{align*}
-  \langle \sigma \rangle = \frac{1}{|\omega|} \int_{\gamma}
+  \langle \tau \rangle = \frac{1}{|\omega|} \int_{\gamma}
     \xxi \otimes \xx ds.
@@
 Here, $[\mu]$ is the intrinsic viscosity, $\phi$ is the area fraction of
-vesicles, $\sigma$ is the stress due to the vesicles, and $\langle \cdot
+vesicles, $/tau$ is the stress due to the vesicles, and $\langle \cdot
 \rangle$ is the spatial average.
-\todo[inline]{Stress $\sigma$ is also used for tension}
 

### 2019-01-26 vesicle_code/docs/adhesion/adhesion.tex
new figures from yny

@@
 \begin{figure}
-\includegraphics[keepaspectratio=true,scale=0.4]{figs/Dec13a_time_scaling01.eps}
-\includegraphics[keepaspectratio=true,scale=0.4]{figs/Dec13a_time_scaling02.eps}
+\includegraphics[keepaspectratio=true,scale=0.4]{figs/Dec13a_time_scaling01.png}
+\includegraphics[keepaspectratio=true,scale=0.4]{figs/Dec13a_time_scaling02.png}
 \caption{\label{fig:qflow00} Scaling of the time it takes for two

### 2019-01-28 vesicle_code/docs/adhesion/adhesion.tex
modifications from yny so far

@@
 
-\title{Hydrodynamics and rheology of adhesive vesicle doublets}
+\title{Hydrodynamics and rheology of weakly adhesive vesicle doublets}
 % Force line breaks with \\
@@
 %
-Collective dynamics of vesicles naturally is dictated by the individual
-vesicle-vesicle interactions.  In numerical simulations of vesicle
-suspensions, it is often assumed that the liquid film between vesicles
-acts to keep the membrane-membrane interaction, such as the van der
-Waals type adhesive interaction, negligible.  However the amphiphilic
+Collective hydrodynamics of vesicles naturally is dictated by the individual
+vesicle-vesicle interactions.  
+In a quiescent flow,
+vesicle-vesicle adhesion leads to formation of vesicle doublets \cite{ZiherlSvetina2007_PNAS} or clusters \cite{SvetinaZiherl2008_Bioelectrochemistry,FlormannAouane2017_SciReports}.
+As a model for red blood cell (RBC) aggregates, an idealized model for adhesive vesicle-vesicle interactions gives rise to 
+vesicle configurations that are observed in experiments of fibrinogen-induced RBC aggregates \cite{SvetinaZiherl2008_Bioelectrochemistry,FlormannAouane2017_SciReports}. 
+Using the L-J potential for pairwise point-point interaction between two vesicle membranes without the detailed molecular details of
+adhesive interactions between RBCs, Flormann {\it et al.} found the contact zone to buckle under strong adhesion \cite{FlormannAouane2017_SciReports}. 
+A direct consequence of the buckling is the
+sigmoidal shape of the adhesion region, which is also observed in RBC doublets and explained in a slightly different model \cite{ZiherlSvetina2007_PNAS}. 
+It remains unknown how adhesive interactions between vesicles might lead to different vesicle hydrodynamics that results in
+different rheological properties of a vesicle suspension. Such studies will provide useful insight to the rheology of blood flow and how to use nano solutes to control the hypertension
+by adjusting the adhesive interactions between RBCs.
+%
+
+In numerical simulations of  a vesicle suspension, the adhesive interaction between two vesicles is often ignored for numerical convenience
+because a smaller time step is often needed to resolve the dynamics of the lubrication thin film between two membranes with adhesion than without.
+However, adhesive interactions  between RBCs lead to different RBC clusters that are expected to alter the rheological properties of the RBC suspension \cite{NeuMeiselman2002_BiophysJ,SvetinaZiherl2008_Bioelectrochemistry}.
+Hydrodynamic simulations of adhesive vesicles in a quiescent flow have revealed physical insights to the equilibrium shapes of RBC aggregates in both experiments 
+\cite{FlormannAouane2017_SciReports} and theory \cite{ZiherlSvetina2007_PNAS}. The main goal in this work is to investigate the hydrodynamics of adhesive vesicles in flowing
+conditions common in microfluidic vesicle flow, such as a planar shear flow or an extensional flow.
+
+%
+The electrostatic
 natures of lipid molecules (a hydrophobic tail and a hydrophilic head
@@
 bilayer membrane and another bilayer
-membrane~\cite{EvansMetcalfe1984_BJ, Book_PhysicalBasisCellAdhesion,
-Book_IntermolecularSurfaceForces} or a solid (such as a glass substrate
-or a nano particle).  Studies confirmed that such interaction potential
-inevitably consists of a long-range attraction component and a
+membrane~\cite{EvansMetcalfe1984_BJ, Book_PhysicalBasisCellAdhesion,Book_IntermolecularSurfaceForces,PerutkovaFrank-Bertoncelij2013_CSB} 
+or a solid (such as a glass substrate
+or a nano particle).  it is reported that such complicated electrostatic contribution in the adhesive interactions between two membranes can be well approximated by the 
+L-J-type potential \cite{FlormannAouane2017_SciReports}, which consists of a long-range attraction component and a
 short-range repulsion component~\cite{Book_IntermolecularSurfaceForces},

### 2019-01-28 vesicle_code/docs/adhesion/adhesion.tex
fixed out some figures

--- 2019-01-26 vesicle_code/docs/adhesion/adhesion.tex
@@
   than $\delta$ are repulsive and distances greater than $\delta$ are
-  attractive.  {\em Right}: The resulting adhesive force of a single
-  vesicle of a doublet using Equation~\eqref{eqn:adhesionForce}.  The
-  point marked with a blue dot is repelled by the region of the vesicle
-  denoted with a thick line, and attracted to the remainder of the
-  vesicle.  The blue region is repelled to the right vesicle and the red
-  region is attracted by the vesicle.}
+  attractive.  {\em Center}: Each point on a vesicle is repelled or
+  attracted by all points on the other vesicles.  {\em Left}: The
+  resulting adhesive force is found by integrating over all points on
+  all other vesicles (equation~\eqref{eqn:adhesionForce}).  The color is
+  the dot product of the adhesion force with the vector joining the
+  vesicles.  Therefore, the green and blue regions are repelled by the
+  other vesicle while the yellow regions are attracted to the other
+  vesicle.}
 \end{figure}
@@
   \centering
-  \includegraphics[width=\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
+  \includegraphics[height=\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
   \end{minipage}
@@
   \begin{minipage}{0.45\textwidth}
-    \todo[inline]{Plot of the final inclination angle of doublets that
-    survive the extensional rate}
+    \includegraphics[height=\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
   \end{minipage}
@@
   $0.70$ submerged in an extensional flow with an extensional rate of
-  $\chi$.}
+  $\chi$.  {\em Right}: The final inclination angle of doublets.
+  Results are not reported for all the low extensional rates since the
+  doublet had not tilted to a steady-state inclination angle for the
+  given time horizon.}
 \end{figure}
@@
   $\chi=0.5$.}
-  \todo[inline]{Superimpose the background velocity on the leftmost plot
-  to indicate the shearing motion}
-\end{figure}
-\todo[inline]{Indicate the shear flow in the right most plot.}
+\end{figure}
 

### 2019-01-28 vesicle_code/examples/output/computeForceStress.m

@@ -6,12 +6,15 @@ end
 if 0
   file = 'shear1VesData.bin';
 end
-if 1
+if 0
   file = 'shear2VesData.bin';
   ax = [-8 8 -3 3];
 end
 if 0
   file = 'shear4VesData.bin';
+end
+if 1
+  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi7em2_ra070/extensional2VesData.bin';
 end
 
 oc = curve;
@@ -20,8 +23,8 @@ oc = curve;
 % load positions, tension, errors, time, number of points, and number of
 % vesicles
 
-adStrength = 0.6;
-adRange = 2e-1;
+adRange = 0.4;
+adStrength = 0.7;
 adhesion = true;
 % adhesion strength, range, and a flag to denote that adhesion is active
 
@@ -31,13 +34,13 @@ ntime = size(posx,3); % number of time steps
 
 Forcex = zeros(nv,ntime);
 Forcey = zeros(nv,ntime);
-Torque = zeros(nv,ntime);
+%Torque = zeros(nv,ntime);
 
 for k = 1:ntime
   X = [posx(:,:,k);posy(:,:,k)];
   sigma = ten(:,:,k);
   vesicle = capsules(X,sigma,[],1e-1,[]);
-  vesicle.center = 0*vesicle.center + 0;
+%  vesicle.center = 0*vesicle.center + 0;
 %  vesicle.center = 2*ones(2,nv);
 
   tanx = vesicle.xt(1:end/2,:);
@@ -47,8 +50,8 @@ for k = 1:ntime
 
 %  f = vesicle.tensionTerm(sigma);
 %  f = vesicle.bendingTerm(X);
-%  f = vesicle.tracJump(X,sigma);
-  f = zeros(2*N,nv);
+  f = vesicle.tracJump(X,sigma);
+%  f = zeros(2*N,nv);
   if adhesion
     f = f + vesicle.adhesionTerm(adStrength,adRange);
   end
@@ -56,51 +59,50 @@ for k = 1:ntime
   Forcex(:,k) = sum(f(1:end/2,:).*vesicle.sa)*2*pi/N;
   Forcey(:,k) = sum(f(end/2+1:end,:).*vesicle.sa)*2*pi/N;
[…]

### 2019-01-28 vesicle_code/docs/adhesion/adhesion.tex
abstract added by yny

--- 2019-01-28 vesicle_code/docs/adhesion/adhesion.tex
@@
 
+The dynamic consequences of weakly adhesive vesicles under various flowing conditions are investigated numerically using a boundary integral formulation with
+adaptive time-marching that facilitates efficient and accurate computations of vesicle hydrodynamics under adhesion. In a quiescent flow, a lubrication analysis illustrates the scaling in 
+the draining dynamics with respect to the adhesion strength and length scale.
+In a microfluid trap, results from boundary integral simulations show that there exists a critical extensional flow rate above which the weak adhesive interaction is overcome by the hydrodynamic diverging stream, thus providing a simple method to measure the adhesion strength between two vesicle membranes.
+In a planar shear flow, numerical simulations reveal that a vesicle doublet may form as they approach each other in a planar shear flow provided that the adhesion
+strength is sufficient large at a given vesicle reduced area. Once a doublet the effective shear viscosity of a dilute suspension of vesicle doublets is found 
+to be a function of both reduced area and the adhesion strength.
+Results from these numerical studies and analysis shed light on the hydrodynamic effects of adhesive interactions between vesicles in a viscous fluid.
 %\begin{description}
@@
 or a solid (such as a glass substrate
-or a nano particle).  it is reported that such complicated electrostatic contribution in the adhesive interactions between two membranes can be well approximated by the 
+or a nano particle).  It is reported that such complicated electrostatic contribution in the adhesive interactions between two membranes can be well approximated by the 
 L-J-type potential \cite{FlormannAouane2017_SciReports}, which consists of a long-range attraction component and a

### 2019-01-28 vesicle_code/docs/adhesion/adhesion.tex
changes in abstract by yny

@@
 
-The dynamic consequences of weakly adhesive vesicles under various flowing conditions are investigated numerically using a boundary integral formulation with
+The dynamics of weakly adhesive vesicles under various flowing conditions is investigated numerically using a boundary integral formulation with
 adaptive time-marching that facilitates efficient and accurate computations of vesicle hydrodynamics under adhesion. In a quiescent flow, a lubrication analysis illustrates the scaling in 

### 2019-01-28 vesicle_code/docs/adhesion/adhesion.tex
some minor changes by yny

@@
 The dynamics of weakly adhesive vesicles under various flowing conditions is investigated numerically using a boundary integral formulation with
-adaptive time-marching that facilitates efficient and accurate computations of vesicle hydrodynamics under adhesion. In a quiescent flow, a lubrication analysis illustrates the scaling in 
-the draining dynamics with respect to the adhesion strength and length scale.
-In a microfluid trap, results from boundary integral simulations show that there exists a critical extensional flow rate above which the weak adhesive interaction is overcome by the hydrodynamic diverging stream, thus providing a simple method to measure the adhesion strength between two vesicle membranes.
+adaptive time-marching that facilitates efficient and accurate computations of vesicle hydrodynamics under adhesion. In a quiescent flow, two nearby vesicles 
+move slowly towards each other under the adhesive potential, pushing out fluid in the gap to  
+form a doublet at equilibrium. A lubrication analysis on such draining of the
+thin film gives the dependencies of draining time on adhesion strength and separation distance that are in good agreement with results from
+boundary integral simulations.
+%
+In a microfluid trap where the stagnation of an extensional flow  is placed in the middle of a vesicle doublet through an active control loop,
+novel dynamics of a vesicle double tis observed.
+Results from boundary integral simulations show that there exists a critical extensional flow rate above which the weak adhesive interaction is overcome by the hydrodynamic diverging stream, thus providing a simple method to measure the adhesion strength between two vesicle membranes.
+%
 In a planar shear flow, numerical simulations reveal that a vesicle doublet may form as they approach each other in a planar shear flow provided that the adhesion
@@
 %
-Collective hydrodynamics of vesicles naturally is dictated by the individual
+Collective hydrodynamics of vesicles is dictated by the individual
 vesicle-vesicle interactions.  
@@
 As a model for red blood cell (RBC) aggregates, an idealized model for adhesive vesicle-vesicle interactions gives rise to 
-vesicle configurations that are observed in experiments of fibrinogen-induced RBC aggregates \cite{SvetinaZiherl2008_Bioelectrochemistry,FlormannAouane2017_SciReports}. 
-Using the L-J potential for pairwise point-point interaction between two vesicle membranes without the detailed molecular details of
+vesicle configurations similar to those observed in experiments of fibrinogen-induced RBC aggregates \cite{SvetinaZiherl2008_Bioelectrochemistry,FlormannAouane2017_SciReports}. 
+Using the L-J potential for point-point interaction between two vesicle membranes without the detailed molecular details of
 adhesive interactions between RBCs, Flormann {\it et al.} found the contact zone to buckle under strong adhesion \cite{FlormannAouane2017_SciReports}. 
@@
 
-In numerical simulations of  a vesicle suspension, the adhesive interaction between two vesicles is often ignored for numerical convenience
+In numerical simulations of  a vesicle suspension, the adhesive interaction between two vesicles is often ignored \cite{Veerapaneni2009_JCP,RahimianVeerapaneniBiros2010_JCP} 
+for numerical convenience
 because a smaller time step is often needed to resolve the dynamics of the lubrication thin film between two membranes with adhesion than without.
@@
 The electrostatic
-natures of lipid molecules (a hydrophobic tail and a hydrophilic head
-with an electric dipole) complicate the interactions between a lipid
+nature of lipid molecules (a hydrophobic tail and a hydrophilic head
+with an electric dipole) complicates the interactions between a lipid
 bilayer membrane and another bilayer
@@
 or a solid (such as a glass substrate
-or a nano particle).  It is reported that such complicated electrostatic contribution in the adhesive interactions between two membranes can be well approximated by the 
+or a nano particle).  In the absence of an external electric field and ions in the solvents, 
+it is reported that 
+%such complicated electrostatic component in 
+the adhesive interactions between two membranes can be well approximated by the 
 L-J-type potential \cite{FlormannAouane2017_SciReports}, which consists of a long-range attraction component and a

### 2019-01-28 vesicle_code/docs/adhesion/adhesion.tex
some minor changes by yny

@@
 In a microfluid trap where the stagnation of an extensional flow  is placed in the middle of a vesicle doublet through an active control loop,
-novel dynamics of a vesicle double tis observed.
+novel dynamics of a vesicle doublet is observed.
 Results from boundary integral simulations show that there exists a critical extensional flow rate above which the weak adhesive interaction is overcome by the hydrodynamic diverging stream, thus providing a simple method to measure the adhesion strength between two vesicle membranes.

### 2019-01-28 vesicle_code/docs/adhesion/adhesion.tex
updated figure 6

@@
   \caption{\label{fig:extensionalPhaseDiagram} {\em Left}:Phase diagram
-  of vesicle hydrodynamics in an extensional flow.  At a fixed Hamaker
-  constant $H=0.7$ and adhesion length scale $\delta=0.4$.  For small
+  of vesicle hydrodynamics in an extensional flow with a fixed Hamaker
+  constant $H=0.7$ and adhesion length scale $\delta = 0.4$.  For small
   extensional rates, the doublet structure is not broken (blue marks),
   while at large extensional rates, the doublet is broken (red marks).
-  {\em Right}: The definition of the inclination angle.  An inclination
-  angle of $\pi$ indicates a doublet whose long axis is parallel to the
-  converging direction, while an inclination angle of $\pi/2$ indicates
-  a doublet whose short axis is parallel to the converging direction.
-  The square mark is a stagnation point while the round point is located
-  at the center of the vesicle.}
+  The size of the round blue marks indicate the final inclination angle
+  with the larger dots rotation less ($\theta=pi$) and the smaller dots
+  rotating more ($\theta = pi/2$).  A square mark is used for
+  simulations that did not result in a steady-state inclination angle in
+  the given time horizon.  {\em Right}: The definition of the
+  inclination angle.  An inclination angle of $\pi$ indicates a doublet
+  whose long axis is parallel to the converging direction, while an
+  inclination angle of $\pi/2$ indicates a doublet whose short axis is
+  parallel to the converging direction.  The square mark is a stagnation
+  point while the round point is located at the center of the vesicle.}
 \end{figure}

### 2019-01-28 vesicle_code/examples/output/makeImages.m

@@ -1,11 +1,12 @@
 addpath ../../src
 set(0,'DefaultAxesFontSize',22)
 
-irate = 10; % controls the speed of the visualization
+irate = 20; % controls the speed of the visualization
 
-if 0
-  file = 'extensional2VesData.bin';
-  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi4em2_ra095/extensional2VesData.bin';
+if 1
+%  file = 'extensional2VesData.bin';
+%  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi1em2_ra070/extensional2VesData.bin';
+  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi6em2_ra090/extensional2VesData.bin';
   ax = [-2 2 -2 2];
   options.confined = false;
 end
@@ -20,7 +21,8 @@ if 0
   options.confined = false;
 end
 if 0
-  file = 'relaxationManyVesData.bin';
+  file = '~/projects/brinkman/vesicle_code/results/relaxationManyVes/Segment3/relaxationManyVesData.bin';
+%  file = 'relaxationManyVesData.bin';
   ax = [-5 5 -6 6];
   options.confined = false;
   options.savefig = false;
@@ -47,9 +49,9 @@ if 0
   ax = [-8 8 -5 5];
   options.confined = false;
 end
-if 1
-  file = 'shear2VesJData.bin.run1';
-%  file = '~/projects/brinkman/vesicle_code/results/shear2Ves/adR4em1adS7em1Chi5em1_ra045/shear2VesData.bin';
+if 0
+%  file = 'shear2VesGData.bin.run1';
+  file = '~/projects/brinkman/vesicle_code/results/shear2Ves/adR4em1adS6em1Chi1p25e0_ra070/shear2VesData.bin';
   ax = [-10 10 -3 3];
   options.confined = false;
 end

### 2019-01-29 vesicle_code/docs/adhesion/adhesion.tex
started fixing up the extensional section ... needs work yet on the language

@@
 extensional rate is sufficiently large that the doublet is broken.  In
-Figure~\ref{fig:extensionalPhaseDiagram}.
+Figure~\ref{fig:extensionalPhaseDiagram}, the red marks correspond to
+parameters where the doublet is broken while the red marks correspond to
+parameters where the doublet tends to a steady-state fluid trap.  In the
+case that there is a fluid trap, the doublet rotates from the unstable
+configuration where the converging rate is in the direction that is
+parallel to the long axis of the vesicles.  At low extensional rates,
+the inclination angle approaches $\pi$ which corresponds to the
+converging direction being aligned with the short axis of the vesicle
+(Figure~\ref{fig:extensional1}).  As the extensional rate is increased,
+the vesicle tilts to a shallower inclination angle
+(Figures~\ref{fig:extensional2} and~\ref{fig:extensional3}).  Finally,
+when the inclination angle is sufficiently large, the doublet is broken
+(Figure~\ref{fig:extensional4}).  In
+Figure~\ref{fig:extensionalPhaseDiagram}, the size of the round marks
+correspond to the inclination angle.  The square marks correspond to
+doublets that do not reach a steady-state inclination angle in the given
+time horizon.
 
@@
 
-In Figures~\ref{fig:extensional1}--\ref{fig:extensional3}, we show
-snapshots of two vesicles of reduced area $0.70$ in an extensional flow
-with three different extensional rates.  Interestingly, when the
-extensional rate does not overcome the adhesion rate, the doublet does
-not remain parallel to the stagnation point, but instead tilts to an
-inclination angle (Figures~\ref{fig:extensional1}
-and~\ref{fig:extensional2}.  We include a plot of the inclination angle
-as a function of time for varying extensional rates (left plot of
-Figure~\ref{fig:extensionalInclinationAngle}).  The inclination angle is
-defined defined in with respect to the diverging direction (right plot
-of Figure~\ref{fig:extensionalInclinationAngle}).  When the doublet is
-broken at reduced area $0.70$, the extensional rate is sufficiently
-large to align the long axis of the vesicle with the diverging direction
-and then the vesicles separate.  However, for larger reduced areas, the
-separation dynamics is different.  Instead, the vesicles tilt to an
-inclination angle and then separate (Figure~\ref{fig:extensional4}).
+%In Figures~\ref{fig:extensional1}--\ref{fig:extensional3}, we show
+%snapshots of two vesicles of reduced area $0.70$ in an extensional flow
+%with three different extensional rates.  Interestingly, when the
+%extensional rate does not overcome the adhesion rate, the doublet does
+%not remain parallel to the stagnation point, but instead tilts to an
+%inclination angle (Figures~\ref{fig:extensional1}
+%and~\ref{fig:extensional2}.
 
@@
   \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
-  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
+  \caption{\label{fig:extensional4} Two vesicles in an extensional flow.
   The reduced area is $0.7$, the Hamaker constant is $H = 0.7$, and the
@@
 
+We include a plot of the inclination angle as a function of time for
+varying extensional rates (left plot of
+Figure~\ref{fig:extensionalInclinationAngle}).  The inclination angle is
+defined defined in with respect to the diverging direction (right plot
+of Figure~\ref{fig:extensionalInclinationAngle}).  When the doublet is
+broken at reduced area $0.70$, the extensional rate is sufficiently
+large to align the long axis of the vesicle with the diverging direction
+and then the vesicles separate.  However, for larger reduced areas, the
+separation dynamics is different.  Instead, the vesicles tilt to an
+inclination angle and then separate (Figure~\ref{fig:extensional4}).
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In our formulation we did not include any electrostatic interactions between membranes under adhesion. When the electrostatic interaction is important, an electro-osmotic pressure
-in the thin film is found to be responsible for the observed membrane undulation \cite{LiraDimova}.
+In our formulation we did not include any electrostatic interactions
+between membranes under adhesion. When the electrostatic interaction is
+important, an electro-osmotic pressure in the thin film is found to be
+responsible for the observed membrane undulation~\cite{LiraDimova}.
 

### 2019-01-29 vesicle_code/examples/output/makeImages.m

@@ -3,7 +3,7 @@ set(0,'DefaultAxesFontSize',22)
 
 irate = 20; % controls the speed of the visualization
 
-if 1
+if 0
 %  file = 'extensional2VesData.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi1em2_ra070/extensional2VesData.bin';
   file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi6em2_ra090/extensional2VesData.bin';
@@ -49,9 +49,9 @@ if 0
   ax = [-8 8 -5 5];
   options.confined = false;
 end
-if 0
+if 1
 %  file = 'shear2VesGData.bin.run1';
-  file = '~/projects/brinkman/vesicle_code/results/shear2Ves/adR4em1adS6em1Chi1p25e0_ra070/shear2VesData.bin';
+  file = '~/projects/brinkman/vesicle_code/results/shear2Ves/adR4em1adS7em1Chi1p25e0_ra070/shear2VesData.bin';
   ax = [-10 10 -3 3];
   options.confined = false;
 end

### 2019-01-29 vesicle_code/docs/adhesion/adhesion.tex
added some subplots to fig 6

@@
 
+The doublet starts at an angle of $\pi$ and rotates towards some number
+less than $\pi/2$ (if it converges).
+
 As expected, we observe two different regimes---the extensional rate is
@@
 \begin{figure}[htp]
-  \begin{minipage}{0.6\textwidth}
+  \begin{minipage}{0.63\textwidth}
     \centering
@@
   \hfill
-  \begin{minipage}{0.33\textwidth}
+  \begin{minipage}{0.35\textwidth}
     \centering
-    \includegraphics[width=\textwidth]{figs/angleDefinition.pdf}
+    \includegraphics[width=0.8\textwidth]{figs/angleDefinition.pdf}
+    \includegraphics[height=0.45\textwidth]{figs/rotate1.pdf}
+    \hfill
+    \includegraphics[height=0.45\textwidth]{figs/rotate2.pdf}
   \end{minipage}
-  \caption{\label{fig:extensionalPhaseDiagram} {\em Left}:Phase diagram
+  \caption{\label{fig:extensionalPhaseDiagram} {\em Left}: Phase diagram
   of vesicle hydrodynamics in an extensional flow with a fixed Hamaker
@@
   The size of the round blue marks indicate the final inclination angle
-  with the larger dots rotation less ($\theta=pi$) and the smaller dots
-  rotating more ($\theta = pi/2$).  A square mark is used for
+  with the larger dots rotation less ($\theta=\pi$) and the smaller dots
+  rotating more ($\theta = \pi/2$).  A square mark is used for
   simulations that did not result in a steady-state inclination angle in
@@
   \centering
-  \includegraphics[height=\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
+  \includegraphics[height=0.8\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
   \end{minipage}
@@
   \begin{minipage}{0.45\textwidth}
-    \includegraphics[height=\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
+    \includegraphics[height=0.8\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
   \end{minipage}

### 2019-01-29 vesicle_code/examples/output/makeImages.m

@@ -3,10 +3,9 @@ set(0,'DefaultAxesFontSize',22)
 
 irate = 20; % controls the speed of the visualization
 
-if 0
+if 1
 %  file = 'extensional2VesData.bin';
-%  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi1em2_ra070/extensional2VesData.bin';
-  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi6em2_ra090/extensional2VesData.bin';
+  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi7em2_ra070/extensional2VesData.bin';
   ax = [-2 2 -2 2];
   options.confined = false;
 end
@@ -49,9 +48,9 @@ if 0
   ax = [-8 8 -5 5];
   options.confined = false;
 end
-if 1
+if 0
 %  file = 'shear2VesGData.bin.run1';
-  file = '~/projects/brinkman/vesicle_code/results/shear2Ves/adR4em1adS7em1Chi1p25e0_ra070/shear2VesData.bin';
+  file = '~/projects/brinkman/vesicle_code/results/shear2Ves/adR4em1adS1e0Chi2e0_ra070/shear2VesData.bin';
   ax = [-10 10 -3 3];
   options.confined = false;
 end

### 2019-01-30 vesicle_code/docs/adhesion/adhesion.tex
bib updated by yny

--- 2019-01-29 vesicle_code/docs/adhesion/adhesion.tex
@@
 In a quiescent flow,
-vesicle-vesicle adhesion leads to formation of vesicle doublets \cite{ZiherlSvetina2007_PNAS} or clusters \cite{SvetinaZiherl2008_Bioelectrochemistry,FlormannAouane2017_SciReports}.
+vesicle-vesicle adhesion leads to formation of vesicle doublets \cite{Ziherl2007_PRL,ZiherlSvetina2007_PNAS} or clusters \cite{SvetinaZiherl2008_Bioelectrochemistry,FlormannAouane2017_SciReports}.
 As a model for red blood cell (RBC) aggregates, an idealized model for adhesive vesicle-vesicle interactions gives rise to 
@@
 because a smaller time step is often needed to resolve the dynamics of the lubrication thin film between two membranes with adhesion than without.
-However, adhesive interactions  between RBCs lead to different RBC clusters that are expected to alter the rheological properties of the RBC suspension \cite{NeuMeiselman2002_BiophysJ,SvetinaZiherl2008_Bioelectrochemistry}.
+However, adhesive interactions  between RBCs lead to different RBC clusters that are expected to alter the rheological properties of the RBC suspension \cite{NeuMeiselman2002_BJ,SvetinaZiherl2008_Bioelectrochemistry}.
 Hydrodynamic simulations of adhesive vesicles in a quiescent flow have revealed physical insights to the equilibrium shapes of RBC aggregates in both experiments 
@@
 %
-The electrostatic
-nature of lipid molecules (a hydrophobic tail and a hydrophilic head
+The electrostatic nature of lipid molecules (a hydrophobic tail and a hydrophilic head
 with an electric dipole) complicates the interactions between a lipid
@@
 important, an electro-osmotic pressure in the thin film is found to be
-responsible for the observed membrane undulation~\cite{LiraDimova}.
+responsible for the observed membrane undulation~\cite{SteinkuhlerAgudo-Canalejo2016_BJ}.
 

### 2019-01-30 vesicle_code/docs/adhesion/adhesion.tex
more chnages in intro by yny

@@
 experiments~\cite{KantslerSegreSteinberg2008_EPL,
-ZabuskySegreDeschamps2011_PoF}.  Between TT and TB vesicle
-hydrodynamics, a breathing (tremble) is also
+ZabuskySegreDeschamps2011_PoF}.  Between TT and TB vesicle dynamics, a breathing (tremble) mode is also
 observed~\cite{Misbah2006_PRL,KantslerSegreSteinberg2008_PRL,
@@
 vesicle configurations similar to those observed in experiments of fibrinogen-induced RBC aggregates \cite{SvetinaZiherl2008_Bioelectrochemistry,FlormannAouane2017_SciReports}. 
-Using the L-J potential for point-point interaction between two vesicle membranes without the detailed molecular details of
+Using the L-J potential for point-point interaction between two vesicle membranes without the molecular details of
 adhesive interactions between RBCs, Flormann {\it et al.} found the contact zone to buckle under strong adhesion \cite{FlormannAouane2017_SciReports}. 
@@
 
-In numerical simulations of  a vesicle suspension, the adhesive interaction between two vesicles is often ignored \cite{Veerapaneni2009_JCP,RahimianVeerapaneniBiros2010_JCP} 
-for numerical convenience
+In numerical simulations of  a vesicle suspension, the adhesive interaction between two vesicles is often 
+ignored \cite{Veerapaneni2009_JCP,RahimianVeerapaneniBiros2010_JCP} 
+for numerical convenience, mostly 
 because a smaller time step is often needed to resolve the dynamics of the lubrication thin film between two membranes with adhesion than without.
 However, adhesive interactions  between RBCs lead to different RBC clusters that are expected to alter the rheological properties of the RBC suspension \cite{NeuMeiselman2002_BJ,SvetinaZiherl2008_Bioelectrochemistry}.
+%
 Hydrodynamic simulations of adhesive vesicles in a quiescent flow have revealed physical insights to the equilibrium shapes of RBC aggregates in both experiments 
@@
 or a solid (such as a glass substrate
-or a nano particle).  In the absence of an external electric field and ions in the solvents, 
+or a nano particle).  Adhesion between a vesicle and a substrate has been extensively studied,
+primarily focused on analyzing the static equilibrium
+shapes~\cite{Seifert1990_PRA, ShiFengGao2006_ActaMechSin,
+LinFreund2007_IntJSolidsStructures, das2008adhesion, zhang2009phase,SteinkuhlerAgudo-Canalejo2016_BJ}
+than the transient adhesion process \cite{cantat1999lift, suk-sei2001, BlountMiksisDavis2013_PRSa}.
+%
+Adhesive interactions between lipid membranes are essential in many biomedical, biological and biophysical
+processes.  For example, vesicle adhesion is crucial to initiate membrane
+fusion/fission in endocytosis and exocytosis, the transport of small
+vesicles through membrane surfaces.
+In the absence of an external electric field and ions in the solvents, 
 it is reported that 
@@
 distance that minimizes the interaction
-potential~\cite{Book_IntermolecularSurfaceForces}. Such adhesive
-potentials are essential in many biomedical, biological and biophysical
-processes.  For example, vesicle adhesion is essential for membrane
-fusion/fission in endocytosis and exocytosis, the transport of small
-vesicles through membrane surfaces.
-
-Adhesion between a vesicle and a substrate has been extensively studied,
-primarily focused on analyzing the static equilibrium
-shapes~\cite{Seifert1990_PRA, ShiFengGao2006_ActaMechSin,
-LinFreund2007_IntJSolidsStructures, das2008adhesion, zhang2009phase}
-than the transient adhesion process; exceptions
-include~\cite{cantat1999lift, suk-sei2001, BlountMiksisDavis2013_PRSa}.
-%
-% The short-range adhesive potential of a lipid bilayer membrane
-% inevitably involves the membrane change redistribution and the membrane potential
-% 
-%  in relation the screening of charges in the electric double layer (EDL) right next to the
-% membrane \cite{Book_IntermolecularSurfaceForces,LiraDimova}.
-% When two vesicles are in close vicinity of each other within the electric double layer,  
-% In this work we do not consider the electrostatic of two lipid bilayer membranes.
-% 
-Adhesion between bilayer membranes was first experimentally observed by
-Evans and Metcalfe~\cite{EvansMetcalfe1984_BJ}, who measured the
+potential~\cite{Book_IntermolecularSurfaceForces}. 
+%%
+%%move this somewhere else Jan30YNY
+%Such adhesive
+%potentials are essential in many biomedical, biological and biophysical
+%processes.  For example, vesicle adhesion is essential for membrane
+%fusion/fission in endocytosis and exocytosis, the transport of small
+%vesicles through membrane surfaces.
+%%move this somewhere else Jan30YNY
+
+%Adhesion between bilayer membranes was first experimentally observed by
+Evans and Metcalfe~\cite{EvansMetcalfe1984_BJ} used the micropipette to measure the adhesive force between two vesicles bound by strong adhesion.
+They were able to  measure the
 reduction in the free energy per unit area of membrane-membrane contact
@@
 physical parameters.
+
+%Adhesion between a vesicle and a substrate has been extensively studied,
+%primarily focused on analyzing the static equilibrium
+%shapes~\cite{Seifert1990_PRA, ShiFengGao2006_ActaMechSin,
+%LinFreund2007_IntJSolidsStructures, das2008adhesion, zhang2009phase}
+%than the transient adhesion process; exceptions
+%include~\cite{cantat1999lift, suk-sei2001, BlountMiksisDavis2013_PRSa}.
+%
+% The short-range adhesive potential of a lipid bilayer membrane
+% inevitably involves the membrane change redistribution and the membrane potential
+% 
+%  in relation the screening of charges in the electric double layer (EDL) right next to the
+% membrane \cite{Book_IntermolecularSurfaceForces,LiraDimova}.
+% When two vesicles are in close vicinity of each other within the electric double layer,  
+% In this work we do not consider the electrostatic of two lipid bilayer membranes.
+%
 

### 2019-01-30 vesicle_code/docs/adhesion/adhesion.tex
working on extensional example

--- 2019-01-30 vesicle_code/docs/adhesion/adhesion.tex
@@
 In a quiescent flow,
-vesicle-vesicle adhesion leads to formation of vesicle doublets \cite{Ziherl2007_PRL,ZiherlSvetina2007_PNAS} or clusters \cite{SvetinaZiherl2008_Bioelectrochemistry,FlormannAouane2017_SciReports}.
+vesicle-vesicle adhesion leads to formation of vesicle doublets \cite{ZiherlSvetina2007_PNAS} or clusters \cite{SvetinaZiherl2008_Bioelectrochemistry,FlormannAouane2017_SciReports}.
 As a model for red blood cell (RBC) aggregates, an idealized model for adhesive vesicle-vesicle interactions gives rise to 
@@
 because a smaller time step is often needed to resolve the dynamics of the lubrication thin film between two membranes with adhesion than without.
-However, adhesive interactions  between RBCs lead to different RBC clusters that are expected to alter the rheological properties of the RBC suspension \cite{NeuMeiselman2002_BJ,SvetinaZiherl2008_Bioelectrochemistry}.
+However, adhesive interactions  between RBCs lead to different RBC clusters that are expected to alter the rheological properties of the RBC suspension \cite{NeuMeiselman2002_BiophysJ,SvetinaZiherl2008_Bioelectrochemistry}.
 Hydrodynamic simulations of adhesive vesicles in a quiescent flow have revealed physical insights to the equilibrium shapes of RBC aggregates in both experiments 
@@
 %
-The electrostatic nature of lipid molecules (a hydrophobic tail and a hydrophilic head
+The electrostatic
+nature of lipid molecules (a hydrophobic tail and a hydrophilic head
 with an electric dipole) complicates the interactions between a lipid
@@
 Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  The stagnation
-point (zero-velocity point) in an extensional flow, $\uu =\chi(-x,y) $,
+point (zero-velocity point) in an extensional flow, $\uu =\chi(-x,y)$,
 is a saddle point where two laminar streams converge along an axis and
@@
 has the same reduced area, membrane area, and bending stiffness.  At low
-extensional rate, $\chi$, we expect the vesicle doublet to stay bound at
+extensional rate, $\chi$, we expect the vesicle doublet to stay fixed at
 the fluid trap stagnation point.  On the other hand, the vesicle doublet
@@
 
+\begin{figure}[htp]
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}
+  \caption{\label{fig:extensional1} Two vesicles in an extensional flow.
+  The reduced area is $A = 0.7$, the Hamaker constant is $H = 0.7$, and
+  the adhesion length scale is $\delta = 0.4$, extensional rate is $\chi
+  = 0.02$.  The center of the vesicle, denoted with a black square, is a
+  stagnation point.}
+\end{figure}
+
+\begin{figure}[htp]
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
+  \caption{\label{fig:extensional2} Two vesicles in an extensional flow.
+  The reduced area is $A = 0.7$, the Hamaker constant is $H = 0.7$, and
+  the adhesion length scale is $\delta = 0.4$, extensional rate is $\chi
+  = 0.07$.  The center of the vesicle, denoted with a black square, is a
+  stagnation point.}
+\end{figure}
+
+\begin{figure}[htp]
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
+  \caption{\label{fig:extensional4} Two vesicles in an extensional flow.
+  The reduced area is $A = 0.7$, the Hamaker constant is $H = 0.7$, and
+  the adhesion length scale is $\delta = 0.4$, extensional rate is $\chi
+  = 0.1$.  The center of the vesicle, denoted with a black square, is a
+  stagnation point.}
+\end{figure}
+
+\begin{figure}[htp]
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
+  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
+  The reduced area is $A = 0.8$, the Hamaker constant is $H = 0.7$, and
+  the adhesion length scale is $\delta = 0.4$, extensional rate is $\chi
+  = 0.1$.  Initially, the doublet tilts to an inclination angle, and
+  then the extensional rate overcomes the adhesive force and the doublet
+  is broken.  The center of the vesicle, denoted with a black square, is
+  a stagnation point.}
+\end{figure}
+
 We consider six pairs of vesicles with reduced areas 0.70, 0.75, 0.80,
-0.85, 0.90, and 0.95, and we use extensional rates between $10^{-2}$ and
-$10^{-1}$.  For all the simulations, the length of the vesicles are
-fixed, while the area is changed to achieve the desired reduced area.
-Since the stagnation point can be controlled in an experimental
+0.85, 0.90, and 0.95, and we vary the extensional rate, $\chi$, between
+$10^{-2}$ and $10^{-1}$.  The length of each of the vesicles is fixed,
+and the area is changed to achieve the desired reduced area.  Since the
+stagnation point can be controlled in an experimental
 setting~\cite{Johnson-Chavarria2011_EMJ}, we translate the vesicles at
 each time step so that the stagnation point occurs exactly in the middle
-of the two vesicles.  With this adjustment, the doublet can not migrate
-towards $(0,\pm \infty)$; instead, for all time, each vesicle is
-centered at $\pm(x_0,y_0)$ for some $(x_0,y_0)$.
+of the two vesicles.  With this adjustment, the vesicles either remain
+as a doublet in the fluid trap centered around the stagnation point, or
+the doublet is broken and the vesicles diverge apart from one another.
+
+In Figures~\ref{fig:extensional1}--\ref{fig:extensional3}, snapshots of
+a fluid trap containing a vesicle doublet of reduced area 0.7 are
+simulated at different extensional rates.  While this double remains
+trapped at around the stagnation point, a doublet with a reduced area of
+0.8 is broken for a sufficiently large extensional rate
+(Figure~\ref{fig:extensional4}).  In the left plot of
+Figure~\ref{fig:extensionalPhaseDiagram}, parameter values with a blue
+mark result in a fluid trap while the parameter values with a red marks
+result in the vesicles separating.
+
+For extensional rates and reduced areas that result in a fluid trap, the
+initial configuration of the vesicles have the diverging stream
+direction is in the parallel to the vesicles' short axis.  Since the
+stable configuration of two vesicles in an extensional flow has the
+converging direction parallel to the vesicles' short axis, we expect the
+vesicles to align themselves with the long axis parallel to the
+diverging direction.  We observe in 
+Figures~\ref{fig:extensional1}--\ref{fig:extensional3} that the vesicles
+do in fact undergo a rotation, but not by a complete 90 degrees.  To
+further analyze this rotation, we define the inclination angle of the
+doublet as described in the right plot of
+Figure~\ref{fig:extensionalPhaseDiagram}.
+
+The doublet starts at an angle of $\pi$ and rotates towards some number
+less than $\pi/2$ (if it converges).
 
@@
 
-%In Figures~\ref{fig:extensional1}--\ref{fig:extensional3}, we show
-%snapshots of two vesicles of reduced area $0.70$ in an extensional flow
-%with three different extensional rates.  Interestingly, when the
-%extensional rate does not overcome the adhesion rate, the doublet does
-%not remain parallel to the stagnation point, but instead tilts to an
-%inclination angle (Figures~\ref{fig:extensional1}
-%and~\ref{fig:extensional2}.
-
-\begin{figure}[htp]
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}
-  \caption{\label{fig:extensional1} Two vesicles in an extensional flow.
-  The reduced area is $0.7$, the Hamaker constant is $H = 0.7$, and the
-  adhesion length scale is $\delta = 0.4$, extensional rate is $\chi =
-  0.02$.  The center of the vesicle, denoted with a black square, is a
-  stagnation point.}
-\end{figure}
-
-\begin{figure}[htp]
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
-  \caption{\label{fig:extensional2} Two vesicles in an extensional flow.
-  The reduced area is $0.7$, the Hamaker constant is $H = 0.7$, and the
-  adhesion length scale is $\delta = 0.4$, extensional rate is $\chi =
-  0.07$.  The center of the vesicle, denoted with a black square, is a
-  stagnation point.}
-\end{figure}
-
-\begin{figure}[htp]
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
-  \caption{\label{fig:extensional4} Two vesicles in an extensional flow.
-  The reduced area is $0.7$, the Hamaker constant is $H = 0.7$, and the
-  adhesion length scale is $\delta = 0.4$, extensional rate is $\chi =
-  0.1$.  The center of the vesicle, denoted with a black square, is a
-  stagnation point.}
-\end{figure}
-
-\begin{figure}[htp]
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
-  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
-  The reduced area is $0.8$, the Hamaker constant is $H = 0.7$, and the
-  adhesion length scale is $\delta = 0.4$, extensional rate is $\chi =
-  0.1$.  Initially, the doublet tilts to an inclination angle, and then
-  the extensional rate overcomes the adhesive force and the doublet is
-  broken.  The center of the vesicle, denoted with a black square, is a
-  stagnation point.}
-\end{figure}
-
 \begin{figure}[htp]
@@
 important, an electro-osmotic pressure in the thin film is found to be
-responsible for the observed membrane undulation~\cite{SteinkuhlerAgudo-Canalejo2016_BJ}.
+responsible for the observed membrane undulation~\cite{LiraDimova}.
 

### 2019-01-30 vesicle_code/docs/adhesion/adhesion.tex

--- 2019-01-30 vesicle_code/docs/adhesion/adhesion.tex
@@
 
+\begin{figure}[htp]
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}
+  \caption{\label{fig:extensional1} Two vesicles in an extensional flow.
+  The reduced area is $A = 0.7$, the Hamaker constant is $H = 0.7$, and
+  the adhesion length scale is $\delta = 0.4$, extensional rate is $\chi
+  = 0.02$.  The center of the vesicle, denoted with a black square, is a
+  stagnation point.}
+\end{figure}
+
+\begin{figure}[htp]
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
+  \caption{\label{fig:extensional2} Two vesicles in an extensional flow.
+  The reduced area is $A = 0.7$, the Hamaker constant is $H = 0.7$, and
+  the adhesion length scale is $\delta = 0.4$, extensional rate is $\chi
+  = 0.07$.  The center of the vesicle, denoted with a black square, is a
+  stagnation point.}
+\end{figure}
+
+\begin{figure}[htp]
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
+  \caption{\label{fig:extensional4} Two vesicles in an extensional flow.
+  The reduced area is $A = 0.7$, the Hamaker constant is $H = 0.7$, and
+  the adhesion length scale is $\delta = 0.4$, extensional rate is $\chi
+  = 0.1$.  The center of the vesicle, denoted with a black square, is a
+  stagnation point.}
+\end{figure}
+
+\begin{figure}[htp]
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
+  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
+  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
+  The reduced area is $A = 0.8$, the Hamaker constant is $H = 0.7$, and
+  the adhesion length scale is $\delta = 0.4$, extensional rate is $\chi
+  = 0.1$.  Initially, the doublet tilts to an inclination angle, and
+  then the extensional rate overcomes the adhesive force and the doublet
+  is broken.  The center of the vesicle, denoted with a black square, is
+  a stagnation point.}
+\end{figure}
+
 We consider six pairs of vesicles with reduced areas 0.70, 0.75, 0.80,
-0.85, 0.90, and 0.95, and we use extensional rates between $10^{-2}$ and
-$10^{-1}$.  For all the simulations, the length of the vesicles are
-fixed, while the area is changed to achieve the desired reduced area.
-Since the stagnation point can be controlled in an experimental
+0.85, 0.90, and 0.95, and we vary the extensional rate, $\chi$, between
+$10^{-2}$ and $10^{-1}$.  The length of each of the vesicles is fixed,
+and the area is changed to achieve the desired reduced area.  Since the
+stagnation point can be controlled in an experimental
 setting~\cite{Johnson-Chavarria2011_EMJ}, we translate the vesicles at
 each time step so that the stagnation point occurs exactly in the middle
-of the two vesicles.  With this adjustment, the doublet can not migrate
-towards $(0,\pm \infty)$; instead, for all time, each vesicle is
-centered at $\pm(x_0,y_0)$ for some $(x_0,y_0)$.
+of the two vesicles.  With this adjustment, the vesicles either remain
+as a doublet in the fluid trap centered around the stagnation point, or
+the doublet is broken and the vesicles diverge apart from one another.
+
+In Figures~\ref{fig:extensional1}--\ref{fig:extensional3}, snapshots of
+a fluid trap containing a vesicle doublet of reduced area 0.7 are
+simulated at different extensional rates.  While this double remains
+trapped at around the stagnation point, a doublet with a reduced area of
+0.8 is broken for a sufficiently large extensional rate
+(Figure~\ref{fig:extensional4}).  In the left plot of
+Figure~\ref{fig:extensionalPhaseDiagram}, parameter values with a blue
+mark result in a fluid trap while the parameter values with a red marks
+result in the vesicles separating.
+
+For extensional rates and reduced areas that result in a fluid trap, the
+initial configuration of the vesicles have the diverging stream
+direction is in the parallel to the vesicles' short axis.  Since the
+stable configuration of two vesicles in an extensional flow has the
+converging direction parallel to the vesicles' short axis, we expect the
+vesicles to align themselves with the long axis parallel to the
+diverging direction.  We observe in 
+Figures~\ref{fig:extensional1}--\ref{fig:extensional3} that the vesicles
+do in fact undergo a rotation, but not by a complete 90 degrees.  To
+further analyze this rotation, we define the inclination angle of the
+doublet as described in the right plot of
+Figure~\ref{fig:extensionalPhaseDiagram}.
 

### 2019-01-30 vesicle_code/docs/adhesion/adhesion.tex
more changes in the text by yny

--- 2019-01-30 vesicle_code/docs/adhesion/adhesion.tex
@@
 
-When the force on each vesicle is a function of separation distance $h$ of the form (with an integer $m\ge 2$)
+When the force on each vesicle is a function of separation distance $h$ of the form (with integers $n>m\ge 2$)
 \begin{align}
@@
 \end{align}
-attraction is dominant at ``large" scales ($h > \delta$) while repulsion
-is dominant at ``small" scales ($h<\delta$).  Integration of
+attraction is dominant at ``large" distance ($h > \delta$) while repulsion
+is dominant at ``small" distance ($h<\delta$).  Integration of
 equation~\eqref{eq:dhdt} with the above $F(h)$ gives the relationship
@@
 and the separation distance $\delta$ affect the time it takes for a pair
-of vesicles to reach equilibrium under adhesion force $F$ in
-equation~\eqref{eq:Fh}.  In particular, the equilibration time $t$ is
+of vesicles to reach the separation distance $\delta$ under adhesion force $F$ in
+equation~\eqref{eq:Fh}.  In particular, the duration $t$ is
 proportional to (1) the separation distance $\delta^{-5/3}$ (thus
@@
 
-To test the scaling of the equilibration time $t$ with respect to $H$
+To test the scaling of the duration $t$ with respect to $H$
 and $\delta$, we simulate the vesicle adhesion dynamics in a quiescent
@@
 two vesicles together until their separation distance is close to
-$\delta$ (where $F$ vanishes).  Depending on the adhesion strength
-relative to the membrane bending rigidity, the vesicle may deform
-significantly in the contact region while still maintain nearly
-spherical shape on the opposite side to the contact
-region~\cite{EvansMetcalfe1984_BJ, Book_PhysicalBasisCellAdhesion,
-Book_IntermolecularSurfaceForces,
-RamachandranAndersonLealIsraelachvili2010_Langmuir}.
+$\delta$ (where the adhesive force $F$ vanishes).  
+%
+Once a vesicle doublet is formed, the membrane shape in the contact region 
+depends on the adhesion strength
+relative to the membrane bending rigidity.
+For weak to moderate adhesion strength, vesicle membranes are flattened in the contact region while the rest of vesicle maintains a nearly spherical shape
+\cite{EvansMetcalfe1984_BJ, Book_PhysicalBasisCellAdhesion, Book_IntermolecularSurfaceForces,RamachandranAndersonLealIsraelachvili2010_Langmuir}.
+Under a strong adhesion, however, the vesicle membranes in the contact region buckle and form a sigmoidal shape  that has been observed in RBC doublet as well
+\cite{Ziherl2007_PRL,ZiherlSvetina2007_PNAS,FlormannAouane2017_SciReports}. An external electric field is also able to buckle a vesicle membrane that is adhered to a solid
+substrate \cite{SteinkuhlerAgudo-Canalejo2016_BJ}.
+
+%the vesicle may deform
+%significantly in the contact region while still maintain nearly
+%spherical shape on the opposite side to the contact
+%region~\cite{EvansMetcalfe1984_BJ, Book_PhysicalBasisCellAdhesion, Book_IntermolecularSurfaceForces,RamachandranAndersonLealIsraelachvili2010_Langmuir}.
+%In the contact region, vesicle membranes are flattened under a weak to moderate adhesive potential.
+%Under a strong adhesion the vesicle membranes buckle and form a sigmoidal shape in the contact region \cite{Ziherl2007_PRL,ZiherlSvetina2007_PNAS,FlormannAouane2017_SciReports}.
+
+In this work we focus on weakly adhesive vesicles whose equilibrium shapes in a quiescent flow are shown in figure~\ref{fig:Dec18_vesicle_shape}(a)
+for three values of reduced area:  $\Delta A=0.95$, $0.75$ and
+$0.6$ with $H=5$ and $\delta = 0.2$. 
 \begin{figure}
@@
 \end{figure}
-
-Figure~\ref{fig:Dec18_vesicle_shape}(a) shows the equilibrium shapes of
-vesicles with three values of reduced area: $\Delta A=0.95$, $0.75$ and
-$0.6$ with $H=5$ and $\delta = 0.2$.  The equilibrium vesicle shape for
-$\Delta A=0.95$ is the circular cap with a flatten contact region.  This
-is similar to the observed shapes of two vesicles under strong adhesive
-interaction
+ The equilibrium vesicle shape for
+$\Delta A=0.95$ is the circular cap with a flat contact region.  This
+is similar to the observed shapes of two vesicles under strong adhesive interaction
 in~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.  
-
-When vesicles are more deflated with a reduced area  $\Delta A = 0.75$, the equilibrium vesicle shape is elongated with a bigger contact region.
+When vesicles are more deflated with a reduced area  $\Delta A = 0.75$, the equilibrium vesicle shape is elongated with a bigger contact region. This is consistent
+with the equilibrium shapes of a vesicle doublet under a L-J potential  ($(m,n) = (12,6)$) \cite{FlormannAouane2017_SciReports}.
 As the reduced area decreases further, we observe undulation of the elongated equilibrium vesicle shape on the non-contact side while the contact region remains flat. 
@@
 We observe that the membrane tension in the contact region is very negative, indicating a dominant compression of membrane when the adhesion force is strong to keep the vesicles bound together.
+
+Figure~\ref{fig:Dec18_vesicle_shape}(b) is a zoom on the membranes in the contact region, where the membranes are not perfectly flat: 
+For all values of reduced area we observe that membranes are slightly curved with a dip at the edge.
+Such membrane undulation in the contact region is predicted by lubrication analyses on the a membrane under adhesion with a solid substrate
+\cite{BlountMiksisDavis2013_PRSa,YoungStone2017_PRF}. 
+Also the dip at the edge of contact region is related to but different from the buckling of membrane under strong adhesion:
+A closer inspection on the dip at the edge shows that the membrane distance is smaller than the neutral separation distance $\delta$ there. Thus the adhesion force is attractive for
+most of the membranes in the contact region except at the edge, where the adhesive force turns repulsive.
+Results from the lubrication analysis shows that this dip and slightly curved shape in the contact region are independent of the adhesion strength. The high membrane curvature
+at the edge may pose a problem for using the contact angle there to estimate the adhesion strength.
+This inspires us to investigate the possibility of using a dynamic fluid trap to measure the adhesion strength (see \S~\ref{sec:eflow}).
 
@@
 
-YNY would like to acknowledge helpful discussions with 
-The authors acknowledge support from NSF-DMS 1614863 and 1412789 (YNY).
+YNY would like to acknowledge helpful discussions with blah blah blah.
+YNY acknowledges support from NSF-DMS 1614863 and 1412789, and Flatiron Institute, part of the Simons Foundation.
 

### 2019-02-01 vesicle_code/docs/adhesion/adhesion.tex
working on extensional example

@@
 a fluid trap containing a vesicle doublet of reduced area 0.7 are
-simulated at different extensional rates.  While this double remains
+simulated at different extensional rates.  While this doublet remains
 trapped at around the stagnation point, a doublet with a reduced area of
@@
 mark result in a fluid trap while the parameter values with a red marks
-result in the vesicles separating.
-
-For extensional rates and reduced areas that result in a fluid trap, the
-initial configuration of the vesicles have the diverging stream
-direction is in the parallel to the vesicles' short axis.  Since the
-stable configuration of two vesicles in an extensional flow has the
-converging direction parallel to the vesicles' short axis, we expect the
-vesicles to align themselves with the long axis parallel to the
-diverging direction.  We observe in 
+result in the vesicles separating.  For extensional rates and reduced
+areas that result in a fluid trap, the initial configuration of the
+vesicles have the diverging stream direction parallel to the vesicles'
+short axis.  Since the stable configuration of two vesicles in an
+extensional flow has the converging direction parallel to the vesicles'
+short axis, we expect the vesicles to align themselves with the long
+axis parallel to the diverging direction.  We observe in
 Figures~\ref{fig:extensional1}--\ref{fig:extensional3} that the vesicles
-do in fact undergo a rotation, but not by a complete 90 degrees.  To
-further analyze this rotation, we define the inclination angle of the
-doublet as described in the right plot of
-Figure~\ref{fig:extensionalPhaseDiagram}.
-
-The doublet starts at an angle of $\pi$ and rotates towards some number
-less than $\pi/2$ (if it converges).
-
-As expected, we observe two different regimes---the extensional rate is
-sufficiently small that the doublet structure is not broken, and the
-extensional rate is sufficiently large that the doublet is broken.  In
-Figure~\ref{fig:extensionalPhaseDiagram}, the red marks correspond to
-parameters where the doublet is broken while the red marks correspond to
-parameters where the doublet tends to a steady-state fluid trap.  In the
-case that there is a fluid trap, the doublet rotates from the unstable
-configuration where the converging rate is in the direction that is
-parallel to the long axis of the vesicles.  At low extensional rates,
-the inclination angle approaches $\pi$ which corresponds to the
-converging direction being aligned with the short axis of the vesicle
-(Figure~\ref{fig:extensional1}).  As the extensional rate is increased,
-the vesicle tilts to a shallower inclination angle
-(Figures~\ref{fig:extensional2} and~\ref{fig:extensional3}).  Finally,
-when the inclination angle is sufficiently large, the doublet is broken
-(Figure~\ref{fig:extensional4}).  In
-Figure~\ref{fig:extensionalPhaseDiagram}, the size of the round marks
-correspond to the inclination angle.  The square marks correspond to
-doublets that do not reach a steady-state inclination angle in the given
-time horizon.
+do in fact rotate, but fall short of aligning their long axis with the
+diverging direction.  In the left plot of
+Figure~\ref{fig:extensionalPhaseDiagram}, the size of the round dots are
+scaled the final inclination angle as defined in the right plot.  At
+smaller extensional rates, the vesicles comes closer to aligning their
+long axis with the diverging direction.  The inclination angle is
+defined defined in with respect to the diverging direction (right plot
+of Figure~\ref{fig:extensionalInclinationAngle}).  When the doublet is
+broken at reduced area $0.70$, the extensional rate is sufficiently
+large to align the long axis of the vesicle with the diverging direction
+and then the vesicles separate.  However, for larger reduced areas, the
+separation dynamics is different.  Instead, the vesicles tilt to an
+inclination angle and then separate (Figure~\ref{fig:extensional4}).
+
+%As expected, we observe two different regimes---the extensional rate is
+%sufficiently small that the doublet structure is not broken, and the
+%extensional rate is sufficiently large that the doublet is broken.  In
+%Figure~\ref{fig:extensionalPhaseDiagram}, the red marks correspond to
+%parameters where the doublet is broken while the red marks correspond to
+%parameters where the doublet tends to a steady-state fluid trap.  In the
+%case that there is a fluid trap, the doublet rotates from the unstable
+%configuration where the converging rate is in the direction that is
+%parallel to the long axis of the vesicles.  At low extensional rates,
+%the inclination angle approaches $\pi$ which corresponds to the
+%converging direction being aligned with the short axis of the vesicle
+%(Figure~\ref{fig:extensional1}).  As the extensional rate is increased,
+%the vesicle tilts to a shallower inclination angle
+%(Figures~\ref{fig:extensional2} and~\ref{fig:extensional3}).  Finally,
+%when the inclination angle is sufficiently large, the doublet is broken
+%(Figure~\ref{fig:extensional4}).  In
+%Figure~\ref{fig:extensionalPhaseDiagram}, the size of the round marks
+%correspond to the inclination angle.  The square marks correspond to
+%doublets that do not reach a steady-state inclination angle in the given
+%time horizon.
 
@@
 
-We include a plot of the inclination angle as a function of time for
-varying extensional rates (left plot of
-Figure~\ref{fig:extensionalInclinationAngle}).  The inclination angle is
-defined defined in with respect to the diverging direction (right plot
-of Figure~\ref{fig:extensionalInclinationAngle}).  When the doublet is
-broken at reduced area $0.70$, the extensional rate is sufficiently
-large to align the long axis of the vesicle with the diverging direction
-and then the vesicles separate.  However, for larger reduced areas, the
-separation dynamics is different.  Instead, the vesicles tilt to an
-inclination angle and then separate (Figure~\ref{fig:extensional4}).
+For very low extensional rates, the time horizon is insufficient for the
+doublet to reach a steady state, and these simulations are marked with a
+square.  In Figure~\ref{fig:extensionalInclinationAngle}, we plot the
+inclination angle as a function of time for four different extensional
+rates (left) and the final inclination angle for all doublets that reach
+a steady state (right).  We observe that not only do larger smaller
+extensional rates result in smaller inclination angles, but smaller
+reduced areas also result in smaller inclination angles.
+
+We further characterize the dynamics by examining the vorticity and
+total force on the vesicles.
 
@@
 \end{figure}
-
-%Figures~\ref{fig:sflow_phase_diagram},
-%~\ref{fig:sflow_1frames}, and~\ref{fig:sflow_2frames}
-%\begin{figure}
-%\includegraphics[keepaspectratio=true,scale=0.41]{figs/shear2Ves01a-iD12a.eps}
-%\includegraphics[keepaspectratio=true,scale=0.415]{Nshear02_adS_ShearRate01.png}
-%% \includegraphics[keepaspectratio=true,scale=0.40]{figs/Nshear02_adS_rA01.png}
-%\caption{(a) Dynamics of a pair of vesicles in a planar shear flow with shear rate $\dot\gamma=1$ and vdW length $\delta = 0.4$.
-(b) Phase diagram of vesicle hydrodynamics in a shear flow.
-At a fixed reduced area $\triangle A=0.95$ and $\delta =0.4$,  the critical vdW potential strength $\sigma$ for binding of two vesicles in a shear flow depends on the shear rate $\dot\gamma$.}
-%\label{fig:sflow_phase_diagram}
-%\end{figure}
 

### 2019-02-01 vesicle_code/docs/adhesion/adhesion.tex
worked on extensional

@@
 
-We further characterize the dynamics by examining the vorticity and
-total force on the vesicles.
+We further characterize the rotating dynamics of a doublet by examining
+the vorticity and total force on the vesicles.  In Figure~\ref{}
+
+\begin{figure}[htp]
+  \includegraphics[width = 0.19\textwidth,trim={6cm 0cm 5cm
+  0cm},clip]{figs/extensionalVorticity01.png}
+  \includegraphics[width = 0.19\textwidth,trim={6cm 0cm 5cm
+  0cm},clip]{figs/extensionalVorticity02.png}
+  \includegraphics[width = 0.19\textwidth,trim={6cm 0cm 5cm
+  0cm},clip]{figs/extensionalVorticity03.png}
+  \includegraphics[width = 0.19\textwidth,trim={6cm 0cm 5cm
+  0cm},clip]{figs/extensionalVorticity04.png}
+  \includegraphics[width = 0.19\textwidth,trim={3cm 0cm 2cm
+  0cm},clip]{figs/extensionalVorticity05.png} \\
+  \includegraphics[width = 0.19\textwidth,trim={6cm 0cm 5cm
+  0cm},clip]{figs/extensionalVorticity06.png}
+  \includegraphics[width = 0.19\textwidth,trim={6cm 0cm 5cm
+  0cm},clip]{figs/extensionalVorticity07.png}
+  \includegraphics[width = 0.19\textwidth,trim={6cm 0cm 5cm
+  0cm},clip]{figs/extensionalVorticity08.png}
+  \includegraphics[width = 0.19\textwidth,trim={6cm 0cm 5cm
+  0cm},clip]{figs/extensionalVorticity09.png}
+  \includegraphics[width = 0.19\textwidth,trim={3cm 0cm 2cm
+  0cm},clip]{figs/extensionalVorticity10.png}
+%  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
+%  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
+%  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
+%  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
+%  \caption{\label{fig:extensionalVorticity} Stuff here}
+\end{figure}
 

### 2019-02-01 vesicle_code/examples/output/makeImages.m

@@ -1,7 +1,8 @@
 addpath ../../src
 set(0,'DefaultAxesFontSize',22)
+options.savefig = false;
 
-irate = 20; % controls the speed of the visualization
+irate = 1; % controls the speed of the visualization
 
 if 1
 %  file = 'extensional2VesData.bin';
@@ -65,6 +66,7 @@ end
 % load positions, tension, stresses, errors, time, number of points, and
 % number of vesicles
 istart = 1;
+iend = numel(time);
 ntime = numel(time);
 
 %min_ten = floor(min(min(min(ten))));
@@ -74,8 +76,6 @@ ntime = numel(time);
 %  max_ss = max_ss + 1;
 %end
 
-%istart = 19000;
-iend = numel(time);
 
 figure(1); clf
 for k = istart:irate:iend

### 2019-02-03 vesicle_code/docs/adhesion/adhesion.tex
added the multiple body simulation

--- 2019-02-01 vesicle_code/docs/adhesion/adhesion.tex
@@
 
-We further characterize the dynamics by examining the vorticity and
-total force on the vesicles.
+We further characterize the rotating dynamics of a doublet by examining
+the vorticity and total force on the vesicles.  In Figure~\ref{}
+
+\begin{figure}[htp]
+  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
+  0cm},clip]{figs/extensionalVorticity01.png}
+  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
+  0cm},clip]{figs/extensionalVorticity02.png}
+  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
+  0cm},clip]{figs/extensionalVorticity03.png}
+  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
+  0cm},clip]{figs/extensionalVorticity04.png}
+  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
+  0cm},clip]{figs/extensionalVorticity05.png} \\
+  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
+  0cm},clip]{figs/extensionalVorticity06.png}
+  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
+  0cm},clip]{figs/extensionalVorticity07.png}
+  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
+  0cm},clip]{figs/extensionalVorticity08.png}
+  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
+  0cm},clip]{figs/extensionalVorticity09.png}
+  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
+  0cm},clip]{figs/extensionalVorticity10.png}
+  \caption{\label{fig:extensionalVorticity} The vorticity and total
+  force of two vesicles in a doublet.  The reduced area is $A = 0.7$,
+  the extensional rate is $\chi = 0.7$, the adhesion length scale is
+  $\delta = 0.4$, and the Hamaker constant is $H_0 = 0.7$.  When the
+  doublet first starts to rotate, the net total force points in the
+  direction of the diverging direction.  Next, there is a shearing
+  motion between the vesicles that results in a recoil type motion near
+  $t=295$.  Finally, the vorticity and the flow between the vesicles
+  approaches zero and the result is a fluid trap containing the
+  doublet.}
+\end{figure}
 
@@
 adhesion to keep vesicles bound under linear flows?
+
+\begin{figure}[htp]
+  \centering
+  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot01.pdf}
+  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot02.pdf}
+  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot03.pdf}
+  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot04.pdf} \\
+  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot05.pdf}
+  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot06.pdf}
+  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot07.pdf}
+  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot08.pdf}
+  \caption{\label{figs:relaxationManyVes} Many vesicles suspended ...}
+\end{figure}
 

### 2019-02-04 vesicle_code/docs/adhesion/adhesion.tex
all the changes from yny so far

@@
 or a solid (such as a glass substrate
-or a nano particle).  Adhesion between a vesicle and a substrate has been extensively studied,
-primarily focused on analyzing the static equilibrium
+or a nano particle).  Adhesion between a vesicle and a substrate has been extensively studied with 
+more focuses on the static equilibrium
 shapes~\cite{Seifert1990_PRA, ShiFengGao2006_ActaMechSin,
-LinFreund2007_IntJSolidsStructures, das2008adhesion, zhang2009phase,SteinkuhlerAgudo-Canalejo2016_BJ}
+LinFreund2007_IntJSolidsStructures, GruhnFrankeDimova2007_Langmuir,das2008adhesion, zhang2009phase,SteinkuhlerAgudo-Canalejo2016_BJ}
 than the transient adhesion process \cite{cantat1999lift, suk-sei2001, BlountMiksisDavis2013_PRSa}.
@@
 reduction in the free energy per unit area of membrane-membrane contact
-formation due to the Van der Waals' attraction. For a membrane-membrane
-separation distance of $\sim 3$ nm, they estimated that the Hamaker
-constant is approximately $5.8\times 10^{-14}$ ergs, which corresponds
-to an adhesion energy density around $1$ mJ/m$^2$. The ratio of adhesion
-energy per unit area to the bending energy (bending rigidity of lipid
-bilayer membranes $\sim 10^{-19}$ J) gives a measure of vesicle
+formation due to the van der Waals' attraction. For the adhesive interaction between two lipid bilayer membranes in buffer solutions, a typical range for the
+energy density is between $1$ to $10$ $\mu J/m^2$, 
+%
+%they reported
+%an energy density of $\sim 10$  $\mu J/m^2$ and a separation distance of $\sim 3$  $nm$.
+%
+% membrane-membrane
+%separation distance of $\sim 3$ $nm$, they estimated that the Hamaker
+%constant is approximately $5.8\times 10^{-14}$ $ergs$, which corresponds
+%to 
+%
+%an adhesion energy density around $1$ $\mu J/m^2$,
+similar to the adhesion energy density of $3$  $\mu J/m^2$ between two RBCs \cite{FlormannAouane2017_SciReports}.
+For adhesion interaction between a vesicle and a substrate  \cite{GruhnFrankeDimova2007_Langmuir}, 
+the boundary between weak and strong adhesion is around $1$ $\mu J/m^2$:
+the vesicle-substrate interaction is ``strong" when the adhesion energy density is larger than $1$ $\mu J/m^2$ and ``weak" when the energy
+density is less than $1$ $\mu J/m^2$.
+%
+%weak adhesion regime 
+%
+%Gruhn {\it et al.} made a distinction between strong and weak adhesion regimes for a vesicle adhering on a substrate.
+%Strong adhesion regime when the adhesion energy density is greater than $1$ $\mu J/m^2$,
+%while weak adhesion regime when adhesion energy density is less than $1$ $\mu J/m^2$.
+%
+In this work we use the ratio of the adhesion energy to the bending energy for classification of adhesion strength:
+The ratio of total adhesion
+energy to the bending energy (bending rigidity of lipid
+bilayer membranes $\sim 10^{-19}$ $J$) gives a measure of vesicle
 deformation in the presence of
-adhesion~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}. In
+adhesion~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.
+
+In
 this work we focus on regimes where the ratio is of order unity, between
-the weak adhesion (ratio $\ll 1$) and strong adhesion (ratio $\gg 1$)
+the weak adhesion (adhesion energy/bending energy $\ll 1$) and strong adhesion (adhesion energy/bending energy $\gg 1$)
 regimes.  In this regime the membrane deformation may increase the
 ``contact area'' between two vesicles and enhance the adhesion effects.
-The equilibration of vesicle membranes under adhesion in these regimes
+The equilibration of vesicle membranes in the strong adhesion regime
 have been well studied and documented
-(see~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir} and
+(see~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir,SteinkuhlerAgudo-Canalejo2016_BJ,FlormannAouane2017_SciReports} and
 references therein). However it is unclear how the adhesion couples to
@@
 In a quiescent environment, sub-micron size vesicles are found to form a
-doublet due to their Van der Waals' attractive
+doublet due to their van der Waals' attractive
 interactions~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.
-Due to the strong Van der Waals' adhesive force, the vesicles are far
+Due to the strong van der Waals' adhesive force, the vesicles are far
 from spherical shape and the membrane is almost flat in the ``contact"
@@
 
-Next we conduct a numerical experiment where a vesicle doublet is placed at the center of a fluid trap, which in microfluidic laboratory 
-can be actively controlled so that fluid trap center is effectively a stagnation point in an extensional flow characterized by a extensional flow rate.
+Next we conduct a numerical experiment where a vesicle doublet is placed at the center of a fluid trap, which 
+can be actively controlled in microfluidic channel so that fluid trap center is effectively the stagnation point of an extensional flow characterized by a extensional flow rate.
 At low flow rate, we find the doublet to rotate ninety degrees to align with the flow such that 
@@
 These results indicate that it is possible to use the fluid trap to separate a vesicle doublet under adhesion, and thus provide a means to
-probe the adhesion strength between membranes. {\color{red} For adhesion energy blahblahblah, an extensional flow rate sososo is required to separate the doublet from our
-simulations. IS THIS PLAUSIBLE?}
-We hope that our simulations might inspire microfluidic experiments.
+probe the adhesion strength between membranes. 
+For a pair of $\mu m$-sized vesicles with a bending rigidity of $\sim 10^{-19}$ $J$, an extensional flow rate of $0.5$ $s^{-1}$ is expected to separate a vesicle
+doublet with reduced area of $0.8$ and a Hamakar constant ${\cal H}=0.7$, which corresponds to $\sim 1$ $\mu J/m^2$. These conditions are quite realizable in micrifulidic
+experiments, and we hope that our simulations might inspire microfluidic experiments.
+%{\color{red} For adhesion energy blahblahblah, an extensional flow rate sososo is required to separate the doublet from our
+%simulations. IS THIS PLAUSIBLE?}
 

### 2019-02-05 vesicle_code/docs/adhesion/adhesion.tex
added a caption
first pass through intro.  Expanded journal names in .bib and fixed other bibtex isues

@@
 
-\title{Hydrodynamics and rheology of weakly adhesive vesicle doublets}
+\title{Hydrodynamics and rheology of adhesive vesicle doublets}
 % Force line breaks with \\
@@
 widely utilized as biological cell mimics in biophysics and material
-engineering \cite{}.  The ever expanding applications have encouraged
-detailed experimental, theoretical and numerical investigations of
-vesicle hydrodynamics in applied flow, electric and magnetic fields.
-Theoretical investigations often take the form of small-deformation
-analysis or spheroidal dynamics of a nearly-spherical vesicle (or
-nearly-circular in two dimensions) subjected to an applied flow or under
-an external forcing~\cite{Barthes-BieselRallison1981_JFM,
-Misbah2006_PRL, Vlahovska2007_PRE, Finken2008_EPL,
-ZhangZahnTanLin2013_PoF, Nganguia2013_PRE}.  On the other hand, various
-numerical methods have been developed for simulating the transient
-hydrodynamics of vesicle suspensions~\cite{BagchiJohoson2005_JBE,
-Biben2005_EJP, Veerapaneni2009_JCP, SeolHuKimLai2016_JCP}.  
-%Experiments are performed to study vesicle hydrodynamics under various flowing conditions or forcing configurations \cite{MaderVitkova2006_EurPhysJE, Abkarian2008_SoftMatt,DahlNarsimhanGouveia2016_SoftMatt}.
+engineering \cite{sackmann1996}.  The ever expanding applications have
+encouraged detailed experimental, theoretical, and numerical
+investigations of vesicle hydrodynamics in applied flow, electric
+fields, and magnetic fields.  Theoretical investigations often take the
+form of small-deformation analysis or spheroidal dynamics of a
+nearly-spherical vesicle (or nearly-circular in two dimensions)
+subjected to an applied flow or under an external
+forcing~\cite{Barthes-BieselRallison1981_JFM, Misbah2006_PRL,
+Vlahovska2007_PRE, Finken2008_EPL, ZhangZahnTanLin2013_PoF,
+Nganguia2013_PRE}.  On the other hand, various numerical methods have
+been developed for simulating the transient hydrodynamics of vesicle
+suspensions~\cite{BagchiJohoson2005_JBE, Biben2005_EJP,
+Veerapaneni2009_JCP, SeolHuKimLai2016_JCP}.
 
@@
 investigated. In a planar shear flow, the vesicle hydrodynamics is
-characterized by excess area (reduced volume), viscosity contrast
-between interior and exterior fluids, and shear rate of the imposed
-far-field fluid flow. In addition a vesicle with a rigid particle inside
-is also investigated as a biological mimic of a eukaryotic cell with a
-nucleus that occupies nearly half of the intracellular
-volume~\cite{Veerapaneni2011_PRL}. Small-deformation analysis shows that
-a vesicle tank-treads in a planar shear flow for low viscosity contrast
-and shear rate. At high viscosity contrast the tank-tread (TT) dynamics
-transitions to tumbling (TB)~\cite{Misbah2006_PRL, Vlahovska2007_PRE},
-and this leads to a transition in effective shear viscosity in the
-vesicle suspension~\cite{Misbah2006_PRL,Vitkova2008_BJ} that is also
-validated by direct numerical
-simulations~\cite{GhigliottiBibenMisbah2010_JFM} and
+characterized by the reduced volume (reduced area in two dimensions),
+viscosity contrast between interior and exterior fluids, and shear rate
+of the imposed far-field fluid flow. In addition, a vesicle with a rigid
+particle inside is also investigated as a biological mimic of a
+eukaryotic cell with a nucleus that occupies nearly half of the
+intracellular volume~\cite{Veerapaneni2011_PRL}. Small-deformation
+analysis shows that a vesicle tank-treads in a planar shear flow for low
+viscosity contrast and shear rate. At high viscosity contrast the
+tank-tread (TT) dynamics transitions to tumbling (TB)
+dynamics~\cite{Misbah2006_PRL, Vlahovska2007_PRE}, and this leads to a
+transition in effective shear viscosity in the vesicle
+suspension~\cite{Misbah2006_PRL,Vitkova2008_BJ} that is also validated
+by direct numerical simulations~\cite{GhigliottiBibenMisbah2010_JFM} and
 experiments~\cite{KantslerSegreSteinberg2008_EPL,
-ZabuskySegreDeschamps2011_PoF}.  Between TT and TB vesicle dynamics, a breathing (tremble) mode is also
+ZabuskySegreDeschamps2011_PoF}.  Between TT and TB vesicle dynamics, a
+breathing (tremble) mode is also
 observed~\cite{Misbah2006_PRL,KantslerSegreSteinberg2008_PRL,
@@
 
-%
-% for example, 
-%it was shown recently that vesicles may align to form chains along the direction of the externally applied DC electric field with ensuing consequences to suspension rheology \cite{wu2018pairwise}.
-%
-Collective hydrodynamics of vesicles is dictated by the individual
-vesicle-vesicle interactions.  
-In a quiescent flow,
-vesicle-vesicle adhesion leads to formation of vesicle doublets \cite{Ziherl2007_PRL,ZiherlSvetina2007_PNAS} or clusters \cite{SvetinaZiherl2008_Bioelectrochemistry,FlormannAouane2017_SciReports}.
-As a model for red blood cell (RBC) aggregates, an idealized model for adhesive vesicle-vesicle interactions gives rise to 
-vesicle configurations similar to those observed in experiments of fibrinogen-induced RBC aggregates \cite{SvetinaZiherl2008_Bioelectrochemistry,FlormannAouane2017_SciReports}. 
-Using the L-J potential for point-point interaction between two vesicle membranes without the molecular details of
-adhesive interactions between RBCs, Flormann {\it et al.} found the contact zone to buckle under strong adhesion \cite{FlormannAouane2017_SciReports}. 
-A direct consequence of the buckling is the
-sigmoidal shape of the adhesion region, which is also observed in RBC doublets and explained in a slightly different model \cite{ZiherlSvetina2007_PNAS}. 
-It remains unknown how adhesive interactions between vesicles might lead to different vesicle hydrodynamics that results in
-different rheological properties of a vesicle suspension. Such studies will provide useful insight to the rheology of blood flow and how to use nano solutes to control the hypertension
-by adjusting the adhesive interactions between RBCs.
-%
-
-In numerical simulations of  a vesicle suspension, the adhesive interaction between two vesicles is often 
-ignored \cite{Veerapaneni2009_JCP,RahimianVeerapaneniBiros2010_JCP} 
-for numerical convenience, mostly 
-because a smaller time step is often needed to resolve the dynamics of the lubrication thin film between two membranes with adhesion than without.
-However, adhesive interactions  between RBCs lead to different RBC clusters that are expected to alter the rheological properties of the RBC suspension \cite{NeuMeiselman2002_BJ,SvetinaZiherl2008_Bioelectrochemistry}.
-%
-Hydrodynamic simulations of adhesive vesicles in a quiescent flow have revealed physical insights to the equilibrium shapes of RBC aggregates in both experiments 
-\cite{FlormannAouane2017_SciReports} and theory \cite{ZiherlSvetina2007_PNAS}. The main goal in this work is to investigate the hydrodynamics of adhesive vesicles in flowing
-conditions common in microfluidic vesicle flow, such as a planar shear flow or an extensional flow.
-
-%
-The electrostatic nature of lipid molecules (a hydrophobic tail and a hydrophilic head
-with an electric dipole) complicates the interactions between a lipid
-bilayer membrane and another bilayer
-membrane~\cite{EvansMetcalfe1984_BJ, Book_PhysicalBasisCellAdhesion,Book_IntermolecularSurfaceForces,PerutkovaFrank-Bertoncelij2013_CSB} 
-or a solid (such as a glass substrate
-or a nano particle).  Adhesion between a vesicle and a substrate has been extensively studied with 
-more focuses on the static equilibrium
-shapes~\cite{Seifert1990_PRA, ShiFengGao2006_ActaMechSin,
-LinFreund2007_IntJSolidsStructures, GruhnFrankeDimova2007_Langmuir,das2008adhesion, zhang2009phase,SteinkuhlerAgudo-Canalejo2016_BJ}
-than the transient adhesion process \cite{cantat1999lift, suk-sei2001, BlountMiksisDavis2013_PRSa}.
-%
-Adhesive interactions between lipid membranes are essential in many biomedical, biological and biophysical
-processes.  For example, vesicle adhesion is crucial to initiate membrane
-fusion/fission in endocytosis and exocytosis, the transport of small
-vesicles through membrane surfaces.
-In the absence of an external electric field and ions in the solvents, 
-it is reported that 
-%such complicated electrostatic component in 
-the adhesive interactions between two membranes can be well approximated by the 
-L-J-type potential \cite{FlormannAouane2017_SciReports}, which consists of a long-range attraction component and a
-short-range repulsion component~\cite{Book_IntermolecularSurfaceForces},
-and the combination of the two gives rise to adhesion at the separation
-distance that minimizes the interaction
+Collective hydrodynamics of vesicles is dictated by the vesicle-vesicle
+interactions.  In a quiescent flow, vesicle-vesicle adhesion leads to
+the formation of vesicle doublets
+\cite{Ziherl2007_PRL,ZiherlSvetina2007_PNAS} or clusters
+\cite{SvetinaZiherl2008_Bioelectrochemistry,FlormannAouane2017_SciReports}.
+As a model for red blood cell (RBC) aggregates, an idealized model for
+adhesive vesicle-vesicle interactions gives rise to vesicle
+configurations similar to those observed in experiments of
+fibrinogen-induced RBC
+aggregates~\cite{SvetinaZiherl2008_Bioelectrochemistry,FlormannAouane2017_SciReports}.
+Using the Lennard-Jones (L-J) potential for point-point interaction
+between two vesicle membranes without the molecular details of adhesive
+interactions between RBCs, Flormann {\em et al.}~found the contact zone
+to buckle under strong adhesion~\cite{FlormannAouane2017_SciReports}.  A
+direct consequence of the buckling is the sigmoidal shape of the
+adhesion region, which is also observed in RBC doublets and explained in
+a slightly different model~\cite{ZiherlSvetina2007_PNAS}.  It remains
+unknown how adhesive interactions between vesicles might lead to
+different vesicle hydrodynamics that results in different rheological
+properties of a vesicle suspension. Such studies will provide useful
+insight to the rheology of blood flow and how to use nano solutes to
+control the hypertension by adjusting the adhesive interactions between
+RBCs.
+
+In numerical simulations of  a vesicle suspension, the adhesive
+interaction between two vesicles is often ignored
+\cite{Veerapaneni2009_JCP,RahimianVeerapaneniBiros2010_JCP} for
+numerical convenience, mostly because a smaller time step is often
+needed to resolve the dynamics of the lubrication thin film between two
+membranes with adhesion than without.  However, adhesive interactions
+between RBCs lead to different RBC clusters that are expected to alter
+the rheological properties of the RBC
+suspension~\cite{NeuMeiselman2002_BJ,
+SvetinaZiherl2008_Bioelectrochemistry}. Hydrodynamic simulations of
+adhesive vesicles in a quiescent flow have revealed physical insights to
+the equilibrium shapes of RBC aggregates in both
+experiments~\cite{FlormannAouane2017_SciReports} and
+theory~\cite{ZiherlSvetina2007_PNAS}. The main goal of this work is to
+investigate the hydrodynamics of adhesive vesicles in flowing conditions
+common in microfluidic vesicle flow, such as a planar shear flow and an
+extensional flow.
+
+The electrostatic nature of lipid molecules (a hydrophobic tail and a
+hydrophilic head with an electric dipole) complicates the interactions
+between a lipid bilayer membrane and another bilayer
+membrane~\cite{EvansMetcalfe1984_BJ, Book_PhysicalBasisCellAdhesion,
+Book_IntermolecularSurfaceForces, PerutkovaFrank-Bertoncelij2013_CSB} or
+a solid (such as a glass substrate or a nano particle).  Adhesion
+between a vesicle and a substrate has been extensively studied with more
+focuses on the static equilibrium shapes~\cite{Seifert1990_PRA,
+ShiFengGao2006_ActaMechSin, LinFreund2007_IntJSolidsStructures,
+GruhnFrankeDimova2007_Langmuir,das2008adhesion, zhang2009phase,
+SteinkuhlerAgudo-Canalejo2016_BJ} than the transient adhesion
+process~\cite{cantat1999lift, suk-sei2001, BlountMiksisDavis2013_PRSa}.
+Adhesive interactions between lipid membranes are essential in many
+biomedical, biological, and biophysical processes.  For example, vesicle
+adhesion is crucial to initiate membrane fusion and fission in
+endocytosis and exocytosis, the transport of small vesicles through
+membrane surfaces.  In the absence of an external electric field and
+ions in the solvents, it is reported that the adhesive interactions
+between two membranes can be well approximated by the L-J-type
+potential~\cite{FlormannAouane2017_SciReports}, that consists of a
+long-range attraction component and a short-range repulsion
+component~\cite{Book_IntermolecularSurfaceForces}, and the combination
+of the two gives rise to adhesion at the separation distance that
+minimizes the interaction
 potential~\cite{Book_IntermolecularSurfaceForces}.
-%%
-%%move this somewhere else Jan30YNY
-%Such adhesive
-%potentials are essential in many biomedical, biological and biophysical
-%processes.  For example, vesicle adhesion is essential for membrane
-%fusion/fission in endocytosis and exocytosis, the transport of small
-%vesicles through membrane surfaces.
-%%move this somewhere else Jan30YNY
-
-%Adhesion between bilayer membranes was first experimentally observed by
-Evans and Metcalfe~\cite{EvansMetcalfe1984_BJ} used the micropipette to measure the adhesive force between two vesicles bound by strong adhesion.
-They were able to  measure the
-reduction in the free energy per unit area of membrane-membrane contact
-formation due to the van der Waals' attraction. For the adhesive interaction between two lipid bilayer membranes in buffer solutions, a typical range for the
-energy density is between $1$ to $10$ $\mu J/m^2$, 
-%
-%they reported
-%an energy density of $\sim 10$  $\mu J/m^2$ and a separation distance of $\sim 3$  $nm$.
-%
-% membrane-membrane
-%separation distance of $\sim 3$ $nm$, they estimated that the Hamaker
-%constant is approximately $5.8\times 10^{-14}$ $ergs$, which corresponds
-%to 
-%
-%an adhesion energy density around $1$ $\mu J/m^2$,
-similar to the adhesion energy density of $3$  $\mu J/m^2$ between two RBCs \cite{FlormannAouane2017_SciReports}.
-For adhesion interaction between a vesicle and a substrate  \cite{GruhnFrankeDimova2007_Langmuir}, 
+
+Evans and Metcalfe~\cite{EvansMetcalfe1984_BJ} used the micropipette to
+measure the adhesive force between two vesicles bound by strong
+adhesion.  They were able to measure the reduction in the free energy
+per unit area of membrane-membrane contact formation due to the van der
+Waals' attraction. For the adhesive interaction between two lipid
+bilayer membranes in buffer solutions, a typical range for the energy
+density is between $1$ to $10$ $\mu J/m^2$, similar to the adhesion
+energy density of $3$ $\mu J/m^2$ between two
+RBCs~\cite{FlormannAouane2017_SciReports}.  For adhesion interaction
+between a vesicle and a substrate~\cite{GruhnFrankeDimova2007_Langmuir},
 the boundary between weak and strong adhesion is around $1$ $\mu J/m^2$:
-the vesicle-substrate interaction is ``strong" when the adhesion energy density is larger than $1$ $\mu J/m^2$ and ``weak" when the energy
-density is less than $1$ $\mu J/m^2$.
-%
-%weak adhesion regime 
-%
-%Gruhn {\it et al.} made a distinction between strong and weak adhesion regimes for a vesicle adhering on a substrate.
-%Strong adhesion regime when the adhesion energy density is greater than $1$ $\mu J/m^2$,
-%while weak adhesion regime when adhesion energy density is less than $1$ $\mu J/m^2$.
-%
-In this work we use the ratio of the adhesion energy to the bending energy for classification of adhesion strength:
-The ratio of total adhesion
-energy to the bending energy (bending rigidity of lipid
-bilayer membranes $\sim 10^{-19}$ $J$) gives a measure of vesicle
-deformation in the presence of
+the vesicle-substrate interaction is ``strong" when the adhesion energy
+density is larger than $1$ $\mu J/m^2$ and ``weak" when the energy
+density is less than $1$ $\mu J/m^2$.  In this work we use the ratio of
+the adhesion energy to the bending energy for classification of adhesion
+strength. The ratio of total adhesion energy to the bending energy
+(bending rigidity of lipid bilayer membranes $\sim 10^{-19}$ $J$) gives
+a measure of vesicle deformation in the presence of
 adhesion~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.
 
-In
-this work we focus on regimes where the ratio is of order unity, between
-the weak adhesion (adhesion energy/bending energy $\ll 1$) and strong adhesion (adhesion energy/bending energy $\gg 1$)
-regimes.  In this regime the membrane deformation may increase the
-``contact area'' between two vesicles and enhance the adhesion effects.
-The equilibration of vesicle membranes in the strong adhesion regime
-have been well studied and documented
-(see~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir,SteinkuhlerAgudo-Canalejo2016_BJ,FlormannAouane2017_SciReports} and
+In this work we focus on regimes where the ratio is of order one,
+between the weak adhesion (adhesion energy/bending energy $\ll 1$) and
+strong adhesion (adhesion energy/bending energy $\gg 1$) regimes.  In
+this regime the membrane deformation may increase the ``contact area''
+between two vesicles and enhance the adhesion effects.  The
+equilibration of vesicle membranes in the strong adhesion regime have
+been well-studied and documented
+(see~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir,
+SteinkuhlerAgudo-Canalejo2016_BJ, FlormannAouane2017_SciReports} and
 references therein). However it is unclear how the adhesion couples to
-the vesicle hydrodynamics in such regime.  Our work in this paper aims
-to address this question with quantitative characterization in terms of
-physical parameters.
+the vesicle hydrodynamics in this regime.  This paper aims to address
+this question with quantitative characterization in terms of physical
+parameters.
 
@@
 from spherical shape and the membrane is almost flat in the ``contact"
-region. Gires {\it et al.} used small-deformation analysis to
+region. Gires {\em et al.}~used small-deformation analysis to
 investigate the hydrodynamic interactions between two vesicles in a
@@
 Boundary integral equation (BIE) approaches are well-suited for solving
-the low Re flow problems considered here as they lead to reduction in
-dimensionality and achieve high-order accuracy even for moving geometry
-problems. When the vesicles adhere, one major issue for BIE solvers is
-to resolve the vesicle-vesicle hydrodynamic forces which become {\em
-nearly singular}. In this work, we use the recently developed
-spectrally-accurate algorithm of~\cite{barnett2015spectrally} for
-overcoming this problem. To overcome the numerical stiffness induced by
-the membrane bending forces, we extend the adaptive time-stepping scheme
-developed in~\cite{quaife2016adaptive} to our setting.
+the low Reynodls flow problems considered here as they lead to reduction
+in dimensionality and achieve high-order accuracy even for moving
+geometry problems. The BIE resolves the self-vesicle interaction using
+quadrature for logarithmically singular integrands~\cite{alp1999}, but
+as the vesicles adhere, the BIE solver must also resolve the
+vesicle-vesicle {\em nearly-singular} hydrodynamic forces.  We use an
+interpolation-based quadrature rule~\cite{qua-bir2014} to maintain
+high-order accuracy for all vesicle-vesicle separation distances.  To
+overcome the numerical stiffness induced by the membrane bending forces
+and to control the global error, we employ a high-order spectrally
+deferred implicit-explicit adaptive time stepping
+scheme~\cite{quaife2016adaptive}.
 
@@
   \caption{\label{fig:extensional1} Two vesicles in an extensional flow.
-  The reduced area is $A = 0.7$, the Hamaker constant is $H = 0.7$, and
-  the adhesion length scale is $\delta = 0.4$, extensional rate is $\chi
-  = 0.02$.  The center of the vesicle, denoted with a black square, is a
-  stagnation point.}
+  The reduced area is $A = 0.7$, the Hamaker constant is $H = 0.7$, the
+  adhesion length scale is $\delta = 0.4$, and the extensional rate is
+  $\chi = 0.02$.  The center of the vesicle, denoted with a black
+  square, is a stagnation point.}
 \end{figure}
@@
   \caption{\label{fig:extensional2} Two vesicles in an extensional flow.
-  The reduced area is $A = 0.7$, the Hamaker constant is $H = 0.7$, and
-  the adhesion length scale is $\delta = 0.4$, extensional rate is $\chi
-  = 0.07$.  The center of the vesicle, denoted with a black square, is a
-  stagnation point.}
+  The reduced area is $A = 0.7$, the Hamaker constant is $H = 0.7$, the
+  adhesion length scale is $\delta = 0.4$, and the extensional rate is
+  $\chi = 0.07$.  The center of the vesicle, denoted with a black
+  square, is a stagnation point.}
 \end{figure}
@@
   \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
-  \caption{\label{fig:extensional4} Two vesicles in an extensional flow.
-  The reduced area is $A = 0.7$, the Hamaker constant is $H = 0.7$, and
-  the adhesion length scale is $\delta = 0.4$, extensional rate is $\chi
-  = 0.1$.  The center of the vesicle, denoted with a black square, is a
-  stagnation point.}
+  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
+  The reduced area is $A = 0.7$, the Hamaker constant is $H = 0.7$, the
+  adhesion length scale is $\delta = 0.4$, and the extensional rate is
+  $\chi = 0.1$.  The center of the vesicle, denoted with a black square,
+  is a stagnation point.}
 \end{figure}
@@
   \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
-  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
-  The reduced area is $A = 0.8$, the Hamaker constant is $H = 0.7$, and
-  the adhesion length scale is $\delta = 0.4$, extensional rate is $\chi
-  = 0.1$.  Initially, the doublet tilts to an inclination angle, and
-  then the extensional rate overcomes the adhesive force and the doublet
-  is broken.  The center of the vesicle, denoted with a black square, is
-  a stagnation point.}
+  \caption{\label{fig:extensional4} Two vesicles in an extensional flow.
+  The reduced area is $A = 0.8$, the Hamaker constant is $H = 0.7$, the
+  adhesion length scale is $\delta = 0.4$, and the extensional rate is
+  $\chi = 0.1$.  Initially, the doublet tilts to an inclination angle,
+  and then the extensional rate overcomes the adhesive force and the
+  doublet is broken.  The center of the vesicle, denoted with a black
+  square, is a stagnation point.}
 \end{figure}
@@
 stagnation point can be controlled in an experimental
-setting~\cite{Johnson-Chavarria2011_EMJ}, we translate the vesicles at
-each time step so that the stagnation point occurs exactly in the middle
-of the two vesicles.  With this adjustment, the vesicles either remain
-as a doublet in the fluid trap centered around the stagnation point, or
-the doublet is broken and the vesicles diverge apart from one another.
+setting~\cite{Johnson-Chavarria2011_EMJ}, we translate the center of the
+doublet at each time step so that the stagnation point occurs exactly in
+the middle of the doublet.  With this adjustment, the vesicles either
+remain as a doublet in the fluid trap centered around the stagnation
+point, or the doublet is broken and the vesicles diverge apart from one
+another.
 
@@
 simulated at different extensional rates.  While this doublet remains
-trapped at around the stagnation point, a doublet with a reduced area of
+trapped around the stagnation point, a doublet with a reduced area of
 0.8 is broken for a sufficiently large extensional rate
-(Figure~\ref{fig:extensional4}).  In the left plot of
-Figure~\ref{fig:extensionalPhaseDiagram}, parameter values with a blue
+(Figure~\ref{fig:extensional4}).  We summarize the reduced areas and
+extensional rates that that result in a fluid trap in left plot of
+Figure~\ref{fig:extensionalPhaseDiagram}. Parameter values with a blue
 mark result in a fluid trap while the parameter values with a red marks
-result in the vesicles separating.  For extensional rates and reduced
-areas that result in a fluid trap, the initial configuration of the
-vesicles have the diverging stream direction parallel to the vesicles'
-short axis.  Since the stable configuration of two vesicles in an
-extensional flow has the converging direction parallel to the vesicles'
-short axis, we expect the vesicles to align themselves with the long
-axis parallel to the diverging direction.  We observe in
+result in vesicle separation.  For extensional rates and reduced areas
+that result in a fluid trap, the initial configuration of the vesicles
+have the diverging stream direction parallel to the vesicles' short
+axis.  Since the stable configuration of two vesicles in an extensional
+flow has the converging direction parallel to the vesicles' short axis,
+we expect the vesicles to align themselves with the long axis parallel
+to the diverging direction.  We observe in
 Figures~\ref{fig:extensional1}--\ref{fig:extensional3} that the vesicles
 do in fact rotate, but fall short of aligning their long axis with the
-diverging direction.  In the left plot of
-Figure~\ref{fig:extensionalPhaseDiagram}, the size of the round dots are
-scaled the final inclination angle as defined in the right plot.  At
-smaller extensional rates, the vesicles comes closer to aligning their
-long axis with the diverging direction.  The inclination angle is
-defined defined in with respect to the diverging direction (right plot
-of Figure~\ref{fig:extensionalInclinationAngle}).  When the doublet is
-broken at reduced area $0.70$, the extensional rate is sufficiently
-large to align the long axis of the vesicle with the diverging direction
-and then the vesicles separate.  However, for larger reduced areas, the
-separation dynamics is different.  Instead, the vesicles tilt to an
-inclination angle and then separate (Figure~\ref{fig:extensional4}).
-
-%As expected, we observe two different regimes---the extensional rate is
-%sufficiently small that the doublet structure is not broken, and the
-%extensional rate is sufficiently large that the doublet is broken.  In
-%Figure~\ref{fig:extensionalPhaseDiagram}, the red marks correspond to
-%parameters where the doublet is broken while the red marks correspond to
-%parameters where the doublet tends to a steady-state fluid trap.  In the
-%case that there is a fluid trap, the doublet rotates from the unstable
-%configuration where the converging rate is in the direction that is
-%parallel to the long axis of the vesicles.  At low extensional rates,
-%the inclination angle approaches $\pi$ which corresponds to the
-%converging direction being aligned with the short axis of the vesicle
-%(Figure~\ref{fig:extensional1}).  As the extensional rate is increased,
-%the vesicle tilts to a shallower inclination angle
-%(Figures~\ref{fig:extensional2} and~\ref{fig:extensional3}).  Finally,
-%when the inclination angle is sufficiently large, the doublet is broken
-%(Figure~\ref{fig:extensional4}).  In
-%Figure~\ref{fig:extensionalPhaseDiagram}, the size of the round marks
-%correspond to the inclination angle.  The square marks correspond to
-%doublets that do not reach a steady-state inclination angle in the given
-%time horizon.
+diverging direction.  We summarize the final inclination angle of the
+doublet in the left plot of Figure~\ref{fig:extensionalPhaseDiagram}.
+The size of the round dots are scaled to the final inclination angle as
+defined in the right plot.  At smaller extensional rates, the vesicles
+comes closer to aligning their long axis with the diverging direction.
+When the doublet is broken at reduced area $0.70$, the extensional rate
+is sufficiently large to align the long axis of the vesicle with the
+diverging direction and then the vesicles separate.  However, for larger
+reduced areas, the separation dynamics is different.  Instead, the
+vesicles tilt to an inclination angle and then separate
+(Figure~\ref{fig:extensional4}).
 
@@
 \section{Conclusions\label{sec:conclusions}}
-\todo[inline]{Concluding remarks}
-In this work we use boundary integral formulation with adaptive time-stepping  to simulate hydrodynamics of two vesicles with adhesive interactions.
-In a quiescent flow,  two vesicles move towards each other under a long-range attraction when they are in close vicinity of each other.
-We use a lubrication theory to estimate the time it takes to reach the separation distance, and found the theoretical scaling to be in good agreement with numerical results.  
-Once two membranes are within separation distance $\delta$, the adhesive force turns repulsive and the membranes flatten to form a contact region.
-Our simulations show that the membranes in the contact region are actually curved with end points at the shortest distance. 
-Once a vesicle doublet forms, we examine the dependence of membrane bending and adhesion energies on reduced area, Hamakar constant and separation distance.
-
-Next we conduct a numerical experiment where a vesicle doublet is placed at the center of a fluid trap, which 
-can be actively controlled in microfluidic channel so that fluid trap center is effectively the stagnation point of an extensional flow characterized by a extensional flow rate.
-At low flow rate, we find the doublet to rotate ninety degrees to align with the flow such that 
-the long axis of the doublet is along the divergent axis and the convergent stream is pushing the two vesicles
-together. As the flow rate increases the vesicle doublet rotates less and we observe tank-treading like motion of both vesicles in the doublet.
-When the flow rate reaches above the critical value, the diverging flow pulls the vesicles apart before the doublet has time to rotate to remain intact.
-These results indicate that it is possible to use the fluid trap to separate a vesicle doublet under adhesion, and thus provide a means to
-probe the adhesion strength between membranes. 
-For a pair of $\mu m$-sized vesicles with a bending rigidity of $\sim 10^{-19}$ $J$, an extensional flow rate of $0.5$ $s^{-1}$ is expected to separate a vesicle
-doublet with reduced area of $0.8$ and a Hamakar constant ${\cal H}=0.7$, which corresponds to $\sim 1$ $\mu J/m^2$. These conditions are quite realizable in micrifulidic
-experiments, and we hope that our simulations might inspire microfluidic experiments.
-%{\color{red} For adhesion energy blahblahblah, an extensional flow rate sososo is required to separate the doublet from our
-%simulations. IS THIS PLAUSIBLE?}
-
-We also examine how adhesive interaction may lead to formation of a vesicle doublet dynamically in flowing conditions.
-We simulate two vesicles approaching each other in a planar shear flow, and examine how their adhesive interactions lead to doublet formation.
-Once a doublet forms, the two vesicle membranes rotate around each other as they deform dynamically. The usual tank-treading motion of a vesicle under shear flow is not 
-observed in each of the two vesicles. We also compute the effective shear viscosity of a dilute suspension of vesicle doublets, and found that membrane adhesion contribution
-increases with decreasing reduced area because deflated vesicles (low reduced area) deform more easily and more membranes in the contact region.
+In this work we use boundary integral formulation with adaptive
+time-stepping  to simulate hydrodynamics of two vesicles with adhesive
+interactions.  In a quiescent flow,  two vesicles move towards each
+other under a long-range attraction when they are in close vicinity of
+each other.  We use a lubrication theory to estimate the time it takes
+to reach the separation distance, and found the theoretical scaling to
+be in good agreement with numerical results.  Once two membranes are
+within separation distance $\delta$, the adhesive force turns repulsive
+and the membranes flatten to form a contact region.  Our simulations
+show that the membranes in the contact region are actually curved with
+end points at the shortest distance.  Once a vesicle doublet forms, we
+examine the dependence of membrane bending and adhesion energies on
+reduced area, Hamakar constant and separation distance.
+
+Next we conduct a numerical experiment where a vesicle doublet is placed
+at the center of a fluid trap, which can be actively controlled in
+microfluidic channel so that fluid trap center is effectively the
+stagnation point of an extensional flow characterized by a extensional
+flow rate.  At low flow rate, we find the doublet to rotate ninety
+degrees to align with the flow such that the long axis of the doublet is
+along the divergent axis and the convergent stream is pushing the two
+vesicles together. As the flow rate increases the vesicle doublet
+rotates less and we observe tank-treading like motion of both vesicles
+in the doublet.  When the flow rate reaches above the critical value,
+the diverging flow pulls the vesicles apart before the doublet has time
+to rotate to remain intact.  These results indicate that it is possible
+to use the fluid trap to separate a vesicle doublet under adhesion, and
+thus provide a means to probe the adhesion strength between membranes.
+For a pair of $\mu m$-sized vesicles with a bending rigidity of $\sim
+10^{-19}$ $J$, an extensional flow rate of $0.5$ $s^{-1}$ is expected to
+separate a vesicle doublet with reduced area of $0.8$ and a Hamakar
+constant ${\cal H}=0.7$, which corresponds to $\sim 1$ $\mu J/m^2$.
+These conditions are quite realizable in micrifulidic experiments, and
+we hope that our simulations might inspire microfluidic experiments.
+
+We also examine how adhesive interaction may lead to formation of a
+vesicle doublet dynamically in flowing conditions.  We simulate two
+vesicles approaching each other in a planar shear flow, and examine how
+their adhesive interactions lead to doublet formation.  Once a doublet
+forms, the two vesicle membranes rotate around each other as they deform
+dynamically. The usual tank-treading motion of a vesicle under shear
+flow is not observed in each of the two vesicles. We also compute the
+effective shear viscosity of a dilute suspension of vesicle doublets,
+and found that membrane adhesion contribution increases with decreasing
+reduced area because deflated vesicles (low reduced area) deform more
+easily and more membranes in the contact region.
 
@@
 important, an electro-osmotic pressure in the thin film is found to be
-responsible for the observed membrane undulation~\cite{SteinkuhlerAgudo-Canalejo2016_BJ}.
+responsible for the observed membrane
+undulation~\cite{SteinkuhlerAgudo-Canalejo2016_BJ}.
 
@@
   \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot08.pdf}
-  \caption{\label{figs:relaxationManyVes} Many vesicles suspended ...}
+  \caption{\label{figs:relaxationManyVes} Five vesicles suspended inside
+  a large vesicle.  The background flow is quiescent, the adhesion
+  length scale is $\delta = 0.4$, and the Hamaker constant is $H_0 =
+  0.7$.  The suspension is near a steady state at the final
+  configuration.}
 \end{figure}

### 2019-02-05 vesicle_code/docs/adhesion/adhesion.tex
worked on quiescent example

@@
 interactions.  In a quiescent flow, vesicle-vesicle adhesion leads to
-the formation of vesicle doublets
-\cite{Ziherl2007_PRL,ZiherlSvetina2007_PNAS} or clusters
-\cite{SvetinaZiherl2008_Bioelectrochemistry,FlormannAouane2017_SciReports}.
-As a model for red blood cell (RBC) aggregates, an idealized model for
-adhesive vesicle-vesicle interactions gives rise to vesicle
-configurations similar to those observed in experiments of
-fibrinogen-induced RBC
-aggregates~\cite{SvetinaZiherl2008_Bioelectrochemistry,FlormannAouane2017_SciReports}.
-Using the Lennard-Jones (L-J) potential for point-point interaction
-between two vesicle membranes without the molecular details of adhesive
-interactions between RBCs, Flormann {\em et al.}~found the contact zone
-to buckle under strong adhesion~\cite{FlormannAouane2017_SciReports}.  A
-direct consequence of the buckling is the sigmoidal shape of the
-adhesion region, which is also observed in RBC doublets and explained in
-a slightly different model~\cite{ZiherlSvetina2007_PNAS}.  It remains
-unknown how adhesive interactions between vesicles might lead to
-different vesicle hydrodynamics that results in different rheological
-properties of a vesicle suspension. Such studies will provide useful
-insight to the rheology of blood flow and how to use nano solutes to
-control the hypertension by adjusting the adhesive interactions between
-RBCs.
+the formation of vesicle doublets~\cite{Ziherl2007_PRL,
+ZiherlSvetina2007_PNAS} or clusters
+\cite{SvetinaZiherl2008_Bioelectrochemistry,
+FlormannAouane2017_SciReports}.  As a model for red blood cell (RBC)
+aggregates, an idealized model for adhesive vesicle-vesicle interactions
+gives rise to vesicle configurations similar to those observed in
+experiments of fibrinogen-induced RBC
+aggregates~\cite{SvetinaZiherl2008_Bioelectrochemistry,
+FlormannAouane2017_SciReports}.  Using the Lennard-Jones (L-J) potential
+for point-point interaction between two vesicle membranes without the
+molecular details of adhesive interactions between RBCs, Flormann {\em
+et al.}~found the contact zone to buckle under strong
+adhesion~\cite{FlormannAouane2017_SciReports}.  A direct consequence of
+the buckling is the sigmoidal shape of the adhesion region, which is
+also observed in RBC doublets and explained in a slightly different
+model~\cite{ZiherlSvetina2007_PNAS}.  It remains unknown how adhesive
+interactions between vesicles might lead to different vesicle
+hydrodynamics that results in different rheological properties of a
+vesicle suspension. Such studies will provide useful insight to the
+rheology of blood flow and how to use nano solutes to control the
+hypertension by adjusting the adhesive interactions between RBCs.
 
 In numerical simulations of a vesicle suspension, the adhesive
-interaction between two vesicles is often ignored
-\cite{Veerapaneni2009_JCP,RahimianVeerapaneniBiros2010_JCP} for
-numerical convenience, mostly because a smaller time step is often
+interaction between two vesicles is often
+ignored~\cite{Veerapaneni2009_JCP,  RahimianVeerapaneniBiros2010_JCP}
+for numerical convenience, mostly because a smaller time step is often
 needed to resolve the dynamics of the lubrication thin film between two
@@
   \xx_s \cdot \uu_s =0, \quad &\xx \in \gamma,
-    &&\mbox{\em vesicle inextensibility} \\
+    &&\mbox{\em local inextensibility} \\
   \llbracket T \rrbracket \nn = \xxi, \quad &\xx \in \gamma,
@@
 \end{equation*}
-where $\xxi$ is the traction jump that depends on a bending, stretching,
-and adhesion.  The bending term is $\BB \xx = -\kappa_b \xx_{ssss}$,
-where $\kappa_b$ is the bending modulus, and this term comes from the
-Helfrich energy.  For the numerical examples, we set $\kappa_b = 1$ and
-use a Hamaker constants ranging from $0.1$ to $1$.  The stretching term
-is $\TT \sigma  = (\sigma \xx_s)_s$, where $\sigma$ is the tension.  The
-resistance to bending and stretching are standard assumptions of
+where $\xxi$ is the traction jump that is the sum of the bending,
+stretching, and adhesion forces.  The bending term $\BB \xx = -\kappa_b
+\xx_{ssss}$ comes from the Helfrich energy, where $\kappa_b$ is the
+bending modulus and $s$ is arclength.  For the numerical examples, we
+set $\kappa_b = 1$ and consider adhesion strengths ranging from $0.1$ to
+$1$ times the bending modulus.  The stretching term is $\TT \sigma  =
+(\sigma \xx_s)_s$, where $\sigma$ is the tension, and the tension acts
+as a Lagrange multiplier to satisfy the local extensibility constraint.
+The resistance to bending and stretching are standard assumptions of
 vesicles.  In this work, we include an adhesive term, $\AA \xx$, that we
@@
 adhesion between a single three-dimensional vesicle and a solid wall at
-$z=0$.  The adhesion potential in their model is of the functional form
-in equation~\eqref{eq:adhesion_potential} with $(m,n) = (4,2)$:
+$z=0$.  They use the adhesion potential of the function form
 \begin{align}
@@
 where $z$ is the distance between the solid wall and the vesicle,
-$H$ is the Hamaker constant, and $\delta$ is the adhesion length
-scale.  We generalize this model to an unbounded suspension of vesicles.
-We assume that the adhesion force applies between all pairs of points on
-different vesicles, so we are interested in Hamaker constants that are
-appropriate for lipid-lipid interactions. In
-Appendix~\ref{sec:appendixA}, the adhesive force at a point $\xx$ on
+$\mathcal{H}$ is the Hamaker constant, $\delta$ is the adhesion length
+scale and $(m,n) = (4,2)$.  We generalize this model to an unbounded
+suspension of vesicles.  We assume that the adhesion force applies
+between all pairs of points on different vesicles, so we are interested
+in Hamaker constants that are appropriate for lipid-lipid interactions.
+In Appendix~\ref{sec:appendixA}, the adhesive force at a point $\xx$ on
 vesicle $j$ is shown to be
 \begin{align}
-  \AA\xx:=-H m \delta^{n}\sum_{\substack{k=1 \\ k \neq j}}^M 
+  \AA\xx:=-\mathcal{H} m \delta^{n}\sum_{\substack{k=1 \\ k \neq j}}^M 
   \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+2}} 
@@
   \caption{\label{fig:adhesionModel} {\em Left}: The adhesion potential
-  $\phi(z)$ in Equation~\eqref{eq:adhesion_potential}.  Distances less
+  $\phi(z)$ in equation~\eqref{eq:adhesion_potential}.  Distances less
   than $\delta$ are repulsive and distances greater than $\delta$ are
   attractive.  {\em Center}: Each point on a vesicle is repelled or
-  attracted by all points on the other vesicles.  {\em Left}: The
+  attracted by all points on the other vesicles.  {\em Right}: The
   resulting adhesive force is found by integrating over all points on
@@
 equation~\eqref{eqn:adhesionForce} is between two small patches of lipid
-bilayer membrane (because the lipid molecules are coarse-grained in the continuum modeling).
-Thus a reasonable choice for $(m,n)$ between two coarse-grained membrane patches
- would be between those for two planar surfaces and two point molecules.
-
- Large value of $m$ corresponds to a sharp increase in the repulsion force as two objects are within the separation distance $\delta$.
- This poses great challenges for simulations as the numerical time-marching can be very stiff (i.e., very small time step) for large $m$. 
- The adaptive time-stepping BIE scheme makes it possible to simulate vesicle adhesive dynamics with specified numerical precision for reasonable computation time.
- We explore several combinations of $(m,n)$ in the simulations 
- of two vesicles forming a doublet in a quiescent flow.
- We found very little difference in both the dynamic evolution and equilibrium configuration between $(m,n)=(8,6)$ and $(m,n)=(4,2)$.
-
- %
-%
-% Thus we argue that a reasonable choice for $(m,n)$ is
-%between $(m,n) = (4,2)$ and $(m,n) = (12,6)$.
+bilayer membrane (because the lipid molecules are coarse-grained in the
+continuum modeling).  Thus a reasonable choice for $(m,n)$ between two
+coarse-grained membrane patches would be between those for two planar
+surfaces and two point molecules.
+
+Large value of $m$ corresponds to a sharp increase in the repulsion
+force as two objects are within the separation distance $\delta$.  This
+poses great challenges for simulations as the problem becomes stiff
+(i.e., requires a very small time step) for large $m$.  The adaptive
+time-stepping BIE scheme makes it possible to simulate vesicle adhesive
+dynamics with specified numerical precision for reasonable computation
+time.  We explore several combinations of $(m,n)$ in the simulations of
+two vesicles forming a doublet in a quiescent flow.  We found very
+little difference in both the dynamic evolution and equilibrium
+configuration between $(m,n)=(8,6)$ and $(m,n)=(4,2)$.
 
@@
 \subsection{Integral Equation Formulation}
-Because the fluid equations are linear and elliptic, an integral
+Because the fluid equations are linear and elliptic, a boundary integral
 equation formulation is possible.  This has several advantages,
@@
 \end{align}
-where $\rr = \xx - \yy$ and $\rho = \|\rr\|$.  The traction jump of the
-velocity $\uu(\xx) = \SS[\ff](\xx)$ is the density function $\ff$, so
-the fluid velocity is $\xx \in \RR^2$ is
-\begin{align*}
-  \uu(\xx) = \uu_{\infty}(\xx) + \SS[\xxi](\xx).
-\end{align*}
-The traction jump is given by three terms: the bending, tension, and
-adhesion.  Therefore
-\begin{align*}
-  \xxi = -\kappa_b \xx_{ssss} + (\sigma \xx_s)_s + \AA \xx.
-\end{align*}
-Applying the no-slip boundary condition on each vesicle, the governing
-equations are
+where $\rr = \xx - \yy$ and $\rho = \|\rr\|$.  Then, given a vesicle
+with a traction jump $\xxi$, the fluid velocity at is~\cite{poz1992}
+\begin{align*}
+  \uu(\xx) = \uu_{\infty}(\xx) + \SS[\xxi](\xx), \quad \xx \in \RR^2.
+\end{align*}
+The traction jump is
+\begin{align*}
+  \xxi = -\kappa_b \xx_{ssss} + (\sigma \xx_s)_s + \AA \xx,
+\end{align*}
+where the three terms correspond to the forces due to bending, tension,
+and adhesion, respectively.  Therefore Applying the no-slip boundary
+condition on each vesicle, the governing equations are
 \begin{align*}
@@
 and the tension operator $\TT[\xx](\sigma) = (\sigma \xx_s)_s$, the
-no-slip boundary condition can be written as
+no-slip boundary condition gives
 \begin{align*}
@@
 that treats both the bending and tension terms
-semi-implicitly~\cite{quaife2016adaptive}. Note that the adhesive term is
+semi-implicitly~\cite{qua-bir2014}. Note that the adhesive term is
 treated explicitly.  Therefore, a single time step requires solving
-\begin{align}
+\begin{align*}
   \xx^{N+1} - \Delta t \SS^N \BB^N \xx^{N+1} - 
@@
     \Delta t \SS^N \AA^N \xx^N,
-  \label{eqn:IMEXEuler}
-\end{align}
+\end{align*}
 along with the inextensibility constraint that is discretized as
@@
 We discretize the vesicles at a set of collocation points, compute the
-bending and tension terms with Fourier differentiation, and apply
-Alpert quadrature to the logarithmically singular single-layer potential
-$\SS$~\cite{alp1999}.  The source and target points of the adhesion
-force never coincide since they are always on different vesicles, so the
+bending and tension terms with Fourier differentiation, and apply Alpert
+quadrature~\cite{alp1999} to the logarithmically singular single-layer
+potential $\SS$.  The source and target points of the adhesion force
+never coincide since they are always on different vesicles, so the
 adhesion force~\eqref{eqn:adhesionForce} is computed with the spectrally
@@
 doublet and its rheological properties.  Therefore, time adaptivity is
-crucial so that a user-specified tolerance is achieved with using a
+crucial so that a user-specified tolerance is achieved without using a
 guess-and-check procedure to find an appropriately small fixed time step
-size.  To control the error and achieve higher-order accuracy in time,
+size.  To control the error and achieve second-order accuracy in time,
 we apply a time adaptive spectral deferred correction
-method~\cite{quaife2016adaptive}.  The SDC method is able to achieve
-second-order accuracy by iteratively applying the first-order
-method~\eqref{eqn:IMEXEuler}.
+method~\cite{quaife2016adaptive}.
 
@@
 \subsection{The Shear and Normal Stresses}
-Consider a single vesicle $\gamma$ and a target point $\xx$ in the fluid
-bulk.  In addition to the velocity $\uu$, we are also interested in
-computing the shear stress and normal stresses of each vesicle.
-Therefore, we must compute the total stress tensor
-\begin{align*}
-  T = - p I + \nabla \uu + \nabla \uu^T
-\end{align*}
-of the single-layer potential~\eqref{eqn:SLP}.  Given a traction jump
-$\xxi$ across a vesicle $\gamma$, the velocity, pressure, and stress
-tensor at a target point $\xx$ are in the bulk
-\begin{align*}
-  \uu(\xx) &= \SS_\uu[\xxi](\xx) = \frac{1}{4\pi\mu}\int_{\gamma} \left( 
+To characterize the rheological properties of the suspension of a
+doublet, it is necessary to compute shear and normal stresses.  At a
+point $\xx$ in the fluid bulk, The velocity $\uu(\xx)$, pressure
+$p(\xx)$, and total stress tensor $T = - p I + \nabla \uu + \nabla
+\uu^T$ of the single-layer potential~\eqref{eqn:SLP} are
+\begin{align*}
+  \uu(\xx) &= \SS_\uu[\ff](\xx) = \frac{1}{4\pi\mu}\int_{\gamma} \left( 
     -\log \rho + \frac{\rr \otimes \rr}{\rho^2} \right) 
-    \xxi ds_\yy, \\
-    p(\xx) &= \SS_p[\xxi](\xx) = \frac{1}{2\pi} \int_{\gamma} 
-    \frac{\rr \cdot \xxi}{\rho^2} ds_\yy, \\
-    T(\xx) &= \SS_T[\xxi](\xx) = -\frac{1}{\pi}\int_{\gamma}
-      \frac{\rr \cdot \xxi}{\rho^2} 
+    \ff ds_\yy, \\
+    p(\xx) &= \SS_p[\ff](\xx) = \frac{1}{2\pi} \int_{\gamma} 
+    \frac{\rr \cdot \ff}{\rho^2} ds_\yy, \\
+    T(\xx) &= \SS_T[\ff](\xx) = -\frac{1}{\pi}\int_{\gamma}
+      \frac{\rr \cdot \ff}{\rho^2} 
       \frac{\rr \otimes \rr}{\rho^2} ds_\yy.
 \end{align*}
-We require the stress tensor on the vesicle, and the layer potential for
-$\SS_T$ has a jump as $\xx$ approaches $\gamma$.  Accounting for the
-jump, the stress tensor at $\xx \in \gamma$ is
-\begin{align*}
-  T(\xx) = \frac{1}{2}(\nn \otimes \xxi) + \frac{1}{2} \left(
+To compute the stress tensor on a vesicle, there is a jump in the layer
+potential $\SS_T$, and the stress tensor is
+\begin{align*}
+  T(\xx) = \frac{1}{2}(\nn \otimes \ff) + \frac{1}{2} \left(
     \tt \otimes \left[
@@
     \end{array}
-    \right] \xxi \right) + 
-  \SS_T[\xxi](\xx).
-\end{align*}
-With the stress tensor computed for $\xx \in \gamma$, we can compute the
-shear stress and normal stress
+    \right] \ff \right) + 
+  \SS_T[\ff](\xx), \quad \xx \in \gamma,
+\end{align*}
+where $\nn$ and $\tt$ are the vesicle's outward unit normal and tangent
+vector, respectively.  With the stress tensor computed for $\xx \in
+\gamma$, the shear and normal stresses are
 \begin{align*}
@@
 \label{sec:qflow} 
-
+We consider the suspension of two identical two-dimensional vesicles
+suspended in a quiescent flow.  Without any external forcing such as an imposed
+electric field or a fluid flow in the far-field, the long-range
+attraction pulls two vesicles together until their separation distance
+is close to $\delta$.  In Section~\ref{subsec:qflow_draining_times}, we
+compute the expected time for the vesicles to reach an equilibrium
+configuration and compare the analysis with numerical simulations.  In
+Section~\ref{subsec:qflow_adhesion_parameters}, we characterize the
+effects of the adhesion parameters and the vesicles' reduced area on the
+bending and adhesive energies.
+
+\subsection{Effects of the adhesion parameters on draining times}
+\label{subsec:qflow_draining_times}
 When two vesicles move towards (or away from) each other under a
@@
 \end{align}
-where $K_a$ is the area expansion modulus, $\mu$ is the viscosity of
-exterior fluid, $R_0$ is the radius of the undeformed vesicle.  For the
-case of a constant forcing $F$ (independent of separation distance $h$
-and time $t$), equation~\eqref{eq:dhdt} can be easily integrated to give
-a relation between film thickness $h$ and time $t$:
-\begin{align*}
-t \sim \frac{\mu R_0^{10/3}}{K_a^{2/3} F^{1/3}}\frac{1}{2 h^2} \bigg|^{h(t)}_{h(0)},
-\end{align*}
-where $h(0)$ is the vesicle separation at $t=0$.
-We note that $F< (>) 0$ for an attractive  (repulsive) interaction
-between two vesicles,  and consequently $h(t)$ decreases (increases)
-from  the initial separation distance $h(0)$.  When the force is
-attractive, $h$ decreases monotonically and $t$ in the above equation is
-the draining time that diverges as $h\rightarrow 0$.
-%Similarly $F>0$ for a repulsive force and consequently $h(t) > h(0)$.
-
-When the force on each vesicle is a function of separation distance $h$ of the form (with integers $n>m\ge 2$)
+where $K_a$ is the area expansion modulus, $\mu$ is the viscosity of the
+exterior fluid, and $R_0$ is the radius of the undeformed vesicle.  For
+the case of a constant forcing $F$ (independent of separation distance
+$h$ and time $t$), equation~\eqref{eq:dhdt} can be easily integrated to
+relate the film thickness $h$ and time $t$:
+\begin{align*}
+  t \sim \frac{\mu R_0^{10/3}}{K_a^{2/3} F^{1/3}}
+    \frac{1}{2 h^2} \bigg|^{h(t)}_{h(0)},
+\end{align*}
+where $h(0)$ is the vesicle separation at $t=0$.  We note that $F< (>)
+0$ for an attractive  (repulsive) interaction between two vesicles,  and
+consequently $h(t)$ decreases (increases) from  the initial separation
+distance $h(0)$.  When the force is attractive, $h$ decreases
+monotonically, and $t$ in the above equation is the draining time that
+diverges as $h\rightarrow 0$.
+
+When the force on each vesicle is a function of the separation distance
+$h$ of the form (with integers $n>m\ge 2$)
 \begin{align}
   \label{eq:Fh}
-F(h) \sim H \frac{\delta^m}{h^{m+1}}\left(\left(\frac{\delta}{h}\right)^{m-n}-1\right),
+  F(h) \sim \mathcal{H} \frac{\delta^m}{h^{m+1}}
+    \left(\left(\frac{\delta}{h}\right)^{m-n}-1\right),
 \end{align}
-attraction is dominant at ``large" distance ($h > \delta$) while repulsion
-is dominant at ``small" distance ($h<\delta$).  Integration of
-equation~\eqref{eq:dhdt} with the above $F(h)$ gives the relationship
-between $t$ and $h$.  In this case the relationship involves an integral
-of a function of dimensionless $\bar{h} \equiv h/\delta$:
-\begin{align*}
-t\frac{K_a^{2/3}}{\mu R_0^{10/3}}& = \int^{h(t)}_{h(0)}-\frac{dh}{h^3
-  F^{1/3}} = -\frac{1}{H^{1/3}\delta^{5/3}}\int^{\bar{h}(t)}_{\bar{h}(0)}\frac{d \bar{h}}{\bar{h}^{(8-m)/3}(\bar{h}^{m-n}-1)^{1/3}},
-\end{align*}
+attraction is dominant at ``large" distances ($h > \delta$) while
+repulsion is dominant at ``small" distances ($h<\delta$).  Integration
+of equation~\eqref{eq:dhdt} with the $F(h)$ as defined in
+equation~\eqref{eq:Fh} gives the relationship between $t$ and $h$.  In
+this case the relationship involves an integral of a function of
+dimensionless $\bar{h} \equiv h/\delta$:
+\begin{align*}
+  t\frac{K_a^{2/3}}{\mu R_0^{10/3}}& = 
+    \int^{h(t)}_{h(0)}-\frac{dh}{h^3 F^{1/3}} = 
+    -\frac{1}{\mathcal{H}^{1/3}\delta^{5/3}}\int^{\bar{h}(t)}_{\bar{h}(0)}
+      \frac{d \bar{h}}{\bar{h}^{(8-m)/3}(\bar{h}^{m-n}-1)^{1/3}},
+\end{align*}
+Solving for $t$,
 \begin{align}
 \label{eq:teq_scaling}
-t\sim \frac{\mu R_0^{10/3}}{K_a^{2/3}}\frac{1}{H^{1/3}\delta^{5/3}}.
+  t\sim \frac{\mu R_0^{10/3}}{K_a^{2/3}}\frac{1}{\mathcal{H}^{1/3}\delta^{5/3}},
 \end{align}
-Equation~\eqref{eq:teq_scaling} tells us that both adhesion strength $H$
-and the separation distance $\delta$ affect the time it takes for a pair
-of vesicles to reach the separation distance $\delta$ under adhesion force $F$ in
-equation~\eqref{eq:Fh}.  In particular, the duration $t$ is
-proportional to (1) the separation distance $\delta^{-5/3}$ (thus
-$t\rightarrow \infty$ as $\delta\rightarrow 0$), and (2) the adhesion
-strength $H^{-1/3}$ (as in constant forcing
+and equation~\eqref{eq:teq_scaling} tells us that both the adhesion
+strength $\mathcal{H}$ and the separation distance $\delta$ affect the
+time it takes for a pair of vesicles to reach the separation distance
+$\delta$ under adhesion force $F$ in equation~\eqref{eq:Fh}.  In
+particular, the duration $t$ is proportional to (i) the separation
+distance $\delta^{-5/3}$ (thus $t\rightarrow \infty$ as
+$\delta\rightarrow 0$), and (ii) the adhesion strength
+$\mathcal{H}^{-1/3}$ (as in constant forcing
 case~\cite{RamachandranLeal2010_PoF}).  From the above analysis we also
@@
   vesicles to reach equilibrium. {\em Left}: Scaling with respect to
-  $\delta$ with $H=0.1$.  {\em Right}: Scaling with respect to $H$ with
+  $\delta$ with $\mathcal{H}=0.1$.  {\em Right}: Scaling with respect to
+  $\mathcal{H}$ with
   $\delta = 0.4$. Arrows indicate the time by when the equilibrium is
   reached within $1\%$.}
-\end{figure}
-
-To test the scaling of the duration $t$ with respect to $H$
+  \todo[inline]{Change the $H$ in the right figure to $\mathcal{H}$}
+\end{figure}
+
+To test the scaling of the duration $t$ with respect to $\mathcal{H}$
 and $\delta$, we simulate the vesicle adhesion dynamics in a quiescent
-flow.  Starting with two vesicles at a distance of twice the radius at
-$t=0$, the long-range attraction pulls the vesicles together.
-Figure~\ref{fig:qflow00}(a) plots the scaled adhesion energy versus time
-with $H=0.1$ and three values of $\delta$ as labeled.  Adhesion energy
-reaches minimum at equilibrium, and the scaled $E_{adh}$ evolves towards
-zero at equilibrium.  The arrow indicate the times when the scaled
-adhesion energy reaches within $1\%$ of equilibrium: $t\sim 96$ for
-$\delta=0.2$, $t\sim 45$ for $\delta = 0.3$, and $t\sim 30$ for
-$\delta=0.4$:
-\begin{align*}
-\frac{t_{\delta=0.2}}{t_{\delta=0.4}} \sim \frac{96}{30}=3.2 &\Longleftrightarrow \left(\frac{0.4}{0.2}\right)^{5/3}\sim 3.17,\\
-\frac{t_{\delta=0.2}}{t_{\delta=0.3}} \sim \frac{96}{45}=2.1 &\Longleftrightarrow \left(\frac{0.3}{0.2}\right)^{5/3}\sim 2.
-\end{align*}
-
-The scaling with respect to adhesion strength $H$ is illustrated in
-Figure~\ref{fig:qflow00}(b), where $\delta = 0.4$ and $H$ varies from
-$0.1$ to $0.5$ as labeled.  Again the arrows indicate the times when the
-equilibrium is reached within $1\%$:
-\begin{align*}
-\frac{t_{H=0.1}}{t_{H=0.5}} \sim \frac{34}{20} = 1.71 &\Longleftrightarrow \left(\frac{0.5}{0.1}\right)^{1/3}\sim 1.71.
-\end{align*}
-From the above results we conclude that the scaling in
+flow.  Starting with two vesicles at a distance of twice the vesicle
+radius at $t=0$, the long-range attraction pulls the vesicles together.
+The left plot of Figure~\ref{fig:qflow00} shows the scaled adhesion
+energy versus time with $\mathcal{H}=0.1$ and three values of $\delta$
+as labeled.  Adhesion energy reaches minimum at equilibrium, and the
+scaled $E_{adh}$ evolves towards zero at equilibrium.  The arrows
+indicate the times when the scaled adhesion energy reaches within $1\%$
+of equilibrium: $t\sim 96$ for $\delta=0.2$, $t\sim 45$ for $\delta =
+0.3$, and $t\sim 30$ for $\delta=0.4$:
+\begin{align*}
+\frac{t_{\delta=0.2}}{t_{\delta=0.4}} \sim \frac{96}{30}=3.2 
+  &\Longleftrightarrow \left(\frac{0.4}{0.2}\right)^{5/3}\sim 3.17,\\
+\frac{t_{\delta=0.2}}{t_{\delta=0.3}} \sim \frac{96}{45}=2.1 
+  &\Longleftrightarrow \left(\frac{0.3}{0.2}\right)^{5/3}\sim 2.
+\end{align*}
+
+The scaling with respect to adhesion strength $\mathcal{H}$ is
+illustrated in the right plot of Figure~\ref{fig:qflow00}, where $\delta
+= 0.4$ and $\mathcal{H}$ varies from $0.1$ to $0.5$ as labeled.  Again
+the arrows indicate the times when the equilibrium is reached within
+$1\%$:
+\begin{align*}
+  \frac{t_{\mathcal{H}=0.1}}{t_{\mathcal{H}=0.5}} \sim \frac{34}{20} = 1.71 
+  &\Longleftrightarrow \left(\frac{0.5}{0.1}\right)^{1/3}\sim 1.71.
+\end{align*}
+From the above results, we conclude that the scaling in
 equation~\eqref{eq:teq_scaling} captures the adhesion dynamics of two
@@
 
-\subsection{Effects of the adhesion parameters on equilibrium configuration of a vesicle pair}
+\subsection{Effects of the adhesion parameters on equilibrium
+configuration of a vesicle pair}
 \label{subsec:qflow_adhesion_parameters} 
-In the simulations of a pair of 2d vesicles interacting with each other
-via the adhesion force in equation~\eqref{eq:Fh}, two vesicles are
-initially placed not too far apart  from each other for numerical
-convenience.  Without any external forcing such as an imposed electric
-field or a fluid flow in the far-field, the long-range attraction pulls
-two vesicles together until their separation distance is close to
-$\delta$ (where the adhesive force $F$ vanishes).  
-%
-Once a vesicle doublet is formed, the membrane shape in the contact region 
-depends on the adhesion strength
-relative to the membrane bending rigidity.
-For weak to moderate adhesion strength, vesicle membranes are flattened in the contact region while the rest of vesicle maintains a nearly spherical shape
-\cite{EvansMetcalfe1984_BJ, Book_PhysicalBasisCellAdhesion, Book_IntermolecularSurfaceForces,RamachandranAndersonLealIsraelachvili2010_Langmuir}.
-Under a strong adhesion, however, the vesicle membranes in the contact region buckle and form a sigmoidal shape  that has been observed in RBC doublet as well
-\cite{Ziherl2007_PRL,ZiherlSvetina2007_PNAS,FlormannAouane2017_SciReports}. An external electric field is also able to buckle a vesicle membrane that is adhered to a solid
-substrate \cite{SteinkuhlerAgudo-Canalejo2016_BJ}.
+We next simulate a pair of identical two-dimensional vesicles
+interacting with each other via the adhesion force in
+equation~\eqref{eq:Fh}.  The initial vesicle placement is smaller than
+in the previous simulations so that the equilibrium configuration is
+achieved with a shorter timer horizon.  Once a vesicle doublet is
+formed, the membrane shape in the contact region depends on the adhesion
+strength relative to the membrane bending rigidity.  For weak to
+moderate adhesion strength, vesicle membranes are flattened in the
+contact region while the rest of vesicle maintains a nearly spherical
+shape~\cite{EvansMetcalfe1984_BJ, Book_PhysicalBasisCellAdhesion,
+Book_IntermolecularSurfaceForces,
+RamachandranAndersonLealIsraelachvili2010_Langmuir}.  Under a strong
+adhesion, however, the vesicle membranes in the contact region buckle
+and form a sigmoidal shape  that has been observed in RBC doublet as
+well~\cite{Ziherl2007_PRL, ZiherlSvetina2007_PNAS,
+FlormannAouane2017_SciReports}.  An external electric field is also able
+to buckle a vesicle membrane that is adhered to a solid
+substrate~\cite{SteinkuhlerAgudo-Canalejo2016_BJ}.
 
@@
 
-In this work we focus on weakly adhesive vesicles whose equilibrium shapes in a quiescent flow are shown in figure~\ref{fig:Dec18_vesicle_shape}(a)
-for three values of reduced area:  $\Delta A=0.95$, $0.75$ and
-$0.6$ with $H=5$ and $\delta = 0.2$. 
+In this work we focus on weakly adhesive vesicles whose equilibrium
+shapes in a quiescent flow are shown in the left plot of
+Figure~\ref{fig:Dec18_vesicle_shape} for three reduced areas: $\Delta
+A=0.95$, $0.75$, and $0.6$ with $\mathcal{H}=5$ and $\delta = 0.2$. 
 \begin{figure}
@@
   \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
-\caption{Two vesicles of length $\pi$ with $\kappa=1$, $H=5$ and
-  $\delta=0.2$.  (a) Equilibrium shapes of two vesicles under adhesive
-  interactions with adhesion strength $H=0.5$ and separation distance
-  $\delta=0.2$.  Vesicle reduced area $\Delta A=0.95$, $0.75$ and $0.6$
-  as labeled.  The color coding is the tension along the vesicle. (b)
-  Membrane shapes in the contact region.}
-\label{fig:Dec18_vesicle_shape}
-\end{figure}
- The equilibrium vesicle shape for
-$\Delta A=0.95$ is the circular cap with a flat contact region.  This
-is similar to the observed shapes of two vesicles under strong adhesive interaction
-in~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.  
-When vesicles are more deflated with a reduced area  $\Delta A = 0.75$, the equilibrium vesicle shape is elongated with a bigger contact region. This is consistent
-with the equilibrium shapes of a vesicle doublet under a L-J potential  ($(m,n) = (12,6)$) \cite{FlormannAouane2017_SciReports}.
-As the reduced area decreases further, we observe undulation of the elongated equilibrium vesicle shape on the non-contact side while the contact region remains flat. 
-The color coding along each curve is for the tension of vesicle membrane.
-We observe that the membrane tension in the contact region is very negative, indicating a dominant compression of membrane when the adhesion force is strong to keep the vesicles bound together.
-
-Figure~\ref{fig:Dec18_vesicle_shape}(b) is a zoom on the membranes in the contact region, where the membranes are not perfectly flat: 
-For all values of reduced area we observe that membranes are slightly curved with a dip at the edge.
-Such membrane undulation in the contact region is predicted by lubrication analyses on the a membrane under adhesion with a solid substrate
-\cite{BlountMiksisDavis2013_PRSa,YoungStone2017_PRF}. 
-Also the dip at the edge of contact region is related to but different from the buckling of membrane under strong adhesion:
-A closer inspection on the dip at the edge shows that the membrane distance is smaller than the neutral separation distance $\delta$ there. Thus the adhesion force is attractive for
-most of the membranes in the contact region except at the edge, where the adhesive force turns repulsive.
-Results from the lubrication analysis shows that this dip and slightly curved shape in the contact region are independent of the adhesion strength. The high membrane curvature
-at the edge may pose a problem for using the contact angle there to estimate the adhesion strength.
-This inspires us to investigate the possibility of using a dynamic fluid trap to measure the adhesion strength (see \S~\ref{sec:eflow}).
+  \caption{\label{fig:Dec18_vesicle_shape} Two vesicles of length $\pi$
+  with $\kappa=1$, $\mathcal{H}=5$, and $\delta=0.2$.  {\em Left}:
+  Equilibrium shapes of two vesicles under adhesive interactions with
+  adhesion strength $\mathcal{H}=0.5$ and separation distance
+  $\delta=0.2$.  Vesicle reduced area $\Delta A=0.95$, $0.75$, and $0.6$
+  are labeled.  The color coding is the tension along the vesicle. {\em
+  Right}: Membrane shapes in the contact region.} \todo[inline]{This
+  caption contradicts itself.  Is it $\mathcal{H} = 0.5$ or $\mathcal{H}
+  = 5$?}
+\end{figure}
+The equilibrium vesicle shape for $\Delta A=0.95$ is the circular cap
+with a flat contact region.  This is similar to the observed shapes of
+two vesicles under strong adhesive interaction
+in~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.  When
+vesicles are more deflated with a reduced area $\Delta A = 0.75$, the
+equilibrium vesicle shape is elongated with a bigger contact region.
+This is consistent with the equilibrium shapes of a vesicle doublet
+under a L-J potential ($(m,n) =
+(12,6)$)~\cite{FlormannAouane2017_SciReports}.  As the reduced area
+decreases further, we observe undulation of the elongated equilibrium
+vesicle shape on the non-contact side while the contact region remains
+flat.  The color coding along each curve is the tension of the vesicle
+membrane.  We observe that the membrane tension in the contact region is
+very negative, indicating a dominant compression of membrane when the
+adhesion force is strong to keep the vesicles bound together.
+
+The right plot of Figure~\ref{fig:Dec18_vesicle_shape} is a zoom on the
+membranes in the contact region, where the membranes are not perfectly
+flat: For all values of reduced area we observe that membranes are
+slightly curved with a dip at the edge.  Such membrane undulation in the
+contact region is predicted by lubrication analyses on a membrane
+under adhesion with a solid substrate~\cite{BlountMiksisDavis2013_PRSa,
+YoungStone2017_PRF}.  Also the dip at the edge of contact region is
+related to but different from the buckling of membrane under strong
+adhesion: A closer inspection on the dip at the edge shows that the
+membrane distance is smaller than the neutral separation distance
+$\delta$ there. Thus the adhesion force is attractive for most of the
+membranes in the contact region except at the edge, where the adhesive
+force turns repulsive.  Results from the lubrication analysis shows that
+this dip and slightly curved shape in the contact region are independent
+of the adhesion strength. The high membrane curvature at the edge may
+pose a problem for using the contact angle there to estimate the
+adhesion strength. This inspires us to investigate the possibility of
+using a dynamic fluid trap to measure the adhesion strength (see
+Section~\ref{sec:eflow}).
 
@@
 \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_EbEadh_vs_rA_adR0p2_adS502.jpeg}
-\caption{Two vesicles of length $\pi$ with $\kappa=1$, $H=5$ and $\delta=0.2$. 
-(a) Total bending energy (solid curve) and adhesion energy (dash-dotted curve) plotted against
-the reduced area $\Delta A$. (b) Sum of two energies plotted against reduced area $\Delta A$.}
-\label{fig:Dec18_vesicle_equilibrium1}
-\end{figure}
-Figure~\ref{fig:Dec18_vesicle_equilibrium1}(a) shows the total bending
-energy as a function of reduced area. The smaller the reduced area, the
-more vesicle area is available for deformation and thus the bending
-energy is higher. Figure~\ref{fig:Dec18_vesicle_equilibrium1}(b) shows
-the total adhesion energy as a function of reduced area. We note that
-the total adhesion energy is more negative as reduced area decreases.
-The sum of two energies is plotted in
-Figure~\ref{fig:Dec18_vesicle_equilibrium1}(c), where a local minimum in
-the total energy is found around $\Delta A =0.8$.
+  \caption{\label{fig:Dec18_vesicle_equilibrium1} Two vesicles of length
+  $\pi$ with $\kappa=1$, $\mathcal{H}=5$ and $\delta=0.2$.  {\em Left}:
+  Total bending energy (solid curve) and adhesion energy (dash-dotted
+  curve) plotted against the reduced area $\Delta A$. {\em Right}: Sum
+  of two energies plotted against reduced area $\Delta A$.}
+\end{figure}
+
+The left plot of Figure~\ref{fig:Dec18_vesicle_equilibrium1} shows the
+total bending energy and adhesion energy as a function of the reduced
+area. The smaller the reduced area, the more vesicle area is available
+for deformation and thus the bending energy is higher.  In contrast, the
+total adhesion energy becomes more negative as the reduced area
+decreases.  The sum of two energies is plotted in the right plot of
+Figure~\ref{fig:Dec18_vesicle_equilibrium1}, where a local minimum in
+the total energy is found around $\Delta A = 0.85$.
 
@@
 \includegraphics[keepaspectratio=true,scale=0.18]{figs/Dec18_Eadh_vs_sigma_rA0p9502.jpeg}
-\caption{Total bending energy (a) and adhesion energy (b) versus the
-  adhesion strength $H$ 
-for two vesicles with reduced area $\Delta A=0.95$, separation distance $\delta = 0.2$ (triangles), $0.3$ (crosses)
-and $0.4$ (circles). }
-\label{fig:Dec18_equilibrium} 
-\end{figure}
-%
-Figure~\ref{fig:Dec18_equilibrium} is an example of how the adhesion
-strength $H$ and separation distance $\delta$ affect the equilibrium
-configuration of two vesicles under adhesive interactions.  For both
-vesicles the reduced area $\Delta A=0.95$ and the bending rigidity is
-$1$.  In Figure~\ref{fig:Dec18_equilibrium}(a) the total bending energy
-at equilibrium is plotted against $H$ for three values of separation
-distance $\delta$.  We observe that for $\Delta A=0.95$ the equilibrium
-vesicle shape does not vary much with the adhesion strength $H$, while
-the total adhesion energy in Figure~\ref{fig:Dec18_equilibrium}(b)
-varies linearly with $H$.
+  \caption{\label{fig:Dec18_equilibrium} Total bending energy (\em left)
+  and adhesion energy {\em right} versus the adhesion strength
+  $\mathcal{H}$ for two vesicles with reduced area $\Delta A=0.95$,
+  separation distance $\delta = 0.2$ (triangles), $0.3$ (crosses), and
+  $0.4$ (circles).}
+  \todo[inline]{Change $H$ to $\mathcal{H}$ in the x-axis.}
+\end{figure}
+
+Figure~\ref{fig:Dec18_equilibrium} demonstrates how the adhesion
+strength $\mathcal{H}$ and separation distance $\delta$ affect the
+equilibrium configuration of two vesicles under adhesive interactions.
+For both vesicles the reduced area $\Delta A=0.95$ and the bending
+rigidity is $\kappa_b = 1$.  The total bending (left) and adhesion
+(right) energies at equilibrium are plotted against $\mathcal{H}$ for
+three values of separation distance $\delta$.  We observe that for
+$\Delta A=0.95$ the equilibrium vesicle shape does not vary much with
+the adhesion strength $\mathcal{H}$, while the total adhesion energy
+varies linearly with $\mathcal{H}$.
 
@@
   \caption{\label{fig:extensional1} Two vesicles in an extensional flow.
-  The reduced area is $A = 0.7$, the Hamaker constant is $H = 0.7$, the
-  adhesion length scale is $\delta = 0.4$, and the extensional rate is
-  $\chi = 0.02$.  The center of the vesicle, denoted with a black
-  square, is a stagnation point.}
+  The reduced area is $A = 0.7$, the Hamaker constant is $\mathcal{H} =
+  0.7$, the adhesion length scale is $\delta = 0.4$, and the extensional
+  rate is $\chi = 0.02$.  The center of the vesicle, denoted with a
+  black square, is a stagnation point.}
 \end{figure}
@@
   \caption{\label{fig:extensional2} Two vesicles in an extensional flow.
-  The reduced area is $A = 0.7$, the Hamaker constant is $H = 0.7$, the
-  adhesion length scale is $\delta = 0.4$, and the extensional rate is
-  $\chi = 0.07$.  The center of the vesicle, denoted with a black
-  square, is a stagnation point.}
+  The reduced area is $A = 0.7$, the Hamaker constant is $\mathcal{H} =
+  0.7$, the adhesion length scale is $\delta = 0.4$, and the extensional
+  rate is $\chi = 0.07$.  The center of the vesicle, denoted with a
+  black square, is a stagnation point.}
 \end{figure}
@@
   \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
-  The reduced area is $A = 0.7$, the Hamaker constant is $H = 0.7$, the
-  adhesion length scale is $\delta = 0.4$, and the extensional rate is
-  $\chi = 0.1$.  The center of the vesicle, denoted with a black square,
-  is a stagnation point.}
+  The reduced area is $A = 0.7$, the Hamaker constant is $\mathcal{H} =
+  0.7$, the adhesion length scale is $\delta = 0.4$, and the extensional
+  rate is $\chi = 0.1$.  The center of the vesicle, denoted with a black
+  square, is a stagnation point.}
 \end{figure}
@@
   \caption{\label{fig:extensional4} Two vesicles in an extensional flow.
-  The reduced area is $A = 0.8$, the Hamaker constant is $H = 0.7$, the
-  adhesion length scale is $\delta = 0.4$, and the extensional rate is
-  $\chi = 0.1$.  Initially, the doublet tilts to an inclination angle,
-  and then the extensional rate overcomes the adhesive force and the
-  doublet is broken.  The center of the vesicle, denoted with a black
-  square, is a stagnation point.}
+  The reduced area is $A = 0.8$, the Hamaker constant is $\mathcal{H} =
+  0.7$, the adhesion length scale is $\delta = 0.4$, and the extensional
+  rate is $\chi = 0.1$.  Initially, the doublet tilts to an inclination
+  angle, and then the extensional rate overcomes the adhesive force and
+  the doublet is broken.  The center of the vesicle, denoted with a
+  black square, is a stagnation point.}
 \end{figure}
@@
   of vesicle hydrodynamics in an extensional flow with a fixed Hamaker
-  constant $H=0.7$ and adhesion length scale $\delta = 0.4$.  For small
-  extensional rates, the doublet structure is not broken (blue marks),
-  while at large extensional rates, the doublet is broken (red marks).
-  The size of the round blue marks indicate the final inclination angle
-  with the larger dots rotation less ($\theta=\pi$) and the smaller dots
-  rotating more ($\theta = \pi/2$).  A square mark is used for
-  simulations that did not result in a steady-state inclination angle in
-  the given time horizon.  {\em Right}: The definition of the
-  inclination angle.  An inclination angle of $\pi$ indicates a doublet
-  whose long axis is parallel to the converging direction, while an
-  inclination angle of $\pi/2$ indicates a doublet whose short axis is
-  parallel to the converging direction.  The square mark is a stagnation
-  point while the round point is located at the center of the vesicle.}
+  constant $\mathcal{H}=0.7$ and adhesion length scale $\delta = 0.4$.
+  For small extensional rates, the doublet structure is not broken (blue
+  marks), while at large extensional rates, the doublet is broken (red
+  marks).  The size of the round blue marks indicate the final
+  inclination angle with the larger dots rotation less ($\theta=\pi$)
+  and the smaller dots rotating more ($\theta = \pi/2$).  A square mark
+  is used for simulations that did not result in an equilibrium
+  inclination angle in the given time horizon.  {\em Right}: The
+  definition of the inclination angle.  An inclination angle of $\pi$
+  indicates a doublet whose long axis is parallel to the converging
+  direction, while an inclination angle of $\pi/2$ indicates a doublet
+  whose short axis is parallel to the converging direction.  The square
+  mark is a stagnation point while the round point is located at the
+  center of the vesicle.}
 \end{figure}
@@
   Results are not reported for all the low extensional rates since the
-  doublet had not tilted to a steady-state inclination angle for the
+  doublet had not tilted to an equilibrium inclination angle for the
   given time horizon.}
@@
 For very low extensional rates, the time horizon is insufficient for the
-doublet to reach a steady state, and these simulations are marked with a
-square.  In Figure~\ref{fig:extensionalInclinationAngle}, we plot the
-inclination angle as a function of time for four different extensional
-rates (left) and the final inclination angle for all doublets that reach
-a steady state (right).  We observe that not only do larger smaller
-extensional rates result in smaller inclination angles, but smaller
-reduced areas also result in smaller inclination angles.
+doublet to reach an equilibrium state, and these simulations are marked
+with a square.  In Figure~\ref{fig:extensionalInclinationAngle}, we plot
+the inclination angle as a function of time for four different
+extensional rates (left) and the final inclination angle for all
+doublets that reach a equilibrium state (right).  We observe that not
+only do larger smaller extensional rates result in smaller inclination
+angles, but smaller reduced areas also result in smaller inclination
+angles.
 
 We further characterize the rotating dynamics of a doublet by examining
-the vorticity and total force on the vesicles.  In Figure~\ref{}
+the vorticity and total force on the vesicles.  In
+Figure~\ref{fig:extensionalVorticity} ...
 
@@
   the extensional rate is $\chi = 0.7$, the adhesion length scale is
-  $\delta = 0.4$, and the Hamaker constant is $H_0 = 0.7$.  When the
-  doublet first starts to rotate, the net total force points in the
+  $\delta = 0.4$, and the Hamaker constant is $\mathcal{H} = 0.7$.  When
+  the doublet first starts to rotate, the net total force points in the
   direction of the diverging direction.  Next, there is a shearing
@@
 vesicles' reduced area, the adhesion length scale $\delta$, the adhesion
-strength $H$, and the shear rate $\chi$.  Figure~\ref{fig:doublet090}
-shows the configuration of two vesicles that have formed a doublet at
-several instances in time.  In Figure~\ref{fig:sflow_phase_diagram}
-(left), we show the minimum distance between the two vesicles as a
-function of time for various adhesion strengths.  The adhesion strength
-corresponding to the red curves is less than a critical strength $H_c$
-for a doublet to form.  In contrast, for larger adhesive strengths,
-doublets are formed (blue curves).
+strength $\mathcal{H}$, and the shear rate $\chi$.
+Figure~\ref{fig:doublet090} shows the configuration of two vesicles that
+have formed a doublet at several instances in time.  In
+Figure~\ref{fig:sflow_phase_diagram} (left), we show the minimum
+distance between the two vesicles as a function of time for various
+adhesion strengths.  The adhesion strength corresponding to the red
+curves is less than a critical strength $\mathcal{H}_c$ for a doublet to
+form.  In contrast, for larger adhesive strengths, doublets are formed
+(blue curves).
 
@@
   \caption{\label{fig:doublet090} The formation of a doublet in a shear
-  flow.  The reduced area is $0.90$, the Hamaker constant is $H=0.7$,
+  flow.  The reduced area is $0.90$, the Hamaker constant is
+  $\mathcal{H}=0.7$,
   the adhesion length scale is $\delta = 0.4$, and the shear rate is
@@
   $\delta = 0.4$.   The different lines correspond to a linear spacing
-  of adhesion strengths ranging from $H=0.1$ and $H=1.0$.  {\em Right}:
+  of adhesion strengths ranging from $\mathcal{H}=0.1$ and $\mathcal{H}=1.0$.  {\em Right}:
   Phase diagram of vesicle hydrodynamics in a shear flow.  At a fixed
   reduced area $\triangle A=0.90$ and $\delta =0.4$,  the critical vdW
-  potential strength $H$ for binding of two vesicles in a shear flow
+  potential strength $\mathcal{H}$ for binding of two vesicles in a shear flow
   depends on the shear rate $\chi$.
@@
   viscosity of a tank treading vesicle (blue) and a doublet (red).  The
-  shear rate is $\chi = 0.5$, the Hamaker constant is $H = 0.7$,
+  shear rate is $\chi = 0.5$, the Hamaker constant is $\mathcal{H} = 0.7$,
   and the adhesion length scale is $\delta = 0.4$.  The length of the
@@
 separate a vesicle doublet with reduced area of $0.8$ and a Hamakar
-constant ${\cal H}=0.7$, which corresponds to $\sim 1$ $\mu J/m^2$.
+constant $\mathcal{H}=0.7$, which corresponds to $\sim 1$ $\mu J/m^2$.
 These conditions are quite realizable in micrifulidic experiments, and
@@
   a large vesicle.  The background flow is quiescent, the adhesion
-  length scale is $\delta = 0.4$, and the Hamaker constant is $H_0 =
-  0.7$.  The suspension is near a steady state at the final
-  configuration.}
+  length scale is $\delta = 0.4$, and the Hamaker constant is
+  $\mathcal{H} = 0.7$.  At the final snapshot, the suspension is near an
+  equilibrium configuration.}
 \end{figure}
@@
 \begin{align*}
-  \phi(z) = H \left[ 
+  \phi(z) = \mathcal{H} \left[ 
     \left(\frac{\delta}{z}\right)^m - \frac{m}{n}\left(\frac{\delta}{z}\right)^n \right],
@@
 \begin{align*}
- \int_{\gamma_2}\nabla \phi(\|\xx_1 - \xx_2\|)ds_{\xx_2} = -m   H\delta^{n}
-   \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+2}} 
+ \int_{\gamma_2}\nabla \phi(\|\xx_1 - \xx_2\|)ds_{\xx_2} = 
+  -m \mathcal{H}\delta^{n} \int_{\gamma_k} 
+  \frac{\xx - \yy}{\|\xx - \yy\|^{m+2}} 
   \left(\delta^{m-n} - \|\xx - \yy\|^{m-n} \right) ds_\yy.
@@
   \int_{\gamma_2}\nabla \phi(\|\xx_1 - \xx_2\|)ds_{\xx_2} = 
-  -4 H \delta^2 \int_{\gamma_2}
+  -4 \mathcal{H} \delta^2 \int_{\gamma_2}
   \frac{\xx_1 - \xx_2}{\|\xx_1 - \xx_2\|^6} 

### 2019-02-05 vesicle_code/docs/adhesion/adhesion.tex
added two-dimensional to intro

@@
 Boundary integral equation (BIE) approaches are well-suited for solving
-the low Reynodls flow problems considered here as they lead to reduction
+the low Reynolds flow problems considered here as they lead to reduction
 in dimensionality and achieve high-order accuracy even for moving
@@
 This paper is organized as follows. In Section~\ref{sec:ge} we formulate
-our model for vesicle hydrodynamics with adhesive interactions between
-membranes of distinct vesicles.  We simulate the adhesion process of two
-vesicles in a quiescent flow in Section~\ref{sec:qflow}, where we also
-present a simple model to estimate how long it takes for two nearby
-vesicles to reach an equilibrium configuration under adhesion. In
-Section~\ref{sec:eflow} we numerically investigate the hydrodynamics of
-a vesicle doublet in a fluid trap where the stagnation point is actively
-controlled to be at the center of the vesicle doublet. From these
-results we propose a novel application of the microfluidic fluid trap to
-probe the adhesion strength between lipid bilayer membranes in
-solutions. In Section~\ref{sec:sflow} we investigate how two vesicles
-may form a doublet as they move toward each other under a planar shear
-flow.  We map out the parameter regions for bound/unbound vesicles under
-a planar shear flow, and we also investigate the effects of adhesive
-interactions on the rheological properties of a dilute suspension of
-vesicle doublets.  Finally in Section~\ref{sec:conclusions} we discuss
-the implications of our results and point out a few potential future
+our model for two-dimensional vesicle hydrodynamics with adhesive
+interactions between membranes of distinct vesicles.  We simulate the
+adhesion process of two vesicles in a quiescent flow in
+Section~\ref{sec:qflow}, where we also present a simple model to
+estimate how long it takes for two nearby vesicles to reach an
+equilibrium configuration under adhesion. In Section~\ref{sec:eflow} we
+numerically investigate the hydrodynamics of a vesicle doublet in a
+fluid trap where the stagnation point is actively controlled to be at
+the center of the vesicle doublet. From these results we propose a novel
+application of the microfluidic fluid trap to probe the adhesion
+strength between lipid bilayer membranes in solutions. In
+Section~\ref{sec:sflow} we investigate how two vesicles may form a
+doublet as they move toward each other under a planar shear flow.  We
+map out the parameter regions for bound/unbound vesicles under a planar
+shear flow, and we also investigate the effects of adhesive interactions
+on the rheological properties of a dilute suspension of vesicle
+doublets.  Finally in Section~\ref{sec:conclusions} we discuss the
+implications of our results and point out a few potential future
 directions.

### 2019-02-05 vesicle_code/docs/adhesion/adhesion.tex
worked on extensional example

@@
 %
-In a planar shear flow, numerical simulations reveal that a vesicle doublet may form as they approach each other in a planar shear flow provided that the adhesion
-strength is sufficient large at a given vesicle reduced area. Once a doublet the effective shear viscosity of a dilute suspension of vesicle doublets is found 
-to be a function of both reduced area and the adhesion strength.
-Results from these numerical studies and analysis shed light on the hydrodynamic effects of adhesive interactions between vesicles in a viscous fluid.
+In a planar shear flow, numerical simulations reveal that a vesicle
+doublet may form as they approach each other in a planar shear flow
+provided that the adhesion strength is sufficient large at a given
+vesicle reduced area. Once a doublet the effective shear viscosity of a
+dilute suspension of vesicle doublets is found to be a function of both
+reduced area and the adhesion strength.  Results from these numerical
+studies and analysis shed light on the hydrodynamic effects of adhesive
+interactions between vesicles in a viscous fluid.
 %\begin{description}
@@
 The hydrodynamics of a single vesicle in an extensional flow has
-revealed novel nonlinear vesicle dynamics not found for a viscous drop
-\cite{KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
+revealed novel nonlinear vesicle dynamics not found for a viscous
+drop~\cite{KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
 Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  The stagnation
@@
 particle can be trapped at the stagnation point for long time scales to
-facilitate image acquisition or other detailed measures such as PIV of
-flow inside and around the particle.  To explore the application of such
-a fluid trap to measure the adhesion strength between two bound vesicle
-membranes, we propose the following thought experiment.
-
-We begin from two vesicles forming a doublet under an adhesion potential
-in a quiescent flow as described in Section~\ref{sec:qflow}.  Once a
-doublet forms and reaches an equilibrium configuration, we turn on the
-fluid trap with the stagnation point placed at the center of the vesicle
-doublet.  For simplification we assume that each vesicle in the doublet
-has the same reduced area, membrane area, and bending stiffness.  At low
-extensional rate, $\chi$, we expect the vesicle doublet to stay fixed at
-the fluid trap stagnation point.  On the other hand, the vesicle doublet
-may become unstable and eventually separate at higher extensional rates.
+facilitate image acquisition or other detailed measures such as particle
+image velocimetry of flow inside and around the particle.  To explore
+the application of such a fluid trap to measure the adhesion strength
+between two bound vesicle membranes, we propose the following thought
+experiment.
+
+We begin with two vesicles identical vesicles forming a doublet under an
+adhesion potential in a quiescent flow as described in
+Section~\ref{sec:qflow}.  Once a doublet forms and reaches an
+equilibrium configuration, we turn on the fluid trap with the stagnation
+point placed at the center of the vesicle doublet.  At low extensional
+rates, $\chi$, we expect the vesicle doublet to stay fixed at the fluid
+trap stagnation point.  On the other hand, the vesicle doublet may
+become unstable and eventually separate at higher extensional rates.
 Thus we expect there to exist a critical extensional rate above which
 the vesicle doublet cannot stay bound under a given adhesion potential.
-The dependence of the critical extensional rate on the adhesion
-potential and the mechanical vesicle properties thus provides a means to
-probe the physics of membrane adhesion.
+Therefore, the dependence of the critical extensional rate on the
+adhesion potential and the mechanical vesicle properties provides a
+means to probe the physics of membrane adhesion.
 
 \begin{figure}[htp]
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}
-  \caption{\label{fig:extensional1} Two vesicles in an extensional flow.
-  The reduced area is $A = 0.7$, the Hamaker constant is $\mathcal{H} =
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}
+  \caption{\label{fig:extensional1} A doublet inside a fluid trap.  The
+  reduced area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} =
   0.7$, the adhesion length scale is $\delta = 0.4$, and the extensional
@@
   black square, is a stagnation point.}
-\end{figure}
-
-\begin{figure}[htp]
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
-  \caption{\label{fig:extensional2} Two vesicles in an extensional flow.
-  The reduced area is $A = 0.7$, the Hamaker constant is $\mathcal{H} =
-  0.7$, the adhesion length scale is $\delta = 0.4$, and the extensional
-  rate is $\chi = 0.07$.  The center of the vesicle, denoted with a
-  black square, is a stagnation point.}
-\end{figure}
-
-\begin{figure}[htp]
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
+
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
+  \caption{\label{fig:extensional2} A doublet inside a fluid trap.  The
+  reduced area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H}
+  = 0.7$, the adhesion length scale is $\delta = 0.4$, and the
+  extensional rate is $\chi = 0.07$.  The center of the vesicle, denoted
+  with a black square, is a stagnation point.}
+
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
   \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
-  The reduced area is $A = 0.7$, the Hamaker constant is $\mathcal{H} =
+  The reduced area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} =
   0.7$, the adhesion length scale is $\delta = 0.4$, and the extensional
@@
   square, is a stagnation point.}
+
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
+  \caption{\label{fig:extensional4} A doublet broken by an extensional
+  flow.  The reduced area is $\Delta A = 0.8$, the Hamaker constant is
+  $\mathcal{H} = 0.7$, the adhesion length scale is $\delta = 0.4$, and
+  the extensional rate is $\chi = 0.1$.  Initially, the doublet tilts to
+  an inclination angle, and then the extensional rate overcomes the
+  adhesive force and the doublet is broken.  The center of the vesicle,
+  denoted with a black square, is a stagnation point.}
 \end{figure}
 
-\begin{figure}[htp]
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
-  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
-  \caption{\label{fig:extensional4} Two vesicles in an extensional flow.
-  The reduced area is $A = 0.8$, the Hamaker constant is $\mathcal{H} =
-  0.7$, the adhesion length scale is $\delta = 0.4$, and the extensional
-  rate is $\chi = 0.1$.  Initially, the doublet tilts to an inclination
-  angle, and then the extensional rate overcomes the adhesive force and
-  the doublet is broken.  The center of the vesicle, denoted with a
-  black square, is a stagnation point.}
-\end{figure}
-
-We consider six pairs of vesicles with reduced areas 0.70, 0.75, 0.80,
-0.85, 0.90, and 0.95, and we vary the extensional rate, $\chi$, between
-$10^{-2}$ and $10^{-1}$.  The length of each of the vesicles is fixed,
-and the area is changed to achieve the desired reduced area.  Since the
-stagnation point can be controlled in an experimental
+We consider vesicle doublets with reduced areas 0.70, 0.75, 0.80, 0.85,
+0.90, and 0.95, all with a length of $\pi$, and we vary the extensional
+rate, $\chi$, between $10^{-2}$ and $10^{-1}$.  Since the stagnation
+point can be controlled in an experimental
 setting~\cite{Johnson-Chavarria2011_EMJ}, we translate the center of the
@@
 remain as a doublet in the fluid trap centered around the stagnation
-point, or the doublet is broken and the vesicles diverge apart from one
-another.
-
-In Figures~\ref{fig:extensional1}--\ref{fig:extensional3}, snapshots of
-a fluid trap containing a vesicle doublet of reduced area 0.7 are
-simulated at different extensional rates.  While this doublet remains
-trapped around the stagnation point, a doublet with a reduced area of
-0.8 is broken for a sufficiently large extensional rate
+point, or the doublet is broken and the vesicles separate from one
+another.  In Figures~\ref{fig:extensional1}--\ref{fig:extensional3},
+snapshots of a fluid trap containing a vesicle doublet of reduced area
+$\Delta A = 0.7$ are simulated at different extensional rates.  While
+this doublet remains trapped around the stagnation point for all the
+considered extensional rates, a doublet with a reduced area of $\Delta A
+= 0.8$ is broken with an extensional rate $\chi = 0.1$
 (Figure~\ref{fig:extensional4}).  We summarize the reduced areas and
-extensional rates that that result in a fluid trap in left plot of
+extensional rates that result in a fluid trap in left plot of
 Figure~\ref{fig:extensionalPhaseDiagram}. Parameter values with a blue
-mark result in a fluid trap while the parameter values with a red marks
-result in vesicle separation.  For extensional rates and reduced areas
-that result in a fluid trap, the initial configuration of the vesicles
-have the diverging stream direction parallel to the vesicles' short
-axis.  Since the stable configuration of two vesicles in an extensional
-flow has the converging direction parallel to the vesicles' short axis,
-we expect the vesicles to align themselves with the long axis parallel
-to the diverging direction.  We observe in
+mark result in a fluid trap and parameter values with a red mark result
+in vesicle separation.
+
+For extensional rates and reduced areas that result in a fluid trap, the
+initial configuration of the vesicles have the diverging stream
+direction parallel to the vesicles' short axis.  Since the stable
+configuration of two vesicles in an extensional flow has the converging
+direction parallel to the vesicles' short axis, we expect the vesicles
+to align themselves with the long axis parallel to the diverging
+direction.  We observe in
 Figures~\ref{fig:extensional1}--\ref{fig:extensional3} that the vesicles
@@
 defined in the right plot.  At smaller extensional rates, the vesicles
-comes closer to aligning their long axis with the diverging direction.
-When the doublet is broken at reduced area $0.70$, the extensional rate
-is sufficiently large to align the long axis of the vesicle with the
-diverging direction and then the vesicles separate.  However, for larger
-reduced areas, the separation dynamics is different.  Instead, the
-vesicles tilt to an inclination angle and then separate
-(Figure~\ref{fig:extensional4}).
+come closer to aligning their long axis with the diverging direction.
+When the doublet is broken at reduced area $\Delta A = 0.80$, the
+extensional rate is sufficiently large to align the long axis of the
+vesicle with the diverging direction and then the vesicles separate
+(Figure~\ref{fig:extensional4}).  For very low extensional rates, the
+time horizon is insufficient for the doublet to reach an equilibrium
+state, and these simulations are marked with a square.
 
 \begin{figure}[htp]
-  \begin{minipage}{0.63\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
-  \end{minipage}
-  \hfill
-  \begin{minipage}{0.35\textwidth}
-    \centering
-    \includegraphics[width=0.8\textwidth]{figs/angleDefinition.pdf}
-    \includegraphics[height=0.45\textwidth]{figs/rotate1.pdf}
-    \hfill
-    \includegraphics[height=0.45\textwidth]{figs/rotate2.pdf}
-  \end{minipage}
-  \caption{\label{fig:extensionalPhaseDiagram} {\em Left}: Phase diagram
-  of vesicle hydrodynamics in an extensional flow with a fixed Hamaker
-  constant $\mathcal{H}=0.7$ and adhesion length scale $\delta = 0.4$.
-  For small extensional rates, the doublet structure is not broken (blue
-  marks), while at large extensional rates, the doublet is broken (red
-  marks).  The size of the round blue marks indicate the final
-  inclination angle with the larger dots rotation less ($\theta=\pi$)
-  and the smaller dots rotating more ($\theta = \pi/2$).  A square mark
-  is used for simulations that did not result in an equilibrium
-  inclination angle in the given time horizon.  {\em Right}: The
-  definition of the inclination angle.  An inclination angle of $\pi$
-  indicates a doublet whose long axis is parallel to the converging
-  direction, while an inclination angle of $\pi/2$ indicates a doublet
-  whose short axis is parallel to the converging direction.  The square
-  mark is a stagnation point while the round point is located at the
-  center of the vesicle.}
-\end{figure}
-
-\begin{figure}[htp]
-  \begin{minipage}{0.45\textwidth}
-  \centering
-  \includegraphics[height=0.8\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
+  \begin{minipage}{0.53\textwidth}
+    \includegraphics[width=0.33\textwidth]{figs/angleDefinition.pdf} \:
+    \includegraphics[width=0.34\textwidth]{figs/rotate1.pdf} \:
+    \includegraphics[width=0.26\textwidth]{figs/rotate2.pdf}
   \end{minipage}
@@
   \begin{minipage}{0.45\textwidth}
-    \includegraphics[height=0.8\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
+    \centering
+    \includegraphics[width=0.8\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
   \end{minipage}
+  \caption{\label{fig:extensionalPhaseDiagram} {\em Left}: The
+  definition of the inclination angle.  An inclination angle of $\pi$
+  indicates a doublet whose long axis is parallel to the diverging
+  direction, while an inclination angle of $\pi/2$ indicates a doublet
+  whose short axis is parallel to the diverging direction.  The square
+  mark is a stagnation point and the round point is located at the
+  center of the vesicle. {\em Right}: A phase diagram of the long-time
+  behavior of a fluid trap formed by two adhering vesicles in an
+  extensional flow.  The Hamaker constant is $\mathcal{H}=0.7$ and the
+  adhesion length scale is $\delta = 0.4$.  For small extensional rates,
+  the doublet structure is not broken (blue marks), while at large
+  extensional rates, the doublet is broken (red marks).  The size of the
+  round blue marks indicates the final inclination angle with the larger
+  dots rotating less ($\theta=\pi$) and the smaller dots rotating more
+  ($\theta = \pi/2$).  A square mark is used for simulations that did
+  not result in an equilibrium inclination angle in the given time
+  horizon.}
+\end{figure}
+
+In Figure~\ref{fig:extensionalInclinationAngle}, we plot the inclination
+angle of the doublet as a function of time for four different
+extensional rates (left) and the final inclination angle for all
+doublets that reach an equilibrium state (right).  We observe that not
+only do larger smaller extensional rates result in smaller inclination
+angles, but smaller reduced areas also result in smaller inclination
+angles.  Moreover, the critical Hamaker constant that determines if the
+doublet remains trapped or is broken decreases with an increasing
+extensional rate.
+
+\begin{figure}[htp]
+  \includegraphics[height=0.35\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
+  \includegraphics[height=0.35\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
   \caption{\label{fig:extensionalInclinationAngle} {\em Left}: The
   inclination angle of a doublet formed by vesicles of reduced area
-  $0.70$ submerged in an extensional flow with an extensional rate of
-  $\chi$.  {\em Right}: The final inclination angle of doublets.
-  Results are not reported for all the low extensional rates since the
-  doublet had not tilted to an equilibrium inclination angle for the
+  $\Delta A = 0.7$ submerged in an extensional flow with an extensional
+  rate of $\chi$.  {\em Right}: The final inclination angle of doublets.
+  At larger extensional rates, the doublet is broken by the flow.
+  Results are not reported for some of the low extensional rates since
+  the doublet had not tilted to an equilibrium inclination angle for the
   given time horizon.}
@@
 
-For very low extensional rates, the time horizon is insufficient for the
-doublet to reach an equilibrium state, and these simulations are marked
-with a square.  In Figure~\ref{fig:extensionalInclinationAngle}, we plot
-the inclination angle as a function of time for four different
-extensional rates (left) and the final inclination angle for all
-doublets that reach a equilibrium state (right).  We observe that not
-only do larger smaller extensional rates result in smaller inclination
-angles, but smaller reduced areas also result in smaller inclination
-angles.
-
-We further characterize the rotating dynamics of a doublet by examining
-the vorticity and total force on the vesicles.  In
-Figure~\ref{fig:extensionalVorticity} ...
-
+Finally, to further characterize the rotating dynamics of a doublet, we
+compute and plot the vorticity and total force on the vesicles in
+Figure~\ref{fig:extensionalVorticity}. We consider the doublet formed
+with a two vesicles of reduced area $\Delta A = 0.7$, adhesion length
+scale $\delta = 0.4$, Hamaker constant $\mathcal{H} = 0.7$, and
+extensional rate $\chi = 0.7$.  The doublet's inclination angle remains
+close to $\pi$ for a period of time (see the left plot of
+Figure~\ref{fig:extensionalInclinationAngle}).  Then, as the doublet
+starts to rotate, the total force first points in the direction of the
+diverging direction and then rotates until it is parallel with the
+vesicles' long axis.  This results in a shearing motion between the
+vesicles that results in a recoil type motion near $t=295$.  Finally,
+the vorticity and the flow between the vesicles approaches zero and the
+result is a fluid trap containing the doublet.
 \begin{figure}[htp]
@@
   \caption{\label{fig:extensionalVorticity} The vorticity and total
-  force of two vesicles in a doublet.  The reduced area is $A = 0.7$,
+  force of two vesicles in a doublet.  The reduced area is $\Delta A = 0.7$,
   the extensional rate is $\chi = 0.7$, the adhesion length scale is
-  $\delta = 0.4$, and the Hamaker constant is $\mathcal{H} = 0.7$.  When
-  the doublet first starts to rotate, the net total force points in the
-  direction of the diverging direction.  Next, there is a shearing
-  motion between the vesicles that results in a recoil type motion near
-  $t=295$.  Finally, the vorticity and the flow between the vesicles
-  approaches zero and the result is a fluid trap containing the
-  doublet.}
+  $\delta = 0.4$, and the Hamaker constant is $\mathcal{H} = 0.7$.}
 \end{figure}
@@
   \caption{\label{fig:doublet090} The formation of a doublet in a shear
-  flow.  The reduced area is $0.90$, the Hamaker constant is
-  $\mathcal{H}=0.7$,
-  the adhesion length scale is $\delta = 0.4$, and the shear rate is
-  $\chi=0.5$.}
+  flow.  The reduced area is $\Delta A = 0.90$, the Hamaker constant is
+  $\mathcal{H}=0.7$, the adhesion length scale is $\delta = 0.4$, and
+  the shear rate is $\chi=0.5$.}
 \end{figure}
@@
   $\delta = 0.4$.   The different lines correspond to a linear spacing
-  of adhesion strengths ranging from $\mathcal{H}=0.1$ and $\mathcal{H}=1.0$.  {\em Right}:
-  Phase diagram of vesicle hydrodynamics in a shear flow.  At a fixed
-  reduced area $\triangle A=0.90$ and $\delta =0.4$,  the critical vdW
-  potential strength $\mathcal{H}$ for binding of two vesicles in a shear flow
-  depends on the shear rate $\chi$.
+  of adhesion strengths ranging from $\mathcal{H}=0.1$ and
+  $\mathcal{H}=1.0$.  {\em Right}: Phase diagram of vesicle
+  hydrodynamics in a shear flow.  At a fixed reduced area $\Delta
+  A=0.90$ and $\delta =0.4$,  the critical vdW potential strength
+  $\mathcal{H}$ for binding of two vesicles in a shear flow depends on
+  the shear rate $\chi$.
 \label{fig:sflow_phase_diagram}}
@@
 10^{-19}$ $J$, an extensional flow rate of $0.5$ $s^{-1}$ is expected to
-separate a vesicle doublet with reduced area of $0.8$ and a Hamakar
-constant $\mathcal{H}=0.7$, which corresponds to $\sim 1$ $\mu J/m^2$.
-These conditions are quite realizable in micrifulidic experiments, and
-we hope that our simulations might inspire microfluidic experiments.
+separate a vesicle doublet with reduced area of $\Delta A = 0.8$ and a
+Hamakar constant $\mathcal{H}=0.7$, which corresponds to $\sim 1$ $\mu
+J/m^2$.  These conditions are quite realizable in micrifulidic
+experiments, and we hope that our simulations might inspire microfluidic
+experiments.
 

### 2019-02-05 vesicle_code/docs/adhesion/adhesion.tex
worked through shear example

@@
 In the absence of adhesion, once the vesicles are sufficiently close,
-they are deflected to opposite sides of the $y$ axis, and the result is
-that the distance between the vesicles goes to infinity.  However, in
-the presence of adhesion, is it possible that the adhesive force keeps
-the vesicles from separating, resulting in the formation of a {\em
-doublet}~\cite{}.
-
-The formation of the doublet depends on four main parameters: the
-vesicles' reduced area, the adhesion length scale $\delta$, the adhesion
-strength $\mathcal{H}$, and the shear rate $\chi$.
-Figure~\ref{fig:doublet090} shows the configuration of two vesicles that
-have formed a doublet at several instances in time.  In
-Figure~\ref{fig:sflow_phase_diagram} (left), we show the minimum
-distance between the two vesicles as a function of time for various
-adhesion strengths.  The adhesion strength corresponding to the red
-curves is less than a critical strength $\mathcal{H}_c$ for a doublet to
-form.  In contrast, for larger adhesive strengths, doublets are formed
-(blue curves).
+they are deflected to opposite sides of the $y$ axis, pass one another,
+and separate from one another.  However, in the presence of adhesion,
+the vesicles can form a doublet for certain values of the adhesion
+length scale $\delta$, Hamaker constant $\mathcal{H}$, shear rate
+$\chi$, and reduced area $\Delta A$.  Figure~\ref{fig:doublet090} shows
+snapshots two vesicles that have formed a doublet and the color coding
+is the tension along the vesicle.  The two vesicles are
+identical with reduced area is $\Delta A = 0.9$, the shear rate is $\chi
+= 0.5$, the adhesion length scale is $\delta = 0.4$, and the Hamaker
+constant is $\mathcal{H} = 0.7$.  Similar to the quiescent example, we
+observe that the membrane tension in the contact region is negative in
+the contact region indicating that the membrane is being compressed when
+the adhesive force is strongest.
 
@@
   \caption{\label{fig:doublet090} The formation of a doublet in a shear
-  flow.  The reduced area is $\Delta A = 0.90$, the Hamaker constant is
+  flow.  The reduced area is $\Delta A = 0.9$, the Hamaker constant is
   $\mathcal{H}=0.7$, the adhesion length scale is $\delta = 0.4$, and
@@
 
+We characterize the effect of the Hamaker constant and shear rate by
+determining a critical Hamaker constant, $\mathcal{H}_c$, which
+determines if the vesicles form a doublet or separate.  We fix the
+adhesion length scale to $\delta = 0.4$ and the vesicle reduced area to
+$\Delta A = 0.9$.  In the left plot of
+Figure~\ref{fig:sflow_phase_diagram}, we plot the minimum distance
+between the vesicles as a function of time for various Hamaker
+constants.  The red curves correspond to Hamaker constants that are too
+small to bind the vesicles into a doublet, and the blue curves
+correspond to Hamaker constants that are sufficiently large to form a
+doublet.
+
 \begin{figure}
-  \includegraphics[height=0.4\textwidth]{figs/shear_adR4em1Chi1e0_ra-090.pdf}
-  \includegraphics[height=0.4\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
+  \includegraphics[height=0.35\textwidth]{figs/shear_adR4em1Chi1e0_ra-090.pdf}
+  \includegraphics[height=0.35\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
   \caption{{\em Left}: Distance between a pair of vesicles in a planar
@@
   hydrodynamics in a shear flow.  At a fixed reduced area $\Delta
-  A=0.90$ and $\delta =0.4$,  the critical vdW potential strength
+  A=0.90$ and $\delta = 0.4$,  the critical Hamaker constant
   $\mathcal{H}$ for binding of two vesicles in a shear flow depends on
@@
 
-We investigate rheology of suspensions by computing the effective
-viscosity of a doublet and compare it to the effective viscosity of a
-single tank-treading vesicle. The effective viscosity is defined as the
-viscosity of a homogeneous Newtonian fluid with the same energy
-dissipation per macroscopic element of fluid.  In a simple shear flow,
-the ambient velocity field is given by $\uu(\xx) = \chi(y,0)$, where
-$\chi$ is the shear rate, and the intrinsic viscosity is
+Finally, we investigate the rheology of a suspension of a doublet by
+computing the effective viscosity of a doublet and compare it to the
+effective viscosity of a single tank-treading vesicle. The effective
+viscosity is defined as the viscosity of a homogeneous Newtonian fluid
+with the same energy dissipation per macroscopic element of fluid.  In a
+simple shear flow, the intrinsic viscosity, $[\mu]$ is
 \begin{align*}
@@
   \langle \tau \rangle = \frac{1}{|\omega|} \int_{\gamma}
-    \xxi \otimes \xx ds.
-\end{align*}
-Here, $[\mu]$ is the intrinsic viscosity, $\phi$ is the area fraction of
-vesicles, $/tau$ is the stress due to the vesicles, and $\langle \cdot
-\rangle$ is the spatial average.
+    \xxi \otimes \xx ds,
+\end{align*}
+where $\phi$ is the area fraction of vesicles, $/tau$ is the stress due
+to the vesicles, and $\langle \cdot \rangle$ is the spatial average.
 
@@
 vesicle (dashed curve) to demonstrate that the bending and tension of
-the doublet behaves similarly, but not identically, to a dilute
+the doublet behave similarly, but not identically, to a dilute
 suspensions of non-adhering tank-treading vesicles.  We see that the
@@
   viscosity of a tank treading vesicle (blue) and a doublet (red).  The
-  shear rate is $\chi = 0.5$, the Hamaker constant is $\mathcal{H} = 0.7$,
-  and the adhesion length scale is $\delta = 0.4$.  The length of the
-  vesicles at each of the reduced areas is fixed, while the area changes
-  with differing reduced areas.  The black marks denote intrinsic
-  viscosity values computed by Ghigliotti et
-  al.~\cite{GhigliottiBibenMisbah2010_JFM} (cf.~Figure 5).  {\em Right}:
-  The decomposition of the intrinsic viscosity into the contributions
-  for the bending and tension (blue) of the vesicles, and the
-  contribution from the vesicle adhesion (red).  Also included is twice
-  the intrinsic viscosity of a single tank-treading vesicle.}
+  shear rate is $\chi = 0.5$, the Hamaker constant is $\mathcal{H} =
+  0.7$, and the adhesion length scale is $\delta = 0.4$, and the length
+  of the vesicles are held fixed.  The black marks denote intrinsic
+  viscosity values computed by Ghigliotti {\em et
+  al.}~\cite{GhigliottiBibenMisbah2010_JFM} (cf.~Figure 5).  {\em
+  Right}: The decomposition of the intrinsic viscosity into the
+  contributions for the bending and tension (blue) of the vesicles, and
+  the contribution from the vesicle adhesion (red).  Also included is
+  twice the intrinsic viscosity of a single tank-treading vesicle
+  (dashed black line).}
 \end{figure}

### 2019-02-05 vesicle_code/docs/adhesion/adhesion.tex
read entire paper and made edits/comments through out

@@
 
-The dynamics of weakly adhesive vesicles under various flowing conditions is investigated numerically using a boundary integral formulation with
-adaptive time-marching that facilitates efficient and accurate computations of vesicle hydrodynamics under adhesion. In a quiescent flow, two nearby vesicles 
-move slowly towards each other under the adhesive potential, pushing out fluid in the gap to  
-form a doublet at equilibrium. A lubrication analysis on such draining of the
-thin film gives the dependencies of draining time on adhesion strength and separation distance that are in good agreement with results from
-boundary integral simulations.
-%
-In a microfluid trap where the stagnation of an extensional flow  is placed in the middle of a vesicle doublet through an active control loop,
-novel dynamics of a vesicle doublet is observed.
-Results from boundary integral simulations show that there exists a critical extensional flow rate above which the weak adhesive interaction is overcome by the hydrodynamic diverging stream, thus providing a simple method to measure the adhesion strength between two vesicle membranes.
+The dynamics of weakly adhesive vesicles under various flowing
+conditions is investigated numerically using a high-order
+adaptive-in-time boundary integral equation formulation. In a quiescent
+flow, two vesicles move slowly towards each other under the adhesive
+potential, pushing out fluid in the gap to form a doublet at
+equilibrium. A lubrication analysis on such draining of the thin film
+gives the dependencies of draining time on adhesion strength and
+separation distance that are in good agreement with numerical results.
+%
+In a microfluid trap where the stagnation of an extensional flow is
+placed in the middle of a vesicle doublet through an active control
+loop, novel dynamics of a vesicle doublet are observed. Numerical
+simulations show that there exists a critical extensional flow rate
+above which the weak adhesive interaction is overcome by the
+hydrodynamic diverging stream, thus providing a simple method to measure
+the adhesion strength between two vesicle membranes. 
 %
 In a planar shear flow, numerical simulations reveal that a vesicle
-doublet may form as they approach each other in a planar shear flow
-provided that the adhesion strength is sufficient large at a given
-vesicle reduced area. Once a doublet the effective shear viscosity of a
-dilute suspension of vesicle doublets is found to be a function of both
-reduced area and the adhesion strength.  Results from these numerical
-studies and analysis shed light on the hydrodynamic effects of adhesive
-interactions between vesicles in a viscous fluid.
+doublet may form as they approach each other provided that the adhesion
+strength is sufficient large at a given vesicle reduced area. Once a
+doublet is formed, the effective shear viscosity of a dilute suspension
+of vesicle doublets is found to be a function of both reduced area and
+the adhesion strength.  Results from these numerical studies and
+analysis shed light on the hydrodynamic effects of adhesive interactions
+between vesicles in a viscous fluid.
 %\begin{description}
@@
 viscosity contrast and shear rate. At high viscosity contrast the
-tank-tread (TT) dynamics transitions to tumbling (TB)
+tank-treading dynamics transitions to tumbling 
 dynamics~\cite{Misbah2006_PRL, Vlahovska2007_PRE}, and this leads to a
@@
 experiments~\cite{KantslerSegreSteinberg2008_EPL,
-ZabuskySegreDeschamps2011_PoF}.  Between TT and TB vesicle dynamics, a
-breathing (tremble) mode is also
+ZabuskySegreDeschamps2011_PoF}.  Between tank-treading and tumbling
+vesicle dynamics, a breathing (tremble) mode is also
 observed~\cite{Misbah2006_PRL,KantslerSegreSteinberg2008_PRL,
@@
 the contact region indicating that the membrane is being compressed when
-the adhesive force is strongest.
+the adhesive force is strongest.  Once the vesicles have formed a
+doublet, the vesicles rotate in tandem rather than performing the usual
+tank-treading motion.
 
@@
 In the left plot of Figure~\ref{fig:shearIntrinsicViscosity}, we compare
-the intrinsic viscosity of a single tank treading vesicle to a doublet.
+the intrinsic viscosity of a single tank-treading vesicle to a doublet.
 To validate our simulations, we superimpose (black marks) the intrinsic
-viscosity calculated by Ghigliotti et
-al.~\cite{GhigliottiBibenMisbah2010_JFM}.  The presence of the doublet
+viscosity calculated by Ghigliotti {\em et
+al.}~\cite{GhigliottiBibenMisbah2010_JFM}.  The presence of the doublet
 significantly increases the intrinsic viscosity at all the reduced
@@
 (blue), and the contribution from the adhesion (red).  We also
-superimpose twice the intrinsic viscosity of a single tank treading
+superimpose twice the intrinsic viscosity of a single tank-treading
 vesicle (dashed curve) to demonstrate that the bending and tension of
@@
   \caption{\label{fig:shearIntrinsicViscosity} {\em Left}: The intrinsic
-  viscosity of a tank treading vesicle (blue) and a doublet (red).  The
+  viscosity of a tank-treading vesicle (blue) and a doublet (red).  The
   shear rate is $\chi = 0.5$, the Hamaker constant is $\mathcal{H} =
@@
 time-stepping to simulate hydrodynamics of two vesicles with adhesive
-interactions.  In a quiescent flow,  two vesicles move towards each
-other under a long-range attraction when they are in close vicinity of
-each other.  We use a lubrication theory to estimate the time it takes
-to reach the separation distance, and found the theoretical scaling to
-be in good agreement with numerical results.  Once two membranes are
-within separation distance $\delta$, the adhesive force turns repulsive
-and the membranes flatten to form a contact region.  Our simulations
-show that the membranes in the contact region are actually curved with
-end points at the shortest distance.  Once a vesicle doublet forms, we
-examine the dependence of membrane bending and adhesion energies on
-reduced area, Hamakar constant and separation distance.
+interactions.  In a quiescent flow, two vesicles that are initially
+sufficiently far apart move towards each other under a long-range
+attraction.  We use a lubrication theory to estimate the time required
+to reach the separation distance, and the theoretical scaling is in good
+agreement with numerical results.  Once two membranes are within
+separation distance $\delta$, the adhesive force turns repulsive and the
+membranes flatten to form a contact region.  Our simulations show that
+the membranes in the contact region are actually curved with end points
+at the shortest distance.  Once a vesicle doublet forms, we examine the
+dependence of membrane bending and adhesion energies on the reduced
+area, the Hamaker constant, and the separation distance.
 
@@
 stagnation point of an extensional flow characterized by a extensional
-flow rate.  At low flow rate, we find the doublet to rotate ninety
+flow rate.  At low flow rate, we find the doublet to rotate nearly ninety
 degrees to align with the flow such that the long axis of the doublet is
 along the divergent axis and the convergent stream is pushing the two
-vesicles together. As the flow rate increases the vesicle doublet
-rotates less and we observe tank-treading like motion of both vesicles
-in the doublet.  When the flow rate reaches above the critical value,
-the diverging flow pulls the vesicles apart before the doublet has time
-to rotate to remain intact.  These results indicate that it is possible
-to use the fluid trap to separate a vesicle doublet under adhesion, and
-thus provide a means to probe the adhesion strength between membranes.
-For a pair of $\mu m$-sized vesicles with a bending rigidity of $\sim
-10^{-19}$ $J$, an extensional flow rate of $0.5$ $s^{-1}$ is expected to
-separate a vesicle doublet with reduced area of $\Delta A = 0.8$ and a
-Hamakar constant $\mathcal{H}=0.7$, which corresponds to $\sim 1$ $\mu
-J/m^2$.  These conditions are quite realizable in micrifulidic
-experiments, and we hope that our simulations might inspire microfluidic
-experiments.
+vesicles together. As the flow rate increases, the vesicle doublet
+rotates less, and when the flow rate reaches above the critical value,
+the diverging flow breaks the doublet structure by pulling the vesicles
+apart.  These results indicate that it is possible to use the fluid trap
+to separate a vesicle doublet under adhesion, and thus provide a means
+to probe the adhesion strength between membranes.  For a pair of $\mu
+m$-sized vesicles with a bending rigidity of $\sim 10^{-19}$ $J$, an
+extensional flow rate of $0.5$ $s^{-1}$ is expected to separate a
+vesicle doublet with reduced area of $\Delta A = 0.8$ and a Hamaker
+constant $\mathcal{H}=0.7$, which corresponds to $\sim 1$ $\mu J/m^2$.
+These conditions are quite realizable in microfluidic experiments, and
+we hope that our simulations will inspire microfluidic experiments.
 
@@
 easily and more membranes in the contact region.
+\todo[inline]{I don't understand this last sentence}
 
@@
 Future work includes three dimensional simulations, viscosity contrast,
-confined suspensions, and dense suspensions.
+dense suspensions, and confined suspensions.  In
+Figure~\ref{fig:relaxationManyVes} illustrate snapshots of five vesicles
+suspended inside of a larger vesicle.  There is no imposed flow, so the
+dynamics are governed entirely by the adhesion, bending, and tension
+forces.  In the absence of confinement, we would expect the vesicles to
+align themselves as a rouleaux with the membranes forming a parachute,
+male-female, or S-shape
+configurations~\cite{FlormannAouane2017_SciReports}.  However, because
+of the bounding vesicle and the dense packing, the interior vesicles
+align themselves differently.  In addition, several parts of the
+bounding membrane closely follow the interior membranes in order to
+minimize the adhesion energy.  In
+Figure~\ref{fig:relaxationManyVesAdhesionTension} we plot the tension
+(left) and adhesion (right) of the final equilibrium configuration.
+
+\begin{figure}[htp]
+  \centering
+  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot01.pdf}
+  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot02.pdf}
+  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot03.pdf}
+  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot04.pdf} \\
+  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot05.pdf}
+  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot06.pdf}
+  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot07.pdf}
+  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot08.pdf}
+  \caption{\label{fig:relaxationManyVes} Five vesicles suspended inside
+  a large vesicle.  The background flow is quiescent, the adhesion
+  length scale is $\delta = 0.4$, and the Hamaker constant is
+  $\mathcal{H} = 0.7$.  At the final snapshot, the suspension is near an
+  equilibrium configuration.}
+\end{figure}
 
@@
 \begin{figure}[htp]
-  \centering
-  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot01.pdf}
-  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot02.pdf}
-  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot03.pdf}
-  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot04.pdf} \\
-  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot05.pdf}
-  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot06.pdf}
-  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot07.pdf}
-  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot08.pdf}
-  \caption{\label{figs:relaxationManyVes} Five vesicles suspended inside
-  a large vesicle.  The background flow is quiescent, the adhesion
-  length scale is $\delta = 0.4$, and the Hamaker constant is
-  $\mathcal{H} = 0.7$.  At the final snapshot, the suspension is near an
-  equilibrium configuration.}
+\todo[inline]{Figures of tension and adhesion of the final
+configuration}
+\caption{\label{fig:relaxationManyVesAdhesionTension} Something smart to
+say ....}
 \end{figure}

### 2019-02-06 vesicle_code/docs/adhesion/adhesion.tex
figures changed by yny

--- 2019-02-05 vesicle_code/docs/adhesion/adhesion.tex
@@
   Equilibrium shapes of two vesicles under adhesive interactions with
-  adhesion strength $\mathcal{H}=0.5$ and separation distance
+  adhesion strength $\mathcal{H}=5$ and separation distance
   $\delta=0.2$.  Vesicle reduced area $\Delta A=0.95$, $0.75$, and $0.6$

### 2019-02-06 vesicle_code/docs/adhesion/adhesion.tex
changes from yny

@@
 
-The dynamics of weakly adhesive vesicles under various flowing
+The dynamics of adhesive vesicles under various flowing
 conditions is investigated numerically using a high-order
 adaptive-in-time boundary integral equation formulation. In a quiescent
-flow, two vesicles move slowly towards each other under the adhesive
+flow, two nearby vesicles move slowly towards each other under the adhesive
 potential, pushing out fluid in the gap to form a doublet at
@@
 widely utilized as biological cell mimics in biophysics and material
-engineering \cite{sackmann1996}.  The ever expanding applications have
+engineering \cite{sackmann1996,Barthes-Biesel2016_ARFM}.  The ever expanding applications have
 encouraged detailed experimental, theoretical, and numerical
@@
 by direct numerical simulations~\cite{GhigliottiBibenMisbah2010_JFM} and
-experiments~\cite{KantslerSegreSteinberg2008_EPL,
+experiments~\cite{DeschampsKantsler2009_PNAS,KantslerSegreSteinberg2008_EPL,
 ZabuskySegreDeschamps2011_PoF}.  Between tank-treading and tumbling
@@
 \subsection{Adhesion Model}
-The adhesion model of Sukumaran and Seifert~\cite{suk-sei2001} considers
+Sukumaran and Seifert~\cite{suk-sei2001} considers
 adhesion between a single three-dimensional vesicle and a solid wall at
@@
   \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
-  \caption{\label{fig:Dec18_vesicle_shape} Two vesicles of length $\pi$
-  with $\kappa=1$, $\mathcal{H}=5$, and $\delta=0.2$.  {\em Left}:
+  \caption{\label{fig:Dec18_vesicle_shape} Two vesicles of the same length, reduced area
+  and bending rigidity ($\kappa=1$)
+  with $\mathcal{H}=5$, and $\delta=0.2$.  {\em Left}:
   Equilibrium shapes of two vesicles under adhesive interactions with
@@
 \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_EbEadh_vs_rA_adR0p2_adS502.jpeg}
-  \caption{\label{fig:Dec18_vesicle_equilibrium1} Two vesicles of length
-  $\pi$ with $\kappa=1$, $\mathcal{H}=5$ and $\delta=0.2$.  {\em Left}:
+  \caption{\label{fig:Dec18_vesicle_equilibrium1} Two vesicles of the same length, reduced area
+  and bending rigidity ($\kappa=1$)  with $\mathcal{H}=5$ and $\delta=0.2$.  {\em Left}:
   Total bending energy (solid curve) and adhesion energy (dash-dotted
@@
 attraction.  We use a lubrication theory to estimate the time required
-to reach the separation distance, and the theoretical scaling is in good
+to reach the separation distance $\delta$, and the theoretical scaling is in good
 agreement with numerical results.  Once two membranes are within
@@
 the diverging flow breaks the doublet structure by pulling the vesicles
-apart.  These results indicate that it is possible to use the fluid trap
+apart.  These results indicate that it is possib le to use the fluid trap
 to separate a vesicle doublet under adhesion, and thus provide a means
@@
 dynamically. The usual tank-treading motion of a vesicle under shear
-flow is not observed in each of the two vesicles. We also compute the
+flow is not observed in each of the two vesicles. We compute the
 effective shear viscosity of a dilute suspension of vesicle doublets,
-and found that membrane adhesion contribution increases with decreasing
-reduced area because deflated vesicles (low reduced area) deform more
-easily and more membranes in the contact region.
-\todo[inline]{I don't understand this last sentence}
+and found it to be more than twice the effective shear viscosity of a dilute suspension of single vesicles.
+Furthermore, we find that the membrane adhesion contribution to the shear viscosity increases with decreasing
+reduced area while the bending/tension contribution increases with the reduced area.
+%
+%because deflated vesicles (low reduced area) deform more
+%easily and more membranes in the contact region.
+\todo[inline]{I don't understand this last sentence --> modified now by yny}
 
@@
 Future work includes three dimensional simulations, viscosity contrast,
-dense suspensions, and confined suspensions.  In
+dense suspensions, and confined suspensions. 
 Figure~\ref{fig:relaxationManyVes} illustrate snapshots of five vesicles

### 2019-02-06 vesicle_code/docs/adhesion/adhesion.tex
removed todo comments

@@
 widely utilized as biological cell mimics in biophysics and material
-engineering \cite{sackmann1996,Barthes-Biesel2016_ARFM}.  The ever expanding applications have
-encouraged detailed experimental, theoretical, and numerical
-investigations of vesicle hydrodynamics in applied flow, electric
-fields, and magnetic fields.  Theoretical investigations often take the
-form of small-deformation analysis or spheroidal dynamics of a
-nearly-spherical vesicle (or nearly-circular in two dimensions)
-subjected to an applied flow or under an external
+engineering~\cite{sackmann1996, Barthes-Biesel2016_ARFM}.  The ever
+expanding applications have encouraged detailed experimental,
+theoretical, and numerical investigations of vesicle hydrodynamics in
+applied flow, electric fields, and magnetic fields.  Theoretical
+investigations often take the form of small-deformation analysis or
+spheroidal dynamics of a nearly-spherical vesicle (or nearly-circular in
+two dimensions) subjected to an applied flow or under an external
 forcing~\cite{Barthes-BieselRallison1981_JFM, Misbah2006_PRL,
@@
 by direct numerical simulations~\cite{GhigliottiBibenMisbah2010_JFM} and
-experiments~\cite{DeschampsKantsler2009_PNAS,KantslerSegreSteinberg2008_EPL,
-ZabuskySegreDeschamps2011_PoF}.  Between tank-treading and tumbling
-vesicle dynamics, a breathing (tremble) mode is also
-observed~\cite{Misbah2006_PRL,KantslerSegreSteinberg2008_PRL,
+experiments~\cite{DeschampsKantsler2009_PNAS,
+KantslerSegreSteinberg2008_EPL, ZabuskySegreDeschamps2011_PoF}.  Between
+tank-treading and tumbling vesicle dynamics, a breathing (tremble) mode
+is also observed~\cite{Misbah2006_PRL, KantslerSegreSteinberg2008_PRL,
 ZhaoShaqfeh2011_JFM, SpannZhaoShaqfeh2014_PoF} to affect the effective
@@
 the formation of vesicle doublets~\cite{Ziherl2007_PRL,
-ZiherlSvetina2007_PNAS} or clusters
-\cite{SvetinaZiherl2008_Bioelectrochemistry,
+ZiherlSvetina2007_PNAS} or
+clusters~\cite{SvetinaZiherl2008_Bioelectrochemistry,
 FlormannAouane2017_SciReports}.  As a model for red blood cell (RBC)
@@
   reached within $1\%$.}
-  \todo[inline]{Change the $H$ in the right figure to $\mathcal{H}$}
 \end{figure}
@@
   are labeled.  The color coding is the tension along the vesicle. {\em
-  Right}: Membrane shapes in the contact region.} \todo[inline]{This
-  caption contradicts itself.  Is it $\mathcal{H} = 0.5$ or $\mathcal{H}
-  = 5$?}
+  Right}: Membrane shapes in the contact region.}
 \end{figure}
@@
   $0.4$ (circles).}
-  \todo[inline]{Change $H$ to $\mathcal{H}$ in the x-axis.}
 \end{figure}
@@
 effective shear viscosity of a dilute suspension of vesicle doublets,
-and found it to be more than twice the effective shear viscosity of a dilute suspension of single vesicles.
-Furthermore, we find that the membrane adhesion contribution to the shear viscosity increases with decreasing
-reduced area while the bending/tension contribution increases with the reduced area.
-%
-%because deflated vesicles (low reduced area) deform more
-%easily and more membranes in the contact region.
-\todo[inline]{I don't understand this last sentence --> modified now by yny}
+and found it to be more than twice the effective shear viscosity of a
+dilute suspension of single vesicles.  Furthermore, we find that the
+membrane adhesion contribution to the shear viscosity increases with
+decreasing reduced area while the bending/tension contribution increases
+with the reduced area.
 

### 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex
some minor changes from yny

--- 2019-02-06 vesicle_code/docs/adhesion/adhesion.tex
@@
 flow, two nearby vesicles move slowly towards each other under the adhesive
-potential, pushing out fluid in the gap to form a doublet at
+potential, pushing out fluid between them to form a doublet at
 equilibrium. A lubrication analysis on such draining of the thin film
@@
 simulations show that there exists a critical extensional flow rate
-above which the weak adhesive interaction is overcome by the
+above which adhesive interaction is overcome by the
 hydrodynamic diverging stream, thus providing a simple method to measure
@@
 engineering \cite{sackmann1996,Barthes-Biesel2016_ARFM}.  The ever expanding applications have
-encouraged detailed experimental, theoretical, and numerical
+encouraged novel experimental, theoretical, and numerical
 investigations of vesicle hydrodynamics in applied flow, electric
@@
 aggregates~\cite{SvetinaZiherl2008_Bioelectrochemistry,
-FlormannAouane2017_SciReports}.  Using the Lennard-Jones (L-J) potential
+FlormannAouane2017_SciReports}.  Using the Lennard-Jones (L.-J.) potential
 for point-point interaction between two vesicle membranes without the
@@
 ions in the solvents, it is reported that the adhesive interactions
-between two membranes can be well approximated by the L-J-type
+between two membranes can be well approximated by the L.-J.-type
 potential~\cite{FlormannAouane2017_SciReports}, that consists of a
@@
 adhesion process of two vesicles in a quiescent flow in
-Section~\ref{sec:qflow}, where we also present a simple model to
-estimate how long it takes for two nearby vesicles to reach an
-equilibrium configuration under adhesion. In Section~\ref{sec:eflow} we
+Section~\ref{sec:qflow}, where we also present a simple lubrication model to
+estimate how long it takes for two nearby vesicles to reach the
+separation distance set by the adhesion potential.
+In Section~\ref{sec:eflow} we
 numerically investigate the hydrodynamics of a vesicle doublet in a
@@
 \xx_{ssss}$ comes from the Helfrich energy, where $\kappa_b$ is the
-bending modulus and $s$ is arclength.  For the numerical examples, we
+bending rigidity modulus and $s$ is arclength.  For the numerical examples, we
 set $\kappa_b = 1$ and consider adhesion strengths ranging from $0.1$ to
-$1$ times the bending modulus.  The stretching term is $\TT \sigma  =
+$1$ times the bending rigidity modulus.  The stretching term is $\TT \sigma  =
 (\sigma \xx_s)_s$, where $\sigma$ is the tension, and the tension acts
@@
 long-range attraction and a short-range repulsion. On the other hand,
-$(m,n) = (12,6)$ corresponds to the L-J potential between two molecules.
+$(m,n) = (12,6)$ corresponds to the L.-J. potential between two molecules.
 In our case, the adhesion potential in the integral of
@@
 attraction pulls two vesicles together until their separation distance
-is close to $\delta$.  In Section~\ref{subsec:qflow_draining_times}, we
+is close to $\delta$ and large deformation occurs in the ``contact region". The L.-J. type potential prohibits
+physical contact between two membranes and instead keep them close to the separation distance $\delta$.
+In Section~\ref{subsec:qflow_draining_times}, we
 compute the expected time for the vesicles to reach an equilibrium
@@
   reached within $1\%$.}
-  \todo[inline]{Change the $H$ in the right figure to $\mathcal{H}$}
+%  \todo[inline]{Change the $H$ in the right figure to $\mathcal{H}$}
 \end{figure}
@@
   \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
-  \caption{\label{fig:Dec18_vesicle_shape} Two vesicles of the same length, reduced area
-  and bending rigidity ($\kappa=1$)
-  with $\mathcal{H}=5$, and $\delta=0.2$.  {\em Left}:
-  Equilibrium shapes of two vesicles under adhesive interactions with
-  adhesion strength $\mathcal{H}=5$ and separation distance
-  $\delta=0.2$.  Vesicle reduced area $\Delta A=0.95$, $0.75$, and $0.6$
-  are labeled.  The color coding is the tension along the vesicle. {\em
-  Right}: Membrane shapes in the contact region.} \todo[inline]{This
-  caption contradicts itself.  Is it $\mathcal{H} = 0.5$ or $\mathcal{H}
-  = 5$?}
+  \caption{\label{fig:Dec18_vesicle_shape} Equilibrium configuration of a doublet of 
+  identical vesicles under adhesion in a quiescent flow. Vesicle reduced area $\Delta A=0.95$, $0.75$, and $0.6$
+  are labeled.  The color coding is the tension along the vesicle. 
+  Vesicle length is fixed at $2\pi$, (dimensionless) bending rigidity modulus $\kappa=1$, $\mathcal{H}=5$, and $\delta=0.2$.
+  {\em Left}: Overall
+  equilibrium shapes of two vesicles under adhesive interactions vary with reduced area.  
+  {\em Right}: Membrane shapes in the contact region.} 
+%  \todo[inline]{This
+%  caption contradicts itself.  Is it $\mathcal{H} = 0.5$ or $\mathcal{H}
+%  = 5$?}
 \end{figure}
@@
 This is consistent with the equilibrium shapes of a vesicle doublet
-under a L-J potential ($(m,n) =
+under a L.-J. potential ($(m,n) =
 (12,6)$)~\cite{FlormannAouane2017_SciReports}.  As the reduced area
-decreases further, we observe undulation of the elongated equilibrium
-vesicle shape on the non-contact side while the contact region remains
+decreases further, we observe undulation of the 
+vesicle membrane on the non-contact side while the contact region remains
 flat.  The color coding along each curve is the tension of the vesicle
@@
 \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_EbEadh_vs_rA_adR0p2_adS502.jpeg}
-  \caption{\label{fig:Dec18_vesicle_equilibrium1} Two vesicles of the same length, reduced area
-  and bending rigidity ($\kappa=1$)  with $\mathcal{H}=5$ and $\delta=0.2$.  {\em Left}:
+  \caption{\label{fig:Dec18_vesicle_equilibrium1}   {\em Left}:
   Total bending energy (solid curve) and adhesion energy (dash-dotted
   curve) plotted against the reduced area $\Delta A$. {\em Right}: Sum
-  of two energies plotted against reduced area $\Delta A$.}
+  of two energies plotted against reduced area $\Delta A$. Two vesicles in the doublet are of the same length, reduced area
+  and bending rigidity modulus ($\kappa=1$) with $\mathcal{H}=5$ and $\delta=0.2$.}
 \end{figure}
@@
 \includegraphics[keepaspectratio=true,scale=0.18]{figs/Dec18_Eadh_vs_sigma_rA0p9502.jpeg}
-  \caption{\label{fig:Dec18_equilibrium} Total bending energy (\em left)
-  and adhesion energy {\em right} versus the adhesion strength
-  $\mathcal{H}$ for two vesicles with reduced area $\Delta A=0.95$,
+  \caption{\label{fig:Dec18_equilibrium} 
+  Total bending energy ({\em left})
+  and adhesion energy ({\em right}) of a vesicle doublet at equilibrium versus the adhesion strength
+  $\mathcal{H}$.  The two vesicles in the doublet have the same length and reduced area $\Delta A=0.95$, with 
   separation distance $\delta = 0.2$ (triangles), $0.3$ (crosses), and
   $0.4$ (circles).}
-  \todo[inline]{Change $H$ to $\mathcal{H}$ in the x-axis.}
+%  \todo[inline]{Change $H$ to $\mathcal{H}$ in the x-axis.}
 \end{figure}
@@
 
-We begin with two vesicles identical vesicles forming a doublet under an
+We begin with two identical vesicles forming a doublet under an
 adhesion potential in a quiescent flow as described in
@@
 %easily and more membranes in the contact region.
-\todo[inline]{I don't understand this last sentence --> modified now by yny}
+%\todo[inline]{I don't understand this last sentence --> modified now by yny}
 

### 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex
small language corrections to intro

@@
 \begin{abstract}
-
-The dynamics of adhesive vesicles under various flowing
-conditions is investigated numerically using a high-order
-adaptive-in-time boundary integral equation formulation. In a quiescent
-flow, two nearby vesicles move slowly towards each other under the adhesive
-potential, pushing out fluid between them to form a doublet at
-equilibrium. A lubrication analysis on such draining of the thin film
-gives the dependencies of draining time on adhesion strength and
-separation distance that are in good agreement with numerical results.
+The dynamics of adhesive vesicles under various flowing conditions is
+investigated numerically using a high-order adaptive-in-time boundary
+integral equation formulation. In a quiescent flow, two nearby vesicles
+move slowly towards each other under the adhesive potential, pushing out
+fluid between them to form a doublet at equilibrium. A lubrication
+analysis on such draining of the thin film gives the dependencies of
+draining time on adhesion strength and separation distance that are in
+good agreement with numerical results.
 %
@@
 simulations show that there exists a critical extensional flow rate
-above which adhesive interaction is overcome by the
-hydrodynamic diverging stream, thus providing a simple method to measure
-the adhesion strength between two vesicle membranes. 
+above which adhesive interaction is overcome by the hydrodynamic
+diverging stream, thus providing a simple method to measure the adhesion
+strength between two vesicle membranes. 
 %
@@
 doublet may form as they approach each other provided that the adhesion
-strength is sufficient large at a given vesicle reduced area. Once a
+strength is sufficiently large at a given vesicle reduced area. Once a
 doublet is formed, the effective shear viscosity of a dilute suspension
@@
 widely utilized as biological cell mimics in biophysics and material
-engineering \cite{sackmann1996,Barthes-Biesel2016_ARFM}.  The ever expanding applications have
-encouraged novel experimental, theoretical, and numerical
-investigations of vesicle hydrodynamics in applied flow, electric
-fields, and magnetic fields.  Theoretical investigations often take the
-form of small-deformation analysis or spheroidal dynamics of a
-nearly-spherical vesicle (or nearly-circular in two dimensions)
-subjected to an applied flow or under an external
+engineering~\cite{sackmann1996, Barthes-Biesel2016_ARFM}.  The ever
+expanding applications have encouraged detailed experimental,
+theoretical, and numerical investigations of vesicle hydrodynamics in
+applied flow, electric fields, and magnetic fields.  Theoretical
+investigations often take the form of small-deformation analysis or
+spheroidal dynamics of a nearly-spherical vesicle (or nearly-circular in
+two dimensions) subjected to an applied flow or under an external
 forcing~\cite{Barthes-BieselRallison1981_JFM, Misbah2006_PRL,
@@
 dynamics~\cite{Misbah2006_PRL, Vlahovska2007_PRE}, and this leads to a
-transition in effective shear viscosity in the vesicle
+transition in effective shear viscosity of the vesicle
 suspension~\cite{Misbah2006_PRL,Vitkova2008_BJ} that is also validated
 by direct numerical simulations~\cite{GhigliottiBibenMisbah2010_JFM} and
-experiments~\cite{DeschampsKantsler2009_PNAS,KantslerSegreSteinberg2008_EPL,
-ZabuskySegreDeschamps2011_PoF}.  Between tank-treading and tumbling
-vesicle dynamics, a breathing (tremble) mode is also
-observed~\cite{Misbah2006_PRL,KantslerSegreSteinberg2008_PRL,
+experiments~\cite{DeschampsKantsler2009_PNAS,
+KantslerSegreSteinberg2008_EPL, ZabuskySegreDeschamps2011_PoF}.  Between
+tank-treading and tumbling vesicle dynamics, a breathing (tremble) mode
+is also observed~\cite{Misbah2006_PRL, KantslerSegreSteinberg2008_PRL,
 ZhaoShaqfeh2011_JFM, SpannZhaoShaqfeh2014_PoF} to affect the effective
@@
 aggregates~\cite{SvetinaZiherl2008_Bioelectrochemistry,
-FlormannAouane2017_SciReports}.  Using the Lennard-Jones (L.-J.) potential
-for point-point interaction between two vesicle membranes without the
-molecular details of adhesive interactions between RBCs, Flormann {\em
-et al.}~found the contact zone to buckle under strong
-adhesion~\cite{FlormannAouane2017_SciReports}.  A direct consequence of
-the buckling is the sigmoidal shape of the adhesion region, which is
-also observed in RBC doublets and explained in a slightly different
-model~\cite{ZiherlSvetina2007_PNAS}.  It remains unknown how adhesive
-interactions between vesicles might lead to different vesicle
-hydrodynamics that results in different rheological properties of a
-vesicle suspension. Such studies will provide useful insight to the
-rheology of blood flow and how to use nano solutes to control the
-hypertension by adjusting the adhesive interactions between RBCs.
+FlormannAouane2017_SciReports}.  Using the Lennard-Jones
+(L.-J.)~potential for point-point interaction between two vesicle
+membranes without the molecular details of adhesive interactions between
+RBCs, Flormann {\em et al.}~found the contact zone to buckle under
+strong adhesion~\cite{FlormannAouane2017_SciReports}.  A direct
+consequence of the buckling is the sigmoidal shape of the adhesion
+region, which is also observed in RBC doublets and explained in a
+slightly different model~\cite{ZiherlSvetina2007_PNAS}.  It remains
+unknown how adhesive interactions between vesicles might lead to
+different vesicle hydrodynamics that results in different rheological
+properties of a vesicle suspension. Such studies will provide useful
+insight to the rheology of blood flow and how to use nano solutes to
+control the hypertension by adjusting the adhesive interactions between
+RBCs.
 
@@
 ignored~\cite{Veerapaneni2009_JCP,  RahimianVeerapaneniBiros2010_JCP}
-for numerical convenience, mostly because a smaller time step is often
+for numerical convenience, mostly because a small time step is often
 needed to resolve the dynamics of the lubrication thin film between two
-membranes with adhesion than without.  However, adhesive interactions
-between RBCs lead to different RBC clusters that are expected to alter
-the rheological properties of the RBC
-suspension~\cite{NeuMeiselman2002_BJ,
+membranes with adhesion.  However, adhesive interactions between RBCs
+lead to different RBC clusters that are expected to alter the
+rheological properties of the RBC suspension~\cite{NeuMeiselman2002_BJ,
 SvetinaZiherl2008_Bioelectrochemistry}. Hydrodynamic simulations of
@@
 \xx_{ssss}$ comes from the Helfrich energy, where $\kappa_b$ is the
-bending rigidity modulus and $s$ is arclength.  For the numerical examples, we
-set $\kappa_b = 1$ and consider adhesion strengths ranging from $0.1$ to
-$1$ times the bending rigidity modulus.  The stretching term is $\TT \sigma  =
-(\sigma \xx_s)_s$, where $\sigma$ is the tension, and the tension acts
-as a Lagrange multiplier to satisfy the local extensibility constraint.
-The resistance to bending and stretching are standard assumptions of
-vesicles.  In this work, we include an adhesive term, $\AA \xx$, that we
-now describe.
+bending rigidity modulus and $s$ is arclength.  For the numerical
+examples, we set $\kappa_b = 1$ and consider adhesion strengths ranging
+from $0.1$ to $1$ times the bending rigidity modulus.  The stretching
+term is $\TT \sigma  = (\sigma \xx_s)_s$, where $\sigma$ is the tension,
+and the tension acts as a Lagrange multiplier to satisfy the local
+extensibility constraint.  The resistance to bending and stretching are
+standard assumptions of vesicles.  In this work, we include an adhesive
+term, $\AA \xx$, that we now describe.
 
@@
   reached within $1\%$.}
-%  \todo[inline]{Change the $H$ in the right figure to $\mathcal{H}$}
 \end{figure}
@@
   \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
-  \caption{\label{fig:Dec18_vesicle_shape} Equilibrium configuration of a doublet of 
-  identical vesicles under adhesion in a quiescent flow. Vesicle reduced area $\Delta A=0.95$, $0.75$, and $0.6$
-  are labeled.  The color coding is the tension along the vesicle. 
-  Vesicle length is fixed at $2\pi$, (dimensionless) bending rigidity modulus $\kappa=1$, $\mathcal{H}=5$, and $\delta=0.2$.
-  {\em Left}: Overall
-  equilibrium shapes of two vesicles under adhesive interactions vary with reduced area.  
-  {\em Right}: Membrane shapes in the contact region.} 
-%  \todo[inline]{This
-%  caption contradicts itself.  Is it $\mathcal{H} = 0.5$ or $\mathcal{H}
-%  = 5$?}
+  \caption{\label{fig:Dec18_vesicle_shape} Equilibrium configuration of
+  a doublet of identical vesicles under adhesion in a quiescent flow.
+  Vesicle reduced area $\Delta A=0.95$, $0.75$, and $0.6$ are labeled.
+  The color coding is the tension along the vesicle.  Vesicle length is
+  fixed at $2\pi$, (dimensionless) bending rigidity modulus $\kappa=1$,
+  $\mathcal{H}=5$, and $\delta=0.2$.  {\em Left}: Overall equilibrium
+  shapes of two vesicles under adhesive interactions vary with reduced
+  area.  {\em Right}: Membrane shapes in the contact region.} 
 \end{figure}
@@
   \caption{\label{fig:Dec18_equilibrium} 
-  Total bending energy ({\em left})
-  and adhesion energy ({\em right}) of a vesicle doublet at equilibrium versus the adhesion strength
-  $\mathcal{H}$.  The two vesicles in the doublet have the same length and reduced area $\Delta A=0.95$, with 
-  separation distance $\delta = 0.2$ (triangles), $0.3$ (crosses), and
-  $0.4$ (circles).}
-%  \todo[inline]{Change $H$ to $\mathcal{H}$ in the x-axis.}
+  Total bending energy ({\em left}) and adhesion energy ({\em right}) of
+  a vesicle doublet at equilibrium versus the adhesion strength
+  $\mathcal{H}$.  The two vesicles in the doublet have the same length
+  and reduced area $\Delta A=0.95$, with separation distance $\delta =
+  0.2$ (triangles), $0.3$ (crosses), and $0.4$ (circles).}
 \end{figure}
@@
 effective shear viscosity of a dilute suspension of vesicle doublets,
-and found it to be more than twice the effective shear viscosity of a dilute suspension of single vesicles.
-Furthermore, we find that the membrane adhesion contribution to the shear viscosity increases with decreasing
-reduced area while the bending/tension contribution increases with the reduced area.
-%
-%because deflated vesicles (low reduced area) deform more
-%easily and more membranes in the contact region.
-%\todo[inline]{I don't understand this last sentence --> modified now by yny}
+and found it to be more than twice the effective shear viscosity of a
+dilute suspension of single vesicles.  Furthermore, we find that the
+membrane adhesion contribution to the shear viscosity increases with
+decreasing reduced area while the bending/tension contribution increases
+with the reduced area.
 
@@
 YNY would like to acknowledge helpful discussions with blah blah blah.
-YNY acknowledges support from NSF-DMS 1614863 and 1412789, and Flatiron Institute, part of the Simons Foundation.
+YNY acknowledges support from NSF-DMS 1614863 and 1412789, and Flatiron
+Institute, part of the Simons Foundation.
 

### 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex
Edited up to end of section II A

@@
 method can be easily adjusted to account for a viscosity contrast.
-Individual vesicles are denoted as $\gamma_j$, and they are
-parameterized in arclength as $\xx_j(s,t)$.  The union of all vesicles
-is denoted by $\gamma$.  Given a background velocity $\uu_\infty$, the
-governing equations are
+Individual vesicles are denoted as $\gamma_j$, $j=1,\ldots,M$, and they
+are parameterized in arclength as $\xx_j(s,t)$.  The union of all
+vesicles is denoted by $\gamma$.  Given a background velocity
+$\uu_\infty$, the governing equations are
 \begin{equation*}
@@
 \end{equation*}
-where $\xxi$ is the traction jump that is the sum of the bending,
-stretching, and adhesion forces.  The bending term $\BB \xx = -\kappa_b
-\xx_{ssss}$ comes from the Helfrich energy, where $\kappa_b$ is the
-bending rigidity modulus and $s$ is arclength.  For the numerical
-examples, we set $\kappa_b = 1$ and consider adhesion strengths ranging
-from $0.1$ to $1$ times the bending rigidity modulus.  The stretching
-term is $\TT \sigma  = (\sigma \xx_s)_s$, where $\sigma$ is the tension,
-and the tension acts as a Lagrange multiplier to satisfy the local
+where $\llbracket T \rrbracket$ is the jump in the stress tensor, and
+$\xxi$ is the traction jump that is the sum of the bending, stretching,
+and adhesion forces.  The bending force, arising from the Helfrich
+energy model, is $\BB \xx = -\kappa_b \xx_{ssss}$, where $\kappa_b$ is
+the bending rigidity modulus which we set to be 1 for all examples. The
+stretching force is $\TT \sigma = (\sigma \xx_s)_s$, where the tension,
+$\sigma$, acts as a Lagrange multiplier to satisfy the local
 extensibility constraint.  The resistance to bending and stretching are
 standard assumptions of vesicles.  In this work, we include an adhesive
-term, $\AA \xx$, that we now describe.
+force, $\AA \xx$, that we now describe.
 
@@
 \subsection{Adhesion Model}
-Sukumaran and Seifert~\cite{suk-sei2001} considers
-adhesion between a single three-dimensional vesicle and a solid wall at
-$z=0$.  They use the adhesion potential of the function form
+Sukumaran and Seifert~\cite{suk-sei2001} consider adhesion between a
+single three-dimensional vesicle and a solid wall at $z=0$.  They use
+the adhesion potential of the function form
 \begin{align}
@@
 $\mathcal{H}$ is the Hamaker constant, $\delta$ is the adhesion length
-scale and $(m,n) = (4,2)$.  We generalize this model to an unbounded
+scale, and $(m,n) = (4,2)$.  We generalize this model to an unbounded
 suspension of vesicles. We assume that the adhesion force applies
@@
 in Hamaker constants that are appropriate for lipid-lipid interactions.
-In Appendix~\ref{sec:appendixA}, the adhesive force at a point $\xx$ on
-vesicle $j$ is shown to be
+We use Hamaker constants ranging from $0.1$ to $1$ times the bending
+rigidity modulus.  In Appendix~\ref{sec:appendixA}, the adhesive force
+at a point $\xx$ on vesicle $j$ is shown to be
 \begin{align}
@@
 long-range attraction and a short-range repulsion. On the other hand,
-$(m,n) = (12,6)$ corresponds to the L.-J. potential between two molecules.
+$(m,n) = (12,6)$ corresponds to the L.-J.~potential between two molecules.
 In our case, the adhesion potential in the integral of
@@
 force as two objects are within the separation distance $\delta$.  This
-poses great challenges for simulations as the problem becomes stiff
-(i.e., requires a very small time step) for large $m$.  The adaptive
+poses a numerical challenge since the problem becomes stiff (i.e.,
+requires a very small time step) for large $m$.  The adaptive
 time-stepping BIE scheme makes it possible to simulate vesicle adhesive
@@
 little difference in both the dynamic evolution and equilibrium
-configuration between $(m,n)=(8,6)$ and $(m,n)=(4,2)$.
+configuration between $(m,n)=(8,6)$ and $(m,n)=(4,2)$.  Therefore, in
+this work, we use $(m,n) = (4,2)$ to regulate the stiffness introduced
+by the adhesive force.
 

### 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex
minor changes by yny

--- 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex
@@
 then diverge in a different direction.  With an active control algorithm
-to fix the position of the stagnation point by adjusting the streaming
+to place the stagnation point at a desirable location by adjusting the streaming
 flow strength with a feedback loop~\cite{Johnson-Chavarria2011_EMJ}, a
@@
 point placed at the center of the vesicle doublet.  At low extensional
-rates, $\chi$, we expect the vesicle doublet to stay fixed at the fluid
+rates, we expect the vesicle doublet to stay at the fluid
 trap stagnation point.  On the other hand, the vesicle doublet may
 become unstable and eventually separate at higher extensional rates.
-Thus we expect there to exist a critical extensional rate above which
+Thus we expect there to exist a critical extensional rate $\chi_c$ above which
 the vesicle doublet cannot stay bound under a given adhesion potential.
-Therefore, the dependence of the critical extensional rate on the
+Therefore, the dependence of the critical extensional rate $\chi_c$ on the
 adhesion potential and the mechanical vesicle properties provides a
@@
 0.90, and 0.95, all with a length of $\pi$, and we vary the extensional
-rate, $\chi$, between $10^{-2}$ and $10^{-1}$.  Since the stagnation
-point can be controlled in an experimental
-setting~\cite{Johnson-Chavarria2011_EMJ}, we translate the center of the
+rate, $\chi$, between $10^{-2}$ and $10^{-1}$.  
+%
+In the simulations we mimic the active control algorithm in the microfluidic experiments by
+moving the center of the
 doublet at each time step so that the stagnation point occurs exactly in
-the middle of the doublet.  With this adjustment, the vesicles either
+the middle of the doublet.  
+%
+With this adjustment, the vesicles either
 remain as a doublet in the fluid trap centered around the stagnation

### 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex
edited up to end of section II

--- 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex
@@
 where $\rr = \xx - \yy$ and $\rho = \|\rr\|$.  Then, given a vesicle
-with a traction jump $\xxi$, the fluid velocity at is~\cite{poz1992}
+with a traction jump $\xxi$, the fluid velocity is~\cite{poz1992}
 \begin{align*}
@@
 where the three terms correspond to the forces due to bending, tension,
-and adhesion, respectively.  Therefore Applying the no-slip boundary
+and adhesion, respectively.  Therefore, applying the no-slip boundary
 condition on each vesicle, the governing equations are
@@
 \end{align*}
-that treats both the bending and tension terms
-semi-implicitly~\cite{qua-bir2014}. Note that the adhesive term is
-treated explicitly.  Therefore, a single time step requires solving
+that discretizes both the bending and tension terms
+semi-implicitly~\cite{qua-bir2014}, and the adhesive term explicitly.
+Therefore, a single time step requires solving
 \begin{align*}
@@
 bending and tension terms with Fourier differentiation, and apply Alpert
-quadrature~\cite{alp1999} to the logarithmically singular single-layer
-potential $\SS$.  The source and target points of the adhesion force
-never coincide since they are always on different vesicles, so the
-adhesion force~\eqref{eqn:adhesionForce} is computed with the spectrally
-accurate trapezoid rule~\cite{tre-wei2014}.
+quadrature~\cite{alp1999} to the weakly-singular single-layer potential
+$\SS$.  The source and target points of the adhesion force never
+coincide since they are always on different vesicles, so the adhesion
+force~\eqref{eqn:adhesionForce} is computed with the spectrally accurate
+trapezoid rule~\cite{tre-wei2014}.
 
@@
 To characterize the rheological properties of the suspension of a
-doublet, it is necessary to compute shear and normal stresses.  At a
-point $\xx$ in the fluid bulk, The velocity $\uu(\xx)$, pressure
-$p(\xx)$, and total stress tensor $T = - p I + \nabla \uu + \nabla
-\uu^T$ of the single-layer potential~\eqref{eqn:SLP} are
+doublet, it is necessary to compute the shear and normal stresses.  At a
+point $\xx \in \RR^2 \backslash \gamma$ in the fluid bulk, the velocity
+$\uu(\xx)$, pressure $p(\xx)$, and total stress tensor $T = - p I +
+\nabla \uu + \nabla \uu^T$ of the single-layer potential~\eqref{eqn:SLP}
+are
 \begin{align*}

### 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex
fixed length of vesicle

@@
 We consider vesicle doublets with reduced areas 0.70, 0.75, 0.80, 0.85,
-0.90, and 0.95, all with a length of $\pi$, and we vary the extensional
+0.90, and 0.95, all with a length of $2\pi$, and we vary the extensional
 rate, $\chi$, between $10^{-2}$ and $10^{-1}$.  Since the stagnation

### 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex

@@
 We consider vesicle doublets with reduced areas 0.70, 0.75, 0.80, 0.85,
-0.90, and 0.95, all with a length of $\pi$, and we vary the extensional
-rate, $\chi$, between $10^{-2}$ and $10^{-1}$.  
-%
-In the simulations we mimic the active control algorithm in the microfluidic experiments by
-moving the center of the
+0.90, and 0.95, all with a length of $2\pi$, and we vary the extensional
+rate, $\chi$, between $10^{-2}$ and $10^{-1}$.  Since the stagnation
+point can be controlled in an experimental
+setting~\cite{Johnson-Chavarria2011_EMJ}, we mimic the active control
+algorithm in the microfluidic experiments by moving the center of the
 doublet at each time step so that the stagnation point occurs exactly in
-the middle of the doublet.  
-%
-With this adjustment, the vesicles either
+the middle of the doublet.  With this adjustment, the vesicles either
 remain as a doublet in the fluid trap centered around the stagnation

### 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex
small changes as discussed with Yuan on skype

@@
 in Hamaker constants that are appropriate for lipid-lipid interactions.
-We use Hamaker constants ranging from $0.1$ to $1$ times the bending
-rigidity modulus.  In Appendix~\ref{sec:appendixA}, the adhesive force
-at a point $\xx$ on vesicle $j$ is shown to be
+We use Hamaker constants ranging from $\mathcal{O}(10^{-1})$ to
+$\mathcal{O}(10^0)$ times the bending rigidity modulus.  In
+Appendix~\ref{sec:appendixA}, the adhesive force at a point $\xx$ on
+vesicle $j$ is shown to be
 \begin{align}
@@
 \end{align*}
-where $\phi$ is the area fraction of vesicles, $/tau$ is the stress due
+where $\phi$ is the area fraction of vesicles, $\tau$ is the stress due
 to the vesicles, and $\langle \cdot \rangle$ is the spatial average.

### 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex
some changes in section 3 by yny

@@
 equilibrium configuration, we turn on the fluid trap with the stagnation
-point placed at the center of the vesicle doublet.  At low extensional
+point placed at the center of the vesicle doublet.  
+When the long axis of the vesicle doublet is aligned with the far-field diverging flow, the converging flow
+pushes vesicles towards each other and the repulsive interaction is essential to keep the two vesicles at the separation distance.
+In this configuration the extensional flow is pushing the vesicles together. With the stagnation point placed at the center of the doublet, this
+configuration appears to be quite stable for low extensional flow rate.
+
+However, when the long axis of vesicle doublet is parallel
+to the far-field converging flow, the diverging flow may overcome the vesicle adhesion to
+split the two vesicles apart. Thus in the following simulation experiments we place the vesicle doublet so that the flat contact region is
+aligned with the axis of converging flow. In this configuration the flow is pulling the vesicles away from each and 
+is expected to be less stable than the orthogonal configuration where the fluid flow is constantly pushing vesicles towards each other. 
+It is also reasonable to expect the vesicle doublet to rotate around the stagnation so the flow is pushing them together rather than pulling them apart.
+
+At low extensional
 rates, we expect the vesicle doublet to stay at the fluid
@@
 doublet at each time step so that the stagnation point occurs exactly in
-the middle of the doublet.  With this adjustment, the vesicles either
+the middle of the doublet.  
+With this adjustment, the vesicles either
 remain as a doublet in the fluid trap centered around the stagnation
 point, or the doublet is broken and the vesicles separate from one
-another.  In Figures~\ref{fig:extensional1}--\ref{fig:extensional3},
+another.
+
+In Figures~\ref{fig:extensional1}--\ref{fig:extensional3},
 snapshots of a fluid trap containing a vesicle doublet of reduced area

### 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex
starting to edit quiescent example

--- 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex
@@
 We consider the suspension of two identical two-dimensional vesicles
-suspended in a quiescent flow.  Without any external forcing such as an imposed
-electric field or a fluid flow in the far-field, the long-range
+suspended in a quiescent flow.  Without any external forcing such as an
+imposed electric field or a fluid flow in the far-field, the long-range
 attraction pulls two vesicles together until their separation distance
-is close to $\delta$ and large deformation occurs in the ``contact region". The L.-J. type potential prohibits
-physical contact between two membranes and instead keep them close to the separation distance $\delta$.
-In Section~\ref{subsec:qflow_draining_times}, we
-compute the expected time for the vesicles to reach an equilibrium
-configuration and compare the analysis with numerical simulations.  In
+is close to $\delta$. The L.-J.~type potential prohibits physical
+contact between two membranes and instead keep them close to the
+separation distance $\delta$.  In
+Section~\ref{subsec:qflow_draining_times}, we compute the expected time
+for the vesicles to reach an equilibrium configuration and compare the
+analysis with numerical simulations.  In
 Section~\ref{subsec:qflow_adhesion_parameters}, we characterize the
@@
 in the previous simulations so that the equilibrium configuration is
-achieved with a shorter timer horizon.  Once a vesicle doublet is
+achieved with a shorter time horizon.  Once a vesicle doublet is
 formed, the membrane shape in the contact region depends on the adhesion

### 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex
read relaxation example again

@@
 imposed electric field or a fluid flow in the far-field, the long-range
-attraction pulls two vesicles together until their separation distance
+attraction pulls the vesicles together until their separation distance
 is close to $\delta$. The L.-J.~type potential prohibits physical
-contact between two membranes and instead keep them close to the
+contact between the two membranes and instead keeps them close to the
 separation distance $\delta$.  In
@@
 effects of the adhesion parameters and the vesicles' reduced area on the
-bending and adhesive energies.
-
+shape of the contact region and the bending and adhesive energies.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Effects of the adhesion parameters on draining times}
@@
 When two vesicles move towards (or away from) each other under a
-constant force $F$ without any external fluid flow, the height $(h)$ of
+constant force $F$ without any external fluid flow, the height, $h$, of
 the thin liquid film between two vesicles follows the draining
@@
 When the force on each vesicle is a function of the separation distance
-$h$ of the form (with integers $n>m\ge 2$)
+$h$ of the form
 \begin{align}
@@
 \end{align}
-attraction is dominant at ``large" distances ($h > \delta$) while
-repulsion is dominant at ``small" distances ($h<\delta$).  Integration
-of equation~\eqref{eq:dhdt} with the $F(h)$ as defined in
-equation~\eqref{eq:Fh} gives the relationship between $t$ and $h$.  In
-this case the relationship involves an integral of a function of
-dimensionless $\bar{h} \equiv h/\delta$:
+with $n>m\ge 2$ being integers, attraction is dominant at ``large"
+distances ($h > \delta$) while repulsion is dominant at ``small"
+distances ($h<\delta$).  Integration of equation~\eqref{eq:dhdt} with
+the $F(h)$ as defined in equation~\eqref{eq:Fh} gives the relationship
+between $t$ and $h$.  In this case, the relationship involves an
+integral of a function of the dimensionless variable $\bar{h} \equiv
+h/\delta$:
 \begin{align*}
@@
     -\frac{1}{\mathcal{H}^{1/3}\delta^{5/3}}\int^{\bar{h}(t)}_{\bar{h}(0)}
-      \frac{d \bar{h}}{\bar{h}^{(8-m)/3}(\bar{h}^{m-n}-1)^{1/3}},
+      \frac{d \bar{h}}{\bar{h}^{(8-m)/3}(\bar{h}^{m-n}-1)^{1/3}}.
 \end{align*}
@@
 $\delta\rightarrow 0$), and (ii) the adhesion strength
-$\mathcal{H}^{-1/3}$ (as in constant forcing
+$\mathcal{H}^{-1/3}$ (as in the constant forcing
 case~\cite{RamachandranLeal2010_PoF}).  From the above analysis we also
@@
 flow.  Starting with two vesicles at a distance of twice the vesicle
-radius at $t=0$, the long-range attraction pulls the vesicles together.
-The left plot of Figure~\ref{fig:qflow00} shows the scaled adhesion
-energy versus time with $\mathcal{H}=0.1$ and three values of $\delta$
-as labeled.  Adhesion energy reaches minimum at equilibrium, and the
-scaled $E_{adh}$ evolves towards zero at equilibrium.  The arrows
-indicate the times when the scaled adhesion energy reaches within $1\%$
-of equilibrium: $t\sim 96$ for $\delta=0.2$, $t\sim 45$ for $\delta =
-0.3$, and $t\sim 30$ for $\delta=0.4$:
+radius, the long-range attraction pulls the vesicles together.  The left
+plot of Figure~\ref{fig:qflow00} shows the scaled adhesion energy versus
+time with $\mathcal{H}=0.1$ and three values of $\delta$ as labeled.
+Adhesion energy reaches minimum at equilibrium, and the scaled $E_{adh}$
+evolves towards zero at equilibrium.  The arrows indicate the times when
+the scaled adhesion energy reaches within $1\%$ of equilibrium: $t\sim
+96$ for $\delta=0.2$, $t\sim 45$ for $\delta = 0.3$, and $t\sim 30$ for
+$\delta=0.4$:
 \begin{align*}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Effects of the adhesion parameters on equilibrium
 configuration of a vesicle pair}
-\label{subsec:qflow_adhesion_parameters} 
-We next simulate a pair of identical two-dimensional vesicles
-interacting with each other via the adhesion force in
-equation~\eqref{eq:Fh}.  The initial vesicle placement is smaller than
-in the previous simulations so that the equilibrium configuration is
-achieved with a shorter time horizon.  Once a vesicle doublet is
-formed, the membrane shape in the contact region depends on the adhesion
-strength relative to the membrane bending rigidity.  For weak to
-moderate adhesion strength, vesicle membranes are flattened in the
-contact region while the rest of vesicle maintains a nearly spherical
-shape~\cite{EvansMetcalfe1984_BJ, Book_PhysicalBasisCellAdhesion,
-Book_IntermolecularSurfaceForces,
+\label{subsec:qflow_adhesion_parameters} We again simulate two identical
+adhering vesicles with the adhesion force in equation~\eqref{eq:Fh}.
+The initial vesicle separation is smaller than in the previous
+simulations so that the equilibrium configuration is achieved in a
+shorter time horizon.  Once a vesicle doublet is formed, the membrane
+shape in the contact region depends on the adhesion strength relative to
+the membrane bending rigidity.  For weak to moderate adhesion strength,
+vesicle membranes are flattened in the contact region while the rest of
+vesicle maintains a nearly spherical shape~\cite{EvansMetcalfe1984_BJ,
+Book_PhysicalBasisCellAdhesion, Book_IntermolecularSurfaceForces,
 RamachandranAndersonLealIsraelachvili2010_Langmuir}.  Under a strong
 adhesion, however, the vesicle membranes in the contact region buckle
-and form a sigmoidal shape  that has been observed in RBC doublet as
-well~\cite{Ziherl2007_PRL, ZiherlSvetina2007_PNAS,
+and form a sigmoidal shape that has also been observed in RBC
+doublets~\cite{Ziherl2007_PRL, ZiherlSvetina2007_PNAS,
 FlormannAouane2017_SciReports}.  An external electric field is also able
@@
   \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
-  \caption{\label{fig:Dec18_vesicle_shape} Equilibrium configuration of
-  a doublet of identical vesicles under adhesion in a quiescent flow.
-  Vesicle reduced area $\Delta A=0.95$, $0.75$, and $0.6$ are labeled.
-  The color coding is the tension along the vesicle.  Vesicle length is
-  fixed at $2\pi$, (dimensionless) bending rigidity modulus $\kappa=1$,
-  $\mathcal{H}=5$, and $\delta=0.2$.  {\em Left}: Overall equilibrium
-  shapes of two vesicles under adhesive interactions vary with reduced
-  area.  {\em Right}: Membrane shapes in the contact region.} 
+  \caption{\label{fig:Dec18_vesicle_shape} The equilibrium configuration
+  of a doublet of identical vesicles under adhesion in a quiescent flow.
+  The vesicle reduced areas of $\Delta A=0.95$, $0.75$, and $0.6$ are
+  labeled.  The color coding is the tension along the vesicle.  The
+  vesicle length is fixed at $2\pi$, the dimensionless bending rigidity
+  modulus is $\kappa_b=1$, the Hamaker constant is $\mathcal{H}=5$, and
+  the separation distance is $\delta=0.2$.  {\em Left}: The overall
+  equilibrium shapes of two vesicles under adhesive interactions vary
+  with the reduced area.  {\em Right}: The membrane shapes in the
+  contact region.} 
 \end{figure}
@@
 This is consistent with the equilibrium shapes of a vesicle doublet
-under a L.-J. potential ($(m,n) =
-(12,6)$)~\cite{FlormannAouane2017_SciReports}.  As the reduced area
-decreases further, we observe undulation of the 
-vesicle membrane on the non-contact side while the contact region remains
-flat.  The color coding along each curve is the tension of the vesicle
-membrane.  We observe that the membrane tension in the contact region is
-very negative, indicating a dominant compression of membrane when the
+under a $(m,n) = (12,6)$
+L.-J.~potential~\cite{FlormannAouane2017_SciReports}.  As the reduced
+area decreases further, we observe undulation of the vesicle membrane on
+the non-contact side while the contact region remains flat.  The color
+coding along each curve is the tension of the vesicle membrane.  We
+observe that the membrane tension in the contact region is very
+negative, indicating a dominant compression of membrane when the
 adhesion force is strong to keep the vesicles bound together.
@@
 membranes in the contact region, where the membranes are not perfectly
-flat: For all values of reduced area we observe that membranes are
-slightly curved with a dip at the edge.  Such membrane undulation in the
-contact region is predicted by lubrication analyses on a membrane
-under adhesion with a solid substrate~\cite{BlountMiksisDavis2013_PRSa,
+flat---at all reduced area we observe that the membranes are slightly
+curved with a dip at the edge.  Such membrane undulation in the contact
+region is predicted by lubrication analyses on a membrane under adhesion
+with a solid substrate~\cite{BlountMiksisDavis2013_PRSa,
 YoungStone2017_PRF}.  Also the dip at the edge of contact region is
@@
 membranes in the contact region except at the edge, where the adhesive
-force turns repulsive.  Results from the lubrication analysis shows that
+force turns repulsive.  Results from the lubrication analysis show that
 this dip and slightly curved shape in the contact region are independent
@@
 \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_EbEadh_vs_rA_adR0p2_adS502.jpeg}
-  \caption{\label{fig:Dec18_vesicle_equilibrium1}   {\em Left}:
-  Total bending energy (solid curve) and adhesion energy (dash-dotted
-  curve) plotted against the reduced area $\Delta A$. {\em Right}: Sum
-  of two energies plotted against reduced area $\Delta A$. Two vesicles in the doublet are of the same length, reduced area
-  and bending rigidity modulus ($\kappa=1$) with $\mathcal{H}=5$ and $\delta=0.2$.}
+  \caption{\label{fig:Dec18_vesicle_equilibrium1}   {\em Left}: The
+  total bending energy (solid curve) and adhesion energy (dash-dotted
+  curve) plotted against the reduced area $\Delta A$. {\em Right}: The
+  sum of two energies plotted against reduced area $\Delta A$. The two
+  vesicles in the doublet are of the same length and reduced area.  The
+  Hamaker constant is $\mathcal{H} = 5$ and the separation distance is
+  $\delta = 0.2$.}
 \end{figure}
@@
   \caption{\label{fig:Dec18_equilibrium} 
-  Total bending energy ({\em left}) and adhesion energy ({\em right}) of
-  a vesicle doublet at equilibrium versus the adhesion strength
-  $\mathcal{H}$.  The two vesicles in the doublet have the same length
-  and reduced area $\Delta A=0.95$, with separation distance $\delta =
-  0.2$ (triangles), $0.3$ (crosses), and $0.4$ (circles).}
+  The total bending energy ({\em left}) and adhesion energy ({\em
+  right}) of a vesicle doublet at equilibrium versus the adhesion
+  strength $\mathcal{H}$.  The two identical vesicles in the doublet
+  have a length of $2\pi$ and a reduced area of $\Delta A=0.95$, with
+  separation distance $\delta = 0.2$ (triangles), $0.3$ (crosses), and
+  $0.4$ (circles).}
 \end{figure}
@@
 equilibrium configuration of two vesicles under adhesive interactions.
-For both vesicles the reduced area $\Delta A=0.95$ and the bending
-rigidity is $\kappa_b = 1$.  The total bending (left) and adhesion
-(right) energies at equilibrium are plotted against $\mathcal{H}$ for
-three values of separation distance $\delta$.  We observe that for
-$\Delta A=0.95$ the equilibrium vesicle shape does not vary much with
-the adhesion strength $\mathcal{H}$, while the total adhesion energy
-varies linearly with $\mathcal{H}$.
+Both vesicles have a length of $2\pi$ and a reduced area of $\Delta A =
+0.95$.  The total bending (left) and adhesion (right) energies at
+equilibrium are plotted against $\mathcal{H}$ for three values of the
+separation distance $\delta$.  We observe that for $\Delta A=0.95$ the
+equilibrium vesicle shape does not vary much with the adhesion strength
+$\mathcal{H}$, while the total adhesion energy varies linearly with
+$\mathcal{H}$.
 

### 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex
added figures for fig 17
finished up some edits

@@
 (left) and adhesion (right) of the final equilibrium configuration.
+Both the vesicle shape, tension, and adhesion qualitatively agree with
+our doublet results.  In particular, the interior vesicles form a flat
+contact region with a large negative tension.
 
@@
 \begin{figure}[htp]
-\todo[inline]{Figures of tension and adhesion of the final
-configuration}
-\caption{\label{fig:relaxationManyVesAdhesionTension} Something smart to
-say ....}
+\centering
+\includegraphics[height=0.4\textwidth]{figs/relaxationManyVesTension.png}
+\includegraphics[height=0.4\textwidth]{figs/relaxationManyVesAdhesion.png}
+\caption{\label{fig:relaxationManyVesAdhesionTension} The tension ({\em
+left}) and adhesion force ({\em right}) of the final configuration from
+Figure~\ref{fig:relaxationManyVes}.  Along the bounding vesicle, the
+tension is largest and the adhesion is smallest in the regions that are
+well-separated from the interior vesicles.  Similar to other
+simulations, the interior vesicles are relatively flat and have a large
+negative tension in the contact regions.}
 \end{figure}
@@
 YNY acknowledges support from NSF-DMS 1614863 and 1412789, and Flatiron
-Institute, part of the Simons Foundation.
+Institute, part of the Simons Foundation.  BQ acknowledges support from
+Florida State University startup funds and Simons Foundation Mathematics
+and Physical Sciences-Collaboration Grants for Mathematicians 527139.
 

### 2019-02-08 vesicle_code/docs/adhesion/adhesion.tex
thrusday night 1st revisions by yny

@@
 
+\begin{figure}[htp]
+  \begin{minipage}{0.53\textwidth}
+    \includegraphics[width=0.33\textwidth]{figs/angleDefinition.pdf} \:
+    \includegraphics[width=0.34\textwidth]{figs/rotate1.pdf} \:
+    \includegraphics[width=0.26\textwidth]{figs/rotate2.pdf}
+  \end{minipage}
+   \caption{\label{fig:InclinationAngle} The
+  definition of the inclination angle.  An inclination angle of $\pi$
+  indicates a doublet whose long axis is parallel to the diverging
+  direction, while an inclination angle of $\pi/2$ indicates a doublet
+  whose short axis is parallel to the diverging direction.  The square
+  mark is a stagnation point and the round point is located at the
+  center of the vesicle.}
+\end{figure}
+
 We begin with two identical vesicles forming a doublet under an
@@
 equilibrium configuration, we turn on the fluid trap with the stagnation
-point placed at the center of the vesicle doublet.  
-When the long axis of the vesicle doublet is aligned with the far-field diverging flow, the converging flow
-pushes vesicles towards each other and the repulsive interaction is essential to keep the two vesicles at the separation distance.
-In this configuration the extensional flow is pushing the vesicles together. With the stagnation point placed at the center of the doublet, this
-configuration appears to be quite stable for low extensional flow rate.
-
-However, when the long axis of vesicle doublet is parallel
-to the far-field converging flow, the diverging flow may overcome the vesicle adhesion to
-split the two vesicles apart. Thus in the following simulation experiments we place the vesicle doublet so that the flat contact region is
-aligned with the axis of converging flow. In this configuration the flow is pulling the vesicles away from each and 
-is expected to be less stable than the orthogonal configuration where the fluid flow is constantly pushing vesicles towards each other. 
-It is also reasonable to expect the vesicle doublet to rotate around the stagnation so the flow is pushing them together rather than pulling them apart.
-
+point placed at the center of the vesicle doublet, which has a flat contact region as shown in \S~\ref{sec:qflow}. 
+Based on how the contact region aligns with the direction of divergent flow, 
+we can define the inclination angle of the vesicle doublet as illustrated in Figure~\ref{fig:InclinationAngle}.
+%
+
+When $\theta=\pi$ (the long axis of the vesicle doublet is aligned with the far-field diverging flow), the converging flow
+pushes vesicles towards each other and the short-range repulsive force is essential to keep the two vesicles at the separation distance.
+With the fluid flow pushing the two vesicles towards the stagnation point dynamically placed at the doublet center, 
+this configuration is expected to be more stable than the configuration in the middle of Figure~\ref{fig:InclinationAngle} where $\theta=\pi/2$ 
+(the long axis of vesicle doublet is parallel to the converging direction).  As shown in the illustration, 
+the diverging flow is pulling the vesicles away from each other when $\theta=\pi/2$. 
+Thus it is possible that the diverging flow may overcome the adhesion and
+break up the doublet. It is also reasonable to expect the vesicle doublet to rotate around the stagnation so the flow is pushing them together rather than pulling them apart.
+
+In the following simulation experiments we place the vesicle doublet with $\theta=\pi/2$ so that the flat contact region is
+orthogonal to the diverging flow that is pulling vesicles away from each other.
+%In this configuration the flow is pulling the vesicles away from each other, and 
+%is expected to be less stable than the $\theta=\pi$ configuration where the fluid flow is constantly pushing vesicles towards each other. 
+%
 At low extensional
@@
 \begin{figure}[htp]
-  \begin{minipage}{0.53\textwidth}
-    \includegraphics[width=0.33\textwidth]{figs/angleDefinition.pdf} \:
-    \includegraphics[width=0.34\textwidth]{figs/rotate1.pdf} \:
-    \includegraphics[width=0.26\textwidth]{figs/rotate2.pdf}
-  \end{minipage}
-  \hfill
+%  \begin{minipage}{0.53\textwidth}
+%    \includegraphics[width=0.33\textwidth]{figs/angleDefinition.pdf} \:
+%    \includegraphics[width=0.34\textwidth]{figs/rotate1.pdf} \:
+%    \includegraphics[width=0.26\textwidth]{figs/rotate2.pdf}
+%  \end{minipage}
+%  \hfill
   \begin{minipage}{0.45\textwidth}
@@
   \end{minipage}
-  \caption{\label{fig:extensionalPhaseDiagram} {\em Left}: The
-  definition of the inclination angle.  An inclination angle of $\pi$
-  indicates a doublet whose long axis is parallel to the diverging
-  direction, while an inclination angle of $\pi/2$ indicates a doublet
-  whose short axis is parallel to the diverging direction.  The square
-  mark is a stagnation point and the round point is located at the
-  center of the vesicle. {\em Right}: A phase diagram of the long-time
+  \caption{\label{fig:extensionalPhaseDiagram}  A phase diagram of the long-time
   behavior of a fluid trap formed by two adhering vesicles in an

### 2019-02-08 vesicle_code/docs/adhesion/adhesion.tex
last edits for Feb 07 from yny

@@
 
+We consider vesicle doublets with reduced areas 0.70, 0.75, 0.80, 0.85,
+0.90, and 0.95, all with a length of $2\pi$, and we vary the extensional
+rate, $\chi$, between $10^{-2}$ and $10^{-1}$.  Since the stagnation
+point can be controlled in an experimental
+setting~\cite{Johnson-Chavarria2011_EMJ}, we mimic the active control
+algorithm in the microfluidic experiments by moving the center of the
+doublet at each time step so that the stagnation point occurs exactly in
+the middle of the doublet.  
+With this adjustment, the vesicles either
+remain as a doublet in the fluid trap centered around the stagnation
+point, or the doublet is broken and the vesicles separate from one
+another.
+
+In Figures~\ref{fig:extensional1}--\ref{fig:extensional3},
+snapshots of a fluid trap containing a vesicle doublet of reduced area
+$\Delta A = 0.7$ are simulated at different extensional rates.  While
+this doublet remains bound for all the
+considered extensional rates, a doublet with a reduced area of $\Delta A
+= 0.8$ is split with an extensional rate $\chi = 0.1$
+(Figure~\ref{fig:extensional4}).  
+%
+For extensional rates and reduced areas that result in a bound vesicle doublet, 
+we observe that the doublet always rotate from the $\theta=\pi/2$ configuration towards
+the more stable $\theta=\pi$ configuration, as shown in Figures~\ref{fig:extensional1}--\ref{fig:extensional3}.
+We also observe that in most cases with moderate extensional flow rates the doublet falls short of 
+aligning their long axis with the diverging direction.
+
 \begin{figure}[htp]
@@
   black square, is a stagnation point.}
-
+  \end{figure}
+
+  \begin{figure}
   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
@@
   with a black square, is a stagnation point.}
-
+  \end{figure}
+
+ \begin{figure}
   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
@@
   square, is a stagnation point.}
-
+  \end{figure}
+
+In Figure~\ref{fig:extensionalInclinationAngle}, we plot the inclination
+angle of the doublet as a function of time for four different
+extensional rates (left) and the final inclination angle for all
+doublets that reach an equilibrium state (middle).  We observe that not
+only do larger smaller extensional rates result in smaller inclination
+angles, but smaller reduced areas also result in smaller inclination
+angles.  Moreover, the critical Hamaker constant that determines if the
+doublet remains trapped or is broken decreases with an increasing
+extensional rate.
+\begin{figure}
   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
@@
 \end{figure}
-
-We consider vesicle doublets with reduced areas 0.70, 0.75, 0.80, 0.85,
-0.90, and 0.95, all with a length of $2\pi$, and we vary the extensional
-rate, $\chi$, between $10^{-2}$ and $10^{-1}$.  Since the stagnation
-point can be controlled in an experimental
-setting~\cite{Johnson-Chavarria2011_EMJ}, we mimic the active control
-algorithm in the microfluidic experiments by moving the center of the
-doublet at each time step so that the stagnation point occurs exactly in
-the middle of the doublet.  
-With this adjustment, the vesicles either
-remain as a doublet in the fluid trap centered around the stagnation
-point, or the doublet is broken and the vesicles separate from one
-another.
-
-In Figures~\ref{fig:extensional1}--\ref{fig:extensional3},
-snapshots of a fluid trap containing a vesicle doublet of reduced area
-$\Delta A = 0.7$ are simulated at different extensional rates.  While
-this doublet remains trapped around the stagnation point for all the
-considered extensional rates, a doublet with a reduced area of $\Delta A
-= 0.8$ is broken with an extensional rate $\chi = 0.1$
-(Figure~\ref{fig:extensional4}).  We summarize the reduced areas and
-extensional rates that result in a fluid trap in left plot of
-Figure~\ref{fig:extensionalPhaseDiagram}. Parameter values with a blue
-mark result in a fluid trap and parameter values with a red mark result
-in vesicle separation.
-
-For extensional rates and reduced areas that result in a fluid trap, the
-initial configuration of the vesicles have the diverging stream
-direction parallel to the vesicles' short axis.  Since the stable
-configuration of two vesicles in an extensional flow has the converging
-direction parallel to the vesicles' short axis, we expect the vesicles
-to align themselves with the long axis parallel to the diverging
-direction.  We observe in
-Figures~\ref{fig:extensional1}--\ref{fig:extensional3} that the vesicles
-do in fact rotate, but fall short of aligning their long axis with the
-diverging direction.  We summarize the final inclination angle of the
-doublet in the left plot of Figure~\ref{fig:extensionalPhaseDiagram}.
+We summarize the final inclination angle of the
+doublet in the right plot of Figure~\ref{fig:extensionalInclinationAngle}.
 The size of the round dots are scaled to the final inclination angle as
@@
 state, and these simulations are marked with a square.
-
-\begin{figure}[htp]
+%
+The right plot of Figure~\ref{fig:extensionalInclinationAngle} 
+also summarizes the  reduced areas and
+extensional rates that result in a bound vesicle doublet in a fluid trap: Parameter values with a blue
+mark result in a fluid trap and parameter values with a red mark result
+in vesicle separation.
+
+%\begin{figure}[htp]
 %  \begin{minipage}{0.53\textwidth}
@@
 %  \hfill
-  \begin{minipage}{0.45\textwidth}
-    \centering
-    \includegraphics[width=0.8\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
-  \end{minipage}
-  \caption{\label{fig:extensionalPhaseDiagram}  A phase diagram of the long-time
-  behavior of a fluid trap formed by two adhering vesicles in an
-  extensional flow.  The Hamaker constant is $\mathcal{H}=0.7$ and the
-  adhesion length scale is $\delta = 0.4$.  For small extensional rates,
-  the doublet structure is not broken (blue marks), while at large
-  extensional rates, the doublet is broken (red marks).  The size of the
-  round blue marks indicates the final inclination angle with the larger
-  dots rotating less ($\theta=\pi$) and the smaller dots rotating more
-  ($\theta = \pi/2$).  A square mark is used for simulations that did
-  not result in an equilibrium inclination angle in the given time
-  horizon.}
-\end{figure}
-
-In Figure~\ref{fig:extensionalInclinationAngle}, we plot the inclination
-angle of the doublet as a function of time for four different
-extensional rates (left) and the final inclination angle for all
-doublets that reach an equilibrium state (right).  We observe that not
-only do larger smaller extensional rates result in smaller inclination
-angles, but smaller reduced areas also result in smaller inclination
-angles.  Moreover, the critical Hamaker constant that determines if the
-doublet remains trapped or is broken decreases with an increasing
-extensional rate.
+%  \begin{minipage}{0.45\textwidth}
+%    \centering
+%    \includegraphics[width=0.8\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
+%  \end{minipage}
+%  \caption{\label{fig:extensionalPhaseDiagram}  A phase diagram of the long-time
+%  behavior of a fluid trap formed by two adhering vesicles in an
+%  extensional flow.  The Hamaker constant is $\mathcal{H}=0.7$ and the
+%  adhesion length scale is $\delta = 0.4$.  For small extensional rates,
+%  the doublet structure is not broken (blue marks), while at large
+%  extensional rates, the doublet is broken (red marks).  The size of the
+%  round blue marks indicates the final inclination angle with the larger
+%  dots rotating less ($\theta=\pi$) and the smaller dots rotating more
+%  ($\theta = \pi/2$).  A square mark is used for simulations that did
+%  not result in an equilibrium inclination angle in the given time
+%  horizon.}
+%\end{figure}
 
 \begin{figure}[htp]
-  \includegraphics[height=0.35\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
-  \includegraphics[height=0.35\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
+  \includegraphics[height=0.27\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
+  \includegraphics[height=0.27\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
+  \includegraphics[height=0.27\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
   \caption{\label{fig:extensionalInclinationAngle} {\em Left}: The
@@
   $\Delta A = 0.7$ submerged in an extensional flow with an extensional
-  rate of $\chi$.  {\em Right}: The final inclination angle of doublets.
+  rate of $\chi$.  {\em Middle}: The final inclination angle of doublets.
   At larger extensional rates, the doublet is broken by the flow.
+  {\em Right}: A phase diagram of the long-time
+  behavior of a fluid trap formed by two adhering vesicles in an
+  extensional flow.
   Results are not reported for some of the low extensional rates since

### 2019-02-08 vesicle_code/docs/adhesion/adhesion.tex
first edits for Feb 08 from yny

@@
 
-\title{Hydrodynamics and rheology of adhesive vesicle doublets}
+\title{Hydrodynamics and rheology of an adhesive vesicle doublet}
 % Force line breaks with \\
@@
 \begin{abstract}
-The dynamics of adhesive vesicles under various flowing conditions is
+The dynamics of an adhesive vesicle doublet under various flowing conditions is
 investigated numerically using a high-order adaptive-in-time boundary
@@
 move slowly towards each other under the adhesive potential, pushing out
-fluid between them to form a doublet at equilibrium. A lubrication
-analysis on such draining of the thin film gives the dependencies of
+fluid between them to form a vesicle doublet at equilibrium. A lubrication
+analysis on such draining of a thin film gives the dependencies of
 draining time on adhesion strength and separation distance that are in
@@
 %
-In a microfluid trap where the stagnation of an extensional flow is
+In a microfluid trap where the stagnation of an extensional flow is dynamically
 placed in the middle of a vesicle doublet through an active control
-loop, novel dynamics of a vesicle doublet are observed. Numerical
+loop, novel dynamics of a vesicle doublet is observed. Numerical
 simulations show that there exists a critical extensional flow rate
-above which adhesive interaction is overcome by the hydrodynamic
+above which adhesive interaction is overcome by the 
 diverging stream, thus providing a simple method to measure the adhesion
@@
 In a planar shear flow, numerical simulations reveal that a vesicle
-doublet may form as they approach each other provided that the adhesion
+doublet may form as two vesicles approach each other provided that the adhesion
 strength is sufficiently large at a given vesicle reduced area. Once a
@@
 Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  The stagnation
-point (zero-velocity point) in an extensional flow, $\uu =\chi(-x,y)$,
+point (zero-velocity at the origin) in an extensional flow, $\uu =\chi(-x,y)$,
 is a saddle point where two laminar streams converge along an axis and
-then diverge in a different direction.  With an active control algorithm
+then diverge in the orthogonal direction.  With an active control algorithm
 to place the stagnation point at a desirable location by adjusting the streaming
@@
    \caption{\label{fig:InclinationAngle} The
-  definition of the inclination angle.  An inclination angle of $\pi$
+  definition of the inclination angle of a vesicle doublet at the center of an extensional flow.  
+  An inclination angle of $\pi$
   indicates a doublet whose long axis is parallel to the diverging
@@
 point placed at the center of the vesicle doublet, which has a flat contact region as shown in \S~\ref{sec:qflow}. 
-Based on how the contact region aligns with the direction of divergent flow, 
+Based on how the contact region aligns with the extensional flow, 
 we can define the inclination angle of the vesicle doublet as illustrated in Figure~\ref{fig:InclinationAngle}.
@@
 
-When $\theta=\pi$ (the long axis of the vesicle doublet is aligned with the far-field diverging flow), the converging flow
+When $\theta=\pi$ (the doublet long axis is aligned with the far-field diverging flow), the converging flow
 pushes vesicles towards each other and the short-range repulsive force is essential to keep the two vesicles at the separation distance.
-With the fluid flow pushing the two vesicles towards the stagnation point dynamically placed at the doublet center, 
-this configuration is expected to be more stable than the configuration in the middle of Figure~\ref{fig:InclinationAngle} where $\theta=\pi/2$ 
-(the long axis of vesicle doublet is parallel to the converging direction).  As shown in the illustration, 
-the diverging flow is pulling the vesicles away from each other when $\theta=\pi/2$. 
-Thus it is possible that the diverging flow may overcome the adhesion and
-break up the doublet. It is also reasonable to expect the vesicle doublet to rotate around the stagnation so the flow is pushing them together rather than pulling them apart.
-
-In the following simulation experiments we place the vesicle doublet with $\theta=\pi/2$ so that the flat contact region is
-orthogonal to the diverging flow that is pulling vesicles away from each other.
+With the converging flow pushing the two vesicles towards the stagnation point dynamically placed at the doublet center, 
+this configuration is expected to be more stable than the $\theta=\pi/2$ configuration in the middle of Figure~\ref{fig:InclinationAngle},  where  
+the doublet long axis is parallel to the converging direction. This is because
+when $\theta=\pi/2$ the diverging flow is pulling the vesicles away from each other as shown in the illustration. 
+With the inclination angle fixed at $\theta=\pi/2$,
+the vesicle doublet stays intact only when the adhesive force is strong enough to dominate over the fluid drag in this configuration.
+Thus it is possible that the diverging flow may overcome adhesion and
+break up the doublet. It is also reasonable to expect a vesicle doublet to rotate from $\theta=\pi/2$ to $\theta=\pi$,
+such that the fluid flow is pushing them together rather than pulling them apart.
+
+In the following numerical experiments we place a vesicle doublet with $\theta=\pi/2$, so that
+the diverging flow may be strong enough to pull vesicles away from the doublet.
 %In this configuration the flow is pulling the vesicles away from each other, and 
@@
 At low extensional
-rates, we expect the vesicle doublet to stay at the fluid
+rates, we expect the $\theta=\pi/2$ doublet to stay intact at the fluid
 trap stagnation point.  On the other hand, the vesicle doublet may
@@
 considered extensional rates, a doublet with a reduced area of $\Delta A
-= 0.8$ is split with an extensional rate $\chi = 0.1$
+= 0.8$ is split with a critical extensional rate $\chi_c \sim 0.1$
 (Figure~\ref{fig:extensional4}).  
 %
-For extensional rates and reduced areas that result in a bound vesicle doublet, 
-we observe that the doublet always rotate from the $\theta=\pi/2$ configuration towards
-the more stable $\theta=\pi$ configuration, as shown in Figures~\ref{fig:extensional1}--\ref{fig:extensional3}.
-We also observe that in most cases with moderate extensional flow rates the doublet falls short of 
-aligning their long axis with the diverging direction.
-
 \begin{figure}[htp]
@@
   \end{figure}
+  %
+  For extensional rates and reduced areas that result in a bound vesicle doublet, 
+we observe that the doublet always rotate from $\theta=\pi/2$ configuration towards
+the more stable $\theta=\pi$ configuration, as shown in Figures~\ref{fig:extensional1}--\ref{fig:extensional3}.
+We also observe that in most cases with moderate extensional flow rates the doublet falls short of 
+aligning their long axis with the diverging direction.
 

### 2019-02-08 vesicle_code/docs/adhesion/adhesion.tex
edits from yny on Feb8

@@
 When two vesicles move towards (or away from) each other under a
-constant force $F$ without any external fluid flow, the height, $h$, of
+constant force $F$ without any imposed external flow, the height, $h$, of
 the thin liquid film between two vesicles follows the draining
@@
 when $\theta=\pi/2$ the diverging flow is pulling the vesicles away from each other as shown in the illustration. 
-With the inclination angle fixed at $\theta=\pi/2$,
+If the doublet inclination angle is fixed at $\theta=\pi/2$,
 the vesicle doublet stays intact only when the adhesive force is strong enough to dominate over the fluid drag in this configuration.
@@
 At low extensional
-rates, we expect the $\theta=\pi/2$ doublet to stay intact at the fluid
+rates, we expect the $\theta=\pi/2$ doublet to stay bound at the fluid
 trap stagnation point.  On the other hand, the vesicle doublet may
@@
 
-In Figures~\ref{fig:extensional1}--\ref{fig:extensional3},
+In Figures~\ref{fig:extensional1},
 snapshots of a fluid trap containing a vesicle doublet of reduced area
@@
 considered extensional rates, a doublet with a reduced area of $\Delta A
-= 0.8$ is split with a critical extensional rate $\chi_c \sim 0.1$
-(Figure~\ref{fig:extensional4}).  
+= 0.8$ is split with a critical extensional rate $\chi_c =0.1$
+(bottom row in Figure~\ref{fig:extensional3}).  
 %
@@
   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}\\
+   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
   \caption{\label{fig:extensional1} A doublet inside a fluid trap.  The
@@
   0.7$, the adhesion length scale is $\delta = 0.4$, and the extensional
-  rate is $\chi = 0.02$.  The center of the vesicle, denoted with a
+  rate $\chi = 0.02$ ({\em top}) and $\chi=0.7$ ({\em bottom}).  The center of the vesicle, denoted with a
   black square, is a stagnation point.}
@@
 
-  \begin{figure}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
-  \caption{\label{fig:extensional2} A doublet inside a fluid trap.  The
-  reduced area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H}
-  = 0.7$, the adhesion length scale is $\delta = 0.4$, and the
-  extensional rate is $\chi = 0.07$.  The center of the vesicle, denoted
-  with a black square, is a stagnation point.}
-  \end{figure}
+%  \begin{figure}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
+%  \caption{\label{fig:extensional2} A doublet inside a fluid trap.  The
+%  reduced area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H}
+%  = 0.7$, the adhesion length scale is $\delta = 0.4$, and the
+%  extensional rate is $\chi = 0.07$.  The center of the vesicle, denoted
+%  with a black square, is a stagnation point.}
+%  \end{figure}
 
@@
   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}\\
+    \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
   \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
-  The reduced area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} =
+  The reduced area $\Delta A = 0.7$ ({\em top}) and $\Delta A=0.8$ ({\em bottom}). The Hamaker constant is $\mathcal{H} =
   0.7$, the adhesion length scale is $\delta = 0.4$, and the extensional
-  rate is $\chi = 0.1$.  The center of the vesicle, denoted with a black
+  rate $\chi = 0.1$.  The center of the vesicle, denoted with a black
   square, is a stagnation point.}
@@
 extensional rate.
-\begin{figure}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
-  \caption{\label{fig:extensional4} A doublet broken by an extensional
-  flow.  The reduced area is $\Delta A = 0.8$, the Hamaker constant is
-  $\mathcal{H} = 0.7$, the adhesion length scale is $\delta = 0.4$, and
-  the extensional rate is $\chi = 0.1$.  Initially, the doublet tilts to
-  an inclination angle, and then the extensional rate overcomes the
-  adhesive force and the doublet is broken.  The center of the vesicle,
-  denoted with a black square, is a stagnation point.}
-\end{figure}
+%\begin{figure}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
+%  \caption{\label{fig:extensional4} A doublet broken by an extensional
+%  flow.  The reduced area is $\Delta A = 0.8$, the Hamaker constant is
+%  $\mathcal{H} = 0.7$, the adhesion length scale is $\delta = 0.4$, and
+%  the extensional rate is $\chi = 0.1$.  Initially, the doublet tilts to
+%  an inclination angle, and then the extensional rate overcomes the
+%  adhesive force and the doublet is broken.  The center of the vesicle,
+%  denoted with a black square, is a stagnation point.}
+%\end{figure}
 We summarize the final inclination angle of the
@@
 vesicle with the diverging direction and then the vesicles separate
-(Figure~\ref{fig:extensional4}).  For very low extensional rates, the
+(bottom row in Figure~\ref{fig:extensional3}).  For very low extensional rates, the
 time horizon is insufficient for the doublet to reach an equilibrium

### 2019-02-08 vesicle_code/docs/adhesion/adhesion.tex
fixing Fig 6
fixed fig 1
fixed up figure 6
2nd edits from yny

@@
 \begin{figure}[htp]
-  \begin{minipage}{0.53\textwidth}
-    \includegraphics[width=0.33\textwidth]{figs/angleDefinition.pdf} \:
-    \includegraphics[width=0.34\textwidth]{figs/rotate1.pdf} \:
-    \includegraphics[width=0.26\textwidth]{figs/rotate2.pdf}
-  \end{minipage}
-   \caption{\label{fig:InclinationAngle} The
-  definition of the inclination angle of a vesicle doublet at the center of an extensional flow.  
-  An inclination angle of $\pi$
-  indicates a doublet whose long axis is parallel to the diverging
-  direction, while an inclination angle of $\pi/2$ indicates a doublet
-  whose short axis is parallel to the diverging direction.  The square
-  mark is a stagnation point and the round point is located at the
-  center of the vesicle.}
+    \includegraphics[width=0.25\textwidth]{figs/angleDefinition.pdf}
+    \includegraphics[width=0.25\textwidth]{figs/rotate1.pdf}
+    \includegraphics[width=0.25\textwidth]{figs/rotate2.pdf}
+   \caption{\label{fig:InclinationAngle} The definition of the
+   inclination angle of a vesicle doublet at the center of an
+   extensional flow.  An inclination angle of $\pi$ indicates a doublet
+   whose long axis is parallel to the diverging direction, while an
+   inclination angle of $\pi/2$ indicates a doublet whose short axis is
+   parallel to the diverging direction.  The square mark is a stagnation
+   point and the round point is located at the center of the vesicle.}
    \end{figure}
@@
 
-Finally, to further characterize the rotating dynamics of a doublet, we
-compute and plot the vorticity and total force on the vesicles in
-Figure~\ref{fig:extensionalVorticity}. We consider the doublet formed
-with a two vesicles of reduced area $\Delta A = 0.7$, adhesion length
-scale $\delta = 0.4$, Hamaker constant $\mathcal{H} = 0.7$, and
-extensional rate $\chi = 0.7$.  The doublet's inclination angle remains
-close to $\pi$ for a period of time (see the left plot of
-Figure~\ref{fig:extensionalInclinationAngle}).  Then, as the doublet
-starts to rotate, the total force first points in the direction of the
-diverging direction and then rotates until it is parallel with the
-vesicles' long axis.  This results in a shearing motion between the
-vesicles that results in a recoil type motion near $t=295$.  Finally,
+Finally, to further characterize the rotating dynamics of a doublet in the fluid trap, we
+compute and plot the vorticity and total force on a doublet with identical vesicles
+with reduced area $\Delta A=0.7$, adhesion length $\delta = 0.4$, Hamaker constant $\mathcal{H} = 0.7$, and
+extensional rate $\chi = 0.7$ in Figure~\ref{fig:extensionalVorticity}.
+Starting from a doublet inclination angle $\theta=\pi/2$, 
+the vesicle doublet slowly begins to rotate around $t\sim 265$
+(see the left plot of
+Figure~\ref{fig:extensionalInclinationAngle}).  We notice that the net force on each vesicle is almost 
+anti-parallel to the diverging flow in the
+far-field so to balance the hydrodynamic drag force that pulls the vesicles apart.
+
+Then, as the doublet
+starts to rotate, each vesicle experiences drag force from both up and down diverging streaming flows.
+For small extensional rate, the rotation will continue until $\theta = \pi$ so the doublet remains perfectly symmetric
+with respect to their mid-plane  and each vesicle experiences drag forces that cancel in both directions.
+For slightly higher extensional rate, we observe that the two vesicles slide against each other as the doublet rotate.
+The slight sliding motion leads to a transition in the contact region membrane shape from a bulging profile to a sigmoidal profile of nearly uniform height.
+This adjustment greatly reduces the net force on each vesicle, leading to an equilibrium configuration with an inclination angle $\theta < \pi$ as shown in 
+the left of Figure~\ref{fig:extensionalInclinationAngle}.  Finally,
 the vorticity and the flow between the vesicles approaches zero and the

### 2019-02-08 vesicle_code/docs/adhesion/adhesion.tex
yny's edits Friday night

@@
   the dot product of the adhesion force with the vector joining the
-  vesicles.  Therefore, the green and blue regions are repelled by the
-  other vesicle while the yellow regions are attracted to the other
+  vesicles.  Therefore, the green and yellow regions are repelled by the
+  other vesicle while the blue regions are attracted to the other
   vesicle.}
@@
 \begin{figure}[htp]
+    \includegraphics[width=0.25\textwidth]{figs/rotate1.pdf}
+    \hspace{20pt}
     \includegraphics[width=0.25\textwidth]{figs/angleDefinition.pdf}
-    \includegraphics[width=0.25\textwidth]{figs/rotate1.pdf}
+    \hspace{20pt}
     \includegraphics[width=0.25\textwidth]{figs/rotate2.pdf}
@@
   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
-  \caption{\label{fig:extensional1} A doublet inside a fluid trap.  The
-  reduced area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} =
-  0.7$, the adhesion length scale is $\delta = 0.4$, and the extensional
+  \caption{\label{fig:extensional1} A vesicle doublet in an extensional flow with an initial inclination angle $\theta=\pi/2$.  The
+  reduced area $\Delta A = 0.7$, the Hamaker constant $\mathcal{H} =
+  0.7$, the adhesion length scale $\delta = 0.4$, and the extensional
   rate $\chi = 0.02$ ({\em top}) and $\chi=0.7$ ({\em bottom}).  The center of the vesicle, denoted with a
@@
   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
-  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
-  The reduced area $\Delta A = 0.7$ ({\em top}) and $\Delta A=0.8$ ({\em bottom}). The Hamaker constant is $\mathcal{H} =
-  0.7$, the adhesion length scale is $\delta = 0.4$, and the extensional
+  \caption{\label{fig:extensional3} A vesicle doublet in an extensional flow with an initial inclination angle $\theta=\pi/2$.
+  The reduced area $\Delta A = 0.7$ ({\em top}) and $\Delta A=0.8$ ({\em bottom}). The Hamaker constant $\mathcal{H} =
+  0.7$, the adhesion length scale $\delta = 0.4$, and the extensional
   rate $\chi = 0.1$.  The center of the vesicle, denoted with a black
@@
 extensional rate $\chi = 0.7$ in Figure~\ref{fig:extensionalVorticity}.
-Starting from a doublet inclination angle $\theta=\pi/2$, 
-the vesicle doublet slowly begins to rotate around $t\sim 265$
+Starting from a vesicle doublet with an initial inclination angle $\theta=\pi/2$, 
+the doublet slowly begins to rotate around $t\sim 265$
 (see the left plot of
-Figure~\ref{fig:extensionalInclinationAngle}).  We notice that the net force on each vesicle is almost 
+Figure~\ref{fig:extensionalVorticity}).  We notice that the net force on each vesicle is almost 
 anti-parallel to the diverging flow in the

### 2019-02-09 vesicle_code/docs/adhesion/adhesion.tex
more changes by yny

@@
 \begin{figure}
-  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_00.jpeg}
-  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
-  \caption{\label{fig:Dec18_vesicle_shape} The equilibrium configuration
-  of a doublet of identical vesicles under adhesion in a quiescent flow.
+%  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_00.jpeg}
+%  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
+   \includegraphics[keepaspectratio=true,scale=0.5]{figs/Dec18_vesicle_shape_vs_rA_composite.png}
+  \caption{\label{fig:Dec18_vesicle_shape} Equilibrium configurations
+  of a doublet of identical vesicles under adhesion in a quiescent flow at three values of $\Delta A$.
   The vesicle reduced areas of $\Delta A=0.95$, $0.75$, and $0.6$ are

### 2019-02-10 vesicle_code/docs/adhesion/adhesion.tex
working on fig 14/15
fixed up figure 14

@@
 dense suspensions, and confined suspensions.
-Figure~\ref{fig:relaxationManyVes} illustrate snapshots of five vesicles
-suspended inside of a larger vesicle.  There is no imposed flow, so the
+Figure~\ref{fig:relaxationManyVes} shows an initial condition of five vesicles
+suspended inside of a larger vesicle, and the configuration and
+streamlines at an intermediate configuration.  There is no imposed flow, so the
 dynamics are governed entirely by the adhesion, bending, and tension
@@
 bounding membrane closely follow the interior membranes in order to
-minimize the adhesion energy.  In
-Figure~\ref{fig:relaxationManyVesAdhesionTension} we plot the tension
-(left) and adhesion (right) of the final equilibrium configuration.
-Both the vesicle shape, tension, and adhesion qualitatively agree with
-our doublet results.  In particular, the interior vesicles form a flat
+minimize the adhesion energy.   We also plot the tension (thrid) and
+adhesion (fourth) of the final equilibrium configuration.  Both the
+vesicle shape, tension, and adhesion qualitatively agree with our
+doublet results.  In particular, the interior vesicles form a flat
 contact region with a large negative tension.
+
+%\begin{figure}[htp]
+%  \centering
+%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot01.pdf}
+%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot02.pdf}
+%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot03.pdf}
+%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot04.pdf} \\
+%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot05.pdf}
+%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot06.pdf}
+%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot07.pdf}
+%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot08.pdf}
+%  \caption{\label{fig:relaxationManyVes} Five vesicles suspended inside
+%  a large vesicle.  The background flow is quiescent, the adhesion
+%  length scale is $\delta = 0.4$, and the Hamaker constant is
+%  $\mathcal{H} = 0.7$.  At the final snapshot, the suspension is near an
+%  equilibrium configuration.}
+%\end{figure}
 
@@
 \centering
-  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot01.pdf}
-  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot02.pdf}
-  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot03.pdf}
-  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot04.pdf} \\
-  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot05.pdf}
-  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot06.pdf}
-  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot07.pdf}
-  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot08.pdf}
-  \caption{\label{fig:relaxationManyVes} Five vesicles suspended inside
-  a large vesicle.  The background flow is quiescent, the adhesion
-  length scale is $\delta = 0.4$, and the Hamaker constant is
-  $\mathcal{H} = 0.7$.  At the final snapshot, the suspension is near an
-  equilibrium configuration.}
+\includegraphics[height=0.24\textwidth,trim={10cm 0cm 10cm 0cm},clip]{figs/relaxationManyVesInitialCondition.png}
+\includegraphics[height=0.24\textwidth,trim={2cm 0cm 2cm 0cm},clip]{figs/relaxationManyVesStreamlines.png}
+\includegraphics[height=0.24\textwidth,trim={2cm 0cm 1cm 0cm},clip]{figs/relaxationManyVesTension.png}
+\includegraphics[height=0.24\textwidth,trim={2cm 0cm 2cm 0cm},clip]{figs/relaxationManyVesAdhesion.png}
+\caption{\label{fig:relaxationManyVes} Five vesicles in a quiescent flow
+suspended in a bounding vesicle.   All vesicles are interacting through
+an adhesion potential with Hamaker constant $\mathcal{H} = 0.7$ and
+separation distance $\delta = 0.4$.  From left to right, the plots are
+the initial condition, streamlines and an intermediate time, tension at
+the steady-state configuration, and the adhesion force projected onto
+the outward unit normal at the steady-state configuration.  Along the
+bounding vesicle, the tension is largest and the adhesion is smallest in
+the regions that are well-separated from the interior vesicles.  Similar
+to other simulations, the interior vesicles are relatively flat and have
+a large negative tension in the contact regions.}
 \end{figure}
@@
 adhesion to keep vesicles bound under linear flows?
-
-\begin{figure}[htp]
-\centering
-\includegraphics[height=0.4\textwidth]{figs/relaxationManyVesTension.png}
-\includegraphics[height=0.4\textwidth]{figs/relaxationManyVesAdhesion.png}
-\caption{\label{fig:relaxationManyVesAdhesionTension} The tension ({\em
-left}) and adhesion force ({\em right}) of the final configuration from
-Figure~\ref{fig:relaxationManyVes}.  Along the bounding vesicle, the
-tension is largest and the adhesion is smallest in the regions that are
-well-separated from the interior vesicles.  Similar to other
-simulations, the interior vesicles are relatively flat and have a large
-negative tension in the contact regions.}
-\end{figure}
 

### 2019-02-10 vesicle_code/docs/adhesion/adhesion.tex
edits to intro

--- 2019-02-09 vesicle_code/docs/adhesion/adhesion.tex
@@
 
-\title{Hydrodynamics and rheology of an adhesive vesicle doublet}
+\title{Adhesion, hydrodynamics and rheology of vesicle doublets}
 % Force line breaks with \\
@@
 \begin{abstract}
-The dynamics of an adhesive vesicle doublet under various flowing conditions is
-investigated numerically using a high-order adaptive-in-time boundary
-integral equation formulation. In a quiescent flow, two nearby vesicles
+The dynamics of an adhesive vesicle doublet under various flow conditions is
+investigated numerically using a high-order, adaptive-in-time boundary
+integral method. In a quiescent flow, two nearby vesicles
 move slowly towards each other under the adhesive potential, pushing out
@@
 expanding applications have encouraged detailed experimental,
-theoretical, and numerical investigations of vesicle hydrodynamics in
-applied flow, electric fields, and magnetic fields.  Theoretical
+theoretical and numerical investigations of vesicle hydrodynamics in
+applied flow, electric and magnetic fields.  Theoretical
 investigations often take the form of small-deformation analysis or
@@
 been developed for simulating the transient hydrodynamics of vesicle
-suspensions~\cite{BagchiJohoson2005_JBE, Biben2005_EJP,
+suspensions e.g., \cite{BagchiJohoson2005_JBE, Biben2005_EJP,
 Veerapaneni2009_JCP, SeolHuKimLai2016_JCP}.
@@
 is also observed~\cite{Misbah2006_PRL, KantslerSegreSteinberg2008_PRL,
-ZhaoShaqfeh2011_JFM, SpannZhaoShaqfeh2014_PoF} to affect the effective
-shear viscosity in a different way.  In an extensional flow (planar or
+ZhaoShaqfeh2011_JFM, SpannZhaoShaqfeh2014_PoF} to alter the effective
+shear viscosity.  In an extensional flow (planar or
 uniaxial), vesicle shape dynamics depends sensitively on the vesicle
@@
 membranes without the molecular details of adhesive interactions between
-RBCs, Flormann {\em et al.}~found the contact zone to buckle under
-strong adhesion~\cite{FlormannAouane2017_SciReports}.  A direct
+RBCs, Flormann {\em et al.}~\cite{FlormannAouane2017_SciReports} found the contact zone to buckle under
+strong adhesion.  A direct
 consequence of the buckling is the sigmoidal shape of the adhesion
@@
 properties of a vesicle suspension. Such studies will provide useful
-insight to the rheology of blood flow and how to use nano solutes to
+insight into the rheology of blood flow and how to use nano solutes to
 control the hypertension by adjusting the adhesive interactions between
@@
 theory~\cite{ZiherlSvetina2007_PNAS}. The main goal of this work is to
-investigate the hydrodynamics of adhesive vesicles in flowing conditions
-common in microfluidic vesicle flow, such as a planar shear flow and an
+investigate the hydrodynamics of adhesive vesicles in flow conditions
+common in microfluidics such as a planar shear flow and an
 extensional flow.
@@
 between a vesicle and a substrate has been extensively studied with more
-focuses on the static equilibrium shapes~\cite{Seifert1990_PRA,
+focus on the static equilibrium shapes~\cite{Seifert1990_PRA,
 ShiFengGao2006_ActaMechSin, LinFreund2007_IntJSolidsStructures,
@@
 adhesion is crucial to initiate membrane fusion and fission in
-endocytosis and exocytosis, the transport of small vesicles through
+endocytosis and exocytosis and the transport of small vesicles through
 membrane surfaces.  In the absence of an external electric field and
@@
 in dimensionality and achieve high-order accuracy even for moving
-geometry problems. The BIE resolves the self-vesicle interaction using
-quadrature for logarithmically singular integrands~\cite{alp1999}, but
-as the vesicles adhere, the BIE solver must also resolve the
-vesicle-vesicle {\em nearly-singular} hydrodynamic forces.  We use an
-interpolation-based quadrature rule~\cite{qua-bir2014} to maintain
+geometry problems. When the vesicles adhere, one major issue for BIE solvers is to resolve the vesicle-vesicle hydrodynamic forces which become {\em nearly singular}. 
+We use an interpolation-based quadrature rule~\cite{qua-bir2014} to maintain
 high-order accuracy for all vesicle-vesicle separation distances.  To
 overcome the numerical stiffness induced by the membrane bending forces
-and to control the global error, we employ a high-order spectrally
+and to control the global error, we employ a high-order spectral
 deferred implicit-explicit adaptive time stepping
@@
 \centering
-\includegraphics[height=0.4\textwidth]{figs/relaxationManyVesTension.png}
-\includegraphics[height=0.4\textwidth]{figs/relaxationManyVesAdhesion.png}
+\fbox{
+\includegraphics[height=0.2\textwidth,trim={10cm 0cm 10cm 0cm},clip]    {figs/relaxationManyVesInitialCondition.png}
+}
+\fbox{
+\includegraphics[height=0.2\textwidth]{figs/relaxationManyVesTension.png}
+}
+\fbox{
+\includegraphics[height=0.2\textwidth]{figs/relaxationManyVesAdhesion.png}
+}
 \caption{\label{fig:relaxationManyVesAdhesionTension} The tension ({\em

### 2019-02-10 vesicle_code/docs/adhesion/adhesion.tex

@@
 adhesion to keep vesicles bound under linear flows?
-
-\begin{figure}[htp]
-\centering
-\fbox{
-\includegraphics[height=0.2\textwidth,trim={10cm 0cm 10cm 0cm},clip]    {figs/relaxationManyVesInitialCondition.png}
-}
-\fbox{
-\includegraphics[height=0.2\textwidth]{figs/relaxationManyVesTension.png}
-}
-\fbox{
-\includegraphics[height=0.2\textwidth]{figs/relaxationManyVesAdhesion.png}
-}
-\caption{\label{fig:relaxationManyVesAdhesionTension} The tension ({\em
-left}) and adhesion force ({\em right}) of the final configuration from
-Figure~\ref{fig:relaxationManyVes}.  Along the bounding vesicle, the
-tension is largest and the adhesion is smallest in the regions that are
-well-separated from the interior vesicles.  Similar to other
-simulations, the interior vesicles are relatively flat and have a large
-negative tension in the contact regions.}
-\end{figure}
 

### 2019-02-10 vesicle_code/docs/adhesion/adhesion.tex
separate sec 2

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Governing Equations \label{sec:ge}}
-We consider suspensions of locally inextensible vesicles in an unbounded
-two-dimensional viscous fluid.  For simplicity, we assume the fluid
-viscosity both inside and outside the vesicles is constant, but our
-method can be easily adjusted to account for a viscosity contrast.
-Individual vesicles are denoted as $\gamma_j$, $j=1,\ldots,M$, and they
-are parameterized in arclength as $\xx_j(s,t)$.  The union of all
-vesicles is denoted by $\gamma$.  Given a background velocity
-$\uu_\infty$, the governing equations are
-\begin{equation*}
-\begin{aligned}
-  \mu \Delta \uu = \nabla p, \quad &\xx \in \RR^2,
-    &&\mbox{\em conservation of momentum} \\
-  \nabla \cdot \uu = 0, \quad &\xx \in \RR^2, 
-    &&\mbox{\em conservation of mass} \\
-  \uu \rightarrow \uu_\infty, \quad &\|\xx\| \rightarrow \infty,
-    &&\mbox{\em far-field condition} \\
-  \uu(\xx,t) = \dot{\xx}, \quad &\xx \in \gamma,
-    &&\mbox{\em velocity continuity} \\
-  \xx_s \cdot \uu_s =0, \quad &\xx \in \gamma,
-    &&\mbox{\em local inextensibility} \\
-  \llbracket T \rrbracket \nn = \xxi, \quad &\xx \in \gamma,
-    &&\mbox{\em non-zero traction jump}
-\end{aligned}
-\end{equation*}
-where $\llbracket T \rrbracket$ is the jump in the stress tensor, and
-$\xxi$ is the traction jump that is the sum of the bending, stretching,
-and adhesion forces.  The bending force, arising from the Helfrich
-energy model, is $\BB \xx = -\kappa_b \xx_{ssss}$, where $\kappa_b$ is
-the bending rigidity modulus which we set to be 1 for all examples. The
-stretching force is $\TT \sigma = (\sigma \xx_s)_s$, where the tension,
-$\sigma$, acts as a Lagrange multiplier to satisfy the local
-extensibility constraint.  The resistance to bending and stretching are
-standard assumptions of vesicles.  In this work, we include an adhesive
-force, $\AA \xx$, that we now describe.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Adhesion Model}
-Sukumaran and Seifert~\cite{suk-sei2001} consider adhesion between a
-single three-dimensional vesicle and a solid wall at $z=0$.  They use
-the adhesion potential of the function form
-\begin{align}
-\label{eq:adhesion_potential}
-  \phi(z) = H \left[ 
-    \left(\frac{\delta}{z}\right)^m - \frac{m}{n} \left(\frac{\delta}{z}\right)^n \right],
-\end{align}
-where $z$ is the distance between the solid wall and the vesicle,
-$\mathcal{H}$ is the Hamaker constant, $\delta$ is the adhesion length
-scale, and $(m,n) = (4,2)$.  We generalize this model to an unbounded
-suspension of vesicles. We assume that the adhesion force applies
-between all pairs of points on different vesicles, so we are interested
-in Hamaker constants that are appropriate for lipid-lipid interactions.
-We use Hamaker constants ranging from $\mathcal{O}(10^{-1})$ to
-$\mathcal{O}(10^0)$ times the bending rigidity modulus.  In
-Appendix~\ref{sec:appendixA}, the adhesive force at a point $\xx$ on
-vesicle $j$ is shown to be
-\begin{align}
-  \AA\xx:=-\mathcal{H} m \delta^{n}\sum_{\substack{k=1 \\ k \neq j}}^M 
-  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+2}} 
-  \left(\delta^{m-n} - \|\xx - \yy\|^{m-n} \right) ds_\yy.
-  \label{eqn:adhesionForce}
-\end{align}
-The adhesion model is illustrated in Figure~\ref{fig:adhesionModel}.
-
-\begin{figure}[htp]
-  \begin{minipage}{0.31\textwidth}
-    \centering
-    \includegraphics[height=5cm,trim={0cm 0cm 2cm 0cm},clip]{figs/adhesionPotential.pdf}
-  \end{minipage}
-  \hfill
-  \begin{minipage}{0.31\textwidth}
-    \centering
-    \includegraphics[height=5cm]{figs/configCartoon.pdf}
-  \end{minipage}
-  \hfill
-  \begin{minipage}{0.31\textwidth}
-    \centering
-    \includegraphics[height=5cm,trim={3cm 0cm 2cm 0cm},clip]{figs/Adhesion_Force.png}
-  \end{minipage}
-  \caption{\label{fig:adhesionModel} {\em Left}: The adhesion potential
-  $\phi(z)$ in equation~\eqref{eq:adhesion_potential}.  Distances less
-  than $\delta$ are repulsive and distances greater than $\delta$ are
-  attractive.  {\em Center}: Each point on a vesicle is repelled or
-  attracted by all points on the other vesicles.  {\em Right}: The
-  resulting adhesive force is found by integrating over all points on
-  all other vesicles (equation~\eqref{eqn:adhesionForce}).  The color is
-  the dot product of the adhesion force with the vector joining the
-  vesicles.  Therefore, the green and yellow regions are repelled by the
-  other vesicle while the blue regions are attracted to the other
-  vesicle.}
-\end{figure}
-
-The exponents $(m,n)$ depend on the geometry of the two objects under
-adhesion~\cite{Book_IntermolecularSurfaceForces}: $(m,n)=(4,2)$
-corresponds to two flat, planar surfaces interacting with each under a
-long-range attraction and a short-range repulsion. On the other hand,
-$(m,n) = (12,6)$ corresponds to the L.-J.~potential between two molecules.
-In our case, the adhesion potential in the integral of
-equation~\eqref{eqn:adhesionForce} is between two small patches of lipid
-bilayer membrane (because the lipid molecules are coarse-grained in the
-continuum modeling).  Thus a reasonable choice for $(m,n)$ between two
-coarse-grained membrane patches would be between those for two planar
-surfaces and two point molecules.
-
-Large value of $m$ corresponds to a sharp increase in the repulsion
-force as two objects are within the separation distance $\delta$.  This
-poses a numerical challenge since the problem becomes stiff (i.e.,
-requires a very small time step) for large $m$.  The adaptive
-time-stepping BIE scheme makes it possible to simulate vesicle adhesive
-dynamics with specified numerical precision for reasonable computation
-time.  We explore several combinations of $(m,n)$ in the simulations of
-two vesicles forming a doublet in a quiescent flow.  We found very
-little difference in both the dynamic evolution and equilibrium
-configuration between $(m,n)=(8,6)$ and $(m,n)=(4,2)$.  Therefore, in
-this work, we use $(m,n) = (4,2)$ to regulate the stiffness introduced
-by the adhesive force.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Integral Equation Formulation}
-Because the fluid equations are linear and elliptic, a boundary integral
-equation formulation is possible.  This has several advantages,
-including that only the vesicle interfaces require discretization.  We
-start by defining the Stokes single-layer potential
-\begin{align}
-  \SS[\ff](\xx) &= \frac{1}{4\pi\mu} \int_\gamma \left(
-    -\log \rho + \frac{\rr \otimes \rr}{\rho^2} \right) 
-    \ff(\yy) ds_\yy, \quad \xx \in \RR^2,
-  \label{eqn:SLP}
-\end{align}
-where $\rr = \xx - \yy$ and $\rho = \|\rr\|$.  Then, given a vesicle
-with a traction jump $\xxi$, the fluid velocity is~\cite{poz1992}
-\begin{align*}
-  \uu(\xx) = \uu_{\infty}(\xx) + \SS[\xxi](\xx), \quad \xx \in \RR^2.
-\end{align*}
-The traction jump is
-\begin{align*}
-  \xxi = -\kappa_b \xx_{ssss} + (\sigma \xx_s)_s + \AA \xx,
-\end{align*}
-where the three terms correspond to the forces due to bending, tension,
-and adhesion, respectively.  Therefore, applying the no-slip boundary
-condition on each vesicle, the governing equations are
-\begin{align*}
-  &\dot{\xx} = \uu_{\infty}(\xx) + \SS[\xxi](\xx), \\
-  &\xx_s \cdot \uu_s = 0, \\
-  &\xxi = -\kappa_b \xx_{ssss} + (\sigma \xx_s)_s + \AA\xx.
-\end{align*}
-Defining the bending operator as $\BB[\xx](\ff) = -\kappa_b \ff_{ssss}$,
-and the tension operator $\TT[\xx](\sigma) = (\sigma \xx_s)_s$, the
-no-slip boundary condition gives
-\begin{align*}
-  \pderiv{\xx}{t} = \SS \BB \xx + \SS \TT \sigma + \SS \AA \xx.
-\end{align*}
-We apply the IMEX-Euler method 
-\begin{align*}
-  \frac{\xx^{N+1} - \xx^N}{\Delta t} = \SS^N \BB^N \xx^{N+1} + 
-  \SS^N \TT^N \sigma^{N+1} + \SS^N \AA^N \xx^N,
-\end{align*}
-that discretizes both the bending and tension terms
-semi-implicitly~\cite{qua-bir2014}, and the adhesive term explicitly.
-Therefore, a single time step requires solving
-\begin{align*}
-  \xx^{N+1} - \Delta t \SS^N \BB^N \xx^{N+1} - 
-    \Delta t \SS^N \TT^N \sigma^{N+1} = \xx^N + 
-    \Delta t \SS^N \AA^N \xx^N,
-\end{align*}
-along with the inextensibility constraint that is discretized as
-\begin{align*}
-  \xx_s^{N} \cdot \xx_{s}^{N+1} = 1.
-\end{align*}
-We discretize the vesicles at a set of collocation points, compute the
-bending and tension terms with Fourier differentiation, and apply Alpert
-quadrature~\cite{alp1999} to the weakly-singular single-layer potential
-$\SS$.  The source and target points of the adhesion force never
-coincide since they are always on different vesicles, so the adhesion
-force~\eqref{eqn:adhesionForce} is computed with the spectrally accurate
-trapezoid rule~\cite{tre-wei2014}.
-
-The dynamics of a doublet undergoes many different time scales over time
-horizons that are sufficiently large to characterize the formation of a
-doublet and its rheological properties.  Therefore, time adaptivity is
-crucial so that a user-specified tolerance is achieved without using a
-guess-and-check procedure to find an appropriately small fixed time step
-size.  To control the error and achieve second-order accuracy in time,
-we apply a time adaptive spectral deferred correction
-method~\cite{quaife2016adaptive}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The Shear and Normal Stresses}
-To characterize the rheological properties of the suspension of a
-doublet, it is necessary to compute the shear and normal stresses.  At a
-point $\xx \in \RR^2 \backslash \gamma$ in the fluid bulk, the velocity
-$\uu(\xx)$, pressure $p(\xx)$, and total stress tensor $T = - p I +
-\nabla \uu + \nabla \uu^T$ of the single-layer potential~\eqref{eqn:SLP}
-are
-\begin{align*}
-  \uu(\xx) &= \SS_\uu[\ff](\xx) = \frac{1}{4\pi\mu}\int_{\gamma} \left( 
-    -\log \rho + \frac{\rr \otimes \rr}{\rho^2} \right) 
-    \ff ds_\yy, \\
-    p(\xx) &= \SS_p[\ff](\xx) = \frac{1}{2\pi} \int_{\gamma} 
-    \frac{\rr \cdot \ff}{\rho^2} ds_\yy, \\
-    T(\xx) &= \SS_T[\ff](\xx) = -\frac{1}{\pi}\int_{\gamma}
-      \frac{\rr \cdot \ff}{\rho^2} 
-      \frac{\rr \otimes \rr}{\rho^2} ds_\yy.
-\end{align*}
-To compute the stress tensor on a vesicle, there is a jump in the layer
-potential $\SS_T$, and the stress tensor is
-\begin{align*}
-  T(\xx) = \frac{1}{2}(\nn \otimes \ff) + \frac{1}{2} \left(
-    \tt \otimes \left[
-    \begin{array}{cc}
-      2 t_x t_y & t_y^2 - t_x^2 \\
-      t_y^2 - t_x^2 & -2 t_x t_y
-    \end{array}
-    \right] \ff \right) + 
-  \SS_T[\ff](\xx), \quad \xx \in \gamma,
-\end{align*}
-where $\nn$ and $\tt$ are the vesicle's outward unit normal and tangent
-vector, respectively.  With the stress tensor computed for $\xx \in
-\gamma$, the shear and normal stresses are
-\begin{align*}
-  \tau^\tt = (T \nn) \cdot \tt, \qquad
-  \tau^\nn = (T \nn) \cdot \nn.
-\end{align*}
+\input{governing.tex}
 
@@
 
-YNY would like to acknowledge helpful discussions with blah blah blah.
-YNY acknowledges support from NSF-DMS 1614863 and 1412789, and Flatiron
-Institute, part of the Simons Foundation.  BQ acknowledges support from
-Florida State University startup funds and Simons Foundation Mathematics
+BQ acknowledges support from Florida State University startup funds and Simons Foundation Mathematics
 and Physical Sciences-Collaboration Grants for Mathematicians 527139.
+SV acknowledges support from NSF under grants DMS-1719834 and DMS-1454010.
+YNY acknowledges support from NSF-DMS 1614863 and 1412789. 
+The work of SV and YNY was also supported by the Flatiron Institute, a division of Simons Foundation.
 

### 2019-02-10 vesicle_code/docs/adhesion/governing.tex
separate sec 2

\section{Governing Equations \label{sec:ge}}
We consider suspensions of locally inextensible vesicles in an unbounded
two-dimensional viscous fluid.  For simplicity, we assume the fluid
viscosity both inside and outside the vesicles is constant, but our
method can be easily adjusted to account for a viscosity contrast.
Individual vesicles are denoted as $\gamma_j$, $j=1,\ldots,M$, and they
are parameterized in arclength as $\xx_j(s,t)$.  The union of all
vesicles is denoted by $\gamma$.  Given a background velocity
$\uu_\infty$, the governing equations are
\begin{equation*}
\begin{aligned}
  \mu \Delta \uu = \nabla p, \quad &\xx \in \RR^2,
    &&\mbox{\em conservation of momentum} \\
  \nabla \cdot \uu = 0, \quad &\xx \in \RR^2, 
    &&\mbox{\em conservation of mass} \\
  \uu \rightarrow \uu_\infty, \quad &\|\xx\| \rightarrow \infty,
    &&\mbox{\em far-field condition} \\
  \uu(\xx,t) = \dot{\xx}, \quad &\xx \in \gamma,
    &&\mbox{\em velocity continuity} \\
  \xx_s \cdot \uu_s =0, \quad &\xx \in \gamma,
    &&\mbox{\em local inextensibility} \\
  \llbracket T \rrbracket \nn = \xxi, \quad &\xx \in \gamma,
    &&\mbox{\em non-zero traction jump}
\end{aligned}
\end{equation*}
where $\llbracket T \rrbracket$ is the jump in the stress tensor, and
$\xxi$ is the traction jump that is the sum of the bending, stretching,
and adhesion forces.  The bending force, arising from the Helfrich
energy model, is $\BB \xx = -\kappa_b \xx_{ssss}$, where $\kappa_b$ is
the bending rigidity modulus which we set to be 1 for all examples. The
stretching force is $\TT \sigma = (\sigma \xx_s)_s$, where the tension,
$\sigma$, acts as a Lagrange multiplier to satisfy the local
extensibility constraint.  The resistance to bending and stretching are
standard assumptions of vesicles.  In this work, we include an adhesive
force, $\AA \xx$, that we now describe.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Adhesion Model}
Sukumaran and Seifert~\cite{suk-sei2001} consider adhesion between a
single three-dimensional vesicle and a solid wall at $z=0$.  They use
the adhesion potential of the function form
\begin{align}
\label{eq:adhesion_potential}
  \phi(z) = H \left[ 
    \left(\frac{\delta}{z}\right)^m - \frac{m}{n} \left(\frac{\delta}{z}\right)^n \right],
\end{align}
where $z$ is the distance between the solid wall and the vesicle,
$\mathcal{H}$ is the Hamaker constant, $\delta$ is the adhesion length
scale, and $(m,n) = (4,2)$.  We generalize this model to an unbounded
suspension of vesicles. We assume that the adhesion force applies
between all pairs of points on different vesicles, so we are interested
in Hamaker constants that are appropriate for lipid-lipid interactions.
We use Hamaker constants ranging from $\mathcal{O}(10^{-1})$ to
$\mathcal{O}(10^0)$ times the bending rigidity modulus.  In
Appendix~\ref{sec:appendixA}, the adhesive force at a point $\xx$ on
vesicle $j$ is shown to be
\begin{align}
  \AA\xx:=-\mathcal{H} m \delta^{n}\sum_{\substack{k=1 \\ k \neq j}}^M 
  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+2}} 
  \left(\delta^{m-n} - \|\xx - \yy\|^{m-n} \right) ds_\yy.
  \label{eqn:adhesionForce}
\end{align}
The adhesion model is illustrated in Figure~\ref{fig:adhesionModel}.

\begin{figure}[htp]
  \begin{minipage}{0.31\textwidth}
    \centering
    \includegraphics[height=5cm,trim={0cm 0cm 2cm 0cm},clip]{figs/adhesionPotential.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.31\textwidth}
    \centering
    \includegraphics[height=5cm]{figs/configCartoon.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.31\textwidth}
    \centering
    \includegraphics[height=5cm,trim={3cm 0cm 2cm 0cm},clip]{figs/Adhesion_Force.png}
  \end{minipage}
  \caption{\label{fig:adhesionModel} {\em Left}: The adhesion potential
  $\phi(z)$ in equation~\eqref{eq:adhesion_potential}.  Distances less
  than $\delta$ are repulsive and distances greater than $\delta$ are
  attractive.  {\em Center}: Each point on a vesicle is repelled or
  attracted by all points on the other vesicles.  {\em Right}: The
  resulting adhesive force is found by integrating over all points on
  all other vesicles (equation~\eqref{eqn:adhesionForce}).  The color is
  the dot product of the adhesion force with the vector joining the
  vesicles.  Therefore, the green and yellow regions are repelled by the
  other vesicle while the blue regions are attracted to the other
  vesicle.}
\end{figure}

The exponents $(m,n)$ depend on the geometry of the two objects under
adhesion~\cite{Book_IntermolecularSurfaceForces}: $(m,n)=(4,2)$
corresponds to two flat, planar surfaces interacting with each under a
long-range attraction and a short-range repulsion. On the other hand,
$(m,n) = (12,6)$ corresponds to the L.-J.~potential between two molecules.
In our case, the adhesion potential in the integral of
equation~\eqref{eqn:adhesionForce} is between two small patches of lipid
bilayer membrane (because the lipid molecules are coarse-grained in the
continuum modeling).  Thus a reasonable choice for $(m,n)$ between two
coarse-grained membrane patches would be between those for two planar
surfaces and two point molecules.

Large value of $m$ corresponds to a sharp increase in the repulsion
force as two objects are within the separation distance $\delta$.  This
poses a numerical challenge since the problem becomes stiff (i.e.,
requires a very small time step) for large $m$.  The adaptive
time-stepping BIE scheme makes it possible to simulate vesicle adhesive
dynamics with specified numerical precision for reasonable computation
time.  We explore several combinations of $(m,n)$ in the simulations of
two vesicles forming a doublet in a quiescent flow.  We found very
little difference in both the dynamic evolution and equilibrium
configuration between $(m,n)=(8,6)$ and $(m,n)=(4,2)$.  Therefore, in
this work, we use $(m,n) = (4,2)$ to regulate the stiffness introduced
by the adhesive force.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Integral Equation Formulation}
Because the fluid equations are linear and elliptic, a boundary integral
equation formulation is possible.  This has several advantages,
including that only the vesicle interfaces require discretization.  We
start by defining the Stokes single-layer potential
\begin{align}
  \SS[\ff](\xx) &= \frac{1}{4\pi\mu} \int_\gamma \left(
    -\log \rho + \frac{\rr \otimes \rr}{\rho^2} \right) 
    \ff(\yy) ds_\yy, \quad \xx \in \RR^2,
  \label{eqn:SLP}
\end{align}
where $\rr = \xx - \yy$ and $\rho = \|\rr\|$.  Then, given a vesicle
with a traction jump $\xxi$, the fluid velocity is~\cite{poz1992}
\begin{align*}
  \uu(\xx) = \uu_{\infty}(\xx) + \SS[\xxi](\xx), \quad \xx \in \RR^2.
\end{align*}
The traction jump is
\begin{align*}
  \xxi = -\kappa_b \xx_{ssss} + (\sigma \xx_s)_s + \AA \xx,
\end{align*}
where the three terms correspond to the forces due to bending, tension,
and adhesion, respectively.  Therefore, applying the no-slip boundary
condition on each vesicle, the governing equations are
\begin{align*}
  &\dot{\xx} = \uu_{\infty}(\xx) + \SS[\xxi](\xx), \\
  &\xx_s \cdot \uu_s = 0, \\
  &\xxi = -\kappa_b \xx_{ssss} + (\sigma \xx_s)_s + \AA\xx.
\end{align*}
Defining the bending operator as $\BB[\xx](\ff) = -\kappa_b \ff_{ssss}$,
and the tension operator $\TT[\xx](\sigma) = (\sigma \xx_s)_s$, the
no-slip boundary condition gives
\begin{align*}
  \pderiv{\xx}{t} = \SS \BB \xx + \SS \TT \sigma + \SS \AA \xx.
\end{align*}
We apply the IMEX-Euler method 
\begin{align*}
  \frac{\xx^{N+1} - \xx^N}{\Delta t} = \SS^N \BB^N \xx^{N+1} + 
  \SS^N \TT^N \sigma^{N+1} + \SS^N \AA^N \xx^N,
\end{align*}
that discretizes both the bending and tension terms
semi-implicitly~\cite{qua-bir2014}, and the adhesive term explicitly.
Therefore, a single time step requires solving
\begin{align*}
  \xx^{N+1} - \Delta t \SS^N \BB^N \xx^{N+1} - 
    \Delta t \SS^N \TT^N \sigma^{N+1} = \xx^N + 
    \Delta t \SS^N \AA^N \xx^N,
\end{align*}
along with the inextensibility constraint that is discretized as
\begin{align*}
  \xx_s^{N} \cdot \xx_{s}^{N+1} = 1.
\end{align*}
We discretize the vesicles at a set of collocation points, compute the
bending and tension terms with Fourier differentiation, and apply Alpert
quadrature~\cite{alp1999} to the weakly-singular single-layer potential
$\SS$.  The source and target points of the adhesion force never
coincide since they are always on different vesicles, so the adhesion
force~\eqref{eqn:adhesionForce} is computed with the spectrally accurate
trapezoid rule~\cite{tre-wei2014}.

The dynamics of a doublet undergoes many different time scales over time
horizons that are sufficiently large to characterize the formation of a
doublet and its rheological properties.  Therefore, time adaptivity is
crucial so that a user-specified tolerance is achieved without using a
guess-and-check procedure to find an appropriately small fixed time step
size.  To control the error and achieve second-order accuracy in time,
we apply a time adaptive spectral deferred correction
method~\cite{quaife2016adaptive}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Shear and Normal Stresses}
To characterize the rheological properties of the suspension of a
doublet, it is necessary to compute the shear and normal stresses.  At a
point $\xx \in \RR^2 \backslash \gamma$ in the fluid bulk, the velocity
$\uu(\xx)$, pressure $p(\xx)$, and total stress tensor $T = - p I +
\nabla \uu + \nabla \uu^T$ of the single-layer potential~\eqref{eqn:SLP}
are
\begin{align*}
  \uu(\xx) &= \SS_\uu[\ff](\xx) = \frac{1}{4\pi\mu}\int_{\gamma} \left( 
    -\log \rho + \frac{\rr \otimes \rr}{\rho^2} \right) 
    \ff ds_\yy, \\
    p(\xx) &= \SS_p[\ff](\xx) = \frac{1}{2\pi} \int_{\gamma} 
    \frac{\rr \cdot \ff}{\rho^2} ds_\yy, \\
    T(\xx) &= \SS_T[\ff](\xx) = -\frac{1}{\pi}\int_{\gamma}
      \frac{\rr \cdot \ff}{\rho^2} 
      \frac{\rr \otimes \rr}{\rho^2} ds_\yy.
\end{align*}
To compute the stress tensor on a vesicle, there is a jump in the layer
potential $\SS_T$, and the stress tensor is
\begin{align*}
  T(\xx) = \frac{1}{2}(\nn \otimes \ff) + \frac{1}{2} \left(
    \tt \otimes \left[
    \begin{array}{cc}
      2 t_x t_y & t_y^2 - t_x^2 \\
      t_y^2 - t_x^2 & -2 t_x t_y
    \end{array}
    \right] \ff \right) + 
  \SS_T[\ff](\xx), \quad \xx \in \gamma,
\end{align*}
where $\nn$ and $\tt$ are the vesicle's outward unit normal and tangent
vector, respectively.  With the stress tensor computed for $\xx \in
\gamma$, the shear and normal stresses are
\begin{align*}
  \tau^\tt = (T \nn) \cdot \tt, \qquad
  \tau^\nn = (T \nn) \cdot \nn.
\end{align*}

### 2019-02-11 vesicle_code/docs/adhesion/adhesion.tex
changes by yny on Feb 11

@@
 
-\title{Adhesion, hydrodynamics and rheology of vesicle doublets}
+\title{Hydrodynamics and rheology of adhesive vesicle doublets}
 % Force line breaks with \\
@@
 undulation~\cite{SteinkuhlerAgudo-Canalejo2016_BJ}.
-
-Future work includes three dimensional simulations, viscosity contrast,
-dense suspensions, and confined suspensions.
-Figure~\ref{fig:relaxationManyVes} shows an initial condition of five vesicles
-suspended inside of a larger vesicle, and the configuration and
-streamlines at an intermediate configuration.  There is no imposed flow, so the
+In addition, simulations presented in this work are for identical vesicles (same reduced area, length, and
+bending rigidity modulus) in the doublet. Flormann {\it et al.} demonstrated that asymmetric vesicle reduced area
+may lead to various equilibrium doublet shape such as male-female, asymmetric S-shape and parachute shape.
+It is also possible that viscosity contrast may also lead to slightly different equilibrium doublet shape.
+Future work includes three dimensional simulations, dispersive vesicle properties (such as
+reduced area and bending modulus), viscosity contrast, and effects of confinement on adhesive interactions.
+
+Flormann {\it et al.} studied the clustering and packing of vesicles in free suspension~\cite{FlormannAouane2017_SciReports}. 
+In engineering applications of vesicle emulsions
+often smaller vesicles are enclosed in a big vesicle, as shown in 
+Figure~\ref{fig:relaxationManyVes}, where  the left panel shows an initial condition of five vesicles
+suspended inside of a larger vesicle.
+The second panel from left shows the membrane configuration and flow
+streamlines at an intermediate time.  There is no imposed flow, so the
 dynamics are governed entirely by the adhesion, bending, and tension
@@
 bounding membrane closely follow the interior membranes in order to
-minimize the adhesion energy.   We also plot the tension (thrid) and
-adhesion (fourth) of the final equilibrium configuration.  Both the
-vesicle shape, tension, and adhesion qualitatively agree with our
-doublet results.  In particular, the interior vesicles form a flat
+minimize the adhesion energy.   As a result of force balance the equilibrium shape of the bounding vesicle
+is far from a symmetric shape while the interior smaller vesicles are of similar shape to each other.
+We also plot the tension (thrid) and
+adhesion (fourth) of the final equilibrium configuration.  
+We remark that the adhesion force is all attractive on all the vesicle membranes while large positive
+membrane tension is found only on the bounding vesicle. 
+%Both the
+%vesicle shape, tension, and adhesion qualitatively agree with our
+%doublet results.  
+In particular, the interior vesicles form a flat
 contact region with a large negative tension.
+We are now conducting simulations of such vesicle configuration under a planar shear flow.
 
@@
 \caption{\label{fig:relaxationManyVes} Five vesicles in a quiescent flow
-suspended in a bounding vesicle.   All vesicles are interacting through
+suspended in a bounding vesicle.   All vesicles are interacting through hydrodynamic flow and
 an adhesion potential with Hamaker constant $\mathcal{H} = 0.7$ and

### 2019-02-11 vesicle_code/docs/adhesion/adhesion.tex
changes by yny on Feb 11

@@
 For slightly higher extensional rate, we observe that the two vesicles slide against each other as the doublet rotate.
-The slight sliding motion leads to a transition in the contact region membrane shape from a bulging profile to a sigmoidal profile of nearly uniform height.
+The slight sliding motion leads to a transition in the contact region membrane shape from a bulging profile to 
+an S-shape profile of nearly uniform height except near the edge of contact region.
 This adjustment greatly reduces the net force on each vesicle, leading to an equilibrium configuration with an inclination angle $\theta < \pi$ as shown in 

### 2019-02-11 vesicle_code/docs/adhesion/adhesion.tex
working on extensional

@@
    \includegraphics[keepaspectratio=true,scale=0.5]{figs/Dec18_vesicle_shape_vs_rA_composite.png}
-  \caption{\label{fig:Dec18_vesicle_shape} Equilibrium configurations
-  of a doublet of identical vesicles under adhesion in a quiescent flow at three values of $\Delta A$.
-  The vesicle reduced areas of $\Delta A=0.95$, $0.75$, and $0.6$ are
-  labeled.  The color coding is the tension along the vesicle.  The
-  vesicle length is fixed at $2\pi$, the dimensionless bending rigidity
-  modulus is $\kappa_b=1$, the Hamaker constant is $\mathcal{H}=5$, and
-  the separation distance is $\delta=0.2$.  {\em Left}: The overall
-  equilibrium shapes of two vesicles under adhesive interactions vary
-  with the reduced area.  {\em Right}: The membrane shapes in the
-  contact region.} 
+  \caption{\label{fig:Dec18_vesicle_shape} Equilibrium configurations of
+  a doublet of identical vesicles under adhesion in a quiescent flow at
+  three values of $\Delta A$.  The vesicle reduced areas of $\Delta
+  A=0.95$, $0.75$, and $0.6$ are labeled.  The color coding is the
+  tension along the vesicle.  The vesicle length is fixed at $2\pi$, the
+  dimensionless bending rigidity modulus is $\kappa_b=1$, the Hamaker
+  constant is $\mathcal{H}=5$, and the separation distance is
+  $\delta=0.2$.  {\em Left}: The overall equilibrium shapes of two
+  vesicles under adhesive interactions vary with the reduced area.  {\em
+  Right}: The membrane shapes in the contact region.} 
 \end{figure}
@@
 between two bound vesicle membranes, we propose the following thought
-experiment.
+experiment.  Beginning with two identical vesicles in an equilibrium
+configuration that form a doublet with a flat contact region
+(Figure~\ref{fig:Dec18_vesicle_shape}), we turn on the fluid trap with
+the stagnation point placed at the center of the vesicle doublet.
+Depending on the Hamaker constant, we expect that either the flow
+overcomes the adhesive force and the doublet is broken, or the adhesive
+force dominates and the doublet reaches a stable stationary
+configuration.
 
@@
 
-We begin with two identical vesicles forming a doublet under an
-adhesion potential in a quiescent flow as described in
-Section~\ref{sec:qflow}.  Once a doublet forms and reaches an
-equilibrium configuration, we turn on the fluid trap with the stagnation
-point placed at the center of the vesicle doublet, which has a flat contact region as shown in \S~\ref{sec:qflow}. 
-Based on how the contact region aligns with the extensional flow, 
-we can define the inclination angle of the vesicle doublet as illustrated in Figure~\ref{fig:InclinationAngle}.
-%
-
-When $\theta=\pi$ (the doublet long axis is aligned with the far-field diverging flow), the converging flow
-pushes vesicles towards each other and the short-range repulsive force is essential to keep the two vesicles at the separation distance.
-With the converging flow pushing the two vesicles towards the stagnation point dynamically placed at the doublet center, 
-this configuration is expected to be more stable than the $\theta=\pi/2$ configuration in the middle of Figure~\ref{fig:InclinationAngle},  where  
-the doublet long axis is parallel to the converging direction. This is because
-when $\theta=\pi/2$ the diverging flow is pulling the vesicles away from each other as shown in the illustration. 
-If the doublet inclination angle is fixed at $\theta=\pi/2$,
-the vesicle doublet stays intact only when the adhesive force is strong enough to dominate over the fluid drag in this configuration.
-Thus it is possible that the diverging flow may overcome adhesion and
-break up the doublet. It is also reasonable to expect a vesicle doublet to rotate from $\theta=\pi/2$ to $\theta=\pi$,
-such that the fluid flow is pushing them together rather than pulling them apart.
-
-In the following numerical experiments we place a vesicle doublet with $\theta=\pi/2$, so that
-the diverging flow may be strong enough to pull vesicles away from the doublet.
-%In this configuration the flow is pulling the vesicles away from each other, and 
-%is expected to be less stable than the $\theta=\pi$ configuration where the fluid flow is constantly pushing vesicles towards each other. 
-%
-At low extensional
-rates, we expect the $\theta=\pi/2$ doublet to stay bound at the fluid
-trap stagnation point.  On the other hand, the vesicle doublet may
-become unstable and eventually separate at higher extensional rates.
-Thus we expect there to exist a critical extensional rate $\chi_c$ above which
-the vesicle doublet cannot stay bound under a given adhesion potential.
-Therefore, the dependence of the critical extensional rate $\chi_c$ on the
-adhesion potential and the mechanical vesicle properties provides a
-means to probe the physics of membrane adhesion.
+In the following numerical experiments we initially place a vesicle
+doublet with $\theta=\pi$, so that the diverging flow may be strong
+enough to pull vesicles away from the doublet.  At low extensional
+rates, we expect the doublet to stay bound at the fluid trap stagnation
+point.  On the other hand, the vesicle doublet may become unstable and
+eventually separate at higher extensional rates.  Thus we expect there
+to exist a critical extensional rate $\chi_c$ above which the vesicle
+doublet cannot stay bound under a given adhesion potential.  Therefore,
+the dependence of the critical extensional rate $\chi_c$ on the adhesion
+potential and the mechanical vesicle properties provides a means to
+probe the physics of membrane adhesion.
+
+Based on how the contact region aligns with the extensional flow, we can
+define the inclination angle of the vesicle doublet as illustrated in
+Figure~\ref{fig:InclinationAngle}. When $\theta=\pi$ (the doublet long
+axis is aligned with the far-field converging flow), the diverging flow
+pulls the vesicles apart from each other and the short-range repulsive
+force is essential to keep the two vesicles from separating.  In
+contrast, when $\theta = \pi/2$ (the doublet long axis is aligned with
+the diverging flow), the converging flow pushes the vesicles towards
+each other and the short-range repulsive force is essential to keep the
+two vesicles at the separation distance.  With the converging flow
+pushing the two vesicles towards the stagnation point dynamically placed
+at the doublet center, this configuration is expected to be more stable
+than the $\theta=\pi$ configuration in the left of
+Figure~\ref{fig:InclinationAngle}, where the doublet long axis is
+parallel to the converging direction. This is because when $\theta=\pi$
+the diverging flow is pulling the vesicles away from each other as shown
+in the illustration.  If the doublet inclination angle is fixed at
+$\theta=\pi/2$, the vesicle doublet stays intact only when the adhesive
+force is strong enough to dominate over the fluid drag in this
+configuration \todo[inline]{I don't follow this sentence}.  Thus it is
+possible that the diverging flow may overcome adhesion and break up the
+doublet. It is also reasonable to expect a vesicle doublet to rotate
+from $\theta=\pi$ to $\theta=\pi/2$, such that the fluid flow is pushing
+them together rather than pulling them apart.
 
@@
 point can be controlled in an experimental
-setting~\cite{Johnson-Chavarria2011_EMJ}, we mimic the active control
-algorithm in the microfluidic experiments by moving the center of the
-doublet at each time step so that the stagnation point occurs exactly in
-the middle of the doublet.  
-With this adjustment, the vesicles either
-remain as a doublet in the fluid trap centered around the stagnation
-point, or the doublet is broken and the vesicles separate from one
-another.
-
-In Figures~\ref{fig:extensional1},
-snapshots of a fluid trap containing a vesicle doublet of reduced area
-$\Delta A = 0.7$ are simulated at different extensional rates.  While
-this doublet remains bound for all the
-considered extensional rates, a doublet with a reduced area of $\Delta A
-= 0.8$ is split with a critical extensional rate $\chi_c =0.1$
-(bottom row in Figure~\ref{fig:extensional3}).  
-%
+setting~\cite{Johnson-Chavarria2011_EMJ}, we mimic the active control of
+the microfluidic experiments by moving the center of the doublet at each
+time step so that the stagnation point occurs exactly in the middle of
+the doublet.  With this adjustment, the vesicles either remain as a
+doublet in the fluid trap centered around the stagnation point, or the
+doublet is broken and the vesicles separate from one another.
+
+In Figures~\ref{fig:extensional1}, snapshots of a fluid trap containing
+a vesicle doublet of reduced area $\Delta A = 0.7$ are simulated at
+three different extensional rates.  While this doublet remains bound for
+all the considered extensional rates, a doublet with a reduced area of
+$\Delta A = 0.8$ is split with a critical extensional rate $\chi_c =0.1$
+(Figure~\ref{fig:extensional3}).  For extensional rates and reduced
+areas that result in a bound vesicle doublet, we observe that the
+doublet always rotates from $\theta=\pi$ configuration towards the more
+stable $\theta=\pi/s$ configuration, as shown in
+Figures~\ref{fig:extensional1}.  We also observe that in most cases with
+moderate extensional flow rates the doublet falls short of aligning
+their long axis with the diverging direction.
+
 \begin{figure}[htp]
@@
   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
-  \caption{\label{fig:extensional1} A vesicle doublet in an extensional flow with an initial inclination angle $\theta=\pi/2$.  The
-  reduced area $\Delta A = 0.7$, the Hamaker constant $\mathcal{H} =
-  0.7$, the adhesion length scale $\delta = 0.4$, and the extensional
-  rate $\chi = 0.02$ ({\em top}) and $\chi=0.7$ ({\em bottom}).  The center of the vesicle, denoted with a
-  black square, is a stagnation point.}
-  \end{figure}
-  %
-  For extensional rates and reduced areas that result in a bound vesicle doublet, 
-we observe that the doublet always rotate from $\theta=\pi/2$ configuration towards
-the more stable $\theta=\pi$ configuration, as shown in Figures~\ref{fig:extensional1}--\ref{fig:extensional3}.
-We also observe that in most cases with moderate extensional flow rates the doublet falls short of 
-aligning their long axis with the diverging direction.
-
-%  \begin{figure}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
-%  \caption{\label{fig:extensional2} A doublet inside a fluid trap.  The
-%  reduced area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H}
-%  = 0.7$, the adhesion length scale is $\delta = 0.4$, and the
-%  extensional rate is $\chi = 0.07$.  The center of the vesicle, denoted
-%  with a black square, is a stagnation point.}
-%  \end{figure}
-
- \begin{figure}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png} \\
   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
@@
   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}\\
+  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
+  \caption{\label{fig:extensional1} A vesicle doublet in an extensional
+  flow with an initial inclination angle $\theta=\pi/2$.  The reduced
+  area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} = 0.7$,
+  the separation distance is $\delta = 0.4$, and the extensional rate is
+  $\chi = 0.02$ ({\em top}), $\chi=0.07$ ({\em middle}), and $\chi =
+  0.1$ ({\em bottom}).  The center of the vesicle, denoted with a black
+  square, is a stagnation point.}
+  \end{figure}
+
+ \begin{figure}
     \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
@@
 extensional rate.
-%\begin{figure}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
-%  \caption{\label{fig:extensional4} A doublet broken by an extensional
-%  flow.  The reduced area is $\Delta A = 0.8$, the Hamaker constant is
-%  $\mathcal{H} = 0.7$, the adhesion length scale is $\delta = 0.4$, and
-%  the extensional rate is $\chi = 0.1$.  Initially, the doublet tilts to
-%  an inclination angle, and then the extensional rate overcomes the
-%  adhesive force and the doublet is broken.  The center of the vesicle,
-%  denoted with a black square, is a stagnation point.}
-%\end{figure}
-We summarize the final inclination angle of the
-doublet in the right plot of Figure~\ref{fig:extensionalInclinationAngle}.
-The size of the round dots are scaled to the final inclination angle as
-defined in the right plot.  At smaller extensional rates, the vesicles
-come closer to aligning their long axis with the diverging direction.
-When the doublet is broken at reduced area $\Delta A = 0.80$, the
-extensional rate is sufficiently large to align the long axis of the
-vesicle with the diverging direction and then the vesicles separate
-(bottom row in Figure~\ref{fig:extensional3}).  For very low extensional rates, the
+
+We summarize the final inclination angle of the doublet in the right
+plot of Figure~\ref{fig:extensionalInclinationAngle}.  The size of the
+round dots are scaled to the final inclination angle as defined in the
+right plot.  At smaller extensional rates, the vesicles come closer to
+aligning their long axis with the diverging direction.  When the doublet
+is broken at reduced area $\Delta A = 0.80$, the extensional rate is
+sufficiently large to align the long axis of the vesicle with the
+diverging direction and then the vesicles separate (bottom row in
+Figure~\ref{fig:extensional3}).  For very low extensional rates, the
 time horizon is insufficient for the doublet to reach an equilibrium
-state, and these simulations are marked with a square.
-%
-The right plot of Figure~\ref{fig:extensionalInclinationAngle} 
-also summarizes the  reduced areas and
-extensional rates that result in a bound vesicle doublet in a fluid trap: Parameter values with a blue
-mark result in a fluid trap and parameter values with a red mark result
-in vesicle separation.
-
-%\begin{figure}[htp]
-%  \begin{minipage}{0.53\textwidth}
-%    \includegraphics[width=0.33\textwidth]{figs/angleDefinition.pdf} \:
-%    \includegraphics[width=0.34\textwidth]{figs/rotate1.pdf} \:
-%    \includegraphics[width=0.26\textwidth]{figs/rotate2.pdf}
-%  \end{minipage}
-%  \hfill
-%  \begin{minipage}{0.45\textwidth}
-%    \centering
-%    \includegraphics[width=0.8\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
-%  \end{minipage}
-%  \caption{\label{fig:extensionalPhaseDiagram}  A phase diagram of the long-time
-%  behavior of a fluid trap formed by two adhering vesicles in an
-%  extensional flow.  The Hamaker constant is $\mathcal{H}=0.7$ and the
-%  adhesion length scale is $\delta = 0.4$.  For small extensional rates,
-%  the doublet structure is not broken (blue marks), while at large
-%  extensional rates, the doublet is broken (red marks).  The size of the
-%  round blue marks indicates the final inclination angle with the larger
-%  dots rotating less ($\theta=\pi$) and the smaller dots rotating more
-%  ($\theta = \pi/2$).  A square mark is used for simulations that did
-%  not result in an equilibrium inclination angle in the given time
-%  horizon.}
-%\end{figure}
+state, and these simulations are marked with a square.  The right plot
+of Figure~\ref{fig:extensionalInclinationAngle} also summarizes the
+reduced areas and extensional rates that result in a bound vesicle
+doublet in a fluid trap: Parameter values with a blue mark result in a
+fluid trap and parameter values with a red mark result in vesicle
+separation.
 
@@
 
-Finally, to further characterize the rotating dynamics of a doublet in the fluid trap, we
-compute and plot the vorticity and total force on a doublet with identical vesicles
-with reduced area $\Delta A=0.7$, adhesion length $\delta = 0.4$, Hamaker constant $\mathcal{H} = 0.7$, and
-extensional rate $\chi = 0.7$ in Figure~\ref{fig:extensionalVorticity}.
-Starting from a vesicle doublet with an initial inclination angle $\theta=\pi/2$, 
-the doublet slowly begins to rotate around $t\sim 265$
-(see the left plot of
-Figure~\ref{fig:extensionalVorticity}).  We notice that the net force on each vesicle is almost 
-anti-parallel to the diverging flow in the
-far-field so to balance the hydrodynamic drag force that pulls the vesicles apart.
-
-Then, as the doublet
-starts to rotate, each vesicle experiences drag force from both up and down diverging streaming flows.
-For small extensional rate, the rotation will continue until $\theta = \pi$ so the doublet remains perfectly symmetric
-with respect to their mid-plane  and each vesicle experiences drag forces that cancel in both directions.
-For slightly higher extensional rate, we observe that the two vesicles slide against each other as the doublet rotate.
-The slight sliding motion leads to a transition in the contact region membrane shape from a bulging profile to 
-an S-shape profile of nearly uniform height except near the edge of contact region.
-This adjustment greatly reduces the net force on each vesicle, leading to an equilibrium configuration with an inclination angle $\theta < \pi$ as shown in 
-the left of Figure~\ref{fig:extensionalInclinationAngle}.  Finally,
-the vorticity and the flow between the vesicles approaches zero and the
-result is a fluid trap containing the doublet.
+Finally, to further characterize the rotating dynamics of a doublet in
+the fluid trap, we compute and plot the vorticity and total force on a
+doublet with identical vesicles with reduced area $\Delta A=0.7$,
+adhesion length $\delta = 0.4$, Hamaker constant $\mathcal{H} = 0.7$,
+and extensional rate $\chi = 0.7$ in
+Figure~\ref{fig:extensionalVorticity}.  Starting from a vesicle doublet
+with an initial inclination angle $\theta=\pi/2$, the doublet slowly
+begins to rotate around $t\sim 265$ (see the left plot of
+Figure~\ref{fig:extensionalVorticity}).  We notice that the net force on
+each vesicle is almost anti-parallel to the diverging flow in the
+far-field so to balance the hydrodynamic drag force that pulls the
+vesicles apart.
+
+Then, as the doublet starts to rotate, each vesicle experiences drag
+force from both up and down diverging streaming flows.  For small
+extensional rate, the rotation will continue until $\theta = \pi$ so the
+doublet remains perfectly symmetric with respect to their mid-plane  and
+each vesicle experiences drag forces that cancel in both directions.
+For slightly higher extensional rate, we observe that the two vesicles
+slide against each other as the doublet rotate.  The slight sliding
+motion leads to a transition in the contact region membrane shape from a
+bulging profile to an S-shape profile of nearly uniform height except
+near the edge of contact region.  This adjustment greatly reduces the
+net force on each vesicle, leading to an equilibrium configuration with
+an inclination angle $\theta < \pi$ as shown in the left of
+Figure~\ref{fig:extensionalInclinationAngle}.  Finally, the vorticity
+and the flow between the vesicles approaches zero and the result is a
+fluid trap containing the doublet.
 \begin{figure}[htp]

### 2019-02-12 vesicle_code/docs/adhesion/adhesion.tex
finished first round of revisions on extenional example

@@
    parallel to the diverging direction.  The square mark is a stagnation
-   point and the round point is located at the center of the vesicle.}
+   point and the round point is located at the center of the vesicle.
+   The initial configurations in this section all have an initial
+   configuration of $\theta = \pi$.}
    \end{figure}
@@
 doublet in the fluid trap centered around the stagnation point, or the
-doublet is broken and the vesicles separate from one another.
-
-In Figures~\ref{fig:extensional1}, snapshots of a fluid trap containing
-a vesicle doublet of reduced area $\Delta A = 0.7$ are simulated at
-three different extensional rates.  While this doublet remains bound for
-all the considered extensional rates, a doublet with a reduced area of
+doublet is broken and the vesicles separate from one another.  In
+Figures~\ref{fig:extensional1}, snapshots of a fluid trap containing a
+vesicle doublet of reduced area $\Delta A = 0.7$ are simulated at three
+different extensional rates.  While this doublet remains bound for all
+the considered extensional rates, a doublet with a reduced area of
 $\Delta A = 0.8$ is split with a critical extensional rate $\chi_c =0.1$
@@
 doublet always rotates from $\theta=\pi$ configuration towards the more
-stable $\theta=\pi/s$ configuration, as shown in
+stable $\theta=\pi/2$ configuration, as shown in
 Figures~\ref{fig:extensional1}.  We also observe that in most cases with
@@
   \caption{\label{fig:extensional1} A vesicle doublet in an extensional
-  flow with an initial inclination angle $\theta=\pi/2$.  The reduced
+  flow with an initial inclination angle $\theta=\pi$.  The reduced
   area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} = 0.7$,
@@
   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
-  \caption{\label{fig:extensional3} A vesicle doublet in an extensional flow with an initial inclination angle $\theta=\pi/2$.
-  The reduced area $\Delta A = 0.7$ ({\em top}) and $\Delta A=0.8$ ({\em bottom}). The Hamaker constant $\mathcal{H} =
-  0.7$, the adhesion length scale $\delta = 0.4$, and the extensional
-  rate $\chi = 0.1$.  The center of the vesicle, denoted with a black
-  square, is a stagnation point.}
+  \caption{\label{fig:extensional3} A vesicle doublet in an extensional
+  flow with an initial inclination angle $\theta=\pi$.  The reduced area
+  $\Delta A = 0.7$ ({\em top}) and $\Delta A=0.8$ ({\em bottom}). The
+  Hamaker constant $\mathcal{H} = 0.7$, the adhesion length scale
+  $\delta = 0.4$, and the extensional rate $\chi = 0.1$.  The center of
+  the vesicle, denoted with a black square, is a stagnation point.}
   \end{figure}
@@
 doublet remains trapped or is broken decreases with an increasing
-extensional rate.
-
-We summarize the final inclination angle of the doublet in the right
-plot of Figure~\ref{fig:extensionalInclinationAngle}.  The size of the
-round dots are scaled to the final inclination angle as defined in the
-right plot.  At smaller extensional rates, the vesicles come closer to
-aligning their long axis with the diverging direction.  When the doublet
-is broken at reduced area $\Delta A = 0.80$, the extensional rate is
-sufficiently large to align the long axis of the vesicle with the
-diverging direction and then the vesicles separate (bottom row in
-Figure~\ref{fig:extensional3}).  For very low extensional rates, the
-time horizon is insufficient for the doublet to reach an equilibrium
-state, and these simulations are marked with a square.  The right plot
-of Figure~\ref{fig:extensionalInclinationAngle} also summarizes the
-reduced areas and extensional rates that result in a bound vesicle
-doublet in a fluid trap: Parameter values with a blue mark result in a
-fluid trap and parameter values with a red mark result in vesicle
-separation.
+extensional rate.  We summarize the final inclination angle of the
+doublet in the right plot of
+Figure~\ref{fig:extensionalInclinationAngle}.  The size of the round
+dots are scaled to the final inclination angle as defined in
+Figure~\ref{fig:InclinationAngle}.  At smaller extensional rates, the
+vesicles come closer to aligning their long axis with the diverging
+direction.  When the doublet is broken at reduced area $\Delta A =
+0.80$, the extensional rate is sufficiently large to align the long axis
+of the vesicle with the diverging direction and then the vesicles
+separate (Figure~\ref{fig:extensional3}).  For very low extensional
+rates, the time horizon is insufficient for the doublet to reach an
+equilibrium state, and these simulations are marked with a square.  The
+right plot of Figure~\ref{fig:extensionalInclinationAngle} also
+summarizes the reduced areas and extensional rates that result in a
+bound vesicle doublet in a fluid trap: Parameter values with a blue mark
+result in a fluid trap and parameter values with a red mark result in
+vesicle separation.
 
@@
   $\Delta A = 0.7$ submerged in an extensional flow with an extensional
-  rate of $\chi$.  {\em Middle}: The final inclination angle of doublets.
-  At larger extensional rates, the doublet is broken by the flow.
-  {\em Right}: A phase diagram of the long-time
-  behavior of a fluid trap formed by two adhering vesicles in an
-  extensional flow.
+  rate of $\chi$.  {\em Middle}: The final inclination angle of
+  doublets.  At larger extensional rates, the doublet is broken by the
+  flow.  {\em Right}: A phase diagram of the long-time behavior of a
+  fluid trap formed by two adhering vesicles in an extensional flow.
   Results are not reported for some of the low extensional rates since
@@
 doublet with identical vesicles with reduced area $\Delta A=0.7$,
-adhesion length $\delta = 0.4$, Hamaker constant $\mathcal{H} = 0.7$,
-and extensional rate $\chi = 0.7$ in
+separation distance $\delta = 0.4$, Hamaker constant $\mathcal{H} =
+0.7$, and extensional rate $\chi = 0.7$ in
 Figure~\ref{fig:extensionalVorticity}.  Starting from a vesicle doublet
-with an initial inclination angle $\theta=\pi/2$, the doublet slowly
-begins to rotate around $t\sim 265$ (see the left plot of
-Figure~\ref{fig:extensionalVorticity}).  We notice that the net force on
+with an initial inclination angle $\theta=\pi$, the doublet slowly
+begins to rotate around $t\sim 265$.  We notice that the net force on
 each vesicle is almost anti-parallel to the diverging flow in the
 far-field so to balance the hydrodynamic drag force that pulls the
-vesicles apart.
-
-Then, as the doublet starts to rotate, each vesicle experiences drag
-force from both up and down diverging streaming flows.  For small
-extensional rate, the rotation will continue until $\theta = \pi$ so the
-doublet remains perfectly symmetric with respect to their mid-plane  and
-each vesicle experiences drag forces that cancel in both directions.
-For slightly higher extensional rate, we observe that the two vesicles
-slide against each other as the doublet rotate.  The slight sliding
-motion leads to a transition in the contact region membrane shape from a
-bulging profile to an S-shape profile of nearly uniform height except
-near the edge of contact region.  This adjustment greatly reduces the
-net force on each vesicle, leading to an equilibrium configuration with
-an inclination angle $\theta < \pi$ as shown in the left of
-Figure~\ref{fig:extensionalInclinationAngle}.  Finally, the vorticity
-and the flow between the vesicles approaches zero and the result is a
-fluid trap containing the doublet.
+vesicles apart.  Then, as the doublet starts to rotate, each vesicle
+experiences a drag force from both up and down diverging streaming flows.
+For small extensional rate, the rotation will continue until $\theta =
+\pi/2$ so the doublet remains perfectly symmetric with respect to their
+mid-plane  and each vesicle experiences drag forces that cancel in both
+directions.  For slightly higher extensional rate, we observe that the
+two vesicles slide against each other as the doublet rotates.  The slight
+sliding motion leads to a transition in the contact region membrane
+shape from a bulging profile to an S-shape profile of nearly uniform
+height except near the edge of contact region.  This adjustment greatly
+reduces the net force on each vesicle, leading to an equilibrium
+configuration with an inclination angle $\theta > \pi/2$ as shown in the
+left of Figure~\ref{fig:extensionalInclinationAngle}.  Finally, the
+vorticity and the flow between the vesicles approaches zero and the
+result is a fluid trap containing the doublet.
 \begin{figure}[htp]
@@
   \caption{\label{fig:extensionalVorticity} The vorticity and total
-  force of two vesicles in a doublet.  The reduced area is $\Delta A = 0.7$,
-  the extensional rate is $\chi = 0.7$, the adhesion length scale is
+  force of two vesicles in a doublet.  The reduced area is $\Delta A =
+  0.7$, the extensional rate is $\chi = 0.7$, the separation distance is
   $\delta = 0.4$, and the Hamaker constant is $\mathcal{H} = 0.7$.}

### 2019-02-12 vesicle_code/docs/adhesion/adhesion.tex
went through extensional again

@@
 Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  The stagnation
-point (zero-velocity at the origin) in an extensional flow, $\uu =\chi(-x,y)$,
-is a saddle point where two laminar streams converge along an axis and
-then diverge in the orthogonal direction.  With an active control algorithm
-to place the stagnation point at a desirable location by adjusting the streaming
-flow strength with a feedback loop~\cite{Johnson-Chavarria2011_EMJ}, a
-particle can be trapped at the stagnation point for long time scales to
-facilitate image acquisition or other detailed measures such as particle
-image velocimetry of flow inside and around the particle.  To explore
-the application of such a fluid trap to measure the adhesion strength
-between two bound vesicle membranes, we propose the following thought
-experiment.  Beginning with two identical vesicles in an equilibrium
-configuration that form a doublet with a flat contact region
+point (zero-velocity at the origin) in an extensional flow, $\uu
+=\chi(-x,y)$, is a saddle point where two laminar streams converge along
+an axis and then diverge in the orthogonal direction.  With an active
+control algorithm to place the stagnation point at a desirable location
+by adjusting the streaming flow strength with a feedback
+loop~\cite{Johnson-Chavarria2011_EMJ}, a particle can be trapped at the
+stagnation point for long time scales to facilitate image acquisition or
+other detailed measures such as particle image velocimetry of flow
+inside and around the particle.  To explore the application of such a
+fluid trap to measure the adhesion strength between two bound vesicle
+membranes, we propose the following thought experiment.  Beginning with
+two identical vesicles in an equilibrium configuration that form a
+doublet with a flat contact region
 (Figure~\ref{fig:Dec18_vesicle_shape}), we turn on the fluid trap with
@@
 overcomes the adhesive force and the doublet is broken, or the adhesive
-force dominates and the doublet reaches a stable stationary
+force is sufficiently strong and the doublet reaches a stable stationary
 configuration.
-
-\begin{figure}[htp]
-    \includegraphics[width=0.25\textwidth]{figs/rotate1.pdf}
-    \hspace{20pt}
-    \includegraphics[width=0.25\textwidth]{figs/angleDefinition.pdf}
-    \hspace{20pt}
-    \includegraphics[width=0.25\textwidth]{figs/rotate2.pdf}
-   \caption{\label{fig:InclinationAngle} The definition of the
-   inclination angle of a vesicle doublet at the center of an
-   extensional flow.  An inclination angle of $\pi$ indicates a doublet
-   whose long axis is parallel to the diverging direction, while an
-   inclination angle of $\pi/2$ indicates a doublet whose short axis is
-   parallel to the diverging direction.  The square mark is a stagnation
-   point and the round point is located at the center of the vesicle.
-   The initial configurations in this section all have an initial
-   configuration of $\theta = \pi$.}
-   \end{figure}
 
@@
 
+\begin{figure}[htp]
+   \includegraphics[width=0.25\textwidth]{figs/rotate1.pdf}
+   \hspace{20pt}
+   \includegraphics[width=0.25\textwidth]{figs/angleDefinition.pdf}
+   \hspace{20pt}
+   \includegraphics[width=0.25\textwidth]{figs/rotate2.pdf}
+   \caption{\label{fig:InclinationAngle} The definition of the
+   inclination angle of a vesicle doublet at the center of an
+   extensional flow.  An inclination angle of $\pi$ indicates a doublet
+   whose long axis is orthogonal to the diverging direction, while an
+   inclination angle of $\pi/2$ indicates a doublet whose short axis is
+   orthogonal to the diverging direction.  The square mark is a
+   stagnation point and the round point is located at the center of the
+   vesicle.  The initial configurations in this section all have an
+   inclination angle of $\theta = \pi$.}
+ \end{figure}
+
 Based on how the contact region aligns with the extensional flow, we can
 define the inclination angle of the vesicle doublet as illustrated in
-Figure~\ref{fig:InclinationAngle}. When $\theta=\pi$ (the doublet long
-axis is aligned with the far-field converging flow), the diverging flow
-pulls the vesicles apart from each other and the short-range repulsive
+Figure~\ref{fig:InclinationAngle}. When $\theta=\pi$, the doublet long
+axis is aligned with the far-field converging flow, and the diverging flow
+pulls the vesicles apart from each other and the long-range attractive
 force is essential to keep the two vesicles from separating.  In
-contrast, when $\theta = \pi/2$ (the doublet long axis is aligned with
-the diverging flow), the converging flow pushes the vesicles towards
+contrast, when $\theta = \pi/2$, the doublet long axis is aligned with
+the diverging flow, the converging flow pushes the vesicles towards
 each other and the short-range repulsive force is essential to keep the
@@
 than the $\theta=\pi$ configuration in the left of
-Figure~\ref{fig:InclinationAngle}, where the doublet long axis is
-parallel to the converging direction. This is because when $\theta=\pi$
-the diverging flow is pulling the vesicles away from each other as shown
-in the illustration.  If the doublet inclination angle is fixed at
-$\theta=\pi/2$, the vesicle doublet stays intact only when the adhesive
-force is strong enough to dominate over the fluid drag in this
-configuration \todo[inline]{I don't follow this sentence}.  Thus it is
+Figure~\ref{fig:InclinationAngle}. This is because when $\theta=\pi$ the
+diverging flow is pulling the vesicles away from each other as shown in
+the illustration.  However, when the doublet inclination angle is fixed
+at $\theta=\pi/2$, the vesicle doublet stays intact if the adhesive
+force is strong enough to dominate the fluid drag.  However, it is
 possible that the diverging flow may overcome adhesion and break up the
 doublet.  It is also reasonable to expect a vesicle doublet to rotate
-from $\theta=\pi$ to $\theta=\pi/2$, such that the fluid flow is pushing
-them together rather than pulling them apart.
+from the less stable configuration $\theta=\pi$ to the more stable
+configuration $\theta=\pi/2$, so that the fluid flow is pushing them
+together rather than pulling them apart.
 
@@
 vesicle doublet of reduced area $\Delta A = 0.7$ are simulated at three
-different extensional rates.  While this doublet remains bound for all
+different extensional rates.  We observe that the doublet rotates from
+$\theta=\pi$ configuration towards the more stable $\theta=\pi/2$
+configuration, as shown in Figures~\ref{fig:extensional1}.  We also
+observe that with moderate extensional rates, the doublet falls short of
+aligning their long axis with the diverging direction.  Moreover, the
+final inclination angle is closest to the stable $\theta=\pi/2$ for the
+smallest extensional rates.  While this doublet remains bound for all
 the considered extensional rates, a doublet with a reduced area of
-$\Delta A = 0.8$ is split with a critical extensional rate $\chi_c =0.1$
-(Figure~\ref{fig:extensional3}).  For extensional rates and reduced
-areas that result in a bound vesicle doublet, we observe that the
-doublet always rotates from $\theta=\pi$ configuration towards the more
-stable $\theta=\pi/2$ configuration, as shown in
-Figures~\ref{fig:extensional1}.  We also observe that in most cases with
-moderate extensional flow rates the doublet falls short of aligning
-their long axis with the diverging direction.
+$\Delta A = 0.8$ is split with a critical extensional rate $\chi_c =
+0.1$ (Figure~\ref{fig:extensional3}).
 
@@
   0.1$ ({\em bottom}).  The center of the vesicle, denoted with a black
-  square, is a stagnation point.}
+  square, is the stagnation point.}
   \end{figure}
@@
   flow with an initial inclination angle $\theta=\pi$.  The reduced area
-  $\Delta A = 0.7$ ({\em top}) and $\Delta A=0.8$ ({\em bottom}). The
-  Hamaker constant $\mathcal{H} = 0.7$, the adhesion length scale
-  $\delta = 0.4$, and the extensional rate $\chi = 0.1$.  The center of
-  the vesicle, denoted with a black square, is a stagnation point.}
+  is $\Delta A = 0.8$, the Hamaker constant $\mathcal{H} = 0.7$, the
+  separation distance is $\delta = 0.4$, and the extensional rate $\chi
+  = 0.1$.  The center of the vesicle, denoted with a black square, is a
+  stagnation point.}
 \end{figure}
@@
 doublets that reach an equilibrium state (middle).  We observe that not
-only do larger smaller extensional rates result in smaller inclination
+only do smaller extensional rates result in smaller inclination
 angles, but smaller reduced areas also result in smaller inclination
@@
 doublet remains trapped or is broken decreases with an increasing
-extensional rate.  We summarize the final inclination angle of the
-doublet in the right plot of
+extensional rate \todo[inline]{not sure how we can say this since we've
+only considered one Hamaker constant}.  We summarize the final
+inclination angle of the doublet in the right plot of
 Figure~\ref{fig:extensionalInclinationAngle}.  The size of the round
@@
   inclination angle of a doublet formed by vesicles of reduced area
-  $\Delta A = 0.7$ submerged in an extensional flow with an extensional
-  rate of $\chi$.  {\em Middle}: The final inclination angle of
-  doublets.  At larger extensional rates, the doublet is broken by the
-  flow.  {\em Right}: A phase diagram of the long-time behavior of a
-  fluid trap formed by two adhering vesicles in an extensional flow.
-  Results are not reported for some of the low extensional rates since
-  the doublet had not tilted to an equilibrium inclination angle for the
-  given time horizon.}
+  $\Delta A = 0.7$ in an extensional flow with an extensional rate
+  $\chi$.  {\em Middle}: The final inclination angle of doublets.  At
+  larger extensional rates, the doublet is broken by the flow.  {\em
+  Right}: A phase diagram of the long-time behavior of a fluid trap
+  formed by two adhering vesicles in an extensional flow.  Results are
+  not reported for some of the low extensional rates since the doublet
+  had not tilted to an equilibrium inclination angle for the given time
+  horizon.}
 \end{figure}
@@
 doublet with identical vesicles with reduced area $\Delta A=0.7$,
-separation distance $\delta = 0.4$, Hamaker constant $\mathcal{H} =
-0.7$, and extensional rate $\chi = 0.7$ in
+Hamaker constant $\mathcal{H} = 0.7$, separation distance $\delta =
+0.4$, and extensional rate $\chi = 0.7$ in
 Figure~\ref{fig:extensionalVorticity}.  Starting from a vesicle doublet
 with an initial inclination angle $\theta=\pi$, the doublet slowly
-begins to rotate around $t\sim 265$.  We notice that the net force on
+begins to rotate around $t\sim 250$.  We notice that the net force on
 each vesicle is almost anti-parallel to the diverging flow in the
@@
 vesicles apart.  Then, as the doublet starts to rotate, each vesicle
-experiences a drag force from both up and down diverging streaming flows.
-For small extensional rate, the rotation will continue until $\theta =
-\pi/2$ so the doublet remains perfectly symmetric with respect to their
-mid-plane  and each vesicle experiences drag forces that cancel in both
-directions.  For slightly higher extensional rate, we observe that the
-two vesicles slide against each other as the doublet rotates.  The slight
-sliding motion leads to a transition in the contact region membrane
-shape from a bulging profile to an S-shape profile of nearly uniform
-height except near the edge of contact region.  This adjustment greatly
-reduces the net force on each vesicle, leading to an equilibrium
+experiences a drag force from both the up and down diverging streaming
+flows.  For small extensional rate, the rotation will continue until
+$\theta = \pi/2$ so the doublet remains perfectly symmetric with respect
+to their mid-plane and each vesicle experiences drag forces that cancel
+in both directions.  For slightly higher extensional rate, we observe
+that the two vesicles slide against each other as the doublet rotates.
+The slight sliding motion leads to a transition in the contact region
+membrane shape from a bulging profile to an S-shape profile of nearly
+uniform height except near the edge of contact region.  This adjustment
+greatly reduces the net force on each vesicle, leading to an equilibrium
 configuration with an inclination angle $\theta > \pi/2$ as shown in the
@@
   force of two vesicles in a doublet.  The reduced area is $\Delta A =
-  0.7$, the extensional rate is $\chi = 0.7$, the separation distance is
-  $\delta = 0.4$, and the Hamaker constant is $\mathcal{H} = 0.7$.}
+  0.7$, the separation distance is $\delta = 0.4$, the Hamaker constant
+  is $\mathcal{H} = 0.7$, and the extensional rate is $\chi = 0.7$.}
 \end{figure}

### 2019-02-12 vesicle_code/docs/adhesion/adhesion.tex
minor changes at the bottom of page 10 by yny
starting shear

@@
 they are deflected to opposite sides of the $y$ axis, pass one another,
-and separate from one another.  However, in the presence of adhesion,
-the vesicles can form a doublet for certain values of the adhesion
-length scale $\delta$, Hamaker constant $\mathcal{H}$, shear rate
-$\chi$, and reduced area $\Delta A$.  Figure~\ref{fig:doublet090} shows
-snapshots two vesicles that have formed a doublet and the color coding
-is the tension along the vesicle.  The two vesicles are
-identical with reduced area is $\Delta A = 0.9$, the shear rate is $\chi
-= 0.5$, the adhesion length scale is $\delta = 0.4$, and the Hamaker
-constant is $\mathcal{H} = 0.7$.  Similar to the quiescent example, we
-observe that the membrane tension in the contact region is negative in
-the contact region indicating that the membrane is being compressed when
-the adhesive force is strongest.  Once the vesicles have formed a
-doublet, the vesicles rotate in tandem rather than performing the usual
-tank-treading motion.
+and then separate.  However, in the presence of adhesion, the vesicles
+can form a doublet for certain values of the separation distance
+$\delta$, Hamaker constant $\mathcal{H}$, shear rate $\chi$, and reduced
+area $\Delta A$.  Figure~\ref{fig:doublet090} shows snapshots of two
+vesicles that have formed a doublet and the color coding is the tension
+along the vesicle.  The two vesicles are identical with reduced area
+$\Delta A = 0.9$, shear rate $\chi = 0.5$, separation distance $\delta =
+0.4$, and Hamaker constant $\mathcal{H} = 0.7$.  The vesicles in the
+doublet move in tandem rather than performing the tank-treading motion
+that is observed in the absence of adhesion.  Similar to the
+quiescent example, the membrane tension is negative in the contact
+region indicating that the membrane is being compressed when the
+adhesive force is strongest.
 

### 2019-02-12 vesicle_code/docs/adhesion/adhesion.tex
edited shear example

@@
 angles, but smaller reduced areas also result in smaller inclination
-angles.  Moreover, the critical Hamaker constant that determines if the
-doublet remains trapped or is broken decreases with an increasing
-extensional rate \todo[inline]{not sure how we can say this since we've
-only considered one Hamaker constant}.  We summarize the final
+angles.  
+%
+%From physics we expect that stronger adhesion is required to keep 
+%the vesicle doublet intact under a fluid trap as we increase the flow rate.
+%
+%It is less obvious how the critical adhesion strength depends on the reduced area of the vesicles.
+%
+%Even though we only used one value of Hamaker constant (${\cal H} = 0.7$) we expect that
+%
+%Moreover, the critical Hamaker constant that determines if the
+%doublet remains trapped or is broken decreases with an increasing
+%extensional rate \todo[inline]{not sure how we can say this since we've
+%only considered one Hamaker constant}.  
+%
+We summarize the final
 inclination angle of the doublet in the right plot of
-Figure~\ref{fig:extensionalInclinationAngle}.  The size of the round
+Figure~\ref{fig:extensionalInclinationAngle}.  
+The size of the round
 dots are scaled to the final inclination angle as defined in
@@
 $\delta$, Hamaker constant $\mathcal{H}$, shear rate $\chi$, and reduced
-area $\Delta A$.  Figure~\ref{fig:doublet090} shows snapshots of two
-vesicles that have formed a doublet and the color coding is the tension
-along the vesicle.  The two vesicles are identical with reduced area
-$\Delta A = 0.9$, shear rate $\chi = 0.5$, separation distance $\delta =
-0.4$, and Hamaker constant $\mathcal{H} = 0.7$.  The vesicles in the
-doublet move in tandem rather than performing the tank-treading motion
-that is observed in the absence of adhesion.  Similar to the
-quiescent example, the membrane tension is negative in the contact
-region indicating that the membrane is being compressed when the
-adhesive force is strongest.
+area $\Delta A$.  At all reduced areas, the vesicles have a length of
+$2\pi$.  Figure~\ref{fig:doublet090} shows snapshots of two vesicles
+that have formed a doublet and the color coding is the tension along the
+vesicle.  The two vesicles are identical with reduced area $\Delta A =
+0.9$, shear rate $\chi = 0.5$, separation distance $\delta = 0.4$, and
+Hamaker constant $\mathcal{H} = 0.7$.  The vesicles in the doublet move
+in tandem rather than performing the tank-treading motion that is
+observed in the absence of adhesion.  Similar to the quiescent example,
+the membrane tension is negative in the contact region indicating that
+the membrane is being compressed when the adhesive force is strongest.
 
@@
   flow.  The reduced area is $\Delta A = 0.9$, the Hamaker constant is
-  $\mathcal{H}=0.7$, the adhesion length scale is $\delta = 0.4$, and
-  the shear rate is $\chi=0.5$.}
+  $\mathcal{H}=0.7$, the separation distance is $\delta = 0.4$, and the
+  shear rate is $\chi=0.5$.}
 \end{figure}
@@
 determines if the vesicles form a doublet or separate.  We fix the
-adhesion length scale to $\delta = 0.4$ and the vesicle reduced area to
+separation distance to $\delta = 0.4$ and the vesicle reduced area to
 $\Delta A = 0.9$.  In the left plot of
@@
   \includegraphics[height=0.35\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
-  \caption{{\em Left}: Distance between a pair of vesicles in a planar
-  shear flow with shear rate $\chi=0.5$ and adhesion length scale
-  $\delta = 0.4$.   The different lines correspond to a linear spacing
-  of adhesion strengths ranging from $\mathcal{H}=0.1$ and
-  $\mathcal{H}=1.0$.  {\em Right}: Phase diagram of vesicle
-  hydrodynamics in a shear flow.  At a fixed reduced area $\Delta
-  A=0.90$ and $\delta = 0.4$,  the critical Hamaker constant
+  \caption{\label{fig:sflow_phase_diagram} {\em Left}: Distance between
+  a pair of vesicles in a planar shear flow with shear rate $\chi=0.5$,
+  and separation distance $\delta = 0.4$.  The different lines
+  correspond to a linear spacing of Hamaker constants ranging from
+  $\mathcal{H}=0.1$ and $\mathcal{H}=1.0$.  {\em Right}: Phase diagram
+  of vesicle hydrodynamics in a shear flow.  At a fixed reduced area
+  $\Delta A=0.90$ and $\delta = 0.4$, the critical Hamaker constant
   $\mathcal{H}$ for binding of two vesicles in a shear flow depends on
-  the shear rate $\chi$.
-\label{fig:sflow_phase_diagram}}
+  the shear rate $\chi$.}
 \end{figure}
@@
 \end{align*}
-where $\phi$ is the area fraction of vesicles, $\tau$ is the stress due
-to the vesicles, and $\langle \cdot \rangle$ is the spatial average.
-
-In the left plot of Figure~\ref{fig:shearIntrinsicViscosity}, we compare
-the intrinsic viscosity of a single tank-treading vesicle to a doublet.
-To validate our simulations, we superimpose (black marks) the intrinsic
+$\phi$ is the area fraction of vesicles, $\tau$ is the stress due to the
+vesicles, and $\langle \cdot \rangle$ is the spatial average.  In the
+left plot of Figure~\ref{fig:shearIntrinsicViscosity}, we compare the
+intrinsic viscosity of a single tank-treading vesicle to a doublet.  To
+validate our simulations, we superimpose (black marks) the intrinsic
 viscosity calculated by Ghigliotti {\em et
@@
   shear rate is $\chi = 0.5$, the Hamaker constant is $\mathcal{H} =
-  0.7$, and the adhesion length scale is $\delta = 0.4$, and the length
-  of the vesicles are held fixed.  The black marks denote intrinsic
-  viscosity values computed by Ghigliotti {\em et
+  0.7$, and the separation distance is $\delta = 0.4$.  The black marks
+  denote intrinsic viscosity values computed by Ghigliotti {\em et
   al.}~\cite{GhigliottiBibenMisbah2010_JFM} (cf.~Figure 5).  {\em
@@
 attraction.  We use a lubrication theory to estimate the time required
-to reach the separation distance $\delta$, and the theoretical scaling is in good
-agreement with numerical results.  Once two membranes are within
-separation distance $\delta$, the adhesive force turns repulsive and the
-membranes flatten to form a contact region.  Our simulations show that
-the membranes in the contact region are actually curved with end points
-at the shortest distance.  Once a vesicle doublet forms, we examine the
-dependence of membrane bending and adhesion energies on the reduced
-area, the Hamaker constant, and the separation distance.
+to reach the separation distance $\delta$, and the theoretical scaling
+is in good agreement with numerical results.  Once two membranes are
+within separation distance $\delta$, the adhesive force turns repulsive
+and the membranes flatten to form a contact region.  Our simulations
+show that the membranes in the contact region are actually curved with
+end points at the shortest distance.  Once a vesicle doublet forms, we
+examine the dependence of membrane bending and adhesion energies on the
+reduced area, the Hamaker constant, and the separation distance.
 
@@
 stagnation point of an extensional flow characterized by a extensional
-flow rate.  At low flow rate, we find the doublet to rotate nearly ninety
-degrees to align with the flow such that the long axis of the doublet is
-along the divergent axis and the convergent stream is pushing the two
-vesicles together. As the flow rate increases, the vesicle doublet
-rotates less, and when the flow rate reaches above the critical value,
-the diverging flow breaks the doublet structure by pulling the vesicles
-apart.  These results indicate that it is possib le to use the fluid trap
-to separate a vesicle doublet under adhesion, and thus provide a means
-to probe the adhesion strength between membranes.  For a pair of $\mu
-m$-sized vesicles with a bending rigidity of $\sim 10^{-19}$ $J$, an
-extensional flow rate of $0.5$ $s^{-1}$ is expected to separate a
-vesicle doublet with reduced area of $\Delta A = 0.8$ and a Hamaker
-constant $\mathcal{H}=0.7$, which corresponds to $\sim 1$ $\mu J/m^2$.
-These conditions are quite realizable in microfluidic experiments, and
-we hope that our simulations will inspire microfluidic experiments.
+flow rate.  At low flow rate, we find the doublet to rotate nearly
+ninety degrees to align with the flow such that the long axis of the
+doublet is along the divergent axis and the convergent stream is pushing
+the two vesicles together. As the flow rate increases, the vesicle
+doublet rotates less, and when the flow rate reaches above the critical
+value, the diverging flow breaks the doublet structure by pulling the
+vesicles apart.  These results indicate that it is possib le to use the
+fluid trap to separate a vesicle doublet under adhesion, and thus
+provide a means to probe the adhesion strength between membranes.  For a
+pair of $\mu m$-sized vesicles with a bending rigidity of $\sim
+10^{-19}$ $J$, an extensional flow rate of $0.5$ $s^{-1}$ is expected to
+separate a vesicle doublet with reduced area of $\Delta A = 0.8$ and a
+Hamaker constant $\mathcal{H}=0.7$, which corresponds to $\sim 1$ $\mu
+J/m^2$.  These conditions are quite realizable in microfluidic
+experiments, and we hope that our simulations will inspire microfluidic
+experiments.
 
@@
 responsible for the observed membrane
-undulation~\cite{SteinkuhlerAgudo-Canalejo2016_BJ}.
-In addition, simulations presented in this work are for identical vesicles (same reduced area, length, and
-bending rigidity modulus) in the doublet. Flormann {\it et al.} demonstrated that asymmetric vesicle reduced area
-may lead to various equilibrium doublet shape such as male-female, asymmetric S-shape and parachute shape.
-It is also possible that viscosity contrast may also lead to slightly different equilibrium doublet shape.
-Future work includes three dimensional simulations, dispersive vesicle properties (such as
-reduced area and bending modulus), viscosity contrast, and effects of confinement on adhesive interactions.
-
-Flormann {\it et al.} studied the clustering and packing of vesicles in free suspension~\cite{FlormannAouane2017_SciReports}. 
-In engineering applications of vesicle emulsions
-often smaller vesicles are enclosed in a big vesicle, as shown in 
-Figure~\ref{fig:relaxationManyVes}, where  the left panel shows an initial condition of five vesicles
-suspended inside of a larger vesicle.
-The second panel from left shows the membrane configuration and flow
-streamlines at an intermediate time.  There is no imposed flow, so the
-dynamics are governed entirely by the adhesion, bending, and tension
-forces.  In the absence of confinement, we would expect the vesicles to
-align themselves as a rouleaux with the membranes forming a parachute,
-male-female, or S-shape
+undulation~\cite{SteinkuhlerAgudo-Canalejo2016_BJ}.  In addition,
+simulations presented in this work are for identical vesicles (same
+reduced area, length, and bending rigidity modulus) in the doublet.
+Flormann {\it et al.} demonstrated that asymmetric vesicle reduced area
+may lead to various equilibrium doublet shape such as male-female,
+asymmetric S-shape and parachute shape.  It is also possible that
+viscosity contrast may also lead to slightly different equilibrium
+doublet shape.  Future work includes three dimensional simulations,
+dispersive vesicle properties (such as reduced area and bending
+modulus), viscosity contrast, and effects of confinement on adhesive
+interactions.
+
+Flormann {\it et al.} studied the clustering and packing of vesicles in
+free suspension~\cite{FlormannAouane2017_SciReports}.  In engineering
+applications of vesicle emulsions often smaller vesicles are enclosed in
+a big vesicle, as shown in Figure~\ref{fig:relaxationManyVes}, where
+the left panel shows an initial condition of five vesicles suspended
+inside of a larger vesicle.  The second panel from left shows the
+membrane configuration and flow streamlines at an intermediate time.
+There is no imposed flow, so the dynamics are governed entirely by the
+adhesion, bending, and tension forces.  In the absence of confinement,
+we would expect the vesicles to align themselves as a rouleaux with the
+membranes forming a parachute, male-female, or S-shape
 configurations~\cite{FlormannAouane2017_SciReports}.  However, because
@@
 bounding membrane closely follow the interior membranes in order to
-minimize the adhesion energy.   As a result of force balance the equilibrium shape of the bounding vesicle
-is far from a symmetric shape while the interior smaller vesicles are of similar shape to each other.
-We also plot the tension (thrid) and
-adhesion (fourth) of the final equilibrium configuration.  
-We remark that the adhesion force is all attractive on all the vesicle membranes while large positive
-membrane tension is found only on the bounding vesicle. 
-%Both the
-%vesicle shape, tension, and adhesion qualitatively agree with our
-%doublet results.  
-In particular, the interior vesicles form a flat
-contact region with a large negative tension.
-We are now conducting simulations of such vesicle configuration under a planar shear flow.
-
-%\begin{figure}[htp]
-%  \centering
-%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot01.pdf}
-%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot02.pdf}
-%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot03.pdf}
-%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot04.pdf} \\
-%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot05.pdf}
-%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot06.pdf}
-%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot07.pdf}
-%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot08.pdf}
-%  \caption{\label{fig:relaxationManyVes} Five vesicles suspended inside
-%  a large vesicle.  The background flow is quiescent, the adhesion
-%  length scale is $\delta = 0.4$, and the Hamaker constant is
-%  $\mathcal{H} = 0.7$.  At the final snapshot, the suspension is near an
-%  equilibrium configuration.}
-%\end{figure}
+minimize the adhesion energy.   As a result of force balance the
+equilibrium shape of the bounding vesicle is far from a symmetric shape
+while the interior smaller vesicles are of similar shape to each other.
+We also plot the tension (thrid) and adhesion (fourth) of the final
+equilibrium configuration.  We remark that the adhesion force is all
+attractive on all the vesicle membranes while large positive membrane
+tension is found only on the bounding vesicle.  In particular, the
+interior vesicles form a flat contact region with a large negative
+tension.  We are now conducting simulations of such vesicle
+configuration under a planar shear flow.
 
@@
 \caption{\label{fig:relaxationManyVes} Five vesicles in a quiescent flow
-suspended in a bounding vesicle.   All vesicles are interacting through hydrodynamic flow and
-an adhesion potential with Hamaker constant $\mathcal{H} = 0.7$ and
-separation distance $\delta = 0.4$.  From left to right, the plots are
-the initial condition, streamlines and an intermediate time, tension at
-the steady-state configuration, and the adhesion force projected onto
-the outward unit normal at the steady-state configuration.  Along the
-bounding vesicle, the tension is largest and the adhesion is smallest in
-the regions that are well-separated from the interior vesicles.  Similar
-to other simulations, the interior vesicles are relatively flat and have
-a large negative tension in the contact regions.}
+suspended in a bounding vesicle.   All vesicles are interacting through
+hydrodynamic flow and an adhesion potential with Hamaker constant
+$\mathcal{H} = 0.7$ and separation distance $\delta = 0.4$.  From left
+to right, the plots are the initial condition, streamlines and an
+intermediate time, tension at the steady-state configuration, and the
+adhesion force projected onto the outward unit normal at the
+steady-state configuration.  Along the bounding vesicle, the tension is
+largest and the adhesion is smallest in the regions that are
+well-separated from the interior vesicles.  Similar to other
+simulations, the interior vesicles are relatively flat and have a large
+negative tension in the contact regions.}
 \end{figure}
@@
 
-BQ acknowledges support from Florida State University startup funds and Simons Foundation Mathematics
-and Physical Sciences-Collaboration Grants for Mathematicians 527139.
-SV acknowledges support from NSF under grants DMS-1719834 and DMS-1454010.
-YNY acknowledges support from NSF-DMS 1614863 and 1412789. 
-The work of SV and YNY was also supported by the Flatiron Institute, a division of Simons Foundation.
+BQ acknowledges support from Florida State University startup funds and
+Simons Foundation Mathematics and Physical Sciences-Collaboration Grants
+for Mathematicians 527139.  SV acknowledges support from NSF under
+grants DMS-1719834 and DMS-1454010.  YNY acknowledges support from
+NSF-DMS 1614863 and 1412789.  The work of SV and YNY was also supported
+by the Flatiron Institute, a division of Simons Foundation.
 

### 2019-02-12 vesicle_code/docs/adhesion/adhesion.tex
edited conclusions

@@
 ninety degrees to align with the flow such that the long axis of the
-doublet is along the divergent axis and the convergent stream is pushing
-the two vesicles together. As the flow rate increases, the vesicle
-doublet rotates less, and when the flow rate reaches above the critical
-value, the diverging flow breaks the doublet structure by pulling the
-vesicles apart.  These results indicate that it is possib le to use the
-fluid trap to separate a vesicle doublet under adhesion, and thus
-provide a means to probe the adhesion strength between membranes.  For a
-pair of $\mu m$-sized vesicles with a bending rigidity of $\sim
+doublet is parallel to the divergent axis and the convergent stream is
+pushing the two vesicles together. As the flow rate increases, the
+vesicle doublet rotates less, and when the flow rate exceeds the
+critical value, the diverging flow breaks the doublet structure by
+pulling the vesicles apart.  These results indicate that it is possible
+to use the fluid trap to separate a vesicle doublet under adhesion, and
+thus provide a means to probe the adhesion strength between membranes.
+For a pair of $\mu m$-sized vesicles with a bending rigidity of $\sim
 10^{-19}$ $J$, an extensional flow rate of $0.5$ $s^{-1}$ is expected to
@@
 
-We also examine how adhesive interaction may lead to formation of a
-vesicle doublet dynamically in flowing conditions.  We simulate two
-vesicles approaching each other in a planar shear flow, and examine how
-their adhesive interactions lead to doublet formation.  Once a doublet
-forms, the two vesicle membranes rotate around each other as they deform
-dynamically. The usual tank-treading motion of a vesicle under shear
-flow is not observed in each of the two vesicles. We compute the
-effective shear viscosity of a dilute suspension of vesicle doublets,
-and found it to be more than twice the effective shear viscosity of a
-dilute suspension of single vesicles.  Furthermore, we find that the
-membrane adhesion contribution to the shear viscosity increases with
-decreasing reduced area while the bending/tension contribution increases
-with the reduced area.
+We also examine how adhesive interaction may dynamically lead to the
+formation of a vesicle doublet.  We simulate two vesicles approaching
+each other in a planar shear flow, and examine how their adhesive
+interactions lead to doublet formation.  Once a doublet forms, the two
+vesicle membranes rotate around each other as they deform dynamically.
+The usual tank-treading motion of a vesicle under shear flow is not
+observed in each of the two vesicles. We compute the effective shear
+viscosity of a dilute suspension of vesicle doublets, and found it to be
+more than twice the effective shear viscosity of a dilute suspension of
+single vesicles.  Furthermore, we find that the membrane adhesion
+contribution to the shear viscosity increases with decreasing reduced
+area while the bending/tension contribution increases with the reduced
+area.
 
@@
 may lead to various equilibrium doublet shape such as male-female,
-asymmetric S-shape and parachute shape.  It is also possible that
-viscosity contrast may also lead to slightly different equilibrium
-doublet shape.  Future work includes three dimensional simulations,
-dispersive vesicle properties (such as reduced area and bending
-modulus), viscosity contrast, and effects of confinement on adhesive
-interactions.
+asymmetric S-shape, and parachute shape.  It is also possible that
+viscosity contrast may also lead to different equilibrium doublet
+shapes.  Future work includes three dimensional simulations, dispersive
+vesicle properties (such as reduced area and bending modulus), viscosity
+contrast, and effects of confinement on adhesive interactions.
 
@@
 free suspension~\cite{FlormannAouane2017_SciReports}.  In engineering
-applications of vesicle emulsions often smaller vesicles are enclosed in
+applications of vesicle emulsions, smaller vesicles are often enclosed in
 a big vesicle, as shown in Figure~\ref{fig:relaxationManyVes}, where
 the left panel shows an initial condition of five vesicles suspended
-inside of a larger vesicle.  The second panel from left shows the
+inside of a larger vesicle.  The second panel from the left shows the
 membrane configuration and flow streamlines at an intermediate time.
 There is no imposed flow, so the dynamics are governed entirely by the
-adhesion, bending, and tension forces.  In the absence of confinement,
+vesicle forces, including adhesion.  In the absence of confinement,
 we would expect the vesicles to align themselves as a rouleaux with the
 membranes forming a parachute, male-female, or S-shape
-configurations~\cite{FlormannAouane2017_SciReports}.  However, because
-of the bounding vesicle and the dense packing, the interior vesicles
-align themselves differently.  In addition, several parts of the
-bounding membrane closely follow the interior membranes in order to
-minimize the adhesion energy.   As a result of force balance the
-equilibrium shape of the bounding vesicle is far from a symmetric shape
-while the interior smaller vesicles are of similar shape to each other.
-We also plot the tension (thrid) and adhesion (fourth) of the final
-equilibrium configuration.  We remark that the adhesion force is all
-attractive on all the vesicle membranes while large positive membrane
-tension is found only on the bounding vesicle.  In particular, the
-interior vesicles form a flat contact region with a large negative
-tension.  We are now conducting simulations of such vesicle
-configuration under a planar shear flow.
+configuration~\cite{FlormannAouane2017_SciReports}.  However, because of
+the bounding vesicle and the dense packing, the interior vesicles align
+themselves differently.  In addition, several parts of the bounding
+membrane closely follow the interior membranes in order to minimize the
+adhesion energy.   As a result of force balance, the equilibrium shape
+of the bounding vesicle is far from a symmetric shape while the interior
+smaller vesicles are of similar shape to each other.  We also plot the
+tension (third) and adhesion (fourth) of the final equilibrium
+configuration.  We remark that the adhesion force is attractive on all
+the vesicle membranes while large positive membrane tension is found
+only on the bounding vesicle.  In particular, the interior vesicles form
+a flat contact region with a large negative tension.  We are now
+conducting simulations of such vesicle configuration under a planar
+shear flow.
 
@@
 $\mathcal{H} = 0.7$ and separation distance $\delta = 0.4$.  From left
-to right, the plots are the initial condition, streamlines and an
+to right, the plots are the initial condition, streamlines at an
 intermediate time, tension at the steady-state configuration, and the
@@
 the coupling between membranes via strong hydrodynamic interactions. In
-particular they demonstrate numerically that the fluctuation in one
+particular, they demonstrate numerically that the fluctuation in one
 membrane is highly correlated to the other membrane without any physical

### 2019-02-12 vesicle_code/docs/adhesion/adhesion.tex
more minor changes from yny

@@
 0.4$, and extensional rate $\chi = 0.7$ in
-Figure~\ref{fig:extensionalVorticity}.  Starting from a vesicle doublet
-with an initial inclination angle $\theta=\pi$, the doublet slowly
-begins to rotate around $t\sim 250$.  We notice that the net force on
+Figure~\ref{fig:extensionalVorticity}.  Starting from an initial inclination angle $\theta=\pi$, the doublet 
+starts to rotate around $t\sim 250$.  We notice that the net force on
 each vesicle is almost anti-parallel to the diverging flow in the
@@
 membrane configuration and flow streamlines at an intermediate time.
-There is no imposed flow, so the dynamics are governed entirely by the
+There is no imposed flow, so the dynamics is governed entirely by the
 vesicle forces, including adhesion.  In the absence of confinement,
@@
 the bounding vesicle and the dense packing, the interior vesicles align
-themselves differently.  In addition, several parts of the bounding
-membrane closely follow the interior membranes in order to minimize the
-adhesion energy.   As a result of force balance, the equilibrium shape
+themselves differently.  
+The bounding membrane evolves dynamically together with all the interior 
+vesicles to minimize the total membrane energy.
+%In addition, several parts of the bounding
+%membrane closely follow the interior membranes in order to minimize the
+%adhesion energy.   
+%
+
+As a result of force balance, the equilibrium shape
 of the bounding vesicle is far from a symmetric shape while the interior
-smaller vesicles are of similar shape to each other.  We also plot the
+smaller vesicles are of similar shape to each other.  
+We also plot the
 tension (third) and adhesion (fourth) of the final equilibrium
@@
 
+Finally, it is not clear how thermal fluctuations may affect the
+hydrodynamics of vesicles under adhesion. For example, does the
+fluctuating hydrodynamics in the thin film between two vesicles enhance
+adhesion to keep vesicles bound under linear flows?
 Recently Liu {\em et al.}~\cite{LiuChuNewbyRead2018_bioRxiv} used
@@
 membrane is highly correlated to the other membrane without any physical
-contact. It is not clear how thermal fluctuations may affect the
-hydrodynamics of vesicles under adhesion. For example, does the
-fluctuating hydrodynamics in the thin film between two vesicles enhance
-adhesion to keep vesicles bound under linear flows?
+contact. We are actively pursuing this direction with ongoing modeling and simulations
+of adhesive membranes with fluctuating hydrodynamics.
 

### 2019-02-13 vesicle_code/docs/adhesion/adhesion.tex
minor changes at the end of conclusion by yny
small changes

@@
 ZhaoShaqfeh2011_JFM, SpannZhaoShaqfeh2014_PoF} to alter the effective
-shear viscosity.  In an extensional flow (planar or
-uniaxial), vesicle shape dynamics depends sensitively on the vesicle
-reduced volume and the elastic capillary
-number~\cite{KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
-Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}: Asymmetric shape
-and oscillatory undulation of the vesicle membrane are two examples of
-the complex vesicle hydrodynamics in an extensional flow.
+shear viscosity.  In an extensional flow (planar or uniaxial), vesicle
+shape dynamics depends sensitively on the vesicle reduced volume and the
+elastic capillary number~\cite{KantslerSegreSteinberg2008_PRL,
+ZhaoShaqfeh2013_JFM, Narsimhan2014_JFM,
+DahlNarsimhanGouveia2016_SoftMatt}: Asymmetric shape and oscillatory
+undulation of the vesicle membrane are two examples of the complex
+vesicle hydrodynamics in an extensional flow.
 
@@
 membranes without the molecular details of adhesive interactions between
-RBCs, Flormann {\em et al.}~\cite{FlormannAouane2017_SciReports} found the contact zone to buckle under
-strong adhesion.  A direct
-consequence of the buckling is the sigmoidal shape of the adhesion
-region, which is also observed in RBC doublets and explained in a
-slightly different model~\cite{ZiherlSvetina2007_PNAS}.  It remains
-unknown how adhesive interactions between vesicles might lead to
-different vesicle hydrodynamics that results in different rheological
-properties of a vesicle suspension. Such studies will provide useful
-insight into the rheology of blood flow and how to use nano solutes to
-control the hypertension by adjusting the adhesive interactions between
-RBCs.
+RBCs, Flormann {\em et al.}~\cite{FlormannAouane2017_SciReports} found
+the contact zone to buckle under strong adhesion.  A direct consequence
+of the buckling is the sigmoidal shape of the adhesion region, which is
+also observed in RBC doublets and explained in a slightly different
+model~\cite{ZiherlSvetina2007_PNAS}.  It remains unknown how adhesive
+interactions between vesicles might lead to different vesicle
+hydrodynamics that results in different rheological properties of a
+vesicle suspension. Such studies will provide useful insight into the
+rheology of blood flow and how to use nano solutes to control the
+hypertension by adjusting the adhesive interactions between RBCs.
 
@@
 in dimensionality and achieve high-order accuracy even for moving
-geometry problems. When the vesicles adhere, one major issue for BIE solvers is to resolve the vesicle-vesicle hydrodynamic forces which become {\em nearly singular}. 
-We use an interpolation-based quadrature rule~\cite{qua-bir2014} to maintain
-high-order accuracy for all vesicle-vesicle separation distances.  To
-overcome the numerical stiffness induced by the membrane bending forces
-and to control the global error, we employ a high-order spectral
-deferred implicit-explicit adaptive time stepping
-scheme~\cite{quaife2016adaptive}.
+geometry problems. When the vesicles adhere, one major issue for BIE
+solvers is to resolve the vesicle-vesicle hydrodynamic forces which
+become {\em nearly singular}.  We use an interpolation-based quadrature
+rule~\cite{qua-bir2014} to maintain high-order accuracy for all
+vesicle-vesicle separation distances.  To overcome the numerical
+stiffness induced by the membrane bending forces and to control the
+global error, we employ a high-order spectral deferred implicit-explicit
+adaptive time stepping scheme~\cite{quaife2016adaptive}.
 
@@
 adhesion process of two vesicles in a quiescent flow in
-Section~\ref{sec:qflow}, where we also present a simple lubrication model to
-estimate how long it takes for two nearby vesicles to reach the
-separation distance set by the adhesion potential.
-In Section~\ref{sec:eflow} we
-numerically investigate the hydrodynamics of a vesicle doublet in a
-fluid trap where the stagnation point is actively controlled to be at
-the center of the vesicle doublet. From these results we propose a novel
-application of the microfluidic fluid trap to probe the adhesion
-strength between lipid bilayer membranes in solutions. In
-Section~\ref{sec:sflow} we investigate how two vesicles may form a
-doublet as they move toward each other under a planar shear flow.  We
-map out the parameter regions for bound/unbound vesicles under a planar
-shear flow, and we also investigate the effects of adhesive interactions
-on the rheological properties of a dilute suspension of vesicle
-doublets.  Finally in Section~\ref{sec:conclusions} we discuss the
-implications of our results and point out a few potential future
+Section~\ref{sec:qflow}, where we also present a simple lubrication
+model to estimate how long it takes for two nearby vesicles to reach the
+separation distance set by the adhesion potential.  In
+Section~\ref{sec:eflow} we numerically investigate the hydrodynamics of
+a vesicle doublet in a fluid trap where the stagnation point is actively
+controlled to be at the center of the vesicle doublet. From these
+results we propose a novel application of the microfluidic fluid trap to
+probe the adhesion strength between lipid bilayer membranes in
+solutions. In Section~\ref{sec:sflow} we investigate how two vesicles
+may form a doublet as they move toward each other under a planar shear
+flow.  We map out the parameter regions for bound/unbound vesicles under
+a planar shear flow, and we also investigate the effects of adhesive
+interactions on the rheological properties of a dilute suspension of
+vesicle doublets.  Finally in Section~\ref{sec:conclusions} we discuss
+the implications of our results and point out a few potential future
 directions.
@@
 When two vesicles move towards (or away from) each other under a
-constant force $F$ without any imposed external flow, the height, $h$, of
-the thin liquid film between two vesicles follows the draining
+constant force $F$ without any imposed external flow, the height, $h$,
+of the thin liquid film between two vesicles follows the draining
 dynamics~\cite{RamachandranLeal2010_PoF}
@@
 doublets that reach an equilibrium state (middle).  We observe that not
-only do smaller extensional rates result in smaller inclination
-angles, but smaller reduced areas also result in smaller inclination
-angles.  
-%
-%From physics we expect that stronger adhesion is required to keep 
-%the vesicle doublet intact under a fluid trap as we increase the flow rate.
-%
-%It is less obvious how the critical adhesion strength depends on the reduced area of the vesicles.
-%
-%Even though we only used one value of Hamaker constant (${\cal H} = 0.7$) we expect that
-%
-%Moreover, the critical Hamaker constant that determines if the
-%doublet remains trapped or is broken decreases with an increasing
-%extensional rate \todo[inline]{not sure how we can say this since we've
-%only considered one Hamaker constant}.  
-%
-We summarize the final
-inclination angle of the doublet in the right plot of
-Figure~\ref{fig:extensionalInclinationAngle}.  
-The size of the round
+only do smaller extensional rates result in smaller inclination angles,
+but smaller reduced areas also result in smaller inclination angles.  We
+summarize the final inclination angle of the doublet in the right plot
+of Figure~\ref{fig:extensionalInclinationAngle}.  The size of the round
 dots are scaled to the final inclination angle as defined in
@@
 \section{Conclusions\label{sec:conclusions}}
-In this work we use boundary integral formulation with adaptive
+In this work we use a boundary integral formulation with adaptive
 time-stepping to simulate hydrodynamics of two vesicles with adhesive
@@
 reduced area, length, and bending rigidity modulus) in the doublet.
-Flormann {\it et al.} demonstrated that asymmetric vesicle reduced area
+Flormann {\em et al.}~demonstrated that asymmetric vesicle reduced area
 may lead to various equilibrium doublet shape such as male-female,
@@
 
-Flormann {\it et al.} studied the clustering and packing of vesicles in
-free suspension~\cite{FlormannAouane2017_SciReports}.  In engineering
+Flormann {\it et al.} studied the clustering and packing of an
+unbounded suspension of vesicles~\cite{FlormannAouane2017_SciReports}.  In engineering
 applications of vesicle emulsions, smaller vesicles are often enclosed in
@@
 There is no imposed flow, so the dynamics is governed entirely by the
-vesicle forces, including adhesion.  In the absence of confinement,
-we would expect the vesicles to align themselves as a rouleaux with the
+vesicle forces, including adhesion.  In the absence of confinement, we
+would expect the vesicles to align themselves as a rouleaux with the
 membranes forming a parachute, male-female, or S-shape
@@
 the bounding vesicle and the dense packing, the interior vesicles align
-themselves differently.  
-The bounding membrane evolves dynamically together with all the interior 
-vesicles to minimize the total membrane energy.
-%In addition, several parts of the bounding
-%membrane closely follow the interior membranes in order to minimize the
-%adhesion energy.   
-%
-
-As a result of force balance, the equilibrium shape
-of the bounding vesicle is far from a symmetric shape while the interior
-smaller vesicles are of similar shape to each other.  
-We also plot the
-tension (third) and adhesion (fourth) of the final equilibrium
-configuration.  We remark that the adhesion force is attractive on all
-the vesicle membranes while large positive membrane tension is found
-only on the bounding vesicle.  In particular, the interior vesicles form
-a flat contact region with a large negative tension.  We are now
-conducting simulations of such vesicle configuration under a planar
-shear flow.
+themselves differently.  The bounding membrane evolves dynamically
+together with all the interior vesicles to minimize the total membrane
+energy.
+
+As a result of force balance, the equilibrium shape of the bounding
+vesicle is far from a symmetric shape while the interior smaller
+vesicles are of similar shape to each other.  We also plot the tension
+(third) and adhesion (fourth) of the final equilibrium configuration.
+We remark that the adhesion force is attractive on all the vesicle
+membranes while large positive membrane tension is found only on the
+bounding vesicle.  In particular, the interior vesicles form a flat
+contact region with a large negative tension.  We are now conducting
+simulations of such vesicle configuration under a planar shear flow.
 
@@
 fluctuating hydrodynamics in the thin film between two vesicles enhance
-adhesion to keep vesicles bound under linear flows?
-Recently Liu {\em et al.}~\cite{LiuChuNewbyRead2018_bioRxiv} used
-immersed boundary simulations to show that, at a separation distance of
-tens of nanometers, the thin film between the two membranes facilitate
-the coupling between membranes via strong hydrodynamic interactions. In
+adhesion to keep vesicles bound under linear flows?  Recently Liu {\em
+et al.}~\cite{LiuChuNewbyRead2018_bioRxiv} used immersed boundary
+simulations to show that, at a separation distance of tens of
+nanometers, the thin film between the two membranes facilitate the
+coupling between membranes via strong hydrodynamic interactions. In
 particular, they demonstrate numerically that the fluctuation in one
 membrane is highly correlated to the other membrane without any physical
-contact. We are actively pursuing this direction with ongoing modeling and simulations
-of adhesive membranes with fluctuating hydrodynamics.
+contact. We are actively pursuing this direction with hydrodynamic
+modeling and simulations of adhesive membranes with thermal fluctions.
 

### 2019-02-13 vesicle_code/docs/adhesion/governing.tex
edits to sec 2

@@
 two-dimensional viscous fluid.  For simplicity, we assume the fluid
-viscosity both inside and outside the vesicles is constant, but our
-method can be easily adjusted to account for a viscosity contrast.
+viscosity both inside and outside the vesicles is the same; however, incorporating viscosity constrast is rather straightforward in our numerical algorithm. 
 Individual vesicles are denoted as $\gamma_j$, $j=1,\ldots,M$, and they
@@
 $\uu_\infty$, the governing equations are
-\begin{equation*}
+\begin{equation}
 \begin{aligned}
@@
     &&\mbox{\em non-zero traction jump}
-\end{aligned}
-\end{equation*}
+\end{aligned} \label{eq:gov}
+\end{equation}
 where $\llbracket T \rrbracket$ is the jump in the stress tensor, and
@@
 extensibility constraint.  The resistance to bending and stretching are
-standard assumptions of vesicles.  In this work, we include an adhesive
+standard assumptions on vesicles.  In this work, we include an adhesive
 force, $\AA \xx$, that we now describe.
@@
 \subsection{Integral Equation Formulation}
-Because the fluid equations are linear and elliptic, a boundary integral
-equation formulation is possible.  This has several advantages,
-including that only the vesicle interfaces require discretization.  We
-start by defining the Stokes single-layer potential
+Using potential theory and following \cite{Veerapaneni2009_JCP}, we recast the governing equations \eqref{eq:gov} as integro-differential equations for the evolution of membrane positions: 
+%
+\begin{align*}
+  &\dot{\xx} = \uu_{\infty}(\xx) + \SS[\xxi](\xx), \\
+  &\xx_s \cdot \dot{\xx}_s = 0,
+ \end{align*}
+%
+where the single-layer potential $\SS[\cdot]$ is defined by
 \begin{align}
-  \SS[\ff](\xx) &= \frac{1}{4\pi\mu} \int_\gamma \left(
-    -\log \rho + \frac{\rr \otimes \rr}{\rho^2} \right) 
-    \ff(\yy) ds_\yy, \quad \xx \in \RR^2,
+  \SS[\xxi](\xx) &= \frac{1}{4\pi\mu} \int_\gamma \left(
+    -\log \|\xx - \yy\| + \frac{(\xx - \yy) \otimes (\xx - \yy)}{\|\xx - \yy\|^2} \right) 
+    \xxi(\yy) ds_\yy, 
   \label{eqn:SLP}
 \end{align}
-where $\rr = \xx - \yy$ and $\rho = \|\rr\|$.  Then, given a vesicle
-with a traction jump $\xxi$, the fluid velocity is~\cite{poz1992}
-\begin{align*}
-  \uu(\xx) = \uu_{\infty}(\xx) + \SS[\xxi](\xx), \quad \xx \in \RR^2.
-\end{align*}
-The traction jump is
-\begin{align*}
-  \xxi = -\kappa_b \xx_{ssss} + (\sigma \xx_s)_s + \AA \xx,
-\end{align*}
-where the three terms correspond to the forces due to bending, tension,
-and adhesion, respectively.  Therefore, applying the no-slip boundary
-condition on each vesicle, the governing equations are
-\begin{align*}
-  &\dot{\xx} = \uu_{\infty}(\xx) + \SS[\xxi](\xx), \\
-  &\xx_s \cdot \uu_s = 0, \\
-  &\xxi = -\kappa_b \xx_{ssss} + (\sigma \xx_s)_s + \AA\xx.
-\end{align*}
+%
+and the membrane force $\xxi$ is a sum of the bending, tension and adhesion forces: 
+\begin{equation*}
+\xxi = -\kappa_b \xx_{ssss} + (\sigma \xx_s)_s + \AA\xx.
+\end{equation*}
 Defining the bending operator as $\BB[\xx](\ff) = -\kappa_b \ff_{ssss}$,

### 2019-02-13 vesicle_code/docs/adhesion/adhesion.tex
small edits to Shravan's edits ... moved governing equations into main tex code

@@
 stiffness induced by the membrane bending forces and to control the
-global error, we employ a high-order spectral deferred implicit-explicit
-adaptive time stepping scheme~\cite{quaife2016adaptive}.
+global error, we employ a second-order spectral deferred
+implicit-explicit adaptive time stepping
+scheme~\cite{quaife2016adaptive}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\input{governing.tex}
+\section{Governing Equations \label{sec:ge}}
+We consider suspensions of locally inextensible vesicles in an unbounded
+two-dimensional viscous fluid.  For simplicity, we assume the fluid
+viscosity both inside and outside the vesicles is the same; however,
+incorporating viscosity constrast is rather straightforward in our
+numerical algorithm.  Individual vesicles are denoted as $\gamma_j$,
+$j=1,\ldots,M$, and they are parameterized in arclength as $\xx_j(s,t)$.
+The union of all vesicles is denoted by $\gamma$.  Given a background
+velocity $\uu_\infty$, the governing equations are
+\begin{equation}
+\begin{aligned}
+  \mu \Delta \uu = \nabla p, \quad &\xx \in \RR^2,
+    &&\mbox{\em conservation of momentum} \\
+  \nabla \cdot \uu = 0, \quad &\xx \in \RR^2, 
+    &&\mbox{\em conservation of mass} \\
+  \uu \rightarrow \uu_\infty, \quad &\|\xx\| \rightarrow \infty,
+    &&\mbox{\em far-field condition} \\
+  \uu(\xx,t) = \dot{\xx}, \quad &\xx \in \gamma,
+    &&\mbox{\em velocity continuity} \\
+  \xx_s \cdot \uu_s =0, \quad &\xx \in \gamma,
+    &&\mbox{\em local inextensibility} \\
+  \llbracket T \rrbracket \nn = \xxi, \quad &\xx \in \gamma,
+    &&\mbox{\em non-zero traction jump}
+\end{aligned} \label{eq:gov}
+\end{equation}
+where $\llbracket T \rrbracket$ is the jump in the stress tensor, and
+$\xxi$ is the traction jump that is the sum of the bending, stretching,
+and adhesion forces.  The bending force, arising from the Helfrich
+energy model, is $\BB \xx = -\kappa_b \xx_{ssss}$, where $\kappa_b$ is
+the bending rigidity modulus which we set to be 1 for all examples. The
+stretching force is $\TT \sigma = (\sigma \xx_s)_s$, where the tension,
+$\sigma$, acts as a Lagrange multiplier to satisfy the local
+extensibility constraint.  The resistance to bending and stretching are
+standard assumptions on vesicles.  In this work, we include an adhesive
+force, $\AA \xx$, that we now describe.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Adhesion Model}
+Sukumaran and Seifert~\cite{suk-sei2001} consider adhesion between a
+single three-dimensional vesicle and a solid wall at $z=0$.  They use
+the adhesion potential of the function form
+\begin{align}
+\label{eq:adhesion_potential}
+  \phi(z) = \mathcal{H} \left[ 
+    \left(\frac{\delta}{z}\right)^m - \frac{m}{n} \left(\frac{\delta}{z}\right)^n \right],
+\end{align}
+where $z$ is the distance between the solid wall and the vesicle,
+$\mathcal{H}$ is the Hamaker constant, $\delta$ is the adhesion length
+scale, and $(m,n) = (4,2)$.  We generalize this model to an unbounded
+suspension of vesicles. We assume that the adhesion force applies
+between all pairs of points on different vesicles, so we are interested
+in Hamaker constants that are appropriate for lipid-lipid interactions.
+We use Hamaker constants ranging from $\mathcal{O}(10^{-1})$ to
+$\mathcal{O}(10^0)$ times the bending rigidity modulus.  In
+Appendix~\ref{sec:appendixA}, the adhesive force at a point $\xx$ on
+vesicle $j$ is shown to be
+\begin{align}
+  \AA\xx:=-\mathcal{H} m \delta^{n}\sum_{\substack{k=1 \\ k \neq j}}^M 
+  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+2}} 
+  \left(\delta^{m-n} - \|\xx - \yy\|^{m-n} \right) ds_\yy.
+  \label{eqn:adhesionForce}
+\end{align}
+The adhesion model is illustrated in Figure~\ref{fig:adhesionModel}.
+
+\begin{figure}[htp]
+  \begin{minipage}{0.31\textwidth}
+    \centering
+    \includegraphics[height=5cm,trim={0cm 0cm 2cm 0cm},clip]{figs/adhesionPotential.pdf}
+  \end{minipage}
+  \hfill
+  \begin{minipage}{0.31\textwidth}
+    \centering
+    \includegraphics[height=5cm]{figs/configCartoon.pdf}
+  \end{minipage}
+  \hfill
+  \begin{minipage}{0.31\textwidth}
+    \centering
+    \includegraphics[height=5cm,trim={3cm 0cm 2cm 0cm},clip]{figs/Adhesion_Force.png}
+  \end{minipage}
+  \caption{\label{fig:adhesionModel} {\em Left}: The adhesion potential
+  $\phi(z)$ in equation~\eqref{eq:adhesion_potential}.  Distances less
+  than $\delta$ are repulsive and distances greater than $\delta$ are
+  attractive.  {\em Center}: Each point on a vesicle is repelled or
+  attracted by all points on the other vesicles.  {\em Right}: The
+  resulting adhesive force is found by integrating over all points on
+  all other vesicles (equation~\eqref{eqn:adhesionForce}).  The color is
+  the dot product of the adhesion force with the vector joining the
+  vesicles.  Therefore, the green and yellow regions are repelled by the
+  other vesicle while the blue regions are attracted to the other
+  vesicle.}
+\end{figure}
+
+The exponents $(m,n)$ depend on the geometry of the two objects under
+adhesion~\cite{Book_IntermolecularSurfaceForces}: $(m,n)=(4,2)$
+corresponds to two flat, planar surfaces interacting with each under a
+long-range attraction and a short-range repulsion. On the other hand,
+$(m,n) = (12,6)$ corresponds to the Lennard-Jones (L.-J.)~potential
+between two molecules.  In our case, the adhesion potential in the
+integral of equation~\eqref{eqn:adhesionForce} is between two small
+patches of lipid bilayer membrane (because the lipid molecules are
+coarse-grained in the continuum modeling).  Thus a reasonable choice for
+$(m,n)$ between two coarse-grained membrane patches would be between
+those for two planar surfaces and two point molecules.
+
+Large value of $m$ corresponds to a sharp increase in the repulsion
+force as two objects are within the separation distance $\delta$.  This
+poses a numerical challenge since the problem becomes stiff (i.e.,
+requires a very small time step) for large $m$.  The adaptive
+time-stepping BIE scheme makes it possible to simulate vesicle adhesive
+dynamics with specified numerical precision for reasonable computation
+time.  We explore several combinations of $(m,n)$ in the simulations of
+two vesicles forming a doublet in a quiescent flow.  We found very
+little difference in both the dynamic evolution and equilibrium
+configuration between $(m,n)=(8,6)$ and $(m,n)=(4,2)$.  Therefore, in
+this work, we use $(m,n) = (4,2)$ to regulate the stiffness introduced
+by the adhesive force.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Integral Equation Formulation}
+Using potential theory and following \cite{Veerapaneni2009_JCP}, we recast the governing equations \eqref{eq:gov} as integro-differential equations for the evolution of membrane positions: 
+%
+\begin{align*}
+  &\dot{\xx} = \uu_{\infty}(\xx) + \SS[\xxi](\xx), \\
+  &\xx_s \cdot \dot{\xx}_s = 0,
+ \end{align*}
+%
+where the single-layer potential $\SS[\cdot]$ is defined by
+\begin{align}
+  \SS[\xxi](\xx) &= \frac{1}{4\pi\mu} \int_\gamma \left(
+    -\log \|\xx - \yy\| + \frac{(\xx - \yy) \otimes (\xx - \yy)}{\|\xx - \yy\|^2} \right) 
+    \xxi(\yy) ds_\yy, 
+  \label{eqn:SLP}
+\end{align}
+%
+and the membrane force $\xxi$ is a sum of the bending, tension and adhesion forces: 
+\begin{equation*}
+\xxi = -\kappa_b \xx_{ssss} + (\sigma \xx_s)_s + \AA\xx.
+\end{equation*}
+Defining the bending operator as $\BB[\xx](\ff) = -\kappa_b \ff_{ssss}$,
+and the tension operator $\TT[\xx](\sigma) = (\sigma \xx_s)_s$, the
+no-slip boundary condition gives
+\begin{align*}
+  \pderiv{\xx}{t} = \SS \BB \xx + \SS \TT \sigma + \SS \AA \xx.
+\end{align*}
+We apply the IMEX-Euler method 
+\begin{align*}
+  \frac{\xx^{N+1} - \xx^N}{\Delta t} = \SS^N \BB^N \xx^{N+1} + 
+  \SS^N \TT^N \sigma^{N+1} + \SS^N \AA^N \xx^N,
+\end{align*}
+that discretizes both the bending and tension terms
+semi-implicitly~\cite{qua-bir2014}, and the adhesive term explicitly.
+Therefore, a single time step requires solving
+\begin{align*}
+  \xx^{N+1} - \Delta t \SS^N \BB^N \xx^{N+1} - 
+    \Delta t \SS^N \TT^N \sigma^{N+1} = \xx^N + 
+    \Delta t \SS^N \AA^N \xx^N,
+\end{align*}
+along with the inextensibility constraint that is discretized as
+\begin{align*}
+  \xx_s^{N} \cdot \xx_{s}^{N+1} = 1.
+\end{align*}
+We discretize the vesicles at a set of collocation points, compute the
+bending and tension terms with Fourier differentiation, and apply Alpert
+quadrature~\cite{alp1999} to the weakly-singular single-layer potential
+$\SS$.  The source and target points of the adhesion force never
+coincide since they are always on different vesicles, so the adhesion
+force~\eqref{eqn:adhesionForce} is computed with the spectrally accurate
+trapezoid rule~\cite{tre-wei2014}.
+
+The dynamics of a doublet undergoes many different time scales over time
+horizons that are sufficiently large to characterize the formation of a
+doublet and its rheological properties.  Therefore, time adaptivity is
+crucial so that a user-specified tolerance is achieved without using a
+guess-and-check procedure to find an appropriately small fixed time step
+size.  To control the error and achieve second-order accuracy in time,
+we use a time adaptive spectral deferred correction method that
+applies IMEX-Euler twice per time step~\cite{quaife2016adaptive}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{The Shear and Normal Stresses}
+To characterize the rheological properties of the suspension of a
+doublet, it is necessary to compute the shear and normal stresses.  At a
+point $\xx \in \RR^2 \backslash \gamma$ in the fluid bulk, the velocity
+$\uu(\xx)$, pressure $p(\xx)$, and total stress tensor $T = - p I +
+\nabla \uu + \nabla \uu^T$ of the single-layer potential~\eqref{eqn:SLP}
+are
+\begin{align*}
+  \uu(\xx) &= \SS_\uu[\ff](\xx) = \frac{1}{4\pi\mu}\int_{\gamma} \left( 
+    -\log \rho + \frac{\rr \otimes \rr}{\rho^2} \right) 
+    \ff ds_\yy, \\
+    p(\xx) &= \SS_p[\ff](\xx) = \frac{1}{2\pi} \int_{\gamma} 
+    \frac{\rr \cdot \ff}{\rho^2} ds_\yy, \\
+    T(\xx) &= \SS_T[\ff](\xx) = -\frac{1}{\pi}\int_{\gamma}
+      \frac{\rr \cdot \ff}{\rho^2} 
+      \frac{\rr \otimes \rr}{\rho^2} ds_\yy,
+\end{align*}
+where $\rr = \xx - \yy$, and $\rho = \|\xx - \yy\|$.  To compute the
+stress tensor on a vesicle, there is a jump in the layer potential
+$\SS_T$, and the stress tensor is
+\begin{align*}
+  T(\xx) = \frac{1}{2}(\nn \otimes \ff) + \frac{1}{2} \left(
+    \tt \otimes \left[
+    \begin{array}{cc}
+      2 t_x t_y & t_y^2 - t_x^2 \\
+      t_y^2 - t_x^2 & -2 t_x t_y
+    \end{array}
+    \right] \ff \right) + 
+  \SS_T[\ff](\xx), \quad \xx \in \gamma,
+\end{align*}
+where $\nn$ and $\tt$ are the vesicle's outward unit normal and tangent
+vector, respectively.  With the stress tensor computed for $\xx \in
+\gamma$, the shear and normal stresses are
+\begin{align*}
+  \tau^\tt = (T \nn) \cdot \tt, \qquad
+  \tau^\nn = (T \nn) \cdot \nn.
+\end{align*}
 

### 2019-02-13 vesicle_code/docs/adhesion/governing.tex
small edits to Shravan's edits ... moved governing equations into main tex code

@@
 two-dimensional viscous fluid.  For simplicity, we assume the fluid
-viscosity both inside and outside the vesicles is the same; however, incorporating viscosity constrast is rather straightforward in our numerical algorithm. 
-Individual vesicles are denoted as $\gamma_j$, $j=1,\ldots,M$, and they
-are parameterized in arclength as $\xx_j(s,t)$.  The union of all
-vesicles is denoted by $\gamma$.  Given a background velocity
-$\uu_\infty$, the governing equations are
+viscosity both inside and outside the vesicles is the same; however,
+incorporating viscosity constrast is rather straightforward in our
+numerical algorithm.  Individual vesicles are denoted as $\gamma_j$,
+$j=1,\ldots,M$, and they are parameterized in arclength as $\xx_j(s,t)$.
+The union of all vesicles is denoted by $\gamma$.  Given a background
+velocity $\uu_\infty$, the governing equations are
 \begin{equation}
@@
 long-range attraction and a short-range repulsion. On the other hand,
-$(m,n) = (12,6)$ corresponds to the L.-J.~potential between two molecules.
-In our case, the adhesion potential in the integral of
-equation~\eqref{eqn:adhesionForce} is between two small patches of lipid
-bilayer membrane (because the lipid molecules are coarse-grained in the
-continuum modeling).  Thus a reasonable choice for $(m,n)$ between two
-coarse-grained membrane patches would be between those for two planar
-surfaces and two point molecules.
+$(m,n) = (12,6)$ corresponds to the Lennard-Jones (L.-J.)~potential
+between two molecules.  In our case, the adhesion potential in the
+integral of equation~\eqref{eqn:adhesionForce} is between two small
+patches of lipid bilayer membrane (because the lipid molecules are
+coarse-grained in the continuum modeling).  Thus a reasonable choice for
+$(m,n)$ between two coarse-grained membrane patches would be between
+those for two planar surfaces and two point molecules.
 
@@
 size.  To control the error and achieve second-order accuracy in time,
-we apply a time adaptive spectral deferred correction
-method~\cite{quaife2016adaptive}.
+we use a time adaptive spectral deferred correction method that
+applies IMEX-Euler twice per time step~\cite{quaife2016adaptive}.
 
@@
       \frac{\rr \cdot \ff}{\rho^2} 
-      \frac{\rr \otimes \rr}{\rho^2} ds_\yy.
+      \frac{\rr \otimes \rr}{\rho^2} ds_\yy,
 \end{align*}
-To compute the stress tensor on a vesicle, there is a jump in the layer
-potential $\SS_T$, and the stress tensor is
+where $\rr = \xx - \yy$, and $\rho = \|\xx - \yy\|$.  To compute the
+stress tensor on a vesicle, there is a jump in the layer potential
+$\SS_T$, and the stress tensor is
 \begin{align*}

### 2019-02-13 vesicle_code/docs/adhesion/adhesion.tex
removing governing.tex from repo

@@
 viscosity both inside and outside the vesicles is the same; however,
-incorporating viscosity constrast is rather straightforward in our
+incorporating viscosity contrast is rather straightforward in our
 numerical algorithm.  Individual vesicles are denoted as $\gamma_j$,
@@
 \subsection{Integral Equation Formulation}
-Using potential theory and following \cite{Veerapaneni2009_JCP}, we recast the governing equations \eqref{eq:gov} as integro-differential equations for the evolution of membrane positions: 
+Using potential theory and following~\cite{Veerapaneni2009_JCP}, we recast the governing equations~\eqref{eq:gov} as integro-differential equations for the evolution of membrane positions: 
 %

### 2019-02-13 vesicle_code/docs/adhesion/adhesion.tex
changes from yny feb 13the morning

--- 2019-02-13 vesicle_code/docs/adhesion/adhesion.tex
@@
 density is larger than $1$ $\mu J/m^2$ and ``weak" when the energy
-density is less than $1$ $\mu J/m^2$.  In this work we use the ratio of
-the adhesion energy to the bending energy for classification of adhesion
-strength. The ratio of total adhesion energy to the bending energy
+density is less than $1$ $\mu J/m^2$.  
+%In this work we use the ratio of
+%the adhesion energy to the bending energy for classification of adhesion
+%strength. 
+The ratio of total adhesion energy to the bending energy
 (bending rigidity of lipid bilayer membranes $\sim 10^{-19}$ $J$) gives
@@
 
-In this work we focus on regimes where the ratio is of order one,
+In this work we focus on regimes where such ratio is of order one,
 between the weak adhesion (adhesion energy/bending energy $\ll 1$) and
@@
 between two vesicles and enhance the adhesion effects.  The
-equilibration of vesicle membranes in the strong adhesion regime have
+equilibration of vesicle membranes in the strong adhesion regime has
 been well-studied and documented

### 2019-02-13 vesicle_code/docs/adhesion/adhesion.tex
changes from yny feb 13the morning

@@
 \section{Governing Equations \label{sec:ge}}
-We consider suspensions of locally inextensible vesicles in an unbounded
+We consider a suspension of locally inextensible vesicles in an unbounded
 two-dimensional viscous fluid.  For simplicity, we assume the fluid
@@
 incorporating viscosity contrast is rather straightforward in our
-numerical algorithm.  Individual vesicles are denoted as $\gamma_j$,
+numerical algorithm.  
+While we focus on a vesicle doublet suspension for the rest of the paper, here we provide the most general formulation with multiple vesicles interacting with
+each other through both hydrodynamic and adhesive forces.
+Individual vesicles are denoted as $\gamma_j$,
 $j=1,\ldots,M$, and they are parameterized in arclength as $\xx_j(s,t)$.

### 2019-02-13 vesicle_code/docs/adhesion/adhesion.tex
all the changes now by yny

@@
 numerical algorithm.  
-While we focus on a vesicle doublet suspension for the rest of the paper, here we provide the most general formulation with multiple vesicles interacting with
+While we focus on a vesicle doublet suspension for the rest of the paper, here we provide the most general formulation for multiple vesicles interacting with
 each other through both hydrodynamic and adhesive forces.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Adhesion Model}
-Sukumaran and Seifert~\cite{suk-sei2001} consider adhesion between a
-single three-dimensional vesicle and a solid wall at $z=0$.  They use
-the adhesion potential of the function form
-\begin{align}
-\label{eq:adhesion_potential}
-  \phi(z) = \mathcal{H} \left[ 
-    \left(\frac{\delta}{z}\right)^m - \frac{m}{n} \left(\frac{\delta}{z}\right)^n \right],
-\end{align}
-where $z$ is the distance between the solid wall and the vesicle,
-$\mathcal{H}$ is the Hamaker constant, $\delta$ is the adhesion length
-scale, and $(m,n) = (4,2)$.  We generalize this model to an unbounded
-suspension of vesicles. We assume that the adhesion force applies
-between all pairs of points on different vesicles, so we are interested
-in Hamaker constants that are appropriate for lipid-lipid interactions.
-We use Hamaker constants ranging from $\mathcal{O}(10^{-1})$ to
-$\mathcal{O}(10^0)$ times the bending rigidity modulus.  In
-Appendix~\ref{sec:appendixA}, the adhesive force at a point $\xx$ on
-vesicle $j$ is shown to be
-\begin{align}
-  \AA\xx:=-\mathcal{H} m \delta^{n}\sum_{\substack{k=1 \\ k \neq j}}^M 
-  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+2}} 
-  \left(\delta^{m-n} - \|\xx - \yy\|^{m-n} \right) ds_\yy.
-  \label{eqn:adhesionForce}
-\end{align}
-The adhesion model is illustrated in Figure~\ref{fig:adhesionModel}.
-
+%\subsection{Adhesion Model}
+%
 \begin{figure}[htp]
@@
 
-The exponents $(m,n)$ depend on the geometry of the two objects under
+Adhesion potential for a vesicle membrane has been modeled by a L.-J. type potential
+%Sukumaran and Seifert~\cite{suk-sei2001} consider adhesion between a
+%single three-dimensional vesicle and a solid wall at $z=0$.  They use
+%the adhesion potential of the function form
+\begin{align}
+\label{eq:adhesion_potential}
+  \phi(z) = \mathcal{H} \left[ 
+    \left(\frac{\delta}{z}\right)^m - \frac{m}{n} \left(\frac{\delta}{z}\right)^n \right],
+\end{align}
+where $\mathcal{H}$ is the Hamaker constant and $\delta$ is the adhesion length
+scale. $z$ is the distance between a patch on the vesicle membrane and a point on the other object,
+which could be another vesicle membrane or a flat solid wall.  The characteristics of the L.-J. potential are summarized in
+the left panel of Figure~\ref{fig:adhesionModel}: The adhesive force is zero at the equilibrium distance $z=\delta$.
+For large distances ($z> \delta$) the adhesive potential is attractive while for small distances ($z < \delta$) the potential is repulsive to prevent physical contact.
+
+The exponents $(m,n)$ depend on the geometry and the molecular details of the two objects under
 adhesion~\cite{Book_IntermolecularSurfaceForces}: $(m,n)=(4,2)$
-corresponds to two flat, planar surfaces interacting with each under a
-long-range attraction and a short-range repulsion. On the other hand,
+corresponds to two flat, planar surfaces interacting with each other, and has been a common choice 
+for studying membrane-solid adhesion  \cite{Seifert1990_PRA,suk-sei2001,ShiFengGao2006_ActaMechSin, LinFreund2007_IntJSolidsStructures,BlountMiksisDavis2013_PRSa,YoungStone2017_PRF}.
+%
+On the other hand,
 $(m,n) = (12,6)$ corresponds to the Lennard-Jones (L.-J.)~potential
-between two molecules.  In our case, the adhesion potential in the
-integral of equation~\eqref{eqn:adhesionForce} is between two small
+between two molecules, and has been used to model membrane-membrane adhesion  \cite{FlormannAouane2017_SciReports}.  
+In our case, the adhesion potential in the
+integral of equation~(\eqref{eqn:adhesionForce}) is between two small
 patches of lipid bilayer membrane (because the lipid molecules are
-coarse-grained in the continuum modeling).  Thus a reasonable choice for
+coarse-grained in the continuum modeling).  
+Thus a reasonable choice for
 $(m,n)$ between two coarse-grained membrane patches would be between
@@
 time.  We explore several combinations of $(m,n)$ in the simulations of
-two vesicles forming a doublet in a quiescent flow.  We found very
+two vesicles forming a doublet in a quiescent flow and in a shear flow.  We found that, as long as the
+close-range interaction is well resolved both in space (using the near-singular evaluations) 
+and time (using the high-order adaptive time integration), there is very
 little difference in both the dynamic evolution and equilibrium
 configuration between $(m,n)=(8,6)$ and $(m,n)=(4,2)$.  Therefore, in
-this work, we use $(m,n) = (4,2)$ to regulate the stiffness introduced
+this work, we use $(m,n) = (4,2)$ to regulate the numerical stiffness introduced
 by the adhesive force. 
+%
+%For some simulations we used both sets of $(m,n)$ and did not notice significant difference
+%in terms of adhesive hydrodynamics of vesicles.
+
+Focusing on intermediate adhesive strengths, 
+we use Hamaker constants ranging from $\mathcal{O}(10^{-1})$ to
+$\mathcal{O}(10^0)$ times the bending rigidity modulus.  
+We assume that the adhesion force from equation~\ref{eq:adhesion_potential} applies
+between all pairs of points on different vesicles, and in
+Appendix~\ref{sec:appendixA} the net adhesive force at a point $\xx$ on
+vesicle $j$ is shown to be
+\begin{align}
+  \AA\xx:=-\mathcal{H} m \delta^{n}\sum_{\substack{k=1 \\ k \neq j}}^M 
+  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+2}} 
+  \left(\delta^{m-n} - \|\xx - \yy\|^{m-n} \right) ds_\yy.
+  \label{eqn:adhesionForce}
+\end{align}
+This summation of adhesive forces is illustrated in the middle panel of Figure~\ref{fig:adhesionModel}. 
+The right panel of Figure~\ref{fig:adhesionModel} is an 
+example of the calculated adhesive force projected onto their center-of-mass vector. We notice that 
+the adhesive force is repulsive in the contact region, while for the rest of the membranes there is an attractive force
+that acts to pull the two vesicles together. The summary of boundary integral formulation can be found in Appendix \ref{sec:AppendixB} and
+Appendix \ref{sec:AppendixC}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Integral Equation Formulation}
-Using potential theory and following~\cite{Veerapaneni2009_JCP}, we recast the governing equations~\eqref{eq:gov} as integro-differential equations for the evolution of membrane positions: 
-%
-\begin{align*}
-  &\dot{\xx} = \uu_{\infty}(\xx) + \SS[\xxi](\xx), \\
-  &\xx_s \cdot \dot{\xx}_s = 0,
- \end{align*}
-%
-where the single-layer potential $\SS[\cdot]$ is defined by
-\begin{align}
-  \SS[\xxi](\xx) &= \frac{1}{4\pi\mu} \int_\gamma \left(
-    -\log \|\xx - \yy\| + \frac{(\xx - \yy) \otimes (\xx - \yy)}{\|\xx - \yy\|^2} \right) 
-    \xxi(\yy) ds_\yy, 
-  \label{eqn:SLP}
-\end{align}
-%
-and the membrane force $\xxi$ is a sum of the bending, tension and adhesion forces: 
-\begin{equation*}
-\xxi = -\kappa_b \xx_{ssss} + (\sigma \xx_s)_s + \AA\xx.
-\end{equation*}
-Defining the bending operator as $\BB[\xx](\ff) = -\kappa_b \ff_{ssss}$,
-and the tension operator $\TT[\xx](\sigma) = (\sigma \xx_s)_s$, the
-no-slip boundary condition gives
-\begin{align*}
-  \pderiv{\xx}{t} = \SS \BB \xx + \SS \TT \sigma + \SS \AA \xx.
-\end{align*}
-We apply the IMEX-Euler method 
-\begin{align*}
-  \frac{\xx^{N+1} - \xx^N}{\Delta t} = \SS^N \BB^N \xx^{N+1} + 
-  \SS^N \TT^N \sigma^{N+1} + \SS^N \AA^N \xx^N,
-\end{align*}
-that discretizes both the bending and tension terms
-semi-implicitly~\cite{qua-bir2014}, and the adhesive term explicitly.
-Therefore, a single time step requires solving
-\begin{align*}
-  \xx^{N+1} - \Delta t \SS^N \BB^N \xx^{N+1} - 
-    \Delta t \SS^N \TT^N \sigma^{N+1} = \xx^N + 
-    \Delta t \SS^N \AA^N \xx^N,
-\end{align*}
-along with the inextensibility constraint that is discretized as
-\begin{align*}
-  \xx_s^{N} \cdot \xx_{s}^{N+1} = 1.
-\end{align*}
-We discretize the vesicles at a set of collocation points, compute the
-bending and tension terms with Fourier differentiation, and apply Alpert
-quadrature~\cite{alp1999} to the weakly-singular single-layer potential
-$\SS$.  The source and target points of the adhesion force never
-coincide since they are always on different vesicles, so the adhesion
-force~\eqref{eqn:adhesionForce} is computed with the spectrally accurate
-trapezoid rule~\cite{tre-wei2014}.
-
-The dynamics of a doublet undergoes many different time scales over time
-horizons that are sufficiently large to characterize the formation of a
-doublet and its rheological properties.  Therefore, time adaptivity is
-crucial so that a user-specified tolerance is achieved without using a
-guess-and-check procedure to find an appropriately small fixed time step
-size.  To control the error and achieve second-order accuracy in time,
-we use a time adaptive spectral deferred correction method that
-applies IMEX-Euler twice per time step~\cite{quaife2016adaptive}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The Shear and Normal Stresses}
-To characterize the rheological properties of the suspension of a
-doublet, it is necessary to compute the shear and normal stresses.  At a
-point $\xx \in \RR^2 \backslash \gamma$ in the fluid bulk, the velocity
-$\uu(\xx)$, pressure $p(\xx)$, and total stress tensor $T = - p I +
-\nabla \uu + \nabla \uu^T$ of the single-layer potential~\eqref{eqn:SLP}
-are
-\begin{align*}
-  \uu(\xx) &= \SS_\uu[\ff](\xx) = \frac{1}{4\pi\mu}\int_{\gamma} \left( 
-    -\log \rho + \frac{\rr \otimes \rr}{\rho^2} \right) 
-    \ff ds_\yy, \\
-    p(\xx) &= \SS_p[\ff](\xx) = \frac{1}{2\pi} \int_{\gamma} 
-    \frac{\rr \cdot \ff}{\rho^2} ds_\yy, \\
-    T(\xx) &= \SS_T[\ff](\xx) = -\frac{1}{\pi}\int_{\gamma}
-      \frac{\rr \cdot \ff}{\rho^2} 
-      \frac{\rr \otimes \rr}{\rho^2} ds_\yy,
-\end{align*}
-where $\rr = \xx - \yy$, and $\rho = \|\xx - \yy\|$.  To compute the
-stress tensor on a vesicle, there is a jump in the layer potential
-$\SS_T$, and the stress tensor is
-\begin{align*}
-  T(\xx) = \frac{1}{2}(\nn \otimes \ff) + \frac{1}{2} \left(
-    \tt \otimes \left[
-    \begin{array}{cc}
-      2 t_x t_y & t_y^2 - t_x^2 \\
-      t_y^2 - t_x^2 & -2 t_x t_y
-    \end{array}
-    \right] \ff \right) + 
-  \SS_T[\ff](\xx), \quad \xx \in \gamma,
-\end{align*}
-where $\nn$ and $\tt$ are the vesicle's outward unit normal and tangent
-vector, respectively.  With the stress tensor computed for $\xx \in
-\gamma$, the shear and normal stresses are
-\begin{align*}
-  \tau^\tt = (T \nn) \cdot \tt, \qquad
-  \tau^\nn = (T \nn) \cdot \nn.
-\end{align*}
 
@@
 
+\section{Integral Equation Formulation}
+\label{sec:AppendixB}
+Using potential theory and following~\cite{Veerapaneni2009_JCP}, we recast the governing equations~\eqref{eq:gov} as integro-differential equations for the evolution of membrane positions: 
+%
+\begin{align*}
+  &\dot{\xx} = \uu_{\infty}(\xx) + \SS[\xxi](\xx), \\
+  &\xx_s \cdot \dot{\xx}_s = 0,
+ \end{align*}
+%
+where the single-layer potential $\SS[\cdot]$ is defined by
+\begin{align}
+  \SS[\xxi](\xx) &= \frac{1}{4\pi\mu} \int_\gamma \left(
+    -\log \|\xx - \yy\| + \frac{(\xx - \yy) \otimes (\xx - \yy)}{\|\xx - \yy\|^2} \right) 
+    \xxi(\yy) ds_\yy, 
+  \label{eqn:SLP}
+\end{align}
+%
+and the membrane force $\xxi$ is a sum of the bending, tension and adhesion forces: 
+\begin{equation*}
+\xxi = -\kappa_b \xx_{ssss} + (\sigma \xx_s)_s + \AA\xx.
+\end{equation*}
+Defining the bending operator as $\BB[\xx](\ff) = -\kappa_b \ff_{ssss}$,
+and the tension operator $\TT[\xx](\sigma) = (\sigma \xx_s)_s$, the
+no-slip boundary condition gives
+\begin{align*}
+  \pderiv{\xx}{t} = \SS \BB \xx + \SS \TT \sigma + \SS \AA \xx.
+\end{align*}
+We apply the IMEX-Euler method 
+\begin{align*}
+  \frac{\xx^{N+1} - \xx^N}{\Delta t} = \SS^N \BB^N \xx^{N+1} + 
+  \SS^N \TT^N \sigma^{N+1} + \SS^N \AA^N \xx^N,
+\end{align*}
+that discretizes both the bending and tension terms
+semi-implicitly~\cite{qua-bir2014}, and the adhesive term explicitly.
+Therefore, a single time step requires solving
+\begin{align*}
+  \xx^{N+1} - \Delta t \SS^N \BB^N \xx^{N+1} - 
+    \Delta t \SS^N \TT^N \sigma^{N+1} = \xx^N + 
+    \Delta t \SS^N \AA^N \xx^N,
+\end{align*}
+along with the inextensibility constraint that is discretized as
+\begin{align*}
+  \xx_s^{N} \cdot \xx_{s}^{N+1} = 1.
+\end{align*}
+We discretize the vesicles at a set of collocation points, compute the
+bending and tension terms with Fourier differentiation, and apply Alpert
+quadrature~\cite{alp1999} to the weakly-singular single-layer potential
+$\SS$.  The source and target points of the adhesion force never
+coincide since they are always on different vesicles, so the adhesion
+force~\eqref{eqn:adhesionForce} is computed with the spectrally accurate
+trapezoid rule~\cite{tre-wei2014}.
+
+The dynamics of a doublet undergoes many different time scales over time
+horizons that are sufficiently large to characterize the formation of a
+doublet and its rheological properties.  Therefore, time adaptivity is
+crucial so that a user-specified tolerance is achieved without using a
+guess-and-check procedure to find an appropriately small fixed time step
+size.  To control the error and achieve second-order accuracy in time,
+we use a time adaptive spectral deferred correction method that
+applies IMEX-Euler twice per time step~\cite{quaife2016adaptive}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{The Shear and Normal Stresses}
+\label{sec:AppendixC}
+To characterize the rheological properties of the suspension of a
+doublet, it is necessary to compute the shear and normal stresses.  At a
+point $\xx \in \RR^2 \backslash \gamma$ in the fluid bulk, the velocity
+$\uu(\xx)$, pressure $p(\xx)$, and total stress tensor $T = - p I +
+\nabla \uu + \nabla \uu^T$ of the single-layer potential~\eqref{eqn:SLP}
+are
+\begin{align*}
+  \uu(\xx) &= \SS_\uu[\ff](\xx) = \frac{1}{4\pi\mu}\int_{\gamma} \left( 
+    -\log \rho + \frac{\rr \otimes \rr}{\rho^2} \right) 
+    \ff ds_\yy, \\
+    p(\xx) &= \SS_p[\ff](\xx) = \frac{1}{2\pi} \int_{\gamma} 
+    \frac{\rr \cdot \ff}{\rho^2} ds_\yy, \\
+    T(\xx) &= \SS_T[\ff](\xx) = -\frac{1}{\pi}\int_{\gamma}
+      \frac{\rr \cdot \ff}{\rho^2} 
+      \frac{\rr \otimes \rr}{\rho^2} ds_\yy,
+\end{align*}
+where $\rr = \xx - \yy$, and $\rho = \|\xx - \yy\|$.  To compute the
+stress tensor on a vesicle, there is a jump in the layer potential
+$\SS_T$, and the stress tensor is
+\begin{align*}
+  T(\xx) = \frac{1}{2}(\nn \otimes \ff) + \frac{1}{2} \left(
+    \tt \otimes \left[
+    \begin{array}{cc}
+      2 t_x t_y & t_y^2 - t_x^2 \\
+      t_y^2 - t_x^2 & -2 t_x t_y
+    \end{array}
+    \right] \ff \right) + 
+  \SS_T[\ff](\xx), \quad \xx \in \gamma,
+\end{align*}
+where $\nn$ and $\tt$ are the vesicle's outward unit normal and tangent
+vector, respectively.  With the stress tensor computed for $\xx \in
+\gamma$, the shear and normal stresses are
+\begin{align*}
+  \tau^\tt = (T \nn) \cdot \tt, \qquad
+  \tau^\nn = (T \nn) \cdot \nn.
+\end{align*}
+
 \end{appendices}

### 2019-02-13 vesicle_code/docs/adhesion/adhesion.tex
small changes and combined appendicies

@@
 
-Adhesion potential for a vesicle membrane has been modeled by a L.-J. type potential
+The Adhesion potential for a vesicle membrane has been modeled by a
+Lennard-Jones (L.-J.)~type potential
 %Sukumaran and Seifert~\cite{suk-sei2001} consider adhesion between a
@@
 \end{align}
-where $\mathcal{H}$ is the Hamaker constant and $\delta$ is the adhesion length
-scale. $z$ is the distance between a patch on the vesicle membrane and a point on the other object,
-which could be another vesicle membrane or a flat solid wall.  The characteristics of the L.-J. potential are summarized in
-the left panel of Figure~\ref{fig:adhesionModel}: The adhesive force is zero at the equilibrium distance $z=\delta$.
-For large distances ($z> \delta$) the adhesive potential is attractive while for small distances ($z < \delta$) the potential is repulsive to prevent physical contact.
-
-The exponents $(m,n)$ depend on the geometry and the molecular details of the two objects under
+where $\mathcal{H}$ is the Hamaker constant and $\delta$ is the adhesion
+length scale, and $z$ is the distance between a patch on the vesicle
+membrane and a point on the other object, which could be another vesicle
+membrane or a flat solid wall.  The characteristics of the
+L.-J.~potential are summarized in the left panel of
+Figure~\ref{fig:adhesionModel}: The adhesive force is zero at the
+equilibrium distance $z=\delta$.  For large distances ($z> \delta$) the
+adhesive potential is attractive while for small distances ($z <
+\delta$) the potential is repulsive to prevent physical contact.
+
+The exponents $(m,n)$ depend on the geometry and the molecular details
+of the two objects under
 adhesion~\cite{Book_IntermolecularSurfaceForces}: $(m,n)=(4,2)$
-corresponds to two flat, planar surfaces interacting with each other, and has been a common choice 
-for studying membrane-solid adhesion  \cite{Seifert1990_PRA,suk-sei2001,ShiFengGao2006_ActaMechSin, LinFreund2007_IntJSolidsStructures,BlountMiksisDavis2013_PRSa,YoungStone2017_PRF}.
-%
-On the other hand,
-$(m,n) = (12,6)$ corresponds to the Lennard-Jones (L.-J.)~potential
-between two molecules, and has been used to model membrane-membrane adhesion  \cite{FlormannAouane2017_SciReports}.  
-In our case, the adhesion potential in the
-integral of equation~(\eqref{eqn:adhesionForce}) is between two small
-patches of lipid bilayer membrane (because the lipid molecules are
-coarse-grained in the continuum modeling).  
-Thus a reasonable choice for
-$(m,n)$ between two coarse-grained membrane patches would be between
-those for two planar surfaces and two point molecules.
+corresponds to two flat, planar surfaces interacting with each other,
+and has been a common choice for studying membrane-solid adhesion
+\cite{Seifert1990_PRA,suk-sei2001, ShiFengGao2006_ActaMechSin,
+LinFreund2007_IntJSolidsStructures, BlountMiksisDavis2013_PRSa,
+YoungStone2017_PRF}.  On the other hand, $(m,n) = (12,6)$ corresponds to
+the L.-J.~potential between two molecules, and has been used to model
+membrane-membrane adhesion  \cite{FlormannAouane2017_SciReports}.  In
+our case, the adhesion potential in the integral of
+equation~\eqref{eqn:adhesionForce} is between two small patches of lipid
+bilayer membrane (because the lipid molecules are coarse-grained in the
+continuum modeling).  Thus a reasonable choice for $(m,n)$ between two
+coarse-grained membrane patches would be between those for two planar
+surfaces and two point molecules.
 
@@
 time.  We explore several combinations of $(m,n)$ in the simulations of
-two vesicles forming a doublet in a quiescent flow and in a shear flow.  We found that, as long as the
-close-range interaction is well resolved both in space (using the near-singular evaluations) 
-and time (using the high-order adaptive time integration), there is very
-little difference in both the dynamic evolution and equilibrium
-configuration between $(m,n)=(8,6)$ and $(m,n)=(4,2)$.  Therefore, in
-this work, we use $(m,n) = (4,2)$ to regulate the numerical stiffness introduced
-by the adhesive force. 
-%
-%For some simulations we used both sets of $(m,n)$ and did not notice significant difference
-%in terms of adhesive hydrodynamics of vesicles.
-
-Focusing on intermediate adhesive strengths, 
-we use Hamaker constants ranging from $\mathcal{O}(10^{-1})$ to
-$\mathcal{O}(10^0)$ times the bending rigidity modulus.  
-We assume that the adhesion force from equation~\ref{eq:adhesion_potential} applies
-between all pairs of points on different vesicles, and in
-Appendix~\ref{sec:appendixA} the net adhesive force at a point $\xx$ on
-vesicle $j$ is shown to be
+two vesicles forming a doublet in a quiescent flow and in a shear flow.
+We found that, as long as the close-range interaction is well resolved
+both in space (using the near-singular evaluations) and time (using the
+high-order adaptive time integration), there is very little difference
+in both the dynamic evolution and equilibrium configuration between
+$(m,n)=(8,6)$ and $(m,n)=(4,2)$.  Therefore, in this work, we use $(m,n)
+= (4,2)$ to regulate the numerical stiffness introduced by the adhesive
+force.
+
+Focusing on intermediate adhesive strengths, we use Hamaker constants
+ranging from $\mathcal{O}(10^{-1})$ to $\mathcal{O}(10^0)$ times the
+bending rigidity modulus.  We assume that the adhesion force from
+equation~\ref{eq:adhesion_potential} applies between all pairs of points
+on different vesicles, and in Appendix~\ref{sec:appendixA} the net
+adhesive force at a point $\xx$ on vesicle $j$ is shown to be
 \begin{align}
@@
 \end{align}
-This summation of adhesive forces is illustrated in the middle panel of Figure~\ref{fig:adhesionModel}. 
-The right panel of Figure~\ref{fig:adhesionModel} is an 
-example of the calculated adhesive force projected onto their center-of-mass vector. We notice that 
-the adhesive force is repulsive in the contact region, while for the rest of the membranes there is an attractive force
-that acts to pull the two vesicles together. The summary of boundary integral formulation can be found in Appendix \ref{sec:AppendixB} and
-Appendix \ref{sec:AppendixC}.
+This summation of adhesive forces is illustrated in the middle panel of
+Figure~\ref{fig:adhesionModel}.  The right panel of
+Figure~\ref{fig:adhesionModel} is an example of the calculated adhesive
+force projected onto their center-of-mass vector. We notice that the
+adhesive force is repulsive in the contact region, while for the rest of
+the membranes there is an attractive force that acts to pull the two
+vesicles together. The summary of boundary integral formulation can be
+found in Appendix~\ref{sec:AppendixB}.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Shear and Normal Stresses}
-\label{sec:AppendixC}
 To characterize the rheological properties of the suspension of a

### 2019-02-13 vesicle_code/docs/adhesion/adhesion.tex
more changes from yny

@@
 the adhesion strength.  Results from these numerical studies and
-analysis shed light on the hydrodynamic effects of adhesive interactions
+analysis shed light on the hydrodynamic and rheological consequences of adhesive interactions
 between vesicles in a viscous fluid.
@@
 membrane-membrane adhesion  \cite{FlormannAouane2017_SciReports}.  In
-our case, the adhesion potential in the integral of
-equation~\eqref{eqn:adhesionForce} is between two small patches of lipid
+our case, the adhesion potential 
+%in the integral of equation~\eqref{eqn:adhesionForce} 
+is between two small patches of lipid
 bilayer membrane (because the lipid molecules are coarse-grained in the
@@
 \label{sec:qflow} 
-We consider the suspension of two identical two-dimensional vesicles
+We consider two identical vesicles
 suspended in a quiescent flow.  Without any external forcing such as an

### 2019-02-13 vesicle_code/docs/adhesion/adhesion.tex
small edits

--- 2019-02-13 vesicle_code/docs/adhesion/adhesion.tex
@@
 expanding applications have encouraged detailed experimental,
-theoretical and numerical investigations of vesicle hydrodynamics in
-applied flow, electric and magnetic fields.  Theoretical
+theoretical, and numerical investigations of vesicle hydrodynamics in
+applied flow, electric fields, and magnetic fields.  Theoretical
 investigations often take the form of small-deformation analysis or
@@
 been developed for simulating the transient hydrodynamics of vesicle
-suspensions e.g., \cite{BagchiJohoson2005_JBE, Biben2005_EJP,
+suspensions~\cite{BagchiJohoson2005_JBE, Biben2005_EJP,
 Veerapaneni2009_JCP, SeolHuKimLai2016_JCP}.
@@
 dynamics~\cite{Misbah2006_PRL, Vlahovska2007_PRE}, and this leads to a
-transition in effective shear viscosity of the vesicle
+transition in the effective shear viscosity of the vesicle
 suspension~\cite{Misbah2006_PRL,Vitkova2008_BJ} that is also validated
@@
 The Adhesion potential for a vesicle membrane has been modeled by a
-Lennard-Jones (L.-J.)~type potential
+L.-J.~type potential
 %Sukumaran and Seifert~\cite{suk-sei2001} consider adhesion between a

### 2019-02-13 vesicle_code/docs/adhesion/adhesion.tex
fixed appendix B

@@
 Defining the bending operator as $\BB[\xx](\ff) = -\kappa_b \ff_{ssss}$,
-and the tension operator $\TT[\xx](\sigma) = (\sigma \xx_s)_s$, the
-no-slip boundary condition gives
-\begin{align*}
-  \pderiv{\xx}{t} = \SS \BB \xx + \SS \TT \sigma + \SS \AA \xx.
-\end{align*}
-We apply the IMEX-Euler method 
-\begin{align*}
-  \frac{\xx^{N+1} - \xx^N}{\Delta t} = \SS^N \BB^N \xx^{N+1} + 
-  \SS^N \TT^N \sigma^{N+1} + \SS^N \AA^N \xx^N,
-\end{align*}
-that discretizes both the bending and tension terms
-semi-implicitly~\cite{qua-bir2014}, and the adhesive term explicitly.
-Therefore, a single time step requires solving
+and the tension operator $\TT[\xx](\sigma) = (\sigma \xx_s)_s$, and
+using IMEX-Euler, the no-slip boundary results in the time stepping
+method
 \begin{align*}
@@
 \end{align*}
-along with the inextensibility constraint that is discretized as
+and the inextensibility constraint that is discretized as
 \begin{align*}

### 2019-02-13 vesicle_code/docs/adhesion/adhesion.tex
fixed Appendix B

@@
 and the membrane force $\xxi$ is a sum of the bending, tension and adhesion forces: 
-\begin{equation*}
+\begin{align*}
 \xxi = -\kappa_b \xx_{ssss} + (\sigma \xx_s)_s + \AA\xx.
-\end{equation*}
+\end{align*}
 Defining the bending operator as $\BB[\xx](\ff) = -\kappa_b \ff_{ssss}$,
-and the tension operator $\TT[\xx](\sigma) = (\sigma \xx_s)_s$, and
-using IMEX-Euler, the no-slip boundary results in the time stepping
-method
+the tension operator $\TT[\xx](\sigma) = (\sigma \xx_s)_s$, and using
+IMEX-Euler, the no-slip boundary results in the time stepping method
 \begin{align*}
@@
 doublet, it is necessary to compute the shear and normal stresses.  At a
-point $\xx \in \RR^2 \backslash \gamma$ in the fluid bulk, the velocity
-$\uu(\xx)$, pressure $p(\xx)$, and total stress tensor $T = - p I +
-\nabla \uu + \nabla \uu^T$ of the single-layer potential~\eqref{eqn:SLP}
-are
-\begin{align*}
-  \uu(\xx) &= \SS_\uu[\ff](\xx) = \frac{1}{4\pi\mu}\int_{\gamma} \left( 
-    -\log \rho + \frac{\rr \otimes \rr}{\rho^2} \right) 
-    \ff ds_\yy, \\
-    p(\xx) &= \SS_p[\ff](\xx) = \frac{1}{2\pi} \int_{\gamma} 
-    \frac{\rr \cdot \ff}{\rho^2} ds_\yy, \\
-    T(\xx) &= \SS_T[\ff](\xx) = -\frac{1}{\pi}\int_{\gamma}
-      \frac{\rr \cdot \ff}{\rho^2} 
-      \frac{\rr \otimes \rr}{\rho^2} ds_\yy,
-\end{align*}
-where $\rr = \xx - \yy$, and $\rho = \|\xx - \yy\|$.  To compute the
-stress tensor on a vesicle, there is a jump in the layer potential
-$\SS_T$, and the stress tensor is
-\begin{align*}
-  T(\xx) = \frac{1}{2}(\nn \otimes \ff) + \frac{1}{2} \left(
+point $\xx \in \RR^2 \backslash \gamma$ in the fluid bulk, the  pressure
+$p(\xx)$ and total stress tensor $T = - p I + \nabla \uu + \nabla \uu^T$
+of the single-layer potential~\eqref{eqn:SLP} are
+\begin{align*}
+    p(\xx) &= \frac{1}{2\pi} \int_{\gamma} 
+    \frac{(\xx - \yy) \cdot \xxi}{\|\xx-\yy\|^2} ds_\yy, \\
+    T(\xx) &= -\frac{1}{\pi}\int_{\gamma}
+      \frac{(\xx-\yy) \cdot \xxi}{\|\xx - \yy\|^2} 
+      \frac{(\xx - \yy) \otimes (\xx - \yy)}{\|\xx - \yy\|^2} ds_\yy.
+\end{align*}
+To compute the stress tensor on a vesicle, there is a jump in the layer
+potential, and the stress tensor is
+\begin{align*}
+  T(\xx) = \frac{1}{2}(\nn \otimes \xxi) + \frac{1}{2} \left(
     \tt \otimes \left[
@@
     \end{array}
-    \right] \ff \right) + 
-  \SS_T[\ff](\xx), \quad \xx \in \gamma,
+    \right] \xxi \right) + 
+  \SS_T[\xxi](\xx), \quad \xx \in \gamma,
 \end{align*}

### 2019-02-13 vesicle_code/docs/adhesion/adhesion.tex
appendix B

@@
 \end{align*}
-To compute the stress tensor on a vesicle, there is a jump in the layer
-potential, and the stress tensor is
-\begin{align*}
-  T(\xx) = \frac{1}{2}(\nn \otimes \xxi) + \frac{1}{2} \left(
+From these identities and the jump in the stress tensor, we compute the
+traction vector on the vesicle as
+\begin{align*}
+  T\nn = \left(T(\xx) + 
+  \frac{1}{2}(\nn \otimes \xxi) + \frac{1}{2} 
     \tt \otimes \left[
@@
     \end{array}
-    \right] \xxi \right) + 
-  \SS_T[\xxi](\xx), \quad \xx \in \gamma,
+    \right] \xxi\right) \nn, \quad \xx \in \gamma,
 \end{align*}
 where $\nn$ and $\tt$ are the vesicle's outward unit normal and tangent
-vector, respectively.  With the stress tensor computed for $\xx \in
-\gamma$, the shear and normal stresses are
-\begin{align*}
-  \tau^\tt = (T \nn) \cdot \tt, \qquad
-  \tau^\nn = (T \nn) \cdot \nn.
-\end{align*}
+vector, respectively.
+
+%With the stress tensor computed for $\xx \in
+%\gamma$, the shear and normal stresses are
+%\begin{align*}
+%  \tau^\tt = (T \nn) \cdot \tt, \qquad
+%  \tau^\nn = (T \nn) \cdot \nn.
+%\end{align*}
 

### 2019-02-13 vesicle_code/docs/adhesion/adhesion.tex
last minute changes

@@
 
-\title{Hydrodynamics and rheology of adhesive vesicle doublets}
+\title{Hydrodynamics and rheology of vesicle doublets}
 % Force line breaks with \\
@@
   \llbracket T \rrbracket \nn = \xxi, \quad &\xx \in \gamma,
-    &&\mbox{\em non-zero traction jump}
+    &&\mbox{\em non-zero stress jump}
 \end{aligned} \label{eq:gov}
@@
 where $\llbracket T \rrbracket$ is the jump in the stress tensor, and
-$\xxi$ is the traction jump that is the sum of the bending, stretching,
+$\xxi$ is the traction that is the sum of the bending, stretching,
 and adhesion forces.  The bending force, arising from the Helfrich
@@
   [\mu]:= \frac{\mu_{\mathrm{eff}} - \mu_0}{\phi \mu_0} = 
-  \frac{1}{\chi \mu_0 T} \int_{T_i}^{T_e} 
-  \langle \sigma_{12} \rangle dt,
+  \frac{1}{\chi \mu_0 (T_e - T_i)} \int_{T_i}^{T_e} 
+  \langle \tau_{12} \rangle dt,
 \end{align*}
@@
 $\phi$ is the area fraction of vesicles, $\tau$ is the stress due to the
-vesicles, and $\langle \cdot \rangle$ is the spatial average.  In the
-left plot of Figure~\ref{fig:shearIntrinsicViscosity}, we compare the
+vesicles, $\langle \cdot \rangle$ is the spatial average, and $\xxi$ is
+the traction as defined in equation~\eqref{eqn:traction}.  In the left
+plot of Figure~\ref{fig:shearIntrinsicViscosity}, we compare the
 intrinsic viscosity of a single tank-treading vesicle to a doublet.  To
@@
 $\mathcal{H} = 0.7$ and separation distance $\delta = 0.4$.  From left
-to right, the plots are the initial condition, streamlines at an
-intermediate time, tension at the steady-state configuration, and the
-adhesion force projected onto the outward unit normal at the
+to right, the plots are the initial condition, the streamlines at an
+intermediate time, the tension at the steady-state configuration, and
+the adhesion force projected onto the outward unit normal at the
 steady-state configuration.  Along the bounding vesicle, the tension is
@@
 and the membrane force $\xxi$ is a sum of the bending, tension and adhesion forces: 
-\begin{align*}
+\begin{align}
 \xxi = -\kappa_b \xx_{ssss} + (\sigma \xx_s)_s + \AA\xx.
-\end{align*}
-Defining the bending operator as $\BB[\xx](\ff) = -\kappa_b \ff_{ssss}$,
-the tension operator $\TT[\xx](\sigma) = (\sigma \xx_s)_s$, and using
+\label{eqn:traction}
+\end{align}
+Defining the bending operator as $\BB[\ff](\xx) = -\kappa_b \ff_{ssss}$,
+the tension operator $\TT[\sigma](\xx) = (\sigma \xx_s)_s$, and using
 IMEX-Euler, the no-slip boundary results in the time stepping method
@@
 
-To characterize the rheological properties of the suspension of a
-doublet, it is necessary to compute the shear and normal stresses.  At a
-point $\xx \in \RR^2 \backslash \gamma$ in the fluid bulk, the  pressure
-$p(\xx)$ and total stress tensor $T = - p I + \nabla \uu + \nabla \uu^T$
-of the single-layer potential~\eqref{eqn:SLP} are
-\begin{align*}
-    p(\xx) &= \frac{1}{2\pi} \int_{\gamma} 
-    \frac{(\xx - \yy) \cdot \xxi}{\|\xx-\yy\|^2} ds_\yy, \\
-    T(\xx) &= -\frac{1}{\pi}\int_{\gamma}
-      \frac{(\xx-\yy) \cdot \xxi}{\|\xx - \yy\|^2} 
-      \frac{(\xx - \yy) \otimes (\xx - \yy)}{\|\xx - \yy\|^2} ds_\yy.
-\end{align*}
-From these identities and the jump in the stress tensor, we compute the
-traction vector on the vesicle as
-\begin{align*}
-  T\nn = \left(T(\xx) + 
-  \frac{1}{2}(\nn \otimes \xxi) + \frac{1}{2} 
-    \tt \otimes \left[
-    \begin{array}{cc}
-      2 t_x t_y & t_y^2 - t_x^2 \\
-      t_y^2 - t_x^2 & -2 t_x t_y
-    \end{array}
-    \right] \xxi\right) \nn, \quad \xx \in \gamma,
-\end{align*}
-where $\nn$ and $\tt$ are the vesicle's outward unit normal and tangent
-vector, respectively.
-
+%To characterize the rheological properties of the suspension of a
+%doublet, it is necessary to compute the shear and normal stresses.  At a
+%point $\xx \in \RR^2 \backslash \gamma$ in the fluid bulk, the  pressure
+%$p(\xx)$ and total stress tensor $T = - p I + \nabla \uu + \nabla \uu^T$
+%of the single-layer potential~\eqref{eqn:SLP} are
+%\begin{align*}
+%    p(\xx) &= \frac{1}{2\pi} \int_{\gamma} 
+%    \frac{(\xx - \yy) \cdot \xxi}{\|\xx-\yy\|^2} ds_\yy, \\
+%    T(\xx) &= -\frac{1}{\pi}\int_{\gamma}
+%      \frac{(\xx-\yy) \cdot \xxi}{\|\xx - \yy\|^2} 
+%      \frac{(\xx - \yy) \otimes (\xx - \yy)}{\|\xx - \yy\|^2} ds_\yy.
+%\end{align*}
+%From these identities and the jump in the stress tensor, we compute the
+%traction vector on the vesicle as
+%\begin{align*}
+%  T(\xx)\nn = \left(
+%  \frac{1}{2}(\nn \otimes \xxi) + \frac{1}{2} 
+%    \tt \otimes \left[
+%    \begin{array}{cc}
+%      2 t_x t_y & t_y^2 - t_x^2 \\
+%      t_y^2 - t_x^2 & -2 t_x t_y
+%    \end{array}
+%    \right] \xxi\right) \nn
+%    -\frac{1}{\pi}\int_{\gamma}
+%      \frac{(\xx-\yy) \cdot \xxi}{\|\xx - \yy\|^2} 
+%      \frac{(\xx - \yy) \cdot \nn}{\|\xx - \yy\|^2} (\xx - \yy)ds_\yy,
+%     \quad \xx \in \gamma,
+%\end{align*}
+%where $\nn$ and $\tt$ are the vesicle's outward unit normal and tangent
+%vector, respectively.  
+%
 %With the stress tensor computed for $\xx \in

### 2019-02-14 vesicle_code/docs/adhesion/adhesion.tex
changes as of Feb 12 9pm by yny

@@
 
-\title{Hydrodynamics and rheology of vesicle doublets}
+\title{Hydrodynamics and rheology of a vesicle doublet suspension}
 % Force line breaks with \\
@@
 In a planar shear flow, numerical simulations reveal that a vesicle
-doublet may form as two vesicles approach each other provided that the adhesion
+doublet may form provided that the adhesion
 strength is sufficiently large at a given vesicle reduced area. Once a
 doublet is formed, the effective shear viscosity of a dilute suspension
-of vesicle doublets is found to be a function of both reduced area and
-the adhesion strength.  Results from these numerical studies and
+of vesicle doublets is found to be a function of  reduced area.  Results from these numerical studies and
 analysis shed light on the hydrodynamic and rheological consequences of adhesive interactions
@@
 widely utilized as biological cell mimics in biophysics and material
-engineering~\cite{sackmann1996, Barthes-Biesel2016_ARFM}.  The ever
-expanding applications have encouraged detailed experimental,
-theoretical, and numerical investigations of vesicle hydrodynamics in
-applied flow, electric fields, and magnetic fields.  Theoretical
-investigations often take the form of small-deformation analysis or
-spheroidal dynamics of a nearly-spherical vesicle (or nearly-circular in
-two dimensions) subjected to an applied flow or under an external
-forcing~\cite{Barthes-BieselRallison1981_JFM, Misbah2006_PRL,
+engineering~\cite{sackmann1996, FenzSengupta2012_IntegrBiol,Barthes-Biesel2016_ARFM}.  The ever
+expanding applications of vesicles have encouraged detailed experimental,
+theoretical, and numerical investigations of vesicle dynamics in
+applied flow, electric fields, and magnetic fields.  
+Experimental investigations of vesicles have uncovered vesicle properties and various novel applications
+\cite{Dobereiner2000_CurrentOpinionCIS,EvansRawiczSmith2013_FaradayDiscussions,SugiyamaToyota2018_Life}. 
+Theoretical investigations are often limited to small-deformation analysis on a nearly spherical vesicle
+or spheroidal analysis on a spheroidal vesicle \cite{Barthes-BieselRallison1981_JFM, Misbah2006_PRL,
 Vlahovska2007_PRE, Finken2008_EPL, ZhangZahnTanLin2013_PoF,
@@
 FlormannAouane2017_SciReports}.  As a model for red blood cell (RBC)
-aggregates, an idealized model for adhesive vesicle-vesicle interactions
-gives rise to vesicle configurations similar to those observed in
+aggregates, a simplified model for adhesive vesicle-vesicle interactions
+can reproduce vesicle shapes similar to those observed in
 experiments of fibrinogen-induced RBC
@@
 RBCs, Flormann {\em et al.}~\cite{FlormannAouane2017_SciReports} found
-the contact zone to buckle under strong adhesion.  A direct consequence
-of the buckling is the sigmoidal shape of the adhesion region, which is
+that, under strong adhesion, 
+the membrane may buckle to a sigmoidal shape in the contact region.
+Such a sigmoidal vesicle shape is 
 also observed in RBC doublets and explained in a slightly different
@@
 ShiFengGao2006_ActaMechSin, LinFreund2007_IntJSolidsStructures,
-GruhnFrankeDimova2007_Langmuir,das2008adhesion, zhang2009phase,
-SteinkuhlerAgudo-Canalejo2016_BJ} than the transient adhesion
+GruhnFrankeDimova2007_Langmuir,das2008adhesion, zhang2009phase,Agudo-Canalejo2015_ACSNano,Agudo-CanalejoLipowsky2015_NanoLett,
+SteinkuhlerAgudo-Canalejo2016_BJ,Agudo-CanalejoLipowsky2017_SoftMatt} than the transient adhesion
 process~\cite{cantat1999lift, suk-sei2001, BlountMiksisDavis2013_PRSa}.
@@
 fluctuating hydrodynamics in the thin film between two vesicles enhance
-adhesion to keep vesicles bound under linear flows?  Recently Liu {\em
+adhesion to keep vesicles bound under linear flows as speculated in cells \cite{FenzBihrSchmidt2017_NaturePhys}?  Recently Liu {\em
 et al.}~\cite{LiuChuNewbyRead2018_bioRxiv} used immersed boundary
@@
 contact. We are actively pursuing this direction with hydrodynamic
-modeling and simulations of adhesive membranes with thermal fluctions.
+modeling and simulations of adhesive membranes with thermal fluctuations.
 

### 2019-02-14 vesicle_code/docs/adhesion/adhesion.tex
more changes from yny

@@
 %  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
-   \includegraphics[keepaspectratio=true,scale=0.5]{figs/Dec18_vesicle_shape_vs_rA_composite.png}
+   \includegraphics[keepaspectratio=true,scale=0.45]{figs/Dec18_vesicle_shape_vs_rA_composite.png}
   \caption{\label{fig:Dec18_vesicle_shape} Equilibrium configurations of
@@
   three values of $\Delta A$.  The vesicle reduced areas of $\Delta
-  A=0.95$, $0.75$, and $0.6$ are labeled.  The color coding is the
-  tension along the vesicle.  The vesicle length is fixed at $2\pi$, the
+  A=0.95$, $0.75$, and $0.6$ are labeled.  The vesicle length is fixed at $2\pi$, the
   dimensionless bending rigidity modulus is $\kappa_b=1$, the Hamaker
   constant is $\mathcal{H}=5$, and the separation distance is
-  $\delta=0.2$.  {\em Left}: The overall equilibrium shapes of two
+  $\delta=0.2$.  {\em Left}:  The color coding is the
+  tension along the vesicle.  The overall equilibrium shapes of two
   vesicles under adhesive interactions vary with the reduced area.  {\em
-  Right}: The membrane shapes in the contact region.} 
+  Right}: The membrane shapes in the contact region. The color coding is the adhesive force
+  projected along the center-of-mass vector.} 
 \end{figure}
@@
 grants DMS-1719834 and DMS-1454010.  YNY acknowledges support from
-NSF-DMS 1614863 and 1412789.  The work of SV and YNY was also supported
+NSF-DMS 1614863 and NSF-DMS 1412789.  Both SV and YNY were also supported
 by the Flatiron Institute, a division of Simons Foundation.

### 2019-02-14 vesicle_code/docs/adhesion/adhesion.tex
changes from yny

@@
 %\documentclass[aps,prb,showpacs,amsmath,amssymb,superscriptaddress]{revtex4-1}
-\documentclass[prf,superscriptaddress,showpacs]{revtex4-1}
+\documentclass[prf,superscriptaddress,showkeys]{revtex4-1}
 
@@
 
-\pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
+\pacs{87.16.D-,83.80.Lz,83.60.-a,47.11.Hj}% PACS, the Physics and Astronomy
                              % Classification Scheme.
-%\keywords{Suggested keywords}%Use showkeys class option if keyword
+\keywords{Vesicle hydrodynamics, membrane adhesion, drop and bubble phenomena/drop interactions, interfacial flows/thin fluid films, rheology/flow confinement, biological fluid dynamics/collective behavior/clustering, emergence of patterns}%Use showkeys class option if keyword
                               %display desired
@@
 membranes with adhesion.  However, adhesive interactions between RBCs
-lead to different RBC clusters that are expected to alter the
+lead to RBC clusters that are expected to alter the
 rheological properties of the RBC suspension~\cite{NeuMeiselman2002_BJ,
@@
 a solid (such as a glass substrate or a nano particle).  Adhesion
-between a vesicle and a substrate has been extensively studied with more
+between a vesicle and a solid has been extensively studied with more
 focus on the static equilibrium shapes~\cite{Seifert1990_PRA,
@@
 adhesion is crucial to initiate membrane fusion and fission in
-endocytosis and exocytosis and the transport of small vesicles through
+endocytosis, exocytosis and the transport of small vesicles through
 membrane surfaces.  In the absence of an external electric field and
@@
 component~\cite{Book_IntermolecularSurfaceForces}, and the combination
-of the two gives rise to adhesion at the separation distance that
-minimizes the interaction
-potential~\cite{Book_IntermolecularSurfaceForces}.
-
+of the two gives rise to an equilibrium distance
+where the interaction potential is at minimum~\cite{Book_IntermolecularSurfaceForces}.
+
+The strength of membrane-membrane adhesion can be estimated through the membrane contact angle at the edge of contact zone \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir,MaresDanielIglic2012_SciWorldJ}.
+Alternatively,
 Evans and Metcalfe~\cite{EvansMetcalfe1984_BJ} used the micropipette to
@@
 The union of all vesicles is denoted by $\gamma$.  Given a background
-velocity $\uu_\infty$, the governing equations are
+velocity $\uu_\infty$, the governing (dimensionless) equations are
 \begin{equation}
@@
   \llbracket T \rrbracket \nn = \xxi, \quad &\xx \in \gamma,
-    &&\mbox{\em non-zero stress jump}
+    &&\mbox{\em stress balance on membranes}
 \end{aligned} \label{eq:gov}
 \end{equation}
-where $\llbracket T \rrbracket$ is the jump in the stress tensor, and
+where $\uu$ is the fluid velocity field, $p$ is the pressure, and the scaled viscosity $\mu=1$ inside the vesicles.
+$\mu=\mu_e/\mu_i$ outside the vesicle, with $\mu_i$ ($\mu_e$)  the viscosity of interior  (exterior) fluid.  We set
+the viscosity ratio $\mu_e/\mu_i=1$ for the rest of the paper.
+$T = - p I + \mu\left(\nabla \uu + \nabla \uu^T\right)$ is the stress tensor, $\llbracket T \rrbracket$ is the jump across membrane, and
 $\xxi$ is the traction that is the sum of the bending, stretching,
-and adhesion forces.  The bending force, arising from the Helfrich
-energy model, is $\BB \xx = -\kappa_b \xx_{ssss}$, where $\kappa_b$ is
+and adhesion forces defined in equation~(\ref{eqn:traction}).  The bending force, arising from the Helfrich
+energy model, is $\BB \xx = -\kappa_b \xx_{ssss}$, where the subscript $s$ denotes derivative with respect to arclength $s$. $\kappa_b$ is
 the bending rigidity modulus which we set to be 1 for all examples. The
@@
 
-The Adhesion potential for a vesicle membrane has been modeled by a
+The adhesion potential for a vesicle membrane has been modeled by a
 L.-J.~type potential
@@
 
-The exponents $(m,n)$ depend on the geometry and the molecular details
+The exponents $(m,n)$ in equation~(\ref{eq:adhesion_potential}) depend on the geometry and the molecular details
 of the two objects under
@@
   \label{eq:Fh}
-  F(h) \sim \mathcal{H} \frac{\delta^m}{h^{m+1}}
-    \left(\left(\frac{\delta}{h}\right)^{m-n}-1\right),
+  F(h) \sim \mathcal{H} \frac{m\delta^m}{h^{m+1}}
+    \left(1-\left(\frac{\delta}{h}\right)^{n-m}\right),
 \end{align}
-with $n>m\ge 2$ being integers, attraction is dominant at ``large"
+with integers $m>n\ge 2$.  Attraction is dominant at ``large"
 distances ($h > \delta$) while repulsion is dominant at ``small"
@@
     \int^{h(t)}_{h(0)}-\frac{dh}{h^3 F^{1/3}} = 
-    -\frac{1}{\mathcal{H}^{1/3}\delta^{5/3}}\int^{\bar{h}(t)}_{\bar{h}(0)}
+    -\frac{1}{m^{1/3}\mathcal{H}^{1/3}\delta^{5/3}}\int^{\bar{h}(t)}_{\bar{h}(0)}
       \frac{d \bar{h}}{\bar{h}^{(8-m)/3}(\bar{h}^{m-n}-1)^{1/3}}.
@@
 \label{eq:teq_scaling}
-  t\sim \frac{\mu R_0^{10/3}}{K_a^{2/3}}\frac{1}{\mathcal{H}^{1/3}\delta^{5/3}},
+  t\sim \frac{\mu R_0^{10/3}}{K_a^{2/3}}\frac{1}{ m^{1/3} \mathcal{H}^{1/3}\delta^{5/3}},
 \end{align}
@@
 
-The right plot of Figure~\ref{fig:Dec18_vesicle_shape} is a zoom on the
+The right plot of Figure~\ref{fig:Dec18_vesicle_shape} is a zoom (not to-scale) on the
 membranes in the contact region, where the membranes are not perfectly
-flat---at all reduced area we observe that the membranes are slightly
+flat at all three values of reduced area: We observe that the membranes are slightly
 curved with a dip at the edge.  Such membrane undulation in the contact
-region is predicted by lubrication analyses on a membrane under adhesion
+region is predicted by lubrication analyses on an elastic membrane under adhesion
 with a solid substrate~\cite{BlountMiksisDavis2013_PRSa,
-YoungStone2017_PRF}.  Also the dip at the edge of contact region is
-related to but different from the buckling of membrane under strong
-adhesion: A closer inspection on the dip at the edge shows that the
-membrane distance is smaller than the neutral separation distance
-$\delta$ there. Thus the adhesion force is attractive for most of the
-membranes in the contact region except at the edge, where the adhesive
-force turns repulsive.  Results from the lubrication analysis show that
+YoungStone2017_PRF}.  
+%
+Results from the lubrication analysis show that
 this dip and slightly curved shape in the contact region are independent
@@
 Section~\ref{sec:eflow}).
+
+Also the dip at the edge of contact region is
+related to (but different from) the buckling of membrane under strong
+adhesion: A closer inspection on the dip at the edge shows that the
+membrane distance is smaller than the neutral separation distance
+$\delta$ there for more deflated vesicles.
+For $\triangle A =0.6$ and $0.75$  the adhesion force is mostly attractive
+ in the contact region except at the edge, where the adhesive
+force turns repulsive.  For $\triangle A=0.95$, however, the adhesion force is mostly repulsive,
+leading to large tension in the rest of the vesicle membrane.
 
@@
 fluid trap to measure the adhesion strength between two bound vesicle
-membranes, we propose the following thought experiment.  Beginning with
+membranes, we propose the following experiment.  Beginning with
 two identical vesicles in an equilibrium configuration that form a
@@
 
-In the following numerical experiments we initially place a vesicle
-doublet with $\theta=\pi$, so that the diverging flow may be strong
-enough to pull vesicles away from the doublet.  At low extensional
-rates, we expect the doublet to stay bound at the fluid trap stagnation
-point.  On the other hand, the vesicle doublet may become unstable and
-eventually separate at higher extensional rates.  Thus we expect there
-to exist a critical extensional rate $\chi_c$ above which the vesicle
-doublet cannot stay bound under a given adhesion potential.  Therefore,
-the dependence of the critical extensional rate $\chi_c$ on the adhesion
-potential and the mechanical vesicle properties provides a means to
-probe the physics of membrane adhesion.
+%In the following numerical experiments we initially place a vesicle
+%doublet with $\theta=\pi$, so that the diverging flow may be strong
+%enough to pull vesicles away from the doublet.  At low extensional
+%rates, we expect the doublet to stay bound at the fluid trap stagnation
+%point.  On the other hand, the vesicle doublet may become unstable and
+%eventually separate at higher extensional rates.  Thus we expect there
+%to exist a critical extensional rate $\chi_c$ above which the vesicle
+%doublet cannot stay bound under a given adhesion potential.  Therefore,
+%the dependence of the critical extensional rate $\chi_c$ on the adhesion
+%potential and the mechanical vesicle properties provides a means to
+%probe the physics of membrane adhesion.
 
@@
 together rather than pulling them apart.
-
-We consider vesicle doublets with reduced areas 0.70, 0.75, 0.80, 0.85,
-0.90, and 0.95, all with a length of $2\pi$, and we vary the extensional
-rate, $\chi$, between $10^{-2}$ and $10^{-1}$.  Since the stagnation
-point can be controlled in an experimental
-setting~\cite{Johnson-Chavarria2011_EMJ}, we mimic the active control of
-the microfluidic experiments by moving the center of the doublet at each
-time step so that the stagnation point occurs exactly in the middle of
-the doublet.  With this adjustment, the vesicles either remain as a
-doublet in the fluid trap centered around the stagnation point, or the
-doublet is broken and the vesicles separate from one another.  In
-Figures~\ref{fig:extensional1}, snapshots of a fluid trap containing a
-vesicle doublet of reduced area $\Delta A = 0.7$ are simulated at three
-different extensional rates.  We observe that the doublet rotates from
-$\theta=\pi$ configuration towards the more stable $\theta=\pi/2$
-configuration, as shown in Figures~\ref{fig:extensional1}.  We also
-observe that with moderate extensional rates, the doublet falls short of
-aligning their long axis with the diverging direction.  Moreover, the
-final inclination angle is closest to the stable $\theta=\pi/2$ for the
-smallest extensional rates.  While this doublet remains bound for all
-the considered extensional rates, a doublet with a reduced area of
-$\Delta A = 0.8$ is split with a critical extensional rate $\chi_c =
-0.1$ (Figure~\ref{fig:extensional3}).
 
@@
 
+In the following numerical experiments we initially place a vesicle
+doublet with $\theta=\pi$, so that the diverging flow may be strong
+enough to pull vesicles away from the doublet.  At low extensional
+rates, we expect the doublet to stay bound at the fluid trap stagnation
+point.  On the other hand, the vesicle doublet may become unstable and
+eventually separate at higher extensional rates.  Thus we expect there
+to exist a critical extensional rate $\chi_c$ above which the vesicle
+doublet cannot stay bound under a given adhesion potential.  Therefore,
+the dependence of the critical extensional rate $\chi_c$ on the adhesion
+potential and the mechanical vesicle properties provides a means to
+probe the physics of membrane adhesion.
+
+We consider vesicle doublets with reduced areas 0.70, 0.75, 0.80, 0.85,
+0.90, and 0.95, all with a length of $2\pi$, and we vary the extensional
+rate, $\chi$, between $10^{-2}$ and $10^{-1}$.  Since the stagnation
+point can be controlled in an experimental
+setting~\cite{Johnson-Chavarria2011_EMJ}, we mimic the active control of
+the microfluidic experiments by moving the center of the doublet at each
+time step so that the stagnation point occurs exactly in the middle of
+the doublet.  With this adjustment, the vesicles either remain as a
+doublet in the fluid trap centered around the stagnation point, or the
+doublet is broken and the vesicles separate from one another.  In
+Figures~\ref{fig:extensional1}, snapshots of a fluid trap containing a
+vesicle doublet of reduced area $\Delta A = 0.7$ are simulated at three
+different extensional rates.  We observe that the doublet rotates from
+$\theta=\pi$ configuration towards the more stable $\theta=\pi/2$
+configuration, as shown in Figures~\ref{fig:extensional1}.  We also
+observe that with moderate extensional rates, the doublet falls short of
+aligning their long axis with the diverging direction.  Moreover, the
+final inclination angle is closest to the stable $\theta=\pi/2$ for the
+smallest extensional rates.  While this doublet remains bound for all
+the considered extensional rates, a doublet with a reduced area of
+$\Delta A = 0.8$ is split with a critical extensional rate $\chi_c =
+0.1$ (Figure~\ref{fig:extensional3}).
+
+%\begin{figure}[htp]
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}\\
+%   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png} \\
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
+%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
+%  \caption{\label{fig:extensional1} A vesicle doublet in an extensional
+%  flow with an initial inclination angle $\theta=\pi$.  The reduced
+%  area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} = 0.7$,
+%  the separation distance is $\delta = 0.4$, and the extensional rate is
+%  $\chi = 0.02$ ({\em top}), $\chi=0.07$ ({\em middle}), and $\chi =
+%  0.1$ ({\em bottom}).  The center of the vesicle, denoted with a black
+%  square, is the stagnation point.}
+%  \end{figure}
+
  \begin{figure}
@@
 vesicles apart.  Then, as the doublet starts to rotate, each vesicle
-experiences a drag force from both the up and down diverging streaming
-flows.  For small extensional rate, the rotation will continue until
+experiences a drag force from the diverging streaming
+flows.  
+%
+For small extensional rate, the rotation continues until
 $\theta = \pi/2$ so the doublet remains perfectly symmetric with respect
-to their mid-plane and each vesicle experiences drag forces that cancel
-in both directions.  For slightly higher extensional rate, we observe
-that the two vesicles slide against each other as the doublet rotates.
+to their mid-plane, and each vesicle experiences drag forces (from the diverging flow) that cancel
+each other.  
+%
+For slightly higher extensional rate in Figure~\ref{fig:extensionalVorticity}, we observe
+that the two vesicles slide against each other (around $t=280$) as the doublet rotates.
 The slight sliding motion leads to a transition in the contact region
@@
 $\delta$, Hamaker constant $\mathcal{H}$, shear rate $\chi$, and reduced
-area $\Delta A$.  At all reduced areas, the vesicles have a length of
-$2\pi$.  Figure~\ref{fig:doublet090} shows snapshots of two vesicles
+area $\Delta A$.  
+At all reduced areas, the vesicles have a length of
+$2\pi$ to be consistent with simulations in previous sections.
+
+Figure~\ref{fig:doublet090} shows snapshots of two vesicles
 that have formed a doublet and the color coding is the tension along the
@@
 [0,1]$.  Here $s$ is the arclength, and we have assumed, without loss of
-generality, that both vesicles have length one.  We use the van der
-Waals potential
+generality, that both vesicles have length one.  We use the  L.-J. type potential
 \begin{align*}
@@
 \end{align*}
-where $z$ is the distance between two points.  Then, we define the total
+where $z$ is the distance between two points on a pair of vesicles.  Then, we define the total
 adhesive energy on $\gamma_1$ to be

### 2019-02-14 vesicle_code/docs/adhesion/adhesion.tex
small changes

@@
 ShiFengGao2006_ActaMechSin, LinFreund2007_IntJSolidsStructures,
-GruhnFrankeDimova2007_Langmuir,das2008adhesion, zhang2009phase,Agudo-Canalejo2015_ACSNano,Agudo-CanalejoLipowsky2015_NanoLett,
-SteinkuhlerAgudo-Canalejo2016_BJ,Agudo-CanalejoLipowsky2017_SoftMatt} than the transient adhesion
-process~\cite{cantat1999lift, suk-sei2001, BlountMiksisDavis2013_PRSa}.
-Adhesive interactions between lipid membranes are essential in many
-biomedical, biological, and biophysical processes.  For example, vesicle
-adhesion is crucial to initiate membrane fusion and fission in
-endocytosis, exocytosis and the transport of small vesicles through
-membrane surfaces.  In the absence of an external electric field and
-ions in the solvents, it is reported that the adhesive interactions
-between two membranes can be well approximated by the L.-J.-type
+GruhnFrankeDimova2007_Langmuir,das2008adhesion,
+zhang2009phase,Agudo-Canalejo2015_ACSNano,Agudo-CanalejoLipowsky2015_NanoLett,
+SteinkuhlerAgudo-Canalejo2016_BJ,Agudo-CanalejoLipowsky2017_SoftMatt}
+than the transient adhesion process~\cite{cantat1999lift, suk-sei2001,
+BlountMiksisDavis2013_PRSa}.  Adhesive interactions between lipid
+membranes are essential in many biomedical, biological, and biophysical
+processes.  For example, vesicle adhesion is crucial to initiate
+membrane fusion and fission in endocytosis, exocytosis, and the
+transport of small vesicles through membrane surfaces.  In the absence
+of an external electric field and ions in the solvents, it is reported
+that the adhesive interactions between two membranes can be well
+approximated by the L.-J.-type
 potential~\cite{FlormannAouane2017_SciReports}, that consists of a
@@
 component~\cite{Book_IntermolecularSurfaceForces}, and the combination
-of the two gives rise to an equilibrium distance
-where the interaction potential is at minimum~\cite{Book_IntermolecularSurfaceForces}.
-
-The strength of membrane-membrane adhesion can be estimated through the membrane contact angle at the edge of contact zone \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir,MaresDanielIglic2012_SciWorldJ}.
-Alternatively,
-Evans and Metcalfe~\cite{EvansMetcalfe1984_BJ} used the micropipette to
-measure the adhesive force between two vesicles bound by strong
-adhesion.  They were able to measure the reduction in the free energy
-per unit area of membrane-membrane contact formation due to the van der
-Waals' attraction. For the adhesive interaction between two lipid
-bilayer membranes in buffer solutions, a typical range for the energy
-density is between $1$ to $10$ $\mu J/m^2$, similar to the adhesion
-energy density of $3$ $\mu J/m^2$ between two
+of the two gives rise to an equilibrium distance where the interaction
+potential is at its minimum~\cite{Book_IntermolecularSurfaceForces}.
+
+The strength of membrane-membrane adhesion can be estimated through the
+membrane contact angle at the edge of contact
+zone~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir,
+MaresDanielIglic2012_SciWorldJ}.  Alternatively, Evans and
+Metcalfe~\cite{EvansMetcalfe1984_BJ} used the micropipette to measure
+the adhesive force between two vesicles bound by strong adhesion.  They
+were able to measure the reduction in the free energy per unit area of
+membrane-membrane contact formation due to the van der Waals'
+attraction. For the adhesive interaction between two lipid bilayer
+membranes in buffer solutions, a typical range for the energy density is
+between $1$ to $10$ $\mu J/m^2$, similar to the adhesion energy density
+of $3$ $\mu J/m^2$ between two
 RBCs~\cite{FlormannAouane2017_SciReports}.  For adhesion interaction
@@
 the viscosity ratio $\mu_e/\mu_i=1$ for the rest of the paper.
-$T = - p I + \mu\left(\nabla \uu + \nabla \uu^T\right)$ is the stress tensor, $\llbracket T \rrbracket$ is the jump across membrane, and
+$T = - p I + \mu\left(\nabla \uu + \nabla \uu^T\right)$ is the stress
+tensor, $\llbracket T \rrbracket$ is the jump across the membrane, and
 $\xxi$ is the traction that is the sum of the bending, stretching,
@@
 
-The exponents $(m,n)$ in equation~(\ref{eq:adhesion_potential}) depend on the geometry and the molecular details
-of the two objects under
+The exponents $(m,n)$ in equation~(\ref{eq:adhesion_potential}) depend
+on the geometry and the molecular details of the two objects under
 adhesion~\cite{Book_IntermolecularSurfaceForces}: $(m,n)=(4,2)$
@@
 membrane-membrane adhesion  \cite{FlormannAouane2017_SciReports}.  In
-our case, the adhesion potential 
-%in the integral of equation~\eqref{eqn:adhesionForce} 
-is between two small patches of lipid
+our case, the adhesion potential is between two small patches of lipid
 bilayer membrane (because the lipid molecules are coarse-grained in the
@@
 
-The right plot of Figure~\ref{fig:Dec18_vesicle_shape} is a zoom (not to-scale) on the
-membranes in the contact region, where the membranes are not perfectly
-flat at all three values of reduced area: We observe that the membranes are slightly
-curved with a dip at the edge.  Such membrane undulation in the contact
-region is predicted by lubrication analyses on an elastic membrane under adhesion
-with a solid substrate~\cite{BlountMiksisDavis2013_PRSa,
-YoungStone2017_PRF}.  
+The right plot of Figure~\ref{fig:Dec18_vesicle_shape} is a zoom (not
+to-scale) on the membranes in the contact region, where the membranes
+are not perfectly flat at all three values of reduced area: We observe
+that the membranes are slightly curved with a dip at the edge.  Such
+membrane undulation in the contact region is predicted by lubrication
+analyses on an elastic membrane under adhesion with a solid
+substrate~\cite{BlountMiksisDavis2013_PRSa, YoungStone2017_PRF}.  
 %
@@
 [0,1]$.  Here $s$ is the arclength, and we have assumed, without loss of
-generality, that both vesicles have length one.  We use the  L.-J. type potential
+generality, that both vesicles have length one.  We use the  L.-J.~type
+potential
 \begin{align*}

### 2019-02-14 vesicle_code/docs/adhesion/adhesion.tex
more changes from yny

@@
 \end{equation}
-where $\uu$ is the fluid velocity field, $p$ is the pressure, and the scaled viscosity $\mu=1$ inside the vesicles.
-$\mu=\mu_e/\mu_i$ outside the vesicle, with $\mu_i$ ($\mu_e$)  the viscosity of interior  (exterior) fluid.  We set
+where $\uu$ is the fluid velocity field, $p$ is the pressure, and the scaled viscosity $\mu=1$ inside the vesicles. Outside the vesicle
+$\mu=\mu_e/\mu_i$ with $\mu_i$ ($\mu_e$)  the viscosity of the interior  (exterior) fluid.  We set
 the viscosity ratio $\mu_e/\mu_i=1$ for the rest of the paper.
@@
 $\xxi$ is the traction that is the sum of the bending, stretching,
-and adhesion forces defined in equation~(\ref{eqn:traction}).  The bending force, arising from the Helfrich
+and adhesion forces defined in equation~(\ref{eqn:traction}) of Appendix \ref{sec:AppendixB}.  The bending force, arising from the Helfrich
 energy model, is $\BB \xx = -\kappa_b \xx_{ssss}$, where the subscript $s$ denotes derivative with respect to arclength $s$. $\kappa_b$ is
@@
 \begin{appendices}
+\section{Integral Equation Formulation}
+\label{sec:AppendixB}
+Using potential theory and following~\cite{Veerapaneni2009_JCP}, we recast the governing equations~\eqref{eq:gov} as integro-differential equations for the evolution of membrane positions: 
+%
+\begin{align*}
+  &\dot{\xx} = \uu_{\infty}(\xx) + \SS[\xxi](\xx), \\
+  &\xx_s \cdot \dot{\xx}_s = 0,
+ \end{align*}
+%
+where the single-layer potential $\SS[\cdot]$ is defined by
+\begin{align}
+  \SS[\xxi](\xx) &= \frac{1}{4\pi\mu} \int_\gamma \left(
+    -\log \|\xx - \yy\| + \frac{(\xx - \yy) \otimes (\xx - \yy)}{\|\xx - \yy\|^2} \right) 
+    \xxi(\yy) ds_\yy, 
+  \label{eqn:SLP}
+\end{align}
+%
+and the membrane force $\xxi$ is a sum of the bending, tension and adhesion forces: 
+\begin{align}
+\xxi = -\kappa_b \xx_{ssss} + (\sigma \xx_s)_s + \AA\xx.
+\label{eqn:traction}
+\end{align}
+Defining the bending operator as $\BB[\ff](\xx) = -\kappa_b \ff_{ssss}$,
+the tension operator $\TT[\sigma](\xx) = (\sigma \xx_s)_s$, and using
+IMEX-Euler, the no-slip boundary results in the time stepping method
+\begin{align*}
+  \xx^{N+1} - \Delta t \SS^N \BB^N \xx^{N+1} - 
+    \Delta t \SS^N \TT^N \sigma^{N+1} = \xx^N + 
+    \Delta t \SS^N \AA^N \xx^N,
+\end{align*}
+and the inextensibility constraint that is discretized as
+\begin{align*}
+  \xx_s^{N} \cdot \xx_{s}^{N+1} = 1.
+\end{align*}
+We discretize the vesicles at a set of collocation points, compute the
+bending and tension terms with Fourier differentiation, and apply Alpert
+quadrature~\cite{alp1999} to the weakly-singular single-layer potential
+$\SS$.  The source and target points of the adhesion force never
+coincide since they are always on different vesicles, so the adhesion
+force~\eqref{eqn:adhesionForce} is computed with the spectrally accurate
+trapezoid rule~\cite{tre-wei2014}.
+
+The dynamics of a doublet undergoes many different time scales over time
+horizons that are sufficiently large to characterize the formation of a
+doublet and its rheological properties.  Therefore, time adaptivity is
+crucial so that a user-specified tolerance is achieved without using a
+guess-and-check procedure to find an appropriately small fixed time step
+size.  To control the error and achieve second-order accuracy in time,
+we use a time adaptive spectral deferred correction method that
+applies IMEX-Euler twice per time step~\cite{quaife2016adaptive}.
+
 \section{Adhesion Force}
@@
 
-\section{Integral Equation Formulation}
-\label{sec:AppendixB}
-Using potential theory and following~\cite{Veerapaneni2009_JCP}, we recast the governing equations~\eqref{eq:gov} as integro-differential equations for the evolution of membrane positions: 
-%
-\begin{align*}
-  &\dot{\xx} = \uu_{\infty}(\xx) + \SS[\xxi](\xx), \\
-  &\xx_s \cdot \dot{\xx}_s = 0,
- \end{align*}
-%
-where the single-layer potential $\SS[\cdot]$ is defined by
-\begin{align}
-  \SS[\xxi](\xx) &= \frac{1}{4\pi\mu} \int_\gamma \left(
-    -\log \|\xx - \yy\| + \frac{(\xx - \yy) \otimes (\xx - \yy)}{\|\xx - \yy\|^2} \right) 
-    \xxi(\yy) ds_\yy, 
-  \label{eqn:SLP}
-\end{align}
-%
-and the membrane force $\xxi$ is a sum of the bending, tension and adhesion forces: 
-\begin{align}
-\xxi = -\kappa_b \xx_{ssss} + (\sigma \xx_s)_s + \AA\xx.
-\label{eqn:traction}
-\end{align}
-Defining the bending operator as $\BB[\ff](\xx) = -\kappa_b \ff_{ssss}$,
-the tension operator $\TT[\sigma](\xx) = (\sigma \xx_s)_s$, and using
-IMEX-Euler, the no-slip boundary results in the time stepping method
-\begin{align*}
-  \xx^{N+1} - \Delta t \SS^N \BB^N \xx^{N+1} - 
-    \Delta t \SS^N \TT^N \sigma^{N+1} = \xx^N + 
-    \Delta t \SS^N \AA^N \xx^N,
-\end{align*}
-and the inextensibility constraint that is discretized as
-\begin{align*}
-  \xx_s^{N} \cdot \xx_{s}^{N+1} = 1.
-\end{align*}
-We discretize the vesicles at a set of collocation points, compute the
-bending and tension terms with Fourier differentiation, and apply Alpert
-quadrature~\cite{alp1999} to the weakly-singular single-layer potential
-$\SS$.  The source and target points of the adhesion force never
-coincide since they are always on different vesicles, so the adhesion
-force~\eqref{eqn:adhesionForce} is computed with the spectrally accurate
-trapezoid rule~\cite{tre-wei2014}.
-
-The dynamics of a doublet undergoes many different time scales over time
-horizons that are sufficiently large to characterize the formation of a
-doublet and its rheological properties.  Therefore, time adaptivity is
-crucial so that a user-specified tolerance is achieved without using a
-guess-and-check procedure to find an appropriately small fixed time step
-size.  To control the error and achieve second-order accuracy in time,
-we use a time adaptive spectral deferred correction method that
-applies IMEX-Euler twice per time step~\cite{quaife2016adaptive}.
-
 %To characterize the rheological properties of the suspension of a

### 2019-03-12 vesicle_code/docs/permeableVes/main.tex
write-up on porous vesicle

\documentclass[aps,prl,twocolumn,showpacs]{revtex4}
\usepackage{amsmath,amsfonts,bm, color}
\usepackage{graphicx,epsfig}
%\input vs_macros.tex
%Dfig puts a figure of specified size at the place indicated.
\newcommand{\Dfig}[2]{\epsfig{figure=#1,width=#2cm}}

%\Eonefigs puts one figure at the top of a page. 3 arguments.
%Usage:
%\Eonefigs{file fig}{caption}{size in inches}
%the file must be eps, but names must be given 
%WITHOUT .eps extension

\newenvironment{Eonefigs}[3]
{        \begin{figure} [t]
          \begin{center}
              \includegraphics[width=0.5\textwidth]{#3} \\
          \vspace{-0.21in}
          \caption{{\footnotesize #2}}
          \label{#1}
          \end{center}
        \vspace{-.3in}
        \end{figure}
}{}

\newcommand{\co}[1]{\marginpar{\scriptsize \textcolor{red}{#1}}} % red comment

\input my_macros2.tex

\begin{document}

\title{Semi-permeable vesicles: mathematical formulation, numerics and physics}
\author{}

\date{\today}

\begin{abstract}
We describe a mathematical model for a semi-permeable vesicle and derive a boundary integral equation formulation for simulating its hydrodynamics.  
\end{abstract}
\maketitle

\section{Problem formulation} \label{sc:formulate}
Consider a semi-permeable vesicle suspended in an unbounded viscous fluid domain, subjected to an imposed flow $\mbu_\infty(\mbx)$, for any $\mbx \in \mathbb{R}^2$.  Assume that the interior and exterior fluids have the same viscosity $\mu$. Let $\mbx$ be the position of the interface $\gamma$, $\mbu$ the fluid velocity and $p$ the pressure. In the vanishing Reynolds number limit, the governing equations for the ambient fluid can be written as: 
%
\begin{subequations}
\begin{align}
-\nabla p + \mu \triangle \mbu = 0 \quad\text{in}\quad \mathbb{R}^2\setminus\gamma  &  \\
% 
\nabla \cdot \mbu = 0  \quad\text{in}\quad \mathbb{R}^2\setminus\gamma &\\
%
\mbu(\mbx) \rightarrow \mbu_\infty(\mbx) \quad \text{as} \quad  \norm{\mbx} \rightarrow \infty & 
 \end{align} \label{eqn:governing}
\end{subequations}%
%
The modified jump conditions in the case of a semi-permeable vesicle can be summarized as follows.  Let $\mbn$ the outward normal to $\gamma$ and $\jump{\cdot}$ denote the jump across the interface. The jump condition for the hydrodynamic stress remains the same:
%
%Then, define
%\beq \mbf_i = \lim_{\mbx \rightarrow \gamma^-} \sigma (\mbx)\cdot\mbn,  \eeq
%\beq \mbf_e =  \lim_{\mbx \rightarrow \gamma^+} \sigma (\mbx)\cdot\mbn, \eeq
%\beq \jump{\mbv\cdot \mbt} = 0 \eeq
%\beq \jump{\mbv\cdot\mbn} = \beta (\mbf_i + \mbf_e)\cdot\mbn \eeq
\beq \jump{\Sigma\cdot\mbn} = \mbf_\text{mem}, \eeq
where $\Sigma$ is the hydrodynamic stress tensor. The fluid velocity is continuous across the membrane i.e.,
\beq \jump{\mbu} = 0. \eeq
However, the kinematic condition is modified to account for the fact that the fluid can move through the membrane. A standard choice appears to be
%
\beq \mbu - \dot{\mbx} = - \beta (\mbf_\text{mem} \cdot \mbn) \mbn \quad\text{on}\quad\gamma. \eeq
%
Here, $\beta$ is a constant and the membrane force is the usual tension + bending.

\section{Integral equation formulation}
There are multiple ways to convert the PDE problem into integral equations. Based on my derivation, the coupled set of integro-differential equations satisfy the given interfacial conditions:
\beq \dot{\mbx} = \mbu_\infty(\mbx) + \beta (\mbf_\text{mem}\cdot\mbn)\mbn + \sgl [\mbf_\text{mem}], \eeq
\beq \mbx_s\cdot\dot{\mbx}_s = 0 \eeq
This satisfies all the jump conditions. As usual, $\sgl$ is the single layer potential. 
\end{document}

### 2019-03-19 vesicle_code/docs/permeableVes/main.tex
making changes to semi-permeable writeup
updated semipermeable writeup

@@
 \section{Integral equation formulation}
-There are multiple ways to convert the PDE problem into integral equations. Based on my derivation, the coupled set of integro-differential equations satisfy the given interfacial conditions:
-\beq \dot{\mbx} = \mbu_\infty(\mbx) + \beta (\mbf_\text{mem}\cdot\mbn)\mbn + \sgl [\mbf_\text{mem}], \eeq
-\beq \mbx_s\cdot\dot{\mbx}_s = 0 \eeq
+There are multiple ways to convert the PDE problem into integral
+equations. Based on my derivation, the coupled set of
+integro-differential equations satisfy the given interfacial conditions:
+\beq 
+  \dot{\mbx} = \mbu_\infty(\mbx) + \beta (\mbf_\text{mem}\cdot\mbn)\mbn + \sgl [\mbf_\text{mem}], 
+  \label{eqn:vesVelocity}
+\eeq
+\beq 
+  \mbx_s\cdot\dot{\mbx}_s = 0 
+\eeq
 This satisfies all the jump conditions. As usual, $\sgl$ is the single layer potential.
+
+\section{Numerics}
+To address stiffness associated with high-order derivatives,
+equation~\eqref{eqn:vesVelocity} is discretized with a semi-implicit
+time stepping method similar to our previous works.  First, we introduce
+the notation
+\begin{align}
+  \BB[\mbx]\mbf &= \frac{d^4}{ds^4} \mbf, \\
+  \TT[\mbx]\sigma &= (\sigma \mbx_s)_s, \\
+  \PP[\mbx]\mbf &= (\mbf \cdot \mbn) \mbn, \\
+  \dbl[\mbx]\mbf &= \mbx_s \cdot \mbf_s
+\end{align}
+where $\mbn$ is the is the outward unit normal of the vesicle
+parameterized by $\mbx$, and $d/ds$ is its arclength derivative.
+Dropping the dependence of the operators on $\mbx$, the dynamics of the
+vesicle are governed by
+\begin{align}
+  \dot{\mbx} &= \mbu_{\infty}(\mbx) + 
+  \beta \PP(\BB\mbx + \TT\sigma) + \sgl(\BB\mbx + \TT\sigma), \\
+  \dbl \dot{\mbx} &= 0.
+\end{align}
+Using the notation $\BB^N$ to denote the bending operator due to the
+vesicle configuration at time $t_N$, and similar notation for the other
+operators, we apply the semi-implicit time
+\begin{multline}  
+  \frac{\mbx^{N+1} - \mbx^N}{\Delta t} = \mbu_\infty(\mbx^N) 
+  + \beta \PP^N(\BB^N\mbx^{N+1} + \TT^N\sigma^{N+1})  \\
+  + \sgl^N(\BB^N\mbx^{N+1} + \TT^N\sigma^{N+1}).
+\end{multline}
+Applying $\dbl$ to the first-order time discretization of
+equation~\eqref{eqn:vesVelocity}, the inextensibility condition is
+\begin{align*}
+  &\dbl^N(\mbx^{N+1} - \mbx^N) = 0 \\ 
+  \Rightarrow &\dbl^N\mbx^{N+1} = \dbl^N \mbx^N \\ 
+  \Rightarrow &\dbl^N\mbx^{N+1} = 1.
+\end{align*}
+Finally, we write the time stepping method in matrix form as
+\begin{align}
+  A \left(
+    \begin{array}{c}
+      \mbx^{N+1} \\ \sigma^{N+1}
+    \end{array}
+  \right) = 
+  \left(
+    \begin{array}{c}
+      \mbx^{N} + \Delta t \mbu_\infty(\mbx^N) \\ \mathbf{1}
+    \end{array}
+  \right),
+\end{align}
+where
+\beq
+ A = \left(
+  \begin{array}{cc}
+    I - \Delta t \beta \PP^N - \Delta t \sgl^N \BB^N & 
+    -\Delta t \PP^N \TT^N - \Delta t \sgl^N \TT^N \\
+    \dbl^N & 0
+  \end{array}
+  \right)
+\eeq
+
+%We obtain the matrix
+%\begin{multline}
+% \begin{pmatrix}
+% 	\mbx^N \\ \textbf{1} 
+% \end{pmatrix} = \\
+%\begin{pmatrix}
+%	I - \Delta t \sgl^N\mathcal{B}^N - \Delta t \beta \mathcal{P}^N\mathcal{B}^N & -\Delta t \sgl^N \mathcal{T}^N-\Delta t\beta \mathcal{P}^N\mathcal{T}^N \\ & \textbf{0}
+%\end{pmatrix}
+%\begin{pmatrix}
+%	\mbx^{N+1} \\ \sigma^{N+1}
+%\end{pmatrix} 
+%\end{multline}
+
 \end{document}

### 2019-03-19 vesicle_code/examples/initVes2D.m

@@ -41,7 +41,7 @@ OptList = {'order','expectedOrder','inextens','farField',...
     'fmm','fmmDLP','confined','usePlot','track',...
     'quiver','axis','saveData','logFile','dataFile','verbose',...
     'profile','collision','timeAdap',...
-    'pressure','SDCcorrect','orderGL','nsdc','adhesion',...
+    'pressure','SDCcorrect','orderGL','nsdc','adhesion','expForce',...
     'correctShape','fmmPrecision','errorFile','saveError'};
 
 defaultOpt.order = 1;
@@ -70,6 +70,7 @@ defaultOpt.SDCcorrect = false;
 defaultOpt.orderGL = 2;
 defaultOpt.nsdc = 0;
 defaultOpt.adhesion = false;
+defaultOpt.expForce = false;
 defaultOpt.correctShape = false;
 defaultOpt.fmmPrecision = 4;
 defaultOpt.errorFile = 'output/exampleError.bin';

### 2019-03-19 vesicle_code/docs/permeableVes/main.tex
Updated semipermeable writeup

@@
 vesicle configuration at time $t_N$, and similar notation for the other
-operators, we apply the semi-implicit time
+operators, we apply the semi-implicit time stepping method
 \begin{multline}  
@@
   \end{array}
-  \right)
+  \right).
 \eeq

### 2019-03-20 vesicle_code/docs/permeableVes/main.tex
Updated semipermeable writeup - notation changes

--- 2019-03-19 vesicle_code/docs/permeableVes/main.tex
@@
 \begin{align}
-  \BB[\mbx]\mbf &= \frac{d^4}{ds^4} \mbf, \\
-  \TT[\mbx]\sigma &= (\sigma \mbx_s)_s, \\
-  \PP[\mbx]\mbf &= (\mbf \cdot \mbn) \mbn, \\
-  \dbl[\mbx]\mbf &= \mbx_s \cdot \mbf_s
+  B[\mbx]\mbf &= -\kappa_b\frac{d^4}{ds^4} \mbf, \\
+  T[\mbx]\sigma &= (\sigma \mbx_s)_s, \\
+  P[\mbx]\mbf &= (\mbf \cdot \mbn) \mbn, \\
+  D[\mbx]\mbf &= \mbx_s \cdot \mbf_s
 \end{align}
@@
   \dot{\mbx} &= \mbu_{\infty}(\mbx) + 
-  \beta \PP(\BB\mbx + \TT\sigma) + \sgl(\BB\mbx + \TT\sigma), \\
-  \dbl \dot{\mbx} &= 0.
+  \beta P(B\mbx + T\sigma) + \sgl(B\mbx + T\sigma), \\
+  D \dot{\mbx} &= 0.
 \end{align}
-Using the notation $\BB^N$ to denote the bending operator due to the
+Using the notation $B^N$ to denote the bending operator due to the
 vesicle configuration at time $t_N$, and similar notation for the other
-operators, we apply the semi-implicit time
+operators, we apply the semi-implicit time stepping method
 \begin{multline}  
   \frac{\mbx^{N+1} - \mbx^N}{\Delta t} = \mbu_\infty(\mbx^N) 
-  + \beta \PP^N(\BB^N\mbx^{N+1} + \TT^N\sigma^{N+1})  \\
-  + \sgl^N(\BB^N\mbx^{N+1} + \TT^N\sigma^{N+1}).
+  + \beta P^N(B^N\mbx^{N+1} + T^N\sigma^{N+1})  \\
+  + \sgl^N(B^N\mbx^{N+1} + T^N\sigma^{N+1}).
 \end{multline}
-Applying $\dbl$ to the first-order time discretization of
+Applying $D$ to the first-order time discretization of
 equation~\eqref{eqn:vesVelocity}, the inextensibility condition is
 \begin{align*}
-  &\dbl^N(\mbx^{N+1} - \mbx^N) = 0 \\ 
-  \Rightarrow &\dbl^N\mbx^{N+1} = \dbl^N \mbx^N \\ 
-  \Rightarrow &\dbl^N\mbx^{N+1} = 1.
+  &D^N(\mbx^{N+1} - \mbx^N) = 0 \\ 
+  \Rightarrow &D^N\mbx^{N+1} = D^N \mbx^N \\ 
+  \Rightarrow &D^N\mbx^{N+1} = 1.
 \end{align*}
@@
   \begin{array}{cc}
-    I - \Delta t \beta \PP^N - \Delta t \sgl^N \BB^N & 
-    -\Delta t \PP^N \TT^N - \Delta t \sgl^N \TT^N \\
-    \dbl^N & 0
+    I - \Delta t \beta P^N - \Delta t \sgl^N B^N & 
+    -\Delta t P^N T^N - \Delta t \sgl^N T^N \\
+    D^N & 0
   \end{array}
-  \right)
+  \right).
 \eeq

### 2019-04-12 vesicle_code/docs/permeableVes/main.tex
Updated the A matrix
Figures for parameter sweeps (Chi, beta, and RA) added to main TeX.

@@
-\documentclass[aps,prl,twocolumn,showpacs]{revtex4}
+\documentclass[aps,prl,showpacs]{revtex4}
 \usepackage{amsmath,amsfonts,bm, color}
@@
   \begin{array}{cc}
-    I - \Delta t \beta P^N - \Delta t \sgl^N B^N & 
+    I + \Delta t \beta P^N B^N + \Delta t \sgl^N B^N & 
     -\Delta t P^N T^N - \Delta t \sgl^N T^N \\
@@
 
-%We obtain the matrix
-%\begin{multline}
-% \begin{pmatrix}
-% 	\mbx^N \\ \textbf{1} 
-% \end{pmatrix} = \\
-%\begin{pmatrix}
-%	I - \Delta t \sgl^N\mathcal{B}^N - \Delta t \beta \mathcal{P}^N\mathcal{B}^N & -\Delta t \sgl^N \mathcal{T}^N-\Delta t\beta \mathcal{P}^N\mathcal{T}^N \\ & \textbf{0}
-%\end{pmatrix}
-%\begin{pmatrix}
-%	\mbx^{N+1} \\ \sigma^{N+1}
-%\end{pmatrix} 
-%\end{multline}
+\begin{figure}
+	\centering
+	\includegraphics[width=.9\textwidth]{figures/1.jpg}
+	\includegraphics[width=.9\textwidth]{figures/2.jpg}
+	\includegraphics[width=.9\textwidth]{figures/3.jpg}
+	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0$.}
+	\label{Shear0}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=.9\textwidth]{figures/4.jpg}
+	\includegraphics[width=.9\textwidth]{figures/5.jpg}
+	\includegraphics[width=.9\textwidth]{figures/6.jpg}
+	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0.5$.}
+	\label{Shear0}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=.9\textwidth]{figures/7.jpg}
+	\includegraphics[width=.9\textwidth]{figures/8.jpg}
+	\includegraphics[width=.9\textwidth]{figures/9.jpg}
+	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 1$.}
+	\label{Shear0}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=.9\textwidth]{figures/10.jpg}
+	\includegraphics[width=.9\textwidth]{figures/11.jpg}
+	\includegraphics[width=.9\textwidth]{figures/12.jpg}
+	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 2$.}
+	\label{Shear0}
+\end{figure}
+
+ \begin{figure}
+ 	\centering
+ 	\includegraphics[width=.9\textwidth]{figures/BE1.jpg}
+ 	\includegraphics[width=.9\textwidth]{figures/BE2.jpg}
+ 	\includegraphics[width=.9\textwidth]{figures/BE3.jpg}
+ 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0$.}
+ 	\label{Shear0}
+ \end{figure}
+
+ \begin{figure}
+ 	\centering
+ 	\includegraphics[width=.9\textwidth]{figures/BE4.jpg}
+ 	\includegraphics[width=.9\textwidth]{figures/BE5.jpg}
+ 	\includegraphics[width=.9\textwidth]{figures/BE6.jpg}
+ 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0.5$.}
+ 	\label{Shear0}
+ \end{figure}
+
+ \begin{figure}
+ 	\centering
+ 	\includegraphics[width=.9\textwidth]{figures/BE7.jpg}
+ 	\includegraphics[width=.9\textwidth]{figures/BE8.jpg}
+ 	\includegraphics[width=.9\textwidth]{figures/BE9.jpg}
+ 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 1$.}
+ 	\label{Shear0}
+ \end{figure}
+
+ \begin{figure}
+ 	\centering
+ 	\includegraphics[width=.9\textwidth]{figures/BE10.jpg}
+ 	\includegraphics[width=.9\textwidth]{figures/BE11.jpg}
+ 	\includegraphics[width=.9\textwidth]{figures/BE12.jpg}
+ 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 2$.}
+ 	\label{Shear0}
+ \end{figure}
 

### 2019-04-12 vesicle_code/examples/relaxation1Ves_AshleyCopy.m

@@ -1,16 +1,17 @@
-%clear all; clc
+clear all; clc
 
 fprintf('Simple elliptical vesicle in a relaxation flow.\n');
 fprintf('First-order semi-implicit time stepping.\n');
 
 % Physics parameters
-prams.N = 32;               % points per vesicle
+prams.N = 128;               % points per vesicle
 prams.nv = 1;               % number of vesicles
 prams.T = 2;               % time horizon (two tumbling)
-prams.m = 200;              % number of time steps
+prams.m = 800;              % number of time steps
 prams.kappa = 1e-2;         % bending coefficient
 prams.viscCont = 1;         % viscosity contrast
-options.farField = 'relaxation'; % background velocity
+options.farField = 'shear'; % background velocity
+options.farFieldSpeed = 2;
 options.order = 1;          % time stepping order
 options.vesves = 'implicit';
 % Discretization of vesicle-vesicle interactions.
@@ -23,7 +24,7 @@ options.semipermeable = true;
 prams.gmresMaxIter = 3*prams.N;
 prams.gmresTol = 1e-10;
 prams.errorTol = 1000;
-prams.PhysBeta = 1e0;
+prams.PhysBeta = 1;
 
 % ADD-ONS
 options.alignCenterAngle = false;
@@ -56,9 +57,9 @@ options.usePlot = true;
 options.axis = [-5 5 -5 5];
 options.track = false;
 % Save vesicle information and create a log file
-options.logFile = 'output/relaxation1Ves.log';
+options.logFile = 'output/1Vesicle_Shear2_beta1_RApt65.log';
 % Name of log file for saving messages
-options.dataFile = 'output/relaxation1VesData.bin';
+options.dataFile = 'output/1Vesicle_Shear2_beta1_RApt65.bin';
 % Name of binary data file for storing vesicle information
 
 options.saveError = true;

### 2019-05-01 vesicle_code/docs/permeableVes/main.tex
added a few notes on adding a concentration field

@@
 \section{Problem formulation} \label{sc:formulate}
-Consider a semi-permeable vesicle suspended in an unbounded viscous fluid domain, subjected to an imposed flow $\mbu_\infty(\mbx)$, for any $\mbx \in \mathbb{R}^2$.
+Consider a semi-permeable vesicle suspended in an unbounded viscous
+fluid domain, subjected to an imposed flow $\mbu_\infty(\mbx)$, for any
+$\mbx \in \RR^2$.
 Assume that the interior and exterior fluids have the same viscosity $\mu$.
@@
 \begin{align}
--\nabla p + \mu \triangle \mbu = 0 \quad\text{in}\quad \mathbb{R}^2\setminus\gamma  &  \\
+-\nabla p + \mu \triangle \mbu = 0 \quad\text{in}\quad
+  \RR^2\setminus\gamma  &  \\
 % 
-\nabla \cdot \mbu = 0  \quad\text{in}\quad \mathbb{R}^2\setminus\gamma &\\
+\nabla \cdot \mbu = 0  \quad\text{in}\quad \RR^2\setminus\gamma &\\
 %
@@
 operators, we apply the semi-implicit time stepping method
-\begin{multline}  
+\begin{align}  
   \frac{\mbx^{N+1} - \mbx^N}{\Delta t} = \mbu_\infty(\mbx^N) 
-  + \beta P^N(B^N\mbx^{N+1} + T^N\sigma^{N+1})  \\
+  + \beta P^N(B^N\mbx^{N+1} + T^N\sigma^{N+1}) 
   + \sgl^N(B^N\mbx^{N+1} + T^N\sigma^{N+1}).
-\end{multline}
+\end{align}
 Applying $D$ to the first-order time discretization of
@@
 where
-\beq
+\begin{align}
  A = \left(
@@
   \right).
-\eeq
+\end{align}
+
+\section{Including a concentration field}
+Based on the work of Yao and Mori~\cite{yao-mor2017}, we introduce a
+chemical concentration field $c$.  The concentration field is governed
+by the advection-diffusion equation
+\begin{align}
+  \pderiv{c}{t} + \nabla \cdot (\mbu c) = D\Delta c.
+\end{align}
+If the concentration is diffusion dominated (zero Peclet number), then
+the concentration satisfies
+\begin{align}
+  \Delta c = 0, \quad \mbx \in \RR^2.
+\end{align}
+The boundary conditions of the concentration field on the vesicle
+$\gamma$ are
+\begin{align}
+  (\mbu c - D\nabla c) \cdot \mbn = c \pderiv{\mbx}{t} \cdot \mbn + 
+    j_c + j_p,
+\end{align}
+where $j_c$ and $j_p$ are the transmembrane chemical flux due to passive
+transport and active transport (pumps), respectively.  In the zero
+Peclet number limit, the absence of an active transport mechanism, and
+the choice for the passive flux, the boundary condition of the
+concentration field is
+\begin{align}
+  -D\pderiv{c}{\mbn} = c \pderiv{\mbx}{t} + 
+    k_c \jump{c}, \quad \mbx \in \gamma.
+\end{align}
+To couple the vesicle dynamics to the concentration, the vesicle
+velocity satisfies the slip condition
+\begin{align}
+  \mbu - \pderiv{\mbx}{t} = j_w \mbn,
+\end{align}
+where $j_w$ is the water flux through the vesicle.
+In~\cite{yao-mor2017}, this flux is
+\begin{align}
+  j_w = -k_w(RT\jump{c} + \mbf_\text{mem} \cdot \mbn).
+\end{align}
+In our current implementation, we drop the $RT\jump{c}$ term, and
+let $\beta = k_w$.
+
+\section{Preliminary results}
 
@@
 
+ \bibliographystyle{plain}
+ \bibliography{refs}
+
 \end{document}

### 2019-05-01 vesicle_code/examples/output/makeImages.m

@@ -2,7 +2,7 @@ addpath ../../src
 set(0,'DefaultAxesFontSize',22)
 options.savefig = false;
 
-irate = 10; % controls the speed of the visualization
+irate = 1; % controls the speed of the visualization
 
 if 0
 %  file = 'extensional2VesData.bin';
@@ -15,15 +15,15 @@ if 0
   ax = [-12 12 -2 2];
   options.confined = false;
 end
-if 1
-  file = '1Vesicle_Shear1_beta0_RApt99.bin';
-  ax = ([-3 3 -3 3]);
+if 0
+  file = '1Vesicle_Shear2_beta1_RApt65.bin';
+  ax = (2*[-3 3 -3 3]);
   options.confined = false;
 end
-if 0
-  file = '~/projects/brinkman/vesicle_code/results/relaxationManyVes/Segment2/relaxationManyVesData.bin';
+if 1
+  file ='~/projects/microtubule/runs/relaxation1Ves_RA095_kappa1em2_expD1ep0/relaxation1VesData.bin';
 %  file = 'relaxationManyVesData.bin';
-  ax = [-5 5 -6 6];
+  ax = [-3 3 -3.5 3.5];
   options.confined = false;
   options.savefig = false;
   count = 1;
@@ -79,14 +79,16 @@ ntime = numel(time);
 
 figure(1); clf
 for k = istart:irate:iend
-  xx = interpft(posx(:,:,k),96); yy = interpft(posy(:,:,k),96);  
+  xx = interpft(posx(:,:,k),256); yy = interpft(posy(:,:,k),256);  
+  xx = posx(:,:,k);
+  yy = posy(:,:,k);
   vec1 = [xx(:,:);xx(1,:)];
   vec2 = [yy(:,:);yy(1,:)];
   if 1
     clf
     plot(vec1,vec2,'r','linewidth',3)
     hold on;
-    plot(vec1(1,:),vec2(1,:),'b.','markersize',20)
+%    plot(vec1(1,:),vec2(1,:),'b.','markersize',20)
     if options.confined
       vec1 = [wallx(:,:);wallx(1,:)];
       vec2 = [wally(:,:);wally(1,:)];

### 2019-05-01 vesicle_code/src/Ves2D.m

@@ -126,6 +126,13 @@ while time < prams.T - 1e-10
   end
   % go back to old time
 
+  if 1
+  xmid = mean(X(1:end/2,1));
+  ymid = mean(X(end/2+1:end,1));
+  X(1:end/2) = X(1:end/2) - xmid;
+  X(end/2+1:end) = X(end/2+1:end) - ymid;
+  end
+
   if 0
   for k = 1:prams.nv
     z = X(1:end/2,k) + 1i*X(end/2+1:end,k);

### 2019-05-01 vesicle_code/docs/permeableVes/main.tex
fixed a few small typos and wordings

@@
   P[\mbx]\mbf &= (\mbf \cdot \mbn) \mbn, \\
-  D[\mbx]\mbf &= \mbx_s \cdot \mbf_s
+  D[\mbx]\mbf &= \mbx_s \cdot \mbf_s,
 \end{align}
-where $\mbn$ is the is the outward unit normal of the vesicle
-parameterized by $\mbx$, and $d/ds$ is its arclength derivative.
-Dropping the dependence of the operators on $\mbx$, the dynamics of the
-vesicle are governed by
+where $\mbn$ is the outward unit normal of the vesicle parameterized by
+$\mbx$, and $d/ds$ is its arclength derivative.  Dropping the dependence
+of the operators on $\mbx$, the dynamics of the vesicle are governed by
 \begin{align}
@@
 \end{align}
-To couple the vesicle dynamics to the concentration, the vesicle
-velocity satisfies the slip condition
+To couple the vesicle dynamics to the concentration, there is a
+difference between the fluid velocity and vesicle velocity
 \begin{align}
@@
 \end{align}
-where $j_w$ is the water flux through the vesicle.
-In~\cite{yao-mor2017}, this flux is
+where $j_w$ is the water flux through the vesicle.  This is the
+osmophoretic flow.  In~\cite{yao-mor2017}, this flux is
 \begin{align}
@@
 	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0$.}
-	\label{Shear0}
+%	\label{Shear0}
 \end{figure}
@@
 	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0.5$.}
-	\label{Shear0}
+%	\label{Shear0}
 \end{figure}
@@
 	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 1$.}
-	\label{Shear0}
+%	\label{Shear0}
 \end{figure}
@@
 	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 2$.}
-	\label{Shear0}
+%	\label{Shear0}
 \end{figure}
@@
  	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0$.}
- 	\label{Shear0}
+% 	\label{Shear0}
  \end{figure}
@@
  	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0.5$.}
- 	\label{Shear0}
+% 	\label{Shear0}
  \end{figure}
@@
  	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 1$.}
- 	\label{Shear0}
+% 	\label{Shear0}
  \end{figure}

### 2019-05-07 vesicle_code/docs/adhesion/revisions/reviewer1.tex
starting rebuttal forms for adhesion paper

\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage{todonotes}
\usepackage{amsmath,amsfonts,amssymb,stmaryrd}
\usepackage{color}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}
\noindent
Thank you for your constructive comments.  The attached manuscript
addresses all the reviewer 1's comments and the result is what we
believe is a stronger manuscript.
\\ \\ \noindent 
We also note that a few typos from the manuscript’s original form have
been addressed. An itemized list of the changes addressing the
reviewers’ comments are below.
\\ \\ \noindent 
Sincerely, \\ \noindent
Yuan-Nan Young, Shravan Veerapaneni, and Bryan Quaife

\vspace{20pt}
\noindent
\comment{While the numerical simulations performed are based on standard
approaches, and the results are supposedly correct, I find the results
not to have a significant impact. Most results presented, for example,
those on vesicle adhesion in quiescent flow, adhered vesicle dynamics in
shear flow, and adhesion of two approaching vesicles in a shear flow,
are not surprising, and similar results were obtained before for red
blood cells, capsules, drops, and adhered particles. Most (maybe all) of
the principals discussed are more-or-less understood, and would
therefore not of themselves constitute a novel contribution.}
\begin{itemize}
  \item rebuttal
\end{itemize}

\noindent
\comment{Second, the simulations are 2D, which makes it difficult to accept
whether the predicted results would be observed in experiments. There
was also no direct comparison with any experimental studies.}
\begin{itemize}
  \item rebuttal
\end{itemize}

\noindent
\comment{My third concern is the use of L-J potential. In practice, the
vesicle surface would be coated with some adhesive molecules (e.g.
receptor/ligand). Is the L-J type adhesive field appropriate for such
interactions? ALso, in reality, these bonds are stochastic in nature.}
\begin{itemize}
  \item rebuttal
\end{itemize}

\noindent
\comment{The authors talks about the "fluid trap". This is indeed a tricky
issue in any experiment dealing with extensional flow as how to
maintain the drop/vesicle at the stagnation point. But in a numerical
simulation this should not be any issue at all., because even of the
vesicle moves away from the stagnation point its dynamics is still
governed by the velocity gradient which is same everywhere in the flow
field.}
\begin{itemize}
  \item rebuttal
\end{itemize}

\noindent
\comment{There was not enough physical insights on the vesicle alignment
in extensional flow as presented in section IV. If the vesicles are
placed centrally, what causes the pair to become asymmetric in the first
place, since all components in the model are deterministic? The authors
used vorticity contours, but the external flow is irrotational; so what
is the origin of vorticity, and is it appropriate to use vorticity to
explain the behavior?}
\begin{itemize}
  \item rebuttal
\end{itemize}

\noindent
\comment{I did not find figure 14 relevant for the present article. This
result is not relevant, and also presented just to show what the authors
intend to do in future.}
\begin{itemize}
  \item rebuttal
\end{itemize}

\end{document}

### 2019-05-07 vesicle_code/docs/adhesion/revisions/reviewer2.tex
starting rebuttal forms for adhesion paper

\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage{todonotes}
\usepackage{amsmath,amsfonts,amssymb,stmaryrd}
\usepackage{color}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}
\noindent
Thank you for your constructive comments.  The attached manuscript
addresses all the reviewer 2's comments and the result is what we
believe is a stronger manuscript.
\\ \\ \noindent 
We also note that a few typos from the manuscript’s original form have
been addressed. An itemized list of the changes addressing the
reviewers’ comments are below.
\\ \\ \noindent 
Sincerely, \\ \noindent
Yuan-Nan Young, Shravan Veerapaneni, and Bryan Quaife

\vspace{20pt}
\noindent
\comment{General comment: I found that the figure captions are often
incomplete and that details of the legends are missing and are only
given in the text. I think figures should be self explanatory (e.g.
signification of symbols of fig. 9 right (angles corresponding to symbol
sizes); in fig. 10: scale/unit of vorticity, Fig 11: indicate in the
caption that the coloraturas corresponds to tension; Fig 12: color code
in figure caption...)}
\begin{itemize}
  \item rebuttal
\end{itemize}

\noindent
\comment{Abstract: it should be mentioned in the abstract that this is 2D
modelling. 2D simulations of vesicles are often perfectly fine to
investigate the physics of phenomena but in some cases 3D effects may
have their importance, at least for quantitative comparisons with
experiments. The reader should identify either from the title or
abstract that this study is 2D.}
\begin{itemize}
  \item rebuttal
\end{itemize}

\noindent
\comment{Introduction, 2nd paragraph: the transition in the effective
viscosity of vesicle or RBC suspensions was also validated
experimentally in ref [18] (Vitkova et al.), not only in [20-22].}
\begin{itemize}
  \item rebuttal
\end{itemize}

\noindent
\comment{Intro, 3rd paragraph: the buckling instability of aggregating RBC
membranes was not only predicted theroretically and numerically in
Flormann et al. [32] but also experimentally. In addition, a more
recent paper by Hoore et al. (Soft Matter 14, 6278-6289 (2018)) showed
the influence of the membrane shear elasticity on doublet shapes by 3D
modelling. This reference may be added.}
\begin{itemize}
  \item rebuttal
\end{itemize}

\noindent
\comment{Concerning the stability and dynamics of clusters of vesicles with
adhesive interaction, there have been at least two papers on clusters
in micro-channel flow (computational and experimental) that should be
cited: Brust et al., Scientific Reports 4, 4348 (2014) and Claveria et
al., Soft Matter. 2016 vol 12(39):8235-8245. About rheology, at least
the historical paper by Chien on the shear-thinning of blood related
to RBC aggregation should be cited : Chien, S., Usami, S., Dellenback,
R.~J., Gregersen, M.~I., Nanninga, L.~B.~\& Guest, M.~M. Blood
viscosity: Influence of erythrocyte aggregation. Science 157, 829–831
(1967).}
\begin{itemize}
  \item rebuttal
\end{itemize}

\noindent
\comment{In addition to ref [54], Gires et al. also published experimental
measurements of hydrodynamic interactions between vesicles in Gires et
al., Phys.~Fluids 26, 013304 (2014)}
\begin{itemize}
  \item rebuttal
\end{itemize}

\noindent
\comment{In II. Governing equations and fig. 1: the right panel of the
figure and comments at the end of the section say that the part of
vesicle membranes that is out of the contact zone, including the parts
that are facing the outer fluid, experience an attractive interaction.
This is an artifact due to the long-range potential chosen by the
authors to model the interaction. In most experimental systems, the
adhesive forces leading to cluster formation are either due to direct
bridging of membranes or depletion phenomena that lead to osmotic
pressure gradients. This is the case for RBC aggregation for instance.
In both mechanisms, there is indeed no attractive force between membrane
parts that are out of the contact zone. It is perfectly fine to model
the interaction by an adhesion potential such as represented in fig 1
left, but its use introduces this artifact that should be acknowledged
by the authors. It is also due to the fact that the value of parameter
$\delta$ (the equilibrium distance) is not small compared to vesicle
dimensions. This is a numerical necessity to avoid the need to have
extremely refined meshes but again in experiments, the equilibrium
distance is usually much smaller that vesicle sizes and is more
comparable to molecular sizes (size of bridging molecules or of
depletion-inducing macromolecules). This deserves to be acknowledged
also, even though it may not impact too much the results.}
\begin{itemize}
  \item rebuttal
\end{itemize}

\noindent
\comment{Along the same line, the repulsing spots in fig 1 right or Fig 3
right as well as the amplitude of the deformation in the contact zone
are again a consequence of the choice of parameter values for the
interaction potential and would probably not be so strong in real
cases where the equilibrium distance between membranes is much shorter
and the range of the potential is shorter.}
\begin{itemize}
  \item rebuttal
\end{itemize}

\noindent
\comment{I cannot figure out why the external part of vesicles on profile 1
in fig 3-left is yellow. Shouldn't the force be weakly attractive in
that region, as in fig 1-right?}
\begin{itemize}
  \item rebuttal
\end{itemize}

\noindent
\comment{Figs 4-5 and related text: it would have been interesting to
compare results with the bending energy of vesicles without adhesion
potential in their equilibrium shape, to show the energy gain due to
adhesion (bending and total energy). This could be a way to compare
the total energy of the doublet to the energy of dissociated vesicles
and infer about the stability of doublets.}
\begin{itemize}
  \item rebuttal
\end{itemize}

\noindent
\comment{Fig 9(right): I regret that the authors did not extend the study
to lower values of the reduced area, to reach values comparable to red
blood cells which are more deflated that $\Delta A=0.7$. Also, the range
of shear rates could have been slightly increased to reach the
stability limit of the most deflated vesicles. Here, we do not know
what happens below reduced areas of 0.8.}
\begin{itemize}
  \item rebuttal
\end{itemize}

\noindent
\comment{ Figs 9(right) and 12(right): the stability diagrams are presented
in different parameter spaces for the extensional and shear flow
cases. It would have been interesting to see e.g. the diagram in the
interaction energy vs. flow strength $\chi$ for both cases, for
comparison.}
\begin{itemize}
  \item rebuttal
\end{itemize}

\noindent
\comment{Fig.~10: the black arrows, as I understand, represent the total
attractive force due to the interaction potential. Would the authors
be able to represent also the total hydrodynamic forces on vesicles
which presumably balance the torque of interaction forces? Is there a
tank-treading motion of membranes?}
\begin{itemize}
  \item rebuttal
\end{itemize}

\noindent
\comment{Fig 12: the authors did not comment the evolution of the
frequency of distance oscillations in doublets when the Hamaker constant
is varied. Can it be compared to the natural rotation frequency of the
shear flow $\chi/2$? Does a strongly adhesive doublet tend to behave as
a tumbling rigid object following something similar to Jeffery orbits?}
\begin{itemize}
  \item rebuttal
\end{itemize}

\noindent
\comment{Fig 12-right: is the stability limit between the red and blue
zones linear? This would mean that a stability criterion could take
the form of a dimensionless number involving the ratio of Hamaker
constant/shear rate, a potentially interesting result.}
\begin{itemize}
  \item rebuttal
\end{itemize}

\noindent
\comment{Fig 13 and comments about rheology: I am not sure to understand
the meaning of the left figure where it is shown that the intrinsic
viscosity of the doublet in suspension is about twice the viscosity of a
single vesicle. By definition, the intrinsic viscosity does not depend
on volume fraction, so I do not expect such a big difference between
bound vesicles and isolated vesicles. With the values chosen for the
Hamaker constant and the shear rate, it seems (from fig 12-left) that
the interaction is quite strong and that the distance between the two
vesicles in the doublet is always very short (close to the equilibrium
distance $\delta$). So the doublet must be roughly tumbling as a single
object and unless a co-rotating tank-treading motion of the two
membranes produces a strong dissipation by shear flow in the gap between
the two vesicles, the difference should not be so large. It is also
quite curious that the intrinsic viscosity of the doublet is so close to
exactly twice the viscosity of a single vesicle. Could the authors check
and elaborate on this ? Was the volume fraction properly scaled out
here? Also in the right panel, the bending/tension part is compared to
twice the intrinsic viscosity of a suspension of isolated vesicles. Why
twice ? Finally, it is not clear how technically the bending/tension and
adhesion parts are separated.  Overall I think the study on rheology
needs much more development than what is presented here with only one
set of parameter values and very little quantitative comments.}
\begin{itemize}
  \item rebuttal
\end{itemize}

\noindent
\comment{In the conclusions, an example of aggregation of vesicles enclosed
in a bigger one is presented. I do not think this brings much to this
paper. Why not keep this for a future paper dedicated to this specific
problem and instead show examples of aggregates without the enclosing
large vesicle? In what conditions (reduced volume, Hamaker constant)
can linear structures (rouleaux) be formed for instance (see the paper
by Hoore et al whose reference is given above for instance).}
\begin{itemize}
  \item rebuttal
\end{itemize}

\end{document}

### 2019-05-07 vesicle_code/src/poten.m

@@ -622,9 +622,48 @@ for k=1:vesicle.nv  % Loop over curves
   
   G(:,:,k) = G(:,:,k).*sak;
   % multiply G by the Jacobian
+
+  G(:,:,k) = 2*G(:,:,k);
+  % qw assumes the scaling is 1/(4*pi) which is what comes out of Stokes
 end % k
 
 end % laplaceSLmatrix
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+function G = laplaceSLmatrixPrime(o,vesicle)
+% G = laplaceSLmatrixPrime(vesicle) generates the derivative of the
+% single-layer potential.  vesicle is a data structure defined as in the
+% capsules class G is (N,N,nv) array where N is the number of points per
+% curve and nv is the number of curves in X
+
+oc = curve;
+[x,y] = oc.getXY(vesicle.X); % Vesicle positions
+nx = vesicle.xt(vesicle.N+1:2*vesicle.N,:);
+ny = -vesicle.xt(1:vesicle.N,:);
+
+G = zeros(o.N,o.N,vesicle.nv);
+% initalize derivative of single-layer potential to zero
+for k=1:vesicle.nv  % Loop over curves
+  for j=1:vesicle.N % Loop over targets
+    rx = x(j,k) - x(:,k);
+    ry = y(j,k) - y(:,k);
+    rdotn = rx*nx(j,k) + ry*ny(j,k);
+    rho2 = rx.^2 + ry.^2;
+    rho2(j) = 1;
+    % Set diagonal term to one to avoid dividing by zero
+
+    G(j,:,k) = rdotn./rho2.*vesicle.sa(:,k);
+
+    G(j,j,k) = 0.5*vesicle.cur(j,k)*vesicle.sa(j,k);
+  end % j
+  G(:,:,k) = G(:,:,k)*2*pi/vesicle.N/(2*pi);
+end % k
+
+
+end % laplaceSLmatrixPrime
+
+
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 function D = laplaceDLmatrix(o,vesicle)
@@ -2100,7 +2139,7 @@ for k2 = 1:ncol % loop over columns of target points
 
 end % k2
 % Evaluate single-layer potential at arbitrary target points
[…]

### 2019-05-20 vesicle_code/examples/output/makeImages.m
starting revisions on adhesion paper

@@ -5,8 +5,8 @@ options.savefig = false;
 irate = 10; % controls the speed of the visualization
 
 if 1
-  file = 'extensional2VesData.bin';
-%  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi7em2_ra070/extensional2VesData.bin';
+%  file = 'extensional2VesDData.bin';
+  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves/adR4em1adS7em1Chi8em2_ra065/extensional2VesData.bin';
   ax = [-2 2 -2 2];
   options.confined = false;
 end

### 2019-05-21 vesicle_code/docs/adhesion/adhesion.tex
improving phase diagrams

@@
 \begin{figure}[htp]
-  \includegraphics[height=0.27\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
-  \includegraphics[height=0.27\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
-  \includegraphics[height=0.27\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
+  \includegraphics[height=0.26\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
+  \includegraphics[height=0.26\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
+  \includegraphics[height=0.26\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
   \caption{\label{fig:extensionalInclinationAngle} {\em Left}: The
@@
 \begin{figure}
-  \includegraphics[height=0.35\textwidth]{figs/shear_adR4em1Chi1e0_ra-090.pdf}
-  \includegraphics[height=0.35\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
+  \includegraphics[height=0.27\textwidth]{figs/shear_adR4em1Chi1e0_ra-090.pdf}
+  \includegraphics[height=0.27\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
+  \includegraphics[height=0.27\textwidth]{figs/shear_adR1em1_ra090_phaseDiagram.pdf}
   \caption{\label{fig:sflow_phase_diagram} {\em Left}: Distance between
@@
   correspond to a linear spacing of Hamaker constants ranging from
-  $\mathcal{H}=0.1$ and $\mathcal{H}=1.0$.  {\em Right}: Phase diagram
-  of vesicle hydrodynamics in a shear flow.  At a fixed reduced area
-  $\Delta A=0.90$ and $\delta = 0.4$, the critical Hamaker constant
-  $\mathcal{H}$ for binding of two vesicles in a shear flow depends on
-  the shear rate $\chi$.}
+  $\mathcal{H}=0.1$ and $\mathcal{H}=1.0$.  {\em Center and Right}:
+  Phase diagram of vesicle hydrodynamics in a shear flow with $\delta =
+  0.4$ (center) and $\delta = 0.1$ (right) with reduced area  $\Delta A
+  = 0.9$. The critical Hamaker constant $\mathcal{H}$ for binding of two
+  vesicles in a shear flow depends on the shear rate $\chi$.  For a
+  doublet to form, lower separation distances require a stronger Hamaker
+  constants at a given shear rate.}
 \end{figure}

### 2019-05-21 vesicle_code/examples/extensional2Ves.m

@@ -1,4 +1,4 @@
-function [] = extensional2Ves
+%function [] = extensional2Ves
 
 clear all; clc
 
@@ -12,7 +12,7 @@ prams.m = 1000;             % number of time steps
 prams.kappa = [1 1];         % bending coefficient
 prams.viscCant = [1 1];         % viscosity contrast
 options.farField = 'extensional'; % background velocity
-options.farFieldSpeed = 0.1;
+options.farFieldSpeed = 0.07;
 aptions.order = 1;          % time stepping order
 options.vesves = 'implicit';
 % Discretization of vesicle-vesicle interactions.
@@ -63,10 +63,10 @@ options.errorFile = 'output/extensional2VesError.bin';
 % Set options and parameters that the user doesn't
 % Also add src to path
 
-posx1 = load('posx1_RA065.dat');
-posy1 = load('posy1_RA065.dat');
-posx2 = load('posx2_RA065.dat');
-posy2 = load('posy2_RA065.dat');
+posx1 = load('posx1_RA070_rotated.dat');
+posy1 = load('posy1_RA070_rotated.dat');
+posx2 = load('posx2_RA070_rotated.dat');
+posy2 = load('posy2_RA070_rotated.dat');
 
 
 if 0

### 2019-05-21 vesicle_code/docs/adhesion/adhesion.tex
renaming a figure to be consistent with parameter values

@@
 Hamaker constant $\mathcal{H} = 0.7$, separation distance $\delta =
-0.4$, and extensional rate $\chi = 0.7$ in
+0.4$, and extensional rate $\chi = 0.07$ in
 Figure~\ref{fig:extensionalVorticity}.  Starting from an initial inclination angle $\theta=\pi$, the doublet 
@@
   0.7$, the separation distance is $\delta = 0.4$, the Hamaker constant
-  is $\mathcal{H} = 0.7$, and the extensional rate is $\chi = 0.7$.}
+  is $\mathcal{H} = 0.7$, and the extensional rate is $\chi = 0.07$.}
 \end{figure}
@@
 \begin{figure}
-  \includegraphics[height=0.27\textwidth]{figs/shear_adR4em1Chi1e0_ra-090.pdf}
+  \includegraphics[height=0.27\textwidth]{figs/shear_adR4em1Chi5em1_ra090.pdf}
   \includegraphics[height=0.27\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}

### 2019-05-23 vesicle_code/docs/adhesion/adhesion.tex
fixing up intrinsic viscosity images
fixed up text in intrinsic viscosity calculation

@@
 $\phi$ is the area fraction of vesicles, $\tau$ is the stress due to the
-vesicles, $\langle \cdot \rangle$ is the spatial average, and $\xxi$ is
-the traction as defined in equation~\eqref{eqn:traction}.  In the left
-plot of Figure~\ref{fig:shearIntrinsicViscosity}, we compare the
-intrinsic viscosity of a single tank-treading vesicle to a doublet.  To
-validate our simulations, we superimpose (black marks) the intrinsic
-viscosity calculated by Ghigliotti {\em et
+vesicles, $\langle \cdot \rangle$ is the spatial average, $|\omega|$ is
+the total area of both vesicles, and $\xxi$ is the traction as defined
+in equation~\eqref{eqn:traction}.  In the left plot of
+Figure~\ref{fig:shearIntrinsicViscosity}, we compare the intrinsic
+viscosity of a single tank-treading vesicle to a doublet.  To validate
+our simulations, we superimpose (black marks) the intrinsic viscosity
+calculated by Ghigliotti {\em et
 al.}~\cite{GhigliottiBibenMisbah2010_JFM}.  The presence of the doublet
-significantly increases the intrinsic viscosity at all the reduced
+slightly increases the intrinsic viscosity at all the reduced
 areas.  To further characterize the effect of adhesion, in the right
@@
 (blue), and the contribution from the adhesion (red).  We also
-superimpose twice the intrinsic viscosity of a single tank-treading
+superimpose the intrinsic viscosity of a single tank-treading
 vesicle (dashed curve) to demonstrate that the bending and tension of
@@
   the contribution from the vesicle adhesion (red).  Also included is
-  twice the intrinsic viscosity of a single tank-treading vesicle
-  (dashed black line).}
+  the intrinsic viscosity of a single tank-treading vesicle (dashed
+  black line).}
 \end{figure}

### 2019-06-17 vesicle_code/docs/adhesion/adhesion.tex
working on revisions

@@
 \usepackage{stmaryrd}
+%\usepackage{subfig}
 %\usepackage{hyperref}% add hypertext capabilities
@@
 
+\newcommand{\subfigimg}[3][,]{%
+  \setbox1=\hbox{\includegraphics[#1]{#3}}% Store image in box
+  \leavevmode\rlap{\usebox1}% Print image
+  \rlap{\hspace*{0pt}\raisebox{\dimexpr\ht1-0\baselineskip}{\bf #2}}% Print label
+  \phantom{\usebox1}% Insert appropriate spcing
+}
+
 \begin{document}
@@
 \begin{abstract}
-The dynamics of an adhesive vesicle doublet under various flow conditions is
-investigated numerically using a high-order, adaptive-in-time boundary
-integral method. In a quiescent flow, two nearby vesicles
-move slowly towards each other under the adhesive potential, pushing out
-fluid between them to form a vesicle doublet at equilibrium. A lubrication
-analysis on such draining of a thin film gives the dependencies of
-draining time on adhesion strength and separation distance that are in
-good agreement with numerical results.
-%
-In a microfluid trap where the stagnation of an extensional flow is dynamically
-placed in the middle of a vesicle doublet through an active control
-loop, novel dynamics of a vesicle doublet is observed. Numerical
+The dynamics of an adhesive two-dimensional vesicle doublet under
+various flow conditions is investigated numerically using a high-order,
+adaptive-in-time boundary integral method. In a quiescent flow, two
+nearby vesicles move slowly towards each other under the adhesive
+potential, pushing out fluid between them to form a vesicle doublet at
+equilibrium. A lubrication analysis on such draining of a thin film
+gives the dependencies of draining time on adhesion strength and
+separation distance that are in good agreement with numerical results.
+%
+In a microfluid trap where the stagnation of an extensional flow is
+dynamically placed in the middle of a vesicle doublet through an active
+control loop, novel dynamics of a vesicle doublet is observed. Numerical
 simulations show that there exists a critical extensional flow rate
-above which adhesive interaction is overcome by the 
-diverging stream, thus providing a simple method to measure the adhesion
-strength between two vesicle membranes. 
+above which adhesive interaction is overcome by the diverging stream,
+thus providing a simple method to measure the adhesion strength between
+two vesicle membranes. 
 %
 In a planar shear flow, numerical simulations reveal that a vesicle
-doublet may form provided that the adhesion
-strength is sufficiently large at a given vesicle reduced area. Once a
-doublet is formed, the effective shear viscosity of a dilute suspension
-of vesicle doublets is found to be a function of  reduced area.  Results from these numerical studies and
-analysis shed light on the hydrodynamic and rheological consequences of adhesive interactions
-between vesicles in a viscous fluid.
+doublet may form provided that the adhesion strength is sufficiently
+large at a given vesicle reduced area. Once a doublet is formed, the
+effective shear viscosity of a dilute suspension of vesicle doublets is
+found to be a function of  reduced area.  Results from these numerical
+studies and analysis shed light on the hydrodynamic and rheological
+consequences of adhesive interactions between vesicles in a viscous
+fluid.
 %\begin{description}
@@
 by direct numerical simulations~\cite{GhigliottiBibenMisbah2010_JFM} and
-experiments~\cite{DeschampsKantsler2009_PNAS,
+experiments~\cite{Vitkova2008_BJ,DeschampsKantsler2009_PNAS,
 KantslerSegreSteinberg2008_EPL, ZabuskySegreDeschamps2011_PoF}.  Between
@@
 $\Delta A = 0.9$.  In the left plot of
-Figure~\ref{fig:sflow_phase_diagram}, we plot the minimum distance
+Figure~\ref{fig:sflow_distance}, we plot the minimum distance
 between the vesicles as a function of time for various Hamaker
@@
 correspond to Hamaker constants that are sufficiently large to form a
-doublet.
+doublet.  Figure~\ref{fig:sflow_phase_diagram} indicates whether a
+doublet with reduced area $\Delta A = 0.9$ is formed (blue) or not (red)
+for a variety of shear rates, Hamaker constants, and at two different
+separation distances.  The plot includes a line of best fit between the
+stable and unstable regions.  Since the transition is linear, this
+indicates that a dimensionless number involving the ratio of the Hamaker
+constant could be used to determine if a doublet forms or not.
 
@@
   \includegraphics[height=0.27\textwidth]{figs/shear_adR4em1Chi5em1_ra090.pdf}
-  \includegraphics[height=0.27\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
-  \includegraphics[height=0.27\textwidth]{figs/shear_adR1em1_ra090_phaseDiagram.pdf}
-  \caption{\label{fig:sflow_phase_diagram} {\em Left}: Distance between
-  a pair of vesicles in a planar shear flow with shear rate $\chi=0.5$,
+  \caption{\label{fig:sflow_distance} {\em Left}: The distance between a
+  pair of vesicles in a planar shear flow with shear rate $\chi=0.5$,
   and separation distance $\delta = 0.4$.  The different lines
   correspond to a linear spacing of Hamaker constants ranging from
-  $\mathcal{H}=0.1$ and $\mathcal{H}=1.0$.  {\em Center and Right}:
-  Phase diagram of vesicle hydrodynamics in a shear flow with $\delta =
-  0.4$ (center) and $\delta = 0.1$ (right) with reduced area  $\Delta A
-  = 0.9$. The critical Hamaker constant $\mathcal{H}$ for binding of two
-  vesicles in a shear flow depends on the shear rate $\chi$.  For a
-  doublet to form, lower separation distances require a stronger Hamaker
-  constants at a given shear rate.}
+  $\mathcal{H}=0.1$ and $\mathcal{H}=1.0$.  {\em Right}:
+  \todo[inline]{frequency of the oscillation}}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[height=0.37\textwidth]{figs/shear_adR1em1_ra090_phaseDiagram.pdf}
+  \includegraphics[height=0.37\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
+  \caption{\label{fig:sflow_phase_diagram} Phase diagram of vesicle
+  hydrodynamics in a shear flow with $\delta = 0.1$ (left) and $\delta =
+  0.4$ (right) with reduced area $\Delta A = 0.9$. The critical Hamaker
+  constant $\mathcal{H}$ for binding of two vesicles in a shear flow
+  depends on the shear rate $\chi$.  For a doublet to form, lower
+  separation distances require a stronger Hamaker constants at a given
+  shear rate.  The stability limit appears to be linear, indicating that
+  there is potentially a stability criteria that depends on a
+  dimensionless number involving the ratio of the Hamaker constant and
+  shear rate.}
 \end{figure}
@@
 
-\begin{figure}[htp]
-  \centering
-  \includegraphics[width=0.45\textwidth]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
-  \includegraphics[width=0.45\textwidth]{figs/doublet_decomp.pdf}
+\begin{figure}[]
+  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
+  \subfigimg[width=\linewidth]{(a)}{figs/doublet_decomp.pdf} &
+  \subfigimg[width=\linewidth]{(b)}{figs/doublet_decomp.pdf}
+  \end{tabular}
+%  \centering
+%  \includegraphics[width=0.45\textwidth]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
+%  \includegraphics[width=0.45\textwidth]{figs/doublet_decomp.pdf}
   \caption{\label{fig:shearIntrinsicViscosity} {\em Left}: The intrinsic

### 2019-06-17 vesicle_code/docs/adhesion/revisions/reviewer2.tex
starting revisions on adhesion paper
working on revisions

@@
 \newcommand{\comment}[1]{{\color{blue} #1}}
+\newcommand{\xxi}{\boldsymbol{\xi}}
 
@@
 \noindent
-\comment{Abstract: it should be mentioned in the abstract that this is 2D
-modelling. 2D simulations of vesicles are often perfectly fine to
+\comment{Abstract: it should be mentioned in the abstract that this is
+2D modelling. 2D simulations of vesicles are often perfectly fine to
 investigate the physics of phenomena but in some cases 3D effects may
@@
 \begin{itemize}
-  \item rebuttal
+  \item We now mention in the abstract that we consider the dynamics of
+    and adhesive two-dimensional vesicle doublet.
 \end{itemize}
@@
 \begin{itemize}
-  \item rebuttal
+  \item We have included reference [18] in the list of experimental
+    works that validated the transition in the effective viscosity
 \end{itemize}
@@
 \begin{itemize}
-  \item rebuttal
+  \item We have extended the results to include vesicles of reduced area
+    0.65, a typical value for two-dimensional red blood cells.
+  \item We have also reported results for larger extensional rates so
+    that the transition from a fluid trap to two separating vesicles can
+    be observed at all the reduced areas.
 \end{itemize}
@@
 \begin{itemize}
-  \item rebuttal
+  \item The reviewer is correct that we miscalculated the intrinsic
+    viscosity.  We had initially divided by only the area inside a
+    single vesicle rather than both vesicles in the doublet.  This has
+    been corrected, and now there is only a small increase in the
+    intrinsic viscosity when compared to a single tank treading vesicle.
+
+  \item With the numbers corrected, the intrinsic viscosity is clearly
+    not equal to the intrinsic viscosity of a tank treading vesicle.
+
+  \item We have double-checked our calculations and the volume fraction
+    has been properly accounted for.
+
+  \item Using twice the intrinsic viscosity of a tank treading vesicle
+    was incorrect.  We now compare the intrinsic viscosity of a single
+    tank treading vesicle with the doublet.
+
+  \item The total force $\xxi$ is the sum of a bending, tension, and
+    adhesion force.  Therefore, the contribution to the intrinsic
+    viscosity due to each of these forces can be individually computed.
 \end{itemize}

### 2019-06-17 vesicle_code/examples/output/makeImages.m

@@ -4,7 +4,7 @@ options.savefig = false;
 
 irate = 10; % controls the speed of the visualization
 
-if 1
+if 0
   file = 'extensional2VesData.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves_rotated/adR4em1adS7em1Chi7em2_ra070/extensional2VesData.bin';
   ax = [-2 2 -2 2];
@@ -21,7 +21,7 @@ if 0
   options.confined = false;
 end
 if 0
-  file = '~/projects/brinkman/vesicle_code/results/May092019/relaxation1Ves/kappa1em1_beta1ep0_ra0p35/relaxation1VesData.bin';
+  file = '~/projects/brinkman/vesicle_code/results/May092019/relaxation1Ves/kappa1em1_beta1ep0_ra0p95/relaxation1VesData.bin';
 %  file = 'relaxationManyVesData.bin';
   ax = [-3 3 -6 6];
   options.confined = false;
@@ -45,14 +45,14 @@ if 0
   options.confined = false;
 end
 if 0
-  file = '~/projects/brinkman/vesicle_code/results/May092019/shear1Ves/kappa1em1_beta1ep0_chi1ep1_ra0p35/shear1VesData.bin';
+  file = '~/projects/brinkman/vesicle_code/results/May092019/shear1Ves/kappa1em1_beta1ep0_chi1ep0_ra0p55/shear1VesData.bin';
 %  file = 'shear1VesData.bin';
   ax = [-5 5 -5 5];
   options.confined = false;
 end
-if 0
+if 1
 %  file = 'shear2VesAData.bin';
-  file = '~/projects/brinkman/vesicle_code/results/shear2Ves/adR4em1adS6em1Chi2p5em1_ra090/shear2VesData.bin';
+  file = '~/projects/brinkman/vesicle_code/results/shear2Ves/adR1em1adS2e0Chi1p25e0_ra090/shear2VesData.bin';
   ax = [-10 10 -3 3];
   options.confined = false;
 end

### 2019-06-17 vesicle_code/docs/adhesion/adhesion.tex
working on revisions

@@
   \leavevmode\rlap{\usebox1}% Print image
-  \rlap{\hspace*{0pt}\raisebox{\dimexpr\ht1-0\baselineskip}{\bf #2}}% Print label
-  \phantom{\usebox1}% Insert appropriate spcing
+  \rlap{\hspace*{0pt}\raisebox{\dimexpr\ht1-0\baselineskip}{\bf
+  \normalsize #2}}% Print label
+  \phantom{\usebox1}% Insert appropriate spacing
 }
@@
 the total area of both vesicles, and $\xxi$ is the traction as defined
-in equation~\eqref{eqn:traction}.  In the left plot of
-Figure~\ref{fig:shearIntrinsicViscosity}, we compare the intrinsic
+in equation~\eqref{eqn:traction}.  In
+Figure~\ref{fig:shearIntrinsicViscosity}(a), we compare the intrinsic
 viscosity of a single tank-treading vesicle to a doublet.  To validate
@@
 al.}~\cite{GhigliottiBibenMisbah2010_JFM}.  The presence of the doublet
-slightly increases the intrinsic viscosity at all the reduced
-areas.  To further characterize the effect of adhesion, in the right
-plot of Figure~\ref{fig:shearIntrinsicViscosity} we decompose the
-intrinsic viscosity into the contributions from the bending and tension
-(blue), and the contribution from the adhesion (red).  We also
-superimpose the intrinsic viscosity of a single tank-treading
-vesicle (dashed curve) to demonstrate that the bending and tension of
-the doublet behave similarly, but not identically, to a dilute
-suspensions of non-adhering tank-treading vesicles.  We see that the
-effect of the adhesion on the intrinsic viscosity is largest for
-vesicles with small reduced areas.
+slightly increases the intrinsic viscosity at all the reduced areas.  To
+further characterize the effect of adhesion, in
+Figure~\ref{fig:shearIntrinsicViscosity}(b) we decompose the intrinsic
+viscosity into the contributions from the bending and tension (blue),
+and the contribution from the adhesion (red).  We also superimpose the
+intrinsic viscosity of a single tank-treading vesicle (dashed curve) to
+demonstrate that the bending and tension of the doublet behave
+similarly, but not identically, to a dilute suspensions of non-adhering
+tank-treading vesicles.  We see that the effect of the adhesion on the
+intrinsic viscosity is largest for vesicles with small reduced areas.
 
@@
 %  \includegraphics[width=0.45\textwidth]{figs/doublet_decomp.pdf}
-  \caption{\label{fig:shearIntrinsicViscosity} {\em Left}: The intrinsic
+  \caption{\label{fig:shearIntrinsicViscosity} (a) The intrinsic
   viscosity of a tank-treading vesicle (blue) and a doublet (red).  The
@@
   denote intrinsic viscosity values computed by Ghigliotti {\em et
-  al.}~\cite{GhigliottiBibenMisbah2010_JFM} (cf.~Figure 5).  {\em
-  Right}: The decomposition of the intrinsic viscosity into the
-  contributions for the bending and tension (blue) of the vesicles, and
-  the contribution from the vesicle adhesion (red).  Also included is
-  the intrinsic viscosity of a single tank-treading vesicle (dashed
-  black line).}
+  al.}~\cite{GhigliottiBibenMisbah2010_JFM} (cf.~Figure 5).  (b) The
+  decomposition of the intrinsic viscosity into the contributions for
+  the bending and tension (blue) of the vesicles, and the contribution
+  from the vesicle adhesion (red).  Also included is the intrinsic
+  viscosity of a single tank-treading vesicle (dashed black line).}
 \end{figure}

### 2019-06-20 vesicle_code/docs/adhesion/adhesion.tex
added author contribution section
started writing about the period

@@
 correspond to Hamaker constants that are sufficiently large to form a
-doublet.  Figure~\ref{fig:sflow_phase_diagram} indicates whether a
-doublet with reduced area $\Delta A = 0.9$ is formed (blue) or not (red)
-for a variety of shear rates, Hamaker constants, and at two different
+doublet.  We also plot the time required for the doublet to make a
+complete revolution at a variety of Hamaker constants and shear rates.
+For a fixed Hamaker contant, as expected, the period decreases for
+larger shear rates.  In addition, for a fixed shear rate, the period
+decreases as the Hamaker constant increases, but the period eventually
+plateaus.  More interesting, for larger shear rates, the period of the
+doublet appears to be independent of the Hamaker constant.
+
+Figure~\ref{fig:sflow_phase_diagram} indicates whether a doublet with
+reduced area $\Delta A = 0.9$ is formed (blue) or not (red) for a
+variety of shear rates, Hamaker constants, and at two different
 separation distances.  The plot includes a line of best fit between the
@@
 \begin{figure}
-  \includegraphics[height=0.27\textwidth]{figs/shear_adR4em1Chi5em1_ra090.pdf}
+  \includegraphics[height=0.34\textwidth]{figs/shear_adR4em1Chi5em1_ra090.pdf}
+  \includegraphics[height=0.34\textwidth]{figs/shear_adR4em1Chi5em1_ra090_period.pdf}
   \caption{\label{fig:sflow_distance} {\em Left}: The distance between a
@@
   correspond to a linear spacing of Hamaker constants ranging from
-  $\mathcal{H}=0.1$ and $\mathcal{H}=1.0$.  {\em Right}:
-  \todo[inline]{frequency of the oscillation}}
+  $\mathcal{H}=0.1$ and $\mathcal{H}=1.0$.  {\em Right}: The time
+  required for a doublet to complete a single rotation.  The reduced
+  area is $\Delta A = 0.90$ and the separation distance is $\delta =
+  0.4$.  The different lines correspond to different shear rates.}
 \end{figure}
@@
 
+BQ and YNY contributed equally to model development, code development,
+and simulations.  All authors contributed equally to writing the
+manuscript.
+
 \begin{appendices}

### 2019-06-20 vesicle_code/docs/adhesion/adhesion.tex
removed multi vesicle example from conclusions

@@
 vesicle properties (such as reduced area and bending modulus), viscosity
-contrast, and effects of confinement on adhesive interactions.
-
-Flormann {\it et al.} studied the clustering and packing of an
-unbounded suspension of vesicles~\cite{FlormannAouane2017_SciReports}.  In engineering
-applications of vesicle emulsions, smaller vesicles are often enclosed in
-a big vesicle, as shown in Figure~\ref{fig:relaxationManyVes}, where
-the left panel shows an initial condition of five vesicles suspended
-inside of a larger vesicle.  The second panel from the left shows the
-membrane configuration and flow streamlines at an intermediate time.
-There is no imposed flow, so the dynamics is governed entirely by the
-vesicle forces, including adhesion.  In the absence of confinement, we
-would expect the vesicles to align themselves as a rouleaux with the
-membranes forming a parachute, male-female, or S-shape
-configuration~\cite{FlormannAouane2017_SciReports}.  However, because of
-the bounding vesicle and the dense packing, the interior vesicles align
-themselves differently.  The bounding membrane evolves dynamically
-together with all the interior vesicles to minimize the total membrane
-energy.
-
-As a result of force balance, the equilibrium shape of the bounding
-vesicle is far from a symmetric shape while the interior smaller
-vesicles are of similar shape to each other.  We also plot the tension
-(third) and adhesion (fourth) of the final equilibrium configuration.
-We remark that the adhesion force is attractive on all the vesicle
-membranes while large positive membrane tension is found only on the
-bounding vesicle.  In particular, the interior vesicles form a flat
-contact region with a large negative tension.  We are now conducting
-simulations of such vesicle configuration under a planar shear flow.
-
-\begin{figure}[htp]
-\centering
-\includegraphics[height=0.24\textwidth,trim={10cm 0cm 10cm 0cm},clip]{figs/relaxationManyVesInitialCondition.png}
-\includegraphics[height=0.24\textwidth,trim={2cm 0cm 2cm 0cm},clip]{figs/relaxationManyVesStreamlines.png}
-\includegraphics[height=0.24\textwidth,trim={2cm 0cm 1cm 0cm},clip]{figs/relaxationManyVesTension.png}
-\includegraphics[height=0.24\textwidth,trim={2cm 0cm 2cm 0cm},clip]{figs/relaxationManyVesAdhesion.png}
-\caption{\label{fig:relaxationManyVes} Five vesicles in a quiescent flow
-suspended in a bounding vesicle.   All vesicles are interacting through
-hydrodynamic flow and an adhesion potential with Hamaker constant
-$\mathcal{H} = 0.7$ and separation distance $\delta = 0.4$.  From left
-to right, the plots are the initial condition, the streamlines at an
-intermediate time, the tension at the steady-state configuration, and
-the adhesion force projected onto the outward unit normal at the
-steady-state configuration.  Along the bounding vesicle, the tension is
-largest and the adhesion is smallest in the regions that are
-well-separated from the interior vesicles.  Similar to other
-simulations, the interior vesicles are relatively flat and have a large
-negative tension in the contact regions.}
-\end{figure}
+contrast, and effects of confinement on adhesive interactions.  Another
+future direction is to consider the clustering and packing of an
+unbounded suspension of vesicles~\cite{FlormannAouane2017_SciReports}.
+
+%Flormann {\it et al.} studied the clustering and packing of an unbounded
+%suspension of vesicles~\cite{FlormannAouane2017_SciReports}.  In
+%engineering applications of vesicle emulsions, smaller vesicles are
+%often enclosed in a big vesicle, as shown in
+%Figure~\ref{fig:relaxationManyVes}, where the left panel shows an
+%initial condition of five vesicles suspended inside of a larger vesicle.
+%The second panel from the left shows the membrane configuration and flow
+%streamlines at an intermediate time.  There is no imposed flow, so the
+%dynamics is governed entirely by the vesicle forces, including adhesion.
+%In the absence of confinement, we would expect the vesicles to align
+%themselves as a rouleaux with the membranes forming a parachute,
+%male-female, or S-shape
+%configuration~\cite{FlormannAouane2017_SciReports}.  However, because of
+%the bounding vesicle and the dense packing, the interior vesicles align
+%themselves differently.  The bounding membrane evolves dynamically
+%together with all the interior vesicles to minimize the total membrane
+%energy.
+%
+%As a result of force balance, the equilibrium shape of the bounding
+%vesicle is far from a symmetric shape while the interior smaller
+%vesicles are of similar shape to each other.  We also plot the tension
+%(third) and adhesion (fourth) of the final equilibrium configuration.
+%We remark that the adhesion force is attractive on all the vesicle
+%membranes while large positive membrane tension is found only on the
+%bounding vesicle.  In particular, the interior vesicles form a flat
+%contact region with a large negative tension.  We are now conducting
+%simulations of such vesicle configuration under a planar shear flow.
+%
+%
+%\begin{figure}[htp]
+%\centering
+%\includegraphics[height=0.24\textwidth,trim={10cm 0cm 10cm 0cm},clip]{figs/relaxationManyVesInitialCondition.png}
+%\includegraphics[height=0.24\textwidth,trim={2cm 0cm 2cm 0cm},clip]{figs/relaxationManyVesStreamlines.png}
+%\includegraphics[height=0.24\textwidth,trim={2cm 0cm 1cm 0cm},clip]{figs/relaxationManyVesTension.png}
+%\includegraphics[height=0.24\textwidth,trim={2cm 0cm 2cm 0cm},clip]{figs/relaxationManyVesAdhesion.png}
+%\caption{\label{fig:relaxationManyVes} Five vesicles in a quiescent flow
+%suspended in a bounding vesicle.   All vesicles are interacting through
+%hydrodynamic flow and an adhesion potential with Hamaker constant
+%$\mathcal{H} = 0.7$ and separation distance $\delta = 0.4$.  From left
+%to right, the plots are the initial condition, the streamlines at an
+%intermediate time, the tension at the steady-state configuration, and
+%the adhesion force projected onto the outward unit normal at the
+%steady-state configuration.  Along the bounding vesicle, the tension is
+%largest and the adhesion is smallest in the regions that are
+%well-separated from the interior vesicles.  Similar to other
+%simulations, the interior vesicles are relatively flat and have a large
+%negative tension in the contact regions.}
+%\end{figure}
 

### 2019-06-21 vesicle_code/docs/adhesion/adhesion.tex
yny

--- 2019-06-17 vesicle_code/docs/adhesion/adhesion.tex
@@
 %\documentclass[aps,prb,showpacs,amsmath,amssymb,superscriptaddress]{revtex4-1}
-\documentclass[prf,superscriptaddress,showkeys]{revtex4-1}
+\documentclass[prf,superscriptaddress,showkeys,longbibliography]{revtex4-1}
 
@@
 \usepackage{stmaryrd}
-%\usepackage{subfig}
 %\usepackage{hyperref}% add hypertext capabilities
@@
 
-\newcommand{\subfigimg}[3][,]{%
-  \setbox1=\hbox{\includegraphics[#1]{#3}}% Store image in box
-  \leavevmode\rlap{\usebox1}% Print image
-  \rlap{\hspace*{0pt}\raisebox{\dimexpr\ht1-0\baselineskip}{\bf
-  \normalsize #2}}% Print label
-  \phantom{\usebox1}% Insert appropriate spacing
-}
-
 \begin{document}
@@
 \begin{abstract}
-The dynamics of an adhesive two-dimensional vesicle doublet under
-various flow conditions is investigated numerically using a high-order,
-adaptive-in-time boundary integral method. In a quiescent flow, two
-nearby vesicles move slowly towards each other under the adhesive
-potential, pushing out fluid between them to form a vesicle doublet at
-equilibrium. A lubrication analysis on such draining of a thin film
-gives the dependencies of draining time on adhesion strength and
-separation distance that are in good agreement with numerical results.
-%
-In a microfluid trap where the stagnation of an extensional flow is
-dynamically placed in the middle of a vesicle doublet through an active
-control loop, novel dynamics of a vesicle doublet is observed. Numerical
+The dynamics of an adhesive vesicle doublet under various flow conditions is
+investigated numerically using a high-order, adaptive-in-time boundary
+integral method. In a quiescent flow, two nearby vesicles
+move slowly towards each other under the adhesive potential, pushing out
+fluid between them to form a vesicle doublet at equilibrium. A lubrication
+analysis on such draining of a thin film gives the dependencies of
+draining time on adhesion strength and separation distance that are in
+good agreement with numerical results.
+%
+In a microfluid trap where the stagnation of an extensional flow is dynamically
+placed in the middle of a vesicle doublet through an active control
+loop, novel dynamics of a vesicle doublet is observed. Numerical
 simulations show that there exists a critical extensional flow rate
-above which adhesive interaction is overcome by the diverging stream,
-thus providing a simple method to measure the adhesion strength between
-two vesicle membranes. 
+above which adhesive interaction is overcome by the 
+diverging stream, thus providing a simple method to measure the adhesion
+strength between two vesicle membranes. 
 %
 In a planar shear flow, numerical simulations reveal that a vesicle
-doublet may form provided that the adhesion strength is sufficiently
-large at a given vesicle reduced area. Once a doublet is formed, the
-effective shear viscosity of a dilute suspension of vesicle doublets is
-found to be a function of  reduced area.  Results from these numerical
-studies and analysis shed light on the hydrodynamic and rheological
-consequences of adhesive interactions between vesicles in a viscous
-fluid.
+doublet may form provided that the adhesion
+strength is sufficiently large at a given vesicle reduced area. Once a
+doublet is formed, the effective shear viscosity of a dilute suspension
+of vesicle doublets is found to be a function of  reduced area.  Results from these numerical studies and
+analysis shed light on the hydrodynamic and rheological consequences of adhesive interactions
+between vesicles in a viscous fluid.
 %\begin{description}
@@
 by direct numerical simulations~\cite{GhigliottiBibenMisbah2010_JFM} and
-experiments~\cite{Vitkova2008_BJ,DeschampsKantsler2009_PNAS,
+experiments~\cite{DeschampsKantsler2009_PNAS,
 KantslerSegreSteinberg2008_EPL, ZabuskySegreDeschamps2011_PoF}.  Between
@@
 \begin{figure}[htp]
-  \includegraphics[height=0.26\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
-  \includegraphics[height=0.26\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
-  \includegraphics[height=0.26\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
+  \includegraphics[height=0.27\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
+  \includegraphics[height=0.27\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
+  \includegraphics[height=0.27\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
   \caption{\label{fig:extensionalInclinationAngle} {\em Left}: The
@@
 Hamaker constant $\mathcal{H} = 0.7$, separation distance $\delta =
-0.4$, and extensional rate $\chi = 0.07$ in
+0.4$, and extensional rate $\chi = 0.7$ in
 Figure~\ref{fig:extensionalVorticity}.  Starting from an initial inclination angle $\theta=\pi$, the doublet 
@@
   0.7$, the separation distance is $\delta = 0.4$, the Hamaker constant
-  is $\mathcal{H} = 0.7$, and the extensional rate is $\chi = 0.07$.}
+  is $\mathcal{H} = 0.7$, and the extensional rate is $\chi = 0.7$.}
 \end{figure}
@@
 $\Delta A = 0.9$.  In the left plot of
-Figure~\ref{fig:sflow_distance}, we plot the minimum distance
+Figure~\ref{fig:sflow_phase_diagram}, we plot the minimum distance
 between the vesicles as a function of time for various Hamaker
@@
 correspond to Hamaker constants that are sufficiently large to form a
-doublet.  Figure~\ref{fig:sflow_phase_diagram} indicates whether a
-doublet with reduced area $\Delta A = 0.9$ is formed (blue) or not (red)
-for a variety of shear rates, Hamaker constants, and at two different
-separation distances.  The plot includes a line of best fit between the
-stable and unstable regions.  Since the transition is linear, this
-indicates that a dimensionless number involving the ratio of the Hamaker
-constant could be used to determine if a doublet forms or not.
+doublet.
 
 \begin{figure}
-  \includegraphics[height=0.27\textwidth]{figs/shear_adR4em1Chi5em1_ra090.pdf}
-  \caption{\label{fig:sflow_distance} {\em Left}: The distance between a
-  pair of vesicles in a planar shear flow with shear rate $\chi=0.5$,
+  \includegraphics[height=0.35\textwidth]{figs/shear_adR4em1Chi1e0_ra-090.pdf}
+  \includegraphics[height=0.35\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
+  \caption{\label{fig:sflow_phase_diagram} {\em Left}: Distance between
+  a pair of vesicles in a planar shear flow with shear rate $\chi=0.5$,
   and separation distance $\delta = 0.4$.  The different lines
   correspond to a linear spacing of Hamaker constants ranging from
-  $\mathcal{H}=0.1$ and $\mathcal{H}=1.0$.  {\em Right}:
-  \todo[inline]{frequency of the oscillation}}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[height=0.37\textwidth]{figs/shear_adR1em1_ra090_phaseDiagram.pdf}
-  \includegraphics[height=0.37\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
-  \caption{\label{fig:sflow_phase_diagram} Phase diagram of vesicle
-  hydrodynamics in a shear flow with $\delta = 0.1$ (left) and $\delta =
-  0.4$ (right) with reduced area $\Delta A = 0.9$. The critical Hamaker
-  constant $\mathcal{H}$ for binding of two vesicles in a shear flow
-  depends on the shear rate $\chi$.  For a doublet to form, lower
-  separation distances require a stronger Hamaker constants at a given
-  shear rate.  The stability limit appears to be linear, indicating that
-  there is potentially a stability criteria that depends on a
-  dimensionless number involving the ratio of the Hamaker constant and
-  shear rate.}
+  $\mathcal{H}=0.1$ and $\mathcal{H}=1.0$.  {\em Right}: Phase diagram
+  of vesicle hydrodynamics in a shear flow.  At a fixed reduced area
+  $\Delta A=0.90$ and $\delta = 0.4$, the critical Hamaker constant
+  $\mathcal{H}$ for binding of two vesicles in a shear flow depends on
+  the shear rate $\chi$.}
 \end{figure}
@@
 $\phi$ is the area fraction of vesicles, $\tau$ is the stress due to the
-vesicles, $\langle \cdot \rangle$ is the spatial average, $|\omega|$ is
-the total area of both vesicles, and $\xxi$ is the traction as defined
-in equation~\eqref{eqn:traction}.  In
-Figure~\ref{fig:shearIntrinsicViscosity}(a), we compare the intrinsic
-viscosity of a single tank-treading vesicle to a doublet.  To validate
-our simulations, we superimpose (black marks) the intrinsic viscosity
-calculated by Ghigliotti {\em et
+vesicles, $\langle \cdot \rangle$ is the spatial average, and $\xxi$ is
+the traction as defined in equation~\eqref{eqn:traction}.  In the left
+plot of Figure~\ref{fig:shearIntrinsicViscosity}, we compare the
+intrinsic viscosity of a single tank-treading vesicle to a doublet.  To
+validate our simulations, we superimpose (black marks) the intrinsic
+viscosity calculated by Ghigliotti {\em et
 al.}~\cite{GhigliottiBibenMisbah2010_JFM}.  The presence of the doublet
-slightly increases the intrinsic viscosity at all the reduced areas.  To
-further characterize the effect of adhesion, in
-Figure~\ref{fig:shearIntrinsicViscosity}(b) we decompose the intrinsic
-viscosity into the contributions from the bending and tension (blue),
-and the contribution from the adhesion (red).  We also superimpose the
-intrinsic viscosity of a single tank-treading vesicle (dashed curve) to
-demonstrate that the bending and tension of the doublet behave
-similarly, but not identically, to a dilute suspensions of non-adhering
-tank-treading vesicles.  We see that the effect of the adhesion on the
-intrinsic viscosity is largest for vesicles with small reduced areas.
-
-\begin{figure}[]
-  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
-  \subfigimg[width=\linewidth]{(a)}{figs/doublet_decomp.pdf} &
-  \subfigimg[width=\linewidth]{(b)}{figs/doublet_decomp.pdf}
-  \end{tabular}
-%  \centering
-%  \includegraphics[width=0.45\textwidth]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
-%  \includegraphics[width=0.45\textwidth]{figs/doublet_decomp.pdf}
-  \caption{\label{fig:shearIntrinsicViscosity} (a) The intrinsic
+significantly increases the intrinsic viscosity at all the reduced
+areas.  To further characterize the effect of adhesion, in the right
+plot of Figure~\ref{fig:shearIntrinsicViscosity} we decompose the
+intrinsic viscosity into the contributions from the bending and tension
+(blue), and the contribution from the adhesion (red).  We also
+superimpose twice the intrinsic viscosity of a single tank-treading
+vesicle (dashed curve) to demonstrate that the bending and tension of
+the doublet behave similarly, but not identically, to a dilute
+suspensions of non-adhering tank-treading vesicles.  We see that the
+effect of the adhesion on the intrinsic viscosity is largest for
+vesicles with small reduced areas.
+
+\begin{figure}[htp]
+  \centering
+  \includegraphics[width=0.45\textwidth]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
+  \includegraphics[width=0.45\textwidth]{figs/doublet_decomp.pdf}
+  \caption{\label{fig:shearIntrinsicViscosity} {\em Left}: The intrinsic
   viscosity of a tank-treading vesicle (blue) and a doublet (red).  The
@@
   denote intrinsic viscosity values computed by Ghigliotti {\em et
-  al.}~\cite{GhigliottiBibenMisbah2010_JFM} (cf.~Figure 5).  (b) The
-  decomposition of the intrinsic viscosity into the contributions for
-  the bending and tension (blue) of the vesicles, and the contribution
-  from the vesicle adhesion (red).  Also included is the intrinsic
-  viscosity of a single tank-treading vesicle (dashed black line).}
+  al.}~\cite{GhigliottiBibenMisbah2010_JFM} (cf.~Figure 5).  {\em
+  Right}: The decomposition of the intrinsic viscosity into the
+  contributions for the bending and tension (blue) of the vesicles, and
+  the contribution from the vesicle adhesion (red).  Also included is
+  twice the intrinsic viscosity of a single tank-treading vesicle
+  (dashed black line).}
 \end{figure}

### 2019-06-21 vesicle_code/examples/relaxation1Ves.m

@@ -6,9 +6,10 @@ fprintf('First-order semi-implicit time stepping.\n');
 % Physics parameters
 prams.N = 256;               % points per vesicle
 prams.nv = 1;               % number of vesicles
-prams.T = 100;               % time horizon (two tumbling)
+prams.T = 30;               % time horizon (two tumbling)
 prams.m = 1000;              % number of time steps
-prams.kappa = 1e-2;         % bending coefficient
+prams.kappa = 1e-4;         % bending coefficient
+prams.kappa = 1e-2;
 prams.viscCont = 1;         % viscosity contrast
 options.farField = 'relaxation'; % background velocity
 options.order = 1;          % time stepping order
@@ -51,7 +52,7 @@ options.expForce = true;
 
 % Plot on-the-fly
 options.usePlot = true;
-options.axis = [-3 3 -3.5 3.5];
+options.axis = [-5 5 -5 5];
 options.track = false;
 % Save vesicle information and create a log file
 options.logFile = 'output/relaxation1Ves.log';
@@ -68,7 +69,7 @@ options.errorFile = 'output/relaxation1VesError.bin';
 % Also add src to path
 
 oc = curve;
-ra = 0.95;
+ra = 0.65;
 %scale = sqrt(ra);
 scale = 1;
 X = oc.initConfig(prams.N,...
@@ -78,7 +79,7 @@ X = oc.initConfig(prams.N,...
     'scale',scale);
 % Initial configuration of reduce area 0.65 and aligned
 ymax = max(X(end/2+1:end));
-X = X/ymax*3; % make maximum y value equal to 3
+X = X/ymax*3.3; % make maximum y value equal to 3
 
 
 %theta = (0:prams.N-1)'*2*pi/prams.N;

### 2019-06-21 vesicle_code/docs/adhesion/revisions/reviewer2.tex

@@
 \begin{itemize}
-  \item rebuttal
+  \item We thank the reviewer for this observation.  We increased the
+    parameter space of the phase diagram, and it does appear that there
+    is a linear relationship.
+  \item We have superimposed a straight line to show the transition
+    between the two doublet and unbounded configurations.
+  \item We also have repeated the phase diagram, but with a smaller
+    separation distance.  With this new separation distance, the
+    transition between the two regions appears to also be linear.
 \end{itemize}
@@
 \begin{itemize}
-  \item rebuttal
+  \item We have removed this example from the manuscript.  Instead, we
+    mention that future work includes a suspension of many vesicles.
 \end{itemize}

### 2019-06-21 vesicle_code/docs/adhesion/adhesion.tex
fixed Fig 14
fixed intrinsic viscosity plot

--- 2019-06-20 vesicle_code/docs/adhesion/adhesion.tex
@@
   \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
-  \subfigimg[width=\linewidth]{(a)}{figs/doublet_decomp.pdf} &
+  \subfigimg[width=\linewidth]{(a)}{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf} &
   \subfigimg[width=\linewidth]{(b)}{figs/doublet_decomp.pdf}
@@
   decomposition of the intrinsic viscosity into the contributions for
-  the bending and tension (blue) of the vesicles, and the contribution
-  from the vesicle adhesion (red).  Also included is the intrinsic
-  viscosity of a single tank-treading vesicle (dashed black line).}
+  the bending and tension (black) of the vesicles, and the contribution
+  from the vesicle adhesion (green).  Also included is the intrinsic
+  viscosity of a single tank-treading vesicle (blue).}
 \end{figure}

### 2019-06-21 vesicle_code/docs/adhesion/adhesion.tex
fixed subfigure labelling

@@
 \begin{figure}[htp]
-  \begin{minipage}{0.31\textwidth}
-    \centering
-    \includegraphics[height=5cm,trim={0cm 0cm 2cm 0cm},clip]{figs/adhesionPotential.pdf}
-  \end{minipage}
-  \hfill
-  \begin{minipage}{0.31\textwidth}
-    \centering
-    \includegraphics[height=5cm]{figs/configCartoon.pdf}
-  \end{minipage}
-  \hfill
-  \begin{minipage}{0.31\textwidth}
-    \centering
-    \includegraphics[height=5cm,trim={3cm 0cm 2cm 0cm},clip]{figs/Adhesion_Force.png}
-  \end{minipage}
-  \caption{\label{fig:adhesionModel} {\em Left}: The adhesion potential
+  \begin{tabular}{@{}p{0.3\linewidth}@{\qquad}p{0.3\linewidth}@{\qquad}p{0.3\linewidth}@{}}
+  \subfigimg[height=\linewidth]{(a)}{figs/adhesionPotential.pdf} &
+  \subfigimg[height=\linewidth]{(b)}{figs/configCartoon.pdf} &
+  \subfigimg[height=\linewidth]{(c)}{figs/Adhesion_Force.png}
+  \end{tabular}
+%  \begin{minipage}{0.31\textwidth}
+%    \centering
+%    \includegraphics[height=5cm,trim={0cm 0cm 2cm 0cm},clip]{figs/adhesionPotential.pdf}
+%  \end{minipage}
+%  \hfill
+%  \begin{minipage}{0.31\textwidth}
+%    \centering
+%    \includegraphics[height=5cm]{figs/configCartoon.pdf}
+%  \end{minipage}
+%  \hfill
+%  \begin{minipage}{0.31\textwidth}
+%    \centering
+%    \includegraphics[height=5cm,trim={3cm 0cm 2cm 0cm},clip]{figs/Adhesion_Force.png}
+%  \end{minipage}
+  \caption{\label{fig:adhesionModel} (a) The adhesion potential
   $\phi(z)$ in equation~\eqref{eq:adhesion_potential}.  Distances less
   than $\delta$ are repulsive and distances greater than $\delta$ are
-  attractive.  {\em Center}: Each point on a vesicle is repelled or
-  attracted by all points on the other vesicles.  {\em Right}: The
-  resulting adhesive force is found by integrating over all points on
-  all other vesicles (equation~\eqref{eqn:adhesionForce}).  The color is
-  the dot product of the adhesion force with the vector joining the
-  vesicles.  Therefore, the green and yellow regions are repelled by the
-  other vesicle while the blue regions are attracted to the other
-  vesicle.}
+  attractive.  (b) Each point on a vesicle is repelled or attracted by
+  all points on the other vesicles.  (c) The resulting adhesive force is
+  found by integrating over all points on all other vesicles
+  (equation~\eqref{eqn:adhesionForce}).  The color is the dot product of
+  the adhesion force with the vector joining the vesicles.  Therefore,
+  the green and yellow regions are repelled by the other vesicle while
+  the blue regions are attracted to the other vesicle.}
 \end{figure}
@@
 membrane or a flat solid wall.  The characteristics of the
-L.-J.~potential are summarized in the left panel of
-Figure~\ref{fig:adhesionModel}: The adhesive force is zero at the
-equilibrium distance $z=\delta$.  For large distances ($z> \delta$) the
-adhesive potential is attractive while for small distances ($z <
-\delta$) the potential is repulsive to prevent physical contact.
+L.-J.~potential are summarized in Figure~\ref{fig:adhesionModel}(a): The
+adhesive force is zero at the equilibrium distance $z=\delta$.  For
+large distances ($z> \delta$) the adhesive potential is attractive while
+for small distances ($z < \delta$) the potential is repulsive to prevent
+physical contact.
 
@@
 \end{align}
-This summation of adhesive forces is illustrated in the middle panel of
-Figure~\ref{fig:adhesionModel}.  The right panel of
-Figure~\ref{fig:adhesionModel} is an example of the calculated adhesive
-force projected onto their center-of-mass vector. We notice that the
-adhesive force is repulsive in the contact region, while for the rest of
-the membranes there is an attractive force that acts to pull the two
-vesicles together. The summary of boundary integral formulation can be
-found in Appendix~\ref{sec:AppendixB}.
+This summation of adhesive forces is illustrated in
+Figure~\ref{fig:adhesionModel}(b).  Figure~\ref{fig:adhesionModel}(c) is
+an example of the calculated adhesive force projected onto their
+center-of-mass vector. We notice that the adhesive force is repulsive in
+the contact region, while for the rest of the membranes there is an
+attractive force that acts to pull the two vesicles together. The
+summary of boundary integral formulation can be found in
+Appendix~\ref{sec:AppendixB}.
 
@@
 \begin{figure}
-\includegraphics[keepaspectratio=true,scale=0.4]{figs/Dec13a_time_scaling01.png}
-\includegraphics[keepaspectratio=true,scale=0.4]{figs/Dec13a_time_scaling02.png}
+  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
+  \subfigimg[width=\linewidth]{(a)}{figs/Dec13a_time_scaling01.png} &
+  \subfigimg[width=\linewidth]{(b)}{figs/Dec13a_time_scaling02.png}
+  \end{tabular}
+%\includegraphics[keepaspectratio=true,scale=0.4]{figs/Dec13a_time_scaling01.png}
+%\includegraphics[keepaspectratio=true,scale=0.4]{figs/Dec13a_time_scaling02.png}
 \caption{\label{fig:qflow00} Scaling of the time it takes for two
-  vesicles to reach equilibrium. {\em Left}: Scaling with respect to
-  $\delta$ with $\mathcal{H}=0.1$.  {\em Right}: Scaling with respect to
-  $\mathcal{H}$ with
-  $\delta = 0.4$. Arrows indicate the time by when the equilibrium is
+vesicles to reach equilibrium. (a) Scaling with respect to $\delta$ with
+$\mathcal{H}=0.1$. (b) Scaling with respect to $\mathcal{H}$ with
+$\delta = 0.4$. The arrows indicate the time by when the equilibrium is
 reached within $1\%$.}
@@
 flow.  Starting with two vesicles at a distance of twice the vesicle
-radius, the long-range attraction pulls the vesicles together.  The left
-plot of Figure~\ref{fig:qflow00} shows the scaled adhesion energy versus
-time with $\mathcal{H}=0.1$ and three values of $\delta$ as labeled.
+radius, the long-range attraction pulls the vesicles together.
+Figure~\ref{fig:qflow00}(a) shows the scaled adhesion energy versus time
+with $\mathcal{H}=0.1$ and three values of $\delta$ as labeled.
 Adhesion energy reaches minimum at equilibrium, and the scaled $E_{adh}$
@@
 The scaling with respect to adhesion strength $\mathcal{H}$ is
-illustrated in the right plot of Figure~\ref{fig:qflow00}, where $\delta
-= 0.4$ and $\mathcal{H}$ varies from $0.1$ to $0.5$ as labeled.  Again
-the arrows indicate the times when the equilibrium is reached within
-$1\%$:
+illustrated in Figure~\ref{fig:qflow00}(b), where $\delta = 0.4$ and
+$\mathcal{H}$ varies from $0.1$ to $0.5$ as labeled.  Again the arrows
+indicate the times when the equilibrium is reached within $1\%$:
 \begin{align*}
@@
    \includegraphics[keepaspectratio=true,scale=0.45]{figs/Dec18_vesicle_shape_vs_rA_composite.png}
-  \caption{\label{fig:Dec18_vesicle_shape} Equilibrium configurations of
-  a doublet of identical vesicles under adhesion in a quiescent flow at
-  three values of $\Delta A$.  The vesicle reduced areas of $\Delta
-  A=0.95$, $0.75$, and $0.6$ are labeled.  The vesicle length is fixed at $2\pi$, the
-  dimensionless bending rigidity modulus is $\kappa_b=1$, the Hamaker
-  constant is $\mathcal{H}=5$, and the separation distance is
-  $\delta=0.2$.  {\em Left}:  The color coding is the
-  tension along the vesicle.  The overall equilibrium shapes of two
-  vesicles under adhesive interactions vary with the reduced area.  {\em
-  Right}: The membrane shapes in the contact region. The color coding is the adhesive force
-  projected along the center-of-mass vector.} 
+  \caption{\label{fig:Dec18_vesicle_shape} The equilibrium
+  configurations of a doublet of identical vesicles under adhesion in a
+  quiescent flow at three values of $\Delta A$.  The vesicle reduced
+  areas of $\Delta A=0.95$, $0.75$, and $0.6$ are labeled.  The vesicle
+  length is fixed at $2\pi$, the dimensionless bending rigidity modulus
+  is $\kappa_b=1$, the Hamaker constant is $\mathcal{H}=5$, and the
+  separation distance is $\delta=0.2$.  The color coding is the tension
+  along the vesicle.  The overall equilibrium shapes of two vesicles
+  under adhesive interactions vary with the reduced area.  The right
+  figure shows the  membrane shapes in the contact region. The color
+  coding is the adhesive force projected along the center-of-mass
+  vector.} 
 \end{figure}
@@
 The right plot of Figure~\ref{fig:Dec18_vesicle_shape} is a zoom (not
-to-scale) on the membranes in the contact region, where the membranes
+to-scale) of the membranes in the contact region, where the membranes
 are not perfectly flat at all three values of reduced area: We observe
@@
 \begin{figure}
-\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_Ebleft_Eadhright_vs_rA_adR0p2_adS502.jpeg}
-\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_EbEadh_vs_rA_adR0p2_adS502.jpeg}
-  \caption{\label{fig:Dec18_vesicle_equilibrium1}   {\em Left}: The
-  total bending energy (solid curve) and adhesion energy (dash-dotted
-  curve) plotted against the reduced area $\Delta A$. {\em Right}: The
-  sum of two energies plotted against reduced area $\Delta A$. The two
-  vesicles in the doublet are of the same length and reduced area.  The
-  Hamaker constant is $\mathcal{H} = 5$ and the separation distance is
-  $\delta = 0.2$.}
+  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
+  \subfigimg[width=\linewidth]{(a)}{figs/Dec18_Ebleft_Eadhright_vs_rA_adR0p2_adS502.jpeg} &
+  \subfigimg[width=\linewidth]{(b)}{figs/Dec18_EbEadh_vs_rA_adR0p2_adS502.jpeg}
+  \end{tabular}
+%\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_Ebleft_Eadhright_vs_rA_adR0p2_adS502.jpeg}
+%\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_EbEadh_vs_rA_adR0p2_adS502.jpeg}
+  \caption{\label{fig:Dec18_vesicle_equilibrium1}   (a) The total
+  bending energy (solid curve) and adhesion energy (dash-dotted curve)
+  plotted against the reduced area $\Delta A$. (b) The sum of two
+  energies plotted against reduced area $\Delta A$. The two vesicles in
+  the doublet are of the same length and reduced area.  The Hamaker
+  constant is $\mathcal{H} = 5$ and the separation distance is $\delta =
+  0.2$.}
 \end{figure}
 
-The left plot of Figure~\ref{fig:Dec18_vesicle_equilibrium1} shows the
-total bending energy and adhesion energy as a function of the reduced
-area. The smaller the reduced area, the more vesicle area is available
-for deformation and thus the bending energy is higher.  In contrast, the
+Figure~\ref{fig:Dec18_vesicle_equilibrium1}(a) shows the total bending
+energy and adhesion energy as a function of the reduced area. The
+smaller the reduced area, the more vesicle area is available for
+deformation and thus the bending energy is higher.  In contrast, the
 total adhesion energy becomes more negative as the reduced area
-decreases.  The sum of two energies is plotted in the right plot of
-Figure~\ref{fig:Dec18_vesicle_equilibrium1}, where a local minimum in
+decreases.  The sum of two energies is plotted in
+Figure~\ref{fig:Dec18_vesicle_equilibrium1}(b), where a local minimum in
 the total energy is found around $\Delta A = 0.85$.
@@
 \begin{figure}
-\includegraphics[keepaspectratio=true,scale=0.18]{figs/Dec18_Eb_vs_sigma_rA0p9502.jpeg}
-\includegraphics[keepaspectratio=true,scale=0.18]{figs/Dec18_Eadh_vs_sigma_rA0p9502.jpeg}
-  \caption{\label{fig:Dec18_equilibrium} 
-  The total bending energy ({\em left}) and adhesion energy ({\em
-  right}) of a vesicle doublet at equilibrium versus the adhesion
-  strength $\mathcal{H}$.  The two identical vesicles in the doublet
-  have a length of $2\pi$ and a reduced area of $\Delta A=0.95$, with
-  separation distance $\delta = 0.2$ (triangles), $0.3$ (crosses), and
-  $0.4$ (circles).}
+  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
+  \subfigimg[width=\linewidth]{(a)}{figs/Dec18_Eb_vs_sigma_rA0p9502.jpeg} &
+  \subfigimg[width=\linewidth]{(b)}{figs/Dec18_Eadh_vs_sigma_rA0p9502.jpeg}
+  \end{tabular}
+%\includegraphics[keepaspectratio=true,scale=0.18]{figs/Dec18_Eb_vs_sigma_rA0p9502.jpeg}
+%\includegraphics[keepaspectratio=true,scale=0.18]{figs/Dec18_Eadh_vs_sigma_rA0p9502.jpeg}
+  \caption{\label{fig:Dec18_equilibrium} The total bending energy (a)
+  and adhesion energy (b) of a vesicle doublet at equilibrium versus the
+  adhesion strength $\mathcal{H}$.  The two identical vesicles in the
+  doublet have a length of $2\pi$ and a reduced area of $\Delta A=0.95$,
+  with separation distance $\delta = 0.2$ (triangles), $0.3$ (crosses),
+  and $0.4$ (circles).}
 \end{figure}
@@
 Both vesicles have a length of $2\pi$ and a reduced area of $\Delta A =
-0.95$.  The total bending (left) and adhesion (right) energies at
-equilibrium are plotted against $\mathcal{H}$ for three values of the
-separation distance $\delta$.  We observe that for $\Delta A=0.95$ the
-equilibrium vesicle shape does not vary much with the adhesion strength
+0.95$.  The total bending (a) and adhesion (b) energies at equilibrium
+are plotted against $\mathcal{H}$ for three values of the separation
+distance $\delta$.  We observe that for $\Delta A=0.95$ the equilibrium
+vesicle shape does not vary much with the adhesion strength
 $\mathcal{H}$, while the total adhesion energy varies linearly with
@@
 fluid trap to measure the adhesion strength between two bound vesicle
-membranes, we propose the following experiment.  Beginning with
-two identical vesicles in an equilibrium configuration that form a
-doublet with a flat contact region
-(Figure~\ref{fig:Dec18_vesicle_shape}), we turn on the fluid trap with
-the stagnation point placed at the center of the vesicle doublet.
-Depending on the Hamaker constant, we expect that either the flow
-overcomes the adhesive force and the doublet is broken, or the adhesive
-force is sufficiently strong and the doublet reaches a stable stationary
-configuration.
+membranes, we propose the following experiment.  Beginning with two
+identical vesicles in an equilibrium configuration that form a doublet
+with a flat contact region (Figure~\ref{fig:Dec18_vesicle_shape}), we
+turn on the fluid trap with the stagnation point placed at the center of
+the vesicle doublet.  Depending on the Hamaker constant, we expect that
+either the flow overcomes the adhesive force and the doublet is broken,
+or the adhesive force is sufficiently strong and the doublet reaches a
+stable stationary configuration.
 
@@
 \begin{figure}[htp]
-   \includegraphics[width=0.25\textwidth]{figs/rotate1.pdf}
-   \hspace{20pt}
-   \includegraphics[width=0.25\textwidth]{figs/angleDefinition.pdf}
-   \hspace{20pt}
-   \includegraphics[width=0.25\textwidth]{figs/rotate2.pdf}
+  \begin{tabular}{@{}p{0.3\linewidth}@{\quad}p{0.3\linewidth}@{\quad}p{0.3\linewidth}@{}}
+  \subfigimg[width=\linewidth]{(a)}{figs/rotate1.pdf} &
+  \subfigimg[width=\linewidth]{(b)}{figs/angleDefinition.pdf} &
+  \subfigimg[width=\linewidth]{(c)}{figs/rotate2.pdf}
+  \end{tabular}
+%   \includegraphics[width=0.25\textwidth]{figs/rotate1.pdf}
+%   \hspace{20pt}
+%   \includegraphics[width=0.25\textwidth]{figs/angleDefinition.pdf}
+%   \hspace{20pt}
+%   \includegraphics[width=0.25\textwidth]{figs/rotate2.pdf}
    \caption{\label{fig:InclinationAngle} The definition of the
@@
 than the $\theta=\pi$ configuration in the left of
-Figure~\ref{fig:InclinationAngle}. This is because when $\theta=\pi$ the
-diverging flow is pulling the vesicles away from each other as shown in
-the illustration.  However, when the doublet inclination angle is fixed
-at $\theta=\pi/2$, the vesicle doublet stays intact if the adhesive
-force is strong enough to dominate the fluid drag.  However, it is
-possible that the diverging flow may overcome adhesion and break up the
-doublet.  It is also reasonable to expect a vesicle doublet to rotate
-from the less stable configuration $\theta=\pi$ to the more stable
-configuration $\theta=\pi/2$, so that the fluid flow is pushing them
-together rather than pulling them apart.
+Figure~\ref{fig:InclinationAngle}(a). This is because when $\theta=\pi$
+the diverging flow is pulling the vesicles away from each other as shown
+in the illustration.  However, when the doublet inclination angle is
+fixed at $\theta=\pi/2$, the vesicle doublet stays intact if the
+adhesive force is strong enough to dominate the fluid drag.  However, it
+is possible that the diverging flow may overcome adhesion and break up
+the doublet.  It is also reasonable to expect a vesicle doublet to
+rotate from the less stable configuration $\theta=\pi$ to the more
+stable configuration $\theta=\pi/2$, so that the fluid flow is pushing
+them together rather than pulling them apart.
 
@@
 
-In Figure~\ref{fig:extensionalInclinationAngle}, we plot the inclination
-angle of the doublet as a function of time for four different
-extensional rates (left) and the final inclination angle for all
-doublets that reach an equilibrium state (middle).  We observe that not
+In Figure~\ref{fig:extensionalInclinationAngle}(a), we plot the
+inclination angle of the doublet as a function of time for four
+different extensional rates,  and the final inclination angle for all
+doublets that reach an equilibrium state are in
+Figure~\ref{fig:extensionalInclinationAngle}(b).  We observe that not
 only do smaller extensional rates result in smaller inclination angles,
 but smaller reduced areas also result in smaller inclination angles.  We
-summarize the final inclination angle of the doublet in the right plot
-of Figure~\ref{fig:extensionalInclinationAngle}.  The size of the round
+summarize the final inclination angle of the doublet in
+Figure~\ref{fig:extensionalInclinationAngle}(c).  The size of the round
 dots are scaled to the final inclination angle as defined in
@@
 rates, the time horizon is insufficient for the doublet to reach an
-equilibrium state, and these simulations are marked with a square.  The
-right plot of Figure~\ref{fig:extensionalInclinationAngle} also
-summarizes the reduced areas and extensional rates that result in a
-bound vesicle doublet in a fluid trap: Parameter values with a blue mark
-result in a fluid trap and parameter values with a red mark result in
-vesicle separation.
+equilibrium state, and these simulations are marked with a square.
+Figure~\ref{fig:extensionalInclinationAngle}(c) also summarizes the
+reduced areas and extensional rates that result in a bound vesicle
+doublet in a fluid trap: Parameter values with a blue mark result in a
+fluid trap and parameter values with a red mark result in vesicle
+separation.
 
 \begin{figure}[htp]
-  \includegraphics[height=0.26\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
-  \includegraphics[height=0.26\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
-  \includegraphics[height=0.26\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
-  \caption{\label{fig:extensionalInclinationAngle} {\em Left}: The
-  inclination angle of a doublet formed by vesicles of reduced area
-  $\Delta A = 0.7$ in an extensional flow with an extensional rate
-  $\chi$.  {\em Middle}: The final inclination angle of doublets.  At
-  larger extensional rates, the doublet is broken by the flow.  {\em
-  Right}: A phase diagram of the long-time behavior of a fluid trap
-  formed by two adhering vesicles in an extensional flow.  Results are
-  not reported for some of the low extensional rates since the doublet
-  had not tilted to an equilibrium inclination angle for the given time
-  horizon.}
+  \begin{tabular}{@{}p{0.3\linewidth}@{\quad}p{0.3\linewidth}@{\quad}p{0.3\linewidth}@{}}
+  \subfigimg[width=\linewidth]{(a)}{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf} &
+  \subfigimg[width=\linewidth]{(b)}{figs/adR4em1adS7em1_finalInclinationAngle.pdf} &
+  \subfigimg[width=\linewidth]{(c)}{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
+  \end{tabular}
+%  \includegraphics[height=0.26\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
+%  \includegraphics[height=0.26\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
+%  \includegraphics[height=0.26\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
+  \caption{\label{fig:extensionalInclinationAngle} (a) The inclination
+  angle of a doublet formed by vesicles of reduced area $\Delta A = 0.7$
+  in an extensional flow with an extensional rate $\chi$.  (b) The final
+  inclination angle of doublets.  At larger extensional rates, the
+  doublet is broken by the flow.  (c) A phase diagram of the long-time
+  behavior of a fluid trap formed by two adhering vesicles in an
+  extensional flow.  Results are not reported for some of the low
+  extensional rates since the doublet had not tilted to an equilibrium
+  inclination angle for the given time horizon.}
 \end{figure}
@@
 separation distance to $\delta = 0.4$ and the vesicle reduced area to
-$\Delta A = 0.9$.  In the left plot of
-Figure~\ref{fig:sflow_distance}, we plot the minimum distance
+$\Delta A = 0.9$.  In
+Figure~\ref{fig:sflow_distance}(a), we plot the minimum distance
 between the vesicles as a function of time for various Hamaker
@@
 correspond to Hamaker constants that are sufficiently large to form a
-doublet.  We also plot the time required for the doublet to make a
-complete revolution at a variety of Hamaker constants and shear rates.
-For a fixed Hamaker contant, as expected, the period decreases for
-larger shear rates.  In addition, for a fixed shear rate, the period
-decreases as the Hamaker constant increases, but the period eventually
-plateaus.  More interesting, for larger shear rates, the period of the
-doublet appears to be independent of the Hamaker constant.
+doublet.  In Figure~\ref{fig:sflow_distance}(b), we plot the time
+required for the doublet to make a complete revolution at a variety of
+Hamaker constants and shear rates.  For a fixed Hamaker contant, as
+expected, the period decreases for larger shear rates.  In addition, for
+a fixed shear rate, the period decreases as the Hamaker constant
+increases, but the period eventually plateaus.
 
@@
 \begin{figure}
-  \includegraphics[height=0.34\textwidth]{figs/shear_adR4em1Chi5em1_ra090.pdf}
-  \includegraphics[height=0.34\textwidth]{figs/shear_adR4em1Chi5em1_ra090_period.pdf}
-  \caption{\label{fig:sflow_distance} {\em Left}: The distance between a
-  pair of vesicles in a planar shear flow with shear rate $\chi=0.5$,
-  and separation distance $\delta = 0.4$.  The different lines
-  correspond to a linear spacing of Hamaker constants ranging from
-  $\mathcal{H}=0.1$ and $\mathcal{H}=1.0$.  {\em Right}: The time
-  required for a doublet to complete a single rotation.  The reduced
-  area is $\Delta A = 0.90$ and the separation distance is $\delta =
-  0.4$.  The different lines correspond to different shear rates.}
+  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
+  \subfigimg[width=\linewidth]{(a)}{figs/shear_adR4em1Chi5em1_ra090.pdf} &
+  \subfigimg[width=\linewidth]{(b)}{figs/shear_adR4em1Chi5em1_ra090_period.pdf}
+  \end{tabular}
+%  \includegraphics[height=0.34\textwidth]{figs/shear_adR4em1Chi5em1_ra090.pdf}
+%  \includegraphics[height=0.34\textwidth]{figs/shear_adR4em1Chi5em1_ra090_period.pdf}
+  \caption{\label{fig:sflow_distance} (a) The distance between a pair of
+  vesicles in a planar shear flow with shear rate $\chi=0.5$, and
+  separation distance $\delta = 0.4$.  The different lines correspond to
+  a linear spacing of Hamaker constants ranging from $\mathcal{H}=0.1$
+  and $\mathcal{H}=1.0$.  (b) The time required for a doublet to
+  complete a single rotation.  The reduced area is $\Delta A = 0.90$ and
+  the separation distance is $\delta = 0.4$.  The different lines
+  correspond to different shear rates.}
 \end{figure}
@@
 \begin{figure}
-  \centering
-  \includegraphics[height=0.37\textwidth]{figs/shear_adR1em1_ra090_phaseDiagram.pdf}
-  \includegraphics[height=0.37\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
+  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
+  \subfigimg[width=\linewidth]{(a)}{figs/shear_adR1em1_ra090_phaseDiagram.pdf} &
+  \subfigimg[width=\linewidth]{(b)}{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
+  \end{tabular}
+%  \centering
+%  \includegraphics[height=0.37\textwidth]{figs/shear_adR1em1_ra090_phaseDiagram.pdf}
+%  \includegraphics[height=0.37\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
   \caption{\label{fig:sflow_phase_diagram} Phase diagram of vesicle
-  hydrodynamics in a shear flow with $\delta = 0.1$ (left) and $\delta =
-  0.4$ (right) with reduced area $\Delta A = 0.9$. The critical Hamaker
+  hydrodynamics in a shear flow with $\delta = 0.1$ (a) and $\delta =
+  0.4$ (b) with reduced area $\Delta A = 0.9$. The critical Hamaker
   constant $\mathcal{H}$ for binding of two vesicles in a shear flow

### 2019-06-25 vesicle_code/docs/adhesion/adhesion.tex
worked on revisions

@@
 correspond to Hamaker constants that are sufficiently large to form a
-doublet.  In Figure~\ref{fig:sflow_distance}(b), we plot the time
-required for the doublet to make a complete revolution at a variety of
-Hamaker constants and shear rates.  For a fixed Hamaker contant, as
-expected, the period decreases for larger shear rates.  In addition, for
-a fixed shear rate, the period decreases as the Hamaker constant
-increases, but the period eventually plateaus.
+doublet.
+
+In Figure~\ref{fig:sflow_distance}(b), we plot the time required for the
+doublet to make a complete revolution at a variety of Hamaker constants
+and shear rates.  For a fixed Hamaker constant, as expected, the period
+decreases for larger shear rates.  In addition, for a fixed shear rate,
+the period decreases as the Hamaker constant increases, but the period
+eventually plateaus.  The dynamics of these doublet have similar
+behavior to a single rigid body undergoing a Jeffery orbit in a shear
+flow.  Therefore, we define the effective aspect ratio
+$\lambda_{\mathrm{eff}}$ which satisfies
+\begin{align*}
+  \frac{2\pi}{\chi}\left(\lambda + \lambda^{-1} \right) = p,
+\end{align*}
+where $p$ is the period of the doublet.  The effective aspect ratio is
+the aspect ratio of an ellipse in a shear flow that is undergoing a
+Jeffery orbit with period $p$.  For the Hamaker constant $\mathcal{H} =
+2$, the shear rates, periods, and effective aspect ratio are summarized
+in Table~\ref{tbl:aspectRatio}.  Since the effective aspect ratio is
+comparable for all three shear rates, this indicates that the dynamics
+of a vesicle doublet in a shear flow resembles a rigid body undergoing a
+Jeffery orbit.
+\begin{table}[htp]
+  \begin{tabular}{>{\centering\arraybackslash}p{2cm}
+>{\centering\arraybackslash}p{2cm}
+>{\centering\arraybackslash}p{2cm}}
+  $\chi$ & $p$ & $\lambda_{\mathrm{eff}}$ \\
+  \hline
+  0.50 & 38.06 & 2.92 \\
+  0.75 & 24.81 & 2.85 \\
+  1.00 & 19.47 & 3.00 
+\end{tabular}
+\caption{\label{tbl:aspectRatio} The shear rate, period, and effective
+aspect ratio of a vesicle doublet with reduced area $\Delta A = 0.9$,
+Hamaker constant $\mathcal{H} = 2$, and separation distance $\delta =
+0.4$.  The effective aspect ratios are comparable for all three shear
+rates.}
+\end{table}
 

### 2019-06-25 vesicle_code/docs/adhesion/revisions/reviewer2.tex
worked on revisions

@@
 \begin{itemize}
-  \item rebuttal
+  \item We now report the period of the doublets at three different
+    shear rates and at a variety of Hamaker constants.
+
+  \item For each of the shear rates and the largest Hamaker constant we
+    consider, we compute an effective aspect ratio which is the aspect
+    ratio of a rigid body ellipse that would undergo the same period in
+    the same shear flow.  The results indicate that the effective aspect
+    ratio is independent of the shear rate, and this suggests that the
+    dynamics of the doublet has similar properties to a rigid body
+    undergoing a Jeffery orbit. 
 \end{itemize}

### 2019-07-09 vesicle_code/examples/output/makeImages.m
worked on Figure 12 (left)

@@ -5,9 +5,10 @@ options.savefig = false;
 irate = 10; % controls the speed of the visualization
 
 if 0
-  file = 'extensional2VesData.bin';
+%  file = 'extensional2VesData.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves_rotated/adR4em1adS7em1Chi7em2_ra070/extensional2VesData.bin';
-  ax = [-2 2 -2 2];
+  file = '~/projects/brinkman/vesicle_code/results/yuan_runs/june_28_2019/extensional2VesData75be.bin';
+  ax = 2*[-2 2 -2 2];
   options.confined = false;
 end
 if 0
@@ -59,7 +60,7 @@ if 0
 end
 if 1
 %  file = 'shear2VesAData.bin';
-  file = '~/projects/brinkman/vesicle_code/results/shear2Ves/adR4em1adS1p9e0Chi7p5em1_ra090/shear2VesData.bin';
+  file = '~/projects/brinkman/vesicle_code/results/shear2Ves/adR4em1adS2p3e0Chi5em1_ra090/shear2VesData.bin';
   ax = [-10 10 -3 3];
   options.confined = false;
 end
@@ -97,10 +98,9 @@ for k = istart:irate:iend
     plot(vec1,vec2,'r','linewidth',3)
     hold on;
     plot(vec1(1,:),vec2(1,:),'b.','markersize',20)
-    ar = 1;
-    plot(ar*cos(linspace(0,2*pi,100)),ar*2.9197*sin(linspace(0,2*pi,100)),'b--')
-    axis equal
-    pause
+%    ar = 1;
+%    plot(ar*cos(linspace(0,2*pi,100)),ar*2.9197*sin(linspace(0,2*pi,100)),'b--')
+%    pause
     if options.confined
       vec1 = [wallx(:,:);wallx(1,:)];
       vec2 = [wally(:,:);wally(1,:)];

### 2019-07-09 vesicle_code/docs/adhesion/adhesion.tex
worked on Figure 12 (left)
added extensional plots

@@
 \label{sec:eflow}
+
+\begin{figure}[htp]
+  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+    {figs/extensional_displacement0_adS7em1_image01.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+    {figs/extensional_displacement0_adS7em1_image02.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+    {figs/extensional_displacement0_adS7em1_image03.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+    {figs/extensional_displacement0_adS7em1_image04.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+    {figs/extensional_displacement0_adS7em1_image05.png} \\
+
+  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+    {figs/extensional_displacement2em2_adS7em1_image01.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+    {figs/extensional_displacement2em2_adS7em1_image02.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+    {figs/extensional_displacement2em2_adS7em1_image03.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+    {figs/extensional_displacement2em2_adS7em1_image04.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+    {figs/extensional_displacement2em2_adS7em1_image05.png} \\
+
+  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+    {figs/extensional_displacement1em1_adS7em1_image01.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+    {figs/extensional_displacement1em1_adS7em1_image02.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+    {figs/extensional_displacement1em1_adS7em1_image03.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+    {figs/extensional_displacement1em1_adS7em1_image04.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+    {figs/extensional_displacement1em1_adS7em1_image05.png} \\
+
+  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+    {figs/extensional_displacement1em1_adS6em1_image01.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+    {figs/extensional_displacement1em1_adS6em1_image02.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+    {figs/extensional_displacement1em1_adS6em1_image03.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+    {figs/extensional_displacement1em1_adS6em1_image04.png}
+  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+    {figs/extensional_displacement1em1_adS6em1_image05.png}
+
+  \caption{\label{fig:extensionalNonsymmetric} }
+  \end{figure}
+
 The hydrodynamics of a single vesicle in an extensional flow has
@@
 \end{tabular}
+\todo[inline]{Update these values with new periods.  Maybe need to
+consider more than one Hamaker constant}
 \caption{\label{tbl:aspectRatio} The shear rate, period, and effective

### 2019-07-09 vesicle_code/examples/output/makeImages.m
updated font size in new figure 6

@@ -60,7 +60,7 @@ if 0
 end
 if 1
 %  file = 'shear2VesAData.bin';
-  file = '~/projects/brinkman/vesicle_code/results/shear2Ves/adR4em1adS3e0Chi5em1_ra090/shear2VesData.bin';
+  file = '~/projects/brinkman/vesicle_code/results/shear2Ves/adR4em1adS3e0Chi7p5em1_ra090/shear2VesData.bin';
   ax = [-3 3 -3 3];
   options.confined = false;
 end

### 2019-07-09 vesicle_code/docs/adhesion/adhesion.tex
updated font size in new figure 6
working on shear revisions

@@
 \section{Governing Equations \label{sec:ge}}
-We consider a suspension of locally inextensible vesicles in an unbounded
-two-dimensional viscous fluid.  For simplicity, we assume the fluid
-viscosity both inside and outside the vesicles is the same; however,
-incorporating viscosity contrast is rather straightforward in our
-numerical algorithm.  
-While we focus on a vesicle doublet suspension for the rest of the paper, here we provide the most general formulation for multiple vesicles interacting with
-each other through both hydrodynamic and adhesive forces.
-Individual vesicles are denoted as $\gamma_j$,
-$j=1,\ldots,M$, and they are parameterized in arclength as $\xx_j(s,t)$.
-The union of all vesicles is denoted by $\gamma$.  Given a background
-velocity $\uu_\infty$, the governing (dimensionless) equations are
+We consider a suspension of locally inextensible vesicles in an
+unbounded two-dimensional viscous fluid.  For simplicity, we assume the
+fluid viscosity both inside and outside the vesicles is the same;
+however, incorporating viscosity contrast is rather straightforward in
+our numerical algorithm.  While we focus on a vesicle doublet suspension
+for the rest of the paper, here we provide the most general formulation
+for multiple vesicles interacting with each other through both
+hydrodynamic and adhesive forces.  Individual vesicles are denoted as
+$\gamma_j$, $j=1,\ldots,M$, and they are parameterized in arclength as
+$\xx_j(s,t)$.  The union of all vesicles is denoted by $\gamma$.  Given
+a background velocity $\uu_\infty$, the governing (dimensionless)
+equations are
 \begin{equation}
@@
 \label{sec:qflow} 
-We consider two identical vesicles
-suspended in a quiescent flow.  Without any external forcing such as an
-imposed electric field or a fluid flow in the far-field, the long-range
-attraction pulls the vesicles together until their separation distance
-is close to $\delta$. The L.-J.~type potential prohibits physical
-contact between the two membranes and instead keeps them close to the
-separation distance $\delta$.  In
-Section~\ref{subsec:qflow_draining_times}, we compute the expected time
-for the vesicles to reach an equilibrium configuration and compare the
-analysis with numerical simulations.  In
+We consider two identical vesicles suspended in a quiescent flow.
+Without any external forcing such as an imposed electric field or a
+fluid flow in the far-field, the long-range attraction pulls the
+vesicles together until their separation distance is close to $\delta$.
+The L.-J.~type potential prohibits physical contact between the two
+membranes and instead keeps them close to the separation distance
+$\delta$.  In Section~\ref{subsec:qflow_draining_times}, we compute the
+expected time for the vesicles to reach an equilibrium configuration and
+compare the analysis with numerical simulations.  In
 Section~\ref{subsec:qflow_adhesion_parameters}, we characterize the
@@
 $\delta$, Hamaker constant $\mathcal{H}$, shear rate $\chi$, and reduced
-area $\Delta A$.  
-At all reduced areas, the vesicles have a length of
+area $\Delta A$.  At all reduced areas, the vesicles have a length of
 $2\pi$ to be consistent with simulations in previous sections.
 
-Figure~\ref{fig:doublet090} shows snapshots of two vesicles
+Figures~\ref{fig:doublet090-weakAdhesion}
+and~\ref{fig:doublet090-strongAdhesion} show snapshots of two vesicles
 that have formed a doublet and the color coding is the tension along the
@@
 0.9$, shear rate $\chi = 0.5$, separation distance $\delta = 0.4$, and
-Hamaker constant $\mathcal{H} = 0.7$.  The vesicles in the doublet move
-in tandem rather than performing the tank-treading motion that is
-observed in the absence of adhesion.  Similar to the quiescent example,
-the membrane tension is negative in the contact region indicating that
-the membrane is being compressed when the adhesive force is strongest.
+Hamaker constant $\mathcal{H} = 0.7$
+(Figure~\ref{fig:doublet090-weakAdhesion}) and $\mathcal{H} = 2.1$
+(Figure~\ref{fig:doublet090-strongAdhesion}).  The vesicles in the
+doublet move in tandem rather than performing the tank-treading motion
+that is observed in the absence of adhesion.  Similar to the quiescent
+example, the membrane tension is negative in the contact region
+indicating that the membrane is being compressed when the adhesive force
+is strongest.
 
@@
   \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image08.png}
-  \caption{\label{fig:doublet090} The formation of a doublet in a shear
-  flow.  The reduced area is $\Delta A = 0.9$, the Hamaker constant is
-  $\mathcal{H}=0.7$, the separation distance is $\delta = 0.4$, and the
-  shear rate is $\chi=0.5$.}
+  \caption{\label{fig:doublet090-weakAdhesion} The formation of a
+  doublet in a shear flow.  The reduced area is $\Delta A = 0.9$, the
+  Hamaker constant is $\mathcal{H}=0.7$, the separation distance is
+  $\delta = 0.4$, and the shear rate is $\chi=0.5$.}
+\end{figure}
+
+\begin{figure}[htp]
+  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image01.png}
+  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image02.png}
+  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image03.png}
+  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image04.png}
+  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image05.png}
+  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image06.png}
+  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image07.png}
+  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image08.png}
+  \caption{\label{fig:doublet090-strongAdhesion} The formation of a
+  doublet in a shear flow.  The reduced area is $\Delta A = 0.9$, the
+  Hamaker constant is $\mathcal{H}=2.1$, the separation distance is
+  $\delta = 0.4$, and the shear rate is $\chi=0.5$.}
 \end{figure}
@@
 separation distance to $\delta = 0.4$ and the vesicle reduced area to
-$\Delta A = 0.9$.  In
-Figure~\ref{fig:sflow_distance}(a), we plot the minimum distance
-between the vesicles as a function of time for various Hamaker
-constants.  The red curves correspond to Hamaker constants that are too
-small to bind the vesicles into a doublet, and the blue curves
+$\Delta A = 0.9$.  In Figure~\ref{fig:sflow_distance}(a), we plot the
+minimum distance between the vesicles as a function of time for various
+Hamaker constants.  The red curves correspond to Hamaker constants that
+are too small to bind the vesicles into a doublet, and the blue curves
 correspond to Hamaker constants that are sufficiently large to form a
@@
 \end{table}
+\todo[inline]{period results with $\delta$ = 0.1, 0.2, 0.3, 0.4 so that
+we can simply say how it affects the period}
 

### 2019-07-10 vesicle_code/docs/adhesion/adhesion.tex
working on shear revisions

@@
 that have formed a doublet and the color coding is the tension along the
-vesicle.  The two vesicles are identical with reduced area $\Delta A =
-0.9$, shear rate $\chi = 0.5$, separation distance $\delta = 0.4$, and
-Hamaker constant $\mathcal{H} = 0.7$
-(Figure~\ref{fig:doublet090-weakAdhesion}) and $\mathcal{H} = 2.1$
-(Figure~\ref{fig:doublet090-strongAdhesion}).  The vesicles in the
-doublet move in tandem rather than performing the tank-treading motion
-that is observed in the absence of adhesion.  Similar to the quiescent
-example, the membrane tension is negative in the contact region
-indicating that the membrane is being compressed when the adhesive force
-is strongest.
+vesicle.  Each of the vesicles have reduced area $\Delta A = 0.9$, shear
+rate $\chi = 0.5$, separation distance $\delta = 0.4$, and Hamaker
+constant $\mathcal{H} = 0.7$ (Figure~\ref{fig:doublet090-weakAdhesion})
+and $\mathcal{H} = 2.1$ (Figure~\ref{fig:doublet090-strongAdhesion}).
+Similar to the quiescent example, the membrane tension is negative in
+the contact region indicating that the membrane is being compressed when
+the adhesive force is strongest.  For both Hamaker constants, the
+vesicles in the doublet move in tandem with a tank-reading motion that
+is much slower than the tank-treading motion that occurs in the absense
+of ahdesion.
 
@@
 
-We characterize the effect of the Hamaker constant and shear rate by
-determining a critical Hamaker constant, $\mathcal{H}_c$, which
-determines if the vesicles form a doublet or separate.  We fix the
-separation distance to $\delta = 0.4$ and the vesicle reduced area to
-$\Delta A = 0.9$.  In Figure~\ref{fig:sflow_distance}(a), we plot the
-minimum distance between the vesicles as a function of time for various
-Hamaker constants.  The red curves correspond to Hamaker constants that
-are too small to bind the vesicles into a doublet, and the blue curves
-correspond to Hamaker constants that are sufficiently large to form a
-doublet.
-
-In Figure~\ref{fig:sflow_distance}(b), we plot the time required for the
-doublet to make a complete revolution at a variety of Hamaker constants
-and shear rates.  For a fixed Hamaker constant, as expected, the period
-decreases for larger shear rates.  In addition, for a fixed shear rate,
-the period decreases as the Hamaker constant increases, but the period
-eventually plateaus.  The dynamics of these doublet have similar
-behavior to a single rigid body undergoing a Jeffery orbit in a shear
-flow.  Therefore, we define the effective aspect ratio
-$\lambda_{\mathrm{eff}}$ which satisfies
+In Figure~\ref{fig:sflow_distance}(a), we plot the minimum distance
+between the two vesicles as a function of time for various Hamaker
+constants.  For Hamaker constants less than a critical value,
+$\mathcal{H}_c$, the adhesive force is not strong enough to form a
+doublet, and the distance between the vesicles grows with time (red
+curves).  However, when $\mathcal{H} > \mathcal{H}_c$, the adhesive
+force is sufficiently strong to bind the vesicles into a doublet, and
+then the doublet undergoes a periodic motion (blue curves).  In
+Figure~\ref{fig:sflow_distance}(b), we plot the time required for the
+doublet to make a complete revolution for three different shear rates.
+For a fixed Hamaker constant, as expected, the period decreases for
+larger shear rates.  More interestingly, at a fixed shear rate, the
+period depends non-monotonically on the Hamaker constant.  When the
+Hamaker constant is first sufficiently large to form a doublet, the
+individual vesicles undergo a sliding motion as they pass one another,
+and the contact region between the vesicles moves along the vesicle
+throughout the simulation (Figure~\ref{fig:doublet090-weakAdhesion}).
+However, at larger Hamaker constants, once the contact region is formed,
+the doublet maintains the same structure and undergoes a tumbling
+dynamic similar to a Jeffery orbit.  The simulations illustrated in
+Figures~\ref{fig:doublet090-weakAdhesion}
+and~\ref{fig:doublet090-strongAdhesion} are chosen so that the doublet
+has roughly the same period, but the structure of the doublet is
+fundamentally different for these different Hamaker constants.
+
+To further understand the behavior of the Jeffery orbit, we define an
+effective aspect ratio $\lambda_{\mathrm{eff}}$ which satisfies
 \begin{align*}
@@
 we can simply say how it affects the period}
+
+We characterize the effect of the Hamaker constant and shear rate by
+determining a critical Hamaker constant, $\mathcal{H}_c$, which
+determines if the vesicles form a doublet or separate.
 

### 2019-07-10 vesicle_code/docs/adhesion/adhesion.tex
yn edition

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Adhesion of two vesicles in an extensional flow} 
+\section{Adhesion of two vesicles in a planar extensional flow} 
 \label{sec:eflow}
@@
 
-  \caption{\label{fig:extensionalNonsymmetric} }
+  \caption{\label{fig:extensionalNonsymmetric}Dynamics of a vesicle pair in a planar extensional flow.
+${\cal H} = 0.7$ for the first three rows, and ${\cal H}=0.6$ for the bottom row.
+From top to bottom, the initial vertical displacement $\triangle y=0$, 0.02, 0.1 and 0.1.
+The reduced area is ???, the strain rate $\chi = ???$ and the adhesion distance $\delta = ???$.
+}
   \end{figure}
@@
 drop~\cite{KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
-Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  The stagnation
-point (zero-velocity at the origin) in an extensional flow, $\uu
-=\chi(-x,y)$, is a saddle point where two laminar streams converge along
-an axis and then diverge in the orthogonal direction.  With an active
+Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  Here we focus on a
+planar extensional flow  where the fluid velocity field $\uu=\chi(-x,y)$ is centered at the 
+the origin ($(x,y)=(0,0)$), the stagnation point where the fluid flow converges horizontally and diverges vertically.
+Placed symmetrically at the stagnation point of an extensional flow,
+a single vesicle may remain steady and symmetric for low strain rate $\chi$.
+For sufficiently large strain rate $\chi$ the vesicle may undergo asymmetric deformation \cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}.
+
+To investigate how two vesicles interact with each other in a planar extensional flow,
+at the beginning of the simulations
+we place a vesicle at the stagnation point (left panels in Figure~\ref{fig:extensionalNonsymmetric}), 
+and the other vesicle at $(x,y) = (2,\triangle y)$ where the initial vertical displacement $\triangle y$ increases from
+$\triangle y=0$ for the top row, $\triangle y = 0.02$ for the second row, to
+$\triangle y =0.1$ for the bottom two rows in Figure~\ref{fig:extensionalNonsymmetric}.
+The adhesion strength ${\cal H} = 0.7$ for the top three rows, and ${\cal H} =0.6$ for the bottom row.
+
+Once the planar extensional flow is turned on at $t=0^+$, two vesicles move
+towards each other  as shown in  Figure \ref{fig:extensionalNonsymmetric}.
+For $\triangle y=0$ in the top row, the two vesicles stay on the $x$-axis as they move towards each other, 
+form a doublet and reach a steady 
+configuration that is symmetric with respect to the stagnation point.
+
+As the initial vertical displacement increases, we observe that 
+the two vesicles rotate as they are within close range of each other 
+and form a doublet for ${\cal H}=0.7$ as they move away from the origin.
+In particular we observe that the two vesicles are in sideway contact for $\triangle y = 0.02$ in the second row,
+ while for $\triangle y = 0.1$ the two vesicles form a contact region near the tip.
+%
+For weaker adhesion ${\cal H}=0.6$ the two vesicles with an initial vertical displacement $\triangle y = 0.1$ no longer form a doublet
+and are separate from each other at $t=100$.
+
+In an extensional flow the two vesicles easily move away from the stagnation point as shown in Figure~\ref{fig:extensionalNonsymmetric}.
+A small initial vertical displacement $\triangle y$ causes the vesicle pair to not only rotate but also move along the diverging flow to large
+distance from the stagnation point, where the flow strength increases.
+Thus in the microfluidic experiment it is often more desirable to trap the vesicle around the center of an extensional flow \cite{Spjut2010_MSThesis_Chapter3}.
+
+With an active
 control algorithm to place the stagnation point at a desirable location

### 2019-07-10 vesicle_code/docs/adhesion/adhesion.tex
fixed up figure 6

@@
 \begin{figure}[htp]
-  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={1cm 0cm 1cm 0cm},clip]
     {figs/extensional_displacement0_adS7em1_image01.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
     {figs/extensional_displacement0_adS7em1_image02.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
     {figs/extensional_displacement0_adS7em1_image03.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
     {figs/extensional_displacement0_adS7em1_image04.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
     {figs/extensional_displacement0_adS7em1_image05.png} \\
 
-  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={1cm 0cm 1cm 0cm},clip]
     {figs/extensional_displacement2em2_adS7em1_image01.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
     {figs/extensional_displacement2em2_adS7em1_image02.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
     {figs/extensional_displacement2em2_adS7em1_image03.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
     {figs/extensional_displacement2em2_adS7em1_image04.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
     {figs/extensional_displacement2em2_adS7em1_image05.png} \\
 
-  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={1cm 0cm 1cm 0cm},clip]
     {figs/extensional_displacement1em1_adS7em1_image01.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
     {figs/extensional_displacement1em1_adS7em1_image02.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
     {figs/extensional_displacement1em1_adS7em1_image03.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
     {figs/extensional_displacement1em1_adS7em1_image04.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
     {figs/extensional_displacement1em1_adS7em1_image05.png} \\
 
-  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={1cm 0cm 1cm 0cm},clip]
     {figs/extensional_displacement1em1_adS6em1_image01.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
     {figs/extensional_displacement1em1_adS6em1_image02.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
     {figs/extensional_displacement1em1_adS6em1_image03.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
     {figs/extensional_displacement1em1_adS6em1_image04.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
     {figs/extensional_displacement1em1_adS6em1_image05.png}
-
   \caption{\label{fig:extensionalNonsymmetric}Dynamics of a vesicle pair in a planar extensional flow.

### 2019-07-10 vesicle_code/docs/adhesion/adhesion.tex
fixed figs 12 and 13

@@
 \begin{figure}[htp]
-  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image01.png}
-  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image02.png}
-  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image03.png}
-  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image04.png}
-  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image05.png}
-  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image06.png}
-  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image07.png}
-  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image08.png}
+  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image01.png}
+  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image02.png}
+  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image03.png}
+  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image04.png}
+  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image05.png}
+  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image06.png}
+  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image07.png}
+  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image08.png}
+  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image09.png}
+  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image10.png}
   \caption{\label{fig:doublet090-weakAdhesion} The formation of a
@@
 \begin{figure}[htp]
-  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image01.png}
-  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image02.png}
-  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image03.png}
-  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image04.png}
-  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image05.png}
-  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image06.png}
-  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image07.png}
-  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image08.png}
+  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image01.png}
+  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image02.png}
+  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image03.png}
+  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image04.png}
+  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image05.png}
+  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image06.png}
+  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image07.png}
+  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image08.png}
+  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image09.png}
+  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image10.png}
   \caption{\label{fig:doublet090-strongAdhesion} The formation of a

### 2019-07-11 vesicle_code/docs/adhesion/adhesion.tex
ynys adhesion

--- 2019-07-10 vesicle_code/docs/adhesion/adhesion.tex
@@
 
-Finally, to further characterize the rotating dynamics of a doublet in
-the fluid trap, we compute and plot the vorticity and total force on a
-doublet with identical vesicles with reduced area $\Delta A=0.7$,
-Hamaker constant $\mathcal{H} = 0.7$, separation distance $\delta =
-0.4$, and extensional rate $\chi = 0.07$ in
-Figure~\ref{fig:extensionalVorticity}.  Starting from an initial inclination angle $\theta=\pi$, the doublet 
-starts to rotate around $t\sim 250$.  We notice that the net force on
-each vesicle is almost anti-parallel to the diverging flow in the
-far-field so to balance the hydrodynamic drag force that pulls the
-vesicles apart.  Then, as the doublet starts to rotate, each vesicle
-experiences a drag force from the diverging streaming
-flows.  
-%
-For small extensional rate, the rotation continues until
-$\theta = \pi/2$ so the doublet remains perfectly symmetric with respect
-to their mid-plane, and each vesicle experiences drag forces (from the diverging flow) that cancel
-each other.  
-%
-For slightly higher extensional rate in Figure~\ref{fig:extensionalVorticity}, we observe
-that the two vesicles slide against each other (around $t=280$) as the doublet rotates.
-The slight sliding motion leads to a transition in the contact region
-membrane shape from a bulging profile to an S-shape profile of nearly
-uniform height except near the edge of contact region.  This adjustment
-greatly reduces the net force on each vesicle, leading to an equilibrium
-configuration with an inclination angle $\theta > \pi/2$ as shown in the
-left of Figure~\ref{fig:extensionalInclinationAngle}.  Finally, the
-vorticity and the flow between the vesicles approaches zero and the
-result is a fluid trap containing the doublet.
-\begin{figure}[htp]
-  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
-  0cm},clip]{figs/extensionalVorticity01.png}
-  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
-  0cm},clip]{figs/extensionalVorticity02.png}
-  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
-  0cm},clip]{figs/extensionalVorticity03.png}
-  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
-  0cm},clip]{figs/extensionalVorticity04.png}
-  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
-  0cm},clip]{figs/extensionalVorticity05.png} \\
-  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
-  0cm},clip]{figs/extensionalVorticity06.png}
-  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
-  0cm},clip]{figs/extensionalVorticity07.png}
-  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
-  0cm},clip]{figs/extensionalVorticity08.png}
-  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
-  0cm},clip]{figs/extensionalVorticity09.png}
-  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
-  0cm},clip]{figs/extensionalVorticity10.png}
-  \caption{\label{fig:extensionalVorticity} The vorticity and total
-  force of two vesicles in a doublet.  The reduced area is $\Delta A =
-  0.7$, the separation distance is $\delta = 0.4$, the Hamaker constant
-  is $\mathcal{H} = 0.7$, and the extensional rate is $\chi = 0.07$.}
-\end{figure}
+%Finally, to further characterize the rotating dynamics of a doublet in
+%the fluid trap, we compute and plot the vorticity and total force on a
+%doublet with identical vesicles with reduced area $\Delta A=0.7$,
+%Hamaker constant $\mathcal{H} = 0.7$, separation distance $\delta =
+%0.4$, and extensional rate $\chi = 0.07$ in
+%Figure~\ref{fig:extensionalVorticity}.  Starting from an initial inclination angle $\theta=\pi$, the doublet 
+%starts to rotate around $t\sim 250$.  We notice that the net force on
+%each vesicle is almost anti-parallel to the diverging flow in the
+%far-field so to balance the hydrodynamic drag force that pulls the
+%vesicles apart.  Then, as the doublet starts to rotate, each vesicle
+%experiences a drag force from the diverging streaming
+%flows.  
+%%
+%For small extensional rate, the rotation continues until
+%$\theta = \pi/2$ so the doublet remains perfectly symmetric with respect
+%to their mid-plane, and each vesicle experiences drag forces (from the diverging flow) that cancel
+%each other.  
+%%
+%For slightly higher extensional rate in Figure~\ref{fig:extensionalVorticity}, we observe
+%that the two vesicles slide against each other (around $t=280$) as the doublet rotates.
+%The slight sliding motion leads to a transition in the contact region
+%membrane shape from a bulging profile to an S-shape profile of nearly
+%uniform height except near the edge of contact region.  This adjustment
+%greatly reduces the net force on each vesicle, leading to an equilibrium
+%configuration with an inclination angle $\theta > \pi/2$ as shown in the
+%left of Figure~\ref{fig:extensionalInclinationAngle}.  Finally, the
+%vorticity and the flow between the vesicles approaches zero and the
+%result is a fluid trap containing the doublet.
+%\begin{figure}[htp]
+%  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
+%  0cm},clip]{figs/extensionalVorticity01.png}
+%  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
+%  0cm},clip]{figs/extensionalVorticity02.png}
+%  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
+%  0cm},clip]{figs/extensionalVorticity03.png}
+%  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
+%  0cm},clip]{figs/extensionalVorticity04.png}
+%  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
+%  0cm},clip]{figs/extensionalVorticity05.png} \\
+%  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
+%  0cm},clip]{figs/extensionalVorticity06.png}
+%  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
+%  0cm},clip]{figs/extensionalVorticity07.png}
+%  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
+%  0cm},clip]{figs/extensionalVorticity08.png}
+%  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
+%  0cm},clip]{figs/extensionalVorticity09.png}
+%  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
+%  0cm},clip]{figs/extensionalVorticity10.png}
+%  \caption{\label{fig:extensionalVorticity} The vorticity and total
+%  force of two vesicles in a doublet.  The reduced area is $\Delta A =
+%  0.7$, the separation distance is $\delta = 0.4$, the Hamaker constant
+%  is $\mathcal{H} = 0.7$, and the extensional rate is $\chi = 0.07$.}
+%\end{figure}
 

### 2019-07-11 vesicle_code/docs/adhesion/adhesion.tex
ynys adhesion

@@
     {figs/extensional_displacement1em1_adS7em1_image04.png}
-  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={3.5cm 0cm 4cm 0cm},clip]
     {figs/extensional_displacement1em1_adS7em1_image05.png} \\
@@
     {figs/extensional_displacement1em1_adS6em1_image04.png}
-  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={3.5cm 0cm 4cm 0cm},clip]
     {figs/extensional_displacement1em1_adS6em1_image05.png}
@@
 we place a vesicle at the stagnation point (left panels in Figure~\ref{fig:extensionalNonsymmetric}), 
-and the other vesicle at $(x,y) = (2,\triangle y)$ where the initial vertical displacement $\triangle y$ increases from
+and the other vesicle at $(x,y) = (3,\triangle y)$ where the initial vertical displacement $\triangle y$ varies from
 $\triangle y=0$ for the top row, $\triangle y = 0.02$ for the second row, to
@@
 towards each other  as shown in  Figure \ref{fig:extensionalNonsymmetric}.
-For $\triangle y=0$ in the top row, the two vesicles stay on the $x$-axis as they move towards each other, 
-form a doublet and reach a steady 
-configuration that is symmetric with respect to the stagnation point.
-
-As the initial vertical displacement increases, we observe that 
-the two vesicles rotate as they are within close range of each other 
-and form a doublet for ${\cal H}=0.7$ as they move away from the origin.
-In particular we observe that the two vesicles are in sideway contact for $\triangle y = 0.02$ in the second row,
- while for $\triangle y = 0.1$ the two vesicles form a contact region near the tip.
-%
-For weaker adhesion ${\cal H}=0.6$ the two vesicles with an initial vertical displacement $\triangle y = 0.1$ no longer form a doublet
-and are separate from each other at $t=100$.
-
-In an extensional flow the two vesicles easily move away from the stagnation point as shown in Figure~\ref{fig:extensionalNonsymmetric}.
-A small initial vertical displacement $\triangle y$ causes the vesicle pair to not only rotate but also move along the diverging flow to large
-distance from the stagnation point, where the flow strength increases.
-Thus in the microfluidic experiment it is often more desirable to trap the vesicle around the center of an extensional flow \cite{Spjut2010_MSThesis_Chapter3}.
+For $\triangle y=0$ in the top row, the two vesicles stay on the $x$-axis as they move closer to 
+form a doublet. We observe that the left vesicle (initially centered at $(0,0)$) moves to the left due to the impinging
+vesicle from the right. As time progresses they form a doublet
+and reach a steady configuration that is symmetric with respect to the stagnation point 
+(filled squares in Figure \ref{fig:extensionalNonsymmetric}).
+
+As the initial vertical displacement $\triangle y$ increases, we observe similar vesicle dynamics only at the beginning 
+when the right vesicle moves towards the left vesicle as the left vesicle is pushed to the left of the stagnation point. 
+As both vesicles come to close vicinity of the stagnation point, the diverging flow pulls the
+right vesicle (elevated with a small vertical displacement at $t=0$) further away, causing rotation of vesicles as a pair. 
+We also observe that the larger the initial vertical displacement, the larger the rotation and the faster both vesicles move
+away from the stagnation point.
+
+For strong adhesion (such as the cases with ${\cal H}=0.7$ in Figure \ref{fig:extensionalNonsymmetric}),
+ the two vesicles rotate and move away from the stagnation point as a doublet even for $\triangle y=0.1$, where
+ two vesicles are in close vicinity of each other only at the tip at $t=100$ in the third row.
+For weaker adhesion (${\cal H}=0.6$ in Figure \ref{fig:extensionalNonsymmetric})  
+the two vesicles no longer form a doublet as they are quite separate from each other at $t=100$.
+
+ with an initial vertical displacement $\triangle y = 0.1$ no longer form a doublet
+and are separate from each other at the end of simulation ($t=100$).
+
+Results in Figure~\ref{fig:extensionalNonsymmetric} illustrate that
+in an extensional flow vesicles are prone to move away from the stagnation point:
+A small initial vertical displacement $\triangle y$ of one vesicle causes both vesicles to not only rotate but also move away from the
+center. Thus in the microfluidic experiment it is often more desirable to trap the vesicle around the center of an extensional flow \cite{Spjut2010_MSThesis_Chapter3}.
 

### 2019-07-11 vesicle_code/docs/adhesion/adhesion.tex
ynys adhesion

@@
 been well-studied and documented
-(see~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir,
+(see~\cite{Agrawal2011_MathMechSolids,RamachandranAndersonLealIsraelachvili2010_Langmuir,
 SteinkuhlerAgudo-Canalejo2016_BJ, FlormannAouane2017_SciReports} and
@@
 From top to bottom, the initial vertical displacement $\triangle y=0$, 0.02, 0.1 and 0.1.
-The reduced area is ???, the strain rate $\chi = ???$ and the adhesion distance $\delta = ???$.
+The reduced area is ???, the extensional rate $\chi = ???$ and the adhesion distance $\delta = ???$.
 }
@@
 Placed symmetrically at the stagnation point of an extensional flow,
-a single vesicle may remain steady and symmetric for low strain rate $\chi$.
-For sufficiently large strain rate $\chi$ the vesicle may undergo asymmetric deformation \cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}.
+a single vesicle may remain steady and symmetric for low extensional rate $\chi$.
+For sufficiently large extensional rate $\chi$ the vesicle may undergo asymmetric deformation \cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}.
 
@@
 As both vesicles come to close vicinity of the stagnation point, the diverging flow pulls the
-right vesicle (elevated with a small vertical displacement at $t=0$) further away, causing rotation of vesicles as a pair. 
+right vesicle (elevated with a small vertical displacement at $t=0$) further away, causing rotation of both vesicles. 
 We also observe that the larger the initial vertical displacement, the larger the rotation and the faster both vesicles move
@@
 
-For strong adhesion (such as the cases with ${\cal H}=0.7$ in Figure \ref{fig:extensionalNonsymmetric}),
- the two vesicles rotate and move away from the stagnation point as a doublet even for $\triangle y=0.1$, where
- two vesicles are in close vicinity of each other only at the tip at $t=100$ in the third row.
-For weaker adhesion (${\cal H}=0.6$ in Figure \ref{fig:extensionalNonsymmetric})  
-the two vesicles no longer form a doublet as they are quite separate from each other at $t=100$.
-
- with an initial vertical displacement $\triangle y = 0.1$ no longer form a doublet
-and are separate from each other at the end of simulation ($t=100$).
+For sufficiently strong adhesion (such as ${\cal H}=0.7$ for first three rows in Figure \ref{fig:extensionalNonsymmetric}),
+ the two vesicles rotate and move away from the stagnation point as a doublet until the end of simulations ($t=100$).
+As the two vesicles move further away from the stagnation point, the extensional flow becomes more effective in pulling the two drops apart
+as shown in the third row of Figure \ref{fig:extensionalNonsymmetric}.
+For ${\cal H}=0.6$ (bottom row in Figure \ref{fig:extensionalNonsymmetric})  
+the two vesicles are separated by the diverging flow as early as $t=75$, and are clearly not a doublet at the end of simulation.
 
@@
 in an extensional flow vesicles are prone to move away from the stagnation point:
-A small initial vertical displacement $\triangle y$ of one vesicle causes both vesicles to not only rotate but also move away from the
-center. Thus in the microfluidic experiment it is often more desirable to trap the vesicle around the center of an extensional flow \cite{Spjut2010_MSThesis_Chapter3}.
+A small initial vertical displacement $\triangle y$ in one  of the vesicles causes both vesicles to not only rotate but also move away from the
+center. Once vesicles move along the diverging stream, their hydrodynamics is dominated by the strong straining flow in the far-field.
+Thus in the microfluidic experiment it is often more desirable to trap the vesicle around the center of an extensional flow \cite{Spjut2010_MSThesis_Chapter3}.
 
@@
 doublet in the fluid trap centered around the stagnation point, or the
-doublet is broken and the vesicles separate from one another.  In
-Figures~\ref{fig:extensional1}, snapshots of a fluid trap containing a
+doublet is broken and the vesicles separate from one another.
+
+In Figures~\ref{fig:extensional1}, snapshots of a fluid trap containing a
 vesicle doublet of reduced area $\Delta A = 0.7$ are simulated at three
@@
 $\theta=\pi$ configuration towards the more stable $\theta=\pi/2$
-configuration, as shown in Figures~\ref{fig:extensional1}.  We also
+configuration, as shown in Figures~\ref{fig:extensional1}.  
+%
+The final configurations in Figures~\ref{fig:extensional1}
+are similar to those at $t=100$ in Figure~\ref{fig:extensionalNonsymmetric}.
+%
+We also
 observe that with moderate extensional rates, the doublet falls short of

### 2019-07-12 vesicle_code/docs/adhesion/adhesion.tex
working on revisions

@@
 We consider two vesicles suspended in the shear flow $\uu = \chi(y,0)$,
-where $\chi$ is the shear rate.  The vesicles are placed on the $y$ axis
-so that the background velocity drives the vesicles towards one another.
-In the absence of adhesion, once the vesicles are sufficiently close,
-they are deflected to opposite sides of the $y$ axis, pass one another,
-and then separate.  However, in the presence of adhesion, the vesicles
-can form a doublet for certain values of the separation distance
-$\delta$, Hamaker constant $\mathcal{H}$, shear rate $\chi$, and reduced
-area $\Delta A$.  At all reduced areas, the vesicles have a length of
-$2\pi$ to be consistent with simulations in previous sections.
+where $\chi$ is the shear rate.  The initial placement of the vesicles
+is chosen so that the flow dives them towards one another.  In the
+absence of adhesion, once the vesicles are sufficiently close, they are
+deflected to opposite sides of the $y$ axis, pass one another, and then
+separate.  However, in the presence of adhesion, the vesicles can form a
+doublet for certain values of the separation distance $\delta$, Hamaker
+constant $\mathcal{H}$, shear rate $\chi$, and reduced area $\Delta A$.
+At all reduced areas, the vesicles have a length of $2\pi$ to be
+consistent with simulations in previous sections.
 
@@
 the contact region indicating that the membrane is being compressed when
-the adhesive force is strongest.  For both Hamaker constants, the
-vesicles in the doublet move in tandem with a tank-reading motion that
-is much slower than the tank-treading motion that occurs in the absense
-of ahdesion.
+the adhesive force is strongest.  The two values for the Hamaker
+constant are chosen since the vesicles dynamics have similar periods of
+$t^* \approx 42$.  For both the Hamaker constants, the vesicles in the
+doublet move in tandem with a tank-reading motion that is much slower
+than the tank-treading motion that occurs in the absense of ahdesion.
+However, the dynamics of a single period for theses two Hamaker
+constants differ significantly.  For the weaker adhesive force, the
+individual vesicles undergo a sliding motion as they pass one another,
+and the contact region between the vesicles moves along the vesicle
+throughout the simulation (Figure~\ref{fig:doublet090-weakAdhesion}).
+However, at larger Hamaker constants, once the contact region is formed,
+the doublet maintains the same structure and undergoes a tumbling
+dynamic similar to a Jeffery orbit.
 
@@
 
-In Figure~\ref{fig:sflow_distance}(a), we plot the minimum distance
-between the two vesicles as a function of time for various Hamaker
-constants.  For Hamaker constants less than a critical value,
-$\mathcal{H}_c$, the adhesive force is not strong enough to form a
-doublet, and the distance between the vesicles grows with time (red
-curves).  However, when $\mathcal{H} > \mathcal{H}_c$, the adhesive
-force is sufficiently strong to bind the vesicles into a doublet, and
-then the doublet undergoes a periodic motion (blue curves).  In
-Figure~\ref{fig:sflow_distance}(b), we plot the time required for the
+To further understand the nature of the doublet,
+Figure~\ref{fig:sflow_distance}(a) shows the minimum distance between
+the two vesicles as a function of time.  For Hamaker constants less than
+a critical value, $\mathcal{H}_c$, the adhesive force is not strong
+enough to form a doublet, and the distance between the vesicles grows
+with time (red curves).  However, when $\mathcal{H} > \mathcal{H}_c$,
+the adhesive force is sufficiently strong to bind the vesicles into a
+doublet, and then the doublet undergoes a periodic motion (blue curves).
+In Figure~\ref{fig:sflow_distance}(b), we plot the time required for the
 doublet to make a complete revolution for three different shear rates.
-For a fixed Hamaker constant, as expected, the period decreases for
-larger shear rates.  More interestingly, at a fixed shear rate, the
-period depends non-monotonically on the Hamaker constant.  When the
-Hamaker constant is first sufficiently large to form a doublet, the
-individual vesicles undergo a sliding motion as they pass one another,
-and the contact region between the vesicles moves along the vesicle
-throughout the simulation (Figure~\ref{fig:doublet090-weakAdhesion}).
-However, at larger Hamaker constants, once the contact region is formed,
-the doublet maintains the same structure and undergoes a tumbling
-dynamic similar to a Jeffery orbit.  The simulations illustrated in
-Figures~\ref{fig:doublet090-weakAdhesion}
-and~\ref{fig:doublet090-strongAdhesion} are chosen so that the doublet
-has roughly the same period, but the structure of the doublet is
-fundamentally different for these different Hamaker constants.
-
-To further understand the behavior of the Jeffery orbit, we define an
-effective aspect ratio $\lambda_{\mathrm{eff}}$ which satisfies
-\begin{align*}
-  \frac{2\pi}{\chi}\left(\lambda + \lambda^{-1} \right) = p,
-\end{align*}
-where $p$ is the period of the doublet.  The effective aspect ratio is
-the aspect ratio of an ellipse in a shear flow that is undergoing a
-Jeffery orbit with period $p$.  For the Hamaker constant $\mathcal{H} =
-2$, the shear rates, periods, and effective aspect ratio are summarized
-in Table~\ref{tbl:aspectRatio}.  Since the effective aspect ratio is
+Initially, as the shear rate increases, the period decreases.  However,
+the transition from the weakly adhesive doublet
+(Figure~\ref{fig:doublet090-weakAdhesion} to the stronger adhesive
+doublet (Figure~\ref{fig:doublet090-strongAdhesion}) results in an
+increase in the period.  However, once the Hamaker constant is
+sufficiently strong that the contact region remains fixed throughout the
+dynamics, the period of the doublet again decreases as the shear rate
+increases.
+
+Especially at the large Hamaker constants, the dynamics of the doublet
+resemble those of a Jeffery orbit.  An ellipse with aspect ratio
+$\lambda$ undergoes a periodic tumbling motion with
+period~\cite{jef1922}
+\begin{align}
+  p = \frac{2\pi}{\chi}\left(\lambda + \lambda^{-1} \right).
+  \label{eqn:JefferyPeriod}
+\end{align}
+Instead of measuring the aspect ratio of a doublet in a flow with shear
+rate $\chi$, we use the computed period to define an effective aspect
+ratio $\lambda_{\mathrm{eff}}$ that satisfies~\eqref{eqn:JefferyPeriod}.
+Therefore, the effective aspect ratio is the aspect ratio of an ellipse
+in a shear flow that is undergoing a Jeffery orbit with period $p$.  For
+the Hamaker constants $\mathcal{H} = 1.5$ and $\mathcal{H} = 3.5$, the
+shear rates, periods, and effective aspect ratio are summarized in
+Table~\ref{tbl:aspectRatio}.
+
+Since the effective aspect ratio is
 comparable for all three shear rates, this indicates that the dynamics
@@
 \begin{table}[htp]
+\begin{minipage}{0.45\textwidth}
+  $\mathcal{H} = 1.5$ \\
   \begin{tabular}{>{\centering\arraybackslash}p{2cm}
@@
   \hline
-  0.50 & 38.06 & 2.92 \\
-  0.75 & 24.81 & 2.85 \\
-  1.00 & 19.47 & 3.00 
+%  0.50 & 38.06 & 2.92 \\
+%  0.75 & 24.81 & 2.85 \\
+%  1.00 & 19.47 & 3.00 
+  0.50 & 36.34 & 2.49 \\
+  0.75 & 25.86 & 2.72 \\
+  1.00 & 20.73 & 2.96 
 \end{tabular}
-\todo[inline]{Update these values with new periods.  Maybe need to
-consider more than one Hamaker constant}
+\end{minipage}
+%\hfill
+\begin{minipage}{0.45\textwidth}
+  $\mathcal{H} = 3.5$ \\
+  \begin{tabular}{>{\centering\arraybackslash}p{2cm}
+>{\centering\arraybackslash}p{2cm}
+>{\centering\arraybackslash}p{2cm}}
+  $\chi$ & $p$ & $\lambda_{\mathrm{eff}}$ \\
+  \hline
+  0.50 & 28.46 & 1.66 \\
+  0.75 & 22.01 & 2.17 \\
+  1.00 & 17.91 & 2.44 
+\end{tabular}
+\end{minipage}
 \caption{\label{tbl:aspectRatio} The shear rate, period, and effective
 aspect ratio of a vesicle doublet with reduced area $\Delta A = 0.9$,
-Hamaker constant $\mathcal{H} = 2$, and separation distance $\delta =
-0.4$.  The effective aspect ratios are comparable for all three shear
-rates.}
+separation distance $\delta = 0.4$, and 
+Hamaker constants $\mathcal{H} = 1.5$ and $\mathcal{H} = 3.5$.  The
+effective aspect ratios depend on both the Hamaker constant and the
+shear rate, indicating that the reported Hamaker constants, the dynamics
+of the doublet differ from that of a Jeffery orbit.}
 \end{table}

### 2019-07-12 vesicle_code/docs/adhesion/adhesion.tex
yny revision July 12

--- 2019-07-11 vesicle_code/docs/adhesion/adhesion.tex
@@
 From top to bottom, the initial vertical displacement $\triangle y=0$, 0.02, 0.1 and 0.1.
-The reduced area is ???, the extensional rate $\chi = ???$ and the adhesion distance $\delta = ???$.
+The reduced area is ???, the extension rate $\chi = ???$ and the adhesion distance $\delta = ???$.
 }
@@
 Placed symmetrically at the stagnation point of an extensional flow,
-a single vesicle may remain steady and symmetric for low extensional rate $\chi$.
-For sufficiently large extensional rate $\chi$ the vesicle may undergo asymmetric deformation \cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}.
+a single vesicle may remain steady and symmetric for low extension rate $\chi$.
+For sufficiently large extension rate $\chi$ the vesicle may undergo asymmetric deformation \cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}, 
+similar to a surfactant-laden viscous drop under a planar extensional flow \cite{JanssenBoonAgterof1997_AIChE,HuPineLeal2000_PoF}.
 
 To investigate how two vesicles interact with each other in a planar extensional flow,
-at the beginning of the simulations
-we place a vesicle at the stagnation point (left panels in Figure~\ref{fig:extensionalNonsymmetric}), 
+at the beginning of the simulations (left panels in Figure~\ref{fig:extensionalNonsymmetric})
+we place a vesicle at $(x,y)=(0,0)$, 
 and the other vesicle at $(x,y) = (3,\triangle y)$ where the initial vertical displacement $\triangle y$ varies from
@@
 and reach a steady configuration that is symmetric with respect to the stagnation point 
-(filled squares in Figure \ref{fig:extensionalNonsymmetric}).
-
-As the initial vertical displacement $\triangle y$ increases, we observe similar vesicle dynamics only at the beginning 
-when the right vesicle moves towards the left vesicle as the left vesicle is pushed to the left of the stagnation point. 
-As both vesicles come to close vicinity of the stagnation point, the diverging flow pulls the
-right vesicle (elevated with a small vertical displacement at $t=0$) further away, causing rotation of both vesicles. 
+(square mark in Figure \ref{fig:extensionalNonsymmetric}).
+
+For $\triangle y>0$ we observe similar vesicle dynamics only at the beginning 
+when the right vesicle moves towards the stagnation point and the left vesicle is pushed to the left of the stagnation point. 
+As both vesicles come to close vicinity of the stagnation point, the elevated right vesicle ($\triangle y >0$) is pulled up by the diverging flow in the $y$ direction,
+causing rotation of both vesicles. 
 We also observe that the larger the initial vertical displacement, the larger the rotation and the faster both vesicles move
 away from the stagnation point.
-
-For sufficiently strong adhesion (such as ${\cal H}=0.7$ for first three rows in Figure \ref{fig:extensionalNonsymmetric}),
+%
+For sufficiently strong adhesion (${\cal H}=0.7$ for the first three rows in Figure \ref{fig:extensionalNonsymmetric}),
  the two vesicles rotate and move away from the stagnation point as a doublet until the end of simulations ($t=100$).
@@
 A small initial vertical displacement $\triangle y$ in one  of the vesicles causes both vesicles to not only rotate but also move away from the
-center. Once vesicles move along the diverging stream, their hydrodynamics is dominated by the strong straining flow in the far-field.
+center. Once vesicles move off the horizontal axis, their hydrodynamics is dominated by the diverging flow as they move further away.
 Thus in the microfluidic experiment it is often more desirable to trap the vesicle around the center of an extensional flow \cite{Spjut2010_MSThesis_Chapter3}.
-
+%
 With an active
 control algorithm to place the stagnation point at a desirable location
-by adjusting the streaming flow strength with a feedback
-loop~\cite{Johnson-Chavarria2011_EMJ}, a particle can be trapped at the
+by adjusting the flow with a feedback
+loop~\cite{BentleyLeal1986_JFMa,Johnson-Chavarria2011_EMJ}, a particle can be trapped at the
 stagnation point for long time scales to facilitate image acquisition or
 other detailed measures such as particle image velocimetry of flow
-inside and around the particle.  To explore the application of such a
-fluid trap to measure the adhesion strength between two bound vesicle
-membranes, we propose the following experiment.  Beginning with two
+inside and around the particle.
+
+To explore the application of such a
+fluid trap to measure the adhesion strength between two bound vesicles, 
+we propose the following experiment.  
+Beginning with two
 identical vesicles in an equilibrium configuration that form a doublet
@@
 %point.  On the other hand, the vesicle doublet may become unstable and
-%eventually separate at higher extensional rates.  Thus we expect there
-%to exist a critical extensional rate $\chi_c$ above which the vesicle
+%eventually separate at higher extension rates.  Thus we expect there
+%to exist a critical extension rate $\chi_c$ above which the vesicle
 %doublet cannot stay bound under a given adhesion potential.  Therefore,
-%the dependence of the critical extensional rate $\chi_c$ on the adhesion
+%the dependence of the critical extension rate $\chi_c$ on the adhesion
 %potential and the mechanical vesicle properties provides a means to
@@
 Based on how the contact region aligns with the extensional flow, we can
-define the inclination angle of the vesicle doublet as illustrated in
-Figure~\ref{fig:InclinationAngle}. When $\theta=\pi$, the doublet long
-axis is aligned with the far-field converging flow, and the diverging flow
-pulls the vesicles apart from each other and the long-range attractive
+define the inclination angle $\theta$ of the vesicle doublet as illustrated in
+Figure~\ref{fig:InclinationAngle}(b). When $\theta=\pi$ (Figure~\ref{fig:InclinationAngle}(a))
+the diverging flow
+pulls the vesicles apart from each other and the attractive adhesion
 force is essential to keep the two vesicles from separating.  In
-contrast, when $\theta = \pi/2$, the doublet long axis is aligned with
-the diverging flow, the converging flow pushes the vesicles towards
-each other and the short-range repulsive force is essential to keep the
+contrast, when $\theta = \pi/2$ (Figure~\ref{fig:InclinationAngle}(c)), 
+%the doublet long axis is aligned with the diverging flow, 
+the converging flow pushes the vesicles towards
+each other and the repulsive force is essential to keep the
 two vesicles at the separation distance.  With the converging flow
 pushing the two vesicles towards the stagnation point dynamically placed
-at the doublet center, this configuration is expected to be more stable
-than the $\theta=\pi$ configuration in the left of
-Figure~\ref{fig:InclinationAngle}(a). This is because when $\theta=\pi$
-the diverging flow is pulling the vesicles away from each other as shown
-in the illustration.  However, when the doublet inclination angle is
-fixed at $\theta=\pi/2$, the vesicle doublet stays intact if the
-adhesive force is strong enough to dominate the fluid drag.  However, it
-is possible that the diverging flow may overcome adhesion and break up
-the doublet.  It is also reasonable to expect a vesicle doublet to
-rotate from the less stable configuration $\theta=\pi$ to the more
-stable configuration $\theta=\pi/2$, so that the fluid flow is pushing
-them together rather than pulling them apart.
+at the doublet center, we expect the $\theta=\pi/2$ configuration to be more stable
+than the $\theta=\pi$ configuration. 
+%
+%This is because when $\theta=\pi$
+%the diverging flow is pulling the vesicles away from each other as shown
+%in the illustration.  However, when the doublet inclination angle is
+%fixed at $\theta=\pi/2$, the vesicle doublet stays intact if the
+%adhesive force is strong enough to dominate the fluid drag.  However, it
+%is possible that the diverging flow may overcome adhesion and break up
+%the doublet.  It is also reasonable to expect a vesicle doublet to
+%rotate from the less stable configuration $\theta=\pi$ to the more
+%stable configuration $\theta=\pi/2$, so that the fluid flow is pushing
+%them together rather than pulling them apart.
 
@@
   area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} = 0.7$,
-  the separation distance is $\delta = 0.4$, and the extensional rate is
+  the separation distance is $\delta = 0.4$, and the extension rate is
   $\chi = 0.02$ ({\em top}), $\chi=0.07$ ({\em middle}), and $\chi =
@@
 doublet with $\theta=\pi$, so that the diverging flow may be strong
-enough to pull vesicles away from the doublet.  At low extensional
+enough to pull vesicles away from the doublet.  At low extension
 rates, we expect the doublet to stay bound at the fluid trap stagnation
 point.  On the other hand, the vesicle doublet may become unstable and
-eventually separate at higher extensional rates.  Thus we expect there
-to exist a critical extensional rate $\chi_c$ above which the vesicle
+eventually separate at higher extension rates.  Thus we expect there
+to exist a critical extension rate $\chi_c$ above which the vesicle
 doublet cannot stay bound under a given adhesion potential.  Therefore,
-the dependence of the critical extensional rate $\chi_c$ on the adhesion
+the dependence of the critical extension rate $\chi_c$ on the adhesion
 potential and the mechanical vesicle properties provides a means to
@@
 We consider vesicle doublets with reduced areas 0.70, 0.75, 0.80, 0.85,
-0.90, and 0.95, all with a length of $2\pi$, and we vary the extensional
-rate, $\chi$, between $10^{-2}$ and $10^{-1}$.  Since the stagnation
+0.90, and 0.95, all with a length of $2\pi$, and we vary the extension
+rate ($\chi$) between $10^{-2}$ and $10^{-1}$.  Since the stagnation
 point can be controlled in an experimental
-setting~\cite{Johnson-Chavarria2011_EMJ}, we mimic the active control of
+setting~\cite{BentleyLeal1986_JFMa,Johnson-Chavarria2011_EMJ}, we mimic the active control of
 the microfluidic experiments by moving the center of the doublet at each
@@
 
-In Figures~\ref{fig:extensional1}, snapshots of a fluid trap containing a
-vesicle doublet of reduced area $\Delta A = 0.7$ are simulated at three
-different extensional rates.  We observe that the doublet rotates from
+Figure~\ref{fig:extensional1} shows snapshots from simulating a vesicle doublet of reduced area  $\Delta A = 0.7$
+at three different extension rates. A general feature of the doublet dynamics is that the doublet rotates from
 $\theta=\pi$ configuration towards the more stable $\theta=\pi/2$
-configuration, as shown in Figures~\ref{fig:extensional1}.  
-%
-The final configurations in Figures~\ref{fig:extensional1}
-are similar to those at $t=100$ in Figure~\ref{fig:extensionalNonsymmetric}.
+configuration.  
 %
 We also
-observe that with moderate extensional rates, the doublet falls short of
+observe that with moderate extension rates, the doublet falls short of
 aligning their long axis with the diverging direction.  Moreover, the
 final inclination angle is closest to the stable $\theta=\pi/2$ for the
-smallest extensional rates. While this doublet remains bound for all
-the considered extensional rates, a doublet with a reduced area of
-$\Delta A = 0.8$ is split with a critical extensional rate $\chi_c =
+smallest extension rates. While this doublet remains bound for all
+the considered extension rates, a doublet with a reduced area of
+$\Delta A = 0.8$ is split with a critical extension rate $\chi_c =
 0.1$ (Figure~\ref{fig:extensional3}).
@@
 %  area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} = 0.7$,
-%  the separation distance is $\delta = 0.4$, and the extensional rate is
+%  the separation distance is $\delta = 0.4$, and the extension rate is
 %  $\chi = 0.02$ ({\em top}), $\chi=0.07$ ({\em middle}), and $\chi =
@@
   is $\Delta A = 0.8$, the Hamaker constant $\mathcal{H} = 0.7$, the
-  separation distance is $\delta = 0.4$, and the extensional rate $\chi
+  separation distance is $\delta = 0.4$, and the extension rate $\chi
   = 0.1$.  The center of the vesicle, denoted with a black square, is a
@@
 
+%
+The equilibrium configuration for low extension rate $\chi=0.02$ (top row in Figure~\ref{fig:extensional1}) is
+almost identical to the equilibrium configuration for $\triangle y=0$ (top row of  Figure~\ref{fig:extensionalNonsymmetric}).
+The rotation of the vesicle doublet 
+from $\theta=\pi$ to $\theta=\pi/2$ can be understood as the transition from an unstable configuration $\theta=\pi$ to a stable configuration $\theta=\pi/2$.
+For higher extension rates (second and third rows in Figure~\ref{fig:extensional1}) the partially rotated vesicle pairs at equilibrium are
+also very similar to the case of $\triangle y=0.02$ (second row of Figure~\ref{fig:extensionalNonsymmetric}).
+Such asymmetric vesicle configuration is reminiscent of the asymmetric deformation of a single vesicle in an extensional flow \cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}.
+To gain more insight into such nonlinear dynamics, in the following we explore more physical characterization of the transition from $\theta=\pi$ to $\theta=\pi/2$ at
+different reduced area and extension rate.
+%
+
 In Figure~\ref{fig:extensionalInclinationAngle}(a), we plot the
 inclination angle of the doublet as a function of time for four
-different extensional rates,  and the final inclination angle for all
+different extension rates,  and the final inclination angle for all
 doublets that reach an equilibrium state are in
 Figure~\ref{fig:extensionalInclinationAngle}(b).  We observe that not
-only do smaller extensional rates result in smaller inclination angles,
+only do smaller extension rates result in smaller inclination angles,
 but smaller reduced areas also result in smaller inclination angles.  We
@@
 dots are scaled to the final inclination angle as defined in
-Figure~\ref{fig:InclinationAngle}.  At smaller extensional rates, the
+Figure~\ref{fig:InclinationAngle}.  At smaller extension rates, the
 vesicles come closer to aligning their long axis with the diverging
 direction.  When the doublet is broken at reduced area $\Delta A =
-0.80$, the extensional rate is sufficiently large to align the long axis
+0.80$, the extension rate is sufficiently large to align the long axis
 of the vesicle with the diverging direction and then the vesicles
@@
 Figure~\ref{fig:extensionalInclinationAngle}(c) also summarizes the
-reduced areas and extensional rates that result in a bound vesicle
+reduced areas and extension rates that result in a bound vesicle
 doublet in a fluid trap: Parameter values with a blue mark result in a
@@
   angle of a doublet formed by vesicles of reduced area $\Delta A = 0.7$
-  in an extensional flow with an extensional rate $\chi$.  (b) The final
-  inclination angle of doublets.  At larger extensional rates, the
+  in an extensional flow with an extension rate $\chi$.  (b) The final
+  inclination angle of doublets.  At larger extension rates, the
   doublet is broken by the flow.  (c) A phase diagram of the long-time
@@
   extensional flow.  Results are not reported for some of the low
-  extensional rates since the doublet had not tilted to an equilibrium
+  extension rates since the doublet had not tilted to an equilibrium
   inclination angle for the given time horizon.}
@@
 %Hamaker constant $\mathcal{H} = 0.7$, separation distance $\delta =
-%0.4$, and extensional rate $\chi = 0.07$ in
+%0.4$, and extension rate $\chi = 0.07$ in
 %Figure~\ref{fig:extensionalVorticity}.  Starting from an initial inclination angle $\theta=\pi$, the doublet 
@@
 %%
-%For small extensional rate, the rotation continues until
+%For small extension rate, the rotation continues until
 %$\theta = \pi/2$ so the doublet remains perfectly symmetric with respect
@@
 %%
-%For slightly higher extensional rate in Figure~\ref{fig:extensionalVorticity}, we observe
+%For slightly higher extension rate in Figure~\ref{fig:extensionalVorticity}, we observe
 %that the two vesicles slide against each other (around $t=280$) as the doublet rotates.
@@
 %  0.7$, the separation distance is $\delta = 0.4$, the Hamaker constant
-%  is $\mathcal{H} = 0.7$, and the extensional rate is $\chi = 0.07$.}
+%  is $\mathcal{H} = 0.7$, and the extension rate is $\chi = 0.07$.}
 %\end{figure}

### 2019-07-12 vesicle_code/docs/adhesion/adhesion.tex
worked on shear example

--- 2019-07-12 vesicle_code/docs/adhesion/adhesion.tex
@@
 shear rates, periods, and effective aspect ratio are summarized in
-Table~\ref{tbl:aspectRatio}.
-
-Since the effective aspect ratio is
-comparable for all three shear rates, this indicates that the dynamics
-of a vesicle doublet in a shear flow resembles a rigid body undergoing a
-Jeffery orbit.
+Table~\ref{tbl:aspectRatio}.  The effective aspect ratio of the doublet
+depends on both the Hamaker constant and the shear rate, and this
+indicates that the doublet's dynamics differ from those of a rigid body
+undergoing a Jeffery orbit.
+
 \begin{table}[htp]
@@
 
-We characterize the effect of the Hamaker constant and shear rate by
-determining a critical Hamaker constant, $\mathcal{H}_c$, which
-determines if the vesicles form a doublet or separate.
-
-Figure~\ref{fig:sflow_phase_diagram} indicates whether a doublet with
-reduced area $\Delta A = 0.9$ is formed (blue) or not (red) for a
-variety of shear rates, Hamaker constants, and at two different
-separation distances.  The plot includes a line of best fit between the
-stable and unstable regions.  Since the transition is linear, this
-indicates that a dimensionless number involving the ratio of the Hamaker
-constant could be used to determine if a doublet forms or not.
+Next, for several shear rates, we determine the critical Hamaker
+constant, $\mathcal{H}_c$, that determines if the vesicles form a
+doublet or separate.  Figure~\ref{fig:sflow_phase_diagram} indicates
+whether a doublet with $\Delta A = 0.9$ is formed (blue) or not (red)
+for two different separation distances.  The plot includes a line of
+best fit between the stable and unstable regions.  Since the transition
+is linear, this indicates that a dimensionless number involving the
+ratio of the Hamaker constant could be used to determine if a doublet
+forms or not.
 
@@
   \end{tabular}
-%  \includegraphics[height=0.34\textwidth]{figs/shear_adR4em1Chi5em1_ra090.pdf}
-%  \includegraphics[height=0.34\textwidth]{figs/shear_adR4em1Chi5em1_ra090_period.pdf}
   \caption{\label{fig:sflow_distance} (a) The distance between a pair of
@@
   \end{tabular}
-%  \centering
-%  \includegraphics[height=0.37\textwidth]{figs/shear_adR1em1_ra090_phaseDiagram.pdf}
-%  \includegraphics[height=0.37\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
   \caption{\label{fig:sflow_phase_diagram} Phase diagram of vesicle

### 2019-07-12 vesicle_code/docs/adhesion/adhesion.tex
yny new tex

@@
 ZiherlSvetina2007_PNAS} or
-clusters~\cite{SvetinaZiherl2008_Bioelectrochemistry,
+clusters~\cite{SvetinaZiherl2008_Bioelectrochemistry,GuWangGunzburger2016_MathBiol,
 FlormannAouane2017_SciReports}.  As a model for red blood cell (RBC)
@@
 experiments of fibrinogen-induced RBC
-aggregates~\cite{SvetinaZiherl2008_Bioelectrochemistry,
-FlormannAouane2017_SciReports}.  Using the Lennard-Jones
+aggregates~\cite{SvetinaZiherl2008_Bioelectrochemistry,GuWangGunzburger2016_MathBiol,
+FlormannAouane2017_SciReports,HooreYayaPodgorski2018_SoftMatt}.  Using the Lennard-Jones
 (L.-J.)~potential for point-point interaction between two vesicle
@@
 between a vesicle and a solid has been extensively studied with more
-focus on the static equilibrium shapes~\cite{Seifert1990_PRA,
+focus on the static equilibrium shapes~\cite{Seifert1990_PRA,BernardGuedeau-Boudeville2000_Langmuir,
 ShiFengGao2006_ActaMechSin, LinFreund2007_IntJSolidsStructures,

### 2019-07-12 vesicle_code/docs/adhesion/adhesion.tex
put in intrinsic viscosity numbers

@@
 Figure~\ref{fig:shearIntrinsicViscosity}(a), we compare the intrinsic
-viscosity of a single tank-treading vesicle to a doublet.  To validate
-our simulations, we superimpose (black marks) the intrinsic viscosity
-calculated by Ghigliotti {\em et
+viscosity of a single tank-treading vesicle to a doublet with Hamaker
+constant $\mathcal{H} = 0.7$, separation distance $\delta = 0.4$, and
+shear rate $\chi = 0.5$.  To validate our simulations, we superimpose
+(black marks) the intrinsic viscosity calculated by Ghigliotti {\em et
 al.}~\cite{GhigliottiBibenMisbah2010_JFM}.  The presence of the doublet
-slightly increases the intrinsic viscosity at all the reduced areas.  To
-further characterize the effect of adhesion, in
+slightly increases the intrinsic viscosity at all the reduced areas.
+We also compute the intrinsic viscosity of a doublet with $\Delta A =
+0.9$, $\chi = 0.5$, and $\mathcal{H} = 2.1$.  Again, this doublet has a
+similar period to the case $\mathcal{H} = 2.1$.  At this larger Hamaker
+constant, the effective viscosity increases slightly from $1.97$ to
+$2.06$.
+
+To further characterize the effect of adhesion, in
 Figure~\ref{fig:shearIntrinsicViscosity}(b) we decompose the intrinsic
@@
 intrinsic viscosity is largest for vesicles with small reduced areas.
+We also decompose the intrinsic viscosity contributions of the doublet
+with $\mathcal{H} = 2.1$ and $\Delta A = 0.9$.  When compared with the
+smaller Hamaker constant, the intrinsic viscosity contribution due to
+bending and tension is reduced from $1.85$ to $1.71$, and the
+contribution due to adhesion is increased from $0.12$ to $0.36$.
+Therefore, as the Hamaker constant increases, the increase in the
+intrinsic viscosity is due to the adhesive force rather than the bending
+and tension.
 

### 2019-07-15 vesicle_code/docs/adhesion/adhesion.tex
added a small todo
working on revisions

@@
 vesicle suspension. Such studies will provide useful insight into the
-rheology of blood flow and how to use nano solutes to control the
-hypertension by adjusting the adhesive interactions between RBCs.
+rheology of blood flow~\cite{chi-usa-del-gre-nan-gue1967} and how to use
+nano solutes to control the hypertension by adjusting the adhesive
+interactions between RBCs.
+\todo[inline]{Add references by Brust aet al.~ and Claveria et al}
 
@@
 membranes with adhesion.  However, adhesive interactions between RBCs
-lead to RBC clusters that are expected to alter the
-rheological properties of the RBC suspension~\cite{NeuMeiselman2002_BJ,
+lead to RBC clusters that are expected to alter the rheological
+properties of the RBC suspension~\cite{NeuMeiselman2002_BJ,
 SvetinaZiherl2008_Bioelectrochemistry}. Hydrodynamic simulations of
@@
 investigate the hydrodynamics of adhesive vesicles in flow conditions
-common in microfluidics such as a planar shear flow and an
-extensional flow.
+common in microfluidics such as a planar shear flow and an extensional
+flow.
 
@@
 planar shear flow with a long separation
-distance~\cite{GiresDankerMisbah2012_PRE}. They found that the vesicle
-interaction could be either attractive or repulsive depending on the
-organization of the two vesicles relative to the shear flow. To the best
-of authors' knowledge, the effects of close-range vesicle adhesion on
-their hydrodynamics under an external flow have not been studied and
+distance~\cite{GiresDankerMisbah2012_PRE}.  \todo[inline]{Also cite
+Gires et al.~Physics of Fluids 26, 013304, 2014} They found that the
+vesicle interaction could be either attractive or repulsive depending on
+the organization of the two vesicles relative to the shear flow. To the
+best of authors' knowledge, the effects of close-range vesicle adhesion
+on their hydrodynamics under an external flow have not been studied and
 quantified. The goal of this work is to use state-of-the-art boundary
@@
 \end{table}
-\todo[inline]{period results with $\delta$ = 0.1, 0.2, 0.3, 0.4 so that
-we can simply say how it affects the period}
 
@@
 0.9$, $\chi = 0.5$, and $\mathcal{H} = 2.1$.  Again, this doublet has a
-similar period to the case $\mathcal{H} = 2.1$.  At this larger Hamaker
+similar period to the case $\mathcal{H} = 0.7$. At this larger Hamaker
 constant, the effective viscosity increases slightly from $1.97$ to
@@
 
-BQ and YNY contributed equally to model development, code development,
-and simulations.  All authors contributed equally to writing the
+BQ and YNY contributed equally to model development and simulations. BQ
+developed the code. All authors contributed equally to writing the
 manuscript.
@@
 \bibliography{refs}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{\label{sec:level2}Second-level heading: Formatting}
-%
-%This file may be formatted in either the \texttt{preprint} or
-%\texttt{reprint} style. \texttt{reprint} format mimics final journal output. 
-%Either format may be used for submission purposes. \texttt{letter} sized paper should
-%be used when submitting to APS journals.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsubsection{Wide text (A level-3 head)}
-%The \texttt{widetext} environment will make the text the width of the
-%full page, as on page~\pageref{eq:wideeq}. (Note the use the
-%\verb+\pageref{#1}+ command to refer to the page number.) 
-%\paragraph{Note (Fourth-level head is run in)}
-%The width-changing commands only take effect in two-column formatting. 
-%There is no effect if text is in a single column.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{\label{sec:citeref}Citations and References}
-%
-%
-%
-%A citation in text uses the command \verb+\cite{#1}+ or
-%\verb+\onlinecite{#1}+ and refers to an entry in the bibliography. 
-%An entry in the bibliography is a reference to another document.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsubsection{Citations}
-
-%Because REV\TeX\ uses the \verb+natbib+ package of Patrick Daly, 
-%the entire repertoire of commands in that package are available for your document;
-%see the \verb+natbib+ documentation for further details. Please note that
-%REV\TeX\ requires version 8.31a or later of \verb+natbib+.
-%
-%\paragraph{Syntax}
-%The argument of \verb+\cite+ may be a single \emph{key}, 
-%or may consist of a comma-separated list of keys.
-%The citation \emph{key} may contain 
-%letters, numbers, the dash (-) character, or the period (.) character. 
-%New with natbib 8.3 is an extension to the syntax that allows for 
-%a star (*) form and two optional arguments on the citation key itself.
-%The syntax of the \verb+\cite+ command is thus (informally stated)
-%\begin{quotation}\flushleft\leftskip1em
-%\verb+\cite+ \verb+{+ \emph{key} \verb+}+, or\\
-%\verb+\cite+ \verb+{+ \emph{optarg+key} \verb+}+, or\\
-%\verb+\cite+ \verb+{+ \emph{optarg+key} \verb+,+ \emph{optarg+key}\ldots \verb+}+,
-%\end{quotation}\noindent
-%where \emph{optarg+key} signifies 
-%\begin{quotation}\flushleft\leftskip1em
-%\emph{key}, or\\
-%\texttt{*}\emph{key}, or\\
-%\texttt{[}\emph{pre}\texttt{]}\emph{key}, or\\
-%\texttt{[}\emph{pre}\texttt{]}\texttt{[}\emph{post}\texttt{]}\emph{key}, or even\\
-%\texttt{*}\texttt{[}\emph{pre}\texttt{]}\texttt{[}\emph{post}\texttt{]}\emph{key}.
-%\end{quotation}\noindent
-%where \emph{pre} and \emph{post} is whatever text you wish to place 
-%at the beginning and end, respectively, of the bibliographic reference
-%(see Ref.~[\onlinecite{witten2001}] and the two under Ref.~[\onlinecite{feyn54}]).
-%(Keep in mind that no automatic space or punctuation is applied.)
-%It is highly recommended that you put the entire \emph{pre} or \emph{post} portion 
-%within its own set of braces, for example: 
-%\verb+\cite+ \verb+{+ \texttt{[} \verb+{+\emph{text}\verb+}+\texttt{]}\emph{key}\verb+}+.
-%The extra set of braces will keep \LaTeX\ out of trouble if your \emph{text} contains the comma (,) character.
-%
-%The star (*) modifier to the \emph{key} signifies that the reference is to be 
-%merged with the previous reference into a single bibliographic entry, 
-%a common idiom in APS and AIP articles (see below, Ref.~[\onlinecite{epr}]). 
-%When references are merged in this way, they are separated by a semicolon instead of 
-%the period (full stop) that would otherwise appear.
-%
-%\paragraph{Eliding repeated information}
-%When a reference is merged, some of its fields may be elided: for example, 
-%when the author matches that of the previous reference, it is omitted. 
-%If both author and journal match, both are omitted.
-%If the journal matches, but the author does not, the journal is replaced by \emph{ibid.},
-%as exemplified by Ref.~[\onlinecite{epr}]. 
-%These rules embody common editorial practice in APS and AIP journals and will only
-%be in effect if the markup features of the APS and AIP Bib\TeX\ styles is employed.
-%
-%\paragraph{The options of the cite command itself}
-%Please note that optional arguments to the \emph{key} change the reference in the bibliography, 
-%not the citation in the body of the document. 
-%For the latter, use the optional arguments of the \verb+\cite+ command itself:
-%\verb+\cite+ \texttt{*}\allowbreak
-%\texttt{[}\emph{pre-cite}\texttt{]}\allowbreak
-%\texttt{[}\emph{post-cite}\texttt{]}\allowbreak
-%\verb+{+\emph{key-list}\verb+}+.
 

### 2019-07-16 vesicle_code/docs/adhesion/adhesion.tex
yny changed extensional section

@@
 similar to a surfactant-laden viscous drop under a planar extensional flow \cite{JanssenBoonAgterof1997_AIChE,HuPineLeal2000_PoF}.
-
-To investigate how two vesicles interact with each other in a planar extensional flow,
-at the beginning of the simulations (left panels in Figure~\ref{fig:extensionalNonsymmetric})
+To our knowledge no studies on the interactions between two vesicles in an extensional flow are available in the literature.
+In the following we first illustrate how two vesicles interact with each other in a planar extensional flow. We then illustrate how the adhesion strength between membranes can be
+measured non-intrusively by using the fluid trap.
+
+%To investigate how two vesicles interact with each other in a planar extensional flow,
+At the beginning of the first set of simulations (left panels in Figure~\ref{fig:extensionalNonsymmetric})
 we place a vesicle at $(x,y)=(0,0)$, 
@@
 The adhesion strength ${\cal H} = 0.7$ for the top three rows, and ${\cal H} =0.6$ for the bottom row.
+The color coding is the membrane tension with the color bar on the right of each row.
 
@@
 and reach a steady configuration that is symmetric with respect to the stagnation point 
-(square mark in Figure \ref{fig:extensionalNonsymmetric}).
+(square marks in the top row of Figure \ref{fig:extensionalNonsymmetric}).
 
@@
 
-Results in Figure~\ref{fig:extensionalNonsymmetric} illustrate that
-in an extensional flow vesicles are prone to move away from the stagnation point:
+Two main observations can be made of results in Figure~\ref{fig:extensionalNonsymmetric}:
+(1) The membrane tension is highly non-uniform on the vesicles, leading to a significant Marangoni stress along the membrane as in the case of a surfactant-laden drop
+at the center of an extensional flow. Thus it is reasonable to expect that the flow around the vesicles is significantly altered.
+(2) In an extensional flow vesicles are prone to move away from the stagnation point.
 A small initial vertical displacement $\triangle y$ in one  of the vesicles causes both vesicles to not only rotate but also move away from the

### 2019-07-17 vesicle_code/docs/adhesion/adhesion.tex
adding tension to extensional plots

@@
   \includegraphics[height = 0.2\textwidth,trim={1cm 0cm 1cm 0cm},clip]
-    {figs/extensional_displacement0_adS7em1_image01.png}
+    {figs/extensional_displacement0_adS7em1_tension_image01.png}
   \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
-    {figs/extensional_displacement0_adS7em1_image02.png}
+    {figs/extensional_displacement0_adS7em1_tension_image02.png}
   \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
-    {figs/extensional_displacement0_adS7em1_image03.png}
+    {figs/extensional_displacement0_adS7em1_tension_image03.png}
   \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
-    {figs/extensional_displacement0_adS7em1_image04.png}
-  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
-    {figs/extensional_displacement0_adS7em1_image05.png} \\
+    {figs/extensional_displacement0_adS7em1_tension_image04.png}
+  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 1cm 0cm},clip]
+    {figs/extensional_displacement0_adS7em1_tension_image05.png} \\
 

### 2019-07-17 vesicle_code/docs/adhesion/adhesion.tex
first draft on new Figure 6

@@
     {figs/extensional_displacement0_adS7em1_tension_image04.png}
-  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 1cm 0cm},clip]
+  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 0cm 0cm},clip]
     {figs/extensional_displacement0_adS7em1_tension_image05.png} \\
@@
   \includegraphics[height = 0.2\textwidth,trim={1cm 0cm 1cm 0cm},clip]
-    {figs/extensional_displacement2em2_adS7em1_image01.png}
+    {figs/extensional_displacement2em2_adS7em1_tension_image01.png}
   \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
-    {figs/extensional_displacement2em2_adS7em1_image02.png}
+    {figs/extensional_displacement2em2_adS7em1_tension_image02.png}
   \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
-    {figs/extensional_displacement2em2_adS7em1_image03.png}
+    {figs/extensional_displacement2em2_adS7em1_tension_image03.png}
   \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
-    {figs/extensional_displacement2em2_adS7em1_image04.png}
+    {figs/extensional_displacement2em2_adS7em1_tension_image04.png}
+  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 0cm 0cm},clip]
+    {figs/extensional_displacement2em2_adS7em1_tension_image05.png} \\
+
+  \includegraphics[height = 0.2\textwidth,trim={1cm 0cm 1cm 0cm},clip]
+    {figs/extensional_displacement1em1_adS7em1_tension_image01.png}
   \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
-    {figs/extensional_displacement2em2_adS7em1_image05.png} \\
+    {figs/extensional_displacement1em1_adS7em1_tension_image02.png}
+  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
+    {figs/extensional_displacement1em1_adS7em1_tension_image03.png}
+  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
+    {figs/extensional_displacement1em1_adS7em1_tension_image04.png}
+  \includegraphics[height = 0.2\textwidth,trim={3.5cm 0cm 0cm 0cm},clip]
+    {figs/extensional_displacement1em1_adS7em1_tension_image05.png} \\
 
   \includegraphics[height = 0.2\textwidth,trim={1cm 0cm 1cm 0cm},clip]
-    {figs/extensional_displacement1em1_adS7em1_image01.png}
+    {figs/extensional_displacement1em1_adS6em1_tension_image01.png}
   \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
-    {figs/extensional_displacement1em1_adS7em1_image02.png}
+    {figs/extensional_displacement1em1_adS6em1_tension_image02.png}
   \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
-    {figs/extensional_displacement1em1_adS7em1_image03.png}
+    {figs/extensional_displacement1em1_adS6em1_tension_image03.png}
   \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
-    {figs/extensional_displacement1em1_adS7em1_image04.png}
-  \includegraphics[height = 0.2\textwidth,trim={3.5cm 0cm 4cm 0cm},clip]
-    {figs/extensional_displacement1em1_adS7em1_image05.png} \\
-
-  \includegraphics[height = 0.2\textwidth,trim={1cm 0cm 1cm 0cm},clip]
-    {figs/extensional_displacement1em1_adS6em1_image01.png}
-  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
-    {figs/extensional_displacement1em1_adS6em1_image02.png}
-  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
-    {figs/extensional_displacement1em1_adS6em1_image03.png}
-  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
-    {figs/extensional_displacement1em1_adS6em1_image04.png}
-  \includegraphics[height = 0.2\textwidth,trim={3.5cm 0cm 4cm 0cm},clip]
-    {figs/extensional_displacement1em1_adS6em1_image05.png}
-  \caption{\label{fig:extensionalNonsymmetric}Dynamics of a vesicle pair in a planar extensional flow.
-${\cal H} = 0.7$ for the first three rows, and ${\cal H}=0.6$ for the bottom row.
-From top to bottom, the initial vertical displacement $\triangle y=0$, 0.02, 0.1 and 0.1.
-The reduced area is ???, the extension rate $\chi = ???$ and the adhesion distance $\delta = ???$.
-}
+    {figs/extensional_displacement1em1_adS6em1_tension_image04.png}
+  \includegraphics[height = 0.2\textwidth,trim={3.5cm 0cm 0cm 0cm},clip]
+    {figs/extensional_displacement1em1_adS6em1_tension_image05.png}
+  \caption{\label{fig:extensionalNonsymmetric}Dynamics of a vesicle pair
+  in a planar extensional flow. ${\cal H} = 0.7$ for the first three
+  rows, and ${\cal H}=0.6$ for the bottom row. From top to bottom, the
+  initial vertical displacement $\triangle y=0$, 0.02, 0.1 and 0.1. The
+  reduced area is $\Delta A = 0.75$, the extensional rate $\chi = ???$
+  \todo[inline]{Yuan: Can you look and see what extensional rates you
+  did for the runs that do not indicate the rate in the file name?} and
+  the adhesion distance $\delta = 0.4$. }
   \end{figure}

### 2019-07-17 vesicle_code/docs/adhesion/adhesion.tex
updated Figures 8 and 9

@@
 \begin{figure}[htp]
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}\\
-   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png} \\
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
+  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
+    {figs/extensional_adR4em1adS7em1Chi2em2_ra070_tension_image01.png}
+  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
+    {figs/extensional_adR4em1adS7em1Chi2em2_ra070_tension_image02.png}
+  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
+    {figs/extensional_adR4em1adS7em1Chi2em2_ra070_tension_image03.png}
+  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
+    {figs/extensional_adR4em1adS7em1Chi2em2_ra070_tension_image04.png}
+  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 3cm 1cm},clip]
+    {figs/extensional_adR4em1adS7em1Chi2em2_ra070_tension_image05.png}
+    \\
+  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
+    {figs/extensional_adR4em1adS7em1Chi7em2_ra070_tension_image01.png}
+  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
+    {figs/extensional_adR4em1adS7em1Chi7em2_ra070_tension_image02.png}
+  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
+    {figs/extensional_adR4em1adS7em1Chi7em2_ra070_tension_image03.png}
+  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
+    {figs/extensional_adR4em1adS7em1Chi7em2_ra070_tension_image04.png}
+  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 3cm 1cm},clip]
+    {figs/extensional_adR4em1adS7em1Chi7em2_ra070_tension_image05.png}
+    \\
+  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
+    {figs/extensional_adR4em1adS7em1Chi1em1_ra070_tension_image01.png}
+  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
+    {figs/extensional_adR4em1adS7em1Chi1em1_ra070_tension_image02.png}
+  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
+    {figs/extensional_adR4em1adS7em1Chi1em1_ra070_tension_image03.png}
+  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
+    {figs/extensional_adR4em1adS7em1Chi1em1_ra070_tension_image04.png}
+  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 3cm 1cm},clip]
+    {figs/extensional_adR4em1adS7em1Chi1em1_ra070_tension_image05.png}
   \caption{\label{fig:extensional1} A vesicle doublet in an extensional
@@
 
-%\begin{figure}[htp]
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}\\
-%   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png} \\
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
-%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
-%  \caption{\label{fig:extensional1} A vesicle doublet in an extensional
-%  flow with an initial inclination angle $\theta=\pi$.  The reduced
-%  area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} = 0.7$,
-%  the separation distance is $\delta = 0.4$, and the extension rate is
-%  $\chi = 0.02$ ({\em top}), $\chi=0.07$ ({\em middle}), and $\chi =
-%  0.1$ ({\em bottom}).  The center of the vesicle, denoted with a black
-%  square, is the stagnation point.}
-%  \end{figure}
-
  \begin{figure}
-    \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
-  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
+  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
+    {figs/extensional_adR4em1adS7em1Chi1em1_ra080_tension_image01.png}
+  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
+    {figs/extensional_adR4em1adS7em1Chi1em1_ra080_tension_image02.png}
+  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
+    {figs/extensional_adR4em1adS7em1Chi1em1_ra080_tension_image03.png}
+  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
+    {figs/extensional_adR4em1adS7em1Chi1em1_ra080_tension_image04.png}
+  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 3cm 1cm},clip]
+    {figs/extensional_adR4em1adS7em1Chi1em1_ra080_tension_image05.png}
   \caption{\label{fig:extensional3} A vesicle doublet in an extensional

### 2019-07-17 vesicle_code/docs/adhesion/adhesion.tex
yny adhesion 01

--- 2019-07-17 vesicle_code/docs/adhesion/adhesion.tex
@@
   initial vertical displacement $\triangle y=0$, 0.02, 0.1 and 0.1. The
-  reduced area is $\Delta A = 0.75$, the extensional rate $\chi = ???$
-  \todo[inline]{Yuan: Can you look and see what extensional rates you
-  did for the runs that do not indicate the rate in the file name?} and
-  the adhesion distance $\delta = 0.4$. }
+  reduced area is $\Delta A = 0.75$, the extensional rate $\chi = 0.09$
+%  \todo[inline]{Yuan: Can you look and see what extensional rates you
+%  did for the runs that do not indicate the rate in the file name?} 
+  and the adhesion distance $\delta = 0.4$. }
   \end{figure}

### 2019-07-17 vesicle_code/docs/adhesion/adhesion.tex
small change
working on revisions

@@
 \label{sec:eflow} 
+\todo[inline]{Do we discuss the slow tank treading motion when the
+vesicles reach steady state.  Reviewer 2 had a comment about this}
 
@@
 We consider two vesicles suspended in the shear flow $\uu = \chi(y,0)$,
-where $\chi$ is the shear rate.  The initial placement of the vesicles
-is chosen so that the flow dives them towards one another.  In the
-absence of adhesion, once the vesicles are sufficiently close, they are
-deflected to opposite sides of the $y$ axis, pass one another, and then
-separate.  However, in the presence of adhesion, the vesicles can form a
-doublet for certain values of the separation distance $\delta$, Hamaker
-constant $\mathcal{H}$, shear rate $\chi$, and reduced area $\Delta A$.
-At all reduced areas, the vesicles have a length of $2\pi$ to be
-consistent with simulations in previous sections.
+where $\chi$ is the shear rate.  To be consistent with simlulations in
+previous sections, the vesicles have a length of $2\pi$ for all reduced
+areas.  The initial placement of the vesicles is chosen so that the flow
+dives them towards one another.  In the absence of adhesion, once the
+vesicles are sufficiently close, they are deflected to opposite sides of
+the $y$ axis, pass one another, and then separate.  However, in the
+presence of adhesion, the vesicles can form a doublet for certain values
+of the separation distance $\delta$, Hamaker constant $\mathcal{H}$,
+shear rate $\chi$, and reduced area $\Delta A$.  If a doublet does form,
+then it undergoes a periodic motion with a period that depends on the
+same parameters.
 
@@
 the adhesive force is strongest.  The two values for the Hamaker
-constant are chosen since the vesicles dynamics have similar periods of
-$t^* \approx 42$.  For both the Hamaker constants, the vesicles in the
-doublet move in tandem with a tank-reading motion that is much slower
-than the tank-treading motion that occurs in the absense of ahdesion.
-However, the dynamics of a single period for theses two Hamaker
-constants differ significantly.  For the weaker adhesive force, the
-individual vesicles undergo a sliding motion as they pass one another,
-and the contact region between the vesicles moves along the vesicle
-throughout the simulation (Figure~\ref{fig:doublet090-weakAdhesion}).
-However, at larger Hamaker constants, once the contact region is formed,
-the doublet maintains the same structure and undergoes a tumbling
-dynamic similar to a Jeffery orbit.
+constant are chosen since the period of the dynamics of the doublets are
+both $t^* \approx 42$.  For both the Hamaker constants, the vesicles in
+the doublet move in tandem with a tank-reading motion that is much
+slower than the tank-treading motion that occurs in the absense of
+ahdesion.  However, the dynamics of a single period for theses two
+Hamaker constants differ significantly.  For the weaker adhesive force,
+the individual vesicles undergo a sliding motion as they pass one
+another (Figure~\ref{fig:doublet090-weakAdhesion}).  However, at larger
+Hamaker constants, once the contact region is formed, the doublet
+maintains the same structure and undergoes a tumbling dynamic similar to
+a Jeffery orbit.
 
@@
   \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image10.png}
-  \caption{\label{fig:doublet090-weakAdhesion} The formation of a
-  doublet in a shear flow.  The reduced area is $\Delta A = 0.9$, the
-  Hamaker constant is $\mathcal{H}=0.7$, the separation distance is
-  $\delta = 0.4$, and the shear rate is $\chi=0.5$.}
+  \caption{\label{fig:doublet090-weakAdhesion} The formation of a weakly
+  adhered doublet in a shear flow.  The reduced area is $\Delta A =
+  0.9$, the Hamaker constant is $\mathcal{H}=0.7$, the separation
+  distance is $\delta = 0.4$, and the shear rate is $\chi=0.5$.  The
+  interaction between the two vesicles is a sliding motion, and the
+  dynamics has a period of about 42.}
 \end{figure}
@@
   \caption{\label{fig:doublet090-strongAdhesion} The formation of a
-  doublet in a shear flow.  The reduced area is $\Delta A = 0.9$, the
-  Hamaker constant is $\mathcal{H}=2.1$, the separation distance is
-  $\delta = 0.4$, and the shear rate is $\chi=0.5$.}
+  strongly adhered doublet in a shear flow.  The reduced area is $\Delta
+  A = 0.9$, the Hamaker constant is $\mathcal{H}=2.1$, the separation
+  distance is $\delta = 0.4$, and the shear rate is $\chi=0.5$.  Since
+  the contact region is unchanged throughout the simulation, the
+  dynamics of the doublet resembles a rigid body motion with a period of
+  about 42.}
 \end{figure}
 
-To further understand the nature of the doublet,
-Figure~\ref{fig:sflow_distance}(a) shows the minimum distance between
-the two vesicles as a function of time.  For Hamaker constants less than
-a critical value, $\mathcal{H}_c$, the adhesive force is not strong
-enough to form a doublet, and the distance between the vesicles grows
-with time (red curves).  However, when $\mathcal{H} > \mathcal{H}_c$,
-the adhesive force is sufficiently strong to bind the vesicles into a
-doublet, and then the doublet undergoes a periodic motion (blue curves).
-In Figure~\ref{fig:sflow_distance}(b), we plot the time required for the
-doublet to make a complete revolution for three different shear rates.
+To further understand the formation of the doublet, we compute the
+distance between two vesicles with reduced area $\Delta A = 0.9$,
+separation distance $\delta = 0.5$, and shear rate $\chi = 0.5$.
+Figure~\ref{fig:sflow_distance}(a) shows this minimum distance as a
+function of time for varying Hamaker constants.  For Hamaker constants
+less than a critical value, $\mathcal{H}_c$, the adhesive force is not
+strong enough to form a doublet, and the distance between the vesicles
+grows with time (red curves).  However, when $\mathcal{H} >
+\mathcal{H}_c$, the adhesive force is sufficiently strong to bind the
+vesicles into a doublet, and then the doublet undergoes a periodic
+motion (blue curves).  In Figure~\ref{fig:sflow_distance}(b), we plot
+the time required for the doublet to make a complete revolution for
+three different shear rates and two different separation distances.
 Initially, as the shear rate increases, the period decreases.  However,
 the transition from the weakly adhesive doublet
-(Figure~\ref{fig:doublet090-weakAdhesion} to the stronger adhesive
+(Figure~\ref{fig:doublet090-weakAdhesion}) to the stronger adhesive
 doublet (Figure~\ref{fig:doublet090-strongAdhesion}) results in an
-increase in the period.  However, once the Hamaker constant is
-sufficiently strong that the contact region remains fixed throughout the
-dynamics, the period of the doublet again decreases as the shear rate
-increases.
+increase in the period.  Once the Hamaker constant is sufficiently
+strong that the contact region remains fixed throughout the dynamics,
+the period of the doublet again decreases as the shear rate increases.
 
@@
 effective aspect ratios depend on both the Hamaker constant and the
-shear rate, indicating that the reported Hamaker constants, the dynamics
-of the doublet differ from that of a Jeffery orbit.}
+shear rate, indicating that for the reported Hamaker constants, the
+dynamics of the doublet differ from that of a Jeffery orbit.}
 \end{table}
@@
 is linear, this indicates that a dimensionless number involving the
-ratio of the Hamaker constant could be used to determine if a doublet
-forms or not.
+ratio of the Hamaker constant and shear rate could be used to determine
+if a doublet forms or not.
 
@@
   the separation distance is $\delta = 0.4$.  The different lines
-  correspond to different shear rates.}
+  correspond to different shear rates and separation distances.}
 \end{figure}
@@
 constant, the effective viscosity increases slightly from $1.97$ to
-$2.06$.
-
-To further characterize the effect of adhesion, in
+$2.06$.  To further characterize the effect of adhesion, in
 Figure~\ref{fig:shearIntrinsicViscosity}(b) we decompose the intrinsic
-viscosity into the contributions from the bending and tension (blue),
-and the contribution from the adhesion (red).  We also superimpose the
-intrinsic viscosity of a single tank-treading vesicle (dashed curve) to
+viscosity into the contributions from the bending and tension (black),
+and the contribution from the adhesion (green).  We also superimpose the
+intrinsic viscosity of a single tank-treading vesicle (blue) to
 demonstrate that the bending and tension of the doublet behave

### 2019-07-17 vesicle_code/docs/adhesion/revisions/reviewer2.tex
working on revisions
small edits

@@
 \begin{itemize}
-  \item rebuttal
+  \item The paper by Hoore et al.~has been added to the introduction.
 \end{itemize}
@@
 \begin{itemize}
-  \item rebuttal
+  \item \todo[inline]{Other 2 papers of Misbah's group}
+  \item The reference of Chien et al.~has been added.
 \end{itemize}
@@
 \begin{itemize}
-  \item rebuttal
+  \item In Figure 3 left, the color is not the adhesive force---it is the
+    tension.  This is mentioned in the caption.  However, in the plot on
+    the right that shows a zoomed in view of the contact zone, the
+    adhesion force is plotted using the same method as in Figure 1.  In
+    this case, the color is yellow only if the vesicle is sufficiently
+    close to the other.
 \end{itemize}
@@
 \begin{itemize}
-  \item rebuttal
+  \item We have removed Figure 10 from the previous version.
+
+  \item There is a very slow tank-treading motion \todo[inline]{Discuss
+    this further}
 \end{itemize}
@@
 
-  \item For each of the shear rates and the largest Hamaker constant we
-    consider, we compute an effective aspect ratio which is the aspect
-    ratio of a rigid body ellipse that would undergo the same period in
-    the same shear flow.  The results indicate that the effective aspect
-    ratio is independent of the shear rate, and this suggests that the
-    dynamics of the doublet has similar properties to a rigid body
-    undergoing a Jeffery orbit. 
+  \item For each of the shear rates and two of the Hamaker constants
+    that we consider, we compute an effective aspect ratio which is the
+    aspect ratio of a rigid body ellipse that would undergo the same
+    period in the same shear flow.  The results indicate that the
+    effective aspect ratio is independent of the shear rate, and this
+    suggests that the dynamics of the doublet has similar properties to
+    a rigid body undergoing a Jeffery orbit. 
 \end{itemize}
@@
 
+  \item We also report numbers for the intrinsic viscosity for a larger
+    Hamaker constant that has a similar period to $\mathcal{H} = 0.7$.
+    The result is an increase in the intrinsic viscosity due to
+    adhesion, a decrease in the intrinsic viscosity due to bending and
+    tension, and a net increase in the intrinsic viscosity.
+
   \item The total force $\xxi$ is the sum of a bending, tension, and

### 2019-07-17 vesicle_code/docs/adhesion/adhesion.tex
yny changes for adhesion.tex

--- 2019-07-17 vesicle_code/docs/adhesion/adhesion.tex
@@
   initial vertical displacement $\triangle y=0$, 0.02, 0.1 and 0.1. The
-  reduced area is $\Delta A = 0.75$, the extensional rate $\chi = 0.09$
-%  \todo[inline]{Yuan: Can you look and see what extensional rates you
+  reduced area is $\Delta A = 0.75$, the extension rate $\dot\epsilon= 0.09$
+%  \todo[inline]{Yuan: Can you look and see what extension rates you
 %  did for the runs that do not indicate the rate in the file name?} 
@@
 Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  Here we focus on a
-planar extensional flow  where the fluid velocity field $\uu=\chi(-x,y)$ is centered at the 
+planar extensional flow  where the fluid velocity field $\uu=\dot\epsilon(-x,y)$ is centered at the 
 the origin ($(x,y)=(0,0)$), the stagnation point where the fluid flow converges horizontally and diverges vertically.
 Placed symmetrically at the stagnation point of an extensional flow,
-a single vesicle may remain steady and symmetric for low extension rate $\chi$.
-For sufficiently large extension rate $\chi$ the vesicle may undergo asymmetric deformation \cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}, 
+a single vesicle may remain steady and symmetric for low extension rate $\dot\epsilon$.
+For sufficiently large extension rate $\dot\epsilon$ the vesicle may undergo asymmetric deformation \cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}, 
 similar to a surfactant-laden viscous drop under a planar extensional flow \cite{JanssenBoonAgterof1997_AIChE,HuPineLeal2000_PoF}.
@@
 The adhesion strength ${\cal H} = 0.7$ for the top three rows, and ${\cal H} =0.6$ for the bottom row.
-The color coding is the membrane tension with the color bar on the right of each row.
+The color coding is the membrane tension with the color bar on the right of each row. We note that the negative membrane tension in an
+extensional flow is consistent with the speculation for a wrinkled membrane in the elongational flow \cite{KantslerSegreSteinberg2007_PRL}.
 
@@
   the separation distance is $\delta = 0.4$, and the extension rate is
-  $\chi = 0.02$ ({\em top}), $\chi=0.07$ ({\em middle}), and $\chi =
+  $\dot\epsilon = 0.02$ ({\em top}), $\dot\epsilon=0.07$ ({\em middle}), and $\dot\epsilon =
   0.1$ ({\em bottom}).  The center of the vesicle, denoted with a black
@@
 eventually separate at higher extension rates.  Thus we expect there
-to exist a critical extension rate $\chi_c$ above which the vesicle
+to exist a critical extension rate $\dot\epsilon_c$ above which the vesicle
 doublet cannot stay bound under a given adhesion potential.  Therefore,
-the dependence of the critical extension rate $\chi_c$ on the adhesion
+the dependence of the critical extension rate $\dot\epsilon_c$ on the adhesion
 potential and the mechanical vesicle properties provides a means to
@@
 0.90, and 0.95, all with a length of $2\pi$, and we vary the extension
-rate ($\chi$) between $10^{-2}$ and $10^{-1}$.  Since the stagnation
+rate ($\dot\epsilon$) between $10^{-2}$ and $10^{-1}$.  Since the stagnation
 point can be controlled in an experimental
@@
 the considered extension rates, a doublet with a reduced area of
-$\Delta A = 0.8$ is split with a critical extension rate $\chi_c =
+$\Delta A = 0.8$ is split with a critical extension rate $\dot\epsilon_c =
 0.1$ (Figure~\ref{fig:extensional3}).
@@
   is $\Delta A = 0.8$, the Hamaker constant $\mathcal{H} = 0.7$, the
-  separation distance is $\delta = 0.4$, and the extension rate $\chi
+  separation distance is $\delta = 0.4$, and the extension rate $\dot\epsilon
   = 0.1$.  The center of the vesicle, denoted with a black square, is a
@@
 %
-The equilibrium configuration for low extension rate $\chi=0.02$ (top row in Figure~\ref{fig:extensional1}) is
+The equilibrium configuration for low extension rate $\dot\epsilon=0.02$ (top row in Figure~\ref{fig:extensional1}) is
 almost identical to the equilibrium configuration for $\triangle y=0$ (top row of  Figure~\ref{fig:extensionalNonsymmetric}).
@@
 of the vesicle with the diverging direction and then the vesicles
-separate (Figure~\ref{fig:extensional3}).  For very low extensional
+separate (Figure~\ref{fig:extensional3}).  For very low extension
 rates, the time horizon is insufficient for the doublet to reach an
@@
   angle of a doublet formed by vesicles of reduced area $\Delta A = 0.7$
-  in an extensional flow with an extension rate $\chi$.  (b) The final
+  in an extensional flow with an extension rate $\dot\epsilon$.  (b) The final
   inclination angle of doublets.  At larger extension rates, the

### 2019-07-17 vesicle_code/docs/adhesion/adhesion.tex
working on edits

--- 2019-07-17 vesicle_code/docs/adhesion/adhesion.tex
@@
   \caption{\label{fig:extensionalNonsymmetric}Dynamics of a vesicle pair
-  in a planar extensional flow. ${\cal H} = 0.7$ for the first three
-  rows, and ${\cal H}=0.6$ for the bottom row. From top to bottom, the
-  initial vertical displacement $\triangle y=0$, 0.02, 0.1 and 0.1. The
-  reduced area is $\Delta A = 0.75$, the extensional rate $\chi = 0.09$
-%  \todo[inline]{Yuan: Can you look and see what extensional rates you
-%  did for the runs that do not indicate the rate in the file name?} 
-  and the adhesion distance $\delta = 0.4$. }
+  in a planar extensional flow. The Hamaker constant is ${\cal H} = 0.7$
+  for the first three rows, and ${\cal H}=0.6$ for the bottom row. From
+  top to bottom, the initial vertical displacement is $\Delta y=0$,
+  $0.02$, $0.1$, and $0.1$. The reduced area is $\Delta A = 0.75$, the
+  extension rate $\chi = 0.09$ and the adhesion distance $\delta =
+  0.4$.  The color coding is the tension.}
   \end{figure}
@@
   0.1$ ({\em bottom}).  The center of the vesicle, denoted with a black
-  square, is the stagnation point.}
+  square, is the stagnation point.  The color coding is the tension.}
   \end{figure}
@@
   is $\Delta A = 0.8$, the Hamaker constant $\mathcal{H} = 0.7$, the
-  separation distance is $\delta = 0.4$, and the extension rate $\chi
+  separation distance is $\delta = 0.4$, and the extension rate is $\chi
   = 0.1$.  The center of the vesicle, denoted with a black square, is a
-  stagnation point.}
+  stagnation point.  The color coding is the tension.}
 \end{figure}
@@
   angle of a doublet formed by vesicles of reduced area $\Delta A = 0.7$
-  in an extensional flow with an extension rate $\chi$.  (b) The final
-  inclination angle of doublets.  At larger extension rates, the
+  in an extensional flow with an extension rate $\chi$.  For all
+  extension rates, the vesicle's orientation angle tends to a value in
+  $(\frac{\pi}{2},\pi)$. (b) The final inclination angle of the doublets
+  for a variety of reduced areas.  At larger extension rates, the
     doublet is broken by the flow.  (c) A phase diagram of the long-time
     behavior of a fluid trap formed by two adhering vesicles in an
-  extensional flow.  Results are not reported for some of the low
-  extension rates since the doublet had not tilted to an equilibrium
-  inclination angle for the given time horizon.}
+    extensional flow.  Reduced areas and extension rates that do not
+    form a doublet are marked in red, and those that do form a doublet
+    are marked in blue.  For the blue marks, the size is proportional to
+    the final inclination angle.  Squares indicate that the doublet had
+    not tilted to an equilibrium inclination angle in the given time
+    horizon.}
 \end{figure}
@@
   interaction between the two vesicles is a sliding motion, and the
-  dynamics has a period of about 42.}
+  dynamics has a period of about 42.  The color coding is the tension.}
 \end{figure}
@@
   dynamics of the doublet resembles a rigid body motion with a period of
-  about 42.}
+  about 42.  The color coding is the tension.}
 \end{figure}

### 2019-07-17 vesicle_code/docs/adhesion/adhesion.tex

--- 2019-07-17 vesicle_code/docs/adhesion/adhesion.tex
@@
   initial vertical displacement $\triangle y=0$, 0.02, 0.1 and 0.1. The
-  reduced area is $\Delta A = 0.75$, the extension rate $\dot\epsilon= 0.09$
-%  \todo[inline]{Yuan: Can you look and see what extension rates you
-%  did for the runs that do not indicate the rate in the file name?} 
-  and the adhesion distance $\delta = 0.4$. }
+  reduced area is $\Delta A = 0.75$, the extension rate $\dot\epsilon=
+  0.09$ and the adhesion distance $\delta = 0.4$.  The color coding is
+  the tension.}
   \end{figure}
@@
   is $\Delta A = 0.8$, the Hamaker constant $\mathcal{H} = 0.7$, the
-  separation distance is $\delta = 0.4$, and the extension rate $\dot\epsilon
-  = 0.1$.  The center of the vesicle, denoted with a black square, is a
-  stagnation point.}
+  separation distance is $\delta = 0.4$, and the extension rate
+  $\dot\epsilon = 0.1$.  The center of the vesicle, denoted with a black
+  square, is a stagnation point.  The color coding is the tension.}
 \end{figure}
@@
   angle of a doublet formed by vesicles of reduced area $\Delta A = 0.7$
-  in an extensional flow with an extension rate $\dot\epsilon$.  (b) The final
-  inclination angle of doublets.  At larger extension rates, the
+  in an extensional flow with an extension rate $\dot\epsilon$.  For all
+  extension rates, the vesicle's orientation angle tends to a value in
+  $(\frac{\pi}{2},\pi)$. (b) The final inclination angle of the doublets
+  for a variety of reduced areas.  At larger extension rates, the
     doublet is broken by the flow.  (c) A phase diagram of the long-time
     behavior of a fluid trap formed by two adhering vesicles in an
-  extensional flow.  Results are not reported for some of the low
-  extension rates since the doublet had not tilted to an equilibrium
-  inclination angle for the given time horizon.}
+    extensional flow.  Reduced areas and extension rates that do not
+    form a doublet are marked in red, and those that do form a doublet
+    are marked in blue.  For the blue marks, the size is proportional to
+    the final inclination angle.  Squares indicate that the doublet had
+    not tilted to an equilibrium inclination angle in the given time
+    horizon.}
 \end{figure}

### 2019-07-17 vesicle_code/docs/adhesion/adhesion.tex
fixed the shear rate notation and extension rate notation in figs and text

@@
 \label{sec:sflow} 
-We consider two vesicles suspended in the shear flow $\uu = \chi(y,0)$,
-where $\chi$ is the shear rate.  To be consistent with simlulations in
-previous sections, the vesicles have a length of $2\pi$ for all reduced
-areas.  The initial placement of the vesicles is chosen so that the flow
-dives them towards one another.  In the absence of adhesion, once the
-vesicles are sufficiently close, they are deflected to opposite sides of
-the $y$ axis, pass one another, and then separate.  However, in the
-presence of adhesion, the vesicles can form a doublet for certain values
-of the separation distance $\delta$, Hamaker constant $\mathcal{H}$,
-shear rate $\chi$, and reduced area $\Delta A$.  If a doublet does form,
-then it undergoes a periodic motion with a period that depends on the
-same parameters.
+We consider two vesicles suspended in the shear flow $\uu =
+\dot\gamma(y,0)$, where $\dot\gamma$ is the shear rate.  To be
+consistent with simlulations in previous sections, the vesicles have a
+length of $2\pi$ for all reduced areas.  The initial placement of the
+vesicles is chosen so that the flow dives them towards one another.  In
+the absence of adhesion, once the vesicles are sufficiently close, they
+are deflected to opposite sides of the $y$ axis, pass one another, and
+then separate.  However, in the presence of adhesion, the vesicles can
+form a doublet for certain values of the separation distance $\delta$,
+Hamaker constant $\mathcal{H}$, shear rate $\dot\gamma$, and reduced
+area $\Delta A$.  If a doublet does form, then it undergoes a periodic
+motion with a period that depends on the same parameters.
 
@@
 vesicle.  Each of the vesicles have reduced area $\Delta A = 0.9$, shear
-rate $\chi = 0.5$, separation distance $\delta = 0.4$, and Hamaker
+rate $\dot\gamma = 0.5$, separation distance $\delta = 0.4$, and Hamaker
 constant $\mathcal{H} = 0.7$ (Figure~\ref{fig:doublet090-weakAdhesion})
@@
 the doublet move in tandem with a tank-reading motion that is much
-slower than the tank-treading motion that occurs in the absense of
-ahdesion.  However, the dynamics of a single period for theses two
+slower than the tank-treading motion that occurs in the absence of
+adhesion.  However, the dynamics of a single period for theses two
 Hamaker constants differ significantly.  For the weaker adhesive force,
@@
   0.9$, the Hamaker constant is $\mathcal{H}=0.7$, the separation
-  distance is $\delta = 0.4$, and the shear rate is $\chi=0.5$.  The
-  interaction between the two vesicles is a sliding motion, and the
+  distance is $\delta = 0.4$, and the shear rate is $\dot\gamma=0.5$.
+  The interaction between the two vesicles is a sliding motion, and the
   dynamics has a period of about 42.  The color coding is the tension.}
@@
   A = 0.9$, the Hamaker constant is $\mathcal{H}=2.1$, the separation
-  distance is $\delta = 0.4$, and the shear rate is $\chi=0.5$.  Since
-  the contact region is unchanged throughout the simulation, the
+  distance is $\delta = 0.4$, and the shear rate is $\dot\gamma=0.5$.
+  Since the contact region is unchanged throughout the simulation, the
   dynamics of the doublet resembles a rigid body motion with a period of
@@
 distance between two vesicles with reduced area $\Delta A = 0.9$,
-separation distance $\delta = 0.5$, and shear rate $\chi = 0.5$.
+separation distance $\delta = 0.5$, and shear rate $\dot\gamma = 0.5$.
 Figure~\ref{fig:sflow_distance}(a) shows this minimum distance as a
@@
 \begin{align}
-  p = \frac{2\pi}{\chi}\left(\lambda + \lambda^{-1} \right).
+  p = \frac{2\pi}{\dot\gamma}\left(\lambda + \lambda^{-1} \right).
   \label{eqn:JefferyPeriod}
@@
 Instead of measuring the aspect ratio of a doublet in a flow with shear
-rate $\chi$, we use the computed period to define an effective aspect
-ratio $\lambda_{\mathrm{eff}}$ that satisfies~\eqref{eqn:JefferyPeriod}.
-Therefore, the effective aspect ratio is the aspect ratio of an ellipse
-in a shear flow that is undergoing a Jeffery orbit with period $p$.  For
-the Hamaker constants $\mathcal{H} = 1.5$ and $\mathcal{H} = 3.5$, the
-shear rates, periods, and effective aspect ratio are summarized in
+rate $\dot\gamma$, we use the computed period to define an effective
+aspect ratio $\lambda_{\mathrm{eff}}$ that
+satisfies~\eqref{eqn:JefferyPeriod}.  Therefore, the effective aspect
+ratio is the aspect ratio of an ellipse in a shear flow that is
+undergoing a Jeffery orbit with period $p$.  For the Hamaker constants
+$\mathcal{H} = 1.5$ and $\mathcal{H} = 3.5$, the shear rates, periods,
+and effective aspect ratio are summarized in
 Table~\ref{tbl:aspectRatio}.  The effective aspect ratio of the doublet
@@
 >{\centering\arraybackslash}p{2cm}}
-  $\chi$ & $p$ & $\lambda_{\mathrm{eff}}$ \\
+  $\dot\gamma$ & $p$ & $\lambda_{\mathrm{eff}}$ \\
   \hline
@@
   \caption{\label{fig:sflow_distance} (a) The distance between a pair of
-  vesicles in a planar shear flow with shear rate $\chi=0.5$, and
+  vesicles in a planar shear flow with shear rate $\dot\gamma=0.5$, and
   separation distance $\delta = 0.4$.  The different lines correspond to
@@
   constant $\mathcal{H}$ for binding of two vesicles in a shear flow
-  depends on the shear rate $\chi$.  For a doublet to form, lower
+  depends on the shear rate $\dot\gamma$.  For a doublet to form, lower
   separation distances require a stronger Hamaker constants at a given
@@
   [\mu]:= \frac{\mu_{\mathrm{eff}} - \mu_0}{\phi \mu_0} = 
-  \frac{1}{\chi \mu_0 (T_e - T_i)} \int_{T_i}^{T_e} 
+  \frac{1}{\dot\gamma \mu_0 (T_e - T_i)} \int_{T_i}^{T_e} 
   \langle \tau_{12} \rangle dt,
@@
 constant $\mathcal{H} = 0.7$, separation distance $\delta = 0.4$, and
-shear rate $\chi = 0.5$.  To validate our simulations, we superimpose
-(black marks) the intrinsic viscosity calculated by Ghigliotti {\em et
-al.}~\cite{GhigliottiBibenMisbah2010_JFM}.  The presence of the doublet
-slightly increases the intrinsic viscosity at all the reduced areas.
-We also compute the intrinsic viscosity of a doublet with $\Delta A =
-0.9$, $\chi = 0.5$, and $\mathcal{H} = 2.1$.  Again, this doublet has a
-similar period to the case $\mathcal{H} = 0.7$. At this larger Hamaker
-constant, the effective viscosity increases slightly from $1.97$ to
-$2.06$.  To further characterize the effect of adhesion, in
-Figure~\ref{fig:shearIntrinsicViscosity}(b) we decompose the intrinsic
-viscosity into the contributions from the bending and tension (black),
-and the contribution from the adhesion (green).  We also superimpose the
-intrinsic viscosity of a single tank-treading vesicle (blue) to
-demonstrate that the bending and tension of the doublet behave
-similarly, but not identically, to a dilute suspensions of non-adhering
-tank-treading vesicles.  We see that the effect of the adhesion on the
-intrinsic viscosity is largest for vesicles with small reduced areas.
-We also decompose the intrinsic viscosity contributions of the doublet
-with $\mathcal{H} = 2.1$ and $\Delta A = 0.9$.  When compared with the
-smaller Hamaker constant, the intrinsic viscosity contribution due to
-bending and tension is reduced from $1.85$ to $1.71$, and the
-contribution due to adhesion is increased from $0.12$ to $0.36$.
-Therefore, as the Hamaker constant increases, the increase in the
-intrinsic viscosity is due to the adhesive force rather than the bending
-and tension.
+shear rate $\dot\gamma = 0.5$.  To validate our simulations, we
+superimpose (black marks) the intrinsic viscosity calculated by
+Ghigliotti {\em et al.}~\cite{GhigliottiBibenMisbah2010_JFM}.  The
+presence of the doublet slightly increases the intrinsic viscosity at
+all the reduced areas.  We also compute the intrinsic viscosity of a
+doublet with $\Delta A = 0.9$, $\dot\gamma = 0.5$, and $\mathcal{H} =
+2.1$.  Again, this doublet has a similar period to the case $\mathcal{H}
+= 0.7$. At this larger Hamaker constant, the effective viscosity
+increases slightly from $1.97$ to $2.06$.  To further characterize the
+effect of adhesion, in Figure~\ref{fig:shearIntrinsicViscosity}(b) we
+decompose the intrinsic viscosity into the contributions from the
+bending and tension (black), and the contribution from the adhesion
+(green).  We also superimpose the intrinsic viscosity of a single
+tank-treading vesicle (blue) to demonstrate that the bending and tension
+of the doublet behave similarly, but not identically, to a dilute
+suspensions of non-adhering tank-treading vesicles.  We see that the
+effect of the adhesion on the intrinsic viscosity is largest for
+vesicles with small reduced areas.  We also decompose the intrinsic
+viscosity contributions of the doublet with $\mathcal{H} = 2.1$ and
+$\Delta A = 0.9$.  When compared with the smaller Hamaker constant, the
+intrinsic viscosity contribution due to bending and tension is reduced
+from $1.85$ to $1.71$, and the contribution due to adhesion is increased
+from $0.12$ to $0.36$.  Therefore, as the Hamaker constant increases,
+the increase in the intrinsic viscosity is due to the adhesive force
+rather than the bending and tension.
 
@@
   viscosity of a tank-treading vesicle (blue) and a doublet (red).  The
-  shear rate is $\chi = 0.5$, the Hamaker constant is $\mathcal{H} =
-  0.7$, and the separation distance is $\delta = 0.4$.  The black marks
-  denote intrinsic viscosity values computed by Ghigliotti {\em et
+  shear rate is $\dot\gamma = 0.5$, the Hamaker constant is $\mathcal{H}
+  = 0.7$, and the separation distance is $\delta = 0.4$.  The black
+  marks denote intrinsic viscosity values computed by Ghigliotti {\em et
   al.}~\cite{GhigliottiBibenMisbah2010_JFM} (cf.~Figure 5).  (b) The

### 2019-07-18 vesicle_code/docs/adhesion/revisions/reviewer1.tex
worked on rebuttal
yny reviewer 1

@@
 \begin{itemize}
-  \item rebuttal
+  \item We thank the referee for this comment. The referee is correct by labeling boundary integral simulation as a standard approach.
+  However, the boundary integral algorithm we used for this work is not standard boundary integral algorithm for two reasons: (1) First the time marching is adaptive, allowing us to efficiently run the simulations for a long time with accuracy and convergence.
+(2) Second we adopted a slightly sophisticated near singular evaluation to ensure that our numerical results are convergent when two boundaries are close to each other.
+Without adaptive time marching, the boundary integral simulations of vesicles often give unreliable results as shown in
+Kabacaoglu {\it et al.}, J. Comp. Phys. (2018). In addition it is very time consuming to simulate two vesicles to equilibrate in close vicinity of each other in a quiescent flow. 
+Without a good near-singular evaluation in the boundary integral calculation, the simulations will be contaminated by the errors incurred when two moving deformable boundaries are close to each other.
+
+  We thank the referee for pointing out that similar physical setup has been studied for red blood cells, capsules, drops and adhere particles. 
+  However it is not clear to us if our results for vesicles are so similar to those for red blood cell/drop/particles in the literature that no new understanding is contributed in this work.
+
+For example, we are able to verify the scaling of the draining time with respect to adhesion strength and equilibrium separation distance by analyzing the numerical simulation results. 
+A similar scaling is found in Ramachandran {\it et al.}, Phys.
+Fluids (2010) where they assumed the vesicles are spherical cap with a flat contact region.
+It is not clear how their scaling for the draining time can differentiate the contribution from either adhesion strength or equilibrium separation distance, while our scaling clearly illustrates how each component contributes differently to the draining time.
+It is also not clear how such scaling can be verified by comparing against experimental data.
+
+For the vesicles in a planar extensional flow, we cannot find any work in the literature that shows how two red blood cells/capsules move toward each other around the stagnation point.
+Furthermore we cannot find any work in the literature that uses extensional flow to measure the adhesion strength between two interfaces/particles/membranes.
+All the work we can find on drop in an extensional flow/four-roll mill is for a single drop (clean drop or a surfactant-laden drop).
+
 \end{itemize}

### 2019-07-18 vesicle_code/docs/adhesion/revisions/reviewer1.tex
yny reviewer 1

@@
 \noindent
-Thank you for your constructive comments.  The attached manuscript
-addresses all the reviewer 1's comments and the result is what we
-believe is a stronger manuscript.
-\\ \\ \noindent 
-We also note that a few typos from the manuscript’s original form have
-been addressed. An itemized list of the changes addressing the
-reviewers’ comments are below.
-\\ \\ \noindent 
+We thank the referee for the comments.  Below are our point-to-point responses to 
+all the reviewer 1's comments.  We have made revisions based on these comments.
+We also note that a few typos from the original manuscript have
+been corrected.  A separate list of changes can be found along with this list of responses.
+
+\noindent 
 Sincerely, \\ \noindent
@@
 \noindent
-\comment{While the numerical simulations performed are based on standard
+
+\begin{enumerate}
+\item\comment{While the numerical simulations performed are based on standard
 approaches, and the results are supposedly correct, I find the results
@@
 \noindent
-\comment{Second, the simulations are 2D, which makes it difficult to accept
+\item\comment{Second, the simulations are 2D, which makes it difficult to accept
 whether the predicted results would be observed in experiments. There
@@
 \begin{itemize}
-  \item rebuttal
+  \item We thank the referee for this comment. The referee is absolutely correct: two-dimensional and three-dimensional hydrodynamics are in general very different. There are
+  cases where the two-dimensional and three-dimensional  vesicle hydrodynamics are in good agreement.
+For example, the two-dimensional simulations of packing of RBCs in Flormann {\it et al.}, Sci.
+Rep.
+(2017) are shown to be in good agreement with both experiments and three-dimensional simulations.
+In addition, the two-dimensional theoretical prediction of the buckling instability of the contact region between RBCs is validated by comparing with experiments in that paper.
+  Another example where two-dimensional vesicle hydrodynamics in shear flow is in general agreement with the three-dimensional vesicle hydrodynamics is illustrated in Ghigliotti {\it et al.}, J.
+Fluid Mech.
+(2010).
+
+  The current work is the first step we took to investigate the effects of adhesion on vesicle hydrodynamics.
+We are working on the three-dimensional version  and with the two-dimensional results as a guidance we will be able to elucidate more physical insight when we analyze the results from three-dimensional simulations in the near future.
+
+  \noindent
+  {\bf Changes:} We have added some comparison with three-dimensional (both numerical and experimental) results of two RBCs in shear flow in the revision.
 \end{itemize}
@@
 \noindent
-\comment{My third concern is the use of L-J potential. In practice, the
+\item\comment{My third concern is the use of L-J potential. In practice, the
 vesicle surface would be coated with some adhesive molecules (e.g.
@@
 \begin{itemize}
-  \item rebuttal
+  \item We thank the referee for this point. We follow the modeling works on red blood cells (RBCs) by Flormann {\it et al.}, Sci. Rep. (2017) and Hoore {\it et al.} Soft Matt. (2018).
+  In both papers the L-J potential is used to model the interaction between RBCs.
+The focus of this work is to show the hydrodynamic implication of such interaction between two vesicles without any coating of adhesive protein macromolecules.
+Results from these modeling works using L-J potential are found to be in good agreement with experiments and previous modeling results using different adhesion potential (Ziherl and Svetina, PNAS (2007)).
+
+  The referee is correct that the biological adhesion requires physical contact and is stochastic in nature.
+We are modeling such stochastic binding for adhesion between two membranes in a viscous solvent.
+
+  \noindent
+  {\bf Changes:} We have added more references and a better description on the usage of L-J potential for vesicle adhesion to explain its validity and applicability.
+
 \end{itemize}
@@
 \noindent
-\comment{The authors talks about the "fluid trap". This is indeed a tricky
+\item\comment{The authors talks about the "fluid trap". This is indeed a tricky
 issue in any experiment dealing with extensional flow as how to
@@
 \begin{itemize}
-  \item rebuttal
+  \item We thank the referee for this comment. The ``fluid trap", in its earliest form, was first achieved in an experiment by Bentley and Leal in 1986: A computer-controlled four-roll mill for
+  investigations  of particle and drop dynamics in two-dimensional linear shear flows, Journal of Fluid Mechanics, vol.
+167, pp.
+219-240 (1986).
+Bentley and Leal showed that their computer-aided feedback control in the four-roll mill can keep the particle/drop at the center of the four-roll mill for a very long time.
+  Over the years the techniques of using the four-roll mill as a fluid trap have been improved and extended to microfluidics (see Hudson {\it et al.}, Applied Phys.
+Lett.
+(2004) and Lee {\it et al.}, Applied Phys.
+Lett.
+(2007) for example.)
+  In the original manuscript we simulate the fluid trap based on the setups by both the Schroeder's group at UIUC and S.
+Muller's group that can efficiently control the location of the stagnation point.
+
+  Our motivation is to present these simulation results so the experimentalist may be interested to use the fluid trap as a non-invasive tool to measure the adhesion strength between vesicles.
+We hope that there will be experimental data for us to compare our simulations results in the near future.
+
+   \noindent
+  {\bf Changes:} We have added these references on fluid trap in the revised manuscript. In addition we have rewritten a couple of relevant paragraphs to convey our motivation.
  \end{itemize}
@@
 \noindent
-\comment{There was not enough physical insights on the vesicle alignment
+\item\comment{There was not enough physical insights on the vesicle alignment
 in extensional flow as presented in section IV. If the vesicles are
@@
 \begin{itemize}
-  \item rebuttal
+  \item We have reorganized section IV based on the referee's feedback.
+To investigate the vesicle hydrodynamics in a planar extensional flow we conducted new simulations where a left vesicle is placed at the stagnation point and the right vesicle is moving towards it.
+Depending on the initial elevation of the right vesicle off the $x$-axis, the vesicle hydrodynamics is different and we find configurations that are similar to those that we observe in the fluid trap.
+The simulation data show that the membrane tension is highly non-uniform, and we speculate that the Marangoni stress contributes to asymmetric configuration of vesicles around the stagnation point, as for a single surfactant-laden drop in an extensional flow.
+
+  \noindent
+  {\bf Changes:} We have removed the part on visualizing flow around vesicles in the fluid trap.
+Instead we added simulations at the beginning of new Section IV to examine the vesicle hydrodynamics in a planar extensional flow.
 \end{itemize}
@@
 \noindent
-\comment{I did not find figure 14 relevant for the present article. This
+\item\comment{I did not find figure 14 relevant for the present article. This
 result is not relevant, and also presented just to show what the authors
@@
 \begin{itemize}
-  \item We have removed this example from the manuscript.  Instead, we
+  \item We agree with the referee and  have removed this example from the manuscript.  Instead, we
     mention that future work includes a suspension of many vesicles.
+
+    \noindent
+    {\bf Changes:} We removed this example from the conclusion and instead we expand future work to include a suspension of many vesicles.
 \end{itemize}
 
+\end{enumerate}
+
 \end{document}

### 2019-07-18 vesicle_code/docs/adhesion/revisions/reviewer1.tex
yny reviewer 1

@@
 \begin{itemize}
-  \item We thank the referee for this comment. The referee is correct by labeling boundary integral simulation as a standard approach.
+  \item We thank the referee for this comment. The referee is absolutely correct by labeling boundary integral simulation as a standard approach.
   However, the boundary integral algorithm we used for this work is not standard boundary integral algorithm for two reasons: (1) First the time marching is adaptive, allowing us to efficiently run the simulations for a long time with accuracy and convergence.
@@
 Furthermore we cannot find any work in the literature that uses extensional flow to measure the adhesion strength between two interfaces/particles/membranes.
-All the work we can find on drop in an extensional flow/four-roll mill is for a single drop (clean drop or a surfactant-laden drop).
+All the work we can find on drop in an extensional flow/four-roll mill is for a single drop (clean drop or a surfactant-laden drop) or a vesicle.
+
+For the vesicles in a planar shear flow, there are numerical simulations and experiments on how two drops/vesicles interact with each other. 
+However, to our best attempt, we did not find any work on the effects of adhesions on drop-drop/vesicle-vesicle interactions in a shear flow (possibly due to the numerical issues that we mentioned earlier).
+Our simulation results show that (1) adhesion significantly affects the vesicle-vesicle interaction in the shear flow, and in the revision we provided means to quantify such effects, and (2) adhesion also induces additional dissipation in a dilute suspension of vesicle doublets.
+To our best knowledge these results are not available in the literature.
+Even though our simulations are two-dimensional, previous works have demonstrated that two-dimensional vesicle hydrodynamics bear some general similarity to their three-dimensional counterparts.
+
+{\bf Changes:} We made revisions with this comment in mind, to make sure that our results are highlighted and the readers can see clearly how these results are unique and maybe useful.
 

### 2019-07-18 vesicle_code/docs/adhesion/adhesion.tex
yny adhesion.tex

@@
 The adhesion strength ${\cal H} = 0.7$ for the top three rows, and ${\cal H} =0.6$ for the bottom row.
-The color coding is the membrane tension with the color bar on the right of each row. We note that the negative membrane tension in an
-extensional flow is consistent with the speculation for a wrinkled membrane in the elongational flow \cite{KantslerSegreSteinberg2007_PRL}.
+The color coding is the membrane tension with the color bar on the right of each row. We note that the negative tension in an
+extensional flow is consistent with the tension for a vesicle with finite bending forces \cite{Narsimhan2014_JFM} and the
+speculation for a wrinkled membrane in the elongational flow \cite{KantslerSegreSteinberg2007_PRL}.
 

### 2019-07-18 vesicle_code/docs/adhesion/adhesion.tex
working on reviewer 2

--- 2019-07-17 vesicle_code/docs/adhesion/adhesion.tex
@@
 aggregates, a simplified model for adhesive vesicle-vesicle interactions
-can reproduce vesicle shapes similar to those observed in
-experiments of fibrinogen-induced RBC
-aggregates~\cite{SvetinaZiherl2008_Bioelectrochemistry,GuWangGunzburger2016_MathBiol,
-FlormannAouane2017_SciReports,HooreYayaPodgorski2018_SoftMatt}.  Using the Lennard-Jones
-(L.-J.)~potential for point-point interaction between two vesicle
-membranes without the molecular details of adhesive interactions between
-RBCs, Flormann {\em et al.}~\cite{FlormannAouane2017_SciReports} found
-that, under strong adhesion, 
-the membrane may buckle to a sigmoidal shape in the contact region.
-Such a sigmoidal vesicle shape is 
-also observed in RBC doublets and explained in a slightly different
+can reproduce vesicle shapes similar to those observed in experiments of
+fibrinogen-induced RBC
+aggregates~\cite{SvetinaZiherl2008_Bioelectrochemistry,GuWangGunzburger2016_MathBiol,FlormannAouane2017_SciReports,HooreYayaPodgorski2018_SoftMatt,bru-aou-thi-flo-ver-Kae-las-sel-ben-pod-cou-mis-wag2014,cla-aou-thi-abk-cou-mis-joh-wag2017}.
+Using the Lennard-Jones (L.-J.)~potential for point-point interaction
+between two vesicle membranes without the molecular details of adhesive
+interactions between RBCs, Flormann {\em et
+al.}~\cite{FlormannAouane2017_SciReports} found that, under strong
+adhesion, the membrane may buckle to a sigmoidal shape in the contact
+region.  Such a sigmoidal vesicle shape is also observed in RBC doublets
+and explained in a slightly different
 model~\cite{ZiherlSvetina2007_PNAS}.  It remains unknown how adhesive
@@
 interactions between RBCs.
-\todo[inline]{Add references by Brust aet al.~ and Claveria et al}
 
@@
 bending rigidity modulus.  We assume that the adhesion force from
-equation~\ref{eq:adhesion_potential} applies between all pairs of points
-on different vesicles, and in Appendix~\ref{sec:appendixA} the net
-adhesive force at a point $\xx$ on vesicle $j$ is shown to be
+equation~\eqref{eq:adhesion_potential} applies between all pairs of
+points on different vesicles, and in Appendix~\ref{sec:appendixA} the
+net adhesive force at a point $\xx$ on vesicle $j$ is shown to be
 \begin{align}
@@
 best fit between the stable and unstable regions.  Since the transition
-is linear, this indicates that a dimensionless number involving the
-ratio of the Hamaker constant and shear rate could be used to determine
-if a doublet forms or not.
+is linear for both separation distances, this indicates that a
+dimensionless number involving the ratio of the Hamaker constant and
+shear rate could be used to determine if a doublet forms or not.
 

### 2019-07-18 vesicle_code/docs/adhesion/revisions/reviewer2.tex
working on edits
working on reviewer 2

@@
 Thank you for your constructive comments.  The attached manuscript
-addresses all the reviewer 2's comments and the result is what we
+addresses all the referee 2's comments and the result is what we
 believe is a stronger manuscript.
@@
 We also note that a few typos from the manuscript’s original form have
-been addressed. An itemized list of the changes addressing the
-reviewers’ comments are below.
+been addressed. An itemized list of the changes addressing the referee's
+comments are below.
 \\ \\ \noindent 
@@
 \begin{itemize}
-  \item rebuttal
+  \item The captions now do a more complete job of explaining the
+    figure.  We paid particular attention to Figure 10 (old Figure 9)
+    since it contains a lot of information.
 \end{itemize}
@@
 \begin{itemize}
-  \item \todo[inline]{Other 2 papers of Misbah's group}
+  \item The reference of Brust et al.~has been added.
+  \item The reference of Claveria et al~Has been added.
   \item The reference of Chien et al.~has been added.
@@
 \begin{itemize}
-  \item rebuttal
+  \item The referee is correct that vesicles outside of the contact zone
+    do not feel a long range attractive interaction.  Our model follows
+    the works on red blood cells by Flormann {\em et al.}~Scientific
+    Reports (2017) and Hoore {\em et al.}~Soft Matter (2018).  In both
+    these papers, the Lennard-Jones potential is used to model the
+    adhesive interaction between red blood cells.  These models are
+    found to be in good agreement with experiments and other models for
+    adhesion (Ziherl and Svetina, PNAS (2017)).
+
+  \item We have added more references and a better description on the
+    usage of the Lennard-Jones potential for vesicle adhesion to explain
+    its validity and applicability.
+
+  \item We have added additional simulations that use a smaller value
+    for the separation distance $\delta$.  First, this demonstrates that
+    we are able to stably simulate adhering vesicles where the
+    lubrication layer is thin.  Second, the decreased value of $\delta$
+    gives similar results.  For example, in Figure 14, we show
+    numerically that, for two different separation distances, there is a
+    linear relationship between the shear rate and Hamaker constant that
+    determines if two vesicles in a shear flow will form a doublet or
+    not.
 \end{itemize}
@@
 \begin{itemize}
-  \item rebuttal
+  \item As mentioned in the Introduction and Section II, we are focusing
+    on intermediate adhesive strengths.  In the Introduction, we give
+    several references where strong adhesion is studied, but the effect
+    of the intermediate adhesion strengths on the vesicle dynamics has
+    not received much attention.
 \end{itemize}
@@
 
-  \item There is a very slow tank-treading motion \todo[inline]{Discuss
-    this further}
+  \item There is a very slow tank-treading motion.  However, since we
+    have removed Figure 10 from the original version, we have chosen to
+    not focus on the vorticity and torque of the vesicles.
 \end{itemize}
@@
 \begin{itemize}
-  \item We thank the reviewer for this observation.  We increased the
+  \item We thank the referee for this observation.  We increased the
     parameter space of the phase diagram, and it does appear that there
@@
 \begin{itemize}
-  \item The reviewer is correct that we miscalculated the intrinsic
+  \item The referee is correct that we miscalculated the intrinsic
     viscosity.  We had initially divided by only the area inside a

### 2019-07-18 vesicle_code/examples/relaxation1Ves.m

@@ -5,15 +5,11 @@ fprintf('First-order semi-implicit time stepping.\n');
 
 % Physics parameters
 prams.N = 128;               % points per vesicle
-prams.N = 256;               % points per vesicle
 prams.nv = 1;               % number of vesicles
-prams.T = 30;               % time horizon (two tumbling)
-prams.m = 1000;              % number of time steps
+prams.T = 1e-3;               % time horizon (two tumbling)
+prams.m = 1;              % number of time steps
 
-prams.kappa = 1e-1;         % bending coefficient
-prams.kappa = 1e-2;         % bending coefficient
-
-
+prams.kappa = 1;         % bending coefficient
 
 prams.viscCont = 1;         % viscosity contrast
 options.farField = 'relaxation'; % background velocity
@@ -25,7 +21,7 @@ options.inextens = 'method1';
 options.near = true;        % near-singular integration
 options.fmm = false;
 options.antiAlias = false;
-options.semipermeable = true;
+options.semipermeable = false;
 prams.gmresMaxIter = 3*prams.N;
 prams.gmresTol = 1e-10;
 prams.errorTol = 1000;
@@ -37,7 +33,7 @@ options.correctShape = false;
 options.reparameterization = false;
 
 % TIME ADAPTIVITY (parameters for new implementation)
-options.timeAdap = true;
+options.timeAdap = false;
 
 prams.rtolArea = 1e10;
 prams.rtolLength = 1e-2;
@@ -52,8 +48,8 @@ if 1
 end
 
 options.orderGL = 2;
-options.nsdc = 0;
-options.expectedOrder = 1;
+options.nsdc = 2;
+options.expectedOrder = 2;
 
 options.expForce = false;
 

### 2019-07-18 vesicle_code/docs/adhesion/adhesion.tex
first draft of reviewer 2 done

@@
 planar shear flow with a long separation
-distance~\cite{GiresDankerMisbah2012_PRE}.  \todo[inline]{Also cite
-Gires et al.~Physics of Fluids 26, 013304, 2014} They found that the
-vesicle interaction could be either attractive or repulsive depending on
-the organization of the two vesicles relative to the shear flow. To the
-best of authors' knowledge, the effects of close-range vesicle adhesion
-on their hydrodynamics under an external flow have not been studied and
-quantified. The goal of this work is to use state-of-the-art boundary
-integral simulations to numerically investigate the dynamics of two
-vesicles in both planar shear flow and extensional flow for a wide range
-of vesicle shapes and adhesive strength and distance.
+distance~\cite{GiresDankerMisbah2012_PRE}.  They found that the vesicle
+interaction could be either attractive or repulsive depending on the
+organization of the two vesicles relative to the shear
+flow~\cite{gir-sri-mis-pod-cou2014}. To the best of authors' knowledge,
+the effects of close-range vesicle adhesion on their hydrodynamics under
+an external flow have not been studied and quantified. The goal of this
+work is to use state-of-the-art boundary integral simulations to
+numerically investigate the dynamics of two vesicles in both planar
+shear flow and extensional flow for a wide range of vesicle shapes and
+adhesive strength and distance.
 
@@
 \label{sec:eflow}
-\todo[inline]{Do we discuss the slow tank treading motion when the
-vesicles reach steady state.  Reviewer 2 had a comment about this}
 
@@
 of the vesicle with the diverging direction and then the vesicles
-separate (Figure~\ref{fig:extensional3}).  For very low extension
-rates, the time horizon is insufficient for the doublet to reach an
-equilibrium state, and these simulations are marked with a square.
+separate (Figure~\ref{fig:extensional3}).  For very low extension rates,
+the time horizon is insufficient for the doublet to reach an equilibrium
+state, and these simulations are marked with a square.
 Figure~\ref{fig:extensionalInclinationAngle}(c) also summarizes the
-reduced areas and extension rates that result in a bound vesicle
-doublet in a fluid trap: Parameter values with a blue mark result in a
-fluid trap and parameter values with a red mark result in vesicle
-separation.
+reduced areas and extension rates that result in a bound vesicle doublet
+in a fluid trap: Parameter values with a blue mark result in a fluid
+trap and parameter values with a red mark result in vesicle separation.
 
@@
 %  \includegraphics[height=0.26\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
-  \caption{\label{fig:extensionalInclinationAngle} (a) The inclination
-  angle of a doublet formed by vesicles of reduced area $\Delta A = 0.7$
-  in an extensional flow with an extension rate $\dot\epsilon$.  For all
-  extension rates, the vesicle's orientation angle tends to a value in
-  $(\frac{\pi}{2},\pi)$. (b) The final inclination angle of the doublets
-  for a variety of reduced areas.  At larger extension rates, the
-    doublet is broken by the flow.  (c) A phase diagram of the long-time
-    behavior of a fluid trap formed by two adhering vesicles in an
-    extensional flow.  Reduced areas and extension rates that do not
-    form a doublet are marked in red, and those that do form a doublet
-    are marked in blue.  For the blue marks, the size is proportional to
-    the final inclination angle.  Squares indicate that the doublet had
-    not tilted to an equilibrium inclination angle in the given time
-    horizon.}
+  \caption{\label{fig:extensionalInclinationAngle} The long time
+  behavior of two vesicles in a fluid trap with Hamaker constant
+  $\mathcal{H} = 0.7$ and separation distance $\delta = 0.4$. (a) The
+  inclination angle of a doublet formed by vesicles of reduced area
+  $\Delta A = 0.7$ in an extensional flow with an extension rate
+  $\dot\epsilon$.  For all extension rates, the vesicle's orientation
+  angle tends to a value in $(\frac{\pi}{2},\pi)$. (b) The final
+  inclination angle of the doublets for a variety of reduced areas.  At
+  larger extension rates, the doublet is broken by the flow.  (c) A
+  phase diagram of the long-time behavior of a fluid trap formed by two
+  adhering vesicles in an extensional flow.  Reduced areas and extension
+  rates that do not form a doublet are marked in red, and those that do
+  form a doublet are marked in blue.  For the blue marks, the size is
+  proportional to the final inclination angle.  Squares indicate that
+  the doublet had not tilted to an equilibrium inclination angle in the
+  given time horizon.}
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Adhesion of two vesicles in a shear flow}
+\section{Adhesion of two vesicles in a planar shear flow}
 \label{sec:sflow} 
-We consider two vesicles suspended in the shear flow $\uu =
+We consider two vesicles suspended in the planar shear flow $\uu =
 \dot\gamma(y,0)$, where $\dot\gamma$ is the shear rate.  To be
-consistent with simlulations in previous sections, the vesicles have a
+consistent with simulations in previous sections, the vesicles have a
 length of $2\pi$ for all reduced areas.  The initial placement of the
-vesicles is chosen so that the flow dives them towards one another.  In
-the absence of adhesion, once the vesicles are sufficiently close, they
-are deflected to opposite sides of the $y$ axis, pass one another, and
-then separate.  However, in the presence of adhesion, the vesicles can
-form a doublet for certain values of the separation distance $\delta$,
-Hamaker constant $\mathcal{H}$, shear rate $\dot\gamma$, and reduced
-area $\Delta A$.  If a doublet does form, then it undergoes a periodic
-motion with a period that depends on the same parameters.
+vesicles is chosen so that the flow dives them towards one another in a
+head-on collision.  In the absence of adhesion, once the vesicles are
+sufficiently close, they are deflected to opposite sides of the $y$
+axis, pass one another, and then separate.  However, in the presence of
+adhesion, the vesicles can form a doublet for certain values of the
+separation distance $\delta$, Hamaker constant $\mathcal{H}$, shear rate
+$\dot\gamma$, and reduced area $\Delta A$.  If a doublet does form, then
+it undergoes a periodic motion with a period that depends on the same
+parameters.
 
@@
 dimensionless number involving the ratio of the Hamaker constant and
-shear rate could be used to determine if a doublet forms or not.
+shear rate could be used to determine if a doublet forms or not.  We
+note that the critical Hamaker constant also depends on the reduced
+area.  For smaller reduced areas, we expect a smaller contact region to
+form and this will lower the Hamaker constant, and this behavior will be
+investigated in future work.
 

### 2019-07-18 vesicle_code/docs/adhesion/revisions/reviewer2.tex
first draft of reviewer 2 done

@@
   \item The reference of Brust et al.~has been added.
-  \item The reference of Claveria et al~Has been added.
+  \item The reference of Claveria et al~has been added.
   \item The reference of Chien et al.~has been added.
@@
 \begin{itemize}
-  \item rebuttal
+  \item The reference of Gires et al.~has been added
 \end{itemize}
@@
 \begin{itemize}
-  \item rebuttal
+  \item For the extensional example, the reduced area has a large effect
+    on determining if the doublet is broken or not, and on the
+    inclination angle if the doublet is not broken.  Therefore, we have
+    elected to investigate the effect of the reduced area for this
+    example.
+
+  \item For the shear example, a smaller reduced area will increase the
+    size of the contact area, and this will determine the critical
+    Hamaker constant required to form a doublet.  However, to avoid
+    diverting the focus of the paper, we have elected to divert an
+    investigation of this behavior to future work.
 \end{itemize}

### 2019-07-18 vesicle_code/docs/adhesion/revisions/reviewer2.tex
yny reviewer2

--- 2019-07-18 vesicle_code/docs/adhesion/revisions/reviewer2.tex
@@
 \noindent
-Thank you for your constructive comments.  The attached manuscript
-addresses all the referee 2's comments and the result is what we
-believe is a stronger manuscript.
-\\ \\ \noindent 
-We also note that a few typos from the manuscript’s original form have
-been addressed. An itemized list of the changes addressing the referee's
-comments are below.
+We thank the referee for the comments.  Below are our point-to-point responses to 
+all the comments from the reviewer.  We have made revisions based on these comments.
+We also note that a few typos from the original manuscript have
+been corrected.  A separate list of changes can be found along with this list of responses.
 \\ \\ \noindent 
@@
 \vspace{20pt}
-\noindent
-\comment{General comment: I found that the figure captions are often
+
+\begin{enumerate}
+\item\comment{General comment: I found that the figure captions are often
 incomplete and that details of the legends are missing and are only
@@
 
-\noindent
-\comment{Abstract: it should be mentioned in the abstract that this is
+\item\comment{Abstract: it should be mentioned in the abstract that this is
 2D modelling. 2D simulations of vesicles are often perfectly fine to
@@
 
-\noindent
-\comment{Introduction, 2nd paragraph: the transition in the effective
+\item\comment{Introduction, 2nd paragraph: the transition in the effective
 viscosity of vesicle or RBC suspensions was also validated
@@
 
-\noindent
-\comment{Intro, 3rd paragraph: the buckling instability of aggregating RBC
+\item\comment{Intro, 3rd paragraph: the buckling instability of aggregating RBC
 membranes was not only predicted theroretically and numerically in
@@
 
-\noindent
-\comment{Concerning the stability and dynamics of clusters of vesicles with
+\item\comment{Concerning the stability and dynamics of clusters of vesicles with
 adhesive interaction, there have been at least two papers on clusters
@@
 
-\noindent
-\comment{In addition to ref [54], Gires et al. also published experimental
+\item\comment{In addition to ref [54], Gires et al. also published experimental
 measurements of hydrodynamic interactions between vesicles in Gires et
@@
 \begin{itemize}
-  \item rebuttal
+  \item The reference of Gires et al.~has been added
 \end{itemize}
 
-\noindent
-\comment{In II. Governing equations and fig. 1: the right panel of the
+\item\comment{In II. Governing equations and fig. 1: the right panel of the
 figure and comments at the end of the section say that the part of
@@
 
-\noindent
-\comment{Along the same line, the repulsing spots in fig 1 right or Fig 3
+\item\comment{Along the same line, the repulsing spots in fig 1 right or Fig 3
 right as well as the amplitude of the deformation in the contact zone
@@
 
-\noindent
-\comment{I cannot figure out why the external part of vesicles on profile 1
+\item\comment{I cannot figure out why the external part of vesicles on profile 1
 in fig 3-left is yellow. Shouldn't the force be weakly attractive in
@@
 
-\noindent
-\comment{Figs 4-5 and related text: it would have been interesting to
+\item\comment{Figs 4-5 and related text: it would have been interesting to
 compare results with the bending energy of vesicles without adhesion
@@
 \begin{itemize}
-  \item rebuttal
+  \item We thank the referee for this suggestion. We did follow the referee's suggestion to check out this comparison. As pointed out by the referee in the seventh comment,
+  the long-range attraction of the L-J potential that is used for membrane-membrane adhesion is not realistic and consequently the doublet always has lower total energy than
+  dissociated vesicles. We are working on a more realistic adhesion potential for RBCs and we believe that this comparison will reveal more information there.
 \end{itemize}
 
-\noindent
-\comment{Fig 9(right): I regret that the authors did not extend the study
+\item\comment{Fig 9(right): I regret that the authors did not extend the study
 to lower values of the reduced area, to reach values comparable to red
@@
 
-\noindent
-\comment{ Figs 9(right) and 12(right): the stability diagrams are presented
+\item\comment{ Figs 9(right) and 12(right): the stability diagrams are presented
 in different parameter spaces for the extensional and shear flow
@@
 \begin{itemize}
-  \item rebuttal
+  \item In the revision for the extensional example we first focus on how an initial vertical displacement 
+  may affect the vesicle dynamics in a planar extensional flow (beginning of the new Section III). 
+  There we find that a vesicle doublet is not likely to form unless the two vesicles are aligned
+  on the converging axis of the straining flow. In the fluid trap simulations we find that
+    the reduced area has a large effect
+    on determining if the doublet is broken or not, and on the
+    inclination angle if the doublet is not broken.  Therefore, we have
+    elected to investigate the effect of the reduced area for this
+    example.
+
+  \item For the shear flow simulations, we place the two vesicles on the same horizontal axis at $t=0$ (initial displacement is zero).
+  Such head-on collision has been well studied for drops (clean or surfactant-laden), capsules, vesicles and red blood cells (without the L-J potential between membranes),
+  and will serve as a good reference point to draw comparison with our results. For head-on collision between two vesicles,
+  we find that  a smaller reduced area will increase the
+    size of the contact area, and this will affect the critical
+    Hamaker constant required to form a doublet. Thus we expect that the critical Hamaker constant for vesicle doublet formation reported will depend on the
+    reduced area, vertical displacement and the shear rate. 
+    To avoid
+    diverting the focus of the paper, we have elected to divert an
+    investigation of this behavior to future work.
 \end{itemize}
 
-\noindent
-\comment{Fig.~10: the black arrows, as I understand, represent the total
+\item\comment{Fig.~10: the black arrows, as I understand, represent the total
 attractive force due to the interaction potential. Would the authors
@@
 
-  \item There is a very slow tank-treading motion.  However, since we
-    have removed Figure 10 from the original version, we have chosen to
-    not focus on the vorticity and torque of the vesicles.
+  \item There is a transient tank-treading motion that eventually (asymptotically) stops towards equilibrium. 
+  Since we removed Figure 10 from the original version, we have chosen to
+    not focus on the transient trank-treading motion and the vorticity and torque of the vesicles.
 \end{itemize}
 
-\noindent
-\comment{Fig 12: the authors did not comment the evolution of the
+\item\comment{Fig 12: the authors did not comment the evolution of the
 frequency of distance oscillations in doublets when the Hamaker constant
@@
 
-\noindent
-\comment{Fig 12-right: is the stability limit between the red and blue
+\item\comment{Fig 12-right: is the stability limit between the red and blue
 zones linear? This would mean that a stability criterion could take
@@
 
-\noindent
-\comment{Fig 13 and comments about rheology: I am not sure to understand
+\item\comment{Fig 13 and comments about rheology: I am not sure to understand
 the meaning of the left figure where it is shown that the intrinsic
@@
 
-\noindent
-\comment{In the conclusions, an example of aggregation of vesicles enclosed
+\item\comment{In the conclusions, an example of aggregation of vesicles enclosed
 in a bigger one is presented. I do not think this brings much to this
@@
 
+\end{enumerate}
+
 \end{document}

### 2019-07-19 vesicle_code/docs/adhesion/revisions/reviewer2.tex
yny review2

@@
     these papers, the Lennard-Jones potential is used to model the
-    adhesive interaction between red blood cells.  These models are
-    found to be in good agreement with experiments and other models for
-    adhesion (Ziherl and Svetina, PNAS (2017)).
+    adhesive interaction between red blood cells.  
+    Results from these modeling works are found to be in good agreement 
+    with experiments and other models for adhesion (Ziherl and Svetina, PNAS (2017)).
 
@@
 \begin{itemize}
-  \item We have removed this example from the manuscript.  Instead, we
+  \item We have removed this example from the manuscript.  We thank the referee for the great suggestion to examine the conditions for formation of
+  linear structures. We have added a few new results in the revision and consequently we
     mention that future work includes a suspension of many vesicles.

### 2019-07-19 vesicle_code/docs/adhesion/revisions/summary_of_changes.tex
yny summary of changes

\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage{todonotes}
\usepackage{amsmath,amsfonts,amssymb,stmaryrd}
\usepackage{color}
\newcommand{\comment}[1]{{\color{blue} #1}}
\newcommand{\xxi}{\boldsymbol{\xi}}

\begin{document}
\noindent
We thank the referees for their comments.   We have made revisions based on these comments and criticisms.
Below is a list of changes in the revision.
\\ \\ \noindent 
Sincerely, \\ \noindent
Yuan-Nan Young, Shravan Veerapaneni, and Bryan Quaife

\vspace{20pt}

\begin{enumerate}

\item We modified the abstract.

\item We modified the introduction with better clarity and more complete citation of references.

\item We modified all the figure captions to make sure that all the figures are self-contained.

\item In Section IV: Adhesion of two vesicles in a planar extensional flow, we conducted new simulation to elucidate the interaction between two vesicles in a planar extensional flow. These results are summarized in Figure 6.

\item In Section IV: Adhesion of two vesicles in a planar extensional flow, we added a set of simulations with reduced area $\triangle A=0.65$ and these results are summarized in the new Figure 10(b) and 10(c).

\item In Section V: Adhesion of two vesicles in a shear flow, we conducted new  simulations with higher Hamaker constant. These results are summarized in Figure 12.

\item In Section V: Adhesion of two vesicles in a shear flow, we conducted more simulations to examine the oscillation of the vesicle doublet and how the oscillation frequency depends on 
the shear rate, separation distance, and Hamaker constant. These results are summarized in Figure 13(b). We also did some analysis to compare the double oscillation with the Jeffery orbit of a rigid ellipse in shear flow.

\item In Section V: Adhesion of two vesicles in a shear flow, we conducted more simulations to examine the effect of the separation distance $\delta$ based on reviewers' suggestions.

\item In Section V: Adhesion of two vesicles in a shear flow, we corrected the calculation of the intrinsic viscosity and the new results are summarized in Figure 15.

\item In Acknowledgements,  a sentence is added to describe the contribution from each author.

\end{enumerate}
\end{document}

### 2019-07-19 vesicle_code/docs/adhesion/adhesion.tex
yny adhesion

@@
 sufficiently close, they are deflected to opposite sides of the $y$
-axis, pass one another, and then separate.  However, in the presence of
+axis, pass one another, and then separate. This head-on collision process of two vesicles or capsules in a planar shear flow
+is found to be similar between two- \cite{LacMorelBarthes-Biesel2007_JFM,RahimianVeerapaneniBiros2010_JCP} and three-dimensions \cite{LacBarthes-Biesel2008_PoF,OmoriIshikawaImaiYamaguchi2013_JBiomechics,RahimianVeerapaneniZorinBiros2015_JCP}.
+However, in the presence of
 adhesion, the vesicles can form a doublet for certain values of the

### 2019-07-19 vesicle_code/docs/adhesion/adhesion.tex
edits through out

--- 2019-07-18 vesicle_code/docs/adhesion/adhesion.tex
@@
 $\delta$ there for more deflated vesicles.
-For $\triangle A =0.6$ and $0.75$  the adhesion force is mostly attractive
+For $\Delta A =0.6$ and $0.75$  the adhesion force is mostly attractive
  in the contact region except at the edge, where the adhesive
-force turns repulsive.  For $\triangle A=0.95$, however, the adhesion force is mostly repulsive,
+force turns repulsive.  For $\Delta A=0.95$, however, the adhesion force is mostly repulsive,
 leading to large tension in the rest of the vesicle membrane.
@@
   \caption{\label{fig:extensionalNonsymmetric}Dynamics of a vesicle pair
-  in a planar extensional flow. ${\cal H} = 0.7$ for the first three
-  rows, and ${\cal H}=0.6$ for the bottom row. From top to bottom, the
-  initial vertical displacement $\triangle y=0$, 0.02, 0.1 and 0.1. The
-  reduced area is $\Delta A = 0.75$, the extension rate $\dot\epsilon=
-  0.09$ and the adhesion distance $\delta = 0.4$.  The color coding is
-  the tension.}
+  in a planar extensional flow. The Hamaker constant is ${\cal H} = 0.7$
+  for the first three rows, and ${\cal H}=0.6$ for the bottom row. From
+    top to bottom, the initial vertical displacement is $\Delta y=0$,
+    $0.02$, $0.1$, and $0.1$. The reduced area is $\Delta A = 0.75$, the
+    extension rate $\dot\epsilon= 0.09$, and the adhesion distance
+    $\delta = 0.4$.  The color coding is the tension.}
   \end{figure}
@@
 drop~\cite{KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
-Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  Here we focus on a
-planar extensional flow  where the fluid velocity field $\uu=\dot\epsilon(-x,y)$ is centered at the 
-the origin ($(x,y)=(0,0)$), the stagnation point where the fluid flow converges horizontally and diverges vertically.
-Placed symmetrically at the stagnation point of an extensional flow,
-a single vesicle may remain steady and symmetric for low extension rate $\dot\epsilon$.
-For sufficiently large extension rate $\dot\epsilon$ the vesicle may undergo asymmetric deformation \cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}, 
-similar to a surfactant-laden viscous drop under a planar extensional flow \cite{JanssenBoonAgterof1997_AIChE,HuPineLeal2000_PoF}.
-To our knowledge no studies on the interactions between two vesicles in an extensional flow are available in the literature.
-In the following we first illustrate how two vesicles interact with each other in a planar extensional flow. We then illustrate how the adhesion strength between membranes can be
+Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  Here we focus on
+a planar extensional flow  where the fluid velocity field
+$\uu=\dot\epsilon(-x,y)$ is centered at the origin ($(x,y)=(0,0)$), the
+stagnation point where the fluid flow converges horizontally and
+diverges vertically.  Placed symmetrically at the stagnation point of an
+extensional flow, a single vesicle may remain steady and symmetric for
+low extension rate $\dot\epsilon$.  For sufficiently large extension
+rate $\dot\epsilon$ the vesicle may undergo asymmetric
+deformation~\cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt},
+similar to a surfactant-laden viscous drop under a planar extensional
+flow~\cite{JanssenBoonAgterof1997_AIChE,HuPineLeal2000_PoF}.  To our
+knowledge no studies on the interactions between two vesicles in an
+extensional flow are available in the literature \todo[inline]{Something
+is off with this sentence}.  In the following we first illustrate how
+two vesicles interact with each other in a planar extensional flow. We
+then illustrate how the adhesion strength between membranes can be
 measured non-intrusively by using the fluid trap.
 
-%To investigate how two vesicles interact with each other in a planar extensional flow,
-At the beginning of the first set of simulations (left panels in Figure~\ref{fig:extensionalNonsymmetric})
-we place a vesicle at $(x,y)=(0,0)$, 
-and the other vesicle at $(x,y) = (3,\triangle y)$ where the initial vertical displacement $\triangle y$ varies from
-$\triangle y=0$ for the top row, $\triangle y = 0.02$ for the second row, to
-$\triangle y =0.1$ for the bottom two rows in Figure~\ref{fig:extensionalNonsymmetric}.
-The adhesion strength ${\cal H} = 0.7$ for the top three rows, and ${\cal H} =0.6$ for the bottom row.
-The color coding is the membrane tension with the color bar on the right of each row. We note that the negative tension in an
-extensional flow is consistent with the tension for a vesicle with finite bending forces \cite{Narsimhan2014_JFM} and the
-speculation for a wrinkled membrane in the elongational flow \cite{KantslerSegreSteinberg2007_PRL}.
-
-Once the planar extensional flow is turned on at $t=0^+$, two vesicles move
-towards each other  as shown in  Figure \ref{fig:extensionalNonsymmetric}.
-For $\triangle y=0$ in the top row, the two vesicles stay on the $x$-axis as they move closer to 
-form a doublet. We observe that the left vesicle (initially centered at $(0,0)$) moves to the left due to the impinging
-vesicle from the right. As time progresses they form a doublet
-and reach a steady configuration that is symmetric with respect to the stagnation point 
-(square marks in the top row of Figure \ref{fig:extensionalNonsymmetric}).
-
-For $\triangle y>0$ we observe similar vesicle dynamics only at the beginning 
-when the right vesicle moves towards the stagnation point and the left vesicle is pushed to the left of the stagnation point. 
-As both vesicles come to close vicinity of the stagnation point, the elevated right vesicle ($\triangle y >0$) is pulled up by the diverging flow in the $y$ direction,
-causing rotation of both vesicles. 
-We also observe that the larger the initial vertical displacement, the larger the rotation and the faster both vesicles move
-away from the stagnation point.
-%
-For sufficiently strong adhesion (${\cal H}=0.7$ for the first three rows in Figure \ref{fig:extensionalNonsymmetric}),
- the two vesicles rotate and move away from the stagnation point as a doublet until the end of simulations ($t=100$).
-As the two vesicles move further away from the stagnation point, the extensional flow becomes more effective in pulling the two drops apart
-as shown in the third row of Figure \ref{fig:extensionalNonsymmetric}.
-For ${\cal H}=0.6$ (bottom row in Figure \ref{fig:extensionalNonsymmetric})  
-the two vesicles are separated by the diverging flow as early as $t=75$, and are clearly not a doublet at the end of simulation.
-
-Two main observations can be made of results in Figure~\ref{fig:extensionalNonsymmetric}:
-(1) The membrane tension is highly non-uniform on the vesicles, leading to a significant Marangoni stress along the membrane as in the case of a surfactant-laden drop
-at the center of an extensional flow. Thus it is reasonable to expect that the flow around the vesicles is significantly altered.
-(2) In an extensional flow vesicles are prone to move away from the stagnation point.
-A small initial vertical displacement $\triangle y$ in one  of the vesicles causes both vesicles to not only rotate but also move away from the
-center. Once vesicles move off the horizontal axis, their hydrodynamics is dominated by the diverging flow as they move further away.
-Thus in the microfluidic experiment it is often more desirable to trap the vesicle around the center of an extensional flow \cite{Spjut2010_MSThesis_Chapter3}.
-%
-With an active
-control algorithm to place the stagnation point at a desirable location
-by adjusting the flow with a feedback
-loop~\cite{BentleyLeal1986_JFMa,Johnson-Chavarria2011_EMJ}, a particle can be trapped at the
-stagnation point for long time scales to facilitate image acquisition or
-other detailed measures such as particle image velocimetry of flow
-inside and around the particle.
-
-To explore the application of such a
-fluid trap to measure the adhesion strength between two bound vesicles, 
-we propose the following experiment.  
-Beginning with two
-identical vesicles in an equilibrium configuration that form a doublet
-with a flat contact region (Figure~\ref{fig:Dec18_vesicle_shape}), we
-turn on the fluid trap with the stagnation point placed at the center of
-the vesicle doublet.  Depending on the Hamaker constant, we expect that
-either the flow overcomes the adhesive force and the doublet is broken,
-or the adhesive force is sufficiently strong and the doublet reaches a
-stable stationary configuration.
+At the beginning of the first set of simulations (left panels in
+Figure~\ref{fig:extensionalNonsymmetric}) we place a vesicle at
+$(x,y)=(0,0)$, and the other vesicle at $(x,y) = (3,\Delta y)$ where
+the initial vertical displacement $\Delta y$ varies from $\Delta
+y=0$ for the top row, $\Delta y = 0.02$ for the second row, to
+$\Delta y =0.1$ for the bottom two rows in
+Figure~\ref{fig:extensionalNonsymmetric}.  The Hamaker constant is ${\cal
+H} = 0.7$ for the top three rows, and is ${\cal H} =0.6$ for the bottom
+row.  The color coding is the membrane tension with the color bar on the
+right of each row. We note that the negative tension in an extensional
+flow is consistent with the tension for a vesicle with finite bending
+forces~\cite{Narsimhan2014_JFM} and the speculation for a wrinkled
+membrane in the elongational flow~\cite{KantslerSegreSteinberg2007_PRL}.
+
+Once the planar extensional flow is turned on at $t=0^+$, two vesicles
+move towards each other as shown in
+Figure~\ref{fig:extensionalNonsymmetric}.  For $\Delta y=0$ in the top
+row, the two vesicles stay on the $x$-axis as they move closer to form a
+doublet.  We observe that the left vesicle (initially centered at
+$(0,0)$) moves to the left due to the impinging vesicle from the right.
+As time progresses they form a doublet and reach a steady configuration
+that is symmetric with respect to the stagnation point (square marks in
+the top row of Figure~\ref{fig:extensionalNonsymmetric}).
+
+For $\Delta y>0$ we observe similar vesicle dynamics only at the
+beginning when the right vesicle moves towards the stagnation point and
+the left vesicle is pushed to the left of the stagnation point.  As both
+vesicles come to close vicinity of the stagnation point, the elevated
+right vesicle ($\Delta y > 0$) is pulled up by the diverging flow in the
+$y$ direction, causing rotation of both vesicles.  We also observe that
+the larger the initial vertical displacement, the larger the rotation
+and the faster both vesicles move away from the stagnation point. For
+sufficiently strong adhesion (${\cal H}=0.7$ for the first three rows in
+Figure~\ref{fig:extensionalNonsymmetric}), the two vesicles rotate and
+move away from the stagnation point as a doublet until the end of
+simulations ($t=100$).  As the two vesicles move farther away from the
+stagnation point, the extensional flow becomes more effective in pulling
+the two drops apart as shown in the third row of
+Figure~\ref{fig:extensionalNonsymmetric}.  For ${\cal H}=0.6$ (bottom
+row in Figure~\ref{fig:extensionalNonsymmetric})  the two vesicles are
+separated by the diverging flow as early as $t=75$, and are clearly not
+a doublet at the end of simulation.
+
+Two main observations that can be drawn from the results in
+Figure~\ref{fig:extensionalNonsymmetric} are: (1) The membrane tension is
+highly non-uniform on the vesicles, leading to a significant Marangoni
+stress along the membrane as in the case of a surfactant-laden drop at
+the center of an extensional flow. Thus it is reasonable to expect that
+the flow around the vesicles is significantly altered.  (2) In an
+extensional flow, vesicles are prone to move away from the stagnation
+point.  A small initial vertical displacement $\Delta y$ in one  of the
+vesicles causes both vesicles to not only rotate but also move away from
+the center. Once vesicles move off the horizontal axis, their
+hydrodynamics is dominated by the diverging flow as they move farther
+away.  Thus in the microfluidic experiment it is often more desirable to
+trap the vesicle around the center of an extensional
+flow~\cite{Spjut2010_MSThesis_Chapter3}. With an active control
+algorithm to place the stagnation point at a desirable location by
+adjusting the flow with a feedback
+loop~\cite{BentleyLeal1986_JFMa,Johnson-Chavarria2011_EMJ}, a particle
+can be trapped at the stagnation point for long time scales to
+facilitate image acquisition or other detailed measures such as particle
+image velocimetry of flow inside and around the particle.
+
+To explore the application of such a fluid trap to measure the adhesion
+strength between two bound vesicles, we propose the following
+experiment.  Beginning with two identical vesicles in an equilibrium
+configuration that form a doublet with a flat contact region
+(Figure~\ref{fig:Dec18_vesicle_shape}), we turn on the fluid trap with
+the stagnation point placed at the center of the vesicle doublet.
+Depending on the Hamaker constant, we expect that either the flow
+overcomes the adhesive force and the doublet is broken, or the adhesive
+force is sufficiently strong and the doublet reaches a stable stationary
+configuration.
 
@@
    inclination angle of $\theta = \pi$.}
+   \todo[inline]{What do you think about reversing (a) and (b)?}
  \end{figure}
@@
 Based on how the contact region aligns with the extensional flow, we can
-define the inclination angle $\theta$ of the vesicle doublet as illustrated in
-Figure~\ref{fig:InclinationAngle}(b). When $\theta=\pi$ (Figure~\ref{fig:InclinationAngle}(a))
-the diverging flow
-pulls the vesicles apart from each other and the attractive adhesion
-force is essential to keep the two vesicles from separating.  In
-contrast, when $\theta = \pi/2$ (Figure~\ref{fig:InclinationAngle}(c)), 
-%the doublet long axis is aligned with the diverging flow, 
-the converging flow pushes the vesicles towards
-each other and the repulsive force is essential to keep the
-two vesicles at the separation distance.  With the converging flow
-pushing the two vesicles towards the stagnation point dynamically placed
-at the doublet center, we expect the $\theta=\pi/2$ configuration to be more stable
-than the $\theta=\pi$ configuration. 
-%
-%This is because when $\theta=\pi$
-%the diverging flow is pulling the vesicles away from each other as shown
-%in the illustration.  However, when the doublet inclination angle is
-%fixed at $\theta=\pi/2$, the vesicle doublet stays intact if the
-%adhesive force is strong enough to dominate the fluid drag.  However, it
-%is possible that the diverging flow may overcome adhesion and break up
-%the doublet.  It is also reasonable to expect a vesicle doublet to
-%rotate from the less stable configuration $\theta=\pi$ to the more
-%stable configuration $\theta=\pi/2$, so that the fluid flow is pushing
-%them together rather than pulling them apart.
+define the inclination angle $\theta$ of the vesicle doublet as
+illustrated in Figure~\ref{fig:InclinationAngle}(b). When $\theta=\pi$
+(Figure~\ref{fig:InclinationAngle}(a)) the diverging flow pulls the
+vesicles apart from each other and the attractive adhesion force is
+essential to keep the two vesicles from separating.  In contrast, when
+$\theta = \pi/2$ (Figure~\ref{fig:InclinationAngle}(c)), the converging
+flow pushes the vesicles towards each other and the repulsive force is
+essential to keep the two vesicles at the separation distance.  With the
+converging flow pushing the two vesicles towards the stagnation point
+dynamically placed at the doublet center, we expect the $\theta=\pi/2$
+configuration to be more stable than the $\theta=\pi$ configuration. 
+%
+%This is because when $\theta=\pi$ the diverging flow is pulling the
+%vesicles away from each other as shown in the illustration.  However,
+%when the doublet inclination angle is fixed at $\theta=\pi/2$, the
+%vesicle doublet stays intact if the adhesive force is strong enough to
+%dominate the fluid drag.  However, it is possible that the diverging
+%flow may overcome adhesion and break up the doublet.  It is also
+%reasonable to expect a vesicle doublet to rotate from the less stable
+%configuration $\theta=\pi$ to the more stable configuration
+%$\theta=\pi/2$, so that the fluid flow is pushing them together rather
+%than pulling them apart.
 
@@
   \caption{\label{fig:extensional1} A vesicle doublet in an extensional
-  flow with an initial inclination angle $\theta=\pi$.  The reduced
-  area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} = 0.7$,
-  the separation distance is $\delta = 0.4$, and the extension rate is
-  $\dot\epsilon = 0.02$ ({\em top}), $\dot\epsilon=0.07$ ({\em middle}), and $\dot\epsilon =
-  0.1$ ({\em bottom}).  The center of the vesicle, denoted with a black
-  square, is the stagnation point.  The color coding is the tension.}
+  flow with an initial inclination angle $\theta=\pi$.  The reduced area
+  is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} = 0.7$, the
+  separation distance is $\delta = 0.4$, and the extension rate is
+  $\dot\epsilon = 0.02$ ({\em top}), $\dot\epsilon=0.07$ ({\em middle}),
+  and $\dot\epsilon = 0.1$ ({\em bottom}).  The center of the vesicle,
+  denoted with a black square, is the stagnation point.  The color
+  coding is the tension.}
   \end{figure}
 
+\todo[inline]{Bryan is here}
 In the following numerical experiments we initially place a vesicle
 doublet with $\theta=\pi$, so that the diverging flow may be strong
-enough to pull vesicles away from the doublet.  At low extension
-rates, we expect the doublet to stay bound at the fluid trap stagnation
-point.  On the other hand, the vesicle doublet may become unstable and
-eventually separate at higher extension rates.  Thus we expect there
-to exist a critical extension rate $\dot\epsilon_c$ above which the vesicle
+enough to pull vesicles away from the doublet.  At low extension rates,
+we expect the doublet to stay bound at the fluid trap stagnation point.
+On the other hand, the vesicle doublet may become unstable and
+eventually separate at higher extension rates.  Thus we expect there to
+exist a critical extension rate $\dot\epsilon_c$ above which the vesicle
 doublet cannot stay bound under a given adhesion potential.  Therefore,
-the dependence of the critical extension rate $\dot\epsilon_c$ on the adhesion
-potential and the mechanical vesicle properties provides a means to
-probe the physics of membrane adhesion.
+the dependence of the critical extension rate $\dot\epsilon_c$ on the
+adhesion potential and the mechanical vesicle properties provides a
+means to probe the physics of membrane adhesion.
 
@@
 0.90, and 0.95, all with a length of $2\pi$, and we vary the extension
-rate ($\dot\epsilon$) between $10^{-2}$ and $10^{-1}$.  Since the stagnation
-point can be controlled in an experimental
-setting~\cite{BentleyLeal1986_JFMa,Johnson-Chavarria2011_EMJ}, we mimic the active control of
-the microfluidic experiments by moving the center of the doublet at each
-time step so that the stagnation point occurs exactly in the middle of
-the doublet.  With this adjustment, the vesicles either remain as a
-doublet in the fluid trap centered around the stagnation point, or the
-doublet is broken and the vesicles separate from one another.
-
-Figure~\ref{fig:extensional1} shows snapshots from simulating a vesicle doublet of reduced area  $\Delta A = 0.7$
-at three different extension rates. A general feature of the doublet dynamics is that the doublet rotates from
-$\theta=\pi$ configuration towards the more stable $\theta=\pi/2$
-configuration.  
-%
-We also
-observe that with moderate extension rates, the doublet falls short of
-aligning their long axis with the diverging direction.  Moreover, the
-final inclination angle is closest to the stable $\theta=\pi/2$ for the
-smallest extension rates. While this doublet remains bound for all
-the considered extension rates, a doublet with a reduced area of
-$\Delta A = 0.8$ is split with a critical extension rate $\dot\epsilon_c =
-0.1$ (Figure~\ref{fig:extensional3}).
+rate ($\dot\epsilon$) between $10^{-2}$ and $10^{-1}$.  Since the
+stagnation point can be controlled in an experimental
+setting~\cite{BentleyLeal1986_JFMa,Johnson-Chavarria2011_EMJ}, we mimic
+the active control of the microfluidic experiments by moving the center
+of the doublet at each time step so that the stagnation point occurs
+exactly in the middle of the doublet.  With this adjustment, the
+vesicles either remain as a doublet in the fluid trap centered around
+the stagnation point, or the doublet is broken and the vesicles separate
+from one another.
+
+Figure~\ref{fig:extensional1} shows snapshots from simulating a vesicle
+doublet of reduced area  $\Delta A = 0.7$ at three different extension
+rates. A general feature of the doublet dynamics is that the doublet
+rotates from $\theta=\pi$ configuration towards the more stable
+$\theta=\pi/2$ configuration.  We also observe that with moderate
+extension rates, the doublet falls short of aligning their long axis
+with the diverging direction.  Moreover, the final inclination angle is
+closest to the stable $\theta=\pi/2$ for the smallest extension rates.
+While this doublet remains bound for all the considered extension rates,
+a doublet with a reduced area of $\Delta A = 0.8$ is split with a
+critical extension rate $\dot\epsilon_c = 0.1$
+(Figure~\ref{fig:extensional3}).
 
@@
 
-%
-The equilibrium configuration for low extension rate $\dot\epsilon=0.02$ (top row in Figure~\ref{fig:extensional1}) is
-almost identical to the equilibrium configuration for $\triangle y=0$ (top row of  Figure~\ref{fig:extensionalNonsymmetric}).
-The rotation of the vesicle doublet 
-from $\theta=\pi$ to $\theta=\pi/2$ can be understood as the transition from an unstable configuration $\theta=\pi$ to a stable configuration $\theta=\pi/2$.
-For higher extension rates (second and third rows in Figure~\ref{fig:extensional1}) the partially rotated vesicle pairs at equilibrium are
-also very similar to the case of $\triangle y=0.02$ (second row of Figure~\ref{fig:extensionalNonsymmetric}).
-Such asymmetric vesicle configuration is reminiscent of the asymmetric deformation of a single vesicle in an extensional flow \cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}.
-To gain more insight into such nonlinear dynamics, in the following we explore more physical characterization of the transition from $\theta=\pi$ to $\theta=\pi/2$ at
-different reduced area and extension rate.
-%
+The equilibrium configuration for low extension rate $\dot\epsilon=0.02$
+(top row in Figure~\ref{fig:extensional1}) is almost identical to the
+equilibrium configuration for $\Delta y=0$ (top row of
+Figure~\ref{fig:extensionalNonsymmetric}).  The rotation of the vesicle
+doublet from $\theta=\pi$ to $\theta=\pi/2$ can be understood as the
+transition from an unstable configuration $\theta=\pi$ to a stable
+configuration $\theta=\pi/2$.  For higher extension rates (second and
+third rows in Figure~\ref{fig:extensional1}) the partially rotated
+vesicle pairs at equilibrium are also very similar to the case of
+$\Delta y=0.02$ (second row of
+Figure~\ref{fig:extensionalNonsymmetric}).  Such asymmetric vesicle
+configuration is reminiscent of the asymmetric deformation of a single
+vesicle in an extensional flow~\cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}.
+To gain more insight into such nonlinear dynamics, in the following we
+explore more physical characterization of the transition from
+$\theta=\pi$ to $\theta=\pi/2$ at different reduced area and extension
+rate.
 
@@
 sufficiently close, they are deflected to opposite sides of the $y$
-axis, pass one another, and then separate.  However, in the presence of
+axis, pass one another, and then separate. This head-on collision
+process of two vesicles or capsules in a planar shear flow is found to
+be similar between two-~\cite{LacMorelBarthes-Biesel2007_JFM,
+RahimianVeerapaneniBiros2010_JCP} and
+three-dimensions~\cite{LacBarthes-Biesel2008_PoF,
+OmoriIshikawaImaiYamaguchi2013_JBiomechics,
+RahimianVeerapaneniZorinBiros2015_JCP}.  However, in the presence of
 adhesion, the vesicles can form a doublet for certain values of the
@@
 \section{Conclusions\label{sec:conclusions}}
+\todo[inline]{conclusions need touched up}
 In this work we use a boundary integral formulation with adaptive

### 2019-07-19 vesicle_code/docs/adhesion/adhesion.tex
yny adhesion july 19

--- 2019-07-18 vesicle_code/docs/adhesion/adhesion.tex
@@
 sufficiently close, they are deflected to opposite sides of the $y$
-axis, pass one another, and then separate.  However, in the presence of
+axis, pass one another, and then separate. This head-on collision process of two vesicles or capsules in a planar shear flow
+is found to be similar between two- \cite{Breyiannis-Pozrikidis:2000,RahimianVeerapaneniBiros2010_JCP} and three-dimensions \cite{LacMorelBarthes-Biesel2007_JFM,LacBarthes-Biesel2008_PoF,OmoriIshikawaImaiYamaguchi2013_JBiomechics,RahimianVeerapaneniZorinBiros2015_JCP}.
+However, in the presence of
 adhesion, the vesicles can form a doublet for certain values of the

### 2019-07-19 vesicle_code/docs/adhesion/adhesion.tex
adding adhesion.tex back to repo

--- 2019-07-19 vesicle_code/docs/adhesion/adhesion.tex
@@
 process of two vesicles or capsules in a planar shear flow is found to
-be similar between two-~\cite{LacMorelBarthes-Biesel2007_JFM,
-RahimianVeerapaneniBiros2010_JCP} and
-three-dimensions~\cite{LacBarthes-Biesel2008_PoF,
+be similar between
+two-~\cite{Breyiannis-Pozrikidis:2000,RahimianVeerapaneniBiros2010_JCP}
+, RahimianVeerapaneniBiros2010_JCP} and
+three-dimensions~\cite{LacMorelBarthes-Biesel2007_JFM,LacBarthes-Biesel2008_PoF,
 OmoriIshikawaImaiYamaguchi2013_JBiomechics,

### 2019-07-19 vesicle_code/docs/adhesion/adhesion.tex
yny adhesion

--- 2019-07-19 vesicle_code/docs/adhesion/adhesion.tex
@@
 process of two vesicles or capsules in a planar shear flow is found to
-be similar between two-~\cite{LacMorelBarthes-Biesel2007_JFM,
-RahimianVeerapaneniBiros2010_JCP} and
-three-dimensions~\cite{LacBarthes-Biesel2008_PoF,
+be similar between
+two-~\cite{Breyiannis-Pozrikidis:2000,RahimianVeerapaneniBiros2010_JCP, RahimianVeerapaneniBiros2010_JCP} and
+three-dimensions~\cite{LacMorelBarthes-Biesel2007_JFM,LacBarthes-Biesel2008_PoF,
 OmoriIshikawaImaiYamaguchi2013_JBiomechics,

### 2019-07-19 vesicle_code/docs/adhesion/adhesion.tex
small edits

@@
 similar to a surfactant-laden viscous drop under a planar extensional
-flow~\cite{JanssenBoonAgterof1997_AIChE,HuPineLeal2000_PoF}.  To our
-knowledge no studies on the interactions between two vesicles in an
-extensional flow are available in the literature \todo[inline]{Something
-is off with this sentence}.  In the following we first illustrate how
-two vesicles interact with each other in a planar extensional flow. We
-then illustrate how the adhesion strength between membranes can be
-measured non-intrusively by using the fluid trap.
+flow~\cite{JanssenBoonAgterof1997_AIChE,HuPineLeal2000_PoF}.  To the
+best of our knowledge, no studies on the interactions between two
+vesicles in an extensional flow are available in the literature.  In the
+following we first illustrate how two vesicles interact with each other
+in a planar extensional flow. We then illustrate how the adhesion
+strength between membranes can be measured non-intrusively by using the
+fluid trap.
 
@@
 Figure~\ref{fig:extensionalNonsymmetric}) we place a vesicle at
-$(x,y)=(0,0)$, and the other vesicle at $(x,y) = (3,\Delta y)$ where
-the initial vertical displacement $\Delta y$ varies from $\Delta
-y=0$ for the top row, $\Delta y = 0.02$ for the second row, to
-$\Delta y =0.1$ for the bottom two rows in
-Figure~\ref{fig:extensionalNonsymmetric}.  The Hamaker constant is ${\cal
-H} = 0.7$ for the top three rows, and is ${\cal H} =0.6$ for the bottom
-row.  The color coding is the membrane tension with the color bar on the
-right of each row. We note that the negative tension in an extensional
-flow is consistent with the tension for a vesicle with finite bending
-forces~\cite{Narsimhan2014_JFM} and the speculation for a wrinkled
-membrane in the elongational flow~\cite{KantslerSegreSteinberg2007_PRL}.
+$(x,y)=(0,0)$, and the other vesicle at $(x,y) = (3,\Delta y)$ where the
+initial vertical displacement $\Delta y$ varies from $\Delta y=0$ for
+the top row, $\Delta y = 0.02$ for the second row, to $\Delta y =0.1$
+for the bottom two rows in Figure~\ref{fig:extensionalNonsymmetric}.
+The Hamaker constant is ${\cal H} = 0.7$ for the top three rows, and is
+${\cal H} =0.6$ for the bottom row.  The color coding is the membrane
+tension with the color bar on the right of each row. We note that the
+negative tension in an extensional flow is consistent with the tension
+for a vesicle with finite bending forces~\cite{Narsimhan2014_JFM} and
+the speculation for a wrinkled membrane in the elongational
+flow~\cite{KantslerSegreSteinberg2007_PRL}.
 
@@
    inclination angle of $\theta = \pi$.}
-   \todo[inline]{What do you think about reversing (a) and (b)?}
  \end{figure}

### 2019-07-19 vesicle_code/docs/adhesion/adhesion.tex
yny adhesion

--- 2019-07-19 vesicle_code/docs/adhesion/adhesion.tex
@@
 show that the membranes in the contact region are actually curved with
-end points at the shortest distance.  Once a vesicle doublet forms, we
+end points at the shortest distance, consistent with results for moderate 
+adhesion strength in \cite{FlormannAouane2017_SciReports}.  
+Once a vesicle doublet forms, we
 examine the dependence of membrane bending and adhesion energies on the
@@
 
-Next we conduct a numerical experiment where a vesicle doublet is placed
+Next we conduct numerical simulations of two vesicles in a planar extensional flow. 
+With initial configurations where two vesicles collide around the stagnation point 
+(one vesicle at the stagnation point and the other vesicle placed close to the converging axis),
+the two vesicles form a doublet and stay around the flow center only when two 
+vesicles collide head-on with no displacement $\triangle y=0$. 
+For $\triangle y >0$ we find that the vesicles rotate and move away from the stagnation point, and eventually
+move further from each other due to the strong diverging flow in the far-field.
+
+This inspires us to conduct a numerical experiment where a vesicle doublet is placed
 at the center of a fluid trap, which can be actively controlled in
@@
 experiments, and we hope that our simulations will inspire microfluidic
-experiments.
+experiments to be designed to measure membrane-membrane adhesion.
 

### 2019-07-19 vesicle_code/docs/adhesion/revisions/summary_of_changes.tex

@@
 
-\item In Section IV: Adhesion of two vesicles in a planar extensional flow, we conducted new simulation to elucidate the interaction between two vesicles in a planar extensional flow.
-These results are summarized in Figure 6.
+\item In Section IV: Adhesion of two vesicles in a planar extensional
+  flow, we conducted new simulations to elucidate the interaction
+    between two vesicles in a planar extensional flow. These results are
+    summarized in Figure 6.
 
@@
 \item In Section V: Adhesion of two vesicles in a shear flow, we conducted more simulations to examine the oscillation of the vesicle doublet and how the oscillation frequency depends on 
-the shear rate, separation distance, and Hamaker constant.
-These results are summarized in Figure 13(b).
-We also did some analysis to compare the double oscillation with the Jeffery orbit of a rigid ellipse in shear flow.
+the shear rate, separation distance, and Hamaker constant. These results are summarized in Figure 13(b).
 
-\item In Section V: Adhesion of two vesicles in a shear flow, we conducted more simulations to examine the effect of the separation distance $\delta$ based on reviewers' suggestions.
+\item In Section V: We did some analysis to compare the double
+  oscillation with the Jeffery orbit of a rigid ellipse in shear flow.
+    These results are summarized in Table I.
 
-\item In Section V: Adhesion of two vesicles in a shear flow, we corrected the calculation of the intrinsic viscosity and the new results are summarized in Figure 15.
+\item In Section V: Adhesion of two vesicles in a shear flow, we
+  conducted more simulations to examine the effect of the separation
+    distance $\delta$ based on reviewers' suggestions.
+
+\item In Section V: Adhesion of two vesicles in a shear flow, we
+  corrected the calculation of the intrinsic viscosity and the new
+    results are summarized in Figure 15.  We also discussed the effect
+    of the separation distance on the intrinsic viscosity.
+
+\item In Section VI: We have modified the conclusions to include a
+  discussion of our new results.
 

### 2019-07-19 vesicle_code/docs/adhesion/revisions/reviewer1.tex
rev1 comment on BIE

@@
 \begin{itemize}
-  \item We thank the referee for this comment. The referee is absolutely correct by labeling boundary integral simulation as a standard approach.
-  However, the boundary integral algorithm we used for this work is not standard boundary integral algorithm for two reasons: (1) First the time marching is adaptive, allowing us to efficiently run the simulations for a long time with accuracy and convergence.
-(2) Second we adopted a slightly sophisticated near singular evaluation to ensure that our numerical results are convergent when two boundaries are close to each other.
+  \item We thank the referee for this comment.
+The referee is absolutely correct by labeling boundary integral simulation as a standard approach.
+However, the boundary integral algorithm as applied to the adhesion problem here is quite novel for two reasons: (1) First, we applied a new adaptive time marching developed recently in \texttt{Quaife, Biros, \textbf{JCP} (2016)}, allowing us to efficiently run long time-horizon simulations.
+(2) Second, the close vesicle-vesicle interactions in the doublet case is quite challenging to capture accurately; here, we employed a novel near-singular integral evaluation scheme which is an extension of the method developed in  \texttt{Quaife, Biros, \textbf{JCP} (2014)}.
 Without adaptive time marching, the boundary integral simulations of vesicles often give unreliable results as shown in

### 2019-07-19 vesicle_code/docs/adhesion/adhesion.tex
yny adhesion
yny adhesion up to page 9

@@
 %
+In a planar extensional flow we find a stable vesicle doublet forms only when two 
+vesicles collide head-on around the stagnation point. 
 In a microfluid trap where the stagnation of an extensional flow is
@@
 doublet may form provided that the adhesion strength is sufficiently
-large at a given vesicle reduced area. Once a doublet is formed, the
-effective shear viscosity of a dilute suspension of vesicle doublets is
+large at a given vesicle reduced area. 
+Once a doublet is formed, its oscillatory dynamics is found to depend on the adhesion strength and their reduced area.
+Furthermore the effective shear viscosity of a dilute suspension of vesicle doublets is
 found to be a function of  reduced area.  Results from these numerical
@@
 potential~\cite{FlormannAouane2017_SciReports}, that consists of a
-long-range attraction component and a short-range repulsion
+long-range attraction component (truncated at some finite distance beyond which membrane interaction becomes negligible) 
+and a short-range repulsion
 component~\cite{Book_IntermolecularSurfaceForces}, and the combination
@@
 The ratio of total adhesion energy to the bending energy
-(bending rigidity of lipid bilayer membranes $\sim 10^{-19}$ $J$) gives
+(bending modulus of lipid bilayer membranes $\sim 10^{-19}$ $J$) gives
 a measure of vesicle deformation in the presence of
@@
 separation distance set by the adhesion potential.  In
-Section~\ref{sec:eflow} we numerically investigate the hydrodynamics of
+Section~\ref{sec:eflow} we first study the hydrodynamics of two vesicles in
+a planar extensional flow. We then numerically investigate the hydrodynamics of
 a vesicle doublet in a fluid trap where the stagnation point is actively
@@
 energy model, is $\BB \xx = -\kappa_b \xx_{ssss}$, where the subscript $s$ denotes derivative with respect to arclength $s$. $\kappa_b$ is
-the bending rigidity modulus which we set to be 1 for all examples. The
+the bending modulus which we set to be 1 for all examples. The
 stretching force is $\TT \sigma = (\sigma \xx_s)_s$, where the tension,
@@
 for small distances ($z < \delta$) the potential is repulsive to prevent
-physical contact.
+physical contact. The long-range attraction component should decay sufficiently fast
+to mimic the finite-range attraction between RBCs. However, here to simplify
+the formulation we do not introduce such a truncation in the attraction.
 
@@
 ranging from $\mathcal{O}(10^{-1})$ to $\mathcal{O}(10^0)$ times the
-bending rigidity modulus.  We assume that the adhesion force from
+bending modulus.  We assume that the adhesion force from
 equation~\eqref{eq:adhesion_potential} applies between all pairs of
@@
 summary of boundary integral formulation can be found in
-Appendix~\ref{sec:AppendixB}.
+Appendix~\ref{sec:AppendixB}. For the rest of the paper, 
+the dimensionless bending modulus is set to be one ($\kappa_b = 1$) unless otherwise specified.
 
@@
 shape in the contact region depends on the adhesion strength relative to
-the membrane bending rigidity.  For weak to moderate adhesion strength,
+the membrane bending modulus.  For weak to moderate adhesion strength,
 vesicle membranes are flattened in the contact region while the rest of
@@
   areas of $\Delta A=0.95$, $0.75$, and $0.6$ are labeled.  The vesicle
-  length is fixed at $2\pi$, the dimensionless bending rigidity modulus
-  is $\kappa_b=1$, the Hamaker constant is $\mathcal{H}=5$, and the
-  separation distance is $\delta=0.2$.  The color coding is the tension
+  length is fixed at $2\pi$, the dimensionless bending modulus
+  $\kappa_b=1$, the Hamaker constant $\mathcal{H}=5$, and the
+  separation distance $\delta=0.2$.  The color coding is the tension
   along the vesicle.  The overall equilibrium shapes of two vesicles
@@
 revealed novel nonlinear vesicle dynamics not found for a viscous
-drop~\cite{KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
+drop~\cite{KantslerSegreSteinberg2007_PRL,KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
 Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  Here we focus on
@@
 tension with the color bar on the right of each row. We note that the
-negative tension in an extensional flow is consistent with the tension
-for a vesicle with finite bending forces~\cite{Narsimhan2014_JFM} and
-the speculation for a wrinkled membrane in the elongational
-flow~\cite{KantslerSegreSteinberg2007_PRL}.
+negative tension in an extensional flow is consistent with the destabilizing tension 
+for a vesicle with finite bending forces~\cite{Narsimhan2014_JFM}.
+%and the speculation for a wrinkled membrane in the elongational flow~\cite{KantslerSegreSteinberg2007_PRL}.
 
@@
   flow with an initial inclination angle $\theta=\pi$.  The reduced area
-  is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} = 0.7$, the
-  separation distance is $\delta = 0.4$, and the extension rate is
+  $\Delta A = 0.7$, the Hamaker constant $\mathcal{H} = 0.7$, the
+  separation distance $\delta = 0.4$, and the extension rate
   $\dot\epsilon = 0.02$ ({\em top}), $\dot\epsilon=0.07$ ({\em middle}),
@@
   flow with an initial inclination angle $\theta=\pi$.  The reduced area
-  is $\Delta A = 0.8$, the Hamaker constant $\mathcal{H} = 0.7$, the
-  separation distance is $\delta = 0.4$, and the extension rate
+  $\Delta A = 0.8$, the Hamaker constant $\mathcal{H} = 0.7$, the
+  separation distance $\delta = 0.4$, and the extension rate
   $\dot\epsilon = 0.1$.  The center of the vesicle, denoted with a black
@@
   \caption{\label{fig:doublet090-weakAdhesion} The formation of a weakly
-  adhered doublet in a shear flow.  The reduced area is $\Delta A =
-  0.9$, the Hamaker constant is $\mathcal{H}=0.7$, the separation
-  distance is $\delta = 0.4$, and the shear rate is $\dot\gamma=0.5$.
+  adhered doublet in a shear flow.  The reduced area $\Delta A =
+  0.9$, the Hamaker constant $\mathcal{H}=0.7$, the separation
+  distance $\delta = 0.4$, and the shear rate $\dot\gamma=0.5$.
   The interaction between the two vesicles is a sliding motion, and the
@@
   viscosity of a tank-treading vesicle (blue) and a doublet (red).  The
-  shear rate is $\dot\gamma = 0.5$, the Hamaker constant is $\mathcal{H}
-  = 0.7$, and the separation distance is $\delta = 0.4$.  The black
+  shear rate $\dot\gamma = 0.5$, the Hamaker constant $\mathcal{H}
+  = 0.7$, and the separation distance $\delta = 0.4$.  The black
   marks denote intrinsic viscosity values computed by Ghigliotti {\em et
@@
 thus provide a means to probe the adhesion strength between membranes.
-For a pair of $\mu m$-sized vesicles with a bending rigidity of $\sim
+For a pair of $\mu m$-sized vesicles with a bending modulus of $\sim
 10^{-19}$ $J$, an extensional flow rate of $0.5$ $s^{-1}$ is expected to
@@
 simulations presented in this work are for identical vesicles (same
-reduced area, length, and bending rigidity modulus) in the doublet.
+reduced area, length, and bending modulus) in the doublet.
 Flormann {\em et al.}~demonstrated that asymmetric vesicle reduced area

### 2019-07-20 vesicle_code/docs/adhesion/adhesion.tex
touched up first 2 sections

@@
 %
-In a planar extensional flow we find a stable vesicle doublet forms only when two 
-vesicles collide head-on around the stagnation point. 
-In a microfluid trap where the stagnation of an extensional flow is
+In a planar extensional flow we find a stable vesicle doublet forms only
+when two vesicles collide head-on around the stagnation point.  In a
+microfluid trap where the stagnation of an extensional flow is
 dynamically placed in the middle of a vesicle doublet through an active
-control loop, novel dynamics of a vesicle doublet is observed. Numerical
-simulations show that there exists a critical extensional flow rate
-above which adhesive interaction is overcome by the diverging stream,
-thus providing a simple method to measure the adhesion strength between
-two vesicle membranes. 
+control loop, novel dynamics of a vesicle doublet are observed.
+Numerical simulations show that there exists a critical extensional flow
+rate above which adhesive interaction is overcome by the diverging
+stream, thus providing a simple method to measure the adhesion strength
+between two vesicle membranes. 
 %
@@
 doublet may form provided that the adhesion strength is sufficiently
-large at a given vesicle reduced area. 
-Once a doublet is formed, its oscillatory dynamics is found to depend on the adhesion strength and their reduced area.
-Furthermore the effective shear viscosity of a dilute suspension of vesicle doublets is
-found to be a function of  reduced area.  Results from these numerical
-studies and analysis shed light on the hydrodynamic and rheological
-consequences of adhesive interactions between vesicles in a viscous
-fluid.
-%\begin{description}
-%\item[Usage]
-%Secondary publications and information retrieval purposes.
-%\item[PACS numbers]
-%May be entered using the \verb+\pacs{#1}+ command.
-%\item[Structure]
-%You may use the \texttt{description} environment to structure your abstract;
-%use the optional argument of the \verb+\item+ command to give the category of each item. 
-%\end{description}
+large at a given vesicle reduced area.  Once a doublet is formed, its
+oscillatory dynamics is found to depend on the adhesion strength and
+their reduced area.  Furthermore the effective shear viscosity of a
+dilute suspension of vesicle doublets is found to be a function of the
+reduced area.  Results from these numerical studies and analysis shed
+light on the hydrodynamic and rheological consequences of adhesive
+interactions between vesicles in a viscous fluid.
 \end{abstract}
@@
 widely utilized as biological cell mimics in biophysics and material
-engineering~\cite{sackmann1996, FenzSengupta2012_IntegrBiol,Barthes-Biesel2016_ARFM}.  The ever
-expanding applications of vesicles have encouraged detailed experimental,
-theoretical, and numerical investigations of vesicle dynamics in
-applied flow, electric fields, and magnetic fields.  
-Experimental investigations of vesicles have uncovered vesicle properties and various novel applications
-\cite{Dobereiner2000_CurrentOpinionCIS,EvansRawiczSmith2013_FaradayDiscussions,SugiyamaToyota2018_Life}. 
-Theoretical investigations are often limited to small-deformation analysis on a nearly spherical vesicle
-or spheroidal analysis on a spheroidal vesicle \cite{Barthes-BieselRallison1981_JFM, Misbah2006_PRL,
+engineering~\cite{sackmann1996, FenzSengupta2012_IntegrBiol,
+Barthes-Biesel2016_ARFM}.  The ever expanding applications of vesicles
+have encouraged detailed experimental, theoretical, and numerical
+investigations of vesicle dynamics in applied flow, electric fields, and
+magnetic fields.  Experimental investigations of vesicles have uncovered
+vesicle properties and various novel
+applications~\cite{Dobereiner2000_CurrentOpinionCIS,
+EvansRawiczSmith2013_FaradayDiscussions, SugiyamaToyota2018_Life}.
+Theoretical investigations are often limited to small-deformation
+analysis on a nearly spherical vesicle or spheroidal analysis on a
+spheroidal vesicle~\cite{Barthes-BieselRallison1981_JFM, Misbah2006_PRL,
 Vlahovska2007_PRE, Finken2008_EPL, ZhangZahnTanLin2013_PoF,
@@
 by direct numerical simulations~\cite{GhigliottiBibenMisbah2010_JFM} and
-experiments~\cite{Vitkova2008_BJ,DeschampsKantsler2009_PNAS,
+experiments~\cite{Vitkova2008_BJ, DeschampsKantsler2009_PNAS,
 KantslerSegreSteinberg2008_EPL, ZabuskySegreDeschamps2011_PoF}.  Between
@@
 ZiherlSvetina2007_PNAS} or
-clusters~\cite{SvetinaZiherl2008_Bioelectrochemistry,GuWangGunzburger2016_MathBiol,
-FlormannAouane2017_SciReports}.  As a model for red blood cell (RBC)
-aggregates, a simplified model for adhesive vesicle-vesicle interactions
-can reproduce vesicle shapes similar to those observed in experiments of
-fibrinogen-induced RBC
-aggregates~\cite{SvetinaZiherl2008_Bioelectrochemistry,GuWangGunzburger2016_MathBiol,FlormannAouane2017_SciReports,HooreYayaPodgorski2018_SoftMatt,bru-aou-thi-flo-ver-Kae-las-sel-ben-pod-cou-mis-wag2014,cla-aou-thi-abk-cou-mis-joh-wag2017}.
-Using the Lennard-Jones (L.-J.)~potential for point-point interaction
-between two vesicle membranes without the molecular details of adhesive
-interactions between RBCs, Flormann {\em et
-al.}~\cite{FlormannAouane2017_SciReports} found that, under strong
-adhesion, the membrane may buckle to a sigmoidal shape in the contact
-region.  Such a sigmoidal vesicle shape is also observed in RBC doublets
-and explained in a slightly different
+clusters~\cite{SvetinaZiherl2008_Bioelectrochemistry,
+GuWangGunzburger2016_MathBiol, FlormannAouane2017_SciReports}.  As a
+model for red blood cell (RBC) aggregates, a simplified model for
+adhesive vesicle-vesicle interactions can reproduce vesicle shapes
+similar to those observed in experiments of fibrinogen-induced RBC
+aggregates~\cite{SvetinaZiherl2008_Bioelectrochemistry,
+GuWangGunzburger2016_MathBiol, FlormannAouane2017_SciReports,
+HooreYayaPodgorski2018_SoftMatt,
+bru-aou-thi-flo-ver-Kae-las-sel-ben-pod-cou-mis-wag2014,
+cla-aou-thi-abk-cou-mis-joh-wag2017}.  Using the Lennard-Jones
+(L.-J.)~potential for point-point interaction between two vesicle
+membranes without the molecular details of adhesive interactions between
+RBCs, Flormann {\em et al.}~\cite{FlormannAouane2017_SciReports} found
+that, under strong adhesion, the membrane may buckle to a sigmoidal
+shape in the contact region.  Such a sigmoidal vesicle shape is also
+observed in RBC doublets and explained in a slightly different
 model~\cite{ZiherlSvetina2007_PNAS}.  It remains unknown how adhesive
@@
 between a vesicle and a solid has been extensively studied with more
-focus on the static equilibrium shapes~\cite{Seifert1990_PRA,BernardGuedeau-Boudeville2000_Langmuir,
-ShiFengGao2006_ActaMechSin, LinFreund2007_IntJSolidsStructures,
-GruhnFrankeDimova2007_Langmuir,das2008adhesion,
-zhang2009phase,Agudo-Canalejo2015_ACSNano,Agudo-CanalejoLipowsky2015_NanoLett,
-SteinkuhlerAgudo-Canalejo2016_BJ,Agudo-CanalejoLipowsky2017_SoftMatt}
-than the transient adhesion process~\cite{cantat1999lift, suk-sei2001,
-BlountMiksisDavis2013_PRSa}.  Adhesive interactions between lipid
-membranes are essential in many biomedical, biological, and biophysical
-processes.  For example, vesicle adhesion is crucial to initiate
-membrane fusion and fission in endocytosis, exocytosis, and the
-transport of small vesicles through membrane surfaces.  In the absence
-of an external electric field and ions in the solvents, it is reported
-that the adhesive interactions between two membranes can be well
-approximated by the L.-J.-type
+focus on the static equilibrium shapes~\cite{Seifert1990_PRA,
+BernardGuedeau-Boudeville2000_Langmuir, ShiFengGao2006_ActaMechSin,
+LinFreund2007_IntJSolidsStructures, GruhnFrankeDimova2007_Langmuir,
+das2008adhesion, zhang2009phase, Agudo-Canalejo2015_ACSNano,
+Agudo-CanalejoLipowsky2015_NanoLett, SteinkuhlerAgudo-Canalejo2016_BJ,
+Agudo-CanalejoLipowsky2017_SoftMatt} than the transient adhesion
+process~\cite{cantat1999lift, suk-sei2001, BlountMiksisDavis2013_PRSa}.
+Adhesive interactions between lipid membranes are essential in many
+biomedical, biological, and biophysical processes.  For example, vesicle
+adhesion is crucial to initiate membrane fusion and fission in
+endocytosis, exocytosis, and the transport of small vesicles through
+membrane surfaces.  In the absence of an external electric field and
+ions in the solvents, it is reported that the adhesive interactions
+between two membranes can be well approximated by the L.-J.-type
 potential~\cite{FlormannAouane2017_SciReports}, that consists of a
-long-range attraction component (truncated at some finite distance beyond which membrane interaction becomes negligible) 
-and a short-range repulsion
-component~\cite{Book_IntermolecularSurfaceForces}, and the combination
-of the two gives rise to an equilibrium distance where the interaction
-potential is at its minimum~\cite{Book_IntermolecularSurfaceForces}.
+long-range attraction component (truncated at some finite distance
+beyond which membrane interaction becomes negligible) and a short-range
+repulsion component~\cite{Book_IntermolecularSurfaceForces}, and the
+combination of the two gives rise to an equilibrium distance where the
+interaction potential is at its
+minimum~\cite{Book_IntermolecularSurfaceForces}.
 
@@
 membrane contact angle at the edge of contact
-zone~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir,
-MaresDanielIglic2012_SciWorldJ}.  Alternatively, Evans and
+zone~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir, MaresDanielIglic2012_SciWorldJ}.  Alternatively, Evans and
 Metcalfe~\cite{EvansMetcalfe1984_BJ} used the micropipette to measure
@@
 density is larger than $1$ $\mu J/m^2$ and ``weak" when the energy
-density is less than $1$ $\mu J/m^2$.  
-%In this work we use the ratio of
-%the adhesion energy to the bending energy for classification of adhesion
-%strength. 
-The ratio of total adhesion energy to the bending energy
-(bending modulus of lipid bilayer membranes $\sim 10^{-19}$ $J$) gives
-a measure of vesicle deformation in the presence of
+density is less than $1$ $\mu J/m^2$. The ratio of total adhesion energy
+to the bending energy (bending modulus of lipid bilayer membranes $\sim
+10^{-19}$ $J$) gives a measure of the vesicle deformation in the
+presence of
 adhesion~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.
@@
 equilibration of vesicle membranes in the strong adhesion regime has
-been well-studied and documented
-(see~\cite{Agrawal2011_MathMechSolids,RamachandranAndersonLealIsraelachvili2010_Langmuir,
+been well-studied and documented (see~\cite{Agrawal2011_MathMechSolids,
+RamachandranAndersonLealIsraelachvili2010_Langmuir,
 SteinkuhlerAgudo-Canalejo2016_BJ, FlormannAouane2017_SciReports} and
@@
 separation distance set by the adhesion potential.  In
-Section~\ref{sec:eflow} we first study the hydrodynamics of two vesicles in
-a planar extensional flow. We then numerically investigate the hydrodynamics of
-a vesicle doublet in a fluid trap where the stagnation point is actively
-controlled to be at the center of the vesicle doublet. From these
-results we propose a novel application of the microfluidic fluid trap to
-probe the adhesion strength between lipid bilayer membranes in
-solutions. In Section~\ref{sec:sflow} we investigate how two vesicles
-may form a doublet as they move toward each other under a planar shear
-flow.  We map out the parameter regions for bound/unbound vesicles under
-a planar shear flow, and we also investigate the effects of adhesive
-interactions on the rheological properties of a dilute suspension of
-vesicle doublets.  Finally in Section~\ref{sec:conclusions} we discuss
-the implications of our results and point out a few potential future
-directions.
+Section~\ref{sec:eflow} we first study the hydrodynamics of two vesicles
+in a planar extensional flow. We then numerically investigate the
+hydrodynamics of a vesicle doublet in a fluid trap where the stagnation
+point is actively controlled to be at the center of the vesicle doublet.
+From these results we propose a novel application of the microfluidic
+fluid trap to probe the adhesion strength between lipid bilayer
+membranes in solutions. In Section~\ref{sec:sflow} we investigate how
+two vesicles may form a doublet as they move toward each other under a
+planar shear flow.  We map out the parameter regions for bound/unbound
+vesicles under a planar shear flow, and we also investigate the effects
+of adhesive interactions on the rheological properties of a dilute
+suspension of vesicle doublets.  Finally in
+Section~\ref{sec:conclusions} we discuss the implications of our results
+and point out a few potential future directions.
 
@@
 \end{equation}
-where $\uu$ is the fluid velocity field, $p$ is the pressure, and the scaled viscosity $\mu=1$ inside the vesicles. Outside the vesicle
-$\mu=\mu_e/\mu_i$ with $\mu_i$ ($\mu_e$)  the viscosity of the interior  (exterior) fluid.  We set
-the viscosity ratio $\mu_e/\mu_i=1$ for the rest of the paper.
-$T = - p I + \mu\left(\nabla \uu + \nabla \uu^T\right)$ is the stress
-tensor, $\llbracket T \rrbracket$ is the jump across the membrane, and
-$\xxi$ is the traction that is the sum of the bending, stretching,
-and adhesion forces defined in equation~(\ref{eqn:traction}) of Appendix \ref{sec:AppendixB}.  The bending force, arising from the Helfrich
-energy model, is $\BB \xx = -\kappa_b \xx_{ssss}$, where the subscript $s$ denotes derivative with respect to arclength $s$. $\kappa_b$ is
-the bending modulus which we set to be 1 for all examples. The
-stretching force is $\TT \sigma = (\sigma \xx_s)_s$, where the tension,
-$\sigma$, acts as a Lagrange multiplier to satisfy the local
-extensibility constraint.  The resistance to bending and stretching are
-standard assumptions on vesicles.  In this work, we include an adhesive
-force, $\AA \xx$, that we now describe.
+where $\uu$ is the fluid velocity field, $p$ is the pressure, and the
+scaled viscosity $\mu=1$ inside the vesicles. Outside the vesicle
+$\mu=\mu_e/\mu_i$ with $\mu_i$ ($\mu_e$) the viscosity of the interior
+(exterior) fluid.  We set the viscosity ratio $\mu_e/\mu_i=1$ for the
+rest of the paper.  $T = - p I + \mu\left(\nabla \uu + \nabla
+\uu^T\right)$ is the stress tensor, $\llbracket T \rrbracket$ is the
+jump across the membrane, and $\xxi$ is the traction that is the sum of
+the bending, stretching, and adhesion forces defined in
+equation~(\ref{eqn:traction}) of Appendix~\ref{sec:AppendixB}.  The
+bending force, arising from the Helfrich energy model, is $\BB \xx =
+-\kappa_b \xx_{ssss}$, where the subscript $s$ denotes derivative with
+respect to arclength $s$. $\kappa_b$ is the bending modulus which we set
+to be 1 for all examples. The stretching force is $\TT \sigma = (\sigma
+\xx_s)_s$, where the tension, $\sigma$, acts as a Lagrange multiplier to
+satisfy the local extensibility constraint.  The resistance to bending
+and stretching are standard assumptions on vesicles.  In this work, we
+include an adhesive force, $\AA \xx$, that we now describe.
 
@@
   \end{tabular}
-%  \begin{minipage}{0.31\textwidth}
-%    \centering
-%    \includegraphics[height=5cm,trim={0cm 0cm 2cm 0cm},clip]{figs/adhesionPotential.pdf}
-%  \end{minipage}
-%  \hfill
-%  \begin{minipage}{0.31\textwidth}
-%    \centering
-%    \includegraphics[height=5cm]{figs/configCartoon.pdf}
-%  \end{minipage}
-%  \hfill
-%  \begin{minipage}{0.31\textwidth}
-%    \centering
-%    \includegraphics[height=5cm,trim={3cm 0cm 2cm 0cm},clip]{figs/Adhesion_Force.png}
-%  \end{minipage}
   \caption{\label{fig:adhesionModel} (a) The adhesion potential
@@
 L.-J.~type potential
-%Sukumaran and Seifert~\cite{suk-sei2001} consider adhesion between a
-%single three-dimensional vesicle and a solid wall at $z=0$.  They use
-%the adhesion potential of the function form
 \begin{align}
@@
 \end{align}
-where $\mathcal{H}$ is the Hamaker constant and $\delta$ is the adhesion
+where $\mathcal{H}$ is the Hamaker constant, $\delta$ is the adhesion
 length scale, and $z$ is the distance between a patch on the vesicle
@@
 adhesive force is zero at the equilibrium distance $z=\delta$.  For
-large distances ($z> \delta$) the adhesive potential is attractive while
-for small distances ($z < \delta$) the potential is repulsive to prevent
-physical contact. The long-range attraction component should decay sufficiently fast
-to mimic the finite-range attraction between RBCs. However, here to simplify
-the formulation we do not introduce such a truncation in the attraction.
+large distances ($z > \delta$) the adhesive potential is attractive
+while for small distances ($z < \delta$) the potential is repulsive to
+prevent physical contact. The long-range attraction component should
+decay sufficiently fast to mimic the finite-range attraction between
+RBCs. However, here to simplify the formulation we do not introduce such
+a truncation in the attraction.
 
@@
 the L.-J.~potential between two molecules, and has been used to model
-membrane-membrane adhesion  \cite{FlormannAouane2017_SciReports}.  In
-our case, the adhesion potential is between two small patches of lipid
+membrane-membrane adhesion~\cite{FlormannAouane2017_SciReports}.  In our
+case, the adhesion potential is between two small patches of lipid
 bilayer membrane (because the lipid molecules are coarse-grained in the
@@
 
-Large value of $m$ corresponds to a sharp increase in the repulsion
+A large value of $m$ corresponds to a sharp increase in the repulsion
 force as two objects are within the separation distance $\delta$.  This
@@
 summary of boundary integral formulation can be found in
-Appendix~\ref{sec:AppendixB}. For the rest of the paper, 
-the dimensionless bending modulus is set to be one ($\kappa_b = 1$) unless otherwise specified.
+Appendix~\ref{sec:AppendixB}. For the rest of the paper, the
+dimensionless bending modulus is set to be one ($\kappa_b = 1$) unless
+otherwise specified.
 
@@
 \label{sec:qflow} 
+\todo[inline]{Bryan is here}
 We consider two identical vesicles suspended in a quiescent flow.
@@
 
-\todo[inline]{Bryan is here}
 In the following numerical experiments we initially place a vesicle

### 2019-07-20 vesicle_code/examples/extensional2Ves.m

@@ -5,10 +5,10 @@ clear all; clc
 fprintf('Two elliptical vesicles in a extensional flow.\n');
 
 % Physics parameters
-prams.N = 128;               % points per vesicle
+prams.N = 64;               % points per vesicle
 prams.nv = 2;               % number of vesicles
-prams.T = 4000;               % time horizon (two tumbling)
-prams.m = 1000;             % number of time steps
+prams.T = 100;               % time horizon (two tumbling)
+prams.m = 100;             % number of time steps
 prams.kappa = [1 1];         % bending coefficient
 prams.viscCant = [1 1];         % viscosity contrast
 options.farField = 'extensional'; % background velocity
@@ -28,21 +28,21 @@ prams.errorTol = 1;
 
 % ADD-ONS
 options.correctShape = false;
-options.adhesion = true;
+options.adhesion = false;
 prams.adRange = 4e-1;
 prams.adStrength = 7e-1;
 
 % TIME ADAPTIVITY (parameters for new implementation)
-options.timeAdap = true;
+options.timeAdap = false;
 
-prams.rtolArea = 1e-1;
-prams.rtolLength = 1e-1;
+prams.rtolArea = 1e-2;
+prams.rtolLength = 1e-2;
 prams.betaUp = 1.2;
 prams.betaDown = 0.5;
 prams.alpha = 0.9;
 
 options.orderGL = 2;
-options.nsdc = 1;
+options.nsdc = 0;
 options.expectedOrder = 1;
 
 % Plot on-the-fly
@@ -100,18 +100,18 @@ posy2 = interpft(posy2,prams.N);
 
 X = [posx1 posx2; posy1 posy2];
 
-%oc = curve;
-%centerx = zeros(1,2);
-%centery = [-1 1];
-%ang = 0*ones(2,1);
-%ra = 0.6;
-%scale = 0.5*sqrt(ra);
-%X = oc.initConfig(prams.N,'nv',prams.nv,...
-%    'reducedArea',ra,...
-%    'center',[centerx;centery],...
-%    'angle',ang,...
-%    'scale',scale);
-%% Initial configuration of reduce area 0.65 and aligned
+oc = curve;
+centerx = [0 3];
+centery = zeros(1,2);
+ang = pi/2*ones(2,1);
+ra = 0.95;
+scale = 0.5*sqrt(ra);
+X = oc.initConfig(prams.N,'nv',prams.nv,...
+    'reducedArea',ra,...
[…]

### 2019-07-20 vesicle_code/examples/output/makeImages.m

@@ -2,13 +2,13 @@ addpath ../../src
 set(0,'DefaultAxesFontSize',22)
 options.savefig = false;
 
-irate = 10; % controls the speed of the visualization
+irate = 5; % controls the speed of the visualization
 
-if 0
-%  file = 'extensional2VesData.bin';
+if 1
+  file = 'extensional1VesData.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/extensional2Ves_rotated/adR4em1adS7em1Chi7em2_ra070/extensional2VesData.bin';
-  file = '~/projects/brinkman/vesicle_code/results/yuan_runs/june_28_2019/extensional2VesData75be.bin';
-  ax = 2*[-2 2 -2 2];
+%  file = '~/projects/brinkman/vesicle_code/results/yuan_runs/june_28_2019/extensional2VesData75be.bin';
+  ax = 1*[-2 2 -2 2];
   options.confined = false;
 end
 if 0
@@ -58,7 +58,7 @@ if 0
   ax = [-5 5 -5 5];
   options.confined = false;
 end
-if 1
+if 0
   file = '~/projects/brinkman/vesicle_code/results/shear2Ves/adR1em1adS4e0Chi5em1_ra090/shear2VesData.bin';
   ax = [-3 3 -3 3];
   options.confined = false;
@@ -76,6 +76,17 @@ end
 istart = 1;
 iend = numel(time);
 ntime = numel(time);
+
+oc = curve;
+[~,~,L] = oc.geomProp([posx(:,1,1);posy(:,1,1)]);
+for k = 1:numel(time)
+  [~,~,cur1] = oc.diffProp([posx(:,1,k);posy(:,1,k)]);
+  ten(:,1,k) = ten(:,1,k) + 1.5*L*cur1.^2;
+
+%  [~,~,cur2] = oc.diffProp([posx(:,2,k);posy(:,2,k)]);
+%  ten(:,2,k) = ten(:,2,k) + 1.5*cur2.^2;
+end
+
 
 %min_ten = floor(min(min(min(ten))));
 %max_ten = floor(max(max(max(ten))));

### 2019-07-20 vesicle_code/docs/adhesion/adhesion.tex
yny adhesion 1st round on july 20

@@
 decay sufficiently fast to mimic the finite-range attraction between
-RBCs. However, here to simplify the formulation we do not introduce such
-a truncation in the attraction.
+RBCs. In this work we are mainly interested in effects of adhesive 
+interactions between two vesicles drawn together by the surrounding linear flow.
+Therefore we  do not introduce any truncation in the long-range attraction.
 
@@
 
-Two main observations that can be drawn from the results in
-Figure~\ref{fig:extensionalNonsymmetric} are: (1) The membrane tension is
+Here we provide two main observations drawn from the results in
+Figure~\ref{fig:extensionalNonsymmetric}: (1) The membrane tension is
 highly non-uniform on the vesicles, leading to a significant Marangoni
@@
 \label{sec:sflow} 
-We consider two vesicles suspended in the planar shear flow $\uu =
+We consider two vesicles under a planar shear flow $\uu =
 \dot\gamma(y,0)$, where $\dot\gamma$ is the shear rate.  To be
@@
 vesicles is chosen so that the flow dives them towards one another in a
-head-on collision.  In the absence of adhesion, once the vesicles are
-sufficiently close, they are deflected to opposite sides of the $y$
-axis, pass one another, and then separate. This head-on collision
+head-on collision.  In the absence of adhesion,  
+two vesicles deform significantly as they collide head-on, 
+deflect to opposite sides of the $y$-axis as they pass one another, and then separate.
+This head-on collision
 process of two vesicles or capsules in a planar shear flow is found to
@@
 Figures~\ref{fig:doublet090-weakAdhesion}
-and~\ref{fig:doublet090-strongAdhesion} show snapshots of two vesicles
+and~\ref{fig:doublet090-strongAdhesion} show snapshots of 
+two vesicles
 that have formed a doublet and the color coding is the tension along the
@@
 the adhesive force is strongest.  The two values for the Hamaker
-constant are chosen since the period of the dynamics of the doublets are
-both $t^* \approx 42$.  For both the Hamaker constants, the vesicles in
+constant are chosen since the oscillation period of the vesicle doublet dynamics is
+both $t^* \approx 42$.  For both cases the vesicles in
 the doublet move in tandem with a tank-reading motion that is much
@@
 adhesion.  However, the dynamics of a single period for theses two
-Hamaker constants differ significantly.  For the weaker adhesive force,
+Hamaker constants differ significantly.  For $\mathcal{H} = 0.7$
 the individual vesicles undergo a sliding motion as they pass one
-another (Figure~\ref{fig:doublet090-weakAdhesion}).  However, at larger
-Hamaker constants, once the contact region is formed, the doublet
+another (Figure~\ref{fig:doublet090-weakAdhesion}).  However, for $\mathcal{H} = 2.1$, once the contact region is formed, the doublet
 maintains the same structure and undergoes a tumbling dynamic similar to
@@
 
-To further understand the formation of the doublet, we compute the
+To further understand the formation of the doublet, we compute the center-to-center
 distance between two vesicles with reduced area $\Delta A = 0.9$,
 separation distance $\delta = 0.5$, and shear rate $\dot\gamma = 0.5$.
-Figure~\ref{fig:sflow_distance}(a) shows this minimum distance as a
+Figure~\ref{fig:sflow_distance}(a) shows this distance as a
 function of time for varying Hamaker constants.  For Hamaker constants
@@
 the period of the doublet again decreases as the shear rate increases.
+\begin{figure}
+  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
+  \subfigimg[width=\linewidth]{(a)}{figs/shear_adR4em1Chi5em1_ra090.pdf} &
+  \subfigimg[width=\linewidth]{(b)}{figs/shear_adR4em1Chi5em1_ra090_period.pdf}
+  \end{tabular}
+  \caption{\label{fig:sflow_distance} (a) The distance between a pair of
+  vesicles in a planar shear flow with shear rate $\dot\gamma=0.5$, and
+  separation distance $\delta = 0.4$.  The different lines correspond to
+  a linear spacing of Hamaker constants ranging from $\mathcal{H}=0.1$
+  and $\mathcal{H}=1.0$.  (b) The time required for a doublet to
+  complete a single rotation.  The reduced area is $\Delta A = 0.90$ and
+  the separation distance is $\delta = 0.4$.  The different lines
+  correspond to different shear rates and separation distances.}
+\end{figure}
 
@@
 and effective aspect ratio are summarized in
-Table~\ref{tbl:aspectRatio}.  The effective aspect ratio of the doublet
-depends on both the Hamaker constant and the shear rate, and this
-indicates that the doublet's dynamics differ from those of a rigid body
-undergoing a Jeffery orbit.
-
+Table~\ref{tbl:aspectRatio}, which illustrates that 
+the effective aspect ratio of the doublet
+depends on both the Hamaker constant and the shear rate.
+%
 \begin{table}[htp]
@@
 \end{table}
+%
+Furthermore the oscillatory dynamics in Figure~\ref{fig:doublet090-weakAdhesion} and Figure~\ref{fig:doublet090-strongAdhesion} 
+illustrate that for similar oscillation periods, the actual aspect ratio of the vesicle doublet may be a dynamical variable as well.
+This
+indicates that the vesicle doublet's oscillatory dynamics in a shear flow is more complicated than the Jeffery orbit a rigid body.
 
@@
 
-\begin{figure}
-  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
-  \subfigimg[width=\linewidth]{(a)}{figs/shear_adR4em1Chi5em1_ra090.pdf} &
-  \subfigimg[width=\linewidth]{(b)}{figs/shear_adR4em1Chi5em1_ra090_period.pdf}
-  \end{tabular}
-  \caption{\label{fig:sflow_distance} (a) The distance between a pair of
-  vesicles in a planar shear flow with shear rate $\dot\gamma=0.5$, and
-  separation distance $\delta = 0.4$.  The different lines correspond to
-  a linear spacing of Hamaker constants ranging from $\mathcal{H}=0.1$
-  and $\mathcal{H}=1.0$.  (b) The time required for a doublet to
-  complete a single rotation.  The reduced area is $\Delta A = 0.90$ and
-  the separation distance is $\delta = 0.4$.  The different lines
-  correspond to different shear rates and separation distances.}
-\end{figure}
+%\begin{figure}
+%  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
+%  \subfigimg[width=\linewidth]{(a)}{figs/shear_adR4em1Chi5em1_ra090.pdf} &
+%  \subfigimg[width=\linewidth]{(b)}{figs/shear_adR4em1Chi5em1_ra090_period.pdf}
+%  \end{tabular}
+%  \caption{\label{fig:sflow_distance} (a) The distance between a pair of
+%  vesicles in a planar shear flow with shear rate $\dot\gamma=0.5$, and
+%  separation distance $\delta = 0.4$.  The different lines correspond to
+%  a linear spacing of Hamaker constants ranging from $\mathcal{H}=0.1$
+%  and $\mathcal{H}=1.0$.  (b) The time required for a doublet to
+%  complete a single rotation.  The reduced area is $\Delta A = 0.90$ and
+%  the separation distance is $\delta = 0.4$.  The different lines
+%  correspond to different shear rates and separation distances.}
+%\end{figure}
 
@@
 
+%
+%\begin{figure}[]
+%  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
+%  \subfigimg[width=\linewidth]{(a)}{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf} &
+%  \subfigimg[width=\linewidth]{(b)}{figs/doublet_decomp.pdf}
+%  \end{tabular}
+%%  \centering
+%%  \includegraphics[width=0.45\textwidth]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
+%%  \includegraphics[width=0.45\textwidth]{figs/doublet_decomp.pdf}
+%  \caption{\label{fig:shearIntrinsicViscosity} (a) The intrinsic
+%  viscosity of a tank-treading vesicle (blue) and a doublet (red).  The
+%  shear rate $\dot\gamma = 0.5$, the Hamaker constant $\mathcal{H}
+%  = 0.7$, and the separation distance $\delta = 0.4$.  The black
+%  marks denote intrinsic viscosity values computed by Ghigliotti {\em et
+%  al.}~\cite{GhigliottiBibenMisbah2010_JFM} (cf.~Figure 5).  (b) The
+%  decomposition of the intrinsic viscosity into the contributions for
+%  the bending and tension (black) of the vesicles, and the contribution
+%  from the vesicle adhesion (green).  Also included is the intrinsic
+%  viscosity of a single tank-treading vesicle (blue).}
+%\end{figure}
 Finally, we investigate the rheology of a suspension of a doublet by
@@
 the total area of both vesicles, and $\xxi$ is the traction as defined
-in equation~\eqref{eqn:traction}.  In
-Figure~\ref{fig:shearIntrinsicViscosity}(a), we compare the intrinsic
+in equation~\eqref{eqn:traction}.
+
+\begin{figure}[h]
+  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
+  \subfigimg[width=\linewidth]{(a)}{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf} &
+  \subfigimg[width=\linewidth]{(b)}{figs/doublet_decomp.pdf}
+  \end{tabular}
+%  \centering
+%  \includegraphics[width=0.45\textwidth]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
+%  \includegraphics[width=0.45\textwidth]{figs/doublet_decomp.pdf}
+  \caption{\label{fig:shearIntrinsicViscosity} (a) The intrinsic
+  viscosity of a tank-treading vesicle (blue) and a doublet (red).  The
+  shear rate $\dot\gamma = 0.5$, the Hamaker constant $\mathcal{H}
+  = 0.7$, and the separation distance $\delta = 0.4$.  The black
+  marks denote intrinsic viscosity values computed by Ghigliotti {\em et
+  al.}~\cite{GhigliottiBibenMisbah2010_JFM} (cf.~Figure 5).  (b) The
+  decomposition of the intrinsic viscosity into the contributions for
+  the bending and tension (black) of the vesicles, and the contribution
+  from the vesicle adhesion (green).  Also included is the intrinsic
+  viscosity of a single tank-treading vesicle (blue).}
+\end{figure}
+In Figure~\ref{fig:shearIntrinsicViscosity}(a), we compare the intrinsic
 viscosity of a single tank-treading vesicle to a doublet with Hamaker
@@
 rather than the bending and tension.
-
-\begin{figure}[]
-  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
-  \subfigimg[width=\linewidth]{(a)}{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf} &
-  \subfigimg[width=\linewidth]{(b)}{figs/doublet_decomp.pdf}
-  \end{tabular}
-%  \centering
-%  \includegraphics[width=0.45\textwidth]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
-%  \includegraphics[width=0.45\textwidth]{figs/doublet_decomp.pdf}
-  \caption{\label{fig:shearIntrinsicViscosity} (a) The intrinsic
-  viscosity of a tank-treading vesicle (blue) and a doublet (red).  The
-  shear rate $\dot\gamma = 0.5$, the Hamaker constant $\mathcal{H}
-  = 0.7$, and the separation distance $\delta = 0.4$.  The black
-  marks denote intrinsic viscosity values computed by Ghigliotti {\em et
-  al.}~\cite{GhigliottiBibenMisbah2010_JFM} (cf.~Figure 5).  (b) The
-  decomposition of the intrinsic viscosity into the contributions for
-  the bending and tension (black) of the vesicles, and the contribution
-  from the vesicle adhesion (green).  Also included is the intrinsic
-  viscosity of a single tank-treading vesicle (blue).}
-\end{figure}
 

### 2019-07-20 vesicle_code/docs/adhesion/revisions/reviewer2.tex
yny reviewer2

@@
 \begin{itemize}
-  \item The referee is correct that vesicles outside of the contact zone
-    do not feel a long range attractive interaction.  Our model follows
-    the works on red blood cells by Flormann {\em et al.}~Scientific
+  \item The referee is correct that the long-range attraction in the L.-J. is an artifact.
+   In this work we focus on the adhesion effects on the hydrodynamics 
+   of two vesicles drawn together by an external flow.
+   Thus the L.-J. type potential is to keep the equilibrium distance, 
+   following the works on red blood cells by Flormann {\em et al.}~Scientific
     Reports (2017) and Hoore {\em et al.}~Soft Matter (2018).  In both
@@
   There we find that a vesicle doublet is not likely to form unless the two vesicles are aligned
-  on the converging axis of the straining flow. In the fluid trap simulations we find that
+  on the converging axis of the extensional flow. In the fluid trap simulations we find that
     the reduced area has a large effect

### 2019-07-20 vesicle_code/docs/adhesion/revisions/reviewer1.tex
yny reviewer1 reviewer2

@@
 \begin{itemize}
-  \item We thank the referee for this point. We follow the modeling works on red blood cells (RBCs) by Flormann {\it et al.}, Sci. Rep. (2017) and Hoore {\it et al.} Soft Matt. (2018).
+  \item We thank the referee for this point. 
+   In this work we focus on the adhesion effects on the hydrodynamics 
+   of two vesicles drawn together by an external flow.
+   Thus the L.-J. type potential is to keep the equilibrium distance, 
+   following the modeling works on red blood cells (RBCs) by Flormann {\it et al.}, Sci. Rep. (2017) and Hoore {\it et al.} Soft Matt. (2018).
   In both papers the L-J potential is used to model the interaction between RBCs.

### 2019-07-20 vesicle_code/docs/adhesion/adhesion.tex
edits to adhesion.tex

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Adhesion Model}
-%
 \begin{figure}[htp]
@@
 \label{sec:qflow} 
-\todo[inline]{Bryan is here}
 We consider two identical vesicles suspended in a quiescent flow.
@@
 
+\todo[inline]{This first sentence is incomplete}
 When the force on each vesicle is a function of the separation distance
@@
 configuration of a vesicle pair}
-\label{subsec:qflow_adhesion_parameters} We again simulate two identical
-adhering vesicles with the adhesion force in equation~\eqref{eq:Fh}.
-The initial vesicle separation is smaller than in the previous
-simulations so that the equilibrium configuration is achieved in a
-shorter time horizon.  Once a vesicle doublet is formed, the membrane
-shape in the contact region depends on the adhesion strength relative to
-the membrane bending modulus.  For weak to moderate adhesion strength,
-vesicle membranes are flattened in the contact region while the rest of
-vesicle maintains a nearly spherical shape~\cite{EvansMetcalfe1984_BJ,
+\label{subsec:qflow_adhesion_parameters} 
+We again simulate two identical adhering vesicles with the adhesion
+force in equation~\eqref{eq:Fh}.  The initial vesicle separation is
+smaller than in the previous simulations so that the equilibrium
+configuration is achieved in a shorter time horizon.  Once a vesicle
+doublet is formed, the membrane shape in the contact region depends on
+the adhesion strength relative to the membrane bending modulus.  For
+weak to moderate adhesion strength, vesicle membranes are flattened in
+the contact region while the rest of vesicle maintains a nearly
+spherical shape~\cite{EvansMetcalfe1984_BJ,
 Book_PhysicalBasisCellAdhesion, Book_IntermolecularSurfaceForces,
@@
   areas of $\Delta A=0.95$, $0.75$, and $0.6$ are labeled.  The vesicle
-  length is fixed at $2\pi$, the dimensionless bending modulus
-  $\kappa_b=1$, the Hamaker constant $\mathcal{H}=5$, and the
-  separation distance $\delta=0.2$.  The color coding is the tension
+  length is fixed at $2\pi$, the dimensionless bending modulus is
+  $\kappa_b=1$, the Hamaker constant is $\mathcal{H}=5$, and the
+  separation distance is $\delta=0.2$.  The color coding is the tension
   along the vesicle.  The overall equilibrium shapes of two vesicles
@@
 to-scale) of the membranes in the contact region, where the membranes
-are not perfectly flat at all three values of reduced area: We observe
+are not perfectly flat at all three values of reduced area. We observe
 that the membranes are slightly curved with a dip at the edge.  Such
@@
 analyses on an elastic membrane under adhesion with a solid
-substrate~\cite{BlountMiksisDavis2013_PRSa, YoungStone2017_PRF}.  
-%
-Results from the lubrication analysis show that
-this dip and slightly curved shape in the contact region are independent
-of the adhesion strength. The high membrane curvature at the edge may
-pose a problem for using the contact angle there to estimate the
-adhesion strength. This inspires us to investigate the possibility of
-using a dynamic fluid trap to measure the adhesion strength (see
-Section~\ref{sec:eflow}).
-
-Also the dip at the edge of contact region is
-related to (but different from) the buckling of membrane under strong
-adhesion: A closer inspection on the dip at the edge shows that the
-membrane distance is smaller than the neutral separation distance
-$\delta$ there for more deflated vesicles.
-For $\Delta A =0.6$ and $0.75$  the adhesion force is mostly attractive
- in the contact region except at the edge, where the adhesive
-force turns repulsive.  For $\Delta A=0.95$, however, the adhesion force is mostly repulsive,
-leading to large tension in the rest of the vesicle membrane.
+substrate~\cite{BlountMiksisDavis2013_PRSa, YoungStone2017_PRF}. Results
+from the lubrication analysis show that this dip and slightly curved
+shape in the contact region are independent of the adhesion strength.
+The high membrane curvature at the edge may pose a problem for using the
+contact angle there to estimate the adhesion strength. This inspires us
+to investigate the possibility of using a dynamic fluid trap to measure
+the adhesion strength (see Section~\ref{sec:eflow}).
+
+Also the dip at the edge of the contact region is related to (but
+different from) the buckling of membrane under strong adhesion: A closer
+inspection on the dip at the edge shows that the membrane distance is
+smaller than the neutral separation distance $\delta$ there for more
+deflated vesicles.  For $\Delta A =0.6$ and $0.75$  the adhesion force
+is mostly attractive in the contact region except at the edge, where the
+adhesive force turns repulsive.  For $\Delta A=0.95$, however, the
+adhesion force is mostly repulsive, leading to large tension in the rest
+of the vesicle membrane.
 
@@
 %\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_EbEadh_vs_rA_adR0p2_adS502.jpeg}
-  \caption{\label{fig:Dec18_vesicle_equilibrium1}   (a) The total
-  bending energy (solid curve) and adhesion energy (dash-dotted curve)
-  plotted against the reduced area $\Delta A$. (b) The sum of two
-  energies plotted against reduced area $\Delta A$. The two vesicles in
-  the doublet are of the same length and reduced area.  The Hamaker
-  constant is $\mathcal{H} = 5$ and the separation distance is $\delta =
-  0.2$.}
+  \caption{\label{fig:Dec18_vesicle_equilibrium1} (a) The total bending
+  energy (solid curve) and adhesion energy (dash-dotted curve) plotted
+  against the reduced area $\Delta A$. (b) The sum of the two energies
+  plotted against reduced area $\Delta A$. The two vesicles in the
+  doublet are of the same length and reduced area.  The Hamaker constant
+  is $\mathcal{H} = 5$ and the separation distance is $\delta = 0.2$.}
 \end{figure}
@@
 total adhesion energy becomes more negative as the reduced area
-decreases.  The sum of two energies is plotted in
+decreases.  The sum of the two energies is plotted in
 Figure~\ref{fig:Dec18_vesicle_equilibrium1}(b), where a local minimum in
@@
     {figs/extensional_displacement1em1_adS6em1_tension_image05.png}
-  \caption{\label{fig:extensionalNonsymmetric}Dynamics of a vesicle pair
-  in a planar extensional flow. The Hamaker constant is ${\cal H} = 0.7$
-  for the first three rows, and ${\cal H}=0.6$ for the bottom row. From
-    top to bottom, the initial vertical displacement is $\Delta y=0$,
+  \caption{\label{fig:extensionalNonsymmetric} The dynamics of a vesicle
+  pair in a planar extensional flow. The Hamaker constant is ${\cal H} =
+  0.7$ for the first three rows, and ${\cal H}=0.6$ for the bottom row.
+  From top to bottom, the initial vertical displacement is $\Delta y=0$,
   $0.02$, $0.1$, and $0.1$. The reduced area is $\Delta A = 0.75$, the
-    extension rate $\dot\epsilon= 0.09$, and the adhesion distance
-    $\delta = 0.4$.  The color coding is the tension.}
+  extension rate $\dot\epsilon= 0.09$, and the adhesion distance $\delta
+  = 0.4$.  The color coding is the tension.}
   \end{figure}
@@
 revealed novel nonlinear vesicle dynamics not found for a viscous
-drop~\cite{KantslerSegreSteinberg2007_PRL,KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
-Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  Here we focus on
-a planar extensional flow  where the fluid velocity field
+drop~\cite{KantslerSegreSteinberg2007_PRL,
+KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM, Narsimhan2014_JFM,
+DahlNarsimhanGouveia2016_SoftMatt}.  Here we focus on a planar
+extensional flow  where the fluid velocity field
 $\uu=\dot\epsilon(-x,y)$ is centered at the origin ($(x,y)=(0,0)$), the
@@
 rate $\dot\epsilon$ the vesicle may undergo asymmetric
-deformation~\cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt},
-similar to a surfactant-laden viscous drop under a planar extensional
-flow~\cite{JanssenBoonAgterof1997_AIChE,HuPineLeal2000_PoF}.  To the
+deformation~\cite{KantslerSegreSteinberg2008_PRL, Narsimhan2014_JFM,
+DahlNarsimhanGouveia2016_SoftMatt}, similar to a surfactant-laden
+viscous drop under a planar extensional
+flow~\cite{JanssenBoonAgterof1997_AIChE, HuPineLeal2000_PoF}.  To the
 best of our knowledge, no studies on the interactions between two
@@
 tension with the color bar on the right of each row. We note that the
-negative tension in an extensional flow is consistent with the destabilizing tension 
-for a vesicle with finite bending forces~\cite{Narsimhan2014_JFM}.
-%and the speculation for a wrinkled membrane in the elongational flow~\cite{KantslerSegreSteinberg2007_PRL}.
+negative tension in an extensional flow is consistent with the
+destabilizing tension for a vesicle with finite bending
+forces~\cite{Narsimhan2014_JFM}.
+%and the speculation for a wrinkled membrane in the elongational
+%flow~\cite{KantslerSegreSteinberg2007_PRL}.
 
@@
 Figure~\ref{fig:extensionalNonsymmetric}.  For ${\cal H}=0.6$ (bottom
-row in Figure~\ref{fig:extensionalNonsymmetric})  the two vesicles are
+row in Figure~\ref{fig:extensionalNonsymmetric}), the two vesicles are
 separated by the diverging flow as early as $t=75$, and are clearly not
@@
 algorithm to place the stagnation point at a desirable location by
-adjusting the flow with a feedback
-loop~\cite{BentleyLeal1986_JFMa,Johnson-Chavarria2011_EMJ}, a particle
-can be trapped at the stagnation point for long time scales to
-facilitate image acquisition or other detailed measures such as particle
-image velocimetry of flow inside and around the particle.
+adjusting the flow with a feedback loop~\cite{BentleyLeal1986_JFMa,
+Johnson-Chavarria2011_EMJ}, a particle can be trapped at the stagnation
+point for long time scales to facilitate image acquisition or other
+detailed measures such as particle image velocimetry of flow inside and
+around the particle.
 
@@
   flow with an initial inclination angle $\theta=\pi$.  The reduced area
-  $\Delta A = 0.7$, the Hamaker constant $\mathcal{H} = 0.7$, the
-  separation distance $\delta = 0.4$, and the extension rate
+  is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} = 0.7$, the
+  separation distance is $\delta = 0.4$, and the extension rate is
   $\dot\epsilon = 0.02$ ({\em top}), $\dot\epsilon=0.07$ ({\em middle}),
@@
 stagnation point can be controlled in an experimental
-setting~\cite{BentleyLeal1986_JFMa,Johnson-Chavarria2011_EMJ}, we mimic
+setting~\cite{BentleyLeal1986_JFMa, Johnson-Chavarria2011_EMJ}, we mimic
 the active control of the microfluidic experiments by moving the center
@@
   flow with an initial inclination angle $\theta=\pi$.  The reduced area
-  $\Delta A = 0.8$, the Hamaker constant $\mathcal{H} = 0.7$, the
-  separation distance $\delta = 0.4$, and the extension rate
+  is $\Delta A = 0.8$, the Hamaker constant is $\mathcal{H} = 0.7$, the
+  separation distance is $\delta = 0.4$, and the extension rate is
   $\dot\epsilon = 0.1$.  The center of the vesicle, denoted with a black
@@
 configuration is reminiscent of the asymmetric deformation of a single
-vesicle in an extensional flow~\cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}.
-To gain more insight into such nonlinear dynamics, in the following we
-explore more physical characterization of the transition from
-$\theta=\pi$ to $\theta=\pi/2$ at different reduced area and extension
-rate.
+vesicle in an extensional flow~\cite{KantslerSegreSteinberg2008_PRL,
+Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  To gain more
+insight into such nonlinear dynamics, in the following we explore more
+physical characterization of the transition from $\theta=\pi$ to
+$\theta=\pi/2$ at different reduced area and extension rate.
 
@@
   proportional to the final inclination angle.  Squares indicate that
-  the doublet had not tilted to an equilibrium inclination angle in the
+  the doublet had not reached an equilibrium inclination angle in the
   given time horizon.}
@@
 vesicles is chosen so that the flow dives them towards one another in a
-head-on collision.  In the absence of adhesion,  
-two vesicles deform significantly as they collide head-on, 
-deflect to opposite sides of the $y$-axis as they pass one another, and then separate.
-This head-on collision
-process of two vesicles or capsules in a planar shear flow is found to
-be similar between
-two-~\cite{Breyiannis-Pozrikidis:2000,RahimianVeerapaneniBiros2010_JCP, RahimianVeerapaneniBiros2010_JCP} and
-three-dimensions~\cite{LacMorelBarthes-Biesel2007_JFM,LacBarthes-Biesel2008_PoF,
-OmoriIshikawaImaiYamaguchi2013_JBiomechics,
+head-on collision.  In the absence of adhesion,  two vesicles deform
+significantly as they collide head-on, deflect to opposite sides of the
+$y$-axis as they pass one another, and then separate.  This head-on
+collision process of two vesicles or capsules in a planar shear flow is
+found to be similar between two-~\cite{Breyiannis-Pozrikidis:2000,
+RahimianVeerapaneniBiros2010_JCP} and
+three-dimensions~\cite{LacMorelBarthes-Biesel2007_JFM,
+LacBarthes-Biesel2008_PoF, OmoriIshikawaImaiYamaguchi2013_JBiomechics,
 RahimianVeerapaneniZorinBiros2015_JCP}.  However, in the presence of
@@
 Figures~\ref{fig:doublet090-weakAdhesion}
-and~\ref{fig:doublet090-strongAdhesion} show snapshots of 
-two vesicles
+and~\ref{fig:doublet090-strongAdhesion} show snapshots of two vesicles
 that have formed a doublet and the color coding is the tension along the
-vesicle.  Each of the vesicles have reduced area $\Delta A = 0.9$, shear
+vesicles.  Each of the vesicles have reduced area $\Delta A = 0.9$, shear
 rate $\dot\gamma = 0.5$, separation distance $\delta = 0.4$, and Hamaker
@@
 the adhesive force is strongest.  The two values for the Hamaker
-constant are chosen since the oscillation period of the vesicle doublet dynamics is
-both $t^* \approx 42$.  For both cases the vesicles in
-the doublet move in tandem with a tank-reading motion that is much
-slower than the tank-treading motion that occurs in the absence of
-adhesion.  However, the dynamics of a single period for theses two
-Hamaker constants differ significantly.  For $\mathcal{H} = 0.7$
-the individual vesicles undergo a sliding motion as they pass one
-another (Figure~\ref{fig:doublet090-weakAdhesion}).  However, for $\mathcal{H} = 2.1$, once the contact region is formed, the doublet
-maintains the same structure and undergoes a tumbling dynamic similar to
-a Jeffery orbit.
+constant are chosen since the oscillation period of the vesicle doublet
+dynamics is both $t^* \approx 42$.  For both cases the vesicles in the
+doublet move in tandem with a tank-reading motion that is much slower
+than the tank-treading motion that occurs in the absence of adhesion.
+However, the dynamics of a single period for these two Hamaker constants
+differ significantly.  For $\mathcal{H} = 0.7$ the individual vesicles
+undergo a sliding motion as they pass one another
+(Figure~\ref{fig:doublet090-weakAdhesion}).  However, for $\mathcal{H} =
+2.1$, once the contact region is formed, the doublet maintains the same
+structure and undergoes a tumbling dynamic similar to a Jeffery orbit.
 
@@
   \caption{\label{fig:doublet090-weakAdhesion} The formation of a weakly
-  adhered doublet in a shear flow.  The reduced area $\Delta A =
-  0.9$, the Hamaker constant $\mathcal{H}=0.7$, the separation
-  distance $\delta = 0.4$, and the shear rate $\dot\gamma=0.5$.
+  adhered doublet in a shear flow.  The reduced area is $\Delta A =
+  0.9$, the Hamaker constant is $\mathcal{H}=0.7$, the separation
+  distance is $\delta = 0.4$, and the shear rate is $\dot\gamma=0.5$.
   The interaction between the two vesicles is a sliding motion, and the
@@
 
-To further understand the formation of the doublet, we compute the center-to-center
-distance between two vesicles with reduced area $\Delta A = 0.9$,
-separation distance $\delta = 0.5$, and shear rate $\dot\gamma = 0.5$.
-Figure~\ref{fig:sflow_distance}(a) shows this distance as a
+To further understand the formation of the doublet, we compute the
+minimum distance between two vesicles with reduced area $\Delta
+A = 0.9$, separation distance $\delta = 0.5$, and shear rate $\dot\gamma
+= 0.5$.  Figure~\ref{fig:sflow_distance}(a) shows this distance as a
 function of time for varying Hamaker constants.  For Hamaker constants
@@
 and effective aspect ratio are summarized in
-Table~\ref{tbl:aspectRatio}, which illustrates that 
-the effective aspect ratio of the doublet
-depends on both the Hamaker constant and the shear rate.
+Table~\ref{tbl:aspectRatio}, which illustrates that the effective aspect
+ratio of the doublet depends on both the Hamaker constant and the shear
+rate.
 %
@@
 aspect ratio of a vesicle doublet with reduced area $\Delta A = 0.9$,
-separation distance $\delta = 0.4$, and 
-Hamaker constants $\mathcal{H} = 1.5$ and $\mathcal{H} = 3.5$.  The
-effective aspect ratios depend on both the Hamaker constant and the
-shear rate, indicating that for the reported Hamaker constants, the
-dynamics of the doublet differ from that of a Jeffery orbit.}
+separation distance $\delta = 0.4$, and Hamaker constants $\mathcal{H} =
+1.5$ and $\mathcal{H} = 3.5$.  The effective aspect ratios depend on
+both the Hamaker constant and the shear rate, indicating that for the
+reported Hamaker constants, the dynamics of the doublet differ from that
+of a Jeffery orbit.}
 \end{table}
 %
-Furthermore the oscillatory dynamics in Figure~\ref{fig:doublet090-weakAdhesion} and Figure~\ref{fig:doublet090-strongAdhesion} 
-illustrate that for similar oscillation periods, the actual aspect ratio of the vesicle doublet may be a dynamical variable as well.
-This
-indicates that the vesicle doublet's oscillatory dynamics in a shear flow is more complicated than the Jeffery orbit a rigid body.
+Furthermore the oscillatory dynamics in
+Figure~\ref{fig:doublet090-weakAdhesion} and
+Figure~\ref{fig:doublet090-strongAdhesion} illustrate that for similar
+oscillation periods, the actual aspect ratio of the vesicle doublet may
+be a dynamical variable as well.  This indicates that the vesicle
+doublet's oscillatory dynamics in a shear flow is more complicated than
+the Jeffery orbit of a rigid body.
 
@@
   \end{tabular}
-  \caption{\label{fig:sflow_phase_diagram} Phase diagram of vesicle
+  \caption{\label{fig:sflow_phase_diagram} The phase diagram of vesicle
   hydrodynamics in a shear flow with $\delta = 0.1$ (a) and $\delta =
@@
   viscosity of a tank-treading vesicle (blue) and a doublet (red).  The
-  shear rate $\dot\gamma = 0.5$, the Hamaker constant $\mathcal{H}
-  = 0.7$, and the separation distance $\delta = 0.4$.  The black
+  shear rate is $\dot\gamma = 0.5$, the Hamaker constant is $\mathcal{H}
+  = 0.7$, and the separation distance is $\delta = 0.4$.  The black
   marks denote intrinsic viscosity values computed by Ghigliotti {\em et
@@
 \section{Conclusions\label{sec:conclusions}}
-\todo[inline]{conclusions need touched up}
 In this work we use a boundary integral formulation with adaptive
@@
 show that the membranes in the contact region are actually curved with
-end points at the shortest distance, consistent with results for moderate 
-adhesion strength in \cite{FlormannAouane2017_SciReports}.  
-Once a vesicle doublet forms, we
-examine the dependence of membrane bending and adhesion energies on the
-reduced area, the Hamaker constant, and the separation distance.
-
-Next we conduct numerical simulations of two vesicles in a planar extensional flow. 
-With initial configurations where two vesicles collide around the stagnation point 
-(one vesicle at the stagnation point and the other vesicle placed close to the converging axis),
-the two vesicles form a doublet and stay around the flow center only when two 
-vesicles collide head-on with no displacement $\triangle y=0$. 
-For $\triangle y >0$ we find that the vesicles rotate and move away from the stagnation point, and eventually
-move further from each other due to the strong diverging flow in the far-field.
-
-This inspires us to conduct a numerical experiment where a vesicle doublet is placed
-at the center of a fluid trap, which can be actively controlled in
-microfluidic channel so that fluid trap center is effectively the
-stagnation point of an extensional flow characterized by a extensional
-flow rate.  At low flow rate, we find the doublet to rotate nearly
-ninety degrees to align with the flow such that the long axis of the
-doublet is parallel to the divergent axis and the convergent stream is
-pushing the two vesicles together. As the flow rate increases, the
-vesicle doublet rotates less, and when the flow rate exceeds the
+end points at the shortest distance, consistent with results for
+moderate adhesion strength in~\cite{FlormannAouane2017_SciReports}.
+Once a vesicle doublet forms, we examine the dependence of membrane
+bending and adhesion energies on the reduced area, the Hamaker constant,
+and the separation distance.
+
+Next we conduct numerical simulations of two vesicles in a planar
+extensional flow.  With initial configurations where two vesicles
+collide around the stagnation point (one vesicle at the stagnation point
+and the other vesicle placed close to the converging axis), the two
+vesicles form a doublet and stay around the flow center only when two
+vesicles collide head-on with no displacement $\Delta y=0$.  For $\Delta
+y > 0$ we find that the vesicles rotate and move away from the
+stagnation point, and eventually move farther from each other due to the
+strong diverging flow in the far-field.
+
+This inspires us to conduct a numerical experiment where a vesicle
+doublet is placed at the center of a fluid trap, which can be actively
+controlled in microfluidic channel so that fluid trap center is
+effectively the stagnation point of an extensional flow characterized by
+a extensional flow rate.  At low flow rate, we find the doublet to
+rotate nearly ninety degrees to align with the flow such that the long
+axis of the doublet is parallel to the divergent axis and the convergent
+stream is pushing the two vesicles together. As the flow rate increases,
+the vesicle doublet rotates less, and when the flow rate exceeds the
 critical value, the diverging flow breaks the doublet structure by
@@
 simulations presented in this work are for identical vesicles (same
-reduced area, length, and bending modulus) in the doublet.
-Flormann {\em et al.}~demonstrated that asymmetric vesicle reduced area
-may lead to various equilibrium doublet shape such as male-female,
-asymmetric S-shape, and parachute shape.  It is also possible that
-viscosity contrast may also lead to different equilibrium doublet
-shapes.  Future work includes three dimensional simulations, dispersive
-vesicle properties (such as reduced area and bending modulus), viscosity
+reduced area, length, and bending modulus) in the doublet.  Flormann
+{\em et al.}~demonstrated that asymmetric vesicle reduced area may lead
+to various equilibrium doublet shape such as male-female, asymmetric
+S-shape, and parachute shape.  It is also possible that viscosity
+contrast may also lead to different equilibrium doublet shapes.  Future
+work includes three dimensional simulations, dispersive vesicle
+properties (such as reduced area and bending modulus), viscosity
 contrast, and effects of confinement on adhesive interactions.  Another
@@
 fluctuating hydrodynamics in the thin film between two vesicles enhance
-adhesion to keep vesicles bound under linear flows as speculated in cells \cite{FenzBihrSchmidt2017_NaturePhys}?  Recently Liu {\em
-et al.}~\cite{LiuChuNewbyRead2018_bioRxiv} used immersed boundary
+adhesion to keep vesicles bound under linear flows as speculated in
+cells~\cite{FenzBihrSchmidt2017_NaturePhys}?  Recently Liu {\em et
+al.}~\cite{LiuChuNewbyRead2018_bioRxiv} used immersed boundary
 simulations to show that, at a separation distance of tens of
-nanometers, the thin film between the two membranes facilitate the
+nanometers, the thin film between the two membranes facilitates the
 coupling between membranes via strong hydrodynamic interactions. In
@@
 contact. We are actively pursuing this direction with hydrodynamic
-modeling and simulations of adhesive membranes with thermal fluctuations.
+modeling and simulations of adhesive membranes with thermal
+fluctuations.
 
@@
 where the single-layer potential $\SS[\cdot]$ is defined by
-\begin{align}
+\begin{align*}
   \SS[\xxi](\xx) &= \frac{1}{4\pi\mu} \int_\gamma \left(
@@
     \xxi(\yy) ds_\yy, 
-  \label{eqn:SLP}
-\end{align}
-%
-and the membrane force $\xxi$ is a sum of the bending, tension and adhesion forces: 
+\end{align*}
+%
+and the membrane force $\xxi$ is a sum of the bending, tension and, adhesion forces: 
 \begin{align}
@@
 \end{align*}
-where $z$ is the distance between two points on a pair of vesicles.  Then, we define the total
-adhesive energy on $\gamma_1$ to be
+where $z$ is the distance between two points on a pair of vesicles.
+Then, we define the total adhesive energy on $\gamma_1$ to be
 \begin{align*}
   U_1 = \int_{\gamma_1} \int_{\gamma_2} \phi(\|\xx_1 - \xx_2\|) 
-    ds_{\xx_2} ds_{\xx_1}
+    ds_{\xx_2} ds_{\xx_1}.
 \end{align*}
-Perturbing $\xx_1$ to $\tilde{\xx}_1 = \xx_1 +  \delta \xx_1$, results
+Perturbing $\xx_1$ to $\tilde{\xx}_1 = \xx_1 +  \delta \xx_1$ results
 in a new vesicle $\tilde{\gamma}_1$, and the perturbed adhesive energy is
@@
   \end{align*}
-When $(m,n) = (4,2)$, the above express becomes
+When $(m,n) = (4,2)$, the above expression becomes
 \begin{align*}

### 2019-07-21 vesicle_code/docs/adhesion/revisions/reviewer1.tex
finished rebuttal for reviewer 1

--- 2019-07-18 vesicle_code/docs/adhesion/revisions/reviewer1.tex
@@
 \noindent
-We thank the referee for the comments.  Below are our point-to-point responses to 
-all the reviewer 1's comments.  We have made revisions based on these comments.
-We also note that a few typos from the original manuscript have
-been corrected.  A separate list of changes can be found along with this list of responses.
+We thank the referee for the comments.  Below are our point-to-point
+responses to all the reviewer 1's comments.  We have made revisions
+based on these comments.  We also note that a few typos from the
+original manuscript have been corrected.  A separate list of changes can
+be found along with this list of responses.
 
+\medskip
 \noindent 
@@
 \begin{itemize}
-  \item We thank the referee for this comment. The referee is absolutely correct by labeling boundary integral simulation as a standard approach.
-  However, the boundary integral algorithm we used for this work is not standard boundary integral algorithm for two reasons: (1) First the time marching is adaptive, allowing us to efficiently run the simulations for a long time with accuracy and convergence.
-(2) Second we adopted a slightly sophisticated near singular evaluation to ensure that our numerical results are convergent when two boundaries are close to each other.
-Without adaptive time marching, the boundary integral simulations of vesicles often give unreliable results as shown in
-Kabacaoglu {\it et al.}, J. Comp. Phys. (2018). In addition it is very time consuming to simulate two vesicles to equilibrate in close vicinity of each other in a quiescent flow. 
-Without a good near-singular evaluation in the boundary integral calculation, the simulations will be contaminated by the errors incurred when two moving deformable boundaries are close to each other.
+\item We thank the referee for this comment. The referee is absolutely
+  correct by labeling boundary integral simulation as a standard
+    approach. However, the boundary integral algorithm as applied to the
+    adhesion problem here is quite novel for two reasons: (1) First, we
+    applied a new adaptive time marching developed recently in Quaife
+    and Biros {\em Journal of Computational Physics}, {\bf
+    306}:478--499, 2016, allowing us to efficiently run long
+    time-horizon simulations. (2) Second, the close vesicle-vesicle
+    interactions in the doublet case is quite challenging to capture
+    accurately; here, we employed a novel near-singular integral
+    evaluation scheme which is an extension of the method developed in
+    Quaife and Biros {\em Journal of Computational Physics}, {\bf
+    274}:245--267, 2014. Without adaptive time marching, the boundary
+    integral simulations of vesicles often give unreliable results as
+    shown in Kabacao\u{g}lu {\em et al.}, {\em Journal of Computational
+    Physics}, {\bf 357}:43--77, 2018. In addition it is very time
+    consuming to simulate two vesicles to equilibrate in close vicinity
+    of each other in a quiescent flow.  Without a good near-singular
+    evaluation in the boundary integral calculation, the simulations
+    will be contaminated by the errors incurred when two moving
+    deformable boundaries are close to each other.
 
-  We thank the referee for pointing out that similar physical setup has been studied for red blood cells, capsules, drops and adhere particles. 
-  However it is not clear to us if our results for vesicles are so similar to those for red blood cell/drop/particles in the literature that no new understanding is contributed in this work.
+ We thank the referee for pointing out that similar physical setup has
+    been studied for red blood cells, capsules, drops, and adhering
+    particles. However, it is not clear to us if our results for
+    vesicles are so similar to those for red blood cells, drops, and
+    particles from the literature. For example, we are able to verify
+    the scaling of the draining time with respect to adhesion strength
+    and equilibrium separation distance by analyzing the numerical
+    simulation results.  A similar scaling is found in Ramachandran {\em
+    et al.}, Phys. Fluids (2010) where they assumed the vesicles are
+    spherical cap with a flat contact region.  It is not clear how their
+    scaling for the draining time can differentiate the contribution
+    from either adhesion strength or equilibrium separation distance,
+    while our scaling clearly illustrates how each component contributes
+    differently to the draining time. It is also not clear how such
+    scaling can be verified by comparing against experimental data.
 
-For example, we are able to verify the scaling of the draining time with respect to adhesion strength and equilibrium separation distance by analyzing the numerical simulation results. 
-A similar scaling is found in Ramachandran {\it et al.}, Phys.
-Fluids (2010) where they assumed the vesicles are spherical cap with a flat contact region.
-It is not clear how their scaling for the draining time can differentiate the contribution from either adhesion strength or equilibrium separation distance, while our scaling clearly illustrates how each component contributes differently to the draining time.
-It is also not clear how such scaling can be verified by comparing against experimental data.
+For the vesicles in a planar extensional flow, we cannot find any work
+    in the literature that shows how two red blood cells or capsules move
+    toward each other around the stagnation point. Furthermore we cannot
+    find any work in the literature that uses extensional flow to
+    measure the adhesion strength between two
+    interfaces/particles/membranes. All the work we can find on a drop
+    in an extensional flow/four-roll mill is for a single drop (clean
+    drop or a surfactant-laden drop) or a vesicle.
 
-For the vesicles in a planar extensional flow, we cannot find any work in the literature that shows how two red blood cells/capsules move toward each other around the stagnation point.
-Furthermore we cannot find any work in the literature that uses extensional flow to measure the adhesion strength between two interfaces/particles/membranes.
-All the work we can find on drop in an extensional flow/four-roll mill is for a single drop (clean drop or a surfactant-laden drop) or a vesicle.
+For the vesicles in a planar shear flow, there are numerical simulations
+    and experiments on how two drops/vesicles interact with each other.
+    However, to our best attempt, we did not find any work on the
+    effects of adhesion on drop-drop/vesicle-vesicle interactions in a
+    shear flow (possibly due to the numerical issues that we mentioned
+    earlier). Our simulation results show that (1) adhesion
+    significantly affects the vesicle-vesicle interaction in the shear
+    flow, and in the revision we provided means to quantify such
+    effects; and (2) adhesion also induces additional dissipation in a
+    dilute suspension of vesicle doublets. To the best of our knowledge,
+    these results are not available in the literature. Even though our
+    simulations are two-dimensional, previous works have demonstrated
+    that two-dimensional vesicle hydrodynamics bear some general
+    similarity to their three-dimensional counterparts.
 
-For the vesicles in a planar shear flow, there are numerical simulations and experiments on how two drops/vesicles interact with each other. 
-However, to our best attempt, we did not find any work on the effects of adhesions on drop-drop/vesicle-vesicle interactions in a shear flow (possibly due to the numerical issues that we mentioned earlier).
-Our simulation results show that (1) adhesion significantly affects the vesicle-vesicle interaction in the shear flow, and in the revision we provided means to quantify such effects, and (2) adhesion also induces additional dissipation in a dilute suspension of vesicle doublets.
-To our best knowledge these results are not available in the literature.
-Even though our simulations are two-dimensional, previous works have demonstrated that two-dimensional vesicle hydrodynamics bear some general similarity to their three-dimensional counterparts.
-
-{\bf Changes:} We made revisions with this comment in mind, to make sure that our results are highlighted and the readers can see clearly how these results are unique and maybe useful.
+{\bf Changes:} We made revisions with this comment in mind, to make sure
+that our results are highlighted and the readers can see clearly how
+these results are unique and maybe useful.
 
@@
 \noindent
-\item\comment{Second, the simulations are 2D, which makes it difficult to accept
-whether the predicted results would be observed in experiments. There
-was also no direct comparison with any experimental studies.}
+\item \comment{Second, the simulations are 2D, which makes it difficult
+  to accept whether the predicted results would be observed in
+  experiments. There was also no direct comparison with any experimental
+  studies.}
 \begin{itemize}
-  \item We thank the referee for this comment. The referee is absolutely correct: two-dimensional and three-dimensional hydrodynamics are in general very different. There are
-  cases where the two-dimensional and three-dimensional  vesicle hydrodynamics are in good agreement.
-For example, the two-dimensional simulations of packing of RBCs in Flormann {\it et al.}, Sci.
-Rep.
-(2017) are shown to be in good agreement with both experiments and three-dimensional simulations.
-In addition, the two-dimensional theoretical prediction of the buckling instability of the contact region between RBCs is validated by comparing with experiments in that paper.
-  Another example where two-dimensional vesicle hydrodynamics in shear flow is in general agreement with the three-dimensional vesicle hydrodynamics is illustrated in Ghigliotti {\it et al.}, J.
-Fluid Mech.
-(2010).
+  \item We thank the referee for this comment. The referee is absolutely
+    correct: two-dimensional and three-dimensional hydrodynamics are in
+    general very different. There are cases where the two-dimensional
+    and three-dimensional vesicle hydrodynamics are in good agreement.
+    For example, the two-dimensional simulations of packing of RBCs in
+    Flormann {\em et al.}, Sci.~Rep.~(2017) are shown to be in good
+    agreement with both experiments and three-dimensional simulations.
+    In addition, the two-dimensional theoretical prediction of the
+    buckling instability of the contact region between RBCs is validated
+    by comparing with experiments in that paper.  Another example where
+    two-dimensional vesicle hydrodynamics in shear flow is in general
+    agreement with the three-dimensional vesicle hydrodynamics is
+    illustrated in Ghigliotti {\em et al.}, J.~Fluid Mech.~(2010).
 
-  The current work is the first step we took to investigate the effects of adhesion on vesicle hydrodynamics.
-We are working on the three-dimensional version  and with the two-dimensional results as a guidance we will be able to elucidate more physical insight when we analyze the results from three-dimensional simulations in the near future.
+  The current work is the first step we took to investigate the effects
+    of adhesion on vesicle hydrodynamics. We are working on the
+    three-dimensional version and with the two-dimensional results as a
+    guidance we will be able to elucidate more physical insight when we
+    analyze the results from three-dimensional simulations in the near
+    future.
 
   \noindent
-  {\bf Changes:} We have added some comparison with three-dimensional (both numerical and experimental) results of two RBCs in shear flow in the revision.
+  {\bf Changes:} We have added some comparison with three-dimensional
+    (both numerical and experimental) results of two RBCs in shear flow
+    in the revision.
 \end{itemize}
@@
 receptor/ligand). Is the L-J type adhesive field appropriate for such
-interactions? ALso, in reality, these bonds are stochastic in nature.}
+interactions? Also, in reality, these bonds are stochastic in nature.}
 \begin{itemize}
-  \item We thank the referee for this point. We follow the modeling works on red blood cells (RBCs) by Flormann {\it et al.}, Sci. Rep. (2017) and Hoore {\it et al.} Soft Matt. (2018).
-  In both papers the L-J potential is used to model the interaction between RBCs.
-The focus of this work is to show the hydrodynamic implication of such interaction between two vesicles without any coating of adhesive protein macromolecules.
-Results from these modeling works using L-J potential are found to be in good agreement with experiments and previous modeling results using different adhesion potential (Ziherl and Svetina, PNAS (2007)).
+  \item We thank the referee for this point.  In this work we focus on
+    the adhesion effects on the hydrodynamics of two vesicles drawn
+    together by an external flow.  Thus the L.-J.~type potential is to
+    keep the equilibrium distance, following the modeling works on red
+    blood cells (RBCs) by Flormann {\em et al.}, Sci.~Rep.~(2017) and
+    Hoore {\em et al.} Soft Matt.!(2018).  In both papers the
+    L.-J.~potential is used to model the interaction between RBCs. The
+    focus of this work is to show the hydrodynamic implication of such
+    interaction between two vesicles without any coating of adhesive
+    protein macromolecules. Results from these modeling works using a
+    L.-J.~potential are found to be in good agreement with experiments
+    and previous modeling results using different adhesion potential
+    (Ziherl and Svetina, PNAS (2007)).
 
-  The referee is correct that the biological adhesion requires physical contact and is stochastic in nature.
-We are modeling such stochastic binding for adhesion between two membranes in a viscous solvent.
+    The referee is correct that the biological adhesion requires
+    physical contact and is stochastic in nature. We are modeling such
+    stochastic binding for adhesion between two membranes in a viscous
+    solvent.
 
   \noindent
-  {\bf Changes:} We have added more references and a better description on the usage of L-J potential for vesicle adhesion to explain its validity and applicability.
+  {\bf Changes:} We have added more references and a better description
+    on the usage of L.-J.~potential for vesicle adhesion to explain its
+    validity and applicability.
 
@@
 \noindent
-\item\comment{The authors talks about the "fluid trap". This is indeed a tricky
-issue in any experiment dealing with extensional flow as how to
-maintain the drop/vesicle at the stagnation point. But in a numerical
-simulation this should not be any issue at all., because even of the
-vesicle moves away from the stagnation point its dynamics is still
-governed by the velocity gradient which is same everywhere in the flow
-field.}
+\item\comment{The authors talks about the ''fluid trap". This is indeed
+  a tricky issue in any experiment dealing with extensional flow as how
+  to maintain the drop/vesicle at the stagnation point. But in a
+  numerical simulation this should not be any issue at all., because
+  even of the vesicle moves away from the stagnation point its dynamics
+  is still governed by the velocity gradient which is same everywhere in
+  the flow field.}
 \begin{itemize}
-  \item We thank the referee for this comment. The ``fluid trap", in its earliest form, was first achieved in an experiment by Bentley and Leal in 1986: A computer-controlled four-roll mill for
-  investigations  of particle and drop dynamics in two-dimensional linear shear flows, Journal of Fluid Mechanics, vol.
-167, pp.
-219-240 (1986).
-Bentley and Leal showed that their computer-aided feedback control in the four-roll mill can keep the particle/drop at the center of the four-roll mill for a very long time.
-  Over the years the techniques of using the four-roll mill as a fluid trap have been improved and extended to microfluidics (see Hudson {\it et al.}, Applied Phys.
-Lett.
-(2004) and Lee {\it et al.}, Applied Phys.
-Lett.
-(2007) for example.)
-  In the original manuscript we simulate the fluid trap based on the setups by both the Schroeder's group at UIUC and S.
-Muller's group that can efficiently control the location of the stagnation point.
+  \item We thank the referee for this comment. The ``fluid trap", in its
+    earliest form, was first achieved in an experiment by Bentley and
+    Leal in 1986: A computer-controlled four-roll mill for
+    investigations of particle and drop dynamics in two-dimensional
+    linear shear flows, {\em Journal of Fluid Mechanics} {\bf
+    167}:219-240, 1986.  Bentley and Leal showed that their
+    computer-aided feedback control in the four-roll mill can keep the
+    particle/drop at the center of the four-roll mill for a very long
+    time.  Over the years the techniques of using the four-roll mill as
+    a fluid trap have been improved and extended to microfluidics (see
+    Hudson {\em et al.}, Applied Phys.~Lett.~(2004) and Lee {\em et
+    al.}, Applied Phys.~Lett.~(2007), for example.) In the original
+    manuscript we simulate the fluid trap based on the setups by both
+    the Schroeder's group at UIUC and S. Muller's group that can
+    efficiently control the location of the stagnation point.
 
-  Our motivation is to present these simulation results so the experimentalist may be interested to use the fluid trap as a non-invasive tool to measure the adhesion strength between vesicles.
-We hope that there will be experimental data for us to compare our simulations results in the near future.
+    Our motivation is to present these simulation results so the
+    experimentalist may be interested to use the fluid trap as a
+    non-invasive tool to measure the adhesion strength between vesicles.
+    We hope that there will be experimental data for us to compare our
+    simulations results in the near future.
 
    \noindent
-  {\bf Changes:} We have added these references on fluid trap in the revised manuscript. In addition we have rewritten a couple of relevant paragraphs to convey our motivation.
+  {\bf Changes:} We have added these references on fluid trap in the
+    revised manuscript. In addition we have rewritten a couple of
+    relevant paragraphs to convey our motivation.
  \end{itemize}
@@
 \noindent
-\item\comment{There was not enough physical insights on the vesicle alignment
-in extensional flow as presented in section IV. If the vesicles are
-placed centrally, what causes the pair to become asymmetric in the first
-place, since all components in the model are deterministic? The authors
-used vorticity contours, but the external flow is irrotational; so what
-is the origin of vorticity, and is it appropriate to use vorticity to
-explain the behavior?}
+\item\comment{There was not enough physical insights on the vesicle
+  alignment in extensional flow as presented in section IV. If the
+  vesicles are placed centrally, what causes the pair to become
+  asymmetric in the first place, since all components in the model are
+  deterministic? The authors used vorticity contours, but the external
+  flow is irrotational; so what is the origin of vorticity, and is it
+  appropriate to use vorticity to explain the behavior?}
 \begin{itemize}
   \item We have reorganized section IV based on the referee's feedback.
-To investigate the vesicle hydrodynamics in a planar extensional flow we conducted new simulations where a left vesicle is placed at the stagnation point and the right vesicle is moving towards it.
-Depending on the initial elevation of the right vesicle off the $x$-axis, the vesicle hydrodynamics is different and we find configurations that are similar to those that we observe in the fluid trap.
-The simulation data show that the membrane tension is highly non-uniform, and we speculate that the Marangoni stress contributes to asymmetric configuration of vesicles around the stagnation point, as for a single surfactant-laden drop in an extensional flow.
+    To investigate the vesicle hydrodynamics in a planar extensional
+    flow, we conducted new simulations where a left vesicle is placed at
+    the stagnation point and the right vesicle is moving towards it.
+    Depending on the initial elevation of the right vesicle off the
+    $x$-axis, the vesicle hydrodynamics is different and we find
+    configurations that are similar to those that we observe in the
+    fluid trap. The simulation data shows that the membrane tension is
+    highly non-uniform, and we speculate that the Marangoni stress
+    contributes to asymmetric configuration of vesicles around the
+    stagnation point, as for a single surfactant-laden drop in an
+    extensional flow.
 
-  \noindent
-  {\bf Changes:} We have removed the part on visualizing flow around vesicles in the fluid trap.
-Instead we added simulations at the beginning of new Section IV to examine the vesicle hydrodynamics in a planar extensional flow.
+  \noindent {\bf Changes:} We have removed the part on visualizing flow
+    around vesicles in the fluid trap. Instead we added simulations at
+    the beginning of new Section IV to examine the vesicle hydrodynamics
+    in a planar extensional flow.
 \end{itemize}
@@
 \noindent
-\item\comment{I did not find figure 14 relevant for the present article. This
-result is not relevant, and also presented just to show what the authors
-intend to do in future.}
+\item\comment{I did not find figure 14 relevant for the present article.
+  This result is not relevant, and also presented just to show what the
+  authors intend to do in future.}
 \begin{itemize}
-  \item We agree with the referee and  have removed this example from the manuscript.  Instead, we
-    mention that future work includes a suspension of many vesicles.
+  \item We agree with the referee and  have removed this example from
+    the manuscript.
 
     \noindent
-    {\bf Changes:} We removed this example from the conclusion and instead we expand future work to include a suspension of many vesicles.
+    {\bf Changes:} We removed this example from the conclusion and
+    instead we expand future work to include a suspension of many
+    vesicles.
 \end{itemize}

### 2019-07-21 vesicle_code/docs/adhesion/revisions/reviewer2.tex
finished reviewer 2 reubuttal

@@
 \noindent
-We thank the referee for the comments.  Below are our point-to-point responses to 
-all the comments from the reviewer.  We have made revisions based on these comments.
-We also note that a few typos from the original manuscript have
-been corrected.  A separate list of changes can be found along with this list of responses.
-\\ \\ \noindent 
+We thank the referee for the comments.  Below are our point-to-point
+responses to all the comments from the reviewer.  We have made revisions
+based on these comments.  We also note that a few typos from the
+original manuscript have been corrected.  A separate list of changes can
+be found along with this list of responses.
+
+\medskip
+\noindent 
 Sincerely, \\ \noindent
@@
 membranes was not only predicted theroretically and numerically in
-Flormann et al. [32] but also experimentally. In addition, a more
-recent paper by Hoore et al. (Soft Matter 14, 6278-6289 (2018)) showed
+Flormann et al.~[32] but also experimentally. In addition, a more
+recent paper by Hoore et al.~(Soft Matter 14, 6278-6289 (2018)) showed
 the influence of the membrane shear elasticity on doublet shapes by 3D
@@
 
-\item\comment{Concerning the stability and dynamics of clusters of vesicles with
-adhesive interaction, there have been at least two papers on clusters
-in micro-channel flow (computational and experimental) that should be
-cited: Brust et al., Scientific Reports 4, 4348 (2014) and Claveria et
-al., Soft Matter. 2016 vol 12(39):8235-8245. About rheology, at least
-the historical paper by Chien on the shear-thinning of blood related
-to RBC aggregation should be cited : Chien, S., Usami, S., Dellenback,
-R.~J., Gregersen, M.~I., Nanninga, L.~B.~\& Guest, M.~M. Blood
-viscosity: Influence of erythrocyte aggregation. Science 157, 829–831
-(1967).}
+\item\comment{Concerning the stability and dynamics of clusters of
+  vesicles with adhesive interaction, there have been at least two
+    papers on clusters in micro-channel flow (computational and
+    experimental) that should be cited: Brust et al., Scientific Reports
+    4, 4348 (2014) and Claveria et al., Soft Matter. 2016 vol
+    12(39):8235-8245. About rheology, at least the historical paper by
+    Chien on the shear-thinning of blood related to RBC aggregation
+    should be cited : Chien, S., Usami, S., Dellenback, R.~J.,
+    Gregersen, M.~I., Nanninga, L.~B.~\& Guest, M.~M. Blood viscosity:
+    Influence of erythrocyte aggregation. Science 157, 829–831 (1967).}
 \begin{itemize}
@@
 \begin{itemize}
-  \item The referee is correct that the long-range attraction in the L.-J. is an artifact.
-   In this work we focus on the adhesion effects on the hydrodynamics 
-   of two vesicles drawn together by an external flow.
-   Thus the L.-J. type potential is to keep the equilibrium distance, 
-   following the works on red blood cells by Flormann {\em et al.}~Scientific
-    Reports (2017) and Hoore {\em et al.}~Soft Matter (2018).  In both
-    these papers, the Lennard-Jones potential is used to model the
-    adhesive interaction between red blood cells.  
-    Results from these modeling works are found to be in good agreement 
-    with experiments and other models for adhesion (Ziherl and Svetina, PNAS (2017)).
+  \item The referee is correct that the long-range attraction in the
+    L.-J.~is an artifact.  In this work we focus on the adhesion effects
+    on the hydrodynamics of two vesicles drawn together by an external
+    flow.  Thus the L.-J.~type potential is to keep the equilibrium
+    distance, following the works on red blood cells by Flormann {\em et
+    al.}~Scientific Reports (2017) and Hoore {\em et al.}~Soft Matter
+    (2018).  In both these papers, the L.-J.~potential is used to model
+    the adhesive interaction between red blood cells.  Results from
+    these modeling works are found to be in good agreement with
+    experiments and other models for adhesion (Ziherl and Svetina, PNAS
+    (2017)).
 
@@
 
-\item\comment{I cannot figure out why the external part of vesicles on profile 1
-in fig 3-left is yellow. Shouldn't the force be weakly attractive in
-that region, as in fig 1-right?}
+\item\comment{I cannot figure out why the external part of vesicles on
+  profile 1 in fig 3-left is yellow. Shouldn't the force be weakly
+  attractive in that region, as in fig 1-right?}
 \begin{itemize}
@@
     the right that shows a zoomed in view of the contact zone, the
-    adhesion force is plotted using the same method as in Figure 1.  In
+    adhesive force is plotted using the same method as in Figure 1.  In
     this case, the color is yellow only if the vesicle is sufficiently
@@
 
-\item\comment{Figs 4-5 and related text: it would have been interesting to
-compare results with the bending energy of vesicles without adhesion
-potential in their equilibrium shape, to show the energy gain due to
-adhesion (bending and total energy). This could be a way to compare
-the total energy of the doublet to the energy of dissociated vesicles
-and infer about the stability of doublets.}
+\item\comment{Figs 4-5 and related text: it would have been interesting
+  to compare results with the bending energy of vesicles without
+  adhesion potential in their equilibrium shape, to show the energy gain
+  due to adhesion (bending and total energy). This could be a way to
+  compare the total energy of the doublet to the energy of dissociated
+  vesicles and infer about the stability of doublets.}
 \begin{itemize}
-  \item We thank the referee for this suggestion. We did follow the referee's suggestion to check out this comparison. As pointed out by the referee in the seventh comment,
-  the long-range attraction of the L-J potential that is used for membrane-membrane adhesion is not realistic and consequently the doublet always has lower total energy than
-  dissociated vesicles. We are working on a more realistic adhesion potential for RBCs and we believe that this comparison will reveal more information there.
+  \item We thank the referee for this suggestion. We did follow the
+    referee's suggestion to check out this comparison. As pointed out by
+    the referee in the seventh comment, the long-range attraction of the
+    L.-J.~potential that is used for membrane-membrane adhesion is not
+    realistic and consequently the doublet always has lower total energy
+    than dissociated vesicles. We are working on a more realistic
+    adhesion potential for RBCs and we believe that this comparison will
+    reveal more information.
 \end{itemize}
 
-\item\comment{Fig 9(right): I regret that the authors did not extend the study
-to lower values of the reduced area, to reach values comparable to red
-blood cells which are more deflated that $\Delta A=0.7$. Also, the range
-of shear rates could have been slightly increased to reach the
-stability limit of the most deflated vesicles. Here, we do not know
-what happens below reduced areas of 0.8.}
+\item\comment{Fig 9(right): I regret that the authors did not extend the
+  study to lower values of the reduced area, to reach values comparable
+  to red blood cells which are more deflated that $\Delta A=0.7$. Also,
+  the range of shear rates could have been slightly increased to reach
+  the stability limit of the most deflated vesicles. Here, we do not
+  know what happens below reduced areas of 0.8.}
 \begin{itemize}
@@
 
-\item\comment{ Figs 9(right) and 12(right): the stability diagrams are presented
-in different parameter spaces for the extensional and shear flow
-cases. It would have been interesting to see e.g. the diagram in the
-interaction energy vs. flow strength $\chi$ for both cases, for
+\item\comment{Figs 9(right) and 12(right): the stability diagrams are
+  presented in different parameter spaces for the extensional and shear
+  flow cases. It would have been interesting to see e.g. the diagram in
+  the interaction energy vs.~flow strength $\chi$ for both cases, for
   comparison.}
 \begin{itemize}
-  \item In the revision for the extensional example we first focus on how an initial vertical displacement 
-  may affect the vesicle dynamics in a planar extensional flow (beginning of the new Section III). 
-  There we find that a vesicle doublet is not likely to form unless the two vesicles are aligned
-  on the converging axis of the extensional flow. In the fluid trap simulations we find that
-    the reduced area has a large effect
-    on determining if the doublet is broken or not, and on the
-    inclination angle if the doublet is not broken.  Therefore, we have
-    elected to investigate the effect of the reduced area for this
-    example.
+  \item In the revision for the extensional example we first focus on
+    how an initial vertical displacement may affect the vesicle dynamics
+    in a planar extensional flow (beginning of the new Section III).
+    There we find that a vesicle doublet is not likely to form unless
+    the two vesicles are aligned on the converging axis of the
+    extensional flow. In the fluid trap simulations we find that the
+    reduced area has a large effect on determining if the doublet is
+    broken or not, and on the inclination angle if the doublet is not
+    broken.  Therefore, we have elected to investigate the effect of the
+    reduced area for this example.
 
-  \item For the shear flow simulations, we place the two vesicles on the same horizontal axis at $t=0$ (initial displacement is zero).
-  Such head-on collision has been well studied for drops (clean or surfactant-laden), capsules, vesicles and red blood cells (without the L-J potential between membranes),
-  and will serve as a good reference point to draw comparison with our results. For head-on collision between two vesicles,
-  we find that  a smaller reduced area will increase the
-    size of the contact area, and this will affect the critical
-    Hamaker constant required to form a doublet. Thus we expect that the critical Hamaker constant for vesicle doublet formation reported will depend on the
-    reduced area, vertical displacement and the shear rate. 
-    To avoid
-    diverting the focus of the paper, we have elected to divert an
-    investigation of this behavior to future work.
+  \item For the shear flow simulations, we place the two vesicles on the
+    same horizontal axis at $t=0$ (initial displacement is zero).  Such
+    head-on collisions have been well-studied for drops (clean or
+    surfactant-laden), capsules, vesicles, and red blood cells (without
+    the L.-J.~potential between membranes), and will serve as a good
+    reference point to draw comparison with our results. For head-on
+    collisions between two vesicles, we find that  a smaller reduced
+    area will increase the size of the contact area, and this will
+    affect the critical Hamaker constant required to form a doublet.
+    Thus we expect that the critical Hamaker constant for vesicle
+    doublet formation reported will depend on the reduced area, vertical
+    displacement and the shear rate.  To avoid diverting the focus of
+    the paper, we have elected to divert an investigation of this
+    behavior to future work.
 \end{itemize}
 
-\item\comment{Fig.~10: the black arrows, as I understand, represent the total
-attractive force due to the interaction potential. Would the authors
-be able to represent also the total hydrodynamic forces on vesicles
-which presumably balance the torque of interaction forces? Is there a
-tank-treading motion of membranes?}
+\item\comment{Fig.~10: the black arrows, as I understand, represent the
+  total attractive force due to the interaction potential. Would the
+  authors be able to represent also the total hydrodynamic forces on
+  vesicles which presumably balance the torque of interaction forces? Is
+  there a tank-treading motion of membranes?}
 \begin{itemize}
@@
 
-  \item There is a transient tank-treading motion that eventually (asymptotically) stops towards equilibrium. 
-  Since we removed Figure 10 from the original version, we have chosen to
-    not focus on the transient trank-treading motion and the vorticity and torque of the vesicles.
+  \item There is a transient tank-treading motion that eventually
+    (asymptotically) stops towards equilibrium.  Since we removed Figure
+    10 from the original version, we have chosen to not focus on the
+    transient tank-treading motion and the vorticity and torque of the
+    vesicles.
 \end{itemize}
@@
 \item\comment{Fig 12: the authors did not comment the evolution of the
-frequency of distance oscillations in doublets when the Hamaker constant
-is varied. Can it be compared to the natural rotation frequency of the
-shear flow $\chi/2$? Does a strongly adhesive doublet tend to behave as
-a tumbling rigid object following something similar to Jeffery orbits?}
+  frequency of distance oscillations in doublets when the Hamaker
+  constant is varied. Can it be compared to the natural rotation
+  frequency of the shear flow $\chi/2$? Does a strongly adhesive doublet
+  tend to behave as a tumbling rigid object following something similar
+  to Jeffery orbits?}
 \begin{itemize}
   \item We now report the period of the doublets at three different
-    shear rates and at a variety of Hamaker constants.
+    shear rates and at a variety of Hamaker constants and separation
+    distances.
 
@@
     period in the same shear flow.  The results indicate that the
-    effective aspect ratio is independent of the shear rate, and this
-    suggests that the dynamics of the doublet has similar properties to
-    a rigid body undergoing a Jeffery orbit. 
+    effective aspect ratio depends on the shear rate, and this suggests
+    that the dynamics of the doublet in a shear flow is more complicated
+    than Jeffery orbits.
 \end{itemize}
 
-\item\comment{Fig 12-right: is the stability limit between the red and blue
-zones linear? This would mean that a stability criterion could take
-the form of a dimensionless number involving the ratio of Hamaker
+\item\comment{Fig 12-right: is the stability limit between the red and
+  blue zones linear? This would mean that a stability criterion could
+  take the form of a dimensionless number involving the ratio of Hamaker
   constant/shear rate, a potentially interesting result.}
@@
     is a linear relationship.
+
   \item We have superimposed a straight line to show the transition
     between the two doublet and unbounded configurations.
+
   \item We also have repeated the phase diagram, but with a smaller
@@
 
-\item\comment{Fig 13 and comments about rheology: I am not sure to understand
-the meaning of the left figure where it is shown that the intrinsic
-viscosity of the doublet in suspension is about twice the viscosity of a
-single vesicle. By definition, the intrinsic viscosity does not depend
-on volume fraction, so I do not expect such a big difference between
-bound vesicles and isolated vesicles. With the values chosen for the
-Hamaker constant and the shear rate, it seems (from fig 12-left) that
-the interaction is quite strong and that the distance between the two
-vesicles in the doublet is always very short (close to the equilibrium
-distance $\delta$). So the doublet must be roughly tumbling as a single
-object and unless a co-rotating tank-treading motion of the two
-membranes produces a strong dissipation by shear flow in the gap between
-the two vesicles, the difference should not be so large. It is also
-quite curious that the intrinsic viscosity of the doublet is so close to
-exactly twice the viscosity of a single vesicle. Could the authors check
-and elaborate on this ? Was the volume fraction properly scaled out
-here? Also in the right panel, the bending/tension part is compared to
-twice the intrinsic viscosity of a suspension of isolated vesicles. Why
-twice ? Finally, it is not clear how technically the bending/tension and
+\item\comment{Fig 13 and comments about rheology: I am not sure to
+  understand the meaning of the left figure where it is shown that the
+  intrinsic viscosity of the doublet in suspension is about twice the
+  viscosity of a single vesicle. By definition, the intrinsic viscosity
+  does not depend on volume fraction, so I do not expect such a big
+  difference between bound vesicles and isolated vesicles. With the
+  values chosen for the Hamaker constant and the shear rate, it seems
+  (from fig 12-left) that the interaction is quite strong and that the
+  distance between the two vesicles in the doublet is always very short
+  (close to the equilibrium distance $\delta$). So the doublet must be
+  roughly tumbling as a single object and unless a co-rotating
+  tank-treading motion of the two membranes produces a strong
+  dissipation by shear flow in the gap between the two vesicles, the
+  difference should not be so large. It is also quite curious that the
+  intrinsic viscosity of the doublet is so close to exactly twice the
+  viscosity of a single vesicle. Could the authors check and elaborate
+  on this? Was the volume fraction properly scaled out here? Also in the
+  right panel, the bending/tension part is compared to twice the
+  intrinsic viscosity of a suspension of isolated vesicles. Why twice?
+  Finally, it is not clear how technically the bending/tension and
   adhesion parts are separated.  Overall I think the study on rheology
@@
 
-\item\comment{In the conclusions, an example of aggregation of vesicles enclosed
-in a bigger one is presented. I do not think this brings much to this
-paper. Why not keep this for a future paper dedicated to this specific
-problem and instead show examples of aggregates without the enclosing
-large vesicle? In what conditions (reduced volume, Hamaker constant)
-can linear structures (rouleaux) be formed for instance (see the paper
-by Hoore et al whose reference is given above for instance).}
+\item\comment{In the conclusions, an example of aggregation of vesicles
+  enclosed in a bigger one is presented. I do not think this brings much
+  to this paper. Why not keep this for a future paper dedicated to this
+  specific problem and instead show examples of aggregates without the
+  enclosing large vesicle? In what conditions (reduced volume, Hamaker
+  constant) can linear structures (rouleaux) be formed for instance (see
+  the paper by Hoore et al whose reference is given above for
+  instance).}
 \begin{itemize}
-  \item We have removed this example from the manuscript.  We thank the referee for the great suggestion to examine the conditions for formation of
-  linear structures. We have added a few new results in the revision and consequently we
-    mention that future work includes a suspension of many vesicles.
+  \item We have removed this example from the manuscript.  We thank the
+    referee for the great suggestion to examine the conditions for
+    formation of linear structures. We have added a few new results in
+    the revision and consequently we mention that future work includes a
+    suspension of many vesicles.
 \end{itemize}

### 2019-07-21 vesicle_code/docs/adhesion/revisions/summary_of_changes.tex
edited summary of changes document

@@
 Below is a list of changes in the revision.
-\\ \\ \noindent 
+
+\medskip \noindent 
 Sincerely, \\ \noindent
@@
 
-\item We modified the introduction with better clarity and more complete citation of references.
+\item We modified the introduction with better clarity and more complete
+  citations of references.
 
-\item We modified all the figure captions to make sure that all the figures are self-contained.
+\item We modified all the figure captions to make sure that all the
+  figures are self-contained.
 
-\item In Section IV: Adhesion of two vesicles in a planar extensional
+\item In Section IV: For adhesion of two vesicles in a planar extensional
   flow, we conducted new simulations to elucidate the interaction
@@
 
-\item In Section IV: Adhesion of two vesicles in a planar extensional flow, we added a set of simulations with reduced area $\triangle A=0.65$ and these results are summarized in the new Figure 10(b) and 10(c).
+\item In Section IV: For adhesion of two vesicles in a planar extensional
+  flow, we added a set of simulations with reduced area $\Delta A=0.65$
+    and these results are included in the new Figure 10(b) and 10(c).
 
-\item In Section V: Adhesion of two vesicles in a shear flow, we conducted new  simulations with higher Hamaker constant. These results are summarized in Figure 12.
+\item In Section V: For adhesion of two vesicles in a shear flow, we
+  conducted new simulations with higher Hamaker constant. These results
+    are summarized in Figure 12.
 
-\item In Section V: Adhesion of two vesicles in a shear flow, we conducted more simulations to examine the oscillation of the vesicle doublet and how the oscillation frequency depends on 
-the shear rate, separation distance, and Hamaker constant. These results are summarized in Figure 13(b).
+\item In Section V: For adhesion of two vesicles in a shear flow, we
+  conducted more simulations to examine the oscillation of the vesicle
+    doublet and how the oscillation frequency depends on the shear rate,
+    separation distance, and Hamaker constant. These results are
+    summarized in Figure 13(b).
 
@@
 
-\item In Section V: Adhesion of two vesicles in a shear flow, we
-  conducted more simulations to examine the effect of the separation
+\item In Section V: For adhesion of two vesicles in a planar shear flow,
+  we conducted more simulations to examine the effect of the separation
     distance $\delta$ based on reviewers' suggestions.
 
-\item In Section V: Adhesion of two vesicles in a shear flow, we
-  corrected the calculation of the intrinsic viscosity and the new
+\item In Section V: For adhesion of two vesicles in a linear shear flow,
+  we corrected the calculation of the intrinsic viscosity and the new
     results are summarized in Figure 15.  We also discussed the effect
@@
 
-\item In Acknowledgements,  a sentence is added to describe the contribution from each author.
+\item In Acknowledgements, a sentence is added to describe the
+  contribution from each author.
 

### 2019-07-21 vesicle_code/docs/adhesion/revisions/reviewer1.tex
yny revisions july 21

@@
 \begin{itemize}
-  \item We have reorganized section IV based on the referee's feedback.
+  \item We agree with the referee that the external flow is irrotational without the
+    vesicles. But once the vesicles are in the flow, the velocity field around the boundaries
+    is altered by the drop deformation and balance of stress on the boundary. 
+    For a viscous drop in an extensional flow a systematic way to compute some 
+    flow perturbation due to a deformable drop can be found in {\it Advanced Transport Phenomena} 
+    by L. Gary Leal, Cambridge University Press.
+
+    To enhance clarity we have reorganized section IV based on the referee's feedback.
     To investigate the vesicle hydrodynamics in a planar extensional
@@
     contributes to asymmetric configuration of vesicles around the
-    stagnation point, as for a single surfactant-laden drop in an
+    stagnation point, as in the case for a single surfactant-laden drop in an
     extensional flow.

### 2019-07-22 vesicle_code/docs/adhesion/adhesion.tex
yny corrected adhesion
yny adhesion

@@
 LinFreund2007_IntJSolidsStructures, GruhnFrankeDimova2007_Langmuir,
-das2008adhesion, zhang2009phase, Agudo-Canalejo2015_ACSNano,
+das2008adhesion,KehWalterLeal2014_PoF,zhang2009phase, Agudo-Canalejo2015_ACSNano,
 Agudo-CanalejoLipowsky2015_NanoLett, SteinkuhlerAgudo-Canalejo2016_BJ,
+KehLeal2016_PRF,
 Agudo-CanalejoLipowsky2017_SoftMatt} than the transient adhesion
@@
 membrane contact angle at the edge of contact
-zone~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir, MaresDanielIglic2012_SciWorldJ}.  Alternatively, Evans and
-Metcalfe~\cite{EvansMetcalfe1984_BJ} used the micropipette to measure
-the adhesive force between two vesicles bound by strong adhesion.  They
-were able to measure the reduction in the free energy per unit area of
+zone~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir, MaresDanielIglic2012_SciWorldJ}.  Alternatively, researchers have
+used the micropipette to measure
+the adhesive force between two vesicles bound by strong adhesion \cite{EvansMetcalfe1984_BJ,FrostadSethBernasekLeal2014_SoftMatt}: 
+Evans and Metcalfe~\cite{EvansMetcalfe1984_BJ} were able to measure the reduction in 
+the free energy per unit area of
 membrane-membrane contact formation due to the van der Waals'
@@
 of $3$ $\mu J/m^2$ between two
-RBCs~\cite{FlormannAouane2017_SciReports}.  For adhesion interaction
+RBCs~\cite{FlormannAouane2017_SciReports}.  
+Frostad {\it et al.}~\cite{FrostadSethBernasekLeal2014_SoftMatt} 
+investigated the depletion-attraction induced adhesion between two
+vesicles, and identified the dynamic role of membrane tension during membrane 
+adhesion/peeling.
+
+For adhesion interaction
 between a vesicle and a substrate~\cite{GruhnFrankeDimova2007_Langmuir},
@@
 
-\todo[inline]{This first sentence is incomplete}
+%\todo[inline]{This first sentence is incomplete}
 When the force on each vesicle is a function of the separation distance
@@
   F(h) \sim \mathcal{H} \frac{m\delta^m}{h^{m+1}}
-    \left(1-\left(\frac{\delta}{h}\right)^{n-m}\right),
+    \left(1-\left(\frac{\delta}{h}\right)^{n-m}\right)
 \end{align}
-with integers $m>n\ge 2$.  Attraction is dominant at ``large"
+with integers $m>n\ge 2$, attraction is dominant at ``large"
 distances ($h > \delta$) while repulsion is dominant at ``small"
@@
 viscous drop under a planar extensional
-flow~\cite{JanssenBoonAgterof1997_AIChE, HuPineLeal2000_PoF}.  To the
-best of our knowledge, no studies on the interactions between two
-vesicles in an extensional flow are available in the literature.  In the
-following we first illustrate how two vesicles interact with each other
-in a planar extensional flow. We then illustrate how the adhesion
+flow~\cite{JanssenBoonAgterof1997_AIChE, HuPineLeal2000_PoF}.  
+Frostad {\it et al.} investigated the draining of thin film between two identical vesicles
+as they collide head-on in an extensional flow \cite{FrostadWalterLeal2013_PoF}, however
+they did not include adhesive interaction between vesicles.
+In the following we first illustrate how two vesicles interact with each other under an adhesive
+potential in a planar extensional flow. We then illustrate how the adhesion
 strength between membranes can be measured non-intrusively by using the

### 2019-09-26 vesicle_code/docs/softmatter/permeableVes.tex
starting soft matter template

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%This is the LaTeX ARTICLE template for RSC journals
%Copyright The Royal Society of Chemistry 2016
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[twoside,twocolumn,9pt]{article}
\usepackage{extsizes}
\usepackage[super,sort&compress,comma]{natbib} 
\usepackage[version=3]{mhchem}
\usepackage[left=1.5cm, right=1.5cm, top=1.785cm, bottom=2.0cm]{geometry}
\usepackage{balance}
\usepackage{times,mathptmx}
\usepackage{sectsty}
\usepackage{graphicx} 
\usepackage{lastpage}
\usepackage[format=plain,justification=justified,singlelinecheck=false,font={stretch=1.125,small,sf},labelfont=bf,labelsep=space]{caption}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{fnpos}
\usepackage[english]{babel}
\addto{\captionsenglish}{%
  \renewcommand{\refname}{Notes and references}
}
\usepackage{array}
\usepackage{droidsans}
\usepackage{charter}
\usepackage[T1]{fontenc}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{setspace}
\usepackage[compact]{titlesec}
\usepackage{hyperref}
%%%Please don't disable any packages in the preamble, as this may cause the template to display incorrectly.%%%

\usepackage{epstopdf}%This line makes .eps figures into .pdf - please comment out if not required.

\definecolor{cream}{RGB}{222,217,201}

\usepackage{amsmath,amsfonts,amssymb,bm}
\usepackage{epsfig}
\DeclareMathAlphabet{\mathcal}{OMS}{cmsy}{m}{n}

\input my_macros2.tex	
\begin{document}

\pagestyle{fancy}
\thispagestyle{plain}
\fancypagestyle{plain}{

%%%HEADER%%%
\fancyhead[C]{\includegraphics[width=18.5cm]{head_foot/header_bar}}
\fancyhead[L]{\hspace{0cm}\vspace{1.5cm}\includegraphics[height=30pt]{head_foot/journal_name}}
\fancyhead[R]{\hspace{0cm}\vspace{1.7cm}\includegraphics[height=55pt]{head_foot/RSC_LOGO_CMYK}}
\renewcommand{\headrulewidth}{0pt}
}
%%%END OF HEADER%%%

%%%PAGE SETUP - Please do not change any commands within this section%%%
\makeFNbottom
\makeatletter
\renewcommand\LARGE{\@setfontsize\LARGE{15pt}{17}}
\renewcommand\Large{\@setfontsize\Large{12pt}{14}}
\renewcommand\large{\@setfontsize\large{10pt}{12}}
\renewcommand\footnotesize{\@setfontsize\footnotesize{7pt}{10}}
\makeatother

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand\footnoterule{\vspace*{1pt}% 
\color{cream}\hrule width 3.5in height 0.4pt \color{black}\vspace*{5pt}} 
\setcounter{secnumdepth}{5}

\makeatletter 
\renewcommand\@biblabel[1]{#1}            
\renewcommand\@makefntext[1]% 
{\noindent\makebox[0pt][r]{\@thefnmark\,}#1}
\makeatother 
\renewcommand{\figurename}{\small{Fig.}~}
\sectionfont{\sffamily\Large}
\subsectionfont{\normalsize}
\subsubsectionfont{\bf}
\setstretch{1.125} %In particular, please do not alter this line.
\setlength{\skip\footins}{0.8cm}
\setlength{\footnotesep}{0.25cm}
\setlength{\jot}{10pt}
\titlespacing*{\section}{0pt}{4pt}{4pt}
\titlespacing*{\subsection}{0pt}{15pt}{1pt}
%%%END OF PAGE SETUP%%%

%%%FOOTER%%%
\fancyfoot{}
\fancyfoot[LO,RE]{\vspace{-7.1pt}\includegraphics[height=9pt]{head_foot/LF}}
\fancyfoot[CO]{\vspace{-7.1pt}\hspace{13.2cm}\includegraphics{head_foot/RF}}
\fancyfoot[CE]{\vspace{-7.2pt}\hspace{-14.2cm}\includegraphics{head_foot/RF}}
\fancyfoot[RO]{\footnotesize{\sffamily{1--\pageref{LastPage} ~\textbar  \hspace{2pt}\thepage}}}
\fancyfoot[LE]{\footnotesize{\sffamily{\thepage~\textbar\hspace{3.45cm} 1--\pageref{LastPage}}}}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt} 
\renewcommand{\footrulewidth}{0pt}
\setlength{\arrayrulewidth}{1pt}
\setlength{\columnsep}{6.5mm}
\setlength\bibsep{1pt}
%%%END OF FOOTER%%%

%%%FIGURE SETUP - please do not change any commands within this section%%%
\makeatletter 
\newlength{\figrulesep} 
\setlength{\figrulesep}{0.5\textfloatsep}

\newcommand{\topfigrule}{\vspace*{-1pt}% 
\noindent{\color{cream}\rule[-\figrulesep]{\columnwidth}{1.5pt}} }

\newcommand{\botfigrule}{\vspace*{-2pt}% 
\noindent{\color{cream}\rule[\figrulesep]{\columnwidth}{1.5pt}} }

\newcommand{\dblfigrule}{\vspace*{-1pt}% 
\noindent{\color{cream}\rule[-\figrulesep]{\textwidth}{1.5pt}} }

\makeatother
%%%END OF FIGURE SETUP%%%

%%%TITLE, AUTHORS AND ABSTRACT%%%
\twocolumn[
\begin{@twocolumnfalse}
\vspace{3cm}
\sffamily
\begin{tabular}{m{4.5cm} p{13.5cm} }

\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Semi-permeable
  vesicles: Mathematical formulation, numerics, and physics}} \\
\vspace{0.3cm} & \vspace{0.3cm} \\

 & \noindent\large{Ashley Gannon,\textit{$^{a}$} Yuan-Nan
  Young,\textit{$^{b}$} Shravan Veeranapanei,\textit{$^{c}$} and Bryan
  Quaife$^{\ast}$ \textit{$^{d}$}} \\

\includegraphics{head_foot/dates} & 
\noindent\normalsize{We consider a single semi-permeable vesicle in a
  variety of flows} \\
\end{tabular}

\end{@twocolumnfalse} \vspace{0.6cm}

]
%%%END OF TITLE, AUTHORS AND ABSTRACT%%%

%%%FONT SETUP - please do not change any commands within this section
\renewcommand*\rmdefault{bch}\normalfont\upshape
\rmfamily
\section*{}
\vspace{-1cm}

%%%FOOTNOTES%%%

\footnotetext{\textit{$^{a}$~Department of Scientific Computing, Florida
State University, Tallahassee, FL, USA.}}
\footnotetext{\textit{$^{b}$~Department of Mathematical Sciences, New
Jersey Institute of Technology, Newark, NJ, USA.}}
\footnotetext{\textit{$^{c}$~Department of Mathematics, University of
Michigan, Ann Arbor, MI, USA.}}
\footnotetext{\textit{$^{d}$~Department of Scientific Computing, Florida
State University, Tallahassee, FL, USA. E-mail: bquaife@fsu.edu}}

%Please use \dag to cite the ESI in the main text of the article.
%If you article does not have ESI please remove the the \dag symbol from the title and the footnotetext below.
%\footnotetext{\dag~Electronic Supplementary Information (ESI) available:
%[details of any supplementary information available should be included
%here]. See DOI: 00.0000/00000000.}
%\footnotetext{\ddag~Additional footnotes to the title and authors can be
%included \textit{e.g.}\ `Present address:' or `These authors contributed
%equally to this work' as above using the symbols: \ddag, \textsection,
%and \P. Please place the appropriate symbol next to the author's name
%and include a \texttt{\textbackslash footnotetext} entry in the the
%correct place in the list.}

%%%END OF FOOTNOTES%%%

%%%MAIN TEXT%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem formulation} \label{sc:formulate}
Consider a semi-permeable vesicle suspended in an unbounded viscous
fluid domain, subjected to an imposed flow $\mbu_\infty(\mbx)$, for any
$\mbx \in \RR^2$.  Assume that the interior and exterior fluids have the same viscosity $\mu$. Let $\mbx$ be the position of the interface $\gamma$, $\mbu$ the fluid velocity and $p$ the pressure. In the vanishing Reynolds number limit, the governing equations for the ambient fluid can be written as: 
%
\begin{subequations}
\begin{align}
-\nabla p + \mu \triangle \mbu = 0 \quad\text{in}\quad
  \RR^2\setminus\gamma  &  \\
% 
\nabla \cdot \mbu = 0  \quad\text{in}\quad \RR^2\setminus\gamma &\\
%
\mbu(\mbx) \rightarrow \mbu_\infty(\mbx) \quad \text{as} \quad  \norm{\mbx} \rightarrow \infty & 
 \end{align} \label{eqn:governing}
\end{subequations}%
%
The modified jump conditions in the case of a semi-permeable vesicle can
be summarized as follows.  Let $\mbn$ the outward normal to $\gamma$ and
$\jump{\cdot}$ denote the jump across the interface. The jump condition
for the hydrodynamic stress remains the same:
\begin{align} 
  \jump{\Sigma\cdot\mbn} = \mbf_\text{mem}, 
\end{align}
where $\Sigma$ is the hydrodynamic stress tensor. The fluid velocity is
continuous across the membrane i.e.,
\begin{align}
  \jump{\mbu} = 0. 
\end{align}
However, the kinematic condition is modified to account for the fact
that the fluid can move through the membrane. A standard choice appears
to be
%
\begin{align}
  \mbu - \dot{\mbx} = - \beta (\mbf_\text{mem} \cdot \mbn) \mbn
      \quad\text{on}\quad\gamma. 
\end{align}
%
Here, $\beta$ is a constant and the membrane force is the usual
sum of the bending and tension forces.

We can use the governing equations to write a differential equation for
the area of the vesicle as a function of time. The area inside a single
vesicle $\gamma$ parameterized with $\mbx$ is
\begin{align}
  A(t) = \frac{1}{2}\int_{\gamma} (\mbx \cdot \mbn)\, ds = 
    \frac{1}{2}\int_{0}^{2\pi} \left(\mbx \cdot
    \pderiv{\mbx}{\theta}^\perp\right)
    \, d\theta.
\end{align}
Taking the time derivative of $A(t)$,
\begin{align}
  \dot{A}(t) &= \frac{1}{2}\int_{0}^{2\pi} \left(\dot{\mbx} \cdot
  \pderiv{\mbx}{\theta}^{\perp} + 
    \mbx \cdot \pderiv{\dot{\mbx}}{\theta}^{\perp}\right) d\theta, \\
  &= \frac{1}{2}
  \int_{0}^{2\pi}(\dot{\mbx}\cdot\mbn)\left\|\pderiv{\mbx}{\theta}\right\|d\theta +
     \frac{1}{2}\int_{0}^{2\pi}
    \left(\mbx \cdot \pderiv{\dot{\mbx}}{\theta}^{\perp}\right)d\theta, \\
  &= \frac{k_w}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds +
  \frac{1}{2}\int_{0}^{2\pi}\left(\mbx \cdot \pderiv{}{t}\left(\mbn
  \left\|\pderiv{\mbx}{\theta}\right\|\right)\right)d\theta, \\
  &= \frac{k_w}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds + \frac{1}{2}
  \int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds + \frac{1}{2}\int_{0}^{2\pi}
  \frac{\mbx\cdot\mbn}{\left\|\pderiv{\mbx}{\theta}\right\|}
  \left(\pderiv{\mbx}{\theta}\cdot
  \pderiv{\dot{\mbx}}{\theta}\right)d\theta \\
  &= \frac{k_w}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds + \frac{1}{2}
  \int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds + \frac{1}{2}\int_{\gamma}
  (\mbx\cdot\mbn) (\mbx_s \cdot \dot{\mbx}_s)\, ds.
\end{align}
To satisfy the inextensibilty condition, $\mbx_s \cdot \dot{\mbx}_s = 0$.
Therefore the time derivative of $A(t)$ is
\begin{align}
     \dot{A}(t) &= \frac{k_w}{2}
     \int_{\gamma}\left(\mbf\cdot\mbn\right)ds
     + \frac{1}{2} \int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds.
\end{align}
... 
\begin{align}
    \dot{A}(t) &= \frac{k_w}{2}
    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right) ds,
\end{align}
which we re-write as
\begin{align}
    \dot{A}(t) &= \frac{k_w}{2}
    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds-\frac{1}{2}\int_{\gamma}\left(\mbx^{\perp}\cdot\dot{\mbx}_s\right) ds.
\end{align}
Applying integration by parts,
\begin{align}
    \dot{A}(t) &= \frac{k_w}{2}
    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\mbx^{\perp}_s\cdot\dot{\mbx}\right) ds,
\end{align}
which we re-write as
\begin{align}
    \dot{A}(t) &= \frac{k_w}{2}
    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\dot{\mbx}\cdot\mbn\right),\\
    \dot{A}(t) &= k_w \int_{\gamma}\left(\mbf\cdot\mbn\right)ds.
\end{align}
At steady stae,
\begin{align}
    \dot{A}(t) &= k_w \int_{\gamma}\left(\mbf\cdot\mbn\right)ds =0.
\end{align}
We now replace $\mbf$ with its relation
\begin{align}
   k_w\int_{\gamma}
   \left((-\kappa_b\mbx_{ssss}+(\sigma\mbx_s)_s)\cdot\mbn\right)ds &=0.
\end{align}
Applying integration by parts,
\begin{align}
     k_w\int_{\gamma}\left(\kappa_b\mbx_{sss}-\sigma\mbx_s\right)\cdot
     \mbn_s ds &=0.
\end{align}
From the Frenet-Serret formulas, we have 
\begin{align}
     -k_w\int_{\gamma}
     \left(\kappa_b\mbx_{sss}-\sigma\mbx_s\right)\cdot\kappa\mbx_s ds &=0.
\end{align}

Applying integration by parts and Frenet-Serret again
\begin{align}
     k_w\int_{\gamma}
     \kappa_b\kappa\left(\mbx_{ss}\cdot\mbx_{ss}\right)ds + k_w
     \int_{\gamma} \kappa_b \kappa_s(\mbx_{ss} \cdot \mbx_s)ds +k_w\int_{\gamma}\kappa\sigma ds  &= 0,\\
    k_w\int_{\gamma} \kappa_b\kappa(\kappa\mbn \cdot
     \kappa\mbn)+ k_w \int_{\gamma} \kappa_b \kappa_s(\mbx_{ss} \cdot
     \mbx_s)ds +k_w\int_{\gamma}\kappa\sigma ds &= 0,
\end{align}
which we re-write as
\begin{align}
   k_w\int_{\gamma}\kappa_b\kappa^3 ds + k_w \int_{\gamma} \kappa_b
   \kappa_s(\mbx_{ss} \cdot \mbx_s)ds +k_w\int_{\gamma} \kappa\sigma ds = 0.
\end{align}
Applying Frenet-serret again,
\begin{align}
    k_w\int_{\gamma}\kappa_b\kappa^3 ds + k_w \int_{\gamma} \kappa_b
    \kappa_s(\kappa\mbn \cdot \TT)ds +k_w\int_{\gamma} \kappa\sigma ds = 0, \\
    k_w\int_{\gamma}\kappa_b\kappa^3 ds +k_w\int_{\gamma} \kappa\sigma ds  = 0, 
\end{align}
we compare this to our numerical results.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Integral equation formulation and non-dimensionalization}
There are multiple ways to convert the PDE problem into integral
equations. The coupled set of
integro-differential equations satisfy the given interfacial conditions:
\begin{align}
  \label{eqn:vesVelocity}
  \dot{\mbx} &= \mbu_\infty(\mbx) + k_w
  (RT\jump{c}+\mbf_\text{mem}\cdot\mbn)\mbn
  + \SS [\mbf_\text{mem}],  \\
  \mbx_s\cdot\dot{\mbx}_s &= 0 
\end{align}
This satisfies all the jump conditions. As usual, $\SS$ is the single
layer potential.  We introduce the notation
\begin{align}
  B[\mbx]\mbf &= -\kappa_b\frac{d^4}{ds^4} \mbf, \\
  T[\mbx]\sigma &= (\sigma \mbx_s)_s, \\
  P[\mbx]\mbf &= (\mbf \cdot \mbn) \mbn, \\
  D[\mbx]\mbf &= \mbx_s \cdot \mbf_s,
\end{align}
where $\mbn$ is the outward unit normal of the vesicle parameterized by
$\mbx$, and $d/ds$ is its arclength derivative.  Dropping the dependence
of the operators on $\mbx$, the dynamics of the vesicle are governed by
\begin{align}
  \dot{\mbx} &= \mbu_{\infty}(\mbx) + 
  k_wRT\jump{c}\mbn + k_wP(B\mbx + T\sigma) + \SS(B\mbx + T\sigma), \label{eq:full}\\
  D \dot{\mbx} &= 0.
\end{align}

Following the analysis of~\cite{vee-gue-zor-bir2009} and
disregarding background flow, we define scales of $\mbx$, $t$, $k_w$,
and $c$ to nondimensionalize equation (\ref{eq:full}) as follows. The
length is scaled using the radius of a circle with the same perimeter,
$L$, as the vesicle, $R_0 = \frac{L}{2\pi}$. From analysis, the time
scale $\tau$ is defined as $\tau = \frac{\mu R_0^2}{k_b}$, the tension
scale, $Q$, is defined as $Q = \frac{k_b}{R_0^2}$, the water flux scale,
$W$, is defined as $W=\frac{R_0}{\mu}$, and the concentration scale,
$C$, is defined as $C=\frac{k_b}{R_0^3RT}$. The governing equation in
nondimensional form is
\begin{align}
    \dot{\Tilde{\mbx}} =  \Tilde{k_w}\jump{\tilde{c}}\mbn +
    \Tilde{k_w}P\big(B[\Tilde{\mbx}]\Tilde{\mbx}+T[\Tilde{\mbx}]\Tilde{\sigma}\big)
    +\SS\big( B[\Tilde{\mbx}]\Tilde{\mbx} + T[\Tilde{\mbx}]\Tilde{\sigma}\big).
\end{align}
In our current implementation, we let $\jump{c} = 0$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical methods}
To address stiffness associated with high-order derivatives,
equation~\eqref{eqn:vesVelocity} is discretized with a semi-implicit
time stepping method similar to our previous works.  First, we introduce
the notation
\begin{align}
  B[\mbx]\mbf &= -\kappa_b\frac{d^4}{ds^4} \mbf, \\
  T[\mbx]\sigma &= (\sigma \mbx_s)_s, \\
  P[\mbx]\mbf &= (\mbf \cdot \mbn) \mbn, \\
  D[\mbx]\mbf &= \mbx_s \cdot \mbf_s,
\end{align}
where $\mbn$ is the outward unit normal of the vesicle
parameterized by $\mbx$, and $d/ds$ is its arclength derivative.
Dropping the dependence of the operators on $\mbx$, the dynamics of the
vesicle are governed by
\begin{align}
  \dot{\mbx} &= \mbu_{\infty}(\mbx) + 
  \beta P(B\mbx + T\sigma) + \sgl(B\mbx + T\sigma), \\
  D \dot{\mbx} &= 0.
\end{align}
Using the notation $B^N$ to denote the bending operator due to the
vesicle configuration at time $t_N$, and similar notation for the other
operators, we apply the semi-implicit time stepping method
\begin{align}  
  \frac{\mbx^{N+1} - \mbx^N}{\Delta t} = \mbu_\infty(\mbx^N) 
  + \beta P^N(B^N\mbx^{N+1} + T^N\sigma^{N+1}) 
  + \sgl^N(B^N\mbx^{N+1} + T^N\sigma^{N+1}).
\end{align}
Applying $D$ to the first-order time discretization of
equation~\eqref{eqn:vesVelocity}, the inextensibility condition is
\begin{align*}
  &D^N(\mbx^{N+1} - \mbx^N) = 0 \\ 
  \Rightarrow &D^N\mbx^{N+1} = D^N \mbx^N \\ 
  \Rightarrow &D^N\mbx^{N+1} = 1.
\end{align*}
Finally, we write the time stepping method in matrix form as
\begin{align}
  A \left(
    \begin{array}{c}
      \mbx^{N+1} \\ \sigma^{N+1}
    \end{array}
  \right) = 
  \left(
    \begin{array}{c}
      \mbx^{N} + \Delta t \mbu_\infty(\mbx^N) \\ \mathbf{1}
    \end{array}
  \right),
\end{align}
where
\begin{align}
 A = \left(
  \begin{array}{cc}
    I + \Delta t \beta P^N B^N + \Delta t \sgl^N B^N & 
    -\Delta t P^N T^N - \Delta t \sgl^N T^N \\
    D^N & 0
  \end{array}
  \right).
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical simulations}
We consider a single vesicle suspended in a viscous fluid under various
conditions.  The main results we have so far are
\begin{itemize}
  \item Given a fixed $\beta$ and vesicle length, the final reduced area
    is independent of the initial reduced area, and even the vesicle
    shape. However, the final reduced area does depend on the initial
    vesicle length and $\beta$.

  \item The final reduced area increases as the shear rate decreases. In
    the limit of zero shear rate (quiescent flow), the semi-permeable
    vesicles always tends to a circle

  \item The inclination angle of a semi-permeable vesicle in a shear
    flow is greater than the inclination angle of a clean vesicle with
    the same reduced area as the final reduced area of the
    semi-permeable vesicle.

  \item We are able to look at the flux across the interface and
    characterize where there is inflow and outflow.

  \item For $\beta$ that depends on arclength, we have observed both a
    breathing motion (semi-permeable only on opposite sides), and
    migration (semi-permeable only on about 25\% of the vesicle).
\end{itemize}

\subsection{Content permeability rate}

\subsection{Variable permeability rate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Conflicts of interest}
In accordance with our policy on
\href{http://www.rsc.org/journals-books-databases/journal-authors-reviewers/author-responsibilities/#code-of-conduct}{Conflicts
of interest} please ensure that a conflicts of interest statement is
included in your manuscript here.  Please note that this statement is
required for all submitted manuscripts.  If no conflicts exist, please
state that ``There are no conflicts to declare''.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
The Acknowledgements come at the end of an article after Conflicts of interest and before the Notes and references.

%%%END OF MAIN TEXT%%%

%The \balance command can be used to balance the columns on the final page if desired. It should be placed anywhere within the first column of the last page.

\balance

%%%REFERENCES%%%
\bibliography{refs} %You need to replace "rsc" on this line with the name of your .bib file
\bibliographystyle{rsc} %the RSC's .bst file

\end{document}

% Template stuff
%The main text of the article\cite{Mena2000} should appear here.
%
%\subsection{This is the subsection heading style}
%Section headings can be typeset with and without numbers.\cite{Abernethy2003}
%
%\subsubsection{This is the subsubsection style.~~} These headings should end in a full point.  
%
%\paragraph{This is the next level heading.~~} For this level please use \texttt{\textbackslash paragraph}. These headings should also end in a full point.
%
%\section{Graphics and tables}
%\subsection{Graphics}
%Graphics should be inserted on the page where they are first mentioned (unless they are equations, which appear in the flow of the text).\cite{Cotton1999}
%
%\begin{figure}[h]
%\centering
%%  \includegraphics[height=3cm]{example1}
%  \caption{An example figure caption.}
%  \label{fgr:example}
%\end{figure}
%
%\begin{figure*}
% \centering
%% \includegraphics[height=3cm]{example2}
% \caption{A two-column figure.}
% \label{fgr:example2col}
%\end{figure*}
%
%\subsection{Tables}
%Tables typeset in RSC house style do not include vertical lines. Table footnote symbols are lower-case italic letters and are typeset at the bottom of the table. Table captions do not end in a full point.\cite{Arduengo1992,Eisenstein2005}
%
%
%\begin{table}[h]
%\small
%  \caption{\ An example of a caption to accompany a table}
%  \label{tbl:example}
%  \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}lll}
%    \hline
%    Header one (units) & Header two & Header three \\
%    \hline
%    1 & 2 & 3 \\
%    4 & 5 & 6 \\
%    7 & 8 & 9 \\
%    10 & 11 & 12 \\
%    \hline
%  \end{tabular*}
%\end{table}
%
%Adding notes to tables can be complicated.  Perhaps the easiest method is to generate these manually.\footnote[4]{Footnotes should appear here. These might include comments relevant to but not central to the matter under discussion, limited experimental and spectral data, and crystallographic data.}
%
%\begin{table*}
%\small
%  \caption{\ An example of a caption to accompany a table \textendash\ table captions do not end in a full point}
%  \label{tbl:example}
%  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lllllll}
%    \hline
%    Header one & Header two & Header three & Header four & Header five & Header six  & Header seven\\
%    \hline
%    1 & 2 & 3 & 4 & 5 & 6  & 7\\
%    8 & 9 & 10 & 11 & 12 & 13 & 14 \\
%    15 & 16 & 17 & 18 & 19 & 20 & 21\\
%    \hline
%  \end{tabular*}
%\end{table*}
%
%\section{Equations}
%
%Equations can be typeset inline \textit{e.g.}\ $ y = mx + c$ or displayed with and without numbers:
%
% \[ A = \pi r^2 \]
%
%\begin{equation}
%  \frac{\gamma}{\epsilon x} r^2 = 2r
%\end{equation}
%
%You can also put lists into the text. You can have bulleted or numbered lists of almost any kind. 
%The \texttt{mhchem} package can also be used so that formulae are easy to input: \texttt{\textbackslash ce\{H2SO4\}} gives \ce{H2SO4}. 
%
%For footnotes in the main text of the article please number the footnotes to avoid duplicate symbols. \textit{e.g.}\ \texttt{\textbackslash footnote[num]\{your text\}}. The corresponding author $\ast$ counts as footnote 1, ESI as footnote 2, \textit{e.g.}\ if there is no ESI, please start at [num]=[2], if ESI is cited in the title please start at [num]=[3] \textit{etc.} Please also cite the ESI within the main body of the text using \dag.

### 2019-09-26 vesicle_code/src/curve.m

@@ -171,6 +171,13 @@ end
 % scale the size of the vesicle (reduced area is invariant under
 % scale)
 
+if(any(strcmp(options,'folds')))
+  folds = options{find(strcmp(options,'folds'))+1};
+else
+  folds = 1;
+end
+% number of folds for a star shape
+
 t = (0:N-1)'*2*pi/N;
 % Discretization in parameter space
 
@@ -184,9 +191,8 @@ if any(strcmp(options,'curly'))
   % radius of curly vesicle
 
 elseif any(strcmp(options,'star'))
-  folds = options{2};
-  radius = 1 + 0.98*cos(folds*t);
-  X = [radius.*cos(t);radius.*sin(t)];
+  radius = 1 + 0.2*cos(folds*t);
+  X = scale*[radius.*cos(t);radius.*sin(t)];
   % a star that comes very close to intersecting itself
   % at the origin
 

### 2019-09-27 vesicle_code/docs/softmatter/permeableVes.tex
made changes to soft matter Tex file.  Area eqs and Num sims section

@@
     \mbx \cdot \pderiv{\dot{\mbx}}{\theta}^{\perp}\right) d\theta, \\
-  &= \frac{1}{2}
-  \int_{0}^{2\pi}(\dot{\mbx}\cdot\mbn)\left\|\pderiv{\mbx}{\theta}\right\|d\theta +
-     \frac{1}{2}\int_{0}^{2\pi}
-    \left(\mbx \cdot \pderiv{\dot{\mbx}}{\theta}^{\perp}\right)d\theta, \\
-  &= \frac{k_w}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds +
-  \frac{1}{2}\int_{0}^{2\pi}\left(\mbx \cdot \pderiv{}{t}\left(\mbn
-  \left\|\pderiv{\mbx}{\theta}\right\|\right)\right)d\theta, \\
-  &= \frac{k_w}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds + \frac{1}{2}
-  \int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds + \frac{1}{2}\int_{0}^{2\pi}
-  \frac{\mbx\cdot\mbn}{\left\|\pderiv{\mbx}{\theta}\right\|}
-  \left(\pderiv{\mbx}{\theta}\cdot
-  \pderiv{\dot{\mbx}}{\theta}\right)d\theta \\
+  %&= \frac{1}{2}
+  %\int_{0}^{2\pi}(\dot{\mbx}\cdot\mbn)\left\|\pderiv{\mbx}{\theta}\right\|d\theta +
+  %   \frac{1}{2}\int_{0}^{2\pi}
+  %  \left(\mbx \cdot \pderiv{\dot{\mbx}}{\theta}^{\perp}\right)d\theta, \\
+  %&= \frac{k_w}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds +
+  %\frac{1}{2}\int_{0}^{2\pi}\left(\mbx \cdot \pderiv{}{t}\left(\mbn
+  %\left\|\pderiv{\mbx}{\theta}\right\|\right)\right)d\theta, \\
+  %&= \frac{k_w}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds + \frac{1}{2}
+  %\int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds + \frac{1}{2}\int_{0}^{2\pi}
+  %\frac{\mbx\cdot\mbn}{\left\|\pderiv{\mbx}{\theta}\right\|}
+  %\left(\pderiv{\mbx}{\theta}\cdot
+  %\pderiv{\dot{\mbx}}{\theta}\right)d\theta \\
   &= \frac{k_w}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds + \frac{1}{2}
@@
 \end{align}
-To satisfy the inextensibilty condition, $\mbx_s \cdot \dot{\mbx}_s = 0$.
-Therefore the time derivative of $A(t)$ is
+To satisfy the inextensibilty condition, $\mbx_s \cdot \dot{\mbx}_s = 0$, the time derivative of $A(t)$ is
 \begin{align}
@@
 \end{align}
-... 
-\begin{align}
-    \dot{A}(t) &= \frac{k_w}{2}
-    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right) ds,
-\end{align}
+%... 
+%\begin{align}
+%    \dot{A}(t) &= \frac{k_w}{2}
+%    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right) ds,
+%\end{align}
 which we re-write as
@@
 \end{align}
-Applying integration by parts,
+Applying integration by parts and re-writing,
+%\begin{align}
+%    \dot{A}(t) &= \frac{k_w}{2}
+%    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\mbx^{\perp}_s\cdot\dot{\mbx}\right) ds,
+%\end{align}
+%which we re-write as
 \begin{align}
-    \dot{A}(t) &= \frac{k_w}{2}
-    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\mbx^{\perp}_s\cdot\dot{\mbx}\right) ds,
-\end{align}
-which we re-write as
-\begin{align}
-    \dot{A}(t) &= \frac{k_w}{2}
-    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\dot{\mbx}\cdot\mbn\right),\\
+ %   \dot{A}(t) &= \frac{k_w}{2}
+ %   \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\dot{\mbx}\cdot\mbn\right),\\
     \dot{A}(t) &= k_w \int_{\gamma}\left(\mbf\cdot\mbn\right)ds.
 \end{align}
-At steady stae,
+At steady state,
 \begin{align}
@@
 \end{align}
-We now replace $\mbf$ with its relation
+Replacing $\mbf$ with its relation, applying integration by parts twice and using Frenet-serret formulas,  
 \begin{align}
-   k_w\int_{\gamma}
-   \left((-\kappa_b\mbx_{ssss}+(\sigma\mbx_s)_s)\cdot\mbn\right)ds &=0.
+k_w\int_{\gamma}\kappa_b\kappa^3 ds +k_w\int_{\gamma} \kappa\sigma ds  = 0. 
 \end{align} 
-Applying integration by parts,
-\begin{align}
-     k_w\int_{\gamma}\left(\kappa_b\mbx_{sss}-\sigma\mbx_s\right)\cdot
-     \mbn_s ds &=0.
-\end{align}
-From the Frenet-Serret formulas, we have 
-\begin{align}
-     -k_w\int_{\gamma}
-     \left(\kappa_b\mbx_{sss}-\sigma\mbx_s\right)\cdot\kappa\mbx_s ds &=0.
-\end{align}
+%We now replace $\mbf$ with its relation
+%\begin{align}
+%   k_w\int_{\gamma}
+%   \left((-\kappa_b\mbx_{ssss}+(\sigma\mbx_s)_s)\cdot\mbn\right)ds &=0.
+%\end{align}
+%Applying integration by parts,
+%\begin{align}
+%     k_w\int_{\gamma}\left(\kappa_b\mbx_{sss}-\sigma\mbx_s\right)\cdot
+%     \mbn_s ds &=0.
+%\end{align}
+%From the Frenet-Serret formulas, we have 
+%\begin{align}
+%     -k_w\int_{\gamma}
+%     \left(\kappa_b\mbx_{sss}-\sigma\mbx_s\right)\cdot\kappa\mbx_s ds &=0.
+%\end{align}
 
-Applying integration by parts and Frenet-Serret again
-\begin{align}
-     k_w\int_{\gamma}
-     \kappa_b\kappa\left(\mbx_{ss}\cdot\mbx_{ss}\right)ds + k_w
-     \int_{\gamma} \kappa_b \kappa_s(\mbx_{ss} \cdot \mbx_s)ds +k_w\int_{\gamma}\kappa\sigma ds  &= 0,\\
-    k_w\int_{\gamma} \kappa_b\kappa(\kappa\mbn \cdot
-     \kappa\mbn)+ k_w \int_{\gamma} \kappa_b \kappa_s(\mbx_{ss} \cdot
-     \mbx_s)ds +k_w\int_{\gamma}\kappa\sigma ds &= 0,
-\end{align}
-which we re-write as
-\begin{align}
-   k_w\int_{\gamma}\kappa_b\kappa^3 ds + k_w \int_{\gamma} \kappa_b
-   \kappa_s(\mbx_{ss} \cdot \mbx_s)ds +k_w\int_{\gamma} \kappa\sigma ds = 0.
-\end{align}
-Applying Frenet-serret again,
-\begin{align}
-    k_w\int_{\gamma}\kappa_b\kappa^3 ds + k_w \int_{\gamma} \kappa_b
-    \kappa_s(\kappa\mbn \cdot \TT)ds +k_w\int_{\gamma} \kappa\sigma ds = 0, \\
-    k_w\int_{\gamma}\kappa_b\kappa^3 ds +k_w\int_{\gamma} \kappa\sigma ds  = 0, 
-\end{align}
-we compare this to our numerical results.
+%Applying integration by parts and Frenet-Serret again
+%\begin{align}
+%     k_w\int_{\gamma}
+%     \kappa_b\kappa\left(\mbx_{ss}\cdot\mbx_{ss}\right)ds + k_w
+%     \int_{\gamma} \kappa_b \kappa_s(\mbx_{ss} \cdot \mbx_s)ds +k_w\int_{\gamma}\kappa\sigma ds  &= 0,\\
+%    k_w\int_{\gamma} \kappa_b\kappa(\kappa\mbn \cdot
+%     \kappa\mbn)+ k_w \int_{\gamma} \kappa_b \kappa_s(\mbx_{ss} \cdot
+%     \mbx_s)ds +k_w\int_{\gamma}\kappa\sigma ds &= 0,
+%\end{align}
+%which we re-write as
+%\begin{align}
+%   k_w\int_{\gamma}\kappa_b\kappa^3 ds + k_w \int_{\gamma} \kappa_b
+%   \kappa_s(\mbx_{ss} \cdot \mbx_s)ds +k_w\int_{\gamma} \kappa\sigma ds = 0.
+%\end{align}
+%Applying Frenet-serret again,
+%\begin{align}
+%    k_w\int_{\gamma}\kappa_b\kappa^3 ds + k_w \int_{\gamma} \kappa_b
+%    \kappa_s(\kappa\mbn \cdot \TT)ds +k_w\int_{\gamma} \kappa\sigma ds = 0, \\
+%    k_w\int_{\gamma}\kappa_b\kappa^3 ds +k_w\int_{\gamma} \kappa\sigma ds  = 0, 
+%\end{align}
+%we compare this to our numerical results.
 
@@
 \begin{align} 
+\begin{split}
   \frac{\mbx^{N+1} - \mbx^N}{\Delta t} = \mbu_\infty(\mbx^N) 
-  + \beta P^N(B^N\mbx^{N+1} + T^N\sigma^{N+1}) 
+  + \beta P^N(B^N\mbx^{N+1} + T^N\sigma^{N+1}) \\
    + \sgl^N(B^N\mbx^{N+1} + T^N\sigma^{N+1}).
+   \end{split} 
 \end{align}
@@
     migration (semi-permeable only on about 25\% of the vesicle).
+
+  \item Compare area results to analytic equation?
 \end{itemize}

### 2019-09-27 vesicle_code/docs/softmatter/permeableVes.tex
Working on soft matter TeX

@@
  \end{align} \label{eqn:governing}
-\end{subequations}%
-%
+\end{subequations}
+\begin{figure}[H]
+	\centering
+	\epsfig{file =figures/vesicleschem.pdf, width=.6\columnwidth}
+	\caption{$\Omega$ is the unbounded fluid domain and $\gamma$ is the vesicle membrane. In addition to the vesicle-induced flow, a shear flow is imposed in the far field, $\mbu_\infty$.}
+\end{figure}
 The modified jump conditions in the case of a semi-permeable vesicle can
@@
 \begin{align} 
-  \jump{\Sigma\cdot\mbn} = \mbf_\text{mem}, 
+  \jump{\Sigma\cdot\mbn} = \mbf, 
 \end{align}
@@
 to be
-%
 \begin{align}
-  \mbu - \dot{\mbx} = - \beta (\mbf_\text{mem} \cdot \mbn) \mbn
+  \mbu - \dot{\mbx} = - \beta (\text{RT}\jump{c}+\mbf \cdot \mbn) \mbn
       \quad\text{on}\quad\gamma. 
 \end{align}
+Here, $\beta$, R, and T are constants, $c$ is the solute concentration, and the membrane force is the usual sum of the bending and tension forces,
+\begin{subequations}
+	\begin{align}
+	\mbf = \mbf_{\text{bending}}+\mbf_{\text{tension}},  &  \\
 	% 
-Here, $\beta$ is a constant and the membrane force is the usual
-sum of the bending and tension forces.
-
-We can use the governing equations to write a differential equation for
-the area of the vesicle as a function of time. The area inside a single
-vesicle $\gamma$ parameterized with $\mbx$ is
-\begin{align}
-  A(t) = \frac{1}{2}\int_{\gamma} (\mbx \cdot \mbn)\, ds = 
-    \frac{1}{2}\int_{0}^{2\pi} \left(\mbx \cdot
-    \pderiv{\mbx}{\theta}^\perp\right)
-    \, d\theta.
-\end{align}
-Taking the time derivative of $A(t)$,
-\begin{align}
-  \dot{A}(t) &= \frac{1}{2}\int_{0}^{2\pi} \left(\dot{\mbx} \cdot
-  \pderiv{\mbx}{\theta}^{\perp} + 
-    \mbx \cdot \pderiv{\dot{\mbx}}{\theta}^{\perp}\right) d\theta, \\
-  %&= \frac{1}{2}
-  %\int_{0}^{2\pi}(\dot{\mbx}\cdot\mbn)\left\|\pderiv{\mbx}{\theta}\right\|d\theta +
-  %   \frac{1}{2}\int_{0}^{2\pi}
-  %  \left(\mbx \cdot \pderiv{\dot{\mbx}}{\theta}^{\perp}\right)d\theta, \\
-  %&= \frac{k_w}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds +
-  %\frac{1}{2}\int_{0}^{2\pi}\left(\mbx \cdot \pderiv{}{t}\left(\mbn
-  %\left\|\pderiv{\mbx}{\theta}\right\|\right)\right)d\theta, \\
-  %&= \frac{k_w}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds + \frac{1}{2}
-  %\int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds + \frac{1}{2}\int_{0}^{2\pi}
-  %\frac{\mbx\cdot\mbn}{\left\|\pderiv{\mbx}{\theta}\right\|}
-  %\left(\pderiv{\mbx}{\theta}\cdot
-  %\pderiv{\dot{\mbx}}{\theta}\right)d\theta \\
-  &= \frac{k_w}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds + \frac{1}{2}
-  \int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds + \frac{1}{2}\int_{\gamma}
-  (\mbx\cdot\mbn) (\mbx_s \cdot \dot{\mbx}_s)\, ds.
-\end{align}
-To satisfy the inextensibilty condition, $\mbx_s \cdot \dot{\mbx}_s = 0$, the time derivative of $A(t)$ is
-\begin{align}
-     \dot{A}(t) &= \frac{k_w}{2}
-     \int_{\gamma}\left(\mbf\cdot\mbn\right)ds
-     + \frac{1}{2} \int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds.
-\end{align}
-%... 
-%\begin{align}
-%    \dot{A}(t) &= \frac{k_w}{2}
-%    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right) ds,
-%\end{align}
-which we re-write as
-\begin{align}
-    \dot{A}(t) &= \frac{k_w}{2}
-    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds-\frac{1}{2}\int_{\gamma}\left(\mbx^{\perp}\cdot\dot{\mbx}_s\right) ds.
-\end{align}
-Applying integration by parts and re-writing,
-%\begin{align}
-%    \dot{A}(t) &= \frac{k_w}{2}
-%    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\mbx^{\perp}_s\cdot\dot{\mbx}\right) ds,
-%\end{align}
-%which we re-write as
-\begin{align}
- %   \dot{A}(t) &= \frac{k_w}{2}
- %   \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\dot{\mbx}\cdot\mbn\right),\\
-    \dot{A}(t) &= k_w \int_{\gamma}\left(\mbf\cdot\mbn\right)ds.
-\end{align}
-At steady state,
-\begin{align}
-    \dot{A}(t) &= k_w \int_{\gamma}\left(\mbf\cdot\mbn\right)ds =0.
-\end{align}
-Replacing $\mbf$ with its relation, applying integration by parts twice and using Frenet-serret formulas,  
-\begin{align}
-k_w\int_{\gamma}\kappa_b\kappa^3 ds +k_w\int_{\gamma} \kappa\sigma ds  = 0. 
-\end{align} 
-%We now replace $\mbf$ with its relation
-%\begin{align}
-%   k_w\int_{\gamma}
-%   \left((-\kappa_b\mbx_{ssss}+(\sigma\mbx_s)_s)\cdot\mbn\right)ds &=0.
-%\end{align}
-%Applying integration by parts,
-%\begin{align}
-%     k_w\int_{\gamma}\left(\kappa_b\mbx_{sss}-\sigma\mbx_s\right)\cdot
-%     \mbn_s ds &=0.
-%\end{align}
-%From the Frenet-Serret formulas, we have 
-%\begin{align}
-%     -k_w\int_{\gamma}
-%     \left(\kappa_b\mbx_{sss}-\sigma\mbx_s\right)\cdot\kappa\mbx_s ds &=0.
-%\end{align}
-
-%Applying integration by parts and Frenet-Serret again
-%\begin{align}
-%     k_w\int_{\gamma}
-%     \kappa_b\kappa\left(\mbx_{ss}\cdot\mbx_{ss}\right)ds + k_w
-%     \int_{\gamma} \kappa_b \kappa_s(\mbx_{ss} \cdot \mbx_s)ds +k_w\int_{\gamma}\kappa\sigma ds  &= 0,\\
-%    k_w\int_{\gamma} \kappa_b\kappa(\kappa\mbn \cdot
-%     \kappa\mbn)+ k_w \int_{\gamma} \kappa_b \kappa_s(\mbx_{ss} \cdot
-%     \mbx_s)ds +k_w\int_{\gamma}\kappa\sigma ds &= 0,
-%\end{align}
-%which we re-write as
-%\begin{align}
-%   k_w\int_{\gamma}\kappa_b\kappa^3 ds + k_w \int_{\gamma} \kappa_b
-%   \kappa_s(\mbx_{ss} \cdot \mbx_s)ds +k_w\int_{\gamma} \kappa\sigma ds = 0.
-%\end{align}
-%Applying Frenet-serret again,
-%\begin{align}
-%    k_w\int_{\gamma}\kappa_b\kappa^3 ds + k_w \int_{\gamma} \kappa_b
-%    \kappa_s(\kappa\mbn \cdot \TT)ds +k_w\int_{\gamma} \kappa\sigma ds = 0, \\
-%    k_w\int_{\gamma}\kappa_b\kappa^3 ds +k_w\int_{\gamma} \kappa\sigma ds  = 0, 
-%\end{align}
-%we compare this to our numerical results.
-
+	\mbf_{\text{bending}} = -\kappa_b\mbx_{ssss}, &\\
+	%
+	\mbf_{\text{tension}} = (\sigma\mbx_s)_s. & 
+	\end{align} \label{eqn:bendten}
+\end{subequations}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \label{eqn:vesVelocity}
-  \dot{\mbx} &= \mbu_\infty(\mbx) + k_w
-  (RT\jump{c}+\mbf_\text{mem}\cdot\mbn)\mbn
-  + \SS [\mbf_\text{mem}],  \\
-  \mbx_s\cdot\dot{\mbx}_s &= 0 
+  \dot{\mbx} = \mbu_\infty(\mbx) + \beta
+  (RT\jump{c}+\mbf\cdot\mbn)\mbn
+  + \sgl [\mbf], & \\
+  \mbx_s\cdot\dot{\mbx}_s = 0 &
 \end{align}
-This satisfies all the jump conditions. As usual, $\SS$ is the single
+This satisfies all the jump conditions. As usual, $\sgl$ is the single
 layer potential.  We introduce the notation
@@
   \dot{\mbx} &= \mbu_{\infty}(\mbx) + 
-  k_wRT\jump{c}\mbn + k_wP(B\mbx + T\sigma) + \SS(B\mbx + T\sigma), \label{eq:full}\\
+  \beta RT\jump{c}\mbn + \beta P(B\mbx + T\sigma) + \sgl(B\mbx + T\sigma), \label{eq:full}\\
   D \dot{\mbx} &= 0.
@@
 Following the analysis of~\cite{vee-gue-zor-bir2009} and
-disregarding background flow, we define scales of $\mbx$, $t$, $k_w$,
+disregarding background flow, we define scales of $\mbx$, $t$, $\beta$,
 and $c$ to nondimensionalize equation (\ref{eq:full}) as follows. The
@@
 \begin{align}
-    \dot{\Tilde{\mbx}} =  \Tilde{k_w}\jump{\tilde{c}}\mbn +
-    \Tilde{k_w}P\big(B[\Tilde{\mbx}]\Tilde{\mbx}+T[\Tilde{\mbx}]\Tilde{\sigma}\big)
-    +\SS\big( B[\Tilde{\mbx}]\Tilde{\mbx} + T[\Tilde{\mbx}]\Tilde{\sigma}\big).
+    \dot{\Tilde{\mbx}} = \Tilde{\mbu}_{\infty} + \Tilde{\beta}\jump{\tilde{c}}\mbn +
+    \Tilde{\beta}P\big(B[\Tilde{\mbx}]\Tilde{\mbx}+T[\Tilde{\mbx}]\Tilde{\sigma}\big)
+    +\sgl\big( B[\Tilde{\mbx}]\Tilde{\mbx} + T[\Tilde{\mbx}]\Tilde{\sigma}\big).
 \end{align}
-In our current implementation, we let $\jump{c} = 0$.
+In our current implementation, we let $\jump{c} = 0$. The remaining equations are written in dimensionless form, unless stated otherwise, and for simplicity of notation we remove the tildes.
 
@@
 equation~\eqref{eqn:vesVelocity} is discretized with a semi-implicit
-time stepping method similar to our previous works.  First, we introduce
-the notation
-\begin{align}
-  B[\mbx]\mbf &= -\kappa_b\frac{d^4}{ds^4} \mbf, \\
-  T[\mbx]\sigma &= (\sigma \mbx_s)_s, \\
-  P[\mbx]\mbf &= (\mbf \cdot \mbn) \mbn, \\
-  D[\mbx]\mbf &= \mbx_s \cdot \mbf_s,
-\end{align}
+time stepping method similar to our previous works.  
 where $\mbn$ is the outward unit normal of the vesicle
@@
 \end{align}
+
+Analytically, we use the governing equations to write a differential equation for
+the area of the vesicle as a function of time. The area inside a single
+vesicle $\gamma$ parameterized with $\mbx$ is
+\begin{align}
+A(t) = \frac{1}{2}\int_{\gamma} (\mbx \cdot \mbn)\, ds = 
+\frac{1}{2}\int_{0}^{2\pi} \left(\mbx \cdot
+\pderiv{\mbx}{\theta}^\perp\right)
+\, d\theta.
+\end{align}
+Taking the time derivative of $A(t)$,
+\begin{align}
+\dot{A}(t) &= \frac{1}{2}\int_{0}^{2\pi} \left(\dot{\mbx} \cdot
+\pderiv{\mbx}{\theta}^{\perp} + 
+\mbx \cdot \pderiv{\dot{\mbx}}{\theta}^{\perp}\right) d\theta, \\
+%&= \frac{1}{2}
+%\int_{0}^{2\pi}(\dot{\mbx}\cdot\mbn)\left\|\pderiv{\mbx}{\theta}\right\|d\theta +
+%   \frac{1}{2}\int_{0}^{2\pi}
+%  \left(\mbx \cdot \pderiv{\dot{\mbx}}{\theta}^{\perp}\right)d\theta, \\
+%&= \frac{\beta}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds +
+%\frac{1}{2}\int_{0}^{2\pi}\left(\mbx \cdot \pderiv{}{t}\left(\mbn
+%\left\|\pderiv{\mbx}{\theta}\right\|\right)\right)d\theta, \\
+%&= \frac{\beta}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds + \frac{1}{2}
+%\int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds + \frac{1}{2}\int_{0}^{2\pi}
+%\frac{\mbx\cdot\mbn}{\left\|\pderiv{\mbx}{\theta}\right\|}
+%\left(\pderiv{\mbx}{\theta}\cdot
+%\pderiv{\dot{\mbx}}{\theta}\right)d\theta \\
+&= \frac{\beta}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds + \frac{1}{2}
+\int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds + \frac{1}{2}\int_{\gamma}
+(\mbx\cdot\mbn) (\mbx_s \cdot \dot{\mbx}_s)\, ds.
+\end{align}
+To satisfy the inextensibilty condition, $\mbx_s \cdot \dot{\mbx}_s = 0$, the time derivative of $A(t)$ is
+\begin{align}
+\dot{A}(t) &= \frac{\beta}{2}
+\int_{\gamma}\left(\mbf\cdot\mbn\right)ds
++ \frac{1}{2} \int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds.
+\end{align}
+%... 
+%\begin{align}
+%    \dot{A}(t) &= \frac{\beta}{2}
+%    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right) ds,
+%\end{align}
+which we re-write as
+\begin{align}
+\dot{A}(t) &= \frac{\beta}{2}
+\int_{\gamma}\left(\mbf\cdot\mbn\right)ds-\frac{1}{2}\int_{\gamma}\left(\mbx^{\perp}\cdot\dot{\mbx}_s\right) ds.
+\end{align}
+Applying integration by parts and re-writing,
+%\begin{align}
+%    \dot{A}(t) &= \frac{\beta}{2}
+%    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\mbx^{\perp}_s\cdot\dot{\mbx}\right) ds,
+%\end{align}
+%which we re-write as
+\begin{align}
+%   \dot{A}(t) &= \frac{\beta}{2}
+%   \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\dot{\mbx}\cdot\mbn\right),\\
+\dot{A}(t) &= \beta \int_{\gamma}\left(\mbf\cdot\mbn\right)ds.
+\end{align}
+At steady state,
+\begin{align}
+\dot{A}(t) &= \beta \int_{\gamma}\left(\mbf\cdot\mbn\right)ds =0.
+\end{align}
+Replacing $\mbf$ with its relation, applying integration by parts twice and using Frenet-serret formulas,  
+\begin{align}
+\beta\int_{\gamma}\kappa_b\kappa^3 ds +\beta\int_{\gamma} \kappa\sigma ds  = 0. 
+\end{align} 
+%We now replace $\mbf$ with its relation
+%\begin{align}
+%   \beta\int_{\gamma}
+%   \left((-\kappa_b\mbx_{ssss}+(\sigma\mbx_s)_s)\cdot\mbn\right)ds &=0.
+%\end{align}
+%Applying integration by parts,
+%\begin{align}
+%     \beta\int_{\gamma}\left(\kappa_b\mbx_{sss}-\sigma\mbx_s\right)\cdot
+%     \mbn_s ds &=0.
+%\end{align}
+%From the Frenet-Serret formulas, we have 
+%\begin{align}
+%     -\beta\int_{\gamma}
+%     \left(\kappa_b\mbx_{sss}-\sigma\mbx_s\right)\cdot\kappa\mbx_s ds &=0.
+%\end{align}
+
+%Applying integration by parts and Frenet-Serret again
+%\begin{align}
+%     \beta\int_{\gamma}
+%     \kappa_b\kappa\left(\mbx_{ss}\cdot\mbx_{ss}\right)ds + \beta
+%     \int_{\gamma} \kappa_b \kappa_s(\mbx_{ss} \cdot \mbx_s)ds +\beta\int_{\gamma}\kappa\sigma ds  &= 0,\\
+%    \beta\int_{\gamma} \kappa_b\kappa(\kappa\mbn \cdot
+%     \kappa\mbn)+ \beta \int_{\gamma} \kappa_b \kappa_s(\mbx_{ss} \cdot
+%     \mbx_s)ds +\beta\int_{\gamma}\kappa\sigma ds &= 0,
+%\end{align}
+%which we re-write as
+%\begin{align}
+%   \beta\int_{\gamma}\kappa_b\kappa^3 ds + \beta \int_{\gamma} \kappa_b
+%   \kappa_s(\mbx_{ss} \cdot \mbx_s)ds +\beta\int_{\gamma} \kappa\sigma ds = 0.
+%\end{align}
+%Applying Frenet-serret again,
+%\begin{align}
+%    \beta\int_{\gamma}\kappa_b\kappa^3 ds + \beta \int_{\gamma} \kappa_b
+%    \kappa_s(\kappa\mbn \cdot \TT)ds +\beta\int_{\gamma} \kappa\sigma ds = 0, \\
+%    \beta\int_{\gamma}\kappa_b\kappa^3 ds +\beta\int_{\gamma} \kappa\sigma ds  = 0, 
+%\end{align}
+%we compare this to our numerical results.
 

### 2019-10-03 vesicle_code/docs/softmatter/permeableVes.tex
soft matter TeX
starting literature review for semiperemable

@@
 
+\begin{itemize}
+  \item Yao and Mori~\cite{yao-mor2017} use an immersed boundary method
+    to simulate osmotic water flow and solute diffusion with a
+    deformable elastic membrane.
+
+  \item Anderson~\cite{and1983} seems to be the first to consider
+    semipermeable vesicles with an osmotic gradient. This work describes
+    the governing equations and does a non-dimensionalization. The
+    scaling behavior of the vesicle velocity with respect to the
+    concentration Peclet number is analyzed.
+
+  \item Gupta et al.~\cite{gup-sre-tha2015} consider diffusio-phoretic
+    motion of a deformable vesicle. The vesicle has a certain region
+    that is chemically active while the rest of the vesicle is
+    noncatalytic. A L-J model is used to describe the molecular motion
+    in the catalytic region and this generates self-propulsion.
+
+  \item Jayathilake et al.~\cite{jay-kho-tan2010} consider a permeable
+    capsule being adhered to a substrate. They use an immersed interface
+    method developed by Leveque and Li in 1994.
+
+  \item Jayathilake et al.~\cite{jay-tan-kho-wij2010} consider osmotic
+    swelling of a deformable elastic membrane. Again, they use an
+    immersed interface method. The formulation and methods are very
+    close to the work of Anita Layton~\cite{lay2006}.
+
+  \item In Jayathlake's Ph.D.~thesis~\cite{jay2010}, he states that a
+    BIE could be used, but it is not applicable for non-linear problems.
+    This is not an issue for us since we are interested in the linear
+    Stokes equations. Section 2.2.1 gives the model formulation
+    including the non-dimensionalization.
+
+  \item Layton~\cite{lay2006} simulates water transport across a
+    elastic water-permeable membrane. Instead of an immersed boundary
+    method, she uses a finite difference method and incorporates the
+    interface using the modified stencils developed my Anita
+    Mayo~\cite{may1984}.  The numerical methods are fairly standard.
+
+  \item Li, Mori, and Sun~\cite{li-mor-sun2015} study flow-driven cell
+    migration in electric fields.  The cell boundaries include water and
+    ionic fluxes.
+
+  \item Liu et al.~\cite{liu-chu-new-rea-low-all2019} consider the
+    physical contact between pairs of permeable membranes. This might be
+    useful when we consider suspensions of semi-permeable vesicles.
+    Model parameters, including the membrane permeability, are given in
+    Table 1. They use a stochastic immersed boundary method.
+
+  \item Nardi et al.~\cite{nar-bru-sac1999} describe how vesicles in a
+    concentration gradient are osmotic motors. This is an experimental
+    paper that shows a velocity that is much larger than what the theory
+    predicts.
+
+  \item Stockie~\cite{sto2009} considers flow through porous immersed
+    boundaries. The method uses an immersed boundary method and the flow
+    through the membrane flux is described with Darcy's law.
+
+\end{itemize}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 disregarding background flow, we define scales of $\mbx$, $t$, $\beta$,
-and $c$ to nondimensionalize equation (\ref{eq:full}) as follows. The
-length is scaled using the radius of a circle with the same perimeter,
-$L$, as the vesicle, $R_0 = \frac{L}{2\pi}$. From analysis, the time
+and $c$ to nondimensionalize equation (\ref{eq:full}) as follows. The length is scaled using the radius of a circle with the same perimeter,
+$L$, as the vesicle, $R_0 = \frac{L}{2\pi}$. The shear rate, $\chi$, is scaled by $\frac{\mu R_0^3}{\kappa_b}$ [REF] and $\Tilde{\mbu}_{\infty} = \Tilde{\chi}(\mbx_2,0)$. From analysis, the time
 scale $\tau$ is defined as $\tau = \frac{\mu R_0^2}{k_b}$, the tension

### 2019-10-04 vesicle_code/docs/softmatter/permeableVes.tex
added new references

@@
     through the membrane flux is described with Darcy's law.
+
+  \item Loitto et al.~\cite{loi-kar-mag2009} give a review article
+    concerning the water flux and its effects on cell motility and
+    membrane protrusion. They discuss the role of aquaporins.
+
+  \item In~\cite{tha-kum-mad-pul2006}, they show experimental results of
+    self-driven drops. They also compare the experiment with numerical
+    results.
+
+  \item Khair~\cite{kha2013} models and simulates diffusiophoresis at a
+    variety of Peclet numbers. In Section 5, he provides estimates for
+    the self-driven velocity of a non-spherical colloid at finite Peclet
+    number.
+
+  \item Keh and Tu~\cite{keh-tu2000} consider osmophoresis of one and
+    two spherical vesicles.  Two vesicles are simulated using the method
+    of reflections. They consider the zero Peclet number limit which is
+    the limit Ashley and Bryan plan to simulate in the next paper.
+    However, they assume the vesicle is nearly spherical so that
+    standard basis functions can be used. Using a BIE would still be
+    new.
 

### 2019-10-04 vesicle_code/examples/output/makeImages.m

@@ -2,7 +2,7 @@ addpath ../../src
 set(0,'DefaultAxesFontSize',22)
 options.savefig = false;
 
-irate = 5; % controls the speed of the visualization
+irate = 20; % controls the speed of the visualization
 
 if 0
   file = 'parabolic1VesData.bin';
@@ -57,8 +57,9 @@ if 0
 end
 if 1
 %  file = '~/projects/brinkman/vesicle_code/results/May092019/shear1Ves/kappa1em1_beta1ep0_chi1ep0_ra0p55/shear1VesData.bin';
-  file = 'shear1VesData.bin';
-  ax = [-5 5 -5 5];
+%  file = 'shear1VesData.bin';
+  file = '~/projects/brinkman/vesicle_code/results/semipermeable/shear1VesData_fluxCoeff2_fluxShape3_fluxWidth1.bin';
+  ax = [-5 55 -5 5];
   options.confined = false;
 end
 if 0
@@ -121,7 +122,7 @@ for k = istart:irate:iend
     end
     hold off
     axis equal
-%    axis(ax)
+    axis(ax)
     titleStr = ['t = ' num2str(time(k),'%4.2e') ...
       ' eA = ' num2str(ea(k),'%4.2e') ...
       ' eL = ' num2str(el(k),'%4.2e')];

### 2020-02-10 vesicle_code/docs/permeableVes/main.tex
starting rebuttal forms for adhesion paper
worked on Figure 12 (left)
commenting shuwang code

@@
 The jump condition for the hydrodynamic stress remains the same:
-%
-%Then, define
-%\beq \mbf_i = \lim_{\mbx \rightarrow \gamma^-} \sigma (\mbx)\cdot\mbn,  \eeq
-%\beq \mbf_e =  \lim_{\mbx \rightarrow \gamma^+} \sigma (\mbx)\cdot\mbn, \eeq
-%\beq \jump{\mbv\cdot \mbt} = 0 \eeq
-%\beq \jump{\mbv\cdot\mbn} = \beta (\mbf_i + \mbf_e)\cdot\mbn \eeq
 \beq \jump{\Sigma\cdot\mbn} = \mbf_\text{mem}, \eeq
@@
 Here, $\beta$ is a constant and the membrane force is the usual tension + bending.
+
+%%%%%%%%%%%%%%
+\section{{$\Theta-L$} formulation}
+Here, we attempt to apply the formulation described by Sohn et
+al.~\cite{soh-tse-li-voi-low2010} to a semi-permeable vesicle.  In the
+semi-permeable formulation, the vesicle velocity is
+\begin{align}
+  \pderiv{\XX}{t} = \mbu(\XX(t)) + \beta (\mbf \cdot \mbn) \mbn.
+\end{align}
+In the {$\Theta-L$} variables, we require a normal velocity $V$, and a
+tangential velocity $T$. Since the inextensibility condition is $T_s +
+\kappa V = 0$, a condition for the vesicle velocity is
+\begin{align}
+  (\mbu \cdot \mbs)_s = -\kappa(\beta (\mbf \cdot \mbn) + 
+      \mbu \cdot \mbn).
+\end{align}
+This equation can be solved following equations (32)--(39)
+in~\cite{soh-tse-li-voi-low2010}, with the only difference being that
+$\tilde{\mbu}$ satisfies
+\begin{align}
+  (\tilde{\mbu} \cdot \mbs)_s + \kappa(\tilde{\mbu} \cdot \mbn) =
+    -(\mbv \cdot \mbs)_s - \kappa(\mbv \cdot \mbn) 
+    - \beta\kappa(\mbf \cdot \mbn).
+\end{align}
+Compared to equation (40), only the last term is new.
 
@@
 \end{align}
-where $\mbn$ is the outward unit normal of the vesicle parameterized by
-$\mbx$, and $d/ds$ is its arclength derivative.  Dropping the dependence
-of the operators on $\mbx$, the dynamics of the vesicle are governed by
+where $\mbn$ is the outward unit normal of the vesicle
+parameterized by $\mbx$, and $d/ds$ is its arclength derivative.
+Dropping the dependence of the operators on $\mbx$, the dynamics of the
+vesicle are governed by
 \begin{align}
@@
   \right).
+\end{align}
+
+\section{Area of a Vesicle}
+The area inside a single vesicle $\gamma$ parameterized with $\mbx$ is
+\begin{align}
+  A(t) = \int_{\gamma} (\mbx \cdot \mbn)\, ds = 
+    \int_{0}^{2\pi} \left(\mbx \cdot \pderiv{\mbx}{\theta}^\perp\right)
+    \, d\theta.
+\end{align}
+Taking the time derivative of $A(t)$,
+\begin{align}
+  \dot{A}(t) &= \int_{0}^{2\pi} \left(
+    \dot{\mbx} \cdot \pderiv{\mbx}{\theta}^{\perp} + 
+    \mbx \cdot \pderiv{\dot{\mbx}}{\theta}^{\perp}\right) \\
+    \, d\theta.
+  &= \int_{0}^{2\pi} \left(
+    (\dot{\mbx} \cdot \mbn)\|\mbx'(\theta)\| \right) d\theta +
+     \int_{0}^{2\pi}
+    \mbx \cdot \frac{d}{dt}\left(\mbn |\frac{d\mbx}{d\theta}| \right)
 \end{align}

### 2020-02-10 vesicle_code/docs/softmatter/permeableVes.tex
commenting shuwang code

@@
 \input my_macros2.tex	
+\usepackage{todonotes}
 \begin{document}
@@
 
-\subsection{Content permeability rate}
+\subsection{Relaxation flow}
+We start by considering a single semi-permeable vesicle suspended in a
+quiescent Stokes flow. In Figure~\ref{fig:relaxationSnapshots}, we plot
+the vesicle configuration at \todo{some number} times. We observe that
+the vesicle inflates towards a circular shape.
+
+\begin{figure}[htp]
+%  \includegrahpics[width=0.3\textwidth]{figures/relaxationTime1.pdf}
+%  \includegrahpics[width=0.3\textwidth]{figures/relaxationTime2.pdf}
+%  \includegrahpics[width=0.3\textwidth]{figures/relaxationTime3.pdf}
+  \caption{\label{fig:relaxationSnapshots} Snapshots of a single vesicle
+  in a relaxation flow. The color on the vesicle is the fluid flux.
+  Since the flux is always positive/negative, the vesicle inflates to a
+  circle.}
+\end{figure}
+
+We next investigate the effect of
 

### 2020-02-10 shuwang_code/fdiff.m

@@ -1,4 +1,5 @@
 function x = fdiff(a,n)
+% fourier differentiation
 
 y = a;
 y(1,n+1) = y(1,1);

### 2020-02-10 shuwang_code/integral3.m

@@ -1,4 +1,5 @@
 % integral of log|sin|: L
+% See first term in equation (43)
 function vel = integral3(sigma,m)
 
 % make sure velocity is zero initially

### 2020-02-10 shuwang_code/selfmatrix.m

@@ -1,23 +1,35 @@
 function  A = selfmatrix(s,kmatrix)
 
 N = numel(s.x); 
-M = numel(s.x);
-r = repmat(s.x,[1 N]) - repmat(s.x.',[M 1]) + diag(ones(1,N));
-% C-# displacements mat
+r = repmat(s.x,[1 N]) - repmat(s.x.',[N 1]) + diag(ones(1,N));
+% target minus source for the single-layer potential, but putting ones
+% on the main diagonal. x-coordinate is in the real part and
+% y-coordinate is in the imaginary part
 
 rt = repmat([1:N]'*pi/N , [1 N]) - ...
-     repmat([1:N]*pi/N, [M 1]) + diag(ones(1,N));
+     repmat([1:N]*pi/N, [N 1]) + diag(ones(1,N));
+% only going from 0 to pi to account for the divided by 2 in the
+% argument of sin in equation (43). ie. rt is (alpha - alpha')/2 in
+% equation (43) where alpha and alpha' go from 0 to 2*pi. Again, putting
+% ones in the diagonal instead the natural limit which is 0
 
 denom = abs(sin(rt));
+% denominator of equation (43)
 
 irr = 1./(conj(r).*r);    % 1/r^2
-d1 = real(r);
-d2 = imag(r);
+d1 = real(r); % x-coordinate of r
+d2 = imag(r); % y-coordinate of r
 Ilogr = -log(abs(r)./denom);  % log(1/r) diag block
+% Putting ones in the diagonal of r and denom results in taking log of
+% something non-zero. Not clear how (or if) they use the true limiting
+% term of this smooth kernel which is log(abs(r))
 
 A12 = d1.*d2.*irr;   % off diag vel block
 A = [(Ilogr + d1.^2.*irr), A12;...
      A12, (Ilogr + d2.^2.*irr)]; 
+% d1^2.*irr is the r1^2/r^2 in equation (6)
+% d2^2.*irr is the r2^2/r^2 in equation (7)
+% d1.*d2.*irr is the r1*r2/r^2 in equations (6) and (7)
 
 A=A.*kmatrix;
 

### 2020-02-10 vesicle_code/examples/relaxation1Ves.m

@@ -1,11 +1,16 @@
-function[Xfinal] = relaxation1Ves(beta, m, betas, ms)
+%function[Xfinal] = relaxation1Ves(beta, m, betas, ms)
 fprintf('Simple elliptical vesicle in a relaxation flow.\n');
 fprintf('First-order semi-implicit time stepping.\n');
 
+beta = 1;
+m = 100;
+ms = m;
+betas = beta;
+
 % Physics parameters
-prams.N = 128;               % points per vesicle
+prams.N = 128*4;               % points per vesicle
 prams.nv = 1;               % number of vesicles
-prams.T = 1e-2;               % time horizon (two tumbling)
+prams.T = 1;               % time horizon (two tumbling)
 prams.m = m;              % number of time steps
 prams.kappa = ones(prams.nv,1); % bending coefficient
 prams.viscCont = ones(prams.nv,1);         % viscosity contrast
@@ -19,12 +24,12 @@ options.near = true;        % near-singular integration
 options.fmm = false;
 options.antiAlias = false;
 options.semipermeable = true;
-options.adhesion = true;
+options.adhesion = false;
 defaultPram.adStrength = 1;
 defaultPram.adRange = 4e-1;
 prams.gmresMaxIter = 3*prams.N;
 prams.gmresTol = 1e-10;
-prams.errortol = 1000;
+prams.errorTol = 1000;
 prams.fluxCoeff = beta*ones(prams.nv,1);
 
 % ADD-ONS
@@ -54,17 +59,21 @@ options.expForce = false;
 
 % Plot on-the-fly
 options.usePlot = true;
-options.axis = [-10 10 -10 10];
+options.axis = [-3 3 -4 4];
 options.track = false;
 % Save vesicle information and create a log file
-options.logFile = sprintf('%s','output/nsdc1_relaxation2Ves',ms,'_',betas,'.log');
+%options.logFile = sprintf('%s','output/nsdc1_relaxation2Ves',ms,'_',betas,'.log');
+options.logFile = 'output/relaxation1Ves.log';
 % Name of log file for saving messages
-options.dataFile = sprintf('%s','output/nsdc1_relaxation2Ves',ms,'_',betas,'.bin');
+%options.dataFile = sprintf('%s','output/nsdc1_relaxation2Ves',ms,'_',betas,'.bin');
+options.dataFile = 'output/relaxation1VesData.bin';
[…]

### 2020-02-20 vesicle_code/examples/output/makeImagesSemiPermeable.m
finished commenting the initilization routines

@@ -2,16 +2,20 @@ addpath ../../src
 set(0,'DefaultAxesFontSize',22)
 options.savefig = false;
 
-irate = 1; % controls the speed of the visualization
+irate = 10000; % controls the speed of the visualization
 %file = 'relaxation1VesData.bin';
-file = 'shear1VesData.bin.20';
+%file = 'shear1VesData.bin';
 %file = 'extensional1VesData.bin';
 %file = '~/projects/brinkman/vesicle_code/results/semipermeable/shear1VesData_fluxCoeff1_fluxShape3_fluxWidth4.bin';
 %file = '~/projects/brinkman/vesicle_code/examples/output/shear1VesData.bin';
+file = '~/projects/brinkman/vesicle_code/results/shear1Ves/Chi1p0e0_ra065_beta1p0e0/shear1VesData.bin';
+chi = 5.0; beta = 1.0;
 
 [posx,posy,sigma,wallx,wally,ea,el,time,n,nv] = loadFile(file);
 % load positions, "tension", stresses, errors, time, number of points, and
 % number of vesicles
+
+op = poten(n);
 
 xmin = min(min(posx));
 xmax = max(max(posx));
@@ -30,16 +34,55 @@ oc = curve;
 tension = zeros(n,ntime);
 trac = zeros(2*n,ntime);
 normal = zeros(2*n,ntime);
+vel = zeros(2*n,ntime);
 cur = zeros(n,ntime);
 jac = zeros(n,ntime);
-for k = 1:numel(time)
+flux = zeros(n,ntime);
+normal_trac = zeros(n,ntime);
+IA = zeros(ntime,1); % inclination angle
+for k = 1:iend
+  [ra(k),area(k)] = oc.geomProp([posx(:,:,k);posy(:,:,k)]);
   ves = capsules([posx(:,:,k);posy(:,:,k)],sigma(:,k),[],1,1);
   trac(:,k) = ves.tracJump([posx(:,:,k);posy(:,:,k)],sigma(:,k));
 
   [jac(:,k),tang,cur(:,k)] = oc.diffProp([posx(:,1,k);posy(:,1,k)]);
   normal(:,k) = [tang(end/2+1:end);-tang(1:end/2)];
[…]

### 2020-02-20 vesicle_code/examples/relaxation1Ves.m

@@ -8,9 +8,9 @@ ms = m;
 betas = beta;
 
 % Physics parameters
-prams.N = 128*4;               % points per vesicle
+prams.N = 128;               % points per vesicle
 prams.nv = 1;               % number of vesicles
-prams.T = 1;               % time horizon (two tumbling)
+prams.T = 10;               % time horizon (two tumbling)
 prams.m = m;              % number of time steps
 prams.kappa = ones(prams.nv,1); % bending coefficient
 prams.viscCont = ones(prams.nv,1);         % viscosity contrast

### 2020-02-21 vesicle_code/docs/permeableVes/main.tex
finished commenting the initilization routines
started to map out paper a bit better

@@
 \usepackage{graphicx,epsfig}
-%\input vs_macros.tex
+\usepackage{todonotes}
 %Dfig puts a figure of specified size at the place indicated.
@@
 \title{Semi-permeable vesicles: mathematical formulation, numerics and physics}
-\author{}
+\author{Ashley Gannon, Bryan Quaife, Shravan Veerapaneni, and Yuan-Nan Young}
 
@@
 \begin{abstract}
-We describe a mathematical model for a semi-permeable vesicle and derive a boundary integral equation formulation for simulating its hydrodynamics.  
+We describe a mathematical model for a semi-permeable vesicle and derive
+  a boundary integral equation formulation for simulating its
+  hydrodynamics.  
 \end{abstract}
@@
 \section{Problem formulation} \label{sc:formulate}
-Consider a semi-permeable vesicle suspended in an unbounded viscous
-fluid domain, subjected to an imposed flow $\mbu_\infty(\mbx)$, for any
-$\mbx \in \RR^2$.
-Assume that the interior and exterior fluids have the same viscosity $\mu$.
-Let $\mbx$ be the position of the interface $\gamma$, $\mbu$ the fluid velocity and $p$ the pressure.
-In the vanishing Reynolds number limit, the governing equations for the ambient fluid can be written as:
+Consider a two-dimensional semi-permeable vesicle suspended in an
+unbounded viscous fluid domain, subjected to an imposed flow
+$\mbu_\infty(\mbx)$, for any $\mbx \in \RR^2$.  Assume that the interior
+and exterior fluids have the same viscosity $\mu$. Let $\mbx$ be the
+position of the interface $\gamma$, $\mbu$ be the fluid velocity, and
+$p$ be the pressure. In the vanishing Reynolds number limit, the
+governing equations for the ambient fluid are
 %
 \begin{subequations}
-\begin{align}
--\nabla p + \mu \triangle \mbu = 0 \quad\text{in}\quad
-  \RR^2\setminus\gamma  &  \\
+\begin{alignat}{3}
+  \label{eqn:governing}
+  -\nabla p + \mu \triangle \mbu &= 0, 
+  &&\mbx \in \RR^2 \setminus \gamma, \\
 % 
-\nabla \cdot \mbu = 0  \quad\text{in}\quad \RR^2\setminus\gamma &\\
+  \nabla \cdot \mbu &= 0,  &&\mbx \in \RR^2 \setminus \gamma, \\
 %
-\mbu(\mbx) \rightarrow \mbu_\infty(\mbx) \quad \text{as} \quad  \norm{\mbx} \rightarrow \infty & 
- \end{align} \label{eqn:governing}
+  \mbu(\mbx) &\rightarrow \mbu_\infty(\mbx),
+    \qquad &&\norm{\mbx} \rightarrow \infty.
+\end{alignat}
 \end{subequations}%
 %
-The modified jump conditions in the case of a semi-permeable vesicle can be summarized as follows.
-Let $\mbn$ the outward normal to $\gamma$ and $\jump{\cdot}$ denote the jump across the interface.
-The jump condition for the hydrodynamic stress remains the same:
-\beq \jump{\Sigma\cdot\mbn} = \mbf_\text{mem}, \eeq
-where $\Sigma$ is the hydrodynamic stress tensor. The fluid velocity is continuous across the membrane i.e.,
-\beq \jump{\mbu} = 0. \eeq
-However, the kinematic condition is modified to account for the fact that the fluid can move through the membrane. A standard choice appears to be
-%
-\beq \mbu - \dot{\mbx} = - \beta (\mbf_\text{mem} \cdot \mbn) \mbn \quad\text{on}\quad\gamma. \eeq
-%
-Here, $\beta$ is a constant and the membrane force is the usual tension + bending.
+Letting $\mbn$ be the outward normal to $\gamma$, $\jump{\cdot}$ denote
+the jump across the interface, and $T$ denote the hydrodynamic stress
+tensor, the boundary conditions along the vesicle are
+\begin{align}
+  \label{eqn:jump1}
+  \jump{T\cdot\mbn} &= \mbf_\text{mem}, \\
+  \label{eqn:jump2}
+  \jump{\mbu} &= 0,
+\end{align}
+where $\mbf_\text{mem}$ is the standard membrane force that includes a
+bending and a tension term. In particular, $\mbf_\text{mem} =
+\mbf_\text{ben} + \mbf_\text{ten}$, where
+\begin{align}
+  \label{eqn:membraneForces}
+  \mbf_\text{ben} = -\kappa_b \mbx_{ssss}, \qquad
+  \mbf_\text{ten} = (\sigma \mbx_s)_s,
+\end{align}
+where $\kappa_b$ is the bending stiffness and $\sigma$ is a Lagrange
+multiplier, which acts like the tension, which is used to satisfy the
+inextensibility condition.
+
+The kinematic condition is modified to account for the fact that the
+fluid can move through the membrane. A standard choice appears
+is~\cite{}
+\begin{align}
+  \mbu - \dot{\mbx} = - \beta (\mbf_\text{mem} \cdot \mbn) \mbn, \qquad
+  \mbx \in \gamma,
+\end{align}
+where $\beta$ is a semi-permeability rate.
+
+\subsection{Integral equation formulation}
+Since the flow is governed by the linear Stokes equations, it can be
+represented in terms of layer potentials. Given the boundary
+conditions~\eqref{eqn:jump1} and~\eqref{eqn:jump2} required on the
+interface, the fluid velocity can be represented as the single-layer
+potential
+\begin{align}
+  \mbu(\mbx) = \mbu_\infty(\mbx) + \sgl[\mbf_\text{mem}](\mbx), \quad
+    \mbx \in \Omega,
+\end{align}
+where
+\begin{align}
+  \sgl[\mbf](\mbx) = \frac{1}{4\pi\mu} \int_{\gamma} \left(
+    -\mathbf{I} \log\rho + \frac{\mbr \otimes \mbr}{\rho^2} \right)
+    \mbf(\mby) ds_{\mby},
+\end{align}
+where $\mbr = \mbx - \mby$ and $\rho = \norm{\mbr}$. Then, by the
+kinematic equation, the dynamics of the vesicle 
+\begin{align}
+  \label{eqn:vesVelocity}
+  \frac{d\mbx}{dt} = \mbu_\infty(\mbx) + \beta (\mbf_\text{mem}\cdot\mbn)\mbn
+  + \sgl [\mbf_\text{mem}](\mbx).
+\end{align}
+Finally, the inextensibility condition is given by
+\begin{align}
+  \mbx_s\cdot\dot{\mbx}_s = 0.
+\end{align}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Vesicle Area}
+Since the vesicle membrane is semi-permeable, the vesicle's area
+fluctuates.  Parameterizing the vesicle with $\mbx$, its area is
+\begin{align}
+  A(t) = \frac{1}{2}\int_{\gamma} (\mbx \cdot \mbn)\, ds = 
+    \frac{1}{2}\int_{0}^{2\pi} \left(\mbx \cdot \pderiv{\mbx}{\theta}^\perp\right)
+    \, d\theta.
+\end{align}
+
+\todo[inline]{Can do this part of the calculation using FTC}
+Taking the time derivative of $A(t)$,
+\begin{align}
+  \dot{A}(t) &= \frac{1}{2}\int_{0}^{2\pi} \left(\dot{\mbx} \cdot
+  \pderiv{\mbx}{\theta}^{\perp} + 
+    \mbx \cdot \pderiv{\dot{\mbx}}{\theta}^{\perp}\right) d\theta, \\
+  &= \frac{1}{2}
+  \int_{0}^{2\pi}(\dot{\mbx}\cdot\mbn)\left\|\pderiv{\mbx}{\theta}\right\|d\theta +
+     \frac{1}{2}\int_{0}^{2\pi}
+    \left(\mbx \cdot \pderiv{\dot{\mbx}}{\theta}^{\perp}\right)d\theta, \\
+  &= \frac{\beta}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds +
+  \frac{1}{2}\int_{0}^{2\pi}\left(\mbx \cdot \pderiv{}{t}\left(\mbn
+  \left\|\pderiv{\mbx}{\theta}\right\|\right)\right)d\theta, \\
+  &= \frac{\beta}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds + \frac{1}{2}
+  \int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds + \frac{1}{2}\int_{0}^{2\pi}
+  \frac{\mbx\cdot\mbn}{\left\|\pderiv{\mbx}{\theta}\right\|}
+  \left(\pderiv{\mbx}{\theta}\cdot
+  \pderiv{\dot{\mbx}}{\theta}\right)d\theta \\
+  &= \frac{\beta}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds + \frac{1}{2}
+  \int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds + \frac{1}{2}\int_{\gamma}
+  (\mbx\cdot\mbn) (\mbx_s \cdot \dot{\mbx}_s)\, ds.
+\end{align}
+To satisfy the inextensibilty condition, $\mbx_s \cdot \dot{\mbx}_s = 0$.
+Therefore the time derivative of $A(t)$ is
+\begin{align}
+     \dot{A}(t) &= \frac{\beta}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds
+     + \frac{1}{2} \int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds.
+\end{align}
+which we re-write as
+\begin{align}
+    \dot{A}(t) &= \frac{\beta}{2}
+    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds-\frac{1}{2}\int_{\gamma}\left(\mbx^{\perp}\cdot\dot{\mbx}_s\right) ds.
+\end{align}
+Applying integration by parts,
+\begin{align}
+    \dot{A}(t) &= \frac{\beta}{2}
+    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\mbx^{\perp}_s\cdot\dot{\mbx}\right) ds,
+\end{align}
+which we re-write as
+\begin{align}
+    \dot{A}(t) &= \frac{\beta}{2}
+    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\dot{\mbx}\cdot\mbn\right),\\
+    \dot{A}(t) &= \beta \int_{\gamma}\left(\mbf\cdot\mbn\right)ds.
+\end{align}
+At steady state,
+\begin{align}
+    \dot{A}(t) &= \beta \int_{\gamma}\left(\mbf\cdot\mbn\right)ds =0.
+\end{align}
+We now replace $\mbf$ with its definition and apply integration by parts
+\begin{align}
+   0=\beta\int_{\gamma} 
+    (-\kappa_b\mbx_{ssss}+(\sigma\mbx_s)_s)\cdot\mbn\, ds =
+   \beta\int_{\gamma}\left(\kappa_b\mbx_{sss}-\sigma\mbx_s\right)\cdot
+     \mbn_s\, ds
+\end{align}
+From the Frenet-Serret formulas, we have 
+\begin{align}
+     -\beta\int_{\gamma}
+     \left(\kappa_b\mbx_{sss}-\sigma\mbx_s\right)\cdot\kappa\mbx_s ds &=0.
+\end{align}
+
+Applying integration by parts and Frenet-Serret again
+\begin{align}
+     \beta\int_{\gamma}
+     \kappa_b\kappa\left(\mbx_{ss}\cdot\mbx_{ss}\right)ds + \beta
+     \int_{\gamma} \kappa_b \kappa_s(\mbx_{ss} \cdot \mbx_s)ds +\beta\int_{\gamma}\kappa\sigma ds  &= 0,\\
+    \beta\int_{\gamma} \kappa_b\kappa(\kappa\mbn \cdot
+     \kappa\mbn)+ \beta \int_{\gamma} \kappa_b \kappa_s(\mbx_{ss} \cdot
+     \mbx_s)ds +\beta\int_{\gamma}\kappa\sigma ds &= 0,
+\end{align}
+which we re-write as
+\begin{align}
+   \beta\int_{\gamma}\kappa_b\kappa^3 ds + \beta \int_{\gamma} \kappa_b
+   \kappa_s(\mbx_{ss} \cdot \mbx_s)ds +\beta\int_{\gamma} \kappa\sigma ds = 0.
+\end{align}
+Applying Frenet-serret again,
+\begin{align}
+    \beta\int_{\gamma}\kappa_b\kappa^3 ds + \beta \int_{\gamma} \kappa_b
+    \kappa_s(\kappa\mbn \cdot \TT)ds +\beta\int_{\gamma} \kappa\sigma ds = 0, \\
+    \beta\int_{\gamma}\kappa_b\kappa^3 ds +\beta\int_{\gamma} \kappa\sigma ds  = 0.
+\end{align}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Numerical Methods}
+\subsection{Discretization in Space}
+
+\subsection{Discretization in Time}
+By using an integral equation formulation, the only unknowns are the
+vesicle position and tension, and the flow in the bulk does not have to
+be computed. However, the high-order derivatives in the bending and
+tension forces~\eqref{eqn:membraneForces} result in stiffness if an
+explicit time stepping method is applied to
+equation~\eqref{eqn:vesVelocity}. We apply a similar semi-implicit time
+stepping method to our previous works~\cite{vee-gue-zor-bir2009,
+qua-bir2014}. First, given a vesicle $\gamma$, with a boundary
+parameterized as $\mbx(s)$, we introduce notation for all the required
+differential and projection operators
+\begin{align}
+  B[\mbx]\mbf &= -\frac{d^4}{ds^4} \mbf, \\
+  T[\mbx]\sigma &= (\sigma \mbx_s)_s, \\
+  D[\mbx]\mbf &= \mbx_s \cdot \mbf_s, \\
+  P[\mbx]\mbf &= (\mbf \cdot \mbn) \mbn. 
+\end{align}
+Here, the normal vector $\mbn$ is the outward unit normal of the
+$\gamma$, and $d/ds$ is its arclength derivative. To simplify notation,
+we write $B\mbf$ to mean $B[\mbx]\mbf$, and use similar notation for the
+other operators. Then, the dynamics of the vesicle are governed by
+\begin{align}
+  \frac{d\mbx}{dt} &= \mbu_{\infty}(\mbx) + 
+  \beta P(B\mbx + T\sigma) + \sgl(B\mbx + T\sigma), \\
+  D \frac{d\mbx}{dt} &= 0.
+\end{align}
+By writing $B^N$ to mean the bending operator due to the vesicle
+configuration at time $t_N$, and similar notation for the other
+operators, we address the stiffness by introducing the semi-implicit
+time stepping method
+\begin{align}  
+  \frac{\mbx^{N+1} - \mbx^N}{\Delta t} = \mbu_\infty(\mbx^N) 
+  + \beta P^N\left(B^N\mbx^{N+1} + T^N\sigma^{N+1}\right) 
+  + \sgl^N\left(B^N\mbx^{N+1} + T^N\sigma^{N+1}\right).
+\end{align}
+Finally, the inextensibility condition is applied by requiring that 
+\begin{align}
+  D^N\mbx^{N+1} = 1.
+\end{align}
+
+\todo[inline]{A few lines about SDC}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Examples}
+We consider a single semi-permeable vesicle in four different flow
+regimes.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Quiescent Flow}
+\begin{itemize}
+  \item Always goes to a circle
+  \item Area formula works
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Shear Flow}
+\begin{itemize}
+  \item Never goes to a circle
+  \item Area formula works
+  \item Mild dependence on initial shape
+  \item Most slender tank treading shapes seen for small $\beta$ and
+    large $\chi$
+\end{itemize}
+
+%\input{figures/shearPhaseDiagram.tikz}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Extensional Flow}
+\begin{itemize}
+  \item ???
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Poiseuille Flow}
+\begin{itemize}
+  \item ???
+\end{itemize}
+
+ \bibliographystyle{plain}
+ \bibliography{refs}
+
+ \newpage
+ \paragraph{\bf \Huge OLD STUFF}
 
@@
 
-\section{Integral equation formulation}
-There are multiple ways to convert the PDE problem into integral
-equations. Based on my derivation, the coupled set of
-integro-differential equations satisfy the given interfacial conditions:
-\beq 
-  \dot{\mbx} = \mbu_\infty(\mbx) + \beta (\mbf_\text{mem}\cdot\mbn)\mbn + \sgl [\mbf_\text{mem}], 
-  \label{eqn:vesVelocity}
-\eeq
-\beq 
-  \mbx_s\cdot\dot{\mbx}_s = 0 
-\eeq
-This satisfies all the jump conditions. As usual, $\sgl$ is the single layer potential.
-
-\section{Numerics}
-To address stiffness associated with high-order derivatives,
-equation~\eqref{eqn:vesVelocity} is discretized with a semi-implicit
-time stepping method similar to our previous works.  First, we introduce
-the notation
-\begin{align}
-  B[\mbx]\mbf &= -\kappa_b\frac{d^4}{ds^4} \mbf, \\
-  T[\mbx]\sigma &= (\sigma \mbx_s)_s, \\
-  P[\mbx]\mbf &= (\mbf \cdot \mbn) \mbn, \\
-  D[\mbx]\mbf &= \mbx_s \cdot \mbf_s,
-\end{align}
-where $\mbn$ is the outward unit normal of the vesicle
-parameterized by $\mbx$, and $d/ds$ is its arclength derivative.
-Dropping the dependence of the operators on $\mbx$, the dynamics of the
-vesicle are governed by
-\begin{align}
-  \dot{\mbx} &= \mbu_{\infty}(\mbx) + 
-  \beta P(B\mbx + T\sigma) + \sgl(B\mbx + T\sigma), \\
-  D \dot{\mbx} &= 0.
-\end{align}
-Using the notation $B^N$ to denote the bending operator due to the
-vesicle configuration at time $t_N$, and similar notation for the other
-operators, we apply the semi-implicit time stepping method
-\begin{align}  
-  \frac{\mbx^{N+1} - \mbx^N}{\Delta t} = \mbu_\infty(\mbx^N) 
-  + \beta P^N(B^N\mbx^{N+1} + T^N\sigma^{N+1}) 
-  + \sgl^N(B^N\mbx^{N+1} + T^N\sigma^{N+1}).
-\end{align}
-Applying $D$ to the first-order time discretization of
-equation~\eqref{eqn:vesVelocity}, the inextensibility condition is
-\begin{align*}
-  &D^N(\mbx^{N+1} - \mbx^N) = 0 \\ 
-  \Rightarrow &D^N\mbx^{N+1} = D^N \mbx^N \\ 
-  \Rightarrow &D^N\mbx^{N+1} = 1.
-\end{align*}
+%%%%%%%%%%%%%%
 Finally, we write the time stepping method in matrix form as
@@
 
- \bibliographystyle{plain}
- \bibliography{refs}
-
 \end{document}

### 2020-02-21 vesicle_code/examples/output/makeImagesSemiPermeable.m

@@ -8,7 +8,7 @@ irate = 10000; % controls the speed of the visualization
 %file = 'extensional1VesData.bin';
 %file = '~/projects/brinkman/vesicle_code/results/semipermeable/shear1VesData_fluxCoeff1_fluxShape3_fluxWidth4.bin';
 %file = '~/projects/brinkman/vesicle_code/examples/output/shear1VesData.bin';
-file = '~/projects/brinkman/vesicle_code/results/shear1Ves/Chi1p0e0_ra065_beta1p0e0/shear1VesData.bin';
+file = '~/projects/brinkman/vesicle_code/results/shear1Ves/Chi9p6e0_ra065_beta2p0e0/shear1VesData.bin';
 chi = 5.0; beta = 1.0;
 
 [posx,posy,sigma,wallx,wally,ea,el,time,n,nv] = loadFile(file);

### 2020-02-25 vesicle_code/docs/permeableVes/main.tex
small changes

@@
 \subsection{Discretization in Space}
+We apply a collocation method where the vesicle is discretized at $N$
+points. We need to compute derivatives of functions defined on the
+vesicle boundary, and these are done with Fourier differentiation.
+Finally, to compute the single-layer potential, we use an eight-order
+Alpert quadrature rule~\cite{alp1999} which resolves the logarithmic
+singularity of the integrand.
 

### 2020-02-25 shuwang_code/frconim.m

@@ -23,15 +23,15 @@ rcons = fd1(termd,m);
 rconss = fd1(rcons,m);
 
 betarcon = 1;
-fcon(1,1:m) = betarcon*rconss(1,1:m)/sl^2;
-fcon(1,m+1) = fcon(1,1);
+fcon(1:m) = betarcon*rconss(1:m)/sl^2;
+fcon(m+1) = fcon(1);
 
 % now we must subtract off the stiffest part in Fourier space.
-temp(1,1:m) = fcon(1,1:m);
-tempt(1,1:m) = rcon(1,1:m);
+temp(1:m) = fcon(1:m);
+tempt(1:m) = rcon(1:m);
 
-temp(1,m+1) = temp(1,1);
-tempt(1,m+1) = tempt(1,1);
+temp = [temp temp(1)];
+tempt = [tempt tempt(1)];
 temp = fft(temp,m);
 tempt = fft(tempt,m);
 

### 2020-03-05 vesicle_code/docs/permeableVes/main.tex
small edits to paper

@@
 \documentclass[aps,prl,showpacs]{revtex4}
+
+\newif\ifTikz
+%\Tikztrue
+\Tikzfalse
+
 \usepackage{amsmath,amsfonts,bm, color}
@@
 unbounded viscous fluid domain, subjected to an imposed flow
-$\mbu_\infty(\mbx)$, for any $\mbx \in \RR^2$.  Assume that the interior
-and exterior fluids have the same viscosity $\mu$. Let $\mbx$ be the
-position of the interface $\gamma$, $\mbu$ be the fluid velocity, and
+$\uu_\infty(\xx)$, for any $\xx \in \RR^2$.  Assume that the interior
+and exterior fluids have the same viscosity $\mu$. Let $\xx$ be the
+position of the interface $\gamma$, $\uu$ be the fluid velocity, and
 $p$ be the pressure. In the vanishing Reynolds number limit, the
@@
   \label{eqn:governing}
-  -\nabla p + \mu \triangle \mbu &= 0, 
-  &&\mbx \in \RR^2 \setminus \gamma, \\
+  -\nabla p + \mu \triangle \uu &= 0, 
+  &&\xx \in \RR^2 \setminus \gamma, \\
 % 
-  \nabla \cdot \mbu &= 0,  &&\mbx \in \RR^2 \setminus \gamma, \\
+  \nabla \cdot \uu &= 0,  &&\xx \in \RR^2 \setminus \gamma, \\
 %
-  \mbu(\mbx) &\rightarrow \mbu_\infty(\mbx),
-    \qquad &&\norm{\mbx} \rightarrow \infty.
+  \uu(\xx) &\rightarrow \uu_\infty(\xx),
+    \qquad &&\norm{\xx} \rightarrow \infty.
 \end{alignat}
@@
 %
-Letting $\mbn$ be the outward normal to $\gamma$, $\jump{\cdot}$ denote
+Letting $\nn$ be the outward normal to $\gamma$, $\jump{\cdot}$ denote
 the jump across the interface, and $T$ denote the hydrodynamic stress
@@
   \label{eqn:jump1}
-  \jump{T\cdot\mbn} &= \mbf_\text{mem}, \\
+  \jump{T\cdot\nn} &= \ff_\text{mem}, \\
   \label{eqn:jump2}
-  \jump{\mbu} &= 0,
+  \jump{\uu} &= 0,
 \end{align}
-where $\mbf_\text{mem}$ is the standard membrane force that includes a
-bending and a tension term. In particular, $\mbf_\text{mem} =
-\mbf_\text{ben} + \mbf_\text{ten}$, where
+where $\ff_\text{mem}$ is the standard merrane force that includes a
+bending and a tension term. In particular, $\ff_\text{mem} =
+\ff_\text{ben} + \ff_\text{ten}$, where
 \begin{align}
-  \label{eqn:membraneForces}
-  \mbf_\text{ben} = -\kappa_b \mbx_{ssss}, \qquad
-  \mbf_\text{ten} = (\sigma \mbx_s)_s,
+  \label{eqn:merraneForces}
+  \ff_\text{ben} = -\kappa_b \xx_{ssss}, \qquad
+  \ff_\text{ten} = (\sigma \xx_s)_s,
 \end{align}
@@
 The kinematic condition is modified to account for the fact that the
-fluid can move through the membrane. A standard choice appears
+fluid can move through the merrane. A standard choice appears
 is~\cite{}
 \begin{align}
-  \mbu - \dot{\mbx} = - \beta (\mbf_\text{mem} \cdot \mbn) \mbn, \qquad
-  \mbx \in \gamma,
+  \uu - \dot{\xx} = - \beta (\ff_\text{mem} \cdot \nn) \nn, \qquad
+  \xx \in \gamma,
 \end{align}
@@
 \begin{align}
-  \mbu(\mbx) = \mbu_\infty(\mbx) + \sgl[\mbf_\text{mem}](\mbx), \quad
-    \mbx \in \Omega,
+  \uu(\xx) = \uu_\infty(\xx) + \sgl[\ff_\text{mem}](\xx), \quad
+    \xx \in \Omega,
 \end{align}
@@
 \begin{align}
-  \sgl[\mbf](\mbx) = \frac{1}{4\pi\mu} \int_{\gamma} \left(
-    -\mathbf{I} \log\rho + \frac{\mbr \otimes \mbr}{\rho^2} \right)
-    \mbf(\mby) ds_{\mby},
+  \sgl[\ff](\xx) = \frac{1}{4\pi\mu} \int_{\gamma} \left(
+    -\mathbf{I} \log\rho + \frac{\rr \otimes \rr}{\rho^2} \right)
+    \ff(\yy) ds_{\yy},
 \end{align}
-where $\mbr = \mbx - \mby$ and $\rho = \norm{\mbr}$. Then, by the
+where $\rr = \xx - \yy$ and $\rho = \norm{\rr}$. Then, by the
 kinematic equation, the dynamics of the vesicle 
@@
   \label{eqn:vesVelocity}
-  \frac{d\mbx}{dt} = \mbu_\infty(\mbx) + \beta (\mbf_\text{mem}\cdot\mbn)\mbn
-  + \sgl [\mbf_\text{mem}](\mbx).
+  \frac{d\xx}{dt} = \uu_\infty(\xx) + \beta (\ff_\text{mem}\cdot\nn)\nn
+  + \sgl [\ff_\text{mem}](\xx).
 \end{align}
@@
 \begin{align}
-  \mbx_s\cdot\dot{\mbx}_s = 0.
+  \xx_s\cdot\dot{\xx}_s = 0.
 \end{align}
@@
 \subsection{Vesicle Area}
-Since the vesicle membrane is semi-permeable, the vesicle's area
-fluctuates.  Parameterizing the vesicle with $\mbx$, its area is
+Since the vesicle merrane is semi-permeable, the vesicle's area
+fluctuates.  Parameterizing the vesicle with $\xx$, its area is
 \begin{align}
-  A(t) = \frac{1}{2}\int_{\gamma} (\mbx \cdot \mbn)\, ds = 
-    \frac{1}{2}\int_{0}^{2\pi} \left(\mbx \cdot \pderiv{\mbx}{\theta}^\perp\right)
+  A(t) = \frac{1}{2}\int_{\gamma} (\xx \cdot \nn)\, ds = 
+    \frac{1}{2}\int_{0}^{2\pi} \left(\xx \cdot \pderiv{\xx}{\theta}^\perp\right)
     \, d\theta.
@@
 \begin{align}
-  \dot{A}(t) &= \frac{1}{2}\int_{0}^{2\pi} \left(\dot{\mbx} \cdot
-  \pderiv{\mbx}{\theta}^{\perp} + 
-    \mbx \cdot \pderiv{\dot{\mbx}}{\theta}^{\perp}\right) d\theta, \\
+  \dot{A}(t) &= \frac{1}{2}\int_{0}^{2\pi} \left(\dot{\xx} \cdot
+  \pderiv{\xx}{\theta}^{\perp} + 
+    \xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right) d\theta, \\
   &= \frac{1}{2}
-  \int_{0}^{2\pi}(\dot{\mbx}\cdot\mbn)\left\|\pderiv{\mbx}{\theta}\right\|d\theta +
+  \int_{0}^{2\pi}(\dot{\xx}\cdot\nn)\left\|\pderiv{\xx}{\theta}\right\|d\theta +
      \frac{1}{2}\int_{0}^{2\pi}
-    \left(\mbx \cdot \pderiv{\dot{\mbx}}{\theta}^{\perp}\right)d\theta, \\
-  &= \frac{\beta}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds +
-  \frac{1}{2}\int_{0}^{2\pi}\left(\mbx \cdot \pderiv{}{t}\left(\mbn
-  \left\|\pderiv{\mbx}{\theta}\right\|\right)\right)d\theta, \\
-  &= \frac{\beta}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds + \frac{1}{2}
-  \int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds + \frac{1}{2}\int_{0}^{2\pi}
-  \frac{\mbx\cdot\mbn}{\left\|\pderiv{\mbx}{\theta}\right\|}
-  \left(\pderiv{\mbx}{\theta}\cdot
-  \pderiv{\dot{\mbx}}{\theta}\right)d\theta \\
-  &= \frac{\beta}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds + \frac{1}{2}
-  \int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds + \frac{1}{2}\int_{\gamma}
-  (\mbx\cdot\mbn) (\mbx_s \cdot \dot{\mbx}_s)\, ds.
+    \left(\xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right)d\theta, \\
+  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds +
+  \frac{1}{2}\int_{0}^{2\pi}\left(\xx \cdot \pderiv{}{t}\left(\nn
+  \left\|\pderiv{\xx}{\theta}\right\|\right)\right)d\theta, \\
+  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds + \frac{1}{2}
+  \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds + \frac{1}{2}\int_{0}^{2\pi}
+  \frac{\xx\cdot\nn}{\left\|\pderiv{\xx}{\theta}\right\|}
+  \left(\pderiv{\xx}{\theta}\cdot
+  \pderiv{\dot{\xx}}{\theta}\right)d\theta \\
+  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds + \frac{1}{2}
+  \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds + \frac{1}{2}\int_{\gamma}
+  (\xx\cdot\nn) (\xx_s \cdot \dot{\xx}_s)\, ds.
 \end{align}
-To satisfy the inextensibilty condition, $\mbx_s \cdot \dot{\mbx}_s = 0$.
+To satisfy the inextensibilty condition, $\xx_s \cdot \dot{\xx}_s = 0$.
 Therefore the time derivative of $A(t)$ is
 \begin{align}
-     \dot{A}(t) &= \frac{\beta}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds
-     + \frac{1}{2} \int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds.
+     \dot{A}(t) &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds
+     + \frac{1}{2} \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds.
 \end{align}
@@
     \dot{A}(t) &= \frac{\beta}{2}
-    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds-\frac{1}{2}\int_{\gamma}\left(\mbx^{\perp}\cdot\dot{\mbx}_s\right) ds.
+    \int_{\gamma}\left(\ff\cdot\nn\right)ds-\frac{1}{2}\int_{\gamma}\left(\xx^{\perp}\cdot\dot{\xx}_s\right) ds.
 \end{align}
@@
     \dot{A}(t) &= \frac{\beta}{2}
-    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\mbx^{\perp}_s\cdot\dot{\mbx}\right) ds,
+    \int_{\gamma}\left(\ff\cdot\nn\right)ds+\frac{1}{2}\int_{\gamma}\left(\xx^{\perp}_s\cdot\dot{\xx}\right) ds,
 \end{align}
@@
     \dot{A}(t) &= \frac{\beta}{2}
-    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\dot{\mbx}\cdot\mbn\right),\\
-    \dot{A}(t) &= \beta \int_{\gamma}\left(\mbf\cdot\mbn\right)ds.
+    \int_{\gamma}\left(\ff\cdot\nn\right)ds+\frac{1}{2}\int_{\gamma}\left(\dot{\xx}\cdot\nn\right),\\
+    \dot{A}(t) &= \beta \int_{\gamma}\left(\ff\cdot\nn\right)ds.
 \end{align}
@@
 \begin{align}
-    \dot{A}(t) &= \beta \int_{\gamma}\left(\mbf\cdot\mbn\right)ds =0.
+    \dot{A}(t) &= \beta \int_{\gamma}\left(\ff\cdot\nn\right)ds =0.
 \end{align}
-We now replace $\mbf$ with its definition and apply integration by parts
+We now replace $\ff$ with its definition and apply integration by parts
 \begin{align}
    0=\beta\int_{\gamma} 
-    (-\kappa_b\mbx_{ssss}+(\sigma\mbx_s)_s)\cdot\mbn\, ds =
-   \beta\int_{\gamma}\left(\kappa_b\mbx_{sss}-\sigma\mbx_s\right)\cdot
-     \mbn_s\, ds
+    (-\kappa_b\xx_{ssss}+(\sigma\xx_s)_s)\cdot\nn\, ds =
+   \beta\int_{\gamma}\left(\kappa_b\xx_{sss}-\sigma\xx_s\right)\cdot
+     \nn_s\, ds
 \end{align}
@@
      -\beta\int_{\gamma}
-     \left(\kappa_b\mbx_{sss}-\sigma\mbx_s\right)\cdot\kappa\mbx_s ds &=0.
+     \left(\kappa_b\xx_{sss}-\sigma\xx_s\right)\cdot\kappa\xx_s ds &=0.
 \end{align}
@@
      \beta\int_{\gamma}
-     \kappa_b\kappa\left(\mbx_{ss}\cdot\mbx_{ss}\right)ds + \beta
-     \int_{\gamma} \kappa_b \kappa_s(\mbx_{ss} \cdot \mbx_s)ds +\beta\int_{\gamma}\kappa\sigma ds  &= 0,\\
-    \beta\int_{\gamma} \kappa_b\kappa(\kappa\mbn \cdot
-     \kappa\mbn)+ \beta \int_{\gamma} \kappa_b \kappa_s(\mbx_{ss} \cdot
-     \mbx_s)ds +\beta\int_{\gamma}\kappa\sigma ds &= 0,
+     \kappa_b\kappa\left(\xx_{ss}\cdot\xx_{ss}\right)ds + \beta
+     \int_{\gamma} \kappa_b \kappa_s(\xx_{ss} \cdot \xx_s)ds +\beta\int_{\gamma}\kappa\sigma ds  &= 0,\\
+    \beta\int_{\gamma} \kappa_b\kappa(\kappa\nn \cdot
+     \kappa\nn)+ \beta \int_{\gamma} \kappa_b \kappa_s(\xx_{ss} \cdot
+     \xx_s)ds +\beta\int_{\gamma}\kappa\sigma ds &= 0,
 \end{align}
@@
    \beta\int_{\gamma}\kappa_b\kappa^3 ds + \beta \int_{\gamma} \kappa_b
-   \kappa_s(\mbx_{ss} \cdot \mbx_s)ds +\beta\int_{\gamma} \kappa\sigma ds = 0.
+   \kappa_s(\xx_{ss} \cdot \xx_s)ds +\beta\int_{\gamma} \kappa\sigma ds = 0.
 \end{align}
@@
     \beta\int_{\gamma}\kappa_b\kappa^3 ds + \beta \int_{\gamma} \kappa_b
-    \kappa_s(\kappa\mbn \cdot \TT)ds +\beta\int_{\gamma} \kappa\sigma ds = 0, \\
+    \kappa_s(\kappa\nn \cdot \TT)ds +\beta\int_{\gamma} \kappa\sigma ds = 0, \\
     \beta\int_{\gamma}\kappa_b\kappa^3 ds +\beta\int_{\gamma} \kappa\sigma ds  = 0.
@@
 be computed. However, the high-order derivatives in the bending and
-tension forces~\eqref{eqn:membraneForces} result in stiffness if an
+tension forces~\eqref{eqn:merraneForces} result in stiffness if an
 explicit time stepping method is applied to
@@
 qua-bir2014}. First, given a vesicle $\gamma$, with a boundary
-parameterized as $\mbx(s)$, we introduce notation for all the required
+parameterized as $\xx(s)$, we introduce notation for all the required
 differential and projection operators
 \begin{align}
-  B[\mbx]\mbf &= -\frac{d^4}{ds^4} \mbf, \\
-  T[\mbx]\sigma &= (\sigma \mbx_s)_s, \\
-  D[\mbx]\mbf &= \mbx_s \cdot \mbf_s, \\
-  P[\mbx]\mbf &= (\mbf \cdot \mbn) \mbn. 
+  B[\xx]\ff &= -\frac{d^4}{ds^4} \ff, \\
+  T[\xx]\sigma &= (\sigma \xx_s)_s, \\
+  D[\xx]\ff &= \xx_s \cdot \ff_s, \\
+  P[\xx]\ff &= (\ff \cdot \nn) \nn. 
 \end{align}
-Here, the normal vector $\mbn$ is the outward unit normal of the
+Here, the normal vector $\nn$ is the outward unit normal of the
 $\gamma$, and $d/ds$ is its arclength derivative. To simplify notation,
-we write $B\mbf$ to mean $B[\mbx]\mbf$, and use similar notation for the
+we write $B\ff$ to mean $B[\xx]\ff$, and use similar notation for the
 other operators. Then, the dynamics of the vesicle are governed by
 \begin{align}
-  \frac{d\mbx}{dt} &= \mbu_{\infty}(\mbx) + 
-  \beta P(B\mbx + T\sigma) + \sgl(B\mbx + T\sigma), \\
-  D \frac{d\mbx}{dt} &= 0.
+  \frac{d\xx}{dt} &= \uu_{\infty}(\xx) + 
+  \beta P(B\xx + T\sigma) + \sgl(B\xx + T\sigma), \\
+  D \frac{d\xx}{dt} &= 0.
 \end{align}
@@
 \begin{align}  
-  \frac{\mbx^{N+1} - \mbx^N}{\Delta t} = \mbu_\infty(\mbx^N) 
-  + \beta P^N\left(B^N\mbx^{N+1} + T^N\sigma^{N+1}\right) 
-  + \sgl^N\left(B^N\mbx^{N+1} + T^N\sigma^{N+1}\right).
+  \frac{\xx^{N+1} - \xx^N}{\Delta t} = \uu_\infty(\xx^N) 
+  + \beta P^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right) 
+  + \sgl^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right).
 \end{align}
@@
 \begin{align}
-  D^N\mbx^{N+1} = 1.
+  D^N\xx^{N+1} = 1.
 \end{align}
@@
 
-%\input{figures/shearPhaseDiagram.tikz}
+We consider a semi-permeable vesicle in the shear flow
+$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$. For impermeable vesicles,
+depending on the reduced area and viscosity contrast, the vesicle will
+either tumble or tank-tread~\cite{fin-lam-sei-gom2008}. Since we are
+considering permeable vesicles, we assume that there is no fluid
+viscosity.
+
+\ifTikz
+\input{figures/shearPhaseDiagram.tikz}
+\fi
 
@@
 \end{itemize}
+
+\ifTikz
+\input{figures/extensionalPhaseDiagram.tikz}
+\fi
 
@@
 \begin{align}
-  \pderiv{\XX}{t} = \mbu(\XX(t)) + \beta (\mbf \cdot \mbn) \mbn.
+  \pderiv{\XX}{t} = \uu(\XX(t)) + \beta (\ff \cdot \nn) \nn.
 \end{align}
@@
 \begin{align}
-  (\mbu \cdot \mbs)_s = -\kappa(\beta (\mbf \cdot \mbn) + 
-      \mbu \cdot \mbn).
+  (\uu \cdot \ss)_s = -\kappa(\beta (\ff \cdot \nn) + 
+      \uu \cdot \nn).
 \end{align}
@@
 in~\cite{soh-tse-li-voi-low2010}, with the only difference being that
-$\tilde{\mbu}$ satisfies
+$\tilde{\uu}$ satisfies
 \begin{align}
-  (\tilde{\mbu} \cdot \mbs)_s + \kappa(\tilde{\mbu} \cdot \mbn) =
-    -(\mbv \cdot \mbs)_s - \kappa(\mbv \cdot \mbn) 
-    - \beta\kappa(\mbf \cdot \mbn).
+  (\tilde{\uu} \cdot \ss)_s + \kappa(\tilde{\uu} \cdot \nn) =
+    -(\vv \cdot \ss)_s - \kappa(\vv \cdot \nn) 
+    - \beta\kappa(\ff \cdot \nn).
 \end{align}
@@
     \begin{array}{c}
-      \mbx^{N+1} \\ \sigma^{N+1}
+      \xx^{N+1} \\ \sigma^{N+1}
     \end{array}
@@
     \begin{array}{c}
-      \mbx^{N} + \Delta t \mbu_\infty(\mbx^N) \\ \mathbf{1}
+      \xx^{N} + \Delta t \uu_\infty(\xx^N) \\ \mathbf{1}
     \end{array}
@@
 \section{Area of a Vesicle}
-The area inside a single vesicle $\gamma$ parameterized with $\mbx$ is
+The area inside a single vesicle $\gamma$ parameterized with $\xx$ is
 \begin{align}
-  A(t) = \int_{\gamma} (\mbx \cdot \mbn)\, ds = 
-    \int_{0}^{2\pi} \left(\mbx \cdot \pderiv{\mbx}{\theta}^\perp\right)
+  A(t) = \int_{\gamma} (\xx \cdot \nn)\, ds = 
+    \int_{0}^{2\pi} \left(\xx \cdot \pderiv{\xx}{\theta}^\perp\right)
     \, d\theta.
@@
   \dot{A}(t) &= \int_{0}^{2\pi} \left(
-    \dot{\mbx} \cdot \pderiv{\mbx}{\theta}^{\perp} + 
-    \mbx \cdot \pderiv{\dot{\mbx}}{\theta}^{\perp}\right) \\
+    \dot{\xx} \cdot \pderiv{\xx}{\theta}^{\perp} + 
+    \xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right) \\
     \, d\theta.
   &= \int_{0}^{2\pi} \left(
-    (\dot{\mbx} \cdot \mbn)\|\mbx'(\theta)\| \right) d\theta +
+    (\dot{\xx} \cdot \nn)\|\xx'(\theta)\| \right) d\theta +
      \int_{0}^{2\pi}
-    \mbx \cdot \frac{d}{dt}\left(\mbn |\frac{d\mbx}{d\theta}| \right)
+    \xx \cdot \frac{d}{dt}\left(\nn |\frac{d\xx}{d\theta}| \right)
 \end{align}
@@
 \begin{align}
-  \pderiv{c}{t} + \nabla \cdot (\mbu c) = D\Delta c.
+  \pderiv{c}{t} + \nabla \cdot (\uu c) = D\Delta c.
 \end{align}
@@
 \begin{align}
-  \Delta c = 0, \quad \mbx \in \RR^2.
+  \Delta c = 0, \quad \xx \in \RR^2.
 \end{align}
@@
 \begin{align}
-  (\mbu c - D\nabla c) \cdot \mbn = c \pderiv{\mbx}{t} \cdot \mbn + 
+  (\uu c - D\nabla c) \cdot \nn = c \pderiv{\xx}{t} \cdot \nn + 
     j_c + j_p,
 \end{align}
-where $j_c$ and $j_p$ are the transmembrane chemical flux due to passive
+where $j_c$ and $j_p$ are the transmerrane chemical flux due to passive
 transport and active transport (pumps), respectively.  In the zero
@@
 \begin{align}
-  -D\pderiv{c}{\mbn} = c \pderiv{\mbx}{t} + 
-    k_c \jump{c}, \quad \mbx \in \gamma.
+  -D\pderiv{c}{\nn} = c \pderiv{\xx}{t} + 
+    k_c \jump{c}, \quad \xx \in \gamma.
 \end{align}
@@
 \begin{align}
-  \mbu - \pderiv{\mbx}{t} = j_w \mbn,
+  \uu - \pderiv{\xx}{t} = j_w \nn,
 \end{align}
@@
 \begin{align}
-  j_w = -k_w(RT\jump{c} + \mbf_\text{mem} \cdot \mbn).
+  j_w = -k_w(RT\jump{c} + \ff_\text{mem} \cdot \nn).
 \end{align}

### 2020-03-11 vesicle_code/docs/permeableVes/main.tex
few comments made in ddriver
cleaned up area of permeable vesicle proof

@@
 \begin{align}
-  \uu(\xx) = \uu_\infty(\xx) + \sgl[\ff_\text{mem}](\xx), \quad
+  \uu(\xx) = \uu_\infty(\xx) + \SS[\ff_\text{mem}](\xx), \quad
     \xx \in \Omega,
@@
 \begin{align}
-  \sgl[\ff](\xx) = \frac{1}{4\pi\mu} \int_{\gamma} \left(
+  \SS[\ff](\xx) = \frac{1}{4\pi\mu} \int_{\gamma} \left(
     -\mathbf{I} \log\rho + \frac{\rr \otimes \rr}{\rho^2} \right)
@@
   \frac{d\xx}{dt} = \uu_\infty(\xx) + \beta (\ff_\text{mem}\cdot\nn)\nn
-  + \sgl [\ff_\text{mem}](\xx).
+  + \SS [\ff_\text{mem}](\xx).
 \end{align}
@@
 \begin{align}
-  A(t) = \frac{1}{2}\int_{\gamma} (\xx \cdot \nn)\, ds = 
-    \frac{1}{2}\int_{0}^{2\pi} \left(\xx \cdot \pderiv{\xx}{\theta}^\perp\right)
-    \, d\theta.
+  A(t) = \frac{1}{2}\int_{\gamma} (\xx \cdot \nn)\, ds .
 \end{align}
-
-\todo[inline]{Can do this part of the calculation using FTC}
-Taking the time derivative of $A(t)$,
+The time derivative of $A(t)$ includes terms due to the time derivative
+of $\xx \cdot \nn$, and a term due to interface
+stretching~\cite{lai-tse-hua2008}. However, this second term is zero
+because of the local inextensibility condition. Therefore, 
 \begin{align}
-  \dot{A}(t) &= \frac{1}{2}\int_{0}^{2\pi} \left(\dot{\xx} \cdot
-  \pderiv{\xx}{\theta}^{\perp} + 
-    \xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right) d\theta, \\
-  &= \frac{1}{2}
-  \int_{0}^{2\pi}(\dot{\xx}\cdot\nn)\left\|\pderiv{\xx}{\theta}\right\|d\theta +
-     \frac{1}{2}\int_{0}^{2\pi}
-    \left(\xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right)d\theta, \\
-  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds +
-  \frac{1}{2}\int_{0}^{2\pi}\left(\xx \cdot \pderiv{}{t}\left(\nn
-  \left\|\pderiv{\xx}{\theta}\right\|\right)\right)d\theta, \\
-  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds + \frac{1}{2}
-  \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds + \frac{1}{2}\int_{0}^{2\pi}
-  \frac{\xx\cdot\nn}{\left\|\pderiv{\xx}{\theta}\right\|}
-  \left(\pderiv{\xx}{\theta}\cdot
-  \pderiv{\dot{\xx}}{\theta}\right)d\theta \\
-  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds + \frac{1}{2}
-  \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds + \frac{1}{2}\int_{\gamma}
-  (\xx\cdot\nn) (\xx_s \cdot \dot{\xx}_s)\, ds.
+  \dot{A}(t) &= \frac{1}{2} \int_{\gamma} \pderiv{}{t} 
+    (\xx \cdot \nn) \, ds = 
+  \frac{1}{2} \int_{\gamma} (\dot{\xx} \cdot \nn)\, ds  + 
+  \frac{1}{2} \int_{\gamma} (\xx \cdot \dot{\nn})\, ds.
 \end{align}
-To satisfy the inextensibilty condition, $\xx_s \cdot \dot{\xx}_s = 0$.
-Therefore the time derivative of $A(t)$ is
+The second integrand can be computed as
 \begin{align}
-     \dot{A}(t) &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds
-     + \frac{1}{2} \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds.
+  \int_\gamma (\xx \cdot \dot{\nn})\, ds 
+    = -\int_\gamma \left(\xx^\perp \cdot \dot{\xx}_s\right)\, ds 
+    = \int_\gamma \left(\xx_s^\perp \cdot \dot{\xx}\right)\, ds 
+    = \int_\gamma (\dot{\xx} \cdot \nn)\, ds.
 \end{align}
-which we re-write as
+Therefore,
 \begin{align}
-    \dot{A}(t) &= \frac{\beta}{2}
-    \int_{\gamma}\left(\ff\cdot\nn\right)ds-\frac{1}{2}\int_{\gamma}\left(\xx^{\perp}\cdot\dot{\xx}_s\right) ds.
+  \dot{A}(t) &= \int_\gamma (\dot{\xx} \cdot \nn)\, ds 
+  = \int_\gamma \left(\beta (\ff \cdot \nn)\nn + \SS[\ff]\right) 
+      \cdot \nn\, ds 
+  = \beta \int_\gamma (\ff \cdot \nn)\, ds,
 \end{align}
-Applying integration by parts,
-\begin{align}
-    \dot{A}(t) &= \frac{\beta}{2}
-    \int_{\gamma}\left(\ff\cdot\nn\right)ds+\frac{1}{2}\int_{\gamma}\left(\xx^{\perp}_s\cdot\dot{\xx}\right) ds,
-\end{align}
-which we re-write as
-\begin{align}
-    \dot{A}(t) &= \frac{\beta}{2}
-    \int_{\gamma}\left(\ff\cdot\nn\right)ds+\frac{1}{2}\int_{\gamma}\left(\dot{\xx}\cdot\nn\right),\\
-    \dot{A}(t) &= \beta \int_{\gamma}\left(\ff\cdot\nn\right)ds.
-\end{align}
-At steady state,
-\begin{align}
-    \dot{A}(t) &= \beta \int_{\gamma}\left(\ff\cdot\nn\right)ds =0.
-\end{align}
-We now replace $\ff$ with its definition and apply integration by parts
-\begin{align}
-   0=\beta\int_{\gamma} 
-    (-\kappa_b\xx_{ssss}+(\sigma\xx_s)_s)\cdot\nn\, ds =
-   \beta\int_{\gamma}\left(\kappa_b\xx_{sss}-\sigma\xx_s\right)\cdot
-     \nn_s\, ds
-\end{align}
-From the Frenet-Serret formulas, we have 
-\begin{align}
-     -\beta\int_{\gamma}
-     \left(\kappa_b\xx_{sss}-\sigma\xx_s\right)\cdot\kappa\xx_s ds &=0.
-\end{align}
-
-Applying integration by parts and Frenet-Serret again
-\begin{align}
-     \beta\int_{\gamma}
-     \kappa_b\kappa\left(\xx_{ss}\cdot\xx_{ss}\right)ds + \beta
-     \int_{\gamma} \kappa_b \kappa_s(\xx_{ss} \cdot \xx_s)ds +\beta\int_{\gamma}\kappa\sigma ds  &= 0,\\
-    \beta\int_{\gamma} \kappa_b\kappa(\kappa\nn \cdot
-     \kappa\nn)+ \beta \int_{\gamma} \kappa_b \kappa_s(\xx_{ss} \cdot
-     \xx_s)ds +\beta\int_{\gamma}\kappa\sigma ds &= 0,
-\end{align}
-which we re-write as
-\begin{align}
-   \beta\int_{\gamma}\kappa_b\kappa^3 ds + \beta \int_{\gamma} \kappa_b
-   \kappa_s(\xx_{ss} \cdot \xx_s)ds +\beta\int_{\gamma} \kappa\sigma ds = 0.
-\end{align}
-Applying Frenet-serret again,
-\begin{align}
-    \beta\int_{\gamma}\kappa_b\kappa^3 ds + \beta \int_{\gamma} \kappa_b
-    \kappa_s(\kappa\nn \cdot \TT)ds +\beta\int_{\gamma} \kappa\sigma ds = 0, \\
-    \beta\int_{\gamma}\kappa_b\kappa^3 ds +\beta\int_{\gamma} \kappa\sigma ds  = 0.
-\end{align}
+where the last equality comes follows from the divergence theorem.
+Finally, using integration by parts and the Frenet-Serret identities, we
+have
+\begin{align*}
+  \dot{A}(t) &= \beta \int_\gamma \left( -\kappa_b \xx_{ssss} + 
+    (\sigma \xx_s)_s \right) \cdot \nn \, ds \\
+  &= \beta \int_\gamma \left(-\kappa_b \xx_{sss} + \sigma \xx_s 
+    \right) \cdot \kappa \xx_s \, ds \\
+  &= \beta \int_\gamma \left(\kappa_b \xx_{ss} \cdot 
+    (\kappa \xx_s)_s \right) \, ds +
+    \beta \int_\gamma \kappa \sigma \, ds \\
+  &= \beta \int_\gamma \left(\kappa_b \kappa (\xx_{ss} \cdot \xx_{ss}) + 
+    \kappa_b \kappa_s (\xx_{ss} \cdot \xx_s) \right) \, ds +
+    \beta \int_\gamma \kappa \sigma \, ds \\
+  &= \beta \int_\gamma \left(\kappa_b \kappa^3 + \kappa \sigma \right) 
+    \, ds.
+\end{align*}
 
@@
   \frac{d\xx}{dt} &= \uu_{\infty}(\xx) + 
-  \beta P(B\xx + T\sigma) + \sgl(B\xx + T\sigma), \\
+  \beta P(B\xx + T\sigma) + \SS(B\xx + T\sigma), \\
   D \frac{d\xx}{dt} &= 0.
@@
   + \beta P^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right) 
-  + \sgl^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right).
+  + \SS^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right).
 \end{align}
@@
   \begin{array}{cc}
-    I + \Delta t \beta P^N B^N + \Delta t \sgl^N B^N & 
-    -\Delta t P^N T^N - \Delta t \sgl^N T^N \\
+    I + \Delta t \beta P^N B^N + \Delta t \SS^N B^N & 
+    -\Delta t P^N T^N - \Delta t \SS^N T^N \\
     D^N & 0
@@
     \xx \cdot \frac{d}{dt}\left(\nn |\frac{d\xx}{d\theta}| \right)
+\end{align}
+
+\begin{align}
+  A(t) = \frac{1}{2}\int_{\gamma} (\xx \cdot \nn)\, ds = 
+    \frac{1}{2}\int_{0}^{2\pi} \left(\xx \cdot \pderiv{\xx}{\theta}^\perp\right)
+    \, d\theta.
+\end{align}
+Taking the time derivative of $A(t)$,
+\begin{align}
+  \dot{A}(t) &= \frac{1}{2}\int_{0}^{2\pi} \left(\dot{\xx} \cdot
+  \pderiv{\xx}{\theta}^{\perp} + 
+    \xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right) d\theta, \\
+  &= \frac{1}{2}
+  \int_{0}^{2\pi}(\dot{\xx}\cdot\nn)\left\|\pderiv{\xx}{\theta}\right\|d\theta +
+     \frac{1}{2}\int_{0}^{2\pi}
+    \left(\xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right)d\theta, \\
+  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds +
+  \frac{1}{2}\int_{0}^{2\pi}\left(\xx \cdot \pderiv{}{t}\left(\nn
+  \left\|\pderiv{\xx}{\theta}\right\|\right)\right)d\theta, \\
+  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds + \frac{1}{2}
+  \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds + \frac{1}{2}\int_{0}^{2\pi}
+  \frac{\xx\cdot\nn}{\left\|\pderiv{\xx}{\theta}\right\|}
+  \left(\pderiv{\xx}{\theta}\cdot
+  \pderiv{\dot{\xx}}{\theta}\right)d\theta \\
+  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds + \frac{1}{2}
+  \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds + \frac{1}{2}\int_{\gamma}
+  (\xx\cdot\nn) (\xx_s \cdot \dot{\xx}_s)\, ds.
+\end{align}
+To satisfy the inextensibilty condition, $\xx_s \cdot \dot{\xx}_s = 0$.
+Therefore the time derivative of $A(t)$ is
+\begin{align}
+     \dot{A}(t) &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds
+     + \frac{1}{2} \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds.
+\end{align}
+which we re-write as
+\begin{align}
+    \dot{A}(t) &= \frac{\beta}{2}
+    \int_{\gamma}\left(\ff\cdot\nn\right)ds-\frac{1}{2}\int_{\gamma}\left(\xx^{\perp}\cdot\dot{\xx}_s\right) ds.
+\end{align}
+Applying integration by parts,
+\begin{align}
+    \dot{A}(t) &= \frac{\beta}{2}
+    \int_{\gamma}\left(\ff\cdot\nn\right)ds+\frac{1}{2}\int_{\gamma}\left(\xx^{\perp}_s\cdot\dot{\xx}\right) ds,
+\end{align}
+which we re-write as
+\begin{align}
+    \dot{A}(t) &= \frac{\beta}{2}
+    \int_{\gamma}\left(\ff\cdot\nn\right)ds+\frac{1}{2}\int_{\gamma}\left(\dot{\xx}\cdot\nn\right),\\
+    \dot{A}(t) &= \beta \int_{\gamma}\left(\ff\cdot\nn\right)ds.
+\end{align}
+
+At steady state,
+\begin{align}
+    \dot{A}(t) &= \beta \int_{\gamma}\left(\ff\cdot\nn\right)ds =0.
+\end{align}
+We now replace $\ff$ with its definition and apply integration by parts
+\begin{align}
+   0=\beta\int_{\gamma} 
+    (-\kappa_b\xx_{ssss}+(\sigma\xx_s)_s)\cdot\nn\, ds =
+   \beta\int_{\gamma}\left(\kappa_b\xx_{sss}-\sigma\xx_s\right)\cdot
+     \nn_s\, ds
+\end{align}
+From the Frenet-Serret formulas, we have 
+\begin{align}
+     -\beta\int_{\gamma}
+     \left(\kappa_b\xx_{sss}-\sigma\xx_s\right)\cdot\kappa\xx_s ds &=0.
+\end{align}
+
+Applying integration by parts and Frenet-Serret again
+\begin{align}
+     \beta\int_{\gamma}
+     \kappa_b\kappa\left(\xx_{ss}\cdot\xx_{ss}\right)ds + \beta
+     \int_{\gamma} \kappa_b \kappa_s(\xx_{ss} \cdot \xx_s)ds +\beta\int_{\gamma}\kappa\sigma ds  &= 0,\\
+    \beta\int_{\gamma} \kappa_b\kappa(\kappa\nn \cdot
+     \kappa\nn)+ \beta \int_{\gamma} \kappa_b \kappa_s(\xx_{ss} \cdot
+     \xx_s)ds +\beta\int_{\gamma}\kappa\sigma ds &= 0,
+\end{align}
+which we re-write as
+\begin{align}
+   \beta\int_{\gamma}\kappa_b\kappa^3 ds + \beta \int_{\gamma} \kappa_b
+   \kappa_s(\xx_{ss} \cdot \xx_s)ds +\beta\int_{\gamma} \kappa\sigma ds = 0.
+\end{align}
+Applying Frenet-serret again,
+\begin{align}
+    \beta\int_{\gamma}\kappa_b\kappa^3 ds + \beta \int_{\gamma} \kappa_b
+    \kappa_s(\kappa\nn \cdot \TT)ds +\beta\int_{\gamma} \kappa\sigma ds = 0, \\
+    \beta\int_{\gamma}\kappa_b\kappa^3 ds +\beta\int_{\gamma} \kappa\sigma ds  = 0.
 \end{align}

### 2020-03-11 shuwang_code/shear1Ves.m

@@ -70,8 +70,9 @@ sl = 2.6442;
 x0 = x0/2;
 y0 = y0/2;
 kmatrix = formkmatrix(ngrid);
-% For Shuwang: Not sure why we need kmatrix. It is a matrix that has a
-% checkerboard pattern of zeros and ones
+% kmatrix is checkerboard pattern of 0s and 1s which is dot multiplied y
+% the layer potential matricies so that the quadrature is odd/even
+% trapezoid rule.
 
 % compute the x velocity, y velocity, Lagrange multiplier, body forces,
 % new shape, and center of mass using the initialized concentration

### 2020-03-13 vesicle_code/docs/permeableVes/main.tex

@@
   &= \beta \int_\gamma \left(\kappa_b \xx_{ss} \cdot 
-    (\kappa \xx_s)_s \right) \, ds +
-    \beta \int_\gamma \kappa \sigma \, ds \\
+    (\kappa \xx_s)_s + \kappa \sigma \right) \, ds \\
   &= \beta \int_\gamma \left(\kappa_b \kappa (\xx_{ss} \cdot \xx_{ss}) + 
-    \kappa_b \kappa_s (\xx_{ss} \cdot \xx_s) \right) \, ds +
-    \beta \int_\gamma \kappa \sigma \, ds \\
+    \kappa_b \kappa_s (\xx_{ss} \cdot \xx_s) + \kappa \sigma \right) 
+    \, ds \\
   &= \beta \int_\gamma \left(\kappa_b \kappa^3 + \kappa \sigma \right) 
@@
 vesicle boundary, and these are done with Fourier differentiation.
-Finally, to compute the single-layer potential, we use an eight-order
+Finally, to compute the single-layer potential, we use an eighth-order
 Alpert quadrature rule~\cite{alp1999} which resolves the logarithmic

### 2020-03-13 vesicle_code/docs/permeableVes/main.tex
picking at paper

@@
   \label{eqn:merraneForces}
-  \ff_\text{ben} = -\kappa_b \xx_{ssss}, \qquad
-  \ff_\text{ten} = (\sigma \xx_s)_s,
+  \ff_\text{ben} = -\xx_{ssss}, \qquad
+  \ff_\text{ten} = (\sigma \xx_s)_s.
 \end{align}
-where $\kappa_b$ is the bending stiffness and $\sigma$ is a Lagrange
-multiplier, which acts like the tension, which is used to satisfy the
-inextensibility condition.
+Since the bending stiffness only sets the time scale, we let $k_b = 1$
+throughout this paper. The Lagrange multiplier $\sigma$ is used to
+satisfy the inextensibility condition.  Finally, the tension of the
+vesicle is
+\begin{align}
+  \Lambda = \sigma + 1.5 \kappa^2,
+\end{align}
+where $\kappa$ is the membrane curvature.
 
@@
 \subsection{Vesicle Area}
-Since the vesicle merrane is semi-permeable, the vesicle's area
+Since the vesicle membrane is semi-permeable, the vesicle's area
 fluctuates.  Parameterizing the vesicle with $\xx$, its area is
@@
 have
-\begin{align*}
-  \dot{A}(t) &= \beta \int_\gamma \left( -\kappa_b \xx_{ssss} + 
+\begin{align}
+  \dot{A}(t) &= \beta \int_\gamma \left( -\xx_{ssss} + 
     (\sigma \xx_s)_s \right) \cdot \nn \, ds \\
-  &= \beta \int_\gamma \left(-\kappa_b \xx_{sss} + \sigma \xx_s 
+  &= \beta \int_\gamma \left(-\xx_{sss} + \sigma \xx_s 
     \right) \cdot \kappa \xx_s \, ds \\
-  &= \beta \int_\gamma \left(\kappa_b \xx_{ss} \cdot 
+  &= \beta \int_\gamma \left(\xx_{ss} \cdot 
     (\kappa \xx_s)_s + \kappa \sigma \right) \, ds \\
-  &= \beta \int_\gamma \left(\kappa_b \kappa (\xx_{ss} \cdot \xx_{ss}) + 
-    \kappa_b \kappa_s (\xx_{ss} \cdot \xx_s) + \kappa \sigma \right) 
+  &= \beta \int_\gamma \left(\kappa (\xx_{ss} \cdot \xx_{ss}) + 
+    \kappa_s (\xx_{ss} \cdot \xx_s) + \kappa \sigma \right) 
     \, ds \\
-  &= \beta \int_\gamma \left(\kappa_b \kappa^3 + \kappa \sigma \right) 
+  &= \beta \int_\gamma \left(\kappa^3 + \kappa \sigma \right) 
     \, ds.
-\end{align*}
+\end{align}
+Finally, using the relationship between the Lagrange multiplier
+$\sigma$, and the tension $\Lambda$, the area of a semi-permeable
+vesicle is governed by
+\begin{align}
+  \dot{A}(t) = \beta \int_\gamma \left(
+    -\frac{\kappa^3}{2} + \kappa \Lambda \right) \, ds.
+\end{align}
 
@@
 By writing $B^N$ to mean the bending operator due to the vesicle
-configuration at time $t_N$, and similar notation for the other
+configuration at time $t^N$, and similar notation for the other
 operators, we address the stiffness by introducing the semi-implicit
@@
 \end{itemize}
+
+We consider a single semi-permeable vesicle in a quiescent flow. For
+impermeable vesicles, the vesicle relaxes to a shape with constant
+negative tension~\cite{kra-win-sei-lip1996}.
 
@@
    0=\beta\int_{\gamma} 
-    (-\kappa_b\xx_{ssss}+(\sigma\xx_s)_s)\cdot\nn\, ds =
-   \beta\int_{\gamma}\left(\kappa_b\xx_{sss}-\sigma\xx_s\right)\cdot
+    (-k_b\xx_{ssss}+(\sigma\xx_s)_s)\cdot\nn\, ds =
+   \beta\int_{\gamma}\left(k_b\xx_{sss}-\sigma\xx_s\right)\cdot
      \nn_s\, ds
@@
      -\beta\int_{\gamma}
-     \left(\kappa_b\xx_{sss}-\sigma\xx_s\right)\cdot\kappa\xx_s ds &=0.
+     \left(k_b\xx_{sss}-\sigma\xx_s\right)\cdot\kappa\xx_s ds &=0.
 \end{align}
@@
      \beta\int_{\gamma}
-     \kappa_b\kappa\left(\xx_{ss}\cdot\xx_{ss}\right)ds + \beta
-     \int_{\gamma} \kappa_b \kappa_s(\xx_{ss} \cdot \xx_s)ds +\beta\int_{\gamma}\kappa\sigma ds  &= 0,\\
-    \beta\int_{\gamma} \kappa_b\kappa(\kappa\nn \cdot
-     \kappa\nn)+ \beta \int_{\gamma} \kappa_b \kappa_s(\xx_{ss} \cdot
+     k_b\kappa\left(\xx_{ss}\cdot\xx_{ss}\right)ds + \beta
+     \int_{\gamma} k_b \kappa_s(\xx_{ss} \cdot \xx_s)ds +\beta\int_{\gamma}\kappa\sigma ds  &= 0,\\
+    \beta\int_{\gamma} k_b\kappa(\kappa\nn \cdot
+     \kappa\nn)+ \beta \int_{\gamma} k_b \kappa_s(\xx_{ss} \cdot
      \xx_s)ds +\beta\int_{\gamma}\kappa\sigma ds &= 0,
@@
 \begin{align}
-   \beta\int_{\gamma}\kappa_b\kappa^3 ds + \beta \int_{\gamma} \kappa_b
+   \beta\int_{\gamma}k_b\kappa^3 ds + \beta \int_{\gamma} k_b
    \kappa_s(\xx_{ss} \cdot \xx_s)ds +\beta\int_{\gamma} \kappa\sigma ds = 0.
@@
 \begin{align}
-    \beta\int_{\gamma}\kappa_b\kappa^3 ds + \beta \int_{\gamma} \kappa_b
+    \beta\int_{\gamma}k_b\kappa^3 ds + \beta \int_{\gamma} k_b
     \kappa_s(\kappa\nn \cdot \TT)ds +\beta\int_{\gamma} \kappa\sigma ds = 0, \\
-    \beta\int_{\gamma}\kappa_b\kappa^3 ds +\beta\int_{\gamma} \kappa\sigma ds  = 0.
+    \beta\int_{\gamma}k_b\kappa^3 ds +\beta\int_{\gamma} \kappa\sigma ds  = 0.
 \end{align}

### 2020-03-31 vesicle_code/docs/permeableVes/main.tex
working on quiescent flow example

@@
 
-\usepackage{amsmath,amsfonts,bm, color}
+%\usepackage{showkeys}
+\usepackage{amsmath,amsfonts,bm}
 \usepackage{graphicx,epsfig}
@@
 \end{align}
-where $\ff_\text{mem}$ is the standard merrane force that includes a
-bending and a tension term. In particular, $\ff_\text{mem} =
-\ff_\text{ben} + \ff_\text{ten}$, where
+where $\nn$ points outward to the vesicle, and $\ff_\text{mem}$ is the
+standard membrane force that includes a bending and a tension term. In
+particular, $\ff_\text{mem} = \ff_\text{ben} + \ff_\text{ten}$, where
 \begin{align}
-  \label{eqn:merraneForces}
+  \label{eqn:membraneForces}
   \ff_\text{ben} = -\xx_{ssss}, \qquad
@@
 The kinematic condition is modified to account for the fact that the
-fluid can move through the merrane. A standard choice appears
+fluid can move through the membrane. A standard choice appears
 is~\cite{}
@@
     -\frac{\kappa^3}{2} + \kappa \Lambda \right) \, ds.
+  \label{eqn:areaROC}
 \end{align}
@@
 be computed. However, the high-order derivatives in the bending and
-tension forces~\eqref{eqn:merraneForces} result in stiffness if an
+tension forces~\eqref{eqn:membraneForces} result in stiffness if an
 explicit time stepping method is applied to
@@
 \end{align}
-Here, the normal vector $\nn$ is the outward unit normal of the
-$\gamma$, and $d/ds$ is its arclength derivative. To simplify notation,
-we write $B\ff$ to mean $B[\xx]\ff$, and use similar notation for the
-other operators. Then, the dynamics of the vesicle are governed by
+Here, the normal vector $\nn$ is the outward unit normal of $\gamma$,
+and $d/ds$ is its arclength derivative. To simplify notation, we write
+$B\ff$ to mean $B[\xx]\ff$, and use similar notation for the other
+operators. Then, the dynamics of the vesicle are governed by
 \begin{align}
@@
 We consider a single semi-permeable vesicle in a quiescent flow. For
-impermeable vesicles, the vesicle relaxes to a shape with constant
-negative tension~\cite{kra-win-sei-lip1996}.
+impermeable vesicles, the vesicle relaxes to a shape where the tension
+$\Lambda$ is constant and negative~\cite{kra-win-sei-lip1996}. In the
+semi-permeable case, the area of the vesicle is governed by
+equation~\eqref{eqn:areaROC}, where $\beta > 0$. We expect the
+semi-permeable vesicle to reach a steady-state shape, meaning that in
+the limit,
+\begin{align}
+  \int_{\gamma} \left(-\frac{\kappa^3}{2} + \kappa \Lambda \right) \, ds
+  \rightarrow 0.
+\end{align}
+Based on numerical observations, the steady-state shape is a circular
+vesicle with constant tension. Since the tension and curvature are
+constant, we can solve for the curvature in terms of the tension $\kappa
+= \sqrt{2\Lambda}$. Therefore, the steady state shape is a circle of
+radius $r = 1/\sqrt{2\Lambda}$, and therefore the length is
+\begin{align}
+  L = \frac{\sqrt{2}\pi}{\sqrt{\Lambda}},
+\end{align}
+which is constant by the local inextensibility constraint. Therefore, we
+can compute the final tension in terms of the length using the formula
+\begin{align}
+  \Lambda = \frac{2\pi^2}{L^2}.
+  \label{eqn:finalTension}
+\end{align}
+Therefore, in contrast to a impermeable vesicle, the final tension is
+positive rather than negative.
+
+We start by simulating a star-shaped vesicle in a quiescent flow with
+semi-permeability rate $\beta=1$. The vesicle shape at five time
+steps is in Figure~\ref{fig:starShape}. To perform this simulation,
+we use an adaptive second-order time stepping
+method~\cite{qua-bir2016}. The times and reduced areas are
+in the titles, and note that the shapes are not eqiuspaced in time.
+
+\begin{figure}[htp]
+  \begin{center}
+    \input{figures/starRelaxation2.tikz}
+    \input{figures/starRelaxation3.tikz}
+    \input{figures/starRelaxation4.tikz}
+    \input{figures/starRelaxation5.tikz}
+    \input{figures/starRelaxation6.tikz}
+  \end{center}
+  \caption{\label{fig:starShape} A initially star-shaped
+  semi-permeable vesicle in a shear quiescent flow with $\beta=1$. Note
+  that the time steps are not equispaced.}
+\end{figure}
+
+\begin{figure}[htp]
+  \input{figures/starAreaDeriv.tikz}
+  \qquad
+  \input{figures/starTension.tikz}
+  \caption{\label{fig:starArea} (a) The area (red) and its derivative
+  (blue) of an initially star-shaped vesicle as a function of time. The
+  dots correspond to the time steps shown in Figure~\ref{fig:starShape}.
+  (b) The tension of the vesicles illustrated in
+  Figure~\ref{fig:starShape}.  The tension at the time horizon $T=1$ is
+  also included. At this point, the vesicle is nearly circular and the
+  tension agrees with the constant value from
+  equation~\eqref{eqn:finalTension}. This dashed black line corresponds
+  to this constant tension value.}
+\end{figure}
 
@@
 \end{align}
-where $j_c$ and $j_p$ are the transmerrane chemical flux due to passive
+where $j_c$ and $j_p$ are the transmembrane chemical flux due to passive
 transport and active transport (pumps), respectively.  In the zero

### 2020-03-31 shuwang_code/arc.m

@@ -9,12 +9,11 @@ dsi = fin(ds,n);
 % get the integration of ds;
  
 ave = dsi(N+1);
-f(1:N+1) = (0:1:N)*ave/N-dsi(1:N+1);
+% ave is the length of the vesicle
+f = (0:1:N)*ave/N - dsi;
 fp = -ds;
 a = f/N;
-b = zeros(1,N+1);
 c = fp/N;
-d = zeros(1,N+1);
 x = fft(a(1:N+1),N);
 y = fft(c(1:N+1),N);
 x(n+1) = x(1);

### 2020-04-06 vesicle_code/docs/permeableVes/main.tex
uncommenting tikz figures
working on relaxation section

@@
 semi-permeable case, the area of the vesicle is governed by
-equation~\eqref{eqn:areaROC}, where $\beta > 0$. We expect the
-semi-permeable vesicle to reach a steady-state shape, meaning that in
-the limit,
+equation~\eqref{eqn:areaROC}, where $\beta > 0$. Therefore, when the
+semi-permeable vesicle reaches a steady-state shape, we have
 \begin{align}
   \int_{\gamma} \left(-\frac{\kappa^3}{2} + \kappa \Lambda \right) \, ds
-  \rightarrow 0.
+  = 0.
 \end{align}
@@
 \end{align}
-which is constant by the local inextensibility constraint. Therefore, we
+which is constant by the local inextensibility constraint. Finally, we
 can compute the final tension in terms of the length using the formula
@@
 We start by simulating a star-shaped vesicle in a quiescent flow with
-semi-permeability rate $\beta=1$. The vesicle shape at five time
-steps is in Figure~\ref{fig:starShape}. To perform this simulation,
-we use an adaptive second-order time stepping
-method~\cite{qua-bir2016}. The times and reduced areas are
-in the titles, and note that the shapes are not eqiuspaced in time.
-
+semi-permeability rate $\beta=1$ (Figure~\ref{fig:starShape}). To
+perform this simulation, we use an adaptive second-order time stepping
+method~\cite{qua-bir2016}. The times and reduced areas are in the
+titles, and note that the shapes are not eqiuspaced in time.
 \begin{figure}[htp]
-  \begin{center}
+  \begin{minipage}{0.55\textwidth}
+    \input{figures/starRelaxation1.tikz}
     \input{figures/starRelaxation2.tikz}
@@
     \input{figures/starRelaxation6.tikz}
-  \end{center}
-  \caption{\label{fig:starShape} A initially star-shaped
-  semi-permeable vesicle in a shear quiescent flow with $\beta=1$. Note
-  that the time steps are not equispaced.}
+  \end{minipage}
+  \hfill
+  \begin{minipage}{0.4\textwidth}
+  \input{figures/starAreaDeriv.tikz}
+  \end{minipage}
+  \caption{\label{fig:starShape} A initially star-shaped semi-permeable
+  vesicle in a shear quiescent flow with $\beta=1$. Note that the time
+  steps are not equispaced. The area (red) and its derivative (blue) of
+  an initially star-shaped vesicle as a function of time. The dots
+  correspond to the time steps shown in six time steps
+  show on the left.}
 \end{figure}
@@
 \begin{figure}[htp]
-  \input{figures/starAreaDeriv.tikz}
-  \qquad
+\begin{minipage}{0.40\textwidth}
 \input{figures/starTension.tikz}
-  \caption{\label{fig:starArea} (a) The area (red) and its derivative
-  (blue) of an initially star-shaped vesicle as a function of time. The
-  dots correspond to the time steps shown in Figure~\ref{fig:starShape}.
-  (b) The tension of the vesicles illustrated in
+\end{minipage}
+\hfill
+\begin{minipage}{0.55\textwidth}
+  \centering
+\includegraphics[width=0.32\textwidth]{figures/StarTensionTime1.pdf}
+\includegraphics[width=0.32\textwidth]{figures/StarTensionTime2.pdf}
+\includegraphics[width=0.32\textwidth]{figures/StarTensionTime3.pdf} \\
+\includegraphics[width=0.32\textwidth]{figures/StarTensionTime4.pdf}
+\includegraphics[width=0.32\textwidth]{figures/StarTensionTime5.pdf}
+\includegraphics[width=0.32\textwidth]{figures/StarTensionTime6.pdf}
+\end{minipage}
+  \caption{\label{fig:starTension} The tension of the time steps shown
+  in Figure~\ref{fig:starShape}. The tension at the time horizon $T=1$
+  is also included. At this point, the vesicle is nearly circular and
+  the tension is constant and positive. The constant is given by
+  equation~\eqref{eqn:finalTension}, and this value corresponds to the
+  dashed black line.}
+\end{figure}
+
+\begin{figure}[htp]
+\begin{minipage}{0.40\textwidth}
+\input{figures/starFlux.tikz}
+\end{minipage}
+\hfill
+\begin{minipage}{0.55\textwidth}
+\includegraphics[width=0.32\textwidth]{figures/StarFluxTime1.pdf}
+\includegraphics[width=0.32\textwidth]{figures/StarFluxTime2.pdf}
+\includegraphics[width=0.32\textwidth]{figures/StarFluxTime3.pdf} \\
+\includegraphics[width=0.32\textwidth]{figures/StarFluxTime4.pdf}
+\includegraphics[width=0.32\textwidth]{figures/StarFluxTime5.pdf}
+\includegraphics[width=0.32\textwidth]{figures/StarFluxTime6.pdf}
+\end{minipage}
+  \caption{\label{fig:starFlux} The flux of the time steps shown in
   Figure~\ref{fig:starShape}. The tension at the time horizon $T=1$ is
-  also included. At this point, the vesicle is nearly circular and the
-  tension agrees with the constant value from
-  equation~\eqref{eqn:finalTension}. This dashed black line corresponds
-  to this constant tension value.}
+  also included. At this point, the vesicle is nearly circular and there
+  is no flux.}
 \end{figure}
+
+%\begin{figure}[htp]
+%  \input{figures/starFlux.tikz}
+%  \caption{\label{fig:starFlux} The flux of the time steps shown in
+%  Figure~\ref{fig:starShape}. The tension at the time horizon $T=1$ is
+%  also included. At this point, the vesicle is nearly circular and their
+%  is no flux.}
+%\end{figure}
 

### 2020-04-06 shuwang_rewrite/curve.m

@@ -155,27 +155,26 @@ end
 if(any(strcmp(options,'parameter')));
   alpha = options{find(strcmp(options,'parameter'))+1};
 else
-  alpha = (0:N-1)'*2*pi/N;
+  alpha = (0:N-1)'/N;
 end
 % Discretization in parameter space
 
 if any(strcmp(options,'curly'))
   a = 1; b = 3*a; c = 0.85; 
-  r = 0.5*sqrt( (a*cos(alpha)).^2 + (b*sin(alpha)).^2) + ...
-      .07*cos(12*alpha);
-  x = scale*c*r.*cos(alpha);
-  y = scale*r.*sin(alpha);
+  r = 0.5*sqrt( (a*cos(2*pi*alpha)).^2 + (b*sin(2*pi*alpha)).^2) + ...
+      .07*cos(12*2*pi*alpha);
+  x = scale*c*r.*cos(2*pi*alpha);
+  y = scale*r.*sin(2*pi*alpha);
   X0 = [x;y];
   % radius of curly vesicle
 
 elseif any(strcmp(options,'star'))
-  radius = 1 + 0.2*cos(folds*alpha);
-  X0 = [radius.*cos(alpha);radius.*sin(alpha)];
-  % a star that comes very close to intersecting itself
-  % at the origin
+  radius = 1 + 0.2*cos(folds*2*pi*alpha);
+  X0 = [radius.*cos(2*pi*alpha);radius.*sin(2*pi*alpha)];
+  % a star that comes very close to intersecting itself at the origin
 
 elseif any(strcmp(options,'ellipse'))
-  X0 = [cos(alpha);shortax*sin(alpha)];
+  X0 = [cos(2*pi*alpha);shortax*sin(2*pi*alpha)];
 else
   X0 = o.ellipse(N,ra);
   % build a vesicle of reduced area ra with N points
@@ -190,13 +189,10 @@ X(N+1:2*N) = scale*(sin(theta) * X0(1:N) +  cos(theta) * X0(N+1:2*N));
 % Rotate and scale vesicle
 
 if ~equispaced
-%  figure(1); clf
-%  plot(X(1:end/2),X(end/2+1:end),'b-o')
-%  axis equal
-%  figure(2); clf;
+%  figure(1); clf;
 %  plot(X(1:end/2),X(end/2+1:end),'b--')
-%  axis equal
-%  hold on
+%  axis equal;
+%  hold on;
   sa = o.diffProp(X); % compute arclength of the vesicle shape
   alpha = o.arc(sa);
[…]

### 2020-04-23 vesicle_code/docs/permeableVes/main.tex

@@
     large $\chi$
+
+  \item Look at tank-treading angle, tank-trading speed, reduced area,
+    absolute value of the permeable flux
+  \item Max flux at the steady state as a function of beta and
+    $\dot{\gamma}$
+
+  \item reduced area/inclination angle for a particular $(\beta,\gamma)$
+    and different flux rates using the gating functions (Apr 7 and 9) as
+    well as constant $\beta$
 \end{itemize}
@@
 
-\ifTikz
+%\ifTikz
 \input{figures/shearPhaseDiagram.tikz} 
-\fi
+%\fi
 
@@
 \begin{itemize}
-  \item ???
+  \item Does permeability affect the rate of migration
 \end{itemize}

### 2020-05-04 vesicle_code/docs/permeableVes/main.tex
working on relaxation

@@
 \title{Semi-permeable vesicles: mathematical formulation, numerics and physics}
-\author{Ashley Gannon, Bryan Quaife, Shravan Veerapaneni, and Yuan-Nan Young}
+\author{Ashley Gannon, Bryan Quaife, and Yuan-Nan Young}
 
@@
   \label{eqn:jump1}
-  \jump{T\cdot\nn} &= \ff_\text{mem}, \\
+  \jump{T\cdot\nn} &= \ff_\{mathrm{mem}, \\
   \label{eqn:jump2}
@@
 \end{align}
-where $\nn$ points outward to the vesicle, and $\ff_\text{mem}$ is the
-standard membrane force that includes a bending and a tension term. In
-particular, $\ff_\text{mem} = \ff_\text{ben} + \ff_\text{ten}$, where
+where $\nn$ points outward to the vesicle, and $\ff_\mathrm{mem}$ is the
+membrane force that includes a bending term that minimizes the Helfrich
+energy, and a tension term that acts as a Lagrange multiplier to satisfy
+the local inextensibility condition. The bending stiffness only sets the
+time scale, so we let $k_b = 1$ throughout the paper. For ease of
+implementation, we modify the bending tension and forces as
+$\ff_\mathrm{mem} = \ff_\mathrm{ben} + \ff_\mathrm{ten}$, where
 \begin{align}
   \label{eqn:membraneForces}
-  \ff_\text{ben} = -\xx_{ssss}, \qquad
-  \ff_\text{ten} = (\sigma \xx_s)_s.
+  \ff_\mathrm{ben} = -\xx_{ssss}, \qquad
+  \ff_\mathrm{ten} = (\sigma \xx_s)_s.
 \end{align}
-Since the bending stiffness only sets the time scale, we let $k_b = 1$
-throughout this paper. The Lagrange multiplier $\sigma$ is used to
-satisfy the inextensibility condition.  Finally, the tension of the
-vesicle is
+However, the physical tension $\Lambda$ can be computed as a
+post-processing step as
 \begin{align}
@@
 \begin{align}
-  \uu - \dot{\xx} = - \beta (\ff_\text{mem} \cdot \nn) \nn, \qquad
+  \uu - \dot{\xx} = - \beta (\ff_\mathrm{mem} \cdot \nn) \nn, \qquad
   \xx \in \gamma,
@@
 \begin{align}
-  \uu(\xx) = \uu_\infty(\xx) + \SS[\ff_\text{mem}](\xx), \quad
+  \uu(\xx) = \uu_\infty(\xx) + \SS[\ff_\mathrm{mem}](\xx), \quad
     \xx \in \Omega,
@@
   \label{eqn:vesVelocity}
-  \frac{d\xx}{dt} = \uu_\infty(\xx) + \beta (\ff_\text{mem}\cdot\nn)\nn
-  + \SS [\ff_\text{mem}](\xx).
+  \frac{d\xx}{dt} = \uu_\infty(\xx) + \beta (\ff_\mathrm{mem}\cdot\nn)\nn
+  + \SS [\ff_\mathrm{mem}](\xx).
 \end{align}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Vesicle Area}
-Since the vesicle membrane is semi-permeable, the vesicle's area
-fluctuates.  Parameterizing the vesicle with $\xx$, its area is
+\subsection{Area Dynamics}
+Following the analysis of Veerapaneni et al.~\cite{vee-raj-bir-pur2009},
+we compute the steady-state shape of a semi-permeable vesicle in a
+quiescent flow. The steady-state shape is a stationary point of the
+Lagrangian
+\begin{align}
+  \mathcal{L} = \frac{1}{2}\int_{\gamma} \kappa^2 \, ds +
+    \Lambda \left(\int_{\gamma} ds  - L \right),
+\end{align}
+where $\Lambda$ is the constant tension that acts as a Lagrange
+multiplier to satisfy the length conservation. Note that there is no
+pressure Lagrange multiplier since the vesicle's area fluctuates. The
+force acing on the membrane is found by taking the variation of
+$\mathcal{L}$ with respect to $\gamma$, and by setting the total force
+to zero, the steady state shape satisfies
+\begin{align}
+  \kappa_{ss} + \frac{1}{2}\kappa^3 - \Lambda \kappa = 0.
+  \label{eqn:curvODE}
+\end{align}
+with initial conditions $\kappa(0) = \kappa_0$ and $\kappa_s(0) = 0$.
+Integrating the differential equation~\eqref{eqn:curvODE} with respect
+to arclength, we have
+\begin{align}
+  \frac{\kappa_s^2}{2} + \frac{\kappa^4}{8} - 
+    \frac{\Lambda}{2}\kappa^2 = \kappa_0^4 - \frac{\Lambda}{2}\kappa_0^2.
+  \label{eqn:curvODE2}
+\end{align}
+Assuming $\kappa_s \neq 0$, this differential equation is separable, and
+can be solved analytically using Mathematica. For impermeable vesicles,
+it is possible for the curvature to be
+periodic~\cite{vee-raj-bir-pur2009}. However, the solution
+of~\eqref{eqn:curvODE2} depends on the {\em EllipticF} function, and it
+can not be made periodic. Therefore, it the only solution
+of~\eqref{eqn:curvODE2} is $\kappa(s) = \kappa_0$, meaning that the
+steady state shape is a circle. By the inextensibility condition, the
+steady state vesicle has a radius of $L/2\pi$, so its curvature and
+tension are
+\begin{align}
+  \kappa = \frac{2\pi}{L}, \: \Lambda = \frac{2\pi^2}{L^2}.
+  \label{eqn:SSshape}
+\end{align}
+Note that in contrast to a impermeable vesicle, the final tension is
+positive rather than negative.
+
+In addition to computing the steady shape, we can compute the transient
+area of the vesicle. Parameterizing the vesicle with $\xx$, its area is
 \begin{align}
@@
 \end{align}
-The time derivative of $A(t)$ includes terms due to the time derivative
-of $\xx \cdot \nn$, and a term due to interface
-stretching~\cite{lai-tse-hua2008}. However, this second term is zero
+The derivative of $A(t)$ includes terms due to the time derivative of
+$\xx \cdot \nn$, and a term due to interface
+stretching~\cite{lai-tse-hua2008}. However, the stretching term is zero
 because of the local inextensibility condition. Therefore,
@@
   \int_\gamma (\xx \cdot \dot{\nn})\, ds 
+    = \int_\gamma \left(\xx \cdot \dot{\xx}_s^\perp \right)
     = -\int_\gamma \left(\xx^\perp \cdot \dot{\xx}_s\right)\, ds 
@@
 \end{align}
-where the last equality comes follows from the divergence theorem.
-Finally, using integration by parts and the Frenet-Serret identities, we
-have
+where the last equality follows from the incompressibility of the
+single-layer potential and the divergence theorem.  Finally, using
+integration by parts and the Frenet-Serret identities, we have
 \begin{align}
@@
     (\sigma \xx_s)_s \right) \cdot \nn \, ds \\
-  &= \beta \int_\gamma \left(-\xx_{sss} + \sigma \xx_s 
+  &= -\beta \int_\gamma \left(-\xx_{sss} + \sigma \xx_s 
     \right) \cdot \kappa \xx_s \, ds \\
-  &= \beta \int_\gamma \left(\xx_{ss} \cdot 
+  &= -\beta \int_\gamma \left(\xx_{ss} \cdot 
     (\kappa \xx_s)_s + \kappa \sigma \right) \, ds \\
-  &= \beta \int_\gamma \left(\kappa (\xx_{ss} \cdot \xx_{ss}) + 
+  &= -\beta \int_\gamma \left(\kappa (\xx_{ss} \cdot \xx_{ss}) + 
     \kappa_s (\xx_{ss} \cdot \xx_s) + \kappa \sigma \right) 
     \, ds \\
-  &= \beta \int_\gamma \left(\kappa^3 + \kappa \sigma \right) 
+  &= -\beta \int_\gamma \left(\kappa^3 + \kappa \sigma \right) 
     \, ds.
@@
   \dot{A}(t) = \beta \int_\gamma \left(
-    -\frac{\kappa^3}{2} + \kappa \Lambda \right) \, ds.
+    \frac{\kappa^3}{2} - \kappa \Lambda \right) \, ds.
   \label{eqn:areaROC}
 \end{align}
+Note that this is consistent with the steady state curvature and
+tension~\eqref{eqn:SSshape} since these constant values result in the
+integrand in equation~\eqref{eqn:areaROC} being zero.
 
@@
 We consider a single semi-permeable vesicle in four different flow
-regimes.
+regimes. All vesicles have a length of $L=4\pi$, but the area is not
+conserved because of semi-permeability. However, the area is bounded
+above by the area of a circle with circumference $L=4\pi$. Therefore,
+$A(t) \leq 4\pi \approx 12.56$ for all simulations. For each simulation,
+we use an adaptive second-order time stepping method~\cite{qua-bir2016}.
 
@@
 \subsection{Quiescent Flow}
-\begin{itemize}
-  \item Always goes to a circle
-  \item Area formula works
-\end{itemize}
+We start by considering a semi-permeable vesicle in a quiescent flow.
+For an impermeable vesicle, the vesicle relaxes to a steady-state shape
+with negative and constant tension~\cite{kra-win-sei-lip1996}. However,
+from equation~\eqref{eqn:SSshape}, we know that a semipermeable vesicle
+will relax to a circle with positive constant tension. The area of a
+semi-permeable vesicle is governed by~\eqref{eqn:areaROC}, so we expect
+that the time to reach steady state scales with $\beta$. In
+Figure~\ref{fig:ellipseArea}, we plot the area of a vesicle with
+different permeability rates. The area is computed directly from the
+vesicle shape (solid lines) and by integrating
+equation~\eqref{eqn:areaROC} (marks) with a first-order method. We also
+include black dashed lines indicating the times, $t_{\mathrm{SS}}$, that
+the area of the vesicle first exceeds 12.4, meaning that its area is
+within 1.3\% of the steady state area.  These times are reported in
+Table~\ref{tbl:ellipseRelaxTime}, and we see that the relaxation time
+does scale with $\beta$.
 
-We consider a single semi-permeable vesicle in a quiescent flow. For
-impermeable vesicles, the vesicle relaxes to a shape where the tension
-$\Lambda$ is constant and negative~\cite{kra-win-sei-lip1996}. In the
-semi-permeable case, the area of the vesicle is governed by
-equation~\eqref{eqn:areaROC}, where $\beta > 0$. Therefore, when the
-semi-permeable vesicle reaches a steady-state shape, we have
-\begin{align}
-  \int_{\gamma} \left(-\frac{\kappa^3}{2} + \kappa \Lambda \right) \, ds
-  = 0.
-\end{align}
-Based on numerical observations, the steady-state shape is a circular
-vesicle with constant tension. Since the tension and curvature are
-constant, we can solve for the curvature in terms of the tension $\kappa
-= \sqrt{2\Lambda}$. Therefore, the steady state shape is a circle of
-radius $r = 1/\sqrt{2\Lambda}$, and therefore the length is
-\begin{align}
-  L = \frac{\sqrt{2}\pi}{\sqrt{\Lambda}},
-\end{align}
-which is constant by the local inextensibility constraint. Finally, we
-can compute the final tension in terms of the length using the formula
-\begin{align}
-  \Lambda = \frac{2\pi^2}{L^2}.
-  \label{eqn:finalTension}
-\end{align}
-Therefore, in contrast to a impermeable vesicle, the final tension is
-positive rather than negative.
+\begin{table}[htp]
+  \centering
+  \begin{tabular}{|C{1cm}|*{6}{C{2cm}}|}
+    \hline
+    $\beta$ & $10^{0}$ & $10^{-1}$ & $10^{-2}$ & 
+             $10^{-3}$ & $10^{-4}$ & $10^{-5}$ \\
+    $t_\mathrm{SS}$ & $6.45 \times 10^{0}$ & $2.00 \times 10^{1}$ & 
+                      $9.61 \times 10^{1}$ & $8.36 \times 10^{2}$ & 
+                      $8.15 \times 10^{3}$ & $8.03 \times 10^{4}$ \\
+    ratio & --- & 3.10 & 4.81 & 8.71 & 9.74 & 9.85 \\
+    \hline
+  \end{tabular}
+  \caption{\label{tbl:ellipseRelaxTime} The time, $t_{\mathrm{SS}}$, for
+  a semi-permeable vesicle to reach steady state.}
+\end{table}
 
-We start by simulating a star-shaped vesicle in a quiescent flow with
-semi-permeability rate $\beta=1$ (Figure~\ref{fig:starShape}). To
-perform this simulation, we use an adaptive second-order time stepping
-method~\cite{qua-bir2016}. The times and reduced areas are in the
-titles, and note that the shapes are not eqiuspaced in time.
 \begin{figure}[htp]
-  \begin{minipage}{0.55\textwidth}
-    \input{figures/starRelaxation1.tikz}
-    \input{figures/starRelaxation2.tikz}
-    \input{figures/starRelaxation3.tikz}
-    \input{figures/starRelaxation4.tikz}
-    \input{figures/starRelaxation5.tikz}
-    \input{figures/starRelaxation6.tikz}
-  \end{minipage}
-  \hfill
-  \begin{minipage}{0.4\textwidth}
-  \input{figures/starAreaDeriv.tikz}
-  \end{minipage}
-  \caption{\label{fig:starShape} A initially star-shaped semi-permeable
-  vesicle in a shear quiescent flow with $\beta=1$. Note that the time
-  steps are not equispaced. The area (red) and its derivative (blue) of
-  an initially star-shaped vesicle as a function of time. The dots
-  correspond to the time steps shown in six time steps
-  show on the left.}
+\centering
+%\ifTikz
+\input{figures/ellipseArea.tikz}
+%\fi
+  \caption{\label{fig:ellipseArea} The area of an elliptical
+  semi-permeable vesicle, with permeability rate $\beta$ in a quiescent
+  flow. The solid lines compute the area directly from the vesicle
+  shape, while the marks are computed by integrating
+  equation~\eqref{eqn:areaROC}. The dashed black lines are the times
+  when the vesicle's area is within 1\% of its maximum value of $4\pi$.}
+\end{figure}
+
+We further analyze the transient dynamics for small $\beta$ by
+considering the contribution of each term in~\eqref{eqn:vesVelocity} to
+the vesicle velocity. Initially, the semi-permeability term $\beta(\ff
+\cdot \nn)\nn$ is much smaller than the velocity due to the force
+balance $\SS[\ff]$. Therefore, the velocity resembles that of an
+impermeable vesicle.  However, as the vesicle approaches the impermeable
+limit, the velocity contribution from the force balance decays below the
+contribution from semi-permeability, and we expect the vesicle to begin
+inflating due to permeability. In Figure~\ref{fig:vesVelocity}, we plot
+the velocities at three times due to force balance (blue) and
+semi-permeability (red), where $\beta = 10^{-3}$. We also plot the
+velocity of an identically initialized impermeable vesicle. At $t=0.5$,
+the velocity due to semi-permeability is small relative to the velocity
+due to force balance, and the semi-permeable vesicle velocity matches
+with the impermeable vesicle velocity. At time $t=5$, the impermeable
+vesicle is near its steady state shape, and its velocity is comparable
+to the semi-permeable velocity, so the vesicle's area begins to
+increase. Then, at time $t=50$, the impermeable vesicle is at its steady
+state, while the semi-permeable vesicle still has contributions due to
+semi-permeability and force balance. In
+Figure~\ref{fig:vesVelocityNorm}, we plot the max norm of the different
+velocity contributions as a function of time. The black dashed lines
+correspond to the times reported in Figure~\ref{fig:vesVelocity}. Again,
+we see that the velocity of a semi-permeable vesicle is initially agrees
+with the velocity of an impermeable vesicle. Then, as the velocity due
+to force balance approaches zero, the semi-permeable term becomes
+significant, causing the vesicle to inflate until it reaches a circular
+shape.
+
+\begin{figure}[htp]
+  \centering
+%  \ifTikz
+  \input{figures/ellipseVelocity1.tikz}
+  \input{figures/ellipseVelocity2.tikz}
+  \input{figures/ellipseVelocity3.tikz}
+%  \fi
+  \caption{\label{fig:vesVelocity} The velocity contributions due to
+  semi-permeability (red) and force balance (blue). The green dashed
+  line is the velocity of an impermeable vesicle with an identical
+  initial shape.}
 \end{figure}
@@
 \begin{figure}[htp]
+%  \ifTikz
+  \input{figures/ellipseVelocityNorms.tikz}
+%  \fi
+  \caption{\label{fig:vesVelocityNorm} The max norm of the velocity due
+  to the force balance (blue) and semi-permeability. Also included is
+  the velocity of an impermeable vesicle (green). The three black lines
+  correspond to the times reported in Figure~\ref{fig:vesVelocity}.}
+\end{figure}
+
+\todo[inline]{Finally, we tension and flux of a non-standard shape
+vesicle.}
+
+\begin{figure}[htp]
 \begin{minipage}{0.40\textwidth}
+\ifTikz
 \input{figures/starTension.tikz}
+\fi
 \end{minipage}
@@
   the tension is constant and positive. The constant is given by
-  equation~\eqref{eqn:finalTension}, and this value corresponds to the
+  equation~\eqref{eqn:SSshape}, and this value corresponds to the
   dashed black line.}
@@
 \begin{minipage}{0.40\textwidth}
+\ifTikz
 \input{figures/starFlux.tikz}
+\fi
 \end{minipage}
@@
 
-%\ifTikz
+\ifTikz
 \input{figures/shearPhaseDiagram.tikz} 
-%\fi
+\fi
 
@@
 
+When the semi-permeable vesicle reaches a steady-state shape, we have
+\begin{align}
+  \int_{\gamma} \left(-\frac{\kappa^3}{2} + \kappa \Lambda \right) \, ds
+  = 0.
+\end{align}
+Based on numerical observations, the steady-state shape is a circular
+vesicle with constant tension. Since the tension and curvature are
+constant, we can solve for the curvature in terms of the tension $\kappa
+= \sqrt{2\Lambda}$. Therefore, the steady state shape is a circle of
+radius $r = 1/\sqrt{2\Lambda}$, and therefore the length is
+\begin{align}
+  L = \frac{\sqrt{2}\pi}{\sqrt{\Lambda}},
+\end{align}
+which is constant by the local inextensibility constraint. Finally, we
+can compute the final tension in terms of the length using the formula
+\begin{align}
+  \Lambda = \frac{2\pi^2}{L^2}.
+\end{align}
+Therefore, in contrast to a impermeable vesicle, the final tension is
+positive rather than negative.
+
+We start by simulating a star-shaped vesicle in a quiescent flow with
+semi-permeability rate $\beta=1$ (Figure~\ref{fig:starShape}). To
+perform this simulation, we use an adaptive second-order time stepping
+method~\cite{qua-bir2016}. The times and reduced areas are in the
+titles, and note that the shapes are not eqiuspaced in time.
+\begin{figure}[htp]
+  \begin{minipage}{0.55\textwidth}
+%    \ifTikz
+    \input{figures/starRelaxation1.tikz}
+    \input{figures/starRelaxation2.tikz}
+    \input{figures/starRelaxation3.tikz}
+    \input{figures/starRelaxation4.tikz}
+    \input{figures/starRelaxation5.tikz}
+    \input{figures/starRelaxation6.tikz}
+%    \fi
+  \end{minipage}
+  \hfill
+  \begin{minipage}{0.4\textwidth}
+%  \ifTikz
+  \input{figures/starAreaDeriv.tikz}
+%  \fi
+  \end{minipage}
+  \caption{\label{fig:starShape} A initially star-shaped semi-permeable
+  vesicle in a shear quiescent flow with $\beta=1$. Note that the time
+  steps are not equispaced. The area (red) and its derivative (blue) of
+  an initially star-shaped vesicle as a function of time. The dots
+  correspond to the time steps shown in six time steps
+  show on the left.}
+\end{figure}
+
 \end{document}

### 2020-05-04 vesicle_code/examples/output/makeImages.m

@@ -2,7 +2,7 @@ addpath ../../src
 set(0,'DefaultAxesFontSize',22)
 options.savefig = false;
 
-irate = 1; % controls the speed of the visualization
+irate = 40; % controls the speed of the visualization
 
 if 0
   file = 'parabolic1VesData.bin';
@@ -35,12 +35,12 @@ end
 
 if 1
   file = 'relaxation1VesData.bin';
-%  file = '~/projects/brinkman/vesicle_code/results/relaxation1Ves/star_beta1p0e0/relaxation1VesData.bin';
-%    file = '~/projects/brinkman/vesicle_code/results/Apr142020/starBeta1em1/relaxation1VesData.bin';
+%  file = '~/projects/brinkman/vesicle_code/results/Apr142020/starBeta1em3/relaxation1VesData.bin';
+%    file = '~/projects/brinkman/vesicle_code/results/Apr232020/ellipseBeta1em5/relaxation1VesData.bin';
 %  ax = [-3 3 -3.5 3.5];
-  ax = 4*[-1 1 -1 1];
+  ax = 3*[-1 1 -1 1];
   options.confined = false;
-  beta = 0.01;
+  beta = 1e-5;
 end
 
 if 0
@@ -111,19 +111,25 @@ end
 % number of vesicles
 istart = 1;
 iend = numel(time);
-ntime = numel(time);
+%iend = 1000;
+ntime = iend;
+%ntime = numel(time);
+time = time(istart:iend);
 
 oc = curve;
 [~,~,L] = oc.geomProp([posx(:,1,1);posy(:,1,1)]);
-area = zeros(size(time));
-length = zeros(size(time));
-ra = zeros(size(time));
-incAng = zeros(size(time));
+area = zeros(ntime,1);
+length = zeros(ntime,1);
+ra = zeros(ntime,1);
+incAng = zeros(ntime,1);
 trac = zeros(2*n,nv,ntime);
 normal = zeros(2*n,nv,ntime);
 flux = zeros(n,ntime);
 cur = zeros(n,nv,ntime);
+jac = zeros(n,nv,ntime);
 sa = zeros(n,nv,ntime);
+velBen = zeros(2*n,ntime);
+velTen = zeros(2*n,ntime);
 velSLP = zeros(2*n,ntime);
[…]

### 2020-05-04 vesicle_code/src/fft1.m

@@ -71,6 +71,29 @@ end % end diffFT
 
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+function intf = intFT(f,IK)
+% intf = intFT(f,IK) computes the integral of an array of periodic
+% functions f using fourier transform. The f(:,1) is the first function,
+% f(:,2) is the second function, etc.  IK is used to speed up the code.
+% It is the index of the fourier modes so that fft and ifft can be used
+% CODE IS CURRENTLY ONLY WRITTEN FOR A SINGLE PERIODIC ARRAY RATHER THAN
+% A MATRIX WHERE EACH COLUMN IS A PERIODIC ARRAY
+
+N = numel(f);
+fh = fft(f);
+
+zeroMode = -sum(fh(2:end)./IK(2:end));
+% zero mode of the integral of f
+intfh = [zeroMode;fh(2:end)./IK(2:end)];
+% non-zero modes of the integral of f
+
+intf = real(fh(1)/N * (0:N-1)'*2*pi/N + ifft(intfh));
+% sum of the linear term and the contribution from the periodic part
+
+end % intFT
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 function IK = modes(N,nv)
 % IK = modes(N) builds the order of the fourier modes required for using
 % fft and ifft to do spectral differentiation

### 2020-05-06 vesicle_code/docs/permeableVes/main.tex
fixed typo
worked on relaxation example

@@
 \newif\ifTikz
-%\Tikztrue
-\Tikzfalse
+\Tikztrue
 
@@
   \label{eqn:jump1}
-  \jump{T\cdot\nn} &= \ff_\{mathrm{mem}, \\
+  \jump{T\cdot\nn} &= \ff_\mathrm{mem}, \\
   \label{eqn:jump2}
@@
 of~\eqref{eqn:curvODE2} depends on the {\em EllipticF} function, and it
-can not be made periodic. Therefore, it the only solution
+can not be made periodic. Therefore, the only solution
 of~\eqref{eqn:curvODE2} is $\kappa(s) = \kappa_0$, meaning that the
@@
 where the last equality follows from the incompressibility of the
-single-layer potential and the divergence theorem.  Finally, using
-integration by parts and the Frenet-Serret identities, we have
+single-layer potential and the divergence theorem.  Using integration by
+parts and the Frenet-Serret identities, we have
 \begin{align}
@@
 from equation~\eqref{eqn:SSshape}, we know that a semipermeable vesicle
-will relax to a circle with positive constant tension. The area of a
-semi-permeable vesicle is governed by~\eqref{eqn:areaROC}, so we expect
-that the time to reach steady state scales with $\beta$. In
-Figure~\ref{fig:ellipseArea}, we plot the area of a vesicle with
-different permeability rates. The area is computed directly from the
-vesicle shape (solid lines) and by integrating
+will relax to a circle with positive constant tension. Since the area of
+a semi-permeable vesicle is governed by~\eqref{eqn:areaROC}, we expect
+that the time to reach steady state, and the time required for a small
+amount of inflation, both scale with $\beta^{-1}$. We simulate a vesicle
+with initial reduced area $0.65$ with several values of $\beta$.  In
+Table~\ref{tbl:ellipseRelaxTimes}, we report the time, $t_\mathrm{SS}$,
+required for the vesicle's area to be within 1.3\% of its maximum area,
+and the time, $t_\mathrm{SP}$, required for the vesicle's area to exceed
+1.3\% of its initial area. We see that both these time scales do scale
+with $\beta^{-1}$. In Figure~\ref{fig:ellipseArea}, we plot the area of
+a vesicle with different permeability rates. The area is computed
+directly from the vesicle shape (solid lines) and by integrating
 equation~\eqref{eqn:areaROC} (marks) with a first-order method. We also
 include black dashed lines indicating the times, $t_{\mathrm{SS}}$, that
-the area of the vesicle first exceeds 12.4, meaning that its area is
-within 1.3\% of the steady state area.  These times are reported in
-Table~\ref{tbl:ellipseRelaxTime}, and we see that the relaxation time
-does scale with $\beta$.
+the vesicle is near its steady state circular shape.
 
@@
   \centering
-  \begin{tabular}{|C{1cm}|*{6}{C{2cm}}|}
+  \begin{tabular}{|C{2cm}C{3cm}C{3cm}C{3cm}C{3cm}|}
     \hline
-    $\beta$ & $10^{0}$ & $10^{-1}$ & $10^{-2}$ & 
-             $10^{-3}$ & $10^{-4}$ & $10^{-5}$ \\
-    $t_\mathrm{SS}$ & $6.45 \times 10^{0}$ & $2.00 \times 10^{1}$ & 
-                      $9.61 \times 10^{1}$ & $8.36 \times 10^{2}$ & 
-                      $8.15 \times 10^{3}$ & $8.03 \times 10^{4}$ \\
-    ratio & --- & 3.10 & 4.81 & 8.71 & 9.74 & 9.85 \\
+    $\beta$ & $t_\mathrm{SS}$ & ratio & $t_\mathrm{SP}$ & ratio \\
+    \hline
+    $10^{0}$  & $6.45 \times 10^{0}$ & ---  
+              & $2.17 \times 10^{-2}$ & --- \\ 
+    $10^{-1}$ & $2.00 \times 10^{1}$ & 3.10 & 
+                $1.25 \times 10^{-1}$ & 5.76 \\
+    $10^{-2}$ & $9.61 \times 10^{1}$ & 4.81 & 
+                $1.59 \times 10^{0}$ & 12.72 \\
+    $10^{-3}$ & $8.36 \times 10^{2}$ & 8.71 & 
+                $2.19 \times 10^{1}$ & 13.77 \\
+    $10^{-4}$ & $8.15 \times 10^{3}$ & 9.74 & 
+                $2.14 \times 10^{2}$ & 9.77 \\
+    $10^{-5}$ & $8.03 \times 10^{4}$ & 9.85 & 
+                $2.20 \times 10^{3}$ & 10.14 \\
     \hline
   \end{tabular}
-  \caption{\label{tbl:ellipseRelaxTime} The time, $t_{\mathrm{SS}}$, for
-  a semi-permeable vesicle to reach steady state.}
+  \caption{\label{tbl:ellipseRelaxTimes} The time for a semi-permeable
+  vesicle to reach relaxation time ($t_\mathrm{SS}$) and to begin
+  inflating ($t_\mathrm{SP}$).}
 \end{table}
@@
 \centering
-%\ifTikz
+\ifTikz
 \input{figures/ellipseArea.tikz}
-%\fi
+\fi
   \caption{\label{fig:ellipseArea} The area of an elliptical
@@
   \centering
-%  \ifTikz
+  \ifTikz
   \input{figures/ellipseVelocity1.tikz}
@@
   \input{figures/ellipseVelocity3.tikz}
-%  \fi
+  \fi
   \caption{\label{fig:vesVelocity} The velocity contributions due to
@@
 \begin{figure}[htp]
-%  \ifTikz
+  \ifTikz
   \input{figures/ellipseVelocityNorms.tikz}
-%  \fi
+  \fi
   \caption{\label{fig:vesVelocityNorm} The max norm of the velocity due
@@
 
-\todo[inline]{Finally, we tension and flux of a non-standard shape
-vesicle.}
+Finally, we consider a semi-permeable vesicle with initial regions of
+positive and negative curvature. The permeability rate is $\beta=1$, and
+several time steps are illustrated in Figure~\ref{fig:starShape}. As
+expected, the steady state shape is circular. The vesicle undergoes
+three general behaviors: (i) for $t \in (0,1.6 \times 10^{-2})$, the
+vesicle has a net negative flux resulting in a loss of area; (ii) for $t
+\in (1.6 \times 10^{-2},1.0 \times 10^{0})$, the vesicle has a net
+positive flux and the tension most of the membrane is undergoing
+negative tension; (iii) for $t \in (1.0 \times 10^{0},2.0 \times
+10^{0})$, the vesicle is near its steady state and transitions to a
+positive constant tension.
+
+We compute the tension $\Lambda$ and the flux $(-\xx_{ssss} + (\sigma
+\xx_s)_s) \cdot \nn$ and plot the results in
+Figure~\ref{fig:starTensionFlux}.  In the first time interval, the
+vesicle deflates. Near the points of largest negative curvature, there
+is a large negative tension and large inflow (positive flux).
+Correspondingly, near the points with largest positive curvature, there
+is a small tension and outflow (negative flux). In the second time
+interval, the tension is negative and the flux is positive nearly
+everywhere. The regions of large negative curvature correspond to
+regions with the largest negative tension and the most inflow. Finally,
+in the last time interval, the tension transitions to a positive
+constant function, the flux transitions to zero, and the result is a
+steady state circular vesicle with positive constant tension.
 
 \begin{figure}[htp]
-\begin{minipage}{0.40\textwidth}
     \ifTikz
-\input{figures/starTension.tikz}
+    \input{figures/starRelaxation1.tikz}
+    \quad
+    \input{figures/starRelaxation2.tikz}
+    \quad
+    \input{figures/starRelaxation3.tikz}
+    \quad
+    \input{figures/starRelaxation4.tikz}
+    \quad
+    \input{figures/starRelaxation5.tikz}
     \fi
-\end{minipage}
-\hfill
-\begin{minipage}{0.55\textwidth}
-  \centering
-\includegraphics[width=0.32\textwidth]{figures/StarTensionTime1.pdf}
-\includegraphics[width=0.32\textwidth]{figures/StarTensionTime2.pdf}
-\includegraphics[width=0.32\textwidth]{figures/StarTensionTime3.pdf} \\
-\includegraphics[width=0.32\textwidth]{figures/StarTensionTime4.pdf}
-\includegraphics[width=0.32\textwidth]{figures/StarTensionTime5.pdf}
-\includegraphics[width=0.32\textwidth]{figures/StarTensionTime6.pdf}
-\end{minipage}
-  \caption{\label{fig:starTension} The tension of the time steps shown
-  in Figure~\ref{fig:starShape}. The tension at the time horizon $T=1$
-  is also included. At this point, the vesicle is nearly circular and
-  the tension is constant and positive. The constant is given by
-  equation~\eqref{eqn:SSshape}, and this value corresponds to the
-  dashed black line.}
+  \caption{\label{fig:starShape} An initially star-shaped semi-permeable
+  vesicle in a shear quiescent flow with $\beta=1$. Note that the time
+  steps are not equispaced.}
 \end{figure}
@@
 \begin{figure}[htp]
-\begin{minipage}{0.40\textwidth}
-\ifTikz
-\input{figures/starFlux.tikz}
-\fi
-\end{minipage}
-\hfill
-\begin{minipage}{0.55\textwidth}
-\includegraphics[width=0.32\textwidth]{figures/StarFluxTime1.pdf}
-\includegraphics[width=0.32\textwidth]{figures/StarFluxTime2.pdf}
-\includegraphics[width=0.32\textwidth]{figures/StarFluxTime3.pdf} \\
-\includegraphics[width=0.32\textwidth]{figures/StarFluxTime4.pdf}
-\includegraphics[width=0.32\textwidth]{figures/StarFluxTime5.pdf}
-\includegraphics[width=0.32\textwidth]{figures/StarFluxTime6.pdf}
-\end{minipage}
-  \caption{\label{fig:starFlux} The flux of the time steps shown in
-  Figure~\ref{fig:starShape}. The tension at the time horizon $T=1$ is
-  also included. At this point, the vesicle is nearly circular and there
-  is no flux.}
+  \centering
+  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
+  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
+  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
+  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
+  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime5.pdf}
+
+  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
+  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
+  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
+  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
+  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
+  \caption{\label{fig:starTensionFlux} The vesicle tension (top) and
+  flux (bottom) of the semi-permeable vesicle in quiescent
+  flow with $\beta=1$.}
 \end{figure}
-
-%\begin{figure}[htp]
-%  \input{figures/starFlux.tikz}
-%  \caption{\label{fig:starFlux} The flux of the time steps shown in
-%  Figure~\ref{fig:starShape}. The tension at the time horizon $T=1$ is
-%  also included. At this point, the vesicle is nearly circular and their
-%  is no flux.}
-%\end{figure}
 
@@
 
-\ifTikz
-\input{figures/shearPhaseDiagram.tikz} 
-\fi
+%\ifTikz
+%\input{figures/shearPhaseDiagram.tikz} 
+%\fi
 
@@
 
-\ifTikz
-\input{figures/extensionalPhaseDiagram.tikz}
-\fi
+%\ifTikz
+%\input{figures/extensionalPhaseDiagram.tikz}
+%\fi
 
@@
 
- \newpage
- \paragraph{\bf \Huge OLD STUFF}
-
-%%%%%%%%%%%%%%
-\section{{$\Theta-L$} formulation}
-Here, we attempt to apply the formulation described by Sohn et
-al.~\cite{soh-tse-li-voi-low2010} to a semi-permeable vesicle.  In the
-semi-permeable formulation, the vesicle velocity is
-\begin{align}
-  \pderiv{\XX}{t} = \uu(\XX(t)) + \beta (\ff \cdot \nn) \nn.
-\end{align}
-In the {$\Theta-L$} variables, we require a normal velocity $V$, and a
-tangential velocity $T$. Since the inextensibility condition is $T_s +
-\kappa V = 0$, a condition for the vesicle velocity is
-\begin{align}
-  (\uu \cdot \ss)_s = -\kappa(\beta (\ff \cdot \nn) + 
-      \uu \cdot \nn).
-\end{align}
-This equation can be solved following equations (32)--(39)
-in~\cite{soh-tse-li-voi-low2010}, with the only difference being that
-$\tilde{\uu}$ satisfies
-\begin{align}
-  (\tilde{\uu} \cdot \ss)_s + \kappa(\tilde{\uu} \cdot \nn) =
-    -(\vv \cdot \ss)_s - \kappa(\vv \cdot \nn) 
-    - \beta\kappa(\ff \cdot \nn).
-\end{align}
-Compared to equation (40), only the last term is new.
-
-%%%%%%%%%%%%%%
-Finally, we write the time stepping method in matrix form as
-\begin{align}
-  A \left(
-    \begin{array}{c}
-      \xx^{N+1} \\ \sigma^{N+1}
-    \end{array}
-  \right) = 
-  \left(
-    \begin{array}{c}
-      \xx^{N} + \Delta t \uu_\infty(\xx^N) \\ \mathbf{1}
-    \end{array}
-  \right),
-\end{align}
-where
-\begin{align}
- A = \left(
-  \begin{array}{cc}
-    I + \Delta t \beta P^N B^N + \Delta t \SS^N B^N & 
-    -\Delta t P^N T^N - \Delta t \SS^N T^N \\
-    D^N & 0
-  \end{array}
-  \right).
-\end{align}
-
-\section{Area of a Vesicle}
-The area inside a single vesicle $\gamma$ parameterized with $\xx$ is
-\begin{align}
-  A(t) = \int_{\gamma} (\xx \cdot \nn)\, ds = 
-    \int_{0}^{2\pi} \left(\xx \cdot \pderiv{\xx}{\theta}^\perp\right)
-    \, d\theta.
-\end{align}
-Taking the time derivative of $A(t)$,
-\begin{align}
-  \dot{A}(t) &= \int_{0}^{2\pi} \left(
-    \dot{\xx} \cdot \pderiv{\xx}{\theta}^{\perp} + 
-    \xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right) \\
-    \, d\theta.
-  &= \int_{0}^{2\pi} \left(
-    (\dot{\xx} \cdot \nn)\|\xx'(\theta)\| \right) d\theta +
-     \int_{0}^{2\pi}
-    \xx \cdot \frac{d}{dt}\left(\nn |\frac{d\xx}{d\theta}| \right)
-\end{align}
-
-\begin{align}
-  A(t) = \frac{1}{2}\int_{\gamma} (\xx \cdot \nn)\, ds = 
-    \frac{1}{2}\int_{0}^{2\pi} \left(\xx \cdot \pderiv{\xx}{\theta}^\perp\right)
-    \, d\theta.
-\end{align}
-Taking the time derivative of $A(t)$,
-\begin{align}
-  \dot{A}(t) &= \frac{1}{2}\int_{0}^{2\pi} \left(\dot{\xx} \cdot
-  \pderiv{\xx}{\theta}^{\perp} + 
-    \xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right) d\theta, \\
-  &= \frac{1}{2}
-  \int_{0}^{2\pi}(\dot{\xx}\cdot\nn)\left\|\pderiv{\xx}{\theta}\right\|d\theta +
-     \frac{1}{2}\int_{0}^{2\pi}
-    \left(\xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right)d\theta, \\
-  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds +
-  \frac{1}{2}\int_{0}^{2\pi}\left(\xx \cdot \pderiv{}{t}\left(\nn
-  \left\|\pderiv{\xx}{\theta}\right\|\right)\right)d\theta, \\
-  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds + \frac{1}{2}
-  \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds + \frac{1}{2}\int_{0}^{2\pi}
-  \frac{\xx\cdot\nn}{\left\|\pderiv{\xx}{\theta}\right\|}
-  \left(\pderiv{\xx}{\theta}\cdot
-  \pderiv{\dot{\xx}}{\theta}\right)d\theta \\
-  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds + \frac{1}{2}
-  \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds + \frac{1}{2}\int_{\gamma}
-  (\xx\cdot\nn) (\xx_s \cdot \dot{\xx}_s)\, ds.
-\end{align}
-To satisfy the inextensibilty condition, $\xx_s \cdot \dot{\xx}_s = 0$.
-Therefore the time derivative of $A(t)$ is
-\begin{align}
-     \dot{A}(t) &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds
-     + \frac{1}{2} \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds.
-\end{align}
-which we re-write as
-\begin{align}
-    \dot{A}(t) &= \frac{\beta}{2}
-    \int_{\gamma}\left(\ff\cdot\nn\right)ds-\frac{1}{2}\int_{\gamma}\left(\xx^{\perp}\cdot\dot{\xx}_s\right) ds.
-\end{align}
-Applying integration by parts,
-\begin{align}
-    \dot{A}(t) &= \frac{\beta}{2}
-    \int_{\gamma}\left(\ff\cdot\nn\right)ds+\frac{1}{2}\int_{\gamma}\left(\xx^{\perp}_s\cdot\dot{\xx}\right) ds,
-\end{align}
-which we re-write as
-\begin{align}
-    \dot{A}(t) &= \frac{\beta}{2}
-    \int_{\gamma}\left(\ff\cdot\nn\right)ds+\frac{1}{2}\int_{\gamma}\left(\dot{\xx}\cdot\nn\right),\\
-    \dot{A}(t) &= \beta \int_{\gamma}\left(\ff\cdot\nn\right)ds.
-\end{align}
-
-At steady state,
-\begin{align}
-    \dot{A}(t) &= \beta \int_{\gamma}\left(\ff\cdot\nn\right)ds =0.
-\end{align}
-We now replace $\ff$ with its definition and apply integration by parts
-\begin{align}
-   0=\beta\int_{\gamma} 
-    (-k_b\xx_{ssss}+(\sigma\xx_s)_s)\cdot\nn\, ds =
-   \beta\int_{\gamma}\left(k_b\xx_{sss}-\sigma\xx_s\right)\cdot
-     \nn_s\, ds
-\end{align}
-From the Frenet-Serret formulas, we have 
-\begin{align}
-     -\beta\int_{\gamma}
-     \left(k_b\xx_{sss}-\sigma\xx_s\right)\cdot\kappa\xx_s ds &=0.
-\end{align}
-
-Applying integration by parts and Frenet-Serret again
-\begin{align}
-     \beta\int_{\gamma}
-     k_b\kappa\left(\xx_{ss}\cdot\xx_{ss}\right)ds + \beta
-     \int_{\gamma} k_b \kappa_s(\xx_{ss} \cdot \xx_s)ds +\beta\int_{\gamma}\kappa\sigma ds  &= 0,\\
-    \beta\int_{\gamma} k_b\kappa(\kappa\nn \cdot
-     \kappa\nn)+ \beta \int_{\gamma} k_b \kappa_s(\xx_{ss} \cdot
-     \xx_s)ds +\beta\int_{\gamma}\kappa\sigma ds &= 0,
-\end{align}
-which we re-write as
-\begin{align}
-   \beta\int_{\gamma}k_b\kappa^3 ds + \beta \int_{\gamma} k_b
-   \kappa_s(\xx_{ss} \cdot \xx_s)ds +\beta\int_{\gamma} \kappa\sigma ds = 0.
-\end{align}
-Applying Frenet-serret again,
-\begin{align}
-    \beta\int_{\gamma}k_b\kappa^3 ds + \beta \int_{\gamma} k_b
-    \kappa_s(\kappa\nn \cdot \TT)ds +\beta\int_{\gamma} \kappa\sigma ds = 0, \\
-    \beta\int_{\gamma}k_b\kappa^3 ds +\beta\int_{\gamma} \kappa\sigma ds  = 0.
-\end{align}
-
-\section{Including a concentration field}
-Based on the work of Yao and Mori~\cite{yao-mor2017}, we introduce a
-chemical concentration field $c$.  The concentration field is governed
-by the advection-diffusion equation
-\begin{align}
-  \pderiv{c}{t} + \nabla \cdot (\uu c) = D\Delta c.
-\end{align}
-If the concentration is diffusion dominated (zero Peclet number), then
-the concentration satisfies
-\begin{align}
-  \Delta c = 0, \quad \xx \in \RR^2.
-\end{align}
-The boundary conditions of the concentration field on the vesicle
-$\gamma$ are
-\begin{align}
-  (\uu c - D\nabla c) \cdot \nn = c \pderiv{\xx}{t} \cdot \nn + 
-    j_c + j_p,
-\end{align}
-where $j_c$ and $j_p$ are the transmembrane chemical flux due to passive
-transport and active transport (pumps), respectively.  In the zero
-Peclet number limit, the absence of an active transport mechanism, and
-the choice for the passive flux, the boundary condition of the
-concentration field is
-\begin{align}
-  -D\pderiv{c}{\nn} = c \pderiv{\xx}{t} + 
-    k_c \jump{c}, \quad \xx \in \gamma.
-\end{align}
-To couple the vesicle dynamics to the concentration, there is a
-difference between the fluid velocity and vesicle velocity
-\begin{align}
-  \uu - \pderiv{\xx}{t} = j_w \nn,
-\end{align}
-where $j_w$ is the water flux through the vesicle.  This is the
-osmophoretic flow.  In~\cite{yao-mor2017}, this flux is
-\begin{align}
-  j_w = -k_w(RT\jump{c} + \ff_\text{mem} \cdot \nn).
-\end{align}
-In our current implementation, we drop the $RT\jump{c}$ term, and
-let $\beta = k_w$.
-
-\section{Preliminary results}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=.9\textwidth]{figures/1.jpg}
-	\includegraphics[width=.9\textwidth]{figures/2.jpg}
-	\includegraphics[width=.9\textwidth]{figures/3.jpg}
-	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0$.}
+% \newpage
+% \paragraph{\bf \Huge OLD STUFF}
+%
+%%%%%%%%%%%%%%%
+%\section{{$\Theta-L$} formulation}
+%Here, we attempt to apply the formulation described by Sohn et
+%al.~\cite{soh-tse-li-voi-low2010} to a semi-permeable vesicle.  In the
+%semi-permeable formulation, the vesicle velocity is
+%\begin{align}
+%  \pderiv{\XX}{t} = \uu(\XX(t)) + \beta (\ff \cdot \nn) \nn.
+%\end{align}
+%In the {$\Theta-L$} variables, we require a normal velocity $V$, and a
+%tangential velocity $T$. Since the inextensibility condition is $T_s +
+%\kappa V = 0$, a condition for the vesicle velocity is
+%\begin{align}
+%  (\uu \cdot \ss)_s = -\kappa(\beta (\ff \cdot \nn) + 
+%      \uu \cdot \nn).
+%\end{align}
+%This equation can be solved following equations (32)--(39)
+%in~\cite{soh-tse-li-voi-low2010}, with the only difference being that
+%$\tilde{\uu}$ satisfies
+%\begin{align}
+%  (\tilde{\uu} \cdot \ss)_s + \kappa(\tilde{\uu} \cdot \nn) =
+%    -(\vv \cdot \ss)_s - \kappa(\vv \cdot \nn) 
+%    - \beta\kappa(\ff \cdot \nn).
+%\end{align}
+%Compared to equation (40), only the last term is new.
+%
+%
+%%%%%%%%%%%%%%%
+%Finally, we write the time stepping method in matrix form as
+%\begin{align}
+%  A \left(
+%    \begin{array}{c}
+%      \xx^{N+1} \\ \sigma^{N+1}
+%    \end{array}
+%  \right) = 
+%  \left(
+%    \begin{array}{c}
+%      \xx^{N} + \Delta t \uu_\infty(\xx^N) \\ \mathbf{1}
+%    \end{array}
+%  \right),
+%\end{align}
+%where
+%\begin{align}
+% A = \left(
+%  \begin{array}{cc}
+%    I + \Delta t \beta P^N B^N + \Delta t \SS^N B^N & 
+%    -\Delta t P^N T^N - \Delta t \SS^N T^N \\
+%    D^N & 0
+%  \end{array}
+%  \right).
+%\end{align}
+%
+%\section{Area of a Vesicle}
+%The area inside a single vesicle $\gamma$ parameterized with $\xx$ is
+%\begin{align}
+%  A(t) = \int_{\gamma} (\xx \cdot \nn)\, ds = 
+%    \int_{0}^{2\pi} \left(\xx \cdot \pderiv{\xx}{\theta}^\perp\right)
+%    \, d\theta.
+%\end{align}
+%Taking the time derivative of $A(t)$,
+%\begin{align}
+%  \dot{A}(t) &= \int_{0}^{2\pi} \left(
+%    \dot{\xx} \cdot \pderiv{\xx}{\theta}^{\perp} + 
+%    \xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right) \\
+%    \, d\theta.
+%  &= \int_{0}^{2\pi} \left(
+%    (\dot{\xx} \cdot \nn)\|\xx'(\theta)\| \right) d\theta +
+%     \int_{0}^{2\pi}
+%    \xx \cdot \frac{d}{dt}\left(\nn |\frac{d\xx}{d\theta}| \right)
+%\end{align}
+%
+%
+%
+%\begin{align}
+%  A(t) = \frac{1}{2}\int_{\gamma} (\xx \cdot \nn)\, ds = 
+%    \frac{1}{2}\int_{0}^{2\pi} \left(\xx \cdot \pderiv{\xx}{\theta}^\perp\right)
+%    \, d\theta.
+%\end{align}
+%Taking the time derivative of $A(t)$,
+%\begin{align}
+%  \dot{A}(t) &= \frac{1}{2}\int_{0}^{2\pi} \left(\dot{\xx} \cdot
+%  \pderiv{\xx}{\theta}^{\perp} + 
+%    \xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right) d\theta, \\
+%  &= \frac{1}{2}
+%  \int_{0}^{2\pi}(\dot{\xx}\cdot\nn)\left\|\pderiv{\xx}{\theta}\right\|d\theta +
+%     \frac{1}{2}\int_{0}^{2\pi}
+%    \left(\xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right)d\theta, \\
+%  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds +
+%  \frac{1}{2}\int_{0}^{2\pi}\left(\xx \cdot \pderiv{}{t}\left(\nn
+%  \left\|\pderiv{\xx}{\theta}\right\|\right)\right)d\theta, \\
+%  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds + \frac{1}{2}
+%  \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds + \frac{1}{2}\int_{0}^{2\pi}
+%  \frac{\xx\cdot\nn}{\left\|\pderiv{\xx}{\theta}\right\|}
+%  \left(\pderiv{\xx}{\theta}\cdot
+%  \pderiv{\dot{\xx}}{\theta}\right)d\theta \\
+%  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds + \frac{1}{2}
+%  \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds + \frac{1}{2}\int_{\gamma}
+%  (\xx\cdot\nn) (\xx_s \cdot \dot{\xx}_s)\, ds.
+%\end{align}
+%To satisfy the inextensibilty condition, $\xx_s \cdot \dot{\xx}_s = 0$.
+%Therefore the time derivative of $A(t)$ is
+%\begin{align}
+%     \dot{A}(t) &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds
+%     + \frac{1}{2} \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds.
+%\end{align}
+%which we re-write as
+%\begin{align}
+%    \dot{A}(t) &= \frac{\beta}{2}
+%    \int_{\gamma}\left(\ff\cdot\nn\right)ds-\frac{1}{2}\int_{\gamma}\left(\xx^{\perp}\cdot\dot{\xx}_s\right) ds.
+%\end{align}
+%Applying integration by parts,
+%\begin{align}
+%    \dot{A}(t) &= \frac{\beta}{2}
+%    \int_{\gamma}\left(\ff\cdot\nn\right)ds+\frac{1}{2}\int_{\gamma}\left(\xx^{\perp}_s\cdot\dot{\xx}\right) ds,
+%\end{align}
+%which we re-write as
+%\begin{align}
+%    \dot{A}(t) &= \frac{\beta}{2}
+%    \int_{\gamma}\left(\ff\cdot\nn\right)ds+\frac{1}{2}\int_{\gamma}\left(\dot{\xx}\cdot\nn\right),\\
+%    \dot{A}(t) &= \beta \int_{\gamma}\left(\ff\cdot\nn\right)ds.
+%\end{align}
+%
+%
+%At steady state,
+%\begin{align}
+%    \dot{A}(t) &= \beta \int_{\gamma}\left(\ff\cdot\nn\right)ds =0.
+%\end{align}
+%We now replace $\ff$ with its definition and apply integration by parts
+%\begin{align}
+%   0=\beta\int_{\gamma} 
+%    (-k_b\xx_{ssss}+(\sigma\xx_s)_s)\cdot\nn\, ds =
+%   \beta\int_{\gamma}\left(k_b\xx_{sss}-\sigma\xx_s\right)\cdot
+%     \nn_s\, ds
+%\end{align}
+%From the Frenet-Serret formulas, we have 
+%\begin{align}
+%     -\beta\int_{\gamma}
+%     \left(k_b\xx_{sss}-\sigma\xx_s\right)\cdot\kappa\xx_s ds &=0.
+%\end{align}
+%
+%Applying integration by parts and Frenet-Serret again
+%\begin{align}
+%     \beta\int_{\gamma}
+%     k_b\kappa\left(\xx_{ss}\cdot\xx_{ss}\right)ds + \beta
+%     \int_{\gamma} k_b \kappa_s(\xx_{ss} \cdot \xx_s)ds +\beta\int_{\gamma}\kappa\sigma ds  &= 0,\\
+%    \beta\int_{\gamma} k_b\kappa(\kappa\nn \cdot
+%     \kappa\nn)+ \beta \int_{\gamma} k_b \kappa_s(\xx_{ss} \cdot
+%     \xx_s)ds +\beta\int_{\gamma}\kappa\sigma ds &= 0,
+%\end{align}
+%which we re-write as
+%\begin{align}
+%   \beta\int_{\gamma}k_b\kappa^3 ds + \beta \int_{\gamma} k_b
+%   \kappa_s(\xx_{ss} \cdot \xx_s)ds +\beta\int_{\gamma} \kappa\sigma ds = 0.
+%\end{align}
+%Applying Frenet-serret again,
+%\begin{align}
+%    \beta\int_{\gamma}k_b\kappa^3 ds + \beta \int_{\gamma} k_b
+%    \kappa_s(\kappa\nn \cdot \TT)ds +\beta\int_{\gamma} \kappa\sigma ds = 0, \\
+%    \beta\int_{\gamma}k_b\kappa^3 ds +\beta\int_{\gamma} \kappa\sigma ds  = 0.
+%\end{align}
+%
+%
+%\section{Including a concentration field}
+%Based on the work of Yao and Mori~\cite{yao-mor2017}, we introduce a
+%chemical concentration field $c$.  The concentration field is governed
+%by the advection-diffusion equation
+%\begin{align}
+%  \pderiv{c}{t} + \nabla \cdot (\uu c) = D\Delta c.
+%\end{align}
+%If the concentration is diffusion dominated (zero Peclet number), then
+%the concentration satisfies
+%\begin{align}
+%  \Delta c = 0, \quad \xx \in \RR^2.
+%\end{align}
+%The boundary conditions of the concentration field on the vesicle
+%$\gamma$ are
+%\begin{align}
+%  (\uu c - D\nabla c) \cdot \nn = c \pderiv{\xx}{t} \cdot \nn + 
+%    j_c + j_p,
+%\end{align}
+%where $j_c$ and $j_p$ are the transmembrane chemical flux due to passive
+%transport and active transport (pumps), respectively.  In the zero
+%Peclet number limit, the absence of an active transport mechanism, and
+%the choice for the passive flux, the boundary condition of the
+%concentration field is
+%\begin{align}
+%  -D\pderiv{c}{\nn} = c \pderiv{\xx}{t} + 
+%    k_c \jump{c}, \quad \xx \in \gamma.
+%\end{align}
+%To couple the vesicle dynamics to the concentration, there is a
+%difference between the fluid velocity and vesicle velocity
+%\begin{align}
+%  \uu - \pderiv{\xx}{t} = j_w \nn,
+%\end{align}
+%where $j_w$ is the water flux through the vesicle.  This is the
+%osmophoretic flow.  In~\cite{yao-mor2017}, this flux is
+%\begin{align}
+%  j_w = -k_w(RT\jump{c} + \ff_\text{mem} \cdot \nn).
+%\end{align}
+%In our current implementation, we drop the $RT\jump{c}$ term, and
+%let $\beta = k_w$.
+%
+%\section{Preliminary results}
+%
+%
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=.9\textwidth]{figures/1.jpg}
+%	\includegraphics[width=.9\textwidth]{figures/2.jpg}
+%	\includegraphics[width=.9\textwidth]{figures/3.jpg}
+%	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0$.}
+%%	\label{Shear0}
+%\end{figure}
+%
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=.9\textwidth]{figures/4.jpg}
+%	\includegraphics[width=.9\textwidth]{figures/5.jpg}
+%	\includegraphics[width=.9\textwidth]{figures/6.jpg}
+%	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0.5$.}
+%%	\label{Shear0}
+%\end{figure}
+%
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=.9\textwidth]{figures/7.jpg}
+%	\includegraphics[width=.9\textwidth]{figures/8.jpg}
+%	\includegraphics[width=.9\textwidth]{figures/9.jpg}
+%	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 1$.}
+%%	\label{Shear0}
+%\end{figure}
+%
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=.9\textwidth]{figures/10.jpg}
+%	\includegraphics[width=.9\textwidth]{figures/11.jpg}
+%	\includegraphics[width=.9\textwidth]{figures/12.jpg}
+%	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 2$.}
+%%	\label{Shear0}
+%\end{figure}
+% 
+% 
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=.9\textwidth]{figures/BE1.jpg}
+% 	\includegraphics[width=.9\textwidth]{figures/BE2.jpg}
+% 	\includegraphics[width=.9\textwidth]{figures/BE3.jpg}
+% 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0$.}
+%% 	\label{Shear0}
+% \end{figure}
+% 
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=.9\textwidth]{figures/BE4.jpg}
+% 	\includegraphics[width=.9\textwidth]{figures/BE5.jpg}
+% 	\includegraphics[width=.9\textwidth]{figures/BE6.jpg}
+% 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0.5$.}
+%% 	\label{Shear0}
+% \end{figure}
+% 
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=.9\textwidth]{figures/BE7.jpg}
+% 	\includegraphics[width=.9\textwidth]{figures/BE8.jpg}
+% 	\includegraphics[width=.9\textwidth]{figures/BE9.jpg}
+% 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 1$.}
+%% 	\label{Shear0}
+% \end{figure}
+% 
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=.9\textwidth]{figures/BE10.jpg}
+% 	\includegraphics[width=.9\textwidth]{figures/BE11.jpg}
+% 	\includegraphics[width=.9\textwidth]{figures/BE12.jpg}
+% 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 2$.}
 % 	\label{Shear0}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=.9\textwidth]{figures/4.jpg}
-	\includegraphics[width=.9\textwidth]{figures/5.jpg}
-	\includegraphics[width=.9\textwidth]{figures/6.jpg}
-	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0.5$.}
-%	\label{Shear0}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=.9\textwidth]{figures/7.jpg}
-	\includegraphics[width=.9\textwidth]{figures/8.jpg}
-	\includegraphics[width=.9\textwidth]{figures/9.jpg}
-	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 1$.}
-%	\label{Shear0}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=.9\textwidth]{figures/10.jpg}
-	\includegraphics[width=.9\textwidth]{figures/11.jpg}
-	\includegraphics[width=.9\textwidth]{figures/12.jpg}
-	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 2$.}
-%	\label{Shear0}
-\end{figure}
-
- \begin{figure}
- 	\centering
- 	\includegraphics[width=.9\textwidth]{figures/BE1.jpg}
- 	\includegraphics[width=.9\textwidth]{figures/BE2.jpg}
- 	\includegraphics[width=.9\textwidth]{figures/BE3.jpg}
- 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0$.}
-% 	\label{Shear0}
- \end{figure}
-
- \begin{figure}
- 	\centering
- 	\includegraphics[width=.9\textwidth]{figures/BE4.jpg}
- 	\includegraphics[width=.9\textwidth]{figures/BE5.jpg}
- 	\includegraphics[width=.9\textwidth]{figures/BE6.jpg}
- 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0.5$.}
-% 	\label{Shear0}
- \end{figure}
-
- \begin{figure}
- 	\centering
- 	\includegraphics[width=.9\textwidth]{figures/BE7.jpg}
- 	\includegraphics[width=.9\textwidth]{figures/BE8.jpg}
- 	\includegraphics[width=.9\textwidth]{figures/BE9.jpg}
- 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 1$.}
-% 	\label{Shear0}
- \end{figure}
-
- \begin{figure}
- 	\centering
- 	\includegraphics[width=.9\textwidth]{figures/BE10.jpg}
- 	\includegraphics[width=.9\textwidth]{figures/BE11.jpg}
- 	\includegraphics[width=.9\textwidth]{figures/BE12.jpg}
- 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 2$.}
- 	\label{Shear0}
- \end{figure}
-
-When the semi-permeable vesicle reaches a steady-state shape, we have
-\begin{align}
-  \int_{\gamma} \left(-\frac{\kappa^3}{2} + \kappa \Lambda \right) \, ds
-  = 0.
-\end{align}
-Based on numerical observations, the steady-state shape is a circular
-vesicle with constant tension. Since the tension and curvature are
-constant, we can solve for the curvature in terms of the tension $\kappa
-= \sqrt{2\Lambda}$. Therefore, the steady state shape is a circle of
-radius $r = 1/\sqrt{2\Lambda}$, and therefore the length is
-\begin{align}
-  L = \frac{\sqrt{2}\pi}{\sqrt{\Lambda}},
-\end{align}
-which is constant by the local inextensibility constraint. Finally, we
-can compute the final tension in terms of the length using the formula
-\begin{align}
-  \Lambda = \frac{2\pi^2}{L^2}.
-\end{align}
-Therefore, in contrast to a impermeable vesicle, the final tension is
-positive rather than negative.
-
-We start by simulating a star-shaped vesicle in a quiescent flow with
-semi-permeability rate $\beta=1$ (Figure~\ref{fig:starShape}). To
-perform this simulation, we use an adaptive second-order time stepping
-method~\cite{qua-bir2016}. The times and reduced areas are in the
-titles, and note that the shapes are not eqiuspaced in time.
-\begin{figure}[htp]
-  \begin{minipage}{0.55\textwidth}
-%    \ifTikz
-    \input{figures/starRelaxation1.tikz}
-    \input{figures/starRelaxation2.tikz}
-    \input{figures/starRelaxation3.tikz}
-    \input{figures/starRelaxation4.tikz}
-    \input{figures/starRelaxation5.tikz}
-    \input{figures/starRelaxation6.tikz}
-%    \fi
-  \end{minipage}
-  \hfill
-  \begin{minipage}{0.4\textwidth}
-%  \ifTikz
-  \input{figures/starAreaDeriv.tikz}
-%  \fi
-  \end{minipage}
-  \caption{\label{fig:starShape} A initially star-shaped semi-permeable
-  vesicle in a shear quiescent flow with $\beta=1$. Note that the time
-  steps are not equispaced. The area (red) and its derivative (blue) of
-  an initially star-shaped vesicle as a function of time. The dots
-  correspond to the time steps shown in six time steps
-  show on the left.}
-\end{figure}
+% \end{figure}
+%
+%When the semi-permeable vesicle reaches a steady-state shape, we have
+%\begin{align}
+%  \int_{\gamma} \left(-\frac{\kappa^3}{2} + \kappa \Lambda \right) \, ds
+%  = 0.
+%\end{align}
+%Based on numerical observations, the steady-state shape is a circular
+%vesicle with constant tension. Since the tension and curvature are
+%constant, we can solve for the curvature in terms of the tension $\kappa
+%= \sqrt{2\Lambda}$. Therefore, the steady state shape is a circle of
+%radius $r = 1/\sqrt{2\Lambda}$, and therefore the length is
+%\begin{align}
+%  L = \frac{\sqrt{2}\pi}{\sqrt{\Lambda}},
+%\end{align}
+%which is constant by the local inextensibility constraint. Finally, we
+%can compute the final tension in terms of the length using the formula
+%\begin{align}
+%  \Lambda = \frac{2\pi^2}{L^2}.
+%\end{align}
+%Therefore, in contrast to a impermeable vesicle, the final tension is
+%positive rather than negative.
+%
+%We start by simulating a star-shaped vesicle in a quiescent flow with
+%semi-permeability rate $\beta=1$ (Figure~\ref{fig:starShape}). To
+%perform this simulation, we use an adaptive second-order time stepping
+%method~\cite{qua-bir2016}. The times and reduced areas are in the
+%titles, and note that the shapes are not eqiuspaced in time.
+%\begin{figure}[htp]
+%  \begin{minipage}{0.55\textwidth}
+%%    \ifTikz
+%    \input{figures/starRelaxation1.tikz}
+%    \input{figures/starRelaxation2.tikz}
+%    \input{figures/starRelaxation3.tikz}
+%    \input{figures/starRelaxation4.tikz}
+%    \input{figures/starRelaxation5.tikz}
+%    \input{figures/starRelaxation6.tikz}
+%%    \fi
+%  \end{minipage}
+%  \hfill
+%  \begin{minipage}{0.4\textwidth}
+%%  \ifTikz
+%  \input{figures/starAreaDeriv.tikz}
+%%  \fi
+%  \end{minipage}
+%%  \caption{\label{fig:starShape} A initially star-shaped semi-permeable
+%%  vesicle in a shear quiescent flow with $\beta=1$. Note that the time
+%%  steps are not equispaced. The area (red) and its derivative (blue) of
+%%  an initially star-shaped vesicle as a function of time. The dots
+%%  correspond to the time steps shown in six time steps
+%%  show on the left.}
+%\end{figure}
+%
+%\begin{table}[htp]
+%  \centering
+%  \begin{tabular}{|C{1cm}|*{6}{C{2cm}}|}
+%    \hline
+%    $\beta$ & $10^{0}$ & $10^{-1}$ & $10^{-2}$ & 
+%             $10^{-3}$ & $10^{-4}$ & $10^{-5}$ \\
+%    $t_\mathrm{SS}$ & $6.45 \times 10^{0}$ & $2.00 \times 10^{1}$ & 
+%                      $9.61 \times 10^{1}$ & $8.36 \times 10^{2}$ & 
+%                      $8.15 \times 10^{3}$ & $8.03 \times 10^{4}$ \\
+%    ratio & --- & 3.10 & 4.81 & 8.71 & 9.74 & 9.85 \\
+%    \hline
+%  \end{tabular}
+%  \caption{\label{tbl:ellipseRelaxTime} The time, $t_{\mathrm{SS}}$, for
+%  a semi-permeable vesicle to reach steady state.}
+%\end{table}
+%
+%\begin{table}[htp]
+%  \centering
+%  \begin{tabular}{|C{1cm}|*{6}{C{2cm}}|}
+%    \hline
+%    $\beta$ & $10^{0}$ & $10^{-1}$ & $10^{-2}$ & 
+%             $10^{-3}$ & $10^{-4}$ & $10^{-5}$ \\
+%    $t_\mathrm{SP}$ & $2.17 \times 10^{-2}$ & $1.25 \times 10^{-1}$ & 
+%                      $1.59 \times 10^{0}$ & $2.19 \times 10^{1}$ & 
+%                      $2.14 \times 10^{2}$ & $2.20 \times 10^{3}$ \\
+%    ratio & --- & 5.76 & 12.72 & 13.77 & 9.77 & 10.14 \\
+%    \hline
+%  \end{tabular}
+%  \caption{\label{tbl:ellipseBLTime} The time, $t_\mathrm{SP}$, for a
+%  semi-permeable vesicle to begin inflating.}
+%\end{table}
+%
+%%\begin{figure}[htp]
+%%\begin{minipage}{0.40\textwidth}
+%%\ifTikz
+%%\input{figures/starTension.tikz}
+%%\fi
+%%\end{minipage}
+%%\hfill
+%%\begin{minipage}{0.55\textwidth}
+%%  \centering
+%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime1.pdf}
+%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime2.pdf}
+%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime3.pdf} \\
+%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime4.pdf}
+%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime5.pdf}
+%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime6.pdf}
+%%\end{minipage}
+%%  \caption{\label{fig:starTension} The tension of the time steps shown
+%%  in Figure~\ref{fig:starShape}. The tension at the time horizon $T=1$
+%%  is also included. At this point, the vesicle is nearly circular and
+%%  the tension is constant and positive. The constant is given by
+%%  equation~\eqref{eqn:SSshape}, and this value corresponds to the
+%%  dashed black line.}
+%%\end{figure}
+%
+%%\begin{figure}[htp]
+%%\begin{minipage}{0.40\textwidth}
+%%%\ifTikz
+%%\input{figures/starFlux.tikz}
+%%%\fi
+%%\end{minipage}
+%%\hfill
+%%\begin{minipage}{0.55\textwidth}
+%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime1.pdf}
+%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime2.pdf}
+%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime3.pdf} \\
+%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime4.pdf}
+%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime5.pdf}
+%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime6.pdf}
+%%\end{minipage}
+%%  \caption{\label{fig:starFlux} The flux of the time steps shown in
+%%  Figure~\ref{fig:starShape}. The tension at the time horizon $T=1$ is
+%%  also included. At this point, the vesicle is nearly circular and there
+%%  is no flux.}
+%%\end{figure}
 

### 2020-05-06 vesicle_code/examples/relaxation1Ves.m

@@ -2,13 +2,13 @@
 fprintf('Simple elliptical vesicle in a relaxation flow.\n');
 fprintf('First-order semi-implicit time stepping.\n');
 
-beta = 1e-5;
+beta = 1;
 m = 100000;
 ms = m;
 betas = beta;
 
 % Physics parameters
-prams.N = 2*192;               % points per vesicle
+prams.N = 256;               % points per vesicle
 prams.nv = 1;               % number of vesicles
 prams.T = 2e5;               % time horizon (two tumbling)
 prams.m = m;              % number of time steps
@@ -85,7 +85,7 @@ X = oc.initConfig(prams.N,'star',...
     'reducedArea',ra,...
     'center',[centerx;centery],...
     'angle',ang,...
-    'scale',scale);
+    'scale',1.18);
 
 
 Xfinal = Ves2D(X,[],prams,options);

### 2020-05-11 vesicle_code/docs/permeableVes/main.tex
worked on shear example

@@
 \Tikztrue
+%\Tikzfalse
 
@@
 
+Reduced area is $\nu = 4\pi A/L^2$.
+
 \subsection{Integral equation formulation}
@@
   A(t) = \frac{1}{2}\int_{\gamma} (\xx \cdot \nn)\, ds .
+  \label{eqn:area}
 \end{align}
@@
 regimes. All vesicles have a length of $L=4\pi$, but the area is not
-conserved because of semi-permeability. However, the area is bounded
-above by the area of a circle with circumference $L=4\pi$. Therefore,
-$A(t) \leq 4\pi \approx 12.56$ for all simulations. For each simulation,
-we use an adaptive second-order time stepping method~\cite{qua-bir2016}.
+conserved because of semi-permeability. However, the area is bounded by
+$4\pi$ which is the area of a circle with length $L=4\pi$. For each
+simulation, we apply an SDC second-order adaptive time stepping
+method~\cite{qua-bir2016}.
 
@@
 \subsection{Quiescent Flow} 
-We start by considering a semi-permeable vesicle in a quiescent flow.
-For an impermeable vesicle, the vesicle relaxes to a steady-state shape
-with negative and constant tension~\cite{kra-win-sei-lip1996}. However,
-from equation~\eqref{eqn:SSshape}, we know that a semipermeable vesicle
-will relax to a circle with positive constant tension. Since the area of
-a semi-permeable vesicle is governed by~\eqref{eqn:areaROC}, we expect
-that the time to reach steady state, and the time required for a small
-amount of inflation, both scale with $\beta^{-1}$. We simulate a vesicle
-with initial reduced area $0.65$ with several values of $\beta$.  In
-Table~\ref{tbl:ellipseRelaxTimes}, we report the time, $t_\mathrm{SS}$,
-required for the vesicle's area to be within 1.3\% of its maximum area,
-and the time, $t_\mathrm{SP}$, required for the vesicle's area to exceed
-1.3\% of its initial area. We see that both these time scales do scale
-with $\beta^{-1}$. In Figure~\ref{fig:ellipseArea}, we plot the area of
-a vesicle with different permeability rates. The area is computed
-directly from the vesicle shape (solid lines) and by integrating
+We consider a semi-permeable vesicle with initial reduced area $0.65$
+and several different permeability rates $\beta$ in a quiescent flow. If
+the vesicle is impermeable, meaning that $\beta = 0$, it will relax to a
+steady-state shape with negative and constant
+tension~\cite{kra-win-sei-lip1996}. However, from
+equation~\eqref{eqn:SSshape}, a semipermeable vesicle relaxes to a
+circle with positive constant tension. Since the area of a
+semi-permeable vesicle is governed by~\eqref{eqn:areaROC}, we expect
+that the time for the vesicle to deviate from its initial area, and the
+time to reach the steady state will both scale with $\beta^{-1}$. In
+Figure~\ref{fig:ellipseArea}, we plot the area of a vesicle with
+different permeability rates. The area is computed directly from the
+vesicle shape (solid lines) and by integrating
 equation~\eqref{eqn:areaROC} (marks) with a first-order method. We also
-include black dashed lines indicating the times, $t_{\mathrm{SS}}$, that
-the vesicle is near its steady state circular shape.
+include black dashed lines indicating the times, $t_{\mathrm{steady}}$,
+that the vesicle is near its steady state circular shape. In
+Table~\ref{tbl:ellipseRelaxTimes}, we report the time,
+$t_\mathrm{steady}$, required for the vesicle's area to be within 1.3\%
+of its maximum area, and the time, $t_\mathrm{inflate}$, required for
+the vesicle's area to exceed 1.3\% of its initial area. We see that both
+times scale with $\beta^{-1}$.
 
@@
     \hline
-    $\beta$ & $t_\mathrm{SS}$ & ratio & $t_\mathrm{SP}$ & ratio \\
+    $\beta$ & $t_\mathrm{steady}$ & ratio & $t_\mathrm{inflate}$ & ratio \\
     \hline
@@
   \caption{\label{tbl:ellipseRelaxTimes} The time for a semi-permeable
-  vesicle to reach relaxation time ($t_\mathrm{SS}$) and to begin
-  inflating ($t_\mathrm{SP}$).}
+  vesicle to its steady state ($t_\mathrm{steady}$) and to begin
+  inflating ($t_\mathrm{inflate}$).}
 \end{table}
@@
   semi-permeable vesicle, with permeability rate $\beta$ in a quiescent
-  flow. The solid lines compute the area directly from the vesicle
-  shape, while the marks are computed by integrating
+  flow. The solid lines compute the area using
+  equation~\eqref{eqn:area}, while the marks are computed by integrating
   equation~\eqref{eqn:areaROC}. The dashed black lines are the times
-  when the vesicle's area is within 1\% of its maximum value of $4\pi$.}
+  when the vesicle's area is within 1.3\% of its maximum value of
+  $4\pi$.}
 \end{figure}
@@
 We further analyze the transient dynamics for small $\beta$ by
-considering the contribution of each term in~\eqref{eqn:vesVelocity} to
-the vesicle velocity. Initially, the semi-permeability term $\beta(\ff
-\cdot \nn)\nn$ is much smaller than the velocity due to the force
-balance $\SS[\ff]$. Therefore, the velocity resembles that of an
-impermeable vesicle. However, as the vesicle approaches the impermeable
-limit, the velocity contribution from the force balance decays below the
-contribution from semi-permeability, and we expect the vesicle to begin
-inflating due to permeability. In Figure~\ref{fig:vesVelocity}, we plot
-the velocities at three times due to force balance (blue) and
-semi-permeability (red), where $\beta = 10^{-3}$. We also plot the
-velocity of an identically initialized impermeable vesicle. At $t=0.5$,
-the velocity due to semi-permeability is small relative to the velocity
-due to force balance, and the semi-permeable vesicle velocity matches
-with the impermeable vesicle velocity. At time $t=5$, the impermeable
-vesicle is near its steady state shape, and its velocity is comparable
-to the semi-permeable velocity, so the vesicle's area begins to
-increase. Then, at time $t=50$, the impermeable vesicle is at its steady
-state, while the semi-permeable vesicle still has contributions due to
-semi-permeability and force balance. In
-Figure~\ref{fig:vesVelocityNorm}, we plot the max norm of the different
-velocity contributions as a function of time. The black dashed lines
-correspond to the times reported in Figure~\ref{fig:vesVelocity}. Again,
-we see that the velocity of a semi-permeable vesicle is initially agrees
-with the velocity of an impermeable vesicle. Then, as the velocity due
-to force balance approaches zero, the semi-permeable term becomes
-significant, causing the vesicle to inflate until it reaches a circular
-shape.
+considering the vesicle velocity~\eqref{eqn:vesVelocity} due to
+semi-permeability, $\beta(\ff \cdot \nn)\nn$, and force balance,
+$\SS[\ff]$. Initially, since $\beta$ is small, the semi-permeability velocity is much
+smaller than the balance velocity. Therefore,
+the velocity resembles that of an impermeable vesicle. However, as the
+vesicle approaches the steady state shape of an impermeable vesicle, the
+force balance velocity decreases below the semi-permeability velocity,
+at which point the semi-permeable vesicle begins to inflate.  Finally,
+the vesicle semi-permeable inflates until it is circular with zero
+membrane force, and therefore zero velocity.  Letting $\beta = 10^{-3}$,
+in Figure~\ref{fig:vesVelocity} we plot the force balance velocity
+(blue) and the semi-permeability velocity (red) at three times. We also
+plot the velocity of an identically initialized impermeable vesicle
+(green). At $t=0.5$, semi-permeability velocity is small relative to the
+force balance velocity, and the semi-permeable velocity matches with the
+impermeable vesicle velocity. At time $t=5$, the velocity of the
+impermeable vesicle, and also the force balance velocity, are comparable
+in size to the semi-permeability velocity, and the semi-permeable
+vesicle begins to inflate. Then, at time $t=50$, the impermeable vesicle
+is at its steady state, while the semi-permeable vesicle still has
+contributions due to semi-permeability and force balance. In
+Figure~\ref{fig:vesVelocityNorm}, we plot the maximum norm of the
+different velocity contributions as a function of time. The black
+vertical lines correspond to the times reported in
+Figure~\ref{fig:vesVelocity}. Again, we see that the velocity of a
+semi-permeable vesicle initially agrees with the velocity of an
+impermeable vesicle. Then, as the force balance velocity approaches
+zero, the semi-permeable velocity becomes significant, causing the
+vesicle to inflate until it reaches a steady state circular shape.
 
@@
   semi-permeability (red) and force balance (blue). The green dashed
-  line is the velocity of an impermeable vesicle with an identical
-  initial shape.}
+  line is the velocity of an impermeable vesicle with the same initial
+  shape as the semi-permeable vesicle.}
 \end{figure}
@@
 
-Finally, we consider a semi-permeable vesicle with initial regions of
-positive and negative curvature. The permeability rate is $\beta=1$, and
-several time steps are illustrated in Figure~\ref{fig:starShape}. As
-expected, the steady state shape is circular. The vesicle undergoes
-three general behaviors: (i) for $t \in (0,1.6 \times 10^{-2})$, the
-vesicle has a net negative flux resulting in a loss of area; (ii) for $t
-\in (1.6 \times 10^{-2},1.0 \times 10^{0})$, the vesicle has a net
-positive flux and the tension most of the membrane is undergoing
-negative tension; (iii) for $t \in (1.0 \times 10^{0},2.0 \times
-10^{0})$, the vesicle is near its steady state and transitions to a
-positive constant tension.
-
-We compute the tension $\Lambda$ and the flux $(-\xx_{ssss} + (\sigma
-\xx_s)_s) \cdot \nn$ and plot the results in
-Figure~\ref{fig:starTensionFlux}.  In the first time interval, the
-vesicle deflates. Near the points of largest negative curvature, there
-is a large negative tension and large inflow (positive flux).
+Finally, we consider a semi-permeable vesicle, with $\beta=1$, that
+initially has regions with positive curvature and others with negative
+curvature. The vesicle shape at several time steps is in
+Figure~\ref{fig:starShape}, and, as we have shown, the steady state
+shape is circular.  We also compute the tension, $\Lambda$, and the
+flux, $\ff \cdot \nn$, and plot the results in
+Figure~\ref{fig:starTensionFlux}. The vesicle undergoes three general
+behaviors: (i) For $t \in (0,1.6 \times 10^{-2})$, the vesicle has a net
+negative flux resulting in a loss of area; (ii) For $t \in (1.6 \times
+10^{-2},1.0)$, the vesicle has a net positive flux and the tension most
+of the membrane is undergoing negative tension; (iii) For $t \in
+(1.0,2.0)$, the vesicle is near its steady state and transitions to a
+positive constant tension. In the first time interval, the vesicle
+deflates. Near the points of largest negative curvature, there is a
+large negative tension and large inflow (positive flux).
 Correspondingly, near the points with largest positive curvature, there
@@
 interval, the tension is negative and the flux is positive nearly
-everywhere. The regions of large negative curvature correspond to
-regions with the largest negative tension and the most inflow. Finally,
-in the last time interval, the tension transitions to a positive
-constant function, the flux transitions to zero, and the result is a
+everywhere. The regions with largest negative curvature correspond to
+regions with largest negative tension and the most inflow. Finally, in
+the last time interval, the tension transitions to a positive constant
+function, the membrane force and flux transition to zero, resulting in a
 steady state circular vesicle with positive constant tension.
@@
   \caption{\label{fig:starShape} An initially star-shaped semi-permeable
-  vesicle in a shear quiescent flow with $\beta=1$. Note that the time
-  steps are not equispaced.}
+  vesicle in a quiescent flow with $\beta=1$. Note that the time steps
+  are not equispaced.}
 \end{figure}
@@
   \caption{\label{fig:starTensionFlux} The vesicle tension (top) and
-  flux (bottom) of the semi-permeable vesicle in quiescent
+  flux (bottom) of the semi-permeable vesicle in a quiescent
   flow with $\beta=1$.}
@@
 \begin{itemize}
-  \item Never goes to a circle
-  \item Area formula works
   \item Mild dependence on initial shape
-  \item Most slender tank treading shapes seen for small $\beta$ and
-    large $\chi$
 
@@
     absolute value of the permeable flux
+
   \item Max flux at the steady state as a function of beta and
@@
 We consider a semi-permeable vesicle in the shear flow
-$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$. For impermeable vesicles,
-depending on the reduced area and viscosity contrast, the vesicle will
-either tumble or tank-tread~\cite{fin-lam-sei-gom2008}. Since we are
-considering permeable vesicles, we assume that there is no fluid
-viscosity.
+$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$ with different permeability
+rates $\beta$ and shear rates $\dot{\gamma}$.  For a two-dimensional
+impermeable vesicle, depending on the reduced area and viscosity
+contrast, vesicles in a shear flow either tank tread or
+tumble~\cite{fin-lam-sei-gom2008,kra-win-sei-lip1996}, but tumbling is
+not possible with viscosity contrast of one. Since we are considering
+semi-permeable vesicles, we assume that there is no viscosity contrast,
+and we do not expect to observe tumbling dynamics.
 
-%\ifTikz
-%\input{figures/shearPhaseDiagram.tikz} 
-%\fi
+We initialize an elliptical vesicle with reduced area $\nu = 0.65$, and
+with its long axis oriented in the $y$-direction. For all permeability
+rates and shear rates, the semi-permeable vesicle tilts to an
+inclination angle and undergoes tank-treading behavior. However, because
+of the semi-permeability, the final reduced area does not agree with the
+initial reduced area. In Figure~\ref{fig:shearPhase}, we plot the final
+shape of the vesicle for various permeability rates, $\beta$, and shear
+rates $\dot{\gamma}$. We also includes lines of constant final reduced
+area. We see that the shear rate has the largest effect on the final
+reduced area. However, for small $\beta$, the permeability rate also has
+a large effect on the final reduced area. In particular, the smallest
+final reduced areas are the result of large shear rates and small
+permeability rates.
+
+\begin{figure}[htp]
+\ifTikz
+\input{figures/shearPhaseDiagram.tikz} 
+\fi
+  \caption{\label{fig:shearPhase} The steady state shape of a
+  semi-permeable vesicle with several different permeability rates
+  $\beta$ and shear rates $\dot{\gamma}$. The black lines represent
+  contour lines of the final reduced areas, and the reduced area are
+  reported on the right.}
+\end{figure}
 

### 2020-05-11 vesicle_code/src/curve.m

@@ -359,6 +359,7 @@ if isempty(X)
   % Rotate vesicles as requested 
 end
 
+
 end % initConfig
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-05-11 vesicle_code/docs/permeableVes/main.tex
put in inclination angle contour lines

@@
 \newif\ifTikz
-\Tikztrue
-%\Tikzfalse
+%\Tikztrue
+\Tikzfalse
 
@@
 permeability rates.
+\todo[inline]{Also reporting inclination angle as well}
 
 \begin{figure}[htp]
-\ifTikz
-\input{figures/shearPhaseDiagram.tikz} 
-\fi
+%\ifTikz
+\input{figures/shearPhaseDiagramRA.tikz} 
+\input{figures/shearPhaseDiagramIA.tikz} 
+%\fi
   \caption{\label{fig:shearPhase} The steady state shape of a
@@
   $\beta$ and shear rates $\dot{\gamma}$. The black lines represent
-  contour lines of the final reduced areas, and the reduced area are
-  reported on the right.}
+  contour lines of the final reduced areas (left) and the inclination
+  angle (right). The reduced area and inclination angle of each
+  contour line are reported.}
 \end{figure}

### 2020-05-12 vesicle_code/examples/choke1Ves.m
doing more shear runs

@@ -67,7 +67,7 @@ prams.alpha = 0.9;
 
 oc = curve;
 X = oc.initConfig(prams.N,'nv',prams.nv,'angle',pi/3,...
-   'scale',0.4,...
+   'scale',0.5,...
    'center',[[-15;1]],'reducedArea',0.65);
 
 % load chokeIC

### 2020-05-20 vesicle_code/examples/shear1Ves.m
trying to finish shear example on new laptop

@@ -20,7 +20,7 @@ options.vesves = 'implicit';
 options.inextens = 'method1';
 options.near = true;        % near-singular integration
 options.fmm = false;
-options.verbose = false;
+options.verbose = true;
 options.semipermeable = true;
 prams.gmresMaxIter = 3*prams.N;
 prams.gmresTol = 1e-8;

### 2020-05-20 vesicle_code/src/Ves2D.m

@@ -1,4 +1,4 @@
-function Xfinal  = Ves2D(X,Xwalls,prams,options,pressTar)
+function Xfinal = Ves2D(X,Xwalls,prams,options,pressTar)
 % Ves2D does time stepping on the intial configuration X
 % with parameters and options defined in prams and options.
 % Also can pass a set of initial target points where one wants 
@@ -9,8 +9,13 @@ global derivs  ;  % number of times we compute differential
                   % operators for preconditioning
 global fmms       % number of fmm calls
 
+om = monitor(X,Xwalls,options,prams);
+% Create class for doing input/output
+
 if nargin == 4
   pressTar = [];   % points to compute pressure for postprocessing
+else
+  om.initializePressure(pressTar); 
 end
 
 matvecs = 0; 
@@ -29,9 +34,6 @@ N = prams.N; % Number of points per vesicle
 nv = prams.nv; % Number of vesicles
 Nbd = prams.Nbd; % number of points per solid wall
 nvbd = prams.nvbd; % number of solid wall components
-
-om = monitor(X,Xwalls,options,prams);
-% Create class for doing input/output
 
 if options.profile
   profile off; profile on -timer real;
@@ -85,8 +87,30 @@ end
 %
 [Xstore,sigStore,uStore,etaStore,RSstore] = ...
     tt.firstSteps(options,prams,Xstore,sigStore,uStore,...
-    walls,wallsCoarse,om,pressTar);
+    walls,wallsCoarse,om);
 % Was for higher-order multistep methods which have been fazed out.
+
+% compute pressure and stress
+if nargin == 5
+  op = poten(walls.N);
+  [~,pressDLPtar] = op.exactPressDL(walls,etaStore,[],pressTar,1);
+  pressDLPtar = pressDLPtar(1:end/2);
+
+  vesicle = capsules(Xstore,sigStore,uStore,...
+    prams.kappa,prams.viscCont,options.semipermeable,...
+    prams.fluxCoeff,options.fluxShape);
+  tracJump = vesicle.tracJump(Xstore,sigStore);
+  % compute traction
+
+  op = poten(vesicle.N);
+  [~,pressSLPtar] = op.exactPressSL(vesicle,tracJump,[],pressTar,1);
+  pressSLPtar = pressSLPtar(1:end/2);
+
+  om.writePressure(pressDLPtar + pressSLPtar);
+  % write the pressure contributions to file
+end
+
+
 
 time = 0;
[…]

### 2020-06-03 vesicle_code/docs/permeableVes/main.tex
doing more shear runs
trying to finish shear example on new laptop
starting parabolic results
switching to PNAS

@@
-\documentclass[aps,prl,showpacs]{revtex4}
+\documentclass[9pt,twocolumn,twoside,lineno]{pnas-new}
+% Use the lineno option to display guide line numbers if required.
+
+\templatetype{pnasresearcharticle} % Choose template 
+% {pnasresearcharticle} = Template for a two-column research article
+% {pnasmathematics} %= Template for a one-column mathematics article
+% {pnasinvited} %= Template for a PNAS invited submission
+
+\title{Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and
+Physics}
+
+% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
+\author[a]{Ashley Gannon}
+\author[b]{Yuan-Nan Young} 
+\author[a,1]{Bryan Quaife}
+
+\affil[a]{Department of Scientific Computing, Florida State University}
+\affil[b]{Department of Mathematical Sciences, New Jeresey Institute of
+Technology}
+
+% Please give the surname of the lead author for the running footer
+\leadauthor{Quaife}
+
+% Please add a significance statement to explain the relevance of your work
+\significancestatement{Authors must submit a 120-word maximum statement
+about the significance of their research paper written at a level
+understandable to an undergraduate educated scientist outside their
+field of speciality. The primary goal of the significance statement is
+to explain the relevance of the work in broad context to a broad
+readership. The significance statement appears in the paper itself and
+is required for all research papers.}
+
+% Please include corresponding author, author contribution and author declaration information
+\authorcontributions{All authors contributed equally.}
+%\authordeclaration{Please declare any competing interests here.}
+%\equalauthors{\textsuperscript{1}A.O.(Author One) contributed equally to this work with A.T. (Author Two) (remove if not applicable).}
+\correspondingauthor{\textsuperscript{1} E-mail: bquaife\@fsu.edu}
+
+% At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
+\keywords{Keyword 1 $|$ Keyword 2 $|$ Keyword 3 $|$ ...}
+
+\begin{abstract}
+We describe a mathematical model for a semi-permeable vesicle and derive
+  a boundary integral equation formulation for simulating its
+  hydrodynamics.
+
+Please provide an abstract of no more than 250 words in a single paragraph.
+Abstracts should explain to the general reader the major contributions of the article.
+References in the abstract must be cited in full within the abstract itself and cited in the text.
+\end{abstract}
+
+\dates{This manuscript was compiled on \today}
+\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}
+
+\input my_macros2.tex
 
@@
 
-%\usepackage{showkeys}
-\usepackage{amsmath,amsfonts,bm}
-\usepackage{graphicx,epsfig}
-\usepackage{todonotes}
-%Dfig puts a figure of specified size at the place indicated.
-\newcommand{\Dfig}[2]{\epsfig{figure=#1,width=#2cm}}
-
-%\Eonefigs puts one figure at the top of a page. 3 arguments.
-%Usage:
-%\Eonefigs{file fig}{caption}{size in inches}
-%the file must be eps, but names must be given 
-%WITHOUT .eps extension
-
-\newenvironment{Eonefigs}[3]
-{        \begin{figure} [t]
-          \begin{center}
-              \includegraphics[width=0.5\textwidth]{#3} \\
-          \vspace{-0.21in}
-          \caption{{\footnotesize #2}}
-          \label{#1}
-          \end{center}
-        \vspace{-.3in}
-        \end{figure}
-}{}
-
-\newcommand{\co}[1]{\marginpar{\scriptsize \textcolor{red}{#1}}} % red comment
-
-\input my_macros2.tex
+%\usepgfplotslibrary{external}
+%\tikzexternalize
 
@@
 
-\title{Semi-permeable vesicles: mathematical formulation, numerics and physics}
-\author{Ashley Gannon, Bryan Quaife, and Yuan-Nan Young}
+\maketitle
+\thispagestyle{firststyle}
+\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
 
-\date{\today}
+\dropcap{T}his PNAS journal template is provided to help you write your
+work in the correct journal format. Instructions for use are provided
+below. We do not start with a section heading for the introduction, but
+rather type the intro starting here.
 
-\begin{abstract}
-We describe a mathematical model for a semi-permeable vesicle and derive
-  a boundary integral equation formulation for simulating its
-  hydrodynamics.  
-\end{abstract}
-\maketitle
-
-\section{Problem formulation} \label{sc:formulate}
+\section*{Governing equations} \label{sc:formulate}
 Consider a two-dimensional semi-permeable vesicle suspended in an
@@
 %
-\begin{subequations}
 \begin{alignat}{3}
@@
   -\nabla p + \mu \triangle \uu &= 0, 
-  &&\xx \in \RR^2 \setminus \gamma, \\
-% 
-  \nabla \cdot \uu &= 0,  &&\xx \in \RR^2 \setminus \gamma, \\
+  \nabla \cdot \uu = 0, \qquad &&\xx \in \RR^2 \setminus \gamma, \\
 %
   \uu(\xx) &\rightarrow \uu_\infty(\xx),
-    \qquad &&\norm{\xx} \rightarrow \infty.
+    &&\norm{\xx} \rightarrow \infty,
 \end{alignat}
-\end{subequations}%
-%
-Letting $\nn$ be the outward normal to $\gamma$, $\jump{\cdot}$ denote
-the jump across the interface, and $T$ denote the hydrodynamic stress
-tensor, the boundary conditions along the vesicle are
+where $\mu$ is the fluid viscosity. Letting $\nn$ be the outward normal
+to $\gamma$, $\jump{\cdot}$ be the jump across the interface, and $T$ be
+the hydrodynamic stress tensor, the interfacial boundary conditions are
 \begin{align}
-  \label{eqn:jump1}
-  \jump{T\cdot\nn} &= \ff_\mathrm{mem}, \\
-  \label{eqn:jump2}
-  \jump{\uu} &= 0,
+  \label{eqn:jump}
+  \jump{T\cdot\nn} = \ff_\mathrm{mem}, \quad \jump{\uu} = 0,
 \end{align}
-where $\nn$ points outward to the vesicle, and $\ff_\mathrm{mem}$ is the
-membrane force that includes a bending term that minimizes the Helfrich
-energy, and a tension term that acts as a Lagrange multiplier to satisfy
-the local inextensibility condition. The bending stiffness only sets the
-time scale, so we let $k_b = 1$ throughout the paper. For ease of
-implementation, we modify the bending tension and forces as
-$\ff_\mathrm{mem} = \ff_\mathrm{ben} + \ff_\mathrm{ten}$, where
+where $\ff_\mathrm{mem}$ is the membrane force that results from the
+Helfrich energy with bending modulus $k_b$, and a tension term that acts
+as a Lagrange multiplier to satisfy the local inextensibility condition.
+Following~\cite{vee-gue-zor-bir2009}, we modify the bending tension and
+forces as
+$\ff_\mathrm{mem} = \ff_\mathrm{ben} +
+\ff_\mathrm{ten}$, where
 \begin{align}
   \label{eqn:membraneForces}
-  \ff_\mathrm{ben} = -\xx_{ssss}, \qquad
+  \ff_\mathrm{ben} = -k_b \xx_{ssss}, \qquad
   \ff_\mathrm{ten} = (\sigma \xx_s)_s.
 \end{align}
-However, the physical tension $\Lambda$ can be computed as a
-post-processing step as
+The physical tension satisfies $\Lambda = \sigma + 1.5 \kappa^2$, where
+$\kappa$ is the membrane curvature.
+
+The kinematic condition is modified to account for flow through the
+vesicle. A standard choice for this flux is the difference in mechanical
+force~\cite{yao-mor2017}
 \begin{align}
-  \Lambda = \sigma + 1.5 \kappa^2,
-\end{align}
-where $\kappa$ is the membrane curvature.
-
-The kinematic condition is modified to account for the fact that the
-fluid can move through the membrane. A standard choice appears
-is~\cite{}
-\begin{align}
+  \label{eqn:vesicleFlux}
   \uu - \dot{\xx} = - \beta (\ff_\mathrm{mem} \cdot \nn) \nn, \qquad
@@
 
-Reduced area is $\nu = 4\pi A/L^2$.
-
-\subsection{Integral equation formulation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Integral equation formulation}
 Since the flow is governed by the linear Stokes equations, it can be
-represented in terms of layer potentials. Given the boundary
-conditions~\eqref{eqn:jump1} and~\eqref{eqn:jump2} required on the
-interface, the fluid velocity can be represented as the single-layer
-potential
+represented in terms of layer potentials. Given the interfacial boundary
+conditions~\eqref{eqn:jump}, the fluid velocity is
 \begin{align}
@@
 \end{align}
-where
+where $\SS$ is the single-layer potential
 \begin{align}
@@
 \end{align}
-where $\rr = \xx - \yy$ and $\rho = \norm{\rr}$. Then, by the
-kinematic equation, the dynamics of the vesicle 
+with $\rr = \xx - \yy$ and $\rho = \norm{\rr}$. Imposing the flux
+condition~\eqref{eqn:vesicleFlux} and the inextensibility condition, the
+vesicle velocity satisfies
 \begin{align}
   \label{eqn:vesVelocity}
-  \frac{d\xx}{dt} = \uu_\infty(\xx) + \beta (\ff_\mathrm{mem}\cdot\nn)\nn
-  + \SS [\ff_\mathrm{mem}](\xx).
-\end{align}
-Finally, the inextensibility condition is given by
-\begin{align}
-  \xx_s\cdot\dot{\xx}_s = 0.
+  \dot{\xx} &= \uu_\infty(\xx) + \beta (\ff_\mathrm{mem}\cdot\nn)\nn
+  + \SS [\ff_\mathrm{mem}](\xx),  \quad
+  \xx_s \cdot \dot{\xx}_s = 0.
 \end{align}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Area Dynamics}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Dimensionless equations}
+The inextensibility condition guarantees that the vesicle's length, $L$,
+is conserved, but its area, $A$, is no longer conserved because of
+semi-permeability. Therefore, the reduced area $\nu = 4\pi A/L^2 \in
+(0,1]$ is not conserved. We non-dimensionalize~\eqref{eqn:vesVelocity}
+by introducing the length scale $R_0 = L/2\pi$ and defining the time
+scale $\tau = \mu R_0^3/k_b$, the tension scale $Q = k_b/R_0^2$, and the
+permeability scale $W = R_0/\mu$. Since the bending stiffness $k_b$ only
+sets the time scale, we let $k_b=1$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Area dynamics}
 Following the analysis of Veerapaneni et al.~\cite{vee-raj-bir-pur2009},
@@
 \end{align}
-where $\Lambda$ is the constant tension that acts as a Lagrange
-multiplier to satisfy the length conservation. Note that there is no
-pressure Lagrange multiplier since the vesicle's area fluctuates. The
-force acing on the membrane is found by taking the variation of
-$\mathcal{L}$ with respect to $\gamma$, and by setting the total force
-to zero, the steady state shape satisfies
-\begin{align}
-  \kappa_{ss} + \frac{1}{2}\kappa^3 - \Lambda \kappa = 0.
-  \label{eqn:curvODE}
-\end{align}
+where the Lagrange multiplier $\Lambda$ the constant tension. Note that
+there is no pressure Lagrange multiplier since the vesicle's area
+fluctuates. Taking the variation of $\mathcal{L}$ with respect to
+$\gamma$, and setting this vesicle force to zero, the steady state shape
+satisfies $\kappa_{ss} + \frac{1}{2}\kappa^3 - \Lambda \kappa = 0$,
 with initial conditions $\kappa(0) = \kappa_0$ and $\kappa_s(0) = 0$.
-Integrating the differential equation~\eqref{eqn:curvODE} with respect
-to arclength, we have
+Integrating once, we have
 \begin{align}
@@
     \frac{\Lambda}{2}\kappa^2 = \kappa_0^4 - \frac{\Lambda}{2}\kappa_0^2.
-  \label{eqn:curvODE2}
+  \label{eqn:curvODE}
 \end{align}
 Assuming $\kappa_s \neq 0$, this differential equation is separable, and
-can be solved analytically using Mathematica. For impermeable vesicles,
-it is possible for the curvature to be
-periodic~\cite{vee-raj-bir-pur2009}. However, the solution
-of~\eqref{eqn:curvODE2} depends on the {\em EllipticF} function, and it
-can not be made periodic. Therefore, the only solution
-of~\eqref{eqn:curvODE2} is $\kappa(s) = \kappa_0$, meaning that the
-steady state shape is a circle. By the inextensibility condition, the
-steady state vesicle has a radius of $L/2\pi$, so its curvature and
-tension are
+can be solved analytically in terms of the {\em EllipticF} function
+using Mathematica. Unlike in the impermeable
+case~\cite{vee-raj-bir-pur2009}, the solution of~\eqref{eqn:curvODE} can
+not be made periodic unless $\kappa(s) = \kappa_0$. Therefore, the
+steady state shape of a semi-permeable vesicle in a quiescent flow is a
+circle. By the inextensibility condition, the steady state vesicle has a
+radius of $L/2\pi$, so its curvature and tension are
 \begin{align}
@@
 In addition to computing the steady shape, we can compute the transient
-area of the vesicle. Parameterizing the vesicle with $\xx$, its area is
+area of the vesicle. The area of the vesicle is
 \begin{align}
-  A(t) = \frac{1}{2}\int_{\gamma} (\xx \cdot \nn)\, ds .
+  A(t) = \frac{1}{2}\int_{\gamma} (\xx \cdot \nn)\, ds,
   \label{eqn:area}
 \end{align}
-The derivative of $A(t)$ includes terms due to the time derivative of
+so the derivative of $A(t)$ includes terms due to the time derivative of
 $\xx \cdot \nn$, and a term due to interface
-stretching~\cite{lai-tse-hua2008}. However, the stretching term is zero
+stretching~\cite{lai-tse-hua2008}, but the stretching term is zero
 because of the local inextensibility condition. Therefore,
 \begin{align}
-  \dot{A}(t) &= \frac{1}{2} \int_{\gamma} \pderiv{}{t} 
-    (\xx \cdot \nn) \, ds = 
+  \dot{A}(t) =
   \frac{1}{2} \int_{\gamma} (\dot{\xx} \cdot \nn)\, ds  + 
@@
 \end{align}
-The second integrand can be computed as
-\begin{align}
-  \int_\gamma (\xx \cdot \dot{\nn})\, ds 
-    = \int_\gamma \left(\xx \cdot \dot{\xx}_s^\perp \right)
-    = -\int_\gamma \left(\xx^\perp \cdot \dot{\xx}_s\right)\, ds 
-    = \int_\gamma \left(\xx_s^\perp \cdot \dot{\xx}\right)\, ds 
-    = \int_\gamma (\dot{\xx} \cdot \nn)\, ds.
-\end{align}
+Applying integration by parts to the second integral, it is equivalent
+to the first.
+%\begin{align}
+%  \int_\gamma (\xx \cdot \dot{\nn})\, ds 
+%    = \int_\gamma \left(\xx \cdot \dot{\xx}_s^\perp \right)
+%    = -\int_\gamma \left(\xx^\perp \cdot \dot{\xx}_s\right)\, ds 
+%    = \int_\gamma \left(\xx_s^\perp \cdot \dot{\xx}\right)\, ds 
+%    = \int_\gamma (\dot{\xx} \cdot \nn)\, ds.
+%\end{align}
 Therefore,
 \begin{align}
-  \dot{A}(t) &= \int_\gamma (\dot{\xx} \cdot \nn)\, ds 
-  = \int_\gamma \left(\beta (\ff \cdot \nn)\nn + \SS[\ff]\right) 
-      \cdot \nn\, ds 
+  \dot{A}(t) = \int_\gamma \left(\beta (\ff \cdot \nn)\nn 
+    + \SS[\ff]\right) \cdot \nn\, ds 
   = \beta \int_\gamma (\ff \cdot \nn)\, ds,
@@
 where the last equality follows from the incompressibility of the
-single-layer potential and the divergence theorem.  Using integration by
-parts and the Frenet-Serret identities, we have
+single-layer potential.  Using integration by parts and the
+Frenet-Serret identities, we have
 \begin{align}
@@
   &= -\beta \int_\gamma \left(\kappa^3 + \kappa \sigma \right) 
-    \, ds.
-\end{align}
-Finally, using the relationship between the Lagrange multiplier
-$\sigma$, and the tension $\Lambda$, the area of a semi-permeable
-vesicle is governed by
-\begin{align}
-  \dot{A}(t) = \beta \int_\gamma \left(
+    \, ds \\
+  &= \beta \int_\gamma \left(
     \frac{\kappa^3}{2} - \kappa \Lambda \right) \, ds.
@@
 \end{align}
-Note that this is consistent with the steady state curvature and
-tension~\eqref{eqn:SSshape} since these constant values result in the
-integrand in equation~\eqref{eqn:areaROC} being zero.
+Note that this is consistent with the steady state curvature and tension
+in~\eqref{eqn:SSshape} since these constant values result in the
+integrand in~\eqref{eqn:areaROC} being zero.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Numerical Methods}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Discretization in Space}
+By using an integral equation formulation, the unknowns are the vesicle
+position and tension which we track at a set of $N$ discretization
+points. All arclength derivatives are computed with Fourier
+differentiation, and eighth-order quadrature is applied to the weakly
+singular single-layer potential~\cite{alp1999}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Discretization in Time}
+The high-order derivatives in the bending and tension
+forces~\eqref{eqn:membraneForces} result in stiffness if an explicit
+time stepping method is applied to equation~\eqref{eqn:vesVelocity}.
+Therefore, we use a modification of a time stepping method that
+discretizes high-order derivatives
+semi-implicitly~\cite{vee-gue-zor-bir2009}. Introducing notation for
+all the required differential and projection operators
+\begin{alignat}{3}
+  &B[\xx]\ff = -\frac{d^4}{ds^4} \ff,  \qquad
+  &&T[\xx]\sigma = (\sigma \xx_s)_s, \\
+  &D[\xx]\ff = \xx_s \cdot \ff_s, 
+  &&P[\xx]\ff = (\ff \cdot \nn) \nn. 
+\end{alignat}
+the dynamics of the vesicle are governed by
+\begin{align}
+  \dot{\xx} = \uu_{\infty}(\xx) + 
+  \beta P(B\xx + T\sigma) + \SS(B\xx + T\sigma), \quad
+  D \dot{\xx} = 0.
+\end{align}
+Letting $B^N$ be the bending operator due to the vesicle
+configuration at time $t^N$, and similar notation for the other
+operators, we use the semi-implicit time stepping method
+\begin{alignat}{3}  
+  \frac{\xx^{N+1} - \xx^N}{\Delta t} &= \uu_\infty(\xx^N) 
+  &&+ \beta P^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right) \nonumber \\
+  & &&+ \SS^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right), \\
+  D^N\xx^{N+1} &= 1.
+\end{alignat}
+
+To achieve high-order accuracy over long time horizons, we modify the
+adaptive spectral deferred correction time stepping method introduced
+in~\cite{qua-bir2016}. Since the area of the vesicle is no longer
+conserved, we only use the length of the vesicle to estimate the
+local truncation error which then determines if a time step is accepted
+or rejected and the subsequent time step size.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Numerical Methods}
-\subsection{Discretization in Space}
-We apply a collocation method where the vesicle is discretized at $N$
-points. We need to compute derivatives of functions defined on the
-vesicle boundary, and these are done with Fourier differentiation.
-Finally, to compute the single-layer potential, we use an eighth-order
-Alpert quadrature rule~\cite{alp1999} which resolves the logarithmic
-singularity of the integrand.
-
-\subsection{Discretization in Time}
-By using an integral equation formulation, the only unknowns are the
-vesicle position and tension, and the flow in the bulk does not have to
-be computed. However, the high-order derivatives in the bending and
-tension forces~\eqref{eqn:membraneForces} result in stiffness if an
-explicit time stepping method is applied to
-equation~\eqref{eqn:vesVelocity}. We apply a similar semi-implicit time
-stepping method to our previous works~\cite{vee-gue-zor-bir2009,
-qua-bir2014}. First, given a vesicle $\gamma$, with a boundary
-parameterized as $\xx(s)$, we introduce notation for all the required
-differential and projection operators
-\begin{align}
-  B[\xx]\ff &= -\frac{d^4}{ds^4} \ff, \\
-  T[\xx]\sigma &= (\sigma \xx_s)_s, \\
-  D[\xx]\ff &= \xx_s \cdot \ff_s, \\
-  P[\xx]\ff &= (\ff \cdot \nn) \nn. 
-\end{align}
-Here, the normal vector $\nn$ is the outward unit normal of $\gamma$,
-and $d/ds$ is its arclength derivative. To simplify notation, we write
-$B\ff$ to mean $B[\xx]\ff$, and use similar notation for the other
-operators. Then, the dynamics of the vesicle are governed by
-\begin{align}
-  \frac{d\xx}{dt} &= \uu_{\infty}(\xx) + 
-  \beta P(B\xx + T\sigma) + \SS(B\xx + T\sigma), \\
-  D \frac{d\xx}{dt} &= 0.
-\end{align}
-By writing $B^N$ to mean the bending operator due to the vesicle
-configuration at time $t^N$, and similar notation for the other
-operators, we address the stiffness by introducing the semi-implicit
-time stepping method
-\begin{align}  
-  \frac{\xx^{N+1} - \xx^N}{\Delta t} = \uu_\infty(\xx^N) 
-  + \beta P^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right) 
-  + \SS^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right).
-\end{align}
-Finally, the inextensibility condition is applied by requiring that 
-\begin{align}
-  D^N\xx^{N+1} = 1.
-\end{align}
-
-\todo[inline]{A few lines about SDC}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Examples}
+\section*{Examples}
 We consider a single semi-permeable vesicle in four different flow
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Quiescent Flow} 
-We consider a semi-permeable vesicle with initial reduced area $0.65$
-and several different permeability rates $\beta$ in a quiescent flow. If
-the vesicle is impermeable, meaning that $\beta = 0$, it will relax to a
-steady-state shape with negative and constant
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Quiescent Flow} 
+We consider a semi-permeable vesicle with initial reduced area $\nu =
+0.65$ and several different permeability rates $\beta$ in a quiescent
+flow. If the vesicle is impermeable, meaning that $\beta = 0$, it will
+relax to a steady-state shape with negative and constant
 tension~\cite{kra-win-sei-lip1996}. However, from
-equation~\eqref{eqn:SSshape}, a semipermeable vesicle relaxes to a
+equation~\eqref{eqn:SSshape}, a semi-permeable vesicle relaxes to a
 circle with positive constant tension. Since the area of a
 semi-permeable vesicle is governed by~\eqref{eqn:areaROC}, we expect
-that the time for the vesicle to deviate from its initial area, and the
-time to reach the steady state will both scale with $\beta^{-1}$. In
+both the time for the vesicle to deviate from its initial area, and the
+time to reach its steady state will scale with $\beta^{-1}$. In
 Figure~\ref{fig:ellipseArea}, we plot the area of a vesicle with
@@
   \centering
-  \begin{tabular}{|C{2cm}C{3cm}C{3cm}C{3cm}C{3cm}|}
-    \hline
+  \caption{\label{tbl:ellipseRelaxTimes} The time for a semi-permeable
+  vesicle to its steady state ($t_\mathrm{steady}$) and to begin
+  inflating ($t_\mathrm{inflate}$).}
+  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
     $\beta$ & $t_\mathrm{steady}$ & ratio & $t_\mathrm{inflate}$ & ratio \\
-    \hline
+    \midrule
     $10^{0}$  & $6.45 \times 10^{0}$ & ---  
@@
                 $2.20 \times 10^{3}$ & 10.14 \\
-    \hline
+    \bottomrule
   \end{tabular}
-  \caption{\label{tbl:ellipseRelaxTimes} The time for a semi-permeable
-  vesicle to its steady state ($t_\mathrm{steady}$) and to begin
-  inflating ($t_\mathrm{inflate}$).}
 \end{table}
@@
   \centering
-\ifTikz
-\input{figures/ellipseArea.tikz}
-\fi
+%  \ifTikz
+%  \input{figures/ellipseArea.tikz}
+%  \fi
+  \includegraphics[width=0.8\linewidth]{figures/ellipseArea}
   \caption{\label{fig:ellipseArea} The area of an elliptical
@@
 plot the velocity of an identically initialized impermeable vesicle
-(green). At $t=0.5$, semi-permeability velocity is small relative to the
+(green). The bottom right plot is the maximum norm of the different
+velocity contributions as a function of time. The black vertical lines
+correspond to the times reported in other three subplots. At $t=0.5$, semi-permeability velocity is small relative to the
 force balance velocity, and the semi-permeable velocity matches with the
@@
 is at its steady state, while the semi-permeable vesicle still has
-contributions due to semi-permeability and force balance. In
-Figure~\ref{fig:vesVelocityNorm}, we plot the maximum norm of the
-different velocity contributions as a function of time. The black
-vertical lines correspond to the times reported in
-Figure~\ref{fig:vesVelocity}. Again, we see that the velocity of a
-semi-permeable vesicle initially agrees with the velocity of an
-impermeable vesicle. Then, as the force balance velocity approaches
-zero, the semi-permeable velocity becomes significant, causing the
-vesicle to inflate until it reaches a steady state circular shape.
+contributions due to semi-permeability and force balance. We see that
+the velocity of a semi-permeable vesicle initially agrees with the
+velocity of an impermeable vesicle. Then, as the force balance velocity
+approaches zero, the semi-permeable velocity becomes significant,
+causing the vesicle to inflate until it reaches a steady state circular
+shape.
 
@@
   \centering
-  \ifTikz
-  \input{figures/ellipseVelocity1.tikz}
-  \input{figures/ellipseVelocity2.tikz}
-  \input{figures/ellipseVelocity3.tikz}
-  \fi
+  \includegraphics[width=0.48\linewidth]{figures/ellipseVelocity1.pdf}
+  \includegraphics[width=0.48\linewidth]{figures/ellipseVelocity2.pdf}
+  \includegraphics[width=0.48\linewidth]{figures/ellipseVelocity3.pdf}
+  \includegraphics[width=0.48\linewidth]{figures/ellipseVelocityNorms.pdf}
   \caption{\label{fig:vesVelocity} The velocity contributions due to
-  semi-permeability (red) and force balance (blue). The green dashed
-  line is the velocity of an impermeable vesicle with the same initial
-  shape as the semi-permeable vesicle.}
-\end{figure}
-
-\begin{figure}[htp]
-  \ifTikz
-  \input{figures/ellipseVelocityNorms.tikz}
-  \fi
-  \caption{\label{fig:vesVelocityNorm} The max norm of the velocity due
-  to the force balance (blue) and semi-permeability. Also included is
-  the velocity of an impermeable vesicle (green). The three black lines
-  correspond to the times reported in Figure~\ref{fig:vesVelocity}.}
+  force balance (blue) and semi-pemeability (red). The green dashed line
+  is the velocity of an impermeable vesicle with the same initial shape
+  as the semi-permeable vesicle. The bottom right plot is the max norm
+  of each of term that contributes to the vesicle velocity.  The three
+  black lines correspond to the times reported in the other three
+  plots.}
 \end{figure}
@@
 initially has regions with positive curvature and others with negative
-curvature. The vesicle shape at several time steps is in
-Figure~\ref{fig:starShape}, and, as we have shown, the steady state
-shape is circular.  We also compute the tension, $\Lambda$, and the
-flux, $\ff \cdot \nn$, and plot the results in
-Figure~\ref{fig:starTensionFlux}. The vesicle undergoes three general
-behaviors: (i) For $t \in (0,1.6 \times 10^{-2})$, the vesicle has a net
-negative flux resulting in a loss of area; (ii) For $t \in (1.6 \times
-10^{-2},1.0)$, the vesicle has a net positive flux and the tension most
-of the membrane is undergoing negative tension; (iii) For $t \in
-(1.0,2.0)$, the vesicle is near its steady state and transitions to a
-positive constant tension. In the first time interval, the vesicle
-deflates. Near the points of largest negative curvature, there is a
-large negative tension and large inflow (positive flux).
+curvature. The vesicle tension, $\Lambda$, and the flux $\ff \cdot \nn$,
+are plotted in Figure~\ref{fig:starTensionFlux}. The vesicle undergoes
+three general behaviors: (i) For $t \in (0,1.6 \times 10^{-2})$, the
+vesicle has a net negative flux resulting in a loss of area; (ii) For $t
+\in (1.6 \times 10^{-2},1.0)$, the vesicle has a net positive flux and
+the tension most of the membrane is undergoing negative tension; (iii)
+For $t \in (1.0,2.0)$, the vesicle is near its steady state and
+transitions to a positive constant tension. In the first time interval,
+the vesicle deflates. Near the points of largest negative curvature,
+there is a large negative tension and large inflow (positive flux).
 Correspondingly, near the points with largest positive curvature, there
@@
 \begin{figure}[htp]
-    \ifTikz
-    \input{figures/starRelaxation1.tikz}
-    \quad
-    \input{figures/starRelaxation2.tikz}
-    \quad
-    \input{figures/starRelaxation3.tikz}
-    \quad
-    \input{figures/starRelaxation4.tikz}
-    \quad
-    \input{figures/starRelaxation5.tikz}
-    \fi
-  \caption{\label{fig:starShape} An initially star-shaped semi-permeable
-  vesicle in a quiescent flow with $\beta=1$. Note that the time steps
-  are not equispaced.}
-\end{figure}
+  \centering
+  \includegraphics[width=0.19\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
+  \includegraphics[width=0.19\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
+  \includegraphics[width=0.19\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
+  \includegraphics[width=0.19\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
+  \includegraphics[width=0.19\linewidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime5.pdf}
 
-\begin{figure}[htp]
-  \centering
-  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
-  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
-  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
-  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
-  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime5.pdf}
-
-  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
-  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
-  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
-  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
-  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
+  \includegraphics[width=0.19\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
+  \includegraphics[width=0.19\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
+  \includegraphics[width=0.19\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
+  \includegraphics[width=0.19\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
+  \includegraphics[width=0.19\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
   \caption{\label{fig:starTensionFlux} The vesicle tension (top) and
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Shear Flow}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Shear Flow}
 \begin{itemize}
@@
 of the semi-permeability, the final reduced area does not agree with the
-initial reduced area. In Figure~\ref{fig:shearPhase}, we plot the final
-shape of the vesicle for various permeability rates, $\beta$, and shear
-rates $\dot{\gamma}$. We also includes lines of constant final reduced
-area. We see that the shear rate has the largest effect on the final
-reduced area. However, for small $\beta$, the permeability rate also has
-a large effect on the final reduced area. In particular, the smallest
-final reduced areas are the result of large shear rates and small
-permeability rates.
+initial reduced area. In Figure~\ref{fig:shearPhaseDiagram}, we plot the
+final shape of the vesicle for various permeability rates, $\beta$, and
+shear rates $\dot{\gamma}$. We also includes lines of constant final
+reduced area. We see that the shear rate has the largest effect on the
+final reduced area. However, for small $\beta$, the permeability rate
+also has a large effect on the final reduced area. In particular, the
+smallest final reduced areas are the result of large shear rates and
+small permeability rates.
 \todo[inline]{Also reporting inclination angle as well}
@@
 \begin{figure}[htp]
+  \centering
   %\ifTikz
-\input{figures/shearPhaseDiagramRA.tikz} 
-\input{figures/shearPhaseDiagramIA.tikz} 
+  %\input{figures/shearPhaseDiagramRA2.tikz}
   %\fi
-  \caption{\label{fig:shearPhase} The steady state shape of a
+  \includegraphics[width=\linewidth]{figures/shearPhaseDiagramRA2.pdf}
+  \caption{\label{fig:shearPhaseDiagram} The steady state shape of a
   semi-permeable vesicle with several different permeability rates
@@
   contour lines of the final reduced areas (left) and the inclination
-  angle (right). The reduced area and inclination angle of each
-  contour line are reported.}
+  angle (right). The reduced area and inclination angle of each contour
+  line are reported.}
 \end{figure}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Extensional Flow}
-\begin{itemize}
-  \item ???
-\end{itemize}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Poiseuille Flow}
+We consider a semi-permeable vesicle in the poiseuille flow $\uu =
+U(1-(y/R)^2,0)$, where $R=10$ determines the flow width, and $U$ is the
+maximum flow rate. The length of the vesicle is $L = 4\pi$ and its
+initial reduced area is $\nu = 0.65$. In
+Figure~\ref{fig:parabolicPhaseDiagram}, plot the steady state
+configuration for a variety of flow rates $U$ and permeability rates
+$\beta$. Similar to the shear example, we see that the flow rate has the
+biggest effect on the final shape, and the effect of the permeability
+rate is much weaker. Instead, the permeability rate determines the time
+required for the vesicle to reach a steady state. In
+Tables~\ref{tbl:parabolicRelaxTimes1}
+and~\ref{tbl:parabolicRelaxTimes2}, we consider two flow rates and
+report the time, $t_\mathrm{steady}$, required for the vesicle's area to
+be within 1.3\% of its maximum area, and the time, $t_\mathrm{inflate}$,
+required for the vesicle's area to exceed 1.3\% of its initial area. We
+see that both times scale with $\beta^{-1}$.
 
-%\ifTikz
-%\input{figures/extensionalPhaseDiagram.tikz}
-%\fi
+\begin{figure}[htp]
+%  \ifTikz
+%  \input{figures/parabolicPhaseDiagram.tikz}
+%  \fi
+  \includegraphics[width=0.8\linewidth]{figures/parabolicPhaseDiagram.pdf}
+  \caption{\label{fig:parabolicPhaseDiagram} The steady state shape of a
+  semi-permeable vesicle with several different permeability rates
+  $\beta$ and flow rates $U$.}
+\end{figure}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Poiseuille Flow}
-\begin{itemize}
-  \item Does permeability affect the rate of migration
-\end{itemize}
+\begin{table}[htp]
+  \centering
+  \caption{\label{tbl:parabolicRelaxTimes1} The time for a
+  semi-permeable vesicle in a Poiseuille flow to reach its steady state
+  ($t_\mathrm{steady}$) and to begin inflating ($t_\mathrm{inflate}$).
+  The flow rate is $U = 10^{-1}$.}
+  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
+    $\beta$ & $t_\mathrm{steady}$ & ratio & $t_\mathrm{inflate}$ & ratio \\
+    \midrule
+    $10^{0}$  & $3.33 \times 10^{0}$ & ---  
+              & $1.67 \times 10^{-2}$ & --- \\ 
+    $10^{-1}$ & $1.37 \times 10^{1}$ & 4.12 & 
+                $8.73 \times 10^{-1}$ & 5.23 \\
+    $10^{-2}$ & $8.60 \times 10^{1}$ & 6.26 & 
+                $1.11 \times 10^{0}$ & 12.74 \\
+    $10^{-3}$ & $7.75 \times 10^{2}$ & 9.01 & 
+                $1.63 \times 10^{1}$ & 14.70 \\
+    $10^{-4}$ & $7.69 \times 10^{3}$ & 9.93 & 
+                $1.74 \times 10^{2}$ & 10.63 \\
+    $10^{-5}$ & $8.01 \times 10^{4}$ & 10.41 & 
+                $1.66 \times 10^{3}$ & 9.58 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
 
- \bibliographystyle{plain}
+\begin{table}[htp]
+  \centering
+  \caption{\label{tbl:parabolicRelaxTimes2} The time for a
+  semi-permeable vesicle in a Poiseuille flow to reach its steady state
+  ($t_\mathrm{steady}$) and to begin inflating ($t_\mathrm{inflate}$).
+  The flow rate is $U = 10^{1}$.}
+  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
+    \midrule
+    $\beta$ & $t_\mathrm{steady}$ & ratio & $t_\mathrm{inflate}$ & ratio \\
+    $10^{0}$  & $3.55 \times 10^{0}$ & ---  
+              & $1.67 \times 10^{-2}$ & --- \\ 
+    $10^{-1}$ & $1.87 \times 10^{1}$ & 5.27 & 
+                $9.01 \times 10^{-2}$ & 5.40 \\
+    $10^{-2}$ & $1.17 \times 10^{2}$ & 6.26 & 
+                $1.52 \times 10^{0}$ & 16.87 \\
+    $10^{-3}$ & $1.06 \times 10^{3}$ & 9.06 & 
+                $2.07 \times 10^{1}$ & 13.62 \\
+    $10^{-4}$ & $1.02 \times 10^{4}$ & 9.62 & 
+                $2.25 \times 10^{2}$ & 10.87 \\
+    $10^{-5}$ & $1.04 \times 10^{5}$ & 10.20 & 
+                $2.25 \times 10^{3}$ & 10.00 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+% \bibliographystyle{plain}
  \bibliography{refs}
@@
 %%\end{figure}
+%\begin{figure}[htp]
+%    \ifTikz
+%    \input{figures/starRelaxation1.tikz}
+%    \quad
+%    \input{figures/starRelaxation2.tikz}
+%    \quad
+%    \input{figures/starRelaxation3.tikz}
+%    \quad
+%    \input{figures/starRelaxation4.tikz}
+%    \quad
+%    \input{figures/starRelaxation5.tikz}
+%    \fi
+%  \caption{\label{fig:starShape} An initially star-shaped semi-permeable
+%  vesicle in a quiescent flow with $\beta=1$. Note that the time steps
+%  are not equispaced.}
+%\end{figure}
+%\begin{figure}[htp]
+%  \centering
+%%  \ifTikz
+%  \input{figures/ellipseVelocity1.tikz}
+%  \input{figures/ellipseVelocity2.tikz}
+%  \input{figures/ellipseVelocity3.tikz}
+%%  \fi
+%  \caption{\label{fig:vesVelocity} The velocity contributions due to
+%  semi-permeability (red) and force balance (blue). The green dashed
+%  line is the velocity of an impermeable vesicle with the same initial
+%  shape as the semi-permeable vesicle.}
+%\end{figure}
+%
+%\begin{figure}[htp]
+%%  \ifTikz
+%  \input{figures/ellipseVelocityNorms.tikz}
+%%  \fi
+%  \caption{\label{fig:vesVelocityNorm} The max norm of the velocity due
+%  to the force balance (blue) and semi-permeability. Also included is
+%  the velocity of an impermeable vesicle (green). The three black lines
+%  correspond to the times reported in Figure~\ref{fig:vesVelocity}.}
+%\end{figure}
 

### 2020-06-03 vesicle_code/examples/output/makeImages.m

@@ -6,7 +6,9 @@ options.pressure = false;
 irate = 1; % controls the speed of the visualization
 
 if 0
-  file = 'parabolic1VesData.bin';
+%  file = 'parabolic1VesData.bin';
+  file = '~/projects/brinkman/vesicle_code/results/parabolic/pflowR10u10B1em4Data.bin';
+  options.confined = false;
 end
 if 0
 %  file = 'extensional1VesCleanData.bin'; irate = 2;
@@ -70,9 +72,9 @@ if 0
   ax = [-2 2 -2 2];
   options.confined = false;
 end
-if 0
-  file = 'shear1VesKData.bin';
-%  file = '~/projects/brinkman/vesicle_code/results/shear1Ves/Chi1p0em0p5_ra065_beta1p0em4p5/shear1VesData.bin';
+if 1
+  file = 'shear1VesNData.bin';
+%  file = '~/projects/brinkman/vesicle_code/results/shear1Ves/Chi1p0e2_ra065_beta1p0em4p5/shear1VesData.bin';
   ax = [-5 5 -5 5];
   options.confined = false;
   beta = 0.2;
@@ -92,9 +94,12 @@ if 0
   options.savefig = false;
   count = 1;
 end
-if 1
-  file = 'slit1VesData.bin';
+if 0
+%  file = 'slit1VesData.bin';
+%  file = '~/projects/brinkman/vesicle_code/results/slit/Scale0p55_Beta0/slit1VesData.bin';
+  file = '~/projects/brinkman/vesicle_code/results/slit/Scale0p55_Beta1em3/slit1VesData.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/slit/Scale0p55_Beta1em4/slit1VesData.bin';
+%  file = '~/projects/brinkman/vesicle_code/results/slit/Scale0p55_Beta1em5/slit1VesData.bin';
   ax = [-5 5 -2.5 2.5];
   options.confined = true;
   options.pressure = true;

### 2020-06-04 vesicle_code/docs/permeableVes/main.tex
working on permeable paper

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Examples}
@@
 \subsection*{Quiescent Flow} 
-We consider a semi-permeable vesicle with initial reduced area $\nu =
-0.65$ and several different permeability rates $\beta$ in a quiescent
-flow. If the vesicle is impermeable, meaning that $\beta = 0$, it will
-relax to a steady-state shape with negative and constant
-tension~\cite{kra-win-sei-lip1996}. However, from
-equation~\eqref{eqn:SSshape}, a semi-permeable vesicle relaxes to a
-circle with positive constant tension. Since the area of a
-semi-permeable vesicle is governed by~\eqref{eqn:areaROC}, we expect
-both the time for the vesicle to deviate from its initial area, and the
-time to reach its steady state will scale with $\beta^{-1}$. In
-Figure~\ref{fig:ellipseArea}, we plot the area of a vesicle with
-different permeability rates. The area is computed directly from the
-vesicle shape (solid lines) and by integrating
-equation~\eqref{eqn:areaROC} (marks) with a first-order method. We also
-include black dashed lines indicating the times, $t_{\mathrm{steady}}$,
-that the vesicle is near its steady state circular shape. In
+We consider a semi-permeable elliptical vesicle with initial reduced
+area $\nu = 0.65$ and several different permeability rates in a
+quiescent flow. The steady-state of an impermeable vesicle has constant
+negative tension~\cite{kra-win-sei-lip1996}, but based
+on~\eqref{eqn:SSshape}, a semi-permeable vesicle relaxes to a circle
+with positive constant tension $\Lambda = 2\pi^2/L^2$. Recalling the
+governing equation for the area in~\eqref{eqn:areaROC}, we expect both
+the time for the vesicle to deviate from its initial area, and the time
+to reach its steady state will scale with $\beta^{-1}$. In
 Table~\ref{tbl:ellipseRelaxTimes}, we report the time,
@@
 the vesicle's area to exceed 1.3\% of its initial area. We see that both
-times scale with $\beta^{-1}$.
-
+times scale with $\beta^{-1}$. We also plot the area of a vesicle with
+six different permeability rates in Figure~\ref{fig:ellipseArea}. The
+area is computed directly from the vesicle shape (solid lines) and by
+integrating equation~\eqref{eqn:areaROC} (marks) with a first-order
+method. We also include black dashed lines indicating the times,
+$t_{\mathrm{steady}}$, that the vesicle is near its steady state
+circular shape.
 \begin{table}[htp]
@@
 semi-permeability, $\beta(\ff \cdot \nn)\nn$, and force balance,
-$\SS[\ff]$. Initially, since $\beta$ is small, the semi-permeability velocity is much
-smaller than the balance velocity. Therefore,
-the velocity resembles that of an impermeable vesicle. However, as the
+$\SS[\ff]$. Initially, since $\beta$ is small, the semi-permeability
+velocity is much smaller than the force balance velocity. Therefore, the
+velocity resembles that of an impermeable vesicle. As the
 vesicle approaches the steady state shape of an impermeable vesicle, the
 force balance velocity decreases below the semi-permeability velocity,
-at which point the semi-permeable vesicle begins to inflate.  Finally,
-the vesicle semi-permeable inflates until it is circular with zero
-membrane force, and therefore zero velocity.  Letting $\beta = 10^{-3}$,
-in Figure~\ref{fig:vesVelocity} we plot the force balance velocity
-(blue) and the semi-permeability velocity (red) at three times. We also
-plot the velocity of an identically initialized impermeable vesicle
-(green). The bottom right plot is the maximum norm of the different
-velocity contributions as a function of time. The black vertical lines
-correspond to the times reported in other three subplots. At $t=0.5$, semi-permeability velocity is small relative to the
-force balance velocity, and the semi-permeable velocity matches with the
-impermeable vesicle velocity. At time $t=5$, the velocity of the
-impermeable vesicle, and also the force balance velocity, are comparable
-in size to the semi-permeability velocity, and the semi-permeable
-vesicle begins to inflate. Then, at time $t=50$, the impermeable vesicle
-is at its steady state, while the semi-permeable vesicle still has
-contributions due to semi-permeability and force balance. We see that
-the velocity of a semi-permeable vesicle initially agrees with the
-velocity of an impermeable vesicle. Then, as the force balance velocity
-approaches zero, the semi-permeable velocity becomes significant,
-causing the vesicle to inflate until it reaches a steady state circular
-shape.
-
+and then the semi-permeable vesicle begins to dominate, causing the
+vesicle to inflate.  As the vesicle becomes more circular, the
+membrane force and the corresponding velocity both converge to
+zero. In Figure~\ref{fig:vesVelocity} we plot the force balance velocity
+(blue) and the semi-permeability velocity (red) at three times with
+$\beta=10^{-3}$. We also plot the velocity of an identically initialized
+impermeable vesicle (green).  At $t=0.5$, semi-permeability velocity is
+small relative to the force balance velocity, and the semi-permeable
+velocity matches with the impermeable vesicle velocity. At time $t=5$,
+the magnitude of the velocity of the impermeable vesicle and the force
+balance velocity are both comparable to the magnitude of the
+semi-permeable velocity, and the semi-permeable vesicle begins to
+inflate. Then, at time $t=50$, the impermeable vesicle is at its steady
+state, while the semi-permeable vesicle still has contributions due to
+semi-permeability and force balance. The bottom right plot is the
+maximum norm of the different velocity contributions as a function of
+time, and the black vertical lines correspond to the times reported in
+other three subplots.
+
+%  \input{figures/ellipseVelocity1.tikz}
+%  \input{figures/ellipseVelocity2.tikz}
+%  \input{figures/ellipseVelocity3.tikz}
+%  \input{figures/ellipseVelocityNorms.tikz}
 \begin{figure}[htp]
   \centering
+%  \input{figures/ellipseVelocity1.tikz}
+%  \input{figures/ellipseVelocity2.tikz}
+%  \input{figures/ellipseVelocity3.tikz}
+%  \input{figures/ellipseVelocityNorms.tikz}
   \includegraphics[width=0.48\linewidth]{figures/ellipseVelocity1.pdf}
@@
 
-Finally, we consider a semi-permeable vesicle, with $\beta=1$, that
-initially has regions with positive curvature and others with negative
-curvature. The vesicle tension, $\Lambda$, and the flux $\ff \cdot \nn$,
+\todo[inline]{redo this paragraph}
+Finally, letting $\beta=1$, we consider a semi-permeable vesicle that
+initially has regions of positive and negative curvature. The vesicle
+tension, $\Lambda$, and the flux, $\ff \cdot \nn$,
 are plotted in Figure~\ref{fig:starTensionFlux}. The vesicle undergoes
@@
   \centering
-  \includegraphics[width=0.19\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
-  \includegraphics[width=0.19\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
-  \includegraphics[width=0.19\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
-  \includegraphics[width=0.19\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
-  \includegraphics[width=0.19\linewidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime5.pdf}
-
-  \includegraphics[width=0.19\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
-  \includegraphics[width=0.19\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
-  \includegraphics[width=0.19\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
-  \includegraphics[width=0.19\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
-  \includegraphics[width=0.19\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
+  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
+  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
+  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
+  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
+  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime5.pdf}
+
+  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
+  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
+  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
+  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
+  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
   \caption{\label{fig:starTensionFlux} The vesicle tension (top) and
@@
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Stenosis}
+We consider a semi-permeable vesicle in a constricted geometry. A
+double-layer potential is used to impose a boundary condition on the
+outer wall, and near-singular integration~\cite{qua-bir2014} quadrature
+resolves the vesicle-wall interaction.
 

### 2020-06-10 vesicle_code/docs/permeableVes/main.tex
pushing paper

@@
 \subsection*{Poiseuille Flow}
-We consider a semi-permeable vesicle in the poiseuille flow $\uu =
+We consider a semi-permeable vesicle in the Poiseuille flow $\uu =
 U(1-(y/R)^2,0)$, where $R=10$ determines the flow width, and $U$ is the
@@
 \end{table}
+
+Finally, we examine the effect of the non-linear Poiseuille flow in the
+migration of semi-permeable vesicle. Similar to experiments performed by
+Kaoui et al.~\cite{kao-bir-mis2009}, we initialize the vesicle's
+center of mass above the $y$-axis and examine the y position of its
+center of mass, denoted by $Y_G$.
+
+\begin{itemize}
+  \item If the flow rate is too small, the vesicle only migrates part
+    way before it turns into a circle. Once it's a circle, it acts like
+    a rigid body, so it no longer migrates towards the center line
+\end{itemize}
 
@@
 
+\input{figures/shearPhaseDiagramRA2.tikz}
+
 \end{document}

### 2020-06-11 vesicle_code/docs/permeableVes/main.tex
updated figures

@@
   semi-permeable vesicle with several different permeability rates
-  $\beta$ and flow rates $U$.}
+  $\beta$ and flow rates $U$. At high flow rates, the vesicle
+  self-intersects before reaching a steady state configuration.}
 \end{figure}
@@
 
-\input{figures/shearPhaseDiagramRA2.tikz}
+%\input{figures/shearPhaseDiagramRA2.tikz}
+%\input{figures/parabolicPhaseDiagram.tikz}
 

### 2020-06-11 vesicle_code/docs/permeableVes/makefigs/parabolic1Ves/parabolicPhase.m

@@ -7,15 +7,17 @@ file{2} = '~/projects/brinkman/vesicle_code/results/parabolic/pflowR10u1em0p5B1e
 file{3} = '~/projects/brinkman/vesicle_code/results/parabolic/pflowR10u1B1em5Data.bin';
 file{4} = '~/projects/brinkman/vesicle_code/results/parabolic/pflowR10u1e0p5B1em5Data.bin';
 file{5} = '~/projects/brinkman/vesicle_code/results/parabolic/pflowR10u10B1em5Data.bin';
-file{6} = '~/projects/brinkman/vesicle_code/results/parabolic/pflowR10u1e1p5B1em5Data.bin';
-file{7} = '~/projects/brinkman/vesicle_code/results/parabolic/pflowR10u100B1em5Data.bin';
+file{6} = '~/projects/brinkman/vesicle_code/results/parabolic/pflowR10u1e1p5B1em5bData.bin';
+%file{7} = '~/projects/brinkman/vesicle_code/results/parabolic/pflowR10u100B1em5Data.bin';
+file{7} = '~/projects/brinkman/vesicle_code/results/parabolic/pflowR10u100B1em5aData.bin';
 
 file{8} = '~/projects/brinkman/vesicle_code/results/parabolic/pflowR10u0p1B1em4Data.bin';
 file{9} = '~/projects/brinkman/vesicle_code/results/parabolic/pflowR10u1em0p5B1em4Data.bin';
 file{10} = '~/projects/brinkman/vesicle_code/results/parabolic/pflowR10u1B1em4Data.bin';
 file{11} = '~/projects/brinkman/vesicle_code/results/parabolic/pflowR10u1e0p5B1em4Data.bin';
 file{12} = '~/projects/brinkman/vesicle_code/results/parabolic/pflowR10u10B1em4Data.bin';
-file{13} = '~/projects/brinkman/vesicle_code/results/parabolic/pflowR10u1e1p5B1em4Data.bin';
+%file{13} = '~/projects/brinkman/vesicle_code/results/parabolic/pflowR10u1e1p5B1em4Data.bin';
+file{13} = '~/projects/brinkman/vesicle_code/results/parabolic/pflowR10u1e1p5B1em4bData.bin';
 file{14} = '~/projects/brinkman/vesicle_code/results/parabolic/pflowR10u100B1em4Data.bin';
 
[…]

### 2020-06-19 vesicle_code/examples/output/makeImages.m
working on stenosis runs

@@ -72,9 +72,9 @@ if 0
   ax = [-2 2 -2 2];
   options.confined = false;
 end
-if 1
-  file = 'shear1VesUData_Part3.bin';
-%  file = '~/projects/brinkman/vesicle_code/results/shear1Ves/Chi1p0e2_ra065_beta1p0em4p5/shear1VesData.bin';
+if 0
+%  file = 'shear1VesFData_Part3.bin';
+  file = '~/projects/brinkman/vesicle_code/results/shear1Ves/Chi1p0e1p5_ra065_beta1p0em4p5/shear1VesData_Part3.bin';
   ax = [-5 5 -5 5];
   options.confined = false;
   beta = 0.2;
@@ -85,14 +85,15 @@ if 0
   ax = [-3 3 -3 3];
   options.confined = false;
 end
-if 0
+if 1
   file = 'choke1VesData.bin';
-%  file = '~/projects/brinkman/vesicle_code/results/choke1Ves/beta0Scale0p55/choke1VesData.bin';
-  ax = [-20.5 20.5 -3.5 3.5];
+%  file = '~/projects/brinkman/vesicle_code/results/choke1Ves/beta0Scale0p40/choke1VesData.bin';
+  ax = [-50 50 -12.5 12.5];
   options.confined = true;
   options.pressure = true;
   options.savefig = false;
   count = 1;
+  irate = 1;
 end
 if 0
 %  file = 'slit1VesData.bin';

### 2020-06-19 vesicle_code/src/curve.m

@@ -233,6 +233,7 @@ elseif any(strcmp(options,'chokeLong'))
   r = (cos(t).^order + sin(t).^order).^(-1/order);
   x = a*r.*cos(t); y = b*r.*sin(t);
   ind = abs(x) < 10;
+%  ind = abs(x) < 0;
   scalRat = 2*c/(1+c)*(0.5-0.5*cos(pi*x(ind(1:end/2))/10)).^10 + ...   
       (1-c)/(1+c);
   y(ind) = y(ind).*[scalRat;scalRat];
@@ -246,12 +247,46 @@ elseif any(strcmp(options,'chokeLong'))
   r = (cos(t).^order + sin(t).^order).^(-1/order);
   x = a*r.*cos(t); y = b*r.*sin(t);
   ind = abs(x) < 10;
+%  ind = abs(x) < 0;
   scalRat = 2*c/(1+c)*(0.5-0.5*cos(pi*x(ind(1:end/2))/10)).^10 + ...   
       (1-c)/(1+c);
   y(ind) = y(ind).*[scalRat;scalRat];
+
+%  t = (0:N-1)'*2*pi/N;
+%  x = 10*cos(t); y = 10*sin(t);
   X0 = [x;y];
   % redistribute points so that it is equispaced in arclength
 
+elseif any(strcmp(options,'chokeLonger'))
+  a = 100; b = 25/2; c = 0.67; order = 8;
+  % parameters for the boundary
+  t = (0:N-1)'*2*pi/N;
+  r = (cos(t).^order + sin(t).^order).^(-1/order);
+  x = a*r.*cos(t); y = b*r.*sin(t);
+  ind = abs(x) < 35;
+  scalRat = 2*c/(1+c)*(0.5-0.5*cos(pi*x(ind(1:end/2))/35)).^10 + ...   
+      (1-c)/(1+c);
+  y(ind) = y(ind).*[scalRat;scalRat];
+  X0 = [x;y];
+  % choked domain.  a and b control the length and height.  c
+  % controls the width of the gap, and order controls the
+  % regularity
+
+  sa = o.diffProp(X0);
+  t = o.arc(sa);
+  r = (cos(t).^order + sin(t).^order).^(-1/order);
+  x = a*r.*cos(t); y = b*r.*sin(t);
+  ind = abs(x) < 35;
+  scalRat = 2*c/(1+c)*(0.5-0.5*cos(pi*x(ind(1:end/2))/35)).^10 + ...   
[…]

### 2020-06-19 vesicle_code/src/poten.m

@@ -1550,7 +1550,6 @@ for k = 1:ncol % loop over columns of target points
   dis2 = (diffx).^2 + (diffy).^2;
   % difference of source and target location and distance squared
   
-  
   rdotnTIMESrdotf = (diffx.*normalx + diffy.*normaly)./dis2.^2 .* ...
       (diffx.*denx + diffy.*deny);
   % \frac{(r \dot n)(r \dot density)}{\rho^{4}} term
@@ -2318,13 +2317,12 @@ for k2 = 1:ncol % loop over columns of target points
     diffxy = [Xtar(j,k2) - x(:,K1) ; Xtar(j+Ntar,k2) - y(:,K1)];
     % distance squared and difference of source and target location
     rdotn = diffxy(1:vesicle.N,:).*nx(:,K1) + ...
-        diffxy(vesicle.N+1:2*vesicle.N,:).*ny(1:vesicle.N,K1); 
-  
-    val = (nx(:,K1) - 2*rdotn./dis2.*...
-        diffxy(1:vesicle.N,:))./dis2 .* denx(:,K1);
-    val = val + (ny(:,K1) - 2*rdotn./dis2.*...
-        diffxy(vesicle.N+1:2*vesicle.N,:))./dis2 .* deny(:,K1);
+        diffxy(vesicle.N+1:2*vesicle.N,:).*ny(:,K1); 
+    rdotden = diffxy(1:vesicle.N,:).*denx(:,K1) + ...
+        diffxy(vesicle.N+1:2*vesicle.N,:).*deny(:,K1);
+    ndotden = nx(:,K1).*denx(:,K1) + ny(:,K1).*deny(:,K1);
 
+    val = 1./dis2.*(ndotden - 2./dis2.*rdotn.*rdotden);
     pressDLPtar(j,k2) = sum(val(:)); 
   end % j
 end % k2

### 2020-07-02 vesicle_code/docs/permeableVes/main.tex
working on stenosis runs
removing asv files

@@
 maximum flow rate. The length of the vesicle is $L = 4\pi$ and its
-initial reduced area is $\nu = 0.65$. In
-Figure~\ref{fig:parabolicPhaseDiagram}, plot the steady state
-configuration for a variety of flow rates $U$ and permeability rates
-$\beta$. Similar to the shear example, we see that the flow rate has the
-biggest effect on the final shape, and the effect of the permeability
-rate is much weaker. Instead, the permeability rate determines the time
-required for the vesicle to reach a steady state. In
-Tables~\ref{tbl:parabolicRelaxTimes1}
+initial reduced area is $\nu = 0.65$. We first investigate the the
+effect of the flow rate $U$ and the permability rate $\beta$ on the
+steady state shape of the vesicle when it is initially placed on the
+center line $y=0$. Figure~\ref{fig:parabolicPhaseDiagram} shows the
+steady state configuration for a variety of flow rates $U$ and
+permeability rates $\beta$. Similar to the shear example, we see that
+the flow rate has the biggest effect on the final shape while the
+permeability rate has a much weaker effect. Instead, the permeability
+rate determines the time required for the vesicle to reach a steady
+state. In Tables~\ref{tbl:parabolicRelaxTimes1}
 and~\ref{tbl:parabolicRelaxTimes2}, we consider two flow rates and
@@
 see that both times scale with $\beta^{-1}$.
+
+As a second experiment, we investigate the effect of $U$ and $\beta$
+when the vesicle is initialized above line $y=0$. Kaoui et
+al.~\cite{kao-bir-mis2009} analyzed the migration of the same
+experiment, but with an impermeable vesicle. They showed that for
+above a critical reduced area, the vesicle migrates to the center line
+$y=0$ as a symmetric shape. However, for smaller reduced areas, the
+limiting shape is a tank-treading slipper with a center of mass above
+the center line $y=0$. We repeat this experiment but with a
+semi-permeable vesicle.
 
@@
 \end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Semi-Permeable Vesicle in Stenosis}
+Inspired by an experiment that measured the effects of cells on the
+dynamical pressure-drop variations along a micrometer-sized
+channel~\cite{abk-fai-sto2006}, we consider a numerical experiment where
+a semi-permeable vesicle passes through a constriction. We also measure
+the pressure-drop variation by measuring the pressure at the inlet and
+outlet of the constriction.
+
+In each experiment, we initialize an elliptical vesicle with longest
+diameter of 9$\mu$m. We use a length scale of $R_0 = 10^{-6}$m, a
+bending stiffness of $k_b = 10^{-19}$J, and fluid viscosity of $\mu=5
+\times 10^{-2}$kg/ms. Using the relaxation time scale $\tau = \mu
+R_0^3/k_b = 5 \times 10^{-1}$s, the velocity scale is $U = 2 \times
+10^{-6}$m/s, and the pressure scale is $P = k_b/R_0^3 = 10^{-1}$Pa.  The
+geometry is similar to the experiment~\cite{abk-fai-sto2006} where the
+membrane starts in a channel with diameter $25\mu$m and passes into a
+channel with length $45\mu$m and diameter $5\mu$m. Our numerical methods
+are unable to achieve the high-speed flow rate in the experiments, so we
+consider a much smaller flow rate.
+
+\begin{figure}[htp]
+%  \ifTikz
+  \input{figures/stenosisGeom.tikz}
+%  \fi
+%  \includegraphics[width=0.8\linewidth]{figures/parabolicPhaseDiagram.pdf}
+  \caption{\label{fig:stenosisGeom} A caption.}
+\end{figure}
 
@@
 
-%\input{figures/shearPhaseDiagramRA2.tikz}
+ \newpage
+\input{figures/shearPhaseDiagramRA2.tikz}
 %\input{figures/parabolicPhaseDiagram.tikz}

### 2020-07-13 vesicle_code/docs/permeableVes/main.tex
few changes to pnas paper

@@
   %\fi
-  \includegraphics[width=\linewidth]{figures/shearPhaseDiagramRA2.pdf}
+  \includegraphics[width=0.9\linewidth]{figures/shearPhaseDiagramRA2.pdf}
   \caption{\label{fig:shearPhaseDiagram} The steady state shape of a
@@
 %  \fi
-  \includegraphics[width=0.8\linewidth]{figures/parabolicPhaseDiagram.pdf}
+  \includegraphics[width=0.9\linewidth]{figures/parabolicPhaseDiagram.pdf}
   \caption{\label{fig:parabolicPhaseDiagram} The steady state shape of a
@@
 \subsection*{Semi-Permeable Vesicle in Stenosis}
-Inspired by an experiment that measured the effects of cells on the
+Inspired by an experiment that measures the effects of cells on 
 dynamical pressure-drop variations along a micrometer-sized
@@
 \times 10^{-2}$kg/ms. Using the relaxation time scale $\tau = \mu
-R_0^3/k_b = 5 \times 10^{-1}$s, the velocity scale is $U = 2 \times
-10^{-6}$m/s, and the pressure scale is $P = k_b/R_0^3 = 10^{-1}$Pa.  The
-geometry is similar to the experiment~\cite{abk-fai-sto2006} where the
-membrane starts in a channel with diameter $25\mu$m and passes into a
-channel with length $45\mu$m and diameter $5\mu$m. Our numerical methods
-are unable to achieve the high-speed flow rate in the experiments, so we
-consider a much smaller flow rate.
+R_0^3/k_b = 5 \times 10^{-1}$s, the pressure scale is $P = k_b/R_0^3 =
+10^{-1}$Pa. The geometry is similar to an
+experiment~\cite{abk-fai-sto2006} where the membrane starts in a channel
+with diameter $25\mu$m and passes into a channel with length $45\mu$m
+and diameter $5\mu$m (Figure~\ref{fig:stenosisGeom}. We impose a
+Poiseuille flow at an inlet and outlet and a no-slip boundary condition
+on the upper and lower walls. The flow rate is chosen so that the
+residency time of the vesicle in the constriction agrees with the
+experimental results.
 
@@
   \caption{\label{fig:stenosisGeom} A caption.}
+  \todo[inline]{Put snapshots of configuration in the geometry}
+\end{figure}
+
+\begin{figure}[htp]
+%  \ifTikz
+  \input{figures/stenosisPressureFluctuation.tikz}
+%  \fi
+  \caption{\label{fig:stenosisPressure} The excess pressure across the
+  constriction in Figure~\ref{fig:stenosisGeom}. The black dashed lines
+  denote the start and end of the constriction. The results are
+  qualitative agreement with~\cite{abk-fai-sto2006}.}
 \end{figure}
@@
 
- \newpage
-\input{figures/shearPhaseDiagramRA2.tikz}
+% \newpage
+%\input{figures/shearPhaseDiagramRA2.tikz}
 %\input{figures/parabolicPhaseDiagram.tikz}

### 2020-08-17 vesicle_code/docs/permeableVes/main.tex
adding new figure to pnas paper

@@
 center of mass, denoted by $Y_G$.
+
+\begin{figure}[htp]
+  \input{figures/parabolicOffCenterPhaseImpermeable.tikz}
+  \caption{\label{fig:parabolicOffCenterPhaseDiagram} Phase diagram of
+  an impermeable vesicle with several different flow rates $U$ and
+  reduced areas $\nu$. As shown by Kaoui et al.~\cite{kao-bir-mis2009},
+  the final vesicle shape is either an asymmetric parachute or bullet
+  (pink region) or a axisymmetric slipper (yellow region).}
+\end{figure}
 

### 2020-08-17 vesicle_code/examples/output/makeImages.m

@@ -6,8 +6,8 @@ options.pressure = false;
 irate = 1; % controls the speed of the visualization
 
 if 1
-  file = 'parabolic1VesData.bin';
-%  file = 'parabolic1Ves_beta1em3_U1e0Data.bin';
+%  file = 'parabolic1VesData.bin';
+  file = 'parabolic1Ves_speed4.00e02_RA6.00em01Data.bin';  
 %  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/July302020/parabolic1VesData_dtMax1em1_Speed10_beta0.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/pflowR10u1e2B1em4Data.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/pflowR10u1e0p5B1em4bData.bin';

### 2020-08-17 vesicle_code/docs/permeableVes/main.tex
worked on pnas paper

@@
 The inextensibility condition guarantees that the vesicle's length, $L$,
-is conserved, but its area, $A$, is no longer conserved because of
-semi-permeability. Therefore, the reduced area $\nu = 4\pi A/L^2 \in
-(0,1]$ is not conserved. We non-dimensionalize~\eqref{eqn:vesVelocity}
-by introducing the length scale $R_0 = L/2\pi$ and defining the time
-scale $\tau = \mu R_0^3/k_b$, the tension scale $Q = k_b/R_0^2$, and the
-permeability scale $W = R_0/\mu$. Since the bending stiffness $k_b$ only
-sets the time scale, we let $k_b=1$.
+is conserved, but its area, $A$, is not because of semi-permeability.
+Therefore, the reduced area $\nu = 4\pi A/L^2 \in (0,1]$ is not
+conserved. We non-dimensionalize~\eqref{eqn:vesVelocity} by introducing
+the length scale $R_0 = L/2\pi$ and defining the time scale $\tau = \mu
+R_0^3/k_b$, the tension scale $Q = k_b/R_0^2$, and the permeability
+scale $W = R_0/\mu$. The background velocity $\uu_\infty$ is
+non-dimensionalized with $R_0/\tau$. For all simulations, the bending
+modulus is $10^{-19}J$. Using these scales, all equations are written in
+dimensionless form.
 
@@
 \end{align}
-where the Lagrange multiplier $\Lambda$ the constant tension. Note that
-there is no pressure Lagrange multiplier since the vesicle's area
-fluctuates. Taking the variation of $\mathcal{L}$ with respect to
-$\gamma$, and setting this vesicle force to zero, the steady state shape
-satisfies $\kappa_{ss} + \frac{1}{2}\kappa^3 - \Lambda \kappa = 0$,
-with initial conditions $\kappa(0) = \kappa_0$ and $\kappa_s(0) = 0$.
-Integrating once, we have
+where the Lagrange multiplier $\Lambda$ is the tension. Note that there
+is no pressure Lagrange multiplier since the vesicle's area fluctuates.
+Taking the variation of $\mathcal{L}$ with respect to $\gamma$ and
+setting it to zero, the steady state shape satisfies $\kappa_{ss} +
+\frac{1}{2}\kappa^3 - \Lambda \kappa = 0$, with initial conditions
+$\kappa(0) = \kappa_0$ and $\kappa_s(0) = 0$.  Integrating once, we have
 \begin{align}
   \frac{\kappa_s^2}{2} + \frac{\kappa^4}{8} - 
-    \frac{\Lambda}{2}\kappa^2 = \kappa_0^4 - \frac{\Lambda}{2}\kappa_0^2.
+    \frac{\Lambda}{2}\kappa^2 = \frac{\kappa_0^4}{8} - 
+    \frac{\Lambda}{2}\kappa_0^2.
   \label{eqn:curvODE}
@@
 
-In addition to computing the steady shape, we can compute the transient
-area of the vesicle. The area of the vesicle is
+In addition to computing the steady shape, we also compute the transient
+area of the vesicle. Since the area of the vesicle is
 \begin{align}
@@
 \end{align}
-so the derivative of $A(t)$ includes terms due to the time derivative of
-$\xx \cdot \nn$, and a term due to interface
-stretching~\cite{lai-tse-hua2008}, but the stretching term is zero
-because of the local inextensibility condition. Therefore,
+its derivative includes terms due to the time derivative of $\xx \cdot
+\nn$ and a term due to interface stretching~\cite{lai-tse-hua2008}, but
+the stretching term is zero because of the local inextensibility
+condition. Therefore,
 \begin{align}
@@
   &= -\beta \int_\gamma \left(\kappa^3 + \kappa \sigma \right) 
-    \, ds \\
-  &= \beta \int_\gamma \left(
+    \, ds = \beta \int_\gamma \left(
     \frac{\kappa^3}{2} - \kappa \Lambda \right) \, ds.
@@
 \end{align}
-Note that this is consistent with the steady state curvature and tension
+This is consistent with the steady state curvature and tension
 in~\eqref{eqn:SSshape} since these constant values result in the
@@
 \subsection*{Discretization in Space}
-By using an integral equation formulation, the unknowns are the vesicle
-position and tension which we track at a set of $N$ discretization
-points. All arclength derivatives are computed with Fourier
-differentiation, and eighth-order quadrature is applied to the weakly
-singular single-layer potential~\cite{alp1999}.
+Using an integral equation formulation, the unknowns are the vesicle's
+position and tension that we track at a set of $N$ discretization
+points. All derivatives are computed with Fourier differentiation, and
+the single-layer potential operator is discretized with eighth-order
+quadrature~\cite{alp1999}. For constricted flows, nearly-singular
+integrals are accurately computed with an interpolation-based quadrature
+rule~\cite{qua-bir2014}.
 
@@
 \subsection*{Discretization in Time}
-The high-order derivatives in the bending and tension
-forces~\eqref{eqn:membraneForces} result in stiffness if an explicit
-time stepping method is applied to equation~\eqref{eqn:vesVelocity}.
-Therefore, we use a modification of a time stepping method that
-discretizes high-order derivatives
-semi-implicitly~\cite{vee-gue-zor-bir2009}. Introducing notation for
-all the required differential and projection operators
+To eliminate stringent time step restrictions, we modify a time stepping
+method that discretizes high-order derivatives
+semi-implicitly~\cite{vee-gue-zor-bir2009}. Introducing notation for the
+differential and projection operators
 \begin{alignat}{3}
@@
   &D[\xx]\ff = \xx_s \cdot \ff_s, 
-  &&P[\xx]\ff = (\ff \cdot \nn) \nn. 
+  &&P[\xx]\ff = (\ff \cdot \nn) \nn,
 \end{alignat}
@@
 \end{align}
-Letting $B^N$ be the bending operator due to the vesicle
-configuration at time $t^N$, and similar notation for the other
-operators, we use the semi-implicit time stepping method
+Letting $B^N$ be the bending operator due to the vesicle configuration
+at time $t^N$, and similar notation for the other operators, we use the
+first-order semi-implicit time stepping method
 \begin{alignat}{3}  
@@
 
-To achieve high-order accuracy over long time horizons, we modify the
-adaptive spectral deferred correction time stepping method introduced
-in~\cite{qua-bir2016}. Since the area of the vesicle is no longer
-conserved, we only use the length of the vesicle to estimate the
-local truncation error which then determines if a time step is accepted
-or rejected and the subsequent time step size.
+To achieve high-order accuracy over long time horizons, we modify an
+adaptive spectral deferred correction time stepping
+method~\cite{qua-bir2016}. Since the area of the vesicle is not
+conserved, we only use the length of the vesicle to estimate the local
+truncation error that determines if a time step is accepted or not and
+the subsequent time step size.
 
@@
 area is computed directly from the vesicle shape (solid lines) and by
-integrating equation~\eqref{eqn:areaROC} (marks) with a first-order
+integrating~\eqref{eqn:areaROC} (marks) with a first-order
 method. We also include black dashed lines indicating the times,
@@
   semi-permeable vesicle, with permeability rate $\beta$ in a quiescent
-  flow. The solid lines compute the area using
-  equation~\eqref{eqn:area}, while the marks are computed by integrating
-  equation~\eqref{eqn:areaROC}. The dashed black lines are the times
-  when the vesicle's area is within 1.3\% of its maximum value of
-  $4\pi$.}
+  flow. The solid lines compute the area using~\eqref{eqn:area}, while
+  the marks are computed by integrating~\eqref{eqn:areaROC}. The dashed
+  black lines are the times when the vesicle's area is within 1.3\% of
+  its maximum value of $4\pi$.}
 \end{figure}
@@
 \subsection*{Shear Flow}
-\begin{itemize}
-  \item Mild dependence on initial shape
-
-  \item Look at tank-treading angle, tank-trading speed, reduced area,
-    absolute value of the permeable flux
-
-  \item Max flux at the steady state as a function of beta and
-    $\dot{\gamma}$
-
-  \item reduced area/inclination angle for a particular $(\beta,\gamma)$
-    and different flux rates using the gating functions (Apr 7 and 9) as
-    well as constant $\beta$
-\end{itemize}
-
 We consider a semi-permeable vesicle in the shear flow
 $\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$ with different permeability
-rates $\beta$ and shear rates $\dot{\gamma}$.  For a two-dimensional
-impermeable vesicle, depending on the reduced area and viscosity
-contrast, vesicles in a shear flow either tank tread or
-tumble~\cite{fin-lam-sei-gom2008,kra-win-sei-lip1996}, but tumbling is
-not possible with viscosity contrast of one. Since we are considering
-semi-permeable vesicles, we assume that there is no viscosity contrast,
-and we do not expect to observe tumbling dynamics.
+rates $\beta$ and shear rates $\dot{\gamma}$. Depending on its reduced
+area and viscosity contrast, two-dimensional vesicles either tank tread
+or tumble~\cite{fin-lam-sei-gom2008,kra-win-sei-lip1996}. Since we are
+considering semi-permeable vesicles, we assume there is no viscosity
+contrast, and tumbling is not possible.
 
@@
 rates and shear rates, the semi-permeable vesicle tilts to an
-inclination angle and undergoes tank-treading behavior. However, because
-of the semi-permeability, the final reduced area does not agree with the
-initial reduced area. In Figure~\ref{fig:shearPhaseDiagram}, we plot the
-final shape of the vesicle for various permeability rates, $\beta$, and
-shear rates $\dot{\gamma}$. We also includes lines of constant final
-reduced area. We see that the shear rate has the largest effect on the
-final reduced area. However, for small $\beta$, the permeability rate
-also has a large effect on the final reduced area. In particular, the
-smallest final reduced areas are the result of large shear rates and
-small permeability rates.
-\todo[inline]{Also reporting inclination angle as well}
+inclination angle and undergoes tank treading behavior. However, because
+of the semi-permeability, the initial and final reduced areas differ. In
+Figure~\ref{fig:shearPhaseDiagram}, we plot the final shape of the
+vesicle for various permeability rates, $\beta$, and shear rates
+$\dot{\gamma}$. The shear rate has the largest effect on the final
+reduced area.
 
@@
   %\fi
-  \includegraphics[width=0.9\linewidth]{figures/shearPhaseDiagramRA2.pdf}
+  \includegraphics[width=\linewidth]{figures/shearPhaseDiagramRA2.pdf}
   \caption{\label{fig:shearPhaseDiagram} The steady state shape of a
   semi-permeable vesicle with several different permeability rates
-  $\beta$ and shear rates $\dot{\gamma}$. The black lines represent
-  contour lines of the final reduced areas (left) and the inclination
-  angle (right). The reduced area and inclination angle of each contour
-  line are reported.}
+  $\beta$ and shear rates $\dot{\gamma}$.}
 \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Stenosis}
-We consider a semi-permeable vesicle in a constricted geometry. A
-double-layer potential is used to impose a boundary condition on the
-outer wall, and near-singular integration~\cite{qua-bir2014} quadrature
-resolves the vesicle-wall interaction.
 
@@
 We consider a semi-permeable vesicle in the Poiseuille flow $\uu =
-U(1-(y/R)^2,0)$, where $R=10$ determines the flow width, and $U$ is the
-maximum flow rate. The length of the vesicle is $L = 4\pi$ and its
-initial reduced area is $\nu = 0.65$. We first investigate the the
-effect of the flow rate $U$ and the permability rate $\beta$ on the
-steady state shape of the vesicle when it is initially placed on the
-center line $y=0$. Figure~\ref{fig:parabolicPhaseDiagram} shows the
-steady state configuration for a variety of flow rates $U$ and
-permeability rates $\beta$. Similar to the shear example, we see that
-the flow rate has the biggest effect on the final shape while the
-permeability rate has a much weaker effect. Instead, the permeability
-rate determines the time required for the vesicle to reach a steady
-state. In Tables~\ref{tbl:parabolicRelaxTimes1}
-and~\ref{tbl:parabolicRelaxTimes2}, we consider two flow rates and
-report the time, $t_\mathrm{steady}$, required for the vesicle's area to
-be within 1.3\% of its maximum area, and the time, $t_\mathrm{inflate}$,
-required for the vesicle's area to exceed 1.3\% of its initial area. We
-see that both times scale with $\beta^{-1}$.
-
-As a second experiment, we investigate the effect of $U$ and $\beta$
-when the vesicle is initialized above line $y=0$. Kaoui et
-al.~\cite{kao-bir-mis2009} analyzed the migration of the same
-experiment, but with an impermeable vesicle. They showed that for
-above a critical reduced area, the vesicle migrates to the center line
-$y=0$ as a symmetric shape. However, for smaller reduced areas, the
-limiting shape is a tank-treading slipper with a center of mass above
-the center line $y=0$. We repeat this experiment but with a
-semi-permeable vesicle.
+U(1-(y/W)^2,0)$, where $U$ is the maximum imposed velocity. The length
+of the vesicle is $L = 4\pi$ and its initial reduced area is $\nu =
+0.65$. The width $W$ is chosen so that $W/R = 10$, where $R$ is the
+radius of the vesicle. We investigate the effect of the maximum velocity
+$U$ and the permeability rate $\beta$ on the steady state shape of a
+vesicle initially placed on the center line $y=0$.
+Figure~\ref{fig:parabolicPhaseDiagram} shows the steady state
+configuration for a variety of maximum velocities and permeability
+rates. Similar to the shear example, the maximum velocity strongly
+affects the final shape while the permeability rate's effect is much
+weaker. Instead, the permeability rate determines the time required for
+the vesicle to reach a steady state. In
+Table~\ref{tbl:parabolicRelaxTimes1}, we consider two maximum velocities
+and report the time, $t_\mathrm{steady}$, required for the vesicle's
+area to be within 1.3\% of its maximum area, and the time,
+$t_\mathrm{inflate}$, required for the vesicle's area to exceed 1.3\% of
+its initial area. We see that both times scale with $\beta^{-1}$.
 
@@
   semi-permeable vesicle with several different permeability rates
-  $\beta$ and flow rates $U$. At high flow rates, the vesicle
-  self-intersects before reaching a steady state configuration.}
+  $\beta$ and flow rates $U$. The numbers reported above each vesicle is
+  its reduced area. At high flow rates, the vesicle self-intersects
+  before reaching a steady state configuration.}
 \end{figure}
@@
   ($t_\mathrm{steady}$) and to begin inflating ($t_\mathrm{inflate}$).
-  The flow rate is $U = 10^{-1}$.}
+  The times are reported for the maximum velocities $0.1 \mu m/s$ and
+  $10 \mu m/s$.}
   \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
+    \multicolumn{5}{c}{$U = 0.1 \mu m/s$} \\
     $\beta$ & $t_\mathrm{steady}$ & ratio & $t_\mathrm{inflate}$ & ratio \\
@@
   \end{tabular}
-\end{table}
-
-\begin{table}[htp]
-  \centering
-  \caption{\label{tbl:parabolicRelaxTimes2} The time for a
-  semi-permeable vesicle in a Poiseuille flow to reach its steady state
-  ($t_\mathrm{steady}$) and to begin inflating ($t_\mathrm{inflate}$).
-  The flow rate is $U = 10^{1}$.}
+
   \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
+    \multicolumn{5}{c}{$U = 10 \mu m/s$} \\
+    $\beta$ & $t_\mathrm{steady}$ & ratio & $t_\mathrm{inflate}$ & ratio \\
     \midrule
-    $\beta$ & $t_\mathrm{steady}$ & ratio & $t_\mathrm{inflate}$ & ratio \\
     $10^{0}$  & $3.55 \times 10^{0}$ & ---  
@@
 
-Finally, we examine the effect of the non-linear Poiseuille flow in the
-migration of semi-permeable vesicle. Similar to experiments performed by
-Kaoui et al.~\cite{kao-bir-mis2009}, we initialize the vesicle's
-center of mass above the $y$-axis and examine the y position of its
-center of mass, denoted by $Y_G$.
+We next examine the effect of the non-linear Poiseuille flow on the
+migration of semi-permeable vesicle. In this experiment, the vesicle is
+initialized above the center line $y=0$. At sufficiently large reduced
+areas and maximum velocities, the steady state vesicle configuration is
+axisymmetric along the center line (parachute or bullet). In contrast,
+for small reduced areas and maximum velocities, the steady-state shape
+is axisymmetric, above the center line, and undergoes a tank treading
+motion (slipper). These dynamics are investigated by Danker et
+al.~\cite{dan-vla-mis2009} and Kaoui et al.~\cite{kao-bir-mis2009}. To
+validate our methods, in Figure~\ref{fig:parabolicOffCenterPhaseDiagram}
+we reconstruct the phase diagram for an impermeable
+vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
+qualitatively agree, Kaoui et al.~report that the vesicles with
+$\nu=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
+axisymmetric. In our simulations these vesicles are slightly asymmetric,
+are undergoing a tank treading motion, and we therefore report them as
+asymmetric slippers.
 
 \begin{figure}[htp]
+  \ifTikz
   \input{figures/parabolicOffCenterPhaseImpermeable.tikz}
+  \fi
   \caption{\label{fig:parabolicOffCenterPhaseDiagram} Phase diagram of
@@
   reduced areas $\nu$. As shown by Kaoui et al.~\cite{kao-bir-mis2009},
-  the final vesicle shape is either an asymmetric parachute or bullet
-  (pink region) or a axisymmetric slipper (yellow region).}
+  the final vesicle shape is either an axisymmetric parachute or bullet
+  (pink region) or an asymmetric slipper (yellow region).}
 \end{figure}
@@
 \begin{figure}[htp]
-%  \ifTikz
+  \ifTikz
   \input{figures/stenosisGeom.tikz}
-%  \fi
+  \fi
 %  \includegraphics[width=0.8\linewidth]{figures/parabolicPhaseDiagram.pdf}
-  \caption{\label{fig:stenosisGeom} A caption.}
-  \todo[inline]{Put snapshots of configuration in the geometry}
+  \caption{\label{fig:stenosisGeom} A single semi-permeable vesicle
+  passing through a constriction. The geometry and parameters are chosen
+  to replicate the experiments of Abkarian et
+  al.~\cite{abk-fai-sto2006}.}
 \end{figure}
@@
 \begin{figure}[htp]
-%  \ifTikz
+  \ifTikz
   \input{figures/stenosisPressureFluctuation.tikz}
-%  \fi
+  \fi
   \caption{\label{fig:stenosisPressure} The excess pressure across the

### 2020-08-17 vesicle_code/examples/output/makeImages.m

@@ -7,7 +7,7 @@ irate = 1; % controls the speed of the visualization
 
 if 1
 %  file = 'parabolic1VesData.bin';
-  file = 'parabolic1Ves_speed4.00e02_RA6.00em01Data.bin';  
+  file = 'parabolic1Ves_speed6.00e02_RA6.00em01Data.bin';  
 %  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/July302020/parabolic1VesData_dtMax1em1_Speed10_beta0.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/pflowR10u1e2B1em4Data.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/pflowR10u1e0p5B1em4bData.bin';
@@ -17,14 +17,7 @@ if 1
 %  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/pflowR10u1ep0B1em4bData.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/pflowR10u1ep1p0B1em4dData.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/pflowR10u1ep1p0B0em4dData.bin';
-%  file = '~/Dropbox/Adhesion/PermeableV/pflowB0/pflowMay14B0Data.bin';
-%  file = '~/Dropbox/Adhesion/PermeableV/pflowB0/pflowMay14R10u100B0Data.bin';
-%  file = '~/Dropbox/Adhesion/PermeableV/pflowB0/pflowMay14R10u10B0Data.bin';
-%  file = '~/Dropbox/Adhesion/PermeableV/pflowB0/pflowR10u1ep1p0B0em4dData.bin';
-%  file = '~/Dropbox/Adhesion/PermeableV/pflowB0/pflowR10u1ep1p0B0em4eData.bin';
-%  file = '~/Dropbox/Adhesion/PermeableV/pflowB0/pflowR10u1ep1p0B0em4fData.bin';
-%  file = '~/Dropbox/Adhesion/PermeableV/pflowB0/pflowR10u2e0B0em4dData.bin';
-%  file = '~/Dropbox/Adhesion/PermeableV/pflowB0/pflowR10u2e0B0em4eData.bin';
[…]

### 2020-08-18 vesicle_code/docs/permeableVes/main.tex
small changs to paper

@@
 \section*{Examples}
-We consider a single semi-permeable vesicle in four different flow
-regimes. All vesicles have a length of $L=4\pi$, but the area is not
-conserved because of semi-permeability. However, the area is bounded by
-$4\pi$ which is the area of a circle with length $L=4\pi$. For each
-simulation, we apply an SDC second-order adaptive time stepping
-method~\cite{qua-bir2016}.
+We consider a single semi-permeable vesicle in quiescent, shear, and
+parabolic flows. We also consider a semi-permeable vesicle passing
+through a constriction. For each example, all vesicles have a length
+$L$, but the area is not conserved because of semi-permeability, but it
+is bounded by $L^2/4\pi$ which is the area of a circle with
+circumference $L$. For each simulation, we apply an SDC second-order
+adaptive time stepping method~\cite{qua-bir2016}.
 
@@
 on~\eqref{eqn:SSshape}, a semi-permeable vesicle relaxes to a circle
-with positive constant tension $\Lambda = 2\pi^2/L^2$. Recalling the
-governing equation for the area in~\eqref{eqn:areaROC}, we expect both
-the time for the vesicle to deviate from its initial area, and the time
-to reach its steady state will scale with $\beta^{-1}$. In
-Table~\ref{tbl:ellipseRelaxTimes}, we report the time,
-$t_\mathrm{steady}$, required for the vesicle's area to be within 1.3\%
-of its maximum area, and the time, $t_\mathrm{inflate}$, required for
-the vesicle's area to exceed 1.3\% of its initial area. We see that both
-times scale with $\beta^{-1}$. We also plot the area of a vesicle with
-six different permeability rates in Figure~\ref{fig:ellipseArea}. The
-area is computed directly from the vesicle shape (solid lines) and by
-integrating~\eqref{eqn:areaROC} (marks) with a first-order
-method. We also include black dashed lines indicating the times,
-$t_{\mathrm{steady}}$, that the vesicle is near its steady state
-circular shape.
+with positive constant tension $\Lambda = 2\pi^2/L^2$. Since the
+governing equation for the area in~\eqref{eqn:areaROC} is proportional
+to $\beta$, we expect both the time for the vesicle to deviate from its
+initial area, and the time to reach its steady state to be proportional
+to $\beta^{-1}$. In Table~\ref{tbl:ellipseRelaxTimes}, we report the
+time, $t_\mathrm{steady}$, required for the vesicle's area to be within
+1.3\% of its maximum area, and the time, $t_\mathrm{inflate}$, required
+for the vesicle's area to exceed 1.3\% of its initial area. Both times
+are proportional to $\beta^{-1}$. Next we plot the area of a vesicle
+with six different permeability rates in Figure~\ref{fig:ellipseArea}.
+The area is computed directly from the vesicle shape (solid lines) and
+by integrating~\eqref{eqn:areaROC} (marks) with a first-order method. We
+include black dashed lines indicating the times, $t_{\mathrm{steady}}$,
+that the vesicle is near its steady state circular shape.
 \begin{table}[htp]
@@
 $\SS[\ff]$. Initially, since $\beta$ is small, the semi-permeability
-velocity is much smaller than the force balance velocity. Therefore, the
-velocity resembles that of an impermeable vesicle. As the
+velocity is much smaller than the force balance velocity and the
+velocity resembles an impermeable vesicle. As the
 vesicle approaches the steady state shape of an impermeable vesicle, the
 force balance velocity decreases below the semi-permeability velocity,
-and then the semi-permeable vesicle begins to dominate, causing the
-vesicle to inflate.  As the vesicle becomes more circular, the
+and then the semi-permeable velocity begins to dominate, causing the
+vesicle to inflate. As the vesicle becomes circular, the
 membrane force and the corresponding velocity both converge to
@@
 $\beta=10^{-3}$. We also plot the velocity of an identically initialized
-impermeable vesicle (green).  At $t=0.5$, semi-permeability velocity is
+impermeable vesicle (green). At $t=0.5$, the semi-permeability velocity is
 small relative to the force balance velocity, and the semi-permeable
 velocity matches with the impermeable vesicle velocity. At time $t=5$,
-the magnitude of the velocity of the impermeable vesicle and the force
-balance velocity are both comparable to the magnitude of the
+the magnitudes of the velocity of the impermeable vesicle and the force
+balance velocity are comparable to the magnitude of the
 semi-permeable velocity, and the semi-permeable vesicle begins to
 inflate. Then, at time $t=50$, the impermeable vesicle is at its steady
-state, while the semi-permeable vesicle still has contributions due to
-semi-permeability and force balance. The bottom right plot is the
+state, while the semi-permeable vesicle is still tending to a circular
+vesicle. The bottom right plot of Figure~\ref{fig:vesVeocity} is the
 maximum norm of the different velocity contributions as a function of

### 2020-08-20 vesicle_code/docs/permeableVes/main.tex
adding new image to pnas draft

@@
 \newif\ifTikz
-%\Tikztrue
-\Tikzfalse
+\Tikztrue
+%\Tikzfalse
 
@@
 
-\todo[inline]{redo this paragraph}
-Finally, letting $\beta=1$, we consider a semi-permeable vesicle that
-initially has regions of positive and negative curvature. The vesicle
-tension, $\Lambda$, and the flux, $\ff \cdot \nn$,
-are plotted in Figure~\ref{fig:starTensionFlux}. The vesicle undergoes
-three general behaviors: (i) For $t \in (0,1.6 \times 10^{-2})$, the
-vesicle has a net negative flux resulting in a loss of area; (ii) For $t
-\in (1.6 \times 10^{-2},1.0)$, the vesicle has a net positive flux and
-the tension most of the membrane is undergoing negative tension; (iii)
-For $t \in (1.0,2.0)$, the vesicle is near its steady state and
-transitions to a positive constant tension. In the first time interval,
-the vesicle deflates. Near the points of largest negative curvature,
-there is a large negative tension and large inflow (positive flux).
-Correspondingly, near the points with largest positive curvature, there
-is a small tension and outflow (negative flux). In the second time
-interval, the tension is negative and the flux is positive nearly
-everywhere. The regions with largest negative curvature correspond to
-regions with largest negative tension and the most inflow. Finally, in
-the last time interval, the tension transitions to a positive constant
-function, the membrane force and flux transition to zero, resulting in a
-steady state circular vesicle with positive constant tension.
+We next investigate the interplay between the tension, flux, and
+curvature of a semi-permeable vesicle. We let $\beta = 1$ and initialize
+the vesicle with regions of both positive and negative curvature. The
+vesicle tension, $\Lambda$, and the flux, $\ff \cdot \nn$, are plotted
+in Figure~\ref{fig:starTensionFlux}. The vesicle undergoes three general
+behaviors: (i) For $t \in (0,1.6 \times 10^{-2})$, the vesicle has a net
+negative flux resulting in a loss of area; (ii) For $t \in (1.6 \times
+10^{-2},1.0)$, the vesicle has a net positive flux and the tension along
+most of the membrane is negative; (iii) For $t \in (1.0,2.0)$, the
+vesicle is near its steady state and transitions to a positive constant
+tension. In the first time interval, the vesicle deflates. Near the
+points of largest negative curvature, there is a large negative tension
+and large inflow (positive flux).  Correspondingly, near the points with
+largest positive curvature, there is a small tension and outflow
+(negative flux). In the second time interval, the tension is negative
+and the flux is positive nearly everywhere. The regions with largest
+negative curvature correspond to regions with largest negative tension
+and the most inflow. Finally, in the last time interval, the tension
+transitions to a positive constant function, the membrane force and flux
+transition to zero, resulting in a steady state circular vesicle with
+positive constant tension.
 
@@
   \centering
-  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
-  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
-  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
-  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
-  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime5.pdf}
-
-  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
-  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
-  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
-  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
-  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
-  \caption{\label{fig:starTensionFlux} The vesicle tension (top) and
-  flux (bottom) of the semi-permeable vesicle in a quiescent
-  flow with $\beta=1$.}
+  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
+  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
+
+  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
+  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
+
+  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
+  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
+
+  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
+  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
+
+  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime5.pdf}
+  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
+  \caption{\label{fig:starTensionFlux} The vesicle tension (left) and
+  flux (right) of the semi-permeable vesicle in a quiescent flow with
+  $\beta=1$.}
 \end{figure}
+
+%\begin{figure}[htp]
+%  \centering
+%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
+%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
+%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
+%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
+%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime5.pdf}
+%
+%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
+%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
+%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
+%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
+%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
+%  \caption{\label{fig:starTensionFlux} The vesicle tension (top) and
+%  flux (bottom) of the semi-permeable vesicle in a quiescent
+%  flow with $\beta=1$.}
+%\end{figure}
 
@@
   (pink region) or an asymmetric slipper (yellow region).}
+\end{figure}
+
+\begin{figure}[htp]
+  \ifTikz
+  \input{figures/parabolicOffCenterPhaseSemipermeable.tikz}
+  \fi
+%  \caption{\label{fig:parabolicOffCenterPhaseDiagram} Phase diagram of
+%  an impermeable vesicle with several different flow rates $U$ and
+%  reduced areas $\nu$. As shown by Kaoui et al.~\cite{kao-bir-mis2009},
+%  the final vesicle shape is either an axisymmetric parachute or bullet
+%  (pink region) or an asymmetric slipper (yellow region).}
 \end{figure}

### 2020-08-26 vesicle_code/docs/permeableVes/main.tex
working on stenosis runs

@@
 rates and shear rates, the semi-permeable vesicle tilts to an
-inclination angle and undergoes tank treading behavior. However, because
-of the semi-permeability, the initial and final reduced areas differ. In
+inclination angle and undergoes tank treading dynamics. Because of the
+semi-permeability, the initial and final reduced areas differ. In
 Figure~\ref{fig:shearPhaseDiagram}, we plot the final shape of the
@@
   %\ifTikz
-  %\input{figures/shearPhaseDiagramRA2.tikz}
+%  \input{figures/shearPhaseDiagramRA2.tikz}
   %\fi
@@
   semi-permeable vesicle with several different permeability rates
-  $\beta$ and shear rates $\dot{\gamma}$.}
+  $\beta$ and shear rates $\dot{\gamma}$. The final reduced areas are
+  reported for the largest and smallest parameter values. The final
+  reduced area decreases with the flow rate, while the permeability rate
+  has a very small effect on the steady state shape.}
 \end{figure}
@@
 al.~\cite{dan-vla-mis2009} and Kaoui et al.~\cite{kao-bir-mis2009}. To
-validate our methods, in Figure~\ref{fig:parabolicOffCenterPhaseDiagram}
-we reconstruct the phase diagram for an impermeable
+validate our methods, in
+Figure~\ref{fig:parabolicOffCenterImpermeablePhaseDiagram} we
+reconstruct the phase diagram for an impermeable
 vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
@@
   \fi
-  \caption{\label{fig:parabolicOffCenterPhaseDiagram} Phase diagram of
-  an impermeable vesicle with several different flow rates $U$ and
-  reduced areas $\nu$. As shown by Kaoui et al.~\cite{kao-bir-mis2009},
-  the final vesicle shape is either an axisymmetric parachute or bullet
-  (pink region) or an asymmetric slipper (yellow region).}
+  \caption{\label{fig:parabolicOffCenterImpermeablePhaseDiagram} Phase
+  diagram of an impermeable vesicle with several different flow rates
+  $U$ and reduced areas $\nu$. As shown by Kaoui et
+  al.~\cite{kao-bir-mis2009}, the final vesicle shape is either an
+  axisymmetric parachute or bullet (pink region) or an asymmetric
+  slipper (yellow region).}
 \end{figure}
@@
   \fi
-%  \caption{\label{fig:parabolicOffCenterPhaseDiagram} Phase diagram of
-%  an impermeable vesicle with several different flow rates $U$ and
-%  reduced areas $\nu$. As shown by Kaoui et al.~\cite{kao-bir-mis2009},
-%  the final vesicle shape is either an axisymmetric parachute or bullet
-%  (pink region) or an asymmetric slipper (yellow region).}
+  \caption{\label{fig:parabolicOffCenterSemipermeablePhaseDiagram} Phase
+  diagram of an semi-permeable vesicle, with $\beta = 10^{-3}$, with
+  several different flow rates $U$ and reduced areas $\nu$. The
+  steady-state reduced area for each flow rate, which is reported along
+  the top of the vesicles, is nearly independent of the initial reduced
+  area. Low flow rates result in axisymmetric vesicles with large
+  reduced area, and high flow rates result in asymmetric vesicles with
+  low reduced area. Results at higher flow rates are not eporeted since
+  the vesicle self-intersects.}
 \end{figure}

### 2020-08-26 vesicle_code/examples/output/makeImages.m

@@ -5,10 +5,10 @@ options.pressure = false;
 
 irate = 1; % controls the speed of the visualization
 
-if 1
+if 0
 %  file = 'parabolic1VesData.bin';
-  file = 'parabolic1Ves_speed8.00e02_RA9.00em01Data.bin';  
-%  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/impermeable/parabolic1Ves_speed2.00e02_RA7.50em01Data.bin';
+  file = 'parabolic1Ves_speed8.00e02_RA6.00em01Data.bin';  
+%  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/semipermeable/parabolic1Ves_speed8.00e02_RA6.00em01Data.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/July302020/parabolic1VesData_dtMax1em1_Speed10_beta0.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/pflowR10u1e2B1em4Data.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/pflowR10u1e0p5B1em4bData.bin';
@@ -89,7 +89,7 @@ if 0
 end
 if 0
 %  file = 'shear1VesDData_Part4.bin';
-  file = '~/projects/brinkman/vesicle_code/results/shear1Ves/Chi1p0e1_ra065_beta1p0em5/shear1VesData_Part5.bin';
+  file = '~/projects/brinkman/vesicle_code/results/shear1Ves/Chi1p0e1p5_ra065_beta1p0em4/shear1VesData_Part3.bin';
   ax = [-5 5 -5 5];
   options.confined = false;
   beta = 0.2;
@@ -111,7 +111,7 @@ if 0
   irate = 1;
 end
 
-if 0
+if 1
   file = 'choke1VesData.bin';
 %file = '~/projects/brinkman/vesicle_code/results/choke1VesLong/beta0Scale1p44_kappa1e0_farfield1e0/choke1VesData.bin'
 %file = '~/projects/brinkman/vesicle_code/results/choke1VesLong/beta0Scale1p44_kappa1e1_farfield1e0/choke1VesData.bin';
@@ -119,15 +119,15 @@ if 0
[…]

### 2020-08-31 vesicle_code/docs/permeableVes/main.tex
updating pnas paper

@@
 \section*{Governing equations} \label{sc:formulate}
-Consider a two-dimensional semi-permeable vesicle suspended in an
-unbounded viscous fluid domain, subjected to an imposed flow
-$\uu_\infty(\xx)$, for any $\xx \in \RR^2$.  Assume that the interior
-and exterior fluids have the same viscosity $\mu$. Let $\xx$ be the
-position of the interface $\gamma$, $\uu$ be the fluid velocity, and
-$p$ be the pressure. In the vanishing Reynolds number limit, the
-governing equations for the ambient fluid are
+We consider a two-dimensional semi-permeable vesicle suspended in an
+unbounded viscous fluid driven by the imposed flow $\uu_\infty(\xx)$.
+Since fluid is transported across the semi-permeable vesicle membrane,
+we only consider fluids with uniform viscosity. Letting $\gamma$ be the
+vesicle interface, the fluid velocity $\uu$ and pressure $p$ satisfy
 %
@@
   \label{eqn:governing}
-  -\nabla p + \mu \triangle \uu &= 0, 
+  -\nabla p + \mu \triangle \uu &= 0, \quad
   \nabla \cdot \uu = 0, \qquad &&\xx \in \RR^2 \setminus \gamma, \\
@@
 \end{align}
-The physical tension satisfies $\Lambda = \sigma + 1.5 \kappa^2$, where
+The physical tension is $\Lambda = \sigma + 1.5 \kappa^2$, where
 $\kappa$ is the membrane curvature.
 
-The kinematic condition is modified to account for flow through the
-vesicle. A standard choice for this flux is the difference in mechanical
-force~\cite{yao-mor2017}
+Semi-permeability is introduced by modifying the vesicle velocity from
+the standard choice. Instead of using the no-slip boundary condition, we
+assume the fluid flux through the boundary is proportional to the
+mechanical force~\cite{yao-mor2017}. That is, 
 \begin{align}
@@
 \end{align}
-where $\beta$ is a semi-permeability rate.
+where $\beta$ is the semi-permeability rate.
 
@@
 \subsection*{Integral equation formulation}
-Since the flow is governed by the linear Stokes equations, it can be
-represented in terms of layer potentials. Given the interfacial boundary
+Since the fluid satisfies the Stokes equations, it can be represented as
+layer potential. Given the interfacial boundary
 conditions~\eqref{eqn:jump}, the fluid velocity is
@@
 The inextensibility condition guarantees that the vesicle's length, $L$,
-is conserved, but its area, $A$, is not because of semi-permeability.
+is conserved, while its area, $A$, can change due to semi-permeability.
 Therefore, the reduced area $\nu = 4\pi A/L^2 \in (0,1]$ is not
@@
 scale $W = R_0/\mu$. The background velocity $\uu_\infty$ is
-non-dimensionalized with $R_0/\tau$. For all simulations, the bending
-modulus is $10^{-19}J$. Using these scales, all equations are written in
-dimensionless form.
+non-dimensionalized with $R_0/\tau$.
 
@@
 Following the analysis of Veerapaneni et al.~\cite{vee-raj-bir-pur2009},
-we compute the steady-state shape of a semi-permeable vesicle in a
-quiescent flow. The steady-state shape is a stationary point of the
+we compute the steady state shape of a semi-permeable vesicle in a
+quiescent flow. The steady state shape is a stationary point of the
 Lagrangian
@@
 \end{align}
-where the Lagrange multiplier $\Lambda$ is the tension. Note that there
-is no pressure Lagrange multiplier since the vesicle's area fluctuates.
+where the Lagrange multiplier $\Lambda$ is the tension. Note the absence
+of the pressure Lagrange multiplier since the vesicle's area fluctuates.
 Taking the variation of $\mathcal{L}$ with respect to $\gamma$ and
@@
     \frac{\Lambda}{2}\kappa_0^2.
-  \label{eqn:curvODE}
-\end{align}
-Assuming $\kappa_s \neq 0$, this differential equation is separable, and
-can be solved analytically in terms of the {\em EllipticF} function
-using Mathematica. Unlike in the impermeable
-case~\cite{vee-raj-bir-pur2009}, the solution of~\eqref{eqn:curvODE} can
-not be made periodic unless $\kappa(s) = \kappa_0$. Therefore, the
-steady state shape of a semi-permeable vesicle in a quiescent flow is a
-circle. By the inextensibility condition, the steady state vesicle has a
-radius of $L/2\pi$, so its curvature and tension are
+  \label{eqn:curveODE}
+\end{align}
+Assuming $\kappa_s \neq 0$,~\eqref{eqn:curveODE} is separable, and can
+be solved analytically in terms of the {\em EllipticF} function using
+Mathematica. Unlike in the impermeable case~\cite{vee-raj-bir-pur2009},
+the solution of~\eqref{eqn:curveODE} is not periodic unless $\kappa(s) =
+\kappa_0$. Therefore, the steady state shape of a semi-permeable vesicle
+in a quiescent flow is a circle with radius $L/2\pi$. Therefore, the
+steady state curvature and tension are
 \begin{align}
@@
 \end{align}
-Note that in contrast to a impermeable vesicle, the final tension is
-positive rather than negative.
-
-In addition to computing the steady shape, we also compute the transient
-area of the vesicle. Since the area of the vesicle is
+Note that in contrast to a impermeable vesicle, the tension is positive
+rather than negative.
+
+We also compute the transient area of the vesicle. Since the area of the
+vesicle is
 \begin{align}
@@
 \nn$ and a term due to interface stretching~\cite{lai-tse-hua2008}, but
-the stretching term is zero because of the local inextensibility
+this latter term term is zero because of the local inextensibility
 condition. Therefore,
@@
 \end{align}
-Applying integration by parts to the second integral, it is equivalent
-to the first.
+Applying integration by parts, the two integrals agree, and we have
 %\begin{align}
@@
 %\end{align}
-Therefore,
 \begin{align}
@@
 \end{align}
-where the last equality follows from the incompressibility of the
-single-layer potential.  Using integration by parts and the
-Frenet-Serret identities, we have
+where we have used the incompressibility of the single-layer potential.
+Repeatedly applying integration by parts, we have
 \begin{align}
@@
 \end{align}
-This is consistent with the steady state curvature and tension
-in~\eqref{eqn:SSshape} since these constant values result in the
-integrand in~\eqref{eqn:areaROC} being zero.
+Note that~\eqref{eqn:SSshape} and are consistent since the constant
+curvature and tension values cause the integrand to vanish.
 
@@
 \subsection*{Discretization in Space}
-Using an integral equation formulation, the unknowns are the vesicle's
-position and tension that we track at a set of $N$ discretization
-points. All derivatives are computed with Fourier differentiation, and
-the single-layer potential operator is discretized with eighth-order
-quadrature~\cite{alp1999}. For constricted flows, nearly-singular
-integrals are accurately computed with an interpolation-based quadrature
-rule~\cite{qua-bir2014}.
+By using a boundary integral equation formulation, the unknowns are the
+vesicle's position and tension that we track at $N$ discretization
+points. Derivatives are computed with Fourier differentiation, and the
+eighth-order quadrature~\cite{alp1999} is applied to the single-layer
+potential. For constricted flows, nearly-singular integrals are computed
+with an interpolation-based quadrature rule~\cite{qua-bir2014}.
 
@@
 method that discretizes high-order derivatives
-semi-implicitly~\cite{vee-gue-zor-bir2009}. Introducing notation for the
-differential and projection operators
+semi-implicitly~\cite{vee-gue-zor-bir2009}. We introduce the notation
 \begin{alignat}{3}
@@
 \end{alignat}
-the dynamics of the vesicle are governed by
-\begin{align}
-  \dot{\xx} = \uu_{\infty}(\xx) + 
-  \beta P(B\xx + T\sigma) + \SS(B\xx + T\sigma), \quad
-  D \dot{\xx} = 0.
-\end{align}
-Letting $B^N$ be the bending operator due to the vesicle configuration
-at time $t^N$, and similar notation for the other operators, we use the
-first-order semi-implicit time stepping method
+for the differential and projection operators. Letting $B^N$ be the
+bending operator due to the vesicle configuration at time $t^N$, and
+similar notation for the other operators, we use the first-order
+semi-implicit time stepping method
 \begin{alignat}{3}  
@@
   &&+ \beta P^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right) \nonumber \\
-  & &&+ \SS^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right), \\
+  & &&+ \SS^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right), 
+\end{alignat}
+and  the inextensibility condition is discretized as
+\begin{align}
   D^N\xx^{N+1} &= 1.
-\end{alignat}
-
-To achieve high-order accuracy over long time horizons, we modify an
+\end{align}
+To achieve second-order accuracy over long time horizons, we modify an
 adaptive spectral deferred correction time stepping
 method~\cite{qua-bir2016}. Since the area of the vesicle is not
-conserved, we only use the length of the vesicle to estimate the local
-truncation error that determines if a time step is accepted or not and
-the subsequent time step size.
+conserved, we only use the length of the vesicle to estimate the error
+which determines if a time step is accepted or not and determines the
+subsequent time step size.
 
@@
 through a constriction. For each example, all vesicles have a length
-$L$, but the area is not conserved because of semi-permeability, but it
-is bounded by $L^2/4\pi$ which is the area of a circle with
-circumference $L$. For each simulation, we apply an SDC second-order
-adaptive time stepping method~\cite{qua-bir2016}.
+$L$, but the area is not conserved because of semi-permeability. We vary
+the initial vesicle reduced area, the permeability rate, and the flow
+rate. For all simulations, the bending modulus is $10^{-19}J$.
 
@@
 area $\nu = 0.65$ and several different permeability rates in a
-quiescent flow. The steady-state of an impermeable vesicle has constant
-negative tension~\cite{kra-win-sei-lip1996}, but based
-on~\eqref{eqn:SSshape}, a semi-permeable vesicle relaxes to a circle
-with positive constant tension $\Lambda = 2\pi^2/L^2$. Since the
-governing equation for the area in~\eqref{eqn:areaROC} is proportional
-to $\beta$, we expect both the time for the vesicle to deviate from its
-initial area, and the time to reach its steady state to be proportional
-to $\beta^{-1}$. In Table~\ref{tbl:ellipseRelaxTimes}, we report the
-time, $t_\mathrm{steady}$, required for the vesicle's area to be within
-1.3\% of its maximum area, and the time, $t_\mathrm{inflate}$, required
-for the vesicle's area to exceed 1.3\% of its initial area. Both times
-are proportional to $\beta^{-1}$. Next we plot the area of a vesicle
-with six different permeability rates in Figure~\ref{fig:ellipseArea}.
-The area is computed directly from the vesicle shape (solid lines) and
-by integrating~\eqref{eqn:areaROC} (marks) with a first-order method. We
-include black dashed lines indicating the times, $t_{\mathrm{steady}}$,
-that the vesicle is near its steady state circular shape.
+quiescent flow. Based on our analysis, the steady state shape is a
+circle with constant tension $\Lambda = 2\pi^2/L^2$.
+By~\eqref{eqn:areaROC}, the area change is proportional to $\beta$, and
+we expect both the time for the vesicle to deviate from its initial
+area, and the time to reach its steady state to be proportional to
+$\beta^{-1}$. In Table~\ref{tbl:ellipseRelaxTimes}, we report the time,
+$t_\mathrm{steady}$, required for the vesicle's area to be within 1.3\%
+of its maximum area, and the time, $t_\mathrm{inflate}$, required for
+the vesicle's area to exceed 1.3\% of its initial area. Both times are
+proportional to $\beta^{-1}$. We plot the area of a vesicle with six
+different permeability rates in Figure~\ref{fig:ellipseArea}. The area
+is computed directly from the vesicle shape and the time axis is scaled
+by $\beta$. The plot verifies that the time for the vesicle to reach a
+circular shape is proportional to $\beta^{-1}$. We also
+solve~\eqref{eqn:areaROC} for the $\beta=10$ simulation and superimpose
+its solution with dots on Figure~\ref{fig:ellipseArea}.
 \begin{table}[htp]
@@
 %  \ifTikz
-%  \input{figures/ellipseArea.tikz}
+  \input{figures/ellipseArea.tikz}
 %  \fi
-  \includegraphics[width=0.8\linewidth]{figures/ellipseArea}
+%  \includegraphics[width=0.8\linewidth]{figures/ellipseArea}
   \caption{\label{fig:ellipseArea} The area of an elliptical
   semi-permeable vesicle, with permeability rate $\beta$ in a quiescent
-  flow. The solid lines compute the area using~\eqref{eqn:area}, while
-  the marks are computed by integrating~\eqref{eqn:areaROC}. The dashed
-  black lines are the times when the vesicle's area is within 1.3\% of
-  its maximum value of $4\pi$.}
+  flow. The time axis is scaled by the permeability rate $\beta$. Since
+  the curves collapse to a single curve, the permeability rate $\beta$
+  sets a relaxation time scale.}
 \end{figure}
 
-We further analyze the transient dynamics for small $\beta$ by
-considering the vesicle velocity~\eqref{eqn:vesVelocity} due to
-semi-permeability, $\beta(\ff \cdot \nn)\nn$, and force balance,
-$\SS[\ff]$. Initially, since $\beta$ is small, the semi-permeability
-velocity is much smaller than the force balance velocity and the
-velocity resembles an impermeable vesicle. As the
-vesicle approaches the steady state shape of an impermeable vesicle, the
-force balance velocity decreases below the semi-permeability velocity,
-and then the semi-permeable velocity begins to dominate, causing the
-vesicle to inflate. As the vesicle becomes circular, the
-membrane force and the corresponding velocity both converge to
-zero. In Figure~\ref{fig:vesVelocity} we plot the force balance velocity
-(blue) and the semi-permeability velocity (red) at three times with
-$\beta=10^{-3}$. We also plot the velocity of an identically initialized
-impermeable vesicle (green). At $t=0.5$, the semi-permeability velocity is
-small relative to the force balance velocity, and the semi-permeable
-velocity matches with the impermeable vesicle velocity. At time $t=5$,
-the magnitudes of the velocity of the impermeable vesicle and the force
-balance velocity are comparable to the magnitude of the
-semi-permeable velocity, and the semi-permeable vesicle begins to
-inflate. Then, at time $t=50$, the impermeable vesicle is at its steady
-state, while the semi-permeable vesicle is still tending to a circular
-vesicle. The bottom right plot of Figure~\ref{fig:vesVeocity} is the
-maximum norm of the different velocity contributions as a function of
-time, and the black vertical lines correspond to the times reported in
-other three subplots.
+We further analyze the transient dynamics by consider the vesicle
+velocity~\eqref{eqn:vesVelocity} for small $\beta$. The vesicle velocity
+depends on two terms: (i) the permeability velocity, $\beta(\ff \cdot
+\nn)\nn$, and (ii) the force balance velocity, $\SS[\ff]$. At early
+times, since $\beta \ll 1$, the permeability velocity is much smaller
+than the force balance velocity and the vesicle dynamics resembles that
+of a relaxing impermeable vesicle. As the force balance velocity
+decreases, the permeability velocity becomes significant, and the
+vesicle begins to inflate to a circle. This results in the membrane
+force converging to zero \todo[inline]{Is this right?}, as does the
+velocity due to permeability and force balance. Letting $\beta =
+10^{-3}$, the force balance velocity (blue) and the permeability
+velocity (red) are plotted at three times in
+Figure~\ref{fig:vesVelocity}. We also plot the velocity of an
+identically initialized impermeable vesicle (green). At $t=0.5$, the
+permeability velocity is small relative to the force balance velocity,
+and the force balance velocity matches with the impermeable vesicle
+velocity. At time $t=5$, all three velocities are comparable in size,
+and the semi-permeable vesicle begins to inflate. Then, at time $t=50$,
+the impermeable vesicle is at its steady state, while the semi-permeable
+vesicle is still inflating. The bottom right plot of
+Figure~\ref{fig:vesVelocity} is the maximum norm of the different
+velocity contributions as a function of time, and the black vertical
+lines correspond to the times reported in the other three subplots.
 
@@
   \caption{\label{fig:vesVelocity} The velocity contributions due to
-  force balance (blue) and semi-pemeability (red). The green dashed line
-  is the velocity of an impermeable vesicle with the same initial shape
-  as the semi-permeable vesicle. The bottom right plot is the max norm
-  of each of term that contributes to the vesicle velocity.  The three
-  black lines correspond to the times reported in the other three
-  plots.}
+  force balance (blue) and permeability (red). The green dashed line is
+  the velocity of an impermeable vesicle with the same initial shape as
+  the semi-permeable vesicle. The bottom right plot is the max norm of
+  each contributor to the vesicle velocities. The three black lines
+  correspond to the times reported in the other three plots.}
 \end{figure}
 
+\todo[inline]{left off here}
 We next investigate the interplay between the tension, flux, and
@@
 U(1-(y/W)^2,0)$, where $U$ is the maximum imposed velocity. The length
-of the vesicle is $L = 4\pi$ and its initial reduced area is $\nu =
-0.65$. The width $W$ is chosen so that $W/R = 10$, where $R$ is the
-radius of the vesicle. We investigate the effect of the maximum velocity
-$U$ and the permeability rate $\beta$ on the steady state shape of a
-vesicle initially placed on the center line $y=0$.
-Figure~\ref{fig:parabolicPhaseDiagram} shows the steady state
-configuration for a variety of maximum velocities and permeability
-rates. Similar to the shear example, the maximum velocity strongly
-affects the final shape while the permeability rate's effect is much
-weaker. Instead, the permeability rate determines the time required for
-the vesicle to reach a steady state. In
-Table~\ref{tbl:parabolicRelaxTimes1}, we consider two maximum velocities
-and report the time, $t_\mathrm{steady}$, required for the vesicle's
-area to be within 1.3\% of its maximum area, and the time,
-$t_\mathrm{inflate}$, required for the vesicle's area to exceed 1.3\% of
-its initial area. We see that both times scale with $\beta^{-1}$.
-
-\begin{figure}[htp]
-%  \ifTikz
-%  \input{figures/parabolicPhaseDiagram.tikz}
-%  \fi
-  \includegraphics[width=0.9\linewidth]{figures/parabolicPhaseDiagram.pdf}
-  \caption{\label{fig:parabolicPhaseDiagram} The steady state shape of a
-  semi-permeable vesicle with several different permeability rates
-  $\beta$ and flow rates $U$. The numbers reported above each vesicle is
-  its reduced area. At high flow rates, the vesicle self-intersects
-  before reaching a steady state configuration.}
-\end{figure}
-
-\begin{table}[htp]
-  \centering
-  \caption{\label{tbl:parabolicRelaxTimes1} The time for a
-  semi-permeable vesicle in a Poiseuille flow to reach its steady state
-  ($t_\mathrm{steady}$) and to begin inflating ($t_\mathrm{inflate}$).
-  The times are reported for the maximum velocities $0.1 \mu m/s$ and
-  $10 \mu m/s$.}
-  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
-    \multicolumn{5}{c}{$U = 0.1 \mu m/s$} \\
-    $\beta$ & $t_\mathrm{steady}$ & ratio & $t_\mathrm{inflate}$ & ratio \\
-    \midrule
-    $10^{0}$  & $3.33 \times 10^{0}$ & ---  
-              & $1.67 \times 10^{-2}$ & --- \\ 
-    $10^{-1}$ & $1.37 \times 10^{1}$ & 4.12 & 
-                $8.73 \times 10^{-1}$ & 5.23 \\
-    $10^{-2}$ & $8.60 \times 10^{1}$ & 6.26 & 
-                $1.11 \times 10^{0}$ & 12.74 \\
-    $10^{-3}$ & $7.75 \times 10^{2}$ & 9.01 & 
-                $1.63 \times 10^{1}$ & 14.70 \\
-    $10^{-4}$ & $7.69 \times 10^{3}$ & 9.93 & 
-                $1.74 \times 10^{2}$ & 10.63 \\
-    $10^{-5}$ & $8.01 \times 10^{4}$ & 10.41 & 
-                $1.66 \times 10^{3}$ & 9.58 \\
-    \bottomrule
-  \end{tabular}
-
-  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
-    \multicolumn{5}{c}{$U = 10 \mu m/s$} \\
-    $\beta$ & $t_\mathrm{steady}$ & ratio & $t_\mathrm{inflate}$ & ratio \\
-    \midrule
-    $10^{0}$  & $3.55 \times 10^{0}$ & ---  
-              & $1.67 \times 10^{-2}$ & --- \\ 
-    $10^{-1}$ & $1.87 \times 10^{1}$ & 5.27 & 
-                $9.01 \times 10^{-2}$ & 5.40 \\
-    $10^{-2}$ & $1.17 \times 10^{2}$ & 6.26 & 
-                $1.52 \times 10^{0}$ & 16.87 \\
-    $10^{-3}$ & $1.06 \times 10^{3}$ & 9.06 & 
-                $2.07 \times 10^{1}$ & 13.62 \\
-    $10^{-4}$ & $1.02 \times 10^{4}$ & 9.62 & 
-                $2.25 \times 10^{2}$ & 10.87 \\
-    $10^{-5}$ & $1.04 \times 10^{5}$ & 10.20 & 
-                $2.25 \times 10^{3}$ & 10.00 \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-We next examine the effect of the non-linear Poiseuille flow on the
-migration of semi-permeable vesicle. In this experiment, the vesicle is
-initialized above the center line $y=0$. At sufficiently large reduced
-areas and maximum velocities, the steady state vesicle configuration is
-axisymmetric along the center line (parachute or bullet). In contrast,
-for small reduced areas and maximum velocities, the steady-state shape
-is axisymmetric, above the center line, and undergoes a tank treading
-motion (slipper). These dynamics are investigated by Danker et
-al.~\cite{dan-vla-mis2009} and Kaoui et al.~\cite{kao-bir-mis2009}. To
-validate our methods, in
+of the vesicle is $L = 2\pi$. We examine the effect of the non-linear
+Poiseuille flow on the migration of semi-permeable vesicle. In this
+experiment, the vesicle is initialized above the center line $y=0$, and
+it migrates towards the center line~\cite{dan-vla-mis2009}. For an
+impermeable vesicle, depending on the vesicles reduced area and the flow
+rate,  the long time vesicle shape is either an axisymmetric parachute
+or bullet, or a asymmetric tank-treading slipper~\cite{kao-bir-mis2009}.
+To validate our methods, in
 Figure~\ref{fig:parabolicOffCenterImpermeablePhaseDiagram} we
@@
 
+Having validated our method, we investigate the dynamics of a
+semi-permeable vesicle in a Poiseuille flow. Using several initial
+reduced areas and flow rates, we recreate the impermeable vesicle phase
+diagram for vesicles with a permeability rate of $\beta = 10^{-3}$. The
+final vesicle configurations are in
+Figure~\ref{fig:parabolicOffCenterSemipermeablePhaseDiagram}.  As we
+observed for the shear flow, the steady state reduced area is
+independent of the initial reduced area, and larger flow rates result in
+smaller steady state reduced areas. We report the steady state reduced
+area in Figure~\ref{fig:parabolicOffCenterSemipermeablePhaseDiagram}.
+At the smallest flow rate of $U = 200 \mu m/s$, the steady state reduced
+area is large, and the result is an axisymmetric bullet. However, at the
+larger flow rates, the steady state reduced area is smaller, and the
+result is an asymmetric tank-treading slipper.
+
 \begin{figure}[htp]
@@
   several different flow rates $U$ and reduced areas $\nu$. The
-  steady-state reduced area for each flow rate, which is reported along
+  steady state reduced area for each flow rate, which is reported along
   the top of the vesicles, is nearly independent of the initial reduced
@@
 %\input{figures/parabolicPhaseDiagram.tikz}
+%\begin{figure}[htp]
+%%  \ifTikz
+%%  \input{figures/parabolicPhaseDiagram.tikz}
+%%  \fi
+%  \includegraphics[width=0.9\linewidth]{figures/parabolicPhaseDiagram.pdf}
+%  \caption{\label{fig:parabolicPhaseDiagram} The steady state shape of a
+%  semi-permeable vesicle with several different permeability rates
+%  $\beta$ and flow rates $U$. The numbers reported above each vesicle is
+%  its reduced area. At high flow rates, the vesicle self-intersects
+%  before reaching a steady state configuration.}
+%\end{figure}
+%
+%
+%\begin{table}[htp]
+%  \centering
+%  \caption{\label{tbl:parabolicRelaxTimes1} The time for a
+%  semi-permeable vesicle in a Poiseuille flow to reach its steady state
+%  ($t_\mathrm{steady}$) and to begin inflating ($t_\mathrm{inflate}$).
+%  The times are reported for the maximum velocities $0.1 \mu m/s$ and
+%  $10 \mu m/s$.}
+%  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
+%    \multicolumn{5}{c}{$U = 0.1 \mu m/s$} \\
+%    $\beta$ & $t_\mathrm{steady}$ & ratio & $t_\mathrm{inflate}$ & ratio \\
+%    \midrule
+%    $10^{0}$  & $3.33 \times 10^{0}$ & ---  
+%              & $1.67 \times 10^{-2}$ & --- \\ 
+%    $10^{-1}$ & $1.37 \times 10^{1}$ & 4.12 & 
+%                $8.73 \times 10^{-1}$ & 5.23 \\
+%    $10^{-2}$ & $8.60 \times 10^{1}$ & 6.26 & 
+%                $1.11 \times 10^{0}$ & 12.74 \\
+%    $10^{-3}$ & $7.75 \times 10^{2}$ & 9.01 & 
+%                $1.63 \times 10^{1}$ & 14.70 \\
+%    $10^{-4}$ & $7.69 \times 10^{3}$ & 9.93 & 
+%                $1.74 \times 10^{2}$ & 10.63 \\
+%    $10^{-5}$ & $8.01 \times 10^{4}$ & 10.41 & 
+%                $1.66 \times 10^{3}$ & 9.58 \\
+%    \bottomrule
+%  \end{tabular}
+%
+%  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
+%    \multicolumn{5}{c}{$U = 10 \mu m/s$} \\
+%    $\beta$ & $t_\mathrm{steady}$ & ratio & $t_\mathrm{inflate}$ & ratio \\
+%    \midrule
+%    $10^{0}$  & $3.55 \times 10^{0}$ & ---  
+%              & $1.67 \times 10^{-2}$ & --- \\ 
+%    $10^{-1}$ & $1.87 \times 10^{1}$ & 5.27 & 
+%                $9.01 \times 10^{-2}$ & 5.40 \\
+%    $10^{-2}$ & $1.17 \times 10^{2}$ & 6.26 & 
+%                $1.52 \times 10^{0}$ & 16.87 \\
+%    $10^{-3}$ & $1.06 \times 10^{3}$ & 9.06 & 
+%                $2.07 \times 10^{1}$ & 13.62 \\
+%    $10^{-4}$ & $1.02 \times 10^{4}$ & 9.62 & 
+%                $2.25 \times 10^{2}$ & 10.87 \\
+%    $10^{-5}$ & $1.04 \times 10^{5}$ & 10.20 & 
+%                $2.25 \times 10^{3}$ & 10.00 \\
+%    \bottomrule
+%  \end{tabular}
+%\end{table}
+%The width $W$ is chosen so that $W/R =
+%10$, where $R$ is the radius of the vesicle. We investigate the effect
+%of the maximum velocity $U$ and the permeability rate $\beta$ on the
+%steady state shape of a vesicle initially placed on the center line
+%$y=0$. Figure~\ref{fig:parabolicPhaseDiagram} shows the steady state
+%configuration for a variety of maximum velocities and permeability
+%rates. Similar to the shear example, the maximum velocity strongly
+%affects the final shape while the permeability rate's effect is much
+%weaker. Instead, the permeability rate determines the time required for
+%the vesicle to reach a steady state. In
+%Table~\ref{tbl:parabolicRelaxTimes1}, we consider two maximum velocities
+%and report the time, $t_\mathrm{steady}$, required for the vesicle's
+%area to be within 1.3\% of its maximum area, and the time,
+%$t_\mathrm{inflate}$, required for the vesicle's area to exceed 1.3\% of
+%its initial area. We see that both times scale with $\beta^{-1}$.
 

### 2020-09-01 vesicle_code/docs/permeableVes/main.tex
worked on paper a bit

@@
 
-We further analyze the transient dynamics by consider the vesicle
-velocity~\eqref{eqn:vesVelocity} for small $\beta$. The vesicle velocity
-depends on two terms: (i) the permeability velocity, $\beta(\ff \cdot
+We further analyze the transient dynamics by considering the vesicle
+velocity~\eqref{eqn:vesVelocity} for small $\beta$. Two terms contribute
+to the vesicle velocity: (i) the permeability velocity, $\beta(\ff \cdot
 \nn)\nn$, and (ii) the force balance velocity, $\SS[\ff]$. At early
@@
 vesicle begins to inflate to a circle. This results in the membrane
-force converging to zero \todo[inline]{Is this right?}, as does the
-velocity due to permeability and force balance. Letting $\beta =
-10^{-3}$, the force balance velocity (blue) and the permeability
-velocity (red) are plotted at three times in
-Figure~\ref{fig:vesVelocity}. We also plot the velocity of an
-identically initialized impermeable vesicle (green). At $t=0.5$, the
-permeability velocity is small relative to the force balance velocity,
-and the force balance velocity matches with the impermeable vesicle
-velocity. At time $t=5$, all three velocities are comparable in size,
-and the semi-permeable vesicle begins to inflate. Then, at time $t=50$,
-the impermeable vesicle is at its steady state, while the semi-permeable
-vesicle is still inflating. The bottom right plot of
-Figure~\ref{fig:vesVelocity} is the maximum norm of the different
-velocity contributions as a function of time, and the black vertical
-lines correspond to the times reported in the other three subplots.
+force and velocity both converging to zero. Letting $\beta = 10^{-3}$,
+the force balance velocity (blue) and the permeability velocity (red)
+are plotted at three times in Figure~\ref{fig:vesVelocity}. We also plot
+the velocity of an identically initialized impermeable vesicle (green).
+At the early time $t=0.5$, the permeability velocity is small relative
+to the force balance velocity, and the force balance velocity matches
+with the impermeable vesicle velocity. At time intermediate time $t=5$,
+all three velocities are comparable in size, and the semi-permeable
+vesicle begins to inflate. Finally, at time $t=50$, the impermeable
+vesicle is at its steady state, while the semi-permeable vesicle is
+still inflating. The bottom right plot of Figure~\ref{fig:vesVelocity}
+is the maximum norm of the different velocity contributions as a
+function of time, and the black vertical lines correspond to the times
+reported in the other three subplots.
 
@@
 
-\todo[inline]{left off here}
-We next investigate the interplay between the tension, flux, and
-curvature of a semi-permeable vesicle. We let $\beta = 1$ and initialize
-the vesicle with regions of both positive and negative curvature. The
-vesicle tension, $\Lambda$, and the flux, $\ff \cdot \nn$, are plotted
-in Figure~\ref{fig:starTensionFlux}. The vesicle undergoes three general
-behaviors: (i) For $t \in (0,1.6 \times 10^{-2})$, the vesicle has a net
-negative flux resulting in a loss of area; (ii) For $t \in (1.6 \times
-10^{-2},1.0)$, the vesicle has a net positive flux and the tension along
-most of the membrane is negative; (iii) For $t \in (1.0,2.0)$, the
-vesicle is near its steady state and transitions to a positive constant
-tension. In the first time interval, the vesicle deflates. Near the
-points of largest negative curvature, there is a large negative tension
-and large inflow (positive flux).  Correspondingly, near the points with
-largest positive curvature, there is a small tension and outflow
-(negative flux). In the second time interval, the tension is negative
-and the flux is positive nearly everywhere. The regions with largest
-negative curvature correspond to regions with largest negative tension
-and the most inflow. Finally, in the last time interval, the tension
-transitions to a positive constant function, the membrane force and flux
-transition to zero, resulting in a steady state circular vesicle with
-positive constant tension.
-
-\begin{figure}[htp]
+We next investigate the interplay between the tension, transmembrane
+flux, and curvature of a semi-permeable vesicle. We let $\beta = 1$ and
+initialize the vesicle with regions of both positive and negative
+curvature. The vesicle tension, $\Lambda$, and the flux, $\ff \cdot
+\nn$, are plotted in Figure~\ref{fig:starTensionFlux}. At early times,
+regions of large negative curvature have negative tension and regions
+with large positive curvature have positive tension. In addition,
+regions with large curvature have a large inflow of fluid (positive
+flux), while the flatter regions have an outflow of fluid. At these
+early times, the net effect is vesicle deflation. As the vesicle starts
+to smooth out, the same general tension and flux profiles persist, but
+the net flux is positive and the vesicle inflates. At later times, the
+tension starts to become positive and the vesicle continues to inflate
+towards a circle. Finally, the tension transitions to a positive
+constant function, the membrane force and flux approach zero, and the
+vesicle shape becomes positive.
+
+%\begin{figure*}[htp]
+%  \centering
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
+%
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
+%
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
+%
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
+%
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime5.pdf}
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
+%
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime6.pdf}
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime6.pdf}
+%  \caption{\label{fig:starTensionFlux} The vesicle tension (left) and
+%  flux (right) of the semi-permeable vesicle in a quiescent flow with
+%  $\beta=1$.}
+%\end{figure*}
+
+\begin{figure*}[htp]
   \centering
-  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
-  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
-
-  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
-  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
-
-  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
-  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
-
-  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
-  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
-
-  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime5.pdf}
-  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
-  \caption{\label{fig:starTensionFlux} The vesicle tension (left) and
-  flux (right) of the semi-permeable vesicle in a quiescent flow with
-  $\beta=1$.}
-\end{figure}
-
-%\begin{figure}[htp]
-%  \centering
-%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
-%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
-%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
-%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
-%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime5.pdf}
-%
-%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
-%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
-%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
-%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
-%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
-%  \caption{\label{fig:starTensionFlux} The vesicle tension (top) and
-%  flux (bottom) of the semi-permeable vesicle in a quiescent
-%  flow with $\beta=1$.}
-%\end{figure}
+  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
+  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
+  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
+  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
+  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime5.pdf}
+  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime6.pdf}
+
+  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
+  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
+  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
+  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
+  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
+  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime6.pdf}
+  \caption{\label{fig:starTensionFlux} The vesicle tension (top) and
+  flux (bottom) of the semi-permeable vesicle in a quiescent
+  flow with $\beta=1$.}
+\end{figure*}
 

### 2020-09-01 vesicle_code/examples/shear1Ves.m

@@ -12,7 +12,7 @@ prams.m = 500;              % number of time steps
 prams.kappa = ones(prams.nv,1);   % bending coefficient
 prams.viscCont = ones(prams.nv,1);         % viscosity contrast
 options.farField = 'shear'; % background velocity
-options.farFieldSpeed = 1e-1;
+options.farFieldSpeed = 1e0;
 %options.farFieldSpeed = farFieldSpeed;
 options.vesves = 'implicit';
 % Discretization of vesicle-vesicle interactions.
@@ -28,7 +28,7 @@ prams.errorTol = 1000;
 prams.fluxCoeff = 1e-3;
 %prams.fluxCoeff = fluxCoeff;
 options.fluxShape = 1;
-prams.saveRate = 1000
+prams.saveRate = 1
 
 options.adhesion = false;
 prams.adRange = 0.4;
@@ -38,7 +38,7 @@ prams.adStrength = 100;
 options.timeAdap = true;
 
 prams.rtolArea = 1e10;
-prams.rtolLength = 1e-1;
+prams.rtolLength = 1e-2;
 prams.dtMax = 1e1;
 prams.dtMin = 1e-4;
 prams.betaUp = 1.2;

### 2020-09-03 vesicle_code/docs/permeableVes/main.tex
worked on pnas paper

@@
 to the vesicle velocity: (i) the permeability velocity, $\beta(\ff \cdot
-\nn)\nn$, and (ii) the force balance velocity, $\SS[\ff]$. At early
-times, since $\beta \ll 1$, the permeability velocity is much smaller
-than the force balance velocity and the vesicle dynamics resembles that
-of a relaxing impermeable vesicle. As the force balance velocity
+\nn)\nn$, and (ii) the force balance velocity, $\SS[\ff]$. Since $\beta
+\ll 1$, the permeability velocity is much smaller than the force balance
+velocity at early times, and the semi-permeable vesicle dynamics
+resembles those of an impermeable vesicle. As the force balance velocity
 decreases, the permeability velocity becomes significant, and the
@@
 force and velocity both converging to zero. Letting $\beta = 10^{-3}$,
-the force balance velocity (blue) and the permeability velocity (red)
-are plotted at three times in Figure~\ref{fig:vesVelocity}. We also plot
-the velocity of an identically initialized impermeable vesicle (green).
-At the early time $t=0.5$, the permeability velocity is small relative
-to the force balance velocity, and the force balance velocity matches
-with the impermeable vesicle velocity. At time intermediate time $t=5$,
-all three velocities are comparable in size, and the semi-permeable
-vesicle begins to inflate. Finally, at time $t=50$, the impermeable
-vesicle is at its steady state, while the semi-permeable vesicle is
-still inflating. The bottom right plot of Figure~\ref{fig:vesVelocity}
-is the maximum norm of the different velocity contributions as a
-function of time, and the black vertical lines correspond to the times
-reported in the other three subplots.
-
-%  \input{figures/ellipseVelocity1.tikz}
-%  \input{figures/ellipseVelocity2.tikz}
-%  \input{figures/ellipseVelocity3.tikz}
-%  \input{figures/ellipseVelocityNorms.tikz}
-\begin{figure}[htp]
+the normal component of the force balance velocity (blue) and the
+permeability velocity (red) are plotted at three times in
+Figure~\ref{fig:vesVelocity}. We also plot the velocity (green) of an
+identically initialized impermeable vesicle. At the early time $t=0.5$,
+the permeability velocity is negligible relative to the force balance
+velocity, and the force balance velocity matches with the impermeable
+vesicle velocity. At intermediate time $t=5$, all three velocities are
+comparable in size, and the semi-permeable vesicle begins to inflate.
+Finally, at time $t=50$, the impermeable vesicle is near steady state,
+while the semi-permeable vesicle is still inflating. The right-most
+plot of Figure~\ref{fig:vesVelocity} is the maximum norm of the
+different velocity contributions as a function of time, and the black
+vertical lines correspond to the times reported in the other three
+subplots.
+
+\begin{figure*}[htp]
   \centering
@@
 %  \input{figures/ellipseVelocityNorms.tikz}
-  \includegraphics[width=0.48\linewidth]{figures/ellipseVelocity1.pdf}
-  \includegraphics[width=0.48\linewidth]{figures/ellipseVelocity2.pdf}
-  \includegraphics[width=0.48\linewidth]{figures/ellipseVelocity3.pdf}
-  \includegraphics[width=0.48\linewidth]{figures/ellipseVelocityNorms.pdf}
+  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity1.pdf}
+  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity2.pdf}
+  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity3.pdf}
+  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocityNorms.pdf}
   \caption{\label{fig:vesVelocity} The velocity contributions due to
-  force balance (blue) and permeability (red). The green dashed line is
-  the velocity of an impermeable vesicle with the same initial shape as
-  the semi-permeable vesicle. The bottom right plot is the max norm of
-  each contributor to the vesicle velocities. The three black lines
-  correspond to the times reported in the other three plots.}
-\end{figure}
+  force balance (blue) and permeability (red). The green line is the
+  velocity of an impermeable vesicle with the same initial shape as the
+  semi-permeable vesicle. The right-most plot is the maximum norm of
+  each velocity contribution. The black lines correspond to the times
+  reported in the other three plots.}
+\end{figure*}
 
@@
 regions of large negative curvature have negative tension and regions
-with large positive curvature have positive tension. In addition,
-regions with large curvature have a large inflow of fluid (positive
-flux), while the flatter regions have an outflow of fluid. At these
-early times, the net effect is vesicle deflation. As the vesicle starts
-to smooth out, the same general tension and flux profiles persist, but
-the net flux is positive and the vesicle inflates. At later times, the
-tension starts to become positive and the vesicle continues to inflate
-towards a circle. Finally, the tension transitions to a positive
-constant function, the membrane force and flux approach zero, and the
-vesicle shape becomes positive.
+with large positive curvature have positive tension, and the same result
+holds for an impermeable vesicle. In addition, regions with large
+curvature have a large inflow of fluid (positive flux), while the
+flatter regions have an outflow of fluid. At these early times, the net
+effect is vesicle deflation. As the vesicle shape relaxes, the same
+general tension and flux trends persist, but the net flux is positive
+and the vesicle inflates. At later times, the tension becomes positive
+and the vesicle continues to inflate towards a circle. Finally, the
+tension transitions to a positive constant function, the membrane force
+and flux approach zero, and the vesicle shape reaches its steady
+circular shape.
 

### 2020-09-03 vesicle_code/examples/output/makeImages.m

@@ -51,7 +51,7 @@ if 0
   options.confined = false;
 end
 
-if 1
+if 0
 %  file = 'relaxation1VesData.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/Apr142020/starBeta1em3/relaxation1VesData.bin';
     file = '~/projects/brinkman/vesicle_code/results/Apr232020/ellipseBeta1em3/relaxation1VesData.bin';
@@ -112,8 +112,8 @@ if 0
   irate = 1;
 end
 
-if 0
-  file = 'choke1VesAData.bin';
+if 1
+  file = 'choke1VesBData.bin';
 %file = '~/projects/brinkman/vesicle_code/results/choke1VesLong/beta0Scale1p44_kappa1e0_farfield1e0/choke1VesData.bin'
 %file = '~/projects/brinkman/vesicle_code/results/choke1VesLong/beta0Scale1p44_kappa1e1_farfield1e0/choke1VesData.bin';
 %file = '~/projects/brinkman/vesicle_code/results/choke1VesLong/beta0Scale1p44_kappa1e2_farfield1e0/choke1VesData.bin';
@@ -128,7 +128,7 @@ if 0
   options.pressure = true;
   options.savefig = false;
   count = 1;
-  irate = 1;
+  irate = 5;
 end
 if 0
 %  file = 'slit1VesData.bin';
@@ -243,7 +243,7 @@ max_flux = +2;
 figure(1); clf
 for k = istart:irate:iend
 %  xx = interpft(posx(:,:,k),256); yy = interpft(posy(:,:,k),256);  
-  xx = posx(:,:,k) - 1*cx(k);
+  xx = posx(:,:,k) - 0*cx(k);
   yy = posy(:,:,k);
   tt = ten(:,:,k);
   if k > 1
@@ -263,7 +263,7 @@ for k = istart:irate:iend
 %    end
 %    plot(0,cy(k),'k.','markersize',10);
 %    plot([-5 5],[0 0],'k--')
-    plot(vec1(1,:),vec2(1,:),'b.','markersize',20)
+%    plot(vec1(1,:),vec2(1,:),'b.','markersize',20)
 %    for j = 1:1
 %      subplot(1,2,1)
 %      h = cline(vec1(:,j),vec2(:,j),vec3(:,j));
@@ -287,9 +287,9 @@ for k = istart:irate:iend
     end
     hold off
     axis equal
[…]

### 2020-09-09 vesicle_code/docs/permeableVes/main.tex
added shear figure

@@
 contrast, and tumbling is not possible.
-
-We initialize an elliptical vesicle with reduced area $\nu = 0.65$, and
-with its long axis oriented in the $y$-direction. For all permeability
-rates and shear rates, the semi-permeable vesicle tilts to an
-inclination angle and undergoes tank treading dynamics. Because of the
-semi-permeability, the initial and final reduced areas differ. In
+\begin{figure}[htp]
+  \centering
+  \input{figures/shearSS.tikz}
+  \caption{\label{fig:shearSS} The reduced area of a semi-permeable
+  vesicle in a shear flow. The final reduced area is nearly independent
+  of the initial reduced area.}
+\end{figure}
+
+In the quiescent flow, the steady state vesicle shape is independent of
+the initial vesicle shape. Here we test if a similar results holds with
+an imposed flow. In Figure~\ref{fig:shearSS}, we plot the reduced area
+of four vesicles with different initial reduced areas. The final shape
+depends on the initial vesicle length, but not on its initial reduced
+area. Therefore, for this example we only consider vesicles with the
+initial reduced area $\nu = 0.65$. For all permeability rates and shear
+rates, the semi-permeable vesicle tilts to an inclination angle and
+undergoes tank treading dynamics. Because of the semi-permeability, the
+initial and final reduced areas differ. In
 Figure~\ref{fig:shearPhaseDiagram}, we plot the final shape of the

### 2020-09-21 vesicle_code/docs/permeableVes/main.tex
added some new stenosis runs

@@
   \centering
-%  \ifTikz
+  \ifTikz
   \input{figures/ellipseArea.tikz}
-%  \fi
+  \fi
 %  \includegraphics[width=0.8\linewidth]{figures/ellipseArea}
@@
   \centering
+  \ifTikz
   \input{figures/shearSS.tikz}
+  \fi
   \caption{\label{fig:shearSS} The reduced area of a semi-permeable
@@
 \subsection*{Semi-Permeable Vesicle in Stenosis}
+We consider the effect of stenosis on a semi-permeable vesicle. To allow
+for large amounts of fluid flux through the membrane, we consider
+geometry with a long constricted region. We start by considering a
+vesicle initialized with reduced area $\nu = 0.65$, and we compare the
+vesicle shape when $\beta = 0$ (impermeable) and $\beta = 10^{-3}$
+(permeable). Figure~\ref{fig:stenosisShape} shows the vesicles' shape at
+several locations along the constriction, and the corresponding tensions
+are in Figure~\ref{fig:stenosisTension}.
+\begin{figure}[htp]
+  \scalebox{0.4}{\input{figures/stenosisShape1.tikz}}
+  \scalebox{0.4}{\input{figures/stenosisShape2.tikz}}
+  \scalebox{0.4}{\input{figures/stenosisShape3.tikz}}
+  \scalebox{0.4}{\input{figures/stenosisShape4.tikz}}
+  \scalebox{0.4}{\input{figures/stenosisShape5.tikz}}
+  \scalebox{0.4}{\input{figures/stenosisShape6.tikz}}
+  \scalebox{0.4}{\input{figures/stenosisShape7.tikz}}
+  \scalebox{0.4}{\input{figures/stenosisShape8.tikz}}
+  \scalebox{0.4}{\input{figures/stenosisShape9.tikz}}
+  \scalebox{0.4}{\input{figures/stenosisShape10.tikz}}
+  \scalebox{0.4}{\input{figures/stenosisShape11.tikz}}
+  \scalebox{0.4}{\input{figures/stenosisShape12.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisShape13.tikz}}
+  \caption{\label{fig:stenosisShape} An impermeable (red) and
+  semi-permeable (dashed blue) vesicle in a stenosed geometry (black).
+  The vesicles' initial configuration are identical with reduced area
+  $\nu = 0.65$. The semi-permeable vesicle deflates throughout the
+  constriction (see Figure~\ref{fig:stenosisArea}) and develops higher
+  curvature regions than its impermeable counterpart.}
+\end{figure}
+
+\begin{figure}[htp]
+  \centering
+  \begin{tabular}{ccc}
+    \scalebox{0.31}{\input{figures/stenosisTension1.tikz}} &
+    \scalebox{0.31}{\input{figures/stenosisTension3.tikz}} &
+    \scalebox{0.31}{\input{figures/stenosisTension5.tikz}} \\
+    \scalebox{0.31}{\input{figures/stenosisTension7.tikz}} &
+    \scalebox{0.31}{\input{figures/stenosisTension9.tikz}} &
+    \scalebox{0.31}{\input{figures/stenosisTension11.tikz}} 
+  \end{tabular}
+  \caption{\label{fig:stenosisTension} The tension of the impermeable
+  (red) and semi-permeable (dashed blue) vesicles in
+  Figure~\ref{fig:stenosisShape}. The point $\theta=0$ corresponds to
+  the right-most point of the vesicle.}
+\end{figure}
+
+\begin{figure}[htp]
+  \centering
+  \begin{tabular}{ccc}
+    \scalebox{0.31}{\input{figures/stenosisFlux1.tikz}} &
+    \scalebox{0.31}{\input{figures/stenosisFlux3.tikz}} &
+    \scalebox{0.31}{\input{figures/stenosisFlux5.tikz}} \\
+    \scalebox{0.31}{\input{figures/stenosisFlux7.tikz}} &
+    \scalebox{0.31}{\input{figures/stenosisFlux9.tikz}} &
+    \scalebox{0.31}{\input{figures/stenosisFlux11.tikz}} 
+  \end{tabular}
+  \caption{\label{fig:stenosisFlux} The flux (equivalent to pressure
+  jump) of the impermeable (red) and semi-permeable (dashed blue)
+  vesicles in Figure~\ref{fig:stenosisShape}. The point $\theta=0$
+  corresponds to the right-most point of the vesicle.}
+\end{figure}
+
+\begin{figure}[htp]
+  \centering
+%  \ifTikz
+  \input{figures/stenosisArea.tikz}
+%  \fi
+%  \includegraphics[width=0.8\linewidth]{figures/ellipseArea}
+  \caption{\label{fig:stenosisArea} The area of a stenosed
+  semi-permeable vesicle, with permeability rate $\beta=10^{-3}$. The
+  $x$-axis is the $x$-coordinate of the center of mass of the vesicle.
+  The vesicle loses fluid at a constant rate throughout the constriction
+  that is between $\pm 60$. The semi-permeable vesicle loses 12.8\% of
+  its fluid.}
+\end{figure}
+
 Inspired by an experiment that measures the effects of cells on 
@@
 with diameter $25\mu$m and passes into a channel with length $45\mu$m
-and diameter $5\mu$m (Figure~\ref{fig:stenosisGeom}. We impose a
+and diameter $5\mu$m (Figure~\_ref{fig:stenosisGeom}. We impose a
 Poiseuille flow at an inlet and outlet and a no-slip boundary condition

### 2020-09-21 vesicle_code/examples/choke1Ves.m

@@ -6,11 +6,11 @@ fprintf('Implicit vesicle-vesicle interactions.\n');
 fprintf('Implicit vesicle-boundary interactions.\n');
 
 %format long
-prams.N = 256;                 % points per vesicle
+prams.N = 256/4;                 % points per vesicle
 prams.nv = 1;                  % number of vesicles
 prams.T = 10;                  %time horizon
 prams.m = 12000;                % number of time steps
-prams.Nbd = 2*1024;               % number of points on solid wall
+prams.Nbd = 2*1024/4;               % number of points on solid wall
 prams.nvbd = 1;                % number of components to solid walls
 prams.kappa = 1e0;            % bending coefficient
 prams.viscCont = 1*ones(prams.nv,1);            % viscosity contrast
@@ -53,7 +53,7 @@ options.verbose = true;
 options.profile = false;    % Profile code
 options.collision = false;   % Collision detection
 
-options.nsdc = 1;
+options.nsdc = 0;
 options.orderGL = 2;
 
 options.timeAdap = true;

### 2020-09-21 vesicle_code/src/tstep.m

@@ -1869,7 +1869,6 @@ end
 % walls.  Sets the layer-potential to zero if using explicit
 % interactions
 
-
 % START COMPUTING REQUIRED DOUBLE-LAYER POTENTIALS FOR VISCOSITY
 % CONTRAST
 if any(vesicle.viscCont ~= 1)

### 2020-09-26 vesicle_code/docs/permeableVes/main.tex
updating paper
worked on stenosis results

--- 2020-09-09 vesicle_code/docs/permeableVes/main.tex
@@
 \subsection*{Semi-Permeable Vesicle in Stenosis}
+We consider the effect of stenosis on a semi-permeable vesicle. To allow
+for large amounts of fluid flux through the membrane, we consider
+geometry with a long constricted region. We start by considering a
+vesicle initialized with reduced area $\nu = 0.65$, and we compare the
+vesicle shape when $\beta = 0$ (impermeable) and $\beta = 10^{-3}$
+(permeable). Figure~\ref{fig:stenosisShape} shows the vesicles' shape at
+several locations along the constriction. The colors along the left
+channel represent the tension and those along the right represent the
+flux. In Figure~\ref{fig:stenosisTensionAndFux}, the tension at location
+$x=20$ and the flux at location $x=30$ are plotted with respect to
+arclength. The value of $\theta=0$ corresponds to the nose of the
+vesicle.
+\begin{figure}[htp]
+  \ifTikz
+%  \scalebox{0.5}{\input{figures/stenosisShapeTension01.tikz}}
+%  \scalebox{0.5}{\input{figures/stenosisShapeFlux02.tikz}}
+  \scalebox{0.5}{\input{figures/stenosisShapeTension03.tikz}}
+  \scalebox{0.5}{\input{figures/stenosisShapeFlux04.tikz}}
+  \scalebox{0.5}{\input{figures/stenosisShapeTension05.tikz}}
+  \scalebox{0.5}{\input{figures/stenosisShapeFlux06.tikz}}
+  \scalebox{0.5}{\input{figures/stenosisShapeTension07.tikz}}
+  \scalebox{0.5}{\input{figures/stenosisShapeFlux08.tikz}}
+  \scalebox{0.5}{\input{figures/stenosisShapeTension09.tikz}}
+  \scalebox{0.5}{\input{figures/stenosisShapeFlux10.tikz}}
+%  \scalebox{0.5}{\input{figures/stenosisShapeTension11.tikz}}
+%  \scalebox{0.5}{\input{figures/stenosisShapeFlux12.tikz}}
+  \fi
+  \caption{\label{fig:stenosisShape} An impermeable (dashed) and
+  semi-permeable (solid) vesicle in a stenosed geometry (black).
+  The vesicles' initial configuration are identical with reduced area
+  $\nu = 0.65$. The color denotes the vesicles' tension (left) and flux
+  (right). The semi-permeable vesicle deflates throughout the
+  constriction (see Figure~\ref{fig:stenosisArea}) and develops higher
+  curvature regions than its impermeable counterpart.}
+\end{figure}
+
+\begin{figure}[htp]
+  \centering
+  \ifTikz
+  \scalebox{0.5}{\input{figures/stenosisTension09.tikz}}
+  \scalebox{0.5}{\input{figures/stenosisFlux10.tikz}}
+  \fi
+  \caption{\label{fig:stenosisTensionAndFlux} The tension (left) and
+  flux (right) of the semi-permeable (red) and impermeable (dashed blue)
+  vesicles in Figure~\ref{fig:stenosisShape} at locations $x=20$ and
+  $x=30$. The point $\theta=0$ corresponds to the right-most point of
+  the vesicle.}
+\end{figure}
+
+\begin{figure}[htp]
+  \centering
+  \ifTikz
+  \input{figures/stenosisArea.tikz}
+  \fi
+%  \includegraphics[width=0.8\linewidth]{figures/ellipseArea}
+  \caption{\label{fig:stenosisArea} The area of a stenosed
+  semi-permeable vesicle, with permeability rate $\beta=10^{-3}$. The
+  $x$-axis is the $x$-coordinate of the center of mass of the vesicle.
+  The vesicle loses fluid at a constant rate throughout the constriction
+  that is between $\pm 60$. The semi-permeable vesicle loses 12.8\% of
+  its fluid.}
+\end{figure}
+
+\begin{figure}[htp]
+  \ifTikz
+  \input{figures/stenosisBL.tikz}
+  \fi
+  \caption{\label{fig:stenosisBL} A stenosed semi-impermeable vesicle
+  with reduced area 0.17. The initial reduced area is $0.20$. The bottom
+  plot shows the velocity relative to the vesicle inside the square.
+  The vesicle velocity in the square is nearly constant.}
+\end{figure}
+
 Inspired by an experiment that measures the effects of cells on 
@@
 
+%\begin{figure}[htp]
+%  \centering
+%  \begin{tabular}{ccc}
+%    \ifTikz
+%    \scalebox{0.31}{\input{figures/stenosisTension1.tikz}} &
+%    \scalebox{0.31}{\input{figures/stenosisTension3.tikz}} &
+%    \scalebox{0.31}{\input{figures/stenosisTension5.tikz}} \\
+%    \scalebox{0.31}{\input{figures/stenosisTension7.tikz}} &
+%    \scalebox{0.31}{\input{figures/stenosisTension9.tikz}} &
+%    \scalebox{0.31}{\input{figures/stenosisTension11.tikz}} 
+%    \fi
+%  \end{tabular}
+%  \caption{\label{fig:stenosisTension} The tension of the impermeable
+%  (red) and semi-permeable (dashed blue) vesicles in
+%  Figure~\ref{fig:stenosisShape}. The point $\theta=0$ corresponds to
+%  the right-most point of the vesicle.}
+%\end{figure}
+%
+%\begin{figure}[htp]
+%  \centering
+%  \begin{tabular}{ccc}
+%    \iftikz
+%    \scalebox{0.31}{\input{figures/stenosisflux1.tikz}} &
+%    \scalebox{0.31}{\input{figures/stenosisflux3.tikz}} &
+%    \scalebox{0.31}{\input{figures/stenosisflux5.tikz}} \\
+%    \scalebox{0.31}{\input{figures/stenosisflux7.tikz}} &
+%    \scalebox{0.31}{\input{figures/stenosisflux9.tikz}} &
+%    \scalebox{0.31}{\input{figures/stenosisflux11.tikz}} 
+%    \fi
+%  \end{tabular}
+%  \caption{\label{fig:stenosisFlux} The flux (equivalent to pressure
+%  jump) of the impermeable (red) and semi-permeable (dashed blue)
+%  vesicles in Figure~\ref{fig:stenosisShape}. The point $\theta=0$
+%  corresponds to the right-most point of the vesicle.}
+%\end{figure}
+
 \end{document}

### 2020-09-26 vesicle_code/examples/output/makeImages.m

@@ -19,9 +19,10 @@ if 0
   options.marker = true;
 end
 if 1
-  file = 'choke1VesLData.bin';
+%  file = 'choke1VesLData.bin';
   options.marker = false;
-%file = '~/projects/brinkman/vesicle_code/results/choke1VesLong/beta0RA0p65/choke1VesData.bin';
+%file = '~/projects/brinkman/vesicle_code/results/choke1VesLong/beta1em3RA0p20/choke1VesData.bin';
+file = '~/projects/brinkman/vesicle_code/results/choke1VesLong/beta0RA0p20/choke1VesData.bin';
 %file = '~/projects/brinkman/vesicle_code/results/choke1VesLong/beta1em3RA0p65Centered/choke1VesData.bin';
 %file = '~/projects/brinkman/vesicle_code/results/choke1VesLong/beta0Scale1p44_kappa1e0_farfield1e0/choke1VesData.bin'
 %file = '~/projects/brinkman/vesicle_code/results/choke1VesLong/beta0Scale1p44_kappa1e1_farfield1e0/choke1VesData.bin';

### 2020-09-29 vesicle_code/docs/permeableVes/main.tex
adding new figures

@@
 channel represent the tension and those along the right represent the
-flux. In Figure~\ref{fig:stenosisTensionAndFux}, the tension at location
-$x=20$ and the flux at location $x=30$ are plotted with respect to
-arclength. The value of $\theta=0$ corresponds to the nose of the
+flux. In Figure~\ref{fig:stenosisTensionAndFlux}, the tension at
+location $x=20$ and the flux at location $x=30$ are plotted with respect
+to arclength. The value of $\theta=0$ corresponds to the nose of the
 vesicle.
@@
 %  \scalebox{0.5}{\input{figures/stenosisShapeFlux02.tikz}}
-  \scalebox{0.5}{\input{figures/stenosisShapeTension03.tikz}}
-  \scalebox{0.5}{\input{figures/stenosisShapeFlux04.tikz}}
-  \scalebox{0.5}{\input{figures/stenosisShapeTension05.tikz}}
-  \scalebox{0.5}{\input{figures/stenosisShapeFlux06.tikz}}
-  \scalebox{0.5}{\input{figures/stenosisShapeTension07.tikz}}
-  \scalebox{0.5}{\input{figures/stenosisShapeFlux08.tikz}}
-  \scalebox{0.5}{\input{figures/stenosisShapeTension09.tikz}}
-  \scalebox{0.5}{\input{figures/stenosisShapeFlux10.tikz}}
+%  \scalebox{0.5}{\input{figures/stenosisShapeTension03.tikz}}
+%  \scalebox{0.5}{\input{figures/stenosisShapeFlux04.tikz}}
+%  \scalebox{0.5}{\input{figures/stenosisShapeTension05.tikz}}
+%  \scalebox{0.5}{\input{figures/stenosisShapeFlux06.tikz}}
+%  \scalebox{0.5}{\input{figures/stenosisShapeTension07.tikz}}
+%  \scalebox{0.5}{\input{figures/stenosisShapeFlux08.tikz}}
+%  \scalebox{0.5}{\input{figures/stenosisShapeTension09.tikz}}
+%  \scalebox{0.5}{\input{figures/stenosisShapeFlux10.tikz}}
 %  \scalebox{0.5}{\input{figures/stenosisShapeTension11.tikz}}
 %  \scalebox{0.5}{\input{figures/stenosisShapeFlux12.tikz}}
+  \scalebox{0.5}{\input{figures/stenosisShapeTension02.tikz}}
+  \scalebox{0.5}{\input{figures/stenosisShapeFlux04.tikz}}
+  \scalebox{0.5}{\input{figures/stenosisShapeTension06.tikz}}
+  \scalebox{0.5}{\input{figures/stenosisShapeFlux08.tikz}}
+  \scalebox{0.5}{\input{figures/stenosisShapeTension10.tikz}}
+  \scalebox{0.5}{\input{figures/stenosisShapeFlux12.tikz}}
   \fi
@@
   \ifTikz
-  \scalebox{0.5}{\input{figures/stenosisTension09.tikz}}
-  \scalebox{0.5}{\input{figures/stenosisFlux10.tikz}}
+  \scalebox{0.5}{\input{figures/stenosisTension12.tikz}}
+  \scalebox{0.5}{\input{figures/stenosisFlux12.tikz}}
+  \scalebox{0.5}{\input{figures/stenosisXvelocity12.tikz}}
+  \scalebox{0.5}{\input{figures/stenosisYvelocity12.tikz}}
   \fi
-  \caption{\label{fig:stenosisTensionAndFlux} The tension (left) and
-  flux (right) of the semi-permeable (red) and impermeable (dashed blue)
-  vesicles in Figure~\ref{fig:stenosisShape} at locations $x=20$ and
-  $x=30$. The point $\theta=0$ corresponds to the right-most point of
-  the vesicle.}
+  \caption{\label{fig:stenosisTensionAndFlux} The tension (top left), 
+  flux (top right), $x$-velocity (bottom left), and $y$-velocity (bottom
+  right) of the semi-permeable (red) and impermeable (dashed blue)
+  vesicles in Figure~\ref{fig:stenosisShape} at location $x=50$. The
+  point $\theta=0$ corresponds to the right-most point of the vesicle.}
 \end{figure}
@@
 \begin{figure}[htp]
+%  \ifTikz
+  \input{figures/stenosisBL.tikz}
+%  \fi
+  \caption{\label{fig:stenosisBL} A stenosed semi-impermeable (red) and
+  imperemable (blue) vesicle. The semi-permeable vesicle has 
+  reduced area 0.17, and both vesicles were initialized with reduce area
+  $0.20$. The bottom plot shows the velocity relative to the vesicle
+  inside the lubrication layer.  The vesicle velocity in the square is
+  nearly constant (see Figure~\ref{fig:stenosisRA020Velocity}.}
+\end{figure}
+
+\begin{figure}[htp]
+  \centering
   \ifTikz
-  \input{figures/stenosisBL.tikz}
+  \scalebox{0.5}{\input{figures/stenosisXvelocityRA020.tikz}}
+  \scalebox{0.5}{\input{figures/stenosisYvelocityRA020.tikz}}
   \fi
-  \caption{\label{fig:stenosisBL} A stenosed semi-impermeable vesicle
-  with reduced area 0.17. The initial reduced area is $0.20$. The bottom
-  plot shows the velocity relative to the vesicle inside the square.
-  The vesicle velocity in the square is nearly constant.}
+  \caption{\label{fig:stenosisRA020Velocity} The $x$ (left) and $y$
+  (right) velocities of the vesicle in Figure~\ref{fig:stenosisBL}. The
+  red lines correspond to the semi-permeable vesicle and the blue dashed
+  lines correspond to the impermeable vesicle.}
 \end{figure}

### 2020-10-06 vesicle_code/examples/contracting1Ves.m
starting contracting geometry runs

@@ -1,0 +1,76 @@
+clear all;
+%clc; clf;
+fprintf('One elliptical vesicles in a contracting geometry.\n');
+
+prams.N = 256/4;                 % points per vesicle
+prams.nv = 1;                  % number of vesicles
+prams.T = 20;                  %time horizon
+prams.m = 10000;                % number of time steps
+prams.Nbd = 1024;               % number of points on solid wall
+prams.nvbd = 1;                % number of components to solid walls
+prams.kappa = 1e0;            % bending coefficient
+prams.viscCont = 1*ones(prams.nv,1);            % viscosity contrast
+prams.gmresTol = 1e-10;        % GMRES tolerance
+prams.errorTol = 8e-1;
+% Maximum relative error in area and length before the simulation
+% is stopped
+prams.dtMin = 1e-5;
+prams.dtMax = 1e0;
+
+options.semipermeable = true;
+prams.fluxCoeff = 1e-3;
+options.fluxShape = 1; % constant value
+
+options.farField = 'contracting';      % Constricted domain
+options.farFieldSpeed = 1;
+% background velocity or solid walls (which comes with a default
+% boundary condition)
+options.vesves = 'implicit';
+% Discretization of vesicle-vesicle and vesicle-boundary 
+% intearctions.  Either 'explicit' or 'implicit'
+options.near = true;        % near-singular integration
+options.fmm = ~true;
+options.fmmDLP = ~true;
+% use FMM to compute single-layer potential
+options.confined = true;   % confined or unbounded geometry
+% Used for geometry and boundary conditins of solid walls
+options.usePlot = true;     % View vesicles during run
+options.axis = [-1 19 -5 5]; 
+% Axis for plots if usePlot = true
+options.saveData = true;    
+% Save vesicle information and create a log file
+options.logFile = 'output/contracting1Ves.log';
+% Name of log file
+options.dataFile = 'output/contracting1VesData.bin';
+% Name of binary data file for storing vesicle information
+options.verbose = true;
+% Decides how much info is written to console
+options.profile = false;    % Profile code
+options.collision = false;   % Collision detection
+
+options.nsdc = 1;
+options.orderGL = 2;
+
+options.timeAdap = true;
+prams.rtolArea = 1e20;
+prams.rtolLength = 1e-2;
+prams.betaUp = 1.5;
[…]

### 2020-10-06 vesicle_code/src/tstep.m

@@ -2863,7 +2863,21 @@ elseif any(strcmp(varargin,'chokeLongest'))
 %  quiver(x,y,vInf(1:end/2),vInf(end/2+1:end))
 %  axis equal
 %  pause
-  
+
+elseif any(strcmp(varargin,'contracting'));
+  vInf = zeros(2*N,nv);
+  xmax = max(x);
+  xmin = min(x);
+  ind = find(x < (xmin + 0.1) | x > (xmax - 0.1));
+  ymax = max(y(ind));
+  vx = (ymax^2-y(ind).^2)/ymax^2;
+  % parabolic flow
+  vInf(ind,:) = vx;
+
+  T11 = zeros(N,nv);
+  T12 = zeros(N,nv);
+  T22 = zeros(N,nv);
+
 elseif any(strcmp(varargin,'couette'))
   vInf = [zeros(2*N,1) 1*[-y(:,2)+mean(y(:,2));x(:,2)-mean(x(:,2))]];
   

### 2020-10-13 vesicle_code/docs/permeableVes/main.tex
starting contracting geometry runs
converted tikz to pdf

@@
 rather type the intro starting here.
+
+\paragraph{Literature to maybe cite}
+\cite{ali-ovr-ran2020} show how beading can occur on nanotubes. This
+happens in regions where proteins congregate and this can lead to
+semi-permeability?
 
@@
   \centering
-  \ifTikz
-  \input{figures/ellipseArea.tikz}
-  \fi
-%  \includegraphics[width=0.8\linewidth]{figures/ellipseArea}
+%  \ifTikz
+%  \input{figures/ellipseArea.tikz}
+%  \fi
+  \includegraphics[width=0.9\linewidth]{figures/ellipseArea}
   \caption{\label{fig:ellipseArea} The area of an elliptical
@@
   \centering
-  \ifTikz
-  \input{figures/shearSS.tikz}
-  \fi
+%  \ifTikz
+%  \input{figures/shearSS.tikz}
+%  \fi
+  \includegraphics[width=0.9\linewidth]{figures/shearSS.pdf}
   \caption{\label{fig:shearSS} The reduced area of a semi-permeable
@@
 \begin{figure}[htp]
-  \ifTikz
-  \input{figures/parabolicOffCenterPhaseImpermeable.tikz}
-  \fi
+%  \ifTikz
+%  \input{figures/parabolicOffCenterPhaseImpermeable.tikz}
+%  \fi
+  \includegraphics[width=0.9\linewidth]{figures/parabolicOffCenterPhaseImpermeable.pdf}
   \caption{\label{fig:parabolicOffCenterImpermeablePhaseDiagram} Phase
@@
 \begin{figure}[htp]
-  \ifTikz
-  \input{figures/parabolicOffCenterPhaseSemipermeable.tikz}
-  \fi
+%  \ifTikz
+%  \input{figures/parabolicOffCenterPhaseSemipermeable.tikz}
+%  \fi
+  \includegraphics[width=0.9\linewidth]{figures/parabolicOffCenterPhaseSemipermeable.pdf}
   \caption{\label{fig:parabolicOffCenterSemipermeablePhaseDiagram} Phase
-  diagram of an semi-permeable vesicle, with $\beta = 10^{-3}$, with
+  diagram of a semi-permeable vesicle, with $\beta = 10^{-3}$, with
   several different flow rates $U$ and reduced areas $\nu$. The
@@
 \end{figure}
-
-\begin{itemize}
-  \item If the flow rate is too small, the vesicle only migrates part
-    way before it turns into a circle. Once it's a circle, it acts like
-    a rigid body, so it no longer migrates towards the center line
-\end{itemize}
 
@@
 \begin{figure}[htp]
-  \ifTikz
+%  \ifTikz
 %  \scalebox{0.5}{\input{figures/stenosisShapeTension01.tikz}}
@@
 %  \scalebox{0.5}{\input{figures/stenosisShapeFlux12.tikz}}
-  \scalebox{0.5}{\input{figures/stenosisShapeTension02.tikz}}
-  \scalebox{0.5}{\input{figures/stenosisShapeFlux04.tikz}}
-  \scalebox{0.5}{\input{figures/stenosisShapeTension06.tikz}}
-  \scalebox{0.5}{\input{figures/stenosisShapeFlux08.tikz}}
-  \scalebox{0.5}{\input{figures/stenosisShapeTension10.tikz}}
-  \scalebox{0.5}{\input{figures/stenosisShapeFlux12.tikz}}
-  \fi
+%  \scalebox{0.5}{\input{figures/stenosisShapeTension02.tikz}}
+%  \scalebox{0.5}{\input{figures/stenosisShapeFlux04.tikz}}
+%  \scalebox{0.5}{\input{figures/stenosisShapeTension06.tikz}}
+%  \scalebox{0.5}{\input{figures/stenosisShapeFlux08.tikz}}
+%  \scalebox{0.5}{\input{figures/stenosisShapeTension10.tikz}}
+%  \scalebox{0.5}{\input{figures/stenosisShapeFlux12.tikz}}
+%  \fi
+  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeTension02.pdf}
+  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeFlux04.pdf}
+  \\
+  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeTension06.pdf}
+  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeFlux08.pdf}
+  \\
+  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeTension10.pdf}
+  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeFlux12.pdf}
   \caption{\label{fig:stenosisShape} An impermeable (dashed) and
@@
   \centering
-  \ifTikz
-  \scalebox{0.5}{\input{figures/stenosisTension12.tikz}}
-  \scalebox{0.5}{\input{figures/stenosisFlux12.tikz}}
-  \scalebox{0.5}{\input{figures/stenosisXvelocity12.tikz}}
-  \scalebox{0.5}{\input{figures/stenosisYvelocity12.tikz}}
-  \fi
+%  \ifTikz
+%  \scalebox{0.5}{\input{figures/stenosisTension12.tikz}}
+%  \scalebox{0.5}{\input{figures/stenosisFlux12.tikz}}
+%  \scalebox{0.5}{\input{figures/stenosisXvelocity12.tikz}}
+%  \scalebox{0.5}{\input{figures/stenosisYvelocity12.tikz}}
+%  \fi
+  \includegraphics[width=0.45\linewidth]{figures/stenosisTension12.pdf}
+  \includegraphics[width=0.45\linewidth]{figures/stenosisFlux12.pdf} \\
+  \includegraphics[width=0.45\linewidth]{figures/stenosisXvelocity12.pdf}
+  \includegraphics[width=0.45\linewidth]{figures/stenosisYvelocity12.pdf}
   \caption{\label{fig:stenosisTensionAndFlux} The tension (top left), 
@@
   \centering
-  \ifTikz
-  \input{figures/stenosisArea.tikz}
-  \fi
-%  \includegraphics[width=0.8\linewidth]{figures/ellipseArea}
+%  \ifTikz
+%  \input{figures/stenosisArea.tikz}
+%  \fi
+  \includegraphics[width=0.8\linewidth]{figures/stenosisArea}
   \caption{\label{fig:stenosisArea} The area of a stenosed
@@
 %  \ifTikz
-  \input{figures/stenosisBL.tikz}
-%  \fi
+%  \input{figures/stenosisBL.tikz}
+%  \fi
+  \includegraphics[width=\linewidth]{figures/stenosisBL.pdf}
   \caption{\label{fig:stenosisBL} A stenosed semi-impermeable (red) and
@@
   \centering
-  \ifTikz
-  \scalebox{0.5}{\input{figures/stenosisXvelocityRA020.tikz}}
-  \scalebox{0.5}{\input{figures/stenosisYvelocityRA020.tikz}}
-  \fi
+%  \ifTikz
+%  \scalebox{0.5}{\input{figures/stenosisXvelocityRA020.tikz}}
+%  \scalebox{0.5}{\input{figures/stenosisYvelocityRA020.tikz}}
+%  \fi
+  \includegraphics[width=0.45\linewidth]{figures/stenosisXvelocityRA020.pdf}
+  \includegraphics[width=0.45\linewidth]{figures/stenosisYvelocityRA020.pdf}
   \caption{\label{fig:stenosisRA020Velocity} The $x$ (left) and $y$
@@
 \begin{figure}[htp]
-  \ifTikz
-  \input{figures/stenosisGeom.tikz}
-  \fi
-%  \includegraphics[width=0.8\linewidth]{figures/parabolicPhaseDiagram.pdf}
+%  \ifTikz
+%  \input{figures/stenosisGeom.tikz}
+%  \fi
+  \includegraphics[width=\linewidth]{figures/stenosisGeom.pdf}
   \caption{\label{fig:stenosisGeom} A single semi-permeable vesicle
@@
 \begin{figure}[htp]
-  \ifTikz
-  \input{figures/stenosisPressureFluctuation.tikz}
-  \fi
+%  \ifTikz
+%  \input{figures/stenosisPressureFluctuation.tikz}
+%  \fi
+  \includegraphics[width=\linewidth]{figures/stenosisPressureFluctuation.pdf}
   \caption{\label{fig:stenosisPressure} The excess pressure across the

### 2020-10-22 vesicle_code/docs/permeableVes/main.tex
putting in contant pressure drop

@@
 
-%\usepgfplotslibrary{external}
-%\tikzexternalize
+\usepgfplotslibrary{external}
+\tikzexternalize
 
@@
 
+\begin{figure*}[htp]
+  \centering
+  \begin{minipage}{0.4\textwidth}
+  \includegraphics[width=\linewidth]{figures/ellipseArea}
+  \end{minipage}
+  \hfill
+  \begin{minipage}{0.56\textwidth}
+  \includegraphics[width=0.31\linewidth]{figures/ellipseVelocity1.pdf}
+  \includegraphics[width=0.31\linewidth]{figures/ellipseVelocity2.pdf}
+  \includegraphics[width=0.31\linewidth]{figures/ellipseVelocity3.pdf}
+  \end{minipage}
+  \caption{A big caption for a composite figure}
+\end{figure*}
+
 \begin{figure}[htp]
@@
   \centering
-%  \input{figures/ellipseVelocity1.tikz}
-%  \input{figures/ellipseVelocity2.tikz}
-%  \input{figures/ellipseVelocity3.tikz}
+%  \scalebox{0.6}{\input{figures/ellipseVelocity1.tikz}}
+%  \scalebox{0.6}{\input{figures/ellipseVelocity2.tikz}}
+%  \scalebox{0.6}{\input{figures/ellipseVelocity3.tikz}}
+%  \scalebox{0.6}{\input{figures/ellipseVelocity4.tikz}}
 %  \input{figures/ellipseVelocityNorms.tikz}
@@
   \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity3.pdf}
-  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocityNorms.pdf}
-  \caption{\label{fig:vesVelocity} The velocity contributions due to
-  force balance (blue) and permeability (red). The green line is the
+  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity4.pdf}
+  \caption{\label{fig:vesVelocity} The normal velocity contributions due
+  to force balance (blue) and permeability (red). The green line is the
   velocity of an impermeable vesicle with the same initial shape as the
-  semi-permeable vesicle. The right-most plot is the maximum norm of
-  each velocity contribution. The black lines correspond to the times
-  reported in the other three plots.}
+  semi-permeable vesicle.}
 \end{figure*}

### 2020-10-22 vesicle_code/src/Ves2D.m

@@ -9,6 +9,11 @@ global derivs  ;  % number of times we compute differential
                   % operators for preconditioning
 global fmms       % number of fmm calls
 
+
+% TODO: THIS SHOULDN'T GO HERE
+pressDrop = 200;
+
+
 om = monitor(X,Xwalls,options,prams);
 % Create class for doing input/output
 
@@ -17,6 +22,7 @@ if nargin == 4
 else
   om.initializePressure(pressTar); 
 end
+pressTar = [0.5;17.5;0;0]; 
 
 matvecs = 0; 
 % counter for the total number of time steps
@@ -58,9 +64,9 @@ om.writeMessage(message,'%s\n')
 message = ' ';
 om.writeMessage(message,'%s\n')
 
-oc = curve;
 tt = tstep(options,prams);
 % build an object of class tstep with required options and parameters
+
 Xstore = zeros(2*N,nv);
 sigStore = zeros(N,nv);
 uStore = zeros(2*N,nv);
@@ -88,7 +94,10 @@ end
 [Xstore,sigStore,uStore,etaStore,RSstore] = ...
     tt.firstSteps(options,prams,Xstore,sigStore,uStore,...
     walls,wallsCoarse,om);
-% Was for higher-order multistep methods which have been fazed out.
+% Was for higher-order multistep methods which have been fazed out. Now
+% it just computes the initial density function and tension that are
+% needed for SDC
+
 
 % compute pressure and stress
 if nargin == 5
@@ -137,6 +146,31 @@ while time < prams.T - 1e-10
   vesicle = capsules(Xstore,sigStore,uStore,...
       prams.kappa,prams.viscCont,options.semipermeable,...
       prams.fluxCoeff,options.fluxShape);
+
+  % TODO: THIS SHOULD BE A FUNCTION IN TSTEP
+  if 1
+    [~,pressDLPtar] = tt.opWall.exactPressDL(walls,etaStore,[],pressTar,1);
+
+    tracJump = vesicle.tracJump(Xstore,sigStore);
+    % compute traction
+
+    [~,pressSLPtar] = tt.op.exactPressSL(vesicle,tracJump,[],pressTar,1);
+
+    press = pressSLPtar(1:end/2) + pressDLPtar(1:end/2);
+    dpress = diff(press);
+    
+%    options.farFieldSpeed = options.farFieldSpeed * (-200)/dpress;
[…]

### 2020-11-25 vesicle_code/docs/permeableVes/main.tex
fixed tikzexternalize
doing shear runs for PNAS

--- 2020-10-13 vesicle_code/docs/permeableVes/main.tex
@@
 \subsection*{Quiescent Flow} 
-We consider a semi-permeable elliptical vesicle with initial reduced
-area $\nu = 0.65$ and several different permeability rates in a
-quiescent flow. Based on our analysis, the steady state shape is a
-circle with constant tension $\Lambda = 2\pi^2/L^2$.
-By~\eqref{eqn:areaROC}, the area change is proportional to $\beta$, and
-we expect both the time for the vesicle to deviate from its initial
-area, and the time to reach its steady state to be proportional to
-$\beta^{-1}$. In Table~\ref{tbl:ellipseRelaxTimes}, we report the time,
-$t_\mathrm{steady}$, required for the vesicle's area to be within 1.3\%
-of its maximum area, and the time, $t_\mathrm{inflate}$, required for
-the vesicle's area to exceed 1.3\% of its initial area. Both times are
-proportional to $\beta^{-1}$. We plot the area of a vesicle with six
-different permeability rates in Figure~\ref{fig:ellipseArea}. The area
-is computed directly from the vesicle shape and the time axis is scaled
-by $\beta$. The plot verifies that the time for the vesicle to reach a
-circular shape is proportional to $\beta^{-1}$. We also
-solve~\eqref{eqn:areaROC} for the $\beta=10$ simulation and superimpose
-its solution with dots on Figure~\ref{fig:ellipseArea}.
+Based on our analysis, a semi-permeable vesicle in a quiescent flow
+relaxes to a circle with constant tension $\Lambda = 2\pi^2/L^2$.
+Furthermore, equation~\eqref{eqn:areaROC} shows that the area change is
+proportional to $\beta$, so we expect the times for the vesicle to
+deviate from its initial reduced area and to reach its steady state to
+both be proportional to $\beta^{-1}$. This is verified by considering a
+vesicle with initial reduced area $\nu = 0.65$ and several different
+semi-permeability rates. In Table~\ref{tbl:ellipseRelaxTimes} we report
+the time, $t_\mathrm{steady}$, required for the vesicle's area to be
+within 1.3\% of its steady state reduced area, and the time,
+$t_\mathrm{inflate}$, required for the vesicle's reduced area to exceed
+1.3\% of its initial reduced area. Both times are proportional to
+$\beta^{-1}$. 
 \begin{table}[htp]
@@
   \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
-    $\beta$ & $t_\mathrm{steady}$ & ratio & $t_\mathrm{inflate}$ & ratio \\
+    $\beta$ & $t_\mathrm{steady}$  & ratio 
+            & $t_\mathrm{inflate}$ & ratio \\
     \midrule
@@
 
-\begin{figure}[htp]
-  \centering
-%  \ifTikz
-%  \input{figures/ellipseArea.tikz}
-%  \fi
-  \includegraphics[width=0.9\linewidth]{figures/ellipseArea}
-  \caption{\label{fig:ellipseArea} The area of an elliptical
-  semi-permeable vesicle, with permeability rate $\beta$ in a quiescent
-  flow. The time axis is scaled by the permeability rate $\beta$. Since
-  the curves collapse to a single curve, the permeability rate $\beta$
-  sets a relaxation time scale.}
-\end{figure}
-
-We further analyze the transient dynamics by considering the vesicle
-velocity~\eqref{eqn:vesVelocity} for small $\beta$. Two terms contribute
-to the vesicle velocity: (i) the permeability velocity, $\beta(\ff \cdot
-\nn)\nn$, and (ii) the force balance velocity, $\SS[\ff]$. Since $\beta
-\ll 1$, the permeability velocity is much smaller than the force balance
-velocity at early times, and the semi-permeable vesicle dynamics
-resembles those of an impermeable vesicle. As the force balance velocity
-decreases, the permeability velocity becomes significant, and the
-vesicle begins to inflate to a circle. This results in the membrane
-force and velocity both converging to zero. Letting $\beta = 10^{-3}$,
-the normal component of the force balance velocity (blue) and the
-permeability velocity (red) are plotted at three times in
-Figure~\ref{fig:vesVelocity}. We also plot the velocity (green) of an
-identically initialized impermeable vesicle. At the early time $t=0.5$,
-the permeability velocity is negligible relative to the force balance
-velocity, and the force balance velocity matches with the impermeable
-vesicle velocity. At intermediate time $t=5$, all three velocities are
-comparable in size, and the semi-permeable vesicle begins to inflate.
-Finally, at time $t=50$, the impermeable vesicle is near steady state,
-while the semi-permeable vesicle is still inflating. The right-most
-plot of Figure~\ref{fig:vesVelocity} is the maximum norm of the
-different velocity contributions as a function of time, and the black
-vertical lines correspond to the times reported in the other three
-subplots.
+In Figure~\ref{fig:relaxationArea}, we examine the transient dynamics of
+four vesicles $\beta = 10^{-3}$ and a variety of initial configurations.
+First, in all cases the vesicle eventually reaches a circular shape of
+reduced area $\nu=1$. Second, we observe that even though the vesicle is
+inflating to a circle, meaning that there is a net flux into the
+vesicle, there are regions where the flux is out of the vesicle. These
+regions are denoted in blue and are only present at early times.
+Finally, the vesicles area does not initially change by much, and
+intermediate shapes of semi-permeable vesicles resemble the shape of an
+impermeable vesicle. This can be explained by considering the two terms
+that contribute to the vesicle velocity: (i) the permeability velocity,
+$\beta(\ff \cdot \nn) \nn$, and (ii) the force balance velocity,
+$\SS[\ff]$. Since $\beta = 10^{-3}$, the permeability velocity is much
+smaller than the force balance velocity at early times, and the
+semi-permeable vesicle dynamics resembles those of an impermeable
+vesicle. As the force balance velocity decreases, the permeability
+velocity dominates, and the vesicle begins to inflate to a circle with
+no vanishing force and velocity.
 
@@
   \centering
-%  \input{figures/ellipseVelocity1.tikz}
-%  \input{figures/ellipseVelocity2.tikz}
-%  \input{figures/ellipseVelocity3.tikz}
-%  \input{figures/ellipseVelocityNorms.tikz}
-  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity1.pdf}
-  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity2.pdf}
-  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity3.pdf}
-  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocityNorms.pdf}
-  \caption{\label{fig:vesVelocity} The velocity contributions due to
-  force balance (blue) and permeability (red). The green line is the
-  velocity of an impermeable vesicle with the same initial shape as the
-  semi-permeable vesicle. The right-most plot is the maximum norm of
-  each velocity contribution. The black lines correspond to the times
-  reported in the other three plots.}
+  \input{figures/relaxationArea.tikz}
+  \caption{\label{fig:relaxationArea} (a): Snapshots of four
+  semi-permeable vesicles with $\beta = 10^{-3}$ submerged in a
+  quiescent flow. The fluid flux along the red regions is into the
+  vesicle, and the fluid flux along the blue regions is out of the
+  vesicle. In all cases, the vesicle reaches a steady-state circular
+  shape. (b): The reduced area of each of the simulations. The
+  particular snapshots in (a) occur at the marks along the curve.}
 \end{figure*}
 
-We next investigate the interplay between the tension, transmembrane
-flux, and curvature of a semi-permeable vesicle. We let $\beta = 1$ and
-initialize the vesicle with regions of both positive and negative
-curvature. The vesicle tension, $\Lambda$, and the flux, $\ff \cdot
-\nn$, are plotted in Figure~\ref{fig:starTensionFlux}. At early times,
-regions of large negative curvature have negative tension and regions
-with large positive curvature have positive tension, and the same result
-holds for an impermeable vesicle. In addition, regions with large
-curvature have a large inflow of fluid (positive flux), while the
-flatter regions have an outflow of fluid. At these early times, the net
-effect is vesicle deflation. As the vesicle shape relaxes, the same
-general tension and flux trends persist, but the net flux is positive
-and the vesicle inflates. At later times, the tension becomes positive
-and the vesicle continues to inflate towards a circle. Finally, the
-tension transitions to a positive constant function, the membrane force
-and flux approach zero, and the vesicle shape reaches its steady
-circular shape.
+%We plot the area of a vesicle with six different permeability rates in
+%Figure~\ref{fig:ellipseArea}. The area is computed directly from the
+%vesicle shape and the time axis is scaled by $\beta$. The plot verifies
+%that the time for the vesicle to reach a circular shape is proportional
+%to $\beta^{-1}$. We also solve~\eqref{eqn:areaROC} for the $\beta=10$
+%simulation and superimpose its solution with dots on
+%Figure~\ref{fig:ellipseArea}.
+
+%\begin{figure}[htp]
+%  \centering
+%%  \ifTikz
+%%  \input{figures/ellipseArea.tikz}
+%%  \fi
+%  \includegraphics[width=0.9\linewidth]{figures/ellipseArea}
+%  \caption{\label{fig:ellipseArea} The area of an elliptical
+%  semi-permeable vesicle, with permeability rate $\beta$ in a quiescent
+%  flow. The time axis is scaled by the permeability rate $\beta$. Since
+%  the curves collapse to a single curve, the permeability rate $\beta$
+%  sets a relaxation time scale.}
+%\end{figure}
+
+%We further analyze the transient dynamics by considering the vesicle
+%velocity~\eqref{eqn:vesVelocity} for small $\beta$. Two terms contribute
+%to the vesicle velocity: (i) the permeability velocity, $\beta(\ff \cdot
+%\nn)\nn$, and (ii) the force balance velocity, $\SS[\ff]$. Since $\beta
+%\ll 1$, the permeability velocity is much smaller than the force balance
+%velocity at early times, and the semi-permeable vesicle dynamics
+%resembles those of an impermeable vesicle. As the force balance velocity
+%decreases, the permeability velocity becomes significant, and the
+%vesicle begins to inflate to a circle. This results in the membrane
+%force and velocity both converging to zero. Letting $\beta = 10^{-3}$,
+%the normal component of the force balance velocity (blue) and the
+%permeability velocity (red) are plotted at three times in
+%Figure~\ref{fig:vesVelocity}. We also plot the velocity (green) of an
+%identically initialized impermeable vesicle. At the early time $t=0.5$,
+%the permeability velocity is negligible relative to the force balance
+%velocity, and the force balance velocity matches with the impermeable
+%vesicle velocity. At intermediate time $t=5$, all three velocities are
+%comparable in size, and the semi-permeable vesicle begins to inflate.
+%Finally, at time $t=50$, the impermeable vesicle is near steady state,
+%while the semi-permeable vesicle is still inflating. The right-most
+%plot of Figure~\ref{fig:vesVelocity} is the maximum norm of the
+%different velocity contributions as a function of time, and the black
+%vertical lines correspond to the times reported in the other three
+%subplots.
+%
+%\begin{figure*}[htp]
+%  \centering
+%%  \scalebox{0.6}{\input{figures/ellipseVelocity1.tikz}}
+%%  \scalebox{0.6}{\input{figures/ellipseVelocity2.tikz}}
+%%  \scalebox{0.6}{\input{figures/ellipseVelocity3.tikz}}
+%%  \scalebox{0.6}{\input{figures/ellipseVelocity4.tikz}}
+%%  \input{figures/ellipseVelocityNorms.tikz}
+%  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity1.pdf}
+%  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity2.pdf}
+%  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity3.pdf}
+%  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity4.pdf}
+%  \caption{\label{fig:vesVelocity} The normal velocity contributions due
+%  to force balance (blue) and permeability (red). The green line is the
+%  velocity of an impermeable vesicle with the same initial shape as the
+%  semi-permeable vesicle.}
+%\end{figure*}
+
+%We next investigate the interplay between the tension, transmembrane
+%flux, and curvature of a semi-permeable vesicle. We let $\beta = 1$ and
+%initialize the vesicle with regions of both positive and negative
+%curvature. The vesicle tension, $\Lambda$, and the flux, $\ff \cdot
+%\nn$, are plotted in Figure~\ref{fig:starTensionFlux}. At early times,
+%regions of large negative curvature have negative tension and regions
+%with large positive curvature have positive tension, and the same result
+%holds for an impermeable vesicle. In addition, regions with large
+%curvature have a large inflow of fluid (positive flux), while the
+%flatter regions have an outflow of fluid. At these early times, the net
+%effect is vesicle deflation. As the vesicle shape relaxes, the same
+%general tension and flux trends persist, but the net flux is positive
+%and the vesicle inflates. At later times, the tension becomes positive
+%and the vesicle continues to inflate towards a circle. Finally, the
+%tension transitions to a positive constant function, the membrane force
+%and flux approach zero, and the vesicle shape reaches its steady
+%circular shape.
 
@@
 
-\begin{figure*}[htp]
-  \centering
-  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
-  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
-  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
-  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
-  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime5.pdf}
-  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime6.pdf}
-
-  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
-  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
-  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
-  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
-  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
-  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime6.pdf}
-  \caption{\label{fig:starTensionFlux} The vesicle tension (top) and
-  flux (bottom) of the semi-permeable vesicle in a quiescent
-  flow with $\beta=1$.}
-\end{figure*}
+%\begin{figure*}[htp]
+%  \centering
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime5.pdf}
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime6.pdf}
+%
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime6.pdf}
+%  \caption{\label{fig:starTensionFlux} The vesicle tension (top) and
+%  flux (bottom) of the semi-permeable vesicle in a quiescent
+%  flow with $\beta=1$.}
+%\end{figure*}
 
@@
   \centering
-%  \ifTikz
-%  \input{figures/shearSS.tikz}
-%  \fi
-  \includegraphics[width=0.9\linewidth]{figures/shearSS.pdf}
+  \ifTikz
+  \input{figures/shearSS.tikz}
+  \fi
+%  \includegraphics[width=0.9\linewidth]{figures/shearSS.pdf}
   \caption{\label{fig:shearSS} The reduced area of a semi-permeable

### 2020-11-25 vesicle_code/docs/permeableVes/makefigs/shear1Ves/shearPhase2.m

@@ -104,7 +104,7 @@ chis = {'1e-1','1e-0.5','1e0','1e0.5','1e1','1e1.5','1e2'};
 
 fid = fopen('data.dat','w');
 %for j = 1:numel(file)
-for j = 5:6
+for j = 1:1
   disp(j)
   [posx,posy,~,~,~,~,~,~,n,~] = loadFile(file{j});
 % some files did not print correctly to file becuase they were either

### 2020-11-25 vesicle_code/src/Ves2D.m

@@ -152,16 +152,16 @@ while time < prams.T - 1e-10
       prams.fluxCoeff,options.fluxShape);
 
   % TODO: THIS SHOULD BE A FUNCTION IN TSTEP
-  if 1
+  if 0
     [ssig,eeta] = vesicle.computeSigAndEta(tt,walls);
 
     [~,pressDLPtar] = tt.opWall.exactPressDL(walls,eeta,[],pressTar,1);
 
     tracJump = vesicle.tracJump(Xstore,ssig);
     % compute traction
-    figure(2); clf;
-    plot(ssig)
-    figure(1)
+%    figure(2); clf;
+%    plot(ssig)
+%    figure(1)
 
     [~,pressSLPtar] = tt.op.exactPressSL(vesicle,tracJump,[],pressTar,1);
 

### 2020-11-26 vesicle_code/docs/permeableVes/main.tex
doing runs

@@
 non-dimensionalized with $R_0/\tau$.
+
+\todo[inline]{This is a dump of information regarding how we
+non-dimensionalize}
+In each experiment, we initialize an elliptical vesicle with longest
+diameter of 9$\mu$m. We use a length scale of $R_0 = 10^{-6}$m, a
+bending stiffness of $k_b = 10^{-19}$J, and fluid viscosity of $\mu=5
+\times 10^{-2}$kg/ms. Using the relaxation time scale $\tau = \mu
+R_0^3/k_b = 5 \times 10^{-1}$s, the pressure scale is $P = k_b/R_0^3 =
+10^{-1}$Pa.
 
@@
 
-In Figure~\ref{fig:relaxationArea}, we examine the transient dynamics of
-four vesicles $\beta = 10^{-3}$ and a variety of initial configurations.
-First, in all cases the vesicle eventually reaches a circular shape of
-reduced area $\nu=1$. Second, we observe that even though the vesicle is
-inflating to a circle, meaning that there is a net flux into the
-vesicle, there are regions where the flux is out of the vesicle. These
-regions are denoted in blue and are only present at early times.
-Finally, the vesicles area does not initially change by much, and
-intermediate shapes of semi-permeable vesicles resemble the shape of an
-impermeable vesicle. This can be explained by considering the two terms
-that contribute to the vesicle velocity: (i) the permeability velocity,
-$\beta(\ff \cdot \nn) \nn$, and (ii) the force balance velocity,
-$\SS[\ff]$. Since $\beta = 10^{-3}$, the permeability velocity is much
-smaller than the force balance velocity at early times, and the
+In Figure~\ref{fig:relaxationComposite}, we examine the transient
+dynamics of four vesicles $\beta = 10^{-3}$ and a variety of initial
+configurations.  First, in all cases the vesicle eventually reaches a
+circular shape of reduced area $\nu=1$. Second, we observe that even
+though the vesicle is inflating to a circle, meaning that there is a net
+flux into the vesicle, there are regions where the flux is out of the
+vesicle. These regions are denoted in blue and are only present at early
+times.  Finally, the vesicles area does not initially change by much,
+and intermediate shapes of semi-permeable vesicles resemble the shape of
+an impermeable vesicle. This can be explained by considering the two
+terms that contribute to the vesicle velocity: (i) the permeability
+velocity, $\beta(\ff \cdot \nn) \nn$, and (ii) the force balance
+velocity, $\SS[\ff]$. Since $\beta = 10^{-3}$, the permeability velocity
+is much smaller than the force balance velocity at early times, and the
 semi-permeable vesicle dynamics resembles those of an impermeable
@@
   \centering
-  \input{figures/relaxationArea.tikz}
-  \caption{\label{fig:relaxationArea} (a): Snapshots of four
+  \ifTikz
+  \input{figures/relaxationComposite.tikz}
+  \fi
+  \caption{\label{fig:relaxationComposite} (a): Snapshots of four
   semi-permeable vesicles with $\beta = 10^{-3}$ submerged in a
@@
 
-%We plot the area of a vesicle with six different permeability rates in
-%Figure~\ref{fig:ellipseArea}. The area is computed directly from the
-%vesicle shape and the time axis is scaled by $\beta$. The plot verifies
-%that the time for the vesicle to reach a circular shape is proportional
-%to $\beta^{-1}$. We also solve~\eqref{eqn:areaROC} for the $\beta=10$
-%simulation and superimpose its solution with dots on
-%Figure~\ref{fig:ellipseArea}.
-
-%\begin{figure}[htp]
-%  \centering
-%%  \ifTikz
-%%  \input{figures/ellipseArea.tikz}
-%%  \fi
-%  \includegraphics[width=0.9\linewidth]{figures/ellipseArea}
-%  \caption{\label{fig:ellipseArea} The area of an elliptical
-%  semi-permeable vesicle, with permeability rate $\beta$ in a quiescent
-%  flow. The time axis is scaled by the permeability rate $\beta$. Since
-%  the curves collapse to a single curve, the permeability rate $\beta$
-%  sets a relaxation time scale.}
-%\end{figure}
-
-%We further analyze the transient dynamics by considering the vesicle
-%velocity~\eqref{eqn:vesVelocity} for small $\beta$. Two terms contribute
-%to the vesicle velocity: (i) the permeability velocity, $\beta(\ff \cdot
-%\nn)\nn$, and (ii) the force balance velocity, $\SS[\ff]$. Since $\beta
-%\ll 1$, the permeability velocity is much smaller than the force balance
-%velocity at early times, and the semi-permeable vesicle dynamics
-%resembles those of an impermeable vesicle. As the force balance velocity
-%decreases, the permeability velocity becomes significant, and the
-%vesicle begins to inflate to a circle. This results in the membrane
-%force and velocity both converging to zero. Letting $\beta = 10^{-3}$,
-%the normal component of the force balance velocity (blue) and the
-%permeability velocity (red) are plotted at three times in
-%Figure~\ref{fig:vesVelocity}. We also plot the velocity (green) of an
-%identically initialized impermeable vesicle. At the early time $t=0.5$,
-%the permeability velocity is negligible relative to the force balance
-%velocity, and the force balance velocity matches with the impermeable
-%vesicle velocity. At intermediate time $t=5$, all three velocities are
-%comparable in size, and the semi-permeable vesicle begins to inflate.
-%Finally, at time $t=50$, the impermeable vesicle is near steady state,
-%while the semi-permeable vesicle is still inflating. The right-most
-%plot of Figure~\ref{fig:vesVelocity} is the maximum norm of the
-%different velocity contributions as a function of time, and the black
-%vertical lines correspond to the times reported in the other three
-%subplots.
-%
-%\begin{figure*}[htp]
-%  \centering
-%%  \scalebox{0.6}{\input{figures/ellipseVelocity1.tikz}}
-%%  \scalebox{0.6}{\input{figures/ellipseVelocity2.tikz}}
-%%  \scalebox{0.6}{\input{figures/ellipseVelocity3.tikz}}
-%%  \scalebox{0.6}{\input{figures/ellipseVelocity4.tikz}}
-%%  \input{figures/ellipseVelocityNorms.tikz}
-%  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity1.pdf}
-%  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity2.pdf}
-%  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity3.pdf}
-%  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity4.pdf}
-%  \caption{\label{fig:vesVelocity} The normal velocity contributions due
-%  to force balance (blue) and permeability (red). The green line is the
-%  velocity of an impermeable vesicle with the same initial shape as the
-%  semi-permeable vesicle.}
-%\end{figure*}
-
-%We next investigate the interplay between the tension, transmembrane
-%flux, and curvature of a semi-permeable vesicle. We let $\beta = 1$ and
-%initialize the vesicle with regions of both positive and negative
-%curvature. The vesicle tension, $\Lambda$, and the flux, $\ff \cdot
-%\nn$, are plotted in Figure~\ref{fig:starTensionFlux}. At early times,
-%regions of large negative curvature have negative tension and regions
-%with large positive curvature have positive tension, and the same result
-%holds for an impermeable vesicle. In addition, regions with large
-%curvature have a large inflow of fluid (positive flux), while the
-%flatter regions have an outflow of fluid. At these early times, the net
-%effect is vesicle deflation. As the vesicle shape relaxes, the same
-%general tension and flux trends persist, but the net flux is positive
-%and the vesicle inflates. At later times, the tension becomes positive
-%and the vesicle continues to inflate towards a circle. Finally, the
-%tension transitions to a positive constant function, the membrane force
-%and flux approach zero, and the vesicle shape reaches its steady
-%circular shape.
-
-%\begin{figure*}[htp]
-%  \centering
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
-%
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
-%
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
-%
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
-%
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime5.pdf}
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
-%
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime6.pdf}
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime6.pdf}
-%  \caption{\label{fig:starTensionFlux} The vesicle tension (left) and
-%  flux (right) of the semi-permeable vesicle in a quiescent flow with
-%  $\beta=1$.}
-%\end{figure*}
-
-%\begin{figure*}[htp]
-%  \centering
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime5.pdf}
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime6.pdf}
-%
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime6.pdf}
-%  \caption{\label{fig:starTensionFlux} The vesicle tension (top) and
-%  flux (bottom) of the semi-permeable vesicle in a quiescent
-%  flow with $\beta=1$.}
-%\end{figure*}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection*{Shear Flow}
+\begin{figure*}[htp]
+  \centering
+  \ifTikz
+  \input{figures/shearComposite.tikz}
+  \fi
+  \caption{\label{fig:shearComposite} (a) The reduced area of a
+  semi-permeable vesicle with $\beta = 10^{-3}$ initialized with four
+  different reduced areas in a shear flow with two different flow rates.
+  (b) The steady state shape of a semi-permeable vesicle with varying
+  flow rates and semi-permeability rates. The circled vesicles
+  correspond to the simulations in part (a).}
+  \todo[inline]{$\nu=0.75$ run needs more temporal resolution.}
+\end{figure*}
+
 We consider a semi-permeable vesicle in the shear flow
@@
 area and viscosity contrast, two-dimensional vesicles either tank tread
-or tumble~\cite{fin-lam-sei-gom2008,kra-win-sei-lip1996}. Since we are
-considering semi-permeable vesicles, we assume there is no viscosity
-contrast, and tumbling is not possible.
-\begin{figure}[htp]
-  \centering
-  \ifTikz
-  \input{figures/shearSS.tikz}
-  \fi
-%  \includegraphics[width=0.9\linewidth]{figures/shearSS.pdf}
-  \caption{\label{fig:shearSS} The reduced area of a semi-permeable
-  vesicle in a shear flow. The final reduced area is nearly independent
-  of the initial reduced area.}
-\end{figure}
+or tumble~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. In our
+experiments, tumbling is impossible since we consider semi-permeable
+vesicles with no viscosity contrast. Similar to the dynamics of an
+impermeable vesicle, a semi-permeable vesicle tilts to an inclination
+angle and undergoes tank treading dynamics.
 
 In the quiescent flow, the steady state vesicle shape is independent of
-the initial vesicle shape. Here we test if a similar results holds with
-an imposed flow. In Figure~\ref{fig:shearSS}, we plot the reduced area
-of four vesicles with different initial reduced areas. The final shape
-depends on the initial vesicle length, but not on its initial reduced
-area. Therefore, for this example we only consider vesicles with the
-initial reduced area $\nu = 0.65$. For all permeability rates and shear
-rates, the semi-permeable vesicle tilts to an inclination angle and
-undergoes tank treading dynamics. Because of the semi-permeability, the
-initial and final reduced areas differ. In
-Figure~\ref{fig:shearPhaseDiagram}, we plot the final shape of the
-vesicle for various permeability rates, $\beta$, and shear rates
-$\dot{\gamma}$. The shear rate has the largest effect on the final
-reduced area.
-
-\begin{figure}[htp]
-  \centering
-  %\ifTikz
-%  \input{figures/shearPhaseDiagramRA2.tikz}
-  %\fi
-  \includegraphics[width=\linewidth]{figures/shearPhaseDiagramRA2.pdf}
-  \caption{\label{fig:shearPhaseDiagram} The steady state shape of a
-  semi-permeable vesicle with several different permeability rates
-  $\beta$ and shear rates $\dot{\gamma}$. The final reduced areas are
-  reported for the largest and smallest parameter values. The final
-  reduced area decreases with the flow rate, while the permeability rate
-  has a very small effect on the steady state shape.}
-\end{figure}
+the initial vesicle shape, and we investigate if this is true when a
+shear flow is imposed. In Figure~\ref{fig:shearComposite}(a), using four
+initial reduced areas and two flow rates, we plot the reduced area of a
+semi-permeable vesicle with $\beta = 10^{-3}$. As we saw for the
+quiescent example, the final shape does not depend on the initial
+reduced area. However, it does depend on the flow rate. We also observe
+a very small change in the reduced area at early times with the vesicle
+dynamics at early times being similar to those of an impermeable
+vesicle.  However, once the vesicle is tank-treading, the normal
+component of the force-balance velocity is small and the permeability
+velocity dominates and leads to a changing reduced area.
+
+We also form the steady state shape for a variety of semi-permeability
+rates and flow rates. Since the final shape is independent of the
+initial reduce area, we choose an vesicle with $\nu = 0.65$ for all the
+simulations. The steady state vesicle shape, along with its reduced
+area, are in Figure~\ref{fig:shearComposite}(b). We see that the flow
+rate significantly affects the final vesicle shape, but the
+semi-permeability rate has no significant effect. Instead, as we saw in
+the quiescent analysis, $\beta$ sets a time scale since the time
+required for a vesicle to reach its steady state configuration is
+proportional to $\beta^{-1}$.
 
@@
 \subsection*{Poiseuille Flow}
+\begin{figure}[htp]
+  \ifTikz
+  \input{figures/parabolicComposite.tikz}
+  \fi
+  \caption{\label{fig:parabolicComposite} (a) The steady-state shape of
+  an impermeable vesicle submerged in a Poiseuille flow with varying
+  initial reduced areas and flow rates. The results agree with Kaoui et
+  al.~\cite{kao-bir-mis2009}. (b) The steady state shape of a
+  semi-permeable vesicle submerged in a Poiseuille flow with varying
+  initial reduced areas and flow rates.}
+\end{figure}
+
 We consider a semi-permeable vesicle in the Poiseuille flow $\uu =
-U(1-(y/W)^2,0)$, where $U$ is the maximum imposed velocity. The length
-of the vesicle is $L = 2\pi$. We examine the effect of the non-linear
-Poiseuille flow on the migration of semi-permeable vesicle. In this
-experiment, the vesicle is initialized above the center line $y=0$, and
-it migrates towards the center line~\cite{dan-vla-mis2009}. For an
-impermeable vesicle, depending on the vesicles reduced area and the flow
-rate,  the long time vesicle shape is either an axisymmetric parachute
-or bullet, or a asymmetric tank-treading slipper~\cite{kao-bir-mis2009}.
-To validate our methods, in
-Figure~\ref{fig:parabolicOffCenterImpermeablePhaseDiagram} we
-reconstruct the phase diagram for an impermeable
+U(1-(y/W)^2,0)$, where $U$ is the maximum imposed velocity. We examine
+the effect of the non-linear Poiseuille flow on the migration of
+semi-permeable vesicle. In this experiment, the vesicle is initialized
+above the center line $y=0$, and it migrates towards the center
+line~\cite{dan-vla-mis2009}. For an impermeable vesicle, depending on
+the vesicles reduced area and the flow rate, the long time vesicle shape
+is either an axisymmetric parachute or bullet, or an asymmetric
+tank-treading slipper~\cite{kao-bir-mis2009}. To validate our methods,
+in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
+for the steady state shape of an impermeable vesicle
 vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
@@
 
-\begin{figure}[htp]
-%  \ifTikz
-%  \input{figures/parabolicOffCenterPhaseImpermeable.tikz}
-%  \fi
-  \includegraphics[width=0.9\linewidth]{figures/parabolicOffCenterPhaseImpermeable.pdf}
-  \caption{\label{fig:parabolicOffCenterImpermeablePhaseDiagram} Phase
-  diagram of an impermeable vesicle with several different flow rates
-  $U$ and reduced areas $\nu$. As shown by Kaoui et
-  al.~\cite{kao-bir-mis2009}, the final vesicle shape is either an
-  axisymmetric parachute or bullet (pink region) or an asymmetric
-  slipper (yellow region).}
-\end{figure}
-
 Having validated our method, we investigate the dynamics of a
@@
 final vesicle configurations are in
-Figure~\ref{fig:parabolicOffCenterSemipermeablePhaseDiagram}.  As we
-observed for the shear flow, the steady state reduced area is
-independent of the initial reduced area, and larger flow rates result in
-smaller steady state reduced areas. We report the steady state reduced
-area in Figure~\ref{fig:parabolicOffCenterSemipermeablePhaseDiagram}.
-At the smallest flow rate of $U = 200 \mu m/s$, the steady state reduced
-area is large, and the result is an axisymmetric bullet. However, at the
-larger flow rates, the steady state reduced area is smaller, and the
-result is an asymmetric tank-treading slipper.
-
-\begin{figure}[htp]
-%  \ifTikz
-%  \input{figures/parabolicOffCenterPhaseSemipermeable.tikz}
-%  \fi
-  \includegraphics[width=0.9\linewidth]{figures/parabolicOffCenterPhaseSemipermeable.pdf}
-  \caption{\label{fig:parabolicOffCenterSemipermeablePhaseDiagram} Phase
-  diagram of a semi-permeable vesicle, with $\beta = 10^{-3}$, with
-  several different flow rates $U$ and reduced areas $\nu$. The
-  steady state reduced area for each flow rate, which is reported along
-  the top of the vesicles, is nearly independent of the initial reduced
-  area. Low flow rates result in axisymmetric vesicles with large
-  reduced area, and high flow rates result in asymmetric vesicles with
-  low reduced area. Results at higher flow rates are not eporeted since
-  the vesicle self-intersects.}
-\end{figure}
+Figure~\ref{fig:parabolicComposite}(b). As observed for the shear flow,
+the steady state reduced area is independent of the initial reduced
+area, and larger flow rates result in smaller steady state reduced
+areas. We report the steady state reduced area in
+Figure~\ref{fig:parabolicComposite}(b). At the smallest flow rate of $U
+= 200 \mu m/s$, the steady state reduced area is large, and the result
+is an axisymmetric bullet. At the larger flow rates, the steady state
+reduced area is smaller, and the result is an asymmetric tank-treading
+slipper.
 
@@
 \subsection*{Semi-Permeable Vesicle in Stenosis}
-We consider the effect of stenosis on a semi-permeable vesicle. To allow
-for large amounts of fluid flux through the membrane, we consider
-geometry with a long constricted region. We start by considering a
-vesicle initialized with reduced area $\nu = 0.65$, and we compare the
-vesicle shape when $\beta = 0$ (impermeable) and $\beta = 10^{-3}$
-(permeable). Figure~\ref{fig:stenosisShape} shows the vesicles' shape at
-several locations along the constriction. The colors along the left
-channel represent the tension and those along the right represent the
-flux. In Figure~\ref{fig:stenosisTensionAndFlux}, the tension at
-location $x=20$ and the flux at location $x=30$ are plotted with respect
-to arclength. The value of $\theta=0$ corresponds to the nose of the
-vesicle.
-\begin{figure}[htp]
-%  \ifTikz
-%  \scalebox{0.5}{\input{figures/stenosisShapeTension01.tikz}}
-%  \scalebox{0.5}{\input{figures/stenosisShapeFlux02.tikz}}
-%  \scalebox{0.5}{\input{figures/stenosisShapeTension03.tikz}}
-%  \scalebox{0.5}{\input{figures/stenosisShapeFlux04.tikz}}
-%  \scalebox{0.5}{\input{figures/stenosisShapeTension05.tikz}}
-%  \scalebox{0.5}{\input{figures/stenosisShapeFlux06.tikz}}
-%  \scalebox{0.5}{\input{figures/stenosisShapeTension07.tikz}}
-%  \scalebox{0.5}{\input{figures/stenosisShapeFlux08.tikz}}
-%  \scalebox{0.5}{\input{figures/stenosisShapeTension09.tikz}}
-%  \scalebox{0.5}{\input{figures/stenosisShapeFlux10.tikz}}
-%  \scalebox{0.5}{\input{figures/stenosisShapeTension11.tikz}}
-%  \scalebox{0.5}{\input{figures/stenosisShapeFlux12.tikz}}
-%  \scalebox{0.5}{\input{figures/stenosisShapeTension02.tikz}}
-%  \scalebox{0.5}{\input{figures/stenosisShapeFlux04.tikz}}
-%  \scalebox{0.5}{\input{figures/stenosisShapeTension06.tikz}}
-%  \scalebox{0.5}{\input{figures/stenosisShapeFlux08.tikz}}
-%  \scalebox{0.5}{\input{figures/stenosisShapeTension10.tikz}}
-%  \scalebox{0.5}{\input{figures/stenosisShapeFlux12.tikz}}
-%  \fi
-  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeTension02.pdf}
-  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeFlux04.pdf}
-  \\
-  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeTension06.pdf}
-  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeFlux08.pdf}
-  \\
-  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeTension10.pdf}
-  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeFlux12.pdf}
-  \caption{\label{fig:stenosisShape} An impermeable (dashed) and
-  semi-permeable (solid) vesicle in a stenosed geometry (black).
-  The vesicles' initial configuration are identical with reduced area
-  $\nu = 0.65$. The color denotes the vesicles' tension (left) and flux
-  (right). The semi-permeable vesicle deflates throughout the
-  constriction (see Figure~\ref{fig:stenosisArea}) and develops higher
-  curvature regions than its impermeable counterpart.}
-\end{figure}
-
-\begin{figure}[htp]
-  \centering
-%  \ifTikz
-%  \scalebox{0.5}{\input{figures/stenosisTension12.tikz}}
-%  \scalebox{0.5}{\input{figures/stenosisFlux12.tikz}}
-%  \scalebox{0.5}{\input{figures/stenosisXvelocity12.tikz}}
-%  \scalebox{0.5}{\input{figures/stenosisYvelocity12.tikz}}
-%  \fi
-  \includegraphics[width=0.45\linewidth]{figures/stenosisTension12.pdf}
-  \includegraphics[width=0.45\linewidth]{figures/stenosisFlux12.pdf} \\
-  \includegraphics[width=0.45\linewidth]{figures/stenosisXvelocity12.pdf}
-  \includegraphics[width=0.45\linewidth]{figures/stenosisYvelocity12.pdf}
-  \caption{\label{fig:stenosisTensionAndFlux} The tension (top left), 
-  flux (top right), $x$-velocity (bottom left), and $y$-velocity (bottom
-  right) of the semi-permeable (red) and impermeable (dashed blue)
-  vesicles in Figure~\ref{fig:stenosisShape} at location $x=50$. The
-  point $\theta=0$ corresponds to the right-most point of the vesicle.}
-\end{figure}
-
-\begin{figure}[htp]
-  \centering
-%  \ifTikz
-%  \input{figures/stenosisArea.tikz}
-%  \fi
-  \includegraphics[width=0.8\linewidth]{figures/stenosisArea}
-  \caption{\label{fig:stenosisArea} The area of a stenosed
-  semi-permeable vesicle, with permeability rate $\beta=10^{-3}$. The
-  $x$-axis is the $x$-coordinate of the center of mass of the vesicle.
-  The vesicle loses fluid at a constant rate throughout the constriction
-  that is between $\pm 60$. The semi-permeable vesicle loses 12.8\% of
-  its fluid.}
-\end{figure}
-
-\begin{figure}[htp]
-%  \ifTikz
-%  \input{figures/stenosisBL.tikz}
-%  \fi
-  \includegraphics[width=\linewidth]{figures/stenosisBL.pdf}
-  \caption{\label{fig:stenosisBL} A stenosed semi-impermeable (red) and
-  imperemable (blue) vesicle. The semi-permeable vesicle has 
-  reduced area 0.17, and both vesicles were initialized with reduce area
-  $0.20$. The bottom plot shows the velocity relative to the vesicle
-  inside the lubrication layer.  The vesicle velocity in the square is
-  nearly constant (see Figure~\ref{fig:stenosisRA020Velocity}.}
-\end{figure}
-
-\begin{figure}[htp]
-  \centering
-%  \ifTikz
-%  \scalebox{0.5}{\input{figures/stenosisXvelocityRA020.tikz}}
-%  \scalebox{0.5}{\input{figures/stenosisYvelocityRA020.tikz}}
-%  \fi
-  \includegraphics[width=0.45\linewidth]{figures/stenosisXvelocityRA020.pdf}
-  \includegraphics[width=0.45\linewidth]{figures/stenosisYvelocityRA020.pdf}
-  \caption{\label{fig:stenosisRA020Velocity} The $x$ (left) and $y$
-  (right) velocities of the vesicle in Figure~\ref{fig:stenosisBL}. The
-  red lines correspond to the semi-permeable vesicle and the blue dashed
-  lines correspond to the impermeable vesicle.}
-\end{figure}
-
-Inspired by an experiment that measures the effects of cells on 
-dynamical pressure-drop variations along a micrometer-sized
-channel~\cite{abk-fai-sto2006}, we consider a numerical experiment where
-a semi-permeable vesicle passes through a constriction. We also measure
-the pressure-drop variation by measuring the pressure at the inlet and
-outlet of the constriction.
-
-In each experiment, we initialize an elliptical vesicle with longest
-diameter of 9$\mu$m. We use a length scale of $R_0 = 10^{-6}$m, a
-bending stiffness of $k_b = 10^{-19}$J, and fluid viscosity of $\mu=5
-\times 10^{-2}$kg/ms. Using the relaxation time scale $\tau = \mu
-R_0^3/k_b = 5 \times 10^{-1}$s, the pressure scale is $P = k_b/R_0^3 =
-10^{-1}$Pa. The geometry is similar to an
-experiment~\cite{abk-fai-sto2006} where the membrane starts in a channel
-with diameter $25\mu$m and passes into a channel with length $45\mu$m
-and diameter $5\mu$m (Figure~\ref{fig:stenosisGeom}. We impose a
-Poiseuille flow at an inlet and outlet and a no-slip boundary condition
-on the upper and lower walls. The flow rate is chosen so that the
-residency time of the vesicle in the constriction agrees with the
-experimental results.
-
-\begin{figure}[htp]
-%  \ifTikz
-%  \input{figures/stenosisGeom.tikz}
-%  \fi
-  \includegraphics[width=\linewidth]{figures/stenosisGeom.pdf}
-  \caption{\label{fig:stenosisGeom} A single semi-permeable vesicle
-  passing through a constriction. The geometry and parameters are chosen
-  to replicate the experiments of Abkarian et
-  al.~\cite{abk-fai-sto2006}.}
-\end{figure}
-
-\begin{figure}[htp]
-%  \ifTikz
-%  \input{figures/stenosisPressureFluctuation.tikz}
-%  \fi
-  \includegraphics[width=\linewidth]{figures/stenosisPressureFluctuation.pdf}
-  \caption{\label{fig:stenosisPressure} The excess pressure across the
-  constriction in Figure~\ref{fig:stenosisGeom}. The black dashed lines
-  denote the start and end of the constriction. The results are
-  qualitative agreement with~\cite{abk-fai-sto2006}.}
-\end{figure}
+We consider the effect of stenosis on a semi-permeable vesicle. Inspired
+by an experiment that measures the effects of cells on the dynamical
+pressure-drop variations along a micrometer-sized
+channel~\cite{abk-fai-sto2006}, we first examining the effect of
+semi-permeability on the pressure fluctuation across a stenosed
+geometry. In this experiment, a pressure drop is used to pass a vesicle
+red blood cell (RBC) through a constriction with diameter $5\mu$m and
+length $45\mu$m. We set up a similar computational geometry with a
+Poiseuille flow imposed at the inlet and outlet
+(Figure~\ref{fig:stenosisComposite}(a)). The flow rate is chosen so that
+the residency time of the RBC in the constriction agrees with the
+experimental results. When the RBC enters the constriction, the result
+is an increase in the pressure drop required to maintain a constant flow
+rate, and the difference between these pressures is called the excess
+pressure. We consider both an impermeable and semi-permeable vesicle
+with initial reduced area $\nu = 0.65$ passing through a constricted
+geometry and compute the pressure drop between the inlet and outlet of
+the constriction. In Figure~\ref{fig:stenosisComposite}(c), we plot the
+excess pressures. The impermeable case agrees with experimental
+results~\cite{abk-fai-sto2006} (see Figure 3), and the results indicate
+that less pressure is required to maintain a constant flow rate when the
+vesicle is semi-permeable. Our simulations indicate the
+semi-permeability does affect the excess pressure, and the vesicle's
+reduced area reduces by about 6.1\%
+(Figure~\ref{fig:stenosisComposite}(d)). Since the area does decrease at
+a constant rate we expect that a larger amounts of deflation is possible
+if the vesicle is stenosed for a longer period of time. Therefore, in
+Figure~\ref{fig:stenosisComposite}(b), we consider a vesicle passing
+through a much longer constriction, and we observe that the reduced area
+decreases by 13.2\% (Figure~\ref{fig:stenosisComposite}(e)).
+
+\begin{figure*}[htp]
+  \ifTikz
+  \input{figures/stenosisComposite.tikz}
+  \fi
+  \caption{\label{fig:stenosisComposite} (a) A semi-permeable vesicle
+  passing through a constricted geometry similar to the experimental
+  device in~\cite{abk-fai-sto2006}. (b) A semi-permeable vesicle passing
+  through a constricted geometry that is over five times longer. (c) The
+  excess pressure of an impermeable and semi-permeable vesicle in the
+  short geometry in (a). (d) The reduced area of the semi-permeable
+  vesicle in the short geometry in (a). (e) The reduced area of the
+  semi-permeable vesicle in the long geometry in (b). In parts (c), (d),
+  and (e), the horizontal axis is the x-coordinate of the vesicle's
+  center of mass.}
+\end{figure*}
+
+%
+%\begin{figure}[htp]
+%%  \ifTikz
+%%  \input{figures/stenosisGeom.tikz}
+%%  \fi
+%  \includegraphics[width=\linewidth]{figures/stenosisGeom.pdf}
+%  \caption{\label{fig:stenosisGeom} A single semi-permeable vesicle
+%  passing through a constriction. The geometry and parameters are chosen
+%  to replicate the experiments of Abkarian et
+%  al.~\cite{abk-fai-sto2006}.}
+%\end{figure}
+%
+%\begin{figure}[htp]
+%%  \ifTikz
+%%  \input{figures/stenosisPressureFluctuation.tikz}
+%%  \fi
+%  \includegraphics[width=\linewidth]{figures/stenosisPressureFluctuation.pdf}
+%  \caption{\label{fig:stenosisPressure} The excess pressure across the
+%  constriction in Figure~\ref{fig:stenosisGeom}. The black dashed lines
+%  denote the start and end of the constriction. The results are
+%  qualitative agreement with~\cite{abk-fai-sto2006}.}
+%\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Semi-Permeable Vesicle in a Contracting Geometry}
 
@@
 \end{document}
+
+% OLD TEXT AND PLOTS FROM THE NUMERICAL EXAMPLES
+
+%We plot the area of a vesicle with six different permeability rates in
+%Figure~\ref{fig:ellipseArea}. The area is computed directly from the
+%vesicle shape and the time axis is scaled by $\beta$. The plot verifies
+%that the time for the vesicle to reach a circular shape is proportional
+%to $\beta^{-1}$. We also solve~\eqref{eqn:areaROC} for the $\beta=10$
+%simulation and superimpose its solution with dots on
+%Figure~\ref{fig:ellipseArea}.
+
+%\begin{figure}[htp]
+%  \centering
+%%  \ifTikz
+%%  \input{figures/ellipseArea.tikz}
+%%  \fi
+%  \includegraphics[width=0.9\linewidth]{figures/ellipseArea}
+%  \caption{\label{fig:ellipseArea} The area of an elliptical
+%  semi-permeable vesicle, with permeability rate $\beta$ in a quiescent
+%  flow. The time axis is scaled by the permeability rate $\beta$. Since
+%  the curves collapse to a single curve, the permeability rate $\beta$
+%  sets a relaxation time scale.}
+%\end{figure}
+
+%We further analyze the transient dynamics by considering the vesicle
+%velocity~\eqref{eqn:vesVelocity} for small $\beta$. Two terms contribute
+%to the vesicle velocity: (i) the permeability velocity, $\beta(\ff \cdot
+%\nn)\nn$, and (ii) the force balance velocity, $\SS[\ff]$. Since $\beta
+%\ll 1$, the permeability velocity is much smaller than the force balance
+%velocity at early times, and the semi-permeable vesicle dynamics
+%resembles those of an impermeable vesicle. As the force balance velocity
+%decreases, the permeability velocity becomes significant, and the
+%vesicle begins to inflate to a circle. This results in the membrane
+%force and velocity both converging to zero. Letting $\beta = 10^{-3}$,
+%the normal component of the force balance velocity (blue) and the
+%permeability velocity (red) are plotted at three times in
+%Figure~\ref{fig:vesVelocity}. We also plot the velocity (green) of an
+%identically initialized impermeable vesicle. At the early time $t=0.5$,
+%the permeability velocity is negligible relative to the force balance
+%velocity, and the force balance velocity matches with the impermeable
+%vesicle velocity. At intermediate time $t=5$, all three velocities are
+%comparable in size, and the semi-permeable vesicle begins to inflate.
+%Finally, at time $t=50$, the impermeable vesicle is near steady state,
+%while the semi-permeable vesicle is still inflating. The right-most
+%plot of Figure~\ref{fig:vesVelocity} is the maximum norm of the
+%different velocity contributions as a function of time, and the black
+%vertical lines correspond to the times reported in the other three
+%subplots.
+%
+%\begin{figure*}[htp]
+%  \centering
+%%  \scalebox{0.6}{\input{figures/ellipseVelocity1.tikz}}
+%%  \scalebox{0.6}{\input{figures/ellipseVelocity2.tikz}}
+%%  \scalebox{0.6}{\input{figures/ellipseVelocity3.tikz}}
+%%  \scalebox{0.6}{\input{figures/ellipseVelocity4.tikz}}
+%%  \input{figures/ellipseVelocityNorms.tikz}
+%  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity1.pdf}
+%  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity2.pdf}
+%  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity3.pdf}
+%  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity4.pdf}
+%  \caption{\label{fig:vesVelocity} The normal velocity contributions due
+%  to force balance (blue) and permeability (red). The green line is the
+%  velocity of an impermeable vesicle with the same initial shape as the
+%  semi-permeable vesicle.}
+%\end{figure*}
+
+%We next investigate the interplay between the tension, transmembrane
+%flux, and curvature of a semi-permeable vesicle. We let $\beta = 1$ and
+%initialize the vesicle with regions of both positive and negative
+%curvature. The vesicle tension, $\Lambda$, and the flux, $\ff \cdot
+%\nn$, are plotted in Figure~\ref{fig:starTensionFlux}. At early times,
+%regions of large negative curvature have negative tension and regions
+%with large positive curvature have positive tension, and the same result
+%holds for an impermeable vesicle. In addition, regions with large
+%curvature have a large inflow of fluid (positive flux), while the
+%flatter regions have an outflow of fluid. At these early times, the net
+%effect is vesicle deflation. As the vesicle shape relaxes, the same
+%general tension and flux trends persist, but the net flux is positive
+%and the vesicle inflates. At later times, the tension becomes positive
+%and the vesicle continues to inflate towards a circle. Finally, the
+%tension transitions to a positive constant function, the membrane force
+%and flux approach zero, and the vesicle shape reaches its steady
+%circular shape.
+
+%\begin{figure*}[htp]
+%  \centering
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
+%
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
+%
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
+%
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
+%
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime5.pdf}
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
+%
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime6.pdf}
+%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime6.pdf}
+%  \caption{\label{fig:starTensionFlux} The vesicle tension (left) and
+%  flux (right) of the semi-permeable vesicle in a quiescent flow with
+%  $\beta=1$.}
+%\end{figure*}
+
+%\begin{figure*}[htp]
+%  \centering
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime5.pdf}
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime6.pdf}
+%
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
+%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime6.pdf}
+%  \caption{\label{fig:starTensionFlux} The vesicle tension (top) and
+%  flux (bottom) of the semi-permeable vesicle in a quiescent
+%  flow with $\beta=1$.}
+%\end{figure*}
+
+%\begin{figure}[htp]
+%  \centering
+%  \ifTikz
+%  \input{figures/shearSS.tikz}
+%  \fi
+%%  \includegraphics[width=0.9\linewidth]{figures/shearSS.pdf}
+%  \caption{\label{fig:shearSS} The reduced area of a semi-permeable
+%  vesicle in a shear flow. The final reduced area is nearly independent
+%  of the initial reduced area.}
+%\end{figure}
+
+%\begin{figure}[htp]
+%  \centering
+%  %\ifTikz
+%  \input{figures/shearPhaseDiagramRA2.tikz}
+%  %\fi
+%%  \includegraphics[width=\linewidth]{figures/shearPhaseDiagramRA2.pdf}
+%  \caption{\label{fig:shearPhaseDiagram} The steady state shape of a
+%  semi-permeable vesicle with several different permeability rates
+%  $\beta$ and shear rates $\dot{\gamma}$. The final reduced areas are
+%  reported for the largest and smallest parameter values. The final
+%  reduced area decreases with the flow rate, while the permeability rate
+%  has a very small effect on the steady state shape.}
+%\end{figure}
+
+%\begin{figure}[htp]
+%%  \ifTikz
+%%  \input{figures/parabolicOffCenterPhaseImpermeable.tikz}
+%%  \fi
+%  \includegraphics[width=0.9\linewidth]{figures/parabolicOffCenterPhaseImpermeable.pdf}
+%  \caption{\label{fig:parabolicOffCenterImpermeablePhaseDiagram} Phase
+%  diagram of an impermeable vesicle with several different flow rates
+%  $U$ and reduced areas $\nu$. As shown by Kaoui et
+%  al.~\cite{kao-bir-mis2009}, the final vesicle shape is either an
+%  axisymmetric parachute or bullet (pink region) or an asymmetric
+%  slipper (yellow region).}
+%\end{figure}
+
+%\begin{figure}[htp]
+%%  \ifTikz
+%%  \input{figures/parabolicOffCenterPhaseSemipermeable.tikz}
+%%  \fi
+%  \includegraphics[width=0.9\linewidth]{figures/parabolicOffCenterPhaseSemipermeable.pdf}
+%  \caption{\label{fig:parabolicOffCenterSemipermeablePhaseDiagram} Phase
+%  diagram of a semi-permeable vesicle, with $\beta = 10^{-3}$, with
+%  several different flow rates $U$ and reduced areas $\nu$. The
+%  steady state reduced area for each flow rate, which is reported along
+%  the top of the vesicles, is nearly independent of the initial reduced
+%  area. Low flow rates result in axisymmetric vesicles with large
+%  reduced area, and high flow rates result in asymmetric vesicles with
+%  low reduced area. Results at higher flow rates are not eporeted since
+%  the vesicle self-intersects.}
+%\end{figure}
+
+%\begin{figure}[htp]
+%%  \ifTikz
+%%  \scalebox{0.5}{\input{figures/stenosisShapeTension01.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux02.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisShapeTension03.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux04.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisShapeTension05.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux06.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisShapeTension07.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux08.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisShapeTension09.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux10.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisShapeTension11.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux12.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisShapeTension02.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux04.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisShapeTension06.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux08.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisShapeTension10.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux12.tikz}}
+%%  \fi
+%  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeTension02.pdf}
+%  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeFlux04.pdf}
+%  \\
+%  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeTension06.pdf}
+%  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeFlux08.pdf}
+%  \\
+%  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeTension10.pdf}
+%  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeFlux12.pdf}
+%  \caption{\label{fig:stenosisShape} An impermeable (dashed) and
+%  semi-permeable (solid) vesicle in a stenosed geometry (black).
+%  The vesicles' initial configuration are identical with reduced area
+%  $\nu = 0.65$. The color denotes the vesicles' tension (left) and flux
+%  (right). The semi-permeable vesicle deflates throughout the
+%  constriction (see Figure~\ref{fig:stenosisArea}) and develops higher
+%  curvature regions than its impermeable counterpart.}
+%\end{figure}
+%
+%\begin{figure}[htp]
+%  \centering
+%%  \ifTikz
+%%  \scalebox{0.5}{\input{figures/stenosisTension12.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisFlux12.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisXvelocity12.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisYvelocity12.tikz}}
+%%  \fi
+%  \includegraphics[width=0.45\linewidth]{figures/stenosisTension12.pdf}
+%  \includegraphics[width=0.45\linewidth]{figures/stenosisFlux12.pdf} \\
+%  \includegraphics[width=0.45\linewidth]{figures/stenosisXvelocity12.pdf}
+%  \includegraphics[width=0.45\linewidth]{figures/stenosisYvelocity12.pdf}
+%  \caption{\label{fig:stenosisTensionAndFlux} The tension (top left), 
+%  flux (top right), $x$-velocity (bottom left), and $y$-velocity (bottom
+%  right) of the semi-permeable (red) and impermeable (dashed blue)
+%  vesicles in Figure~\ref{fig:stenosisShape} at location $x=50$. The
+%  point $\theta=0$ corresponds to the right-most point of the vesicle.}
+%\end{figure}
+%
+%\begin{figure}[htp]
+%  \centering
+%%  \ifTikz
+%%  \input{figures/stenosisArea.tikz}
+%%  \fi
+%  \includegraphics[width=0.8\linewidth]{figures/stenosisArea}
+%  \caption{\label{fig:stenosisArea} The area of a stenosed
+%  semi-permeable vesicle, with permeability rate $\beta=10^{-3}$. The
+%  $x$-axis is the $x$-coordinate of the center of mass of the vesicle.
+%  The vesicle loses fluid at a constant rate throughout the constriction
+%  that is between $\pm 60$. The semi-permeable vesicle loses 12.8\% of
+%  its fluid.}
+%\end{figure}
+%
+%
+%\begin{figure}[htp]
+%%  \ifTikz
+%%  \input{figures/stenosisBL.tikz}
+%%  \fi
+%  \includegraphics[width=\linewidth]{figures/stenosisBL.pdf}
+%  \caption{\label{fig:stenosisBL} A stenosed semi-impermeable (red) and
+%  imperemable (blue) vesicle. The semi-permeable vesicle has 
+%  reduced area 0.17, and both vesicles were initialized with reduce area
+%  $0.20$. The bottom plot shows the velocity relative to the vesicle
+%  inside the lubrication layer.  The vesicle velocity in the square is
+%  nearly constant (see Figure~\ref{fig:stenosisRA020Velocity}.}
+%\end{figure}
+%
+%
+%\begin{figure}[htp]
+%  \centering
+%%  \ifTikz
+%%  \scalebox{0.5}{\input{figures/stenosisXvelocityRA020.tikz}}
+%%  \scalebox{0.5}{\input{figures/stenosisYvelocityRA020.tikz}}
+%%  \fi
+%  \includegraphics[width=0.45\linewidth]{figures/stenosisXvelocityRA020.pdf}
+%  \includegraphics[width=0.45\linewidth]{figures/stenosisYvelocityRA020.pdf}
+%  \caption{\label{fig:stenosisRA020Velocity} The $x$ (left) and $y$
+%  (right) velocities of the vesicle in Figure~\ref{fig:stenosisBL}. The
+%  red lines correspond to the semi-permeable vesicle and the blue dashed
+%  lines correspond to the impermeable vesicle.}
+%\end{figure}
+%
+%We consider the effect of stenosis on a semi-permeable vesicle. To allow
+%for large amounts of fluid flux through the membrane, we consider
+%geometry with a long constricted region. We start by considering a
+%vesicle initialized with reduced area $\nu = 0.65$, and we compare the
+%vesicle shape when $\beta = 0$ (impermeable) and $\beta = 10^{-3}$
+%(permeable). Figure~\ref{fig:stenosisShape} shows the vesicles' shape at
+%several locations along the constriction. The colors along the left
+%channel represent the tension and those along the right represent the
+%flux. In Figure~\ref{fig:stenosisTensionAndFlux}, the tension at
+%location $x=20$ and the flux at location $x=30$ are plotted with respect
+%to arclength. The value of $\theta=0$ corresponds to the nose of the
+%vesicle.

### 2020-11-26 vesicle_code/docs/permeableVes/makefigs/shear1Ves/shearPhase2.m

@@ -104,7 +104,7 @@ chis = {'1e-1','1e-0.5','1e0','1e0.5','1e1','1e1.5','1e2'};
 
 fid = fopen('data.dat','w');
 %for j = 1:numel(file)
-for j = 1:1
+for j = 15:35
   disp(j)
   [posx,posy,~,~,~,~,~,~,n,~] = loadFile(file{j});
 % some files did not print correctly to file becuase they were either

### 2020-12-07 vesicle_code/docs/permeableVes/main.tex
edits to PNAS
yny

@@
 \affil[a]{Department of Scientific Computing, Florida State University}
-\affil[b]{Department of Mathematical Sciences, New Jeresey Institute of
+\affil[b]{Department of Mathematical Sciences, New Jeresy Institute of
 Technology}
@@
 
-\dropcap{T}his PNAS journal template is provided to help you write your
-work in the correct journal format. Instructions for use are provided
-below. We do not start with a section heading for the introduction, but
-rather type the intro starting here.
+\dropcap{W}ater balance is an essential process in the adaptation of a living cell to its environment \cite{AlbertsMolecularBiology}.  
+For example, erythrocytes demonstrate efficient exchange of water to participate in efficient body water homeostasis \cite{SugieIntaglietta2018_AmJPhysiolHCP}.
+The cell membrane is permeable to water and water-soluble molecules \cite{Dick1964_JTB,FettiplaceHaydon1980_PhysRev,DeamerBramhall1986_ChemPhysLipids,Grafmueller2019_ABLS}.
+In the presence of osmolarity (a contrast in the concentration of a solute impermeable to the membrane), water flows in or out of the membrane to adjust the interior cellular volume.
+In the red blood cell membrane, aquaporin-1 (AQP1) channels give rise to a much higher water permeability of $\sim 1.8\times 10^{-2}$ cm/s in erythrocytes \cite{YangMaVerkman2001_JBC} while for an artificial lipid bilayer membrane the water permeability is in the range of $10^{-4}-10^{-3}$ cm/s \cite{ThompsonHuang1966_ANYAS,FettiplaceHaydon1980_PhysRev,Grafmueller2019_ABLS}.
+
+ Most modeling of water transport across the membrane focuses on the water flux due to osmolarity.
+However, the osmotic flux is inevitably coupled with the mechanical effects for a deformable membrane \cite{yao-mor2017}.
 
@@
   correspond to the simulations in part (a).}
-  \todo[inline]{$\nu=0.75$ run needs more temporal resolution.}
 \end{figure*}

### 2020-12-07 vesicle_code/examples/output/makeImages.m
working on figs

@@ -7,9 +7,9 @@ options.marker = false;
 
 irate = 1; % controls the speed of the visualization
 
-if 0
+if 1
 %  file = 'parabolic1VesData.bin';
-  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/semipermeable/parabolic1Ves_speed8.00e02_RA6.00em01Data.bin';
+  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/semipermeable/parabolic1Ves_speed8.00e02_RA9.00em01Data.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/impermeable/parabolic1Ves_speed1.20e03_RA6.00em01Data.bin';
 
   ax = 1*[-2 2 -2 2];
@@ -19,7 +19,7 @@ if 0
   options.marker = true;
 end
 
-if 1
+if 0
 %file = '~/projects/brinkman/vesicle_code/results/choke1VesLong/beta1em3RA0p25/choke1VesData.bin';
 %file = '~/projects/brinkman/vesicle_code/results/choke1VesLong/beta1em3Scale1p44_kappa1e0_farfield5e2_offcenter/choke1VesData.bin';
 file = '~/Dropbox/Adhesion/PermeableV/choke1Ves/choke1VesBData.bin';
@@ -131,7 +131,7 @@ if 0
   options.confined = false;
 end
 if 0
-  file = 'shear1VesAData.bin';
+  file = 'shear1VesDData.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/shear1Ves/Chi1p0e1_ra065_beta1p0em3/shear1VesData.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/PNAS_runs/shear/Chi1p0e0_ra075_beta1p0em3/shear1VesData.bin';
   ax = [-5 5 -5 5];
@@ -223,7 +223,7 @@ for k = istart:1:iend
   [ra(k),area(k),length(k)] = oc.geomProp([posx(:,1,k);posy(:,1,k)]);
 %  incAng(k) = InclinationAngle(posx(:,1,k),posy(:,1,k));
 
-  if 0
+  if 1
     vesicle = capsules([posx(:,:,k);posy(:,:,k)],[],[],1,1);
     normal(1:end/2,:,k) = +vesicle.xt(end/2+1:end,:);
     normal(end/2+1:end,:,k) = -vesicle.xt(1:end/2,:);

### 2020-12-07 vesicle_code/docs/permeableVes/main.tex
working on figs
yny

@@
 For example, erythrocytes demonstrate efficient exchange of water to participate in efficient body water homeostasis \cite{SugieIntaglietta2018_AmJPhysiolHCP}.
+Another example is the regulation of cell volume and the cell membrane tension in cell migration \cite{SaadounPapadopoulosWatanabeEtAl2005_JCS}.
 The cell membrane is permeable to water and water-soluble molecules \cite{Dick1964_JTB,FettiplaceHaydon1980_PhysRev,DeamerBramhall1986_ChemPhysLipids,Grafmueller2019_ABLS}.
 In the presence of osmolarity (a contrast in the concentration of a solute impermeable to the membrane), water flows in or out of the membrane to adjust the interior cellular volume.
-In the red blood cell membrane, aquaporin-1 (AQP1) channels give rise to a much higher water permeability of $\sim 1.8\times 10^{-2}$ cm/s in erythrocytes \cite{YangMaVerkman2001_JBC} while for an artificial lipid bilayer membrane the water permeability is in the range of $10^{-4}-10^{-3}$ cm/s \cite{ThompsonHuang1966_ANYAS,FettiplaceHaydon1980_PhysRev,Grafmueller2019_ABLS}.
-
- Most modeling of water transport across the membrane focuses on the water flux due to osmolarity.
-However, the osmotic flux is inevitably coupled with the mechanical effects for a deformable membrane \cite{yao-mor2017}.
+In the red blood cell membrane, aquaporin-1 (AQP1) channels give rise to a much higher water permeability of $\sim 1.8\times 10^{-2}$ cm/s in erythrocytes \cite{YangMaVerkman2001_JBC} while for an artificial lipid bilayer membrane the water permeability is in the range of $10^{-4}-10^{-3}$ cm/s \cite{ThompsonHuang1966_ANYAS,FettiplaceHaydon1980_PhysRev,Grafmueller2019_ABLS,Dimova2020_GVB}.
+
+Vesicles (self-enclosed lipid bilayer membranes) have been used as a model system to study reshaping, remodeling and scission of cell membranes due to osmotic stress \cite{OgleckaEtAl2014_eLife,CamposSaric2020_bioRxiv,Dimova2020_GVB}.
+Under an osmotic shock, a vesicle may undergo oscillatory variation in its enclosed volume \cite{ChabanonHoLiedberg2017_BJ}.
+In these situations, the osmolarity is the main drive for water transport across the membrane.
+Thus most modeling works ignore the mechanical effects (capillary pressure, bending force and membrane tension) on vesicles under an osmotic stress.
+However, the osmotic water flux is inevitably coupled with the mechanical pressure jump across the membrane\cite{yao-mor2017}, which could become comparable to osmotic stress when the membrane deformation is large \cite{LiMoriSun2015_PRL,yao-mor2017}.
 

### 2020-12-08 vesicle_code/docs/permeableVes/main.tex
yny

@@
 In the presence of osmolarity (a contrast in the concentration of a solute impermeable to the membrane), water flows in or out of the membrane to adjust the interior cellular volume.
-In the red blood cell membrane, aquaporin-1 (AQP1) channels give rise to a much higher water permeability of $\sim 1.8\times 10^{-2}$ cm/s in erythrocytes \cite{YangMaVerkman2001_JBC} while for an artificial lipid bilayer membrane the water permeability is in the range of $10^{-4}-10^{-3}$ cm/s \cite{ThompsonHuang1966_ANYAS,FettiplaceHaydon1980_PhysRev,Grafmueller2019_ABLS,Dimova2020_GVB}.
+In the red blood cell membrane, aquaporin-1 (AQP1) channels give rise to a much higher water permeability of $\sim 1.8\times 10^{-2}$ cm/s in erythrocytes \cite{YangMaVerkman2001_JBC} while the intrinsic water permeability of a lipid bilayer membrane is in the range of $10^{-4}-10^{-3}$ cm/s \cite{ThompsonHuang1966_ANYAS,FettiplaceHaydon1980_PhysRev,Grafmueller2019_ABLS,Dimova2020_GVB}.
 
@@
 However, the osmotic water flux is inevitably coupled with the mechanical pressure jump across the membrane\cite{yao-mor2017}, which could become comparable to osmotic stress when the membrane deformation is large \cite{LiMoriSun2015_PRL,yao-mor2017}.
+
+The intrinsic water permeability of a lipid bilayer membrane depends on the temperature, ph value in the solvent, and the hydration  energy of the membrane.
 

### 2020-12-08 vesicle_code/docs/permeableVes/main.tex
edits to figs
working on parabolic example

@@
 \begin{figure}[htp]
-  \ifTikz
+%  \ifTikz
   \input{figures/parabolicComposite.tikz}
-  \fi
-  \caption{\label{fig:parabolicComposite} (a) The steady-state shape of
-  an impermeable vesicle submerged in a Poiseuille flow with varying
-  initial reduced areas and flow rates. The results agree with Kaoui et
-  al.~\cite{kao-bir-mis2009}. (b) The steady state shape of a
+%  \fi
+  \caption{\label{fig:parabolicComposite} (a) The steady state shape of a
   semi-permeable vesicle submerged in a Poiseuille flow with varying
-  initial reduced areas and flow rates.}
+  initial reduced areas and flow rates. (b) The steady-state inclination
+  angle for four different flow velocities. The steady-state shapes are
+  superimposed. (c) The reduced area of the slipper formed with the
+  flow rate of 800 $\mu m/s$. (d) The vesicle shape shown with the
+  background imposed flow. The channel width is 12.5 times larger than
+  the vesicle radius. The corresponding reduced area for each shape is
+  indicated by the marks in plot (c).}
 \end{figure}

### 2020-12-08 vesicle_code/docs/permeableVes/main.tex
updated shear language

@@
 $\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$ with different permeability
-rates $\beta$ and shear rates $\dot{\gamma}$. Depending on its reduced
-area and viscosity contrast, two-dimensional vesicles either tank tread
-or tumble~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. In our
-experiments, tumbling is impossible since we consider semi-permeable
-vesicles with no viscosity contrast. Similar to the dynamics of an
-impermeable vesicle, a semi-permeable vesicle tilts to an inclination
-angle and undergoes tank treading dynamics.
-
-In the quiescent flow, the steady state vesicle shape is independent of
-the initial vesicle shape, and we investigate if this is true when a
-shear flow is imposed. In Figure~\ref{fig:shearComposite}(a), using four
-initial reduced areas and two flow rates, we plot the reduced area of a
-semi-permeable vesicle with $\beta = 10^{-3}$. As we saw for the
-quiescent example, the final shape does not depend on the initial
-reduced area. However, it does depend on the flow rate. We also observe
-a very small change in the reduced area at early times with the vesicle
-dynamics at early times being similar to those of an impermeable
-vesicle.  However, once the vesicle is tank-treading, the normal
-component of the force-balance velocity is small and the permeability
-velocity dominates and leads to a changing reduced area.
-
-We also form the steady state shape for a variety of semi-permeability
-rates and flow rates. Since the final shape is independent of the
-initial reduce area, we choose an vesicle with $\nu = 0.65$ for all the
-simulations. The steady state vesicle shape, along with its reduced
-area, are in Figure~\ref{fig:shearComposite}(b). We see that the flow
+rates $\beta$ and shear rates $\dot{\gamma}$. A vesicle's reduced area
+and viscosity contrast determines whether it tank treads or
+tumbles~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. Similar to the
+dynamics of an impermeable vesicle, a semi-permeable vesicle tilts to an
+inclination angle and undergoes tank treading dynamics. Since we
+consider semi-permeable vesicles, there is no viscosity contrast and
+tumbling is not possible.
+
+In Figure~\ref{fig:shearComposite}(a), using four initial reduced areas
+and two flow rates, we plot the reduced area of a semi-permeable vesicle
+with $\beta = 10^{-3}$. As observed in a quiescent flow, the final
+vesicle shape is independent of the initial reduced area. However, it
+does depend on the flow rate. We also observe small changes in the
+reduced area at early times with the vesicle dynamics at early times
+that are similar to those of an impermeable vesicle. However, once the
+vesicle is tank-treading, the normal component of the force-balance
+velocity is small and the permeability velocity dominates and leads to a
+changing reduced area.
+
+We form the steady state shape for a variety of semi-permeability rates
+and flow rates. Since the final shape is independent of the initial
+reduce area, for all simulations we initialize the vesicle with reduced
+area $\nu = 0.65$. The steady state vesicle shape and its reduced
+area are in Figure~\ref{fig:shearComposite}(b). We see that the flow
 rate significantly affects the final vesicle shape, but the
-semi-permeability rate has no significant effect. Instead, as we saw in
-the quiescent analysis, $\beta$ sets a time scale since the time
-required for a vesicle to reach its steady state configuration is
-proportional to $\beta^{-1}$.
+semi-permeability rate has a minor effect. Instead, as we saw in the
+quiescent analysis, $\beta$ sets a time scale since the time required
+for a vesicle to reach its steady state configuration is proportional to
+$\beta^{-1}$.
 
@@
 \begin{figure}[htp]
-%  \ifTikz
+  \ifTikz
   \input{figures/parabolicComposite.tikz}
-%  \fi
+  \fi
   \caption{\label{fig:parabolicComposite} (a) The steady state shape of a

### 2020-12-09 vesicle_code/docs/permeableVes/main.tex
yny

--- 2020-12-08 vesicle_code/docs/permeableVes/main.tex
@@
 For example, erythrocytes demonstrate efficient exchange of water to participate in efficient body water homeostasis \cite{SugieIntaglietta2018_AmJPhysiolHCP}.
-Another example is the regulation of cell volume and the cell membrane tension in cell migration \cite{SaadounPapadopoulosWatanabeEtAl2005_JCS}.
+Another example is the simultaneous regulation of cell volume and the cell membrane tension during cell migration through trafficking of aquaporin proteins \cite{SaadounPapadopoulosWatanabeEtAl2005_JCS}.
+
 The cell membrane is permeable to water and water-soluble molecules \cite{Dick1964_JTB,FettiplaceHaydon1980_PhysRev,DeamerBramhall1986_ChemPhysLipids,Grafmueller2019_ABLS}.
-In the presence of osmolarity (a contrast in the concentration of a solute impermeable to the membrane), water flows in or out of the membrane to adjust the interior cellular volume.
+In the presence of an osmotic gradient across the membrane (such as a contrast in the concentration of an impermeable solute), water flows in or out of the membrane to adjust the interior cellular volume.
 In the red blood cell membrane, aquaporin-1 (AQP1) channels give rise to a much higher water permeability of $\sim 1.8\times 10^{-2}$ cm/s in erythrocytes \cite{YangMaVerkman2001_JBC} while the intrinsic water permeability of a lipid bilayer membrane is in the range of $10^{-4}-10^{-3}$ cm/s \cite{ThompsonHuang1966_ANYAS,FettiplaceHaydon1980_PhysRev,Grafmueller2019_ABLS,Dimova2020_GVB}.
@@
 Under an osmotic shock, a vesicle may undergo oscillatory variation in its enclosed volume \cite{ChabanonHoLiedberg2017_BJ}.
-In these situations, the osmolarity is the main drive for water transport across the membrane.
-Thus most modeling works ignore the mechanical effects (capillary pressure, bending force and membrane tension) on vesicles under an osmotic stress.
+In these situations, the osmotic stress is the dominant driving force for water transport across the membrane.
+Thus most modeling works ignore the mechanical effects (capillary pressure, bending force and membrane tension) on vesicles under an osmotic shock.
 However, the osmotic water flux is inevitably coupled with the mechanical pressure jump across the membrane\cite{yao-mor2017}, which could become comparable to osmotic stress when the membrane deformation is large \cite{LiMoriSun2015_PRL,yao-mor2017}.
 
-The intrinsic water permeability of a lipid bilayer membrane depends on the temperature, ph value in the solvent, and the hydration  energy of the membrane.
+Without aquaporins or other membrane channels that promotes water permeability, the intrinsic water permeability is known to depend on the temperature \cite{}, solvent ph \cite{}, and the hydration  energy of the membrane \cite{}.
+In this work we focus on the intrinsic water permeability and study the hydrodynamics of a semipermeable membrane.
+Specifically we focus on the water permeability due to jump in normal membrane traction.
 
@@
 \begin{figure}[htp]
-  \ifTikz
+%  \ifTikz
   \input{figures/parabolicComposite.tikz}
-  \fi
+%  \fi
   \caption{\label{fig:parabolicComposite} (a) The steady-state shape of

### 2020-12-09 vesicle_code/docs/permeableVes/main.tex
updating figure a little bit

@@
 \subsection*{Quiescent Flow} 
-Based on our analysis, a semi-permeable vesicle in a quiescent flow
+Our analysis indicates that a semi-permeable vesicle in a quiescent flow
 relaxes to a circle with constant tension $\Lambda = 2\pi^2/L^2$.
 Furthermore, equation~\eqref{eqn:areaROC} shows that the area change is
-proportional to $\beta$, so we expect the times for the vesicle to
-deviate from its initial reduced area and to reach its steady state to
-both be proportional to $\beta^{-1}$. This is verified by considering a
-vesicle with initial reduced area $\nu = 0.65$ and several different
-semi-permeability rates. In Table~\ref{tbl:ellipseRelaxTimes} we report
-the time, $t_\mathrm{steady}$, required for the vesicle's area to be
-within 1.3\% of its steady state reduced area, and the time,
-$t_\mathrm{inflate}$, required for the vesicle's reduced area to exceed
-1.3\% of its initial reduced area. Both times are proportional to
-$\beta^{-1}$. 
+proportional to $\beta$, and the times for the vesicle to deviate from
+its initial reduced area and to reach its steady state should both be
+proportional to $\beta^{-1}$. This is verified for a vesicle with
+initial reduced area $\nu = 0.65$ and with different semi-permeability
+rates. In Table~\ref{tbl:ellipseRelaxTimes} we report the required time,
+$t_\mathrm{steady}$, for the vesicle's reduced area to be within 1.3\%
+of its steady state reduced area, and the required time,
+$t_\mathrm{inflate}$, for the vesicle's reduced area to exceed 1.3\% of
+its initial reduced area. Both times are proportional to $\beta^{-1}$,
+and for this reason, our numerical results are reported in terms of the
+scaled time $\beta t$.
 \begin{table}[htp]
@@
 In Figure~\ref{fig:relaxationComposite}, we examine the transient
-dynamics of four vesicles $\beta = 10^{-3}$ and a variety of initial
-configurations.  First, in all cases the vesicle eventually reaches a
-circular shape of reduced area $\nu=1$. Second, we observe that even
-though the vesicle is inflating to a circle, meaning that there is a net
-flux into the vesicle, there are regions where the flux is out of the
-vesicle. These regions are denoted in blue and are only present at early
-times.  Finally, the vesicles area does not initially change by much,
-and intermediate shapes of semi-permeable vesicles resemble the shape of
-an impermeable vesicle. This can be explained by considering the two
-terms that contribute to the vesicle velocity: (i) the permeability
-velocity, $\beta(\ff \cdot \nn) \nn$, and (ii) the force balance
-velocity, $\SS[\ff]$. Since $\beta = 10^{-3}$, the permeability velocity
-is much smaller than the force balance velocity at early times, and the
-semi-permeable vesicle dynamics resembles those of an impermeable
-vesicle. As the force balance velocity decreases, the permeability
-velocity dominates, and the vesicle begins to inflate to a circle with
-no vanishing force and velocity.
+dynamics of four vesicles with $\beta = 10^{-3}$ and a variety of
+initial configurations. As expected, each vesicle eventually
+reaches a circular shape with reduced area $\nu=1$. Next, we observe
+that even though the vesicle is inflating to a circle, meaning that
+there is a net flux into the vesicle, there are regions where the flux
+is out of the vesicle. These regions are denoted in blue and are only
+present at early times. Finally, the vesicles's reduced area do not 
+change by much at early times, and intermediate shapes of semi-permeable vesicles
+resemble the shape of an impermeable vesicle. This can be explained by
+considering the two terms that contribute to the vesicle velocity: (i)
+the permeability velocity, $\beta(\ff \cdot \nn) \nn$, and (ii) the
+force balance velocity, $\SS[\ff]$. Since $\beta = 10^{-3}$, the
+permeability velocity is much smaller than the force balance velocity at
+early times, and the semi-permeable vesicle dynamics resembles those of
+an impermeable vesicle. As the force balance velocity decreases, the
+permeability velocity dominates, and the vesicle begins to inflate to a
+circle with no vanishing force and velocity.
 
@@
 \subsection*{Poiseuille Flow}
-\begin{figure}[htp]
-  \ifTikz
+\begin{figure*}[htp]
+%  \ifTikz
   \input{figures/parabolicComposite.tikz}
-  \fi
+%  \fi
   \caption{\label{fig:parabolicComposite} (a) The steady state shape of a
@@
   indicated by the marks in plot (c).}
-\end{figure}
+  \todo[inline]{shift right plot to the right and increase necessary
+  font sizes}
+\end{figure*}
 

### 2020-12-09 vesicle_code/docs/permeableVes/main.tex
yny

--- 2020-12-09 vesicle_code/docs/permeableVes/main.tex
@@
 \dropcap{W}ater balance is an essential process in the adaptation of a living cell to its environment \cite{AlbertsMolecularBiology}.
-For example, erythrocytes demonstrate efficient exchange of water to participate in efficient body water homeostasis \cite{SugieIntaglietta2018_AmJPhysiolHCP}.
+For example, erythrocytes participate in efficient body water homeostasis by regulating its exchange of water  \cite{SugieIntaglietta2018_AmJPhysiolHCP}.
 Another example is the simultaneous regulation of cell volume and the cell membrane tension during cell migration through trafficking of aquaporin proteins \cite{SaadounPapadopoulosWatanabeEtAl2005_JCS}.

### 2020-12-11 vesicle_code/docs/permeableVes/main.tex
yny

@@
 \dropcap{W}ater balance is an essential process in the adaptation of a living cell to its environment \cite{AlbertsMolecularBiology}.
-For example, erythrocytes participate in efficient body water homeostasis by regulating its exchange of water  \cite{SugieIntaglietta2018_AmJPhysiolHCP}.
-Another example is the simultaneous regulation of cell volume and the cell membrane tension during cell migration through trafficking of aquaporin proteins \cite{SaadounPapadopoulosWatanabeEtAl2005_JCS}.
+Erythrocytes are known to  participate in efficient body water homeostasis by regulating its exchange of water  \cite{YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP}.
+Cells achieve motility by simultaneously regulating their cell volume and cell membrane tension through trafficking of aquaporin proteins \cite{SaadounPapadopoulosWatanabeEtAl2005_JCS,Verkman2008_JMM,BerthaudEtAl2016_SM} and flattening of caveolae \cite{Keren2011_EurBJ}.
+Water transport in and out of cell is also found to be important to 
+active cell shape fluctuations leading to bleb formation \cite{TaloniKardashSalmanEtAl2015_PRL}.
 
 The cell membrane is permeable to water and water-soluble molecules \cite{Dick1964_JTB,FettiplaceHaydon1980_PhysRev,DeamerBramhall1986_ChemPhysLipids,Grafmueller2019_ABLS}.
-In the presence of an osmotic gradient across the membrane (such as a contrast in the concentration of an impermeable solute), water flows in or out of the membrane to adjust the interior cellular volume.
+In the presence of an osmotic gradient across the membrane (such as a contrast in the concentration of an impermeable solute), water flows in or out of the membrane to neutralize the osmotic gradient.
 In the red blood cell membrane, aquaporin-1 (AQP1) channels give rise to a much higher water permeability of $\sim 1.8\times 10^{-2}$ cm/s in erythrocytes \cite{YangMaVerkman2001_JBC} while the intrinsic water permeability of a lipid bilayer membrane is in the range of $10^{-4}-10^{-3}$ cm/s \cite{ThompsonHuang1966_ANYAS,FettiplaceHaydon1980_PhysRev,Grafmueller2019_ABLS,Dimova2020_GVB}.
@@
 
-\section*{Governing equations} \label{sc:formulate}
+\section*{Governing equations \label{sc:formulate}}
 We consider a two-dimensional semi-permeable vesicle suspended in an

### 2020-12-11 vesicle_code/docs/permeableVes/main.tex
edits to results

--- 2020-12-09 vesicle_code/docs/permeableVes/main.tex
@@
 \subsection*{Quiescent Flow} 
-Our analysis indicates that a semi-permeable vesicle in a quiescent flow
-relaxes to a circle with constant tension $\Lambda = 2\pi^2/L^2$.
-Furthermore, equation~\eqref{eqn:areaROC} shows that the area change is
-proportional to $\beta$, and the times for the vesicle to deviate from
-its initial reduced area and to reach its steady state should both be
-proportional to $\beta^{-1}$. This is verified for a vesicle with
-initial reduced area $\nu = 0.65$ and with different semi-permeability
-rates. In Table~\ref{tbl:ellipseRelaxTimes} we report the required time,
-$t_\mathrm{steady}$, for the vesicle's reduced area to be within 1.3\%
-of its steady state reduced area, and the required time,
-$t_\mathrm{inflate}$, for the vesicle's reduced area to exceed 1.3\% of
-its initial reduced area. Both times are proportional to $\beta^{-1}$,
-and for this reason, our numerical results are reported in terms of the
-scaled time $\beta t$.
+\begin{figure*}[htp]
+  \centering
+  \ifTikz
+  \input{figures/relaxationComposite.tikz}
+  \fi
+  \caption{\label{fig:relaxationComposite} (a): Snapshots of four
+  semi-permeable vesicles with $\beta = 10^{-3}$ submerged in a
+  quiescent flow. The fluid flux along the red regions is into the
+  vesicle, and the fluid flux along the blue regions is out of the
+  vesicle. In all cases, the vesicle reaches a steady state circular
+  shape. (b): The reduced area of each of the simulations. The
+  particular snapshots in (a) occur at the marks along the curve.}
+\end{figure*}
+Our analysis shows that a semi-permeable vesicle in a quiescent flow
+relaxes to a circle at a rate that is proportional to $\beta$, and the
+steady state tension is $\Lambda = 2\pi^2/L^2$. Therefore, the times for
+the vesicle to deviate from its initial reduced area and to reach its
+steady state are proportional to $\beta^{-1}$. This is verified for a
+vesicle with initial reduced area $\nu = 0.65$ and with different
+semi-permeability rates. In Table~\ref{tbl:ellipseRelaxTimes} we report
+the required time, $t_\mathrm{steady}$, for the vesicle's reduced area
+to be within 1.3\% of its steady state reduced area, and the required
+time, $t_\mathrm{inflate}$, for the vesicle's reduced area to exceed
+1.3\% of its initial reduced area. Both times are proportional to
+$\beta^{-1}$, and for this reason, our numerical results are reported in
+terms of the scaled time $\beta t$.
 \begin{table}[htp]
@@
 
-\begin{figure*}[htp]
-  \centering
-  \ifTikz
-  \input{figures/relaxationComposite.tikz}
-  \fi
-  \caption{\label{fig:relaxationComposite} (a): Snapshots of four
-  semi-permeable vesicles with $\beta = 10^{-3}$ submerged in a
-  quiescent flow. The fluid flux along the red regions is into the
-  vesicle, and the fluid flux along the blue regions is out of the
-  vesicle. In all cases, the vesicle reaches a steady-state circular
-  shape. (b): The reduced area of each of the simulations. The
-  particular snapshots in (a) occur at the marks along the curve.}
-\end{figure*}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection*{Shear Flow}
-\begin{figure*}[htp]
+\begin{figure}[htp]
   \centering
@@
   correspond to the simulations in part (a).}
-\end{figure*}
+\end{figure}
 
@@
 rates $\beta$ and shear rates $\dot{\gamma}$. A vesicle's reduced area
-and viscosity contrast determines whether it tank treads or
+and viscosity contrast determine whether it tank treads or
 tumbles~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. Similar to the
@@
 consider semi-permeable vesicles, there is no viscosity contrast and
-tumbling is not possible.
+we do not observe tumbling.
 
@@
 does depend on the flow rate. We also observe small changes in the
-reduced area at early times with the vesicle dynamics at early times
-that are similar to those of an impermeable vesicle. However, once the
-vesicle is tank-treading, the normal component of the force-balance
-velocity is small and the permeability velocity dominates and leads to a
-changing reduced area.
+reduced area at early times when the semi-permeable vesicle behaves like
+an impermeable vesicle. However, once the vesicle is tank-treading, the
+normal component of the force-balance velocity is small and the
+permeability velocity dominates and leads to a changing reduced area.
 
@@
 \begin{figure*}[htp]
-%  \ifTikz
+  \ifTikz
+  \centering
   \input{figures/parabolicComposite.tikz}
-%  \fi
-  \caption{\label{fig:parabolicComposite} (a) The steady state shape of a
-  semi-permeable vesicle submerged in a Poiseuille flow with varying
-  initial reduced areas and flow rates. (b) The steady-state inclination
-  angle for four different flow velocities. The steady-state shapes are
-  superimposed. (c) The reduced area of the slipper formed with the
-  flow rate of 800 $\mu m/s$. (d) The vesicle shape shown with the
-  background imposed flow. The channel width is 12.5 times larger than
-  the vesicle radius. The corresponding reduced area for each shape is
-  indicated by the marks in plot (c).}
-  \todo[inline]{shift right plot to the right and increase necessary
-  font sizes}
+  \fi
+  \caption{\label{fig:parabolicComposite} (a) The steady state shape of
+  a semi-permeable vesicle submerged in a Poiseuille flow with varying
+  initial reduced areas and flow rates. (b) The steady state inclination
+  angle for four different flow velocities. The steady state shapes are
+  superimposed. (c) The reduced area of the slipper formed with the flow
+  rate of 800 $\mu m/s$. (d) The vesicle shape shown with the background
+  imposed flow. The channel width is 12.5 times larger than the vesicle
+  radius. The corresponding reduced area of each vesicle is indicated by
+  the marks in plot (c).}
 \end{figure*}

### 2020-12-11 vesicle_code/docs/permeableVes/main.tex
yny

--- 2020-12-11 vesicle_code/docs/permeableVes/main.tex
@@
 The cell membrane is permeable to water and water-soluble molecules \cite{Dick1964_JTB,FettiplaceHaydon1980_PhysRev,DeamerBramhall1986_ChemPhysLipids,Grafmueller2019_ABLS}.
-In the presence of an osmotic gradient across the membrane (such as a contrast in the concentration of an impermeable solute), water flows in or out of the membrane to neutralize the osmotic gradient.
+Without aquaporins or other membrane channels that promotes water permeability, the intrinsic water permeability is known to depend on the temperature \cite{}, solvent ph \cite{}, and the hydration  energy of the membrane \cite{}.
 In the red blood cell membrane, aquaporin-1 (AQP1) channels give rise to a much higher water permeability of $\sim 1.8\times 10^{-2}$ cm/s in erythrocytes \cite{YangMaVerkman2001_JBC} while the intrinsic water permeability of a lipid bilayer membrane is in the range of $10^{-4}-10^{-3}$ cm/s \cite{ThompsonHuang1966_ANYAS,FettiplaceHaydon1980_PhysRev,Grafmueller2019_ABLS,Dimova2020_GVB}.
+
+In the presence of an osmotic gradient across the membrane (such as a contrast in the concentration of an impermeable solute), water flows against the osmotic gradient across the membrane to neutralize the osmolarity.
+The resultant swelling/shrinking of cell is inevitably coupled to changes in membrane tension and cell shape \cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL}.
+In this work we focus on the intrinsic water permeability and study the subtle balance between hydrodynamics and elasticity of a semipermeable membrane under various flowing conditions and confinement.
+Specifically we focus on the effects of intrinsic water permeability in a vesicle under stress due to flows and/or confinement.
 
@@
 However, the osmotic water flux is inevitably coupled with the mechanical pressure jump across the membrane\cite{yao-mor2017}, which could become comparable to osmotic stress when the membrane deformation is large \cite{LiMoriSun2015_PRL,yao-mor2017}.
-
-Without aquaporins or other membrane channels that promotes water permeability, the intrinsic water permeability is known to depend on the temperature \cite{}, solvent ph \cite{}, and the hydration  energy of the membrane \cite{}.
-In this work we focus on the intrinsic water permeability and study the hydrodynamics of a semipermeable membrane.
-Specifically we focus on the water permeability due to jump in normal membrane traction.
 

### 2020-12-12 vesicle_code/docs/permeableVes/main.tex
yny

@@
 % Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
+\author[a]{Bryan Quaife}
 \author[a]{Ashley Gannon}
-\author[b]{Yuan-Nan Young} 
-\author[a,1]{Bryan Quaife}
+\author[b,1]{Y.-N. Young}
 
@@
 %\equalauthors{\textsuperscript{1}A.O.(Author One) contributed equally to this work with A.T. (Author Two) (remove if not applicable).}
-\correspondingauthor{\textsuperscript{1} E-mail: bquaife\@fsu.edu}
+%\correspondingauthor{\textsuperscript{1} E-mail: bquaife\@fsu.edu}
+\correspondingauthor{\textsuperscript{1} E-mail: yyoung@njit.edu}
 
@@
 
-\dropcap{W}ater balance is an essential process in the adaptation of a living cell to its environment \cite{AlbertsMolecularBiology}.
-Erythrocytes are known to  participate in efficient body water homeostasis by regulating its exchange of water  \cite{YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP}.
+\dropcap{W}ater balance is an essential process in the adaptation of a living cell to its environment \cite{AlbertsMolecularBiology}: Erythrocytes are known to  participate in efficient body water homeostasis by regulating its exchange of water  \cite{YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP}.
 Cells achieve motility by simultaneously regulating their cell volume and cell membrane tension through trafficking of aquaporin proteins \cite{SaadounPapadopoulosWatanabeEtAl2005_JCS,Verkman2008_JMM,BerthaudEtAl2016_SM} and flattening of caveolae \cite{Keren2011_EurBJ}.
-Water transport in and out of cell is also found to be important to 
-active cell shape fluctuations leading to bleb formation \cite{TaloniKardashSalmanEtAl2015_PRL}.
+Cells also need to control water transport across the cell membrane as they activate shape fluctuations prior to the bleb formation \cite{TaloniKardashSalmanEtAl2015_PRL}.
 
 The cell membrane is permeable to water and water-soluble molecules \cite{Dick1964_JTB,FettiplaceHaydon1980_PhysRev,DeamerBramhall1986_ChemPhysLipids,Grafmueller2019_ABLS}.
-Without aquaporins or other membrane channels that promotes water permeability, the intrinsic water permeability is known to depend on the temperature \cite{}, solvent ph \cite{}, and the hydration  energy of the membrane \cite{}.
-In the red blood cell membrane, aquaporin-1 (AQP1) channels give rise to a much higher water permeability of $\sim 1.8\times 10^{-2}$ cm/s in erythrocytes \cite{YangMaVerkman2001_JBC} while the intrinsic water permeability of a lipid bilayer membrane is in the range of $10^{-4}-10^{-3}$ cm/s \cite{ThompsonHuang1966_ANYAS,FettiplaceHaydon1980_PhysRev,Grafmueller2019_ABLS,Dimova2020_GVB}.
-
-In the presence of an osmotic gradient across the membrane (such as a contrast in the concentration of an impermeable solute), water flows against the osmotic gradient across the membrane to neutralize the osmolarity.
-The resultant swelling/shrinking of cell is inevitably coupled to changes in membrane tension and cell shape \cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL}.
+In the presence of an osmotic gradient across the membrane (such as a contrast in the concentration of an impermeable solute), water flows against the osmotic gradient  to neutralize the osmolarity.
+Without aquaporins or other membrane channels that promotes water permeability, the intrinsic water permeability is known to depend on the temperature \cite{OlbrichRawiczNeedhamEtAl2000_BJ}, lipid composition \cite{OlbrichRawiczNeedhamEtAl2000_BJ}, and the hydration  energy of the membrane \cite{MarrinkBerendsen1994_JPhysChem}.
+In the red blood cell membrane, aquaporin-1 channels give rise to a much higher water permeability of $\sim 1.8\times 10^{-2}$ cm/s in erythrocytes \cite{YangMaVerkman2001_JBC} while the intrinsic water permeability of a lipid bilayer membrane is in the range of $10^{-4}-10^{-3}$ cm/s \cite{ThompsonHuang1966_ANYAS,FettiplaceHaydon1980_PhysRev,Grafmueller2019_ABLS,Dimova2020_GVB,BhatiaRobinsonDimova2020_SoftMatt}.
+
+The swelling/shrinking of a cell is inevitably coupled to changes in membrane tension and cell shape \cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL}.  
+Most studies focus on the osmolarity-induced water flux, while mechanical pressure may also contribute to the permeable water flow \cite{yao-mor2017}.
+%The response of a cell to an osmotic gradient is inevitably both mechanical (tension redistribution and shape change) and chemical (water flux across the membrane).  
 In this work we focus on the intrinsic water permeability and study the subtle balance between hydrodynamics and elasticity of a semipermeable membrane under various flowing conditions and confinement.
@@
 
-Vesicles (self-enclosed lipid bilayer membranes) have been used as a model system to study reshaping, remodeling and scission of cell membranes due to osmotic stress \cite{OgleckaEtAl2014_eLife,CamposSaric2020_bioRxiv,Dimova2020_GVB}.
+Vesicles (self-enclosed lipid bilayer membranes) have been used as a model system to study reshaping, remodeling and scission of cell membranes due to osmotic stress \cite{OgleckaEtAl2014_eLife,CamposSaric2020_bioRxiv,Dimova2020_GVB,BhatiaChrist2020_SoftMatt}.
 Under an osmotic shock, a vesicle may undergo oscillatory variation in its enclosed volume \cite{ChabanonHoLiedberg2017_BJ}.
-In these situations, the osmotic stress is the dominant driving force for water transport across the membrane.
-Thus most modeling works ignore the mechanical effects (capillary pressure, bending force and membrane tension) on vesicles under an osmotic shock.
-However, the osmotic water flux is inevitably coupled with the mechanical pressure jump across the membrane\cite{yao-mor2017}, which could become comparable to osmotic stress when the membrane deformation is large \cite{LiMoriSun2015_PRL,yao-mor2017}.
-
-\paragraph{Literature to maybe cite}
-\cite{ali-ovr-ran2020} show how beading can occur on nanotubes. This
-happens in regions where proteins congregate and this can lead to
-semi-permeability?
-
-\section*{Governing equations \label{sc:formulate}}
-We consider a two-dimensional semi-permeable vesicle suspended in an
-unbounded viscous fluid driven by the imposed flow $\uu_\infty(\xx)$.
-Since fluid is transported across the semi-permeable vesicle membrane,
-we only consider fluids with uniform viscosity. Letting $\gamma$ be the
-vesicle interface, the fluid velocity $\uu$ and pressure $p$ satisfy
-%
-\begin{alignat}{3}
-  \label{eqn:governing}
-  -\nabla p + \mu \triangle \uu &= 0, \quad
-  \nabla \cdot \uu = 0, \qquad &&\xx \in \RR^2 \setminus \gamma, \\
-%
-  \uu(\xx) &\rightarrow \uu_\infty(\xx),
-    &&\norm{\xx} \rightarrow \infty,
-\end{alignat}
-where $\mu$ is the fluid viscosity. Letting $\nn$ be the outward normal
-to $\gamma$, $\jump{\cdot}$ be the jump across the interface, and $T$ be
-the hydrodynamic stress tensor, the interfacial boundary conditions are
-\begin{align}
-  \label{eqn:jump}
-  \jump{T\cdot\nn} = \ff_\mathrm{mem}, \quad \jump{\uu} = 0,
-\end{align}
-where $\ff_\mathrm{mem}$ is the membrane force that results from the
-Helfrich energy with bending modulus $k_b$, and a tension term that acts
-as a Lagrange multiplier to satisfy the local inextensibility condition.
-Following~\cite{vee-gue-zor-bir2009}, we modify the bending tension and
-forces as
-$\ff_\mathrm{mem} = \ff_\mathrm{ben} +
-\ff_\mathrm{ten}$, where
-\begin{align}
-  \label{eqn:membraneForces}
-  \ff_\mathrm{ben} = -k_b \xx_{ssss}, \qquad
-  \ff_\mathrm{ten} = (\sigma \xx_s)_s.
-\end{align}
-The physical tension is $\Lambda = \sigma + 1.5 \kappa^2$, where
-$\kappa$ is the membrane curvature.
-
-Semi-permeability is introduced by modifying the vesicle velocity from
-the standard choice. Instead of using the no-slip boundary condition, we
-assume the fluid flux through the boundary is proportional to the
-mechanical force~\cite{yao-mor2017}. That is, 
-\begin{align}
-  \label{eqn:vesicleFlux}
-  \uu - \dot{\xx} = - \beta (\ff_\mathrm{mem} \cdot \nn) \nn, \qquad
-  \xx \in \gamma,
-\end{align}
-where $\beta$ is the semi-permeability rate.
-
+When trapped in a microfluidic channel, an osmotic shock induces
+ vesicle shape changes, tank-treading and tumbling motions \cite{BhatiaRobinsonDimova2020_SoftMatt,BhatiaChrist2020_SoftMatt}, an illustration that the permeable water flow is inevitably coupled with the mechanical pressure jump across the membrane\cite{yao-mor2017}, which could become comparable to osmotic stress when the membrane deformation is large \cite{LiMoriSun2015_PRL,yao-mor2017}.
+In this work we use numerical simulations to examine the hydrodynamics of a semipermeable vesicle in two dimensions.
+Focusing on the effects of water permeability on the hydrodynamics of a vesicle under mechanical stresses, we investigate how a semipermeable vesicle may behave differently from their impermeable counterpart in familiar situations such as shear flows, a stenosis channel, and a contracting channel.
+
+%
+%\paragraph{Literature to maybe cite}
+%\cite{ali-ovr-ran2020} show how beading can occur on nanotubes. This
+%happens in regions where proteins congregate and this can lead to
+%semi-permeability?
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Integral equation formulation}
-Since the fluid satisfies the Stokes equations, it can be represented as
-layer potential. Given the interfacial boundary
-conditions~\eqref{eqn:jump}, the fluid velocity is
-\begin{align}
-  \uu(\xx) = \uu_\infty(\xx) + \SS[\ff_\mathrm{mem}](\xx), \quad
-    \xx \in \Omega,
-\end{align}
-where $\SS$ is the single-layer potential
-\begin{align}
-  \SS[\ff](\xx) = \frac{1}{4\pi\mu} \int_{\gamma} \left(
-    -\mathbf{I} \log\rho + \frac{\rr \otimes \rr}{\rho^2} \right)
-    \ff(\yy) ds_{\yy},
-\end{align}
-with $\rr = \xx - \yy$ and $\rho = \norm{\rr}$. Imposing the flux
-condition~\eqref{eqn:vesicleFlux} and the inextensibility condition, the
-vesicle velocity satisfies
-\begin{align}
-  \label{eqn:vesVelocity}
-  \dot{\xx} &= \uu_\infty(\xx) + \beta (\ff_\mathrm{mem}\cdot\nn)\nn
-  + \SS [\ff_\mathrm{mem}](\xx),  \quad
-  \xx_s \cdot \dot{\xx}_s = 0.
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Dimensionless equations}
-The inextensibility condition guarantees that the vesicle's length, $L$,
-is conserved, while its area, $A$, can change due to semi-permeability.
-Therefore, the reduced area $\nu = 4\pi A/L^2 \in (0,1]$ is not
-conserved. We non-dimensionalize~\eqref{eqn:vesVelocity} by introducing
-the length scale $R_0 = L/2\pi$ and defining the time scale $\tau = \mu
-R_0^3/k_b$, the tension scale $Q = k_b/R_0^2$, and the permeability
-scale $W = R_0/\mu$. The background velocity $\uu_\infty$ is
-non-dimensionalized with $R_0/\tau$.
-
-\todo[inline]{This is a dump of information regarding how we
-non-dimensionalize}
-In each experiment, we initialize an elliptical vesicle with longest
-diameter of 9$\mu$m. We use a length scale of $R_0 = 10^{-6}$m, a
-bending stiffness of $k_b = 10^{-19}$J, and fluid viscosity of $\mu=5
-\times 10^{-2}$kg/ms. Using the relaxation time scale $\tau = \mu
-R_0^3/k_b = 5 \times 10^{-1}$s, the pressure scale is $P = k_b/R_0^3 =
-10^{-1}$Pa.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Area dynamics}
-Following the analysis of Veerapaneni et al.~\cite{vee-raj-bir-pur2009},
-we compute the steady state shape of a semi-permeable vesicle in a
-quiescent flow. The steady state shape is a stationary point of the
-Lagrangian
-\begin{align}
-  \mathcal{L} = \frac{1}{2}\int_{\gamma} \kappa^2 \, ds +
-    \Lambda \left(\int_{\gamma} ds  - L \right),
-\end{align}
-where the Lagrange multiplier $\Lambda$ is the tension. Note the absence
-of the pressure Lagrange multiplier since the vesicle's area fluctuates.
-Taking the variation of $\mathcal{L}$ with respect to $\gamma$ and
-setting it to zero, the steady state shape satisfies $\kappa_{ss} +
-\frac{1}{2}\kappa^3 - \Lambda \kappa = 0$, with initial conditions
-$\kappa(0) = \kappa_0$ and $\kappa_s(0) = 0$.  Integrating once, we have
-\begin{align}
-  \frac{\kappa_s^2}{2} + \frac{\kappa^4}{8} - 
-    \frac{\Lambda}{2}\kappa^2 = \frac{\kappa_0^4}{8} - 
-    \frac{\Lambda}{2}\kappa_0^2.
-  \label{eqn:curveODE}
-\end{align}
-Assuming $\kappa_s \neq 0$,~\eqref{eqn:curveODE} is separable, and can
-be solved analytically in terms of the {\em EllipticF} function using
-Mathematica. Unlike in the impermeable case~\cite{vee-raj-bir-pur2009},
-the solution of~\eqref{eqn:curveODE} is not periodic unless $\kappa(s) =
-\kappa_0$. Therefore, the steady state shape of a semi-permeable vesicle
-in a quiescent flow is a circle with radius $L/2\pi$. Therefore, the
-steady state curvature and tension are
-\begin{align}
-  \kappa = \frac{2\pi}{L}, \: \Lambda = \frac{2\pi^2}{L^2}.
-  \label{eqn:SSshape}
-\end{align}
-Note that in contrast to a impermeable vesicle, the tension is positive
-rather than negative.
-
-We also compute the transient area of the vesicle. Since the area of the
-vesicle is
-\begin{align}
-  A(t) = \frac{1}{2}\int_{\gamma} (\xx \cdot \nn)\, ds,
-  \label{eqn:area}
-\end{align}
-its derivative includes terms due to the time derivative of $\xx \cdot
-\nn$ and a term due to interface stretching~\cite{lai-tse-hua2008}, but
-this latter term term is zero because of the local inextensibility
-condition. Therefore,
-\begin{align}
-  \dot{A}(t) =
-  \frac{1}{2} \int_{\gamma} (\dot{\xx} \cdot \nn)\, ds  + 
-  \frac{1}{2} \int_{\gamma} (\xx \cdot \dot{\nn})\, ds.
-\end{align}
-Applying integration by parts, the two integrals agree, and we have
-%\begin{align}
-%  \int_\gamma (\xx \cdot \dot{\nn})\, ds 
-%    = \int_\gamma \left(\xx \cdot \dot{\xx}_s^\perp \right)
-%    = -\int_\gamma \left(\xx^\perp \cdot \dot{\xx}_s\right)\, ds 
-%    = \int_\gamma \left(\xx_s^\perp \cdot \dot{\xx}\right)\, ds 
-%    = \int_\gamma (\dot{\xx} \cdot \nn)\, ds.
-%\end{align}
-\begin{align}
-  \dot{A}(t) = \int_\gamma \left(\beta (\ff \cdot \nn)\nn 
-    + \SS[\ff]\right) \cdot \nn\, ds 
-  = \beta \int_\gamma (\ff \cdot \nn)\, ds,
-\end{align}
-where we have used the incompressibility of the single-layer potential.
-Repeatedly applying integration by parts, we have
-\begin{align}
-  \dot{A}(t) &= \beta \int_\gamma \left( -\xx_{ssss} + 
-    (\sigma \xx_s)_s \right) \cdot \nn \, ds \\
-  &= -\beta \int_\gamma \left(-\xx_{sss} + \sigma \xx_s 
-    \right) \cdot \kappa \xx_s \, ds \\
-  &= -\beta \int_\gamma \left(\xx_{ss} \cdot 
-    (\kappa \xx_s)_s + \kappa \sigma \right) \, ds \\
-  &= -\beta \int_\gamma \left(\kappa (\xx_{ss} \cdot \xx_{ss}) + 
-    \kappa_s (\xx_{ss} \cdot \xx_s) + \kappa \sigma \right) 
-    \, ds \\
-  &= -\beta \int_\gamma \left(\kappa^3 + \kappa \sigma \right) 
-    \, ds = \beta \int_\gamma \left(
-    \frac{\kappa^3}{2} - \kappa \Lambda \right) \, ds.
-  \label{eqn:areaROC}
-\end{align}
-Note that~\eqref{eqn:SSshape} and are consistent since the constant
-curvature and tension values cause the integrand to vanish.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Numerical Methods}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Discretization in Space}
-By using a boundary integral equation formulation, the unknowns are the
-vesicle's position and tension that we track at $N$ discretization
-points. Derivatives are computed with Fourier differentiation, and the
-eighth-order quadrature~\cite{alp1999} is applied to the single-layer
-potential. For constricted flows, nearly-singular integrals are computed
-with an interpolation-based quadrature rule~\cite{qua-bir2014}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Discretization in Time}
-To eliminate stringent time step restrictions, we modify a time stepping
-method that discretizes high-order derivatives
-semi-implicitly~\cite{vee-gue-zor-bir2009}. We introduce the notation
-\begin{alignat}{3}
-  &B[\xx]\ff = -\frac{d^4}{ds^4} \ff,  \qquad
-  &&T[\xx]\sigma = (\sigma \xx_s)_s, \\
-  &D[\xx]\ff = \xx_s \cdot \ff_s, 
-  &&P[\xx]\ff = (\ff \cdot \nn) \nn,
-\end{alignat}
-for the differential and projection operators. Letting $B^N$ be the
-bending operator due to the vesicle configuration at time $t^N$, and
-similar notation for the other operators, we use the first-order
-semi-implicit time stepping method
-\begin{alignat}{3}  
-  \frac{\xx^{N+1} - \xx^N}{\Delta t} &= \uu_\infty(\xx^N) 
-  &&+ \beta P^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right) \nonumber \\
-  & &&+ \SS^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right), 
-\end{alignat}
-and  the inextensibility condition is discretized as
-\begin{align}
-  D^N\xx^{N+1} &= 1.
-\end{align}
-To achieve second-order accuracy over long time horizons, we modify an
-adaptive spectral deferred correction time stepping
-method~\cite{qua-bir2016}. Since the area of the vesicle is not
-conserved, we only use the length of the vesicle to estimate the error
-which determines if a time step is accepted or not and determines the
-subsequent time step size.
+\section*{Formulation}
 
@@
 
+\section*{Supplementary Material: Formulation \label{sc:formulate}}
+We consider a two-dimensional semi-permeable vesicle suspended in an
+unbounded viscous fluid driven by the imposed flow $\uu_\infty(\xx)$.
+Since fluid is transported across the semi-permeable vesicle membrane,
+we only consider fluids with uniform viscosity. Letting $\gamma$ be the
+vesicle interface, the fluid velocity $\uu$ and pressure $p$ satisfy
+%
+\begin{alignat}{3}
+  \label{eqn:governing}
+  -\nabla p + \mu \triangle \uu &= 0, \quad
+  \nabla \cdot \uu = 0, \qquad &&\xx \in \RR^2 \setminus \gamma, \\
+%
+  \uu(\xx) &\rightarrow \uu_\infty(\xx),
+    &&\norm{\xx} \rightarrow \infty,
+\end{alignat}
+where $\mu$ is the fluid viscosity. Letting $\nn$ be the outward normal
+to $\gamma$, $\jump{\cdot}$ be the jump across the interface, and $T$ be
+the hydrodynamic stress tensor, the interfacial boundary conditions are
+\begin{align}
+  \label{eqn:jump}
+  \jump{T\cdot\nn} = \ff_\mathrm{mem}, \quad \jump{\uu} = 0,
+\end{align}
+where $\ff_\mathrm{mem}$ is the membrane force that results from the
+Helfrich energy with bending modulus $k_b$, and a tension term that acts
+as a Lagrange multiplier to satisfy the local inextensibility condition.
+Following~\cite{vee-gue-zor-bir2009}, we modify the bending tension and
+forces as
+$\ff_\mathrm{mem} = \ff_\mathrm{ben} +
+\ff_\mathrm{ten}$, where
+\begin{align}
+  \label{eqn:membraneForces}
+  \ff_\mathrm{ben} = -k_b \xx_{ssss}, \qquad
+  \ff_\mathrm{ten} = (\sigma \xx_s)_s.
+\end{align}
+The physical tension is $\Lambda = \sigma + 1.5 \kappa^2$, where
+$\kappa$ is the membrane curvature.
+
+Semi-permeability is introduced by modifying the vesicle velocity from
+the standard choice. Instead of using the no-slip boundary condition, we
+assume the fluid flux through the boundary is proportional to the
+mechanical force~\cite{yao-mor2017}. That is, 
+\begin{align}
+  \label{eqn:vesicleFlux}
+  \uu - \dot{\xx} = - \beta (\ff_\mathrm{mem} \cdot \nn) \nn, \qquad
+  \xx \in \gamma,
+\end{align}
+where $\beta$ is the semi-permeability rate.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Integral equation formulation}
+Since the fluid satisfies the Stokes equations, it can be represented as
+layer potential. Given the interfacial boundary
+conditions~\eqref{eqn:jump}, the fluid velocity is
+\begin{align}
+  \uu(\xx) = \uu_\infty(\xx) + \SS[\ff_\mathrm{mem}](\xx), \quad
+    \xx \in \Omega,
+\end{align}
+where $\SS$ is the single-layer potential
+\begin{align}
+  \SS[\ff](\xx) = \frac{1}{4\pi\mu} \int_{\gamma} \left(
+    -\mathbf{I} \log\rho + \frac{\rr \otimes \rr}{\rho^2} \right)
+    \ff(\yy) ds_{\yy},
+\end{align}
+with $\rr = \xx - \yy$ and $\rho = \norm{\rr}$. Imposing the flux
+condition~\eqref{eqn:vesicleFlux} and the inextensibility condition, the
+vesicle velocity satisfies
+\begin{align}
+  \label{eqn:vesVelocity}
+  \dot{\xx} &= \uu_\infty(\xx) + \beta (\ff_\mathrm{mem}\cdot\nn)\nn
+  + \SS [\ff_\mathrm{mem}](\xx),  \quad
+  \xx_s \cdot \dot{\xx}_s = 0.
+\end{align}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Dimensionless equations}
+The inextensibility condition guarantees that the vesicle's length, $L$,
+is conserved, while its area, $A$, can change due to semi-permeability.
+Therefore, the reduced area $\nu = 4\pi A/L^2 \in (0,1]$ is not
+conserved. We non-dimensionalize~\eqref{eqn:vesVelocity} by introducing
+the length scale $R_0 = L/2\pi$ and defining the time scale $\tau = \mu
+R_0^3/k_b$, the tension scale $Q = k_b/R_0^2$, and the permeability
+scale $W = R_0/\mu$. The background velocity $\uu_\infty$ is
+non-dimensionalized with $R_0/\tau$.
+
+\todo[inline]{This is a dump of information regarding how we
+non-dimensionalize}
+In each experiment, we initialize an elliptical vesicle with longest
+diameter of 9$\mu$m. We use a length scale of $R_0 = 10^{-6}$m, a
+bending stiffness of $k_b = 10^{-19}$J, and fluid viscosity of $\mu=5
+\times 10^{-2}$kg/ms. Using the relaxation time scale $\tau = \mu
+R_0^3/k_b = 5 \times 10^{-1}$s, the pressure scale is $P = k_b/R_0^3 =
+10^{-1}$Pa.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Area dynamics}
+Following the analysis of Veerapaneni et al.~\cite{vee-raj-bir-pur2009},
+we compute the steady state shape of a semi-permeable vesicle in a
+quiescent flow. The steady state shape is a stationary point of the
+Lagrangian
+\begin{align}
+  \mathcal{L} = \frac{1}{2}\int_{\gamma} \kappa^2 \, ds +
+    \Lambda \left(\int_{\gamma} ds  - L \right),
+\end{align}
+where the Lagrange multiplier $\Lambda$ is the tension. Note the absence
+of the pressure Lagrange multiplier since the vesicle's area fluctuates.
+Taking the variation of $\mathcal{L}$ with respect to $\gamma$ and
+setting it to zero, the steady state shape satisfies $\kappa_{ss} +
+\frac{1}{2}\kappa^3 - \Lambda \kappa = 0$, with initial conditions
+$\kappa(0) = \kappa_0$ and $\kappa_s(0) = 0$.  Integrating once, we have
+\begin{align}
+  \frac{\kappa_s^2}{2} + \frac{\kappa^4}{8} - 
+    \frac{\Lambda}{2}\kappa^2 = \frac{\kappa_0^4}{8} - 
+    \frac{\Lambda}{2}\kappa_0^2.
+  \label{eqn:curveODE}
+\end{align}
+Assuming $\kappa_s \neq 0$,~\eqref{eqn:curveODE} is separable, and can
+be solved analytically in terms of the {\em EllipticF} function using
+Mathematica. Unlike in the impermeable case~\cite{vee-raj-bir-pur2009},
+the solution of~\eqref{eqn:curveODE} is not periodic unless $\kappa(s) =
+\kappa_0$. Therefore, the steady state shape of a semi-permeable vesicle
+in a quiescent flow is a circle with radius $L/2\pi$. Therefore, the
+steady state curvature and tension are
+\begin{align}
+  \kappa = \frac{2\pi}{L}, \: \Lambda = \frac{2\pi^2}{L^2}.
+  \label{eqn:SSshape}
+\end{align}
+Note that in contrast to a impermeable vesicle, the tension is positive
+rather than negative.
+
+We also compute the transient area of the vesicle. Since the area of the
+vesicle is
+\begin{align}
+  A(t) = \frac{1}{2}\int_{\gamma} (\xx \cdot \nn)\, ds,
+  \label{eqn:area}
+\end{align}
+its derivative includes terms due to the time derivative of $\xx \cdot
+\nn$ and a term due to interface stretching~\cite{lai-tse-hua2008}, but
+this latter term term is zero because of the local inextensibility
+condition. Therefore,
+\begin{align}
+  \dot{A}(t) =
+  \frac{1}{2} \int_{\gamma} (\dot{\xx} \cdot \nn)\, ds  + 
+  \frac{1}{2} \int_{\gamma} (\xx \cdot \dot{\nn})\, ds.
+\end{align}
+Applying integration by parts, the two integrals agree, and we have
+%\begin{align}
+%  \int_\gamma (\xx \cdot \dot{\nn})\, ds 
+%    = \int_\gamma \left(\xx \cdot \dot{\xx}_s^\perp \right)
+%    = -\int_\gamma \left(\xx^\perp \cdot \dot{\xx}_s\right)\, ds 
+%    = \int_\gamma \left(\xx_s^\perp \cdot \dot{\xx}\right)\, ds 
+%    = \int_\gamma (\dot{\xx} \cdot \nn)\, ds.
+%\end{align}
+\begin{align}
+  \dot{A}(t) = \int_\gamma \left(\beta (\ff \cdot \nn)\nn 
+    + \SS[\ff]\right) \cdot \nn\, ds 
+  = \beta \int_\gamma (\ff \cdot \nn)\, ds,
+\end{align}
+where we have used the incompressibility of the single-layer potential.
+Repeatedly applying integration by parts, we have
+\begin{align}
+  \dot{A}(t) &= \beta \int_\gamma \left( -\xx_{ssss} + 
+    (\sigma \xx_s)_s \right) \cdot \nn \, ds \\
+  &= -\beta \int_\gamma \left(-\xx_{sss} + \sigma \xx_s 
+    \right) \cdot \kappa \xx_s \, ds \\
+  &= -\beta \int_\gamma \left(\xx_{ss} \cdot 
+    (\kappa \xx_s)_s + \kappa \sigma \right) \, ds \\
+  &= -\beta \int_\gamma \left(\kappa (\xx_{ss} \cdot \xx_{ss}) + 
+    \kappa_s (\xx_{ss} \cdot \xx_s) + \kappa \sigma \right) 
+    \, ds \\
+  &= -\beta \int_\gamma \left(\kappa^3 + \kappa \sigma \right) 
+    \, ds = \beta \int_\gamma \left(
+    \frac{\kappa^3}{2} - \kappa \Lambda \right) \, ds.
+  \label{eqn:areaROC}
+\end{align}
+Note that~\eqref{eqn:SSshape} and are consistent since the constant
+curvature and tension values cause the integrand to vanish.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Supplementary Material: Numerical Methods}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Discretization in Space}
+By using a boundary integral equation formulation, the unknowns are the
+vesicle's position and tension that we track at $N$ discretization
+points. Derivatives are computed with Fourier differentiation, and the
+eighth-order quadrature~\cite{alp1999} is applied to the single-layer
+potential. For constricted flows, nearly-singular integrals are computed
+with an interpolation-based quadrature rule~\cite{qua-bir2014}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Discretization in Time}
+To eliminate stringent time step restrictions, we modify a time stepping
+method that discretizes high-order derivatives
+semi-implicitly~\cite{vee-gue-zor-bir2009}. We introduce the notation
+\begin{alignat}{3}
+  &B[\xx]\ff = -\frac{d^4}{ds^4} \ff,  \qquad
+  &&T[\xx]\sigma = (\sigma \xx_s)_s, \\
+  &D[\xx]\ff = \xx_s \cdot \ff_s, 
+  &&P[\xx]\ff = (\ff \cdot \nn) \nn,
+\end{alignat}
+for the differential and projection operators. Letting $B^N$ be the
+bending operator due to the vesicle configuration at time $t^N$, and
+similar notation for the other operators, we use the first-order
+semi-implicit time stepping method
+\begin{alignat}{3}  
+  \frac{\xx^{N+1} - \xx^N}{\Delta t} &= \uu_\infty(\xx^N) 
+  &&+ \beta P^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right) \nonumber \\
+  & &&+ \SS^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right), 
+\end{alignat}
+and  the inextensibility condition is discretized as
+\begin{align}
+  D^N\xx^{N+1} &= 1.
+\end{align}
+To achieve second-order accuracy over long time horizons, we modify an
+adaptive spectral deferred correction time stepping
+method~\cite{qua-bir2016}. Since the area of the vesicle is not
+conserved, we only use the length of the vesicle to estimate the error
+which determines if a time step is accepted or not and determines the
+subsequent time step size.
+
 \end{document}

### 2020-12-13 vesicle_code/docs/permeableVes/main.tex
yny

--- 2020-12-12 vesicle_code/docs/permeableVes/main.tex
@@
 \section*{Formulation}
+We consider a two-dimensional semi-permeable vesicle (permeable only to water) suspended in a viscous fluid, see figure~\ref{fig:schematics}.
+To focus on the effect of water flow on vesicle hydrodynamics in various conditions, we assume the fluid is the same inside and outside the vesicle membrane ($\gamma$).
+On the membrane the permeable water flux gives rise to a difference between the fluid velocity ${\bf u}({\bf x}\in \gamma)$
+and the membrane velocity $\dot{\bf x}$ \cite{yao-mor2017}:
+\begin{align}
+  \label{eqn:vesicleFlux}
+  \uu - \dot{\xx} = - \beta (R T \triangle c + \ff_\mathrm{mem} \cdot \nn) \nn, \qquad
+  \xx \in \gamma,
+\end{align}
+where $\beta$ is the water permeability, $R$ is the ideal gas constant, $T$ is the temperature ($^{\circ}$K), $\triangle c$ is contrast in a solute concentration (mol/volume),
+and $\ff_\mathrm{mem}$ is the membrane stress that consists of both bending $ \ff_\mathrm{ben}= -k_b \xx_{ssss}$ and tension $\ff_\mathrm{ten}=(\sigma \xx_s)_s$ ($s$
+is the arclength along the membrane, see figure~\ref{fig:schematics}.
 

### 2020-12-13 vesicle_code/docs/permeableVes/main.tex
yny

--- 2020-12-13 vesicle_code/docs/permeableVes/main.tex
@@
   \label{eqn:vesicleFlux}
-  \uu - \dot{\xx} = - \beta (R T \triangle c + \ff_\mathrm{mem} \cdot \nn) \nn, \qquad
+  \uu - \dot{\xx} = - k_w (R T \triangle c + \ff_\mathrm{mem} \cdot \nn) \nn, \qquad
   \xx \in \gamma,
 \end{align}
-where $\beta$ is the water permeability, $R$ is the ideal gas constant, $T$ is the temperature ($^{\circ}$K), $\triangle c$ is contrast in a solute concentration (mol/volume),
+where $k_w$ is the water permeability, $R$ is the ideal gas constant, $T$ is the temperature ($^{\circ}$K), $\triangle c$ is contrast in a solute concentration (mol/volume),
 and $\ff_\mathrm{mem}$ is the membrane stress that consists of both bending $ \ff_\mathrm{ben}= -k_b \xx_{ssss}$ and tension $\ff_\mathrm{ten}=(\sigma \xx_s)_s$ ($s$
 is the arclength along the membrane, see figure~\ref{fig:schematics}.
+Using $k_w\sim 10^{-12}$ m$^2$s/kg (typical of mammalian cell membranes \cite{LiMoriSun2015_PRL}) and an osmolarity $\triangle c = 1$ mol/L, the permeable water flow is of the order $v_\mathrm{o}=1 \mu$m/s.
+Assuming that the membrane bending stiffness $k_b = 10^{-19}$J, a membrane tension $10^{-3}$N/m (one tenth of the lysis tension) and a characteristic length scale of $10^{-6}$m, the tension contribution ($v_\mathrm{t}$) and elastic stress contribution
+($v_\mathrm{e}$) to the permeable water flow can be scaled to $v_\mathrm{o}$ as $v_\mathrm{o}:v_\mathrm{t}:v_\mathrm{e}=1:10^{-3}:10^{-7}$.
+We note that this result shows that the osmotic stress contributes much more to the permeable water flow than then tension and bending stresses.
+Furthermore, we note that in the absence of an osmotic stress, the water permeable flow can be significant when the membrane tension is large due to the external stress such as the hydrodynamics stress due to an external flow and/or due to confinement.
+In the following we will explore both.
 

### 2020-12-14 vesicle_code/docs/permeableVes/main.tex
yny

@@
 Cells achieve motility by simultaneously regulating their cell volume and cell membrane tension through trafficking of aquaporin proteins \cite{SaadounPapadopoulosWatanabeEtAl2005_JCS,Verkman2008_JMM,BerthaudEtAl2016_SM} and flattening of caveolae \cite{Keren2011_EurBJ}.
-Cells also need to control water transport across the cell membrane as they activate shape fluctuations prior to the bleb formation \cite{TaloniKardashSalmanEtAl2015_PRL}.
+Cells also control water transport  as they activate shape fluctuations in the membrane for the bleb formation \cite{TaloniKardashSalmanEtAl2015_PRL}.
 
@@
 In the red blood cell membrane, aquaporin-1 channels give rise to a much higher water permeability of $\sim 1.8\times 10^{-2}$ cm/s in erythrocytes \cite{YangMaVerkman2001_JBC} while the intrinsic water permeability of a lipid bilayer membrane is in the range of $10^{-4}-10^{-3}$ cm/s \cite{ThompsonHuang1966_ANYAS,FettiplaceHaydon1980_PhysRev,Grafmueller2019_ABLS,Dimova2020_GVB,BhatiaRobinsonDimova2020_SoftMatt}.
-
-The swelling/shrinking of a cell is inevitably coupled to changes in membrane tension and cell shape \cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL}.  
-Most studies focus on the osmolarity-induced water flux, while mechanical pressure may also contribute to the permeable water flow \cite{yao-mor2017}.
+%
+The swelling/shrinking of a cell is inevitably coupled to changes in membrane tension and cell shape \cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}.  
+%The osmolarity-induced water flux has been well studied, while mechanical pressure may also contribute to the permeable water flow \cite{yao-mor2017}.
 %The response of a cell to an osmotic gradient is inevitably both mechanical (tension redistribution and shape change) and chemical (water flux across the membrane).  
-In this work we focus on the intrinsic water permeability and study the subtle balance between hydrodynamics and elasticity of a semipermeable membrane under various flowing conditions and confinement.
-Specifically we focus on the effects of intrinsic water permeability in a vesicle under stress due to flows and/or confinement.
+In this work we focus on the intrinsic water permeability and study the subtle balance between hydrodynamics, tension and elasticity of a semipermeable membrane under various flowing conditions and confinement.
 
@@
 In this work we use numerical simulations to examine the hydrodynamics of a semipermeable vesicle in two dimensions.
-Focusing on the effects of water permeability on the hydrodynamics of a vesicle under mechanical stresses, we investigate how a semipermeable vesicle may behave differently from their impermeable counterpart in familiar situations such as shear flows, a stenosis channel, and a contracting channel.
+ It is challenging to keep a freely suspended vesicle in a steady flow for more than a few days. It is also difficult to quantify the change in vesicle area/volume in the experiments.
+ Using numerical simulations we can quantify  the effects of water permeability on the hydrodynamics of a vesicle under mechanical stresses. 
+ In the absence of an osmotic gradient, we first show that a freely suspended semipermeable vesicle behaves differently from an impermeable vesicle over a long time.
+Next we show that, at normal physiological conditions, the permeable water flow can be amplified by extreme confinement and results in observable change in both vesicle hydrodynamics and reduced area.
+ These results will shed light on the dynamic aging process of living cells that constantly go through flows and constrictions over a period of days.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Examples}
-We consider a single semi-permeable vesicle in quiescent, shear, and
-parabolic flows. We also consider a semi-permeable vesicle passing
-through a constriction. For each example, all vesicles have a length
-$L$, but the area is not conserved because of semi-permeability. We vary
-the initial vesicle reduced area, the permeability rate, and the flow
-rate. For all simulations, the bending modulus is $10^{-19}J$.
+\section*{Effects of membrane water permeability}
+We consider a single semi-permeable vesicle in familiar configurations to highlight the effects of membrane water permeability.
+In free space we put a semi-permeable vesicle in a quiescent flow, a planar shear flow and a Poiseuille flow.
+We also consider a semi-permeable vesicle in confinement: a long channel and a contracting channel.
+For each example, we fix the vesicle length and examine the enclosed area as a dynamical consequence of water flow, vesicle shape deformation and membrane tension distribution.
+%
+%all vesicles have a length
+%$L$, but the area is not conserved because of semi-permeability. We vary
+%the initial vesicle reduced area, the permeability rate, and the flow
+%rate. For all simulations, the bending modulus is $10^{-19}J$.
 

### 2020-12-14 vesicle_code/examples/output/makeImages.m
working on contracting images

@@ -7,7 +7,7 @@ options.marker = false;
 
 irate = 1; % controls the speed of the visualization
 
-if 1
+if 0
 %  file = 'parabolic1VesData.bin';
   file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/semipermeable/parabolic1Ves_speed8.00e02_RA9.00em01Data.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/impermeable/parabolic1Ves_speed1.20e03_RA6.00em01Data.bin';
@@ -45,9 +45,9 @@ file = '~/Dropbox/Adhesion/PermeableV/choke1Ves/choke1VesBData.bin';
   irate = 5;
 end
 
-if 0
-  file = 'contracting1VesData.bin';
-%  file = '~/projects/brinkman/vesicle_code/results/contracting/beta1em3Rate1em1/contracting1VesData.bin';
+if 1
+%  file = 'contracting1VesData.bin';
+%  file = '~/projects/brinkman/vesicle_code/results/contracting/beta1em3Rate1e1/contracting1VesData.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/contracting/beta1em3Rate1em0p5/contracting1VesData.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/contracting/beta1em3Rate1e0/contracting1VesData.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/contracting/beta0Rate1e0/contracting1VesData.bin';
@@ -55,13 +55,13 @@ if 0
 %  file = '~/projects/brinkman/vesicle_code/results/contracting/beta1em3Rate1e1/contracting1VesData.bin';
 %  file = '~/Dropbox/Adhesion/PermeableV/contracting1Ves/contracting1VesP3Data.bin';
 %  file = '~/Dropbox/Adhesion/PermeableV/contracting1Ves/Ncontracting1Ves3aData.bin';
-  file = '~/Dropbox/Adhesion/PermeableV/contracting1Ves/Ncontracting1Ves1aData.bin';
+  file = '~/Dropbox/Adhesion/PermeableV/contracting1Ves/contracting1VesP4Data.bin';
   ax = [-1 19 -5 5];
   options.confined = true;
   options.pressure = false;
   options.savefig = false;
   count = 1;
-  irate = 1;
+  irate = 10;
 end
 
 

### 2020-12-14 vesicle_code/docs/permeableVes/main.tex
working on contracting images
updated title

@@
 
-\title{Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and
-Physics}
+%\title{Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and
+%Physics}
+\title{Hydrodynamics of a Semi-Permeable Vesicle Under Flow and
+Confinement???}
 
@@
 
+\begin{figure*}[htp]
+  \centering
+%  \ifTikz
+  \input{figures/contractingComposite.tikz}
+%  \fi
+  \caption{\label{fig:contractingComposite} (a) A semi-permeable vesicle
+  passing through a contracting geometry similar to the experimental
+  device in~\cite{}. The narrowest part of the channel is $1.6\mu$m, and
+  the vesicle height is initially $10\mu$m.}
+\end{figure*}
+
 % \bibliographystyle{plain}

### 2020-12-15 vesicle_code/docs/permeableVes/main.tex
plot flux sign on vesicle shapes and updated notation for reduced area

@@
 steady state are proportional to $\beta^{-1}$. This is verified for a
-vesicle with initial reduced area $\nu = 0.65$ and with different
+vesicle with initial reduced area $\alpha = 0.65$ and with different
 semi-permeability rates. In Table~\ref{tbl:ellipseRelaxTimes} we report
@@
 initial configurations. As expected, each vesicle eventually
-reaches a circular shape with reduced area $\nu=1$. Next, we observe
+reaches a circular shape with reduced area $\alpha=1$. Next, we observe
 that even though the vesicle is inflating to a circle, meaning that
@@
 reduce area, for all simulations we initialize the vesicle with reduced
-area $\nu = 0.65$. The steady state vesicle shape and its reduced
+area $\alpha = 0.65$. The steady state vesicle shape and its reduced
 area are in Figure~\ref{fig:shearComposite}(b). We see that the flow
@@
   a semi-permeable vesicle submerged in a Poiseuille flow with varying
-  initial reduced areas and flow rates. (b) The steady state inclination
-  angle for four different flow velocities. The steady state shapes are
+  initial reduced areas and flow rates. The fluid flux along the red
+  regions is into the vesicle, and the fluid flux along the blue regions
+  is out of the vesicle.  (b) The steady state inclination angle for
+  four different flow velocities. The steady state shapes are
   superimposed. (c) The reduced area of the slipper formed with the flow
@@
 qualitatively agree, Kaoui et al.~report that the vesicles with
-$\nu=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
+$\alpha=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
 axisymmetric. In our simulations these vesicles are slightly asymmetric,
@@
 pressure. We consider both an impermeable and semi-permeable vesicle
-with initial reduced area $\nu = 0.65$ passing through a constricted
+with initial reduced area $\alpha = 0.65$ passing through a constricted
 geometry and compute the pressure drop between the inlet and outlet of
@@
 
-%
-%\begin{figure}[htp]
-%%  \ifTikz
-%%  \input{figures/stenosisGeom.tikz}
-%%  \fi
-%  \includegraphics[width=\linewidth]{figures/stenosisGeom.pdf}
-%  \caption{\label{fig:stenosisGeom} A single semi-permeable vesicle
-%  passing through a constriction. The geometry and parameters are chosen
-%  to replicate the experiments of Abkarian et
-%  al.~\cite{abk-fai-sto2006}.}
-%\end{figure}
-%
-%\begin{figure}[htp]
-%%  \ifTikz
-%%  \input{figures/stenosisPressureFluctuation.tikz}
-%%  \fi
-%  \includegraphics[width=\linewidth]{figures/stenosisPressureFluctuation.pdf}
-%  \caption{\label{fig:stenosisPressure} The excess pressure across the
-%  constriction in Figure~\ref{fig:stenosisGeom}. The black dashed lines
-%  denote the start and end of the constriction. The results are
-%  qualitative agreement with~\cite{abk-fai-sto2006}.}
-%\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+Velocity scale is $100\mu$m/s.
+
 \begin{figure*}[htp]
   \centering
-%  \ifTikz
+  \ifTikz
   \input{figures/contractingComposite.tikz}
-%  \fi
+  \fi
   \caption{\label{fig:contractingComposite} (a) A semi-permeable vesicle
   passing through a contracting geometry similar to the experimental
-  device in~\cite{}. The narrowest part of the channel is $1.6\mu$m, and
-  the vesicle height is initially $10\mu$m.}
+  device in~\cite{}. The narrowest part of the channel is $1.6\mu$m, 
+  the vesicle height is initially $10\mu$m, and the maximum background
+  flow velocity is $316\mu$m/s. The fluid flux along the red regions is
+  into the vesicle, and the fluid flux along the blue regions is out of
+  the vesicle.}
 \end{figure*}
@@
 is conserved, while its area, $A$, can change due to semi-permeability.
-Therefore, the reduced area $\nu = 4\pi A/L^2 \in (0,1]$ is not
+Therefore, the reduced area $\alpha = 4\pi A/L^2 \in (0,1]$ is not
 conserved. We non-dimensionalize~\eqref{eqn:vesVelocity} by introducing

### 2020-12-16 vesicle_code/docs/permeableVes/main.tex
working on figures

@@
 \subsection*{Semi-Permeable Vesicle in a Contracting Geometry} 
-
-Velocity scale is $100\mu$m/s.
+We expose a single semi-permeable vesicle to even larger deformations by
+simulating its hydrodynamics in a contracting microfluidic geometry.
+Similar to~\cite{wu2015critical}, we consider a geometry whose width
+gradually reduces from $16\mu$m to $1.6\mu$m and then immediately opens
+again to $16\mu$m. We initialize a semi-permeable vesicle with $\alpha =
+0.65$ that spans $10\mu$m of the total channel width. We start by
+investigating whether the vesicle passes through the constriction with
+different flow rates and permeability rates.
 
@@
   \centering
-  \ifTikz
+%  \ifTikz
   \input{figures/contractingComposite.tikz}
-  \fi
+%  \fi
   \caption{\label{fig:contractingComposite} (a) A semi-permeable vesicle

### 2020-12-16 vesicle_code/docs/permeableVes/main.tex
converted tikz to pdf

--- 2020-12-15 vesicle_code/docs/permeableVes/main.tex
@@
   \input{figures/relaxationComposite.tikz}
+  \else
+  \includegraphics{figures/relaxationComposite.pdf}
   \fi
@@
   \input{figures/shearComposite.tikz}
+  \else
+  \includegraphics{figures/shearComposite.pdf}
   \fi
@@
   \input{figures/parabolicComposite.tikz}
+  \else
+  \includegraphics{figures/parabolicComposite.pdf}
   \fi
@@
 \subsection*{Semi-Permeable Vesicle in a Contracting Geometry} 
-
-Velocity scale is $100\mu$m/s.
+We expose a single semi-permeable vesicle to even larger deformations by
+simulating its hydrodynamics in a contracting microfluidic geometry.
+Similar to~\cite{wu2015critical}, we consider a channel whose width
+gradually reduces from $16\mu$m to $1.6\mu$m and then immediately opens
+again to $16\mu$m (Figure~\ref{fig:contractingComposite}). We impose a
+Poiseuille flow at the inlet and outlet with a constant maximum flow
+rate of $U_{\max}$. We initialize a semi-permeable vesicle with $\alpha
+= 0.65$ that spans $10\mu$m of the total channel width and investigate
+the effects of the permeability rate and the maximum flow velocity. We
+color the vesicle according to the sign of its flux---fluid flows
+into the vesicle in red regions and out of the vesicle in blue
+regions.
+
+In Figures~\ref{fig:contractingComposite}(a)
+and~\ref{fig:contractingComposite}(b), we plot snapshots of vesicles
+with different permeability rates, and
+Figure~\ref{fig:contractingComposite}(c) shows that the reduced area as
+a function of the vesicles' location. For sufficiently large
+permeability rates, the vesicle initially inflates, but then deflates as
+it passes through the constriction. However, if the semi-permeability
+rate is too low, the vesicle is too large when it reaches the narrowest
+part of the channel, and it is unable to pass. In
+Figures~\ref{fig:contractingComposite}(d)
+and~\ref{fig:constractingComposite}{e}, we plot snapshots of vesicles
+with different imposed maximum velocities, and
+Figure~\ref{fig:contractingComposite}(f) shows that the reduced area as
+a function of the vesicles' location. At low velocities, the vesicle
+inflates similar to the unbounded parabolic flow example, and it is
+unable to pass through the constrictions. However, higher flow rates
+result in additional deflation and the vesicle passes through the
+contraction.
+
+To understand long term effects of a vesicle passing through a
+contracting geometry, in Figures~\ref{fig:contractingComposite}(g) we
+simulate a vesicle passing six times through the contracting geometry.
+In Figure~\ref{fig:contractingComposite}(h), we show that the vesicle
+deflates each time it passes through the constriction followed by a
+rapid inflation. The total area loss over the history of the vesicle is
+almost 50\%. In Figure~\ref{fig:contractingComposite}(i), we show the
+vesicle velocity as a function of the vesicle's center of mass. As the
+vesicle passes through the contraction, it accelerates followed by a
+rapid deacceleration once it has passed through the contraction.
 
@@
   \input{figures/contractingComposite.tikz}
+  \else
+  \includegraphics{figures/contractingComposite.pdf}
   \fi

### 2020-12-16 vesicle_code/docs/permeableVes/main.tex
yny

--- 2020-12-15 vesicle_code/docs/permeableVes/main.tex
@@
 %Physics}
-\title{Hydrodynamics of a Semi-Permeable Vesicle Under Flow and
-Confinement???}
+\title{Effects of Water Permeability on the Hydrodynamics of a Vesicle Under Flow and Confinement}
 
@@
 We consider a two-dimensional semi-permeable vesicle (permeable only to water) suspended in a viscous fluid, see figure~\ref{fig:schematics}.
-To focus on the effect of water flow on vesicle hydrodynamics in various conditions, we assume the fluid is the same inside and outside the vesicle membrane ($\gamma$).
+To focus on the effect of water flow on vesicle hydrodynamics in various conditions, we assume the fluid is the same inside and outside the vesicle membrane ($\gamma$) with an outward normal $\nn$.
 On the membrane the permeable water flux gives rise to a difference between the fluid velocity ${\bf u}({\bf x}\in \gamma)$
@@
 is the arclength along the membrane, see figure~\ref{fig:schematics}.
-Using $k_w\sim 10^{-12}$ m$^2$s/kg (typical of mammalian cell membranes \cite{LiMoriSun2015_PRL}) and an osmolarity $\triangle c = 1$ mol/L, the permeable water flow is of the order $v_\mathrm{o}=1 \mu$m/s.
+Using $k_w\sim 10^{-12}$ m$^2$s/kg (typical of mammalian cell membranes \cite{LiMoriSun2015_PRL}) and an osmolarity $\triangle c = 1$ mol/L (consistent with the osmotic forces in vesicle aspiration experiments \cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the corresponding water flow is of the order $v_\mathrm{o}=1 \mu$m/s.
 Assuming that the membrane bending stiffness $k_b = 10^{-19}$J, a membrane tension $10^{-3}$N/m (one tenth of the lysis tension) and a characteristic length scale of $10^{-6}$m, the tension contribution ($v_\mathrm{t}$) and elastic stress contribution
 ($v_\mathrm{e}$) to the permeable water flow can be scaled to $v_\mathrm{o}$ as $v_\mathrm{o}:v_\mathrm{t}:v_\mathrm{e}=1:10^{-3}:10^{-7}$.
-We note that this result shows that the osmotic stress contributes much more to the permeable water flow than then tension and bending stresses.
 Furthermore, we note that in the absence of an osmotic stress, the water permeable flow can be significant when the membrane tension is large due to the external stress such as the hydrodynamics stress due to an external flow and/or due to confinement.
@@
 For each example, we fix the vesicle length and examine the enclosed area as a dynamical consequence of water flow, vesicle shape deformation and membrane tension distribution.
+
+In experiments vesicle under shear flows are measured for a minute (chapter 19 in \cite{Dimova2020_GVB}), a duration over which vesicle can be assumed impermeable \cite{AbkarianViallat2005_BJ}.
+Our simulations of a semi-permeable vesicle
+in these flows show that water permeability may lead to different vesicle hydrodynamics over a time scale of 10 to 100 minutes.
+{\bf YNY: is this correct?
+The shear flow results seem to suggest that the permeability may lead to change in area in less than a second???}
+For vesicles in a narrow micro-fluidic channel, the typical time scale is of $ms$ \cite{abk-fai-sto2006}.
+Our simulations show that strong confinement can lead to amplification of water permeability at such short time scale.
 %
@@
 \end{figure*}
+
 Our analysis shows that a semi-permeable vesicle in a quiescent flow
 relaxes to a circle at a rate that is proportional to $\beta$, and the
-steady state tension is $\Lambda = 2\pi^2/L^2$. Therefore, the times for
-the vesicle to deviate from its initial reduced area and to reach its
-steady state are proportional to $\beta^{-1}$. This is verified for a
-vesicle with initial reduced area $\alpha = 0.65$ and with different
-semi-permeability rates. In Table~\ref{tbl:ellipseRelaxTimes} we report
-the required time, $t_\mathrm{steady}$, for the vesicle's reduced area
-to be within 1.3\% of its steady state reduced area, and the required
-time, $t_\mathrm{inflate}$, for the vesicle's reduced area to exceed
-1.3\% of its initial reduced area. Both times are proportional to
-$\beta^{-1}$, and for this reason, our numerical results are reported in
-terms of the scaled time $\beta t$.
-\begin{table}[htp]
-  \centering
-  \caption{\label{tbl:ellipseRelaxTimes} The time for a semi-permeable
-  vesicle to its steady state ($t_\mathrm{steady}$) and to begin
-  inflating ($t_\mathrm{inflate}$).}
-  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
-    $\beta$ & $t_\mathrm{steady}$  & ratio 
-            & $t_\mathrm{inflate}$ & ratio \\
-    \midrule
-    $10^{0}$  & $6.45 \times 10^{0}$ & ---  
-              & $2.17 \times 10^{-2}$ & --- \\ 
-    $10^{-1}$ & $2.00 \times 10^{1}$ & 3.10 & 
-                $1.25 \times 10^{-1}$ & 5.76 \\
-    $10^{-2}$ & $9.61 \times 10^{1}$ & 4.81 & 
-                $1.59 \times 10^{0}$ & 12.72 \\
-    $10^{-3}$ & $8.36 \times 10^{2}$ & 8.71 & 
-                $2.19 \times 10^{1}$ & 13.77 \\
-    $10^{-4}$ & $8.15 \times 10^{3}$ & 9.74 & 
-                $2.14 \times 10^{2}$ & 9.77 \\
-    $10^{-5}$ & $8.03 \times 10^{4}$ & 9.85 & 
-                $2.20 \times 10^{3}$ & 10.14 \\
-    \bottomrule
-  \end{tabular}
-\end{table}
+steady state tension is $\Lambda = 2\pi^2/L^2$, see Supplementary Material. 
+Our analysis further shows that the time for 
+a semipermeable vesicle to deviate from its initial reduced area and to reach its
+steady state is proportional to $\beta^{-1}$. For this reason, our numerical results below 
+are reported in terms of the scaled time $\beta t$.
+
+%This is verified for a
+%vesicle with initial reduced area $\nu = 0.65$ and with different
+%semi-permeability rates. In Table~\ref{tbl:ellipseRelaxTimes} we report
+%the required time, $t_\mathrm{steady}$, for the vesicle's reduced area
+%to be within 1.3\% of its steady state reduced area, and the required
+%time, $t_\mathrm{inflate}$, for the vesicle's reduced area to exceed
+%1.3\% of its initial reduced area. Both times are proportional to
+%$\beta^{-1}$, and for this reason, our numerical results are reported in
+%terms of the scaled time $\beta t$.
+%\begin{table}[htp]
+%  \centering
+%  \caption{\label{tbl:ellipseRelaxTimes} The time for a semi-permeable
+%  vesicle to its steady state ($t_\mathrm{steady}$) and to begin
+%  inflating ($t_\mathrm{inflate}$).}
+%  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
+%    $\beta$ & $t_\mathrm{steady}$  & ratio 
+%            & $t_\mathrm{inflate}$ & ratio \\
+%    \midrule
+%    $10^{0}$  & $6.45 \times 10^{0}$ & ---  
+%              & $2.17 \times 10^{-2}$ & --- \\ 
+%    $10^{-1}$ & $2.00 \times 10^{1}$ & 3.10 & 
+%                $1.25 \times 10^{-1}$ & 5.76 \\
+%    $10^{-2}$ & $9.61 \times 10^{1}$ & 4.81 & 
+%                $1.59 \times 10^{0}$ & 12.72 \\
+%    $10^{-3}$ & $8.36 \times 10^{2}$ & 8.71 & 
+%                $2.19 \times 10^{1}$ & 13.77 \\
+%    $10^{-4}$ & $8.15 \times 10^{3}$ & 9.74 & 
+%                $2.14 \times 10^{2}$ & 9.77 \\
+%    $10^{-5}$ & $8.03 \times 10^{4}$ & 9.85 & 
+%                $2.20 \times 10^{3}$ & 10.14 \\
+%    \bottomrule
+%  \end{tabular}
+%\end{table}
 
@@
 dynamics of four vesicles with $\beta = 10^{-3}$ and a variety of
-initial configurations. As expected, each vesicle eventually
-reaches a circular shape with reduced area $\alpha=1$. Next, we observe
-that even though the vesicle is inflating to a circle, meaning that
-there is a net flux into the vesicle, there are regions where the flux
-is out of the vesicle. These regions are denoted in blue and are only
-present at early times. Finally, the vesicles's reduced area do not 
+initial configurations. The vesicles on the left are color-coded by the permeable flux: red denotes a flux into the vesicle, and blue denotes a flux out of the vesicle.
+First we observe
+that even though the vesicle is inflating to a circle (meaning that
+there is a net flux into the vesicle), there are regions where the flux
+is out of the vesicle.
+
+For the vesicle with an initial reduced area ($\alpha(0)=0.12$ in the bottom row) we observe that vesicle deflates (blue regions) first due to the high interior capillary pressure.  Over time
+all vesicles inflate and as expected, each vesicle eventually
+reaches a circular shape with reduced area $\alpha=1$. 
+%These regions are denoted in blue and are only present at early times. 
+Finally, the vesicles's reduced area do not 
 change by much at early times, and intermediate shapes of semi-permeable vesicles
@@
 permeability velocity dominates, and the vesicle begins to inflate to a
-circle with no vanishing force and velocity.
+circle with no vanishing force and velocity. {\bf YNY: We should put a tick on the time when this transition occurs for each of the vesicles}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Shear Flow}
+\subsection*{Planar Shear Flow}
 \begin{figure}[htp]
@@
   flow rates and semi-permeability rates. The circled vesicles
-  correspond to the simulations in part (a).}
+  correspond to the simulations in part (a). {\bf YNY: should this be two-column wide?}}
 \end{figure}
 
-We consider a semi-permeable vesicle in the shear flow
+We consider a semi-permeable vesicle in a planar shear flow
 $\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$ with different permeability
-rates $\beta$ and shear rates $\dot{\gamma}$. A vesicle's reduced area
+rates $\beta$ and shear rates $\dot{\gamma}$. 
+When $\beta=0$ (impermeable case), a vesicle's reduced area
 and viscosity contrast determine whether it tank treads or
@@
 
-We form the steady state shape for a variety of semi-permeability rates
-and flow rates. Since the final shape is independent of the initial
-reduce area, for all simulations we initialize the vesicle with reduced
-area $\alpha = 0.65$. The steady state vesicle shape and its reduced
-area are in Figure~\ref{fig:shearComposite}(b). We see that the flow
+For a variety of semi-permeability rates
+and flow rates, a semipermeable vesicle reaches a steady equilibrium as in Figure~\ref{fig:shearComposite}(a).
+Since the final shape is independent of the initial
+reduce area,  we initialize the vesicle with reduced
+area $\nu = 0.65$ for all simulations in Figure~\ref{fig:shearComposite}(b), where we summarize the steady state vesicle shape and its reduced
+area. We see that the flow
 rate significantly affects the final vesicle shape, but the
@@
   a semi-permeable vesicle submerged in a Poiseuille flow with varying
-  initial reduced areas and flow rates. The fluid flux along the red
-  regions is into the vesicle, and the fluid flux along the blue regions
-  is out of the vesicle.  (b) The steady state inclination angle for
-  four different flow velocities. The steady state shapes are
+  initial reduced areas and flow rates. (b) The steady state inclination
+  angle for four different flow velocities. The steady state shapes are
   superimposed. (c) The reduced area of the slipper formed with the flow
@@
 We consider a semi-permeable vesicle in the Poiseuille flow $\uu =
-U(1-(y/W)^2,0)$, where $U$ is the maximum imposed velocity. We examine
-the effect of the non-linear Poiseuille flow on the migration of
-semi-permeable vesicle. In this experiment, the vesicle is initialized
-above the center line $y=0$, and it migrates towards the center
-line~\cite{dan-vla-mis2009}. For an impermeable vesicle, depending on
-the vesicles reduced area and the flow rate, the long time vesicle shape
-is either an axisymmetric parachute or bullet, or an asymmetric
-tank-treading slipper~\cite{kao-bir-mis2009}. To validate our methods,
-in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
-for the steady state shape of an impermeable vesicle
-vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
-qualitatively agree, Kaoui et al.~report that the vesicles with
-$\alpha=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
-axisymmetric. In our simulations these vesicles are slightly asymmetric,
-are undergoing a tank treading motion, and we therefore report them as
-asymmetric slippers.
-
-Having validated our method, we investigate the dynamics of a
-semi-permeable vesicle in a Poiseuille flow. Using several initial
+U(1-(y/W)^2,0)$, where $U$ is the maximum velocity at $y=0$. The non-linear effects of the Poiseuille flow
+on the migration of an impermeable vesicle have been well-studied \cite{kao-bir-mis2009}: At a given value of $U$,
+there exists a critical reduced volume above which the equilibrium vesicle shape is symmetric (parachute or bullet shapes) and the vesicle stays at $y=0$.
+Below this critical reduced volume the equilibrium vesicle moves off the center and is asymmetric (tank-treading slipper shape).
+We validated our numerical codes by comparing against results in Kaoui {\it et al.} \cite{kao-bir-mis2009}, see Supplementary Material.
+
+%
+%
+%We examine the effect of the non-linear Poiseuille flow on the migration of
+%semi-permeable vesicle. In this experiment, the vesicle is initialized
+%above the center line $y=0$, and it migrates towards the center
+%line~\cite{dan-vla-mis2009}. 
+%
+%For an impermeable vesicle, depending on
+%the vesicles reduced area and the flow rate, the equilibrium vesicle shape
+%is either an axisymmetric parachute or bullet, or an asymmetric
+%tank-treading slipper~\cite{kao-bir-mis2009}. 
+%We validated our numerical codes by comparing against results in Kaoui {\it et al.} \cite{kao-bir-mis2009}.
+%One of the most salient features of an impermeable vesicle in the Poiseuille flow is that, 
+%%
+%%To validate our methods,
+%%in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
+%%for the steady state shape of an impermeable vesicle
+%%vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
+%%qualitatively agree, Kaoui et al.~report that the vesicles with
+%%$\nu=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
+%%axisymmetric. In our simulations these vesicles are slightly asymmetric,
+%%are undergoing a tank treading motion, and we therefore report them as
+%%asymmetric slippers.
+%
+%Having validated our method, we investigate the dynamics of a semi-permeable vesicle in a Poiseuille flow. 
+Using several initial
 reduced areas and flow rates, we recreate the impermeable vesicle phase
@@
 final vesicle configurations are in
-Figure~\ref{fig:parabolicComposite}(b). As observed for the shear flow,
+Figure~\ref{fig:parabolicComposite}(a). An example of a semi-permeable vesicle with $\alpha(0) = 0.9$ and $U=800$ $\mu m/s$ is
+shown in Figure~\ref{fig:parabolicComposite}(c) and (d). 
+%
+As observed for the planar shear flow,
 the steady state reduced area is independent of the initial reduced
@@
 areas. We report the steady state reduced area in
-Figure~\ref{fig:parabolicComposite}(b). At the smallest flow rate of $U
+Figure~\ref{fig:parabolicComposite}(a). At the smallest flow rate of $U
 = 200 \mu m/s$, the steady state reduced area is large, and the result
@@
 slipper.
+We observe that the membrane permeability to water drastically alters the vesicle shape and position relative to the flow at equilibrium: At $\beta=10^{-3}$ the equilibrium vesicle depends only on the maximum velocity $U$ of the nonlinear shear flow.
+The higher $U$ the smaller the equilibrium reduced area and the further away vesicle is relative to the flow center at $y=0$.
 
@@
 \subsection*{Semi-Permeable Vesicle in Stenosis}
-We consider the effect of stenosis on a semi-permeable vesicle. Inspired
-by an experiment that measures the effects of cells on the dynamical
-pressure-drop variations along a micrometer-sized
-channel~\cite{abk-fai-sto2006}, we first examining the effect of
+Cells experience stretching and release messengers when they pass through capillary vessels \cite{Wan2008_PNAS,ForsythWan2011_PNAS,Pak2015_PNAS}.
+Many cells exhibit extraordinary flexibility as they go through narrow channels \cite{AuStoreyMoore2016_PNAS}, and adjustment of area to volume ratio may be a key factor for successful passages.
+Here we quantify the effect of water permeability on a vesicle going through a stenosis (a long microfluidic channel with a cross section smaller than the cell radius).
+Based on the findings in 
+%We consider the effect of stenosis on a semi-permeable vesicle. Inspired
+%by an experiment that measures the effects of cells on the dynamical
+%pressure-drop variations along a micrometer-sized
+\cite{abk-fai-sto2006}, we first examining the effect of
 semi-permeability on the pressure fluctuation across a stenosed
-geometry. In this experiment, a pressure drop is used to pass a vesicle
+geometry. In this experiment, a pressure drop is used to squeeze a
 red blood cell (RBC) through a constriction with diameter $5\mu$m and
@@
 pressure. We consider both an impermeable and semi-permeable vesicle
-with initial reduced area $\alpha = 0.65$ passing through a constricted
+with initial reduced area $\nu = 0.65$ passing through a constricted
 geometry and compute the pressure drop between the inlet and outlet of
@@
 
+%
+%\begin{figure}[htp]
+%%  \ifTikz
+%%  \input{figures/stenosisGeom.tikz}
+%%  \fi
+%  \includegraphics[width=\linewidth]{figures/stenosisGeom.pdf}
+%  \caption{\label{fig:stenosisGeom} A single semi-permeable vesicle
+%  passing through a constriction. The geometry and parameters are chosen
+%  to replicate the experiments of Abkarian et
+%  al.~\cite{abk-fai-sto2006}.}
+%\end{figure}
+%
+%\begin{figure}[htp]
+%%  \ifTikz
+%%  \input{figures/stenosisPressureFluctuation.tikz}
+%%  \fi
+%  \includegraphics[width=\linewidth]{figures/stenosisPressureFluctuation.pdf}
+%  \caption{\label{fig:stenosisPressure} The excess pressure across the
+%  constriction in Figure~\ref{fig:stenosisGeom}. The black dashed lines
+%  denote the start and end of the constriction. The results are
+%  qualitative agreement with~\cite{abk-fai-sto2006}.}
+%\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Velocity scale is $100\mu$m/s.
-
 \begin{figure*}[htp]
   \centering
-  \ifTikz
+%  \ifTikz
   \input{figures/contractingComposite.tikz}
-  \fi
+%  \fi
   \caption{\label{fig:contractingComposite} (a) A semi-permeable vesicle
   passing through a contracting geometry similar to the experimental
-  device in~\cite{}. The narrowest part of the channel is $1.6\mu$m, 
-  the vesicle height is initially $10\mu$m, and the maximum background
-  flow velocity is $316\mu$m/s. The fluid flux along the red regions is
-  into the vesicle, and the fluid flux along the blue regions is out of
-  the vesicle.}
+  device in~\cite{}. The narrowest part of the channel is $1.6\mu$m, and
+  the vesicle height is initially $10\mu$m.}
 \end{figure*}
@@
 is conserved, while its area, $A$, can change due to semi-permeability.
-Therefore, the reduced area $\alpha = 4\pi A/L^2 \in (0,1]$ is not
+Therefore, the reduced area $\nu = 4\pi A/L^2 \in (0,1]$ is not
 conserved. We non-dimensionalize~\eqref{eqn:vesVelocity} by introducing

### 2020-12-17 vesicle_code/docs/permeableVes/main.tex
working on contracting

--- 2020-12-16 vesicle_code/docs/permeableVes/main.tex
@@
 \begin{figure*}[htp]
-  \ifTikz
+%  \ifTikz
   \input{figures/stenosisComposite.tikz}
-  \fi
+%  \fi
   \caption{\label{fig:stenosisComposite} (a) A semi-permeable vesicle
@@
 the effects of the permeability rate and the maximum flow velocity. We
-color the vesicle according to the sign of its flux---fluid flows
-into the vesicle in red regions and out of the vesicle in blue
-regions.
-
-In Figures~\ref{fig:contractingComposite}(a)
-and~\ref{fig:contractingComposite}(b), we plot snapshots of vesicles
-with different permeability rates, and
-Figure~\ref{fig:contractingComposite}(c) shows that the reduced area as
-a function of the vesicles' location. For sufficiently large
-permeability rates, the vesicle initially inflates, but then deflates as
-it passes through the constriction. However, if the semi-permeability
-rate is too low, the vesicle is too large when it reaches the narrowest
-part of the channel, and it is unable to pass. In
-Figures~\ref{fig:contractingComposite}(d)
-and~\ref{fig:constractingComposite}{e}, we plot snapshots of vesicles
-with different imposed maximum velocities, and
-Figure~\ref{fig:contractingComposite}(f) shows that the reduced area as
-a function of the vesicles' location. At low velocities, the vesicle
+color the vesicle according to the sign of its flux---fluid flows into
+the vesicle in red regions and out of the vesicle in blue regions.
+
+In Figures~\ref{fig:contractingComposite}a
+and~\ref{fig:contractingComposite}b, we plot snapshots of vesicles with
+different permeability rates, and Figure~\ref{fig:contractingComposite}c
+shows that the reduced area as a function of the vesicles' location. For
+sufficiently large permeability rates, the vesicle initially inflates,
+but then deflates as it passes through the constriction. However, if the
+semi-permeability rate is too low, the vesicle is too large when it
+reaches the narrowest part of the channel, and it is unable to pass. In
+Figures~\ref{fig:contractingComposite}d
+and~\ref{fig:contractingComposite}e, we plot snapshots of vesicles with
+different imposed maximum velocities, and
+Figure~\ref{fig:contractingComposite}f shows that the reduced area as a
+function of the vesicles' location. At low velocities, the vesicle
 inflates similar to the unbounded parabolic flow example, and it is
@@
 To understand long term effects of a vesicle passing through a
-contracting geometry, in Figures~\ref{fig:contractingComposite}(g) we
+contracting geometry, in Figures~\ref{fig:contractingComposite}g we
 simulate a vesicle passing six times through the contracting geometry.
-In Figure~\ref{fig:contractingComposite}(h), we show that the vesicle
+In Figure~\ref{fig:contractingComposite}h, we show that the vesicle
 deflates each time it passes through the constriction followed by a
 rapid inflation. The total area loss over the history of the vesicle is
-almost 50\%. In Figure~\ref{fig:contractingComposite}(i), we show the
+almost 50\%. In Figure~\ref{fig:contractingComposite}i, we show the
 vesicle velocity as a function of the vesicle's center of mass. As the

### 2020-12-17 vesicle_code/docs/permeableVes/main.tex
fixed merge conflicts

--- 2020-12-16 vesicle_code/docs/permeableVes/main.tex
@@
 relaxes to a circle at a rate that is proportional to $\beta$, and the
-steady state tension is $\Lambda = 2\pi^2/L^2$, see Supplementary Material. 
-Our analysis further shows that the time for 
-a semipermeable vesicle to deviate from its initial reduced area and to reach its
-steady state is proportional to $\beta^{-1}$. For this reason, our numerical results below 
-are reported in terms of the scaled time $\beta t$.
+steady state tension is $\Lambda = 2\pi^2/L^2$ (see Supplementary
+Material). Our analysis further shows that the time for a semipermeable
+vesicle to deviate from its initial reduced area and to reach its steady
+state is proportional to $\beta^{-1}$. For this reason, our numerical
+results below are reported in terms of the scaled time $\beta t$.
 
@@
 %These regions are denoted in blue and are only present at early times. 
-Finally, the vesicles's reduced area do not 
-change by much at early times, and intermediate shapes of semi-permeable vesicles
-resemble the shape of an impermeable vesicle. This can be explained by
-considering the two terms that contribute to the vesicle velocity: (i)
-the permeability velocity, $\beta(\ff \cdot \nn) \nn$, and (ii) the
-force balance velocity, $\SS[\ff]$. Since $\beta = 10^{-3}$, the
-permeability velocity is much smaller than the force balance velocity at
-early times, and the semi-permeable vesicle dynamics resembles those of
-an impermeable vesicle. As the force balance velocity decreases, the
-permeability velocity dominates, and the vesicle begins to inflate to a
-circle with no vanishing force and velocity. {\bf YNY: We should put a tick on the time when this transition occurs for each of the vesicles}
+Finally, the vesicles's reduced area do not steady state tension is
+$\Lambda = 2\pi^2/L^2$. Therefore, the times for
+the vesicle to deviate from its initial reduced area and to reach its
+steady state are proportional to $\beta^{-1}$.
+
+In Figure~\ref{fig:relaxationComposite}, we examine the transient
+dynamics of four vesicles with $\beta = 10^{-3}$ and a variety of
+initial configurations. As expected, each vesicle eventually
+reaches a circular shape with reduced area $\alpha=1$. Next, we observe
+that even though the vesicle is inflating to a circle, meaning that
+there is a net flux into the vesicle, there are regions where the flux
+is out of the vesicle. These regions are denoted in blue and are only
+present at early times. Finally, the vesicles's reduced area do not
+change by much at early times, and intermediate shapes of semi-permeable
+vesicles resemble the shape of an impermeable vesicle. This can be
+explained by considering the two terms that contribute to the vesicle
+velocity: (i) the permeability velocity, $\beta(\ff \cdot \nn) \nn$, and
+(ii) the force balance velocity, $\SS[\ff]$. Since $\beta = 10^{-3}$,
+the permeability velocity is much smaller than the force balance
+velocity at early times, and the semi-permeable vesicle dynamics
+resembles those of an impermeable vesicle. As the force balance velocity
+decreases, the permeability velocity dominates, and the vesicle begins
+to inflate to a circle with no vanishing force and velocity. {\bf YNY:
+We should put a tick on the time when this transition occurs for each of
+the vesicles}
 
@@
 
-For a variety of semi-permeability rates
-and flow rates, a semipermeable vesicle reaches a steady equilibrium as in Figure~\ref{fig:shearComposite}(a).
-Since the final shape is independent of the initial
-reduce area,  we initialize the vesicle with reduced
-area $\nu = 0.65$ for all simulations in Figure~\ref{fig:shearComposite}(b), where we summarize the steady state vesicle shape and its reduced
-area. We see that the flow
-rate significantly affects the final vesicle shape, but the
-semi-permeability rate has a minor effect. Instead, as we saw in the
-quiescent analysis, $\beta$ sets a time scale since the time required
-for a vesicle to reach its steady state configuration is proportional to
-$\beta^{-1}$.
+For a variety of semi-permeability rates and flow rates, a semipermeable
+vesicle reaches a steady equilibrium as in
+Figure~\ref{fig:shearComposite}(a).  Since the final shape is
+independent of the initial reduced area,  we initialize the vesicle with
+reduced area $\alpha = 0.65$ for all simulations in
+Figure~\ref{fig:shearComposite}(b), where we summarize the steady state
+vesicle shape and its reduced area. We see that the flow rate
+significantly affects the final vesicle shape, but the semi-permeability
+rate has a minor effect. Instead, as we saw in the quiescent analysis,
+$\beta$ sets a time scale since the time required for a vesicle to reach
+its steady state configuration is proportional to $\beta^{-1}$.
 
@@
 %Having validated our method, we investigate the dynamics of a semi-permeable vesicle in a Poiseuille flow. 
-Using several initial
-reduced areas and flow rates, we recreate the impermeable vesicle phase
+Using several initial reduced areas and flow rates, we recreate the impermeable vesicle phase
 diagram for vesicles with a permeability rate of $\beta = 10^{-3}$. The
@@
 
-%
-%\begin{figure}[htp]
-%%  \ifTikz
-%%  \input{figures/stenosisGeom.tikz}
-%%  \fi
-%  \includegraphics[width=\linewidth]{figures/stenosisGeom.pdf}
-%  \caption{\label{fig:stenosisGeom} A single semi-permeable vesicle
-%  passing through a constriction. The geometry and parameters are chosen
-%  to replicate the experiments of Abkarian et
-%  al.~\cite{abk-fai-sto2006}.}
-%\end{figure}
-%
-%\begin{figure}[htp]
-%%  \ifTikz
-%%  \input{figures/stenosisPressureFluctuation.tikz}
-%%  \fi
-%  \includegraphics[width=\linewidth]{figures/stenosisPressureFluctuation.pdf}
-%  \caption{\label{fig:stenosisPressure} The excess pressure across the
-%  constriction in Figure~\ref{fig:stenosisGeom}. The black dashed lines
-%  denote the start and end of the constriction. The results are
-%  qualitative agreement with~\cite{abk-fai-sto2006}.}
-%\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection*{Semi-Permeable Vesicle in a Contracting Geometry} 
+We expose a single semi-permeable vesicle to even larger deformations by
+simulating its hydrodynamics in a contracting microfluidic geometry.
+Similar to~\cite{wu2015critical}, we consider a channel whose width
+gradually reduces from $16\mu$m to $1.6\mu$m and then immediately opens
+again to $16\mu$m (Figure~\ref{fig:contractingComposite}). We impose a
+Poiseuille flow at the inlet and outlet with a constant maximum flow
+rate of $U_{\max}$. We initialize a semi-permeable vesicle with $\alpha
+= 0.65$ that spans $10\mu$m of the total channel width and investigate
+the effects of the permeability rate and the maximum flow velocity. We
+color the vesicle according to the sign of its flux---fluid flows into
+the vesicle in red regions and out of the vesicle in blue regions.
+
+In Figures~\ref{fig:contractingComposite}a
+and~\ref{fig:contractingComposite}b, we plot snapshots of vesicles with
+different permeability rates, and Figure~\ref{fig:contractingComposite}c
+shows that the reduced area as a function of the vesicles' location. For
+sufficiently large permeability rates, the vesicle initially inflates,
+but then deflates as it passes through the constriction. However, if the
+semi-permeability rate is too low, the vesicle is too large when it
+reaches the narrowest part of the channel, and it is unable to pass. In
+Figures~\ref{fig:contractingComposite}d
+and~\ref{fig:contractingComposite}e, we plot snapshots of vesicles with
+different imposed maximum velocities, and
+Figure~\ref{fig:contractingComposite}f shows that the reduced area as a
+function of the vesicles' location. At low velocities, the vesicle
+inflates similar to the unbounded parabolic flow example, and it is
+unable to pass through the constrictions. However, higher flow rates
+result in additional deflation and the vesicle passes through the
+contraction.
+
+To understand long term effects of a vesicle passing through a
+contracting geometry, in Figures~\ref{fig:contractingComposite}g we
+simulate a vesicle passing six times through the contracting geometry.
+In Figure~\ref{fig:contractingComposite}h, we show that the vesicle
+deflates each time it passes through the constriction followed by a
+rapid inflation. The total area loss over the history of the vesicle is
+almost 50\%. In Figure~\ref{fig:contractingComposite}i, we show the
+vesicle velocity as a function of the vesicle's center of mass. As the
+vesicle passes through the contraction, it accelerates followed by a
+rapid deacceleration once it has passed through the contraction.
 
@@
   \centering
-%  \ifTikz
+  \ifTikz
   \input{figures/contractingComposite.tikz}
-%  \fi
+  \else
+  \includegraphics{figures/contractingComposite.pdf}
+  \fi
   \caption{\label{fig:contractingComposite} (a) A semi-permeable vesicle
   passing through a contracting geometry similar to the experimental
-  device in~\cite{}. The narrowest part of the channel is $1.6\mu$m, and
-  the vesicle height is initially $10\mu$m.}
+  device in~\cite{}. The narrowest part of the channel is $1.6\mu$m, 
+  the vesicle height is initially $10\mu$m, and the maximum background
+  flow velocity is $316\mu$m/s. The fluid flux along the red regions is
+  into the vesicle, and the fluid flux along the blue regions is out of
+  the vesicle.}
 \end{figure*}

### 2020-12-17 vesicle_code/docs/permeableVes/main.tex

@@
 %Having validated our method, we investigate the dynamics of a semi-permeable vesicle in a Poiseuille flow.
+
+Using several initial
+$U(1-(y/W)^2,0)$, where $U$ is the maximum imposed velocity. We examine
+the effect of the non-linear Poiseuille flow on the migration of
+semi-permeable vesicle. In this experiment, the vesicle is initialized
+above the center line $y=0$, and it migrates towards the center
+line~\cite{dan-vla-mis2009}. For an impermeable vesicle, depending on
+the vesicles reduced area and the flow rate, the long time vesicle shape
+is either an axisymmetric parachute or bullet, or an asymmetric
+tank-treading slipper~\cite{kao-bir-mis2009}. To validate our methods,
+in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
+for the steady state shape of an impermeable vesicle
+vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
+qualitatively agree, Kaoui et al.~report that the vesicles with
+$\alpha=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
+axisymmetric. In our simulations these vesicles are slightly asymmetric,
+are undergoing a tank treading motion, and we therefore report them as
+asymmetric slippers.
+
 Using several initial reduced areas and flow rates, we recreate the impermeable vesicle phase
@@
 areas. We report the steady state reduced area in
-Figure~\ref{fig:parabolicComposite}(a). At the smallest flow rate of $U
-= 200 \mu m/s$, the steady state reduced area is large, and the result
+Figure~\ref{fig:parabolicComposite}(a). At the smallest flow rate of $U= 200 \mu m/s$, the steady state reduced area is large, and the result
 is an axisymmetric bullet. At the larger flow rates, the steady state

### 2020-12-17 vesicle_code/docs/permeableVes/main.tex
yny

@@
 \affil[a]{Department of Scientific Computing, Florida State University}
-\affil[b]{Department of Mathematical Sciences, New Jeresy Institute of
+\affil[b]{Department of Mathematical Sciences, New Jersey Institute of
 Technology}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Semi-Permeable Vesicle in Stenosis}
+\subsection*{Semi-Permeable Vesicle in a Narrow Channel (Stenosis)}
 Cells experience stretching and release messengers when they pass through capillary vessels \cite{Wan2008_PNAS,ForsythWan2011_PNAS,Pak2015_PNAS}.
-Many cells exhibit extraordinary flexibility as they go through narrow channels \cite{AuStoreyMoore2016_PNAS}, and adjustment of area to volume ratio may be a key factor for successful passages.
-Here we quantify the effect of water permeability on a vesicle going through a stenosis (a long microfluidic channel with a cross section smaller than the cell radius).
+Many cells exhibit extraordinary flexibility as they go through narrow channels \cite{AuStoreyMoore2016_PNAS}, and adjustment of area to volume ratio may be a key factor for a successful passage.
+Here we quantify the effect of water permeability on a vesicle going through a stenosis (a long microfluidic channel with a width smaller than the cell radius).
 Based on the findings in 
@@
 the residency time of the RBC in the constriction agrees with the
-experimental results. When the RBC enters the constriction, the result
-is an increase in the pressure drop required to maintain a constant flow
-rate, and the difference between these pressures is called the excess
-pressure. We consider both an impermeable and semi-permeable vesicle
+experimental results. When the RBC enters the channel, an increase in the pressure drop is required to maintain a constant flow
+rate, and the difference in the pressure drop is called the excess
+pressure.
+
+We consider both an impermeable and semi-permeable vesicle
 with initial reduced area $\alpha = 0.65$ passing through a constricted
-geometry and compute the pressure drop between the inlet and outlet of
-the constriction. In Figure~\ref{fig:stenosisComposite}(c), we plot the
-excess pressures. The impermeable case agrees with experimental
-results~\cite{abk-fai-sto2006} (see Figure 3), and the results indicate
-that less pressure is required to maintain a constant flow rate when the
+geometry and compute the excess pressure as a function of vesicle position in the channel, see Figure~\ref{fig:stenosisComposite}(c). 
+The impermeable case agrees with experimental
+results in Figure 3 of \cite{abk-fai-sto2006}, and the results indicate
+that less excess pressure is required to maintain a constant flow rate when the
 vesicle is semi-permeable. Our simulations indicate the
@@
 Figure~\ref{fig:stenosisComposite}(b), we consider a vesicle passing
-through a much longer constriction, and we observe that the reduced area
+through a channel of double the length, and we observe that the reduced area
 decreases by 13.2\% (Figure~\ref{fig:stenosisComposite}(e)).
@@
 \subsection*{Semi-Permeable Vesicle in a Contracting Geometry} 
-We expose a single semi-permeable vesicle to even larger deformations by
-simulating its hydrodynamics in a contracting microfluidic geometry.
-Similar to~\cite{wu2015critical}, we consider a channel whose width
-gradually reduces from $16\mu$m to $1.6\mu$m and then immediately opens
-again to $16\mu$m (Figure~\ref{fig:contractingComposite}). We impose a
-Poiseuille flow at the inlet and outlet with a constant maximum flow
+Squeezing a cell or an elastic vesicle through a slit in microfluidics has gained popularity for its application in stress-induced release of macromolecules
+\cite{ShareiEtAl2013_PNAS,Pak2015_PNAS,ZhangShenHoganBarakatMisbah2018_BJ,LuoBai2019_PoF}.
+RBCs go through submicron slits many times during their lifetime, and such process selects healthy, flexible RBCs to survive \cite{wu2015critical,LuPeng2019_PoF}.
+Here we investigate the role of membrane permeability to water when a cell is squeezed through a contracting microfluidic channel similar to~\cite{wu2015critical},
+where the width of the channel gradually decreases from $16\mu$m to $1.6\mu$m. The channel then immediately opens
+again to $16\mu$m (Figure~\ref{fig:contractingComposite}). A
+Poiseuille flow is imposed at the inlet and outlet with a constant maximum flow
 rate of $U_{\max}$. We initialize a semi-permeable vesicle with $\alpha
@@
 and~\ref{fig:contractingComposite}b, we plot snapshots of vesicles with
-different permeability rates, and Figure~\ref{fig:contractingComposite}c
-shows that the reduced area as a function of the vesicles' location. For
-sufficiently large permeability rates, the vesicle initially inflates,
-but then deflates as it passes through the constriction. However, if the
+different permeability rates and membrane is color coded by the permeable flux (red for influx and blue for eflux).
+Figure~\ref{fig:contractingComposite}c
+shows the corresponding reduced area as a function of the vesicles' location. 
+The reduced area in Figure~\ref{fig:contractingComposite}c and f shows that the vesicle always inflates
+before it reaches the neck.  However, if the
 semi-permeability rate is too low, the vesicle is too large when it
@@
 
-To understand long term effects of a vesicle passing through a
-contracting geometry, in Figures~\ref{fig:contractingComposite}g we
-simulate a vesicle passing six times through the contracting geometry.
+To understand the effects of water permeability on cells that repeatedly go through micro-capillary vessels or sub-micron slits, 
+we construct a contracting geometry (see Figures~\ref{fig:contractingComposite}g)
+to simulate a vesicle passing through the contracting geometry six times.
 In Figure~\ref{fig:contractingComposite}h, we show that the vesicle

### 2020-12-17 vesicle_code/docs/permeableVes/main.tex
yny2

@@
 and~\ref{fig:contractingComposite}b, we plot snapshots of vesicles with
-different permeability rates and membrane is color coded by the permeable flux (red for influx and blue for eflux).
+different permeability rates. 
 Figure~\ref{fig:contractingComposite}c
 shows the corresponding reduced area as a function of the vesicles' location. 
-The reduced area in Figure~\ref{fig:contractingComposite}c and f shows that the vesicle always inflates
-before it reaches the neck.  However, if the
+The reduced area in Figure~\ref{fig:contractingComposite}c and f shows that the vesicle always inflates gradually
+before it reaches the neck, where vesicle quickly deflates.  
+{\bf YNY: inflates over seconds but deflates over ms?}
+However, if the
 semi-permeability rate is too low, the vesicle is too large when it

### 2020-12-18 vesicle_code/docs/permeableVes/main.tex
adjusted line size and created stenosis in pdf format
yny

@@
 We consider both an impermeable and semi-permeable vesicle
-with initial reduced area $\alpha = 0.65$ passing through a constricted
-geometry and compute the excess pressure as a function of vesicle position in the channel, see Figure~\ref{fig:stenosisComposite}(c). 
+with initial reduced area $\alpha = 0.65$ passing through a long narrow channel
+and compute the excess pressure as a function of vesicle position in the channel, see Figure~\ref{fig:stenosisComposite}(c). 
 The impermeable case agrees with experimental
@@
 that less excess pressure is required to maintain a constant flow rate when the
-vesicle is semi-permeable. Our simulations indicate the
+vesicle is semi-permeable.
+First we note that the vesicle deflates from the beginning due to the high flow velocity, consistent with the results for a vesicle in a Poiseuille flow in open space.
+{\bf YNY: What is the flow velocity in the inlet/outlet?
+need to specify these to make connection to the phase diagram in the Poiseuille flow section.}
+As the vesicle enters the stenosis channel, the vesicle continues to deflate in the front even though we observe influx (red segment) at various rear locations in the membrane. 
+These results are consistent with the results in \cite{Pak2015_PNAS} where the membrane tension is sufficiently large in the front of the vesicle as it goes through a constrictive channel.
+
+Our simulations indicate the
 semi-permeability does affect the excess pressure, and the vesicle's

### 2020-12-20 vesicle_code/docs/permeableVes/main.tex
cleaned up contractin example

@@
 \begin{figure*}[htp]
-%  \ifTikz
+  \ifTikz
   \input{figures/stenosisComposite.tikz}
-%  \fi
+  \else
+  \includegraphics{figures/stenosisComposite.pdf}
+  \fi
   \caption{\label{fig:stenosisComposite} (a) A semi-permeable vesicle
@@
 
+\begin{itemize}
+  \item Vesicle velocity in plot (a) varies from 5 to 24 microns/s
+  \item Vesicle velocity in plot (b) varies from 5 to 28 microns/s
+  \item Vesicle velocity in plot (c) varies from 0.2 to 2 microns/s
+  \item Vesicle velocity in plot (d) varies from 5 to 25 microns/s
+  \item Vesicle velocity in plot (g) varies from 14 to 95 microns/s (see
+    plot (i))
+\end{itemize}
+
 \begin{figure*}[htp]
   \centering
-  \ifTikz
+%  \ifTikz
   \input{figures/contractingComposite.tikz}
-  \else
-  \includegraphics{figures/contractingComposite.pdf}
-  \fi
-  \caption{\label{fig:contractingComposite} (a) A semi-permeable vesicle
-  passing through a contracting geometry similar to the experimental
-  device in~\cite{}. The narrowest part of the channel is $1.6\mu$m, 
-  the vesicle height is initially $10\mu$m, and the maximum background
-  flow velocity is $316\mu$m/s. The fluid flux along the red regions is
-  into the vesicle, and the fluid flux along the blue regions is out of
-  the vesicle.}
+%  \else
+%  \includegraphics{figures/contractingComposite.pdf}
+%  \fi
+  \caption{\label{fig:contractingComposite} A contracting geometry
+  similar to the experimental device in~\cite{wu2015critical}. The
+  channel width varies from $18\mu$m to $1.8\mu$m, and it repeats every
+  $45\mu$m. The fluid flux along the red regions is into the vesicle,
+  and the fluid flux along the blue regions is out of the vesicle.
+  (a--c) The ability for a semi-permeable vesicle to pass through the
+  constriction depends on the semi-permeability rate. (d--f) The ability
+  for a semi-permeable vesicle to pass through the constriction depends
+  on the flow rate. (g) A semi-permeable vesicle passing through six
+  periods of the constricting geometry. (h) The reduced area with the
+  marks representing shapes in (g). (i) The vesicle velocity with the
+  marks representing shapes in (g).}
 \end{figure*}

### 2020-12-20 vesicle_code/docs/permeableVes/main.tex
yny

--- 2020-12-18 vesicle_code/docs/permeableVes/main.tex
@@
 The cell membrane is permeable to water and water-soluble molecules \cite{Dick1964_JTB,FettiplaceHaydon1980_PhysRev,DeamerBramhall1986_ChemPhysLipids,Grafmueller2019_ABLS}. 
-In the presence of an osmotic gradient across the membrane (such as a contrast in the concentration of an impermeable solute), water flows against the osmotic gradient  to neutralize the osmolarity.
+%
+%In the presence of an osmotic gradient across the membrane (such as a contrast in the concentration of an impermeable solute), water flows against the osmotic gradient  to neutralize the osmolarity. 
+%
 Without aquaporins or other membrane channels that promotes water permeability, the intrinsic water permeability is known to depend on the temperature \cite{OlbrichRawiczNeedhamEtAl2000_BJ}, lipid composition \cite{OlbrichRawiczNeedhamEtAl2000_BJ}, and the hydration  energy of the membrane \cite{MarrinkBerendsen1994_JPhysChem}.
@@
 %
-The swelling/shrinking of a cell is inevitably coupled to changes in membrane tension and cell shape \cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}.  
+The swelling/shrinking of a cell is inevitably coupled to changes in membrane tension and deformation.
+Under a strong confinement (such as going through a microcapillary or submicron slit),  the transmembrane water flow may have comparable contributions from both osmotic and mechanical stresses \cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}.
+Furthermore, molecular dynamic (MD) and coarse-grained (CG) MD simulations show that membrane poration is inevitable when membrane tension is of the order of $2-4$ mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references therein).
+%The CGMD results further show that a stretched RBC membrane may have pores that might contribute to transmembrane transport of both water and ATP molecules \cite{RazizadehNikfarPaulLiu2020_BJ}. 
+Thus an important outstanding question in stress-induced ATP release of highly deformed RBCs is if there is any transmembrane flow when RBCs release ATP as they experience large
+mechanical load due to confinement or large shear stress?  To address such question, the first step we take is to focus on the permeable water flux induced by mechanical stress.
+%
+%RBCs are known to release ATP under large deformation and microfluidic experiments have been used to study the correlation between RBC deformation and ATP release \cite{Wan2008_PNAS,ForsythWan2011_PNAS,ZhangShenHoganBarakatMisbah2018_BJ}.
+%
+%Why is it interesting to study the dynamics of a semi-permeable membrane induced by mechanical stress/confinement?
+%
 %The osmolarity-induced water flux has been well studied, while mechanical pressure may also contribute to the permeable water flow \cite{yao-mor2017}.

### 2020-12-20 vesicle_code/docs/permeableVes/main.tex
yny

@@
 
-\dropcap{W}ater balance is an essential process in the adaptation of a living cell to its environment \cite{AlbertsMolecularBiology}: Erythrocytes are known to  participate in efficient body water homeostasis by regulating its exchange of water  \cite{YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP}.
+\dropcap{W}ater balance is an essential process in the adaptation of a living cell to its environment \cite{AlbertsMolecularBiology,YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP,SaadounPapadopoulosWatanabeEtAl2005_JCS,Verkman2008_JMM,BerthaudEtAl2016_SM,Keren2011_EurBJ,TaloniKardashSalmanEtAl2015_PRL}.
+In response to external stimuli, cells move, deform, and release signaling molecules, such as ATP in red blood cells \cite{ZhangShenHoganBarakatMisbah2018_BJ} and cyclooxygenase-2 in endothelial cells \cite{Russell-PuleriPazAdams2016_AJHCP}.
+Water permeation is often assumed to play a negligible role in such chemomechanical processes, and yet recent findings suggest that both osmotic and mechanical stresses can induce water permeation that is significant enough for tumor cells to migrate under strong confinement \cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}, leading to a dynamic surface-to-volume ratio over time.
+To elucidate the effects of mechanically induced water permeation (which is a great challenge to quantify in experiments), in this work we use accurate numerical simulations to study the dynamic surface-to-volume ratio in a semi-permeable vesicle induced by mechanical stress.
+
+%Cells also send out chemicals in response to 
+%
+% Erythrocytes are known to  participate in efficient body water homeostasis by regulating its exchange of water  \cite{YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP}.
 Cells achieve motility by simultaneously regulating their cell volume and cell membrane tension through trafficking of aquaporin proteins \cite{SaadounPapadopoulosWatanabeEtAl2005_JCS,Verkman2008_JMM,BerthaudEtAl2016_SM} and flattening of caveolae \cite{Keren2011_EurBJ}.
-Cells also control water transport  as they activate shape fluctuations in the membrane for the bleb formation \cite{TaloniKardashSalmanEtAl2015_PRL}.
+%Cells also control water transport  as they activate shape fluctuations in the membrane for the bleb formation \cite{TaloniKardashSalmanEtAl2015_PRL}.
+%
+%
+%%\dropcap{W}ater balance is an essential process in the adaptation of a living cell to its environment \cite{AlbertsMolecularBiology}: Erythrocytes are known to  participate in efficient body water homeostasis by regulating its exchange of water  \cite{YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP}.
+Cells achieve motility by simultaneously regulating their cell volume and cell membrane tension through trafficking of aquaporin proteins \cite{SaadounPapadopoulosWatanabeEtAl2005_JCS,Verkman2008_JMM,BerthaudEtAl2016_SM} and flattening of caveolae \cite{Keren2011_EurBJ}.
+%%Cells also control water transport  as they activate shape fluctuations in the membrane for the bleb formation \cite{TaloniKardashSalmanEtAl2015_PRL}.
 
@@
  vesicle shape changes, tank-treading and tumbling motions \cite{BhatiaRobinsonDimova2020_SoftMatt,BhatiaChrist2020_SoftMatt}, an illustration that the permeable water flow is inevitably coupled with the mechanical pressure jump across the membrane\cite{yao-mor2017}, which could become comparable to osmotic stress when the membrane deformation is large \cite{LiMoriSun2015_PRL,yao-mor2017}.
+
  In this work we use numerical simulations to examine the hydrodynamics of a semipermeable vesicle in two dimensions. 

### 2020-12-21 vesicle_code/docs/permeableVes/main.tex
added some flow velocities to stenosis example

@@
 
-We consider both an impermeable and semi-permeable vesicle
-with initial reduced area $\alpha = 0.65$ passing through a long narrow channel
-and compute the excess pressure as a function of vesicle position in the channel, see Figure~\ref{fig:stenosisComposite}(c). 
-The impermeable case agrees with experimental
-results in Figure 3 of \cite{abk-fai-sto2006}, and the results indicate
-that less excess pressure is required to maintain a constant flow rate when the
-vesicle is semi-permeable.
-First we note that the vesicle deflates from the beginning due to the high flow velocity, consistent with the results for a vesicle in a Poiseuille flow in open space.
-{\bf YNY: What is the flow velocity in the inlet/outlet?
-need to specify these to make connection to the phase diagram in the Poiseuille flow section.}
-As the vesicle enters the stenosis channel, the vesicle continues to deflate in the front even though we observe influx (red segment) at various rear locations in the membrane. 
-These results are consistent with the results in \cite{Pak2015_PNAS} where the membrane tension is sufficiently large in the front of the vesicle as it goes through a constrictive channel.
+We consider both an impermeable and semi-permeable vesicle with initial
+reduced area $\alpha = 0.65$ passing through a long narrow channel and
+compute the excess pressure as a function of vesicle position in the
+channel, see Figure~\ref{fig:stenosisComposite}(c). A constant
+Poiseuille velocity with a maximum value of $1000\mu$m/s is maintained
+at the inlet and outlet. The impermeable case agrees with experimental
+results in Figure 3 of~\cite{abk-fai-sto2006}, and the results indicate
+that less excess pressure is required to maintain a constant flow rate
+when the vesicle is semi-permeable. First we note that the vesicle
+deflates from the beginning due to the high flow velocity, consistent
+with the results for a vesicle in a Poiseuille flow in open space. As
+the vesicle enters the stenosis channel, the vesicle continues to
+deflate in the front even though we observe influx (red segment) at
+various rear locations in the membrane.  These results are consistent
+with the results in~\cite{Pak2015_PNAS} where the membrane tension is
+sufficiently large in the front of the vesicle as it goes through a
+constrictive channel.
 

### 2020-12-21 vesicle_code/examples/choke1Ves.m

@@ -6,11 +6,11 @@ fprintf('Implicit vesicle-vesicle interactions.\n');
 fprintf('Implicit vesicle-boundary interactions.\n');
 
 %format long
-prams.N = 192;                 % points per vesicle
+prams.N = 256;                 % points per vesicle
 prams.nv = 1;                  % number of vesicles
-prams.T = 0.1;                  %time horizon
+prams.T = 30;                  %time horizon
 prams.m = 12000;                % number of time steps
-prams.Nbd = 1024;               % number of points on solid wall
+prams.Nbd = 2048;               % number of points on solid wall
 prams.nvbd = 1;                % number of components to solid walls
 prams.kappa = 1e0;            % bending coefficient
 prams.viscCont = 1*ones(prams.nv,1);            % viscosity contrast
@@ -25,9 +25,9 @@ options.semipermeable = true;
 prams.fluxCoeff = 1e-3;
 options.fluxShape = 1; % constant value
 
-options.farField = 'chokeLonger';      % Constricted domain
-options.farFieldSpeed = 4200;
-%options.farFieldSpeed = 4.2;
+options.farField = 'chokeLongest';      % Constricted domain
+%options.farFieldSpeed = 500;
+options.farFieldSpeed = 4.2;
 % background velocity or solid walls (which comes with a default
 % boundary condition)
 options.vesves = 'implicit';
@@ -68,12 +68,12 @@ prams.alpha = 0.9;
 % Also add src to path
 
 oc = curve;
-X = oc.initConfig(prams.N,'nv',prams.nv,'angle',-pi/3,...
+%X = oc.initConfig(prams.N,'nv',prams.nv,'angle',-pi/3,...
+%   'scale',1.44,...
+%   'center',[[-45;5]],'reducedArea',0.65);
+X = oc.initConfig(prams.N,'nv',prams.nv,'angle',pi/2,...
    'scale',1.44,...
-   'center',[[-45;5]],'reducedArea',0.65);
-%X = oc.initConfig(prams.N,'nv',prams.nv,'angle',pi/2,...
-%   'scale',1,...
-%   'center',[[-45;0]],'reducedArea',0.65);
+   'center',[[-105;5]],'reducedArea',0.65);
 
 % load chokeIC
 Xwalls = oc.initConfig(prams.Nbd,options.farField);

### 2020-12-21 vesicle_code/docs/permeableVes/main.tex
another note about flow rate
added a few todos

@@
 \end{figure*}
+\todo[inline]{put a vertical dashed line at the times when permeability
+starts to be important. Convert to physical time.}
 
@@
 
-Our simulations indicate the
-semi-permeability does affect the excess pressure, and the vesicle's
-reduced area reduces by about 6.1\%
+Our simulations indicate the semi-permeability does affect the excess
+pressure, and the vesicle's reduced area reduces by about 6.1\%
 (Figure~\ref{fig:stenosisComposite}(d)). Since the area does decrease at
@@
 Figure~\ref{fig:stenosisComposite}(b), we consider a vesicle passing
-through a channel of double the length, and we observe that the reduced area
-decreases by 13.2\% (Figure~\ref{fig:stenosisComposite}(e)).
+through a channel of double the length, and we observe that the reduced
+area decreases by 13.2\% (Figure~\ref{fig:stenosisComposite}(e)).
+\todo[inline]{This example also used a smaller flow rate of $8.4\mu$m/s}
+\todo[inline]{Membrane tension. Look at each of the five cases and find
+the instance where tension reaches its max value. Plot the tension as
+the colorbar along the vesicle shape.}
 
@@
 \end{itemize}
+\todo[inline]{Center of mass vs.~time}
+\todo[inline]{Membrane tension. Look at each of the five cases and find
+the instance where tension reaches its max value. Plot the tension as
+the colorbar along the vesicle shape.}
 

### 2020-12-22 vesicle_code/docs/permeableVes/main.tex
added pics of tension for stenosis runs
yny

@@
 
-\dropcap{W}ater balance is an essential process in the adaptation of a living cell to its environment \cite{AlbertsMolecularBiology,YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP,SaadounPapadopoulosWatanabeEtAl2005_JCS,Verkman2008_JMM,BerthaudEtAl2016_SM,Keren2011_EurBJ,TaloniKardashSalmanEtAl2015_PRL}.
-In response to external stimuli, cells move, deform, and release signaling molecules, such as ATP in red blood cells \cite{ZhangShenHoganBarakatMisbah2018_BJ} and cyclooxygenase-2 in endothelial cells \cite{Russell-PuleriPazAdams2016_AJHCP}.
-Water permeation is often assumed to play a negligible role in such chemomechanical processes, and yet recent findings suggest that both osmotic and mechanical stresses can induce water permeation that is significant enough for tumor cells to migrate under strong confinement \cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}, leading to a dynamic surface-to-volume ratio over time.
-To elucidate the effects of mechanically induced water permeation (which is a great challenge to quantify in experiments), in this work we use accurate numerical simulations to study the dynamic surface-to-volume ratio in a semi-permeable vesicle induced by mechanical stress.
+\dropcap{W}ater exchange is essential as a living cell adapts to its environment \cite{AlbertsMolecularBiology,YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP,SaadounPapadopoulosWatanabeEtAl2005_JCS,Verkman2008_JMM,BerthaudEtAl2016_SM,Keren2011_EurBJ,TaloniKardashSalmanEtAl2015_PRL}.
+%
+%Water permeation across the cell membrane due to an osmotic shock has been well studied \cite{AlbertsMolecularBiology}. 
+Recent findings suggest that both osmotic and mechanical stresses can induce water permeation that is significant enough for cells to migrate under strong confinement \cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}, leading to a dynamic surface-to-volume ratio of the migrating cell.
+While stress-induced release of messengers in cells has been well studied \cite{Wan2008_PNAS, ForsythWan2011_PNAS,Russell-PuleriPazAdams2016_AJHCP,ZhangShenHoganBarakatMisbah2018_BJ,GordonShimmelFrye2020_FP},
+%osmotic effects on cellular dynamics have been well studied \cite{AlbertsMolecularBiology}, 
+mechanically induced water permeation is often associated with membrane poration or rupture under extreme stresses \cite{RazizadehNikfarPaulLiu2020_BJ}.
+In this work we use modeling and state-of-the-art numerical simulations to show that the intrinsic membrane permeability to water can give rise to significantly distinct hydrodynamics of a semipermeable vesicle without poration or rupture in the membrane.
+%
+%
+%One of the most direct ways to induce water permeation across cell membranes is to impose an osmotic shock }.
+%
+%A gradient in the osmotic stress across the cellular membrane is the most direct way to induce water permeation, yet 
+%%
+%%In response to external stimuli, cells move, deform, and release signaling molecules, such as ATP in red blood cells \cite{ZhangShenHoganBarakatMisbah2018_BJ} and cyclooxygenase-2 in endothelial cells \cite{Russell-PuleriPazAdams2016_AJHCP}.
+%%
+%%Water permeation is often neglected in such release processes, yet 
+%%
+%recent findings suggest that both osmotic and mechanical stresses can induce water permeation that is significant enough for tumor cells to migrate under strong confinement \cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}, leading to a dynamic surface-to-volume ratio over time.
+%
+%
+%To elucidate the effects of mechanically induced water permeation (which is a great challenge to quantify in experiments), in this work we use accurate numerical simulations to study the hydrodynamics of a semi-permeable vesicle in various configurations.
 
@@
 %
-The swelling/shrinking of a cell is inevitably coupled to changes in membrane tension and deformation.
+%The swelling/shrinking of a cell is inevitably coupled to changes in membrane tension and deformation.
 Under a strong confinement (such as going through a microcapillary or submicron slit),  the transmembrane water flow may have comparable contributions from both osmotic and mechanical stresses \cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}.
-Furthermore, molecular dynamic (MD) and coarse-grained (CG) MD simulations show that membrane poration is inevitable when membrane tension is of the order of $2-4$ mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references therein).
-%The CGMD results further show that a stretched RBC membrane may have pores that might contribute to transmembrane transport of both water and ATP molecules \cite{RazizadehNikfarPaulLiu2020_BJ}. 
-Thus an important outstanding question in stress-induced ATP release of highly deformed RBCs is if there is any transmembrane flow when RBCs release ATP as they experience large
-mechanical load due to confinement or large shear stress?  To address such question, the first step we take is to focus on the permeable water flux induced by mechanical stress.
-%
-%RBCs are known to release ATP under large deformation and microfluidic experiments have been used to study the correlation between RBC deformation and ATP release \cite{Wan2008_PNAS,ForsythWan2011_PNAS,ZhangShenHoganBarakatMisbah2018_BJ}.
-%
-%Why is it interesting to study the dynamics of a semi-permeable membrane induced by mechanical stress/confinement?
-%
-%The osmolarity-induced water flux has been well studied, while mechanical pressure may also contribute to the permeable water flow \cite{yao-mor2017}.
-%The response of a cell to an osmotic gradient is inevitably both mechanical (tension redistribution and shape change) and chemical (water flux across the membrane).  
-In this work we focus on the intrinsic water permeability and study the subtle balance between hydrodynamics, tension and elasticity of a semipermeable membrane under various flowing conditions and confinement.
-
+Molecular dynamic (MD) 
+%and coarse-grained (CG) MD 
+simulations show that a stretched RBC membrane may porate when membrane tension reaches the order of $2-4$ mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references therein), giving rise to enhanced membrane permeability to both water and macromolecules.
+Consequently under conditions where membrane remains intact (no poration or rupture), RBCs and vesicles are assumed to be of the same volume throughout the experiments no longer than tens of minutes.
+%
+%membrane poration is inevitable when membrane tension is of the order of $2-4$ mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references therein). 
+%%The CGMD results further show that a stretched RBC membrane may have pores that might contribute to transmembrane transport of both water and ATP molecules \cite{RazizadehNikfarPaulLiu2020_BJ}. 
+%Thus an important outstanding question in stress-induced ATP release of highly deformed RBCs is if there is any transmembrane flow when RBCs release ATP as they experience large
+%mechanical load due to confinement or large shear stress?  To address such question, the first step we take is to focus on the permeable water flux induced by mechanical stress.
+%%
+%%RBCs are known to release ATP under large deformation and microfluidic experiments have been used to study the correlation between RBC deformation and ATP release \cite{Wan2008_PNAS,ForsythWan2011_PNAS,ZhangShenHoganBarakatMisbah2018_BJ}.
+%%
+%%Why is it interesting to study the dynamics of a semi-permeable membrane induced by mechanical stress/confinement?
+%%
+%%The osmolarity-induced water flux has been well studied, while mechanical pressure may also contribute to the permeable water flow \cite{yao-mor2017}.
+%%The response of a cell to an osmotic gradient is inevitably both mechanical (tension redistribution and shape change) and chemical (water flux across the membrane).  
+Under what condition is this a good assumption? What is the dynamic consequence when permeable water flux affects the membrane hydrodynamics?
+To answer these questions, we investigate the balance between hydrodynamics, tension and elasticity of a semipermeable membrane under various flowing conditions and confinement. 
+%Specifically our numerical simulations yield the quantification of the time scale and length scale over which water permeation becomes important.
+
+ In this work we use numerical simulations to examine the hydrodynamics of a semipermeable vesicle in two dimensions. 
 Vesicles (self-enclosed lipid bilayer membranes) have been used as a model system to study reshaping, remodeling and scission of cell membranes due to osmotic stress \cite{OgleckaEtAl2014_eLife,CamposSaric2020_bioRxiv,Dimova2020_GVB,BhatiaChrist2020_SoftMatt}.
@@
  vesicle shape changes, tank-treading and tumbling motions \cite{BhatiaRobinsonDimova2020_SoftMatt,BhatiaChrist2020_SoftMatt}, an illustration that the permeable water flow is inevitably coupled with the mechanical pressure jump across the membrane\cite{yao-mor2017}, which could become comparable to osmotic stress when the membrane deformation is large \cite{LiMoriSun2015_PRL,yao-mor2017}.
-
- In this work we use numerical simulations to examine the hydrodynamics of a semipermeable vesicle in two dimensions. 
- It is challenging to keep a freely suspended vesicle in a steady flow for more than a few days. It is also difficult to quantify the change in vesicle area/volume in the experiments.
+ In microfluidic experiments, it is challenging to keep a freely suspended vesicle in a steady flow for more than a few hours.
+It is also difficult to quantify the vesicle area/volume ratio accurately.
 Using numerical simulations we can quantify  the effects of water permeability on the hydrodynamics of a vesicle under mechanical stresses.
@@
 is the arclength along the membrane, see figure~\ref{fig:schematics}.
-Using $k_w\sim 10^{-12}$ m$^2$s/kg (typical of mammalian cell membranes \cite{LiMoriSun2015_PRL}) and an osmolarity $\triangle c = 1$ mol/L (consistent with the osmotic forces in vesicle aspiration experiments \cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the corresponding water flow is of the order $v_\mathrm{o}=1 \mu$m/s.
+Using $k_w\sim 10^{-12}$ m$^2$s/kg (typical of mammalian cell membranes \cite{LiMoriSun2015_PRL}) and an osmolarity $\triangle c = 0.1$ mol/L (consistent with the osmotic forces in vesicle aspiration experiments \cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the corresponding water flow is of the order $v_\mathrm{o}=0.1 \mu$m/s.
 Assuming that the membrane bending stiffness $k_b = 10^{-19}$J, a membrane tension $10^{-3}$N/m (one tenth of the lysis tension) and a characteristic length scale of $10^{-6}$m, the tension contribution ($v_\mathrm{t}$) and elastic stress contribution
-($v_\mathrm{e}$) to the permeable water flow can be scaled to $v_\mathrm{o}$ as $v_\mathrm{o}:v_\mathrm{t}:v_\mathrm{e}=1:10^{-3}:10^{-7}$.
+($v_\mathrm{e}$) to the permeable water flow can be scaled to $v_\mathrm{o}$ as $v_\mathrm{o}:v_\mathrm{t}:v_\mathrm{e}=1:10^{-2}:10^{-6}$.
 Furthermore, we note that in the absence of an osmotic stress, the water permeable flow can be significant when the membrane tension is large due to the external stress such as the hydrodynamics stress due to an external flow and/or due to confinement.

### 2020-12-23 vesicle_code/docs/permeableVes/main.tex
converting stenosis to pdf
fixed up some figures and did some todos

@@
 \end{figure*}
-\todo[inline]{put a vertical dashed line at the times when permeability
-starts to be important. Convert to physical time.}
 
@@
 \todo[inline]{This example also used a smaller flow rate of $8.4\mu$m/s}
-\todo[inline]{Membrane tension. Look at each of the five cases and find
-the instance where tension reaches its max value. Plot the tension as
-the colorbar along the vesicle shape.}
 
@@
 \begin{itemize}
-  \item Vesicle velocity in plot (a) varies from 5 to 24 microns/s
-  \item Vesicle velocity in plot (b) varies from 5 to 28 microns/s
-  \item Vesicle velocity in plot (c) varies from 0.2 to 2 microns/s
-  \item Vesicle velocity in plot (d) varies from 5 to 25 microns/s
+  \item Vesicle velocity in plot (a) varies from 5 to 24 microns/s.
+  \item Vesicle velocity in plot (b) varies from 5 to 28 microns/s. Time
+    that vesicle first completely passes through constriction is 4.75s
+  \item Vesicle velocity in plot (c) varies from 0.2 to 2 microns/s.
+  \item Vesicle velocity in plot (d) varies from 5 to 25 microns/s. Time
+    that vesicle first completely passes through constriction is 4.76s
   \item Vesicle velocity in plot (g) varies from 14 to 95 microns/s (see
-    plot (i))
+    plot (i)). Time that vesicle first completely passes through
+    constriction is 1.43s
 \end{itemize}
-\todo[inline]{Center of mass vs.~time}
-\todo[inline]{Membrane tension. Look at each of the five cases and find
-the instance where tension reaches its max value. Plot the tension as
-the colorbar along the vesicle shape.}
 
@@
   \centering
-%  \ifTikz
+  \ifTikz
   \input{figures/contractingComposite.tikz}
-%  \else
-%  \includegraphics{figures/contractingComposite.pdf}
-%  \fi
+  \else
+  \includegraphics{figures/contractingComposite.pdf}
+  \fi
   \caption{\label{fig:contractingComposite} A contracting geometry

### 2020-12-28 vesicle_code/docs/permeableVes/main.tex
added in first template of schematic plot
yny

@@
 
-\dropcap{W}ater exchange is essential as a living cell adapts to its environment \cite{AlbertsMolecularBiology,YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP,SaadounPapadopoulosWatanabeEtAl2005_JCS,Verkman2008_JMM,BerthaudEtAl2016_SM,Keren2011_EurBJ,TaloniKardashSalmanEtAl2015_PRL}.
+\dropcap{W}ater exchange is essential as a living cell adapts to its environment over a wide range of timescales \cite{CadartVenkovaRechoEtAl2019_NaturePhys,AlbertsMolecularBiology,YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP,SaadounPapadopoulosWatanabeEtAl2005_JCS,Verkman2008_JMM,BerthaudEtAl2016_SM,Keren2011_EurBJ,TaloniKardashSalmanEtAl2015_PRL}.
 %
 %Water permeation across the cell membrane due to an osmotic shock has been well studied \cite{AlbertsMolecularBiology}. 
-Recent findings suggest that both osmotic and mechanical stresses can induce water permeation that is significant enough for cells to migrate under strong confinement \cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}, leading to a dynamic surface-to-volume ratio of the migrating cell.
+Recent findings confim that both osmotic and mechanical stresses contribute to significant water permeation for cells to migrate under strong confinement \cite{JiangSun2013_BJ,StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}, leading to a dynamic surface-to-volume ratio of a migrating cell.
 While stress-induced release of messengers in cells has been well studied \cite{Wan2008_PNAS, ForsythWan2011_PNAS,Russell-PuleriPazAdams2016_AJHCP,ZhangShenHoganBarakatMisbah2018_BJ,GordonShimmelFrye2020_FP},
@@
 mechanically induced water permeation is often associated with membrane poration or rupture under extreme stresses \cite{RazizadehNikfarPaulLiu2020_BJ}.
-In this work we use modeling and state-of-the-art numerical simulations to show that the intrinsic membrane permeability to water can give rise to significantly distinct hydrodynamics of a semipermeable vesicle without poration or rupture in the membrane.
+In this work we use modeling and state-of-the-art numerical simulations to show that the intrinsic membrane permeability to water can give rise to significantly distinct hydrodynamics of a semipermeable vesicle without poration or rupture in the lipid bilayer membrane.
 %
@@
 
-The cell membrane is permeable to water and water-soluble molecules \cite{Dick1964_JTB,FettiplaceHaydon1980_PhysRev,DeamerBramhall1986_ChemPhysLipids,Grafmueller2019_ABLS}. 
+The lipid bilayer membrane is permeable to water and water-soluble molecules \cite{Dick1964_JTB,FettiplaceHaydon1980_PhysRev,DeamerBramhall1986_ChemPhysLipids,Grafmueller2019_ABLS}. 
 %
@@
 %
-Without aquaporins or other membrane channels that promotes water permeability, the intrinsic water permeability is known to depend on the temperature \cite{OlbrichRawiczNeedhamEtAl2000_BJ}, lipid composition \cite{OlbrichRawiczNeedhamEtAl2000_BJ}, and the hydration  energy of the membrane \cite{MarrinkBerendsen1994_JPhysChem}.
+Without aquaporins or other membrane channels that promotes water permeability, the intrinsic water permeability is known to depend on the temperature \cite{OlbrichRawiczNeedhamEtAl2000_BJ}, lipid composition \cite{OlbrichRawiczNeedhamEtAl2000_BJ}, and the hydration of the membrane \cite{MarrinkBerendsen1994_JPhysChem}.
 In the red blood cell membrane, aquaporin-1 channels give rise to a much higher water permeability of $\sim 1.8\times 10^{-2}$ cm/s in erythrocytes \cite{YangMaVerkman2001_JBC} while the intrinsic water permeability of a lipid bilayer membrane is in the range of $10^{-4}-10^{-3}$ cm/s \cite{ThompsonHuang1966_ANYAS,FettiplaceHaydon1980_PhysRev,Grafmueller2019_ABLS,Dimova2020_GVB,BhatiaRobinsonDimova2020_SoftMatt}.
@@
 simulations show that a stretched RBC membrane may porate when membrane tension reaches the order of $2-4$ mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references therein), giving rise to enhanced membrane permeability to both water and macromolecules.
-Consequently under conditions where membrane remains intact (no poration or rupture), RBCs and vesicles are assumed to be of the same volume throughout the experiments no longer than tens of minutes.
+Consequently, as long as the lipid bilayer membrane remains intact (no poration or rupture), RBCs and vesicles are assumed to be of the same volume throughout experiments of durations no longer than tens of minutes.
 %
@@
 %%The response of a cell to an osmotic gradient is inevitably both mechanical (tension redistribution and shape change) and chemical (water flux across the membrane).  
-Under what condition is this a good assumption? What is the dynamic consequence when permeable water flux affects the membrane hydrodynamics?
+Under what condition is this a good assumption? What is the dynamic consequence when permeable water flux/eflux affects the membrane hydrodynamics?
 To answer these questions, we investigate the balance between hydrodynamics, tension and elasticity of a semipermeable membrane under various flowing conditions and confinement. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htp]
+  \centering
+   \includegraphics[width=0.475\textwidth]{figures/sketch_sample.png}
+  \caption{\label{fig:sketch} Schematics showing the effects of semipermeability on vesicle hydrodynamics in various configurations.}
+\end{figure}
 \section*{Formulation}
-We consider a two-dimensional semi-permeable vesicle (permeable only to water) suspended in a viscous fluid, see figure~\ref{fig:schematics}.
+We consider a two-dimensional semi-permeable vesicle (permeable only to water) suspended in a viscous fluid, see figure~\ref{fig:sketch}.
 To focus on the effect of water flow on vesicle hydrodynamics in various conditions, we assume the fluid is the same inside and outside the vesicle membrane ($\gamma$) with an outward normal $\nn$.
@@
 and $\ff_\mathrm{mem}$ is the membrane stress that consists of both bending $ \ff_\mathrm{ben}= -k_b \xx_{ssss}$ and tension $\ff_\mathrm{ten}=(\sigma \xx_s)_s$ ($s$
-is the arclength along the membrane, see figure~\ref{fig:schematics}.
+is the arclength along the membrane, see figure~\ref{fig:sketch}.
 Using $k_w\sim 10^{-12}$ m$^2$s/kg (typical of mammalian cell membranes \cite{LiMoriSun2015_PRL}) and an osmolarity $\triangle c = 0.1$ mol/L (consistent with the osmotic forces in vesicle aspiration experiments \cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the corresponding water flow is of the order $v_\mathrm{o}=0.1 \mu$m/s.
@@
 \end{figure*}
-
-Our analysis shows that a semi-permeable vesicle in a quiescent flow
+In a quiescent flow, a semipermeable vesicle in free space can be quantified in terms of its area dynamics and its transition to the equilibrium shape:
+Our analysis in Supplementary Material shows that a semi-permeable vesicle
 relaxes to a circle at a rate that is proportional to $\beta$, and the
-steady state tension is $\Lambda = 2\pi^2/L^2$ (see Supplementary
-Material). Our analysis further shows that the time for a semipermeable
+steady state tension is $\Lambda = 2\pi^2/L^2$. Our analysis further shows that the time for a semipermeable
 vesicle to deviate from its initial reduced area and to reach its steady
@@
 
-In Figure~\ref{fig:relaxationComposite}, we examine the transient
-dynamics of four vesicles with $\beta = 10^{-3}$ and a variety of
-initial configurations. The vesicles on the left are color-coded by the permeable flux: red denotes a flux into the vesicle, and blue denotes a flux out of the vesicle.
-First we observe
-that even though the vesicle is inflating to a circle (meaning that
-there is a net flux into the vesicle), there are regions where the flux
-is out of the vesicle.
-
-For the vesicle with an initial reduced area ($\alpha(0)=0.12$ in the bottom row) we observe that vesicle deflates (blue regions) first due to the high interior capillary pressure.  Over time
-all vesicles inflate and as expected, each vesicle eventually
+In Figure~\ref{fig:relaxationComposite}, we examine the relaxation
+dynamics of a semipermeable vesicle with four initial shapes and reduced areas as labeled.
+%$\beta = 10^{-3}$ and a variety of initial configurations. 
+The vesicles on the left are color-coded by the water permeation flux: red denotes an influx into the vesicle, and blue denotes an efflux out of the vesicle.
+%
+First we observe that the initial vesicle shape determines the direction of water flux.
+For the vesicle with an initial reduced area ($\alpha(0)=0.12$ in the bottom row) the vesicle deflates (blue regions) first due to the high interior capillary pressure that corresponds to the high membrane curvatures.
+For the other three cases efflux is found at some locations of high curvature, while mostly water permeates into the vesicle and significant change in the reduced area is found at $t\sim 10$ minutes.
+Over time (about ten hours) all vesicles inflate and as expected, each vesicle eventually
 reaches a circular shape with reduced area $\alpha=1$. 
-%These regions are denoted in blue and are only present at early times. 
-Finally, the vesicles's reduced area do not steady state tension is
-$\Lambda = 2\pi^2/L^2$. Therefore, the times for
-the vesicle to deviate from its initial reduced area and to reach its
-steady state are proportional to $\beta^{-1}$.
-
-In Figure~\ref{fig:relaxationComposite}, we examine the transient
-dynamics of four vesicles with $\beta = 10^{-3}$ and a variety of
-initial configurations. As expected, each vesicle eventually
-reaches a circular shape with reduced area $\alpha=1$. Next, we observe
-that even though the vesicle is inflating to a circle, meaning that
-there is a net flux into the vesicle, there are regions where the flux
-is out of the vesicle. These regions are denoted in blue and are only
-present at early times. Finally, the vesicles's reduced area do not
-change by much at early times, and intermediate shapes of semi-permeable
+%%These regions are denoted in blue and are only present at early times. 
+%Finally, the vesicles's reduced area do not steady state tension is
+%$\Lambda = 2\pi^2/L^2$. 
+%Therefore, the times for the vesicle to deviate from its initial reduced area and to reach its
+%steady state are proportional to $\beta^{-1}$. 
+%
+%Each of the four cases in Figure~\ref{fig:relaxationComposite} eventually
+%reaches a circular shape with reduced area $\alpha=1$. Next, we observe
+%that even though the vesicle is inflating to a circle, 
+%%meaning that there is a net flux into the vesicle, 
+%there are regions where the flux
+%is out of the vesicle. These regions are denoted in blue and are only
+%present at early times. 
+%
+%Finally, the vesicles's reduced area do not
+%change by much at early times (up to ten minutes), and
+
+Between $t=10$ seconds and $t=10$ minutes, the 
+intermediate shapes of semi-permeable
 vesicles resemble the shape of an impermeable vesicle. This can be
@@
 velocity: (i) the permeability velocity, $\beta(\ff \cdot \nn) \nn$, and
-(ii) the force balance velocity, $\SS[\ff]$. Since $\beta = 10^{-3}$,
+(ii) the force balance velocity, $\SS[\ff]$. Since $\beta = 10^{-6}$,
 the permeability velocity is much smaller than the force balance
@@
 decreases, the permeability velocity dominates, and the vesicle begins
-to inflate to a circle with no vanishing force and velocity. {\bf YNY:
-We should put a tick on the time when this transition occurs for each of
-the vesicles}
+to inflate to a circle with no vanishing force and velocity. 
+%{\bf YNY:We should put a tick on the time when this transition occurs for each of the vesicles}
 
@@
 and viscosity contrast determine whether it tank treads or
-tumbles~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. Similar to the
-dynamics of an impermeable vesicle, a semi-permeable vesicle tilts to an
-inclination angle and undergoes tank treading dynamics. Since we
-consider semi-permeable vesicles, there is no viscosity contrast and
-we do not observe tumbling.
+tumbles~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. 
+Focusing on semi-permeable vesicles with no viscosity contrast, 
+we find that a semi-permeable vesicle tilts to an
+inclination angle and undergoes tank treading dynamics, similar to the case of  an impermeable vesicle.
 
@@
 vesicle shape is independent of the initial reduced area. However, it
-does depend on the flow rate. We also observe small changes in the
-reduced area at early times when the semi-permeable vesicle behaves like
-an impermeable vesicle. However, once the vesicle is tank-treading, the
-normal component of the force-balance velocity is small and the
-permeability velocity dominates and leads to a changing reduced area.
+does depend on the flow rate.  We also observe that the reduced area remains constant until $t\sim 10$ minutes, when
+the vesicle starts to tank-tread and the normal component of the force-balance velocity becomes significantly smaller than the permeable velocity, leading to a changing reduced area.
 
@@
 U(1-(y/W)^2,0)$, where $U$ is the maximum velocity at $y=0$. The non-linear effects of the Poiseuille flow
-on the migration of an impermeable vesicle have been well-studied \cite{kao-bir-mis2009}: At a given value of $U$,
+on the migration of an impermeable vesicle have been well-studied \cite{kao-bir-mis2009}: At a given value of the maximum velocity $U$,
 there exists a critical reduced volume above which the equilibrium vesicle shape is symmetric (parachute or bullet shapes) and the vesicle stays at $y=0$.
@@
 %Having validated our method, we investigate the dynamics of a semi-permeable vesicle in a Poiseuille flow. 
-
-Using several initial
-$U(1-(y/W)^2,0)$, where $U$ is the maximum imposed velocity. We examine
-the effect of the non-linear Poiseuille flow on the migration of
-semi-permeable vesicle. In this experiment, the vesicle is initialized
+%
+%Using several initial
+%$U(1-(y/W)^2,0)$, where $U$ is the maximum imposed velocity. We examine
+%the effect of the non-linear Poiseuille flow on the migration of
+%semi-permeable vesicle. 
+%
+
+At the beginning of the simulations a vesicle is initialized
 above the center line $y=0$, and it migrates towards the center
 line~\cite{dan-vla-mis2009}. For an impermeable vesicle, depending on
-the vesicles reduced area and the flow rate, the long time vesicle shape
+the vesicles reduced area and the flow rate, the equilibrium vesicle shape
 is either an axisymmetric parachute or bullet, or an asymmetric
-tank-treading slipper~\cite{kao-bir-mis2009}. To validate our methods,
-in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
-for the steady state shape of an impermeable vesicle
-vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
-qualitatively agree, Kaoui et al.~report that the vesicles with
-$\alpha=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
-axisymmetric. In our simulations these vesicles are slightly asymmetric,
-are undergoing a tank treading motion, and we therefore report them as
-asymmetric slippers.
-
+tank-treading slipper~\cite{kao-bir-mis2009}. 
+%
+%To validate our methods,
+%in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
+%for the steady state shape of an impermeable vesicle
+%vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
+%qualitatively agree, Kaoui et al.~report that the vesicles with
+%$\alpha=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
+%axisymmetric. In our simulations these vesicles are slightly asymmetric,
+%are undergoing a tank treading motion, and we therefore report them as
+%asymmetric slippers.
+%
 Using several initial reduced areas and flow rates, we recreate the impermeable vesicle phase
-diagram for vesicles with a permeability rate of $\beta = 10^{-3}$. The
-final vesicle configurations are in
+diagram for vesicles with a permeability rate of $\beta = 10^{-3}$. The equilibrium vesicle shape for different $U$ and initial reduced area is summarized in
 Figure~\ref{fig:parabolicComposite}(a). An example of a semi-permeable vesicle with $\alpha(0) = 0.9$ and $U=800$ $\mu m/s$ is
@@
 area, and larger flow rates result in smaller steady state reduced
-areas. We report the steady state reduced area in
+areas. We report the reduced area of the equilibrium vesicle shape in
 Figure~\ref{fig:parabolicComposite}(a). At the smallest flow rate of $U= 200 \mu m/s$, the steady state reduced area is large, and the result
@@
 %pressure-drop variations along a micrometer-sized
-\cite{abk-fai-sto2006}, we first examining the effect of
+\cite{abk-fai-sto2006}, we first examine the effect of
 semi-permeability on the pressure fluctuation across a stenosed
@@
 subsequent time step size.
+
+\subsection*{Numerical validation: An impermeable vesicle in a Poiseuille flow}
+To validate our methods,
+in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
+for the steady state shape of an impermeable vesicle
+vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
+qualitatively agree, Kaoui et al.~report that the vesicles with
+$\alpha=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
+axisymmetric. In our simulations these vesicles are slightly asymmetric,
+are undergoing a tank treading motion, and we therefore report them as
+asymmetric slippers.
 

### 2020-12-28 vesicle_code/docs/permeableVes/main.tex
worked on fig 1 and 7

@@
   \centering
-   \includegraphics[width=0.475\textwidth]{figures/sketch_sample.png}
-  \caption{\label{fig:sketch} Schematics showing the effects of semipermeability on vesicle hydrodynamics in various configurations.}
+  \includegraphics[width=0.45\textwidth]{figures/schematic.pdf}
+  \caption{\label{fig:sketch} Schematics showing the effects of
+  semipermeability on vesicle hydrodynamics in various configurations.
+  The slipper in (a) is the steady-state shape of a semi-permeable
+  vesicle in a Poiseuille flow.}
 \end{figure}
@@
 \end{figure*}
+
+\begin{figure}[htp]
+  \ifTikz
+  \input{figures/contractingComposite2.tikz}
+  \else
+  \includegraphics{figures/contractingComposite2.pdf}
+  \fi
+  \caption{\label{fig:contractingComposite2} Vesicle reduced area and
+  velocity vs.~time.}
+\end{figure}
 

### 2020-12-28 vesicle_code/docs/permeableVes/main.tex
fixed up figure 5

@@
 Figure~\ref{fig:stenosisComposite}(b), we consider a vesicle passing
-through a channel of double the length, and we observe that the reduced
+through a channel of triple the length, and we observe that the reduced
 area decreases by 13.2\% (Figure~\ref{fig:stenosisComposite}(e)).
-\todo[inline]{This example also used a smaller flow rate of $8.4\mu$m/s}
+\begin{itemize}
+  \item In plot (a), flow rate is $1000 \mu m/s$ and residency time is
+    $t_R = 45.6 \times 10^{-2}$ s.
+  \item In plot (b), flow rate is $8.4 \mu m/s$ and residency time is
+    $t_R =  16.2$ s.
+\end{itemize}
 
@@
   short geometry in (a). (d) The reduced area of the semi-permeable
-  vesicle in the short geometry in (a). (e) The reduced area of the
-  semi-permeable vesicle in the long geometry in (b). In parts (c), (d),
-  and (e), the horizontal axis is the x-coordinate of the vesicle's
-  center of mass.}
+  vesicles in the geometries in (a) and (b) as a function of the
+  vesicles' center of mass. The $x$-axis is scaled by $1/L$ where $L$ is
+  half the length of the constriction. (e) The reduced area of the
+  semi-permeable vesicles in the geometries in (a) and (b) as a function
+  of time. The time axis is scaled by $1/t_R$ where $t_R$ is the
+  residency time. In parts (c) and (d), the dashed lines correspond to
+  the locations of the inlet and outlet. In part (e), the dashed lines
+  correspond to the times that the vesicle enters and exits the
+  constriction.}
 \end{figure*}

### 2020-12-28 vesicle_code/docs/permeableVes/main.tex
yny

--- 2020-12-28 vesicle_code/docs/permeableVes/main.tex
@@
 
+\begin{figure}[htp]
+  \centering
+  \includegraphics[width=0.45\textwidth]{figures/schematic.pdf}
+  \caption{\label{fig:schematics} A caption}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-At the beginning of the simulations a vesicle is initialized
+At the beginning of the simulations a semipermeable vesicle is initialized
 above the center line $y=0$, and it migrates towards the center
-line~\cite{dan-vla-mis2009}. For an impermeable vesicle, depending on
-the vesicles reduced area and the flow rate, the equilibrium vesicle shape
+line as in the impermeable case~\cite{dan-vla-mis2009}. However, for an impermeable vesicle, depending on
+the initial reduced area and the maximum flow velocity $U$, the equilibrium vesicle shape
 is either an axisymmetric parachute or bullet, or an asymmetric
@@
 %
+
 As observed for the planar shear flow,
@@
 RBCs go through submicron slits many times during their lifetime, and such process selects healthy, flexible RBCs to survive \cite{wu2015critical,LuPeng2019_PoF}.
-Here we investigate the role of membrane permeability to water when a cell is squeezed through a contracting microfluidic channel similar to~\cite{wu2015critical},
+Here we investigate the role of membrane permeability to water when a semi-permeable vesicle is squeezed through a contracting microfluidic channel similar to~\cite{wu2015critical},
 where the width of the channel gradually decreases from $16\mu$m to $1.6\mu$m. The channel then immediately opens
@@
 = 0.65$ that spans $10\mu$m of the total channel width and investigate
-the effects of the permeability rate and the maximum flow velocity. We
-color the vesicle according to the sign of its flux---fluid flows into
-the vesicle in red regions and out of the vesicle in blue regions.
+the effects of the membrane permeability to water and the maximum flow velocity on whether a vesicle can successfully pass through the slit. 
+We color the vesicle according to the sign of its flux---red for influx and blue for efflux.
 

### 2020-12-28 vesicle_code/docs/permeableVes/main.tex
working on supp material

--- 2020-12-28 vesicle_code/docs/permeableVes/main.tex
@@
 \end{figure}
+
 \section*{Formulation}
@@
 
-\section*{Supplementary Material: Formulation \label{sc:formulate}}
-We consider a two-dimensional semi-permeable vesicle suspended in an
-unbounded viscous fluid driven by the imposed flow $\uu_\infty(\xx)$.
-Since fluid is transported across the semi-permeable vesicle membrane,
-we only consider fluids with uniform viscosity. Letting $\gamma$ be the
-vesicle interface, the fluid velocity $\uu$ and pressure $p$ satisfy
-%
-\begin{alignat}{3}
+\section*{Supplementary Material}
+\subsection*{Formulation}
+We consider a two-dimensional inextensible semi-permeable vesicle,
+$\gamma$, suspended in unconfined and confined geometries. The
+suspending fluid is assumed to be viscous so that the fluid velocity
+$\uu$ and pressure $p$ are governed by the incompressible Stokes
+equations
+\begin{align}
   \label{eqn:governing}
-  -\nabla p + \mu \triangle \uu &= 0, \quad
-  \nabla \cdot \uu = 0, \qquad &&\xx \in \RR^2 \setminus \gamma, \\
-%
-  \uu(\xx) &\rightarrow \uu_\infty(\xx),
-    &&\norm{\xx} \rightarrow \infty,
-\end{alignat}
-where $\mu$ is the fluid viscosity. Letting $\nn$ be the outward normal
-to $\gamma$, $\jump{\cdot}$ be the jump across the interface, and $T$ be
-the hydrodynamic stress tensor, the interfacial boundary conditions are
+  -\nabla p + \mu \triangle \uu = 0, \quad
+  \nabla \cdot \uu = 0, \qquad \xx \in \RR^2 \setminus \gamma,
+\end{align}
+where $\mu$ is the fluid viscosity. In an unconfined geometry, the
+condition $\uu(\xx) \rightarrow \uu_\infty(\xx)$ is enforced as $\xx
+\rightarrow \infty$, and in a confined geometry with boundary $\Gamma$,
+the boundary condition $\uu(\xx) = \UU(\xx)$ is enforced on $\Gamma$,
+where $\UU(\xx)$ is prescribed. Along the vesicle $\gamma$, mass
+continuity and force balance are enforced by requiring
 \begin{align}
@@
 \end{align}
-where $\ff_\mathrm{mem}$ is the membrane force that results from the
-Helfrich energy with bending modulus $k_b$, and a tension term that acts
-as a Lagrange multiplier to satisfy the local inextensibility condition.
-Following~\cite{vee-gue-zor-bir2009}, we modify the bending tension and
-forces as
-$\ff_\mathrm{mem} = \ff_\mathrm{ben} +
-\ff_\mathrm{ten}$, where
-\begin{align}
-  \label{eqn:membraneForces}
-  \ff_\mathrm{ben} = -k_b \xx_{ssss}, \qquad
-  \ff_\mathrm{ten} = (\sigma \xx_s)_s.
-\end{align}
-The physical tension is $\Lambda = \sigma + 1.5 \kappa^2$, where
+where $\nn$ is the outward normal of $\gamma$, $\jump{\cdot}$ is the
+jump across the interface, and $T$ is the hydrodynamic stress tensor.
+The membrane force $\ff_\mathrm{mem}$ is the sum of a bending force
+with bending modulus $k_b$ and a force due to the tension $\Lambda$.
+Following~\cite{vee-gue-zor-bir2009}, we modify the bending and tension
+forces as $\ff_\mathrm{ben} = -k_b \xx_{ssss}$, and $\ff_\mathrm{ten} =
+(\sigma \xx_s)_s$, where $s$ is arclength. The physical tension can be
+recovered using the identity $\Lambda = \sigma + 1.5 \kappa^2$, where
 $\kappa$ is the membrane curvature.
+\todo[inline]{need inextensibility}
 

### 2020-12-28 vesicle_code/docs/permeableVes/main.tex
worked on supp material

@@
 where $\UU(\xx)$ is prescribed. Along the vesicle $\gamma$, mass
-continuity and force balance are enforced by requiring
+continuity, a force balance, and local inextensibility are enforced by
+requiring
 \begin{align}
   \label{eqn:jump}
-  \jump{T\cdot\nn} = \ff_\mathrm{mem}, \quad \jump{\uu} = 0,
+  \jump{\uu} = 0, \quad
+  \jump{T\cdot\nn} = \ff_\mathrm{mem}, \quad
+  \xx_s \cdot \uu_s = 0,
 \end{align}
@@
 $\kappa$ is the membrane curvature.
-\todo[inline]{need inextensibility}
 
@@
   \label{eqn:vesicleFlux}
-  \uu - \dot{\xx} = - \beta (\ff_\mathrm{mem} \cdot \nn) \nn, \qquad
+  \uu - \dot{\xx} = - k_w (\ff_\mathrm{mem} \cdot \nn) \nn, \qquad
   \xx \in \gamma,
 \end{align}
-where $\beta$ is the semi-permeability rate.
+where $k_w$ is the water permeability.
+
+The governing equations are non-dimensionalized by introducing a length
+scale that we take to be $R_0 = 10^{-6}$m. Using a bending stiffness of
+$k_b = 10^{-19}$J and fluid viscosity $5 \times 10^{-2}$kg/ms, we define
+the time scale $\tau = \mu R_0^3/k_b = 0.5s$, the velocity scale $U =
+R_0/\tau = 2\mu$m/s, the pressure scale $P = k_b/R_0^3 = 10^{-1}$Pa, the
+tension scale $Q = k_b/R_0 = 10^{-13}$N, and the permeability scale $W =
+R_0\mu = 2 \times 10^{-5}$m$^2$s/kg. The other standard dimensionless
+variable of a vesicle is its reduced area $\nu = 4\pi A/L^2 \in (0,1]$.
+The length $L$ is conserved by the local inextensibility condition.
+However, the area $A$ is not conserved because of semi-permeability, and
+therefore $\nu$ is also not conserved.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Dimensionless equations}
-The inextensibility condition guarantees that the vesicle's length, $L$,
-is conserved, while its area, $A$, can change due to semi-permeability.
-Therefore, the reduced area $\alpha = 4\pi A/L^2 \in (0,1]$ is not
-conserved. We non-dimensionalize~\eqref{eqn:vesVelocity} by introducing
-the length scale $R_0 = L/2\pi$ and defining the time scale $\tau = \mu
-R_0^3/k_b$, the tension scale $Q = k_b/R_0^2$, and the permeability
-scale $W = R_0/\mu$. The background velocity $\uu_\infty$ is
-non-dimensionalized with $R_0/\tau$.
-
-\todo[inline]{This is a dump of information regarding how we
-non-dimensionalize}
-In each experiment, we initialize an elliptical vesicle with longest
-diameter of 9$\mu$m. We use a length scale of $R_0 = 10^{-6}$m, a
-bending stiffness of $k_b = 10^{-19}$J, and fluid viscosity of $\mu=5
-\times 10^{-2}$kg/ms. Using the relaxation time scale $\tau = \mu
-R_0^3/k_b = 5 \times 10^{-1}$s, the pressure scale is $P = k_b/R_0^3 =
-10^{-1}$Pa.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection*{Dimensionless equations}
+%The inextensibility condition guarantees that the vesicle's length, $L$,
+%is conserved, while its area, $A$, can change due to semi-permeability.
+%Therefore, the reduced area $\alpha = 4\pi A/L^2 \in (0,1]$ is not
+%conserved. We non-dimensionalize~\eqref{eqn:vesVelocity} by introducing
+%the length scale $R_0 = L/2\pi$ and defining the time scale $\tau = \mu
+%R_0^3/k_b$, the tension scale $Q = k_b/R_0^2$, and the permeability
+%scale $W = R_0/\mu$. The background velocity $\uu_\infty$ is
+%non-dimensionalized with $R_0/\tau$.
+%
+%In each experiment, we initialize an elliptical vesicle with longest
+%diameter of 9$\mu$m. We use a length scale of $R_0 = 10^{-6}$m, a
+%bending stiffness of $k_b = 10^{-19}$J, and fluid viscosity of $\mu=5
+%\times 10^{-2}$kg/ms. Using the relaxation time scale $\tau = \mu
+%R_0^3/k_b = 5 \times 10^{-1}$s, the pressure scale is $P = k_b/R_0^3 =
+%10^{-1}$Pa.
 

### 2020-12-29 vesicle_code/docs/permeableVes/main.tex
yny

--- 2020-12-28 vesicle_code/docs/permeableVes/main.tex
@@
 
-\dropcap{W}ater exchange is essential as a living cell adapts to its environment over a wide range of timescales \cite{CadartVenkovaRechoEtAl2019_NaturePhys,AlbertsMolecularBiology,YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP,SaadounPapadopoulosWatanabeEtAl2005_JCS,Verkman2008_JMM,BerthaudEtAl2016_SM,Keren2011_EurBJ,TaloniKardashSalmanEtAl2015_PRL}.
+\dropcap{W}ater exchange is essential for a living cell to adapt to its environment over a wide range of timescales \cite{CadartVenkovaRechoEtAl2019_NaturePhys,AlbertsMolecularBiology,YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP,SaadounPapadopoulosWatanabeEtAl2005_JCS,Verkman2008_JMM,BerthaudEtAl2016_SM,Keren2011_EurBJ,TaloniKardashSalmanEtAl2015_PRL}.
 %
@@
 %osmotic effects on cellular dynamics have been well studied \cite{AlbertsMolecularBiology}, 
-mechanically induced water permeation is often associated with membrane poration or rupture under extreme stresses \cite{RazizadehNikfarPaulLiu2020_BJ}.
-In this work we use modeling and state-of-the-art numerical simulations to show that the intrinsic membrane permeability to water can give rise to significantly distinct hydrodynamics of a semipermeable vesicle without poration or rupture in the lipid bilayer membrane.
+mechanically induced water permeation is often associated with membrane poration or rupture under extreme stresses \cite{HarmanBertrandJoos2017_CJP,RazizadehNikfarPaulLiu2020_BJ}.
+In this work we use modeling and direct numerical simulations to show that,
+over the appropriate time scales or under strong confinement,
+the intrinsic membrane permeability to water can give rise to significantly distinct hydrodynamics of a semipermeable vesicle without poration or rupture in the lipid bilayer membrane. 
 %
@@
 %and coarse-grained (CG) MD 
-simulations show that a stretched RBC membrane may porate when membrane tension reaches the order of $2-4$ mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references therein), giving rise to enhanced membrane permeability to both water and macromolecules.
+simulations show that a stretched RBC membrane porates when the membrane tension reaches the order of $2-4$ mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references therein), giving rise to enhanced membrane permeability to both water and macromolecules.
 Consequently, as long as the lipid bilayer membrane remains intact (no poration or rupture), RBCs and vesicles are assumed to be of the same volume throughout experiments of durations no longer than tens of minutes.
@@
 %%The response of a cell to an osmotic gradient is inevitably both mechanical (tension redistribution and shape change) and chemical (water flux across the membrane).  
-Under what condition is this a good assumption? What is the dynamic consequence when permeable water flux/eflux affects the membrane hydrodynamics?
+Under what condition is this a good assumption? Do vesicles conserve volume over hours under flow? What is the dynamic consequence when water influx/efflux affects the membrane hydrodynamics?
 To answer these questions, we investigate the balance between hydrodynamics, tension and elasticity of a semipermeable membrane under various flowing conditions and confinement. 
@@
 
- In this work we use numerical simulations to examine the hydrodynamics of a semipermeable vesicle in two dimensions. 
+% In this work we use numerical simulations to examine the hydrodynamics of a semipermeable vesicle in two dimensions. 
+In microfluidic experiments, it is challenging to keep a freely suspended RBC or vesicle in a steady flow for more than a few hours.
+It is also difficult to quantify the vesicle area/volume ratio accurately.
+Using numerical simulations we can quantify  the effects of water permeability on the hydrodynamics of a vesicle under mechanical stresses.
 Vesicles (self-enclosed lipid bilayer membranes) have been used as a model system to study reshaping, remodeling and scission of cell membranes due to osmotic stress \cite{OgleckaEtAl2014_eLife,CamposSaric2020_bioRxiv,Dimova2020_GVB,BhatiaChrist2020_SoftMatt}.
@@
  vesicle shape changes, tank-treading and tumbling motions \cite{BhatiaRobinsonDimova2020_SoftMatt,BhatiaChrist2020_SoftMatt}, an illustration that the permeable water flow is inevitably coupled with the mechanical pressure jump across the membrane\cite{yao-mor2017}, which could become comparable to osmotic stress when the membrane deformation is large \cite{LiMoriSun2015_PRL,yao-mor2017}.
- In microfluidic experiments, it is challenging to keep a freely suspended vesicle in a steady flow for more than a few hours.
-It is also difficult to quantify the vesicle area/volume ratio accurately.
-Using numerical simulations we can quantify  the effects of water permeability on the hydrodynamics of a vesicle under mechanical stresses.
 In the absence of an osmotic gradient, we first show that a freely suspended semipermeable vesicle behaves differently from an impermeable vesicle over a long time.
@@
 \end{figure}
-
 \section*{Formulation}
 We consider a two-dimensional semi-permeable vesicle (permeable only to water) suspended in a viscous fluid, see figure~\ref{fig:sketch}.
-To focus on the effect of water flow on vesicle hydrodynamics in various conditions, we assume the fluid is the same inside and outside the vesicle membrane ($\gamma$) with an outward normal $\nn$.
+To focus on the effect of water flow on vesicle hydrodynamics in various conditions, we assume the fluid is the same inside and outside the vesicle membrane.
+%($\gamma$) with an outward normal $\nn$.
 On the membrane the permeable water flux gives rise to a difference between the fluid velocity ${\bf u}({\bf x}\in \gamma)$
@@
 \end{align}
-where $k_w$ is the water permeability, $R$ is the ideal gas constant, $T$ is the temperature ($^{\circ}$K), $\triangle c$ is contrast in a solute concentration (mol/volume),
+where $\gamma$ denotes the membrane boundary with an outward normal $\nn$, $k_w$ is the water permeability, $R$ is the ideal gas constant, $T$ is the temperature ($^{\circ}$K), $\triangle c$ is contrast in a solute concentration (mol/volume),
 and $\ff_\mathrm{mem}$ is the membrane stress that consists of both bending $ \ff_\mathrm{ben}= -k_b \xx_{ssss}$ and tension $\ff_\mathrm{ten}=(\sigma \xx_s)_s$ ($s$
@@
 in these flows show that water permeability may lead to different vesicle hydrodynamics over a time scale of 10 to 100 minutes. 
-{\bf YNY: is this correct?
-The shear flow results seem to suggest that the permeability may lead to change in area in less than a second???}
+%{\bf YNY: is this correct? The shear flow results seem to suggest that the permeability may lead to change in area in less than a second???}
 For vesicles in a narrow micro-fluidic channel, the typical time scale is of $ms$ \cite{abk-fai-sto2006}.
@@
 We consider a semi-permeable vesicle in a planar shear flow
-$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$ with different permeability
-rates $\beta$ and shear rates $\dot{\gamma}$. 
+$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$ with different permeability  $\beta$ and shear rates $\dot{\gamma}$. 
 When $\beta=0$ (impermeable case), a vesicle's reduced area
@@
 Poiseuille flow imposed at the inlet and outlet
-(Figure~\ref{fig:stenosisComposite}(a)). The flow rate is chosen so that
-the residency time of the RBC in the constriction agrees with the
-experimental results. When the RBC enters the channel, an increase in the pressure drop is required to maintain a constant flow
+(Figure~\ref{fig:stenosisComposite}(a)). The flow velocity $U_{max} = 1000 \mu$m/s is chosen so that
+the residency time of the vesicle  in the stenosis channel $t_R \approx 0.5$ s agrees with the
+experimental results \cite{abk-fai-sto2006}. When the RBC enters the channel, an increase in the pressure drop is required to maintain a constant flow
 rate, and the difference in the pressure drop is called the excess
@@
 compute the excess pressure as a function of vesicle position in the
-channel, see Figure~\ref{fig:stenosisComposite}(c). A constant
-Poiseuille velocity with a maximum value of $1000\mu$m/s is maintained
+channel, see Figure~\ref{fig:stenosisComposite}(c). A 
+Poiseuille flow with a maximum value of $1000 \mu$m/s is maintained
 at the inlet and outlet. The impermeable case agrees with experimental
-results in Figure 3 of~\cite{abk-fai-sto2006}, and the results indicate
-that less excess pressure is required to maintain a constant flow rate
-when the vesicle is semi-permeable. First we note that the vesicle
+results in Figure 3 of~\cite{abk-fai-sto2006}. Our simulations show that
+less excess pressure is needed to drive a semi-permeable vesicle through the closely-fit channel.
+Once in the channel, the vesicle takes a bullet shape with maximum tension in the front and minimum tension in the back (see Figure~\ref{fig:stenosisComposite}(a)),
+consistent with earlier results \cite{Pak2015_PNAS,HarmanBertrandJoos2017_CJP}.
+
+Figure~\ref{fig:stenosisComposite}(d)) shows
+that the vesicle
 deflates from the beginning due to the high flow velocity, consistent
 with the results for a vesicle in a Poiseuille flow in open space. As
-the vesicle enters the stenosis channel, the vesicle continues to
+the vesicle enters the stenosis channel, it continues to
 deflate in the front even though we observe influx (red segment) at
-various rear locations in the membrane.  These results are consistent
-with the results in~\cite{Pak2015_PNAS} where the membrane tension is
-sufficiently large in the front of the vesicle as it goes through a
-constrictive channel.
-
-Our simulations indicate the semi-permeability does affect the excess
-pressure, and the vesicle's reduced area reduces by about 6.1\%
-(Figure~\ref{fig:stenosisComposite}(d)). Since the area does decrease at
-a constant rate we expect that a larger amounts of deflation is possible
-if the vesicle is stenosed for a longer period of time. Therefore, in
-Figure~\ref{fig:stenosisComposite}(b), we consider a vesicle passing
-through a channel of triple the length, and we observe that the reduced
+various rear locations in the membrane. Overall, the vesicle loses about 6.1\% of its initial total water at a constant rate as shown in
+Figure~\ref{fig:stenosisComposite}(d).  Thus we expect that a larger amount of deflation is possible
+if the vesicle is inside a longer stenosis: we consider a vesicle passing
+through a channel of triple the length in
+Figure~\ref{fig:stenosisComposite}(b) with $U_{max}=8.4 \mu$m/s, and we observe that vesicle stays inside the stenosis  for a residence time $t_R=16.2$ seconds and the reduced
 area decreases by 13.2\% (Figure~\ref{fig:stenosisComposite}(e)).
-\begin{itemize}
-  \item In plot (a), flow rate is $1000 \mu m/s$ and residency time is
-    $t_R = 45.6 \times 10^{-2}$ s.
-  \item In plot (b), flow rate is $8.4 \mu m/s$ and residency time is
-    $t_R =  16.2$ s.
-\end{itemize}
+%\begin{itemize}
+%  \item In plot (a), flow rate is $1000 \mu m/s$ and residency time is
+%    $t_R = 45.6 \times 10^{-2}$ s.
+%  \item In plot (b), flow rate is $8.4 \mu m/s$ and residency time is
+%    $t_R =  16.2$ s.
+%\end{itemize}
 
@@
 Here we investigate the role of membrane permeability to water when a semi-permeable vesicle is squeezed through a contracting microfluidic channel similar to~\cite{wu2015critical},
-where the width of the channel gradually decreases from $16\mu$m to $1.6\mu$m. The channel then immediately opens
-again to $16\mu$m (Figure~\ref{fig:contractingComposite}). A
+where the width of the channel gradually decreases from $16 \mu$m to $1.6 \mu$m. The channel then immediately opens
+again to $16 \mu$m (Figure~\ref{fig:contractingComposite}). A
 Poiseuille flow is imposed at the inlet and outlet with a constant maximum flow
 rate of $U_{\max}$. We initialize a semi-permeable vesicle with $\alpha
-= 0.65$ that spans $10\mu$m of the total channel width and investigate
+= 0.65$ that spans $10 \mu$m of the total channel width and investigate
 the effects of the membrane permeability to water and the maximum flow velocity on whether a vesicle can successfully pass through the slit. 
@@
 and~\ref{fig:contractingComposite}b, we plot snapshots of vesicles with
-different permeability rates. 
+different permeability $\beta$. 
 Figure~\ref{fig:contractingComposite}c
 shows the corresponding reduced area as a function of the vesicles' location. 
-The reduced area in Figure~\ref{fig:contractingComposite}c and f shows that the vesicle always inflates gradually
-before it reaches the neck, where vesicle quickly deflates.  
-{\bf YNY: inflates over seconds but deflates over ms?}
+The reduced area in Figure~\ref{fig:contractingComposite}c and f shows that the vesicle always inflates gradually over seconds
+before it reaches the neck, where vesicle quickly deflates within a fraction of a second.
+%{\bf YNY: inflates over seconds but deflates over ms?}
 However, if the
@@
 deflates each time it passes through the constriction followed by a
-rapid inflation. The total area loss over the history of the vesicle is
+gradual inflation (over seconds). The total area loss over the history of the vesicle is
 almost 50\%. In Figure~\ref{fig:contractingComposite}i, we show the
 vesicle velocity as a function of the vesicle's center of mass. As the
-vesicle passes through the contraction, it accelerates followed by a
-rapid deacceleration once it has passed through the contraction.
-
-\begin{itemize}
-  \item Vesicle velocity in plot (a) varies from 5 to 24 microns/s.
-  \item Vesicle velocity in plot (b) varies from 5 to 28 microns/s. Time
-    that vesicle first completely passes through constriction is 4.75s
-  \item Vesicle velocity in plot (c) varies from 0.2 to 2 microns/s.
-  \item Vesicle velocity in plot (d) varies from 5 to 25 microns/s. Time
-    that vesicle first completely passes through constriction is 4.76s
-  \item Vesicle velocity in plot (g) varies from 14 to 95 microns/s (see
-    plot (i)). Time that vesicle first completely passes through
-    constriction is 1.43s
-\end{itemize}
+vesicle passes through the contraction, it first accelerates until it reaches the neck where it abruptly decelerates
+to go through the contraction. Their corresponding variation with respect to time is shown in Figure~\ref{fig:contractingComposite2}.
+
+%
+%\begin{itemize}
+%  \item Vesicle velocity in plot (a) varies from 5 to 24 microns/s.
+%  \item Vesicle velocity in plot (b) varies from 5 to 28 microns/s. Time
+%    that vesicle first completely passes through constriction is 4.75s
+%  \item Vesicle velocity in plot (c) varies from 0.2 to 2 microns/s.
+%  \item Vesicle velocity in plot (d) varies from 5 to 25 microns/s. Time
+%    that vesicle first completely passes through constriction is 4.76s
+%  \item Vesicle velocity in plot (g) varies from 14 to 95 microns/s (see
+%    plot (i)). Time that vesicle first completely passes through
+%    constriction is 1.43s
+%\end{itemize}
 
@@
 \end{figure}
+
+\section*{Discussion}
 
@@
 
-\section*{Supplementary Material}
-\subsection*{Formulation}
-We consider a two-dimensional inextensible semi-permeable vesicle,
-$\gamma$, suspended in unconfined and confined geometries. The
-suspending fluid is assumed to be viscous so that the fluid velocity
-$\uu$ and pressure $p$ are governed by the incompressible Stokes
-equations
-\begin{align}
+\section*{Supplementary Material: Formulation \label{sc:formulate}}
+We consider a two-dimensional semi-permeable vesicle suspended in an
+unbounded viscous fluid driven by the imposed flow $\uu_\infty(\xx)$.
+Since fluid is transported across the semi-permeable vesicle membrane,
+we only consider fluids with uniform viscosity. Letting $\gamma$ be the
+vesicle interface, the fluid velocity $\uu$ and pressure $p$ satisfy
+%
+\begin{alignat}{3}
   \label{eqn:governing}
-  -\nabla p + \mu \triangle \uu = 0, \quad
-  \nabla \cdot \uu = 0, \qquad \xx \in \RR^2 \setminus \gamma,
-\end{align}
-where $\mu$ is the fluid viscosity. In an unconfined geometry, the
-condition $\uu(\xx) \rightarrow \uu_\infty(\xx)$ is enforced as $\xx
-\rightarrow \infty$, and in a confined geometry with boundary $\Gamma$,
-the boundary condition $\uu(\xx) = \UU(\xx)$ is enforced on $\Gamma$,
-where $\UU(\xx)$ is prescribed. Along the vesicle $\gamma$, mass
-continuity and force balance are enforced by requiring
+  -\nabla p + \mu \triangle \uu &= 0, \quad
+  \nabla \cdot \uu = 0, \qquad &&\xx \in \RR^2 \setminus \gamma, \\
+%
+  \uu(\xx) &\rightarrow \uu_\infty(\xx),
+    &&\norm{\xx} \rightarrow \infty,
+\end{alignat}
+where $\mu$ is the fluid viscosity. Letting $\nn$ be the outward normal
+to $\gamma$, $\jump{\cdot}$ be the jump across the interface, and $T$ be
+the hydrodynamic stress tensor, the interfacial boundary conditions are
 \begin{align}
@@
 \end{align}
-where $\nn$ is the outward normal of $\gamma$, $\jump{\cdot}$ is the
-jump across the interface, and $T$ is the hydrodynamic stress tensor.
-The membrane force $\ff_\mathrm{mem}$ is the sum of a bending force
-with bending modulus $k_b$ and a force due to the tension $\Lambda$.
-Following~\cite{vee-gue-zor-bir2009}, we modify the bending and tension
-forces as $\ff_\mathrm{ben} = -k_b \xx_{ssss}$, and $\ff_\mathrm{ten} =
-(\sigma \xx_s)_s$, where $s$ is arclength. The physical tension can be
-recovered using the identity $\Lambda = \sigma + 1.5 \kappa^2$, where
+where $\ff_\mathrm{mem}$ is the membrane force that results from the
+Helfrich energy with bending modulus $k_b$, and a tension term that acts
+as a Lagrange multiplier to satisfy the local inextensibility condition.
+Following~\cite{vee-gue-zor-bir2009}, we modify the bending tension and
+forces as
+$\ff_\mathrm{mem} = \ff_\mathrm{ben} +
+\ff_\mathrm{ten}$, where
+\begin{align}
+  \label{eqn:membraneForces}
+  \ff_\mathrm{ben} = -k_b \xx_{ssss}, \qquad
+  \ff_\mathrm{ten} = (\sigma \xx_s)_s.
+\end{align}
+The physical tension is $\Lambda = \sigma + 1.5 \kappa^2$, where
 $\kappa$ is the membrane curvature.
-\todo[inline]{need inextensibility}
 

### 2020-12-29 vesicle_code/docs/permeableVes/main.tex

@@
 
-\section*{Supplementary Material: Formulation \label{sc:formulate}}
-We consider a two-dimensional semi-permeable vesicle suspended in an
-unbounded viscous fluid driven by the imposed flow $\uu_\infty(\xx)$.
-Since fluid is transported across the semi-permeable vesicle membrane,
-we only consider fluids with uniform viscosity. Letting $\gamma$ be the
-vesicle interface, the fluid velocity $\uu$ and pressure $p$ satisfy
-%
-\begin{alignat}{3}
+\section*{Supplementary Material}
+\subsection*{Formulation}
+We consider a two-dimensional inextensible semi-permeable vesicle,
+$\gamma$, suspended in unconfined and confined geometries. The
+suspending fluid is assumed to be viscous so that the fluid velocity
+$\uu$ and pressure $p$ are governed by the incompressible Stokes
+equations
+\begin{align}
   \label{eqn:governing}
-  -\nabla p + \mu \triangle \uu &= 0, \quad
-  \nabla \cdot \uu = 0, \qquad &&\xx \in \RR^2 \setminus \gamma, \\
-%
-  \uu(\xx) &\rightarrow \uu_\infty(\xx),
-    &&\norm{\xx} \rightarrow \infty,
-\end{alignat}
-where $\mu$ is the fluid viscosity. Letting $\nn$ be the outward normal
-to $\gamma$, $\jump{\cdot}$ be the jump across the interface, and $T$ be
-the hydrodynamic stress tensor, the interfacial boundary conditions are
+  -\nabla p + \mu \triangle \uu = 0, \quad
+  \nabla \cdot \uu = 0, \qquad \xx \in \RR^2 \setminus \gamma,
+\end{align}
+where $\mu$ is the fluid viscosity. In an unconfined geometry, the
+condition $\uu(\xx) \rightarrow \uu_\infty(\xx)$ is enforced as $\xx
+\rightarrow \infty$, and in a confined geometry with boundary $\Gamma$,
+the boundary condition $\uu(\xx) = \UU(\xx)$ is enforced on $\Gamma$,
+where $\UU(\xx)$ is prescribed. Along the vesicle $\gamma$, mass
+continuity, a force balance, and local inextensibility are enforced by
+requiring
 \begin{align}
   \label{eqn:jump}
-  \jump{T\cdot\nn} = \ff_\mathrm{mem}, \quad \jump{\uu} = 0,
+  \jump{\uu} = 0, \quad
+  \jump{T\cdot\nn} = \ff_\mathrm{mem}, \quad
+  \xx_s \cdot \uu_s = 0,
 \end{align}
-where $\ff_\mathrm{mem}$ is the membrane force that results from the
-Helfrich energy with bending modulus $k_b$, and a tension term that acts
-as a Lagrange multiplier to satisfy the local inextensibility condition.
-Following~\cite{vee-gue-zor-bir2009}, we modify the bending tension and
-forces as
-$\ff_\mathrm{mem} = \ff_\mathrm{ben} +
-\ff_\mathrm{ten}$, where
-\begin{align}
-  \label{eqn:membraneForces}
-  \ff_\mathrm{ben} = -k_b \xx_{ssss}, \qquad
-  \ff_\mathrm{ten} = (\sigma \xx_s)_s.
-\end{align}
-The physical tension is $\Lambda = \sigma + 1.5 \kappa^2$, where
+where $\nn$ is the outward normal of $\gamma$, $\jump{\cdot}$ is the
+jump across the interface, and $T$ is the hydrodynamic stress tensor.
+The membrane force $\ff_\mathrm{mem}$ is the sum of a bending force
+with bending modulus $k_b$ and a force due to the tension $\Lambda$.
+Following~\cite{vee-gue-zor-bir2009}, we modify the bending and tension
+forces as $\ff_\mathrm{ben} = -k_b \xx_{ssss}$, and $\ff_\mathrm{ten} =
+(\sigma \xx_s)_s$, where $s$ is arclength. The physical tension can be
+recovered using the identity $\Lambda = \sigma + 1.5 \kappa^2$, where
 $\kappa$ is the membrane curvature.

### 2020-12-29 vesicle_code/docs/permeableVes/main.tex
first draft of supplementary material

@@
 
-% \newpage
-% \paragraph{\bf \Huge OLD STUFF}
-%
-%%%%%%%%%%%%%%%
-%\section{{$\Theta-L$} formulation}
-%Here, we attempt to apply the formulation described by Sohn et
-%al.~\cite{soh-tse-li-voi-low2010} to a semi-permeable vesicle.  In the
-%semi-permeable formulation, the vesicle velocity is
-%\begin{align}
-%  \pderiv{\XX}{t} = \uu(\XX(t)) + \beta (\ff \cdot \nn) \nn.
-%\end{align}
-%In the {$\Theta-L$} variables, we require a normal velocity $V$, and a
-%tangential velocity $T$. Since the inextensibility condition is $T_s +
-%\kappa V = 0$, a condition for the vesicle velocity is
-%\begin{align}
-%  (\uu \cdot \ss)_s = -\kappa(\beta (\ff \cdot \nn) + 
-%      \uu \cdot \nn).
-%\end{align}
-%This equation can be solved following equations (32)--(39)
-%in~\cite{soh-tse-li-voi-low2010}, with the only difference being that
-%$\tilde{\uu}$ satisfies
-%\begin{align}
-%  (\tilde{\uu} \cdot \ss)_s + \kappa(\tilde{\uu} \cdot \nn) =
-%    -(\vv \cdot \ss)_s - \kappa(\vv \cdot \nn) 
-%    - \beta\kappa(\ff \cdot \nn).
-%\end{align}
-%Compared to equation (40), only the last term is new.
-%
-%
-%%%%%%%%%%%%%%%
-%Finally, we write the time stepping method in matrix form as
-%\begin{align}
-%  A \left(
-%    \begin{array}{c}
-%      \xx^{N+1} \\ \sigma^{N+1}
-%    \end{array}
-%  \right) = 
-%  \left(
-%    \begin{array}{c}
-%      \xx^{N} + \Delta t \uu_\infty(\xx^N) \\ \mathbf{1}
-%    \end{array}
-%  \right),
-%\end{align}
-%where
-%\begin{align}
-% A = \left(
-%  \begin{array}{cc}
-%    I + \Delta t \beta P^N B^N + \Delta t \SS^N B^N & 
-%    -\Delta t P^N T^N - \Delta t \SS^N T^N \\
-%    D^N & 0
-%  \end{array}
-%  \right).
-%\end{align}
-%
-%\section{Area of a Vesicle}
-%The area inside a single vesicle $\gamma$ parameterized with $\xx$ is
-%\begin{align}
-%  A(t) = \int_{\gamma} (\xx \cdot \nn)\, ds = 
-%    \int_{0}^{2\pi} \left(\xx \cdot \pderiv{\xx}{\theta}^\perp\right)
-%    \, d\theta.
-%\end{align}
-%Taking the time derivative of $A(t)$,
-%\begin{align}
-%  \dot{A}(t) &= \int_{0}^{2\pi} \left(
-%    \dot{\xx} \cdot \pderiv{\xx}{\theta}^{\perp} + 
-%    \xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right) \\
-%    \, d\theta.
-%  &= \int_{0}^{2\pi} \left(
-%    (\dot{\xx} \cdot \nn)\|\xx'(\theta)\| \right) d\theta +
-%     \int_{0}^{2\pi}
-%    \xx \cdot \frac{d}{dt}\left(\nn |\frac{d\xx}{d\theta}| \right)
-%\end{align}
-%
-%
-%
-%\begin{align}
-%  A(t) = \frac{1}{2}\int_{\gamma} (\xx \cdot \nn)\, ds = 
-%    \frac{1}{2}\int_{0}^{2\pi} \left(\xx \cdot \pderiv{\xx}{\theta}^\perp\right)
-%    \, d\theta.
-%\end{align}
-%Taking the time derivative of $A(t)$,
-%\begin{align}
-%  \dot{A}(t) &= \frac{1}{2}\int_{0}^{2\pi} \left(\dot{\xx} \cdot
-%  \pderiv{\xx}{\theta}^{\perp} + 
-%    \xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right) d\theta, \\
-%  &= \frac{1}{2}
-%  \int_{0}^{2\pi}(\dot{\xx}\cdot\nn)\left\|\pderiv{\xx}{\theta}\right\|d\theta +
-%     \frac{1}{2}\int_{0}^{2\pi}
-%    \left(\xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right)d\theta, \\
-%  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds +
-%  \frac{1}{2}\int_{0}^{2\pi}\left(\xx \cdot \pderiv{}{t}\left(\nn
-%  \left\|\pderiv{\xx}{\theta}\right\|\right)\right)d\theta, \\
-%  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds + \frac{1}{2}
-%  \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds + \frac{1}{2}\int_{0}^{2\pi}
-%  \frac{\xx\cdot\nn}{\left\|\pderiv{\xx}{\theta}\right\|}
-%  \left(\pderiv{\xx}{\theta}\cdot
-%  \pderiv{\dot{\xx}}{\theta}\right)d\theta \\
-%  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds + \frac{1}{2}
-%  \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds + \frac{1}{2}\int_{\gamma}
-%  (\xx\cdot\nn) (\xx_s \cdot \dot{\xx}_s)\, ds.
-%\end{align}
-%To satisfy the inextensibilty condition, $\xx_s \cdot \dot{\xx}_s = 0$.
-%Therefore the time derivative of $A(t)$ is
-%\begin{align}
-%     \dot{A}(t) &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds
-%     + \frac{1}{2} \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds.
-%\end{align}
-%which we re-write as
-%\begin{align}
-%    \dot{A}(t) &= \frac{\beta}{2}
-%    \int_{\gamma}\left(\ff\cdot\nn\right)ds-\frac{1}{2}\int_{\gamma}\left(\xx^{\perp}\cdot\dot{\xx}_s\right) ds.
-%\end{align}
-%Applying integration by parts,
-%\begin{align}
-%    \dot{A}(t) &= \frac{\beta}{2}
-%    \int_{\gamma}\left(\ff\cdot\nn\right)ds+\frac{1}{2}\int_{\gamma}\left(\xx^{\perp}_s\cdot\dot{\xx}\right) ds,
-%\end{align}
-%which we re-write as
-%\begin{align}
-%    \dot{A}(t) &= \frac{\beta}{2}
-%    \int_{\gamma}\left(\ff\cdot\nn\right)ds+\frac{1}{2}\int_{\gamma}\left(\dot{\xx}\cdot\nn\right),\\
-%    \dot{A}(t) &= \beta \int_{\gamma}\left(\ff\cdot\nn\right)ds.
-%\end{align}
-%
-%
-%At steady state,
-%\begin{align}
-%    \dot{A}(t) &= \beta \int_{\gamma}\left(\ff\cdot\nn\right)ds =0.
-%\end{align}
-%We now replace $\ff$ with its definition and apply integration by parts
-%\begin{align}
-%   0=\beta\int_{\gamma} 
-%    (-k_b\xx_{ssss}+(\sigma\xx_s)_s)\cdot\nn\, ds =
-%   \beta\int_{\gamma}\left(k_b\xx_{sss}-\sigma\xx_s\right)\cdot
-%     \nn_s\, ds
-%\end{align}
-%From the Frenet-Serret formulas, we have 
-%\begin{align}
-%     -\beta\int_{\gamma}
-%     \left(k_b\xx_{sss}-\sigma\xx_s\right)\cdot\kappa\xx_s ds &=0.
-%\end{align}
-%
-%Applying integration by parts and Frenet-Serret again
-%\begin{align}
-%     \beta\int_{\gamma}
-%     k_b\kappa\left(\xx_{ss}\cdot\xx_{ss}\right)ds + \beta
-%     \int_{\gamma} k_b \kappa_s(\xx_{ss} \cdot \xx_s)ds +\beta\int_{\gamma}\kappa\sigma ds  &= 0,\\
-%    \beta\int_{\gamma} k_b\kappa(\kappa\nn \cdot
-%     \kappa\nn)+ \beta \int_{\gamma} k_b \kappa_s(\xx_{ss} \cdot
-%     \xx_s)ds +\beta\int_{\gamma}\kappa\sigma ds &= 0,
-%\end{align}
-%which we re-write as
-%\begin{align}
-%   \beta\int_{\gamma}k_b\kappa^3 ds + \beta \int_{\gamma} k_b
-%   \kappa_s(\xx_{ss} \cdot \xx_s)ds +\beta\int_{\gamma} \kappa\sigma ds = 0.
-%\end{align}
-%Applying Frenet-serret again,
-%\begin{align}
-%    \beta\int_{\gamma}k_b\kappa^3 ds + \beta \int_{\gamma} k_b
-%    \kappa_s(\kappa\nn \cdot \TT)ds +\beta\int_{\gamma} \kappa\sigma ds = 0, \\
-%    \beta\int_{\gamma}k_b\kappa^3 ds +\beta\int_{\gamma} \kappa\sigma ds  = 0.
-%\end{align}
-%
-%
-%\section{Including a concentration field}
-%Based on the work of Yao and Mori~\cite{yao-mor2017}, we introduce a
-%chemical concentration field $c$.  The concentration field is governed
-%by the advection-diffusion equation
-%\begin{align}
-%  \pderiv{c}{t} + \nabla \cdot (\uu c) = D\Delta c.
-%\end{align}
-%If the concentration is diffusion dominated (zero Peclet number), then
-%the concentration satisfies
-%\begin{align}
-%  \Delta c = 0, \quad \xx \in \RR^2.
-%\end{align}
-%The boundary conditions of the concentration field on the vesicle
-%$\gamma$ are
-%\begin{align}
-%  (\uu c - D\nabla c) \cdot \nn = c \pderiv{\xx}{t} \cdot \nn + 
-%    j_c + j_p,
-%\end{align}
-%where $j_c$ and $j_p$ are the transmembrane chemical flux due to passive
-%transport and active transport (pumps), respectively.  In the zero
-%Peclet number limit, the absence of an active transport mechanism, and
-%the choice for the passive flux, the boundary condition of the
-%concentration field is
-%\begin{align}
-%  -D\pderiv{c}{\nn} = c \pderiv{\xx}{t} + 
-%    k_c \jump{c}, \quad \xx \in \gamma.
-%\end{align}
-%To couple the vesicle dynamics to the concentration, there is a
-%difference between the fluid velocity and vesicle velocity
-%\begin{align}
-%  \uu - \pderiv{\xx}{t} = j_w \nn,
-%\end{align}
-%where $j_w$ is the water flux through the vesicle.  This is the
-%osmophoretic flow.  In~\cite{yao-mor2017}, this flux is
-%\begin{align}
-%  j_w = -k_w(RT\jump{c} + \ff_\text{mem} \cdot \nn).
-%\end{align}
-%In our current implementation, we drop the $RT\jump{c}$ term, and
-%let $\beta = k_w$.
-%
-%\section{Preliminary results}
-%
-%
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=.9\textwidth]{figures/1.jpg}
-%	\includegraphics[width=.9\textwidth]{figures/2.jpg}
-%	\includegraphics[width=.9\textwidth]{figures/3.jpg}
-%	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0$.}
-%%	\label{Shear0}
-%\end{figure}
-%
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=.9\textwidth]{figures/4.jpg}
-%	\includegraphics[width=.9\textwidth]{figures/5.jpg}
-%	\includegraphics[width=.9\textwidth]{figures/6.jpg}
-%	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0.5$.}
-%%	\label{Shear0}
-%\end{figure}
-%
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=.9\textwidth]{figures/7.jpg}
-%	\includegraphics[width=.9\textwidth]{figures/8.jpg}
-%	\includegraphics[width=.9\textwidth]{figures/9.jpg}
-%	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 1$.}
-%%	\label{Shear0}
-%\end{figure}
-%
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=.9\textwidth]{figures/10.jpg}
-%	\includegraphics[width=.9\textwidth]{figures/11.jpg}
-%	\includegraphics[width=.9\textwidth]{figures/12.jpg}
-%	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 2$.}
-%%	\label{Shear0}
-%\end{figure}
-% 
-% 
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[width=.9\textwidth]{figures/BE1.jpg}
-% 	\includegraphics[width=.9\textwidth]{figures/BE2.jpg}
-% 	\includegraphics[width=.9\textwidth]{figures/BE3.jpg}
-% 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0$.}
-%% 	\label{Shear0}
-% \end{figure}
-% 
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[width=.9\textwidth]{figures/BE4.jpg}
-% 	\includegraphics[width=.9\textwidth]{figures/BE5.jpg}
-% 	\includegraphics[width=.9\textwidth]{figures/BE6.jpg}
-% 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0.5$.}
-%% 	\label{Shear0}
-% \end{figure}
-% 
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[width=.9\textwidth]{figures/BE7.jpg}
-% 	\includegraphics[width=.9\textwidth]{figures/BE8.jpg}
-% 	\includegraphics[width=.9\textwidth]{figures/BE9.jpg}
-% 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 1$.}
-%% 	\label{Shear0}
-% \end{figure}
-% 
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[width=.9\textwidth]{figures/BE10.jpg}
-% 	\includegraphics[width=.9\textwidth]{figures/BE11.jpg}
-% 	\includegraphics[width=.9\textwidth]{figures/BE12.jpg}
-% 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 2$.}
-% 	\label{Shear0}
-% \end{figure}
-%
-%When the semi-permeable vesicle reaches a steady-state shape, we have
-%\begin{align}
-%  \int_{\gamma} \left(-\frac{\kappa^3}{2} + \kappa \Lambda \right) \, ds
-%  = 0.
-%\end{align}
-%Based on numerical observations, the steady-state shape is a circular
-%vesicle with constant tension. Since the tension and curvature are
-%constant, we can solve for the curvature in terms of the tension $\kappa
-%= \sqrt{2\Lambda}$. Therefore, the steady state shape is a circle of
-%radius $r = 1/\sqrt{2\Lambda}$, and therefore the length is
-%\begin{align}
-%  L = \frac{\sqrt{2}\pi}{\sqrt{\Lambda}},
-%\end{align}
-%which is constant by the local inextensibility constraint. Finally, we
-%can compute the final tension in terms of the length using the formula
-%\begin{align}
-%  \Lambda = \frac{2\pi^2}{L^2}.
-%\end{align}
-%Therefore, in contrast to a impermeable vesicle, the final tension is
-%positive rather than negative.
-%
-%We start by simulating a star-shaped vesicle in a quiescent flow with
-%semi-permeability rate $\beta=1$ (Figure~\ref{fig:starShape}). To
-%perform this simulation, we use an adaptive second-order time stepping
-%method~\cite{qua-bir2016}. The times and reduced areas are in the
-%titles, and note that the shapes are not eqiuspaced in time.
-%\begin{figure}[htp]
-%  \begin{minipage}{0.55\textwidth}
-%%    \ifTikz
-%    \input{figures/starRelaxation1.tikz}
-%    \input{figures/starRelaxation2.tikz}
-%    \input{figures/starRelaxation3.tikz}
-%    \input{figures/starRelaxation4.tikz}
-%    \input{figures/starRelaxation5.tikz}
-%    \input{figures/starRelaxation6.tikz}
-%%    \fi
-%  \end{minipage}
-%  \hfill
-%  \begin{minipage}{0.4\textwidth}
-%%  \ifTikz
-%  \input{figures/starAreaDeriv.tikz}
-%%  \fi
-%  \end{minipage}
-%%  \caption{\label{fig:starShape} A initially star-shaped semi-permeable
-%%  vesicle in a shear quiescent flow with $\beta=1$. Note that the time
-%%  steps are not equispaced. The area (red) and its derivative (blue) of
-%%  an initially star-shaped vesicle as a function of time. The dots
-%%  correspond to the time steps shown in six time steps
-%%  show on the left.}
-%\end{figure}
-%
-%\begin{table}[htp]
-%  \centering
-%  \begin{tabular}{|C{1cm}|*{6}{C{2cm}}|}
-%    \hline
-%    $\beta$ & $10^{0}$ & $10^{-1}$ & $10^{-2}$ & 
-%             $10^{-3}$ & $10^{-4}$ & $10^{-5}$ \\
-%    $t_\mathrm{SS}$ & $6.45 \times 10^{0}$ & $2.00 \times 10^{1}$ & 
-%                      $9.61 \times 10^{1}$ & $8.36 \times 10^{2}$ & 
-%                      $8.15 \times 10^{3}$ & $8.03 \times 10^{4}$ \\
-%    ratio & --- & 3.10 & 4.81 & 8.71 & 9.74 & 9.85 \\
-%    \hline
-%  \end{tabular}
-%  \caption{\label{tbl:ellipseRelaxTime} The time, $t_{\mathrm{SS}}$, for
-%  a semi-permeable vesicle to reach steady state.}
-%\end{table}
-%
-%\begin{table}[htp]
-%  \centering
-%  \begin{tabular}{|C{1cm}|*{6}{C{2cm}}|}
-%    \hline
-%    $\beta$ & $10^{0}$ & $10^{-1}$ & $10^{-2}$ & 
-%             $10^{-3}$ & $10^{-4}$ & $10^{-5}$ \\
-%    $t_\mathrm{SP}$ & $2.17 \times 10^{-2}$ & $1.25 \times 10^{-1}$ & 
-%                      $1.59 \times 10^{0}$ & $2.19 \times 10^{1}$ & 
-%                      $2.14 \times 10^{2}$ & $2.20 \times 10^{3}$ \\
-%    ratio & --- & 5.76 & 12.72 & 13.77 & 9.77 & 10.14 \\
-%    \hline
-%  \end{tabular}
-%  \caption{\label{tbl:ellipseBLTime} The time, $t_\mathrm{SP}$, for a
-%  semi-permeable vesicle to begin inflating.}
-%\end{table}
-%
-%%\begin{figure}[htp]
-%%\begin{minipage}{0.40\textwidth}
-%%\ifTikz
-%%\input{figures/starTension.tikz}
-%%\fi
-%%\end{minipage}
-%%\hfill
-%%\begin{minipage}{0.55\textwidth}
-%%  \centering
-%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime1.pdf}
-%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime2.pdf}
-%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime3.pdf} \\
-%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime4.pdf}
-%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime5.pdf}
-%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime6.pdf}
-%%\end{minipage}
-%%  \caption{\label{fig:starTension} The tension of the time steps shown
-%%  in Figure~\ref{fig:starShape}. The tension at the time horizon $T=1$
-%%  is also included. At this point, the vesicle is nearly circular and
-%%  the tension is constant and positive. The constant is given by
-%%  equation~\eqref{eqn:SSshape}, and this value corresponds to the
-%%  dashed black line.}
-%%\end{figure}
-%
-%%\begin{figure}[htp]
-%%\begin{minipage}{0.40\textwidth}
-%%%\ifTikz
-%%\input{figures/starFlux.tikz}
-%%%\fi
-%%\end{minipage}
-%%\hfill
-%%\begin{minipage}{0.55\textwidth}
-%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime1.pdf}
-%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime2.pdf}
-%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime3.pdf} \\
-%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime4.pdf}
-%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime5.pdf}
-%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime6.pdf}
-%%\end{minipage}
-%%  \caption{\label{fig:starFlux} The flux of the time steps shown in
-%%  Figure~\ref{fig:starShape}. The tension at the time horizon $T=1$ is
-%%  also included. At this point, the vesicle is nearly circular and there
-%%  is no flux.}
-%%\end{figure}
-%\begin{figure}[htp]
-%    \ifTikz
-%    \input{figures/starRelaxation1.tikz}
-%    \quad
-%    \input{figures/starRelaxation2.tikz}
-%    \quad
-%    \input{figures/starRelaxation3.tikz}
-%    \quad
-%    \input{figures/starRelaxation4.tikz}
-%    \quad
-%    \input{figures/starRelaxation5.tikz}
-%    \fi
-%  \caption{\label{fig:starShape} An initially star-shaped semi-permeable
-%  vesicle in a quiescent flow with $\beta=1$. Note that the time steps
-%  are not equispaced.}
-%\end{figure}
-%\begin{figure}[htp]
-%  \centering
-%%  \ifTikz
-%  \input{figures/ellipseVelocity1.tikz}
-%  \input{figures/ellipseVelocity2.tikz}
-%  \input{figures/ellipseVelocity3.tikz}
-%%  \fi
-%  \caption{\label{fig:vesVelocity} The velocity contributions due to
-%  semi-permeability (red) and force balance (blue). The green dashed
-%  line is the velocity of an impermeable vesicle with the same initial
-%  shape as the semi-permeable vesicle.}
-%\end{figure}
-%
-%\begin{figure}[htp]
-%%  \ifTikz
-%  \input{figures/ellipseVelocityNorms.tikz}
-%%  \fi
-%  \caption{\label{fig:vesVelocityNorm} The max norm of the velocity due
-%  to the force balance (blue) and semi-permeability. Also included is
-%  the velocity of an impermeable vesicle (green). The three black lines
-%  correspond to the times reported in Figure~\ref{fig:vesVelocity}.}
-%\end{figure}
-
-% \newpage
-%\input{figures/shearPhaseDiagramRA2.tikz}
-%\input{figures/parabolicPhaseDiagram.tikz}
-%\begin{figure}[htp]
-%%  \ifTikz
-%%  \input{figures/parabolicPhaseDiagram.tikz}
-%%  \fi
-%  \includegraphics[width=0.9\linewidth]{figures/parabolicPhaseDiagram.pdf}
-%  \caption{\label{fig:parabolicPhaseDiagram} The steady state shape of a
-%  semi-permeable vesicle with several different permeability rates
-%  $\beta$ and flow rates $U$. The numbers reported above each vesicle is
-%  its reduced area. At high flow rates, the vesicle self-intersects
-%  before reaching a steady state configuration.}
-%\end{figure}
-%
-%
-%\begin{table}[htp]
-%  \centering
-%  \caption{\label{tbl:parabolicRelaxTimes1} The time for a
-%  semi-permeable vesicle in a Poiseuille flow to reach its steady state
-%  ($t_\mathrm{steady}$) and to begin inflating ($t_\mathrm{inflate}$).
-%  The times are reported for the maximum velocities $0.1 \mu m/s$ and
-%  $10 \mu m/s$.}
-%  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
-%    \multicolumn{5}{c}{$U = 0.1 \mu m/s$} \\
-%    $\beta$ & $t_\mathrm{steady}$ & ratio & $t_\mathrm{inflate}$ & ratio \\
-%    \midrule
-%    $10^{0}$  & $3.33 \times 10^{0}$ & ---  
-%              & $1.67 \times 10^{-2}$ & --- \\ 
-%    $10^{-1}$ & $1.37 \times 10^{1}$ & 4.12 & 
-%                $8.73 \times 10^{-1}$ & 5.23 \\
-%    $10^{-2}$ & $8.60 \times 10^{1}$ & 6.26 & 
-%                $1.11 \times 10^{0}$ & 12.74 \\
-%    $10^{-3}$ & $7.75 \times 10^{2}$ & 9.01 & 
-%                $1.63 \times 10^{1}$ & 14.70 \\
-%    $10^{-4}$ & $7.69 \times 10^{3}$ & 9.93 & 
-%                $1.74 \times 10^{2}$ & 10.63 \\
-%    $10^{-5}$ & $8.01 \times 10^{4}$ & 10.41 & 
-%                $1.66 \times 10^{3}$ & 9.58 \\
-%    \bottomrule
-%  \end{tabular}
-%
-%  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
-%    \multicolumn{5}{c}{$U = 10 \mu m/s$} \\
-%    $\beta$ & $t_\mathrm{steady}$ & ratio & $t_\mathrm{inflate}$ & ratio \\
-%    \midrule
-%    $10^{0}$  & $3.55 \times 10^{0}$ & ---  
-%              & $1.67 \times 10^{-2}$ & --- \\ 
-%    $10^{-1}$ & $1.87 \times 10^{1}$ & 5.27 & 
-%                $9.01 \times 10^{-2}$ & 5.40 \\
-%    $10^{-2}$ & $1.17 \times 10^{2}$ & 6.26 & 
-%                $1.52 \times 10^{0}$ & 16.87 \\
-%    $10^{-3}$ & $1.06 \times 10^{3}$ & 9.06 & 
-%                $2.07 \times 10^{1}$ & 13.62 \\
-%    $10^{-4}$ & $1.02 \times 10^{4}$ & 9.62 & 
-%                $2.25 \times 10^{2}$ & 10.87 \\
-%    $10^{-5}$ & $1.04 \times 10^{5}$ & 10.20 & 
-%                $2.25 \times 10^{3}$ & 10.00 \\
-%    \bottomrule
-%  \end{tabular}
-%\end{table}
-%The width $W$ is chosen so that $W/R =
-%10$, where $R$ is the radius of the vesicle. We investigate the effect
-%of the maximum velocity $U$ and the permeability rate $\beta$ on the
-%steady state shape of a vesicle initially placed on the center line
-%$y=0$. Figure~\ref{fig:parabolicPhaseDiagram} shows the steady state
-%configuration for a variety of maximum velocities and permeability
-%rates. Similar to the shear example, the maximum velocity strongly
-%affects the final shape while the permeability rate's effect is much
-%weaker. Instead, the permeability rate determines the time required for
-%the vesicle to reach a steady state. In
-%Table~\ref{tbl:parabolicRelaxTimes1}, we consider two maximum velocities
-%and report the time, $t_\mathrm{steady}$, required for the vesicle's
-%area to be within 1.3\% of its maximum area, and the time,
-%$t_\mathrm{inflate}$, required for the vesicle's area to exceed 1.3\% of
-%its initial area. We see that both times scale with $\beta^{-1}$.
-
-%\begin{figure}[htp]
-%  \centering
-%  \begin{tabular}{ccc}
-%    \ifTikz
-%    \scalebox{0.31}{\input{figures/stenosisTension1.tikz}} &
-%    \scalebox{0.31}{\input{figures/stenosisTension3.tikz}} &
-%    \scalebox{0.31}{\input{figures/stenosisTension5.tikz}} \\
-%    \scalebox{0.31}{\input{figures/stenosisTension7.tikz}} &
-%    \scalebox{0.31}{\input{figures/stenosisTension9.tikz}} &
-%    \scalebox{0.31}{\input{figures/stenosisTension11.tikz}} 
-%    \fi
-%  \end{tabular}
-%  \caption{\label{fig:stenosisTension} The tension of the impermeable
-%  (red) and semi-permeable (dashed blue) vesicles in
-%  Figure~\ref{fig:stenosisShape}. The point $\theta=0$ corresponds to
-%  the right-most point of the vesicle.}
-%\end{figure}
-%
-%\begin{figure}[htp]
-%  \centering
-%  \begin{tabular}{ccc}
-%    \iftikz
-%    \scalebox{0.31}{\input{figures/stenosisflux1.tikz}} &
-%    \scalebox{0.31}{\input{figures/stenosisflux3.tikz}} &
-%    \scalebox{0.31}{\input{figures/stenosisflux5.tikz}} \\
-%    \scalebox{0.31}{\input{figures/stenosisflux7.tikz}} &
-%    \scalebox{0.31}{\input{figures/stenosisflux9.tikz}} &
-%    \scalebox{0.31}{\input{figures/stenosisflux11.tikz}} 
-%    \fi
-%  \end{tabular}
-%  \caption{\label{fig:stenosisFlux} The flux (equivalent to pressure
-%  jump) of the impermeable (red) and semi-permeable (dashed blue)
-%  vesicles in Figure~\ref{fig:stenosisShape}. The point $\theta=0$
-%  corresponds to the right-most point of the vesicle.}
-%\end{figure}
-
-\section*{Supplementary Material}
-\subsection*{Formulation}
+\section*{Supplementary Material: Formulation}
 We consider a two-dimensional inextensible semi-permeable vesicle,
-$\gamma$, suspended in unconfined and confined geometries. The
+$\gamma$, suspended in unconfined and confined geometries $\Omega$. The
 suspending fluid is assumed to be viscous so that the fluid velocity
@@
   -\nabla p + \mu \triangle \uu = 0, \quad
-  \nabla \cdot \uu = 0, \qquad \xx \in \RR^2 \setminus \gamma,
+  \nabla \cdot \uu = 0, \qquad \xx \in \Omega \setminus \gamma,
 \end{align}
@@
 condition $\uu(\xx) \rightarrow \uu_\infty(\xx)$ is enforced as $\xx
-\rightarrow \infty$, and in a confined geometry with boundary $\Gamma$,
-the boundary condition $\uu(\xx) = \UU(\xx)$ is enforced on $\Gamma$,
-where $\UU(\xx)$ is prescribed. Along the vesicle $\gamma$, mass
-continuity, a force balance, and local inextensibility are enforced by
-requiring
+\rightarrow \infty$, and in a confined geometry, the boundary condition
+$\uu(\xx) = \UU(\xx)$ is enforced on $\partial \Omega$, where $\UU(\xx)$
+is prescribed. Along the vesicle $\gamma$, mass continuity, a force
+balance, and local inextensibility are enforced by requiring
 \begin{align}
@@
 Semi-permeability is introduced by modifying the vesicle velocity from
-the standard choice. Instead of using the no-slip boundary condition, we
-assume the fluid flux through the boundary is proportional to the
-mechanical force~\cite{yao-mor2017}. That is, 
+the standard no-slip condition $\cdot{\xx} = \uu(\xx)$, where $\xx(s,t)$
+parameterizes the vesicle shape $\gamma$ at time $t$ with respect to
+arclength. Instead, we consider the case where the flux through the
+vesicle is proportional to the mechanical force~\cite{yao-mor2017}. That
+is, 
 \begin{align}
@@
 tension scale $Q = k_b/R_0 = 10^{-13}$N, and the permeability scale $W =
-R_0\mu = 2 \times 10^{-5}$m$^2$s/kg. The other standard dimensionless
-variable of a vesicle is its reduced area $\nu = 4\pi A/L^2 \in (0,1]$.
-The length $L$ is conserved by the local inextensibility condition.
-However, the area $A$ is not conserved because of semi-permeability, and
-therefore $\nu$ is also not conserved.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Integral equation formulation}
-Since the fluid satisfies the Stokes equations, it can be represented as
-layer potential. Given the interfacial boundary
+R_0\mu = 2 \times 10^{-5}$m$^2$s/kg. Another standard dimensionless
+variable in vesicle suspensions is the reduced area $\nu = 4\pi A/L^2
+\in (0,1]$, where $L$ is the vesicle length and $A$ is its area. The
+length is conserved by the local inextensibility condition, but the area
+is not because of semi-permeability. Therefore, the reduced area is
+dynamic.
+
+Since the fluid satisfies the Stokes equations, its velocity can be
+represented as a layer potential. Given the interfacial boundary
 conditions~\eqref{eqn:jump}, the fluid velocity is
@@
 condition~\eqref{eqn:vesicleFlux} and the inextensibility condition, the
-vesicle velocity satisfies
+vesicle velocity satisfies the boundary integral equation
 \begin{align}
@@
   + \SS [\ff_\mathrm{mem}](\xx),  \quad
-  \xx_s \cdot \dot{\xx}_s = 0.
+  \xx_s \cdot \dot{\xx}_s = 0,
 \end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection*{Dimensionless equations}
-%The inextensibility condition guarantees that the vesicle's length, $L$,
-%is conserved, while its area, $A$, can change due to semi-permeability.
-%Therefore, the reduced area $\alpha = 4\pi A/L^2 \in (0,1]$ is not
-%conserved. We non-dimensionalize~\eqref{eqn:vesVelocity} by introducing
-%the length scale $R_0 = L/2\pi$ and defining the time scale $\tau = \mu
-%R_0^3/k_b$, the tension scale $Q = k_b/R_0^2$, and the permeability
-%scale $W = R_0/\mu$. The background velocity $\uu_\infty$ is
-%non-dimensionalized with $R_0/\tau$.
-%
-%In each experiment, we initialize an elliptical vesicle with longest
-%diameter of 9$\mu$m. We use a length scale of $R_0 = 10^{-6}$m, a
-%bending stiffness of $k_b = 10^{-19}$J, and fluid viscosity of $\mu=5
-%\times 10^{-2}$kg/ms. Using the relaxation time scale $\tau = \mu
-%R_0^3/k_b = 5 \times 10^{-1}$s, the pressure scale is $P = k_b/R_0^3 =
-%10^{-1}$Pa.
+where $\beta = k_w/W$ is the dimensionless water permeability. In
+confined geometries, the far field term $\uu_\infty$ is replaced by a
+double-layer potential with a density defined on $\partial\Omega$. The
+unknown density function allows us to satisfy the Dirichlet boundary
+condition $\uu(\xx) = \UU(\xx)$ for $\xx \in \partial\Omega$.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Area dynamics}
-Following the analysis of Veerapaneni et al.~\cite{vee-raj-bir-pur2009},
-we compute the steady state shape of a semi-permeable vesicle in a
-quiescent flow. The steady state shape is a stationary point of the
-Lagrangian
+\section*{Supplementary Material: Vesicle Area}
+In the absence of an imposed flow, the steady state vesicle shape and a
+differential equation for the area of the vesicle can be derived. We
+start by following the analysis of Veerapaneni et
+al.~\cite{vee-raj-bir-pur2009} by computing the steady state shape of a
+semi-permeable vesicle in a quiescent flow. The steady state shape is a
+stationary point of the Lagrangian
 \begin{align}
@@
 be solved analytically in terms of the {\em EllipticF} function using
-Mathematica. Unlike in the impermeable case~\cite{vee-raj-bir-pur2009},
-the solution of~\eqref{eqn:curveODE} is not periodic unless $\kappa(s) =
-\kappa_0$. Therefore, the steady state shape of a semi-permeable vesicle
-in a quiescent flow is a circle with radius $L/2\pi$. Therefore, the
-steady state curvature and tension are
-\begin{align}
-  \kappa = \frac{2\pi}{L}, \: \Lambda = \frac{2\pi^2}{L^2}.
-  \label{eqn:SSshape}
-\end{align}
-Note that in contrast to a impermeable vesicle, the tension is positive
-rather than negative.
-
-We also compute the transient area of the vesicle. Since the area of the
+Mathematica. Unlike in the impermeable case, the solution
+of~\eqref{eqn:curveODE} is not periodic unless $\kappa(s) = \kappa_0$.
+Therefore, the steady state shape of a semi-permeable vesicle in a
+quiescent flow is a circle with radius $L/2\pi$. Therefore, the steady
+state curvature and tension are $\Lambda = 2\pi^2/L^2.$ Note that in
+contrast to a impermeable vesicle, the tension is positive rather than
+negative.
+
+We next compute the transient area of the vesicle. Since the area of the
 vesicle is
@@
 \end{align}
-Note that~\eqref{eqn:SSshape} and are consistent since the constant
-curvature and tension values cause the integrand to vanish.
+Note that the integrand in~\eqref{eqn:areaROC} is zero when the vesicle
+reaches its steady state which guarantees that $\dot{A}(t) = 0$.
 
@@
 \section*{Supplementary Material: Numerical Methods}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 By using a boundary integral equation formulation, the unknowns are the
-vesicle's position and tension that we track at $N$ discretization
-points. Derivatives are computed with Fourier differentiation, and the
+vesicle's position and tension that we track at $N$ collocation points.
+Derivatives are computed with Fourier differentiation, and the
 eighth-order quadrature~\cite{alp1999} is applied to the single-layer
-potential. For constricted flows, nearly-singular integrals are computed
-with an interpolation-based quadrature rule~\cite{qua-bir2014}.
+potential. For confined geometries, the trapezoid rule is used to
+approximate the double-layer potential since its kernel is smooth and
+periodic. Nearly-singular integrals are computed with an
+interpolation-based quadrature rule~\cite{qua-bir2014}.
 
@@
 \end{alignat}
-for the differential and projection operators. Letting $B^N$ be the
-bending operator due to the vesicle configuration at time $t^N$, and
-similar notation for the other operators, we use the first-order
-semi-implicit time stepping method
+for the differential and projection operators. Then, the
+governing equations~\eqref{eqn:vesVelocity} are
+\begin{align}
+  \dot{\xx} &= \uu_\infty(\xx) + \beta P(B\xx + T\sigma)
+  + \SS (B\xx + T\sigma), \quad
+  D \dot{\xx} = 0, 
+\end{align}
+We note that the integral and differential operators, which all depend
+on the vesicle shape, are non-linear with respect to the vesicle
+shape. We construct a time stepping scheme by letting $B^N$ be the
+bending operator due to the vesicle configuration at time $t^N$, and use
+similar notation for the other operators. Then, a first-order
+semi-implicit time stepping method of~\eqref{eqn:vesVelocity} is
 \begin{alignat}{3}  
@@
   &&+ \beta P^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right) \nonumber \\
-  & &&+ \SS^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right), 
+  & &&+ \SS^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right),  \\
+  D^N\xx^{N+1} &= 1.
 \end{alignat}
-and  the inextensibility condition is discretized as
-\begin{align}
-  D^N\xx^{N+1} &= 1.
-\end{align}
+This is a linear system that we solve with matrix-free GMRES.
+
 To achieve second-order accuracy over long time horizons, we modify an
@@
 
-\subsection*{Numerical validation: An impermeable vesicle in a Poiseuille flow}
-To validate our methods,
-in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
-for the steady state shape of an impermeable vesicle
-vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
-qualitatively agree, Kaoui et al.~report that the vesicles with
-$\alpha=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
-axisymmetric. In our simulations these vesicles are slightly asymmetric,
-are undergoing a tank treading motion, and we therefore report them as
-asymmetric slippers.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Numerical Validation}
+To validate our methods, we construct a phase diagram of the steady
+state shape of an impermeable vesicle in a Poiseuille flow. Depending on
+the flow rate and the reduced area, the steady state vesicle becomes
+either a symmetric bullet or parachute, or an asymmetric
+slipper~\cite{kao-bir-mis2009}. Comparing our results
+(Figure~\ref{fig:PoiseuillePhase}) with those in~\cite{kao-bir-mis2009}
+(see Figure 2), we see that the results qualitatively agree. We note
+that Kaoui et al.~report that the vesicles with $\alpha=0.7$ and flow
+rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are axisymmetric. In our
+simulations these vesicles are slightly asymmetric, are undergoing a
+tank treading motion, and we therefore report them as asymmetric
+slippers.
+\begin{figure}[htp]
+  \centering
+  \ifTikz
+  \input{figures/parabolicImpermeable.tikz}
+  \else
+  \includegraphics{figures/parabolicImpermeable.pdf}
+  \fi
+  \caption{\label{fig:PoiseuillePhase} Phase diagram of an impermeable
+  vesicle with various flow rates and reduced areas. The shapes agree
+  qualitatively with Kaoui et al.~\cite{kao-bir-mis2009} (see Figure
+  2).}
+\end{figure}
 
@@
 %vesicle.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection*{Dimensionless equations}
+%The inextensibility condition guarantees that the vesicle's length, $L$,
+%is conserved, while its area, $A$, can change due to semi-permeability.
+%Therefore, the reduced area $\alpha = 4\pi A/L^2 \in (0,1]$ is not
+%conserved. We non-dimensionalize~\eqref{eqn:vesVelocity} by introducing
+%the length scale $R_0 = L/2\pi$ and defining the time scale $\tau = \mu
+%R_0^3/k_b$, the tension scale $Q = k_b/R_0^2$, and the permeability
+%scale $W = R_0/\mu$. The background velocity $\uu_\infty$ is
+%non-dimensionalized with $R_0/\tau$.
+%
+%In each experiment, we initialize an elliptical vesicle with longest
+%diameter of 9$\mu$m. We use a length scale of $R_0 = 10^{-6}$m, a
+%bending stiffness of $k_b = 10^{-19}$J, and fluid viscosity of $\mu=5
+%\times 10^{-2}$kg/ms. Using the relaxation time scale $\tau = \mu
+%R_0^3/k_b = 5 \times 10^{-1}$s, the pressure scale is $P = k_b/R_0^3 =
+%10^{-1}$Pa. 
+% \newpage
+% \paragraph{\bf \Huge OLD STUFF}
+%
+%%%%%%%%%%%%%%%
+%\section{{$\Theta-L$} formulation}
+%Here, we attempt to apply the formulation described by Sohn et
+%al.~\cite{soh-tse-li-voi-low2010} to a semi-permeable vesicle.  In the
+%semi-permeable formulation, the vesicle velocity is
+%\begin{align}
+%  \pderiv{\XX}{t} = \uu(\XX(t)) + \beta (\ff \cdot \nn) \nn.
+%\end{align}
+%In the {$\Theta-L$} variables, we require a normal velocity $V$, and a
+%tangential velocity $T$. Since the inextensibility condition is $T_s +
+%\kappa V = 0$, a condition for the vesicle velocity is
+%\begin{align}
+%  (\uu \cdot \ss)_s = -\kappa(\beta (\ff \cdot \nn) + 
+%      \uu \cdot \nn).
+%\end{align}
+%This equation can be solved following equations (32)--(39)
+%in~\cite{soh-tse-li-voi-low2010}, with the only difference being that
+%$\tilde{\uu}$ satisfies
+%\begin{align}
+%  (\tilde{\uu} \cdot \ss)_s + \kappa(\tilde{\uu} \cdot \nn) =
+%    -(\vv \cdot \ss)_s - \kappa(\vv \cdot \nn) 
+%    - \beta\kappa(\ff \cdot \nn).
+%\end{align}
+%Compared to equation (40), only the last term is new.
+%
+%
+%%%%%%%%%%%%%%%
+%Finally, we write the time stepping method in matrix form as
+%\begin{align}
+%  A \left(
+%    \begin{array}{c}
+%      \xx^{N+1} \\ \sigma^{N+1}
+%    \end{array}
+%  \right) = 
+%  \left(
+%    \begin{array}{c}
+%      \xx^{N} + \Delta t \uu_\infty(\xx^N) \\ \mathbf{1}
+%    \end{array}
+%  \right),
+%\end{align}
+%where
+%\begin{align}
+% A = \left(
+%  \begin{array}{cc}
+%    I + \Delta t \beta P^N B^N + \Delta t \SS^N B^N & 
+%    -\Delta t P^N T^N - \Delta t \SS^N T^N \\
+%    D^N & 0
+%  \end{array}
+%  \right).
+%\end{align}
+%
+%\section{Area of a Vesicle}
+%The area inside a single vesicle $\gamma$ parameterized with $\xx$ is
+%\begin{align}
+%  A(t) = \int_{\gamma} (\xx \cdot \nn)\, ds = 
+%    \int_{0}^{2\pi} \left(\xx \cdot \pderiv{\xx}{\theta}^\perp\right)
+%    \, d\theta.
+%\end{align}
+%Taking the time derivative of $A(t)$,
+%\begin{align}
+%  \dot{A}(t) &= \int_{0}^{2\pi} \left(
+%    \dot{\xx} \cdot \pderiv{\xx}{\theta}^{\perp} + 
+%    \xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right) \\
+%    \, d\theta.
+%  &= \int_{0}^{2\pi} \left(
+%    (\dot{\xx} \cdot \nn)\|\xx'(\theta)\| \right) d\theta +
+%     \int_{0}^{2\pi}
+%    \xx \cdot \frac{d}{dt}\left(\nn |\frac{d\xx}{d\theta}| \right)
+%\end{align}
+%
+%
+%
+%\begin{align}
+%  A(t) = \frac{1}{2}\int_{\gamma} (\xx \cdot \nn)\, ds = 
+%    \frac{1}{2}\int_{0}^{2\pi} \left(\xx \cdot \pderiv{\xx}{\theta}^\perp\right)
+%    \, d\theta.
+%\end{align}
+%Taking the time derivative of $A(t)$,
+%\begin{align}
+%  \dot{A}(t) &= \frac{1}{2}\int_{0}^{2\pi} \left(\dot{\xx} \cdot
+%  \pderiv{\xx}{\theta}^{\perp} + 
+%    \xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right) d\theta, \\
+%  &= \frac{1}{2}
+%  \int_{0}^{2\pi}(\dot{\xx}\cdot\nn)\left\|\pderiv{\xx}{\theta}\right\|d\theta +
+%     \frac{1}{2}\int_{0}^{2\pi}
+%    \left(\xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right)d\theta, \\
+%  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds +
+%  \frac{1}{2}\int_{0}^{2\pi}\left(\xx \cdot \pderiv{}{t}\left(\nn
+%  \left\|\pderiv{\xx}{\theta}\right\|\right)\right)d\theta, \\
+%  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds + \frac{1}{2}
+%  \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds + \frac{1}{2}\int_{0}^{2\pi}
+%  \frac{\xx\cdot\nn}{\left\|\pderiv{\xx}{\theta}\right\|}
+%  \left(\pderiv{\xx}{\theta}\cdot
+%  \pderiv{\dot{\xx}}{\theta}\right)d\theta \\
+%  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds + \frac{1}{2}
+%  \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds + \frac{1}{2}\int_{\gamma}
+%  (\xx\cdot\nn) (\xx_s \cdot \dot{\xx}_s)\, ds.
+%\end{align}
+%To satisfy the inextensibilty condition, $\xx_s \cdot \dot{\xx}_s = 0$.
+%Therefore the time derivative of $A(t)$ is
+%\begin{align}
+%     \dot{A}(t) &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds
+%     + \frac{1}{2} \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds.
+%\end{align}
+%which we re-write as
+%\begin{align}
+%    \dot{A}(t) &= \frac{\beta}{2}
+%    \int_{\gamma}\left(\ff\cdot\nn\right)ds-\frac{1}{2}\int_{\gamma}\left(\xx^{\perp}\cdot\dot{\xx}_s\right) ds.
+%\end{align}
+%Applying integration by parts,
+%\begin{align}
+%    \dot{A}(t) &= \frac{\beta}{2}
+%    \int_{\gamma}\left(\ff\cdot\nn\right)ds+\frac{1}{2}\int_{\gamma}\left(\xx^{\perp}_s\cdot\dot{\xx}\right) ds,
+%\end{align}
+%which we re-write as
+%\begin{align}
+%    \dot{A}(t) &= \frac{\beta}{2}
+%    \int_{\gamma}\left(\ff\cdot\nn\right)ds+\frac{1}{2}\int_{\gamma}\left(\dot{\xx}\cdot\nn\right),\\
+%    \dot{A}(t) &= \beta \int_{\gamma}\left(\ff\cdot\nn\right)ds.
+%\end{align}
+%
+%
+%At steady state,
+%\begin{align}
+%    \dot{A}(t) &= \beta \int_{\gamma}\left(\ff\cdot\nn\right)ds =0.
+%\end{align}
+%We now replace $\ff$ with its definition and apply integration by parts
+%\begin{align}
+%   0=\beta\int_{\gamma} 
+%    (-k_b\xx_{ssss}+(\sigma\xx_s)_s)\cdot\nn\, ds =
+%   \beta\int_{\gamma}\left(k_b\xx_{sss}-\sigma\xx_s\right)\cdot
+%     \nn_s\, ds
+%\end{align}
+%From the Frenet-Serret formulas, we have 
+%\begin{align}
+%     -\beta\int_{\gamma}
+%     \left(k_b\xx_{sss}-\sigma\xx_s\right)\cdot\kappa\xx_s ds &=0.
+%\end{align}
+%
+%Applying integration by parts and Frenet-Serret again
+%\begin{align}
+%     \beta\int_{\gamma}
+%     k_b\kappa\left(\xx_{ss}\cdot\xx_{ss}\right)ds + \beta
+%     \int_{\gamma} k_b \kappa_s(\xx_{ss} \cdot \xx_s)ds +\beta\int_{\gamma}\kappa\sigma ds  &= 0,\\
+%    \beta\int_{\gamma} k_b\kappa(\kappa\nn \cdot
+%     \kappa\nn)+ \beta \int_{\gamma} k_b \kappa_s(\xx_{ss} \cdot
+%     \xx_s)ds +\beta\int_{\gamma}\kappa\sigma ds &= 0,
+%\end{align}
+%which we re-write as
+%\begin{align}
+%   \beta\int_{\gamma}k_b\kappa^3 ds + \beta \int_{\gamma} k_b
+%   \kappa_s(\xx_{ss} \cdot \xx_s)ds +\beta\int_{\gamma} \kappa\sigma ds = 0.
+%\end{align}
+%Applying Frenet-serret again,
+%\begin{align}
+%    \beta\int_{\gamma}k_b\kappa^3 ds + \beta \int_{\gamma} k_b
+%    \kappa_s(\kappa\nn \cdot \TT)ds +\beta\int_{\gamma} \kappa\sigma ds = 0, \\
+%    \beta\int_{\gamma}k_b\kappa^3 ds +\beta\int_{\gamma} \kappa\sigma ds  = 0.
+%\end{align}
+%
+%
+%\section{Including a concentration field}
+%Based on the work of Yao and Mori~\cite{yao-mor2017}, we introduce a
+%chemical concentration field $c$.  The concentration field is governed
+%by the advection-diffusion equation
+%\begin{align}
+%  \pderiv{c}{t} + \nabla \cdot (\uu c) = D\Delta c.
+%\end{align}
+%If the concentration is diffusion dominated (zero Peclet number), then
+%the concentration satisfies
+%\begin{align}
+%  \Delta c = 0, \quad \xx \in \RR^2.
+%\end{align}
+%The boundary conditions of the concentration field on the vesicle
+%$\gamma$ are
+%\begin{align}
+%  (\uu c - D\nabla c) \cdot \nn = c \pderiv{\xx}{t} \cdot \nn + 
+%    j_c + j_p,
+%\end{align}
+%where $j_c$ and $j_p$ are the transmembrane chemical flux due to passive
+%transport and active transport (pumps), respectively.  In the zero
+%Peclet number limit, the absence of an active transport mechanism, and
+%the choice for the passive flux, the boundary condition of the
+%concentration field is
+%\begin{align}
+%  -D\pderiv{c}{\nn} = c \pderiv{\xx}{t} + 
+%    k_c \jump{c}, \quad \xx \in \gamma.
+%\end{align}
+%To couple the vesicle dynamics to the concentration, there is a
+%difference between the fluid velocity and vesicle velocity
+%\begin{align}
+%  \uu - \pderiv{\xx}{t} = j_w \nn,
+%\end{align}
+%where $j_w$ is the water flux through the vesicle.  This is the
+%osmophoretic flow.  In~\cite{yao-mor2017}, this flux is
+%\begin{align}
+%  j_w = -k_w(RT\jump{c} + \ff_\text{mem} \cdot \nn).
+%\end{align}
+%In our current implementation, we drop the $RT\jump{c}$ term, and
+%let $\beta = k_w$.
+%
+%\section{Preliminary results}
+%
+%
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=.9\textwidth]{figures/1.jpg}
+%	\includegraphics[width=.9\textwidth]{figures/2.jpg}
+%	\includegraphics[width=.9\textwidth]{figures/3.jpg}
+%	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0$.}
+%%	\label{Shear0}
+%\end{figure}
+%
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=.9\textwidth]{figures/4.jpg}
+%	\includegraphics[width=.9\textwidth]{figures/5.jpg}
+%	\includegraphics[width=.9\textwidth]{figures/6.jpg}
+%	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0.5$.}
+%%	\label{Shear0}
+%\end{figure}
+%
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=.9\textwidth]{figures/7.jpg}
+%	\includegraphics[width=.9\textwidth]{figures/8.jpg}
+%	\includegraphics[width=.9\textwidth]{figures/9.jpg}
+%	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 1$.}
+%%	\label{Shear0}
+%\end{figure}
+%
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=.9\textwidth]{figures/10.jpg}
+%	\includegraphics[width=.9\textwidth]{figures/11.jpg}
+%	\includegraphics[width=.9\textwidth]{figures/12.jpg}
+%	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 2$.}
+%%	\label{Shear0}
+%\end{figure}
+% 
+% 
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=.9\textwidth]{figures/BE1.jpg}
+% 	\includegraphics[width=.9\textwidth]{figures/BE2.jpg}
+% 	\includegraphics[width=.9\textwidth]{figures/BE3.jpg}
+% 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0$.}
+%% 	\label{Shear0}
+% \end{figure}
+% 
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=.9\textwidth]{figures/BE4.jpg}
+% 	\includegraphics[width=.9\textwidth]{figures/BE5.jpg}
+% 	\includegraphics[width=.9\textwidth]{figures/BE6.jpg}
+% 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0.5$.}
+%% 	\label{Shear0}
+% \end{figure}
+% 
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=.9\textwidth]{figures/BE7.jpg}
+% 	\includegraphics[width=.9\textwidth]{figures/BE8.jpg}
+% 	\includegraphics[width=.9\textwidth]{figures/BE9.jpg}
+% 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 1$.}
+%% 	\label{Shear0}
+% \end{figure}
+% 
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=.9\textwidth]{figures/BE10.jpg}
+% 	\includegraphics[width=.9\textwidth]{figures/BE11.jpg}
+% 	\includegraphics[width=.9\textwidth]{figures/BE12.jpg}
+% 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 2$.}
+% 	\label{Shear0}
+% \end{figure}
+%
+%When the semi-permeable vesicle reaches a steady-state shape, we have
+%\begin{align}
+%  \int_{\gamma} \left(-\frac{\kappa^3}{2} + \kappa \Lambda \right) \, ds
+%  = 0.
+%\end{align}
+%Based on numerical observations, the steady-state shape is a circular
+%vesicle with constant tension. Since the tension and curvature are
+%constant, we can solve for the curvature in terms of the tension $\kappa
+%= \sqrt{2\Lambda}$. Therefore, the steady state shape is a circle of
+%radius $r = 1/\sqrt{2\Lambda}$, and therefore the length is
+%\begin{align}
+%  L = \frac{\sqrt{2}\pi}{\sqrt{\Lambda}},
+%\end{align}
+%which is constant by the local inextensibility constraint. Finally, we
+%can compute the final tension in terms of the length using the formula
+%\begin{align}
+%  \Lambda = \frac{2\pi^2}{L^2}.
+%\end{align}
+%Therefore, in contrast to a impermeable vesicle, the final tension is
+%positive rather than negative.
+%
+%We start by simulating a star-shaped vesicle in a quiescent flow with
+%semi-permeability rate $\beta=1$ (Figure~\ref{fig:starShape}). To
+%perform this simulation, we use an adaptive second-order time stepping
+%method~\cite{qua-bir2016}. The times and reduced areas are in the
+%titles, and note that the shapes are not eqiuspaced in time.
+%\begin{figure}[htp]
+%  \begin{minipage}{0.55\textwidth}
+%%    \ifTikz
+%    \input{figures/starRelaxation1.tikz}
+%    \input{figures/starRelaxation2.tikz}
+%    \input{figures/starRelaxation3.tikz}
+%    \input{figures/starRelaxation4.tikz}
+%    \input{figures/starRelaxation5.tikz}
+%    \input{figures/starRelaxation6.tikz}
+%%    \fi
+%  \end{minipage}
+%  \hfill
+%  \begin{minipage}{0.4\textwidth}
+%%  \ifTikz
+%  \input{figures/starAreaDeriv.tikz}
+%%  \fi
+%  \end{minipage}
+%%  \caption{\label{fig:starShape} A initially star-shaped semi-permeable
+%%  vesicle in a shear quiescent flow with $\beta=1$. Note that the time
+%%  steps are not equispaced. The area (red) and its derivative (blue) of
+%%  an initially star-shaped vesicle as a function of time. The dots
+%%  correspond to the time steps shown in six time steps
+%%  show on the left.}
+%\end{figure}
+%
+%\begin{table}[htp]
+%  \centering
+%  \begin{tabular}{|C{1cm}|*{6}{C{2cm}}|}
+%    \hline
+%    $\beta$ & $10^{0}$ & $10^{-1}$ & $10^{-2}$ & 
+%             $10^{-3}$ & $10^{-4}$ & $10^{-5}$ \\
+%    $t_\mathrm{SS}$ & $6.45 \times 10^{0}$ & $2.00 \times 10^{1}$ & 
+%                      $9.61 \times 10^{1}$ & $8.36 \times 10^{2}$ & 
+%                      $8.15 \times 10^{3}$ & $8.03 \times 10^{4}$ \\
+%    ratio & --- & 3.10 & 4.81 & 8.71 & 9.74 & 9.85 \\
+%    \hline
+%  \end{tabular}
+%  \caption{\label{tbl:ellipseRelaxTime} The time, $t_{\mathrm{SS}}$, for
+%  a semi-permeable vesicle to reach steady state.}
+%\end{table}
+%
+%\begin{table}[htp]
+%  \centering
+%  \begin{tabular}{|C{1cm}|*{6}{C{2cm}}|}
+%    \hline
+%    $\beta$ & $10^{0}$ & $10^{-1}$ & $10^{-2}$ & 
+%             $10^{-3}$ & $10^{-4}$ & $10^{-5}$ \\
+%    $t_\mathrm{SP}$ & $2.17 \times 10^{-2}$ & $1.25 \times 10^{-1}$ & 
+%                      $1.59 \times 10^{0}$ & $2.19 \times 10^{1}$ & 
+%                      $2.14 \times 10^{2}$ & $2.20 \times 10^{3}$ \\
+%    ratio & --- & 5.76 & 12.72 & 13.77 & 9.77 & 10.14 \\
+%    \hline
+%  \end{tabular}
+%  \caption{\label{tbl:ellipseBLTime} The time, $t_\mathrm{SP}$, for a
+%  semi-permeable vesicle to begin inflating.}
+%\end{table}
+%
+%%\begin{figure}[htp]
+%%\begin{minipage}{0.40\textwidth}
+%%\ifTikz
+%%\input{figures/starTension.tikz}
+%%\fi
+%%\end{minipage}
+%%\hfill
+%%\begin{minipage}{0.55\textwidth}
+%%  \centering
+%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime1.pdf}
+%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime2.pdf}
+%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime3.pdf} \\
+%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime4.pdf}
+%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime5.pdf}
+%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime6.pdf}
+%%\end{minipage}
+%%  \caption{\label{fig:starTension} The tension of the time steps shown
+%%  in Figure~\ref{fig:starShape}. The tension at the time horizon $T=1$
+%%  is also included. At this point, the vesicle is nearly circular and
+%%  the tension is constant and positive. The constant is given by
+%%  equation~\eqref{eqn:SSshape}, and this value corresponds to the
+%%  dashed black line.}
+%%\end{figure}
+%
+%%\begin{figure}[htp]
+%%\begin{minipage}{0.40\textwidth}
+%%%\ifTikz
+%%\input{figures/starFlux.tikz}
+%%%\fi
+%%\end{minipage}
+%%\hfill
+%%\begin{minipage}{0.55\textwidth}
+%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime1.pdf}
+%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime2.pdf}
+%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime3.pdf} \\
+%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime4.pdf}
+%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime5.pdf}
+%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime6.pdf}
+%%\end{minipage}
+%%  \caption{\label{fig:starFlux} The flux of the time steps shown in
+%%  Figure~\ref{fig:starShape}. The tension at the time horizon $T=1$ is
+%%  also included. At this point, the vesicle is nearly circular and there
+%%  is no flux.}
+%%\end{figure}
+%\begin{figure}[htp]
+%    \ifTikz
+%    \input{figures/starRelaxation1.tikz}
+%    \quad
+%    \input{figures/starRelaxation2.tikz}
+%    \quad
+%    \input{figures/starRelaxation3.tikz}
+%    \quad
+%    \input{figures/starRelaxation4.tikz}
+%    \quad
+%    \input{figures/starRelaxation5.tikz}
+%    \fi
+%  \caption{\label{fig:starShape} An initially star-shaped semi-permeable
+%  vesicle in a quiescent flow with $\beta=1$. Note that the time steps
+%  are not equispaced.}
+%\end{figure}
+%\begin{figure}[htp]
+%  \centering
+%%  \ifTikz
+%  \input{figures/ellipseVelocity1.tikz}
+%  \input{figures/ellipseVelocity2.tikz}
+%  \input{figures/ellipseVelocity3.tikz}
+%%  \fi
+%  \caption{\label{fig:vesVelocity} The velocity contributions due to
+%  semi-permeability (red) and force balance (blue). The green dashed
+%  line is the velocity of an impermeable vesicle with the same initial
+%  shape as the semi-permeable vesicle.}
+%\end{figure}
+%
+%\begin{figure}[htp]
+%%  \ifTikz
+%  \input{figures/ellipseVelocityNorms.tikz}
+%%  \fi
+%  \caption{\label{fig:vesVelocityNorm} The max norm of the velocity due
+%  to the force balance (blue) and semi-permeability. Also included is
+%  the velocity of an impermeable vesicle (green). The three black lines
+%  correspond to the times reported in Figure~\ref{fig:vesVelocity}.}
+%\end{figure}
+
+% \newpage
+%\input{figures/shearPhaseDiagramRA2.tikz}
+%\input{figures/parabolicPhaseDiagram.tikz}
+%\begin{figure}[htp]
+%%  \ifTikz
+%%  \input{figures/parabolicPhaseDiagram.tikz}
+%%  \fi
+%  \includegraphics[width=0.9\linewidth]{figures/parabolicPhaseDiagram.pdf}
+%  \caption{\label{fig:parabolicPhaseDiagram} The steady state shape of a
+%  semi-permeable vesicle with several different permeability rates
+%  $\beta$ and flow rates $U$. The numbers reported above each vesicle is
+%  its reduced area. At high flow rates, the vesicle self-intersects
+%  before reaching a steady state configuration.}
+%\end{figure}
+%
+%
+%\begin{table}[htp]
+%  \centering
+%  \caption{\label{tbl:parabolicRelaxTimes1} The time for a
+%  semi-permeable vesicle in a Poiseuille flow to reach its steady state
+%  ($t_\mathrm{steady}$) and to begin inflating ($t_\mathrm{inflate}$).
+%  The times are reported for the maximum velocities $0.1 \mu m/s$ and
+%  $10 \mu m/s$.}
+%  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
+%    \multicolumn{5}{c}{$U = 0.1 \mu m/s$} \\
+%    $\beta$ & $t_\mathrm{steady}$ & ratio & $t_\mathrm{inflate}$ & ratio \\
+%    \midrule
+%    $10^{0}$  & $3.33 \times 10^{0}$ & ---  
+%              & $1.67 \times 10^{-2}$ & --- \\ 
+%    $10^{-1}$ & $1.37 \times 10^{1}$ & 4.12 & 
+%                $8.73 \times 10^{-1}$ & 5.23 \\
+%    $10^{-2}$ & $8.60 \times 10^{1}$ & 6.26 & 
+%                $1.11 \times 10^{0}$ & 12.74 \\
+%    $10^{-3}$ & $7.75 \times 10^{2}$ & 9.01 & 
+%                $1.63 \times 10^{1}$ & 14.70 \\
+%    $10^{-4}$ & $7.69 \times 10^{3}$ & 9.93 & 
+%                $1.74 \times 10^{2}$ & 10.63 \\
+%    $10^{-5}$ & $8.01 \times 10^{4}$ & 10.41 & 
+%                $1.66 \times 10^{3}$ & 9.58 \\
+%    \bottomrule
+%  \end{tabular}
+%
+%  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
+%    \multicolumn{5}{c}{$U = 10 \mu m/s$} \\
+%    $\beta$ & $t_\mathrm{steady}$ & ratio & $t_\mathrm{inflate}$ & ratio \\
+%    \midrule
+%    $10^{0}$  & $3.55 \times 10^{0}$ & ---  
+%              & $1.67 \times 10^{-2}$ & --- \\ 
+%    $10^{-1}$ & $1.87 \times 10^{1}$ & 5.27 & 
+%                $9.01 \times 10^{-2}$ & 5.40 \\
+%    $10^{-2}$ & $1.17 \times 10^{2}$ & 6.26 & 
+%                $1.52 \times 10^{0}$ & 16.87 \\
+%    $10^{-3}$ & $1.06 \times 10^{3}$ & 9.06 & 
+%                $2.07 \times 10^{1}$ & 13.62 \\
+%    $10^{-4}$ & $1.02 \times 10^{4}$ & 9.62 & 
+%                $2.25 \times 10^{2}$ & 10.87 \\
+%    $10^{-5}$ & $1.04 \times 10^{5}$ & 10.20 & 
+%                $2.25 \times 10^{3}$ & 10.00 \\
+%    \bottomrule
+%  \end{tabular}
+%\end{table}
+%The width $W$ is chosen so that $W/R =
+%10$, where $R$ is the radius of the vesicle. We investigate the effect
+%of the maximum velocity $U$ and the permeability rate $\beta$ on the
+%steady state shape of a vesicle initially placed on the center line
+%$y=0$. Figure~\ref{fig:parabolicPhaseDiagram} shows the steady state
+%configuration for a variety of maximum velocities and permeability
+%rates. Similar to the shear example, the maximum velocity strongly
+%affects the final shape while the permeability rate's effect is much
+%weaker. Instead, the permeability rate determines the time required for
+%the vesicle to reach a steady state. In
+%Table~\ref{tbl:parabolicRelaxTimes1}, we consider two maximum velocities
+%and report the time, $t_\mathrm{steady}$, required for the vesicle's
+%area to be within 1.3\% of its maximum area, and the time,
+%$t_\mathrm{inflate}$, required for the vesicle's area to exceed 1.3\% of
+%its initial area. We see that both times scale with $\beta^{-1}$.
+
+%\begin{figure}[htp]
+%  \centering
+%  \begin{tabular}{ccc}
+%    \ifTikz
+%    \scalebox{0.31}{\input{figures/stenosisTension1.tikz}} &
+%    \scalebox{0.31}{\input{figures/stenosisTension3.tikz}} &
+%    \scalebox{0.31}{\input{figures/stenosisTension5.tikz}} \\
+%    \scalebox{0.31}{\input{figures/stenosisTension7.tikz}} &
+%    \scalebox{0.31}{\input{figures/stenosisTension9.tikz}} &
+%    \scalebox{0.31}{\input{figures/stenosisTension11.tikz}} 
+%    \fi
+%  \end{tabular}
+%  \caption{\label{fig:stenosisTension} The tension of the impermeable
+%  (red) and semi-permeable (dashed blue) vesicles in
+%  Figure~\ref{fig:stenosisShape}. The point $\theta=0$ corresponds to
+%  the right-most point of the vesicle.}
+%\end{figure}
+%
+%\begin{figure}[htp]
+%  \centering
+%  \begin{tabular}{ccc}
+%    \iftikz
+%    \scalebox{0.31}{\input{figures/stenosisflux1.tikz}} &
+%    \scalebox{0.31}{\input{figures/stenosisflux3.tikz}} &
+%    \scalebox{0.31}{\input{figures/stenosisflux5.tikz}} \\
+%    \scalebox{0.31}{\input{figures/stenosisflux7.tikz}} &
+%    \scalebox{0.31}{\input{figures/stenosisflux9.tikz}} &
+%    \scalebox{0.31}{\input{figures/stenosisflux11.tikz}} 
+%    \fi
+%  \end{tabular}
+%  \caption{\label{fig:stenosisFlux} The flux (equivalent to pressure
+%  jump) of the impermeable (red) and semi-permeable (dashed blue)
+%  vesicles in Figure~\ref{fig:stenosisShape}. The point $\theta=0$
+%  corresponds to the right-most point of the vesicle.}
+%\end{figure}

### 2020-12-29 vesicle_code/docs/permeableVes/main.tex
all

--- 2020-12-29 vesicle_code/docs/permeableVes/main.tex
@@
 \begin{abstract}
-We describe a mathematical model for a semi-permeable vesicle and derive
-  a boundary integral equation formulation for simulating its
-  hydrodynamics.
-
-Please provide an abstract of no more than 250 words in a single paragraph.
+In this work we use boundary integral simulations to investigate the effects of water permeability on the hydrodynamics of a vesicle under various flows and confinement configurations.
+Using the Helfrich free energy extended for the coupling of membrane permeability with the membrane elastic stress, tension and mechanical stress, we illustrate that, in the absence of an osmotic stress gradient, a typical liposome may be significantly affected by membrane permeability over a sufficiently long time or under strong confinement.
+Lipid bilayer membranes are permeable to water molecules, and water influx/efflux  is often assumed to be negligible in the absence of osmolarity, even when the membrane undergoes large deformation.
+Our simulation results quantify the conditions for such assumption to be valid, and shed light on how confinement can be utilized to estimate membrane permeability.
+%
+%osmotic stress gradient 
+%We describe a mathematical model for a semi-permeable vesicle and derive
+%  a boundary integral equation formulation for simulating its
+%  hydrodynamics.  
+%
+%Please provide an abstract of no more than 250 words in a single paragraph.
 Abstracts should explain to the general reader the major contributions of the article.
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{figures/schematic.pdf}
+  \includegraphics[width=0.5\textwidth]{figures/schematic.pdf}
   \caption{\label{fig:sketch} Schematics showing the effects of
@@
 \section*{Formulation}
-We consider a two-dimensional semi-permeable vesicle (permeable only to water) suspended in a viscous fluid, see figure~\ref{fig:sketch}.
+We consider a two-dimensional semi-permeable vesicle (permeable only to water) suspended in a viscous fluid, see Figure~\ref{fig:sketch}.
 To focus on the effect of water flow on vesicle hydrodynamics in various conditions, we assume the fluid is the same inside and outside the vesicle membrane.
@@
 \end{align}
-where $\gamma$ denotes the membrane boundary with an outward normal $\nn$, $k_w$ is the water permeability, $R$ is the ideal gas constant, $T$ is the temperature ($^{\circ}$K), $\triangle c$ is contrast in a solute concentration (mol/volume),
+where $\gamma$ denotes the membrane boundary with an outward normal $\nn$ (Figure~\ref{fig:sketch}), $k_w$ is the water permeability, $R$ is the ideal gas constant, $T$ is the temperature ($^{\circ}$K), $\triangle c$ is contrast in a solute concentration (mol/volume),
 and $\ff_\mathrm{mem}$ is the membrane stress that consists of both bending $ \ff_\mathrm{ben}= -k_b \xx_{ssss}$ and tension $\ff_\mathrm{ten}=(\sigma \xx_s)_s$ ($s$
-is the arclength along the membrane, see figure~\ref{fig:sketch}.
+is the arclength along the membrane, see Supplementary Material).
 Using $k_w\sim 10^{-12}$ m$^2$s/kg (typical of mammalian cell membranes \cite{LiMoriSun2015_PRL}) and an osmolarity $\triangle c = 0.1$ mol/L (consistent with the osmotic forces in vesicle aspiration experiments \cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the corresponding water flow is of the order $v_\mathrm{o}=0.1 \mu$m/s.
@@
   flow rates and semi-permeability rates. The circled vesicles
-  correspond to the simulations in part (a). {\bf YNY: should this be two-column wide?}}
+  correspond to the simulations in part (a). 
+  %{\bf YNY: should this be two-column wide?}
+  }
 \end{figure}
@@
 \section*{Discussion}
+In this work we investigated the effects of membrane permeability to water on the vesicle hydrodynamics.
+Without any external flow or confinement, our analysis shows that a semi-permeable vesicle always inflates to maximize the water content inside the vesicle of a fixed length (area) in two (three) dimensions.
+Results from analysis and numerical simulation show that such relaxation of a semi-permeable vesicle is characterized by a rescaled time $\beta t$.
+We further illustrate that the relaxation process consists of at least two phases: The
+first phase is dominated by the balance between membrane traction and viscous stress at early times (up to a minute), when the vesicle behaves like an impermeable membrane.
+The second phase sets in after a few minutes, when water influx begins to dominate and inflate the vesicle.
+Over a timescale of a few hours a semipermeable vesicle is fully inflated, independent of its initial surface-to-volume ratio.
+
+The two phases in the relaxation dynamics are also observed  in the hydrodynamics of a semipermeable vesicle under a shear flow (both the planar and Poiseuille flows) in free space. 
+As an impermeable vesicle in a shear flow, a semipermeable vesicle also reaches an equilibrium shape and position.
+Yet for a semi-permeable vesicle the equilibrium shape depends on the strength of the shear flow (shear rate $\dot\gamma$ for the planar shear flow, and $U_{max}$ for the Poiseuille flow).
+Our simulations also show that, in a Poiseuille flow, symmetric equilibrium vesicle shape is possible only at low flow velocity.
+In experiments it may take a few hours for the semipermeable vesicle to reach such  equilibria that could be used to quantify the flow strength.
+
+Under strong confinement we show that water permeation can be amplified on a timescale of a few seconds as a vesicle is squeezed through a closely fit channel and a contracting 
+channel. As a semi-permeable vesicle goes through a long closely-fit channel, we observe that the vesicle loses water at a constant rate, and the longer the channel the more the loss 
+of water. In the case of contracting channel, we find that both permeability and the pressure gradient across the slit must be sufficiently large for a successful passage. Throughout 
+these simulations the membrane tension is below the threshold for membrane poration. Thus we expect the continuum membrane theory to well-capture the vesicle hydrodynamics, 
+and our simulation results shed light on the configuration and timescales needed to observe the effects of permeability on vesicle hydrodynamics under confinement.
 

### 2020-12-29 vesicle_code/docs/permeableVes/main.tex
yny
working on supp mat

@@
 \newif\ifTikz
-\Tikztrue
-%\Tikzfalse
-
-\usepgfplotslibrary{external}
-\tikzexternalize
+%\Tikztrue
+\Tikzfalse
+
+%\usepgfplotslibrary{external}
+%\tikzexternalize
 
@@
 there exists a critical reduced volume above which the equilibrium vesicle shape is symmetric (parachute or bullet shapes) and the vesicle stays at $y=0$.
-Below this critical reduced volume the equilibrium vesicle moves off the center and is asymmetric (tank-treading slipper shape).
-We validated our numerical codes by comparing against results in Kaoui {\it et al.} \cite{kao-bir-mis2009}, see Supplementary Material.
+Below this critical reduced volume the equilibrium vesicle moves off the
+center and is asymmetric (tank-treading slipper shape).  We validated
+our numerical codes by comparing against results in Kaoui {\em et
+al.}~\cite{kao-bir-mis2009}, see Supplementary Material.
 
@@
 $\gamma$, suspended in unconfined and confined geometries $\Omega$. The
-suspending fluid is assumed to be viscous so that the fluid velocity
-$\uu$ and pressure $p$ are governed by the incompressible Stokes
-equations
+vesicle is parameterized as $\xx(s,t)$ where $s$ is arclength and $t$ is
+time. The suspending fluid is assumed to be viscous so that the fluid
+velocity $\uu$ and pressure $p$ are governed by the incompressible
+Stokes equations
 \begin{align}
@@
 where $\mu$ is the fluid viscosity. In an unconfined geometry, the
-condition $\uu(\xx) \rightarrow \uu_\infty(\xx)$ is enforced as $\xx
+condition $\uu(\xx) \rightarrow \uu_\infty(\xx)$ is enforced as $|\xx|
 \rightarrow \infty$, and in a confined geometry, the boundary condition
 $\uu(\xx) = \UU(\xx)$ is enforced on $\partial \Omega$, where $\UU(\xx)$
-is prescribed. Along the vesicle $\gamma$, mass continuity, a force
+is prescribed. Along the vesicle $\gamma$, mass continuity, force
 balance, and local inextensibility are enforced by requiring
@@
 with bending modulus $k_b$ and a force due to the tension $\Lambda$.
-Following~\cite{vee-gue-zor-bir2009}, we modify the bending and tension
-forces as $\ff_\mathrm{ben} = -k_b \xx_{ssss}$, and $\ff_\mathrm{ten} =
-(\sigma \xx_s)_s$, where $s$ is arclength. The physical tension can be
-recovered using the identity $\Lambda = \sigma + 1.5 \kappa^2$, where
-$\kappa$ is the membrane curvature.
+Following~\cite{vee-gue-zor-bir2009}, we introduce the variable $\sigma
+= \Lambda - 1.5\kappa^2$, where $\kappa$ is the vesicle curvature. Then,
+the bending and tension forces are $\ff_\mathrm{ben} = -k_b \xx_{ssss}$
+and $\ff_\mathrm{ten} = (\sigma \xx_s)_s$.
 
 Semi-permeability is introduced by modifying the vesicle velocity from
-the standard no-slip condition $\cdot{\xx} = \uu(\xx)$, where $\xx(s,t)$
-parameterizes the vesicle shape $\gamma$ at time $t$ with respect to
-arclength. Instead, we consider the case where the flux through the
-vesicle is proportional to the mechanical force~\cite{yao-mor2017}. That
-is, 
+the standard no-slip condition $\dot{\xx} = \uu(\xx)$. Instead, we
+assume that the flux through the vesicle is proportional to the
+mechanical force~\cite{yao-mor2017}. That is, 
 \begin{align}
@@
 R_0/\tau = 2\mu$m/s, the pressure scale $P = k_b/R_0^3 = 10^{-1}$Pa, the
-tension scale $Q = k_b/R_0 = 10^{-13}$N, and the permeability scale $W =
-R_0\mu = 2 \times 10^{-5}$m$^2$s/kg. Another standard dimensionless
+tension scale $Q = k_b/R_0^2 = 10^{-7}$N/m, and the permeability scale
+$W = R_0\mu = 2 \times 10^{-5}$m$^2$s/kg. Another standard dimensionless
 variable in vesicle suspensions is the reduced area $\nu = 4\pi A/L^2
@@
 
-Since the fluid satisfies the Stokes equations, its velocity can be
-represented as a layer potential. Given the interfacial boundary
-conditions~\eqref{eqn:jump}, the fluid velocity is
+Since the fluid satisfies the Stokes equations, the velocity and
+pressure can be represented as layer potentials. Given the interfacial
+boundary conditions~\eqref{eqn:jump}, the fluid velocity is
 \begin{align}
@@
 \end{align}
-with $\rr = \xx - \yy$ and $\rho = \norm{\rr}$. Imposing the flux
+with $\rr = \xx - \yy$ and $\rho = |\rr|$. Imposing the flux
 condition~\eqref{eqn:vesicleFlux} and the inextensibility condition, the
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Supplementary Material: Numerical Methods}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Discretization in Space}
+By using a boundary integral equation formulation, the unknowns are the
+vesicle's position and tension and the unknown density function for
+confined flows. Both $\gamma$ and $\partial\Omega$ are discretized at
+$N$ and $N_\text{wall}$ points. Derivatives are computed with Fourier
+differentiation, and the eighth-order quadrature~\cite{alp1999} is
+applied to the weakly singular single-layer potential. For confined
+geometries, the trapezoid rule is used to approximate the double-layer
+potential since its kernel is smooth and periodic. Nearly-singular
+integrals are computed with an interpolation-based quadrature
+rule~\cite{qua-bir2014}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Discretization in Time}
+To eliminate stringent time step restrictions, we modify a time stepping
+method that discretizes high-order derivatives
+semi-implicitly~\cite{vee-gue-zor-bir2009}. We introduce the notation
+\begin{alignat}{3}
+  &B[\xx]\ff = -\frac{d^4}{ds^4} \ff,  \qquad
+  &&T[\xx]\sigma = (\sigma \xx_s)_s, \\
+  &D[\xx]\ff = \xx_s \cdot \ff_s, 
+  &&P[\xx]\ff = (\ff \cdot \nn) \nn,
+\end{alignat}
+for the differential and projection operators. Then, the
+governing equations~\eqref{eqn:vesVelocity} are
+\begin{align}
+  \dot{\xx} &= \uu_\infty(\xx) + \beta P(B\xx + T\sigma)
+  + \SS (B\xx + T\sigma), \quad
+  D \dot{\xx} = 0.
+\end{align}
+We note that the integral and differential operators, which all depend
+on the vesicle shape, are non-linear with respect to the vesicle
+shape. We construct a time stepping scheme by letting $B^N$ be the
+bending operator due to the vesicle configuration at time $t^N$, and use
+similar notation for the other operators. Then, a first-order
+semi-implicit time stepping method of~\eqref{eqn:vesVelocity} is
+\begin{alignat}{3}  
+  \frac{\xx^{N+1} - \xx^N}{\Delta t} &= \uu_\infty(\xx^N) 
+  &&+ \beta P^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right) \nonumber \\
+  & &&+ \SS^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right),  \\
+  D^N\xx^{N+1} &= 1,
+\end{alignat}
+and this is a linear system that we solve with matrix-free GMRES.
+
+To achieve second-order accuracy over long time horizons, we modify an
+adaptive spectral deferred correction time stepping
+method~\cite{qua-bir2016}. Since the area of the vesicle is not
+conserved, we only use the length of the vesicle to estimate the error
+which determines if a time step is accepted or not and determines the
+subsequent time step size.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Numerical Validation}
+To validate our methods, we construct a phase diagram of the steady
+state shape of an impermeable vesicle in a Poiseuille flow. Depending on
+the flow rate and the reduced area, the steady state vesicle becomes
+either a axisymmetric bullet, a axisymmetric parachute, or a tank
+treading asymmetric slipper~\cite{kao-bir-mis2009}. Comparing our
+results (Figure~\ref{fig:PoiseuillePhase}) with those
+in~\cite{kao-bir-mis2009} (see Figure 2), we see that the vesicle shapes
+qualitatively agree. We note that Kaoui {\em et al.}~report that the vesicles
+with $\alpha=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu
+m/s$ are axisymmetric.  In our simulations these vesicles are slightly
+asymmetric, are undergoing a tank treading motion, and we therefore
+report them as asymmetric slippers.
+\begin{figure}[htp]
+  \centering
+  \ifTikz
+  \input{figures/parabolicImpermeable.tikz}
+  \else
+  \includegraphics{figures/parabolicImpermeable.pdf}
+  \fi
+  \caption{\label{fig:PoiseuillePhase} Phase diagram of an impermeable
+  vesicle with various reduced areas submerged in a Poiseuille flow with
+  various flow rates. The shapes agree qualitatively with Kaoui {\em et
+  al.}~\cite{kao-bir-mis2009} (see Figure 2).}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Supplementary Material: Vesicle Area}
@@
 differential equation for the area of the vesicle can be derived. We
-start by following the analysis of Veerapaneni et
-al.~\cite{vee-raj-bir-pur2009} by computing the steady state shape of a
+start by following the analysis of Veerapaneni {\em et
+al.}~\cite{vee-raj-bir-pur2009} by computing the steady state shape of a
 semi-permeable vesicle in a quiescent flow. The steady state shape is a
@@
 Therefore, the steady state shape of a semi-permeable vesicle in a
-quiescent flow is a circle with radius $L/2\pi$. Therefore, the steady
-state curvature and tension are $\Lambda = 2\pi^2/L^2.$ Note that in
-contrast to a impermeable vesicle, the tension is positive rather than
-negative.
+quiescent flow is a circle with radius $L/2\pi$ and constant tension
+$\Lambda = 2\pi^2/L^2.$ Note that in contrast to a impermeable vesicle,
+the tension is positive rather than negative.
 
@@
 Note that the integrand in~\eqref{eqn:areaROC} is zero when the vesicle
-reaches its steady state which guarantees that $\dot{A}(t) = 0$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Supplementary Material: Numerical Methods}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Discretization in Space}
-By using a boundary integral equation formulation, the unknowns are the
-vesicle's position and tension that we track at $N$ collocation points.
-Derivatives are computed with Fourier differentiation, and the
-eighth-order quadrature~\cite{alp1999} is applied to the single-layer
-potential. For confined geometries, the trapezoid rule is used to
-approximate the double-layer potential since its kernel is smooth and
-periodic. Nearly-singular integrals are computed with an
-interpolation-based quadrature rule~\cite{qua-bir2014}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Discretization in Time}
-To eliminate stringent time step restrictions, we modify a time stepping
-method that discretizes high-order derivatives
-semi-implicitly~\cite{vee-gue-zor-bir2009}. We introduce the notation
-\begin{alignat}{3}
-  &B[\xx]\ff = -\frac{d^4}{ds^4} \ff,  \qquad
-  &&T[\xx]\sigma = (\sigma \xx_s)_s, \\
-  &D[\xx]\ff = \xx_s \cdot \ff_s, 
-  &&P[\xx]\ff = (\ff \cdot \nn) \nn,
-\end{alignat}
-for the differential and projection operators. Then, the
-governing equations~\eqref{eqn:vesVelocity} are
-\begin{align}
-  \dot{\xx} &= \uu_\infty(\xx) + \beta P(B\xx + T\sigma)
-  + \SS (B\xx + T\sigma), \quad
-  D \dot{\xx} = 0, 
-\end{align}
-We note that the integral and differential operators, which all depend
-on the vesicle shape, are non-linear with respect to the vesicle
-shape. We construct a time stepping scheme by letting $B^N$ be the
-bending operator due to the vesicle configuration at time $t^N$, and use
-similar notation for the other operators. Then, a first-order
-semi-implicit time stepping method of~\eqref{eqn:vesVelocity} is
-\begin{alignat}{3}  
-  \frac{\xx^{N+1} - \xx^N}{\Delta t} &= \uu_\infty(\xx^N) 
-  &&+ \beta P^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right) \nonumber \\
-  & &&+ \SS^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right),  \\
-  D^N\xx^{N+1} &= 1.
-\end{alignat}
-This is a linear system that we solve with matrix-free GMRES.
-
-To achieve second-order accuracy over long time horizons, we modify an
-adaptive spectral deferred correction time stepping
-method~\cite{qua-bir2016}. Since the area of the vesicle is not
-conserved, we only use the length of the vesicle to estimate the error
-which determines if a time step is accepted or not and determines the
-subsequent time step size.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Numerical Validation}
-To validate our methods, we construct a phase diagram of the steady
-state shape of an impermeable vesicle in a Poiseuille flow. Depending on
-the flow rate and the reduced area, the steady state vesicle becomes
-either a symmetric bullet or parachute, or an asymmetric
-slipper~\cite{kao-bir-mis2009}. Comparing our results
-(Figure~\ref{fig:PoiseuillePhase}) with those in~\cite{kao-bir-mis2009}
-(see Figure 2), we see that the results qualitatively agree. We note
-that Kaoui et al.~report that the vesicles with $\alpha=0.7$ and flow
-rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are axisymmetric. In our
-simulations these vesicles are slightly asymmetric, are undergoing a
-tank treading motion, and we therefore report them as asymmetric
-slippers.
-\begin{figure}[htp]
-  \centering
-  \ifTikz
-  \input{figures/parabolicImpermeable.tikz}
-  \else
-  \includegraphics{figures/parabolicImpermeable.pdf}
-  \fi
-  \caption{\label{fig:PoiseuillePhase} Phase diagram of an impermeable
-  vesicle with various flow rates and reduced areas. The shapes agree
-  qualitatively with Kaoui et al.~\cite{kao-bir-mis2009} (see Figure
-  2).}
-\end{figure}
+reaches its steady state which confirms that $\dot{A}(t) = 0$.
 

### 2020-12-29 vesicle_code/docs/permeableVes/main.tex
yny

@@
 %Physics}
-\title{Effects of Water Permeability on the Hydrodynamics of a Vesicle Under Flow and Confinement}
+\title{Hydrodynamics of a  Semi-permeable Vesicle Under Flow and Confinement}
 
@@
 \author[a]{Ashley Gannon}
-\author[b,1]{Y.-N. Young}
-
-\affil[a]{Department of Scientific Computing, Florida State University}
-\affil[b]{Department of Mathematical Sciences, New Jersey Institute of
-Technology}
+\author[b]{Howard A. Stone}
+\author[c,1]{Y.-N. Young}
+
+\affil[a]{Department of Scientific Computing, Florida State University, Tallahessee, FL 33306}
+\affil[b]{Department of Mechanical and Aerospace Engineering, Princeton University, Princeton, NJ 08544}
+\affil[c]{Department of Mathematical Sciences, New Jersey Institute of
+Technology, Newark, NJ 07102}
 

### 2020-12-29 vesicle_code/docs/permeableVes/main.tex
added a todo
editing early sections

@@
 
-%\title{Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and
+%\title{Semipermeable Vesicles: Mathematical Formulation, Numerics, and
 %Physics}
-\title{Hydrodynamics of a  Semi-permeable Vesicle Under Flow and Confinement}
+\title{Hydrodynamics of a  Semipermeable Vesicle Under Flow and
+Confinement}
 
@@
 \author[a]{Ashley Gannon}
-\author[b]{Howard A. Stone}
-\author[c,1]{Y.-N. Young}
+\author[b]{Howard A.~Stone}
+\author[c,1]{Y.-N.~Young}
 
@@
 \begin{abstract}
-In this work we use boundary integral simulations to investigate the effects of water permeability on the hydrodynamics of a vesicle under various flows and confinement configurations.
-Using the Helfrich free energy extended for the coupling of membrane permeability with the membrane elastic stress, tension and mechanical stress, we illustrate that, in the absence of an osmotic stress gradient, a typical liposome may be significantly affected by membrane permeability over a sufficiently long time or under strong confinement.
-Lipid bilayer membranes are permeable to water molecules, and water influx/efflux  is often assumed to be negligible in the absence of osmolarity, even when the membrane undergoes large deformation.
-Our simulation results quantify the conditions for such assumption to be valid, and shed light on how confinement can be utilized to estimate membrane permeability.
+In this work we use boundary integral simulations to investigate the
+effects of water permeability on the hydrodynamics of a vesicle under
+various flows and confinement configurations. Using the Helfrich free
+energy extended for the coupling of membrane permeability with the
+membrane elastic stress, tension and mechanical stress, we illustrate
+that, in the absence of an osmotic stress gradient, a typical liposome
+may be significantly affected by membrane permeability over a
+sufficiently long time or under strong confinement. Lipid bilayer
+membranes are permeable to water molecules, and water influx/efflux is
+often assumed to be negligible in the absence of osmolarity, even when
+the membrane undergoes large deformation. Our simulation results
+quantify the conditions for such assumption to be valid, and shed
+light on how confinement can be utilized to estimate membrane
+permeability.
 %
 %osmotic stress gradient 
-%We describe a mathematical model for a semi-permeable vesicle and derive
+%We describe a mathematical model for a semipermeable vesicle and derive
 %  a boundary integral equation formulation for simulating its
@@
 
-\dropcap{W}ater exchange is essential for a living cell to adapt to its environment over a wide range of timescales \cite{CadartVenkovaRechoEtAl2019_NaturePhys,AlbertsMolecularBiology,YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP,SaadounPapadopoulosWatanabeEtAl2005_JCS,Verkman2008_JMM,BerthaudEtAl2016_SM,Keren2011_EurBJ,TaloniKardashSalmanEtAl2015_PRL}.
+\dropcap{W}ater exchange is essential for a living cell to adapt to its
+environment over a wide range of
+timescales~\cite{CadartVenkovaRechoEtAl2019_NaturePhys,
+AlbertsMolecularBiology, YangMaVerkman2001_JBC,
+SugieIntaglietta2018_AmJPhysiolHCP,
+SaadounPapadopoulosWatanabeEtAl2005_JCS, Verkman2008_JMM,
+BerthaudEtAl2016_SM, Keren2011_EurBJ, TaloniKardashSalmanEtAl2015_PRL}.  
 %
 %Water permeation across the cell membrane due to an osmotic shock has been well studied \cite{AlbertsMolecularBiology}. 
-Recent findings confim that both osmotic and mechanical stresses contribute to significant water permeation for cells to migrate under strong confinement \cite{JiangSun2013_BJ,StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}, leading to a dynamic surface-to-volume ratio of a migrating cell.
-While stress-induced release of messengers in cells has been well studied \cite{Wan2008_PNAS, ForsythWan2011_PNAS,Russell-PuleriPazAdams2016_AJHCP,ZhangShenHoganBarakatMisbah2018_BJ,GordonShimmelFrye2020_FP},
-%osmotic effects on cellular dynamics have been well studied \cite{AlbertsMolecularBiology}, 
-mechanically induced water permeation is often associated with membrane poration or rupture under extreme stresses \cite{HarmanBertrandJoos2017_CJP,RazizadehNikfarPaulLiu2020_BJ}.
-In this work we use modeling and direct numerical simulations to show that,
-over the appropriate time scales or under strong confinement,
-the intrinsic membrane permeability to water can give rise to significantly distinct hydrodynamics of a semipermeable vesicle without poration or rupture in the lipid bilayer membrane. 
+Recent findings confirm that both osmotic and mechanical stresses
+contribute to significant water permeation for cells to migrate under
+strong confinement~\cite{JiangSun2013_BJ, StrokaJiangChenEtAl2014_Cell,
+LiMoriSun2015_PRL, yao-mor2017}, leading to a dynamic surface-to-volume
+ratio of a migrating cell. While stress-induced release of messengers in
+cells has been well studied~\cite{Wan2008_PNAS, ForsythWan2011_PNAS, 
+Russell-PuleriPazAdams2016_AJHCP, ZhangShenHoganBarakatMisbah2018_BJ,
+GordonShimmelFrye2020_FP},
+%osmotic effects on cellular dynamics have been well studied
+%\cite{AlbertsMolecularBiology}, 
+mechanically induced water permeation is often associated with membrane
+poration or rupture under extreme
+stresses~\cite{HarmanBertrandJoos2017_CJP,
+RazizadehNikfarPaulLiu2020_BJ}. In this work we use modeling and direct
+numerical simulations to show that, over the appropriate time scales or
+under strong confinement, the intrinsic membrane permeability to water
+can give rise to significantly distinct hydrodynamics of a semipermeable
+vesicle without poration or rupture in the lipid bilayer membrane. 
 %
@@
 %
-%To elucidate the effects of mechanically induced water permeation (which is a great challenge to quantify in experiments), in this work we use accurate numerical simulations to study the hydrodynamics of a semi-permeable vesicle in various configurations.
+%To elucidate the effects of mechanically induced water permeation (which is a great challenge to quantify in experiments), in this work we use accurate numerical simulations to study the hydrodynamics of a semipermeable vesicle in various configurations.
 
@@
 
-The lipid bilayer membrane is permeable to water and water-soluble molecules \cite{Dick1964_JTB,FettiplaceHaydon1980_PhysRev,DeamerBramhall1986_ChemPhysLipids,Grafmueller2019_ABLS}. 
+The lipid bilayer membrane is permeable to water and water-soluble
+molecules~\cite{Dick1964_JTB, FettiplaceHaydon1980_PhysRev,
+DeamerBramhall1986_ChemPhysLipids, Grafmueller2019_ABLS}. 
 %
@@
 %
-Without aquaporins or other membrane channels that promotes water permeability, the intrinsic water permeability is known to depend on the temperature \cite{OlbrichRawiczNeedhamEtAl2000_BJ}, lipid composition \cite{OlbrichRawiczNeedhamEtAl2000_BJ}, and the hydration of the membrane \cite{MarrinkBerendsen1994_JPhysChem}.
-In the red blood cell membrane, aquaporin-1 channels give rise to a much higher water permeability of $\sim 1.8\times 10^{-2}$ cm/s in erythrocytes \cite{YangMaVerkman2001_JBC} while the intrinsic water permeability of a lipid bilayer membrane is in the range of $10^{-4}-10^{-3}$ cm/s \cite{ThompsonHuang1966_ANYAS,FettiplaceHaydon1980_PhysRev,Grafmueller2019_ABLS,Dimova2020_GVB,BhatiaRobinsonDimova2020_SoftMatt}.
-%
-%The swelling/shrinking of a cell is inevitably coupled to changes in membrane tension and deformation.
-Under a strong confinement (such as going through a microcapillary or submicron slit),  the transmembrane water flow may have comparable contributions from both osmotic and mechanical stresses \cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}.
-Molecular dynamic (MD) 
-%and coarse-grained (CG) MD 
-simulations show that a stretched RBC membrane porates when the membrane tension reaches the order of $2-4$ mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references therein), giving rise to enhanced membrane permeability to both water and macromolecules.
-Consequently, as long as the lipid bilayer membrane remains intact (no poration or rupture), RBCs and vesicles are assumed to be of the same volume throughout experiments of durations no longer than tens of minutes.
-%
-%membrane poration is inevitable when membrane tension is of the order of $2-4$ mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references therein). 
+Without aquaporins or other membrane channels that promote water
+permeability, the intrinsic water permeability is known to depend on the
+temperature~\cite{OlbrichRawiczNeedhamEtAl2000_BJ}, lipid
+composition~\cite{OlbrichRawiczNeedhamEtAl2000_BJ}, \todo[inline]{Same
+reference twice?} and the hydration of
+the membrane~\cite{MarrinkBerendsen1994_JPhysChem}. In the red blood
+cell membrane, aquaporin-1 channels give rise to a much higher water
+permeability of approximately $1.8\times 10^{-2}$ cm/s in
+erythrocytes~\cite{YangMaVerkman2001_JBC} while the intrinsic water
+permeability of a lipid bilayer membrane is in the range of
+$10^{-4}$--$10^{-3}$ cm/s~\cite{ThompsonHuang1966_ANYAS,
+FettiplaceHaydon1980_PhysRev, Grafmueller2019_ABLS, Dimova2020_GVB,
+BhatiaRobinsonDimova2020_SoftMatt}. 
+%
+%The swelling/shrinking of a cell is inevitably coupled to changes in
+%membrane tension and deformation. Under a strong confinement (such as
+%going through a microcapillary or submicron slit),  the transmembrane
+%water flow may have comparable contributions from both osmotic and
+%mechanical stresses
+%\cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}.  
+Molecular dynamic (MD) simulations show that a stretched red blood cell
+(RBC) membrane porates when the membrane tension reaches the order of
+$2$--$4$ mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references
+therein), giving rise to enhanced membrane permeability to both water
+and macromolecules.  Consequently, as long as the lipid bilayer membrane
+remains intact (no poration or rupture), RBCs and vesicles are assumed
+to be of the same volume throughout experiments of durations no longer
+than tens of minutes.
+%
+%membrane poration is inevitable when membrane tension is of the order
+%of $2-4$ mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references
+%therein). 
 %%The CGMD results further show that a stretched RBC membrane may have pores that might contribute to transmembrane transport of both water and ATP molecules \cite{RazizadehNikfarPaulLiu2020_BJ}. 
-%Thus an important outstanding question in stress-induced ATP release of highly deformed RBCs is if there is any transmembrane flow when RBCs release ATP as they experience large
-%mechanical load due to confinement or large shear stress?  To address such question, the first step we take is to focus on the permeable water flux induced by mechanical stress.
+%Thus an important outstanding question in stress-induced ATP release of
+%highly deformed RBCs is if there is any transmembrane flow when RBCs
+%release ATP as they experience large mechanical load due to confinement
+%or large shear stress?  To address such question, the first step we
+%take is to focus on the permeable water flux induced by mechanical
+%stress.
 %%
@@
 %%
-%%Why is it interesting to study the dynamics of a semi-permeable membrane induced by mechanical stress/confinement?
+%%Why is it interesting to study the dynamics of a semipermeable membrane induced by mechanical stress/confinement?
 %%
@@
 %%The response of a cell to an osmotic gradient is inevitably both mechanical (tension redistribution and shape change) and chemical (water flux across the membrane).  
-Under what condition is this a good assumption? Do vesicles conserve volume over hours under flow? What is the dynamic consequence when water influx/efflux affects the membrane hydrodynamics?
-To answer these questions, we investigate the balance between hydrodynamics, tension and elasticity of a semipermeable membrane under various flowing conditions and confinement. 
-%Specifically our numerical simulations yield the quantification of the time scale and length scale over which water permeation becomes important.
-
-% In this work we use numerical simulations to examine the hydrodynamics of a semipermeable vesicle in two dimensions. 
-In microfluidic experiments, it is challenging to keep a freely suspended RBC or vesicle in a steady flow for more than a few hours.
-It is also difficult to quantify the vesicle area/volume ratio accurately.
-Using numerical simulations we can quantify  the effects of water permeability on the hydrodynamics of a vesicle under mechanical stresses.
-Vesicles (self-enclosed lipid bilayer membranes) have been used as a model system to study reshaping, remodeling and scission of cell membranes due to osmotic stress \cite{OgleckaEtAl2014_eLife,CamposSaric2020_bioRxiv,Dimova2020_GVB,BhatiaChrist2020_SoftMatt}.
-Under an osmotic shock, a vesicle may undergo oscillatory variation in its enclosed volume \cite{ChabanonHoLiedberg2017_BJ}.
-When trapped in a microfluidic channel, an osmotic shock induces
- vesicle shape changes, tank-treading and tumbling motions \cite{BhatiaRobinsonDimova2020_SoftMatt,BhatiaChrist2020_SoftMatt}, an illustration that the permeable water flow is inevitably coupled with the mechanical pressure jump across the membrane\cite{yao-mor2017}, which could become comparable to osmotic stress when the membrane deformation is large \cite{LiMoriSun2015_PRL,yao-mor2017}.
-In the absence of an osmotic gradient, we first show that a freely suspended semipermeable vesicle behaves differently from an impermeable vesicle over a long time.
-Next we show that, at normal physiological conditions, the permeable water flow can be amplified by extreme confinement and results in observable change in both vesicle hydrodynamics and reduced area.
-These results will shed light on the dynamic aging process of living cells that constantly go through flows and constrictions over a period of days.
-
-%
-%\paragraph{Literature to maybe cite}
-%\cite{ali-ovr-ran2020} show how beading can occur on nanotubes. This
-%happens in regions where proteins congregate and this can lead to
-%semi-permeability?
+Under what condition is this a good assumption? Do vesicles conserve
+volume over hours under flow? What is the dynamic consequence when water
+influx/efflux affects the membrane hydrodynamics? To answer these
+questions, we investigate the balance between hydrodynamics, tension,
+and elasticity of a semipermeable membrane under various flowing
+conditions and confinement. 
+%Specifically our numerical simulations yield the quantification of the
+%time scale and length scale over which water permeation becomes
+%important.
+
+% In this work we use numerical simulations to examine the hydrodynamics
+% of a semipermeable vesicle in two dimensions. 
+In microfluidic experiments, it is challenging to keep a freely
+suspended RBC or vesicle in a steady flow for more than a few hours. It
+is also difficult to quantify the vesicle area/volume ratio accurately.
+Using numerical simulations we can quantify the effects of water
+permeability on the hydrodynamics of a vesicle under mechanical
+stresses. Vesicles (self-enclosed lipid bilayer membranes) have been
+used as a model system to study reshaping, remodeling, and scission of
+cell membranes due to osmotic stress~\cite{OgleckaEtAl2014_eLife,
+CamposSaric2020_bioRxiv, Dimova2020_GVB, BhatiaChrist2020_SoftMatt}.
+Under an osmotic shock, a vesicle may undergo oscillatory variation in
+its enclosed volume~\cite{ChabanonHoLiedberg2017_BJ}. When trapped in a
+microfluidic channel, an osmotic shock induces vesicle shape changes,
+tank-treading and tumbling
+motions~\cite{BhatiaRobinsonDimova2020_SoftMatt,
+BhatiaChrist2020_SoftMatt}, an illustration that the permeable water
+flow is inevitably coupled with the mechanical pressure jump across the
+membrane~\cite{yao-mor2017}, which could become comparable to osmotic
+stress when the membrane deformation is large~\cite{LiMoriSun2015_PRL,
+yao-mor2017}. In the absence of an osmotic gradient, we first show that
+a freely suspended semipermeable vesicle behaves differently from an
+impermeable vesicle over a long time. Next we show that, at normal
+physiological conditions, the permeable water flow can be amplified by
+extreme confinement and results in observable change in both vesicle
+hydrodynamics and reduced area. These results will shed light on the
+dynamic aging process of living cells that constantly go through flows
+and constrictions over a period of days.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   semipermeability on vesicle hydrodynamics in various configurations.
-  The slipper in (a) is the steady-state shape of a semi-permeable
+  The slipper in (a) is the steady-state shape of a semipermeable
   vesicle in a Poiseuille flow.}
@@
 \section*{Formulation}
-We consider a two-dimensional semi-permeable vesicle (permeable only to water) suspended in a viscous fluid, see Figure~\ref{fig:sketch}.
-To focus on the effect of water flow on vesicle hydrodynamics in various conditions, we assume the fluid is the same inside and outside the vesicle membrane.
-%($\gamma$) with an outward normal $\nn$.
-On the membrane the permeable water flux gives rise to a difference between the fluid velocity ${\bf u}({\bf x}\in \gamma)$
-and the membrane velocity $\dot{\bf x}$ \cite{yao-mor2017}:
+We consider a two-dimensional semipermeable vesicle (permeable only to
+water) suspended in a viscous fluid (Figure~\ref{fig:sketch}). To focus
+on the effect of water flow on vesicle hydrodynamics in various
+conditions, we assume the fluid is the same inside and outside the
+vesicle membrane. On the membrane the permeable water flux gives rise to
+a difference between the fluid velocity ${\uu}({\xx}\in \gamma)$ and the
+membrane velocity $\dot{\xx}$~\cite{yao-mor2017}:
 \begin{align}
-  \label{eqn:vesicleFlux}
   \uu - \dot{\xx} = - k_w (R T \triangle c + \ff_\mathrm{mem} \cdot \nn) \nn, \qquad
@@
 \end{align}
-where $\gamma$ denotes the membrane boundary with an outward normal $\nn$ (Figure~\ref{fig:sketch}), $k_w$ is the water permeability, $R$ is the ideal gas constant, $T$ is the temperature ($^{\circ}$K), $\triangle c$ is contrast in a solute concentration (mol/volume),
-and $\ff_\mathrm{mem}$ is the membrane stress that consists of both bending $ \ff_\mathrm{ben}= -k_b \xx_{ssss}$ and tension $\ff_\mathrm{ten}=(\sigma \xx_s)_s$ ($s$
-is the arclength along the membrane, see Supplementary Material).
-Using $k_w\sim 10^{-12}$ m$^2$s/kg (typical of mammalian cell membranes \cite{LiMoriSun2015_PRL}) and an osmolarity $\triangle c = 0.1$ mol/L (consistent with the osmotic forces in vesicle aspiration experiments \cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the corresponding water flow is of the order $v_\mathrm{o}=0.1 \mu$m/s.
-Assuming that the membrane bending stiffness $k_b = 10^{-19}$J, a membrane tension $10^{-3}$N/m (one tenth of the lysis tension) and a characteristic length scale of $10^{-6}$m, the tension contribution ($v_\mathrm{t}$) and elastic stress contribution
-($v_\mathrm{e}$) to the permeable water flow can be scaled to $v_\mathrm{o}$ as $v_\mathrm{o}:v_\mathrm{t}:v_\mathrm{e}=1:10^{-2}:10^{-6}$.
-Furthermore, we note that in the absence of an osmotic stress, the water permeable flow can be significant when the membrane tension is large due to the external stress such as the hydrodynamics stress due to an external flow and/or due to confinement.
-In the following we will explore both.
+where $\gamma$ denotes the membrane boundary with an outward normal
+$\nn$ (Figure~\ref{fig:sketch}), $k_w$ is the water permeability, $R$ is
+the ideal gas constant, $T$ is the temperature ($^{\circ}$K), $\triangle
+c$ is contrast in a solute concentration (mol/volume), and
+$\ff_\mathrm{mem}$ is the membrane stress that consists of both bending
+$ \ff_\mathrm{ben}= -k_b \xx_{ssss}$ and tension
+$\ff_\mathrm{ten}=(\sigma \xx_s)_s$ ($s$ is the arclength along the
+membrane, see Supplementary Material). Using $k_w\sim 10^{-12}$
+m$^2$s/kg (typical of mammalian cell membranes~\cite{LiMoriSun2015_PRL})
+and an osmolarity $\triangle c = 0.1$ mol/L (consistent with the osmotic
+forces in vesicle aspiration
+experiments~\cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the corresponding
+water flow is of the order $v_\mathrm{o}=0.1 \mu$m/s. Assuming that the
+membrane bending stiffness $k_b = 10^{-19}$J, a membrane tension
+$10^{-3}$N/m (one tenth of the lysis tension) and a characteristic
+length scale of $10^{-6}$m, the tension contribution ($v_\mathrm{t}$)
+and elastic stress contribution ($v_\mathrm{e}$) to the permeable water
+flow can be scaled to $v_\mathrm{o}$ as
+$v_\mathrm{o}:v_\mathrm{t}:v_\mathrm{e}=10^{0}:10^{-2}:10^{-6}$.
+Furthermore, we note that in the absence of an osmotic stress, the water
+permeable flow can be significant when the membrane tension is large due
+to the external stress such as the hydrodynamics stress due to an
+external flow, confinement, or both. In the following we will explore
+both.
 
@@
 \section*{Effects of membrane water permeability}
-We consider a single semi-permeable vesicle in familiar configurations to highlight the effects of membrane water permeability.
-In free space we put a semi-permeable vesicle in a quiescent flow, a planar shear flow and a Poiseuille flow.
-We also consider a semi-permeable vesicle in confinement: a long channel and a contracting channel.
-For each example, we fix the vesicle length and examine the enclosed area as a dynamical consequence of water flow, vesicle shape deformation and membrane tension distribution.
-
-In experiments vesicle under shear flows are measured for a minute (chapter 19 in \cite{Dimova2020_GVB}), a duration over which vesicle can be assumed impermeable \cite{AbkarianViallat2005_BJ}.
-Our simulations of a semi-permeable vesicle
-in these flows show that water permeability may lead to different vesicle hydrodynamics over a time scale of 10 to 100 minutes. 
-%{\bf YNY: is this correct? The shear flow results seem to suggest that the permeability may lead to change in area in less than a second???}
-For vesicles in a narrow micro-fluidic channel, the typical time scale is of $ms$ \cite{abk-fai-sto2006}.
-Our simulations show that strong confinement can lead to amplification of water permeability at such short time scale.
+We consider a single semipermeable vesicle in familiar configurations to
+highlight the effects of membrane water permeability. In free space we
+place a semipermeable vesicle in a quiescent flow, a planar shear flow,
+and a Poiseuille flow. We also consider a semipermeable vesicle in
+confinement: a long channel and a contracting channel. For each example,
+we fix the vesicle length and examine the enclosed area as a dynamical
+consequence of water flow, vesicle shape deformation, and membrane
+tension distribution.
+
+In experiments, vesicles under shear flows are measured for a minute
+(chapter 19 in~\cite{Dimova2020_GVB}), a duration over which vesicle can
+be assumed impermeable~\cite{AbkarianViallat2005_BJ}. Our simulations of
+a semipermeable vesicle in these flows show that water permeability may
+lead to different vesicle hydrodynamics over a time scale of 10 to 100
+minutes. 
+%{\bf YNY: is this correct? The shear flow results seem to suggest that
+%the permeability may lead to change in area in less than a second???}
+For vesicles in a narrow microfluidic channel, the typical time scale is
+milliseconds~\cite{abk-fai-sto2006}. Our simulations show that strong
+confinement can lead to amplification of water permeability at such
+short time scale.
 %
 %all vesicles have a length
-%$L$, but the area is not conserved because of semi-permeability. We vary
+%$L$, but the area is not conserved because of semipermeability. We vary
 %the initial vesicle reduced area, the permeability rate, and the flow
@@
   \caption{\label{fig:relaxationComposite} (a): Snapshots of four
-  semi-permeable vesicles with $\beta = 10^{-3}$ submerged in a
-  quiescent flow. The fluid flux along the red regions is into the
-  vesicle, and the fluid flux along the blue regions is out of the
-  vesicle. In all cases, the vesicle reaches a steady state circular
-  shape. (b): The reduced area of each of the simulations. The
+  semipermeable vesicles with $\beta = 10^{-3}$ submerged in a quiescent
+  flow. The red regions correspond to influx and the blue regions
+  correspond to efflux. In all cases, the vesicle reaches a steady state
+  circular shape. (b): The reduced area of each of the simulations. The
   particular snapshots in (a) occur at the marks along the curve.}
 \end{figure*}
-In a quiescent flow, a semipermeable vesicle in free space can be quantified in terms of its area dynamics and its transition to the equilibrium shape:
-Our analysis in Supplementary Material shows that a semi-permeable vesicle
-relaxes to a circle at a rate that is proportional to $\beta$, and the
-steady state tension is $\Lambda = 2\pi^2/L^2$. Our analysis further shows that the time for a semipermeable
-vesicle to deviate from its initial reduced area and to reach its steady
-state is proportional to $\beta^{-1}$. For this reason, our numerical
-results below are reported in terms of the scaled time $\beta t$.
-
-%This is verified for a
-%vesicle with initial reduced area $\nu = 0.65$ and with different
-%semi-permeability rates. In Table~\ref{tbl:ellipseRelaxTimes} we report
-%the required time, $t_\mathrm{steady}$, for the vesicle's reduced area
-%to be within 1.3\% of its steady state reduced area, and the required
-%time, $t_\mathrm{inflate}$, for the vesicle's reduced area to exceed
-%1.3\% of its initial reduced area. Both times are proportional to
-%$\beta^{-1}$, and for this reason, our numerical results are reported in
-%terms of the scaled time $\beta t$.
-%\begin{table}[htp]
-%  \centering
-%  \caption{\label{tbl:ellipseRelaxTimes} The time for a semi-permeable
-%  vesicle to its steady state ($t_\mathrm{steady}$) and to begin
-%  inflating ($t_\mathrm{inflate}$).}
-%  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
-%    $\beta$ & $t_\mathrm{steady}$  & ratio 
-%            & $t_\mathrm{inflate}$ & ratio \\
-%    \midrule
-%    $10^{0}$  & $6.45 \times 10^{0}$ & ---  
-%              & $2.17 \times 10^{-2}$ & --- \\ 
-%    $10^{-1}$ & $2.00 \times 10^{1}$ & 3.10 & 
-%                $1.25 \times 10^{-1}$ & 5.76 \\
-%    $10^{-2}$ & $9.61 \times 10^{1}$ & 4.81 & 
-%                $1.59 \times 10^{0}$ & 12.72 \\
-%    $10^{-3}$ & $8.36 \times 10^{2}$ & 8.71 & 
-%                $2.19 \times 10^{1}$ & 13.77 \\
-%    $10^{-4}$ & $8.15 \times 10^{3}$ & 9.74 & 
-%                $2.14 \times 10^{2}$ & 9.77 \\
-%    $10^{-5}$ & $8.03 \times 10^{4}$ & 9.85 & 
-%                $2.20 \times 10^{3}$ & 10.14 \\
-%    \bottomrule
-%  \end{tabular}
-%\end{table}
+In a quiescent flow, a semipermeable vesicle in free space can be
+quantified in terms of its area dynamics and its transition to the
+equilibrium shape. Our analysis in Supplementary Material shows that a
+semipermeable vesicle relaxes to a circle at a rate that is proportional
+to $\beta$, and the steady state tension is $\Lambda = 2\pi^2/L^2$. Our
+analysis further shows that the time for a semipermeable vesicle to
+deviate from its initial reduced area and to reach its steady state is
+proportional to $\beta^{-1}$. For this reason, our numerical results
+below are reported in terms of the scaled time $\beta t$.
 
 In Figure~\ref{fig:relaxationComposite}, we examine the relaxation
-dynamics of a semipermeable vesicle with four initial shapes and reduced areas as labeled.
+dynamics of a semipermeable vesicle with four initial shapes and reduced
+areas as labeled.
 %$\beta = 10^{-3}$ and a variety of initial configurations. 
@@
 %
-First we observe that the initial vesicle shape determines the direction of water flux.
-For the vesicle with an initial reduced area ($\alpha(0)=0.12$ in the bottom row) the vesicle deflates (blue regions) first due to the high interior capillary pressure that corresponds to the high membrane curvatures.
-For the other three cases efflux is found at some locations of high curvature, while mostly water permeates into the vesicle and significant change in the reduced area is found at $t\sim 10$ minutes.
-Over time (about ten hours) all vesicles inflate and as expected, each vesicle eventually
-reaches a circular shape with reduced area $\alpha=1$. 
+First we observe that the initial vesicle shape determines the direction
+of water flux. For the vesicle with an initial reduced area
+($\alpha(0)=0.12$ in the bottom row) the vesicle deflates (blue regions)
+first due to the high interior capillary pressure that corresponds to
+the high membrane curvatures. For the other three cases efflux is found
+at some locations of high curvature, while mostly water permeates into
+the vesicle and significant change in the reduced area is found at
+$t\sim 10$ minutes. Over time (about ten hours) all vesicles inflate and
+as expected, each vesicle eventually reaches a circular shape with
+reduced area $\alpha=1$. 
 %%These regions are denoted in blue and are only present at early times. 
@@
 
-Between $t=10$ seconds and $t=10$ minutes, the 
-intermediate shapes of semi-permeable
-vesicles resemble the shape of an impermeable vesicle. This can be
-explained by considering the two terms that contribute to the vesicle
-velocity: (i) the permeability velocity, $\beta(\ff \cdot \nn) \nn$, and
-(ii) the force balance velocity, $\SS[\ff]$. Since $\beta = 10^{-6}$,
-the permeability velocity is much smaller than the force balance
-velocity at early times, and the semi-permeable vesicle dynamics
+Between $t=10$ seconds and $t=10$ minutes, the intermediate shapes of
+semipermeable vesicles resemble the shape of an impermeable vesicle.
+This can be explained by considering the two terms that contribute to
+the vesicle velocity: (i) the permeability velocity, $\beta(\ff \cdot
+\nn) \nn$, and (ii) the force balance velocity, $\SS[\ff]$. Since $\beta
+= 10^{-6}$, the permeability velocity is much smaller than the force
+balance velocity at early times, and the semipermeable vesicle dynamics
 resembles those of an impermeable vesicle. As the force balance velocity
@@
 to inflate to a circle with no vanishing force and velocity. 
-%{\bf YNY:We should put a tick on the time when this transition occurs for each of the vesicles}
+\todo[inline]{There might be some confusion regarding the value of
+$\beta$. The caption says one value and the text says another.}
 
@@
   \fi
-  \caption{\label{fig:shearComposite} (a) The reduced area of a
-  semi-permeable vesicle with $\beta = 10^{-3}$ initialized with four
+  \caption{\label{fig:shearComposite} (a): The reduced area of a
+  semipermeable vesicle with $\beta = 10^{-3}$ initialized with four
   different reduced areas in a shear flow with two different flow rates.
-  (b) The steady state shape of a semi-permeable vesicle with varying
-  flow rates and semi-permeability rates. The circled vesicles
-  correspond to the simulations in part (a). 
-  %{\bf YNY: should this be two-column wide?}
-  }
+  (b): The steady state shape of a semipermeable vesicle with varying
+  flow rates and semipermeability rates. The circled vesicles correspond
+  to the simulations in part (a).}
 \end{figure}
 
-We consider a semi-permeable vesicle in a planar shear flow
-$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$ with different permeability  $\beta$ and shear rates $\dot{\gamma}$. 
-When $\beta=0$ (impermeable case), a vesicle's reduced area
-and viscosity contrast determine whether it tank treads or
-tumbles~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. 
-Focusing on semi-permeable vesicles with no viscosity contrast, 
-we find that a semi-permeable vesicle tilts to an
-inclination angle and undergoes tank treading dynamics, similar to the case of  an impermeable vesicle.
+We consider a semipermeable vesicle in a planar shear flow
+$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$ with different permeability
+$\beta$ and shear rates $\dot{\gamma}$. When $\beta=0$ (impermeable
+case), a vesicle's reduced area and viscosity contrast determine whether
+it tank treads or tumbles~\cite{fin-lam-sei-gom2008,
+kra-win-sei-lip1996}. Focusing on semipermeable vesicles with no
+viscosity contrast, we find that a semipermeable vesicle tilts to an
+inclination angle and undergoes tank treading dynamics, similar to the
+case of an impermeable vesicle.
 
 In Figure~\ref{fig:shearComposite}(a), using four initial reduced areas
-and two flow rates, we plot the reduced area of a semi-permeable vesicle
+and two flow rates, we plot the reduced area of a semipermeable vesicle
 with $\beta = 10^{-3}$. As observed in a quiescent flow, the final
 vesicle shape is independent of the initial reduced area. However, it
-does depend on the flow rate.  We also observe that the reduced area remains constant until $t\sim 10$ minutes, when
-the vesicle starts to tank-tread and the normal component of the force-balance velocity becomes significantly smaller than the permeable velocity, leading to a changing reduced area.
-
-For a variety of semi-permeability rates and flow rates, a semipermeable
+does depend on the flow rate. We also observe that the reduced area
+remains constant until $t\sim 10$ minutes, when the vesicle starts to
+tank-tread and the normal component of the force-balance velocity
+becomes significantly smaller than the permeable velocity, leading to a
+changing reduced area.
+
+For a variety of semipermeability rates and flow rates, a semipermeable
 vesicle reaches a steady equilibrium as in
-Figure~\ref{fig:shearComposite}(a).  Since the final shape is
-independent of the initial reduced area,  we initialize the vesicle with
-reduced area $\alpha = 0.65$ for all simulations in
+Figure~\ref{fig:shearComposite}(a). Since the final shape is independent
+of the initial reduced area, we initialize the vesicle with reduced area
+$\alpha = 0.65$ for all simulations in
 Figure~\ref{fig:shearComposite}(b), where we summarize the steady state
 vesicle shape and its reduced area. We see that the flow rate
-significantly affects the final vesicle shape, but the semi-permeability
+significantly affects the final vesicle shape, but the semipermeability
 rate has a minor effect. Instead, as we saw in the quiescent analysis,
@@
   \fi
-  \caption{\label{fig:parabolicComposite} (a) The steady state shape of
-  a semi-permeable vesicle submerged in a Poiseuille flow with varying
-  initial reduced areas and flow rates. The fluid flux along the red
-  regions is into the vesicle, and the fluid flux along the blue regions
-  is out of the vesicle.  (b) The steady state inclination angle for
-  four different flow velocities. The steady state shapes are
-  superimposed. (c) The reduced area of the slipper formed with the flow
-  rate of 800 $\mu m/s$. (d) The vesicle shape shown with the background
-  imposed flow. The channel width is 12.5 times larger than the vesicle
-  radius. The corresponding reduced area of each vesicle is indicated by
-  the marks in plot (c).}
+  \caption{\label{fig:parabolicComposite} (a): The steady state shape of
+  a semipermeable vesicle submerged in a Poiseuille flow with varying
+  initial reduced areas and flow rates. The red regions correspond to
+  influx and the blue regions correspond to efflux. (b): The steady
+  state inclination angle for four different flow velocities. The steady
+  state shapes are superimposed. (c): The reduced area of the slipper
+  formed with the flow rate of 800 $\mu m/s$. (d): The vesicle shape
+  shown with the background imposed flow. The channel width is 12.5
+  times larger than the vesicle radius. The corresponding reduced area
+  of each vesicle is indicated by the marks in plot (c).}
 \end{figure*}
 
-We consider a semi-permeable vesicle in the Poiseuille flow $\uu =
-U(1-(y/W)^2,0)$, where $U$ is the maximum velocity at $y=0$. The non-linear effects of the Poiseuille flow
-on the migration of an impermeable vesicle have been well-studied \cite{kao-bir-mis2009}: At a given value of the maximum velocity $U$,
-there exists a critical reduced volume above which the equilibrium vesicle shape is symmetric (parachute or bullet shapes) and the vesicle stays at $y=0$.
-Below this critical reduced volume the equilibrium vesicle moves off the
-center and is asymmetric (tank-treading slipper shape).  We validated
-our numerical codes by comparing against results in Kaoui {\em et
+We consider a semipermeable vesicle in the Poiseuille flow $\uu =
+U(1-(y/W)^2,0)$, where $U$ is the maximum velocity at $y=0$. The
+non-linear effects of the Poiseuille flow on the migration of an
+impermeable vesicle have been well-studied~\cite{kao-bir-mis2009}: At a
+given value of the maximum velocity $U$, there exists a critical reduced
+volume above which the equilibrium vesicle shape is symmetric (parachute
+or bullet shapes) and the vesicle stays at $y=0$. Below this critical
+reduced volume the equilibrium vesicle moves off the center and is
+asymmetric (tank-treading slipper shape). We validated our numerical
+codes by comparing against results in Kaoui {\em et
 al.}~\cite{kao-bir-mis2009}, see Supplementary Material.
@@
 %We examine the effect of the non-linear Poiseuille flow on the migration of
-%semi-permeable vesicle. In this experiment, the vesicle is initialized
+%semipermeable vesicle. In this experiment, the vesicle is initialized
 %above the center line $y=0$, and it migrates towards the center
@@
 %
-%Having validated our method, we investigate the dynamics of a semi-permeable vesicle in a Poiseuille flow. 
+%Having validated our method, we investigate the dynamics of a semipermeable vesicle in a Poiseuille flow. 
 %
@@
 %the effect of the non-linear Poiseuille flow on the migration of
-%semi-permeable vesicle. 
-%
-
-At the beginning of the simulations a semipermeable vesicle is initialized
-above the center line $y=0$, and it migrates towards the center
-line as in the impermeable case~\cite{dan-vla-mis2009}. However, for an impermeable vesicle, depending on
-the initial reduced area and the maximum flow velocity $U$, the equilibrium vesicle shape
-is either an axisymmetric parachute or bullet, or an asymmetric
-tank-treading slipper~\cite{kao-bir-mis2009}. 
+%semipermeable vesicle. 
+%
+
+At the beginning of the simulations a semipermeable vesicle is
+initialized above the center line $y=0$, and it migrates towards the
+center line as in the impermeable case~\cite{dan-vla-mis2009}. 
+%
+%However,
+%for an impermeable vesicle, depending on the initial reduced area and
+%the maximum flow velocity $U$, the equilibrium vesicle shape is either
+%an axisymmetric parachute or bullet, or an asymmetric tank-treading
+%slipper~\cite{kao-bir-mis2009}. 
 %
@@
 %
-Using several initial reduced areas and flow rates, we recreate the impermeable vesicle phase
-diagram for vesicles with a permeability rate of $\beta = 10^{-3}$. The equilibrium vesicle shape for different $U$ and initial reduced area is summarized in
-Figure~\ref{fig:parabolicComposite}(a). An example of a semi-permeable vesicle with $\alpha(0) = 0.9$ and $U=800$ $\mu m/s$ is
-shown in Figure~\ref{fig:parabolicComposite}(c) and (d). 
-%
-
-As observed for the planar shear flow,
-the steady state reduced area is independent of the initial reduced
-area, and larger flow rates result in smaller steady state reduced
-areas. We report the reduced area of the equilibrium vesicle shape in
-Figure~\ref{fig:parabolicComposite}(a). At the smallest flow rate of $U= 200 \mu m/s$, the steady state reduced area is large, and the result
-is an axisymmetric bullet. At the larger flow rates, the steady state
-reduced area is smaller, and the result is an asymmetric tank-treading
-slipper.
-We observe that the membrane permeability to water drastically alters the vesicle shape and position relative to the flow at equilibrium: At $\beta=10^{-3}$ the equilibrium vesicle depends only on the maximum velocity $U$ of the nonlinear shear flow.
-The higher $U$ the smaller the equilibrium reduced area and the further away vesicle is relative to the flow center at $y=0$.
+Using several initial reduced areas and flow rates, we recreate the
+impermeable vesicle phase diagram for vesicles with a permeability rate
+of $\beta = 10^{-3}$. The equilibrium vesicle shape for different $U$
+and initial reduced area is summarized in
+Figure~\ref{fig:parabolicComposite}(a), and the vertical displacement of
+the vesicle's center of mass is in
+Figure~\ref{fig:parabolicComposite}(b). The effect of semipermeability
+of a vesicle with $alpha(0) = 0.9$ and $U=800 \mu$m/s on its reduced
+area and migration pattern are shown in
+Figure~\ref{fig:parabolicComposite}(c) and (d). 
+%
+
+As observed for the planar shear flow, the steady state reduced area is
+independent of the initial reduced area, and larger flow rates result in
+smaller steady state reduced areas. We report the reduced area of the
+equilibrium vesicle shape in Figure~\ref{fig:parabolicComposite}(a). At
+the smallest flow rate of $U= 200 \mu$m/s, the steady state reduced
+area is large, and the result is an axisymmetric bullet. At the larger
+flow rates, the steady state reduced area is smaller, and the result is
+an asymmetric tank-treading slipper. We observe that the membrane
+permeability to water drastically alters the vesicle shape and position
+relative to the flow at equilibrium: At $\beta=10^{-3}$ the equilibrium
+vesicle depends only on the maximum velocity $U$ of the nonlinear shear
+flow. The higher $U$ the smaller the equilibrium reduced area and the
+further away vesicle is relative to the flow center at $y=0$.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Semi-Permeable Vesicle in a Narrow Channel (Stenosis)}
-Cells experience stretching and release messengers when they pass through capillary vessels \cite{Wan2008_PNAS,ForsythWan2011_PNAS,Pak2015_PNAS}.
-Many cells exhibit extraordinary flexibility as they go through narrow channels \cite{AuStoreyMoore2016_PNAS}, and adjustment of area to volume ratio may be a key factor for a successful passage.
-Here we quantify the effect of water permeability on a vesicle going through a stenosis (a long microfluidic channel with a width smaller than the cell radius).
-Based on the findings in 
-%We consider the effect of stenosis on a semi-permeable vesicle. Inspired
-%by an experiment that measures the effects of cells on the dynamical
-%pressure-drop variations along a micrometer-sized
-\cite{abk-fai-sto2006}, we first examine the effect of
-semi-permeability on the pressure fluctuation across a stenosed
-geometry. In this experiment, a pressure drop is used to squeeze a
-red blood cell (RBC) through a constriction with diameter $5\mu$m and
-length $45\mu$m. We set up a similar computational geometry with a
-Poiseuille flow imposed at the inlet and outlet
-(Figure~\ref{fig:stenosisComposite}(a)). The flow velocity $U_{max} = 1000 \mu$m/s is chosen so that
-the residency time of the vesicle  in the stenosis channel $t_R \approx 0.5$ s agrees with the
-experimental results \cite{abk-fai-sto2006}. When the RBC enters the channel, an increase in the pressure drop is required to maintain a constant flow
+\subsection*{Semipermeable Vesicle in a Narrow Channel (Stenosis)}
+Cells experience stretching and release messengers when they pass
+through capillary vessels~\cite{Wan2008_PNAS, ForsythWan2011_PNAS,
+Pak2015_PNAS}.  Many cells exhibit extraordinary flexibility as they go
+through narrow channels~\cite{AuStoreyMoore2016_PNAS}, and adjustment of
+area to volume ratio may be a key factor for a successful passage.  Here
+we quantify the effect of water permeability on a vesicle going through
+a stenosis (a long microfluidic channel with a width smaller than the
+cell radius).  Based on the findings in~\cite{abk-fai-sto2006}, we first
+examine the effect of semipermeability on the pressure fluctuation
+across a stenosed geometry. In this experiment, a pressure drop is used
+to squeeze a red blood cell (RBC) through a constriction with diameter
+$5\mu$m and length $45\mu$m. We set up a similar computational geometry
+with a Poiseuille flow imposed at the inlet and outlet
+(Figure~\ref{fig:stenosisComposite}(a)). The flow velocity $U_{max} =
+1000 \mu$m/s is chosen so that the residency time of the vesicle  in the
+stenosis channel $t_R \approx 0.5$ s agrees with the experimental
+results~\cite{abk-fai-sto2006}. When the RBC enters the channel, an
+increase in the pressure drop is required to maintain a constant flow
 rate, and the difference in the pressure drop is called the excess
@@
 
-We consider both an impermeable and semi-permeable vesicle with initial
+We consider both an impermeable and semipermeable vesicle with initial
 reduced area $\alpha = 0.65$ passing through a long narrow channel and
@@
 results in Figure 3 of~\cite{abk-fai-sto2006}. Our simulations show that
-less excess pressure is needed to drive a semi-permeable vesicle through the closely-fit channel.
+less excess pressure is needed to drive a semipermeable vesicle through the closely-fit channel.
 Once in the channel, the vesicle takes a bullet shape with maximum tension in the front and minimum tension in the back (see Figure~\ref{fig:stenosisComposite}(a)),
-consistent with earlier results \cite{Pak2015_PNAS,HarmanBertrandJoos2017_CJP}.
+consistent with earlier results~\cite{Pak2015_PNAS,HarmanBertrandJoos2017_CJP}.
 
@@
   \fi
-  \caption{\label{fig:stenosisComposite} (a) A semi-permeable vesicle
+  \caption{\label{fig:stenosisComposite} (a): A semipermeable vesicle
   passing through a constricted geometry similar to the experimental
-  device in~\cite{abk-fai-sto2006}. (b) A semi-permeable vesicle passing
-  through a constricted geometry that is over five times longer. (c) The
-  excess pressure of an impermeable and semi-permeable vesicle in the
-  short geometry in (a). (d) The reduced area of the semi-permeable
+  device in~\cite{abk-fai-sto2006}. (b): A semipermeable vesicle passing
+  through a constricted geometry that is over five times longer. (c):
+  The excess pressure of an impermeable and semipermeable vesicle in the
+  short geometry in (a). (d): The reduced area of the semipermeable
   vesicles in the geometries in (a) and (b) as a function of the
@@
   half the length of the constriction. (e) The reduced area of the
-  semi-permeable vesicles in the geometries in (a) and (b) as a function
+  semipermeable vesicles in the geometries in (a) and (b) as a function
   of time. The time axis is scaled by $1/t_R$ where $t_R$ is the
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Semi-Permeable Vesicle in a Contracting Geometry} 
-Squeezing a cell or an elastic vesicle through a slit in microfluidics has gained popularity for its application in stress-induced release of macromolecules
-\cite{ShareiEtAl2013_PNAS,Pak2015_PNAS,ZhangShenHoganBarakatMisbah2018_BJ,LuoBai2019_PoF}.
-RBCs go through submicron slits many times during their lifetime, and such process selects healthy, flexible RBCs to survive \cite{wu2015critical,LuPeng2019_PoF}.
-Here we investigate the role of membrane permeability to water when a semi-permeable vesicle is squeezed through a contracting microfluidic channel similar to~\cite{wu2015critical},
-where the width of the channel gradually decreases from $16 \mu$m to $1.6 \mu$m. The channel then immediately opens
-again to $16 \mu$m (Figure~\ref{fig:contractingComposite}). A
-Poiseuille flow is imposed at the inlet and outlet with a constant maximum flow
-rate of $U_{\max}$. We initialize a semi-permeable vesicle with $\alpha
-= 0.65$ that spans $10 \mu$m of the total channel width and investigate
-the effects of the membrane permeability to water and the maximum flow velocity on whether a vesicle can successfully pass through the slit. 
-We color the vesicle according to the sign of its flux---red for influx and blue for efflux.
+\subsection*{Semipermeable Vesicle in a Contracting Geometry} 
+Squeezing a cell or an elastic vesicle through a slit in microfluidics
+has gained popularity for its application in stress-induced release of
+macromolecules~\cite{ShareiEtAl2013_PNAS,Pak2015_PNAS,ZhangShenHoganBarakatMisbah2018_BJ,LuoBai2019_PoF}.
+RBCs go through submicron slits many times during their lifetime, and
+such process selects healthy, flexible RBCs to
+survive~\cite{wu2015critical,LuPeng2019_PoF}.  Here we investigate the
+role of membrane permeability to water when a semipermeable vesicle is
+squeezed through a contracting microfluidic channel similar
+to~\cite{wu2015critical}, where the width of the channel gradually
+decreases from $16 \mu$m to $1.6 \mu$m. The channel then immediately
+opens again to $16 \mu$m (Figure~\ref{fig:contractingComposite}). A
+Poiseuille flow is imposed at the inlet and outlet with a constant
+maximum flow rate of $U_{\max}$. We initialize a semipermeable vesicle
+with $\alpha = 0.65$ that spans $10 \mu$m of the total channel width and
+investigate the effects of the membrane permeability to water and the
+maximum flow velocity on whether a vesicle can successfully pass through
+the slit.  We color the vesicle according to the sign of its flux---red
+for influx and blue for efflux.
 
@@
 However, if the
-semi-permeability rate is too low, the vesicle is too large when it
+semipermeability rate is too low, the vesicle is too large when it
 reaches the narrowest part of the channel, and it is unable to pass. In
@@
   and the fluid flux along the blue regions is out of the vesicle.
-  (a--c) The ability for a semi-permeable vesicle to pass through the
-  constriction depends on the semi-permeability rate. (d--f) The ability
-  for a semi-permeable vesicle to pass through the constriction depends
-  on the flow rate. (g) A semi-permeable vesicle passing through six
-  periods of the constricting geometry. (h) The reduced area with the
-  marks representing shapes in (g). (i) The vesicle velocity with the
+  (a--c): The ability for a semipermeable vesicle to pass through the
+  constriction depends on the semipermeability rate. (d--f): The ability
+  for a semipermeable vesicle to pass through the constriction depends
+  on the flow rate. (g): A semipermeable vesicle passing through six
+  periods of the constricting geometry. (h): The reduced area with the
+  marks representing shapes in (g). (i): The vesicle velocity with the
   marks representing shapes in (g).}
@@
 In this work we investigated the effects of membrane permeability to water on the vesicle hydrodynamics.
-Without any external flow or confinement, our analysis shows that a semi-permeable vesicle always inflates to maximize the water content inside the vesicle of a fixed length (area) in two (three) dimensions.
-Results from analysis and numerical simulation show that such relaxation of a semi-permeable vesicle is characterized by a rescaled time $\beta t$.
+Without any external flow or confinement, our analysis shows that a semipermeable vesicle always inflates to maximize the water content inside the vesicle of a fixed length (area) in two (three) dimensions.
+Results from analysis and numerical simulation show that such relaxation of a semipermeable vesicle is characterized by a rescaled time $\beta t$.
 We further illustrate that the relaxation process consists of at least two phases: The
@@
 As an impermeable vesicle in a shear flow, a semipermeable vesicle also reaches an equilibrium shape and position.
-Yet for a semi-permeable vesicle the equilibrium shape depends on the strength of the shear flow (shear rate $\dot\gamma$ for the planar shear flow, and $U_{max}$ for the Poiseuille flow).
+Yet for a semipermeable vesicle the equilibrium shape depends on the strength of the shear flow (shear rate $\dot\gamma$ for the planar shear flow, and $U_{max}$ for the Poiseuille flow).
 Our simulations also show that, in a Poiseuille flow, symmetric equilibrium vesicle shape is possible only at low flow velocity.
@@
 Under strong confinement we show that water permeation can be amplified on a timescale of a few seconds as a vesicle is squeezed through a closely fit channel and a contracting 
-channel. As a semi-permeable vesicle goes through a long closely-fit channel, we observe that the vesicle loses water at a constant rate, and the longer the channel the more the loss 
+channel. As a semipermeable vesicle goes through a long closely-fit channel, we observe that the vesicle loses water at a constant rate, and the longer the channel the more the loss 
 of water. In the case of contracting channel, we find that both permeability and the pressure gradient across the slit must be sufficiently large for a successful passage. Throughout 
@@
 \section*{Supplementary Material: Formulation}
-We consider a two-dimensional inextensible semi-permeable vesicle,
+We consider a two-dimensional inextensible semipermeable vesicle,
 $\gamma$, suspended in unconfined and confined geometries $\Omega$. The
@@
 
-Semi-permeability is introduced by modifying the vesicle velocity from
+Semipermeability is introduced by modifying the vesicle velocity from
 the standard no-slip condition $\dot{\xx} = \uu(\xx)$. Instead, we
@@
 length is conserved by the local inextensibility condition, but the area
-is not because of semi-permeability. Therefore, the reduced area is
+is not because of semipermeability. Therefore, the reduced area is
 dynamic.
@@
 method that discretizes high-order derivatives
-semi-implicitly~\cite{vee-gue-zor-bir2009}. We introduce the notation
+semiimplicitly~\cite{vee-gue-zor-bir2009}. We introduce the notation
 \begin{alignat}{3}
@@
 similar notation for the other operators. Then, a first-order
-semi-implicit time stepping method of~\eqref{eqn:vesVelocity} is
+semiimplicit time stepping method of~\eqref{eqn:vesVelocity} is
 \begin{alignat}{3}  
-  \frac{\xx^{N+1} - \xx^N}{\Delta t} &= \uu_\infty(\xx^N) 
+  \frac{\xx^{N+1} - \xx^N}{\triangle t} &= \uu_\infty(\xx^N) 
   &&+ \beta P^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right) \nonumber \\
@@
 al.}~\cite{vee-raj-bir-pur2009} by computing the steady state shape of a
-semi-permeable vesicle in a quiescent flow. The steady state shape is a
+semipermeable vesicle in a quiescent flow. The steady state shape is a
 stationary point of the Lagrangian
@@
 of~\eqref{eqn:curveODE} is not periodic unless $\kappa(s) = \kappa_0$.
-Therefore, the steady state shape of a semi-permeable vesicle in a
+Therefore, the steady state shape of a semipermeable vesicle in a
 quiescent flow is a circle with radius $L/2\pi$ and constant tension
@@
 
+\todo[inline]{Break up figure 6 in half}
+
 \end{document}
@@
 %  \caption{\label{fig:ellipseArea} The area of an elliptical
-%  semi-permeable vesicle, with permeability rate $\beta$ in a quiescent
+%  semipermeable vesicle, with permeability rate $\beta$ in a quiescent
 %  flow. The time axis is scaled by the permeability rate $\beta$. Since
@@
 %\ll 1$, the permeability velocity is much smaller than the force balance
-%velocity at early times, and the semi-permeable vesicle dynamics
+%velocity at early times, and the semipermeable vesicle dynamics
 %resembles those of an impermeable vesicle. As the force balance velocity
@@
 %vesicle velocity. At intermediate time $t=5$, all three velocities are
-%comparable in size, and the semi-permeable vesicle begins to inflate.
+%comparable in size, and the semipermeable vesicle begins to inflate.
 %Finally, at time $t=50$, the impermeable vesicle is near steady state,
-%while the semi-permeable vesicle is still inflating. The right-most
+%while the semipermeable vesicle is still inflating. The right-most
 %plot of Figure~\ref{fig:vesVelocity} is the maximum norm of the
@@
 %  velocity of an impermeable vesicle with the same initial shape as the
-%  semi-permeable vesicle.}
+%  semipermeable vesicle.}
 %\end{figure*}
@@
 %We next investigate the interplay between the tension, transmembrane
-%flux, and curvature of a semi-permeable vesicle. We let $\beta = 1$ and
+%flux, and curvature of a semipermeable vesicle. We let $\beta = 1$ and
 %initialize the vesicle with regions of both positive and negative
@@
 %  \caption{\label{fig:starTensionFlux} The vesicle tension (left) and
-%  flux (right) of the semi-permeable vesicle in a quiescent flow with
+%  flux (right) of the semipermeable vesicle in a quiescent flow with
 %  $\beta=1$.}
@@
 %  \caption{\label{fig:starTensionFlux} The vesicle tension (top) and
-%  flux (bottom) of the semi-permeable vesicle in a quiescent
+%  flux (bottom) of the semipermeable vesicle in a quiescent
 %  flow with $\beta=1$.}
@@
 %%  \includegraphics[width=0.9\linewidth]{figures/shearSS.pdf}
-%  \caption{\label{fig:shearSS} The reduced area of a semi-permeable
+%  \caption{\label{fig:shearSS} The reduced area of a semipermeable
 %  vesicle in a shear flow. The final reduced area is nearly independent
@@
 %  \caption{\label{fig:shearPhaseDiagram} The steady state shape of a
-%  semi-permeable vesicle with several different permeability rates
+%  semipermeable vesicle with several different permeability rates
 %  $\beta$ and shear rates $\dot{\gamma}$. The final reduced areas are
@@
 %  \caption{\label{fig:parabolicOffCenterSemipermeablePhaseDiagram} Phase
-%  diagram of a semi-permeable vesicle, with $\beta = 10^{-3}$, with
+%  diagram of a semipermeable vesicle, with $\beta = 10^{-3}$, with
 %  several different flow rates $U$ and reduced areas $\nu$. The
@@
 %  \caption{\label{fig:stenosisShape} An impermeable (dashed) and
-%  semi-permeable (solid) vesicle in a stenosed geometry (black).
+%  semipermeable (solid) vesicle in a stenosed geometry (black).
 %  The vesicles' initial configuration are identical with reduced area
 %  $\nu = 0.65$. The color denotes the vesicles' tension (left) and flux
-%  (right). The semi-permeable vesicle deflates throughout the
+%  (right). The semipermeable vesicle deflates throughout the
 %  constriction (see Figure~\ref{fig:stenosisArea}) and develops higher
@@
 %  flux (top right), $x$-velocity (bottom left), and $y$-velocity (bottom
-%  right) of the semi-permeable (red) and impermeable (dashed blue)
+%  right) of the semipermeable (red) and impermeable (dashed blue)
 %  vesicles in Figure~\ref{fig:stenosisShape} at location $x=50$. The
@@
 %  \caption{\label{fig:stenosisArea} The area of a stenosed
-%  semi-permeable vesicle, with permeability rate $\beta=10^{-3}$. The
+%  semipermeable vesicle, with permeability rate $\beta=10^{-3}$. The
 %  $x$-axis is the $x$-coordinate of the center of mass of the vesicle.
 %  The vesicle loses fluid at a constant rate throughout the constriction
-%  that is between $\pm 60$. The semi-permeable vesicle loses 12.8\% of
+%  that is between $\pm 60$. The semipermeable vesicle loses 12.8\% of
 %  its fluid.}
@@
 %  \includegraphics[width=\linewidth]{figures/stenosisBL.pdf}
-%  \caption{\label{fig:stenosisBL} A stenosed semi-impermeable (red) and
-%  imperemable (blue) vesicle. The semi-permeable vesicle has 
+%  \caption{\label{fig:stenosisBL} A stenosed semiimpermeable (red) and
+%  imperemable (blue) vesicle. The semipermeable vesicle has 
 %  reduced area 0.17, and both vesicles were initialized with reduce area
@@
 %  (right) velocities of the vesicle in Figure~\ref{fig:stenosisBL}. The
-%  red lines correspond to the semi-permeable vesicle and the blue dashed
+%  red lines correspond to the semipermeable vesicle and the blue dashed
 %  lines correspond to the impermeable vesicle.}
@@
 %
-%We consider the effect of stenosis on a semi-permeable vesicle. To allow
+%We consider the effect of stenosis on a semipermeable vesicle. To allow
 %for large amounts of fluid flux through the membrane, we consider
@@
 %The inextensibility condition guarantees that the vesicle's length, $L$,
-%is conserved, while its area, $A$, can change due to semi-permeability.
+%is conserved, while its area, $A$, can change due to semipermeability.
 %Therefore, the reduced area $\alpha = 4\pi A/L^2 \in (0,1]$ is not
@@
 %Here, we attempt to apply the formulation described by Sohn et
-%al.~\cite{soh-tse-li-voi-low2010} to a semi-permeable vesicle.  In the
-%semi-permeable formulation, the vesicle velocity is
+%al.~\cite{soh-tse-li-voi-low2010} to a semipermeable vesicle.  In the
+%semipermeable formulation, the vesicle velocity is
 %\begin{align}
@@
 %
-%When the semi-permeable vesicle reaches a steady-state shape, we have
+%When the semipermeable vesicle reaches a steady-state shape, we have
 %\begin{align}
@@
 %We start by simulating a star-shaped vesicle in a quiescent flow with
-%semi-permeability rate $\beta=1$ (Figure~\ref{fig:starShape}). To
+%semipermeability rate $\beta=1$ (Figure~\ref{fig:starShape}). To
 %perform this simulation, we use an adaptive second-order time stepping
@@
 %  \end{minipage}
-%%  \caption{\label{fig:starShape} A initially star-shaped semi-permeable
+%%  \caption{\label{fig:starShape} A initially star-shaped semipermeable
 %%  vesicle in a shear quiescent flow with $\beta=1$. Note that the time
@@
 %  \caption{\label{tbl:ellipseRelaxTime} The time, $t_{\mathrm{SS}}$, for
-%  a semi-permeable vesicle to reach steady state.}
+%  a semipermeable vesicle to reach steady state.}
 %\end{table}
@@
 %  \caption{\label{tbl:ellipseBLTime} The time, $t_\mathrm{SP}$, for a
-%  semi-permeable vesicle to begin inflating.}
+%  semipermeable vesicle to begin inflating.}
 %\end{table}
@@
 %    \fi
-%  \caption{\label{fig:starShape} An initially star-shaped semi-permeable
+%  \caption{\label{fig:starShape} An initially star-shaped semipermeable
 %  vesicle in a quiescent flow with $\beta=1$. Note that the time steps
@@
 %  \caption{\label{fig:vesVelocity} The velocity contributions due to
-%  semi-permeability (red) and force balance (blue). The green dashed
+%  semipermeability (red) and force balance (blue). The green dashed
 %  line is the velocity of an impermeable vesicle with the same initial
-%  shape as the semi-permeable vesicle.}
+%  shape as the semipermeable vesicle.}
 %\end{figure}
@@
 %  \caption{\label{fig:vesVelocityNorm} The max norm of the velocity due
-%  to the force balance (blue) and semi-permeability. Also included is
+%  to the force balance (blue) and semipermeability. Also included is
 %  the velocity of an impermeable vesicle (green). The three black lines
@@
 %  \caption{\label{fig:parabolicPhaseDiagram} The steady state shape of a
-%  semi-permeable vesicle with several different permeability rates
+%  semipermeable vesicle with several different permeability rates
 %  $\beta$ and flow rates $U$. The numbers reported above each vesicle is
@@
 %  \caption{\label{tbl:parabolicRelaxTimes1} The time for a
-%  semi-permeable vesicle in a Poiseuille flow to reach its steady state
+%  semipermeable vesicle in a Poiseuille flow to reach its steady state
 %  ($t_\mathrm{steady}$) and to begin inflating ($t_\mathrm{inflate}$).
@@
 %  \caption{\label{fig:stenosisTension} The tension of the impermeable
-%  (red) and semi-permeable (dashed blue) vesicles in
+%  (red) and semipermeable (dashed blue) vesicles in
 %  Figure~\ref{fig:stenosisShape}. The point $\theta=0$ corresponds to
@@
 %  \caption{\label{fig:stenosisFlux} The flux (equivalent to pressure
-%  jump) of the impermeable (red) and semi-permeable (dashed blue)
+%  jump) of the impermeable (red) and semipermeable (dashed blue)
 %  vesicles in Figure~\ref{fig:stenosisShape}. The point $\theta=0$
@@
 %\end{figure}
+%This is verified for a
+%vesicle with initial reduced area $\nu = 0.65$ and with different
+%semipermeability rates. In Table~\ref{tbl:ellipseRelaxTimes} we report
+%the required time, $t_\mathrm{steady}$, for the vesicle's reduced area
+%to be within 1.3\% of its steady state reduced area, and the required
+%time, $t_\mathrm{inflate}$, for the vesicle's reduced area to exceed
+%1.3\% of its initial reduced area. Both times are proportional to
+%$\beta^{-1}$, and for this reason, our numerical results are reported in
+%terms of the scaled time $\beta t$.
+%\begin{table}[htp]
+%  \centering
+%  \caption{\label{tbl:ellipseRelaxTimes} The time for a semipermeable
+%  vesicle to its steady state ($t_\mathrm{steady}$) and to begin
+%  inflating ($t_\mathrm{inflate}$).}
+%  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
+%    $\beta$ & $t_\mathrm{steady}$  & ratio 
+%            & $t_\mathrm{inflate}$ & ratio \\
+%    \midrule
+%    $10^{0}$  & $6.45 \times 10^{0}$ & ---  
+%              & $2.17 \times 10^{-2}$ & --- \\ 
+%    $10^{-1}$ & $2.00 \times 10^{1}$ & 3.10 & 
+%                $1.25 \times 10^{-1}$ & 5.76 \\
+%    $10^{-2}$ & $9.61 \times 10^{1}$ & 4.81 & 
+%                $1.59 \times 10^{0}$ & 12.72 \\
+%    $10^{-3}$ & $8.36 \times 10^{2}$ & 8.71 & 
+%                $2.19 \times 10^{1}$ & 13.77 \\
+%    $10^{-4}$ & $8.15 \times 10^{3}$ & 9.74 & 
+%                $2.14 \times 10^{2}$ & 9.77 \\
+%    $10^{-5}$ & $8.03 \times 10^{4}$ & 9.85 & 
+%                $2.20 \times 10^{3}$ & 10.14 \\
+%    \bottomrule
+%  \end{tabular}
+%\end{table}

### 2020-12-29 vesicle_code/docs/permeableVes/main.tex
yny

@@
 permeability, the intrinsic water permeability is known to depend on the
-temperature~\cite{OlbrichRawiczNeedhamEtAl2000_BJ}, lipid
-composition~\cite{OlbrichRawiczNeedhamEtAl2000_BJ}, \todo[inline]{Same
-reference twice?} and the hydration of
+temperature, lipid composition~\cite{OlbrichRawiczNeedhamEtAl2000_BJ}, 
+%\todo[inline]{Same reference twice?} 
+and the hydration of
 the membrane~\cite{MarrinkBerendsen1994_JPhysChem}. In the red blood
@@
 the vesicle velocity: (i) the permeability velocity, $\beta(\ff \cdot
-\nn) \nn$, and (ii) the force balance velocity, $\SS[\ff]$. Since $\beta
-= 10^{-6}$, the permeability velocity is much smaller than the force
+\nn) \nn$, and (ii) the force balance velocity, $\SS[\ff]$. Since 
+%$\beta = 10^{-6}$, 
+$\beta\ll 1$,
+the permeability velocity is much smaller than the force
 balance velocity at early times, and the semipermeable vesicle dynamics
@@
 to inflate to a circle with no vanishing force and velocity. 
-\todo[inline]{There might be some confusion regarding the value of
-$\beta$. The caption says one value and the text says another.}
+%\todo[inline]{There might be some confusion regarding the value of $\beta$. The caption says one value and the text says another.}
 

### 2020-12-29 vesicle_code/docs/permeableVes/main.tex
working on contracting fig
fixed fig 6 and 7

@@
 
-\begin{figure*}[htp]
+\begin{figure}[htp]
   \centering
@@
   for a semipermeable vesicle to pass through the constriction depends
-  on the flow rate. (g): A semipermeable vesicle passing through six
-  periods of the constricting geometry. (h): The reduced area with the
-  marks representing shapes in (g). (i): The vesicle velocity with the
-  marks representing shapes in (g).}
-\end{figure*}
+  on the flow rate.}
+\end{figure}
 
@@
   \caption{\label{fig:contractingComposite2} Vesicle reduced area and
-  velocity vs.~time.}
+  velocity vs.~time. Permeability rate is $\beta = 10^{-3}$ and maximum
+  velocity is $18\mu$m/s. (a): A semipermeable vesicle passing through
+  six periods of the contracting geometry. (b): The reduced area with
+  the marks representing shapes in (a). (c): The vesicle velocity with
+  the marks representing shapes in (a). In (b) and (c), the bottom
+  x-axis is the $x$-coordinate of the center of mass, and the upper
+  x-axis is time.}
 \end{figure}
@@
 reaches its steady state which confirms that $\dot{A}(t) = 0$.
-
-\todo[inline]{Break up figure 6 in half}
 

### 2020-12-30 vesicle_code/docs/permeableVes/main.tex
yny

@@
 \begin{abstract}
+Lipid bilayer membranes have a native (albeit small) permeability for water molecules. 
+As long as the bilayer structure stays intact without poration or rupture under load, 
+the water influx/efflux  is
+often assumed to be negligible in the absence of a gradient of osmotic stress. 
 In this work we use boundary integral simulations to investigate the
 effects of water permeability on the hydrodynamics of a vesicle under
-various flows and confinement configurations. Using the Helfrich free
-energy extended for the coupling of membrane permeability with the
-membrane elastic stress, tension and mechanical stress, we illustrate
-that, in the absence of an osmotic stress gradient, a typical liposome
-may be significantly affected by membrane permeability over a
-sufficiently long time or under strong confinement. Lipid bilayer
-membranes are permeable to water molecules, and water influx/efflux is
-often assumed to be negligible in the absence of osmolarity, even when
-the membrane undergoes large deformation. Our simulation results
-quantify the conditions for such assumption to be valid, and shed
-light on how confinement can be utilized to estimate membrane
-permeability.
+various flows and confinement configurations. Coupling the membrane permeability with membrane elastic stress, tension and mechanical stress 
+in the framework of Helfrich free energy, we illustrate
+that, in the absence of an osmotic stress gradient, a giant unilamellar vesicle may be significantly affected by water influx/efflux over a
+sufficiently long time or under a strong confinement. 
+Our simulation results quantify the conditions for water permeation to be negligible in terms of the timescales, flow strength of an external flow, and degree of confinement.
+These results shed light on how microfluidic confinement can be utilized to estimate membrane permeability.
 %
@@
 Figure~\ref{fig:parabolicComposite}(b). The effect of semipermeability
-of a vesicle with $alpha(0) = 0.9$ and $U=800 \mu$m/s on its reduced
+of a vesicle with $\alpha(0) = 0.9$ and $U=800 \mu$m/s on its reduced
 area and migration pattern are shown in
@@
 The two phases in the relaxation dynamics are also observed  in the hydrodynamics of a semipermeable vesicle under a shear flow (both the planar and Poiseuille flows) in free space. 
-As an impermeable vesicle in a shear flow, a semipermeable vesicle also reaches an equilibrium shape and position.
+Similar to an impermeable vesicle in a shear flow, a semipermeable vesicle also reaches an equilibrium shape and position.
 Yet for a semipermeable vesicle the equilibrium shape depends on the strength of the shear flow (shear rate $\dot\gamma$ for the planar shear flow, and $U_{max}$ for the Poiseuille flow).

### 2020-12-30 vesicle_code/docs/permeableVes/main.tex
edited up to beginning of supp material

@@
 
-\affil[a]{Department of Scientific Computing, Florida State University, Tallahessee, FL 33306}
+\affil[a]{Department of Scientific Computing, Florida State University, Tallahessee, FL 32306}
 \affil[b]{Department of Mechanical and Aerospace Engineering, Princeton University, Princeton, NJ 08544}
@@
 \begin{abstract}
-Lipid bilayer membranes have a native (albeit small) permeability for water molecules. 
-As long as the bilayer structure stays intact without poration or rupture under load, 
-the water influx/efflux  is
-often assumed to be negligible in the absence of a gradient of osmotic stress. 
-In this work we use boundary integral simulations to investigate the
-effects of water permeability on the hydrodynamics of a vesicle under
-various flows and confinement configurations. Coupling the membrane permeability with membrane elastic stress, tension and mechanical stress 
-in the framework of Helfrich free energy, we illustrate
-that, in the absence of an osmotic stress gradient, a giant unilamellar vesicle may be significantly affected by water influx/efflux over a
-sufficiently long time or under a strong confinement. 
-Our simulation results quantify the conditions for water permeation to be negligible in terms of the timescales, flow strength of an external flow, and degree of confinement.
-These results shed light on how microfluidic confinement can be utilized to estimate membrane permeability.
+Lipid bilayer membranes have a native (albeit small) permeability for
+water molecules. As long as the bilayer structure stays intact
+without poration or rupture under load, the water influx/efflux is
+often assumed to be negligible in the absence of a gradient of osmotic
+stress. In this work we use boundary integral simulations to
+investigate the effects of water permeability on the hydrodynamics of
+a vesicle under various flows and confinement configurations. Coupling
+the membrane permeability with membrane elastic stress, tension, and
+mechanical stress in the framework of Helfrich free energy, we
+illustrate that, in the absence of an osmotic stress gradient, a giant
+unilamellar vesicle may be significantly affected by water
+influx/efflux over a sufficiently long time or under a strong
+confinement. Our simulation results quantify the conditions for water
+permeation to be negligible in terms of the time scales, flow strength
+of an external flow, and degree of confinement. These results shed
+light on how microfluidic confinement can be utilized to estimate
+membrane permeability.
 %
@@
 \dropcap{W}ater exchange is essential for a living cell to adapt to its
-environment over a wide range of
-timescales~\cite{CadartVenkovaRechoEtAl2019_NaturePhys,
+environment over a wide range of time
+scales~\cite{CadartVenkovaRechoEtAl2019_NaturePhys,
 AlbertsMolecularBiology, YangMaVerkman2001_JBC,
@@
 Molecular dynamic (MD) simulations show that a stretched red blood cell
-(RBC) membrane porates when the membrane tension reaches the order of
-$2$--$4$ mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references
-therein), giving rise to enhanced membrane permeability to both water
-and macromolecules.  Consequently, as long as the lipid bilayer membrane
-remains intact (no poration or rupture), RBCs and vesicles are assumed
-to be of the same volume throughout experiments of durations no longer
-than tens of minutes.
+membrane porates when the membrane tension reaches the order of $2$--$4$
+mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references therein),
+giving rise to enhanced membrane permeability to both water and
+macromolecules. Consequently, as long as the lipid bilayer membrane
+remains intact (no poration or rupture), red blood cells and vesicles
+are assumed to be of the same volume throughout experiments of durations
+no longer than tens of minutes.
 %
@@
 In microfluidic experiments, it is challenging to keep a freely
-suspended RBC or vesicle in a steady flow for more than a few hours. It
+suspended red blood cell or vesicle in a steady flow for more than a few hours. It
 is also difficult to quantify the vesicle area/volume ratio accurately.
@@
 membrane bending stiffness $k_b = 10^{-19}$J, a membrane tension
-$10^{-3}$N/m (one tenth of the lysis tension) and a characteristic
+$10^{-3}$N/m (one tenth of the lysis tension), and a characteristic
 length scale of $10^{-6}$m, the tension contribution ($v_\mathrm{t}$)
@@
 permeable flow can be significant when the membrane tension is large due
-to the external stress such as the hydrodynamics stress due to an
-external flow, confinement, or both. In the following we will explore
-both.
+to the external stress such as the hydrodynamic stress due to an
+external flow or confinement. In the following we will explore both.
 
@@
 and a Poiseuille flow. We also consider a semipermeable vesicle in
-confinement: a long channel and a contracting channel. For each example,
-we fix the vesicle length and examine the enclosed area as a dynamical
-consequence of water flow, vesicle shape deformation, and membrane
-tension distribution.
+confinement: a long close-fitting channel and a contracting channel. For
+each example, we fix the vesicle length and examine the enclosed area as
+a dynamic consequence of water flow, vesicle shape deformation, and
+membrane tension distribution.
 
@@
 deviate from its initial reduced area and to reach its steady state is
-proportional to $\beta^{-1}$. For this reason, our numerical results
-below are reported in terms of the scaled time $\beta t$.
+proportional to $\beta^{-1}$. For this reason, our numerical results are
+reported in terms of the scaled time $\beta t$.
 
@@
 dynamics of a semipermeable vesicle with four initial shapes and reduced
-areas as labeled.
-%$\beta = 10^{-3}$ and a variety of initial configurations. 
-The vesicles on the left are color-coded by the water permeation flux: red denotes an influx into the vesicle, and blue denotes an efflux out of the vesicle.
+areas as labeled. The vesicles on the left are color-coded by the water
+permeation flux: red denotes an influx into the vesicle, and blue
+denotes an efflux out of the vesicle.
 %
@@
 \nn) \nn$, and (ii) the force balance velocity, $\SS[\ff]$. Since
-%$\beta = 10^{-6}$, 
-$\beta\ll 1$,
-the permeability velocity is much smaller than the force
+$\beta\ll 1$, the permeability velocity is much smaller than the force
 balance velocity at early times, and the semipermeable vesicle dynamics
-resembles those of an impermeable vesicle. As the force balance velocity
+resemble those of an impermeable vesicle. As the force balance velocity
 decreases, the permeability velocity dominates, and the vesicle begins
 to inflate to a circle with no vanishing force and velocity.
-%\todo[inline]{There might be some confusion regarding the value of $\beta$. The caption says one value and the text says another.}
 
@@
   influx and the blue regions correspond to efflux. (b): The steady
-  state inclination angle for four different flow velocities. The steady
-  state shapes are superimposed. (c): The reduced area of the slipper
-  formed with the flow rate of 800 $\mu m/s$. (d): The vesicle shape
-  shown with the background imposed flow. The channel width is 12.5
-  times larger than the vesicle radius. The corresponding reduced area
-  of each vesicle is indicated by the marks in plot (c).}
+  state vertical displacement for four different flow velocities. The
+  steady state shapes are superimposed. (c): The reduced area of the
+  slipper formed with the flow rate of $800 \mu$m/s. (d): The vesicle
+  shape shown with the background imposed flow. The channel width is
+  12.5 times larger than the vesicle radius. The corresponding reduced
+  area of each vesicle is indicated by the marks in plot (c).}
 \end{figure*}
@@
 Figure~\ref{fig:parabolicComposite}(c) and (d).
-%
 
@@
 across a stenosed geometry. In this experiment, a pressure drop is used
-to squeeze a red blood cell (RBC) through a constriction with diameter
-$5\mu$m and length $45\mu$m. We set up a similar computational geometry
-with a Poiseuille flow imposed at the inlet and outlet
+to squeeze a red blood cell through a constriction with diameter $5\mu$m
+and length $45\mu$m. We set up a similar computational geometry with a
+Poiseuille flow imposed at the inlet and outlet
 (Figure~\ref{fig:stenosisComposite}(a)). The flow velocity $U_{max} =
-1000 \mu$m/s is chosen so that the residency time of the vesicle  in the
-stenosis channel $t_R \approx 0.5$ s agrees with the experimental
-results~\cite{abk-fai-sto2006}. When the RBC enters the channel, an
-increase in the pressure drop is required to maintain a constant flow
-rate, and the difference in the pressure drop is called the excess
-pressure.
+1000 \mu$m/s is maintained at the inlet and outlet and is chosen so that the residency time of the vesicle in the
+stenosis channel is $t_R \approx 0.5$s which agrees with the
+experimental results~\cite{abk-fai-sto2006}. When the red blood cell
+enters the channel, an increase in the pressure drop is required to
+maintain a constant flow rate, and the difference in the pressure drop
+is called the excess pressure.
 
@@
 compute the excess pressure as a function of vesicle position in the
-channel, see Figure~\ref{fig:stenosisComposite}(c). A 
-Poiseuille flow with a maximum value of $1000 \mu$m/s is maintained
-at the inlet and outlet. The impermeable case agrees with experimental
-results in Figure 3 of~\cite{abk-fai-sto2006}. Our simulations show that
-less excess pressure is needed to drive a semipermeable vesicle through the closely-fit channel.
-Once in the channel, the vesicle takes a bullet shape with maximum tension in the front and minimum tension in the back (see Figure~\ref{fig:stenosisComposite}(a)),
-consistent with earlier results~\cite{Pak2015_PNAS,HarmanBertrandJoos2017_CJP}.
-
-Figure~\ref{fig:stenosisComposite}(d)) shows
-that the vesicle
-deflates from the beginning due to the high flow velocity, consistent
-with the results for a vesicle in a Poiseuille flow in open space. As
-the vesicle enters the stenosis channel, it continues to
-deflate in the front even though we observe influx (red segment) at
-various rear locations in the membrane. Overall, the vesicle loses about 6.1\% of its initial total water at a constant rate as shown in
-Figure~\ref{fig:stenosisComposite}(d).  Thus we expect that a larger amount of deflation is possible
-if the vesicle is inside a longer stenosis: we consider a vesicle passing
-through a channel of triple the length in
-Figure~\ref{fig:stenosisComposite}(b) with $U_{max}=8.4 \mu$m/s, and we observe that vesicle stays inside the stenosis  for a residence time $t_R=16.2$ seconds and the reduced
-area decreases by 13.2\% (Figure~\ref{fig:stenosisComposite}(e)).
-%\begin{itemize}
-%  \item In plot (a), flow rate is $1000 \mu m/s$ and residency time is
-%    $t_R = 45.6 \times 10^{-2}$ s.
-%  \item In plot (b), flow rate is $8.4 \mu m/s$ and residency time is
-%    $t_R =  16.2$ s.
-%\end{itemize}
+channel, see Figure~\ref{fig:stenosisComposite}(c). The impermeable case
+agrees with experimental results~\cite{abk-fai-sto2006} (see Figure 3).
+Our simulations show that less excess pressure is needed to drive a
+semipermeable vesicle through the closely-fit channel. Once in the
+channel, the vesicle takes a bullet shape with maximum tension in the
+front and minimum tension in the back (see
+Figure~\ref{fig:stenosisComposite}(a)), consistent with earlier
+results~\cite{Pak2015_PNAS, HarmanBertrandJoos2017_CJP}.
+
+Figure~\ref{fig:stenosisComposite}(d)) shows that the vesicle deflates
+from the beginning due to the high flow velocity, consistent with the
+results for a vesicle in a Poiseuille flow in open space. As the vesicle
+enters the stenosis channel, it continues to deflate in the front even
+though we observe influx (red segment) at various rear locations in the
+membrane. Overall, the vesicle loses about 6.1\% of its initial total
+water at a constant rate as shown in
+Figure~\ref{fig:stenosisComposite}(d). Thus we expect that a larger
+amount of deflation is possible if the vesicle is inside a longer
+stenosis: we consider a vesicle passing through a channel of triple the
+length in Figure~\ref{fig:stenosisComposite}(b) with $U_{max}=8.4
+\mu$m/s, and we observe that vesicle stays inside the stenosis for a
+residence time $t_R=16.2$s and the reduced area decreases by 13.2\%
+(Figure~\ref{fig:stenosisComposite}(e)).
 
@@
   correspond to the times that the vesicle enters and exits the
-  constriction.}
+  constriction. The colored vesicles show the tension distribution in
+  N/m of the circled vesicles. Throughout the entire simulation, these
+  vesicle configurations have the largest tension.}
 \end{figure*}
@@
 macromolecules~\cite{ShareiEtAl2013_PNAS,Pak2015_PNAS,ZhangShenHoganBarakatMisbah2018_BJ,LuoBai2019_PoF}.
-RBCs go through submicron slits many times during their lifetime, and
-such process selects healthy, flexible RBCs to
+Red blood cells go through submicron slits many times during their
+lifetime, and such process selects healthy, flexible red blood cells to
 survive~\cite{wu2015critical,LuPeng2019_PoF}. Here we investigate the
@@
 to~\cite{wu2015critical}, where the width of the channel gradually
-decreases from $16 \mu$m to $1.6 \mu$m. The channel then immediately
-opens again to $16 \mu$m (Figure~\ref{fig:contractingComposite}). A
+decreases from $18 \mu$m to $1.8 \mu$m. The channel then immediately
+opens again to $18 \mu$m (Figure~\ref{fig:contractingComposite}). A
 Poiseuille flow is imposed at the inlet and outlet with a constant
@@
 and~\ref{fig:contractingComposite}b, we plot snapshots of vesicles with
-different permeability $\beta$. 
-Figure~\ref{fig:contractingComposite}c
-shows the corresponding reduced area as a function of the vesicles' location. 
-The reduced area in Figure~\ref{fig:contractingComposite}c and f shows that the vesicle always inflates gradually over seconds
-before it reaches the neck, where vesicle quickly deflates within a fraction of a second.
-%{\bf YNY: inflates over seconds but deflates over ms?}
-However, if the
+different permeability $\beta$. Figure~\ref{fig:contractingComposite}c
+shows the corresponding reduced area as a function of the vesicles'
+location. We observe that if the permeability is sufficiently large, the
+vesicle inflates gradually over seconds before it reaches the neck, and
+then it quickly deflates within a fraction of a second. However, if the
 semipermeability rate is too low, the vesicle is too large when it
@@
 different imposed maximum velocities, and
-Figure~\ref{fig:contractingComposite}f shows that the reduced area as a
+Figure~\ref{fig:contractingComposite}f shows the reduced area as a
 function of the vesicles' location. At low velocities, the vesicle
 inflates similar to the unbounded parabolic flow example, and it is
-unable to pass through the constrictions. However, higher flow rates
+unable to pass through the contraction. However, higher flow rates
 result in additional deflation and the vesicle passes through the
@@
 
-To understand the effects of water permeability on cells that repeatedly go through micro-capillary vessels or sub-micron slits, 
-we construct a contracting geometry (see Figures~\ref{fig:contractingComposite}g)
-to simulate a vesicle passing through the contracting geometry six times.
-In Figure~\ref{fig:contractingComposite}h, we show that the vesicle
-deflates each time it passes through the constriction followed by a
-gradual inflation (over seconds). The total area loss over the history of the vesicle is
-almost 50\%. In Figure~\ref{fig:contractingComposite}i, we show the
-vesicle velocity as a function of the vesicle's center of mass. As the
-vesicle passes through the contraction, it first accelerates until it reaches the neck where it abruptly decelerates
-to go through the contraction. Their corresponding variation with respect to time is shown in Figure~\ref{fig:contractingComposite2}.
+To understand the effects of water permeability on cells that repeatedly
+go through micro-capillary vessels or sub-micron slits, we construct a
+contracting geometry (see Figures~\ref{fig:contractingComposite2}) to
+simulate a vesicle passing through the contracting geometry six times.
+In Figure~\ref{fig:contractingComposite2}b, we show that the vesicle
+deflates each time it passes through the contraction followed by a
+gradual inflation (over seconds). The total area loss over the history
+of the vesicle is almost 50\%. In
+Figure~\ref{fig:contractingComposite}c, we show the vesicle velocity as
+a function of the vesicle's center of mass. As the vesicle passes
+through the contraction, it first accelerates until it reaches the neck
+where it abruptly decelerates to go through the contraction. The
+variation of the reduced area and velocity with respect to time are also
+shown in Figure~\ref{fig:contractingComposite2}.
 
@@
   (a--c): The ability for a semipermeable vesicle to pass through the
-  constriction depends on the semipermeability rate. (d--f): The ability
-  for a semipermeable vesicle to pass through the constriction depends
-  on the flow rate.}
+  contraction depends on the semipermeability rate. (d--f): The ability
+  for a semipermeable vesicle to pass through the contraction depends
+  on the flow rate. The colored vesicles show the tension distribution
+  in N/m of the circled vesicles. Throughout the entire simulation,
+  these vesicle configurations have the largest tension.}
 \end{figure}
@@
   x-axis is the $x$-coordinate of the center of mass, and the upper
-  x-axis is time.}
+  x-axis is time. The colored vesicles show the tension distribution in
+  N/m of the circled vesicles. Throughout the entire simulation, these
+  vesicle configurations have the largest tension.}
 \end{figure}
@@
 \section*{Discussion}
-In this work we investigated the effects of membrane permeability to water on the vesicle hydrodynamics.
-Without any external flow or confinement, our analysis shows that a semipermeable vesicle always inflates to maximize the water content inside the vesicle of a fixed length (area) in two (three) dimensions.
-Results from analysis and numerical simulation show that such relaxation of a semipermeable vesicle is characterized by a rescaled time $\beta t$.
-We further illustrate that the relaxation process consists of at least two phases: The
-first phase is dominated by the balance between membrane traction and viscous stress at early times (up to a minute), when the vesicle behaves like an impermeable membrane.
-The second phase sets in after a few minutes, when water influx begins to dominate and inflate the vesicle.
-Over a timescale of a few hours a semipermeable vesicle is fully inflated, independent of its initial surface-to-volume ratio.
-
-The two phases in the relaxation dynamics are also observed  in the hydrodynamics of a semipermeable vesicle under a shear flow (both the planar and Poiseuille flows) in free space. 
-Similar to an impermeable vesicle in a shear flow, a semipermeable vesicle also reaches an equilibrium shape and position.
-Yet for a semipermeable vesicle the equilibrium shape depends on the strength of the shear flow (shear rate $\dot\gamma$ for the planar shear flow, and $U_{max}$ for the Poiseuille flow).
-Our simulations also show that, in a Poiseuille flow, symmetric equilibrium vesicle shape is possible only at low flow velocity.
-In experiments it may take a few hours for the semipermeable vesicle to reach such equilibria that could be used to quantify the flow strength.
-
-Under strong confinement we show that water permeation can be amplified on a timescale of a few seconds as a vesicle is squeezed through a closely fit channel and a contracting 
-channel. As a semipermeable vesicle goes through a long closely-fit channel, we observe that the vesicle loses water at a constant rate, and the longer the channel the more the loss 
-of water. In the case of contracting channel, we find that both permeability and the pressure gradient across the slit must be sufficiently large for a successful passage. Throughout 
-these simulations the membrane tension is below the threshold for membrane poration. Thus we expect the continuum membrane theory to well-capture the vesicle hydrodynamics, 
-and our simulation results shed light on the configuration and timescales needed to observe the effects of permeability on vesicle hydrodynamics under confinement.
+In this work we investigated the effects of membrane permeability to
+water on vesicle hydrodynamics. Without any external flow or
+confinement, our analysis shows that a semipermeable vesicle always
+inflates to maximize the water content inside the vesicle of a fixed
+length (area) in two (three) dimensions. Results from analysis and
+numerical simulation show that such relaxation of a semipermeable
+vesicle is characterized by a rescaled time $\beta t$. We further
+illustrate that the relaxation process consists of at least two phases:
+The first phase is dominated by the balance between membrane traction
+and viscous stress at early times (up to a minute), when the vesicle
+behaves like an impermeable membrane. The second phase sets in after a
+few minutes, when water influx begins to dominate and inflate the
+vesicle. Over a time scale of a few hours, a semipermeable vesicle is
+fully inflated, independent of its initial surface-to-volume ratio.
+
+Under strong confinement we show that water permeation can be amplified
+on a time scale of a few seconds as a vesicle is squeezed through a
+closely fit channel and a contracting channel. As a semipermeable
+vesicle goes through a long closely-fit channel, we observe that the
+vesicle loses water at a constant rate, and the longer the channel the
+more the loss of water. In the case of a contracting channel, we find
+that both permeability and the pressure gradient across the slit must be
+sufficiently large for a successful passage. Throughout these
+simulations the membrane tension is below the threshold for membrane
+poration. Thus we expect the continuum membrane theory to well-capture
+the vesicle hydrodynamics, and our simulation results shed light on the
+configuration and time scales needed to observe the effects of
+permeability on vesicle hydrodynamics under confinement.
 
@@
 in~\cite{kao-bir-mis2009} (see Figure 2), we see that the vesicle shapes
-qualitatively agree. We note that Kaoui {\em et al.}~report that the vesicles
-with $\alpha=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu
-m/s$ are axisymmetric.  In our simulations these vesicles are slightly
-asymmetric, are undergoing a tank treading motion, and we therefore
-report them as asymmetric slippers.
+qualitatively agree. We note that Kaoui {\em et al.}~report that the
+vesicles with $\alpha=0.7$ and flow rates $U = 1200 \mu$ m/s and $U =
+1600 \mu$m/s are axisymmetric.  In our simulations these vesicles are
+slightly asymmetric, are undergoing a tank treading motion, and we
+therefore report them as asymmetric slippers.
 \begin{figure}[htp]

### 2020-12-30 vesicle_code/docs/permeableVes/main.tex
small edit

@@
 \subsection*{Semipermeable Vesicle in a Contracting Geometry} 
-Squeezing a cell or an elastic vesicle through a slit in microfluidics
-has gained popularity for its application in stress-induced release of
-macromolecules~\cite{ShareiEtAl2013_PNAS,Pak2015_PNAS,ZhangShenHoganBarakatMisbah2018_BJ,LuoBai2019_PoF}.
-Red blood cells go through submicron slits many times during their
-lifetime, and such process selects healthy, flexible red blood cells to
-survive~\cite{wu2015critical,LuPeng2019_PoF}. Here we investigate the
-role of membrane permeability to water when a semipermeable vesicle is
-squeezed through a contracting microfluidic channel similar
-to~\cite{wu2015critical}, where the width of the channel gradually
-decreases from $18 \mu$m to $1.8 \mu$m. The channel then immediately
-opens again to $18 \mu$m (Figure~\ref{fig:contractingComposite}). A
-Poiseuille flow is imposed at the inlet and outlet with a constant
-maximum flow rate of $U_{\max}$. We initialize a semipermeable vesicle
-with $\alpha = 0.65$ that spans $10 \mu$m of the total channel width and
-investigate the effects of the membrane permeability to water and the
-maximum flow velocity on whether a vesicle can successfully pass through
-the slit. We color the vesicle according to the sign of its flux---red
-for influx and blue for efflux.
-
-In Figures~\ref{fig:contractingComposite}a
-and~\ref{fig:contractingComposite}b, we plot snapshots of vesicles with
-different permeability $\beta$. Figure~\ref{fig:contractingComposite}c
-shows the corresponding reduced area as a function of the vesicles'
-location. We observe that if the permeability is sufficiently large, the
-vesicle inflates gradually over seconds before it reaches the neck, and
-then it quickly deflates within a fraction of a second. However, if the
-semipermeability rate is too low, the vesicle is too large when it
-reaches the narrowest part of the channel, and it is unable to pass. In
-Figures~\ref{fig:contractingComposite}d
-and~\ref{fig:contractingComposite}e, we plot snapshots of vesicles with
-different imposed maximum velocities, and
-Figure~\ref{fig:contractingComposite}f shows the reduced area as a
-function of the vesicles' location. At low velocities, the vesicle
-inflates similar to the unbounded parabolic flow example, and it is
-unable to pass through the contraction. However, higher flow rates
-result in additional deflation and the vesicle passes through the
-contraction.
-
-To understand the effects of water permeability on cells that repeatedly
-go through micro-capillary vessels or sub-micron slits, we construct a
-contracting geometry (see Figures~\ref{fig:contractingComposite2}) to
-simulate a vesicle passing through the contracting geometry six times.
-In Figure~\ref{fig:contractingComposite2}b, we show that the vesicle
-deflates each time it passes through the contraction followed by a
-gradual inflation (over seconds). The total area loss over the history
-of the vesicle is almost 50\%. In
-Figure~\ref{fig:contractingComposite}c, we show the vesicle velocity as
-a function of the vesicle's center of mass. As the vesicle passes
-through the contraction, it first accelerates until it reaches the neck
-where it abruptly decelerates to go through the contraction. The
-variation of the reduced area and velocity with respect to time are also
-shown in Figure~\ref{fig:contractingComposite2}.
-
-%
-%\begin{itemize}
-%  \item Vesicle velocity in plot (a) varies from 5 to 24 microns/s.
-%  \item Vesicle velocity in plot (b) varies from 5 to 28 microns/s. Time
-%    that vesicle first completely passes through constriction is 4.75s
-%  \item Vesicle velocity in plot (c) varies from 0.2 to 2 microns/s.
-%  \item Vesicle velocity in plot (d) varies from 5 to 25 microns/s. Time
-%    that vesicle first completely passes through constriction is 4.76s
-%  \item Vesicle velocity in plot (g) varies from 14 to 95 microns/s (see
-%    plot (i)). Time that vesicle first completely passes through
-%    constriction is 1.43s
-%\end{itemize}
-
 \begin{figure}[htp]
@@
 \end{figure}
+Squeezing a cell or an elastic vesicle through a slit in microfluidics
+has gained popularity for its application in stress-induced release of
+macromolecules~\cite{ShareiEtAl2013_PNAS, Pak2015_PNAS,
+ZhangShenHoganBarakatMisbah2018_BJ, LuoBai2019_PoF}. Red blood cells go
+through submicron slits many times during their lifetime, and such
+process selects healthy, flexible red blood cells to
+survive~\cite{wu2015critical,LuPeng2019_PoF}. Here we investigate the
+role of membrane permeability to water when a semipermeable vesicle is
+squeezed through a contracting microfluidic channel similar
+to~\cite{wu2015critical}, where the width of the channel gradually
+decreases from $18 \mu$m to $1.8 \mu$m. The channel then immediately
+opens again to $18 \mu$m (Figure~\ref{fig:contractingComposite}). A
+Poiseuille flow is imposed at the inlet and outlet with a constant
+maximum flow rate of $U_{\max}$. We initialize a semipermeable vesicle
+with $\alpha = 0.65$ that spans $10 \mu$m of the total channel width and
+investigate the effects of the membrane permeability to water and the
+maximum flow velocity on whether a vesicle can successfully pass through
+the slit. We color the vesicle according to the sign of its flux---red
+for influx and blue for efflux.
+
+In Figures~\ref{fig:contractingComposite}a
+and~\ref{fig:contractingComposite}b, we plot snapshots of vesicles with
+different permeability $\beta$. Figure~\ref{fig:contractingComposite}c
+shows the corresponding reduced area as a function of the vesicles'
+location. We observe that if the permeability is sufficiently large, the
+vesicle inflates gradually over seconds before it reaches the neck, and
+then it quickly deflates within a fraction of a second. However, if the
+semipermeability rate is too low, the vesicle is too large when it
+reaches the narrowest part of the channel, and it is unable to pass. In
+Figures~\ref{fig:contractingComposite}d
+and~\ref{fig:contractingComposite}e, we plot snapshots of vesicles with
+different imposed maximum velocities, and
+Figure~\ref{fig:contractingComposite}f shows the reduced area as a
+function of the vesicles' location. At low velocities, the vesicle
+inflates similar to the unbounded parabolic flow example, and it is
+unable to pass through the contraction. However, higher flow rates
+result in additional deflation and the vesicle passes through the
+contraction.
+
+To understand the effects of water permeability on cells that repeatedly
+go through micro-capillary vessels or sub-micron slits, we construct a
+contracting geometry (see Figures~\ref{fig:contractingComposite2}) to
+simulate a vesicle passing through the contracting geometry six times.
+In Figure~\ref{fig:contractingComposite2}b, we show that the vesicle
+deflates each time it passes through the contraction followed by a
+gradual inflation (over seconds). The total area loss over the history
+of the vesicle is almost 50\%. In
+Figure~\ref{fig:contractingComposite}c, we show the vesicle velocity as
+a function of the vesicle's center of mass. As the vesicle passes
+through the contraction, it first accelerates until it reaches the neck
+where it abruptly decelerates to go through the contraction. The
+variation of the reduced area and velocity with respect to time are also
+shown in Figure~\ref{fig:contractingComposite2}.
+
+%
+%\begin{itemize}
+%  \item Vesicle velocity in plot (a) varies from 5 to 24 microns/s.
+%  \item Vesicle velocity in plot (b) varies from 5 to 28 microns/s. Time
+%    that vesicle first completely passes through constriction is 4.75s
+%  \item Vesicle velocity in plot (c) varies from 0.2 to 2 microns/s.
+%  \item Vesicle velocity in plot (d) varies from 5 to 25 microns/s. Time
+%    that vesicle first completely passes through constriction is 4.76s
+%  \item Vesicle velocity in plot (g) varies from 14 to 95 microns/s (see
+%    plot (i)). Time that vesicle first completely passes through
+%    constriction is 1.43s
+%\end{itemize}
 

### 2020-12-30 vesicle_code/docs/permeableVes/main.tex
fixed figures 6 and 7 pdf versions

@@
 $\uu(\xx) = \UU(\xx)$ is enforced on $\partial \Omega$, where $\UU(\xx)$
-is prescribed. Along the vesicle $\gamma$, mass continuity, force
-balance, and local inextensibility are enforced by requiring
+is prescribed. Along the vesicle, mass continuity, force balance, and
+local inextensibility are enforced by requiring
 \begin{align}
@@
 = \Lambda - 1.5\kappa^2$, where $\kappa$ is the vesicle curvature. Then,
-the bending and tension forces are $\ff_\mathrm{ben} = -k_b \xx_{ssss}$
-and $\ff_\mathrm{ten} = (\sigma \xx_s)_s$.
+the bending and tension forces corresponding to the Helfrich energy are
+$\ff_\mathrm{ben} = -k_b \xx_{ssss}$ and $\ff_\mathrm{ten} = (\sigma
+\xx_s)_s$.
 
@@
 $W = R_0\mu = 2 \times 10^{-5}$m$^2$s/kg. Another standard dimensionless
-variable in vesicle suspensions is the reduced area $\nu = 4\pi A/L^2
+variable in vesicle suspensions is the reduced area $\alpha = 4\pi A/L^2
 \in (0,1]$, where $L$ is the vesicle length and $A$ is its area. The

### 2020-12-30 vesicle_code/docs/permeableVes/main.tex
yny

--- 2020-12-30 vesicle_code/docs/permeableVes/main.tex
@@
 Lipid bilayer membranes have a native (albeit small) permeability for
-water molecules. As long as the bilayer structure stays intact
-without poration or rupture under load, the water influx/efflux is
-often assumed to be negligible in the absence of a gradient of osmotic
-stress. In this work we use boundary integral simulations to
-investigate the effects of water permeability on the hydrodynamics of
-a vesicle under various flows and confinement configurations. Coupling
-the membrane permeability with membrane elastic stress, tension, and
+water molecules. Provided that the bilayer structure stays intact
+without membrane poration or rupture under load, the water influx/efflux is
+often assumed negligible in the absence of a gradient of osmotic
+stress. 
+%
+In this work we focus on physical regimes where the membrane tension is below the critical value for membrane poration, and use boundary integral simulations to
+investigate the effects of native water permeability on the hydrodynamics of
+a vesicle under various flows and confinement configurations. 
+%
+Coupling the membrane permeability with membrane elastic stress, tension, and
 mechanical stress in the framework of Helfrich free energy, we
@@
 and elasticity of a semipermeable membrane under various flowing
-conditions and confinement. 
+conditions and confinement, see Figure~\ref{fig:sketch}.
 %Specifically our numerical simulations yield the quantification of the
@@
 %important.
+
+\begin{figure}[htp]
+  \centering
+  \includegraphics[width=0.5\textwidth]{figures/schematic.pdf}
+  \caption{\label{fig:sketch} Schematics showing the effects of
+  semipermeability on vesicle hydrodynamics in various configurations. 
+  The lipid bilayer membrane (modeled as an interface $\gamma$ of zero thickness and an outward normal $\nn$) 
+  is permeable to water molecules, depending on the mechanical normal stress balance on the membrane.
+  The slipper in (a) is the steady-state shape of a semipermeable
+  vesicle in a Poiseuille flow.}
+\end{figure}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htp]
-  \centering
-  \includegraphics[width=0.5\textwidth]{figures/schematic.pdf}
-  \caption{\label{fig:sketch} Schematics showing the effects of
-  semipermeability on vesicle hydrodynamics in various configurations.
-  The slipper in (a) is the steady-state shape of a semipermeable
-  vesicle in a Poiseuille flow.}
-\end{figure}
-
 \section*{Formulation}
@@
 \subsection*{Semipermeable Vesicle in a Narrow Channel (Stenosis)}
-Cells experience stretching and release messengers when they pass
-through capillary vessels~\cite{Wan2008_PNAS, ForsythWan2011_PNAS,
-Pak2015_PNAS}.  Many cells exhibit extraordinary flexibility as they go
-through narrow channels~\cite{AuStoreyMoore2016_PNAS}, and adjustment of
-area to volume ratio may be a key factor for a successful passage.  Here
-we quantify the effect of water permeability on a vesicle going through
-a stenosis (a long microfluidic channel with a width smaller than the
-cell radius).  Based on the findings in~\cite{abk-fai-sto2006}, we first
-examine the effect of semipermeability on the pressure fluctuation
-across a stenosed geometry. In this experiment, a pressure drop is used
-to squeeze a red blood cell through a constriction with diameter $5\mu$m
-and length $45\mu$m. We set up a similar computational geometry with a
-Poiseuille flow imposed at the inlet and outlet
-(Figure~\ref{fig:stenosisComposite}(a)). The flow velocity $U_{max} =
-1000 \mu$m/s is maintained at the inlet and outlet and is chosen so that the residency time of the vesicle in the
-stenosis channel is $t_R \approx 0.5$s which agrees with the
-experimental results~\cite{abk-fai-sto2006}. When the red blood cell
-enters the channel, an increase in the pressure drop is required to
-maintain a constant flow rate, and the difference in the pressure drop
-is called the excess pressure.
-
-We consider both an impermeable and semipermeable vesicle with initial
-reduced area $\alpha = 0.65$ passing through a long narrow channel and
-compute the excess pressure as a function of vesicle position in the
-channel, see Figure~\ref{fig:stenosisComposite}(c). The impermeable case
-agrees with experimental results~\cite{abk-fai-sto2006} (see Figure 3).
-Our simulations show that less excess pressure is needed to drive a
-semipermeable vesicle through the closely-fit channel. Once in the
-channel, the vesicle takes a bullet shape with maximum tension in the
-front and minimum tension in the back (see
-Figure~\ref{fig:stenosisComposite}(a)), consistent with earlier
-results~\cite{Pak2015_PNAS, HarmanBertrandJoos2017_CJP}.
-
-Figure~\ref{fig:stenosisComposite}(d)) shows that the vesicle deflates
-from the beginning due to the high flow velocity, consistent with the
-results for a vesicle in a Poiseuille flow in open space. As the vesicle
-enters the stenosis channel, it continues to deflate in the front even
-though we observe influx (red segment) at various rear locations in the
-membrane. Overall, the vesicle loses about 6.1\% of its initial total
-water at a constant rate as shown in
-Figure~\ref{fig:stenosisComposite}(d). Thus we expect that a larger
-amount of deflation is possible if the vesicle is inside a longer
-stenosis: we consider a vesicle passing through a channel of triple the
-length in Figure~\ref{fig:stenosisComposite}(b) with $U_{max}=8.4
-\mu$m/s, and we observe that vesicle stays inside the stenosis for a
-residence time $t_R=16.2$s and the reduced area decreases by 13.2\%
-(Figure~\ref{fig:stenosisComposite}(e)).
-
  \begin{figure*}[htp]
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Semipermeable Vesicle in a Contracting Geometry} 
+Cells experience stretching and release messengers when they pass
+through capillary vessels~\cite{Wan2008_PNAS, ForsythWan2011_PNAS,
+Pak2015_PNAS}.  Many cells exhibit extraordinary flexibility as they go
+through narrow channels~\cite{AuStoreyMoore2016_PNAS}, and adjustment of
+area to volume ratio may be a key factor for a successful passage.  Here
+we quantify the effect of water permeability on a vesicle going through
+a stenosis (a long microfluidic channel with a width smaller than the
+cell radius).  Based on the findings in~\cite{abk-fai-sto2006}, we first
+examine the effect of semipermeability on the pressure fluctuation
+across a stenosed geometry. In this experiment, a pressure drop is used
+to squeeze a red blood cell through a constriction with diameter $5\mu$m
+and length $45\mu$m. We set up a similar computational geometry with a
+Poiseuille flow imposed at the inlet and outlet
+(Figure~\ref{fig:stenosisComposite}(a)). The flow velocity $U_{max} =
+1000 \mu$m/s is maintained at the inlet and outlet and is chosen so that the residency time of the vesicle in the
+stenosis channel is $t_R \approx 0.5$s which agrees with the
+experimental results~\cite{abk-fai-sto2006}. When the red blood cell
+enters the channel, an increase in the pressure drop is required to
+maintain a constant flow rate, and the difference in the pressure drop
+is called the excess pressure.
+
+We consider both an impermeable and semipermeable vesicle with initial
+reduced area $\alpha = 0.65$ passing through a long narrow channel and
+compute the excess pressure as a function of vesicle position in the
+channel, see Figure~\ref{fig:stenosisComposite}(c). The impermeable case
+agrees with experimental results~\cite{abk-fai-sto2006} (see Figure 3).
+Our simulations show that less excess pressure is needed to drive a
+semipermeable vesicle through the closely-fit channel. Once in the
+channel, the vesicle takes a bullet shape with maximum tension in the
+front and minimum tension in the back (see
+Figure~\ref{fig:stenosisComposite}(a)), consistent with earlier
+results~\cite{Pak2015_PNAS, HarmanBertrandJoos2017_CJP}.
+
 \begin{figure}[htp]
@@
 \end{figure}
+
+Figure~\ref{fig:stenosisComposite}(d)) shows that the vesicle deflates
+from the beginning due to the high flow velocity, consistent with the
+results for a vesicle in a Poiseuille flow in open space. As the vesicle
+enters the stenosis channel, it continues to deflate in the front even
+though we observe influx (red segment) at various rear locations in the
+membrane. Overall, the vesicle loses about 6.1\% of its initial total
+water at a constant rate as shown in
+Figure~\ref{fig:stenosisComposite}(d). Thus we expect that a larger
+amount of deflation is possible if the vesicle is inside a longer
+stenosis: we consider a vesicle passing through a channel of triple the
+length in Figure~\ref{fig:stenosisComposite}(b) with $U_{max}=8.4
+\mu$m/s, and we observe that vesicle stays inside the stenosis for a
+residence time $t_R=16.2$s and the reduced area decreases by 13.2\%
+(Figure~\ref{fig:stenosisComposite}(e)).
+
+%\begin{figure*}[htp]
+%  \ifTikz
+%  \input{figures/stenosisComposite.tikz}
+%  \else
+%  \includegraphics{figures/stenosisComposite.pdf}
+%  \fi
+%  \caption{\label{fig:stenosisComposite} (a): A semipermeable vesicle
+%  passing through a constricted geometry similar to the experimental
+%  device in~\cite{abk-fai-sto2006}. (b): A semipermeable vesicle passing
+%  through a constricted geometry that is over five times longer. (c):
+%  The excess pressure of an impermeable and semipermeable vesicle in the
+%  short geometry in (a). (d): The reduced area of the semipermeable
+%  vesicles in the geometries in (a) and (b) as a function of the
+%  vesicles' center of mass. The $x$-axis is scaled by $1/L$ where $L$ is
+%  half the length of the constriction. (e) The reduced area of the
+%  semipermeable vesicles in the geometries in (a) and (b) as a function
+%  of time. The time axis is scaled by $1/t_R$ where $t_R$ is the
+%  residency time. In parts (c) and (d), the dashed lines correspond to
+%  the locations of the inlet and outlet. In part (e), the dashed lines
+%  correspond to the times that the vesicle enters and exits the
+%  constriction. The colored vesicles show the tension distribution in
+%  N/m of the circled vesicles. Throughout the entire simulation, these
+%  vesicle configurations have the largest tension.}
+%\end{figure*}
+%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Semipermeable Vesicle in a Contracting Geometry} 
+\begin{figure}[htp]
+  \ifTikz
+  \input{figures/contractingComposite2.tikz}
+  \else
+  \includegraphics{figures/contractingComposite2.pdf}
+  \fi
+  \caption{\label{fig:contractingComposite2} Vesicle reduced area and
+  velocity vs.~time. Permeability rate is $\beta = 10^{-3}$ and maximum
+  velocity is $18\mu$m/s. (a): A semipermeable vesicle passing through
+  six periods of the contracting geometry. (b): The reduced area with
+  the marks representing shapes in (a). (c): The vesicle velocity with
+  the marks representing shapes in (a). In (b) and (c), the bottom
+  x-axis is the $x$-coordinate of the center of mass, and the upper
+  x-axis is time. The colored vesicles show the tension distribution in
+  N/m of the circled vesicles. Throughout the entire simulation, these
+  vesicle configurations have the largest tension.}
+\end{figure}
+
 Squeezing a cell or an elastic vesicle through a slit in microfluidics
@@
 %\end{itemize}
-
-\begin{figure}[htp]
-  \ifTikz
-  \input{figures/contractingComposite2.tikz}
-  \else
-  \includegraphics{figures/contractingComposite2.pdf}
-  \fi
-  \caption{\label{fig:contractingComposite2} Vesicle reduced area and
-  velocity vs.~time. Permeability rate is $\beta = 10^{-3}$ and maximum
-  velocity is $18\mu$m/s. (a): A semipermeable vesicle passing through
-  six periods of the contracting geometry. (b): The reduced area with
-  the marks representing shapes in (a). (c): The vesicle velocity with
-  the marks representing shapes in (a). In (b) and (c), the bottom
-  x-axis is the $x$-coordinate of the center of mass, and the upper
-  x-axis is time. The colored vesicles show the tension distribution in
-  N/m of the circled vesicles. Throughout the entire simulation, these
-  vesicle configurations have the largest tension.}
-\end{figure}
 

### 2020-12-30 vesicle_code/docs/permeableVes/main.tex
working on supp material

--- 2020-12-30 vesicle_code/docs/permeableVes/main.tex
@@
 \end{figure}
+
+\begin{figure}[htp]
+  \ifTikz
+  \input{figures/contractingComposite2.tikz}
+  \else
+  \includegraphics{figures/contractingComposite2.pdf}
+  \fi
+  \caption{\label{fig:contractingComposite2} Vesicle reduced area and
+  velocity vs.~time. Permeability rate is $\beta = 10^{-3}$ and maximum
+  velocity is $18\mu$m/s. (a): A semipermeable vesicle passing through
+  six periods of the contracting geometry. (b): The reduced area with
+  the marks representing shapes in (a). (c): The vesicle velocity with
+  the marks representing shapes in (a). In (b) and (c), the bottom
+  x-axis is the $x$-coordinate of the center of mass, and the upper
+  x-axis is time. The colored vesicles show the tension distribution in
+  N/m of the circled vesicles. Throughout the entire simulation, these
+  vesicle configurations have the largest tension.}
+\end{figure}
+
 Squeezing a cell or an elastic vesicle through a slit in microfluidics
@@
 confined flows. Both $\gamma$ and $\partial\Omega$ are discretized at
-$N$ and $N_\text{wall}$ points. Derivatives are computed with Fourier
-differentiation, and the eighth-order quadrature~\cite{alp1999} is
-applied to the weakly singular single-layer potential. For confined
-geometries, the trapezoid rule is used to approximate the double-layer
-potential since its kernel is smooth and periodic. Nearly-singular
-integrals are computed with an interpolation-based quadrature
-rule~\cite{qua-bir2014}.
+$N$ and $N_\text{wall}$ points, respectively. Derivatives are computed
+with Fourier differentiation, and the eighth-order
+quadrature~\cite{alp1999} is applied to the weakly singular single-layer
+potential. For confined geometries, the trapezoid rule is used to
+approximate the double-layer potential since its kernel is smooth and
+periodic. Nearly-singular integrals are computed with an
+interpolation-based quadrature rule~\cite{qua-bir2014}.
 
@@
 method that discretizes high-order derivatives
-semiimplicitly~\cite{vee-gue-zor-bir2009}. We introduce the notation
+semi-implicitly~\cite{vee-gue-zor-bir2009}. We introduce the notation
 \begin{alignat}{3}
@@
 similar notation for the other operators. Then, a first-order
-semiimplicit time stepping method of~\eqref{eqn:vesVelocity} is
+semi-implicit time stepping method of~\eqref{eqn:vesVelocity} is
 \begin{alignat}{3}  
@@
 \end{alignat}
-and this is a linear system that we solve with matrix-free GMRES.
+and this linear system is solved with matrix-free GMRES.
 
@@
 quiescent flow is a circle with radius $L/2\pi$ and constant tension
-$\Lambda = 2\pi^2/L^2.$ Note that in contrast to a impermeable vesicle,
-the tension is positive rather than negative.
+$\Lambda = \kappa^2/2 = 2\pi^2/L^2.$ Note that in contrast to a
+impermeable vesicle, the tension is positive rather than negative.
 

### 2020-12-30 vesicle_code/docs/permeableVes/main.tex

--- 2020-12-30 vesicle_code/docs/permeableVes/main.tex
@@
 \begin{figure*}[htp]
+  \centering
   \ifTikz
-  \centering
   \input{figures/parabolicComposite.tikz}
@@
  \begin{figure*}[htp]
+  \centering
   \ifTikz
@@
 \begin{figure}[htp]
+  \centering
   \ifTikz

### 2020-12-30 vesicle_code/docs/permeableVes/main.tex
yny

@@
 \author[a]{Ashley Gannon}
-\author[b]{Howard A.~Stone}
-\author[c,1]{Y.-N.~Young}
+\author[b,1]{Y.-N.~Young}
 
 \affil[a]{Department of Scientific Computing, Florida State University, Tallahessee, FL 32306}
-\affil[b]{Department of Mechanical and Aerospace Engineering, Princeton University, Princeton, NJ 08544}
-\affil[c]{Department of Mathematical Sciences, New Jersey Institute of
+\affil[b]{Department of Mathematical Sciences, New Jersey Institute of
 Technology, Newark, NJ 07102}
@@
 Lipid bilayer membranes have a native (albeit small) permeability for
-water molecules. Provided that the bilayer structure stays intact
-without membrane poration or rupture under load, the water influx/efflux is
-often assumed negligible in the absence of a gradient of osmotic
-stress. 
+water molecules. Provided that the bilayer structure stays intact (no membrane poration or rupture) under load, the water influx/efflux is
+often assumed negligible in the absence of a osmolarity pressure across the membrane. 
 %

### 2020-12-31 vesicle_code/docs/permeableVes/main.tex
starting addressing comments from Howard

@@
   semipermeability on vesicle hydrodynamics in various configurations. 
-  The lipid bilayer membrane (modeled as an interface $\gamma$ of zero thickness and an outward normal $\nn$) 
-  is permeable to water molecules, depending on the mechanical normal stress balance on the membrane.
-  The slipper in (a) is the steady-state shape of a semipermeable
-  vesicle in a Poiseuille flow.}
+  The lipid bilayer membrane (modeled as an interface $\gamma$ of zero
+  thickness and an outward normal $\nn$) is permeable to water
+  molecules, depending on the mechanical normal stress balance on the
+  membrane.  The slipper in (a) is the steady-state shape of a
+  semipermeable vesicle in a Poiseuille flow.}
 \end{figure}
@@
 In microfluidic experiments, it is challenging to keep a freely
-suspended red blood cell or vesicle in a steady flow for more than a few hours. It
-is also difficult to quantify the vesicle area/volume ratio accurately.
-Using numerical simulations we can quantify the effects of water
-permeability on the hydrodynamics of a vesicle under mechanical
+suspended red blood cell or vesicle in a steady flow for more than a few
+hours. It is also difficult to quantify the vesicle area/volume ratio
+accurately.  Using numerical simulations we can quantify the effects of
+water permeability on the hydrodynamics of a vesicle under mechanical
 stresses. Vesicles (self-enclosed lipid bilayer membranes) have been
@@
 \section*{Formulation}
+\begin{figure*}[hbp]
+  \centering
+  \ifTikz
+  \input{figures/relaxationComposite.tikz}
+  \else
+  \includegraphics{figures/relaxationComposite.pdf}
+  \fi
+  \caption{\label{fig:relaxationComposite} (a) Snapshots of four
+  semipermeable vesicles with $\beta = 10^{-3}$ submerged in a fluid
+  with no background flow flow. Time goes from left to right. The red
+  regions correspond to influx and the blue regions correspond to
+  efflux. In all cases, the vesicle reaches a steady state circular
+  shape. (b) The reduced area of each of the simulations. The
+  particular snapshots in (a) occur at the marks along the curve.}
+\end{figure*}
 We consider a two-dimensional semipermeable vesicle (permeable only to
-water) suspended in a viscous fluid (Figure~\ref{fig:sketch}). To focus
-on the effect of water flow on vesicle hydrodynamics in various
-conditions, we assume the fluid is the same inside and outside the
-vesicle membrane. On the membrane the permeable water flux gives rise to
-a difference between the fluid velocity ${\uu}({\xx}\in \gamma)$ and the
-membrane velocity $\dot{\xx}$~\cite{yao-mor2017}:
+water) suspended in a viscous fluid (Figure~\ref{fig:sketch}), and we
+let $\gamma$ denote the membrane boundary. We let
+$\alpha=4\pi A/L^2$ be the vesicle's reduced area where $A$ is its area
+and $L$ is its length. To focus on the effect of water flow on vesicle
+hydrodynamics in various conditions, we assume the fluid is the same
+inside and outside the vesicle membrane. On the membrane the permeable
+water flux gives rise to a difference between the fluid velocity
+${\uu}({\xx}\in \gamma)$ and the membrane velocity
+$\dot{\xx}$~\cite{yao-mor2017}:
 \begin{align}
@@
 \end{align}
-where $\gamma$ denotes the membrane boundary with an outward normal
-$\nn$ (Figure~\ref{fig:sketch}), $k_w$ is the water permeability, $R$ is
-the ideal gas constant, $T$ is the temperature ($^{\circ}$K), $\triangle
-c$ is contrast in a solute concentration (mol/volume), and
-$\ff_\mathrm{mem}$ is the membrane stress that consists of both bending
-$ \ff_\mathrm{ben}= -k_b \xx_{ssss}$ and tension
-$\ff_\mathrm{ten}=(\sigma \xx_s)_s$ ($s$ is the arclength along the
-membrane, see Supplementary Material). Using $k_w\sim 10^{-12}$
-m$^2$s/kg (typical of mammalian cell membranes~\cite{LiMoriSun2015_PRL})
-and an osmolarity $\triangle c = 0.1$ mol/L (consistent with the osmotic
-forces in vesicle aspiration
+where $\nn$ is the outward normal (Figure~\ref{fig:sketch}), $k_w$ is
+the water permeability, $R$ is the ideal gas constant, $T$ is the
+temperature ($^{\circ}$K), $\triangle c$ is contrast in a solute
+concentration (mol/volume), and $\ff_\mathrm{mem}$ is the membrane
+stress that consists of both bending $ \ff_\mathrm{ben}= -k_b
+\xx_{ssss}$ and tension $\ff_\mathrm{ten}=(\sigma \xx_s)_s$ ($s$ is the
+arclength along the membrane, see Supplementary Material). Using
+$k_w\sim 10^{-12}$ m$^2$s/kg (typical of mammalian cell
+membranes~\cite{LiMoriSun2015_PRL}) and an osmolarity $\triangle c =
+0.1$ mol/L (consistent with the osmotic forces in vesicle aspiration
 experiments~\cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the corresponding
@@
 \section*{Effects of membrane water permeability}
-We consider a single semipermeable vesicle in familiar configurations to
+We consider a single semipermeable vesicle, with dimensionless
+permeability coefficient $\beta$, in familiar configurations to
 highlight the effects of membrane water permeability. In free space we
@@
 For vesicles in a narrow microfluidic channel, the typical time scale is
-milliseconds~\cite{abk-fai-sto2006}. Our simulations show that strong
+milliseconds~\cite{abk-fai-sto2006} \todo[inline]{Howard talked about
+this statement not always being true}. Our simulations show that strong
 confinement can lead to amplification of water permeability at such
@@
   \ifTikz
-  \input{figures/relaxationComposite.tikz}
+  \input{figures/shearComposite.tikz}
   \else
-  \includegraphics{figures/relaxationComposite.pdf}
+  \includegraphics{figures/shearComposite.pdf}
   \fi
-  \caption{\label{fig:relaxationComposite} (a): Snapshots of four
-  semipermeable vesicles with $\beta = 10^{-3}$ submerged in a quiescent
-  flow. The red regions correspond to influx and the blue regions
-  correspond to efflux. In all cases, the vesicle reaches a steady state
-  circular shape. (b): The reduced area of each of the simulations. The
-  particular snapshots in (a) occur at the marks along the curve.}
+  \caption{\label{fig:shearComposite} (a) The reduced area of a
+  semipermeable vesicle with $\beta = 10^{-3}$ initialized with four
+  different reduced areas in a shear flow with two different flow rates.
+  (b) The steady state shape of a semipermeable vesicle with varying
+  flow rates and semipermeability rates. The circled vesicles correspond
+  to the simulations in part (a). \todo[inline]{Runs at smallest value
+  of $\beta$ are being redone.}}
 \end{figure*}
-In a quiescent flow, a semipermeable vesicle in free space can be
-quantified in terms of its area dynamics and its transition to the
-equilibrium shape. Our analysis in Supplementary Material shows that a
-semipermeable vesicle relaxes to a circle at a rate that is proportional
-to $\beta$, and the steady state tension is $\Lambda = 2\pi^2/L^2$. Our
-analysis further shows that the time for a semipermeable vesicle to
-deviate from its initial reduced area and to reach its steady state is
-proportional to $\beta^{-1}$. For this reason, our numerical results are
-reported in terms of the scaled time $\beta t$.
+In the absence of a background flow, a semipermeable vesicle in free
+space can be quantified in terms of its area dynamics and its transition
+to the equilibrium shape. Our analysis in Supplementary Material shows
+that a semipermeable vesicle relaxes to a circle at a rate that is
+proportional to $\beta$, and the steady state tension is $\Lambda =
+2\pi^2/L^2$. Our analysis further shows that the time for a
+semipermeable vesicle to deviate from its initial reduced area and to
+reach its steady state is proportional to $\beta^{-1}$. For this reason,
+our numerical results are reported in terms of the scaled time $\beta
+t$.
 
@@
 \subsection*{Planar Shear Flow}
-\begin{figure}[htp]
-  \centering
-  \ifTikz
-  \input{figures/shearComposite.tikz}
-  \else
-  \includegraphics{figures/shearComposite.pdf}
-  \fi
-  \caption{\label{fig:shearComposite} (a): The reduced area of a
-  semipermeable vesicle with $\beta = 10^{-3}$ initialized with four
-  different reduced areas in a shear flow with two different flow rates.
-  (b): The steady state shape of a semipermeable vesicle with varying
-  flow rates and semipermeability rates. The circled vesicles correspond
-  to the simulations in part (a).}
-\end{figure}
 
@@
   \fi
-  \caption{\label{fig:parabolicComposite} (a): The steady state shape of
+  \caption{\label{fig:parabolicComposite} (a) The steady state shape of
   a semipermeable vesicle submerged in a Poiseuille flow with varying
   initial reduced areas and flow rates. The red regions correspond to
-  influx and the blue regions correspond to efflux. (b): The steady
+  influx and the blue regions correspond to efflux. (b) The steady
   state vertical displacement for four different flow velocities. The
-  steady state shapes are superimposed. (c): The reduced area of the
-  slipper formed with the flow rate of $800 \mu$m/s. (d): The vesicle
+  steady state shapes are superimposed. (c) The reduced area of the
+  slipper formed with the flow rate of $800 \mu$m/s. (d) The vesicle
   shape shown with the background imposed flow. The channel width is
@@
   \fi
-  \caption{\label{fig:stenosisComposite} (a): A semipermeable vesicle
+  \caption{\label{fig:stenosisComposite} (a) A semipermeable vesicle
   passing through a constricted geometry similar to the experimental
-  device in~\cite{abk-fai-sto2006}. (b): A semipermeable vesicle passing
-  through a constricted geometry that is over five times longer. (c):
+  device in~\cite{abk-fai-sto2006}. (b) A semipermeable vesicle passing
+  through a constricted geometry that is over five times longer. (c)
   The excess pressure of an impermeable and semipermeable vesicle in the
-  short geometry in (a). (d): The reduced area of the semipermeable
+  short geometry in (a). (d) The reduced area of the semipermeable
    vesicles in the geometries in (a) and (b) as a function of the
-  vesicles' center of mass. The $x$-axis is scaled by $1/L$ where $L$ is
-  half the length of the constriction. (e) The reduced area of the
-  semipermeable vesicles in the geometries in (a) and (b) as a function
-  of time. The time axis is scaled by $1/t_R$ where $t_R$ is the
-  residency time. In parts (c) and (d), the dashed lines correspond to
-  the locations of the inlet and outlet. In part (e), the dashed lines
-  correspond to the times that the vesicle enters and exits the
-  constriction. The colored vesicles show the tension distribution in
-  N/m of the circled vesicles. Throughout the entire simulation, these
-  vesicle configurations have the largest tension.}
+   vesicles' center of mass. In (c) and (d), the $x$-axis is scaled by
+   $1/L$ where $L$ is half the length of the constriction. (e) The
+   reduced area of the semipermeable vesicles in the geometries in (a)
+   and (b) as a function of time. The time axis is scaled by $1/t_R$
+   where $t_R$ is the residency time. In parts (c) and (d), the dashed
+   lines correspond to the locations of the inlet and outlet. In part
+   (e), the dashed lines correspond to the times that the vesicle enters
+   and exits the constriction. The colored vesicles show the tension
+   distribution in N/m of the circled vesicles. Throughout the entire
+   simulation, these vesicle configurations have the largest tension.
+   \todo[inline]{Figure out the oscillations in excess pressure}}
 \end{figure*}
@@
   velocity vs.~time. Permeability rate is $\beta = 10^{-3}$ and maximum
-  velocity is $18\mu$m/s. (a): A semipermeable vesicle passing through
-  six periods of the contracting geometry. (b): The reduced area with
-  the marks representing shapes in (a). (c): The vesicle velocity with
+  velocity is $18\mu$m/s. (a) A semipermeable vesicle passing through
+  six periods of the contracting geometry. (b) The reduced area with
+  the marks representing shapes in (a). (c) The vesicle velocity with
   the marks representing shapes in (a). In (b) and (c), the bottom
@@
   N/m of the circled vesicles. Throughout the entire simulation, these
-  vesicle configurations have the largest tension.}
+  vesicle configurations have the largest tension.\todo[inline]{Make the
+  time steps equispaced and the values of $x$ non-uniform. Reverse their
+  orders between to and bottom.}}
 \end{figure}

### 2020-12-31 vesicle_code/docs/permeableVes/makefigs/shear1Ves/shearPhase2.m

@@ -104,7 +104,7 @@ chis = {'1e-1','1e-0.5','1e0','1e0.5','1e1','1e1.5','1e2'};
 
 fid = fopen('data.dat','w');
 %for j = 1:numel(file)
-for j = 15:35
+for j = 8:42
   disp(j)
   [posx,posy,~,~,~,~,~,~,n,~] = loadFile(file{j});
 % some files did not print correctly to file becuase they were either
@@ -127,6 +127,7 @@ for j = 15:35
 
   str = ['%% beta = ',betas{ceil(j/7)},...
       ',shear rate = ',chis{mod(j-1,7)+1},'\n'];
+  disp(str)
   fprintf(fid,str,'%s');
   str = '\\addplot[red,line width=0.5pt] coordinates{\n';
   fprintf(fid,str,'%s');

### 2021-01-01 vesicle_code/docs/permeableVes/main.tex
fixed up fig 2 and worked on 3

@@
   \caption{\label{fig:relaxationComposite} (a) Snapshots of four
-  semipermeable vesicles with $\beta = 10^{-3}$ submerged in a fluid
-  with no background flow flow. Time goes from left to right. The red
-  regions correspond to influx and the blue regions correspond to
+  semipermeable vesicles with $\beta = 5 \times 10^{-7}$ submerged in a
+  fluid with no background flow flow. Time goes from left to right. The
+  red regions correspond to influx and the blue regions correspond to
   efflux. In all cases, the vesicle reaches a steady state circular
-  shape. (b) The reduced area of each of the simulations. The
-  particular snapshots in (a) occur at the marks along the curve.}
+  shape. (b) The reduced area of each of the simulations. The particular
+  snapshots in (a) occur at the marks along the curve.}
 \end{figure*}
@@
 
-Between $t=10$ seconds and $t=10$ minutes, the intermediate shapes of
+Between $t=50$ seconds and $t=50$ minutes, the intermediate shapes of
 semipermeable vesicles resemble the shape of an impermeable vesicle.

### 2021-01-01 vesicle_code/examples/output/makeImages.m

@@ -19,13 +19,13 @@ if 0
   options.marker = true;
 end
 
-if 1
+if 0
 %  file = '~/projects/brinkman/vesicle_code/results/PNAS_runs/stenosis/shortConstriction_beta1em3/choke1VesData.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/PNAS_runs/stenosis/longConstriction_ra065_beta1em3/choke1VesData.bin';
 %file = '~/projects/brinkman/vesicle_code/results/choke1VesLong/beta1em3RA0p25/choke1VesData.bin';
 %file = '~/projects/brinkman/vesicle_code/results/choke1VesLong/beta1em3Scale1p44_kappa1e0_farfield5e2_offcenter/choke1VesData.bin';
 %file = '~/Dropbox/Adhesion/PermeableV/choke1Ves/choke1VesBData.bin';
-file = 'choke1VesData.bin';
+file = 'choke1VesBData.bin';
 
   options.marker = false;
 %file = '~/projects/brinkman/vesicle_code/results/choke1VesLong/beta1em3RA0p20/choke1VesData.bin';
@@ -132,9 +132,9 @@ if 0
   ax = [-2 2 -2 2];
   options.confined = false;
 end
-if 0
-  file = 'shear1VesAData.bin';
-%  file = '~/projects/brinkman/vesicle_code/results/shear1Ves/Chi1p0e1_ra065_beta1p0em3/shear1VesData.bin';
+if 1
+  file = 'shear1VesBData.bin';
+%  file = '~/projects/brinkman/vesicle_code/results/shear1Ves/Chi1p0em1_ra065_beta1p0em4p5/shear1VesData.bin.old';
 %  file = '~/projects/brinkman/vesicle_code/results/PNAS_runs/shear/Chi1p0e0_ra075_beta1p0em3/shear1VesData.bin';
   ax = [-5 5 -5 5];
   options.confined = false;

### 2021-01-03 vesicle_code/docs/permeableVes/main.tex
updated shear example

@@
   different reduced areas in a shear flow with two different flow rates.
-  (b) The steady state shape of a semipermeable vesicle with varying
-  flow rates and semipermeability rates. The circled vesicles correspond
-  to the simulations in part (a). \todo[inline]{Runs at smallest value
-  of $\beta$ are being redone.}}
+  (b) The steady state shape of a vesicle with varying flow rates and
+  semipermeability rates. The circled vesicles correspond to the
+  simulations in part (a).}
 \end{figure*}

### 2021-01-03 vesicle_code/examples/output/makeImages.m

@@ -19,7 +19,7 @@ if 0
   options.marker = true;
 end
 
-if 0
+if 1
 %  file = '~/projects/brinkman/vesicle_code/results/PNAS_runs/stenosis/shortConstriction_beta1em3/choke1VesData.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/PNAS_runs/stenosis/longConstriction_ra065_beta1em3/choke1VesData.bin';
 %file = '~/projects/brinkman/vesicle_code/results/choke1VesLong/beta1em3RA0p25/choke1VesData.bin';
@@ -132,8 +132,8 @@ if 0
   ax = [-2 2 -2 2];
   options.confined = false;
 end
-if 1
-  file = 'shear1VesBData.bin';
+if 0
+  file = 'shear1VesDData.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/shear1Ves/Chi1p0em1_ra065_beta1p0em4p5/shear1VesData.bin.old';
 %  file = '~/projects/brinkman/vesicle_code/results/PNAS_runs/shear/Chi1p0e0_ra075_beta1p0em3/shear1VesData.bin';
   ax = [-5 5 -5 5];

### 2021-01-04 vesicle_code/docs/permeableVes/main.tex
rearranged figures a bit
yny

@@
 % Please add a significance statement to explain the relevance of your work
-\significancestatement{Authors must submit a 120-word maximum statement
-about the significance of their research paper written at a level
-understandable to an undergraduate educated scientist outside their
-field of speciality. The primary goal of the significance statement is
-to explain the relevance of the work in broad context to a broad
-readership. The significance statement appears in the paper itself and
-is required for all research papers.}
+\significancestatement{This work focuses on effects of membrane permeability to water on the hydrodynamics of a vesicle (self-enclosing lipid bilayer membrane) under flows and/or confinement.
+Without membrane poration or rupture, we use direct numerical simulations to illustrate that over sufficiently long time the water permeability does affect the equilibrium vesicle shapes in open space.
+Under confinement, we show that water permeability may be quickly amplified to induce significant change in shape as the vesicle goes through a closely-fit long channel and a narrow slit.
+These results provide a quantitative measure of membrane permeability to water in terms of vesicle inflation/deflation under load.
+%
+%Authors must submit a 120-word maximum statement
+%about the significance of their research paper written at a level
+%understandable to an undergraduate educated scientist outside their
+%field of speciality. The primary goal of the significance statement is
+%to explain the relevance of the work in broad context to a broad
+%readership. The significance statement appears in the paper itself and
+%is required for all research papers.
+%
+}
 
@@
 Lipid bilayer membranes have a native (albeit small) permeability for
-water molecules. Provided that the bilayer structure stays intact (no membrane poration or rupture) under load, the water influx/efflux is
+water molecules. Under load, as long as the bilayer membrane stays intact (no poration or rupture), the water influx/efflux is
 often assumed negligible in the absence of a osmolarity pressure across the membrane. 
@@
 
-\begin{figure}[htp]
+\begin{figure*}[htp]
   \centering
-  \includegraphics[width=0.5\textwidth]{figures/schematic.pdf}
+  \includegraphics[width=0.9\textwidth]{figures/schematic.pdf}
   \caption{\label{fig:sketch} Schematics showing the effects of
@@
   membrane.  The slipper in (a) is the steady-state shape of a
-  semipermeable vesicle in a Poiseuille flow.}
-\end{figure}
+  semipermeable vesicle in a Poiseuille flow. \todo[inline]{Fix font
+  size of block (d)}}
+\end{figure*}
 
@@
 
-%\begin{figure*}[htp]
-%  \ifTikz
-%  \input{figures/stenosisComposite.tikz}
-%  \else
-%  \includegraphics{figures/stenosisComposite.pdf}
-%  \fi
-%  \caption{\label{fig:stenosisComposite} (a): A semipermeable vesicle
-%  passing through a constricted geometry similar to the experimental
-%  device in~\cite{abk-fai-sto2006}. (b): A semipermeable vesicle passing
-%  through a constricted geometry that is over five times longer. (c):
-%  The excess pressure of an impermeable and semipermeable vesicle in the
-%  short geometry in (a). (d): The reduced area of the semipermeable
-%  vesicles in the geometries in (a) and (b) as a function of the
-%  vesicles' center of mass. The $x$-axis is scaled by $1/L$ where $L$ is
-%  half the length of the constriction. (e) The reduced area of the
-%  semipermeable vesicles in the geometries in (a) and (b) as a function
-%  of time. The time axis is scaled by $1/t_R$ where $t_R$ is the
-%  residency time. In parts (c) and (d), the dashed lines correspond to
-%  the locations of the inlet and outlet. In part (e), the dashed lines
-%  correspond to the times that the vesicle enters and exits the
-%  constriction. The colored vesicles show the tension distribution in
-%  N/m of the circled vesicles. Throughout the entire simulation, these
-%  vesicle configurations have the largest tension.}
-%\end{figure*}
-%
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection*{Semipermeable Vesicle in a Contracting Geometry}
-\begin{figure}[htp]
+
+Squeezing a cell or an elastic vesicle through a slit in microfluidics
+has gained popularity for its application in stress-induced release of
+macromolecules~\cite{ShareiEtAl2013_PNAS, Pak2015_PNAS,
+ZhangShenHoganBarakatMisbah2018_BJ, LuoBai2019_PoF}. Red blood cells go
+through submicron slits many times during their lifetime, and such
+process selects healthy, flexible red blood cells to
+survive~\cite{wu2015critical,LuPeng2019_PoF}. Here we investigate the
+role of membrane permeability to water when a semipermeable vesicle is
+squeezed through a contracting microfluidic channel similar
+to~\cite{wu2015critical}, where the width of the channel gradually
+decreases from $18 \mu$m to $1.8 \mu$m. The channel then immediately
+opens again to $18 \mu$m (Figure~\ref{fig:contractingComposite}). A
+Poiseuille flow is imposed at the inlet and outlet with a constant
+maximum flow rate of $U_{\max}$. We initialize a semipermeable vesicle
+with $\alpha = 0.65$ that spans $10 \mu$m of the total channel width and
+investigate the effects of the membrane permeability to water and the
+maximum flow velocity on whether a vesicle can successfully pass through
+the slit. We color the vesicle according to the sign of its flux---red
+for influx and blue for efflux.
+
+In Figures~\ref{fig:contractingComposite}a
+and~\ref{fig:contractingComposite}b, we plot snapshots of vesicles with
+different permeability $\beta$. Figure~\ref{fig:contractingComposite}c
+shows the corresponding reduced area as a function of the vesicles'
+location. We observe that if the permeability is sufficiently large, the
+vesicle inflates gradually over seconds before it reaches the neck, and
+then it quickly deflates within a fraction of a second. However, if the
+semipermeability rate is too low, the vesicle is too large when it
+reaches the narrowest part of the channel, and it is unable to pass. In
+Figures~\ref{fig:contractingComposite}d
+and~\ref{fig:contractingComposite}e, we plot snapshots of vesicles with
+different imposed maximum velocities, and
+Figure~\ref{fig:contractingComposite}f shows the reduced area as a
+function of the vesicles' location. At low velocities, the vesicle
+inflates similar to the unbounded parabolic flow example, and it is
+unable to pass through the contraction. However, higher flow rates
+result in additional deflation and the vesicle passes through the
+contraction.
+
+To understand the effects of water permeability on cells that repeatedly
+go through micro-capillary vessels or sub-micron slits, we construct a
+contracting geometry (see Figures~\ref{fig:contractingComposite2}) to
+simulate a vesicle passing through the contracting geometry six times.
+In Figure~\ref{fig:contractingComposite2}b, we show that the vesicle
+deflates each time it passes through the contraction followed by a
+gradual inflation (over seconds). The total area loss over the history
+of the vesicle is almost 50\%. In
+Figure~\ref{fig:contractingComposite}c, we show the vesicle velocity as
+a function of the vesicle's center of mass. As the vesicle passes
+through the contraction, it first accelerates until it reaches the neck
+where it abruptly decelerates to go through the contraction. The
+variation of the reduced area and velocity with respect to time are also
+shown in Figure~\ref{fig:contractingComposite2}.
+\begin{figure}[hbp]
   \centering
@@
 \end{figure}
-
-Squeezing a cell or an elastic vesicle through a slit in microfluidics
-has gained popularity for its application in stress-induced release of
-macromolecules~\cite{ShareiEtAl2013_PNAS, Pak2015_PNAS,
-ZhangShenHoganBarakatMisbah2018_BJ, LuoBai2019_PoF}. Red blood cells go
-through submicron slits many times during their lifetime, and such
-process selects healthy, flexible red blood cells to
-survive~\cite{wu2015critical,LuPeng2019_PoF}. Here we investigate the
-role of membrane permeability to water when a semipermeable vesicle is
-squeezed through a contracting microfluidic channel similar
-to~\cite{wu2015critical}, where the width of the channel gradually
-decreases from $18 \mu$m to $1.8 \mu$m. The channel then immediately
-opens again to $18 \mu$m (Figure~\ref{fig:contractingComposite}). A
-Poiseuille flow is imposed at the inlet and outlet with a constant
-maximum flow rate of $U_{\max}$. We initialize a semipermeable vesicle
-with $\alpha = 0.65$ that spans $10 \mu$m of the total channel width and
-investigate the effects of the membrane permeability to water and the
-maximum flow velocity on whether a vesicle can successfully pass through
-the slit. We color the vesicle according to the sign of its flux---red
-for influx and blue for efflux.
-
-In Figures~\ref{fig:contractingComposite}a
-and~\ref{fig:contractingComposite}b, we plot snapshots of vesicles with
-different permeability $\beta$. Figure~\ref{fig:contractingComposite}c
-shows the corresponding reduced area as a function of the vesicles'
-location. We observe that if the permeability is sufficiently large, the
-vesicle inflates gradually over seconds before it reaches the neck, and
-then it quickly deflates within a fraction of a second. However, if the
-semipermeability rate is too low, the vesicle is too large when it
-reaches the narrowest part of the channel, and it is unable to pass. In
-Figures~\ref{fig:contractingComposite}d
-and~\ref{fig:contractingComposite}e, we plot snapshots of vesicles with
-different imposed maximum velocities, and
-Figure~\ref{fig:contractingComposite}f shows the reduced area as a
-function of the vesicles' location. At low velocities, the vesicle
-inflates similar to the unbounded parabolic flow example, and it is
-unable to pass through the contraction. However, higher flow rates
-result in additional deflation and the vesicle passes through the
-contraction.
-
-To understand the effects of water permeability on cells that repeatedly
-go through micro-capillary vessels or sub-micron slits, we construct a
-contracting geometry (see Figures~\ref{fig:contractingComposite2}) to
-simulate a vesicle passing through the contracting geometry six times.
-In Figure~\ref{fig:contractingComposite2}b, we show that the vesicle
-deflates each time it passes through the contraction followed by a
-gradual inflation (over seconds). The total area loss over the history
-of the vesicle is almost 50\%. In
-Figure~\ref{fig:contractingComposite}c, we show the vesicle velocity as
-a function of the vesicle's center of mass. As the vesicle passes
-through the contraction, it first accelerates until it reaches the neck
-where it abruptly decelerates to go through the contraction. The
-variation of the reduced area and velocity with respect to time are also
-shown in Figure~\ref{fig:contractingComposite2}.
 

### 2021-01-04 vesicle_code/docs/permeableVes/main.tex
language to signiicance statement

@@
 % Please add a significance statement to explain the relevance of your work
-\significancestatement{This work focuses on effects of membrane permeability to water on the hydrodynamics of a vesicle (self-enclosing lipid bilayer membrane) under flows and/or confinement.
-Without membrane poration or rupture, we use direct numerical simulations to illustrate that over sufficiently long time the water permeability does affect the equilibrium vesicle shapes in open space.
+\significancestatement{This work focuses on effects of membrane
+permeability to water on the hydrodynamics of a vesicle (self-enclosing
+lipid bilayer membrane) under flows and confinement. Without membrane
+poration or rupture, we use direct numerical simulations to illustrate
+that over sufficiently long time the water permeability affects the equilibrium vesicle shapes in open space.
 Under confinement, we show that water permeability may be quickly amplified to induce significant change in shape as the vesicle goes through a closely-fit long channel and a narrow slit.
@@
 temperature, lipid composition~\cite{OlbrichRawiczNeedhamEtAl2000_BJ},
-%\todo[inline]{Same reference twice?} 
-and the hydration of
-the membrane~\cite{MarrinkBerendsen1994_JPhysChem}. In the red blood
-cell membrane, aquaporin-1 channels give rise to a much higher water
-permeability of approximately $1.8\times 10^{-2}$ cm/s in
+and the hydration of the membrane~\cite{MarrinkBerendsen1994_JPhysChem}.
+In the red blood cell membrane, aquaporin-1 channels give rise to a much
+higher water permeability of approximately $1.8\times 10^{-2}$ cm/s in
 erythrocytes~\cite{YangMaVerkman2001_JBC} while the intrinsic water
@@
   membrane.  The slipper in (a) is the steady-state shape of a
-  semipermeable vesicle in a Poiseuille flow. \todo[inline]{Fix font
-  size of block (d)}}
+  semipermeable vesicle in a Poiseuille flow.}
 \end{figure*}

### 2021-01-04 vesicle_code/docs/permeableVes/main.tex
fixed fig 7
yny

@@
 \begin{abstract}
-Lipid bilayer membranes have a native (albeit small) permeability for
-water molecules. Under load, as long as the bilayer membrane stays intact (no poration or rupture), the water influx/efflux is
-often assumed negligible in the absence of a osmolarity pressure across the membrane. 
-%
-In this work we focus on physical regimes where the membrane tension is below the critical value for membrane poration, and use boundary integral simulations to
-investigate the effects of native water permeability on the hydrodynamics of
-a vesicle under various flows and confinement configurations. 
-%
-Coupling the membrane permeability with membrane elastic stress, tension, and
-mechanical stress in the framework of Helfrich free energy, we
-illustrate that, in the absence of an osmotic stress gradient, a giant
-unilamellar vesicle may be significantly affected by water
-influx/efflux over a sufficiently long time or under a strong
-confinement. Our simulation results quantify the conditions for water
-permeation to be negligible in terms of the time scales, flow strength
-of an external flow, and degree of confinement. These results shed
-light on how microfluidic confinement can be utilized to estimate
-membrane permeability.
-%
-%osmotic stress gradient 
-%We describe a mathematical model for a semipermeable vesicle and derive
-%  a boundary integral equation formulation for simulating its
-%  hydrodynamics.  
-%
-%Please provide an abstract of no more than 250 words in a single paragraph.
+Lipid bilayer membranes have a native (albeit small) permeability for water molecules. Under an external load 
+ the water influx/efflux is often assumed  negligible in the absence of osmolarity, provided 
+that the lipid bilayer membrane remains intact (no poration or rupture),. 
+%
+In this work we use boundary integral simulations to investigate the effects
+of native water permeability on the vesicle hydrodynamics due to a mechanical load,  such as the viscous stress
+from an external flow deforming a vesicle in free space or pushing the vesicle through a confinement. Coupling the 
+membrane permeability with membrane elastic stress and tension in the framework of Helfrich free energy, we 
+illustrate that, in the absence of an osmotic stress gradient, a giant unilamellar vesicle may be affected by water 
+influx/efflux over a sufficiently long time or under a strong confinement. Our simulation results quantify the conditions 
+for water permeation to be negligible in terms of the time scales, flow strength and confinement. These results shed 
+light on how microfluidic confinement can be utilized to estimate membrane permeability.
+%
+%Lipid bilayer membranes have a native (albeit small) permeability for
+%water molecules. Under load, as long as the bilayer membrane stays intact (no poration or rupture), the water influx/efflux is
+%often assumed negligible in the absence of a osmolarity pressure across the membrane. 
+%%
+%In this work we focus on physical regimes where the membrane tension is below the critical value for membrane poration, and use boundary integral simulations to
+%investigate the effects of native water permeability on the hydrodynamics of
+%a vesicle under various flows and confinement configurations. 
+%%
+%Coupling the membrane permeability with membrane elastic stress, tension, and
+%mechanical stress in the framework of Helfrich free energy, we
+%illustrate that, in the absence of an osmotic stress gradient, a giant
+%unilamellar vesicle may be significantly affected by water
+%influx/efflux over a sufficiently long time or under a strong
+%confinement. Our simulation results quantify the conditions for water
+%permeation to be negligible in terms of the time scales, flow strength
+%of an external flow, and degree of confinement. These results shed
+%light on how microfluidic confinement can be utilized to estimate
+%membrane permeability.
+%%
+%%osmotic stress gradient 
+%%We describe a mathematical model for a semipermeable vesicle and derive
+%%  a boundary integral equation formulation for simulating its
+%%  hydrodynamics.  
+%%
+%%Please provide an abstract of no more than 250 words in a single paragraph.
 Abstracts should explain to the general reader the major contributions of the article.
@@
   N/m of the circled vesicles. Throughout the entire simulation, these
-  vesicle configurations have the largest tension.\todo[inline]{Make the
-  time steps equispaced and the values of $x$ non-uniform. Reverse their
-  orders between to and bottom.}}
+  vesicle configurations have the largest tension.}
 \end{figure}

### 2021-01-07 shuwang_rewrite/curve.m
added tension for relaxatin examples

@@ -71,7 +71,8 @@ end
 
 if nargout>2  % if user requires curvature
   IK = o.modes(N);
-  [DDx,DDy] = oc.getDXY([Dx,Dy]);
+  [DDx,DDy] = o.getDXY([Dx,Dy]);
+  DDx = DDx(:); DDy = DDy(:);
   curvature = (Dx.*DDy - Dy.*DDx)./(jacobian.^3);
 end
 % curvature of the curve
@@ -364,11 +365,11 @@ function X = recon(o,N,x0,y0,L,theta)
 IK = o.modes(N);
 x = x0 + L*o.intFT(cos(theta),IK);%/2/pi;
 y = y0 + L*o.intFT(sin(theta),IK);%/2/pi;
-figure(1);clf;
-%semilogy(abs(fftshift(fft(theta-2*pi*(0:N-1)'/N))))
-semilogy(abs(fftshift(fft(sin(theta)))),'r')
-%semilogy(abs(fftshift(fft(y))),'r')
-pause
+%figure(1);clf;
+%%semilogy(abs(fftshift(fft(theta-2*pi*(0:N-1)'/N))))
+%semilogy(abs(fftshift(fft(sin(theta)))),'r')
+%%semilogy(abs(fftshift(fft(y))),'r')
+%pause
 
 X = o.setXY(x,y);
 
@@ -446,6 +447,7 @@ end %rmLinearPart
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 function fntheta = fthetaim(o,ves,un,ut,fdotn)
+
 N = ves.N;
 L = ves.L;  
 theta = ves.theta;
@@ -465,12 +467,22 @@ var2 = fft(theta-[2*pi*(0:N-1)]'/N);
 %plot(ut)
 %pause
 fntheta = real(ifft(var1 - rlen.*var2));
+%clf;
+%figure(1); hold on
+%figure(1); clf
+%semilogy(abs(fftshift(fft(fntheta))),'r*')
+%semilogy(abs(real(fftshift(fft(fntheta)))),'bo')
+%pause
 %figure(3)
 %clf;
 %semilogy(abs(fftshift(fft(un))))
 %hold on
 %Krasney filter applied to smooth out spurious high frequency terms
+%clf;
+%semilogy(abs(fftshift(fft(fntheta))),'bo')
[…]

### 2021-01-07 vesicle_code/docs/permeableVes/main.tex
added tension for relaxatin examples
yny

@@
 \begin{abstract}
-Lipid bilayer membranes have a native (albeit small) permeability for water molecules. Under an external load 
- the water influx/efflux is often assumed  negligible in the absence of osmolarity, provided 
-that the lipid bilayer membrane remains intact (no poration or rupture),. 
+Lipid bilayer membranes have a native (albeit small) permeability for water molecules. Under an external load, a lipid membrane deforms and its
+water influx/efflux is often assumed  negligible in the absence of osmolarity, provided 
+that the bilayer structure stays intact and does not suffer from poration or rupture. 
 %
@@
 of native water permeability on the vesicle hydrodynamics due to a mechanical load,  such as the viscous stress
-from an external flow deforming a vesicle in free space or pushing the vesicle through a confinement. Coupling the 
+from an external flow deforming a vesicle membrane in free space or pushing it through a confinement. Coupling the 
 membrane permeability with membrane elastic stress and tension in the framework of Helfrich free energy, we 

### 2021-01-10 vesicle_code/src/capsules.m
added tension plots

@@ -313,6 +313,11 @@ tt.Galpert = op.stokesSLmatrix(vesicle);
 % single-layer potential
 tt.D = op.stokesDLmatrix(vesicle);
 % double-layer potential
+if tt.confined
+  tt.wallDLP = tt.opWall.stokesDLmatrix(walls);
+  tt.wallN0 = tt.opWall.stokesN0matrix(walls);
+  tt.bdiagWall = tt.wallsPrecond(walls);
+end
 
 if tt.near
   if tt.confined
@@ -436,7 +441,7 @@ end
 %plot(tt.sigDenMatVec(tt.preconditionerBD(rhs),vesicle,walls) - rhs)
 %pause
 
-z = tt.sigDenMatVec(rhs,vesicle,walls);
+%z = tt.sigDenMatVec(rhs,vesicle,walls);
 % DEBUG
 
 [sigDen,F,R,I] = gmres(@(X) tt.sigDenMatVec(X,vesicle,walls),rhs,...

### 2021-01-10 vesicle_code/docs/permeableVes/main.tex
added tension plots
yny

@@
 % of a semipermeable vesicle in two dimensions.
-In microfluidic experiments, it is challenging to keep a freely
-suspended red blood cell or vesicle in a steady flow for more than a few
-hours. It is also difficult to quantify the vesicle area/volume ratio
-accurately.  Using numerical simulations we can quantify the effects of
-water permeability on the hydrodynamics of a vesicle under mechanical
-stresses. Vesicles (self-enclosed lipid bilayer membranes) have been
+
+Vesicles (self-enclosed lipid bilayer membranes) have been
 used as a model system to study reshaping, remodeling, and scission of
@@
 stress when the membrane deformation is large~\cite{LiMoriSun2015_PRL,
-yao-mor2017}. In the absence of an osmotic gradient, we first show that
+yao-mor2017}.
+
+In microfluidic experiments, it is challenging to keep a freely
+suspended red blood cell or vesicle in a steady flow for more than a few
+hours. It is also difficult to quantify the vesicle area/volume ratio
+accurately.  Using numerical simulations we can quantify the effects of
+water permeability on the hydrodynamics of a vesicle under mechanical
+stresses. 
+In the absence of an osmotic gradient, we first show that
 a freely suspended semipermeable vesicle behaves differently from an
@@
 %the permeability may lead to change in area in less than a second???}
-For vesicles in a narrow microfluidic channel, the typical time scale is
-milliseconds~\cite{abk-fai-sto2006} \todo[inline]{Howard talked about
-this statement not always being true}. Our simulations show that strong
+For vesicles in a narrow microfluidic channel, the experiments usually do not last longer than a few minutes~\cite{abk-fai-sto2006}.
+%\todo[inline]{Howard talked aboutthis statement not always being true}. 
+Our simulations show that strong
 confinement can lead to amplification of water permeability at such
@@
 Semipermeability is introduced by modifying the vesicle velocity from
-the standard no-slip condition $\dot{\xx} = \uu(\xx)$. Instead, we
-assume that the flux through the vesicle is proportional to the
-mechanical force~\cite{yao-mor2017}. That is, 
+the standard no-slip condition $\dot{\xx} = \uu(\xx)$. Instead,
+the permeating water flux through the lipid bilayer membrane is proportional to the
+membrane traction~\cite{yao-mor2017}. That is, 
 \begin{align}
@@
 Applying integration by parts, the two integrals agree, and we have
-%\begin{align}
-%  \int_\gamma (\xx \cdot \dot{\nn})\, ds 
-%    = \int_\gamma \left(\xx \cdot \dot{\xx}_s^\perp \right)
-%    = -\int_\gamma \left(\xx^\perp \cdot \dot{\xx}_s\right)\, ds 
-%    = \int_\gamma \left(\xx_s^\perp \cdot \dot{\xx}\right)\, ds 
-%    = \int_\gamma (\dot{\xx} \cdot \nn)\, ds.
-%\end{align}
 \begin{align}
@@
 reaches its steady state which confirms that $\dot{A}(t) = 0$.
+
+\section*{Vesicle Tensions}
+\begin{figure*}[htp]
+  \centering
+  \ifTikz
+    \input{figures/relaxationTensions.tikz}
+  \else
+    \includegraphics{figures/relaxationTensions.pdf}
+  \fi
+  \caption{\label{fig:relaxationTensions} Tension of images in
+  relaxation.}
+\end{figure*}
 

### 2021-01-10 vesicle_code/docs/permeableVes/main.tex
yny

@@
 
-The governing equations are non-dimensionalized by introducing a length
-scale that we take to be $R_0 = 10^{-6}$m. Using a bending stiffness of
-$k_b = 10^{-19}$J and fluid viscosity $5 \times 10^{-2}$kg/ms, we define
-the time scale $\tau = \mu R_0^3/k_b = 0.5s$, the velocity scale $U =
-R_0/\tau = 2\mu$m/s, the pressure scale $P = k_b/R_0^3 = 10^{-1}$Pa, the
-tension scale $Q = k_b/R_0^2 = 10^{-7}$N/m, and the permeability scale
-$W = R_0\mu = 2 \times 10^{-5}$m$^2$s/kg. Another standard dimensionless
-variable in vesicle suspensions is the reduced area $\alpha = 4\pi A/L^2
-\in (0,1]$, where $L$ is the vesicle length and $A$ is its area. The
-length is conserved by the local inextensibility condition, but the area
-is not because of semipermeability. Therefore, the reduced area is
+%The governing equations are non-dimensionalized by introducing a length
+%scale that we take to be $R_0 = 10^{-6}$m. Using a bending stiffness of
+%$k_b = 10^{-19}$J and fluid viscosity $5 \times 10^{-2}$kg/ms, we define
+%the time scale $\tau = \mu R_0^3/k_b = 0.5s$, the velocity scale $U =
+%R_0/\tau = 2\mu$m/s, the pressure scale $P = k_b/R_0^3 = 10^{-1}$Pa, the
+%tension scale $Q = k_b/R_0^2 = 10^{-7}$N/m, and the permeability scale
+%$W = R_0\mu = 2 \times 10^{-5}$m$^2$s/kg. Another standard dimensionless
+%variable in vesicle suspensions is the reduced area $\alpha = 4\pi A/L^2
+%\in (0,1]$, where $L$ is the vesicle length and $A$ is its area. The
+%length is conserved by the local inextensibility condition, but the area
+%is not because of semipermeability. Therefore, the reduced area is
+%dynamic.
+
+The governing equations are non-dimensionalized by using a 
+characteristic length scale $R_0 = 10^{-6}$m, a bending stiffness of
+$k_b = 10^{-19}$J and fluid viscosity $5 \times 10^{-2}$kg/ms. We scale time by $\tau\equiv\mu R_0^3/k_b = 0.5s$, 
+the velocity by $R_0/\tau = 2\mu$m/s, the pressure by $k_b/R_0^3 = 10^{-1}$Pa, 
+tension by $k_b/R_0^2 = 10^{-7}$N/m, and the permeability by $R_0\mu = 2 \times 10^{-5}$m$^2$s/kg. 
+Under this nondimensionalization, a two-dimensional semipermeable vesicle in a viscous fluid is characterized by 
+(a) its reduced area $\alpha = 4\pi A/L^2
+\in (0,1]$, where $L$ is the vesicle length and $A$ is its area, and 
+(b) its permeability $\beta = k_w/W$.
+In two dimensions, the membrane length is conserved by the local inextensibility condition, 
+but the enclosed area is not because of semipermeability. Therefore, the reduced area is
 dynamic.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Vesicle Tensions}
@@
   \fi
-  \caption{\label{fig:relaxationTensions} Tension of images in
+  \caption{\label{fig:relaxationTensions} Tension of vesicles in
   relaxation.}
+\end{figure*}
+
+\begin{figure*}[htp]
+  \centering
+  \ifTikz
+    \input{figures/stenosisTensions.tikz}
+  \else
+    \includegraphics{figures/stenosisTensions.pdf}
+  \fi
+  \caption{\label{fig:stenosisTensions} Tension of vesicles in
+  stenosis.}
 \end{figure*}

### 2021-01-10 vesicle_code/docs/permeableVes/main.tex
yny

@@
 
-We consider a semipermeable vesicle in a planar shear flow
-$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$ with different permeability
-$\beta$ and shear rates $\dot{\gamma}$. When $\beta=0$ (impermeable
+We consider a semipermeable vesicle in a planar shear flow, characterized by the elastic capillary number
+$Ca_E=\dot{\gamma}\tau$, where $\tau$ is the characteristic time scale in the system (see Supplementary Material) and
+$\dot{\gamma}$ is the shear rate of the planar shear flow
+$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$.
+ %with different permeability $\beta$ and shear rates $\dot{\gamma}$. 
+ When $\beta=0$ (impermeable
 case), a vesicle's reduced area and viscosity contrast determine whether
@@
 \in (0,1]$, where $L$ is the vesicle length and $A$ is its area, and 
-(b) its permeability $\beta = k_w/W$.
+(b) its permeability $\beta = k_w/(R_0\mu)$.
 In two dimensions, the membrane length is conserved by the local inextensibility condition, 
@@
 \begin{align}
-  \SS[\ff](\xx) = \frac{1}{4\pi\mu} \int_{\gamma} \left(
+  \SS[\ff](\xx) = \frac{1}{4\pi} \int_{\gamma} \left(
     -\mathbf{I} \log\rho + \frac{\rr \otimes \rr}{\rho^2} \right)
     \ff(\yy) ds_{\yy},
+%  \SS[\ff](\xx) = \frac{1}{4\pi\mu} \int_{\gamma} \left(
+%    -\mathbf{I} \log\rho + \frac{\rr \otimes \rr}{\rho^2} \right)
+%    \ff(\yy) ds_{\yy},
 \end{align}
@@
   + \SS [\ff_\mathrm{mem}](\xx),  \quad
-  \xx_s \cdot \dot{\xx}_s = 0,
+  \xx_s \cdot \dot{\xx}_s = 0.
 \end{align}
-where $\beta = k_w/W$ is the dimensionless water permeability. In
-confined geometries, the far field term $\uu_\infty$ is replaced by a
+%where $\beta = k_w/W$ is the dimensionless water permeability. 
+In confined geometries, the far field term $\uu_\infty$ is replaced by a
 double-layer potential with a density defined on $\partial\Omega$. The

### 2021-01-10 vesicle_code/docs/permeableVes/main.tex
yny

@@
 We consider a semipermeable vesicle in a planar shear flow, characterized by the elastic capillary number
-$Ca_E=\dot{\gamma}\tau$, where $\tau$ is the characteristic time scale in the system (see Supplementary Material) and
+$Ca_\mathrm{E}=\dot{\gamma}\tau$, where $\tau$ is the characteristic time scale in the system (see Supplementary Material) and
 $\dot{\gamma}$ is the shear rate of the planar shear flow
@@
 
-For a variety of semipermeability rates and flow rates, a semipermeable
+For a variety of semipermeability rates and $Ca_\mathrm{E}$, a semipermeable
 vesicle reaches a steady equilibrium as in
@@
 Figure~\ref{fig:shearComposite}(b), where we summarize the steady state
-vesicle shape and its reduced area. We see that the flow rate
+vesicle shape and its reduced area. We see that the capillary number (flow rate)
 significantly affects the final vesicle shape, but the semipermeability

### 2021-01-11 vesicle_code/docs/permeableVes/main.tex
put capillary number in Fig 3 rather than shear rate
fixed capillary number notation
put in pdf for shear composite
yny

@@
 
+\setboolean{displaywatermark}{false}
+
 \begin{document}
@@
 hours. It is also difficult to quantify the vesicle area/volume ratio
-accurately.  Using numerical simulations we can quantify the effects of
+accurately \cite{MinetttiCallensCoupier2008_AppliedOptics}.  Using numerical simulations we can quantify the effects of
 water permeability on the hydrodynamics of a vesicle under mechanical
@@
 We consider a semipermeable vesicle in a planar shear flow, characterized by the elastic capillary number
-$Ca_\mathrm{E}=\dot{\gamma}\tau$, where $\tau$ is the characteristic time scale in the system (see Supplementary Material) and
+$Ca_\mathrm{E}=\dot{\gamma}\tau$, where $\tau$ is the characteristic time scale in the non-dimensionalization (see Supplementary Material) and
 $\dot{\gamma}$ is the shear rate of the planar shear flow

### 2021-01-11 vesicle_code/docs/permeableVes/main.tex
added in shear and stenosis tensions
adding tension plots

--- 2021-01-10 vesicle_code/docs/permeableVes/main.tex
@@
   relaxation.}
+  \todo[inline]{Redo using cline}
+\end{figure*}
+
+\begin{figure*}[hbp]
+  \begin{tikzpicture}[scale=1]
+    \node[inner sep=0pt] at (0,0) {
+    \includegraphics[width=\textwidth]{figures/shearTensions.pdf}
+    };
+    \node at (-8.54,0.6) {(a)};
+    \node at (-6.00,0.6) {(b)};
+    \node at (-3.46,0.6) {(c)};
+    \node at (-0.92,0.6) {(d)};
+    \node at (+1.60,0.6) {(e)};
+    \node at (+4.16,0.6) {(f)};
+    \node at (+6.70,0.6) {(g)};
+  \end{tikzpicture}
+%  \includegraphics[width=\textwidth]{figures/shearTensions.pdf}
+  \caption{\label{fig:shearTensions} Tension of vesicles in
+  shear flow. The semi-permeability constant is $\beta = 10^{-4}$ for
+  all these cases, and the elastic capillary number ranges from
+  $10^{-1}$ to $10^{2}$ as in Figure~\ref{fig:shearComposite}.}
+\end{figure*}
+
+\begin{figure*}[hbp]
+  \centering
+  \begin{tikzpicture}[scale=1]
+    \node[inner sep=0pt] at (0,0) {
+    \includegraphics[width=\textwidth]{figures/parabolicTensions.pdf}
+    };
+    \node at (-8.2,1.5) {(a)};
+    \node at (-3.8,1.5) {(b)};
+    \node at (+0.6,1.5) {(c)};
+    \node at (+5.0,1.5) {(d)};
+  \end{tikzpicture}
+  \caption{\label{fig:parabolicTensions} The steady state tension
+  profile of a semipermeable vesicle with $\beta=10^{-3}$ in a parabolic
+  flow (see Figure~\ref{fig:parabolicComposite}). The flow velocities
+  are (a) 200$\mu$m/s, (b) 400$\mu$m/s, (c) 600$\mu$m/s, and (d)
+  800$\mu$m/s.}
 \end{figure*}
@@
   \centering
-  \ifTikz
-    \input{figures/stenosisTensions.tikz}
-  \else
-    \includegraphics{figures/stenosisTensions.pdf}
-  \fi
+  \begin{tikzpicture}[scale=1]
+    \node[inner sep=0pt] at (0,0) {
+    \includegraphics[width=\textwidth]{figures/stenosisTensions.pdf}
+    };
+    \node at (-8.6,0.7) {(a)};
+    \node at (-1.6,0.7) {(b)};
+  \end{tikzpicture}
   \caption{\label{fig:stenosisTensions} Tension of vesicles in

### 2021-01-12 vesicle_code/docs/permeableVes/main.tex
fixed up fig 2

--- 2021-01-11 vesicle_code/docs/permeableVes/main.tex
@@
   \caption{\label{fig:relaxationComposite} (a) Snapshots of four
-  semipermeable vesicles with $\beta = 5 \times 10^{-7}$ submerged in a
-  fluid with no background flow flow. Time goes from left to right. The
-  red regions correspond to influx and the blue regions correspond to
+  semipermeable vesicles with $\beta = 10^{-7}$ submerged in a fluid
+  with no background flow flow. Time goes from left to right. The red
+  regions correspond to influx and the blue regions correspond to
   efflux. In all cases, the vesicle reaches a steady state circular

### 2021-01-13 vesicle_code/docs/permeableVes/main.tex
yny

@@
   different reduced areas in a shear flow with two different flow rates.
-  (b) The steady state shape of a vesicle with varying flow rates and
+  (b) The equilibrium shape of a vesicle with varying flow rates and
   semipermeability rates. The circled vesicles correspond to the
@@
   \fi
-  \caption{\label{fig:parabolicComposite} (a) The steady state shape of
+  \caption{\label{fig:parabolicComposite} (a) The equilibrium shape of
   a semipermeable vesicle submerged in a Poiseuille flow with varying
@@
   \caption{\label{fig:stenosisComposite} (a) A semipermeable vesicle
-  passing through a constricted geometry similar to the experimental
+  passing through a closely-fit channel similar to the experimental
   device in~\cite{abk-fai-sto2006}. (b) A semipermeable vesicle passing
-  through a constricted geometry that is over five times longer. (c)
+  through a  (four-times) longer closely-fit channel than (a). (c)
   The excess pressure of an impermeable and semipermeable vesicle in the
@@
     \, ds \\
-  &= -\beta \int_\gamma \left(\kappa^3 + \kappa \sigma \right) 
+  &  = -\beta \int_\gamma \left(\kappa^3 + \kappa \sigma \right) 
     \, ds = \beta \int_\gamma \left(
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Vesicle Tensions}
+\section*{Supplementary Material: Vesicle Tensions}
+
+\subsection*{Vesicle Relaxation}
+Figure~\ref{fig:relaxationTensions} shows the membrane tension distribution along the relaxing vesicles in Figure~\ref{fig:relaxationComposite}. 
+The membrane tension (color bars) is in N/m. As the semipermeable vesicle relaxes, the membrane tension reduces in magnitude and becomes more
+evenly distributed along the membrane.
+In the top row the vesicle nearly relaxes to a circle on the right, and the membrane tension is uniform and equal to $k_b \kappa^2/2$ as predicted by our analysis (see Eq.~\ref{eqn:areaROC}).
+In the bottom row, the initial vesicle shape has a lot of high curvature regions (and thus the low reduced area), and it takes more than four hours to 
+inflate to twice the total water content for $\beta=10^{-7}$. In contrast the water enclosed inside the vesicle in the top row remains nearly constant in four hours.
 \begin{figure*}[htp]
@@
   \fi
-  \caption{\label{fig:relaxationTensions} Tension of vesicles in
-  relaxation.}
+  \caption{\label{fig:relaxationTensions} Tension distribution of vesicles in
+  relaxation that corresponds to Figure~\ref{fig:relaxationComposite}.}
   \todo[inline]{Redo using cline}
@@
 
+\subsection*{Vesicle in a planar shear flow}
+Our integral simulations of a semipermeable vesicle in a planar shear flow show that the equilibrium
+vesicle shape depends mostly on the capillary number $Ca_\mathrm{E}$, independent of the dimensionless water permeability $\beta$.
+Our simulations show that the time it takes for a semipermeable vesicle to reach equilibrium in a planar shear flow is inversely proportional to $\beta$, just like the relaxing vesicle.
+The tension distribution along the equilibrium vesicle at $\beta=10^{-4}$ is shown in Figure~\ref{fig:shearTensions}, where the color bars are for the membrane tension in N/m.
+The capillary number $Ca_\mathrm{E}$ increases from Figure~\ref{fig:shearTensions}(a) to (g), and we observe that the tension magnitude also increases almost linearly with
+$Ca_\mathrm{E}$.  We also observe that the membrane tension is relatively small at the tip when the membrane curvature is large due to the extensional component in the shear flow.
 \begin{figure*}[hbp]
@@
 %  \includegraphics[width=\textwidth]{figures/shearTensions.pdf}
-  \caption{\label{fig:shearTensions} Tension of vesicles in
-  shear flow. The semi-permeability constant is $\beta = 10^{-4}$ for
+  \caption{\label{fig:shearTensions} Tension distribution along a vesicle in
+  a linear shear flow. The semi-permeability constant is $\beta = 10^{-4}$ for
   all these cases, and the elastic capillary number ranges from
@@
 
+\subsection*{Vesicle in a Poiseuille flow}
+In a nonlinear shear flow, an impermeable vesicle can reach equilibrium position at the mid-plane of the shear flow
+for sufficiently large reduced area, regardless of the maximum flow velocity $U$. For a semi-permeable vesicle, however,
+our simulation results (summarized in Figure~\ref{fig:parabolicComposite}) show that the equilibrium vesicle shape (and position) is determined by $U$, 
+and independent of the initial vesicle reduced area and permeability $\beta$.
+The corresponding membrane tension distribution is shown in Figure~\ref{fig:parabolicTensions} as a function of flow velocity $U$ from $200\mu$m/s  to $800\mu$m/s.
 \begin{figure*}[hbp]
@@
   \end{tikzpicture}
-  \caption{\label{fig:parabolicTensions} The steady state tension
-  profile of a semipermeable vesicle with $\beta=10^{-3}$ in a parabolic
+  \caption{\label{fig:parabolicTensions} The equilibrium tension
+  distribution of a semipermeable vesicle with $\beta=10^{-3}$ in a parabolic
   flow (see Figure~\ref{fig:parabolicComposite}). The flow velocities
@@
 
+We note that in the Poiseuille flow the membrane tension is positive in the front, and negative in the rear part of the vesicle.
+Furthermore we also note that the tension magnitude is almost linearly proportional to $U$ as in the linear shear flow.
+
+\subsection*{Vesicle in a closely-fit channel}
+When a semi-permeable vesicle goes through a closely-fit channel, we observe that the water efflux is found in the front, and the influx is in the rear of the vesicle membrane (Figure~\ref{fig:stenosisComposite}).
+This corresponds well to the corresponding tension distribution in Figure~\ref{fig:stenosisTensions}: Larger tension in the front, and smaller tension in the rear.
 \begin{figure*}[htp]
@@
   \end{tikzpicture}
-  \caption{\label{fig:stenosisTensions} Tension of vesicles in
-  stenosis.}
+  \caption{\label{fig:stenosisTensions} Tension distribution along a semi-permeable vesicle going through a closely-fit channel.}
 \end{figure*}

### 2021-01-13 vesicle_code/docs/permeableVes/main.tex
added contracting tension results

@@
 
+\begin{figure*}[htp]
+  \centering
+  \begin{tikzpicture}[scale=1]
+    \node[inner sep=0pt] at (0,0) {
+    \includegraphics[width=\textwidth]{figures/contractingTensions1.pdf}
+    };
+    \node at (-8.62,4.3) {(a)};
+    \node at (+1.1,4.3) {(c)};
+    \node at (-8.62,-1.2) {(b)};
+    \node at (+1.1,-1.2) {(d)};
+  \end{tikzpicture}
+
+  \begin{tikzpicture}[scale=1]
+    \node[inner sep=0pt] at (0,0) {
+    \includegraphics[width=0.8\textwidth]{figures/contractingTensions2.pdf}
+    };
+    \node at (-6.79,1.4) {(e)};
+  \end{tikzpicture}
+
+  \caption{\label{fig:contractingTensions1} Tension distribution along a
+  semi-permeable vesicle going through a contracting geometry. The
+  vesicle tension increases by up to five orders of magnitude when as it
+  enters the neck. The permeability constant and flow rates are (a)
+  $U_{\max} = 5.7\mu$m/s, $\beta = 5 \times 10^{-4}$; (b) $U_{\max} =
+  5.7\mu$m/s, $\beta = 5 \times 10^{-3}$; (c) $U_{\max} = 0.57\mu$m/s,
+  $\beta = 1 \times 10^{-3}$; (d) $U_{\max} = 5.7\mu$m/s, $\beta = 1
+  \times 10^{-3}$; (e) $U_{\max} = 18\mu$m/s, $\beta = 1 \times
+  10^{-3}$.}
+\end{figure*}
+
 \end{document}

### 2021-01-13 vesicle_code/docs/permeableVes/main.tex
yny

--- 2021-01-13 vesicle_code/docs/permeableVes/main.tex
@@
 membrane permeability with membrane elastic stress and tension in the framework of Helfrich free energy, we 
-illustrate that, in the absence of an osmotic stress gradient, a giant unilamellar vesicle may be affected by water 
+illustrate that, in the absence of an osmotic stress gradient, the model semipermeable vesicle is affected by water 
 influx/efflux over a sufficiently long time or under a strong confinement. Our simulation results quantify the conditions 
@@
 %
-Without aquaporins or other membrane channels that promote water
-permeability, the intrinsic water permeability is known to depend on the
-temperature, lipid composition~\cite{OlbrichRawiczNeedhamEtAl2000_BJ},
-and the hydration of the membrane~\cite{MarrinkBerendsen1994_JPhysChem}.
 In the red blood cell membrane, aquaporin-1 channels give rise to a much
@@
 BhatiaRobinsonDimova2020_SoftMatt}. 
+Without aquaporins or other membrane channels that promote water
+permeability, the intrinsic membrane permeability is known to depend on the
+temperature, lipid composition~\cite{OlbrichRawiczNeedhamEtAl2000_BJ},
+and the hydration of the membrane~\cite{MarrinkBerendsen1994_JPhysChem}.
 %
@@
 macromolecules. Consequently, as long as the lipid bilayer membrane
-remains intact (no poration or rupture), red blood cells and vesicles
-are assumed to be of the same volume throughout experiments of durations
+remains intact (no poration or rupture), the total amount of water enclosed by the membrane 
+is assumed to remain the same throughout experiments of durations
 no longer than tens of minutes.

### 2021-01-13 vesicle_code/docs/permeableVes/main.tex
finished up first draft for relaxation tensions
yny

@@
   \fi
-  \caption{\label{fig:contractingComposite} A contracting geometry
-  similar to the experimental device in~\cite{wu2015critical}. The
+  \caption{\label{fig:contractingComposite} A contracting channel
+  similar to the experimental configuration in~\cite{wu2015critical}. The
   channel width varies from $18\mu$m to $1.8\mu$m, and it repeats every
@@
 
+\subsection*{Vesicle going through a contracting channel (slit)}
+When a semipermeable vesicle goes through a contracting channel (slit) the numerical simulations show that both the driving flow and the membrane permeability have to be sufficiently large for a successful passage through the slit, see Figure \ref{fig:contractingComposite}.
+As the vesicle goes through the contracting channel, the gradual confinement first leads to a slow inflation.
+Once the vesicle is close to the neck, it quickly deflates in order to fit the constriction.
+When the vesicle is near the neck, simulations show that the the water effluxes are in the front and rear of vesicle while most water influx is in the middle.
+The tension distribution along the vesicle as a function of their position in the contracting channel is summarized in Figure~\ref{fig:contractingTension1}, where we observe the membrane tension has the largest magnitude when the vesicle is at the neck.
+Away from the neck the membrane tension is quite small due to th
 \begin{figure*}[htp]
@@
   \end{tikzpicture}
-
   \begin{tikzpicture}[scale=1]
@@
   \end{tikzpicture}
-
   \caption{\label{fig:contractingTensions1} Tension distribution along a

### 2021-01-14 vesicle_code/docs/permeableVes/main.tex
edited everything but supplementary material

--- 2021-01-13 vesicle_code/docs/permeableVes/main.tex
@@
 % At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
-\keywords{Keyword 1 $|$ Keyword 2 $|$ Keyword 3 $|$ ...}
+\keywords{Semipermeable $|$ Vesicle $|$ Extreme confinement $|$
+Boundary Integral Equations $|$ Stokes flow}
 
 \begin{abstract}
-Lipid bilayer membranes have a native (albeit small) permeability for water molecules. Under an external load, a lipid membrane deforms and its
-water influx/efflux is often assumed  negligible in the absence of osmolarity, provided 
-that the bilayer structure stays intact and does not suffer from poration or rupture. 
-%
-In this work we use boundary integral simulations to investigate the effects
-of native water permeability on the vesicle hydrodynamics due to a mechanical load,  such as the viscous stress
-from an external flow deforming a vesicle membrane in free space or pushing it through a confinement. Coupling the 
-membrane permeability with membrane elastic stress and tension in the framework of Helfrich free energy, we 
-illustrate that, in the absence of an osmotic stress gradient, the model semipermeable vesicle is affected by water 
-influx/efflux over a sufficiently long time or under a strong confinement. Our simulation results quantify the conditions 
-for water permeation to be negligible in terms of the time scales, flow strength and confinement. These results shed 
-light on how microfluidic confinement can be utilized to estimate membrane permeability.
+Lipid bilayer membranes have a native (albeit small) permeability for
+water molecules. Under an external load, a lipid membrane deforms and
+its water influx/efflux is often assumed  negligible in the absence of
+osmolarity, provided that the bilayer structure stays intact and does
+not suffer from poration or rupture. 
+%
+In this work we use boundary integral simulations to investigate the
+effects of native water permeability on the vesicle hydrodynamics due to
+a mechanical load,  such as the viscous stress from an external flow
+deforming a vesicle membrane in free space or pushing it through a
+confinement. Coupling the membrane permeability with membrane elastic
+stress and tension in the framework of Helfrich free energy, we
+illustrate that, in the absence of an osmotic stress gradient, the
+model semipermeable vesicle is affected by water influx/efflux over a
+sufficiently long time or under a strong confinement. Our simulation
+results quantify the conditions for water permeation to be negligible
+in terms of the time scales, flow strength, and confinement. These
+results shed light on how microfluidic confinement can be utilized to
+estimate membrane permeability.
 %
@@
 ratio of a migrating cell. While stress-induced release of messengers in
-cells has been well studied~\cite{Wan2008_PNAS, ForsythWan2011_PNAS, 
+cells has been well-studied~\cite{Wan2008_PNAS, ForsythWan2011_PNAS, 
 Russell-PuleriPazAdams2016_AJHCP, ZhangShenHoganBarakatMisbah2018_BJ,
@@
 
-Vesicles (self-enclosed lipid bilayer membranes) have been
-used as a model system to study reshaping, remodeling, and scission of
-cell membranes due to osmotic stress~\cite{OgleckaEtAl2014_eLife,
+Vesicles (self-enclosed lipid bilayer membranes) have been used as a
+model system to study reshaping, remodeling, and scission of cell
+membranes due to osmotic stress~\cite{OgleckaEtAl2014_eLife,
 CamposSaric2020_bioRxiv, Dimova2020_GVB, BhatiaChrist2020_SoftMatt}.
@@
 suspended red blood cell or vesicle in a steady flow for more than a few
-hours. It is also difficult to quantify the vesicle area/volume ratio
-accurately \cite{MinetttiCallensCoupier2008_AppliedOptics}.  Using numerical simulations we can quantify the effects of
-water permeability on the hydrodynamics of a vesicle under mechanical
-stresses. 
-In the absence of an osmotic gradient, we first show that
-a freely suspended semipermeable vesicle behaves differently from an
-impermeable vesicle over a long time. Next we show that, at normal
-physiological conditions, the permeable water flow can be amplified by
-extreme confinement and results in observable change in both vesicle
-hydrodynamics and reduced area. These results will shed light on the
-dynamic aging process of living cells that constantly go through flows
-and constrictions over a period of days.
+hours. It is also difficult to quantify the vesicle surface-to-volume
+ratio accurately~\cite{MinetttiCallensCoupier2008_AppliedOptics}. Using
+numerical simulations we can quantify the effects of water permeability
+on the hydrodynamics of a vesicle under mechanical stresses.  In the
+absence of an osmotic gradient, we first show that a freely suspended
+semipermeable vesicle behaves differently from an impermeable vesicle
+over a long time. Next we show that, at normal physiological conditions,
+the permeable water flow can be amplified by extreme confinement and
+results in observable change in both vesicle hydrodynamics and reduced
+volume. These results will shed light on the dynamic aging process of
+living cells that constantly go through flows and constrictions over a
+period of days.
 
@@
 to the external stress such as the hydrodynamic stress due to an
-external flow or confinement. In the following we will explore both.
+external flow or confinement. In the following we explore both.
 
@@
 lead to different vesicle hydrodynamics over a time scale of 10 to 100
-minutes. 
-%{\bf YNY: is this correct? The shear flow results seem to suggest that
-%the permeability may lead to change in area in less than a second???}
-For vesicles in a narrow microfluidic channel, the experiments usually do not last longer than a few minutes~\cite{abk-fai-sto2006}.
-%\todo[inline]{Howard talked aboutthis statement not always being true}. 
-Our simulations show that strong
-confinement can lead to amplification of water permeability at such
-short time scale.
-%
-%all vesicles have a length
-%$L$, but the area is not conserved because of semipermeability. We vary
-%the initial vesicle reduced area, the permeability rate, and the flow
-%rate. For all simulations, the bending modulus is $10^{-19}J$.
+minutes. For vesicles in a narrow microfluidic channel, the experiments
+usually do not last longer than a few minutes~\cite{abk-fai-sto2006}.
+Our simulations show that strong confinement can lead to amplification
+of water permeability at such short time scales.
 
@@
 the vesicle and significant change in the reduced area is found at
-$t\sim 10$ minutes. Over time (about ten hours) all vesicles inflate and
-as expected, each vesicle eventually reaches a circular shape with
-reduced area $\alpha=1$. 
+$t\sim 1$ hour. Over time (about ten days) all vesicles inflate and as
+expected, each vesicle eventually reaches a circular shape with reduced
+area $\alpha=1$. 
 %%These regions are denoted in blue and are only present at early times. 
@@
 
-Between $t=50$ seconds and $t=50$ minutes, the intermediate shapes of
+Between $t=250$ seconds and $t=250$ minutes, the intermediate shapes of
 semipermeable vesicles resemble the shape of an impermeable vesicle.
@@
 decreases, the permeability velocity dominates, and the vesicle begins
-to inflate to a circle with no vanishing force and velocity.
+to inflate to a circle with vanishing force and velocity.
 
@@
 \subsection*{Planar Shear Flow}
-
-We consider a semipermeable vesicle in a planar shear flow, characterized by the elastic capillary number
-$Ca_\mathrm{E}=\dot{\gamma}\tau$, where $\tau$ is the characteristic time scale in the non-dimensionalization (see Supplementary Material) and
-$\dot{\gamma}$ is the shear rate of the planar shear flow
-$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$.
- %with different permeability $\beta$ and shear rates $\dot{\gamma}$. 
- When $\beta=0$ (impermeable
-case), a vesicle's reduced area and viscosity contrast determine whether
-it tank treads or tumbles~\cite{fin-lam-sei-gom2008,
-kra-win-sei-lip1996}. Focusing on semipermeable vesicles with no
-viscosity contrast, we find that a semipermeable vesicle tilts to an
-inclination angle and undergoes tank treading dynamics, similar to the
-case of an impermeable vesicle.
-
-In Figure~\ref{fig:shearComposite}(a), using four initial reduced areas
-and two flow rates, we plot the reduced area of a semipermeable vesicle
-with $\beta = 10^{-3}$. As observed in a quiescent flow, the final
-vesicle shape is independent of the initial reduced area. However, it
-does depend on the flow rate. We also observe that the reduced area
-remains constant until $t\sim 10$ minutes, when the vesicle starts to
-tank-tread and the normal component of the force-balance velocity
-becomes significantly smaller than the permeable velocity, leading to a
-changing reduced area.
-
-For a variety of semipermeability rates and $Ca_\mathrm{E}$, a semipermeable
-vesicle reaches a steady equilibrium as in
-Figure~\ref{fig:shearComposite}(a). Since the final shape is independent
-of the initial reduced area, we initialize the vesicle with reduced area
-$\alpha = 0.65$ for all simulations in
-Figure~\ref{fig:shearComposite}(b), where we summarize the steady state
-vesicle shape and its reduced area. We see that the capillary number (flow rate)
-significantly affects the final vesicle shape, but the semipermeability
-rate has a minor effect. Instead, as we saw in the quiescent analysis,
-$\beta$ sets a time scale since the time required for a vesicle to reach
-its steady state configuration is proportional to $\beta^{-1}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Poiseuille Flow}
-\begin{figure*}[htp]
+\begin{figure*}[hbp]
   \centering
@@
 
+We consider a semipermeable vesicle in a planar shear flow, characterized by the elastic capillary number
+$Ca_\mathrm{E}=\dot{\gamma}\tau$, where $\tau$ is the characteristic time scale in the non-dimensionalization (see Supplementary Material) and
+$\dot{\gamma}$ is the shear rate of the planar shear flow
+$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$.
+ %with different permeability $\beta$ and shear rates $\dot{\gamma}$. 
+ When $\beta=0$ (impermeable
+case), a vesicle's reduced area and viscosity contrast determine whether
+it tank treads or tumbles~\cite{fin-lam-sei-gom2008,
+kra-win-sei-lip1996}. Focusing on semipermeable vesicles with no
+viscosity contrast, we find that a semipermeable vesicle tilts to an
+inclination angle and undergoes tank treading dynamics, similar to the
+case of an impermeable vesicle.
+
+In Figure~\ref{fig:shearComposite}(a), using four initial reduced areas
+and two flow rates, we plot the reduced area of a semipermeable vesicle
+with $\beta = 10^{-3}$. As observed in a quiescent flow, the final
+vesicle shape is independent of the initial reduced area. However, it
+does depend on the flow rate. We also observe that the reduced area
+remains constant until $t\sim 10$ minutes, when the vesicle starts to
+tank-tread and the normal component of the force-balance velocity
+becomes significantly smaller than the permeable velocity, leading to a
+changing reduced area.
+
+For a variety of semipermeability rates and $Ca_\mathrm{E}$, a
+semipermeable vesicle reaches a steady equilibrium as in
+Figure~\ref{fig:shearComposite}(a). Since the final shape is independent
+of the initial reduced area, we initialize the vesicle with reduced area
+$\alpha = 0.65$ for all simulations in
+Figure~\ref{fig:shearComposite}(b), where we summarize the steady state
+vesicle shape and its reduced area. We see that the capillary number
+(flow rate) significantly affects the final vesicle shape, but the
+semipermeability rate has a minor effect. Instead, as we saw in the
+quiescent analysis, $\beta$ sets a time scale since the time required
+for a vesicle to reach its steady state configuration is proportional to
+$\beta^{-1}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Poiseuille Flow}
+
 We consider a semipermeable vesicle in the Poiseuille flow $\uu =
@@
 codes by comparing against results in Kaoui {\em et
-al.}~\cite{kao-bir-mis2009}, see Supplementary Material.
+al.}~\cite{kao-bir-mis2009} (see Supplementary Material).
 
@@
 Using several initial reduced areas and flow rates, we recreate the
-impermeable vesicle phase diagram for vesicles with a permeability rate
-of $\beta = 10^{-3}$. The equilibrium vesicle shape for different $U$
-and initial reduced area is summarized in
-Figure~\ref{fig:parabolicComposite}(a), and the vertical displacement of
-the vesicle's center of mass is in
+impermeable vesicle phase diagram for vesicles with $\beta = 10^{-3}$.
+The equilibrium vesicle shape for different $U$ and initial reduced area
+is summarized in Figure~\ref{fig:parabolicComposite}(a), and the
+vertical displacement of the vesicle's center of mass is in
 Figure~\ref{fig:parabolicComposite}(b). The effect of semipermeability
@@
 area and migration pattern are shown in
-Figure~\ref{fig:parabolicComposite}(c) and (d).
+Figures~\ref{fig:parabolicComposite}(c)
+and~\ref{fig:parabolicComposite}(d), respectively.
 
@@
 \subsection*{Semipermeable Vesicle in a Narrow Channel (Stenosis)}
- \begin{figure*}[htp]
+ \begin{figure*}[hbp]
   \centering
@@
 (Figure~\ref{fig:stenosisComposite}(a)). The flow velocity $U_{max} =
-1000 \mu$m/s is maintained at the inlet and outlet and is chosen so that the residency time of the vesicle in the
-stenosis channel is $t_R \approx 0.5$s which agrees with the
-experimental results~\cite{abk-fai-sto2006}. When the red blood cell
-enters the channel, an increase in the pressure drop is required to
-maintain a constant flow rate, and the difference in the pressure drop
-is called the excess pressure.
+1000 \mu$m/s is maintained at the inlet and outlet and is chosen so that
+the residency time of the vesicle in the stenosis channel is $t_R
+\approx 0.5$s which agrees with the experimental
+results~\cite{abk-fai-sto2006}. When the red blood cell enters the
+channel, an increase in the pressure drop is required to maintain a
+constant flow rate, and the difference in the pressure drop is called
+the excess pressure.
 
@@
 
+Figures~\ref{fig:stenosisComposite}(d)
+and~\ref{fig:stenosisComposite}(e) show that the vesicle deflates from
+the beginning due to the high flow velocity, consistent with the results
+for a vesicle in a Poiseuille flow in open space (blue curves). As the
+vesicle enters the stenosis channel, it continues to deflate in the
+front even though we observe influx (red segment) at various rear
+locations in the membrane. Overall, the vesicle loses about 6.1\% of its
+initial total water at a constant rate as shown in
+Figures~\ref{fig:stenosisComposite}(d)
+and~\ref{fig:stenosisComposite}i(e). Thus we expect that a larger amount
+of deflation is possible if the vesicle is inside a longer stenosis: we
+consider a vesicle passing through a channel of triple the length in
+Figure~\ref{fig:stenosisComposite}(b) with $U_{max}=8.4 \mu$m/s, and we
+observe that vesicle stays inside the stenosis for a residence time
+$t_R=16.2$s and the reduced area decreases by 13.2\% (red curves).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Semipermeable Vesicle in a Contracting Geometry} 
 \begin{figure}[htp]
@@
 \end{figure}
-
-Figure~\ref{fig:stenosisComposite}(d)) shows that the vesicle deflates
-from the beginning due to the high flow velocity, consistent with the
-results for a vesicle in a Poiseuille flow in open space. As the vesicle
-enters the stenosis channel, it continues to deflate in the front even
-though we observe influx (red segment) at various rear locations in the
-membrane. Overall, the vesicle loses about 6.1\% of its initial total
-water at a constant rate as shown in
-Figure~\ref{fig:stenosisComposite}(d). Thus we expect that a larger
-amount of deflation is possible if the vesicle is inside a longer
-stenosis: we consider a vesicle passing through a channel of triple the
-length in Figure~\ref{fig:stenosisComposite}(b) with $U_{max}=8.4
-\mu$m/s, and we observe that vesicle stays inside the stenosis for a
-residence time $t_R=16.2$s and the reduced area decreases by 13.2\%
-(Figure~\ref{fig:stenosisComposite}(e)).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Semipermeable Vesicle in a Contracting Geometry}
 
@@
 decreases from $18 \mu$m to $1.8 \mu$m. The channel then immediately
-opens again to $18 \mu$m (Figure~\ref{fig:contractingComposite}). A
+reopens to $18 \mu$m (Figure~\ref{fig:contractingComposite}). A
 Poiseuille flow is imposed at the inlet and outlet with a constant
@@
 
-In Figures~\ref{fig:contractingComposite}a
-and~\ref{fig:contractingComposite}b, we plot snapshots of vesicles with
-different permeability $\beta$. Figure~\ref{fig:contractingComposite}c
-shows the corresponding reduced area as a function of the vesicles'
-location. We observe that if the permeability is sufficiently large, the
-vesicle inflates gradually over seconds before it reaches the neck, and
-then it quickly deflates within a fraction of a second. However, if the
-semipermeability rate is too low, the vesicle is too large when it
-reaches the narrowest part of the channel, and it is unable to pass. In
-Figures~\ref{fig:contractingComposite}d
-and~\ref{fig:contractingComposite}e, we plot snapshots of vesicles with
-different imposed maximum velocities, and
-Figure~\ref{fig:contractingComposite}f shows the reduced area as a
-function of the vesicles' location. At low velocities, the vesicle
+In Figures~\ref{fig:contractingComposite}(a)
+and~\ref{fig:contractingComposite}(b), we plot snapshots of vesicles
+with different permeability $\beta$.
+Figure~\ref{fig:contractingComposite}(c) shows the corresponding reduced
+area as a function of the vesicle's location. We observe that if the
+permeability is sufficiently large, the vesicle inflates gradually over
+seconds before it reaches the neck, and then it quickly deflates within
+a fraction of a second. However, if the semipermeability rate is too
+low, the vesicle is too large when it reaches the narrowest part of the
+channel, and it is unable to pass. In
+Figures~\ref{fig:contractingComposite}(d)
+and~\ref{fig:contractingComposite}(e), we plot snapshots of vesicles
+with different imposed maximum velocities, and
+Figure~\ref{fig:contractingComposite}(f) shows the reduced area as a
+function of the vesicle's location. At low velocities, the vesicle
 inflates similar to the unbounded parabolic flow example, and it is
@@
 contraction.
-
-To understand the effects of water permeability on cells that repeatedly
-go through micro-capillary vessels or sub-micron slits, we construct a
-contracting geometry (see Figures~\ref{fig:contractingComposite2}) to
-simulate a vesicle passing through the contracting geometry six times.
-In Figure~\ref{fig:contractingComposite2}b, we show that the vesicle
-deflates each time it passes through the contraction followed by a
-gradual inflation (over seconds). The total area loss over the history
-of the vesicle is almost 50\%. In
-Figure~\ref{fig:contractingComposite}c, we show the vesicle velocity as
-a function of the vesicle's center of mass. As the vesicle passes
-through the contraction, it first accelerates until it reaches the neck
-where it abruptly decelerates to go through the contraction. The
-variation of the reduced area and velocity with respect to time are also
-shown in Figure~\ref{fig:contractingComposite2}.
-\begin{figure}[hbp]
+\begin{figure}[htp]
   \centering
@@
 
-%
-%\begin{itemize}
-%  \item Vesicle velocity in plot (a) varies from 5 to 24 microns/s.
-%  \item Vesicle velocity in plot (b) varies from 5 to 28 microns/s. Time
-%    that vesicle first completely passes through constriction is 4.75s
-%  \item Vesicle velocity in plot (c) varies from 0.2 to 2 microns/s.
-%  \item Vesicle velocity in plot (d) varies from 5 to 25 microns/s. Time
-%    that vesicle first completely passes through constriction is 4.76s
-%  \item Vesicle velocity in plot (g) varies from 14 to 95 microns/s (see
-%    plot (i)). Time that vesicle first completely passes through
-%    constriction is 1.43s
-%\end{itemize}
+To understand the effects of water permeability on cells that repeatedly
+pass through micro-capillary vessels or sub-micron slits, we construct a
+contracting geometry (see Figure~\ref{fig:contractingComposite2}) to
+simulate a vesicle passing through the contracting geometry six times.
+In Figure~\ref{fig:contractingComposite2}(b), we show that the vesicle
+deflates each time it passes through the contraction followed by a
+gradual inflation (over seconds). The total area loss over the history
+of the vesicle is almost 50\%. In
+Figure~\ref{fig:contractingComposite2}(c), we show the vesicle velocity
+as a function of the vesicle's center of mass. As the vesicle passes
+through the contraction, it first accelerates until it reaches the neck
+where it abruptly decelerates to go through the contraction. The
+variation of the reduced area and velocity with respect to time are also
+shown in Figure~\ref{fig:contractingComposite2}.
 
@@
 fully inflated, independent of its initial surface-to-volume ratio.
+\todo[inline]{Do the time scales in this paragraph reflect the
+adjustments we made to $\beta$ for the quiescent case?}
 
@@
 \subsection*{Vesicle Relaxation}
-Figure~\ref{fig:relaxationTensions} shows the membrane tension distribution along the relaxing vesicles in Figure~\ref{fig:relaxationComposite}. 
-The membrane tension (color bars) is in N/m. As the semipermeable vesicle relaxes, the membrane tension reduces in magnitude and becomes more
-evenly distributed along the membrane.
-In the top row the vesicle nearly relaxes to a circle on the right, and the membrane tension is uniform and equal to $k_b \kappa^2/2$ as predicted by our analysis (see Eq.~\ref{eqn:areaROC}).
-In the bottom row, the initial vesicle shape has a lot of high curvature regions (and thus the low reduced area), and it takes more than four hours to 
-inflate to twice the total water content for $\beta=10^{-7}$. In contrast the water enclosed inside the vesicle in the top row remains nearly constant in four hours.
+Figure~\ref{fig:relaxationTensions} shows the membrane tension
+distribution along the relaxing vesicles in
+Figure~\ref{fig:relaxationComposite}. The membrane tension (color bars)
+is in N/m. As the semipermeable vesicle relaxes, the membrane tension
+reduces in magnitude and becomes more evenly distributed along the
+membrane. In the top row the vesicle nearly relaxes to a circle on the
+right, and the membrane tension is uniform and equal to $k_b \kappa^2/2$
+as predicted by our analysis (see Eq.~\ref{eqn:areaROC}). In the bottom
+row, the initial vesicle shape has a lot of high curvature regions (and
+thus the low reduced area), and it takes more than four hours to inflate
+to twice the total water content for $\beta=10^{-7}$. In contrast the
+water enclosed inside the vesicle in the top row remains nearly constant
+in four hours.
 \begin{figure*}[htp]
-  \centering
-  \ifTikz
-    \input{figures/relaxationTensions.tikz}
-  \else
-    \includegraphics{figures/relaxationTensions.pdf}
-  \fi
+  \includegraphics[width=\textwidth]{figures/relaxationTensions2.pdf}
+
+%  \centering
+%  \ifTikz
+%    \input{figures/relaxationTensions.tikz}
+%  \else
+%    \includegraphics{figures/relaxationTensions.pdf}
+%  \fi
   \caption{\label{fig:relaxationTensions} Tension distribution of vesicles in
   relaxation that corresponds to Figure~\ref{fig:relaxationComposite}.}
-  \todo[inline]{Redo using cline}
 \end{figure*}
@@
 
+\subsection*{Vesicle going through a contracting channel (slit)}
+When a semipermeable vesicle goes through a contracting channel (slit)
+the numerical simulations show that both the driving flow and the
+membrane permeability have to be sufficiently large for a successful
+passage through the slit, see Figure~\ref{fig:contractingComposite}.  As
+the vesicle goes through the contracting channel, the gradual
+confinement first leads to a slow inflation. Once the vesicle is close
+to the neck, it quickly deflates in order to fit the constriction. When
+the vesicle is near the neck, simulations show that the water efflux is
+in the front and rear of vesicle while most water influx is in the
+middle. The tension distribution along the vesicle as a function of
+their position in the contracting channel is summarized in
+Figure~\ref{fig:contractingTensions1}, where we observe the membrane
+tension has the largest magnitude when the vesicle is at the neck. Away
+from the neck the membrane tension is quite small due to th
 \begin{figure*}[htp]

### 2021-01-14 vesicle_code/docs/permeableVes/main.tex
touched up supp material

@@
 characteristic length scale $R_0 = 10^{-6}$m, a bending stiffness of
-$k_b = 10^{-19}$J and fluid viscosity $5 \times 10^{-2}$kg/ms. We scale time by $\tau\equiv\mu R_0^3/k_b = 0.5s$, 
-the velocity by $R_0/\tau = 2\mu$m/s, the pressure by $k_b/R_0^3 = 10^{-1}$Pa, 
-tension by $k_b/R_0^2 = 10^{-7}$N/m, and the permeability by $R_0\mu = 2 \times 10^{-5}$m$^2$s/kg. 
-Under this nondimensionalization, a two-dimensional semipermeable vesicle in a viscous fluid is characterized by 
-(a) its reduced area $\alpha = 4\pi A/L^2
-\in (0,1]$, where $L$ is the vesicle length and $A$ is its area, and 
-(b) its permeability $\beta = k_w/(R_0\mu)$.
-In two dimensions, the membrane length is conserved by the local inextensibility condition, 
-but the enclosed area is not because of semipermeability. Therefore, the reduced area is
-dynamic.
+$k_b = 10^{-19}$J, and fluid viscosity $5 \times 10^{-2}$kg/ms. We scale
+time by $\tau\equiv\mu R_0^3/k_b = 0.5s$, the velocity by $R_0/\tau =
+2\mu$m/s, the pressure by $k_b/R_0^3 = 10^{-1}$Pa, tension by $k_b/R_0^2
+= 10^{-7}$N/m, and the permeability by $R_0\mu = 2 \times
+10^{-5}$m$^2$s/kg. Under this nondimensionalization, a two-dimensional
+semipermeable vesicle in a viscous fluid is characterized by (a) its
+reduced area $\alpha = 4\pi A/L^2 \in (0,1]$, where $L$ is the vesicle
+length and $A$ is its area, and (b) its permeability $\beta =
+k_w/(R_0\mu)$. In two dimensions, the membrane length is conserved by
+the local inextensibility condition, but the enclosed area is not
+because of semipermeability. Therefore, the reduced area is dynamic.
 
@@
 \end{align}
-%where $\beta = k_w/W$ is the dimensionless water permeability. 
-In confined geometries, the far field term $\uu_\infty$ is replaced by a
-double-layer potential with a density defined on $\partial\Omega$. The
-unknown density function allows us to satisfy the Dirichlet boundary
+In confined geometries, the far field term $\uu_\infty(\xx)$ is replaced
+by a double-layer potential with a density defined on $\partial\Omega$.
+The unknown density function allows us to satisfy the Dirichlet boundary
 condition $\uu(\xx) = \UU(\xx)$ for $\xx \in \partial\Omega$.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Numerical Validation}
-To validate our methods, we construct a phase diagram of the steady
-state shape of an impermeable vesicle in a Poiseuille flow. Depending on
-the flow rate and the reduced area, the steady state vesicle becomes
-either a axisymmetric bullet, a axisymmetric parachute, or a tank
-treading asymmetric slipper~\cite{kao-bir-mis2009}. Comparing our
-results (Figure~\ref{fig:PoiseuillePhase}) with those
-in~\cite{kao-bir-mis2009} (see Figure 2), we see that the vesicle shapes
-qualitatively agree. We note that Kaoui {\em et al.}~report that the
-vesicles with $\alpha=0.7$ and flow rates $U = 1200 \mu$ m/s and $U =
-1600 \mu$m/s are axisymmetric.  In our simulations these vesicles are
-slightly asymmetric, are undergoing a tank treading motion, and we
-therefore report them as asymmetric slippers.
 \begin{figure}[htp]
@@
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Numerical Validation}
+To validate our methods, we construct a phase diagram of the steady
+state shape of an impermeable vesicle in a Poiseuille flow. Depending on
+the flow rate and the reduced area, the steady state vesicle is either a
+axisymmetric bullet, a axisymmetric parachute, or a tank treading
+asymmetric slipper~\cite{kao-bir-mis2009}. Comparing our results
+(Figure~\ref{fig:PoiseuillePhase}) with those in~\cite{kao-bir-mis2009}
+(see Figure 2), we see that the vesicle shapes qualitatively agree. We
+note that Kaoui {\em et al.}~report that the vesicles with $\alpha=0.7$
+and flow rates $U = 1200 \mu$m/s and $U = 1600 \mu$m/s are axisymmetric.
+In our simulations these vesicles are slightly asymmetric, are
+undergoing a tank treading motion, and we therefore report them as
+asymmetric slippers.
 
@@
 $\Lambda = \kappa^2/2 = 2\pi^2/L^2.$ Note that in contrast to a
-impermeable vesicle, the tension is positive rather than negative.
+impermeable vesicle, the steady state tension is positive rather than
+negative.
 
@@
 \section*{Supplementary Material: Vesicle Tensions}
+\begin{figure*}[htp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/relaxationTensions2.pdf}
+%  \ifTikz
+%    \input{figures/relaxationTensions.tikz}
+%  \else
+%    \includegraphics{figures/relaxationTensions.pdf}
+%  \fi
+  \caption{\label{fig:relaxationTensions} The tension distribution of
+  vesicles in relaxation that corresponds to
+  Figure~\ref{fig:relaxationComposite}.}
+\end{figure*}
 
@@
 right, and the membrane tension is uniform and equal to $k_b \kappa^2/2$
-as predicted by our analysis (see Eq.~\ref{eqn:areaROC}). In the bottom
+as predicted by our analysis (see \eqref{eqn:areaROC}). In the bottom
 row, the initial vesicle shape has a lot of high curvature regions (and
@@
 in four hours.
-\begin{figure*}[htp]
-  \includegraphics[width=\textwidth]{figures/relaxationTensions2.pdf}
-
-%  \centering
-%  \ifTikz
-%    \input{figures/relaxationTensions.tikz}
-%  \else
-%    \includegraphics{figures/relaxationTensions.pdf}
-%  \fi
-  \caption{\label{fig:relaxationTensions} Tension distribution of vesicles in
-  relaxation that corresponds to Figure~\ref{fig:relaxationComposite}.}
-\end{figure*}
+\todo[inline]{I don't understand this last sentence}
 
 \subsection*{Vesicle in a planar shear flow}
-Our integral simulations of a semipermeable vesicle in a planar shear flow show that the equilibrium
-vesicle shape depends mostly on the capillary number $Ca_\mathrm{E}$, independent of the dimensionless water permeability $\beta$.
-Our simulations show that the time it takes for a semipermeable vesicle to reach equilibrium in a planar shear flow is inversely proportional to $\beta$, just like the relaxing vesicle.
-The tension distribution along the equilibrium vesicle at $\beta=10^{-4}$ is shown in Figure~\ref{fig:shearTensions}, where the color bars are for the membrane tension in N/m.
-The capillary number $Ca_\mathrm{E}$ increases from Figure~\ref{fig:shearTensions}(a) to (g), and we observe that the tension magnitude also increases almost linearly with
-$Ca_\mathrm{E}$.  We also observe that the membrane tension is relatively small at the tip when the membrane curvature is large due to the extensional component in the shear flow.
+Our simulations of a semipermeable vesicle in a planar shear flow show
+that the equilibrium vesicle shape depends mostly on the capillary
+number $Ca_\mathrm{E}$, independent of the dimensionless water
+permeability $\beta$. Our simulations show that the time it takes for a
+semipermeable vesicle to reach equilibrium in a planar shear flow is
+inversely proportional to $\beta$, just like the relaxing vesicle. The
+tension distribution along the equilibrium vesicle at $\beta=10^{-4}$ is
+shown in Figure~\ref{fig:shearTensions}, where the color bars are for
+the membrane tension in N/m. The capillary number $Ca_\mathrm{E}$
+increases from Figure~\ref{fig:shearTensions}(a) to (g), and we observe
+that the tension magnitude also increases almost linearly with
+$Ca_\mathrm{E}$. We also observe that the membrane tension is relatively
+small at the tip when the membrane curvature is large due to the
+extensional component in the shear flow.
 \begin{figure*}[hbp]
@@
 %  \includegraphics[width=\textwidth]{figures/shearTensions.pdf}
-  \caption{\label{fig:shearTensions} Tension distribution along a vesicle in
-  a linear shear flow. The semi-permeability constant is $\beta = 10^{-4}$ for
-  all these cases, and the elastic capillary number ranges from
-  $10^{-1}$ to $10^{2}$ as in Figure~\ref{fig:shearComposite}.}
+  \caption{\label{fig:shearTensions} The tension distribution along a
+  vesicle in a linear shear flow. The semi-permeability constant is
+  $\beta = 10^{-4}$ for all these cases, and the elastic capillary
+  number ranges from $10^{-1}$ to $10^{2}$ as in
+  Figure~\ref{fig:shearComposite}.}
 \end{figure*}
 
-\subsection*{Vesicle in a Poiseuille flow}
-In a nonlinear shear flow, an impermeable vesicle can reach equilibrium position at the mid-plane of the shear flow
-for sufficiently large reduced area, regardless of the maximum flow velocity $U$. For a semi-permeable vesicle, however,
-our simulation results (summarized in Figure~\ref{fig:parabolicComposite}) show that the equilibrium vesicle shape (and position) is determined by $U$, 
-and independent of the initial vesicle reduced area and permeability $\beta$.
-The corresponding membrane tension distribution is shown in Figure~\ref{fig:parabolicTensions} as a function of flow velocity $U$ from $200\mu$m/s  to $800\mu$m/s.
-\begin{figure*}[hbp]
+\begin{figure*}[htp]
   \centering
@@
 
-We note that in the Poiseuille flow the membrane tension is positive in the front, and negative in the rear part of the vesicle.
-Furthermore we also note that the tension magnitude is almost linearly proportional to $U$ as in the linear shear flow.
+\subsection*{Vesicle in a Poiseuille flow}
+In a nonlinear shear flow, an impermeable vesicle can reach equilibrium
+position at the mid-plane of the shear flow for sufficiently large
+reduced area, regardless of the maximum flow velocity $U$. For a
+semi-permeable vesicle, however, our simulation results (summarized in
+Figure~\ref{fig:parabolicComposite}) show that the equilibrium vesicle
+shape and position are determined by $U$, and independent of the initial
+vesicle reduced area and permeability $\beta$. The corresponding
+membrane tension distribution is shown in
+Figure~\ref{fig:parabolicTensions} as a function of flow velocity $U$
+from $200\mu$m/s to $800\mu$m/s.
+
+We note that in the Poiseuille flow the membrane tension is positive in
+the front, and negative in the rear part of the vesicle. Furthermore we
+also note that the tension magnitude is almost linearly proportional to
+$U$ as in the linear shear flow.
 
@@
   \end{tikzpicture}
-  \caption{\label{fig:stenosisTensions} Tension distribution along a semi-permeable vesicle going through a closely-fit channel.}
+  \caption{\label{fig:stenosisTensions} The tension distribution along a
+  semi-permeable vesicle going through a closely-fit channel of two
+  different lengths.}
 \end{figure*}
@@
 membrane permeability have to be sufficiently large for a successful
-passage through the slit, see Figure~\ref{fig:contractingComposite}.  As
+passage through the slit (see Figure~\ref{fig:contractingComposite}). As
 the vesicle goes through the contracting channel, the gradual
@@
 from the neck the membrane tension is quite small due to th
-\begin{figure*}[htp]
+\todo[inline]{I might have accidentally deleted some of your work here.
+Sorry!}
+\begin{figure*}[hbp]
   \centering
@@
   \end{tikzpicture}
-  \caption{\label{fig:contractingTensions1} Tension distribution along a
-  semi-permeable vesicle going through a contracting geometry. The
-  vesicle tension increases by up to five orders of magnitude when as it
-  enters the neck. The permeability constant and flow rates are (a)
-  $U_{\max} = 5.7\mu$m/s, $\beta = 5 \times 10^{-4}$; (b) $U_{\max} =
-  5.7\mu$m/s, $\beta = 5 \times 10^{-3}$; (c) $U_{\max} = 0.57\mu$m/s,
+  \caption{\label{fig:contractingTensions1} The tension distribution
+  along a semi-permeable vesicle going through a contracting geometry.
+  The vesicle tension increases by up to five orders of magnitude when
+  as it enters the neck. The permeability constant and flow rates are
+  (a) $U_{\max} = 5.7\mu$m/s, $\beta = 5 \times 10^{-4}$; (b) $U_{\max}
+  = 5.7\mu$m/s, $\beta = 5 \times 10^{-3}$; (c) $U_{\max} = 0.57\mu$m/s,
   $\beta = 1 \times 10^{-3}$; (d) $U_{\max} = 5.7\mu$m/s, $\beta = 1

### 2021-01-14 vesicle_code/docs/permeableVes/main.tex
yny

@@
 macromolecules. Consequently, as long as the lipid bilayer membrane
-remains intact (no poration or rupture), the total amount of water enclosed by the membrane 
-is assumed to remain the same throughout experiments of durations
+remains intact (no poration or rupture), the total amount of water inside the membrane 
+is assumed constant throughout the experiment of duration
 no longer than tens of minutes.
@@
 %%The response of a cell to an osmotic gradient is inevitably both mechanical (tension redistribution and shape change) and chemical (water flux across the membrane).  
-Under what condition is this a good assumption? Do vesicles conserve
+Under what condition is this a good assumption? Do liposomes conserve
 volume over hours under flow? What is the dynamic consequence when water
@@
 questions, we investigate the balance between hydrodynamics, tension,
-and elasticity of a semipermeable membrane under various flowing
+and elasticity of a semipermeable vesicle under various flowing
 conditions and confinement, see Figure~\ref{fig:sketch}.
@@
 %important. 
-
+%
 \begin{figure*}[htp]
@@
 \end{figure*}
-
+%
 % In this work we use numerical simulations to examine the hydrodynamics
@@
 
-Vesicles (self-enclosed lipid bilayer membranes) have been used as a
+Vesicles 
+%(self-enclosed lipid bilayer membranes) 
+have been used as a
 model system to study reshaping, remodeling, and scission of cell
-membranes due to osmotic stress~\cite{OgleckaEtAl2014_eLife,
+membranes due to osmotic stress~\cite{OgleckaEtAl2014_eLife, BhatiaRobinsonDimova2020_SoftMatt,
 CamposSaric2020_bioRxiv, Dimova2020_GVB, BhatiaChrist2020_SoftMatt}.
-Under an osmotic shock, a vesicle may undergo oscillatory variation in
-its enclosed volume~\cite{ChabanonHoLiedberg2017_BJ}. When trapped in a
-microfluidic channel, an osmotic shock induces vesicle shape changes,
-tank-treading and tumbling
-motions~\cite{BhatiaRobinsonDimova2020_SoftMatt,
-BhatiaChrist2020_SoftMatt}, an illustration that the permeable water
+%Under an osmotic shock, a vesicle may undergo oscillatory variation in
+%its enclosed volume~\cite{ChabanonHoLiedberg2017_BJ}. 
+%When trapped in a
+%microfluidic channel, an osmotic shock induces vesicle shape changes,
+%tank-treading and tumbling
+%motions~\cite{BhatiaRobinsonDimova2020_SoftMatt,
+%BhatiaChrist2020_SoftMatt}, an 
+These results illustrate that the permeable water
 flow is inevitably coupled with the mechanical pressure jump across the
@@
 yao-mor2017}. 
-
+%
 In microfluidic experiments, it is challenging to keep a freely
@@
 numerical simulations we can quantify the effects of water permeability
-on the hydrodynamics of a vesicle under mechanical stresses.  In the
-absence of an osmotic gradient, we first show that a freely suspended
+on the hydrodynamics of a vesicle under mechanical stresses.  
+Without an osmotic gradient, we first show that a freely suspended
 semipermeable vesicle behaves differently from an impermeable vesicle
-over a long time. Next we show that, at normal physiological conditions,
-the permeable water flow can be amplified by extreme confinement and
-results in observable change in both vesicle hydrodynamics and reduced
-volume. These results will shed light on the dynamic aging process of
-living cells that constantly go through flows and constrictions over a
-period of days.
+over a long time. Next we show that
+%, at normal physiological conditions,
+the permeating water flow can be amplified by extreme confinement to give rise to observable change in both hydrodynamics and water content. 
+These results provide insight into quantifying the effects of membrane permeability on vesicle hydrodynamics in microfluidics.
+%
+%shed light on the dynamic aging process of
+%living cells that constantly go through flows and constrictions over a
+%period of days.
 
@@
 The first phase is dominated by the balance between membrane traction
-and viscous stress at early times (up to a minute), when the vesicle
+and viscous stress at early times (up to five minutes), when the vesicle
 behaves like an impermeable membrane. The second phase sets in after a
-few minutes, when water influx begins to dominate and inflate the
-vesicle. Over a time scale of a few hours, a semipermeable vesicle is
+few hours, when water influx begins to dominate and inflate the
+vesicle. Over a time scale of more than ten days, a semipermeable vesicle is
 fully inflated, independent of its initial surface-to-volume ratio.
-\todo[inline]{Do the time scales in this paragraph reflect the
-adjustments we made to $\beta$ for the quiescent case?}
+%\todo[inline]{Do the time scales in this paragraph reflect the
+%adjustments we made to $\beta$ for the quiescent case?}
 
@@
 \begin{align}
-  \dot{A}(t) &= \beta \int_\gamma \left( -\xx_{ssss} + 
-    (\sigma \xx_s)_s \right) \cdot \nn \, ds \\
-  &= -\beta \int_\gamma \left(-\xx_{sss} + \sigma \xx_s 
-    \right) \cdot \kappa \xx_s \, ds \\
-  &= -\beta \int_\gamma \left(\xx_{ss} \cdot 
-    (\kappa \xx_s)_s + \kappa \sigma \right) \, ds \\
-  &= -\beta \int_\gamma \left(\kappa (\xx_{ss} \cdot \xx_{ss}) + 
-    \kappa_s (\xx_{ss} \cdot \xx_s) + \kappa \sigma \right) 
-    \, ds \\
-  &  = -\beta \int_\gamma \left(\kappa^3 + \kappa \sigma \right) 
-    \, ds = \beta \int_\gamma \left(
+  \dot{A}(t) & = \beta \int_\gamma \left(
     \frac{\kappa^3}{2} - \kappa \Lambda \right) \, ds.
@@
 \end{align}
-Note that the integrand in~\eqref{eqn:areaROC} is zero when the vesicle
-reaches its steady state which confirms that $\dot{A}(t) = 0$.
+%\begin{align}
+%  \dot{A}(t) &= \beta \int_\gamma \left( -\xx_{ssss} + 
+%    (\sigma \xx_s)_s \right) \cdot \nn \, ds \\
+%  &= -\beta \int_\gamma \left(-\xx_{sss} + \sigma \xx_s 
+%    \right) \cdot \kappa \xx_s \, ds \\
+%  &= -\beta \int_\gamma \left(\xx_{ss} \cdot 
+%    (\kappa \xx_s)_s + \kappa \sigma \right) \, ds \\
+%  &= -\beta \int_\gamma \left(\kappa (\xx_{ss} \cdot \xx_{ss}) + 
+%    \kappa_s (\xx_{ss} \cdot \xx_s) + \kappa \sigma \right) 
+%    \, ds \\
+%  &  = -\beta \int_\gamma \left(\kappa^3 + \kappa \sigma \right) 
+%    \, ds = \beta \int_\gamma \left(
+%    \frac{\kappa^3}{2} - \kappa \Lambda \right) \, ds.
+%  \label{eqn:areaROC}
+%\end{align}
+Note that the integrand in~\eqref{eqn:areaROC} is zero when the membrane tension balances the elastic force:
+\begin{align}
+\Lambda &= \frac{\kappa^2}{2}=\frac{\kappa_0^2}{2} \;\mathrm{ at }\; \mathrm{equilibrium},
+\end{align}
+which is consistent with the equilibrium results in the vesicle area dynamics.
+
+%reaches its steady state which confirms that $\dot{A}(t) = 0$.
 
@@
 water enclosed inside the vesicle in the top row remains nearly constant
-in four hours.
-\todo[inline]{I don't understand this last sentence}
+in the first four hours.
+%\todo[inline]{I don't understand this last sentence}
 
@@
 from the neck the membrane tension is quite small due to th
-\todo[inline]{I might have accidentally deleted some of your work here.
-Sorry!}
+%\todo[inline]{I might have accidentally deleted some of your work here.Sorry!}
 \begin{figure*}[hbp]

### 2021-01-15 vesicle_code/docs/permeableVes/main.tex
yny
new pressure and reduced size of Fig 13

@@
    device in~\cite{abk-fai-sto2006}. (b) A semipermeable vesicle passing
-  through a  (four-times) longer closely-fit channel than (a). (c)
-  The excess pressure of an impermeable and semipermeable vesicle in the
+   through a  (four-times) longer closely-fit channel than (a). (c) The
+   excess pressure of an impermeable and semipermeable vesicle in the
    short geometry in (a). (d) The reduced area of the semipermeable
@@
    distribution in N/m of the circled vesicles. Throughout the entire
-   simulation, these vesicle configurations have the largest tension.
-   \todo[inline]{Figure out the oscillations in excess pressure}}
+   simulation, these vesicle configurations have the largest tension.}
 \end{figure*}
@@
 the residency time of the vesicle in the stenosis channel is $t_R
-\approx 0.5$s which agrees with the experimental
+\approx 25$ms which agrees with the experimental
 results~\cite{abk-fai-sto2006}. When the red blood cell enters the
@@
 consider a vesicle passing through a channel of triple the length in
-Figure~\ref{fig:stenosisComposite}(b) with $U_{max}=8.4 \mu$m/s, and we
-observe that vesicle stays inside the stenosis for a residence time
-$t_R=16.2$s and the reduced area decreases by 13.2\% (red curves).
+Figure~\ref{fig:stenosisComposite}(b) with $U_{\max}=1000\mu$m/s, and we
+observe that vesicle stays inside the stenosis for a residence time $t_R
+\approx 70$ms and the reduced area decreases by 13.2\% (red curves).
 
@@
 where we have used the incompressibility of the single-layer potential.
-Repeatedly applying integration by parts, we have
+Repeatedly applying integration by parts, we finally obtain
 \begin{align}
@@
 %\todo[inline]{I might have accidentally deleted some of your work here.Sorry!}
-\begin{figure*}[hbp]
+\begin{figure}[htp]
   \centering
@@
     \node[inner sep=0pt] at (0,0) {
-    \includegraphics[width=\textwidth]{figures/contractingTensions1.pdf}
+    \includegraphics[width=0.5\textwidth]{figures/contractingTensions1.pdf}
     };
-    \node at (-8.62,4.3) {(a)};
-    \node at (+1.1,4.3) {(c)};
-    \node at (-8.62,-1.2) {(b)};
-    \node at (+1.1,-1.2) {(d)};
-  \end{tikzpicture}
-  \begin{tikzpicture}[scale=1]
-    \node[inner sep=0pt] at (0,0) {
-    \includegraphics[width=0.8\textwidth]{figures/contractingTensions2.pdf}
+    \node[inner sep=0pt] at (0,-2.3) {
+    \includegraphics[width=0.5\textwidth]{figures/contractingTensions2.pdf}
     };
-    \node at (-6.79,1.4) {(e)};
+    \node[inner sep=0pt] at (0,-4.8) {
+    \includegraphics[width=0.5\textwidth]{figures/contractingTensions3.pdf}
+    };
+    \node at (-4.2,0.9) {(a)};
+    \node at (-4.2,-1.4) {(b)};
+    \node at (+0.8,0.9) {(c)};
+    \node at (+0.8,-1.4) {(d)};
+    \node at (-4.2,-3.7) {(e)};
   \end{tikzpicture}
@@
   10^{-3}$.}
-\end{figure*}
+\end{figure}
 

### 2021-01-18 vesicle_code/docs/permeableVes/main.tex
yny

@@
 
-To understand the effects of water permeability on cells that repeatedly
-pass through micro-capillary vessels or sub-micron slits, we construct a
+To understand the effects of water permeability on a vesicle that repeatedly
+passes through micro-capillary vessels or sub-micron slits, we construct a
 contracting geometry (see Figure~\ref{fig:contractingComposite2}) to
@@
 \begin{align}
+\label{eqn:areaROC2}
 \Lambda &= \frac{\kappa^2}{2}=\frac{\kappa_0^2}{2} \;\mathrm{ at }\; \mathrm{equilibrium},
@@
 distribution along the relaxing vesicles in
-Figure~\ref{fig:relaxationComposite}. The membrane tension (color bars)
-is in N/m. As the semipermeable vesicle relaxes, the membrane tension
+Figure~\ref{fig:relaxationComposite}. The membrane tension magnitude (color bars) is in N/m.
+As the semipermeable vesicle relaxes, the membrane tension
 reduces in magnitude and becomes more evenly distributed along the
-membrane. In the top row the vesicle nearly relaxes to a circle on the
-right, and the membrane tension is uniform and equal to $k_b \kappa^2/2$
-as predicted by our analysis (see \eqref{eqn:areaROC}). In the bottom
-row, the initial vesicle shape has a lot of high curvature regions (and
+membrane. In the top row ($\alpha(0)=0.95$) the vesicle nearly relaxes to a circle on the
+right, and the membrane tension is uniform and equal to $k_b \kappa_0^2/2$
+as predicted by our analysis (see \eqref{eqn:areaROC2}). In the bottom
+row ($\alpha(0)=0.12$), the initial vesicle shape has a lot of high curvature regions (and
 thus the low reduced area), and it takes more than four hours to inflate
-to twice the total water content for $\beta=10^{-7}$. In contrast the
+to twice the initial total water content for $\beta=10^{-7}$. In contrast the
 water enclosed inside the vesicle in the top row remains nearly constant
@@
 their position in the contracting channel is summarized in
-Figure~\ref{fig:contractingTensions1}, where we observe the membrane
-tension has the largest magnitude when the vesicle is at the neck. Away
-from the neck the membrane tension is quite small due to th
+Figure~\ref{fig:contractingTensions1}, where we observe the
+tension has the largest magnitude when the vesicle is at the neck. 
+%Away from the neck the tension is relatively small, and water efflux is found in the corner of the vesicle.
 %\todo[inline]{I might have accidentally deleted some of your work here.Sorry!}

### 2021-01-19 vesicle_code/docs/permeableVes/main.tex
yny

@@
 that over sufficiently long time the water permeability affects the equilibrium vesicle shapes in open space.
-Under confinement, we show that water permeability may be quickly amplified to induce significant change in shape as the vesicle goes through a closely-fit long channel and a narrow slit.
+Under confinement, we show that water permeability may be quickly amplified to induce significant change in shape as the vesicle goes through a closely-fit slender channel and a contracting  channel.
 These results provide a quantitative measure of membrane permeability to water in terms of vesicle inflation/deflation under load.
@@
 % Please include corresponding author, author contribution and author declaration information
-\authorcontributions{All authors contributed equally.}
+\authorcontributions{B. Q. and Y.-N. Y. designed research with A. G.'s assistance. B.Q. and Y.-N.Y.
+performed the research, analyzed the data, and wrote the paper.}
 %\authordeclaration{Please declare any competing interests here.}
-%\equalauthors{\textsuperscript{1}A.O.(Author One) contributed equally to this work with A.T. (Author Two) (remove if not applicable).}
-%\correspondingauthor{\textsuperscript{1} E-mail: bquaife\@fsu.edu}
 \correspondingauthor{\textsuperscript{1} E-mail: yyoung@njit.edu}
@@
 % At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
-\keywords{Semipermeable $|$ Vesicle $|$ Extreme confinement $|$
+\keywords{Semipermeable membrane$|$ Vesicle $|$ Extreme confinement $|$
 Boundary Integral Equations $|$ Stokes flow}
@@
 Lipid bilayer membranes have a native (albeit small) permeability for
-water molecules. Under an external load, a lipid membrane deforms and
+water molecules. Under an external load, 
+provided that the bilayer structure stays intact and does
+not suffer from poration or rupture,
+a lipid membrane deforms and
 its water influx/efflux is often assumed negligible in the absence of
-osmolarity, provided that the bilayer structure stays intact and does
-not suffer from poration or rupture. 
+osmolarity. 
 %
@@
 
-The lipid bilayer membrane is permeable to water and water-soluble
+The lipid bilayer membrane is permeable to water and lipid-soluble
 molecules~\cite{Dick1964_JTB, FettiplaceHaydon1980_PhysRev,
@@
 In the red blood cell membrane, aquaporin-1 channels give rise to a much
-higher water permeability of approximately $1.8\times 10^{-2}$ cm/s in
+higher water permeability coefficient of approximately $1.8\times 10^{-2}$ cm/s in
 erythrocytes~\cite{YangMaVerkman2001_JBC} while the intrinsic water
@@
 influx/efflux affects the membrane hydrodynamics? To answer these
-questions, we investigate the balance between hydrodynamics, tension,
-and elasticity of a semipermeable vesicle under various flowing
+questions, we investigate the balance between hydrodynamics stresses, tension,
+and elastic stress of a semipermeable membrane under various flowing
 conditions and confinement, see Figure~\ref{fig:sketch}.
@@
 where $\nn$ is the outward normal (Figure~\ref{fig:sketch}), $k_w$ is
-the water permeability, $R$ is the ideal gas constant, $T$ is the
+the hydraulic permeability, $R$ is the ideal gas constant, $T$ is the
 temperature ($^{\circ}$K), $\triangle c$ is contrast in a solute
@@
 \xx_{ssss}$ and tension $\ff_\mathrm{ten}=(\sigma \xx_s)_s$ ($s$ is the
-arclength along the membrane, see Supplementary Material). Using
+arclength and $\sigma$ is the membrane tension along the membrane, see Supplementary Material). Using
 $k_w\sim 10^{-12}$ m$^2$s/kg (typical of mammalian cell
@@
 
-Between $t=250$ seconds and $t=250$ minutes, the intermediate shapes of
-semipermeable vesicles resemble the shape of an impermeable vesicle.
+Between $t=250$ seconds and $t=250$ minutes, the total water content is nearly constant.
+%
+%the intermediate shapes of
+%semipermeable vesicles resemble the shape of an impermeable vesicle.
+%
 This can be explained by considering the two terms that contribute to
@@
   steady state shapes are superimposed. (c) The reduced area of the
-  slipper formed with the flow rate of $800 \mu$m/s. (d) The vesicle
+  slipper formed with the flow rate of $800 \; \mu$m/s. (d) The vesicle
   shape shown with the background imposed flow. The channel width is
@@
 viscosity contrast, we find that a semipermeable vesicle tilts to an
-inclination angle and undergoes tank treading dynamics, similar to the
+inclination angle and undergoes tank-treading dynamics, similar to the
 case of an impermeable vesicle.
@@
 Figure~\ref{fig:parabolicComposite}(b). The effect of semipermeability
-of a vesicle with $\alpha(0) = 0.9$ and $U=800 \mu$m/s on its reduced
+of a vesicle with $\alpha(0) = 0.9$ and $U=800\; \mu$m/s on its reduced
 area and migration pattern are shown in
@@
 equilibrium vesicle shape in Figure~\ref{fig:parabolicComposite}(a). At
-the smallest flow rate of $U= 200 \mu$m/s, the steady state reduced
+the smallest flow rate of $U= 200\; \mu$m/s, the steady state reduced
 area is large, and the result is an axisymmetric bullet. At the larger
@@
 (Figure~\ref{fig:stenosisComposite}(a)). The flow velocity $U_{max} =
-1000 \mu$m/s is maintained at the inlet and outlet and is chosen so that
+1000 \;\mu$m/s is maintained at the inlet and outlet and is chosen so that
 the residency time of the vesicle in the stenosis channel is $t_R
-\approx 25$ms which agrees with the experimental
+\approx 25$ ms which agrees with the experimental
 results~\cite{abk-fai-sto2006}. When the red blood cell enters the
@@
 Figures~\ref{fig:stenosisComposite}(d)
-and~\ref{fig:stenosisComposite}i(e). Thus we expect that a larger amount
+and~\ref{fig:stenosisComposite}(e). Thus we expect that a larger amount
 of deflation is possible if the vesicle is inside a longer stenosis: we
 consider a vesicle passing through a channel of triple the length in
-Figure~\ref{fig:stenosisComposite}(b) with $U_{\max}=1000\mu$m/s, and we
+Figure~\ref{fig:stenosisComposite}(b) with $U_{\max}=1000\;\mu$m/s, and we
 observe that vesicle stays inside the stenosis for a residence time $t_R
-\approx 70$ms and the reduced area decreases by 13.2\% (red curves).
+\approx 70$ ms and the reduced area decreases by 13.2\% (red curves).
 
@@
   similar to the experimental configuration in~\cite{wu2015critical}. The
-  channel width varies from $18\mu$m to $1.8\mu$m, and it repeats every
-  $45\mu$m. The fluid flux along the red regions is into the vesicle,
+  channel width varies from $18\;\mu$m to $1.8\;\mu$m, and it repeats every
+  $45\;\mu$m. The fluid flux along the red regions is into the vesicle,
   and the fluid flux along the blue regions is out of the vesicle.
@@
 to~\cite{wu2015critical}, where the width of the channel gradually
-decreases from $18 \mu$m to $1.8 \mu$m. The channel then immediately
+decreases from $18 \;\mu$m to $1.8\; \mu$m. The channel then immediately
 reopens to $18 \mu$m (Figure~\ref{fig:contractingComposite}). A
@@
 maximum flow rate of $U_{\max}$. We initialize a semipermeable vesicle
-with $\alpha = 0.65$ that spans $10 \mu$m of the total channel width and
+with $\alpha = 0.65$ that spans $10\; \mu$m of the total channel width and
 investigate the effects of the membrane permeability to water and the
@@
 
+\acknow{We thank Howard Stone for suggestions .
+B.Q.~acknowledges support from the Simons Foundation, Mathematics and
+Physical Sciences-Collaboration Grants for Mathematicians, Award Number
+527139. Y.-N.Y.~acknowledges support from NSF (DMS 1614863, DMS 195160) and Flatiron Institute, part of Simons Foundation.}
+
+\showacknow{} % display acknowledgments
+
 % \bibliographystyle{plain}
@@
 The governing equations are non-dimensionalized by using a
-characteristic length scale $R_0 = 10^{-6}$m, a bending stiffness of
-$k_b = 10^{-19}$J, and fluid viscosity $5 \times 10^{-2}$kg/ms. We scale
-time by $\tau\equiv\mu R_0^3/k_b = 0.5s$, the velocity by $R_0/\tau =
-2\mu$m/s, the pressure by $k_b/R_0^3 = 10^{-1}$Pa, tension by $k_b/R_0^2
-= 10^{-7}$N/m, and the permeability by $R_0\mu = 2 \times
-10^{-5}$m$^2$s/kg. Under this nondimensionalization, a two-dimensional
+characteristic length scale $R_0 = 10^{-6}$ m, a bending stiffness of
+$k_b = 10^{-19}$ J, and fluid viscosity $5 \times 10^{-2}$ kg/ms. We scale
+time by $\tau\equiv\mu R_0^3/k_b = 0.5\;s$, the velocity by $R_0/\tau =
+2\;\mu$m/s, the pressure by $k_b/R_0^3 = 10^{-1}$ Pa, tension by $k_b/R_0^2
+= 10^{-7}$ N/m, and the permeability by $R_0\mu = 2 \times
+10^{-5}$ m$^2$s/kg. Under this nondimensionalization, a two-dimensional
 semipermeable vesicle in a viscous fluid is characterized by (a) its
@@
 the flow rate and the reduced area, the steady state vesicle is either a
-axisymmetric bullet, a axisymmetric parachute, or a tank treading
+axisymmetric bullet, a axisymmetric parachute, or a tank-treading
 asymmetric slipper~\cite{kao-bir-mis2009}. Comparing our results
@@
 note that Kaoui {\em et al.}~report that the vesicles with $\alpha=0.7$
-and flow rates $U = 1200 \mu$m/s and $U = 1600 \mu$m/s are axisymmetric.
+and flow rates $U = 1200\; \mu$m/s and $U = 1600\; \mu$m/s are axisymmetric.
 In our simulations these vesicles are slightly asymmetric, are
-undergoing a tank treading motion, and we therefore report them as
+undergoing a tank-treading motion, and we therefore report them as
 asymmetric slippers.
@@
   flow (see Figure~\ref{fig:parabolicComposite}). The flow velocities
-  are (a) 200$\mu$m/s, (b) 400$\mu$m/s, (c) 600$\mu$m/s, and (d)
-  800$\mu$m/s.}
+  are (a) 200 $\mu$m/s, (b) 400 $\mu$m/s, (c) 600 $\mu$m/s, and (d)
+  800 $\mu$m/s.}
 \end{figure*}
@@
 Figure~\ref{fig:parabolicTensions} as a function of flow velocity $U$
-from $200\mu$m/s to $800\mu$m/s.
+from $200\;\mu$m/s to $800 \;\mu$m/s.
 

### 2021-01-20 vesicle_code/docs/permeableVes/main.tex
small fixes

@@
 % Please include corresponding author, author contribution and author declaration information
-\authorcontributions{B. Q. and Y.-N. Y. designed research with A. G.'s assistance. B.Q. and Y.-N.Y.
-performed the research, analyzed the data, and wrote the paper.}
+\authorcontributions{B.Q.~and Y.-N.Y.~designed and perfored research
+with A.~G.'s assistance. B.Q.~and Y.-N.Y.~analyzed the data and wrote
+the paper.}
 %\authordeclaration{Please declare any competing interests here.}
@@
 \keywords{Semipermeable membrane$|$ Vesicle $|$ Extreme confinement $|$
-Boundary Integral Equations $|$ Stokes flow}
+Boundary integral equations $|$ Stokes flow}
 
@@
 illustrate that, in the absence of an osmotic stress gradient, the
-model semipermeable vesicle is affected by water influx/efflux over a
+semipermeable vesicle is affected by water influx/efflux over a
 sufficiently long time or under a strong confinement. Our simulation
@@
 influx/efflux affects the membrane hydrodynamics? To answer these
-questions, we investigate the balance between hydrodynamics stresses, tension,
-and elastic stress of a semipermeable membrane under various flowing
-conditions and confinement, see Figure~\ref{fig:sketch}.
+questions, we investigate the balance between hydrodynamics stresses,
+tension, and elastic stress of a semipermeable membrane under various
+flowing conditions and confinement (see Figure~\ref{fig:sketch}).
 %Specifically our numerical simulations yield the quantification of the
@@
 the hydraulic permeability, $R$ is the ideal gas constant, $T$ is the
-temperature ($^{\circ}$K), $\triangle c$ is contrast in a solute
-concentration (mol/volume), and $\ff_\mathrm{mem}$ is the membrane
-stress that consists of both bending $ \ff_\mathrm{ben}= -k_b
-\xx_{ssss}$ and tension $\ff_\mathrm{ten}=(\sigma \xx_s)_s$ ($s$ is the
-arclength and $\sigma$ is the membrane tension along the membrane, see Supplementary Material). Using
-$k_w\sim 10^{-12}$ m$^2$s/kg (typical of mammalian cell
+temperature (K), $\triangle c$ is contrast in a solute concentration
+(mol/volume), and $\ff_\mathrm{mem}$ is the membrane stress that
+consists of both bending $ \ff_\mathrm{ben}= -k_b \xx_{ssss}$ and
+tension $\ff_\mathrm{ten}=(\sigma \xx_s)_s$ ($s$ is the arclength and
+$\sigma$ is the membrane tension along the membrane, see Supplementary
+Material). Using $k_w\sim 10^{-12}$ m$^2$s/kg (typical of mammalian cell
 membranes~\cite{LiMoriSun2015_PRL}) and an osmolarity $\triangle c =
@@
 experiments~\cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the corresponding
-water flow is of the order $v_\mathrm{o}=0.1 \mu$m/s. Assuming that the
-membrane bending stiffness $k_b = 10^{-19}$J, a membrane tension
-$10^{-3}$N/m (one tenth of the lysis tension), and a characteristic
-length scale of $10^{-6}$m, the tension contribution ($v_\mathrm{t}$)
+water flow is of the order $v_\mathrm{o}=0.1 \; \mu$m/s. Assuming a
+membrane bending stiffness of $k_b = 10^{-19}$ J, a membrane tension of
+$10^{-3}$ N/m (one tenth of the lysis tension), and a characteristic
+length scale of $10^{-6}$ m, the tension contribution ($v_\mathrm{t}$)
 and elastic stress contribution ($v_\mathrm{e}$) to the permeable water
@@
 In experiments, vesicles under shear flows are measured for a minute
-(chapter 19 in~\cite{Dimova2020_GVB}), a duration over which vesicle can
-be assumed impermeable~\cite{AbkarianViallat2005_BJ}. Our simulations of
-a semipermeable vesicle in these flows show that water permeability may
-lead to different vesicle hydrodynamics over a time scale of 10 to 100
-minutes. For vesicles in a narrow microfluidic channel, the experiments
-usually do not last longer than a few minutes~\cite{abk-fai-sto2006}.
-Our simulations show that strong confinement can lead to amplification
-of water permeability at such short time scales.
+(chapter 19 in~\cite{Dimova2020_GVB}), a duration over which a vesicle
+can be assumed impermeable~\cite{AbkarianViallat2005_BJ}. Our
+simulations of a semipermeable vesicle in these flows show that water
+permeability may lead to different vesicle hydrodynamics over a time
+scale of 10 to 100 minutes. For vesicles in a narrow microfluidic
+channel, the experiments usually do not last longer than a few
+minutes~\cite{abk-fai-sto2006}. Our simulations show that strong
+confinement can lead to amplification of water permeability at such
+short time scales.
 
@@
 permeation flux: red denotes an influx into the vesicle, and blue
-denotes an efflux out of the vesicle.
-%
-First we observe that the initial vesicle shape determines the direction
-of water flux. For the vesicle with an initial reduced area
-($\alpha(0)=0.12$ in the bottom row) the vesicle deflates (blue regions)
-first due to the high interior capillary pressure that corresponds to
-the high membrane curvatures. For the other three cases efflux is found
-at some locations of high curvature, while mostly water permeates into
-the vesicle and significant change in the reduced area is found at
-$t\sim 1$ hour. Over time (about ten days) all vesicles inflate and as
-expected, each vesicle eventually reaches a circular shape with reduced
-area $\alpha=1$. 
+denotes an efflux out of the vesicle. First we observe that the initial
+vesicle shape determines the direction of water flux. For the vesicle
+with an initial reduced area $\alpha(0)=0.12$ (bottom row) the vesicle
+deflates (blue regions) first due to the high interior capillary
+pressure that corresponds to the high membrane curvatures. For the other
+three cases efflux is found at some locations of high curvature, while
+mostly water permeates into the vesicle and significant change in the
+reduced area is found at $t\sim 1$ hour. Over time (about ten days) all
+vesicles inflate and as expected, each vesicle eventually reaches a
+circular shape with reduced area $\alpha=1$. 
 %%These regions are denoted in blue and are only present at early times. 
@@
 \subsection*{Semipermeable Vesicle in a Narrow Channel (Stenosis)}
- \begin{figure*}[hbp]
+ \begin{figure*}[htp]
   \centering
@@
 
+\begin{figure}[hbp]
+  \centering
+  \ifTikz
+  \input{figures/contractingComposite.tikz}
+  \else
+  \includegraphics{figures/contractingComposite.pdf}
+  \fi
+  \caption{\label{fig:contractingComposite} A contracting channel
+  similar to the experimental configuration in~\cite{wu2015critical}.
+  The channel width varies from $18\;\mu$m to $1.8\;\mu$m, and it
+  repeats every $45\;\mu$m. The fluid flux along the red regions is into
+  the vesicle, and the fluid flux along the blue regions is out of the
+  vesicle.  (a--c): The ability for a semipermeable vesicle to pass
+  through the contraction depends on the semipermeability rate. (d--f):
+  The ability for a semipermeable vesicle to pass through the
+  contraction depends on the flow rate. The colored vesicles show the
+  tension distribution in N/m of the circled vesicles. Throughout the
+  entire simulation, these vesicle configurations have the largest
+  tension.}
+\end{figure}
+
 Cells experience stretching and release messengers when they pass
@@
 across a stenosed geometry. In this experiment, a pressure drop is used
-to squeeze a red blood cell through a constriction with diameter $5\mu$m
-and length $45\mu$m. We set up a similar computational geometry with a
-Poiseuille flow imposed at the inlet and outlet
-(Figure~\ref{fig:stenosisComposite}(a)). The flow velocity $U_{max} =
-1000 \;\mu$m/s is maintained at the inlet and outlet and is chosen so that
-the residency time of the vesicle in the stenosis channel is $t_R
+to squeeze a red blood cell through a constriction with diameter
+$5\;\mu$m and length $45\;\mu$m. We set up a similar computational
+geometry with a Poiseuille flow imposed at the inlet and outlet
+(Figure~\ref{fig:stenosisComposite}(a)). The flow velocity $U_{\max} =
+1000 \;\mu$m/s is maintained at the inlet and outlet and is chosen so
+that the residency time of the vesicle in the stenosis channel is $t_R
 \approx 25$ ms which agrees with the experimental
@@
 Figures~\ref{fig:stenosisComposite}(d)
-and~\ref{fig:stenosisComposite}(e). Thus we expect that a larger amount
-of deflation is possible if the vesicle is inside a longer stenosis: we
-consider a vesicle passing through a channel of triple the length in
-Figure~\ref{fig:stenosisComposite}(b) with $U_{\max}=1000\;\mu$m/s, and we
-observe that vesicle stays inside the stenosis for a residence time $t_R
-\approx 70$ ms and the reduced area decreases by 13.2\% (red curves).
+and~\ref{fig:stenosisComposite}(e) (blue curves). Thus we expect that a
+larger amount of deflation is possible if the vesicle is inside a longer
+stenosis: we consider a vesicle passing through a channel of triple the
+length in Figure~\ref{fig:stenosisComposite}(b) with
+$U_{\max}=1000\;\mu$m/s, and we observe that vesicle stays inside the
+stenosis for a residence time $t_R \approx 70$ ms and the reduced area
+decreases by 13.2\% (red curves).
 
@@
 \subsection*{Semipermeable Vesicle in a Contracting Geometry} 
-\begin{figure}[htp]
-  \centering
-  \ifTikz
-  \input{figures/contractingComposite.tikz}
-  \else
-  \includegraphics{figures/contractingComposite.pdf}
-  \fi
-  \caption{\label{fig:contractingComposite} A contracting channel
-  similar to the experimental configuration in~\cite{wu2015critical}. The
-  channel width varies from $18\;\mu$m to $1.8\;\mu$m, and it repeats every
-  $45\;\mu$m. The fluid flux along the red regions is into the vesicle,
-  and the fluid flux along the blue regions is out of the vesicle.
-  (a--c): The ability for a semipermeable vesicle to pass through the
-  contraction depends on the semipermeability rate. (d--f): The ability
-  for a semipermeable vesicle to pass through the contraction depends
-  on the flow rate. The colored vesicles show the tension distribution
-  in N/m of the circled vesicles. Throughout the entire simulation,
-  these vesicle configurations have the largest tension.}
-\end{figure}
-
 Squeezing a cell or an elastic vesicle through a slit in microfluidics
@@
 decreases from $18 \;\mu$m to $1.8\; \mu$m. The channel then immediately
-reopens to $18 \mu$m (Figure~\ref{fig:contractingComposite}). A
+reopens to $18\;\mu$m (Figure~\ref{fig:contractingComposite}). A
 Poiseuille flow is imposed at the inlet and outlet with a constant
@@
 contraction.
-\begin{figure}[htp]
+
+\begin{figure}[hbp]
   \centering
@@
   velocity vs.~time. Permeability rate is $\beta = 10^{-3}$ and maximum
-  velocity is $18\mu$m/s. (a) A semipermeable vesicle passing through
+  velocity is $18\;\mu$m/s. (a) A semipermeable vesicle passing through
   six periods of the contracting geometry. (b) The reduced area with
@@
 
-To understand the effects of water permeability on a vesicle that repeatedly
-passes through micro-capillary vessels or sub-micron slits, we construct a
-contracting geometry (see Figure~\ref{fig:contractingComposite2}) to
-simulate a vesicle passing through the contracting geometry six times.
-In Figure~\ref{fig:contractingComposite2}(b), we show that the vesicle
+To understand the effects of water permeability on a vesicle that
+repeatedly passes through micro-capillary vessels or sub-micron slits,
+we construct a contracting geometry (see
+Figure~\ref{fig:contractingComposite2}) to simulate a vesicle passing
+through the contracting geometry six times.  In
+Figure~\ref{fig:contractingComposite2}(b), we show that the vesicle
 deflates each time it passes through the contraction followed by a
@@
 behaves like an impermeable membrane. The second phase sets in after a
-few hours, when water influx begins to dominate and inflate the
-vesicle. Over a time scale of more than ten days, a semipermeable vesicle is
+few hours, when water influx begins to dominate and inflate the vesicle.
+Over a time scale of more than ten days, a semipermeable vesicle is
 fully inflated, independent of its initial surface-to-volume ratio.
-%\todo[inline]{Do the time scales in this paragraph reflect the
-%adjustments we made to $\beta$ for the quiescent case?}
 
@@
 
-\acknow{We thank Howard Stone for suggestions .
-B.Q.~acknowledges support from the Simons Foundation, Mathematics and
-Physical Sciences-Collaboration Grants for Mathematicians, Award Number
-527139. Y.-N.Y.~acknowledges support from NSF (DMS 1614863, DMS 195160) and Flatiron Institute, part of Simons Foundation.}
+\acknow{We thank Howard Stone for suggestions. B.Q.~acknowledges support
+from the Simons Foundation, Mathematics and Physical
+Sciences-Collaboration Grants for Mathematicians, Award Number 527139.
+Y.-N.Y.~acknowledges support from NSF (DMS 1614863, DMS 195160) and
+Flatiron Institute, part of Simons Foundation.}
 
@@
 note that Kaoui {\em et al.}~report that the vesicles with $\alpha=0.7$
-and flow rates $U = 1200\; \mu$m/s and $U = 1600\; \mu$m/s are axisymmetric.
-In our simulations these vesicles are slightly asymmetric, are
-undergoing a tank-treading motion, and we therefore report them as
-asymmetric slippers.
+and flow rates $U = 1200\; \mu$m/s and $U = 1600\; \mu$m/s are
+axisymmetric.  In our simulations these vesicles are slightly
+asymmetric, are undergoing a tank-treading motion, and we therefore
+report them as asymmetric slippers.
 
@@
 distribution along the relaxing vesicles in
-Figure~\ref{fig:relaxationComposite}. The membrane tension magnitude (color bars) is in N/m.
-As the semipermeable vesicle relaxes, the membrane tension
-reduces in magnitude and becomes more evenly distributed along the
-membrane. In the top row ($\alpha(0)=0.95$) the vesicle nearly relaxes to a circle on the
-right, and the membrane tension is uniform and equal to $k_b \kappa_0^2/2$
-as predicted by our analysis (see \eqref{eqn:areaROC2}). In the bottom
-row ($\alpha(0)=0.12$), the initial vesicle shape has a lot of high curvature regions (and
-thus the low reduced area), and it takes more than four hours to inflate
-to twice the initial total water content for $\beta=10^{-7}$. In contrast the
-water enclosed inside the vesicle in the top row remains nearly constant
-in the first four hours.
-%\todo[inline]{I don't understand this last sentence}
+Figure~\ref{fig:relaxationComposite}. The membrane tension magnitude
+(color bars) is in N/m.  As the semipermeable vesicle relaxes, the
+membrane tension reduces in magnitude and becomes more evenly
+distributed along the membrane. In the top row ($\alpha(0)=0.95$) the
+vesicle nearly relaxes to a circle on the right, and the membrane
+tension is uniform and equal to $k_b \kappa_0^2/2$ as predicted by our
+analysis (see \eqref{eqn:areaROC2}). In the bottom row
+($\alpha(0)=0.12$), the initial vesicle shape has a lot of high
+curvature regions (and thus the low reduced area), and it takes more
+than four hours to inflate to twice the initial total water content for
+$\beta=10^{-7}$. In contrast the water enclosed inside the vesicle in
+the top row remains nearly constant in the first four hours.
 
@@
   as it enters the neck. The permeability constant and flow rates are
-  (a) $U_{\max} = 5.7\mu$m/s, $\beta = 5 \times 10^{-4}$; (b) $U_{\max}
-  = 5.7\mu$m/s, $\beta = 5 \times 10^{-3}$; (c) $U_{\max} = 0.57\mu$m/s,
-  $\beta = 1 \times 10^{-3}$; (d) $U_{\max} = 5.7\mu$m/s, $\beta = 1
-  \times 10^{-3}$; (e) $U_{\max} = 18\mu$m/s, $\beta = 1 \times
-  10^{-3}$.}
+  (a) $U_{\max} = 5.7\;\mu$m/s, $\beta = 5 \times 10^{-4}$; (b)
+  $U_{\max} = 5.7\;\mu$m/s, $\beta = 5 \times 10^{-3}$; (c) $U_{\max} =
+  0.57\;\mu$m/s, $\beta = 1 \times 10^{-3}$; (d) $U_{\max} =
+  5.7\;\mu$m/s, $\beta = 1 \times 10^{-3}$; (e) $U_{\max} = 18\;\mu$m/s,
+  $\beta = 1 \times 10^{-3}$.}
 \end{figure}

### 2021-01-20 vesicle_code/docs/permeableVes/main.tex
small fixes

@@
    vesicles in the geometries in (a) and (b) as a function of the
-   vesicles' center of mass. In (c) and (d), the $x$-axis is scaled by
+   vesicles' center of mass. In (c) and (d), the x-axis is scaled by
    $1/L$ where $L$ is half the length of the constriction. (e) The
@@
   velocity is $18\;\mu$m/s. (a) A semipermeable vesicle passing through
-  six periods of the contracting geometry. (b) The reduced area with
-  the marks representing shapes in (a). (c) The vesicle velocity with
-  the marks representing shapes in (a). In (b) and (c), the bottom
-  x-axis is the $x$-coordinate of the center of mass, and the upper
-  x-axis is time. The colored vesicles show the tension distribution in
-  N/m of the circled vesicles. Throughout the entire simulation, these
-  vesicle configurations have the largest tension.}
+  six periods of the contracting geometry. (b) The reduced area with the
+  marks representing shapes in (a). (c) The vesicle velocity with the
+  marks representing shapes in (a). In (b) and (c), the bottom x-axis is
+  the x-coordinate of the center of mass, and the upper x-axis is time.
+  The colored vesicles show the tension distribution in N/m of the
+  circled vesicles. Throughout the entire simulation, these vesicle
+  configurations have the largest tension.}
 \end{figure}
@@
 on a time scale of a few seconds as a vesicle is squeezed through a
-closely fit channel and a contracting channel. As a semipermeable
+closely-fit channel and a contracting channel. As a semipermeable
 vesicle goes through a long closely-fit channel, we observe that the

### 2021-01-20 vesicle_code/docs/permeableVes/main.tex
yny

@@
 \section*{Supplementary Material: Formulation}
-We consider a two-dimensional inextensible semipermeable vesicle,
-$\gamma$, suspended in unconfined and confined geometries $\Omega$. The
-vesicle is parameterized as $\xx(s,t)$ where $s$ is arclength and $t$ is
-time. The suspending fluid is assumed to be viscous so that the fluid
-velocity $\uu$ and pressure $p$ are governed by the incompressible
+We consider a two-dimensional inextensible semipermeable vesicle membrane $\gamma$
+suspended in a viscous Newtonian fluid in domain $\Omega$.
+The vesicle membrane $\gamma$ is parameterized as $\xx(s,t)$ where $s$ is arclength and $t$ is
+time. In the suspending fluid the flow velocity $\uu$ and pressure $p$ are governed by the incompressible
 Stokes equations
@@
 \end{align}
-where $\mu$ is the fluid viscosity. In an unconfined geometry, the
-condition $\uu(\xx) \rightarrow \uu_\infty(\xx)$ is enforced as $|\xx|
-\rightarrow \infty$, and in a confined geometry, the boundary condition
-$\uu(\xx) = \UU(\xx)$ is enforced on $\partial \Omega$, where $\UU(\xx)$
-is prescribed. Along the vesicle, mass continuity, force balance, and
-local inextensibility are enforced by requiring
+where $\mu$ is the fluid viscosity.  When $\Omega$ is an unconfined geometry, the
+condition $\uu(\xx) \rightarrow \uu_\infty(\xx)$ as $|\xx|
+\rightarrow \infty$ is enforced. When $\Omega$ is a confined geometry, the boundary condition
+$\uu(\xx) = \UU(\xx)$ is enforced on the domain boundary $\partial \Omega$, where $\UU(\xx)$
+is prescribed. Along the vesicle membrane, mass continuity, force balance, and
+local inextensibility are enforced on $\gamma$ by requiring
 \begin{align}
@@
 \end{align}
-where $k_w$ is the water permeability.
+where $k_w$ is the hydraulic permeability.
 
@@
 k_w/(R_0\mu)$. In two dimensions, the membrane length is conserved by
-the local inextensibility condition, but the enclosed area is not
+the local inextensibility condition, but the enclosed area is not conserved
 because of semipermeability. Therefore, the reduced area is dynamic.
@@
 \subsection*{Numerical Validation}
-To validate our methods, we construct a phase diagram of the steady
-state shape of an impermeable vesicle in a Poiseuille flow. Depending on
-the flow rate and the reduced area, the steady state vesicle is either a
-axisymmetric bullet, a axisymmetric parachute, or a tank-treading
+To validate our numerical codes for simulating vesicle hydrodynamics, we reproduce a phase diagram of the equilibrium
+shape of an impermeable vesicle in a Poiseuille flow. Depending on
+the maximum flow velocity and the vesicle reduced area, the equilibrium vesicle shape is either an
+axisymmetric bullet, an axisymmetric parachute, or a tank-treading
 asymmetric slipper~\cite{kao-bir-mis2009}. Comparing our results
 (Figure~\ref{fig:PoiseuillePhase}) with those in~\cite{kao-bir-mis2009}
-(see Figure 2), we see that the vesicle shapes qualitatively agree. We
-note that Kaoui {\em et al.}~report that the vesicles with $\alpha=0.7$
+(see Figure 2), we observe quantitative agreement in the equilibrium vesicle shapes except that,
+%
+%see that the vesicle shapes qualitatively agree. We
+%note that 
+%
+Kaoui {\em et al.}~report that the vesicles with $\alpha=0.7$
 and flow rates $U = 1200\; \mu$m/s and $U = 1600\; \mu$m/s are
@@
 where the Lagrange multiplier $\Lambda$ is the tension. Note the absence
-of the pressure Lagrange multiplier since the vesicle's area fluctuates.
+of the pressure Lagrange multiplier since the total water content inside the vesicle membrane is not conserved.
 Taking the variation of $\mathcal{L}$ with respect to $\gamma$ and
@@
 of~\eqref{eqn:curveODE} is not periodic unless $\kappa(s) = \kappa_0$.
-Therefore, the steady state shape of a semipermeable vesicle in a
+Therefore, the equilibrium shape of a semipermeable vesicle in a
 quiescent flow is a circle with radius $L/2\pi$ and constant tension
@@
 impermeable vesicle, the steady state tension is positive rather than
-negative.
+negative. Such equilibrium shape of a semipermeable vesicle results from the balance between elastic stress and membrane tension. 
+For an elastic membrane with a large pore, the equilibrium membrane (hemispherical) shape also results from such balance \cite{Ryham2018_JFM}.
 

### 2021-01-20 vesicle_code/docs/permeableVes/main.tex
fixed up fig 1 and touched up small things

@@
 % Please include corresponding author, author contribution and author declaration information
-\authorcontributions{B.Q.~and Y.-N.Y.~designed and perfored research
-with A.~G.'s assistance. B.Q.~and Y.-N.Y.~analyzed the data and wrote
+\authorcontributions{B.Q.~and Y.-N.Y.~designed and performed research
+with A.G.'s assistance. B.Q.~and Y.-N.Y.~analyzed the data and wrote
 the paper.}
@@
 
-We consider a semipermeable vesicle in a planar shear flow, characterized by the elastic capillary number
-$Ca_\mathrm{E}=\dot{\gamma}\tau$, where $\tau$ is the characteristic time scale in the non-dimensionalization (see Supplementary Material) and
-$\dot{\gamma}$ is the shear rate of the planar shear flow
-$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$.
- %with different permeability $\beta$ and shear rates $\dot{\gamma}$. 
- When $\beta=0$ (impermeable
-case), a vesicle's reduced area and viscosity contrast determine whether
-it tank treads or tumbles~\cite{fin-lam-sei-gom2008,
-kra-win-sei-lip1996}. Focusing on semipermeable vesicles with no
-viscosity contrast, we find that a semipermeable vesicle tilts to an
-inclination angle and undergoes tank-treading dynamics, similar to the
-case of an impermeable vesicle.
+We consider a semipermeable vesicle in a planar shear flow,
+characterized by the elastic capillary number $Ca_\mathrm{E}=\chi\tau$,
+where $\tau$ is the characteristic time scale in the
+non-dimensionalization (see Supplementary Material) and $\chi$ is the
+shear rate of the planar shear flow $\uu_{\infty}(\xx) = \chi (y,0)$.
+When $\beta=0$ (impermeable case), a vesicle's reduced area and
+viscosity contrast determine whether it tank treads or
+tumbles~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. Focusing on
+semipermeable vesicles with no viscosity contrast, we find that a
+semipermeable vesicle tilts to an inclination angle and undergoes
+tank-treading dynamics, similar to the case of an impermeable vesicle.
 
@@
 \section*{Supplementary Material: Formulation}
-We consider a two-dimensional inextensible semipermeable vesicle membrane $\gamma$
-suspended in a viscous Newtonian fluid in domain $\Omega$.
-The vesicle membrane $\gamma$ is parameterized as $\xx(s,t)$ where $s$ is arclength and $t$ is
-time. In the suspending fluid the flow velocity $\uu$ and pressure $p$ are governed by the incompressible
+We consider a two-dimensional inextensible semipermeable vesicle
+membrane $\gamma$ suspended in a viscous Newtonian fluid in domain
+$\Omega$.  The vesicle membrane $\gamma$ is parameterized as $\xx(s,t)$
+where $s$ is arclength and $t$ is time. In the suspending fluid the flow
+velocity $\uu$ and pressure $p$ are governed by the incompressible
 Stokes equations
@@
 \end{align}
-where $\mu$ is the fluid viscosity.  When $\Omega$ is an unconfined geometry, the
-condition $\uu(\xx) \rightarrow \uu_\infty(\xx)$ as $|\xx|
-\rightarrow \infty$ is enforced. When $\Omega$ is a confined geometry, the boundary condition
-$\uu(\xx) = \UU(\xx)$ is enforced on the domain boundary $\partial \Omega$, where $\UU(\xx)$
-is prescribed. Along the vesicle membrane, mass continuity, force balance, and
-local inextensibility are enforced on $\gamma$ by requiring
+where $\mu$ is the fluid viscosity. When $\Omega$ is an unconfined
+geometry, the condition $\uu(\xx) \rightarrow \uu_\infty(\xx)$ as $|\xx|
+\rightarrow \infty$ is enforced. In the confined examples, we enforce a
+no-slip boundary condition along the top and bottom of the channel and a
+Hagen–Poiseuille flow at the inlet and outlet---this boundary condition
+has been used in similar vesicle setups~\cite{qua-bir2014,
+rah-vee-bir2010, lu-rah-zor2017}. Along the vesicle membrane $\gamma$,
+mass continuity, force balance, and local inextensibility are enforced
+by requiring
 \begin{align}
@@
 The governing equations are non-dimensionalized by using a
-characteristic length scale $R_0 = 10^{-6}$ m, a bending stiffness of
-$k_b = 10^{-19}$ J, and fluid viscosity $5 \times 10^{-2}$ kg/ms. We scale
+characteristic length scale $R_0 = 10^{-6}$ m, a bending stiffness $k_b
+= 10^{-19}$ J, and fluid viscosity $5 \times 10^{-2}$ kg/ms. We scale
 time by $\tau\equiv\mu R_0^3/k_b = 0.5\;s$, the velocity by $R_0/\tau =
-2\;\mu$m/s, the pressure by $k_b/R_0^3 = 10^{-1}$ Pa, tension by $k_b/R_0^2
-= 10^{-7}$ N/m, and the permeability by $R_0\mu = 2 \times
+2\;\mu$m/s, the pressure by $k_b/R_0^3 = 10^{-1}$ Pa, tension by
+$k_b/R_0^2 = 10^{-7}$ N/m, and the permeability by $R_0\mu = 2 \times
 10^{-5}$ m$^2$s/kg. Under this nondimensionalization, a two-dimensional
@@
 k_w/(R_0\mu)$. In two dimensions, the membrane length is conserved by
-the local inextensibility condition, but the enclosed area is not conserved
-because of semipermeability. Therefore, the reduced area is dynamic.
+the local inextensibility condition, but the enclosed area is not
+conserved because of semipermeability. Therefore, the reduced area is
+dynamic.
 
@@
 by a double-layer potential with a density defined on $\partial\Omega$.
-The unknown density function allows us to satisfy the Dirichlet boundary
-condition $\uu(\xx) = \UU(\xx)$ for $\xx \in \partial\Omega$.
+The unknown density function allows us to satisfy the boundary condition
+on $\partial\Omega$.
 
@@
 where we have used the incompressibility of the single-layer potential.
-Repeatedly applying integration by parts, we finally obtain
+Repeatedly applying integration by parts, we obtain
 \begin{align}
@@
   \caption{\label{fig:shearTensions} The tension distribution along a
-  vesicle in a linear shear flow. The semi-permeability constant is
+  vesicle in a linear shear flow. The semipermeability constant is
   $\beta = 10^{-4}$ for all these cases, and the elastic capillary
@@
 reduced area, regardless of the maximum flow velocity $U$. For a
-semi-permeable vesicle, however, our simulation results (summarized in
+semipermeable vesicle, however, our simulation results (summarized in
 Figure~\ref{fig:parabolicComposite}) show that the equilibrium vesicle
@@
 \subsection*{Vesicle in a closely-fit channel}
-When a semi-permeable vesicle goes through a closely-fit channel, we observe that the water efflux is found in the front, and the influx is in the rear of the vesicle membrane (Figure~\ref{fig:stenosisComposite}).
+When a semipermeable vesicle goes through a closely-fit channel, we observe that the water efflux is found in the front, and the influx is in the rear of the vesicle membrane (Figure~\ref{fig:stenosisComposite}).
 This corresponds well to the corresponding tension distribution in Figure~\ref{fig:stenosisTensions}: Larger tension in the front, and smaller tension in the rear.
@@
   \caption{\label{fig:stenosisTensions} The tension distribution along a
-  semi-permeable vesicle going through a closely-fit channel of two
-  different lengths.}
+  semipermeable vesicle with $\beta = 10^{-3}$ going through a
+  closely-fit channel of two different lengths.}
 \end{figure*}
@@
 tension has the largest magnitude when the vesicle is at the neck. 
-%Away from the neck the tension is relatively small, and water efflux is found in the corner of the vesicle.
-%\todo[inline]{I might have accidentally deleted some of your work here.Sorry!}
 \begin{figure}[htp]
@@
   \caption{\label{fig:contractingTensions1} The tension distribution
-  along a semi-permeable vesicle going through a contracting geometry.
+  along a semipermeable vesicle going through a contracting geometry.
   The vesicle tension increases by up to five orders of magnitude when

### 2021-01-21 vesicle_code/docs/permeableVes/main.tex
yny

@@
 permeable flow can be significant when the membrane tension is large due
-to the external stress such as the hydrodynamic stress due to an
+to the external stress such as the hydrodynamic stress from an
 external flow or confinement. In the following we explore both.
@@
 
-In experiments, vesicles under shear flows are measured for a minute
+In experiments, vesicles under shear flows are measured for a few minutes
 (chapter 19 in~\cite{Dimova2020_GVB}), a duration over which a vesicle
 can be assumed impermeable~\cite{AbkarianViallat2005_BJ}. Our
-simulations of a semipermeable vesicle in these flows show that water
-permeability may lead to different vesicle hydrodynamics over a time
-scale of 10 to 100 minutes. For vesicles in a narrow microfluidic
+simulations of a semipermeable vesicle under these flows in open geometry show that water
+permeability may lead to different vesicle hydrodynamics only after  a duration of $\sim 200$ minutes. For vesicles in a narrow microfluidic
 channel, the experiments usually do not last longer than a few
 minutes~\cite{abk-fai-sto2006}. Our simulations show that strong
-confinement can lead to amplification of water permeability at such
-short time scales.
+confinement can lead to amplification of water permeation at a time scale shorter than a few minutes.
+%short time scales.
 
@@
 shear rate of the planar shear flow $\uu_{\infty}(\xx) = \chi (y,0)$.
-When $\beta=0$ (impermeable case), a vesicle's reduced area and
-viscosity contrast determine whether it tank treads or
+When $\beta=0$ (impermeable case),  the vesicle reduced area and fluid
+viscosity contrast determine whether a vesicle tank treads or
 tumbles~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. Focusing on
@@
 vesicle shape is independent of the initial reduced area. However, it
-does depend on the flow rate. We also observe that the reduced area
-remains constant until $t\sim 10$ minutes, when the vesicle starts to
-tank-tread and the normal component of the force-balance velocity
+does depend on the flow rate. We also observe that the amount of water inside the vesicle 
+remains constant until $t\sim 10$ minutes, when 
+%the vesicle starts to tank-tread and 
+the normal component of the flow velocity 
 becomes significantly smaller than the permeable velocity, leading to a
@@
 
-For a variety of semipermeability rates and $Ca_\mathrm{E}$, a
-semipermeable vesicle reaches a steady equilibrium as in
-Figure~\ref{fig:shearComposite}(a). Since the final shape is independent
+For a variety of dimensionless permeability coefficient $\beta>0$ and capillary number $Ca_\mathrm{E}$, a
+semipermeable vesicle reaches an equilibrium shape as in
+Figure~\ref{fig:shearComposite}(a). Since the equilibrium shape is selected by $Ca_\mathrm{E}$ and independent
 of the initial reduced area, we initialize the vesicle with reduced area
 $\alpha = 0.65$ for all simulations in
-Figure~\ref{fig:shearComposite}(b), where we summarize the steady state
+Figure~\ref{fig:shearComposite}(b), where we summarize the equilibrium
 vesicle shape and its reduced area. We see that the capillary number
 (flow rate) significantly affects the final vesicle shape, but the
-semipermeability rate has a minor effect. Instead, as we saw in the
+permeability coefficient has a very minor effect. Instead, as we saw in the
 quiescent analysis, $\beta$ sets a time scale since the time required
@@
 At the beginning of the simulations a semipermeable vesicle is
-initialized above the center line $y=0$, and it migrates towards the
+placed above the center line $y=0$, and it migrates towards the
 center line as in the impermeable case~\cite{dan-vla-mis2009}. 
@@
 
-As observed for the planar shear flow, the steady state reduced area is
-independent of the initial reduced area, and larger flow rates result in
-smaller steady state reduced areas. We report the reduced area of the
-equilibrium vesicle shape in Figure~\ref{fig:parabolicComposite}(a). At
-the smallest flow rate of $U= 200\; \mu$m/s, the steady state reduced
-area is large, and the result is an axisymmetric bullet. At the larger
-flow rates, the steady state reduced area is smaller, and the result is
-an asymmetric tank-treading slipper. We observe that the membrane
-permeability to water drastically alters the vesicle shape and position
-relative to the flow at equilibrium: At $\beta=10^{-3}$ the equilibrium
+As observed for the planar shear flow, the equilibrium vesicle reduced area is
+independent of the initial reduced area and $\beta$, and  larger maximum flow velocity $U$ results in
+smaller equilibrium reduced areas, as summarized in Figure~\ref{fig:parabolicComposite}(a). At
+the smallest velocitty $U= 200\; \mu$m/s, the steady state reduced
+area is large, and the equilibrium vesicle shape is an axisymmetric bullet. The equilibrium reduced area
+decreases with increasing $U$, and the nonlinear flow profile gives rise to 
+an asymmetric tank-treading slipper for $U\ge 400$ $\mu m/s$. We observe that the membrane
+permeability to water drastically alters the equilibrium vesicle shape and position
+relative to the Poiseuille flow: At $\beta=10^{-3}$ the equilibrium
 vesicle depends only on the maximum velocity $U$ of the nonlinear shear
@@
 
-Cells experience stretching and release messengers when they pass
-through capillary vessels~\cite{Wan2008_PNAS, ForsythWan2011_PNAS,
-Pak2015_PNAS}. Many cells exhibit extraordinary flexibility as they go
+When cells go through small capillary vessels, they experience
+large shape deformation and significant membrane stretching that leads to release of messengers 
+%Cells experience stretching and release messengers when they pass
+%through capillary vessels
+~\cite{Wan2008_PNAS, ForsythWan2011_PNAS,Pak2015_PNAS}. 
+Many cells exhibit extraordinary flexibility as they go
 through narrow channels~\cite{AuStoreyMoore2016_PNAS}, and adjustment of
@@
 (Figure~\ref{fig:stenosisComposite}(a)). The flow velocity $U_{\max} =
-1000 \;\mu$m/s is maintained at the inlet and outlet and is chosen so
+1000 \;\mu$m/s at the inlet and outlet and is chosen so
 that the residency time of the vesicle in the stenosis channel is $t_R

### 2021-01-22 vesicle_code/docs/permeableVes/main.tex
yny

@@
 where $\nn$ is the outward normal (Figure~\ref{fig:sketch}), $k_w$ is
-the hydraulic permeability, $R$ is the ideal gas constant, $T$ is the
+the hydraulic conductivity, $R$ is the ideal gas constant, $T$ is the
 temperature (K), $\triangle c$ is contrast in a solute concentration
@@
 $\sigma$ is the membrane tension along the membrane, see Supplementary
-Material). Using $k_w\sim 10^{-12}$ m$^2$s/kg (typical of mammalian cell
-membranes~\cite{LiMoriSun2015_PRL}) and an osmolarity $\triangle c =
-0.1$ mol/L (consistent with the osmotic forces in vesicle aspiration
-experiments~\cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the corresponding
+Material). Using $k_w\sim 10^{-12}$ m$^2$s/kg 
+%(typical of mammalian cell membranes~\cite{LiMoriSun2015_PRL}) 
+and an osmolarity $\triangle c =
+0.1$ mol/L (consistent with the osmotic filtration experiments~\cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the corresponding
 water flow is of the order $v_\mathrm{o}=0.1 \; \mu$m/s. Assuming a
@@
   (b) The equilibrium shape of a vesicle with varying flow rates and
-  semipermeability rates. The circled vesicles correspond to the
+  membrane permeability. The circled vesicles correspond to the
   simulations in part (a).}
@@
 pressure that corresponds to the high membrane curvatures. For the other
-three cases efflux is found at some locations of high curvature, while
-mostly water permeates into the vesicle and significant change in the
-reduced area is found at $t\sim 1$ hour. Over time (about ten days) all
+three cases efflux is dominated by influx, especially after $t=250$ minutes when
+the increase in total water content becomes significant.
+%
+%is found at some locations of high curvature, while
+%mostly water permeates into the vesicle and significant change in the
+%reduced area is found at $t\sim 1$ hour. 
+%
+Over time (about ten days) all
 vesicles inflate and as expected, each vesicle eventually reaches a
@@
 We consider a semipermeable vesicle in a planar shear flow,
-characterized by the elastic capillary number $Ca_\mathrm{E}=\chi\tau$,
-where $\tau$ is the characteristic time scale in the
-non-dimensionalization (see Supplementary Material) and $\chi$ is the
+characterized by the elastic capillary number $Ca_\mathrm{E}=\chi\tau$ where $\tau$ is the characteristic time scale from balancing the viscous stress with the elastic stress
+%in the non-dimensionalization 
+(see Supplementary Material) and $\chi$ is the
 shear rate of the planar shear flow $\uu_{\infty}(\xx) = \chi (y,0)$.
@@
 
-As observed for the planar shear flow, the equilibrium vesicle reduced area is
+As observed for the planar shear flow, the equilibrium reduced area of a semipermeable vesicle in a Poiseuille flow is
 independent of the initial reduced area and $\beta$, and  larger maximum flow velocity $U$ results in
-smaller equilibrium reduced areas, as summarized in Figure~\ref{fig:parabolicComposite}(a). At
-the smallest velocitty $U= 200\; \mu$m/s, the steady state reduced
+smaller equilibrium reduced area, see Figure~\ref{fig:parabolicComposite}(a). At
+the smallest velocity $U= 200\; \mu$m/s, the steady state reduced
 area is large, and the equilibrium vesicle shape is an axisymmetric bullet. The equilibrium reduced area
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Semipermeable Vesicle in a Narrow Channel (Stenosis)}
+\subsection*{Semipermeable Vesicle in a Closely-fit Channel (Stenosis)}
  \begin{figure*}[htp]
@@
   vesicle.  (a--c): The ability for a semipermeable vesicle to pass
-  through the contraction depends on the semipermeability rate. (d--f):
+  through the contraction depends on the permeability $\beta$. (d--f):
   The ability for a semipermeable vesicle to pass through the
@@
 
-When cells go through small capillary vessels, they experience
-large shape deformation and significant membrane stretching that leads to release of messengers 
+When red blood cells go through small capillary vessels, they experience
+large shape deformation and significant membrane stretching that triggers ATP release
 %Cells experience stretching and release messengers when they pass
 %through capillary vessels
-~\cite{Wan2008_PNAS, ForsythWan2011_PNAS,Pak2015_PNAS}. 
+~\cite{Wan2008_PNAS, ForsythWan2011_PNAS}. 
 Many cells exhibit extraordinary flexibility as they go
-through narrow channels~\cite{AuStoreyMoore2016_PNAS}, and adjustment of
+through narrow vessels~\cite{AuStoreyMoore2016_PNAS}, and adjustment of
 area to volume ratio may be a key factor for a successful passage.  Here
@@
 geometry with a Poiseuille flow imposed at the inlet and outlet
-(Figure~\ref{fig:stenosisComposite}(a)). The flow velocity $U_{\max} =
-1000 \;\mu$m/s at the inlet and outlet and is chosen so
+(Figure~\ref{fig:stenosisComposite}(a)). We fix the flow velocity $U_{\max} =
+1000 \;\mu$m/s at the inlet and outlet so
 that the residency time of the vesicle in the stenosis channel is $t_R
@@
 seconds before it reaches the neck, and then it quickly deflates within
-a fraction of a second. However, if the semipermeability rate is too
+a fraction of a second. However, if the permeability $\beta$ is too
 low, the vesicle is too large when it reaches the narrowest part of the
@@
 
-\acknow{We thank Howard Stone for suggestions. B.Q.~acknowledges support
+\acknow{We thank Howard Stone, Michael J. Shelley, Petia Vlahovska, Chaoqui Misbah, Manouk Abkarian, Sangwoo Shin and Shravan K. Veerapaneni for discussions. B.Q.~acknowledges support
 from the Simons Foundation, Mathematics and Physical
@@
 \end{align}
-where $k_w$ is the hydraulic permeability.
+where $k_w$ is the hydraulic conductivity.
 
@@
 2\;\mu$m/s, the pressure by $k_b/R_0^3 = 10^{-1}$ Pa, tension by
-$k_b/R_0^2 = 10^{-7}$ N/m, and the permeability by $R_0\mu = 2 \times
-10^{-5}$ m$^2$s/kg. Under this nondimensionalization, a two-dimensional
+$k_b/R_0^2 = 10^{-7}$ N/m, and the permeability by $R_0/\mu = 10^{-3}$ m$^2$s/kg. Under this nondimensionalization, a two-dimensional
 semipermeable vesicle in a viscous fluid is characterized by (a) its
@@
 length and $A$ is its area, and (b) its permeability $\beta =
-k_w/(R_0\mu)$. In two dimensions, the membrane length is conserved by
+k_w \mu /R_0$.  For a polyunsaturated PC bilayer
+the hydraulic conductivity $k_w$ is in the range 
+$10^{-14}\le k_w\le 10^{-12}$ m$^2$s/kg, and the corresponding range for $\beta$ is $10^{-11}\le \beta\le 10^{-9}$.
+
+In two dimensions, the membrane length is conserved by
 the local inextensibility condition, but the enclosed area is not
@@
 dynamic.
-
+%
 Since the fluid satisfies the Stokes equations, the velocity and

### 2021-01-22 vesicle_code/docs/permeableVes/main.tex
updated figure 2

@@
   \caption{\label{fig:relaxationComposite} (a) Snapshots of four
-  semipermeable vesicles with $\beta = 10^{-7}$ submerged in a fluid
+  semipermeable vesicles with $\beta = 10^{-8}$ submerged in a fluid
   with no background flow flow. Time goes from left to right. The red

### 2021-01-22 vesicle_code/docs/permeableVes/main.tex
yny

--- 2021-01-22 vesicle_code/docs/permeableVes/main.tex
@@
 length and $A$ is its area, and (b) its permeability $\beta =
-k_w \mu /R_0$.  For a polyunsaturated PC bilayer
-the hydraulic conductivity $k_w$ is in the range 
-$10^{-14}\le k_w\le 10^{-12}$ m$^2$s/kg, and the corresponding range for $\beta$ is $10^{-11}\le \beta\le 10^{-9}$.
+k_w \mu /R_0$.  
+We convert the apparent permeability of 
+a polyunsaturated PC bilayer  \cite{OlbrichRawiczNeedhamEtAl2000_BJ}
+to the hydraulic conductivity $k_w$ using the conversion in \cite{FettiplaceHaydon1980_PhysRev}, and  found that 
+$10^{-14}\le k_w\le 10^{-12}$ m$^2$s/kg, thus $\beta$ is  in the range $10^{-11}\le \beta\le 10^{-9}$.
 

### 2021-01-22 vesicle_code/docs/permeableVes/main.tex
yny

@@
 $v_\mathrm{o}:v_\mathrm{t}:v_\mathrm{e}=10^{0}:10^{-2}:10^{-6}$.
-Furthermore, we note that in the absence of an osmotic stress, the water
-permeable flow can be significant when the membrane tension is large due
+Furthermore, we note that in the absence of an osmotic stress, the permeating water
+flow may be non-negligible when the membrane tension becomes large due
 to the external stress such as the hydrodynamic stress from an
 external flow or confinement. In the following we explore both.
+
+For a semipermeable vesicle without confinement, our simulations show that the
+dynamic evolution towards equilibrium is dictated by the background flow field, while the permeability $\beta$ only rescales the time in the dynamics.
+With confinement, we find that we need to use larger value of $\beta$ to keep the membrane tension below the poration value $\sim 10^{-3}$ N/m. 
+Such large value of $\beta$ may pertain to 
+a lipid bilayer membrane with aquaporin proteins at a high temperature.
 
@@
 simulations of a semipermeable vesicle under these flows in open geometry show that water
-permeability may lead to different vesicle hydrodynamics only after  a duration of $\sim 200$ minutes. For vesicles in a narrow microfluidic
+permeability may lead to different vesicle hydrodynamics only after  a duration of $\sim 1$ day. For vesicles in a narrow microfluidic
 channel, the experiments usually do not last longer than a few
@@
 pressure that corresponds to the high membrane curvatures. For the other
-three cases efflux is dominated by influx, especially after $t=250$ minutes when
-the increase in total water content becomes significant.
+three cases efflux is dominated by influx, especially after $t=1$ day when
+the increase in total water content becomes non-negligible.
 %
@@
 %
-Over time (about ten days) all
+Over time (about four weeks) all
 vesicles inflate and as expected, each vesicle eventually reaches a
@@
 
-Between $t=250$ seconds and $t=250$ minutes, the total water content is nearly constant.
+Between $t=30$ minutes and $t=1$ day, the total water content is nearly constant.
 %

### 2021-01-22 vesicle_code/docs/permeableVes/main.tex
fixed minor things

@@
 poration or rupture, we use direct numerical simulations to illustrate
-that over sufficiently long time the water permeability affects the equilibrium vesicle shapes in open space.
-Under confinement, we show that water permeability may be quickly amplified to induce significant change in shape as the vesicle goes through a closely-fit slender channel and a contracting  channel.
-These results provide a quantitative measure of membrane permeability to water in terms of vesicle inflation/deflation under load.
+that over sufficiently long time the water permeability affects the
+equilibrium vesicle shapes in open space. Under confinement, we show
+that water permeability may be quickly amplified to induce significant
+change in shape as the vesicle goes through a closely-fit slender
+channel and a contracting channel. These results provide a quantitative
+measure of membrane permeability to water in terms of vesicle
+inflation/deflation under load.
 %
@@
 semipermeable vesicle is affected by water influx/efflux over a
-sufficiently long time or under a strong confinement. Our simulation
-results quantify the conditions for water permeation to be negligible
-in terms of the time scales, flow strength, and confinement. These
-results shed light on how microfluidic confinement can be utilized to
-estimate membrane permeability.
+sufficiently long time or under a strong confinement. Our simulations
+quantify the conditions for water permeation to be negligible in terms
+of the time scales, flow strength, and confinement. These results shed
+light on how microfluidic confinement can be utilized to estimate
+membrane permeability.
 %
@@
 numerical simulations we can quantify the effects of water permeability
-on the hydrodynamics of a vesicle under mechanical stresses.  
-Without an osmotic gradient, we first show that a freely suspended
-semipermeable vesicle behaves differently from an impermeable vesicle
-over a long time. Next we show that
+on the hydrodynamics of a vesicle under mechanical stresses.  Without an
+osmotic gradient, we first show that a freely suspended semipermeable
+vesicle behaves differently from an impermeable vesicle over a long
+time. Next we show that
 %, at normal physiological conditions,
@@
   semipermeable vesicles with $\beta = 10^{-8}$ submerged in a fluid
-  with no background flow flow. Time goes from left to right. The red
-  regions correspond to influx and the blue regions correspond to
-  efflux. In all cases, the vesicle reaches a steady state circular
-  shape. (b) The reduced area of each of the simulations. The particular
-  snapshots in (a) occur at the marks along the curve.}
+  with no background flow. Time goes from left to right. The red regions
+  correspond to influx and the blue regions correspond to efflux. In all
+  cases, the vesicle reaches a steady state circular shape. (b) The
+  reduced area of each of the simulations. The particular snapshots in
+  (a) occur at the marks along the curve.}
 \end{figure*}
@@
 
-For a semipermeable vesicle without confinement, our simulations show that the
-dynamic evolution towards equilibrium is dictated by the background flow field, while the permeability $\beta$ only rescales the time in the dynamics.
-With confinement, we find that we need to use larger value of $\beta$ to keep the membrane tension below the poration value $\sim 10^{-3}$ N/m. 
-Such large value of $\beta$ may pertain to 
-a lipid bilayer membrane with aquaporin proteins at a high temperature.
+For a semipermeable vesicle without confinement, our simulations show
+that the dynamic evolution towards equilibrium is dictated by the
+background flow field, while the permeability $\beta$ only rescales the
+time in the dynamics. With confinement, we find that we need to use
+larger values of $\beta$ to keep the membrane tension below the poration
+value $\sim 10^{-3}$ N/m. Such large values of $\beta$ may pertain to a
+lipid bilayer membrane with aquaporin proteins at a high temperature.
 
@@
 
-In experiments, vesicles under shear flows are measured for a few minutes
-(chapter 19 in~\cite{Dimova2020_GVB}), a duration over which a vesicle
-can be assumed impermeable~\cite{AbkarianViallat2005_BJ}. Our
-simulations of a semipermeable vesicle under these flows in open geometry show that water
-permeability may lead to different vesicle hydrodynamics only after  a duration of $\sim 1$ day. For vesicles in a narrow microfluidic
-channel, the experiments usually do not last longer than a few
-minutes~\cite{abk-fai-sto2006}. Our simulations show that strong
-confinement can lead to amplification of water permeation at a time scale shorter than a few minutes.
+In experiments, vesicles under shear flows are measured for a few
+minutes (chapter 19 in~\cite{Dimova2020_GVB}), a duration over which a
+vesicle can be assumed impermeable~\cite{AbkarianViallat2005_BJ}. Our
+simulations of a semipermeable vesicle under these flows in open
+geometry show that water permeability may lead to different vesicle
+hydrodynamics only after a duration of $\sim 1$ day. For vesicles in a
+narrow microfluidic channel, the experiments usually do not last longer
+than a few minutes~\cite{abk-fai-sto2006}. Our simulations show that
+strong confinement can lead to amplification of water permeation at a
+time scale shorter than a few minutes.
 %short time scales.
@@
 pressure that corresponds to the high membrane curvatures. For the other
-three cases efflux is dominated by influx, especially after $t=1$ day when
-the increase in total water content becomes non-negligible.
+three cases efflux is dominated by influx, especially after $t=1$ day
+when the increase in total water content becomes non-negligible.
 %
@@
 %
-Over time (about four weeks) all
-vesicles inflate and as expected, each vesicle eventually reaches a
-circular shape with reduced area $\alpha=1$. 
+Over time (about four weeks) all vesicles inflate and as expected, each
+vesicle eventually reaches a circular shape with reduced area
+$\alpha=1$. 
 %%These regions are denoted in blue and are only present at early times. 
@@
   influx and the blue regions correspond to efflux. (b) The steady
-  state vertical displacement for four different flow velocities. The
+  state vertical displacement at four different flow velocities. The
   steady state shapes are superimposed. (c) The reduced area of the
@@
 %in the non-dimensionalization 
-(see Supplementary Material) and $\chi$ is the
-shear rate of the planar shear flow $\uu_{\infty}(\xx) = \chi (y,0)$.
-When $\beta=0$ (impermeable case),  the vesicle reduced area and fluid
-viscosity contrast determine whether a vesicle tank treads or
+(see Supplementary Material) and $\chi$ is the shear rate of the planar
+shear flow $\uu_{\infty}(\xx) = \chi (y,0)$.  When $\beta=0$
+(impermeable case), the vesicle reduced area and fluid viscosity
+contrast determine whether a vesicle tank treads or
 tumbles~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. Focusing on
@@
 vesicle shape is independent of the initial reduced area. However, it
-does depend on the flow rate. We also observe that the amount of water inside the vesicle 
-remains constant until $t\sim 10$ minutes, when 
-%the vesicle starts to tank-tread and 
-the normal component of the flow velocity 
-becomes significantly smaller than the permeable velocity, leading to a
-changing reduced area.
+does depend on the flow rate. We also observe that the amount of water
+inside the vesicle remains constant until $t\sim 2$ hours, when the
+normal component of the flow velocity becomes significantly smaller than
+the permeable velocity, leading to a changing reduced area.
 
@@
 
-As observed for the planar shear flow, the equilibrium reduced area of a semipermeable vesicle in a Poiseuille flow is
-independent of the initial reduced area and $\beta$, and  larger maximum flow velocity $U$ results in
-smaller equilibrium reduced area, see Figure~\ref{fig:parabolicComposite}(a). At
-the smallest velocity $U= 200\; \mu$m/s, the steady state reduced
-area is large, and the equilibrium vesicle shape is an axisymmetric bullet. The equilibrium reduced area
-decreases with increasing $U$, and the nonlinear flow profile gives rise to 
-an asymmetric tank-treading slipper for $U\ge 400$ $\mu m/s$. We observe that the membrane
-permeability to water drastically alters the equilibrium vesicle shape and position
-relative to the Poiseuille flow: At $\beta=10^{-3}$ the equilibrium
-vesicle depends only on the maximum velocity $U$ of the nonlinear shear
-flow. The higher $U$ the smaller the equilibrium reduced area and the
-further away vesicle is relative to the flow center at $y=0$.
+As observed for the planar shear flow, the equilibrium reduced area of a
+semipermeable vesicle in a Poiseuille flow is independent of the initial
+reduced area and $\beta$, and  larger maximum flow velocity $U$ results
+in smaller equilibrium reduced area (see
+Figure~\ref{fig:parabolicComposite}(a)). At the smallest velocity $U=
+200\; \mu$m/s, the steady state reduced area is large, and the
+equilibrium vesicle shape is an axisymmetric bullet. The equilibrium
+reduced area decreases with increasing $U$, and the nonlinear flow
+profile gives rise to an asymmetric tank-treading slipper for $U\ge 400$
+$\mu m/s$. We observe that the membrane permeability to water
+drastically alters the equilibrium vesicle shape and position relative
+to the Poiseuille flow: At $\beta=10^{-3}$ the equilibrium vesicle
+depends only on the maximum velocity $U$ of the nonlinear shear flow.
+The higher $U$ the smaller the equilibrium reduced area and the further
+away vesicle is relative to the flow center at $y=0$.
 
@@
 When red blood cells go through small capillary vessels, they experience
-large shape deformation and significant membrane stretching that triggers ATP release
-%Cells experience stretching and release messengers when they pass
-%through capillary vessels
-~\cite{Wan2008_PNAS, ForsythWan2011_PNAS}. 
-Many cells exhibit extraordinary flexibility as they go
-through narrow vessels~\cite{AuStoreyMoore2016_PNAS}, and adjustment of
-area to volume ratio may be a key factor for a successful passage.  Here
-we quantify the effect of water permeability on a vesicle going through
-a stenosis (a long microfluidic channel with a width smaller than the
-cell radius).  Based on the findings in~\cite{abk-fai-sto2006}, we first
-examine the effect of semipermeability on the pressure fluctuation
-across a stenosed geometry. In this experiment, a pressure drop is used
-to squeeze a red blood cell through a constriction with diameter
-$5\;\mu$m and length $45\;\mu$m. We set up a similar computational
-geometry with a Poiseuille flow imposed at the inlet and outlet
-(Figure~\ref{fig:stenosisComposite}(a)). We fix the flow velocity $U_{\max} =
-1000 \;\mu$m/s at the inlet and outlet so
-that the residency time of the vesicle in the stenosis channel is $t_R
+large shape deformation and significant membrane stretching that
+triggers ATP release~\cite{Wan2008_PNAS, ForsythWan2011_PNAS}.  Many
+cells exhibit extraordinary flexibility as they go through narrow
+vessels~\cite{AuStoreyMoore2016_PNAS}, and adjustment of
+surface-to-volume ratio may be a key factor for a successful passage.
+Here we quantify the effect of water permeability on a vesicle going
+through a stenosis (a long microfluidic channel with a width smaller
+than the cell radius).  Based on the findings in~\cite{abk-fai-sto2006},
+we first examine the effect of semipermeability on the pressure
+fluctuation across a stenosed geometry. In this experiment, a pressure
+drop is used to squeeze a red blood cell through a constriction with
+diameter $5\;\mu$m and length $45\;\mu$m. We set up a similar
+computational geometry with a Poiseuille flow imposed at the inlet and
+outlet (Figure~\ref{fig:stenosisComposite}(a)). We set the maximum flow
+velocity to $U_{\max} = 1000 \;\mu$m/s at the inlet and outlet so that
+the residency time of the vesicle in the stenosis channel is $t_R
 \approx 25$ ms which agrees with the experimental
@@
 compute the excess pressure as a function of vesicle position in the
-channel, see Figure~\ref{fig:stenosisComposite}(c). The impermeable case
-agrees with experimental results~\cite{abk-fai-sto2006} (see Figure 3).
-Our simulations show that less excess pressure is needed to drive a
+channel (see Figure~\ref{fig:stenosisComposite}(c)). The impermeable
+case agrees with experimental results~\cite{abk-fai-sto2006} (see Figure
+3).  Our simulations show that less excess pressure is needed to drive a
 semipermeable vesicle through the closely-fit channel. Once in the
@@
 the beginning due to the high flow velocity, consistent with the results
-for a vesicle in a Poiseuille flow in open space (blue curves). As the
-vesicle enters the stenosis channel, it continues to deflate in the
-front even though we observe influx (red segment) at various rear
-locations in the membrane. Overall, the vesicle loses about 6.1\% of its
-initial total water at a constant rate as shown in
+for a vesicle in a Poiseuille flow in open space. As the vesicle enters
+the stenosis channel, it continues to deflate in the front even though
+we observe influx (red segment) at various rear locations in the
+membrane. Overall, the vesicle loses about 6.1\% of its initial total
+water at a constant rate as shown in
 Figures~\ref{fig:stenosisComposite}(d)
@@
 $U_{\max}=1000\;\mu$m/s, and we observe that vesicle stays inside the
-stenosis for a residence time $t_R \approx 70$ ms and the reduced area
-decreases by 13.2\% (red curves).
+stenosis for a residence time $t_R \approx 70$ ms and the area decreases
+by 13.2\% (red curves).
 
@@
   \caption{\label{fig:contractingComposite2} Vesicle reduced area and
-  velocity vs.~time. Permeability rate is $\beta = 10^{-3}$ and maximum
-  velocity is $18\;\mu$m/s. (a) A semipermeable vesicle passing through
-  six periods of the contracting geometry. (b) The reduced area with the
-  marks representing shapes in (a). (c) The vesicle velocity with the
-  marks representing shapes in (a). In (b) and (c), the bottom x-axis is
-  the x-coordinate of the center of mass, and the upper x-axis is time.
-  The colored vesicles show the tension distribution in N/m of the
-  circled vesicles. Throughout the entire simulation, these vesicle
-  configurations have the largest tension.}
+  velocity vs.~time. The permeability coefficient is $\beta = 10^{-3}$
+  and the maximum velocity is $18\;\mu$m/s. (a) A semipermeable vesicle
+  passing through six periods of the contracting geometry. (b) The
+  reduced area with the marks representing shapes in (a). (c) The
+  vesicle velocity with the marks representing shapes in (a). In (b) and
+  (c), the lower x-axis is the x-coordinate of the center of mass, and
+  the upper x-axis is time. The colored vesicles show the tension
+  distribution in N/m of the circled vesicles. Throughout the entire
+  simulation, these vesicle configurations have the largest tension.}
 \end{figure}
@@
 through the contraction, it first accelerates until it reaches the neck
-where it abruptly decelerates to go through the contraction. The
-variation of the reduced area and velocity with respect to time are also
-shown in Figure~\ref{fig:contractingComposite2}.
+where it abruptly decelerates to go through the contraction. The reduced
+area and velocity with respect to time are also shown in
+Figure~\ref{fig:contractingComposite2}.
 
 \section*{Discussion}
-In this work we investigated the effects of membrane permeability to
+In this work we investigate the effects of membrane permeability to
 water on vesicle hydrodynamics. Without any external flow or
@@
 few hours, when water influx begins to dominate and inflate the vesicle.
-Over a time scale of more than ten days, a semipermeable vesicle is
+Over a time scale of more than four weeks, a semipermeable vesicle is
 fully inflated, independent of its initial surface-to-volume ratio.
@@
 
-\acknow{We thank Howard Stone, Michael J. Shelley, Petia Vlahovska, Chaoqui Misbah, Manouk Abkarian, Sangwoo Shin and Shravan K. Veerapaneni for discussions. B.Q.~acknowledges support
-from the Simons Foundation, Mathematics and Physical
-Sciences-Collaboration Grants for Mathematicians, Award Number 527139.
-Y.-N.Y.~acknowledges support from NSF (DMS 1614863, DMS 195160) and
-Flatiron Institute, part of Simons Foundation.}
+\acknow{We thank Howard Stone, Michael J. Shelley, Petia Vlahovska,
+Chaoqui Misbah, Manouk Abkarian, Sangwoo Shin, and Shravan K.
+Veerapaneni for discussions. B.Q.~acknowledges support from the Simons
+Foundation, Mathematics and Physical Sciences-Collaboration Grants for
+Mathematicians, Award Number 527139.  Y.-N.Y.~acknowledges support from
+NSF (DMS 1614863, DMS 195160) and Flatiron Institute, part of Simons
+Foundation.}
 
@@
 by a double-layer potential with a density defined on $\partial\Omega$.
-The unknown density function allows us to satisfy the boundary condition
+The unknown density function is used to satisfy the boundary condition
 on $\partial\Omega$.
@@
 (Figure~\ref{fig:PoiseuillePhase}) with those in~\cite{kao-bir-mis2009}
-(see Figure 2), we observe quantitative agreement in the equilibrium vesicle shapes except that,
+(see Figure 2), we observe qualitative agreement in the equilibrium
+vesicle shapes except that,
 %
@@
 \nn$ and a term due to interface stretching~\cite{lai-tse-hua2008}, but
-this latter term term is zero because of the local inextensibility
-condition. Therefore,
+this latter term is zero because of the local inextensibility condition.
+Therefore,
 \begin{align}

### 2021-01-23 vesicle_code/docs/permeableVes/main.tex
yny

@@
 In this work we use boundary integral simulations to investigate the
-effects of native water permeability on the vesicle hydrodynamics due to
+effects of water permeability on the vesicle hydrodynamics due to
 a mechanical load, such as the viscous stress from an external flow
@@
 Under what condition is this a good assumption? Do liposomes conserve
-volume over hours under flow? What is the dynamic consequence when water
+volume under flow over a long time (hours)? What is the dynamic consequence when water
 influx/efflux affects the membrane hydrodynamics? To answer these
@@
 %BhatiaChrist2020_SoftMatt}, an 
-These results illustrate that the permeable water
+These results illustrate that the permeating water
 flow is inevitably coupled with the mechanical pressure jump across the
@@
 \begin{align}
+\label{eq:water_flux}
   \uu - \dot{\xx} = - k_w (R T \triangle c + \ff_\mathrm{mem} \cdot \nn) \nn, \qquad
@@
 $v_\mathrm{o}:v_\mathrm{t}:v_\mathrm{e}=10^{0}:10^{-2}:10^{-6}$.
-Furthermore, we note that in the absence of an osmotic stress, the permeating water
+Furthermore, we note that in the absence of an osmotic stress ($\triangle c = 0$), the permeating water
 flow may be non-negligible when the membrane tension becomes large due
@@
 
-For a semipermeable vesicle without confinement, our simulations show
-that the dynamic evolution towards equilibrium is dictated by the
-background flow field, while the permeability $\beta$ only rescales the
-time in the dynamics. With confinement, we find that we need to use
-larger values of $\beta$ to keep the membrane tension below the poration
-value $\sim 10^{-3}$ N/m. Such large values of $\beta$ may pertain to a
-lipid bilayer membrane with aquaporin proteins at a high temperature.
+Specifically we focus on the mechanical component of the water flux in Eq. (\ref{eq:water_flux}) with $\triangle c =0$ in this work.
+In our non-dimensionnalization the hydraulic conductivity is scaled to $R_0/\mu$ (where $R_0$ is a characteristic length and $\mu$ is the solvent viscosity): $\beta \equiv k_w/(R_0/\mu)$
+(see Supplementary Material): $\beta=0$ for an impermeable vesicle and $\beta>0$ for a semipermeable vesicle.
+%
+Under strong confinement,
+a large value of $\beta$ is needed in our simulations to keep the membrane tension below the threshold value for membrane poration
+$\sim 10^{-3}$ N/m. Such large value of $\beta$ may pertain to
+red blood cell membranes with aquaporin proteins.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Effects of membrane water permeability}
-We consider a single semipermeable vesicle, with dimensionless
-permeability coefficient $\beta$, in familiar configurations to
-highlight the effects of membrane water permeability. In free space we
+\section*{Hydrodynamics of a semipermeable vesicle in free space}
+To highlight the effects of membrane permeability for water,
+we consider a single semipermeable vesicle, with (dimensionless)
+permeability coefficient $\beta>0$, in familiar configurations: In free space we
 place a semipermeable vesicle in a quiescent flow, a planar shear flow,
-and a Poiseuille flow. We also consider a semipermeable vesicle in
-confinement: a long close-fitting channel and a contracting channel. For
-each example, we fix the vesicle length and examine the enclosed area as
+and a Poiseuille flow.  For each example, we fix the vesicle length and examine the enclosed water content as
 a dynamic consequence of water flow, vesicle shape deformation, and
@@
 
+Under these flows, our simulations show
+that the steady state of an impermeable vesicle is different from that of a semipermeable vesicle, which depends only on the strength of the external flow and does not depend on permeability $\beta$ (as long as $\beta>0$).
+Our simulations show that $\beta$ only rescales time in the dynamic evolution towards equilibrium.
 In experiments, vesicles under shear flows are measured for a few
@@
 geometry show that water permeability may lead to different vesicle
-hydrodynamics only after a duration of $\sim 1$ day. For vesicles in a
-narrow microfluidic channel, the experiments usually do not last longer
-than a few minutes~\cite{abk-fai-sto2006}. Our simulations show that
-strong confinement can lead to amplification of water permeation at a
-time scale shorter than a few minutes.
+hydrodynamics only after a duration of $\sim 1$ day.
+
 %short time scales.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{A semipermeable vesicle under strong confinement}
+Here we consider a semipermeable vesicle under strong
+confinement: a long closely-fit channel and a contracting channel.
+%
+In a narrow microfluidic channel, a large pressure jump is often needed to push the vesicle through a closely-fit channel~\cite{abk-fai-sto2006}.
+Our simulations show that such configuration can lead to amplification of water permeation at a
+time scale shorter than a few minutes. In addition, we find that a large value of $\beta$
+is needed to keep the membrane tension below the threshold value for membrane poration. 
+%
+Such high permeability for water may be regarded as an indication that the lipid bilayer membrane is porated under strong confinement, and our model vesicle is for a porated vesicle within the Helfrich free energy framework.
+As in the previous examples, we fix the vesicle length and examine the enclosed water content as
+a dynamic consequence of water flow, vesicle shape deformation, and
+membrane tension distribution.
+
 \subsection*{Semipermeable Vesicle in a Closely-fit Channel (Stenosis)}

### 2021-01-24 vesicle_code/docs/permeableVes/main.tex
minor touchups to paper

@@
 
-Specifically we focus on the mechanical component of the water flux in Eq. (\ref{eq:water_flux}) with $\triangle c =0$ in this work.
-In our non-dimensionnalization the hydraulic conductivity is scaled to $R_0/\mu$ (where $R_0$ is a characteristic length and $\mu$ is the solvent viscosity): $\beta \equiv k_w/(R_0/\mu)$
-(see Supplementary Material): $\beta=0$ for an impermeable vesicle and $\beta>0$ for a semipermeable vesicle.
-%
-Under strong confinement,
-a large value of $\beta$ is needed in our simulations to keep the membrane tension below the threshold value for membrane poration
-$\sim 10^{-3}$ N/m. Such large value of $\beta$ may pertain to
-red blood cell membranes with aquaporin proteins.
+Specifically we focus on the mechanical component of the water flux
+in~\eqref{eq:water_flux} with $\triangle c =0$.  In our
+non-dimensionalization the hydraulic conductivity is scaled to $R_0/\mu$
+(where $R_0$ is a characteristic length and $\mu$ is the solvent
+viscosity): $\beta \equiv k_w/(R_0/\mu)$ (see Supplementary Material):
+$\beta=0$ for an impermeable vesicle and $\beta>0$ for a semipermeable
+vesicle. Under strong confinement, a large value of $\beta$ is needed in
+our simulations to keep the membrane tension below the threshold value
+for membrane poration $\sim 10^{-3}$ N/m. Such large value of $\beta$
+may pertain to red blood cell membranes with aquaporin proteins.
 
@@
 
-As observed for the planar shear flow, the equilibrium reduced area of a
-semipermeable vesicle in a Poiseuille flow is independent of the initial
-reduced area and $\beta$, and  larger maximum flow velocity $U$ results
-in smaller equilibrium reduced area (see
-Figure~\ref{fig:parabolicComposite}(a)). At the smallest velocity $U=
-200\; \mu$m/s, the steady state reduced area is large, and the
-equilibrium vesicle shape is an axisymmetric bullet. The equilibrium
-reduced area decreases with increasing $U$, and the nonlinear flow
-profile gives rise to an asymmetric tank-treading slipper for $U\ge 400$
-$\mu m/s$. We observe that the membrane permeability to water
-drastically alters the equilibrium vesicle shape and position relative
-to the Poiseuille flow: At $\beta=10^{-3}$ the equilibrium vesicle
-depends only on the maximum velocity $U$ of the nonlinear shear flow.
-The higher $U$ the smaller the equilibrium reduced area and the further
-away vesicle is relative to the flow center at $y=0$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{A semipermeable vesicle under strong confinement}
-Here we consider a semipermeable vesicle under strong
-confinement: a long closely-fit channel and a contracting channel.
-%
-In a narrow microfluidic channel, a large pressure jump is often needed to push the vesicle through a closely-fit channel~\cite{abk-fai-sto2006}.
-Our simulations show that such configuration can lead to amplification of water permeation at a
-time scale shorter than a few minutes. In addition, we find that a large value of $\beta$
-is needed to keep the membrane tension below the threshold value for membrane poration. 
-%
-Such high permeability for water may be regarded as an indication that the lipid bilayer membrane is porated under strong confinement, and our model vesicle is for a porated vesicle within the Helfrich free energy framework.
-As in the previous examples, we fix the vesicle length and examine the enclosed water content as
-a dynamic consequence of water flow, vesicle shape deformation, and
-membrane tension distribution.
-
-\subsection*{Semipermeable Vesicle in a Closely-fit Channel (Stenosis)}
- \begin{figure*}[htp]
+ \begin{figure*}[hbp]
   \centering
@@
 
-\begin{figure}[hbp]
-  \centering
-  \ifTikz
-  \input{figures/contractingComposite.tikz}
-  \else
-  \includegraphics{figures/contractingComposite.pdf}
-  \fi
-  \caption{\label{fig:contractingComposite} A contracting channel
-  similar to the experimental configuration in~\cite{wu2015critical}.
-  The channel width varies from $18\;\mu$m to $1.8\;\mu$m, and it
-  repeats every $45\;\mu$m. The fluid flux along the red regions is into
-  the vesicle, and the fluid flux along the blue regions is out of the
-  vesicle.  (a--c): The ability for a semipermeable vesicle to pass
-  through the contraction depends on the permeability $\beta$. (d--f):
-  The ability for a semipermeable vesicle to pass through the
-  contraction depends on the flow rate. The colored vesicles show the
-  tension distribution in N/m of the circled vesicles. Throughout the
-  entire simulation, these vesicle configurations have the largest
-  tension.}
-\end{figure}
-
+As observed for the planar shear flow, the equilibrium reduced area of a
+semipermeable vesicle in a Poiseuille flow is independent of the initial
+reduced area and $\beta$, and  larger maximum flow velocity $U$ results
+in smaller equilibrium reduced area (see
+Figure~\ref{fig:parabolicComposite}(a)). At the smallest velocity $U=
+200\; \mu$m/s, the steady state reduced area is large, and the
+equilibrium vesicle shape is an axisymmetric bullet. The equilibrium
+reduced area decreases with increasing $U$, and the nonlinear flow
+profile gives rise to an asymmetric tank-treading slipper for $U\ge 400$
+$\mu m/s$. We observe that the membrane permeability to water
+drastically alters the equilibrium vesicle shape and position relative
+to the Poiseuille flow: At $\beta=10^{-3}$ the equilibrium vesicle
+depends only on the maximum velocity $U$ of the nonlinear shear flow.
+The higher $U$ the smaller the equilibrium reduced area and the further
+away vesicle is relative to the flow center at $y=0$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{A semipermeable vesicle under strong confinement}
+Here we consider a semipermeable vesicle under strong confinement: a
+long closely-fit channel and a contracting channel. In a narrow
+microfluidic channel, a large pressure jump is often needed to push the
+vesicle through a closely-fit channel~\cite{abk-fai-sto2006}.  Our
+simulations show that such a configuration can lead to an amplification
+of water permeation at a time scale shorter than a few minutes. In
+addition, we find that a large value of $\beta$ is needed to keep the
+membrane tension below the threshold value for membrane poration. Such
+high permeability for water may be regarded as an indication that the
+lipid bilayer membrane is porated under strong confinement, and our
+model vesicle is for a porated vesicle within the Helfrich free energy
+framework.  As in the previous examples, we fix the vesicle length and
+examine the enclosed water content as a dynamic consequence of water
+flow, vesicle shape deformation, and membrane tension distribution.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Semipermeable Vesicle in a Closely-fit Channel (Stenosis)}
 When red blood cells go through small capillary vessels, they experience
@@
 the excess pressure.
+\begin{figure}[htp]
+  \centering
+  \ifTikz
+  \input{figures/contractingComposite.tikz}
+  \else
+  \includegraphics{figures/contractingComposite.pdf}
+  \fi
+  \caption{\label{fig:contractingComposite} A contracting channel
+  similar to the experimental configuration in~\cite{wu2015critical}.
+  The channel width varies from $18\;\mu$m to $1.8\;\mu$m, and it
+  repeats every $45\;\mu$m. The fluid flux along the red regions is into
+  the vesicle, and the fluid flux along the blue regions is out of the
+  vesicle.  (a--c): The ability for a semipermeable vesicle to pass
+  through the contraction depends on the permeability $\beta$. (d--f):
+  The ability for a semipermeable vesicle to pass through the
+  contraction depends on the flow rate. The colored vesicles show the
+  tension distribution in N/m of the circled vesicles. Throughout the
+  entire simulation, these vesicle configurations have the largest
+  tension.}
+\end{figure}
 
@@
 maximum flow rate of $U_{\max}$. We initialize a semipermeable vesicle
-with $\alpha = 0.65$ that spans $10\; \mu$m of the total channel width and
-investigate the effects of the membrane permeability to water and the
-maximum flow velocity on whether a vesicle can successfully pass through
-the slit. We color the vesicle according to the sign of its flux---red
-for influx and blue for efflux.
+with $\alpha = 0.65$ that spans $10\; \mu$m of the total channel width
+and investigate the effects of the membrane permeability to water and
+the maximum flow velocity on whether a vesicle can successfully pass
+through the slit. We color the vesicle according to the sign of its
+flux---red for influx and blue for efflux.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Discussion}
@@
 
-\acknow{We thank Howard Stone, Michael J. Shelley, Petia Vlahovska,
-Chaoqui Misbah, Manouk Abkarian, Sangwoo Shin, and Shravan K.
-Veerapaneni for discussions. B.Q.~acknowledges support from the Simons
-Foundation, Mathematics and Physical Sciences-Collaboration Grants for
-Mathematicians, Award Number 527139.  Y.-N.Y.~acknowledges support from
-NSF (DMS 1614863, DMS 195160) and Flatiron Institute, part of Simons
-Foundation.}
+\acknow{We thank Howard Stone, Michael J.~Shelley, Petia Vlahovska,
+Chaoqui Misbah, Manouk Abkarian, Sangwoo Shin, and Shravan
+K.~Veerapaneni for discussions. B.Q.~acknowledges support from the
+Simons Foundation, Mathematics and Physical Sciences-Collaboration
+Grants for Mathematicians, Award Number 527139.  Y.-N.Y.~acknowledges
+support from NSF (DMS 1614863, DMS 195160) and Flatiron Institute, part
+of Simons Foundation.}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Supplementary Material: Formulation}
@@
 
-\subsection*{Vesicle in a planar shear flow}
+\subsection*{Vesicle in a Planar Shear Flow}
 Our simulations of a semipermeable vesicle in a planar shear flow show
@@
 
-\subsection*{Vesicle in a closely-fit channel}
+\subsection*{Vesicle in a Closely-Fit Channel}
 When a semipermeable vesicle goes through a closely-fit channel, we observe that the water efflux is found in the front, and the influx is in the rear of the vesicle membrane (Figure~\ref{fig:stenosisComposite}).
@@
 
-\subsection*{Vesicle going through a contracting channel (slit)}
+\subsection*{Vesicle Going Through a Contracting Channel (Slit)}
 When a semipermeable vesicle goes through a contracting channel (slit)

### 2021-01-25 vesicle_code/docs/permeableVes/main.tex
yny
edited up to start of Quiescent flow

@@
 %\authordeclaration{Please declare any competing interests here.}
-\correspondingauthor{\textsuperscript{1} E-mail: yyoung@njit.edu}
+\correspondingauthor{\textsuperscript{1} Corresponding author's e-mail: yyoung@njit.edu}
 
@@
 where $\nn$ is the outward normal (Figure~\ref{fig:sketch}), $k_w$ is
-the hydraulic conductivity, $R$ is the ideal gas constant, $T$ is the
-temperature (K), $\triangle c$ is contrast in a solute concentration
-(mol/volume), and $\ff_\mathrm{mem}$ is the membrane stress that
-consists of both bending $ \ff_\mathrm{ben}= -k_b \xx_{ssss}$ and
-tension $\ff_\mathrm{ten}=(\sigma \xx_s)_s$ ($s$ is the arclength and
-$\sigma$ is the membrane tension along the membrane, see Supplementary
-Material). Using $k_w\sim 10^{-12}$ m$^2$s/kg 
+the hydraulic conductivity (m$^2$s/kg), $R$ is the ideal gas constant,
+$T$ is the temperature (K), $\triangle c$ is contrast in a solute
+concentration (mol/volume), and $\ff_\mathrm{mem}$ is the membrane
+stress that consists of both bending $ \ff_\mathrm{ben}= -k_b
+\xx_{ssss}$ and tension $\ff_\mathrm{ten}=(\sigma \xx_s)_s$, where $s$
+is the arclength and $\sigma$ depends on the membrane tension (see
+Supplementary Material). Using $k_w\sim 10^{-12}$ m$^2$s/kg 
 %(typical of mammalian cell membranes~\cite{LiMoriSun2015_PRL}) 
-and an osmolarity $\triangle c =
-0.1$ mol/L (consistent with the osmotic filtration experiments~\cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the corresponding
-water flow is of the order $v_\mathrm{o}=0.1 \; \mu$m/s. Assuming a
-membrane bending stiffness of $k_b = 10^{-19}$ J, a membrane tension of
-$10^{-3}$ N/m (one tenth of the lysis tension), and a characteristic
-length scale of $10^{-6}$ m, the tension contribution ($v_\mathrm{t}$)
-and elastic stress contribution ($v_\mathrm{e}$) to the permeable water
-flow can be scaled to $v_\mathrm{o}$ as
+and an osmolarity $\triangle c = 0.1$ mol/L (consistent with the osmotic
+filtration experiments~\cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the
+corresponding water flow is of the order $v_\mathrm{o}=0.1 \; \mu$m/s.
+Assuming a membrane bending stiffness of $k_b = 10^{-19}$ J, a membrane
+tension of $10^{-3}$ N/m (one tenth of the lysis tension), and a
+characteristic length scale of $10^{-6}$ m, the tension contribution
+($v_\mathrm{t}$) and elastic stress contribution ($v_\mathrm{e}$) to the
+permeable water flow can be scaled to $v_\mathrm{o}$ as
 $v_\mathrm{o}:v_\mathrm{t}:v_\mathrm{e}=10^{0}:10^{-2}:10^{-6}$.
-Furthermore, we note that in the absence of an osmotic stress ($\triangle c = 0$), the permeating water
-flow may be non-negligible when the membrane tension becomes large due
-to the external stress such as the hydrodynamic stress from an
-external flow or confinement. In the following we explore both.
+Furthermore, we note that in the absence of an osmotic stress
+($\triangle c = 0$), the permeating water flow may be non-negligible
+when the membrane tension becomes large due to the external stress such
+as the hydrodynamic stress from an external flow or confinement. In the
+following we explore both.
 
@@
 \section*{Hydrodynamics of a semipermeable vesicle in free space}
-To highlight the effects of membrane permeability for water,
-we consider a single semipermeable vesicle, with (dimensionless)
-permeability coefficient $\beta>0$, in familiar configurations: In free space we
+To highlight the effects of membrane permeability to water, we consider
+a single semipermeable vesicle, with (dimensionless) permeability
+coefficient $\beta>0$, in familiar configurations: In free space we
 place a semipermeable vesicle in a quiescent flow, a planar shear flow,
-and a Poiseuille flow.  For each example, we fix the vesicle length and examine the enclosed water content as
-a dynamic consequence of water flow, vesicle shape deformation, and
-membrane tension distribution.
+and a Poiseuille flow. For each example, we fix the vesicle length and
+examine the enclosed water content as a dynamic consequence of water
+flow, vesicle shape deformation, and membrane tension distribution.
 

### 2021-01-26 vesicle_code/docs/permeableVes/main.tex
minor changes throughout

@@
 tension, and elastic stress of a semipermeable membrane under various
-flowing conditions and confinement (see Figure~\ref{fig:sketch}).
+flowing conditions and confinement (Figure~\ref{fig:sketch}).
 %Specifically our numerical simulations yield the quantification of the
@@
 \section*{Formulation}
-\begin{figure*}[hbp]
+\begin{figure*}[htp]
   \centering
@@
 \xx_{ssss}$ and tension $\ff_\mathrm{ten}=(\sigma \xx_s)_s$, where $s$
-is the arclength and $\sigma$ depends on the membrane tension (see
+is the arclength, $\sigma = \Lambda - \frac{3}{2}\kappa^2$, $\Lambda$ is the
+membrane tension, and $\kappa$ is the membrane curvature (see
 Supplementary Material). Using $k_w\sim 10^{-12}$ m$^2$s/kg 
@@
 (where $R_0$ is a characteristic length and $\mu$ is the solvent
-viscosity): $\beta \equiv k_w/(R_0/\mu)$ (see Supplementary Material):
-$\beta=0$ for an impermeable vesicle and $\beta>0$ for a semipermeable
+viscosity): $\beta = k_w/(R_0/\mu)$ (see Supplementary Material),
+$\beta=0$ for an impermeable vesicle, and $\beta>0$ for a semipermeable
 vesicle. Under strong confinement, a large value of $\beta$ is needed in
@@
 \subsection*{Planar Shear Flow}
-\begin{figure*}[hbp]
+We consider a semipermeable vesicle in a planar shear flow,
+characterized by the elastic capillary number $Ca_\mathrm{E}=\chi\tau$ where $\tau$ is the characteristic time scale from balancing the viscous stress with the elastic stress
+%in the non-dimensionalization 
+(see Supplementary Material) and $\chi$ is the shear rate of the planar
+shear flow $\uu_{\infty}(\xx) = \chi (y,0)$.  When $\beta=0$
+(impermeable case), the vesicle reduced area and fluid viscosity
+contrast determine whether a vesicle tank treads or
+tumbles~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. Focusing on
+semipermeable vesicles with no viscosity contrast, we find that a
+semipermeable vesicle tilts to an inclination angle and undergoes
+tank-treading dynamics, similar to the case of an impermeable vesicle.
+
+In Figure~\ref{fig:shearComposite}(a), using four initial reduced areas
+and two flow rates, we plot the reduced area of a semipermeable vesicle
+with $\beta = 10^{-3}$. As observed in a quiescent flow, the final
+vesicle shape is independent of the initial reduced area. However, it
+does depend on the flow rate. We also observe that the amount of water
+inside the vesicle remains constant until $t\sim 2$ hours, when the
+normal component of the flow velocity becomes significantly smaller than
+the permeable velocity, leading to a changing reduced area.
+
+For a variety of dimensionless permeability coefficient $\beta>0$ and
+capillary number $Ca_\mathrm{E}$, a semipermeable vesicle reaches an
+equilibrium shape as in Figure~\ref{fig:shearComposite}(a). Since the
+equilibrium shape depends on $Ca_\mathrm{E}$ and is independent of the
+initial reduced area, we initialize the vesicle with reduced area
+$\alpha = 0.65$ for all simulations in
+Figure~\ref{fig:shearComposite}(b), where we summarize the equilibrium
+vesicle shape and its reduced area. We see that the capillary number
+(flow rate) significantly affects the final vesicle shape, but the
+permeability coefficient has a very minor effect. Instead, as we saw in
+the quiescent analysis, $\beta$ sets a time scale since the time
+required for a vesicle to reach its steady state configuration is
+proportional to $\beta^{-1}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Poiseuille Flow}
+\begin{figure*}[htp]
   \centering
@@
 
-We consider a semipermeable vesicle in a planar shear flow,
-characterized by the elastic capillary number $Ca_\mathrm{E}=\chi\tau$ where $\tau$ is the characteristic time scale from balancing the viscous stress with the elastic stress
-%in the non-dimensionalization 
-(see Supplementary Material) and $\chi$ is the shear rate of the planar
-shear flow $\uu_{\infty}(\xx) = \chi (y,0)$.  When $\beta=0$
-(impermeable case), the vesicle reduced area and fluid viscosity
-contrast determine whether a vesicle tank treads or
-tumbles~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. Focusing on
-semipermeable vesicles with no viscosity contrast, we find that a
-semipermeable vesicle tilts to an inclination angle and undergoes
-tank-treading dynamics, similar to the case of an impermeable vesicle.
-
-In Figure~\ref{fig:shearComposite}(a), using four initial reduced areas
-and two flow rates, we plot the reduced area of a semipermeable vesicle
-with $\beta = 10^{-3}$. As observed in a quiescent flow, the final
-vesicle shape is independent of the initial reduced area. However, it
-does depend on the flow rate. We also observe that the amount of water
-inside the vesicle remains constant until $t\sim 2$ hours, when the
-normal component of the flow velocity becomes significantly smaller than
-the permeable velocity, leading to a changing reduced area.
-
-For a variety of dimensionless permeability coefficient $\beta>0$ and capillary number $Ca_\mathrm{E}$, a
-semipermeable vesicle reaches an equilibrium shape as in
-Figure~\ref{fig:shearComposite}(a). Since the equilibrium shape is selected by $Ca_\mathrm{E}$ and independent
-of the initial reduced area, we initialize the vesicle with reduced area
-$\alpha = 0.65$ for all simulations in
-Figure~\ref{fig:shearComposite}(b), where we summarize the equilibrium
-vesicle shape and its reduced area. We see that the capillary number
-(flow rate) significantly affects the final vesicle shape, but the
-permeability coefficient has a very minor effect. Instead, as we saw in the
-quiescent analysis, $\beta$ sets a time scale since the time required
-for a vesicle to reach its steady state configuration is proportional to
-$\beta^{-1}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Poiseuille Flow}
-
 We consider a semipermeable vesicle in the Poiseuille flow $\uu =
@@
 
-At the beginning of the simulations a semipermeable vesicle is
-placed above the center line $y=0$, and it migrates towards the
-center line as in the impermeable case~\cite{dan-vla-mis2009}. 
+At the beginning of the simulations, a semipermeable vesicle is placed
+above the center line $y=0$ and it migrates towards the center line as
+in the impermeable case~\cite{dan-vla-mis2009}. 
 %
@@
 reduced area and $\beta$, and  larger maximum flow velocity $U$ results
-in smaller equilibrium reduced area (see
-Figure~\ref{fig:parabolicComposite}(a)). At the smallest velocity $U=
+in smaller equilibrium reduced area
+(Figure~\ref{fig:parabolicComposite}(a)). At the smallest velocity $U=
 200\; \mu$m/s, the steady state reduced area is large, and the
@@
 depends only on the maximum velocity $U$ of the nonlinear shear flow.
-The higher $U$ the smaller the equilibrium reduced area and the further
-away vesicle is relative to the flow center at $y=0$.
+The higher $U$ the smaller the equilibrium reduced area and the farther
+away the vesicle is relative to the flow center at $y=0$.
 
@@
 compute the excess pressure as a function of vesicle position in the
-channel (see Figure~\ref{fig:stenosisComposite}(c)). The impermeable
-case agrees with experimental results~\cite{abk-fai-sto2006} (see Figure
-3).  Our simulations show that less excess pressure is needed to drive a
+channel (Figure~\ref{fig:stenosisComposite}(c)). The impermeable case
+agrees with experimental results~\cite{abk-fai-sto2006} (see Figure 3).
+Our simulations show that less excess pressure is needed to drive a
 semipermeable vesicle through the closely-fit channel. Once in the
 channel, the vesicle takes a bullet shape with maximum tension in the
-front and minimum tension in the back (see
-Figure~\ref{fig:stenosisComposite}(a)), consistent with earlier
+front and minimum tension in the back
+(Figure~\ref{fig:stenosisComposite}(a)), consistent with earlier
 results~\cite{Pak2015_PNAS, HarmanBertrandJoos2017_CJP}.
@@
 ZhangShenHoganBarakatMisbah2018_BJ, LuoBai2019_PoF}. Red blood cells go
-through submicron slits many times during their lifetime, and such
+through submicron slits many times during their lifetime, and this
 process selects healthy, flexible red blood cells to
@@
 repeatedly passes through micro-capillary vessels or sub-micron slits,
-we construct a contracting geometry (see
-Figure~\ref{fig:contractingComposite2}) to simulate a vesicle passing
+we construct a contracting geometry
+(Figure~\ref{fig:contractingComposite2}) to simulate a vesicle passing
 through the contracting geometry six times.  In
@@
 
-% \bibliographystyle{plain}
+% \bibliographystyle{pnas-new}
  \bibliography{refs}
@@
 Following~\cite{vee-gue-zor-bir2009}, we introduce the variable $\sigma
-= \Lambda - 1.5\kappa^2$, where $\kappa$ is the vesicle curvature. Then,
+= \Lambda - \frac{3}{2}\kappa^2$, where $\kappa$ is the vesicle curvature. Then,
 the bending and tension forces corresponding to the Helfrich energy are
@@
 = 10^{-19}$ J, and fluid viscosity $5 \times 10^{-2}$ kg/ms. We scale
-time by $\tau\equiv\mu R_0^3/k_b = 0.5\;s$, the velocity by $R_0/\tau =
-2\;\mu$m/s, the pressure by $k_b/R_0^3 = 10^{-1}$ Pa, tension by
-$k_b/R_0^2 = 10^{-7}$ N/m, and the permeability by $R_0/\mu = 10^{-3}$ m$^2$s/kg. Under this nondimensionalization, a two-dimensional
+time by $\tau = \mu R_0^3/k_b = 0.5\;s$, the velocity by $R_0/\tau =
+2\;\mu$m/s, the pressure by $k_b/R_0^3 = 10^{-1}$ Pa, the tension by
+$k_b/R_0^2 = 10^{-7}$ N/m, and the permeability by $R_0/\mu = 10^{-3}$
+m$^2$s/kg. Under this nondimensionalization, a two-dimensional
 semipermeable vesicle in a viscous fluid is characterized by (a) its
 reduced area $\alpha = 4\pi A/L^2 \in (0,1]$, where $L$ is the vesicle
-length and $A$ is its area, and (b) its permeability $\beta =
-k_w \mu /R_0$.  
-We convert the apparent permeability of 
-a polyunsaturated PC bilayer  \cite{OlbrichRawiczNeedhamEtAl2000_BJ}
-to the hydraulic conductivity $k_w$ using the conversion in \cite{FettiplaceHaydon1980_PhysRev}, and  found that 
-$10^{-14}\le k_w\le 10^{-12}$ m$^2$s/kg, thus $\beta$ is  in the range $10^{-11}\le \beta\le 10^{-9}$.
-
-In two dimensions, the membrane length is conserved by
-the local inextensibility condition, but the enclosed area is not
-conserved because of semipermeability. Therefore, the reduced area is
-dynamic.
-%
+length and $A$ is its area, and (b) its permeability $\beta = k_w \mu
+/R_0$. In two dimensions, the membrane length is conserved by the local
+inextensibility condition, but the enclosed area is not conserved
+because of semipermeability. Therefore, the reduced area is dynamic. We
+convert the apparent permeability of a polyunsaturated PC
+bilayer~\cite{OlbrichRawiczNeedhamEtAl2000_BJ} to the hydraulic
+conductivity $k_w$ using the conversion
+in~\cite{FettiplaceHaydon1980_PhysRev}, and found that $10^{-14}\le
+k_w\le 10^{-12}$ m$^2$s/kg, thus $\beta$ is in the range $10^{-11}\le
+\beta\le 10^{-9}$.
+
 Since the fluid satisfies the Stokes equations, the velocity and
@@
 In confined geometries, the far field term $\uu_\infty(\xx)$ is replaced
-by a double-layer potential with a density defined on $\partial\Omega$.
-The unknown density function is used to satisfy the boundary condition
-on $\partial\Omega$.
+by a double-layer potential with an unknown density defined on
+$\partial\Omega$. The density function is used to satisfy the boundary
+condition on $\partial\Omega$.
 
@@
 vesicle's position and tension and the unknown density function for
-confined flows. Both $\gamma$ and $\partial\Omega$ are discretized at
-$N$ and $N_\text{wall}$ points, respectively. Derivatives are computed
-with Fourier differentiation, and the eighth-order
-quadrature~\cite{alp1999} is applied to the weakly singular single-layer
-potential. For confined geometries, the trapezoid rule is used to
-approximate the double-layer potential since its kernel is smooth and
-periodic. Nearly-singular integrals are computed with an
-interpolation-based quadrature rule~\cite{qua-bir2014}.
+confined flows. Both $\gamma$ and $\partial\Omega$ are discretized at a
+set of collocation points. Derivatives are computed with Fourier
+differentiation, and the eighth-order quadrature~\cite{alp1999} is
+applied to the weakly singular single-layer potential. For confined
+geometries, the trapezoid rule is used to approximate the double-layer
+potential since its kernel is smooth and periodic. Nearly-singular
+integrals are computed with an interpolation-based quadrature
+rule~\cite{qua-bir2014}.
 
@@
 tension is uniform and equal to $k_b \kappa_0^2/2$ as predicted by our
-analysis (see \eqref{eqn:areaROC2}). In the bottom row
+analysis (see~\eqref{eqn:areaROC2}). In the bottom row
 ($\alpha(0)=0.12$), the initial vesicle shape has a lot of high
@@
   distribution of a semipermeable vesicle with $\beta=10^{-3}$ in a parabolic
-  flow (see Figure~\ref{fig:parabolicComposite}). The flow velocities
+  flow (Figure~\ref{fig:parabolicComposite}). The flow velocities
   are (a) 200 $\mu$m/s, (b) 400 $\mu$m/s, (c) 600 $\mu$m/s, and (d)
@@
 membrane permeability have to be sufficiently large for a successful
-passage through the slit (see Figure~\ref{fig:contractingComposite}). As
+passage through the slit (Figure~\ref{fig:contractingComposite}). As
 the vesicle goes through the contracting channel, the gradual

### 2021-01-26 vesicle_code/docs/permeableVes/main.tex
first draft of concluding paragraph

@@
 
+Using scaling arguments, we showed that permeability due to osmolarity
+is two orders of magnitude larger than permeability due to tension, and
+six orders of magnitude larger than permeability due to bending.
+Therefore, future studies will investigate semi-permeability in the
+presence of a solute concentration. The presence of such a solute
+concentrations is responsible for many physiological processes including
+cell migration in confined
+microenvironments~\cite{StrokaJiangChenEtAl2014_Cell},
+dialysis~\cite{wan2006}, and
+apoptosis~\cite{marchetti1996mitochondrial}. We plan to investigate
+vesicle motion in a solute in the zero Peclet number limit which was
+analyzed for spherical vesicles by Anderson~\cite{and1983} and more
+general shapes using a finite element method by Jaeger {\em et
+al.}~\cite{jae-car-med-try1999}.
+
 \acknow{We thank Howard Stone, Michael J.~Shelley, Petia Vlahovska,

### 2021-01-26 vesicle_code/docs/permeableVes/main.tex
yny

@@
 flow, vesicle shape deformation, and membrane tension distribution.
-
+%
 Under these flows, our simulations show
-that the steady state of an impermeable vesicle is different from that of a semipermeable vesicle, which depends only on the strength of the external flow and does not depend on permeability $\beta$ (as long as $\beta>0$).
-Our simulations show that $\beta$ only rescales time in the dynamic evolution towards equilibrium.
+that the steady state of an impermeable vesicle is different from that of a semipermeable vesicle, which depends only on the strength of the external flow and is insensitive to permeability $\beta$ (as long as $\beta>0$).
+We find that  the time in the dynamic evolution towards equilibrium is scaled by $\beta^{-1}$: the smaller $\beta$ is the longer it takes to reach the steady state.
+
 In experiments, vesicles under shear flows are measured for a few

### 2021-01-28 vesicle_code/docs/permeableVes/main.tex

@@
 microenvironments~\cite{StrokaJiangChenEtAl2014_Cell},
-dialysis~\cite{wan2006}, and
+dialysis~\cite{wan2006}, cell desiccation~\cite{vogl2014effect} and
 apoptosis~\cite{marchetti1996mitochondrial}. We plan to investigate

### 2021-01-28 vesicle_code/docs/permeableVes/main.tex
worked on discussion

--- 2021-01-26 vesicle_code/docs/permeableVes/main.tex
@@
 
+To understand the effects of water permeability on a vesicle that
+repeatedly passes through micro-capillary vessels or sub-micron slits,
+we construct a contracting geometry
+(Figure~\ref{fig:contractingComposite2}) to simulate a vesicle passing
+through the contracting geometry six times.  In
+Figure~\ref{fig:contractingComposite2}(b), we show that the vesicle
+deflates each time it passes through the contraction followed by a
+gradual inflation (over seconds). The total area loss over the history
+of the vesicle is almost 50\%. In
+Figure~\ref{fig:contractingComposite2}(c), we show the vesicle velocity
+as a function of the vesicle's center of mass. As the vesicle passes
+through the contraction, it first accelerates until it reaches the neck
+where it abruptly decelerates to go through the contraction. The reduced
+area and velocity with respect to time are also shown in
+Figure~\ref{fig:contractingComposite2}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Discussion}
+In this work we investigate the effects of membrane permeability to
+water on vesicle hydrodynamics. Without any external flow or
+confinement, our analysis shows that a semipermeable vesicle always
+inflates to maximize the water content inside the vesicle of a fixed
+length (area) in two (three) dimensions. Results from analysis and
+numerical simulation show that such relaxation of a semipermeable
+vesicle is characterized by a rescaled time $\beta t$. We further
+illustrate that the relaxation process consists of at least two phases:
+The first phase is dominated by the balance between membrane traction
+and viscous stress at early times (up to five minutes), when the vesicle
+behaves like an impermeable membrane. The second phase sets in after a
+few hours, when water influx begins to dominate and inflate the vesicle.
+Over a time scale of more than four weeks, a semipermeable vesicle is
+fully inflated, independent of its initial surface-to-volume ratio.
+
 \begin{figure}[hbp]
@@
 
-To understand the effects of water permeability on a vesicle that
-repeatedly passes through micro-capillary vessels or sub-micron slits,
-we construct a contracting geometry
-(Figure~\ref{fig:contractingComposite2}) to simulate a vesicle passing
-through the contracting geometry six times.  In
-Figure~\ref{fig:contractingComposite2}(b), we show that the vesicle
-deflates each time it passes through the contraction followed by a
-gradual inflation (over seconds). The total area loss over the history
-of the vesicle is almost 50\%. In
-Figure~\ref{fig:contractingComposite2}(c), we show the vesicle velocity
-as a function of the vesicle's center of mass. As the vesicle passes
-through the contraction, it first accelerates until it reaches the neck
-where it abruptly decelerates to go through the contraction. The reduced
-area and velocity with respect to time are also shown in
-Figure~\ref{fig:contractingComposite2}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Discussion}
-In this work we investigate the effects of membrane permeability to
-water on vesicle hydrodynamics. Without any external flow or
-confinement, our analysis shows that a semipermeable vesicle always
-inflates to maximize the water content inside the vesicle of a fixed
-length (area) in two (three) dimensions. Results from analysis and
-numerical simulation show that such relaxation of a semipermeable
-vesicle is characterized by a rescaled time $\beta t$. We further
-illustrate that the relaxation process consists of at least two phases:
-The first phase is dominated by the balance between membrane traction
-and viscous stress at early times (up to five minutes), when the vesicle
-behaves like an impermeable membrane. The second phase sets in after a
-few hours, when water influx begins to dominate and inflate the vesicle.
-Over a time scale of more than four weeks, a semipermeable vesicle is
-fully inflated, independent of its initial surface-to-volume ratio.
-
 Under strong confinement we show that water permeation can be amplified
@@
 six orders of magnitude larger than permeability due to bending.
-Therefore, future studies will investigate semi-permeability in the
-presence of a solute concentration. The presence of such a solute
-concentrations is responsible for many physiological processes including
-cell migration in confined
-microenvironments~\cite{StrokaJiangChenEtAl2014_Cell},
-dialysis~\cite{wan2006}, and
-apoptosis~\cite{marchetti1996mitochondrial}. We plan to investigate
-vesicle motion in a solute in the zero Peclet number limit which was
-analyzed for spherical vesicles by Anderson~\cite{and1983} and more
-general shapes using a finite element method by Jaeger {\em et
-al.}~\cite{jae-car-med-try1999}.
+Therefore, future studies will investigate semipermeable membranes
+suspended in a solvent with a solute concentration. The presence of a
+solute is responsible for many physiological processes including cell
+migration in confined
+microenvironments~\cite{StrokaJiangChenEtAl2014_Cell,
+papadopoulos2008aquaporins}, dialysis~\cite{wan2006}, cell
+desiccation~\cite{vogl2014effect}, and
+apoptosis~\cite{marchetti1996mitochondrial}. While the solute dynamics
+is governed by an advection-diffusion equation, many biophysical
+applications involve speeds no greater than $\sim 50$
+$\mu$m/hour~\cite{StrokaJiangChenEtAl2014_Cell}, a length scale of 10
+$\mu$m, and a solute diffusivity of $\sim 10^{-10}$ m$^2$/s (glucose in
+water). The resulting Peclet number is $\sim 10^{-2}$, and this limit
+has been analyzed for spherical vesicles by Anderson~\cite{and1983} and
+more general shapes using a finite element method by Jaeger {\em et
+al.}~\cite{jae-car-med-try1999}. Since the dynamics of the concentration
+is diffusion-dominated, we will use a stable and accurate boundary
+integral method that is similar to the numerical method we apply to the
+hydrodynamics (see Supplementary Material).
 

### 2021-01-28 vesicle_code/docs/permeableVes/main.tex
yny

@@
 desiccation~\cite{vogl2014effect}, and
-apoptosis~\cite{marchetti1996mitochondrial}. While the solute dynamics
-is governed by an advection-diffusion equation, many biophysical
-applications involve speeds no greater than $\sim 50$
-$\mu$m/hour~\cite{StrokaJiangChenEtAl2014_Cell}, a length scale of 10
-$\mu$m, and a solute diffusivity of $\sim 10^{-10}$ m$^2$/s (glucose in
-water). The resulting Peclet number is $\sim 10^{-2}$, and this limit
-has been analyzed for spherical vesicles by Anderson~\cite{and1983} and
-more general shapes using a finite element method by Jaeger {\em et
-al.}~\cite{jae-car-med-try1999}. Since the dynamics of the concentration
-is diffusion-dominated, we will use a stable and accurate boundary
-integral method that is similar to the numerical method we apply to the
-hydrodynamics (see Supplementary Material).
+apoptosis~\cite{marchetti1996mitochondrial}.
+
+Cells exhibit a dynamic volume-to-surface ratio in 
+many physiological processes, such as 
+cell migration in confined microenvironments~\cite{StrokaJiangChenEtAl2014_Cell, papadopoulos2008aquaporins}, 
+dialysis~\cite{wan2006}, cell desiccation~\cite{vogl2014effect}, cell division~\cite{FredChang} and
+apoptosis~\cite{marchetti1996mitochondrial}.
+%osmotic flow across the membrane.
+While osmotic stress  is more effective and efficient than mechanical stress in contributing to change in cellular volume, our results suggest that the water permeation due to the capillary pressure may be non-negligible over long times and/or under strong confinement in these physiological processes.
+Currently we are investigating the effects of osmotic stress in the small Peclet number limit, which is relevant to cellular migration in the presence of both confinement and a solute gradient~\cite{StrokaJiangChenEtAl2014_Cell} and has been studied numerically by Jaeger {\em et al.}~\cite{jae-car-med-try1999}
+
+%While the solute dynamics
+%is governed by an advection-diffusion equation, many biophysical
+%applications involve speeds no greater than $\sim 50$
+%$\mu$m/hour~\cite{StrokaJiangChenEtAl2014_Cell}, a length scale of 10
+%$\mu$m, and a solute diffusivity of $\sim 10^{-10}$ m$^2$/s (glucose in
+%water). The resulting Peclet number is $\sim 10^{-2}$, and this limit
+%has been analyzed for spherical vesicles by Anderson~\cite{and1983} and
+%more general shapes using a finite element method by Jaeger {\em et
+%al.}~\cite{jae-car-med-try1999}. Since the dynamics of the concentration
+%is diffusion-dominated, we will use a stable and accurate boundary
+%integral method that is similar to the numerical method we apply to the
+%hydrodynamics (see Supplementary Material).
 

### 2021-01-28 vesicle_code/docs/permeableVes/main.tex
yny

@@
 %osmotic flow across the membrane.
-While osmotic stress  is more effective and efficient than mechanical stress in contributing to change in cellular volume, our results suggest that the water permeation due to the capillary pressure may be non-negligible over long times and/or under strong confinement in these physiological processes.
-Currently we are investigating the effects of osmotic stress in the small Peclet number limit, which is relevant to cellular migration in the presence of both confinement and a solute gradient~\cite{StrokaJiangChenEtAl2014_Cell} and has been studied numerically by Jaeger {\em et al.}~\cite{jae-car-med-try1999}
+While osmotic stress  is more effective and efficient than mechanical stress in contributing to change in cellular volume, our results suggest that the water permeation due to the capillary pressure may be non-negligible over long times or under strong confinement in these physiological processes.
+Currently we are examining the combined effects of osmotic and mechanical stresses in the small Peclet number limit, which is relevant to cellular migration in the presence of both confinement and a solute gradient~\cite{StrokaJiangChenEtAl2014_Cell} and has been studied numerically by Jaeger {\em et al.}~\cite{jae-car-med-try1999}
 

### 2021-01-28 vesicle_code/docs/permeableVes/main.tex
yny

@@
 
-Using scaling arguments, we showed that permeability due to osmolarity
-is two orders of magnitude larger than permeability due to tension, and
-six orders of magnitude larger than permeability due to bending.
-Therefore, future studies will investigate semipermeable membranes
-suspended in a solvent with a solute concentration. The presence of a
-solute is responsible for many physiological processes including cell
-migration in confined
-microenvironments~\cite{StrokaJiangChenEtAl2014_Cell,
-papadopoulos2008aquaporins}, dialysis~\cite{wan2006}, cell
-desiccation~\cite{vogl2014effect}, and
-apoptosis~\cite{marchetti1996mitochondrial}.
+%Using scaling arguments, we showed that permeability due to osmolarity
+%is two orders of magnitude larger than permeability due to tension, and
+%six orders of magnitude larger than permeability due to bending.
+%Therefore, future studies will investigate semipermeable membranes
+%suspended in a solvent with a solute concentration. The presence of a
+%solute is responsible for many physiological processes including cell
+%migration in confined
+%microenvironments~\cite{StrokaJiangChenEtAl2014_Cell,
+%papadopoulos2008aquaporins}, dialysis~\cite{wan2006}, cell
+%desiccation~\cite{vogl2014effect}, and
+%apoptosis~\cite{marchetti1996mitochondrial}.
 

### 2021-01-28 vesicle_code/docs/permeableVes/main.tex
punctuation

@@
 cell migration in confined microenvironments~\cite{StrokaJiangChenEtAl2014_Cell, papadopoulos2008aquaporins}, 
-dialysis~\cite{wan2006}, cell desiccation~\cite{vogl2014effect}, cell division~\cite{FredChang} and
+dialysis~\cite{wan2006}, cell desiccation~\cite{vogl2014effect}, cell
+division~\cite{FredChang}, and
 apoptosis~\cite{marchetti1996mitochondrial}.
 %osmotic flow across the membrane.
-While osmotic stress  is more effective and efficient than mechanical stress in contributing to change in cellular volume, our results suggest that the water permeation due to the capillary pressure may be non-negligible over long times or under strong confinement in these physiological processes.
-Currently we are examining the combined effects of osmotic and mechanical stresses in the small Peclet number limit, which is relevant to cellular migration in the presence of both confinement and a solute gradient~\cite{StrokaJiangChenEtAl2014_Cell} and has been studied numerically by Jaeger {\em et al.}~\cite{jae-car-med-try1999}
+While osmotic stress  is more effective and efficient than mechanical
+stress in contributing to change in cellular volume, our results suggest
+that the water permeation due to the capillary pressure may be
+non-negligible over long times or under strong confinement in these
+physiological processes. Currently we are examining the combined effects
+of osmotic and mechanical stresses in the small Peclet number limit,
+which is relevant to cellular migration in the presence of both
+confinement and a solute gradient~\cite{StrokaJiangChenEtAl2014_Cell}
+and has been studied numerically by Jaeger {\em et
+al.}~\cite{jae-car-med-try1999}.
 

### 2021-01-29 vesicle_code/docs/permeableVes/main.tex
yny

--- 2021-01-28 vesicle_code/docs/permeableVes/main.tex
@@
 deforming a vesicle membrane in free space or pushing it through a
-confinement. Coupling the membrane permeability with membrane elastic
-stress and tension in the framework of Helfrich free energy, we
+confinement. Incorporating the membrane permeability into the framework of Helfrich free energy for an inextensible, elastic membrane as a model for a semipermeable vesicle, we
 illustrate that, in the absence of an osmotic stress gradient, the
@@
 cell migration in confined microenvironments~\cite{StrokaJiangChenEtAl2014_Cell, papadopoulos2008aquaporins}, 
-dialysis~\cite{wan2006}, cell desiccation~\cite{vogl2014effect}, cell division~\cite{FredChang} and
+dialysis~\cite{wan2006}, cell desiccation~\cite{vogl2014effect}, cell division~\cite{OdermattMiettinenKangEtAl2020_bioRxiv} and
 apoptosis~\cite{marchetti1996mitochondrial}.
 %osmotic flow across the membrane.
-While osmotic stress  is more effective and efficient than mechanical stress in contributing to change in cellular volume, our results suggest that the water permeation due to the capillary pressure may be non-negligible over long times or under strong confinement in these physiological processes.
-Currently we are examining the combined effects of osmotic and mechanical stresses in the small Peclet number limit, which is relevant to cellular migration in the presence of both confinement and a solute gradient~\cite{StrokaJiangChenEtAl2014_Cell} and has been studied numerically by Jaeger {\em et al.}~\cite{jae-car-med-try1999}
+While osmotic stress  is more effective and efficient than mechanical stress in contributing to change in cellular volume, our results suggest that the water permeation due to the capillary pressure may be non-negligible over long times or under strong confinement in simple configurations.
+To examine if this is the case in the physiological processes,  currently we are examining the combined effects of osmotic and mechanical stresses on water permeation in the small Peclet number limit, which is relevant to cellular migration in the presence of both confinement and a solute gradient~\cite{StrokaJiangChenEtAl2014_Cell} and has been studied numerically by Jaeger {\em et al.}~\cite{jae-car-med-try1999}
 

### 2021-02-05 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
converting to prf

--- 2021-01-29 vesicle_code/docs/permeableVes/main.tex
@@
-\documentclass[9pt,twocolumn,twoside,lineno]{pnas-new}
-% Use the lineno option to display guide line numbers if required.
-
-\templatetype{pnasresearcharticle} % Choose template 
-% {pnasresearcharticle} = Template for a two-column research article
-% {pnasmathematics} %= Template for a one-column mathematics article
-% {pnasinvited} %= Template for a PNAS invited submission
-
-%\title{Semipermeable Vesicles: Mathematical Formulation, Numerics, and
-%Physics}
+%\documentclass[prb,preprint,showpacs,preprintnumbers,amsmath,amssymb,longbibliography]{revtex4-1}
+%\documentclass[1p]{elsarticle}
+%\documentclass[11pt]{revtex4}
+
+\documentclass[prb,preprint,showpacs,preprintnumbers,amsmath,amssymb,longbibliography]{revtex4-1}
+
+\usepackage[dvipsnames]{xcolor}
+\usepackage{graphicx}% Include figure files
+\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{bm}% bold math
+\usepackage{stmaryrd}
+\usepackage[sort&compress]{natbib}
+\usepackage{color}
+%\usepackage{stmaryrd,bm}
+%\usepackage{pdfpages,longtable}
+% package to prepare author and affiliation blocks
+%\usepackage{authblk}
+%\parindent=0mm
+%\parskip=2mm
+%\textwidth=17.0cm
+%\evensidemargin = -3mm
+%\oddsidemargin = -3mm
+
+\def\etal {\mbox{\it et al.}}
+\def\etals {\mbox{\it et al.}'s }
+\def\etalcomma {\mbox{\it et al.,} }
+\def\a    {\mbox{\it a\/}}
+\def\b    {\mbox{\it b\/}}
+\def\c    {\mbox{\it c\/}}
+\def\d    {\mbox{\it d\/}}
+\def\e    {\mbox{\it e\/}}
+\def\f    {\mbox{\it f\/}}
+\def\bi #1{\mbox{\boldmath $#1$}}
+\def\V  {{\bf V}}
+\def\v   {{\bf v}}
+\def\Vt  {\tilde{\V}}
+\def\vt  {\tilde{\v}}
+\def\n   {{\bf n}}
+\def\t   {{\bf t}}
+\def\E   {{\bf E}}
+\def\e   {{\bf e}}
+\def\I   {{\bf I}}
+
+\def\bii #1#2{\mbox{\boldmath $#1#2$}}
+\def\bij #1#2#3#4{\mbox{\boldmath $#1#2#3#4$}}
+%\def\beq {\begin{equation}}
+%\def\eeq {\end{equation}}
+%\def\beqa {\begin{eqnarray}}
+%\def\eeqa {\end{eqnarray}}
+\def\red {\color{red}}
+\def\blu {\color{blue}}
+\newcommand{\comment}[1]{}
+\renewcommand{\baselinestretch}{1.1}
+
+%\theoremstyle{plain}
+\newtheorem{theorem}{Theorem}
+%\theoremstyle{definition}
+\newtheorem{problem}{Problem}
+\newtheorem{remark}{Remark}
+\newtheorem{note}{Note}
+\newtheorem{definition}{Definition}
+\newcommand{\bp}{\begin{problem}}
+\newcommand{\ep}{\end{problem}}
+\newcommand{\bn}{\begin{note}}
+\newcommand{\en}{\end{note}}
+
+\newcommand{\ds}{\displaystyle}
+%\newcommand{\ben}{\renewcommand{\theenumi}{\alph{enumi}}\renewcommand{\labelenumi}{(\theenumi)}\begin{enumerate}}
+%\newcommand{\een}{\end{enumerate}}
+
+\newcommand{\Z}{\mathbb{Z}} 
+\newcommand{\N}{\mathbb{N}} 
+\newcommand{\R}{\mathbb{R}} 
+\newcommand{\C}{\mathbb{C}}
+%\newcommand{\v}{\vec{v}}
+
+\newcommand{\eps}{\epsilon}
+\newcommand{\be}{\begin{equation}}
+\newcommand{\ee}{\end{equation}}
+\newcommand{\bal}{\begin{align}}
+\newcommand{\eal}{\end{align}}
+\newcommand{\el}{\nonumber \\}
+\def\etal{\mbox{\it et al.\ }}
+
+\graphicspath{{Figures/}}
+\input my_macros2.tex
+
+\newif\ifTikz
+%\Tikztrue
+\Tikzfalse
+
+\begin{document}
+
 \title{Hydrodynamics of a  Semipermeable Vesicle Under Flow and
@@
 
-% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
-\author[a]{Bryan Quaife}
-\author[a]{Ashley Gannon}
-\author[b,1]{Y.-N.~Young}
-
-\affil[a]{Department of Scientific Computing, Florida State University, Tallahessee, FL 32306}
-\affil[b]{Department of Mathematical Sciences, New Jersey Institute of
-Technology, Newark, NJ 07102}
-
-% Please give the surname of the lead author for the running footer
-\leadauthor{Quaife}
-
-% Please add a significance statement to explain the relevance of your work
-\significancestatement{This work focuses on effects of membrane
-permeability to water on the hydrodynamics of a vesicle (self-enclosing
-lipid bilayer membrane) under flows and confinement. Without membrane
-poration or rupture, we use direct numerical simulations to illustrate
-that over sufficiently long time the water permeability affects the
-equilibrium vesicle shapes in open space. Under confinement, we show
-that water permeability may be quickly amplified to induce significant
-change in shape as the vesicle goes through a closely-fit slender
-channel and a contracting channel. These results provide a quantitative
-measure of membrane permeability to water in terms of vesicle
-inflation/deflation under load.
-%
-%Authors must submit a 120-word maximum statement
-%about the significance of their research paper written at a level
-%understandable to an undergraduate educated scientist outside their
-%field of speciality. The primary goal of the significance statement is
-%to explain the relevance of the work in broad context to a broad
-%readership. The significance statement appears in the paper itself and
-%is required for all research papers.
-%
-}
-
-% Please include corresponding author, author contribution and author declaration information
-\authorcontributions{B.Q.~and Y.-N.Y.~designed and performed research
-with A.G.'s assistance. B.Q.~and Y.-N.Y.~analyzed the data and wrote
-the paper.}
-%\authordeclaration{Please declare any competing interests here.}
-\correspondingauthor{\textsuperscript{1} Corresponding author's e-mail: yyoung@njit.edu}
-
-% At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
-\keywords{Semipermeable membrane$|$ Vesicle $|$ Extreme confinement $|$
-Boundary integral equations $|$ Stokes flow}
+\author{Bryan Quaife$^{1}$, Ashley Gannon$^{1}$ and Y.-N. Young$^{2*}$}
+\affiliation{$^1$Department of Scientific Computing, Florida State University, Tallahessee, Florida, 32306, USA\\
+$^2$Department of Mathematical Sciences, New Jersey Institute of Technology, Newark, New Jersey, 07102, USA\\}
+
+\date{\today}
 
@@
 membrane permeability.
-%
-%Lipid bilayer membranes have a native (albeit small) permeability for
-%water molecules. Under load, as long as the bilayer membrane stays intact (no poration or rupture), the water influx/efflux is
-%often assumed negligible in the absence of a osmolarity pressure across the membrane. 
-%%
-%In this work we focus on physical regimes where the membrane tension is below the critical value for membrane poration, and use boundary integral simulations to
-%investigate the effects of native water permeability on the hydrodynamics of
-%a vesicle under various flows and confinement configurations. 
-%%
-%Coupling the membrane permeability with membrane elastic stress, tension, and
-%mechanical stress in the framework of Helfrich free energy, we
-%illustrate that, in the absence of an osmotic stress gradient, a giant
-%unilamellar vesicle may be significantly affected by water
-%influx/efflux over a sufficiently long time or under a strong
-%confinement. Our simulation results quantify the conditions for water
-%permeation to be negligible in terms of the time scales, flow strength
-%of an external flow, and degree of confinement. These results shed
-%light on how microfluidic confinement can be utilized to estimate
-%membrane permeability.
-%%
-%%osmotic stress gradient 
-%%We describe a mathematical model for a semipermeable vesicle and derive
-%%  a boundary integral equation formulation for simulating its
-%%  hydrodynamics.  
-%%
-%%Please provide an abstract of no more than 250 words in a single paragraph.
-Abstracts should explain to the general reader the major contributions of the article.
-References in the abstract must be cited in full within the abstract itself and cited in the text.
 \end{abstract}
 
-\dates{This manuscript was compiled on \today}
-\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}
-
-\input my_macros2.tex
-
-\newif\ifTikz
-%\Tikztrue
-\Tikzfalse
-
-%\usepgfplotslibrary{external}
-%\tikzexternalize
-
-\setboolean{displaywatermark}{false}
-
-\begin{document}
+\pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
+                             % Classification Scheme.
+%\keywords{Suggested keywords}%Use showkeys class option if keyword
+                              %display desired
+
+% Suggested referees: McMinn, Hu, Fogelson, Kumar, Mori, Strychalski
 
 \maketitle
-\thispagestyle{firststyle}
-\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
-
-\dropcap{W}ater exchange is essential for a living cell to adapt to its
+\section{Introduction\label{s:introduction}}
+Water exchange is essential for a living cell to adapt to its
 environment over a wide range of time
@@
 vesicle without poration or rupture in the lipid bilayer membrane.
-%
-%
-%One of the most direct ways to induce water permeation across cell membranes is to impose an osmotic shock }.
-%
-%A gradient in the osmotic stress across the cellular membrane is the most direct way to induce water permeation, yet 
-%%
-%%In response to external stimuli, cells move, deform, and release signaling molecules, such as ATP in red blood cells \cite{ZhangShenHoganBarakatMisbah2018_BJ} and cyclooxygenase-2 in endothelial cells \cite{Russell-PuleriPazAdams2016_AJHCP}.
-%%
-%%Water permeation is often neglected in such release processes, yet 
-%%
-%recent findings suggest that both osmotic and mechanical stresses can induce water permeation that is significant enough for tumor cells to migrate under strong confinement \cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}, leading to a dynamic surface-to-volume ratio over time.
-%
-%
-%To elucidate the effects of mechanically induced water permeation (which is a great challenge to quantify in experiments), in this work we use accurate numerical simulations to study the hydrodynamics of a semipermeable vesicle in various configurations.
-
-%Cells also send out chemicals in response to 
-%
-% Erythrocytes are known to  participate in efficient body water homeostasis by regulating its exchange of water  \cite{YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP}.
-Cells achieve motility by simultaneously regulating their cell volume and cell membrane tension through trafficking of aquaporin proteins \cite{SaadounPapadopoulosWatanabeEtAl2005_JCS,Verkman2008_JMM,BerthaudEtAl2016_SM} and flattening of caveolae \cite{Keren2011_EurBJ}.
-%Cells also control water transport  as they activate shape fluctuations in the membrane for the bleb formation \cite{TaloniKardashSalmanEtAl2015_PRL}.
-%
-%
-%%\dropcap{W}ater balance is an essential process in the adaptation of a living cell to its environment \cite{AlbertsMolecularBiology}: Erythrocytes are known to  participate in efficient body water homeostasis by regulating its exchange of water  \cite{YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP}.
-Cells achieve motility by simultaneously regulating their cell volume and cell membrane tension through trafficking of aquaporin proteins \cite{SaadounPapadopoulosWatanabeEtAl2005_JCS,Verkman2008_JMM,BerthaudEtAl2016_SM} and flattening of caveolae \cite{Keren2011_EurBJ}.
-%%Cells also control water transport  as they activate shape fluctuations in the membrane for the bleb formation \cite{TaloniKardashSalmanEtAl2015_PRL}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Formulation}
-\begin{figure*}[htp]
-  \centering
-  \ifTikz
-  \input{figures/relaxationComposite.tikz}
-  \else
-  \includegraphics{figures/relaxationComposite.pdf}
-  \fi
-  \caption{\label{fig:relaxationComposite} (a) Snapshots of four
-  semipermeable vesicles with $\beta = 10^{-8}$ submerged in a fluid
-  with no background flow. Time goes from left to right. The red regions
-  correspond to influx and the blue regions correspond to efflux. In all
-  cases, the vesicle reaches a steady state circular shape. (b) The
-  reduced area of each of the simulations. The particular snapshots in
-  (a) occur at the marks along the curve.}
-\end{figure*}
+
+\section{Formulation\label{sec:formulation}}
 We consider a two-dimensional semipermeable vesicle (permeable only to
@@
 is the arclength, $\sigma = \Lambda - \frac{3}{2}\kappa^2$, $\Lambda$ is the
-membrane tension, and $\kappa$ is the membrane curvature (see
-Supplementary Material). Using $k_w\sim 10^{-12}$ m$^2$s/kg 
+membrane tension, and $\kappa$ is the membrane curvature.
+
+Using $k_w\sim 10^{-12}$ m$^2$s/kg 
 %(typical of mammalian cell membranes~\cite{LiMoriSun2015_PRL}) 
@@
 (where $R_0$ is a characteristic length and $\mu$ is the solvent
-viscosity): $\beta = k_w/(R_0/\mu)$ (see Supplementary Material),
+viscosity): $\beta = k_w/(R_0/\mu)$,
 $\beta=0$ for an impermeable vesicle, and $\beta>0$ for a semipermeable
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Hydrodynamics of a semipermeable vesicle in free space}
-To highlight the effects of membrane permeability to water, we consider
-a single semipermeable vesicle, with (dimensionless) permeability
-coefficient $\beta>0$, in familiar configurations: In free space we
-place a semipermeable vesicle in a quiescent flow, a planar shear flow,
-and a Poiseuille flow. For each example, we fix the vesicle length and
-examine the enclosed water content as a dynamic consequence of water
-flow, vesicle shape deformation, and membrane tension distribution.
-%
-Under these flows, our simulations show
-that the steady state of an impermeable vesicle is different from that of a semipermeable vesicle, which depends only on the strength of the external flow and is insensitive to permeability $\beta$ (as long as $\beta>0$).
-We find that  the time in the dynamic evolution towards equilibrium is scaled by $\beta^{-1}$: the smaller $\beta$ is the longer it takes to reach the steady state.
-
-In experiments, vesicles under shear flows are measured for a few
-minutes (chapter 19 in~\cite{Dimova2020_GVB}), a duration over which a
-vesicle can be assumed impermeable~\cite{AbkarianViallat2005_BJ}. Our
-simulations of a semipermeable vesicle under these flows in open
-geometry show that water permeability may lead to different vesicle
-hydrodynamics only after a duration of $\sim 1$ day.
-
-%short time scales.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Quiescent Flow} 
-\begin{figure*}[htp]
-  \centering
-  \ifTikz
-  \input{figures/shearComposite.tikz}
-  \else
-  \includegraphics{figures/shearComposite.pdf}
-  \fi
-  \caption{\label{fig:shearComposite} (a) The reduced area of a
-  semipermeable vesicle with $\beta = 10^{-3}$ initialized with four
-  different reduced areas in a shear flow with two different flow rates.
-  (b) The equilibrium shape of a vesicle with varying flow rates and
-  membrane permeability. The circled vesicles correspond to the
-  simulations in part (a).}
-\end{figure*}
-In the absence of a background flow, a semipermeable vesicle in free
-space can be quantified in terms of its area dynamics and its transition
-to the equilibrium shape. Our analysis in Supplementary Material shows
-that a semipermeable vesicle relaxes to a circle at a rate that is
-proportional to $\beta$, and the steady state tension is $\Lambda =
-2\pi^2/L^2$. Our analysis further shows that the time for a
-semipermeable vesicle to deviate from its initial reduced area and to
-reach its steady state is proportional to $\beta^{-1}$. For this reason,
-our numerical results are reported in terms of the scaled time $\beta
-t$.
-
-In Figure~\ref{fig:relaxationComposite}, we examine the relaxation
-dynamics of a semipermeable vesicle with four initial shapes and reduced
-areas as labeled. The vesicles on the left are color-coded by the water
-permeation flux: red denotes an influx into the vesicle, and blue
-denotes an efflux out of the vesicle. First we observe that the initial
-vesicle shape determines the direction of water flux. For the vesicle
-with an initial reduced area $\alpha(0)=0.12$ (bottom row) the vesicle
-deflates (blue regions) first due to the high interior capillary
-pressure that corresponds to the high membrane curvatures. For the other
-three cases efflux is dominated by influx, especially after $t=1$ day
-when the increase in total water content becomes non-negligible.
-%
-%is found at some locations of high curvature, while
-%mostly water permeates into the vesicle and significant change in the
-%reduced area is found at $t\sim 1$ hour. 
-%
-Over time (about four weeks) all vesicles inflate and as expected, each
-vesicle eventually reaches a circular shape with reduced area
-$\alpha=1$. 
-%%These regions are denoted in blue and are only present at early times. 
-%Finally, the vesicles's reduced area do not steady state tension is
-%$\Lambda = 2\pi^2/L^2$. 
-%Therefore, the times for the vesicle to deviate from its initial reduced area and to reach its
-%steady state are proportional to $\beta^{-1}$. 
-%
-%Each of the four cases in Figure~\ref{fig:relaxationComposite} eventually
-%reaches a circular shape with reduced area $\alpha=1$. Next, we observe
-%that even though the vesicle is inflating to a circle, 
-%%meaning that there is a net flux into the vesicle, 
-%there are regions where the flux
-%is out of the vesicle. These regions are denoted in blue and are only
-%present at early times. 
-%
-%Finally, the vesicles's reduced area do not
-%change by much at early times (up to ten minutes), and
-
-Between $t=30$ minutes and $t=1$ day, the total water content is nearly constant.
-%
-%the intermediate shapes of
-%semipermeable vesicles resemble the shape of an impermeable vesicle.
-%
-This can be explained by considering the two terms that contribute to
-the vesicle velocity: (i) the permeability velocity, $\beta(\ff \cdot
-\nn) \nn$, and (ii) the force balance velocity, $\SS[\ff]$. Since
-$\beta\ll 1$, the permeability velocity is much smaller than the force
-balance velocity at early times, and the semipermeable vesicle dynamics
-resemble those of an impermeable vesicle. As the force balance velocity
-decreases, the permeability velocity dominates, and the vesicle begins
-to inflate to a circle with vanishing force and velocity.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Planar Shear Flow}
-We consider a semipermeable vesicle in a planar shear flow,
-characterized by the elastic capillary number $Ca_\mathrm{E}=\chi\tau$ where $\tau$ is the characteristic time scale from balancing the viscous stress with the elastic stress
-%in the non-dimensionalization 
-(see Supplementary Material) and $\chi$ is the shear rate of the planar
-shear flow $\uu_{\infty}(\xx) = \chi (y,0)$.  When $\beta=0$
-(impermeable case), the vesicle reduced area and fluid viscosity
-contrast determine whether a vesicle tank treads or
-tumbles~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. Focusing on
-semipermeable vesicles with no viscosity contrast, we find that a
-semipermeable vesicle tilts to an inclination angle and undergoes
-tank-treading dynamics, similar to the case of an impermeable vesicle.
-
-In Figure~\ref{fig:shearComposite}(a), using four initial reduced areas
-and two flow rates, we plot the reduced area of a semipermeable vesicle
-with $\beta = 10^{-3}$. As observed in a quiescent flow, the final
-vesicle shape is independent of the initial reduced area. However, it
-does depend on the flow rate. We also observe that the amount of water
-inside the vesicle remains constant until $t\sim 2$ hours, when the
-normal component of the flow velocity becomes significantly smaller than
-the permeable velocity, leading to a changing reduced area.
-
-For a variety of dimensionless permeability coefficient $\beta>0$ and
-capillary number $Ca_\mathrm{E}$, a semipermeable vesicle reaches an
-equilibrium shape as in Figure~\ref{fig:shearComposite}(a). Since the
-equilibrium shape depends on $Ca_\mathrm{E}$ and is independent of the
-initial reduced area, we initialize the vesicle with reduced area
-$\alpha = 0.65$ for all simulations in
-Figure~\ref{fig:shearComposite}(b), where we summarize the equilibrium
-vesicle shape and its reduced area. We see that the capillary number
-(flow rate) significantly affects the final vesicle shape, but the
-permeability coefficient has a very minor effect. Instead, as we saw in
-the quiescent analysis, $\beta$ sets a time scale since the time
-required for a vesicle to reach its steady state configuration is
-proportional to $\beta^{-1}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Poiseuille Flow}
-\begin{figure*}[htp]
-  \centering
-  \ifTikz
-  \input{figures/parabolicComposite.tikz}
-  \else
-  \includegraphics{figures/parabolicComposite.pdf}
-  \fi
-  \caption{\label{fig:parabolicComposite} (a) The equilibrium shape of
-  a semipermeable vesicle submerged in a Poiseuille flow with varying
-  initial reduced areas and flow rates. The red regions correspond to
-  influx and the blue regions correspond to efflux. (b) The steady
-  state vertical displacement at four different flow velocities. The
-  steady state shapes are superimposed. (c) The reduced area of the
-  slipper formed with the flow rate of $800 \; \mu$m/s. (d) The vesicle
-  shape shown with the background imposed flow. The channel width is
-  12.5 times larger than the vesicle radius. The corresponding reduced
-  area of each vesicle is indicated by the marks in plot (c).}
-\end{figure*}
-
-We consider a semipermeable vesicle in the Poiseuille flow $\uu =
-U(1-(y/W)^2,0)$, where $U$ is the maximum velocity at $y=0$. The
-non-linear effects of the Poiseuille flow on the migration of an
-impermeable vesicle have been well-studied~\cite{kao-bir-mis2009}: At a
-given value of the maximum velocity $U$, there exists a critical reduced
-volume above which the equilibrium vesicle shape is symmetric (parachute
-or bullet shapes) and the vesicle stays at $y=0$. Below this critical
-reduced volume the equilibrium vesicle moves off the center and is
-asymmetric (tank-treading slipper shape). We validated our numerical
-codes by comparing against results in Kaoui {\em et
-al.}~\cite{kao-bir-mis2009} (see Supplementary Material).
-
-%
-%
-%We examine the effect of the non-linear Poiseuille flow on the migration of
-%semipermeable vesicle. In this experiment, the vesicle is initialized
-%above the center line $y=0$, and it migrates towards the center
-%line~\cite{dan-vla-mis2009}. 
-%
-%For an impermeable vesicle, depending on
-%the vesicles reduced area and the flow rate, the equilibrium vesicle shape
-%is either an axisymmetric parachute or bullet, or an asymmetric
-%tank-treading slipper~\cite{kao-bir-mis2009}. 
-%We validated our numerical codes by comparing against results in Kaoui {\it et al.} \cite{kao-bir-mis2009}.
-%One of the most salient features of an impermeable vesicle in the Poiseuille flow is that, 
-%%
-%%To validate our methods,
-%%in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
-%%for the steady state shape of an impermeable vesicle
-%%vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
-%%qualitatively agree, Kaoui et al.~report that the vesicles with
-%%$\nu=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
-%%axisymmetric. In our simulations these vesicles are slightly asymmetric,
-%%are undergoing a tank treading motion, and we therefore report them as
-%%asymmetric slippers.
-%
-%Having validated our method, we investigate the dynamics of a semipermeable vesicle in a Poiseuille flow. 
-%
-%Using several initial
-%$U(1-(y/W)^2,0)$, where $U$ is the maximum imposed velocity. We examine
-%the effect of the non-linear Poiseuille flow on the migration of
-%semipermeable vesicle. 
-%
-
-At the beginning of the simulations, a semipermeable vesicle is placed
-above the center line $y=0$ and it migrates towards the center line as
-in the impermeable case~\cite{dan-vla-mis2009}. 
-%
-%However,
-%for an impermeable vesicle, depending on the initial reduced area and
-%the maximum flow velocity $U$, the equilibrium vesicle shape is either
-%an axisymmetric parachute or bullet, or an asymmetric tank-treading
-%slipper~\cite{kao-bir-mis2009}. 
-%
-%To validate our methods,
-%in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
-%for the steady state shape of an impermeable vesicle
-%vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
-%qualitatively agree, Kaoui et al.~report that the vesicles with
-%$\alpha=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
-%axisymmetric. In our simulations these vesicles are slightly asymmetric,
-%are undergoing a tank treading motion, and we therefore report them as
-%asymmetric slippers.
-%
-Using several initial reduced areas and flow rates, we recreate the
-impermeable vesicle phase diagram for vesicles with $\beta = 10^{-3}$.
-The equilibrium vesicle shape for different $U$ and initial reduced area
-is summarized in Figure~\ref{fig:parabolicComposite}(a), and the
-vertical displacement of the vesicle's center of mass is in
-Figure~\ref{fig:parabolicComposite}(b). The effect of semipermeability
-of a vesicle with $\alpha(0) = 0.9$ and $U=800\; \mu$m/s on its reduced
-area and migration pattern are shown in
-Figures~\ref{fig:parabolicComposite}(c)
-and~\ref{fig:parabolicComposite}(d), respectively.
-
- \begin{figure*}[hbp]
-  \centering
-  \ifTikz
-  \input{figures/stenosisComposite.tikz}
-  \else
-  \includegraphics{figures/stenosisComposite.pdf}
-  \fi
-  \caption{\label{fig:stenosisComposite} (a) A semipermeable vesicle
-   passing through a closely-fit channel similar to the experimental
-   device in~\cite{abk-fai-sto2006}. (b) A semipermeable vesicle passing
-   through a  (four-times) longer closely-fit channel than (a). (c) The
-   excess pressure of an impermeable and semipermeable vesicle in the
-   short geometry in (a). (d) The reduced area of the semipermeable
-   vesicles in the geometries in (a) and (b) as a function of the
-   vesicles' center of mass. In (c) and (d), the x-axis is scaled by
-   $1/L$ where $L$ is half the length of the constriction. (e) The
-   reduced area of the semipermeable vesicles in the geometries in (a)
-   and (b) as a function of time. The time axis is scaled by $1/t_R$
-   where $t_R$ is the residency time. In parts (c) and (d), the dashed
-   lines correspond to the locations of the inlet and outlet. In part
-   (e), the dashed lines correspond to the times that the vesicle enters
-   and exits the constriction. The colored vesicles show the tension
-   distribution in N/m of the circled vesicles. Throughout the entire
-   simulation, these vesicle configurations have the largest tension.}
-\end{figure*}
-
-As observed for the planar shear flow, the equilibrium reduced area of a
-semipermeable vesicle in a Poiseuille flow is independent of the initial
-reduced area and $\beta$, and  larger maximum flow velocity $U$ results
-in smaller equilibrium reduced area
-(Figure~\ref{fig:parabolicComposite}(a)). At the smallest velocity $U=
-200\; \mu$m/s, the steady state reduced area is large, and the
-equilibrium vesicle shape is an axisymmetric bullet. The equilibrium
-reduced area decreases with increasing $U$, and the nonlinear flow
-profile gives rise to an asymmetric tank-treading slipper for $U\ge 400$
-$\mu m/s$. We observe that the membrane permeability to water
-drastically alters the equilibrium vesicle shape and position relative
-to the Poiseuille flow: At $\beta=10^{-3}$ the equilibrium vesicle
-depends only on the maximum velocity $U$ of the nonlinear shear flow.
-The higher $U$ the smaller the equilibrium reduced area and the farther
-away the vesicle is relative to the flow center at $y=0$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{A semipermeable vesicle under strong confinement}
-Here we consider a semipermeable vesicle under strong confinement: a
-long closely-fit channel and a contracting channel. In a narrow
-microfluidic channel, a large pressure jump is often needed to push the
-vesicle through a closely-fit channel~\cite{abk-fai-sto2006}.  Our
-simulations show that such a configuration can lead to an amplification
-of water permeation at a time scale shorter than a few minutes. In
-addition, we find that a large value of $\beta$ is needed to keep the
-membrane tension below the threshold value for membrane poration. Such
-high permeability for water may be regarded as an indication that the
-lipid bilayer membrane is porated under strong confinement, and our
-model vesicle is for a porated vesicle within the Helfrich free energy
-framework.  As in the previous examples, we fix the vesicle length and
-examine the enclosed water content as a dynamic consequence of water
-flow, vesicle shape deformation, and membrane tension distribution.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Semipermeable Vesicle in a Closely-fit Channel (Stenosis)}
-When red blood cells go through small capillary vessels, they experience
-large shape deformation and significant membrane stretching that
-triggers ATP release~\cite{Wan2008_PNAS, ForsythWan2011_PNAS}.  Many
-cells exhibit extraordinary flexibility as they go through narrow
-vessels~\cite{AuStoreyMoore2016_PNAS}, and adjustment of
-surface-to-volume ratio may be a key factor for a successful passage.
-Here we quantify the effect of water permeability on a vesicle going
-through a stenosis (a long microfluidic channel with a width smaller
-than the cell radius).  Based on the findings in~\cite{abk-fai-sto2006},
-we first examine the effect of semipermeability on the pressure
-fluctuation across a stenosed geometry. In this experiment, a pressure
-drop is used to squeeze a red blood cell through a constriction with
-diameter $5\;\mu$m and length $45\;\mu$m. We set up a similar
-computational geometry with a Poiseuille flow imposed at the inlet and
-outlet (Figure~\ref{fig:stenosisComposite}(a)). We set the maximum flow
-velocity to $U_{\max} = 1000 \;\mu$m/s at the inlet and outlet so that
-the residency time of the vesicle in the stenosis channel is $t_R
-\approx 25$ ms which agrees with the experimental
-results~\cite{abk-fai-sto2006}. When the red blood cell enters the
-channel, an increase in the pressure drop is required to maintain a
-constant flow rate, and the difference in the pressure drop is called
-the excess pressure.
-\begin{figure}[htp]
-  \centering
-  \ifTikz
-  \input{figures/contractingComposite.tikz}
-  \else
-  \includegraphics{figures/contractingComposite.pdf}
-  \fi
-  \caption{\label{fig:contractingComposite} A contracting channel
-  similar to the experimental configuration in~\cite{wu2015critical}.
-  The channel width varies from $18\;\mu$m to $1.8\;\mu$m, and it
-  repeats every $45\;\mu$m. The fluid flux along the red regions is into
-  the vesicle, and the fluid flux along the blue regions is out of the
-  vesicle.  (a--c): The ability for a semipermeable vesicle to pass
-  through the contraction depends on the permeability $\beta$. (d--f):
-  The ability for a semipermeable vesicle to pass through the
-  contraction depends on the flow rate. The colored vesicles show the
-  tension distribution in N/m of the circled vesicles. Throughout the
-  entire simulation, these vesicle configurations have the largest
-  tension.}
-\end{figure}
-
-We consider both an impermeable and semipermeable vesicle with initial
-reduced area $\alpha = 0.65$ passing through a long narrow channel and
-compute the excess pressure as a function of vesicle position in the
-channel (Figure~\ref{fig:stenosisComposite}(c)). The impermeable case
-agrees with experimental results~\cite{abk-fai-sto2006} (see Figure 3).
-Our simulations show that less excess pressure is needed to drive a
-semipermeable vesicle through the closely-fit channel. Once in the
-channel, the vesicle takes a bullet shape with maximum tension in the
-front and minimum tension in the back
-(Figure~\ref{fig:stenosisComposite}(a)), consistent with earlier
-results~\cite{Pak2015_PNAS, HarmanBertrandJoos2017_CJP}.
-
-Figures~\ref{fig:stenosisComposite}(d)
-and~\ref{fig:stenosisComposite}(e) show that the vesicle deflates from
-the beginning due to the high flow velocity, consistent with the results
-for a vesicle in a Poiseuille flow in open space. As the vesicle enters
-the stenosis channel, it continues to deflate in the front even though
-we observe influx (red segment) at various rear locations in the
-membrane. Overall, the vesicle loses about 6.1\% of its initial total
-water at a constant rate as shown in
-Figures~\ref{fig:stenosisComposite}(d)
-and~\ref{fig:stenosisComposite}(e) (blue curves). Thus we expect that a
-larger amount of deflation is possible if the vesicle is inside a longer
-stenosis: we consider a vesicle passing through a channel of triple the
-length in Figure~\ref{fig:stenosisComposite}(b) with
-$U_{\max}=1000\;\mu$m/s, and we observe that vesicle stays inside the
-stenosis for a residence time $t_R \approx 70$ ms and the area decreases
-by 13.2\% (red curves).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Semipermeable Vesicle in a Contracting Geometry} 
-Squeezing a cell or an elastic vesicle through a slit in microfluidics
-has gained popularity for its application in stress-induced release of
-macromolecules~\cite{ShareiEtAl2013_PNAS, Pak2015_PNAS,
-ZhangShenHoganBarakatMisbah2018_BJ, LuoBai2019_PoF}. Red blood cells go
-through submicron slits many times during their lifetime, and this
-process selects healthy, flexible red blood cells to
-survive~\cite{wu2015critical,LuPeng2019_PoF}. Here we investigate the
-role of membrane permeability to water when a semipermeable vesicle is
-squeezed through a contracting microfluidic channel similar
-to~\cite{wu2015critical}, where the width of the channel gradually
-decreases from $18 \;\mu$m to $1.8\; \mu$m. The channel then immediately
-reopens to $18\;\mu$m (Figure~\ref{fig:contractingComposite}). A
-Poiseuille flow is imposed at the inlet and outlet with a constant
-maximum flow rate of $U_{\max}$. We initialize a semipermeable vesicle
-with $\alpha = 0.65$ that spans $10\; \mu$m of the total channel width
-and investigate the effects of the membrane permeability to water and
-the maximum flow velocity on whether a vesicle can successfully pass
-through the slit. We color the vesicle according to the sign of its
-flux---red for influx and blue for efflux.
-
-In Figures~\ref{fig:contractingComposite}(a)
-and~\ref{fig:contractingComposite}(b), we plot snapshots of vesicles
-with different permeability $\beta$.
-Figure~\ref{fig:contractingComposite}(c) shows the corresponding reduced
-area as a function of the vesicle's location. We observe that if the
-permeability is sufficiently large, the vesicle inflates gradually over
-seconds before it reaches the neck, and then it quickly deflates within
-a fraction of a second. However, if the permeability $\beta$ is too
-low, the vesicle is too large when it reaches the narrowest part of the
-channel, and it is unable to pass. In
-Figures~\ref{fig:contractingComposite}(d)
-and~\ref{fig:contractingComposite}(e), we plot snapshots of vesicles
-with different imposed maximum velocities, and
-Figure~\ref{fig:contractingComposite}(f) shows the reduced area as a
-function of the vesicle's location. At low velocities, the vesicle
-inflates similar to the unbounded parabolic flow example, and it is
-unable to pass through the contraction. However, higher flow rates
-result in additional deflation and the vesicle passes through the
-contraction.
-
-To understand the effects of water permeability on a vesicle that
-repeatedly passes through micro-capillary vessels or sub-micron slits,
-we construct a contracting geometry
-(Figure~\ref{fig:contractingComposite2}) to simulate a vesicle passing
-through the contracting geometry six times.  In
-Figure~\ref{fig:contractingComposite2}(b), we show that the vesicle
-deflates each time it passes through the contraction followed by a
-gradual inflation (over seconds). The total area loss over the history
-of the vesicle is almost 50\%. In
-Figure~\ref{fig:contractingComposite2}(c), we show the vesicle velocity
-as a function of the vesicle's center of mass. As the vesicle passes
-through the contraction, it first accelerates until it reaches the neck
-where it abruptly decelerates to go through the contraction. The reduced
-area and velocity with respect to time are also shown in
-Figure~\ref{fig:contractingComposite2}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Discussion}
-In this work we investigate the effects of membrane permeability to
-water on vesicle hydrodynamics. Without any external flow or
-confinement, our analysis shows that a semipermeable vesicle always
-inflates to maximize the water content inside the vesicle of a fixed
-length (area) in two (three) dimensions. Results from analysis and
-numerical simulation show that such relaxation of a semipermeable
-vesicle is characterized by a rescaled time $\beta t$. We further
-illustrate that the relaxation process consists of at least two phases:
-The first phase is dominated by the balance between membrane traction
-and viscous stress at early times (up to five minutes), when the vesicle
-behaves like an impermeable membrane. The second phase sets in after a
-few hours, when water influx begins to dominate and inflate the vesicle.
-Over a time scale of more than four weeks, a semipermeable vesicle is
-fully inflated, independent of its initial surface-to-volume ratio.
-
-\begin{figure}[hbp]
-  \centering
-  \ifTikz
-  \input{figures/contractingComposite2.tikz}
-  \else
-  \includegraphics{figures/contractingComposite2.pdf}
-  \fi
-  \caption{\label{fig:contractingComposite2} Vesicle reduced area and
-  velocity vs.~time. The permeability coefficient is $\beta = 10^{-3}$
-  and the maximum velocity is $18\;\mu$m/s. (a) A semipermeable vesicle
-  passing through six periods of the contracting geometry. (b) The
-  reduced area with the marks representing shapes in (a). (c) The
-  vesicle velocity with the marks representing shapes in (a). In (b) and
-  (c), the lower x-axis is the x-coordinate of the center of mass, and
-  the upper x-axis is time. The colored vesicles show the tension
-  distribution in N/m of the circled vesicles. Throughout the entire
-  simulation, these vesicle configurations have the largest tension.}
-\end{figure}
-
-Under strong confinement we show that water permeation can be amplified
-on a time scale of a few seconds as a vesicle is squeezed through a
-closely-fit channel and a contracting channel. As a semipermeable
-vesicle goes through a long closely-fit channel, we observe that the
-vesicle loses water at a constant rate, and the longer the channel the
-more the loss of water. In the case of a contracting channel, we find
-that both permeability and the pressure gradient across the slit must be
-sufficiently large for a successful passage. Throughout these
-simulations the membrane tension is below the threshold for membrane
-poration. Thus we expect the continuum membrane theory to well-capture
-the vesicle hydrodynamics, and our simulation results shed light on the
-configuration and time scales needed to observe the effects of
-permeability on vesicle hydrodynamics under confinement.
-
-%Using scaling arguments, we showed that permeability due to osmolarity
-%is two orders of magnitude larger than permeability due to tension, and
-%six orders of magnitude larger than permeability due to bending.
-%Therefore, future studies will investigate semipermeable membranes
-%suspended in a solvent with a solute concentration. The presence of a
-%solute is responsible for many physiological processes including cell
-%migration in confined
-%microenvironments~\cite{StrokaJiangChenEtAl2014_Cell,
-%papadopoulos2008aquaporins}, dialysis~\cite{wan2006}, cell
-%desiccation~\cite{vogl2014effect}, and
-%apoptosis~\cite{marchetti1996mitochondrial}.
-
-Cells exhibit a dynamic volume-to-surface ratio in 
-many physiological processes, such as 
-cell migration in confined microenvironments~\cite{StrokaJiangChenEtAl2014_Cell, papadopoulos2008aquaporins}, 
-dialysis~\cite{wan2006}, cell desiccation~\cite{vogl2014effect}, cell division~\cite{OdermattMiettinenKangEtAl2020_bioRxiv} and
-apoptosis~\cite{marchetti1996mitochondrial}.
-%osmotic flow across the membrane.
-While osmotic stress  is more effective and efficient than mechanical stress in contributing to change in cellular volume, our results suggest that the water permeation due to the capillary pressure may be non-negligible over long times or under strong confinement in simple configurations.
-To examine if this is the case in the physiological processes,  currently we are examining the combined effects of osmotic and mechanical stresses on water permeation in the small Peclet number limit, which is relevant to cellular migration in the presence of both confinement and a solute gradient~\cite{StrokaJiangChenEtAl2014_Cell} and has been studied numerically by Jaeger {\em et al.}~\cite{jae-car-med-try1999}
-
-%While the solute dynamics
-%is governed by an advection-diffusion equation, many biophysical
-%applications involve speeds no greater than $\sim 50$
-%$\mu$m/hour~\cite{StrokaJiangChenEtAl2014_Cell}, a length scale of 10
-%$\mu$m, and a solute diffusivity of $\sim 10^{-10}$ m$^2$/s (glucose in
-%water). The resulting Peclet number is $\sim 10^{-2}$, and this limit
-%has been analyzed for spherical vesicles by Anderson~\cite{and1983} and
-%more general shapes using a finite element method by Jaeger {\em et
-%al.}~\cite{jae-car-med-try1999}. Since the dynamics of the concentration
-%is diffusion-dominated, we will use a stable and accurate boundary
-%integral method that is similar to the numerical method we apply to the
-%hydrodynamics (see Supplementary Material).
-
-\acknow{We thank Howard Stone, Michael J.~Shelley, Petia Vlahovska,
-Chaoqui Misbah, Manouk Abkarian, Sangwoo Shin, and Shravan
-K.~Veerapaneni for discussions. B.Q.~acknowledges support from the
-Simons Foundation, Mathematics and Physical Sciences-Collaboration
-Grants for Mathematicians, Award Number 527139.  Y.-N.Y.~acknowledges
-support from NSF (DMS 1614863, DMS 195160) and Flatiron Institute, part
-of Simons Foundation.}
-
-\showacknow{} % display acknowledgments
-
-% \bibliographystyle{pnas-new}
- \bibliography{refs}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Supplementary Material: Formulation}
 We consider a two-dimensional inextensible semipermeable vesicle
@@
 geometry, the condition $\uu(\xx) \rightarrow \uu_\infty(\xx)$ as $|\xx|
-\rightarrow \infty$ is enforced. In the confined examples, we enforce a
-no-slip boundary condition along the top and bottom of the channel and a
-Hagen–Poiseuille flow at the inlet and outlet---this boundary condition
-has been used in similar vesicle setups~\cite{qua-bir2014,
-rah-vee-bir2010, lu-rah-zor2017}. Along the vesicle membrane $\gamma$,
-mass continuity, force balance, and local inextensibility are enforced
-by requiring
-\begin{align}
-  \label{eqn:jump}
-  \jump{\uu} = 0, \quad
-  \jump{T\cdot\nn} = \ff_\mathrm{mem}, \quad
-  \xx_s \cdot \uu_s = 0,
-\end{align}
-where $\nn$ is the outward normal of $\gamma$, $\jump{\cdot}$ is the
-jump across the interface, and $T$ is the hydrodynamic stress tensor.
-The membrane force $\ff_\mathrm{mem}$ is the sum of a bending force
-with bending modulus $k_b$ and a force due to the tension $\Lambda$.
-Following~\cite{vee-gue-zor-bir2009}, we introduce the variable $\sigma
-= \Lambda - \frac{3}{2}\kappa^2$, where $\kappa$ is the vesicle curvature. Then,
-the bending and tension forces corresponding to the Helfrich energy are
-$\ff_\mathrm{ben} = -k_b \xx_{ssss}$ and $\ff_\mathrm{ten} = (\sigma
-\xx_s)_s$.
-
-Semipermeability is introduced by modifying the vesicle velocity from
-the standard no-slip condition $\dot{\xx} = \uu(\xx)$. Instead,
-the permeating water flux through the lipid bilayer membrane is proportional to the
-membrane traction~\cite{yao-mor2017}. That is, 
-\begin{align}
-  \label{eqn:vesicleFlux}
-  \uu - \dot{\xx} = - k_w (\ff_\mathrm{mem} \cdot \nn) \nn, \qquad
-  \xx \in \gamma,
-\end{align}
-where $k_w$ is the hydraulic conductivity.
-
-%The governing equations are non-dimensionalized by introducing a length
-%scale that we take to be $R_0 = 10^{-6}$m. Using a bending stiffness of
-%$k_b = 10^{-19}$J and fluid viscosity $5 \times 10^{-2}$kg/ms, we define
-%the time scale $\tau = \mu R_0^3/k_b = 0.5s$, the velocity scale $U =
-%R_0/\tau = 2\mu$m/s, the pressure scale $P = k_b/R_0^3 = 10^{-1}$Pa, the
-%tension scale $Q = k_b/R_0^2 = 10^{-7}$N/m, and the permeability scale
-%$W = R_0\mu = 2 \times 10^{-5}$m$^2$s/kg. Another standard dimensionless
-%variable in vesicle suspensions is the reduced area $\alpha = 4\pi A/L^2
-%\in (0,1]$, where $L$ is the vesicle length and $A$ is its area. The
-%length is conserved by the local inextensibility condition, but the area
-%is not because of semipermeability. Therefore, the reduced area is
-%dynamic.
+\rightarrow \infty$ is enforced.
 
@@
 
+In the confined examples, we enforce a
+no-slip boundary condition along the top and bottom of the channel and a
+Hagen–Poiseuille flow at the inlet and outlet---this boundary condition
+has been used in similar vesicle setups~\cite{qua-bir2014,
+rah-vee-bir2010, lu-rah-zor2017}. Along the vesicle membrane $\gamma$,
+mass continuity, force balance, and local inextensibility are enforced
+by requiring
+\begin{align}
+  \label{eqn:jump}
+  \jump{\uu} = 0, \quad
+  \jump{T\cdot\nn} = \ff_\mathrm{mem}, \quad
+  \xx_s \cdot \uu_s = 0,
+\end{align}
+where $\nn$ is the outward normal of $\gamma$, $\jump{\cdot}$ is the
+jump across the interface, and $T$ is the hydrodynamic stress tensor.
+The membrane force $\ff_\mathrm{mem}$ is the sum of a bending force
+with bending modulus $k_b$ and a force due to the tension $\Lambda$.
+Following~\cite{vee-gue-zor-bir2009}, we introduce the variable $\sigma
+= \Lambda - \frac{3}{2}\kappa^2$, where $\kappa$ is the vesicle curvature. Then,
+the bending and tension forces corresponding to the Helfrich energy are
+$\ff_\mathrm{ben} = -k_b \xx_{ssss}$ and $\ff_\mathrm{ten} = (\sigma
+\xx_s)_s$.
+
+Semipermeability is introduced by modifying the vesicle velocity from
+the standard no-slip condition $\dot{\xx} = \uu(\xx)$. Instead,
+the permeating water flux through the lipid bilayer membrane is proportional to the
+membrane traction~\cite{yao-mor2017}. That is, 
+\begin{align}
+  \label{eqn:vesicleFlux}
+  \uu - \dot{\xx} = - k_w (\ff_\mathrm{mem} \cdot \nn) \nn, \qquad
+  \xx \in \gamma,
+\end{align}
+where $k_w$ is the hydraulic conductivity.
+
+%The governing equations are non-dimensionalized by introducing a length
+%scale that we take to be $R_0 = 10^{-6}$m. Using a bending stiffness of
+%$k_b = 10^{-19}$J and fluid viscosity $5 \times 10^{-2}$kg/ms, we define
+%the time scale $\tau = \mu R_0^3/k_b = 0.5s$, the velocity scale $U =
+%R_0/\tau = 2\mu$m/s, the pressure scale $P = k_b/R_0^3 = 10^{-1}$Pa, the
+%tension scale $Q = k_b/R_0^2 = 10^{-7}$N/m, and the permeability scale
+%$W = R_0\mu = 2 \times 10^{-5}$m$^2$s/kg. Another standard dimensionless
+%variable in vesicle suspensions is the reduced area $\alpha = 4\pi A/L^2
+%\in (0,1]$, where $L$ is the vesicle length and $A$ is its area. The
+%length is conserved by the local inextensibility condition, but the area
+%is not because of semipermeability. Therefore, the reduced area is
+%dynamic.
+
 Since the fluid satisfies the Stokes equations, the velocity and
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Supplementary Material: Numerical Methods}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Discretization in Space}
-By using a boundary integral equation formulation, the unknowns are the
-vesicle's position and tension and the unknown density function for
-confined flows. Both $\gamma$ and $\partial\Omega$ are discretized at a
-set of collocation points. Derivatives are computed with Fourier
-differentiation, and the eighth-order quadrature~\cite{alp1999} is
-applied to the weakly singular single-layer potential. For confined
-geometries, the trapezoid rule is used to approximate the double-layer
-potential since its kernel is smooth and periodic. Nearly-singular
-integrals are computed with an interpolation-based quadrature
-rule~\cite{qua-bir2014}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Discretization in Time}
-To eliminate stringent time step restrictions, we modify a time stepping
-method that discretizes high-order derivatives
-semi-implicitly~\cite{vee-gue-zor-bir2009}. We introduce the notation
-\begin{alignat}{3}
-  &B[\xx]\ff = -\frac{d^4}{ds^4} \ff,  \qquad
-  &&T[\xx]\sigma = (\sigma \xx_s)_s, \\
-  &D[\xx]\ff = \xx_s \cdot \ff_s, 
-  &&P[\xx]\ff = (\ff \cdot \nn) \nn,
-\end{alignat}
-for the differential and projection operators. Then, the
-governing equations~\eqref{eqn:vesVelocity} are
-\begin{align}
-  \dot{\xx} &= \uu_\infty(\xx) + \beta P(B\xx + T\sigma)
-  + \SS (B\xx + T\sigma), \quad
-  D \dot{\xx} = 0.
-\end{align}
-We note that the integral and differential operators, which all depend
-on the vesicle shape, are non-linear with respect to the vesicle
-shape. We construct a time stepping scheme by letting $B^N$ be the
-bending operator due to the vesicle configuration at time $t^N$, and use
-similar notation for the other operators. Then, a first-order
-semi-implicit time stepping method of~\eqref{eqn:vesVelocity} is
-\begin{alignat}{3}  
-  \frac{\xx^{N+1} - \xx^N}{\triangle t} &= \uu_\infty(\xx^N) 
-  &&+ \beta P^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right) \nonumber \\
-  & &&+ \SS^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right),  \\
-  D^N\xx^{N+1} &= 1,
-\end{alignat}
-and this linear system is solved with matrix-free GMRES.
-
-To achieve second-order accuracy over long time horizons, we modify an
-adaptive spectral deferred correction time stepping
-method~\cite{qua-bir2016}. Since the area of the vesicle is not
-conserved, we only use the length of the vesicle to estimate the error
-which determines if a time step is accepted or not and determines the
-subsequent time step size.
-
-\begin{figure}[htp]
-  \centering
-  \ifTikz
-  \input{figures/parabolicImpermeable.tikz}
-  \else
-  \includegraphics{figures/parabolicImpermeable.pdf}
-  \fi
-  \caption{\label{fig:PoiseuillePhase} Phase diagram of an impermeable
-  vesicle with various reduced areas submerged in a Poiseuille flow with
-  various flow rates. The shapes agree qualitatively with Kaoui {\em et
-  al.}~\cite{kao-bir-mis2009} (see Figure 2).}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Numerical Validation}
-To validate our numerical codes for simulating vesicle hydrodynamics, we reproduce a phase diagram of the equilibrium
-shape of an impermeable vesicle in a Poiseuille flow. Depending on
-the maximum flow velocity and the vesicle reduced area, the equilibrium vesicle shape is either an
-axisymmetric bullet, an axisymmetric parachute, or a tank-treading
-asymmetric slipper~\cite{kao-bir-mis2009}. Comparing our results
-(Figure~\ref{fig:PoiseuillePhase}) with those in~\cite{kao-bir-mis2009}
-(see Figure 2), we observe qualitative agreement in the equilibrium
-vesicle shapes except that,
-%
-%see that the vesicle shapes qualitatively agree. We
-%note that 
-%
-Kaoui {\em et al.}~report that the vesicles with $\alpha=0.7$
-and flow rates $U = 1200\; \mu$m/s and $U = 1600\; \mu$m/s are
-axisymmetric.  In our simulations these vesicles are slightly
-asymmetric, are undergoing a tank-treading motion, and we therefore
-report them as asymmetric slippers.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Supplementary Material: Vesicle Area}
+\subsection{Dynamics of Vesicle Area\label{subsec:area_dynamics}}
 In the absence of an imposed flow, the steady state vesicle shape and a
@@
 
-%reaches its steady state which confirms that $\dot{A}(t) = 0$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Supplementary Material: Vesicle Tensions}
+\section{Numerical Methods}
+By using a boundary integral equation formulation, the unknowns are the
+vesicle's position and tension and the unknown density function for
+confined flows. Both $\gamma$ and $\partial\Omega$ are discretized at a
+set of collocation points. Derivatives are computed with Fourier
+differentiation, and the eighth-order quadrature~\cite{alp1999} is
+applied to the weakly singular single-layer potential. For confined
+geometries, the trapezoid rule is used to approximate the double-layer
+potential since its kernel is smooth and periodic. Nearly-singular
+integrals are computed with an interpolation-based quadrature
+rule~\cite{qua-bir2014}.
+
+\subsection{Discretization in Time}
+To eliminate stringent time step restrictions, we modify a time stepping
+method that discretizes high-order derivatives
+semi-implicitly~\cite{vee-gue-zor-bir2009}. We introduce the notation
+\begin{alignat}{3}
+  &B[\xx]\ff = -\frac{d^4}{ds^4} \ff,  \qquad
+  &&T[\xx]\sigma = (\sigma \xx_s)_s, \\
+  &D[\xx]\ff = \xx_s \cdot \ff_s, 
+  &&P[\xx]\ff = (\ff \cdot \nn) \nn,
+\end{alignat}
+for the differential and projection operators. Then, the
+governing equations~\eqref{eqn:vesVelocity} are
+\begin{align}
+  \dot{\xx} &= \uu_\infty(\xx) + \beta P(B\xx + T\sigma)
+  + \SS (B\xx + T\sigma), \quad
+  D \dot{\xx} = 0.
+\end{align}
+We note that the integral and differential operators, which all depend
+on the vesicle shape, are non-linear with respect to the vesicle
+shape. We construct a time stepping scheme by letting $B^N$ be the
+bending operator due to the vesicle configuration at time $t^N$, and use
+similar notation for the other operators. Then, a first-order
+semi-implicit time stepping method of~\eqref{eqn:vesVelocity} is
+\begin{alignat}{3}  
+  \frac{\xx^{N+1} - \xx^N}{\triangle t} &= \uu_\infty(\xx^N) 
+  &&+ \beta P^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right) \nonumber \\
+  & &&+ \SS^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right),  \\
+  D^N\xx^{N+1} &= 1,
+\end{alignat}
+and this linear system is solved with matrix-free GMRES.
+
+To achieve second-order accuracy over long time horizons, we modify an
+adaptive spectral deferred correction time stepping
+method~\cite{qua-bir2016}. Since the area of the vesicle is not
+conserved, we only use the length of the vesicle to estimate the error
+which determines if a time step is accepted or not and determines the
+subsequent time step size.
+
+\begin{figure}[htp]
+  \centering
+  \ifTikz
+  \input{figures/parabolicImpermeable.tikz}
+  \else
+  \includegraphics{figures/parabolicImpermeable.pdf}
+  \fi
+  \caption{\label{fig:PoiseuillePhase} Phase diagram of an impermeable
+  vesicle with various reduced areas submerged in a Poiseuille flow with
+  various flow rates. The shapes agree qualitatively with Kaoui {\em et
+  al.}~\cite{kao-bir-mis2009} (see Figure 2).}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Numerical Validation\label{subsec:numerical_validation}}
+To validate our numerical codes for simulating vesicle hydrodynamics, we reproduce a phase diagram of the equilibrium
+shape of an impermeable vesicle in a Poiseuille flow. Depending on
+the maximum flow velocity and the vesicle reduced area, the equilibrium vesicle shape is either an
+axisymmetric bullet, an axisymmetric parachute, or a tank-treading
+asymmetric slipper~\cite{kao-bir-mis2009}. Comparing our results
+(Figure~\ref{fig:PoiseuillePhase}) with those in~\cite{kao-bir-mis2009}
+(see Figure 2), we observe qualitative agreement in the equilibrium
+vesicle shapes except that,
+%
+%see that the vesicle shapes qualitatively agree. We
+%note that 
+%
+Kaoui {\em et al.}~report that the vesicles with $\alpha=0.7$
+and flow rates $U = 1200\; \mu$m/s and $U = 1600\; \mu$m/s are
+axisymmetric.  In our simulations these vesicles are slightly
+asymmetric, are undergoing a tank-treading motion, and we therefore
+report them as asymmetric slippers.
+
+\section{Hydrodynamics of a semipermeable vesicle in free space}
+To highlight the effects of membrane permeability to water, we consider
+a single semipermeable vesicle, with (dimensionless) permeability
+coefficient $\beta>0$, in familiar configurations: In free space we
+place a semipermeable vesicle in a quiescent flow, a planar shear flow,
+and a Poiseuille flow. For each example, we fix the vesicle length and
+examine the enclosed water content as a dynamic consequence of water
+flow, vesicle shape deformation, and membrane tension distribution.
+%
+Under these flows, our simulations show
+that the steady state of an impermeable vesicle is different from that of a semipermeable vesicle, which depends only on the strength of the external flow and is insensitive to permeability $\beta$ (as long as $\beta>0$).
+We find that  the time in the dynamic evolution towards equilibrium is scaled by $\beta^{-1}$: the smaller $\beta$ is the longer it takes to reach the steady state.
+
+In experiments, vesicles under shear flows are measured for a few
+minutes (chapter 19 in~\cite{Dimova2020_GVB}), a duration over which a
+vesicle can be assumed impermeable~\cite{AbkarianViallat2005_BJ}. Our
+simulations of a semipermeable vesicle under these flows in open
+geometry show that water permeability may lead to different vesicle
+hydrodynamics only after a duration of $\sim 1$ day.
+
+%short time scales.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Quiescent Flow} 
 \begin{figure*}[htp]
   \centering
-  \includegraphics[width=\textwidth]{figures/relaxationTensions2.pdf}
-%  \ifTikz
-%    \input{figures/relaxationTensions.tikz}
-%  \else
-%    \includegraphics{figures/relaxationTensions.pdf}
-%  \fi
-  \caption{\label{fig:relaxationTensions} The tension distribution of
-  vesicles in relaxation that corresponds to
-  Figure~\ref{fig:relaxationComposite}.}
+  \ifTikz
+  \input{figures/relaxationComposite.tikz}
+  \else
+  \includegraphics{figures/relaxationComposite.pdf}
+  \fi
+  \caption{\label{fig:relaxationComposite} (a) Snapshots of four
+  semipermeable vesicles with $\beta = 10^{-8}$ submerged in a fluid
+  with no background flow. Time goes from left to right. The red regions
+  correspond to influx and the blue regions correspond to efflux. In all
+  cases, the vesicle reaches a steady state circular shape. (b) The
+  reduced area of each of the simulations. The particular snapshots in
+  (a) occur at the marks along the curve.}
 \end{figure*}
-
-\subsection*{Vesicle Relaxation}
-Figure~\ref{fig:relaxationTensions} shows the membrane tension
-distribution along the relaxing vesicles in
-Figure~\ref{fig:relaxationComposite}. The membrane tension magnitude
-(color bars) is in N/m.  As the semipermeable vesicle relaxes, the
-membrane tension reduces in magnitude and becomes more evenly
-distributed along the membrane. In the top row ($\alpha(0)=0.95$) the
-vesicle nearly relaxes to a circle on the right, and the membrane
-tension is uniform and equal to $k_b \kappa_0^2/2$ as predicted by our
-analysis (see~\eqref{eqn:areaROC2}). In the bottom row
-($\alpha(0)=0.12$), the initial vesicle shape has a lot of high
-curvature regions (and thus the low reduced area), and it takes more
-than four hours to inflate to twice the initial total water content for
-$\beta=10^{-7}$. In contrast the water enclosed inside the vesicle in
-the top row remains nearly constant in the first four hours.
-
-\subsection*{Vesicle in a Planar Shear Flow}
+In the absence of a background flow, a semipermeable vesicle in free
+space can be quantified in terms of its area dynamics and its transition
+to the equilibrium shape. Our analysis in \S~\ref{subsec:area_dynamics} shows
+that a semipermeable vesicle relaxes to a circle at a rate that is
+proportional to $\beta$, and the steady state tension is $\Lambda =
+2\pi^2/L^2$. Our analysis further shows that the time for a
+semipermeable vesicle to deviate from its initial reduced area and to
+reach its steady state is proportional to $\beta^{-1}$. For this reason,
+our numerical results are reported in terms of the scaled time $\beta
+t$.
+
+In Figure~\ref{fig:relaxationComposite}, we examine the relaxation
+dynamics of a semipermeable vesicle with four initial shapes and reduced
+areas as labeled. The vesicles on the left are color-coded by the water
+permeation flux: red denotes an influx into the vesicle, and blue
+denotes an efflux out of the vesicle. First we observe that the initial
+vesicle shape determines the direction of water flux. For the vesicle
+with an initial reduced area $\alpha(0)=0.12$ (bottom row) the vesicle
+deflates (blue regions) first due to the high interior capillary
+pressure that corresponds to the high membrane curvatures. For the other
+three cases efflux is dominated by influx, especially after $t=1$ day
+when the increase in total water content becomes non-negligible.
+%
+%is found at some locations of high curvature, while
+%mostly water permeates into the vesicle and significant change in the
+%reduced area is found at $t\sim 1$ hour. 
+%
+Over time (about four weeks) all vesicles inflate and as expected, each
+vesicle eventually reaches a circular shape with reduced area
+$\alpha=1$. 
+%%These regions are denoted in blue and are only present at early times. 
+%Finally, the vesicles's reduced area do not steady state tension is
+%$\Lambda = 2\pi^2/L^2$. 
+%Therefore, the times for the vesicle to deviate from its initial reduced area and to reach its
+%steady state are proportional to $\beta^{-1}$. 
+%
+%Each of the four cases in Figure~\ref{fig:relaxationComposite} eventually
+%reaches a circular shape with reduced area $\alpha=1$. Next, we observe
+%that even though the vesicle is inflating to a circle, 
+%%meaning that there is a net flux into the vesicle, 
+%there are regions where the flux
+%is out of the vesicle. These regions are denoted in blue and are only
+%present at early times. 
+%
+%Finally, the vesicles's reduced area do not
+%change by much at early times (up to ten minutes), and
+
+Between $t=30$ minutes and $t=1$ day, the total water content is nearly constant.
+%
+%the intermediate shapes of
+%semipermeable vesicles resemble the shape of an impermeable vesicle.
+%
+This can be explained by considering the two terms that contribute to
+the vesicle velocity: (i) the permeability velocity, $\beta(\ff \cdot
+\nn) \nn$, and (ii) the force balance velocity, $\SS[\ff]$. Since
+$\beta\ll 1$, the permeability velocity is much smaller than the force
+balance velocity at early times, and the semipermeable vesicle dynamics
+resemble those of an impermeable vesicle. As the force balance velocity
+decreases, the permeability velocity dominates, and the vesicle begins
+to inflate to a circle with vanishing force and velocity.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Planar Shear Flow}
+\begin{figure*}[htp]
+  \centering
+  \ifTikz
+  \input{figures/shearComposite.tikz}
+  \else
+  \includegraphics{figures/shearComposite.pdf}
+  \fi
+  \caption{\label{fig:shearComposite} (a) The reduced area of a
+  semipermeable vesicle with $\beta = 10^{-3}$ initialized with four
+  different reduced areas in a shear flow with two different flow rates.
+  (b) The equilibrium shape of a vesicle with varying flow rates and
+  membrane permeability. The circled vesicles correspond to the
+  simulations in part (a).}
+\end{figure*}
+
+We consider a semipermeable vesicle in a planar shear flow,
+characterized by the elastic capillary number $Ca_\mathrm{E}=\chi\tau$ where $\tau$ is the characteristic time scale from balancing the viscous stress with the elastic stress
+%in the non-dimensionalization 
+(see \S~\ref{sec:formulation}) and $\chi$ is the shear rate of the planar
+shear flow $\uu_{\infty}(\xx) = \chi (y,0)$.  When $\beta=0$
+(impermeable case), the vesicle reduced area and fluid viscosity
+contrast determine whether a vesicle tank treads or
+tumbles~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. Focusing on
+semipermeable vesicles with no viscosity contrast, we find that a
+semipermeable vesicle tilts to an inclination angle and undergoes
+tank-treading dynamics, similar to the case of an impermeable vesicle.
+
+In Figure~\ref{fig:shearComposite}(a), using four initial reduced areas
+and two flow rates, we plot the reduced area of a semipermeable vesicle
+with $\beta = 10^{-3}$. As observed in a quiescent flow, the final
+vesicle shape is independent of the initial reduced area. However, it
+does depend on the flow rate. We also observe that the amount of water
+inside the vesicle remains constant until $t\sim 2$ hours, when the
+normal component of the flow velocity becomes significantly smaller than
+the permeable velocity, leading to a changing reduced area.
+
+For a variety of dimensionless permeability coefficient $\beta>0$ and
+capillary number $Ca_\mathrm{E}$, a semipermeable vesicle reaches an
+equilibrium shape as in Figure~\ref{fig:shearComposite}(a). Since the
+equilibrium shape depends on $Ca_\mathrm{E}$ and is independent of the
+initial reduced area, we initialize the vesicle with reduced area
+$\alpha = 0.65$ for all simulations in
+Figure~\ref{fig:shearComposite}(b), where we summarize the equilibrium
+vesicle shape and its reduced area. We see that the capillary number
+(flow rate) significantly affects the final vesicle shape, but the
+permeability coefficient has a very minor effect. Instead, as we saw in
+the quiescent analysis, $\beta$ sets a time scale since the time
+required for a vesicle to reach its steady state configuration is
+proportional to $\beta^{-1}$.
+
 Our simulations of a semipermeable vesicle in a planar shear flow show
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Poiseuille Flow}
+\begin{figure*}[htp]
+  \centering
+  \ifTikz
+  \input{figures/parabolicComposite.tikz}
+  \else
+  \includegraphics{figures/parabolicComposite.pdf}
+  \fi
+  \caption{\label{fig:parabolicComposite} (a) The equilibrium shape of
+  a semipermeable vesicle submerged in a Poiseuille flow with varying
+  initial reduced areas and flow rates. The red regions correspond to
+  influx and the blue regions correspond to efflux. (b) The steady
+  state vertical displacement at four different flow velocities. The
+  steady state shapes are superimposed. (c) The reduced area of the
+  slipper formed with the flow rate of $800 \; \mu$m/s. (d) The vesicle
+  shape shown with the background imposed flow. The channel width is
+  12.5 times larger than the vesicle radius. The corresponding reduced
+  area of each vesicle is indicated by the marks in plot (c).}
+\end{figure*}
+
+We consider a semipermeable vesicle in the Poiseuille flow $\uu =
+U(1-(y/W)^2,0)$, where $U$ is the maximum velocity at $y=0$. The
+non-linear effects of the Poiseuille flow on the migration of an
+impermeable vesicle have been well-studied~\cite{kao-bir-mis2009}: At a
+given value of the maximum velocity $U$, there exists a critical reduced
+volume above which the equilibrium vesicle shape is symmetric (parachute
+or bullet shapes) and the vesicle stays at $y=0$. Below this critical
+reduced volume the equilibrium vesicle moves off the center and is
+asymmetric (tank-treading slipper shape). We validated our numerical
+codes by comparing against results in Kaoui {\em et
+al.}~\cite{kao-bir-mis2009} (see \S~\ref{subsec:numerical_validation}).
+
+%
+%
+%We examine the effect of the non-linear Poiseuille flow on the migration of
+%semipermeable vesicle. In this experiment, the vesicle is initialized
+%above the center line $y=0$, and it migrates towards the center
+%line~\cite{dan-vla-mis2009}. 
+%
+%For an impermeable vesicle, depending on
+%the vesicles reduced area and the flow rate, the equilibrium vesicle shape
+%is either an axisymmetric parachute or bullet, or an asymmetric
+%tank-treading slipper~\cite{kao-bir-mis2009}. 
+%We validated our numerical codes by comparing against results in Kaoui {\it et al.} \cite{kao-bir-mis2009}.
+%One of the most salient features of an impermeable vesicle in the Poiseuille flow is that, 
+%%
+%%To validate our methods,
+%%in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
+%%for the steady state shape of an impermeable vesicle
+%%vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
+%%qualitatively agree, Kaoui et al.~report that the vesicles with
+%%$\nu=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
+%%axisymmetric. In our simulations these vesicles are slightly asymmetric,
+%%are undergoing a tank treading motion, and we therefore report them as
+%%asymmetric slippers.
+%
+%Having validated our method, we investigate the dynamics of a semipermeable vesicle in a Poiseuille flow. 
+%
+%Using several initial
+%$U(1-(y/W)^2,0)$, where $U$ is the maximum imposed velocity. We examine
+%the effect of the non-linear Poiseuille flow on the migration of
+%semipermeable vesicle. 
+%
+
+At the beginning of the simulations, a semipermeable vesicle is placed
+above the center line $y=0$ and it migrates towards the center line as
+in the impermeable case~\cite{dan-vla-mis2009}. 
+%
+%However,
+%for an impermeable vesicle, depending on the initial reduced area and
+%the maximum flow velocity $U$, the equilibrium vesicle shape is either
+%an axisymmetric parachute or bullet, or an asymmetric tank-treading
+%slipper~\cite{kao-bir-mis2009}. 
+%
+%To validate our methods,
+%in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
+%for the steady state shape of an impermeable vesicle
+%vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
+%qualitatively agree, Kaoui et al.~report that the vesicles with
+%$\alpha=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
+%axisymmetric. In our simulations these vesicles are slightly asymmetric,
+%are undergoing a tank treading motion, and we therefore report them as
+%asymmetric slippers.
+%
+Using several initial reduced areas and flow rates, we recreate the
+impermeable vesicle phase diagram for vesicles with $\beta = 10^{-3}$.
+The equilibrium vesicle shape for different $U$ and initial reduced area
+is summarized in Figure~\ref{fig:parabolicComposite}(a), and the
+vertical displacement of the vesicle's center of mass is in
+Figure~\ref{fig:parabolicComposite}(b). The effect of semipermeability
+of a vesicle with $\alpha(0) = 0.9$ and $U=800\; \mu$m/s on its reduced
+area and migration pattern are shown in
+Figures~\ref{fig:parabolicComposite}(c)
+and~\ref{fig:parabolicComposite}(d), respectively.
+
+As observed for the planar shear flow, the equilibrium reduced area of a
+semipermeable vesicle in a Poiseuille flow is independent of the initial
+reduced area and $\beta$, and  larger maximum flow velocity $U$ results
+in smaller equilibrium reduced area
+(Figure~\ref{fig:parabolicComposite}(a)). At the smallest velocity $U=
+200\; \mu$m/s, the steady state reduced area is large, and the
+equilibrium vesicle shape is an axisymmetric bullet. The equilibrium
+reduced area decreases with increasing $U$, and the nonlinear flow
+profile gives rise to an asymmetric tank-treading slipper for $U\ge 400$
+$\mu m/s$. We observe that the membrane permeability to water
+drastically alters the equilibrium vesicle shape and position relative
+to the Poiseuille flow: At $\beta=10^{-3}$ the equilibrium vesicle
+depends only on the maximum velocity $U$ of the nonlinear shear flow.
+The higher $U$ the smaller the equilibrium reduced area and the farther
+away the vesicle is relative to the flow center at $y=0$.
+
+In a nonlinear shear flow, an impermeable vesicle can reach equilibrium
+position at the mid-plane of the shear flow for sufficiently large
+reduced area, regardless of the maximum flow velocity $U$. For a
+semipermeable vesicle, however, our simulation results (summarized in
+Figure~\ref{fig:parabolicComposite}) show that the equilibrium vesicle
+shape and position are determined by $U$, and independent of the initial
+vesicle reduced area and permeability $\beta$. The corresponding
+membrane tension distribution is shown in
+Figure~\ref{fig:parabolicTensions} as a function of flow velocity $U$
+from $200\;\mu$m/s to $800 \;\mu$m/s.
+
 \begin{figure*}[htp]
@@
 
-\subsection*{Vesicle in a Poiseuille flow}
-In a nonlinear shear flow, an impermeable vesicle can reach equilibrium
-position at the mid-plane of the shear flow for sufficiently large
-reduced area, regardless of the maximum flow velocity $U$. For a
-semipermeable vesicle, however, our simulation results (summarized in
-Figure~\ref{fig:parabolicComposite}) show that the equilibrium vesicle
-shape and position are determined by $U$, and independent of the initial
-vesicle reduced area and permeability $\beta$. The corresponding
-membrane tension distribution is shown in
-Figure~\ref{fig:parabolicTensions} as a function of flow velocity $U$
-from $200\;\mu$m/s to $800 \;\mu$m/s.
-
 We note that in the Poiseuille flow the membrane tension is positive in
@@
 
-\subsection*{Vesicle in a Closely-Fit Channel}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{A semipermeable vesicle under strong confinement}
+Here we consider a semipermeable vesicle under strong confinement: a
+long closely-fit channel and a contracting channel. In a narrow
+microfluidic channel, a large pressure jump is often needed to push the
+vesicle through a closely-fit channel~\cite{abk-fai-sto2006}.  Our
+simulations show that such a configuration can lead to an amplification
+of water permeation at a time scale shorter than a few minutes. In
+addition, we find that a large value of $\beta$ is needed to keep the
+membrane tension below the threshold value for membrane poration. Such
+high permeability for water may be regarded as an indication that the
+lipid bilayer membrane is porated under strong confinement, and our
+model vesicle is for a porated vesicle within the Helfrich free energy
+framework.  As in the previous examples, we fix the vesicle length and
+examine the enclosed water content as a dynamic consequence of water
+flow, vesicle shape deformation, and membrane tension distribution.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Semipermeable Vesicle in a Closely-fit Channel (Stenosis)}
+ \begin{figure*}[hbp]
+  \centering
+  \ifTikz
+  \input{figures/stenosisComposite.tikz}
+  \else
+  \includegraphics{figures/stenosisComposite.pdf}
+  \fi
+  \caption{\label{fig:stenosisComposite} (a) A semipermeable vesicle
+   passing through a closely-fit channel similar to the experimental
+   device in~\cite{abk-fai-sto2006}. (b) A semipermeable vesicle passing
+   through a  (four-times) longer closely-fit channel than (a). (c) The
+   excess pressure of an impermeable and semipermeable vesicle in the
+   short geometry in (a). (d) The reduced area of the semipermeable
+   vesicles in the geometries in (a) and (b) as a function of the
+   vesicles' center of mass. In (c) and (d), the x-axis is scaled by
+   $1/L$ where $L$ is half the length of the constriction. (e) The
+   reduced area of the semipermeable vesicles in the geometries in (a)
+   and (b) as a function of time. The time axis is scaled by $1/t_R$
+   where $t_R$ is the residency time. In parts (c) and (d), the dashed
+   lines correspond to the locations of the inlet and outlet. In part
+   (e), the dashed lines correspond to the times that the vesicle enters
+   and exits the constriction. The colored vesicles show the tension
+   distribution in N/m of the circled vesicles. Throughout the entire
+   simulation, these vesicle configurations have the largest tension.}
+\end{figure*}
+
+When red blood cells go through small capillary vessels, they experience
+large shape deformation and significant membrane stretching that
+triggers ATP release~\cite{Wan2008_PNAS, ForsythWan2011_PNAS}.  Many
+cells exhibit extraordinary flexibility as they go through narrow
+vessels~\cite{AuStoreyMoore2016_PNAS}, and adjustment of
+surface-to-volume ratio may be a key factor for a successful passage.
+Here we quantify the effect of water permeability on a vesicle going
+through a stenosis (a long microfluidic channel with a width smaller
+than the cell radius).  Based on the findings in~\cite{abk-fai-sto2006},
+we first examine the effect of semipermeability on the pressure
+fluctuation across a stenosed geometry. In this experiment, a pressure
+drop is used to squeeze a red blood cell through a constriction with
+diameter $5\;\mu$m and length $45\;\mu$m. We set up a similar
+computational geometry with a Poiseuille flow imposed at the inlet and
+outlet (Figure~\ref{fig:stenosisComposite}(a)). We set the maximum flow
+velocity to $U_{\max} = 1000 \;\mu$m/s at the inlet and outlet so that
+the residency time of the vesicle in the stenosis channel is $t_R
+\approx 25$ ms which agrees with the experimental
+results~\cite{abk-fai-sto2006}. When the red blood cell enters the
+channel, an increase in the pressure drop is required to maintain a
+constant flow rate, and the difference in the pressure drop is called
+the excess pressure.
+
+We consider both an impermeable and semipermeable vesicle with initial
+reduced area $\alpha = 0.65$ passing through a long narrow channel and
+compute the excess pressure as a function of vesicle position in the
+channel (Figure~\ref{fig:stenosisComposite}(c)). The impermeable case
+agrees with experimental results~\cite{abk-fai-sto2006} (see Figure 3).
+Our simulations show that less excess pressure is needed to drive a
+semipermeable vesicle through the closely-fit channel. Once in the
+channel, the vesicle takes a bullet shape with maximum tension in the
+front and minimum tension in the back
+(Figure~\ref{fig:stenosisComposite}(a)), consistent with earlier
+results~\cite{Pak2015_PNAS, HarmanBertrandJoos2017_CJP}.
+
+Figures~\ref{fig:stenosisComposite}(d)
+and~\ref{fig:stenosisComposite}(e) show that the vesicle deflates from
+the beginning due to the high flow velocity, consistent with the results
+for a vesicle in a Poiseuille flow in open space. As the vesicle enters
+the stenosis channel, it continues to deflate in the front even though
+we observe influx (red segment) at various rear locations in the
+membrane. Overall, the vesicle loses about 6.1\% of its initial total
+water at a constant rate as shown in
+Figures~\ref{fig:stenosisComposite}(d)
+and~\ref{fig:stenosisComposite}(e) (blue curves). Thus we expect that a
+larger amount of deflation is possible if the vesicle is inside a longer
+stenosis: we consider a vesicle passing through a channel of triple the
+length in Figure~\ref{fig:stenosisComposite}(b) with
+$U_{\max}=1000\;\mu$m/s, and we observe that vesicle stays inside the
+stenosis for a residence time $t_R \approx 70$ ms and the area decreases
+by 13.2\% (red curves).
+
 When a semipermeable vesicle goes through a closely-fit channel, we observe that the water efflux is found in the front, and the influx is in the rear of the vesicle membrane (Figure~\ref{fig:stenosisComposite}).
@@
 
-\subsection*{Vesicle Going Through a Contracting Channel (Slit)}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Semipermeable Vesicle in a Contracting Geometry} 
+\begin{figure}[htp]
+  \centering
+  \ifTikz
+  \input{figures/contractingComposite.tikz}
+  \else
+  \includegraphics{figures/contractingComposite.pdf}
+  \fi
+  \caption{\label{fig:contractingComposite} A contracting channel
+  similar to the experimental configuration in~\cite{wu2015critical}.
+  The channel width varies from $18\;\mu$m to $1.8\;\mu$m, and it
+  repeats every $45\;\mu$m. The fluid flux along the red regions is into
+  the vesicle, and the fluid flux along the blue regions is out of the
+  vesicle.  (a--c): The ability for a semipermeable vesicle to pass
+  through the contraction depends on the permeability $\beta$. (d--f):
+  The ability for a semipermeable vesicle to pass through the
+  contraction depends on the flow rate. The colored vesicles show the
+  tension distribution in N/m of the circled vesicles. Throughout the
+  entire simulation, these vesicle configurations have the largest
+  tension.}
+\end{figure}
+
+Squeezing a cell or an elastic vesicle through a slit in microfluidics
+has gained popularity for its application in stress-induced release of
+macromolecules~\cite{ShareiEtAl2013_PNAS, Pak2015_PNAS,
+ZhangShenHoganBarakatMisbah2018_BJ, LuoBai2019_PoF}. Red blood cells go
+through submicron slits many times during their lifetime, and this
+process selects healthy, flexible red blood cells to
+survive~\cite{wu2015critical,LuPeng2019_PoF}. Here we investigate the
+role of membrane permeability to water when a semipermeable vesicle is
+squeezed through a contracting microfluidic channel similar
+to~\cite{wu2015critical}, where the width of the channel gradually
+decreases from $18 \;\mu$m to $1.8\; \mu$m. The channel then immediately
+reopens to $18\;\mu$m (Figure~\ref{fig:contractingComposite}). A
+Poiseuille flow is imposed at the inlet and outlet with a constant
+maximum flow rate of $U_{\max}$. We initialize a semipermeable vesicle
+with $\alpha = 0.65$ that spans $10\; \mu$m of the total channel width
+and investigate the effects of the membrane permeability to water and
+the maximum flow velocity on whether a vesicle can successfully pass
+through the slit. We color the vesicle according to the sign of its
+flux---red for influx and blue for efflux.
+
+In Figures~\ref{fig:contractingComposite}(a)
+and~\ref{fig:contractingComposite}(b), we plot snapshots of vesicles
+with different permeability $\beta$.
+Figure~\ref{fig:contractingComposite}(c) shows the corresponding reduced
+area as a function of the vesicle's location. We observe that if the
+permeability is sufficiently large, the vesicle inflates gradually over
+seconds before it reaches the neck, and then it quickly deflates within
+a fraction of a second. However, if the permeability $\beta$ is too
+low, the vesicle is too large when it reaches the narrowest part of the
+channel, and it is unable to pass. In
+Figures~\ref{fig:contractingComposite}(d)
+and~\ref{fig:contractingComposite}(e), we plot snapshots of vesicles
+with different imposed maximum velocities, and
+Figure~\ref{fig:contractingComposite}(f) shows the reduced area as a
+function of the vesicle's location. At low velocities, the vesicle
+inflates similar to the unbounded parabolic flow example, and it is
+unable to pass through the contraction. However, higher flow rates
+result in additional deflation and the vesicle passes through the
+contraction.
+
+\begin{figure}[hbp]
+  \centering
+  \ifTikz
+  \input{figures/contractingComposite2.tikz}
+  \else
+  \includegraphics{figures/contractingComposite2.pdf}
+  \fi
+  \caption{\label{fig:contractingComposite2} Vesicle reduced area and
+  velocity vs.~time. The permeability coefficient is $\beta = 10^{-3}$
+  and the maximum velocity is $18\;\mu$m/s. (a) A semipermeable vesicle
+  passing through six periods of the contracting geometry. (b) The
+  reduced area with the marks representing shapes in (a). (c) The
+  vesicle velocity with the marks representing shapes in (a). In (b) and
+  (c), the lower x-axis is the x-coordinate of the center of mass, and
+  the upper x-axis is time. The colored vesicles show the tension
+  distribution in N/m of the circled vesicles. Throughout the entire
+  simulation, these vesicle configurations have the largest tension.}
+\end{figure}
+To understand the effects of water permeability on a vesicle that
+repeatedly passes through micro-capillary vessels or sub-micron slits,
+we construct a contracting geometry
+(Figure~\ref{fig:contractingComposite2}) to simulate a vesicle passing
+through the contracting geometry six times.  In
+Figure~\ref{fig:contractingComposite2}(b), we show that the vesicle
+deflates each time it passes through the contraction followed by a
+gradual inflation (over seconds). The total area loss over the history
+of the vesicle is almost 50\%. In
+Figure~\ref{fig:contractingComposite2}(c), we show the vesicle velocity
+as a function of the vesicle's center of mass. As the vesicle passes
+through the contraction, it first accelerates until it reaches the neck
+where it abruptly decelerates to go through the contraction. The reduced
+area and velocity with respect to time are also shown in
+Figure~\ref{fig:contractingComposite2}.
+
 When a semipermeable vesicle goes through a contracting channel (slit)
@@
 
+\section{Discussion}
+In this work we investigate the effects of membrane permeability to
+water on vesicle hydrodynamics. Without any external flow or
+confinement, our analysis shows that a semipermeable vesicle always
+inflates to maximize the water content inside the vesicle of a fixed
+length (area) in two (three) dimensions. Results from analysis and
+numerical simulation show that such relaxation of a semipermeable
+vesicle is characterized by a rescaled time $\beta t$. We further
+illustrate that the relaxation process consists of at least two phases:
+The first phase is dominated by the balance between membrane traction
+and viscous stress at early times (up to five minutes), when the vesicle
+behaves like an impermeable membrane. The second phase sets in after a
+few hours, when water influx begins to dominate and inflate the vesicle.
+Over a time scale of more than four weeks, a semipermeable vesicle is
+fully inflated, independent of its initial surface-to-volume ratio.
+
+Under strong confinement we show that water permeation can be amplified
+on a time scale of a few seconds as a vesicle is squeezed through a
+closely-fit channel and a contracting channel. As a semipermeable
+vesicle goes through a long closely-fit channel, we observe that the
+vesicle loses water at a constant rate, and the longer the channel the
+more the loss of water. In the case of a contracting channel, we find
+that both permeability and the pressure gradient across the slit must be
+sufficiently large for a successful passage. Throughout these
+simulations the membrane tension is below the threshold for membrane
+poration. Thus we expect the continuum membrane theory to well-capture
+the vesicle hydrodynamics, and our simulation results shed light on the
+configuration and time scales needed to observe the effects of
+permeability on vesicle hydrodynamics under confinement.
+
+%Using scaling arguments, we showed that permeability due to osmolarity
+%is two orders of magnitude larger than permeability due to tension, and
+%six orders of magnitude larger than permeability due to bending.
+%Therefore, future studies will investigate semipermeable membranes
+%suspended in a solvent with a solute concentration. The presence of a
+%solute is responsible for many physiological processes including cell
+%migration in confined
+%microenvironments~\cite{StrokaJiangChenEtAl2014_Cell,
+%papadopoulos2008aquaporins}, dialysis~\cite{wan2006}, cell
+%desiccation~\cite{vogl2014effect}, and
+%apoptosis~\cite{marchetti1996mitochondrial}.
+
+Cells exhibit a dynamic volume-to-surface ratio in 
+many physiological processes, such as 
+cell migration in confined microenvironments~\cite{StrokaJiangChenEtAl2014_Cell, papadopoulos2008aquaporins}, 
+dialysis~\cite{wan2006}, cell desiccation~\cite{vogl2014effect}, cell division~\cite{OdermattMiettinenKangEtAl2020_bioRxiv}, and
+apoptosis~\cite{marchetti1996mitochondrial}.
+%osmotic flow across the membrane.
+While osmotic stress  is more effective and efficient than mechanical stress in contributing to change in cellular volume, our results suggest that the water permeation due to the capillary pressure may be non-negligible over long times or under strong confinement in simple configurations.
+To examine if this is the case in the physiological processes,  currently we are examining the combined effects of osmotic and mechanical stresses on water permeation in the small Peclet number limit, which is relevant to cellular migration in the presence of both confinement and a solute gradient~\cite{StrokaJiangChenEtAl2014_Cell} and has been studied numerically by Jaeger {\em et al.}~\cite{jae-car-med-try1999}.
+
+%While the solute dynamics
+%is governed by an advection-diffusion equation, many biophysical
+%applications involve speeds no greater than $\sim 50$
+%$\mu$m/hour~\cite{StrokaJiangChenEtAl2014_Cell}, a length scale of 10
+%$\mu$m, and a solute diffusivity of $\sim 10^{-10}$ m$^2$/s (glucose in
+%water). The resulting Peclet number is $\sim 10^{-2}$, and this limit
+%has been analyzed for spherical vesicles by Anderson~\cite{and1983} and
+%more general shapes using a finite element method by Jaeger {\em et
+%al.}~\cite{jae-car-med-try1999}. Since the dynamics of the concentration
+%is diffusion-dominated, we will use a stable and accurate boundary
+%integral method that is similar to the numerical method we apply to the
+%hydrodynamics (see Supplementary Material).
+
+\acknowledgments
+We thank Howard Stone, Michael J.~Shelley, Petia Vlahovska,
+Chaoqui Misbah, Manouk Abkarian, Sangwoo Shin, and Shravan
+K.~Veerapaneni for discussions. B.Q.~acknowledges support from the
+Simons Foundation, Mathematics and Physical Sciences-Collaboration
+Grants for Mathematicians, Award Number 527139.  Y.-N.Y.~acknowledges
+support from NSF (DMS 1614863, DMS 195160) and Flatiron Institute, part
+of Simons Foundation.
+
+\bigskip
+
+ \bibliography{refs}
 \end{document}
-
-% OLD TEXT AND PLOTS FROM THE NUMERICAL EXAMPLES
-
-%We plot the area of a vesicle with six different permeability rates in
-%Figure~\ref{fig:ellipseArea}. The area is computed directly from the
-%vesicle shape and the time axis is scaled by $\beta$. The plot verifies
-%that the time for the vesicle to reach a circular shape is proportional
-%to $\beta^{-1}$. We also solve~\eqref{eqn:areaROC} for the $\beta=10$
-%simulation and superimpose its solution with dots on
-%Figure~\ref{fig:ellipseArea}.
-
-%\begin{figure}[htp]
-%  \centering
-%%  \ifTikz
-%%  \input{figures/ellipseArea.tikz}
-%%  \fi
-%  \includegraphics[width=0.9\linewidth]{figures/ellipseArea}
-%  \caption{\label{fig:ellipseArea} The area of an elliptical
-%  semipermeable vesicle, with permeability rate $\beta$ in a quiescent
-%  flow. The time axis is scaled by the permeability rate $\beta$. Since
-%  the curves collapse to a single curve, the permeability rate $\beta$
-%  sets a relaxation time scale.}
-%\end{figure}
-
-%We further analyze the transient dynamics by considering the vesicle
-%velocity~\eqref{eqn:vesVelocity} for small $\beta$. Two terms contribute
-%to the vesicle velocity: (i) the permeability velocity, $\beta(\ff \cdot
-%\nn)\nn$, and (ii) the force balance velocity, $\SS[\ff]$. Since $\beta
-%\ll 1$, the permeability velocity is much smaller than the force balance
-%velocity at early times, and the semipermeable vesicle dynamics
-%resembles those of an impermeable vesicle. As the force balance velocity
-%decreases, the permeability velocity becomes significant, and the
-%vesicle begins to inflate to a circle. This results in the membrane
-%force and velocity both converging to zero. Letting $\beta = 10^{-3}$,
-%the normal component of the force balance velocity (blue) and the
-%permeability velocity (red) are plotted at three times in
-%Figure~\ref{fig:vesVelocity}. We also plot the velocity (green) of an
-%identically initialized impermeable vesicle. At the early time $t=0.5$,
-%the permeability velocity is negligible relative to the force balance
-%velocity, and the force balance velocity matches with the impermeable
-%vesicle velocity. At intermediate time $t=5$, all three velocities are
-%comparable in size, and the semipermeable vesicle begins to inflate.
-%Finally, at time $t=50$, the impermeable vesicle is near steady state,
-%while the semipermeable vesicle is still inflating. The right-most
-%plot of Figure~\ref{fig:vesVelocity} is the maximum norm of the
-%different velocity contributions as a function of time, and the black
-%vertical lines correspond to the times reported in the other three
-%subplots.
-%
-%\begin{figure*}[htp]
-%  \centering
-%%  \scalebox{0.6}{\input{figures/ellipseVelocity1.tikz}}
-%%  \scalebox{0.6}{\input{figures/ellipseVelocity2.tikz}}
-%%  \scalebox{0.6}{\input{figures/ellipseVelocity3.tikz}}
-%%  \scalebox{0.6}{\input{figures/ellipseVelocity4.tikz}}
-%%  \input{figures/ellipseVelocityNorms.tikz}
-%  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity1.pdf}
-%  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity2.pdf}
-%  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity3.pdf}
-%  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity4.pdf}
-%  \caption{\label{fig:vesVelocity} The normal velocity contributions due
-%  to force balance (blue) and permeability (red). The green line is the
-%  velocity of an impermeable vesicle with the same initial shape as the
-%  semipermeable vesicle.}
-%\end{figure*}
-
-%We next investigate the interplay between the tension, transmembrane
-%flux, and curvature of a semipermeable vesicle. We let $\beta = 1$ and
-%initialize the vesicle with regions of both positive and negative
-%curvature. The vesicle tension, $\Lambda$, and the flux, $\ff \cdot
-%\nn$, are plotted in Figure~\ref{fig:starTensionFlux}. At early times,
-%regions of large negative curvature have negative tension and regions
-%with large positive curvature have positive tension, and the same result
-%holds for an impermeable vesicle. In addition, regions with large
-%curvature have a large inflow of fluid (positive flux), while the
-%flatter regions have an outflow of fluid. At these early times, the net
-%effect is vesicle deflation. As the vesicle shape relaxes, the same
-%general tension and flux trends persist, but the net flux is positive
-%and the vesicle inflates. At later times, the tension becomes positive
-%and the vesicle continues to inflate towards a circle. Finally, the
-%tension transitions to a positive constant function, the membrane force
-%and flux approach zero, and the vesicle shape reaches its steady
-%circular shape.
-
-%\begin{figure*}[htp]
-%  \centering
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
-%
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
-%
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
-%
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
-%
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime5.pdf}
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
-%
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime6.pdf}
-%  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime6.pdf}
-%  \caption{\label{fig:starTensionFlux} The vesicle tension (left) and
-%  flux (right) of the semipermeable vesicle in a quiescent flow with
-%  $\beta=1$.}
-%\end{figure*}
-
-%\begin{figure*}[htp]
-%  \centering
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime5.pdf}
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime6.pdf}
-%
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
-%  \includegraphics[width=0.16\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime6.pdf}
-%  \caption{\label{fig:starTensionFlux} The vesicle tension (top) and
-%  flux (bottom) of the semipermeable vesicle in a quiescent
-%  flow with $\beta=1$.}
-%\end{figure*}
-
-%\begin{figure}[htp]
-%  \centering
-%  \ifTikz
-%  \input{figures/shearSS.tikz}
-%  \fi
-%%  \includegraphics[width=0.9\linewidth]{figures/shearSS.pdf}
-%  \caption{\label{fig:shearSS} The reduced area of a semipermeable
-%  vesicle in a shear flow. The final reduced area is nearly independent
-%  of the initial reduced area.}
-%\end{figure}
-
-%\begin{figure}[htp]
-%  \centering
-%  %\ifTikz
-%  \input{figures/shearPhaseDiagramRA2.tikz}
-%  %\fi
-%%  \includegraphics[width=\linewidth]{figures/shearPhaseDiagramRA2.pdf}
-%  \caption{\label{fig:shearPhaseDiagram} The steady state shape of a
-%  semipermeable vesicle with several different permeability rates
-%  $\beta$ and shear rates $\dot{\gamma}$. The final reduced areas are
-%  reported for the largest and smallest parameter values. The final
-%  reduced area decreases with the flow rate, while the permeability rate
-%  has a very small effect on the steady state shape.}
-%\end{figure}
-
-%\begin{figure}[htp]
-%%  \ifTikz
-%%  \input{figures/parabolicOffCenterPhaseImpermeable.tikz}
-%%  \fi
-%  \includegraphics[width=0.9\linewidth]{figures/parabolicOffCenterPhaseImpermeable.pdf}
-%  \caption{\label{fig:parabolicOffCenterImpermeablePhaseDiagram} Phase
-%  diagram of an impermeable vesicle with several different flow rates
-%  $U$ and reduced areas $\nu$. As shown by Kaoui et
-%  al.~\cite{kao-bir-mis2009}, the final vesicle shape is either an
-%  axisymmetric parachute or bullet (pink region) or an asymmetric
-%  slipper (yellow region).}
-%\end{figure}
-
-%\begin{figure}[htp]
-%%  \ifTikz
-%%  \input{figures/parabolicOffCenterPhaseSemipermeable.tikz}
-%%  \fi
-%  \includegraphics[width=0.9\linewidth]{figures/parabolicOffCenterPhaseSemipermeable.pdf}
-%  \caption{\label{fig:parabolicOffCenterSemipermeablePhaseDiagram} Phase
-%  diagram of a semipermeable vesicle, with $\beta = 10^{-3}$, with
-%  several different flow rates $U$ and reduced areas $\nu$. The
-%  steady state reduced area for each flow rate, which is reported along
-%  the top of the vesicles, is nearly independent of the initial reduced
-%  area. Low flow rates result in axisymmetric vesicles with large
-%  reduced area, and high flow rates result in asymmetric vesicles with
-%  low reduced area. Results at higher flow rates are not eporeted since
-%  the vesicle self-intersects.}
-%\end{figure}
-
-%\begin{figure}[htp]
-%%  \ifTikz
-%%  \scalebox{0.5}{\input{figures/stenosisShapeTension01.tikz}}
-%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux02.tikz}}
-%%  \scalebox{0.5}{\input{figures/stenosisShapeTension03.tikz}}
-%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux04.tikz}}
-%%  \scalebox{0.5}{\input{figures/stenosisShapeTension05.tikz}}
-%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux06.tikz}}
-%%  \scalebox{0.5}{\input{figures/stenosisShapeTension07.tikz}}
-%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux08.tikz}}
-%%  \scalebox{0.5}{\input{figures/stenosisShapeTension09.tikz}}
-%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux10.tikz}}
-%%  \scalebox{0.5}{\input{figures/stenosisShapeTension11.tikz}}
-%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux12.tikz}}
-%%  \scalebox{0.5}{\input{figures/stenosisShapeTension02.tikz}}
-%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux04.tikz}}
-%%  \scalebox{0.5}{\input{figures/stenosisShapeTension06.tikz}}
-%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux08.tikz}}
-%%  \scalebox{0.5}{\input{figures/stenosisShapeTension10.tikz}}
-%%  \scalebox{0.5}{\input{figures/stenosisShapeFlux12.tikz}}
-%%  \fi
-%  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeTension02.pdf}
-%  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeFlux04.pdf}
-%  \\
-%  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeTension06.pdf}
-%  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeFlux08.pdf}
-%  \\
-%  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeTension10.pdf}
-%  \includegraphics[width=0.45\linewidth]{figures/stenosisShapeFlux12.pdf}
-%  \caption{\label{fig:stenosisShape} An impermeable (dashed) and
-%  semipermeable (solid) vesicle in a stenosed geometry (black).
-%  The vesicles' initial configuration are identical with reduced area
-%  $\nu = 0.65$. The color denotes the vesicles' tension (left) and flux
-%  (right). The semipermeable vesicle deflates throughout the
-%  constriction (see Figure~\ref{fig:stenosisArea}) and develops higher
-%  curvature regions than its impermeable counterpart.}
-%\end{figure}
-%
-%\begin{figure}[htp]
-%  \centering
-%%  \ifTikz
-%%  \scalebox{0.5}{\input{figures/stenosisTension12.tikz}}
-%%  \scalebox{0.5}{\input{figures/stenosisFlux12.tikz}}
-%%  \scalebox{0.5}{\input{figures/stenosisXvelocity12.tikz}}
-%%  \scalebox{0.5}{\input{figures/stenosisYvelocity12.tikz}}
-%%  \fi
-%  \includegraphics[width=0.45\linewidth]{figures/stenosisTension12.pdf}
-%  \includegraphics[width=0.45\linewidth]{figures/stenosisFlux12.pdf} \\
-%  \includegraphics[width=0.45\linewidth]{figures/stenosisXvelocity12.pdf}
-%  \includegraphics[width=0.45\linewidth]{figures/stenosisYvelocity12.pdf}
-%  \caption{\label{fig:stenosisTensionAndFlux} The tension (top left), 
-%  flux (top right), $x$-velocity (bottom left), and $y$-velocity (bottom
-%  right) of the semipermeable (red) and impermeable (dashed blue)
-%  vesicles in Figure~\ref{fig:stenosisShape} at location $x=50$. The
-%  point $\theta=0$ corresponds to the right-most point of the vesicle.}
-%\end{figure}
-%
-%\begin{figure}[htp]
-%  \centering
-%%  \ifTikz
-%%  \input{figures/stenosisArea.tikz}
-%%  \fi
-%  \includegraphics[width=0.8\linewidth]{figures/stenosisArea}
-%  \caption{\label{fig:stenosisArea} The area of a stenosed
-%  semipermeable vesicle, with permeability rate $\beta=10^{-3}$. The
-%  $x$-axis is the $x$-coordinate of the center of mass of the vesicle.
-%  The vesicle loses fluid at a constant rate throughout the constriction
-%  that is between $\pm 60$. The semipermeable vesicle loses 12.8\% of
-%  its fluid.}
-%\end{figure}
-%
-%
-%\begin{figure}[htp]
-%%  \ifTikz
-%%  \input{figures/stenosisBL.tikz}
-%%  \fi
-%  \includegraphics[width=\linewidth]{figures/stenosisBL.pdf}
-%  \caption{\label{fig:stenosisBL} A stenosed semiimpermeable (red) and
-%  imperemable (blue) vesicle. The semipermeable vesicle has 
-%  reduced area 0.17, and both vesicles were initialized with reduce area
-%  $0.20$. The bottom plot shows the velocity relative to the vesicle
-%  inside the lubrication layer.  The vesicle velocity in the square is
-%  nearly constant (see Figure~\ref{fig:stenosisRA020Velocity}.}
-%\end{figure}
-%
-%
-%\begin{figure}[htp]
-%  \centering
-%%  \ifTikz
-%%  \scalebox{0.5}{\input{figures/stenosisXvelocityRA020.tikz}}
-%%  \scalebox{0.5}{\input{figures/stenosisYvelocityRA020.tikz}}
-%%  \fi
-%  \includegraphics[width=0.45\linewidth]{figures/stenosisXvelocityRA020.pdf}
-%  \includegraphics[width=0.45\linewidth]{figures/stenosisYvelocityRA020.pdf}
-%  \caption{\label{fig:stenosisRA020Velocity} The $x$ (left) and $y$
-%  (right) velocities of the vesicle in Figure~\ref{fig:stenosisBL}. The
-%  red lines correspond to the semipermeable vesicle and the blue dashed
-%  lines correspond to the impermeable vesicle.}
-%\end{figure}
-%
-%We consider the effect of stenosis on a semipermeable vesicle. To allow
-%for large amounts of fluid flux through the membrane, we consider
-%geometry with a long constricted region. We start by considering a
-%vesicle initialized with reduced area $\nu = 0.65$, and we compare the
-%vesicle shape when $\beta = 0$ (impermeable) and $\beta = 10^{-3}$
-%(permeable). Figure~\ref{fig:stenosisShape} shows the vesicles' shape at
-%several locations along the constriction. The colors along the left
-%channel represent the tension and those along the right represent the
-%flux. In Figure~\ref{fig:stenosisTensionAndFlux}, the tension at
-%location $x=20$ and the flux at location $x=30$ are plotted with respect
-%to arclength. The value of $\theta=0$ corresponds to the nose of the
-%vesicle.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection*{Dimensionless equations}
-%The inextensibility condition guarantees that the vesicle's length, $L$,
-%is conserved, while its area, $A$, can change due to semipermeability.
-%Therefore, the reduced area $\alpha = 4\pi A/L^2 \in (0,1]$ is not
-%conserved. We non-dimensionalize~\eqref{eqn:vesVelocity} by introducing
-%the length scale $R_0 = L/2\pi$ and defining the time scale $\tau = \mu
-%R_0^3/k_b$, the tension scale $Q = k_b/R_0^2$, and the permeability
-%scale $W = R_0/\mu$. The background velocity $\uu_\infty$ is
-%non-dimensionalized with $R_0/\tau$.
-%
-%In each experiment, we initialize an elliptical vesicle with longest
-%diameter of 9$\mu$m. We use a length scale of $R_0 = 10^{-6}$m, a
-%bending stiffness of $k_b = 10^{-19}$J, and fluid viscosity of $\mu=5
-%\times 10^{-2}$kg/ms. Using the relaxation time scale $\tau = \mu
-%R_0^3/k_b = 5 \times 10^{-1}$s, the pressure scale is $P = k_b/R_0^3 =
-%10^{-1}$Pa. 
-% \newpage
-% \paragraph{\bf \Huge OLD STUFF}
-%
-%%%%%%%%%%%%%%%
-%\section{{$\Theta-L$} formulation}
-%Here, we attempt to apply the formulation described by Sohn et
-%al.~\cite{soh-tse-li-voi-low2010} to a semipermeable vesicle.  In the
-%semipermeable formulation, the vesicle velocity is
-%\begin{align}
-%  \pderiv{\XX}{t} = \uu(\XX(t)) + \beta (\ff \cdot \nn) \nn.
-%\end{align}
-%In the {$\Theta-L$} variables, we require a normal velocity $V$, and a
-%tangential velocity $T$. Since the inextensibility condition is $T_s +
-%\kappa V = 0$, a condition for the vesicle velocity is
-%\begin{align}
-%  (\uu \cdot \ss)_s = -\kappa(\beta (\ff \cdot \nn) + 
-%      \uu \cdot \nn).
-%\end{align}
-%This equation can be solved following equations (32)--(39)
-%in~\cite{soh-tse-li-voi-low2010}, with the only difference being that
-%$\tilde{\uu}$ satisfies
-%\begin{align}
-%  (\tilde{\uu} \cdot \ss)_s + \kappa(\tilde{\uu} \cdot \nn) =
-%    -(\vv \cdot \ss)_s - \kappa(\vv \cdot \nn) 
-%    - \beta\kappa(\ff \cdot \nn).
-%\end{align}
-%Compared to equation (40), only the last term is new.
-%
-%
-%%%%%%%%%%%%%%%
-%Finally, we write the time stepping method in matrix form as
-%\begin{align}
-%  A \left(
-%    \begin{array}{c}
-%      \xx^{N+1} \\ \sigma^{N+1}
-%    \end{array}
-%  \right) = 
-%  \left(
-%    \begin{array}{c}
-%      \xx^{N} + \Delta t \uu_\infty(\xx^N) \\ \mathbf{1}
-%    \end{array}
-%  \right),
-%\end{align}
-%where
-%\begin{align}
-% A = \left(
-%  \begin{array}{cc}
-%    I + \Delta t \beta P^N B^N + \Delta t \SS^N B^N & 
-%    -\Delta t P^N T^N - \Delta t \SS^N T^N \\
-%    D^N & 0
-%  \end{array}
-%  \right).
-%\end{align}
-%
-%\section{Area of a Vesicle}
-%The area inside a single vesicle $\gamma$ parameterized with $\xx$ is
-%\begin{align}
-%  A(t) = \int_{\gamma} (\xx \cdot \nn)\, ds = 
-%    \int_{0}^{2\pi} \left(\xx \cdot \pderiv{\xx}{\theta}^\perp\right)
-%    \, d\theta.
-%\end{align}
-%Taking the time derivative of $A(t)$,
-%\begin{align}
-%  \dot{A}(t) &= \int_{0}^{2\pi} \left(
-%    \dot{\xx} \cdot \pderiv{\xx}{\theta}^{\perp} + 
-%    \xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right) \\
-%    \, d\theta.
-%  &= \int_{0}^{2\pi} \left(
-%    (\dot{\xx} \cdot \nn)\|\xx'(\theta)\| \right) d\theta +
-%     \int_{0}^{2\pi}
-%    \xx \cdot \frac{d}{dt}\left(\nn |\frac{d\xx}{d\theta}| \right)
-%\end{align}
-%
-%
-%
-%\begin{align}
-%  A(t) = \frac{1}{2}\int_{\gamma} (\xx \cdot \nn)\, ds = 
-%    \frac{1}{2}\int_{0}^{2\pi} \left(\xx \cdot \pderiv{\xx}{\theta}^\perp\right)
-%    \, d\theta.
-%\end{align}
-%Taking the time derivative of $A(t)$,
-%\begin{align}
-%  \dot{A}(t) &= \frac{1}{2}\int_{0}^{2\pi} \left(\dot{\xx} \cdot
-%  \pderiv{\xx}{\theta}^{\perp} + 
-%    \xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right) d\theta, \\
-%  &= \frac{1}{2}
-%  \int_{0}^{2\pi}(\dot{\xx}\cdot\nn)\left\|\pderiv{\xx}{\theta}\right\|d\theta +
-%     \frac{1}{2}\int_{0}^{2\pi}
-%    \left(\xx \cdot \pderiv{\dot{\xx}}{\theta}^{\perp}\right)d\theta, \\
-%  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds +
-%  \frac{1}{2}\int_{0}^{2\pi}\left(\xx \cdot \pderiv{}{t}\left(\nn
-%  \left\|\pderiv{\xx}{\theta}\right\|\right)\right)d\theta, \\
-%  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds + \frac{1}{2}
-%  \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds + \frac{1}{2}\int_{0}^{2\pi}
-%  \frac{\xx\cdot\nn}{\left\|\pderiv{\xx}{\theta}\right\|}
-%  \left(\pderiv{\xx}{\theta}\cdot
-%  \pderiv{\dot{\xx}}{\theta}\right)d\theta \\
-%  &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds + \frac{1}{2}
-%  \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds + \frac{1}{2}\int_{\gamma}
-%  (\xx\cdot\nn) (\xx_s \cdot \dot{\xx}_s)\, ds.
-%\end{align}
-%To satisfy the inextensibilty condition, $\xx_s \cdot \dot{\xx}_s = 0$.
-%Therefore the time derivative of $A(t)$ is
-%\begin{align}
-%     \dot{A}(t) &= \frac{\beta}{2} \int_{\gamma}\left(\ff\cdot\nn\right)ds
-%     + \frac{1}{2} \int_{\gamma}\left(\xx\cdot\dot{\nn}\right)ds.
-%\end{align}
-%which we re-write as
-%\begin{align}
-%    \dot{A}(t) &= \frac{\beta}{2}
-%    \int_{\gamma}\left(\ff\cdot\nn\right)ds-\frac{1}{2}\int_{\gamma}\left(\xx^{\perp}\cdot\dot{\xx}_s\right) ds.
-%\end{align}
-%Applying integration by parts,
-%\begin{align}
-%    \dot{A}(t) &= \frac{\beta}{2}
-%    \int_{\gamma}\left(\ff\cdot\nn\right)ds+\frac{1}{2}\int_{\gamma}\left(\xx^{\perp}_s\cdot\dot{\xx}\right) ds,
-%\end{align}
-%which we re-write as
-%\begin{align}
-%    \dot{A}(t) &= \frac{\beta}{2}
-%    \int_{\gamma}\left(\ff\cdot\nn\right)ds+\frac{1}{2}\int_{\gamma}\left(\dot{\xx}\cdot\nn\right),\\
-%    \dot{A}(t) &= \beta \int_{\gamma}\left(\ff\cdot\nn\right)ds.
-%\end{align}
-%
-%
-%At steady state,
-%\begin{align}
-%    \dot{A}(t) &= \beta \int_{\gamma}\left(\ff\cdot\nn\right)ds =0.
-%\end{align}
-%We now replace $\ff$ with its definition and apply integration by parts
-%\begin{align}
-%   0=\beta\int_{\gamma} 
-%    (-k_b\xx_{ssss}+(\sigma\xx_s)_s)\cdot\nn\, ds =
-%   \beta\int_{\gamma}\left(k_b\xx_{sss}-\sigma\xx_s\right)\cdot
-%     \nn_s\, ds
-%\end{align}
-%From the Frenet-Serret formulas, we have 
-%\begin{align}
-%     -\beta\int_{\gamma}
-%     \left(k_b\xx_{sss}-\sigma\xx_s\right)\cdot\kappa\xx_s ds &=0.
-%\end{align}
-%
-%Applying integration by parts and Frenet-Serret again
-%\begin{align}
-%     \beta\int_{\gamma}
-%     k_b\kappa\left(\xx_{ss}\cdot\xx_{ss}\right)ds + \beta
-%     \int_{\gamma} k_b \kappa_s(\xx_{ss} \cdot \xx_s)ds +\beta\int_{\gamma}\kappa\sigma ds  &= 0,\\
-%    \beta\int_{\gamma} k_b\kappa(\kappa\nn \cdot
-%     \kappa\nn)+ \beta \int_{\gamma} k_b \kappa_s(\xx_{ss} \cdot
-%     \xx_s)ds +\beta\int_{\gamma}\kappa\sigma ds &= 0,
-%\end{align}
-%which we re-write as
-%\begin{align}
-%   \beta\int_{\gamma}k_b\kappa^3 ds + \beta \int_{\gamma} k_b
-%   \kappa_s(\xx_{ss} \cdot \xx_s)ds +\beta\int_{\gamma} \kappa\sigma ds = 0.
-%\end{align}
-%Applying Frenet-serret again,
-%\begin{align}
-%    \beta\int_{\gamma}k_b\kappa^3 ds + \beta \int_{\gamma} k_b
-%    \kappa_s(\kappa\nn \cdot \TT)ds +\beta\int_{\gamma} \kappa\sigma ds = 0, \\
-%    \beta\int_{\gamma}k_b\kappa^3 ds +\beta\int_{\gamma} \kappa\sigma ds  = 0.
-%\end{align}
-%
-%
-%\section{Including a concentration field}
-%Based on the work of Yao and Mori~\cite{yao-mor2017}, we introduce a
-%chemical concentration field $c$.  The concentration field is governed
-%by the advection-diffusion equation
-%\begin{align}
-%  \pderiv{c}{t} + \nabla \cdot (\uu c) = D\Delta c.
-%\end{align}
-%If the concentration is diffusion dominated (zero Peclet number), then
-%the concentration satisfies
-%\begin{align}
-%  \Delta c = 0, \quad \xx \in \RR^2.
-%\end{align}
-%The boundary conditions of the concentration field on the vesicle
-%$\gamma$ are
-%\begin{align}
-%  (\uu c - D\nabla c) \cdot \nn = c \pderiv{\xx}{t} \cdot \nn + 
-%    j_c + j_p,
-%\end{align}
-%where $j_c$ and $j_p$ are the transmembrane chemical flux due to passive
-%transport and active transport (pumps), respectively.  In the zero
-%Peclet number limit, the absence of an active transport mechanism, and
-%the choice for the passive flux, the boundary condition of the
-%concentration field is
-%\begin{align}
-%  -D\pderiv{c}{\nn} = c \pderiv{\xx}{t} + 
-%    k_c \jump{c}, \quad \xx \in \gamma.
-%\end{align}
-%To couple the vesicle dynamics to the concentration, there is a
-%difference between the fluid velocity and vesicle velocity
-%\begin{align}
-%  \uu - \pderiv{\xx}{t} = j_w \nn,
-%\end{align}
-%where $j_w$ is the water flux through the vesicle.  This is the
-%osmophoretic flow.  In~\cite{yao-mor2017}, this flux is
-%\begin{align}
-%  j_w = -k_w(RT\jump{c} + \ff_\text{mem} \cdot \nn).
-%\end{align}
-%In our current implementation, we drop the $RT\jump{c}$ term, and
-%let $\beta = k_w$.
-%
-%\section{Preliminary results}
-%
-%
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=.9\textwidth]{figures/1.jpg}
-%	\includegraphics[width=.9\textwidth]{figures/2.jpg}
-%	\includegraphics[width=.9\textwidth]{figures/3.jpg}
-%	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0$.}
-%%	\label{Shear0}
-%\end{figure}
-%
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=.9\textwidth]{figures/4.jpg}
-%	\includegraphics[width=.9\textwidth]{figures/5.jpg}
-%	\includegraphics[width=.9\textwidth]{figures/6.jpg}
-%	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0.5$.}
-%%	\label{Shear0}
-%\end{figure}
-%
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=.9\textwidth]{figures/7.jpg}
-%	\includegraphics[width=.9\textwidth]{figures/8.jpg}
-%	\includegraphics[width=.9\textwidth]{figures/9.jpg}
-%	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 1$.}
-%%	\label{Shear0}
-%\end{figure}
-%
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=.9\textwidth]{figures/10.jpg}
-%	\includegraphics[width=.9\textwidth]{figures/11.jpg}
-%	\includegraphics[width=.9\textwidth]{figures/12.jpg}
-%	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 2$.}
-%%	\label{Shear0}
-%\end{figure}
-% 
-% 
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[width=.9\textwidth]{figures/BE1.jpg}
-% 	\includegraphics[width=.9\textwidth]{figures/BE2.jpg}
-% 	\includegraphics[width=.9\textwidth]{figures/BE3.jpg}
-% 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0$.}
-%% 	\label{Shear0}
-% \end{figure}
-% 
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[width=.9\textwidth]{figures/BE4.jpg}
-% 	\includegraphics[width=.9\textwidth]{figures/BE5.jpg}
-% 	\includegraphics[width=.9\textwidth]{figures/BE6.jpg}
-% 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0.5$.}
-%% 	\label{Shear0}
-% \end{figure}
-% 
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[width=.9\textwidth]{figures/BE7.jpg}
-% 	\includegraphics[width=.9\textwidth]{figures/BE8.jpg}
-% 	\includegraphics[width=.9\textwidth]{figures/BE9.jpg}
-% 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 1$.}
-%% 	\label{Shear0}
-% \end{figure}
-% 
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[width=.9\textwidth]{figures/BE10.jpg}
-% 	\includegraphics[width=.9\textwidth]{figures/BE11.jpg}
-% 	\includegraphics[width=.9\textwidth]{figures/BE12.jpg}
-% 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 2$.}
-% 	\label{Shear0}
-% \end{figure}
-%
-%When the semipermeable vesicle reaches a steady-state shape, we have
-%\begin{align}
-%  \int_{\gamma} \left(-\frac{\kappa^3}{2} + \kappa \Lambda \right) \, ds
-%  = 0.
-%\end{align}
-%Based on numerical observations, the steady-state shape is a circular
-%vesicle with constant tension. Since the tension and curvature are
-%constant, we can solve for the curvature in terms of the tension $\kappa
-%= \sqrt{2\Lambda}$. Therefore, the steady state shape is a circle of
-%radius $r = 1/\sqrt{2\Lambda}$, and therefore the length is
-%\begin{align}
-%  L = \frac{\sqrt{2}\pi}{\sqrt{\Lambda}},
-%\end{align}
-%which is constant by the local inextensibility constraint. Finally, we
-%can compute the final tension in terms of the length using the formula
-%\begin{align}
-%  \Lambda = \frac{2\pi^2}{L^2}.
-%\end{align}
-%Therefore, in contrast to a impermeable vesicle, the final tension is
-%positive rather than negative.
-%
-%We start by simulating a star-shaped vesicle in a quiescent flow with
-%semipermeability rate $\beta=1$ (Figure~\ref{fig:starShape}). To
-%perform this simulation, we use an adaptive second-order time stepping
-%method~\cite{qua-bir2016}. The times and reduced areas are in the
-%titles, and note that the shapes are not eqiuspaced in time.
-%\begin{figure}[htp]
-%  \begin{minipage}{0.55\textwidth}
-%%    \ifTikz
-%    \input{figures/starRelaxation1.tikz}
-%    \input{figures/starRelaxation2.tikz}
-%    \input{figures/starRelaxation3.tikz}
-%    \input{figures/starRelaxation4.tikz}
-%    \input{figures/starRelaxation5.tikz}
-%    \input{figures/starRelaxation6.tikz}
-%%    \fi
-%  \end{minipage}
-%  \hfill
-%  \begin{minipage}{0.4\textwidth}
-%%  \ifTikz
-%  \input{figures/starAreaDeriv.tikz}
-%%  \fi
-%  \end{minipage}
-%%  \caption{\label{fig:starShape} A initially star-shaped semipermeable
-%%  vesicle in a shear quiescent flow with $\beta=1$. Note that the time
-%%  steps are not equispaced. The area (red) and its derivative (blue) of
-%%  an initially star-shaped vesicle as a function of time. The dots
-%%  correspond to the time steps shown in six time steps
-%%  show on the left.}
-%\end{figure}
-%
-%\begin{table}[htp]
-%  \centering
-%  \begin{tabular}{|C{1cm}|*{6}{C{2cm}}|}
-%    \hline
-%    $\beta$ & $10^{0}$ & $10^{-1}$ & $10^{-2}$ & 
-%             $10^{-3}$ & $10^{-4}$ & $10^{-5}$ \\
-%    $t_\mathrm{SS}$ & $6.45 \times 10^{0}$ & $2.00 \times 10^{1}$ & 
-%                      $9.61 \times 10^{1}$ & $8.36 \times 10^{2}$ & 
-%                      $8.15 \times 10^{3}$ & $8.03 \times 10^{4}$ \\
-%    ratio & --- & 3.10 & 4.81 & 8.71 & 9.74 & 9.85 \\
-%    \hline
-%  \end{tabular}
-%  \caption{\label{tbl:ellipseRelaxTime} The time, $t_{\mathrm{SS}}$, for
-%  a semipermeable vesicle to reach steady state.}
-%\end{table}
-%
-%\begin{table}[htp]
-%  \centering
-%  \begin{tabular}{|C{1cm}|*{6}{C{2cm}}|}
-%    \hline
-%    $\beta$ & $10^{0}$ & $10^{-1}$ & $10^{-2}$ & 
-%             $10^{-3}$ & $10^{-4}$ & $10^{-5}$ \\
-%    $t_\mathrm{SP}$ & $2.17 \times 10^{-2}$ & $1.25 \times 10^{-1}$ & 
-%                      $1.59 \times 10^{0}$ & $2.19 \times 10^{1}$ & 
-%                      $2.14 \times 10^{2}$ & $2.20 \times 10^{3}$ \\
-%    ratio & --- & 5.76 & 12.72 & 13.77 & 9.77 & 10.14 \\
-%    \hline
-%  \end{tabular}
-%  \caption{\label{tbl:ellipseBLTime} The time, $t_\mathrm{SP}$, for a
-%  semipermeable vesicle to begin inflating.}
-%\end{table}
-%
-%%\begin{figure}[htp]
-%%\begin{minipage}{0.40\textwidth}
-%%\ifTikz
-%%\input{figures/starTension.tikz}
-%%\fi
-%%\end{minipage}
-%%\hfill
-%%\begin{minipage}{0.55\textwidth}
-%%  \centering
-%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime1.pdf}
-%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime2.pdf}
-%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime3.pdf} \\
-%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime4.pdf}
-%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime5.pdf}
-%%\includegraphics[width=0.32\textwidth]{figures/StarTensionTime6.pdf}
-%%\end{minipage}
-%%  \caption{\label{fig:starTension} The tension of the time steps shown
-%%  in Figure~\ref{fig:starShape}. The tension at the time horizon $T=1$
-%%  is also included. At this point, the vesicle is nearly circular and
-%%  the tension is constant and positive. The constant is given by
-%%  equation~\eqref{eqn:SSshape}, and this value corresponds to the
-%%  dashed black line.}
-%%\end{figure}
-%
-%%\begin{figure}[htp]
-%%\begin{minipage}{0.40\textwidth}
-%%%\ifTikz
-%%\input{figures/starFlux.tikz}
-%%%\fi
-%%\end{minipage}
-%%\hfill
-%%\begin{minipage}{0.55\textwidth}
-%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime1.pdf}
-%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime2.pdf}
-%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime3.pdf} \\
-%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime4.pdf}
-%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime5.pdf}
-%%\includegraphics[width=0.32\textwidth]{figures/StarFluxTime6.pdf}
-%%\end{minipage}
-%%  \caption{\label{fig:starFlux} The flux of the time steps shown in
-%%  Figure~\ref{fig:starShape}. The tension at the time horizon $T=1$ is
-%%  also included. At this point, the vesicle is nearly circular and there
-%%  is no flux.}
-%%\end{figure}
-%\begin{figure}[htp]
-%    \ifTikz
-%    \input{figures/starRelaxation1.tikz}
-%    \quad
-%    \input{figures/starRelaxation2.tikz}
-%    \quad
-%    \input{figures/starRelaxation3.tikz}
-%    \quad
-%    \input{figures/starRelaxation4.tikz}
-%    \quad
-%    \input{figures/starRelaxation5.tikz}
-%    \fi
-%  \caption{\label{fig:starShape} An initially star-shaped semipermeable
-%  vesicle in a quiescent flow with $\beta=1$. Note that the time steps
-%  are not equispaced.}
-%\end{figure}
-%\begin{figure}[htp]
-%  \centering
-%%  \ifTikz
-%  \input{figures/ellipseVelocity1.tikz}
-%  \input{figures/ellipseVelocity2.tikz}
-%  \input{figures/ellipseVelocity3.tikz}
-%%  \fi
-%  \caption{\label{fig:vesVelocity} The velocity contributions due to
-%  semipermeability (red) and force balance (blue). The green dashed
-%  line is the velocity of an impermeable vesicle with the same initial
-%  shape as the semipermeable vesicle.}
-%\end{figure}
-%
-%\begin{figure}[htp]
-%%  \ifTikz
-%  \input{figures/ellipseVelocityNorms.tikz}
-%%  \fi
-%  \caption{\label{fig:vesVelocityNorm} The max norm of the velocity due
-%  to the force balance (blue) and semipermeability. Also included is
-%  the velocity of an impermeable vesicle (green). The three black lines
-%  correspond to the times reported in Figure~\ref{fig:vesVelocity}.}
-%\end{figure}
-
-% \newpage
-%\input{figures/shearPhaseDiagramRA2.tikz}
-%\input{figures/parabolicPhaseDiagram.tikz}
-%\begin{figure}[htp]
-%%  \ifTikz
-%%  \input{figures/parabolicPhaseDiagram.tikz}
-%%  \fi
-%  \includegraphics[width=0.9\linewidth]{figures/parabolicPhaseDiagram.pdf}
-%  \caption{\label{fig:parabolicPhaseDiagram} The steady state shape of a
-%  semipermeable vesicle with several different permeability rates
-%  $\beta$ and flow rates $U$. The numbers reported above each vesicle is
-%  its reduced area. At high flow rates, the vesicle self-intersects
-%  before reaching a steady state configuration.}
-%\end{figure}
-%
-%
-%\begin{table}[htp]
-%  \centering
-%  \caption{\label{tbl:parabolicRelaxTimes1} The time for a
-%  semipermeable vesicle in a Poiseuille flow to reach its steady state
-%  ($t_\mathrm{steady}$) and to begin inflating ($t_\mathrm{inflate}$).
-%  The times are reported for the maximum velocities $0.1 \mu m/s$ and
-%  $10 \mu m/s$.}
-%  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
-%    \multicolumn{5}{c}{$U = 0.1 \mu m/s$} \\
-%    $\beta$ & $t_\mathrm{steady}$ & ratio & $t_\mathrm{inflate}$ & ratio \\
-%    \midrule
-%    $10^{0}$  & $3.33 \times 10^{0}$ & ---  
-%              & $1.67 \times 10^{-2}$ & --- \\ 
-%    $10^{-1}$ & $1.37 \times 10^{1}$ & 4.12 & 
-%                $8.73 \times 10^{-1}$ & 5.23 \\
-%    $10^{-2}$ & $8.60 \times 10^{1}$ & 6.26 & 
-%                $1.11 \times 10^{0}$ & 12.74 \\
-%    $10^{-3}$ & $7.75 \times 10^{2}$ & 9.01 & 
-%                $1.63 \times 10^{1}$ & 14.70 \\
-%    $10^{-4}$ & $7.69 \times 10^{3}$ & 9.93 & 
-%                $1.74 \times 10^{2}$ & 10.63 \\
-%    $10^{-5}$ & $8.01 \times 10^{4}$ & 10.41 & 
-%                $1.66 \times 10^{3}$ & 9.58 \\
-%    \bottomrule
-%  \end{tabular}
-%
-%  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
-%    \multicolumn{5}{c}{$U = 10 \mu m/s$} \\
-%    $\beta$ & $t_\mathrm{steady}$ & ratio & $t_\mathrm{inflate}$ & ratio \\
-%    \midrule
-%    $10^{0}$  & $3.55 \times 10^{0}$ & ---  
-%              & $1.67 \times 10^{-2}$ & --- \\ 
-%    $10^{-1}$ & $1.87 \times 10^{1}$ & 5.27 & 
-%                $9.01 \times 10^{-2}$ & 5.40 \\
-%    $10^{-2}$ & $1.17 \times 10^{2}$ & 6.26 & 
-%                $1.52 \times 10^{0}$ & 16.87 \\
-%    $10^{-3}$ & $1.06 \times 10^{3}$ & 9.06 & 
-%                $2.07 \times 10^{1}$ & 13.62 \\
-%    $10^{-4}$ & $1.02 \times 10^{4}$ & 9.62 & 
-%                $2.25 \times 10^{2}$ & 10.87 \\
-%    $10^{-5}$ & $1.04 \times 10^{5}$ & 10.20 & 
-%                $2.25 \times 10^{3}$ & 10.00 \\
-%    \bottomrule
-%  \end{tabular}
-%\end{table}
-%The width $W$ is chosen so that $W/R =
-%10$, where $R$ is the radius of the vesicle. We investigate the effect
-%of the maximum velocity $U$ and the permeability rate $\beta$ on the
-%steady state shape of a vesicle initially placed on the center line
-%$y=0$. Figure~\ref{fig:parabolicPhaseDiagram} shows the steady state
-%configuration for a variety of maximum velocities and permeability
-%rates. Similar to the shear example, the maximum velocity strongly
-%affects the final shape while the permeability rate's effect is much
-%weaker. Instead, the permeability rate determines the time required for
-%the vesicle to reach a steady state. In
-%Table~\ref{tbl:parabolicRelaxTimes1}, we consider two maximum velocities
-%and report the time, $t_\mathrm{steady}$, required for the vesicle's
-%area to be within 1.3\% of its maximum area, and the time,
-%$t_\mathrm{inflate}$, required for the vesicle's area to exceed 1.3\% of
-%its initial area. We see that both times scale with $\beta^{-1}$.
-
-%\begin{figure}[htp]
-%  \centering
-%  \begin{tabular}{ccc}
-%    \ifTikz
-%    \scalebox{0.31}{\input{figures/stenosisTension1.tikz}} &
-%    \scalebox{0.31}{\input{figures/stenosisTension3.tikz}} &
-%    \scalebox{0.31}{\input{figures/stenosisTension5.tikz}} \\
-%    \scalebox{0.31}{\input{figures/stenosisTension7.tikz}} &
-%    \scalebox{0.31}{\input{figures/stenosisTension9.tikz}} &
-%    \scalebox{0.31}{\input{figures/stenosisTension11.tikz}} 
-%    \fi
-%  \end{tabular}
-%  \caption{\label{fig:stenosisTension} The tension of the impermeable
-%  (red) and semipermeable (dashed blue) vesicles in
-%  Figure~\ref{fig:stenosisShape}. The point $\theta=0$ corresponds to
-%  the right-most point of the vesicle.}
-%\end{figure}
-%
-%\begin{figure}[htp]
-%  \centering
-%  \begin{tabular}{ccc}
-%    \iftikz
-%    \scalebox{0.31}{\input{figures/stenosisflux1.tikz}} &
-%    \scalebox{0.31}{\input{figures/stenosisflux3.tikz}} &
-%    \scalebox{0.31}{\input{figures/stenosisflux5.tikz}} \\
-%    \scalebox{0.31}{\input{figures/stenosisflux7.tikz}} &
-%    \scalebox{0.31}{\input{figures/stenosisflux9.tikz}} &
-%    \scalebox{0.31}{\input{figures/stenosisflux11.tikz}} 
-%    \fi
-%  \end{tabular}
-%  \caption{\label{fig:stenosisFlux} The flux (equivalent to pressure
-%  jump) of the impermeable (red) and semipermeable (dashed blue)
-%  vesicles in Figure~\ref{fig:stenosisShape}. The point $\theta=0$
-%  corresponds to the right-most point of the vesicle.}
-%\end{figure}
-%This is verified for a
-%vesicle with initial reduced area $\nu = 0.65$ and with different
-%semipermeability rates. In Table~\ref{tbl:ellipseRelaxTimes} we report
-%the required time, $t_\mathrm{steady}$, for the vesicle's reduced area
-%to be within 1.3\% of its steady state reduced area, and the required
-%time, $t_\mathrm{inflate}$, for the vesicle's reduced area to exceed
-%1.3\% of its initial reduced area. Both times are proportional to
-%$\beta^{-1}$, and for this reason, our numerical results are reported in
-%terms of the scaled time $\beta t$.
-%\begin{table}[htp]
-%  \centering
-%  \caption{\label{tbl:ellipseRelaxTimes} The time for a semipermeable
-%  vesicle to its steady state ($t_\mathrm{steady}$) and to begin
-%  inflating ($t_\mathrm{inflate}$).}
-%  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
-%    $\beta$ & $t_\mathrm{steady}$  & ratio 
-%            & $t_\mathrm{inflate}$ & ratio \\
-%    \midrule
-%    $10^{0}$  & $6.45 \times 10^{0}$ & ---  
-%              & $2.17 \times 10^{-2}$ & --- \\ 
-%    $10^{-1}$ & $2.00 \times 10^{1}$ & 3.10 & 
-%                $1.25 \times 10^{-1}$ & 5.76 \\
-%    $10^{-2}$ & $9.61 \times 10^{1}$ & 4.81 & 
-%                $1.59 \times 10^{0}$ & 12.72 \\
-%    $10^{-3}$ & $8.36 \times 10^{2}$ & 8.71 & 
-%                $2.19 \times 10^{1}$ & 13.77 \\
-%    $10^{-4}$ & $8.15 \times 10^{3}$ & 9.74 & 
-%                $2.14 \times 10^{2}$ & 9.77 \\
-%    $10^{-5}$ & $8.03 \times 10^{4}$ & 9.85 & 
-%                $2.20 \times 10^{3}$ & 10.14 \\
-%    \bottomrule
-%  \end{tabular}
-%\end{table}

### 2021-02-05 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
yny

@@
 
-Specifically we focus on the mechanical component of the water flux
+In this work we focus on the mechanical component of the water flux
 in~\eqref{eq:water_flux} with $\triangle c =0$. In our
@@
 
-We consider a two-dimensional inextensible semipermeable vesicle
-membrane $\gamma$ suspended in a viscous Newtonian fluid in domain
-$\Omega$.  The vesicle membrane $\gamma$ is parameterized as $\xx(s,t)$
+In our formulation, an inextensible semipermeable vesicle is suspended in a viscous Newtonian fluid 
+(in domain $\Omega$).  The vesicle membrane $\gamma$ is parameterized as $\xx(s,t)$
 where $s$ is arclength and $t$ is time. In the suspending fluid the flow
@@
 
-The governing equations are non-dimensionalized by using a
+We non-dimensionalize the governing equations by a
 characteristic length scale $R_0 = 10^{-6}$ m, a bending stiffness $k_b
@@
   \label{eqn:vesicleFlux}
-  \uu - \dot{\xx} = - k_w (\ff_\mathrm{mem} \cdot \nn) \nn, \qquad
+  \uu - \dot{\xx} = - \beta (\ff_\mathrm{mem} \cdot \nn) \nn, \qquad
   \xx \in \gamma,
 \end{align}
-where $k_w$ is the hydraulic conductivity.
+where $\beta = k_w/(R_0/\mu)$ is the dimensionless membrane permeability for water.
 
@@
 axisymmetric bullet, an axisymmetric parachute, or a tank-treading
-asymmetric slipper~\cite{kao-bir-mis2009}. Comparing our results
-(Figure~\ref{fig:PoiseuillePhase}) with those in~\cite{kao-bir-mis2009}
-(see Figure 2), we observe qualitative agreement in the equilibrium
+asymmetric slipper~\cite{kao-bir-mis2009}. Comparing against the simulation results of an impermeable vesicle in Poiseuille flow
+(specifically Figure 2 in~\citet{kao-bir-mis2009}),
+%
+%(Figure~\ref{fig:PoiseuillePhase}) with those in~\cite{kao-bir-mis2009}
+%(see Figure 2), 
+%
+we observe general agreement in the equilibrium
 vesicle shapes except that,

### 2021-02-05 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
working on prf rewrite

@@
 
+\begin{figure*}[htp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/relaxationTensions2.pdf}
+%  \ifTikz
+%    \input{figures/relaxationTensions.tikz}
+%  \else
+%    \includegraphics{figures/relaxationTensions.pdf}
+%  \fi
+  \caption{\label{fig:relaxationTensions} The tension distribution of
+  vesicles in relaxation that corresponds to
+  Figure~\ref{fig:relaxationComposite}.}
+\end{figure*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     };
-    \node at (-8.54,0.6) {(a)};
-    \node at (-6.00,0.6) {(b)};
-    \node at (-3.46,0.6) {(c)};
-    \node at (-0.92,0.6) {(d)};
-    \node at (+1.60,0.6) {(e)};
-    \node at (+4.16,0.6) {(f)};
-    \node at (+6.70,0.6) {(g)};
+%    \node at (-8.54,0.6) {(a)};
+%    \node at (-6.00,0.6) {(b)};
+%    \node at (-3.46,0.6) {(c)};
+%    \node at (-0.92,0.6) {(d)};
+%    \node at (+1.60,0.6) {(e)};
+%    \node at (+4.16,0.6) {(f)};
+%    \node at (+6.70,0.6) {(g)};
   \end{tikzpicture}
@@
   \centering
-  \ifTikz
+%  \ifTikz
   \input{figures/stenosisComposite.tikz}
-  \else
-  \includegraphics{figures/stenosisComposite.pdf}
-  \fi
+%  \else
+%  \includegraphics{figures/stenosisComposite.pdf}
+%  \fi
   \caption{\label{fig:stenosisComposite} (a) A semipermeable vesicle
@@
 This corresponds well to the corresponding tension distribution in Figure~\ref{fig:stenosisTensions}: Larger tension in the front, and smaller tension in the rear.
-\begin{figure*}[htp]
-  \centering
-  \begin{tikzpicture}[scale=1]
-    \node[inner sep=0pt] at (0,0) {
-    \includegraphics[width=\textwidth]{figures/stenosisTensions.pdf}
-    };
-    \node at (-8.6,0.7) {(a)};
-    \node at (-1.6,0.7) {(b)};
-  \end{tikzpicture}
-  \caption{\label{fig:stenosisTensions} The tension distribution along a
-  semipermeable vesicle with $\beta = 10^{-3}$ going through a
-  closely-fit channel of two different lengths.}
-\end{figure*}
+%\begin{figure*}[htp]
+%  \centering
+%  \begin{tikzpicture}[scale=1]
+%    \node[inner sep=0pt] at (0,0) {
+%    \includegraphics[width=\textwidth]{figures/stenosisTensions.pdf}
+%    };
+%    \node at (-8.6,0.7) {(a)};
+%    \node at (-1.6,0.7) {(b)};
+%  \end{tikzpicture}
+%  \caption{\label{fig:stenosisTensions} The tension distribution along a
+%  semipermeable vesicle with $\beta = 10^{-3}$ going through a
+%  closely-fit channel of two different lengths.}
+%\end{figure*}
 
@@
   \else
+  \begin{minipage}{0.45\textwidth}
+    \centering
   \includegraphics{figures/contractingComposite.pdf}
+  \end{minipage}
+  \hfill
+  \begin{minipage}{0.45\textwidth}
+    \centering
+  \includegraphics[width=\textwidth]{figures/contractingTensions1.pdf}
+  \includegraphics[width=\textwidth]{figures/contractingTensions2.pdf}
+    \todo[inline]{Maximum tension as a function of center of mass down
+    here}
+  \end{minipage}
   \fi
@@
   \centering
-  \ifTikz
+%  \ifTikz
   \input{figures/contractingComposite2.tikz}
-  \else
-  \includegraphics{figures/contractingComposite2.pdf}
-  \fi
+%  \else
+%  \includegraphics{figures/contractingComposite2.pdf}
+%  \fi
   \caption{\label{fig:contractingComposite2} Vesicle reduced area and
@@
 tension has the largest magnitude when the vesicle is at the neck. 
-\begin{figure}[htp]
-  \centering
-  \begin{tikzpicture}[scale=1]
-    \node[inner sep=0pt] at (0,0) {
-    \includegraphics[width=0.5\textwidth]{figures/contractingTensions1.pdf}
-    };
-    \node[inner sep=0pt] at (0,-2.3) {
-    \includegraphics[width=0.5\textwidth]{figures/contractingTensions2.pdf}
-    };
-    \node[inner sep=0pt] at (0,-4.8) {
-    \includegraphics[width=0.5\textwidth]{figures/contractingTensions3.pdf}
-    };
-    \node at (-4.2,0.9) {(a)};
-    \node at (-4.2,-1.4) {(b)};
-    \node at (+0.8,0.9) {(c)};
-    \node at (+0.8,-1.4) {(d)};
-    \node at (-4.2,-3.7) {(e)};
-  \end{tikzpicture}
-  \caption{\label{fig:contractingTensions1} The tension distribution
-  along a semipermeable vesicle going through a contracting geometry.
-  The vesicle tension increases by up to five orders of magnitude when
-  as it enters the neck. The permeability constant and flow rates are
-  (a) $U_{\max} = 5.7\;\mu$m/s, $\beta = 5 \times 10^{-4}$; (b)
-  $U_{\max} = 5.7\;\mu$m/s, $\beta = 5 \times 10^{-3}$; (c) $U_{\max} =
-  0.57\;\mu$m/s, $\beta = 1 \times 10^{-3}$; (d) $U_{\max} =
-  5.7\;\mu$m/s, $\beta = 1 \times 10^{-3}$; (e) $U_{\max} = 18\;\mu$m/s,
-  $\beta = 1 \times 10^{-3}$.}
-\end{figure}
+%\begin{figure}[htp]
+%  \centering
+%  \begin{tikzpicture}[scale=1]
+%%    \node[inner sep=0pt] at (0,0) {
+%%    \includegraphics[width=0.5\textwidth]{figures/contractingTensions1.pdf}
+%%    };
+%%    \node[inner sep=0pt] at (0,-2.3) {
+%%    \includegraphics[width=0.5\textwidth]{figures/contractingTensions2.pdf}
+%%    };
+%    \node[inner sep=0pt] at (0,-4.8) {
+%    \includegraphics[width=0.5\textwidth]{figures/contractingTensions3.pdf}
+%    };
+%    \node at (-4.2,0.9) {(a)};
+%    \node at (-4.2,-1.4) {(b)};
+%    \node at (+0.8,0.9) {(c)};
+%    \node at (+0.8,-1.4) {(d)};
+%    \node at (-4.2,-3.7) {(e)};
+%  \end{tikzpicture}
+%  \caption{\label{fig:contractingTensions1} The tension distribution
+%  along a semipermeable vesicle going through a contracting geometry.
+%  The vesicle tension increases by up to five orders of magnitude when
+%  as it enters the neck. The permeability constant and flow rates are
+%  (a) $U_{\max} = 5.7\;\mu$m/s, $\beta = 5 \times 10^{-4}$; (b)
+%  $U_{\max} = 5.7\;\mu$m/s, $\beta = 5 \times 10^{-3}$; (c) $U_{\max} =
+%  0.57\;\mu$m/s, $\beta = 1 \times 10^{-3}$; (d) $U_{\max} =
+%  5.7\;\mu$m/s, $\beta = 1 \times 10^{-3}$; (e) $U_{\max} = 18\;\mu$m/s,
+%  $\beta = 1 \times 10^{-3}$.}
+%\end{figure}
 

### 2021-02-06 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
yny

--- 2021-02-05 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
@@
 can give rise to significantly distinct hydrodynamics of a semipermeable
-vesicle without poration or rupture in the lipid bilayer membrane.
+vesicle.
 

### 2021-02-06 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
yny

@@
 membrane porates when the membrane tension reaches the order of $2$--$4$
-mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references therein),
+mN/m (see \citet{RazizadehNikfarPaulLiu2020_BJ} and references therein),
 giving rise to enhanced membrane permeability to both water and
@@
 vesicle behaves differently from an impermeable vesicle over a long
-time. Next we show that
+time in \S~\ref{sec:free_space}. Next in \S~\ref{sec:confinement} we show that
 %, at normal physiological conditions,
-the permeating water flow can be amplified by extreme confinement to give rise to observable change in both hydrodynamics and water content. 
+the permeating water flow can be amplified by extreme confinement to give rise to observable change in both  vesicle hydrodynamics and vesicle's water content. 
 These results provide insight into quantifying the effects of membrane permeability on vesicle hydrodynamics in microfluidics.
@@
 water) suspended in a viscous fluid (Figure~\ref{fig:sketch}), and we
-let $\gamma$ denote the membrane boundary. We let
-$\alpha=4\pi A/L^2$ be the vesicle's reduced area where $A$ is its area
-and $L$ is its length. To focus on the effect of water flow on vesicle
+let $\gamma$ denote the membrane boundary, of length $L$ and enclosing an area $A$.
+%
+%$\alpha=4\pi A/L^2$ be the vesicle's reduced area where $A$ is its area
+%and $L$ is its length. 
+%
+To focus on the effect of water flow on vesicle
 hydrodynamics in various conditions, we assume the fluid is the same
@@
 \begin{align}
-\label{eq:water_flux}
+\label{eqn:water_flux}
   \uu - \dot{\xx} = - k_w (R T \triangle c + \ff_\mathrm{mem} \cdot \nn) \nn, \qquad
@@
 when the membrane tension becomes large due to the external stress such
-as the hydrodynamic stress from an external flow or confinement. In the
-following we explore both.
-
-In this work we focus on the mechanical component of the water flux
-in~\eqref{eq:water_flux} with $\triangle c =0$. In our
-non-dimensionalization the hydraulic conductivity is scaled to $R_0/\mu$
-(where $R_0$ is a characteristic length and $\mu$ is the solvent
-viscosity): $\beta = k_w/(R_0/\mu)$,
-$\beta=0$ for an impermeable vesicle, and $\beta>0$ for a semipermeable
-vesicle. Under strong confinement, a large value of $\beta$ is needed in
-our simulations to keep the membrane tension below the threshold value
-for membrane poration $\sim 10^{-3}$ N/m. Such large value of $\beta$
-may pertain to red blood cell membranes with aquaporin proteins.
-
-In our formulation, an inextensible semipermeable vesicle is suspended in a viscous Newtonian fluid 
+as the hydrodynamic stress from an external flow or confinement. 
+In this work we set $\triangle c =0$ in Equation~\eqref{eqn:water_flux}  to
+focus on the water flux driven by the pressure difference due to an external flow or confinement.
+
+%In our non-dimensionalization the hydraulic conductivity is scaled to $R_0/\mu$
+%(where $R_0$ is a characteristic length and $\mu$ is the solvent
+%viscosity): $\beta = k_w/(R_0/\mu)$,
+%$\beta=0$ for an impermeable vesicle, and $\beta>0$ for a semipermeable
+%vesicle. Under strong confinement, a large value of $\beta$ is needed in
+%our simulations to keep the membrane tension below the threshold value
+%for membrane poration $\sim 10^{-3}$ N/m. Such large value of $\beta$
+%may pertain to red blood cell membranes with aquaporin proteins.
+
+In our formulation, a semipermeable vesicle is suspended in a viscous Newtonian fluid 
 (in domain $\Omega$).  The vesicle membrane $\gamma$ is parameterized as $\xx(s,t)$
@@
 \rightarrow \infty$ is enforced. 
-
-We non-dimensionalize the governing equations by a
+%
+Along the vesicle membrane $\gamma$,
+mass continuity, force balance, and local inextensibility are enforced
+by requiring
+\begin{align}
+  \label{eqn:jump}
+  \jump{\uu} = 0, \quad
+  \jump{T\cdot\nn} = \ff_\mathrm{mem}, \quad
+  \xx_s \cdot \uu_s = 0,
+\end{align}
+where $\nn$ is the outward normal of $\gamma$, $\jump{\cdot}$ is the
+jump across the interface, and $T$ is the hydrodynamic stress tensor.
+The membrane force $\ff_\mathrm{mem}$ is the sum of a bending force
+with bending modulus $k_b$ and a force due to the tension $\Lambda$.
+Following~\cite{vee-gue-zor-bir2009}, we introduce the variable $\sigma
+= \Lambda - \frac{3}{2}\kappa^2$, where $\kappa$ is the vesicle curvature. Then,
+the bending and tension forces corresponding to the Helfrich energy are
+$\ff_\mathrm{ben} = -k_b \xx_{ssss}$ and $\ff_\mathrm{ten} = (\sigma
+\xx_s)_s$.
+
+We non-dimensionalize the governing equations (Equations~(\ref{eqn:water_flux}-\ref{eqn:jump})) by a
 characteristic length scale $R_0 = 10^{-6}$ m, a bending stiffness $k_b
@@
 length and $A$ is its area, and (b) its permeability $\beta = k_w \mu
-/R_0$. In two dimensions, the membrane length is conserved by the local
-inextensibility condition, but the enclosed area is not conserved
-because of semipermeability. Therefore, the reduced area is dynamic. We
-convert the apparent permeability of a polyunsaturated PC
-bilayer~\cite{OlbrichRawiczNeedhamEtAl2000_BJ} to the hydraulic
-conductivity $k_w$ using the conversion
-in~\cite{FettiplaceHaydon1980_PhysRev}, and found that $10^{-14}\le
-k_w\le 10^{-12}$ m$^2$s/kg, thus $\beta$ is in the range $10^{-11}\le
-\beta\le 10^{-9}$.
-
-In the confined examples, we enforce a
-no-slip boundary condition along the top and bottom of the channel and a
-Hagen–Poiseuille flow at the inlet and outlet---this boundary condition
-has been used in similar vesicle setups~\cite{qua-bir2014,
-rah-vee-bir2010, lu-rah-zor2017}. Along the vesicle membrane $\gamma$,
-mass continuity, force balance, and local inextensibility are enforced
-by requiring
-\begin{align}
-  \label{eqn:jump}
-  \jump{\uu} = 0, \quad
-  \jump{T\cdot\nn} = \ff_\mathrm{mem}, \quad
-  \xx_s \cdot \uu_s = 0,
-\end{align}
-where $\nn$ is the outward normal of $\gamma$, $\jump{\cdot}$ is the
-jump across the interface, and $T$ is the hydrodynamic stress tensor.
-The membrane force $\ff_\mathrm{mem}$ is the sum of a bending force
-with bending modulus $k_b$ and a force due to the tension $\Lambda$.
-Following~\cite{vee-gue-zor-bir2009}, we introduce the variable $\sigma
-= \Lambda - \frac{3}{2}\kappa^2$, where $\kappa$ is the vesicle curvature. Then,
-the bending and tension forces corresponding to the Helfrich energy are
-$\ff_\mathrm{ben} = -k_b \xx_{ssss}$ and $\ff_\mathrm{ten} = (\sigma
-\xx_s)_s$.
-
-Semipermeability is introduced by modifying the vesicle velocity from
-the standard no-slip condition $\dot{\xx} = \uu(\xx)$. Instead,
-the permeating water flux through the lipid bilayer membrane is proportional to the
-membrane traction~\cite{yao-mor2017}. That is, 
-\begin{align}
-  \label{eqn:vesicleFlux}
-  \uu - \dot{\xx} = - \beta (\ff_\mathrm{mem} \cdot \nn) \nn, \qquad
-  \xx \in \gamma,
-\end{align}
-where $\beta = k_w/(R_0/\mu)$ is the dimensionless membrane permeability for water.
+/R_0$. 
+In two dimensions, the conservation of total lipids in the membrane corresponds to the inextensibility (fixed length $L$) of $\gamma$.
+Due to semipermeability to water ($\beta>0$),  the enclosed area $A$ is not conserved and the reduced area $\alpha$ is dynamic.
 
@@
 \end{align}
-with $\rr = \xx - \yy$ and $\rho = |\rr|$. Imposing the flux
-condition~\eqref{eqn:vesicleFlux} and the inextensibility condition, the
-vesicle velocity satisfies the boundary integral equation
+with $\rr = \xx - \yy$ and $\rho = |\rr|$. 
+Together with the inextensibility constraint and the dimensionless boundary condition
+\begin{align}
+  \label{eqn:vesicleFlux}
+  \uu - \dot{\xx} = - \beta (\ff_\mathrm{mem} \cdot \nn) \nn, \qquad
+  \xx \in \gamma,
+\end{align}
+%
+%Semipermeability is introduced by modifying the vesicle velocity from
+%the standard no-slip condition $\dot{\xx} = \uu(\xx)$. Instead,
+%the permeating water flux through the lipid bilayer membrane is proportional to the
+%membrane traction~\cite{yao-mor2017}. That is, 
+%\begin{align}
+%  \label{eqn:vesicleFlux}
+%  \uu - \dot{\xx} = - \beta (\ff_\mathrm{mem} \cdot \nn) \nn, \qquad
+%  \xx \in \gamma,
+%\end{align}
+%where $\beta = k_w/(R_0/\mu)$ is the dimensionless membrane permeability for water.
+%
+%Imposing the flux
+%condition~\eqref{eqn:vesicleFlux} and the inextensibility condition, 
+the vesicle membrane velocity satisfies the boundary integral equation
 \begin{align}
@@
 $\partial\Omega$. The density function is used to satisfy the boundary
-condition on $\partial\Omega$.
+condition on $\partial\Omega$. Specifically, in the two examples of a semipermeable vesicle under strong confinement, we enforce a
+no-slip boundary condition along the top and bottom of the channel and a
+Hagen–Poiseuille flow at the inlet and outlet---this boundary condition
+has been used in similar vesicle setups~\cite{qua-bir2014,
+rah-vee-bir2010, lu-rah-zor2017}.
+
+The value of $\beta$ can be estimated by first
+converting the apparent permeability of a 
+bilayer~\cite{OlbrichRawiczNeedhamEtAl2000_BJ} to the hydraulic
+conductivity $k_w$ using the conversion
+in~\cite{FettiplaceHaydon1980_PhysRev}, and then scaling $k_w$ to $R_0/\mu$. We found that for most lipid bilayer membranes, $10^{-14}\le
+k_w\le 10^{-12}$ m$^2$s/kg, thus the range of $\beta$ corresponding to the native membrane permeability for water is $10^{-11}\le
+\beta\le 10^{-9}$. 
+%
+Under strong confinement, a large value of $\beta$ is needed in
+our simulations to keep the membrane tension below the threshold value
+for membrane poration $\sim 10^{-3}$ N/m. Such large value of $\beta$
+may pertain to red blood cell membranes with aquaporin proteins.
 
@@
 
-\section{Hydrodynamics of a semipermeable vesicle in free space}
+\section{Hydrodynamics of a semipermeable vesicle in free space\label{sec:free_space}}
 To highlight the effects of membrane permeability to water, we consider
@@
 
-\section{A semipermeable vesicle under strong confinement}
+\section{A semipermeable vesicle under strong confinement\label{sec:confinement}}
 Here we consider a semipermeable vesicle under strong confinement: a
@@
 \acknowledgments
-We thank Howard Stone, Michael J.~Shelley, Petia Vlahovska,
+We thank Howard A.~Stone, Michael J.~Shelley, Petia M.~Vlahovska,
 Chaoqui Misbah, Manouk Abkarian, Sangwoo Shin, and Shravan

### 2021-02-06 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
yny

@@
 \frac{1}{2}\kappa^3 - \Lambda \kappa = 0$, with initial conditions
-$\kappa(0) = \kappa_0$ and $\kappa_s(0) = 0$.  Integrating once, we have
+$\kappa(0) = \kappa_0$ and $\kappa_s(0) = 0$.  Multpiying $\kappa_s$ and integrating once, we have
 \begin{align}
@@
 
-We next compute the transient area of the vesicle. Since the area of the
+We next compute the area dynamics of a semipermeable vesicle. Since the area of the
 vesicle is
@@
 \section{Numerical Methods}
-By using a boundary integral equation formulation, the unknowns are the
-vesicle's position and tension and the unknown density function for
-confined flows. Both $\gamma$ and $\partial\Omega$ are discretized at a
+In the  boundary integral equation formulation, the unknowns are the
+vesicle's position and tension without confinement.
+With confinement, an extra unknown (the density function) is added to enforce the no-slip boundary conditions on the confinement wall.
+Both $\gamma$ and $\partial\Omega$ are discretized at a
 set of collocation points. Derivatives are computed with Fourier

### 2021-02-07 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
small changes

--- 2021-02-06 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
@@
 
+%\usepgfplotslibrary{external}
+%\tikzexternalize
+
 \begin{document}
@@
 \author{Bryan Quaife$^{1}$, Ashley Gannon$^{1}$ and Y.-N. Young$^{2*}$}
-\affiliation{$^1$Department of Scientific Computing, Florida State University, Tallahessee, Florida, 32306, USA\\
+\affiliation{$^1$Department of Scientific Computing, Florida State
+University, Tallahassee, Florida, 32306, USA\\
 $^2$Department of Mathematical Sciences, New Jersey Institute of Technology, Newark, New Jersey, 07102, USA\\}
@@
 can give rise to significantly distinct hydrodynamics of a semipermeable
-vesicle.
+vesicle without poration or rupture in the lipid bilayer membrane.
 
@@
 where we have used the incompressibility of the single-layer potential.
-Repeatedly applying integration by parts, we obtain
+Substituting in $\ff = \ff_\mathrm{ben} + \ff_\mathrm{ten}$ and
+repeatedly applying integration by parts, we obtain
 \begin{align}
@@
   \frac{\xx^{N+1} - \xx^N}{\triangle t} &= \uu_\infty(\xx^N) 
-  &&+ \beta P^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right) \nonumber \\
-  & &&+ \SS^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right),  \\
+  + \beta P^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right) 
+  + \SS^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right),  \\
+%  \frac{\xx^{N+1} - \xx^N}{\triangle t} &= \uu_\infty(\xx^N) 
+%  &&+ \beta P^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right) \nonumber \\
+%  & &&+ \SS^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right),  \\
   D^N\xx^{N+1} &= 1,
@@
   \caption{\label{fig:parabolicTensions} The equilibrium tension
-  distribution of a semipermeable vesicle with $\beta=10^{-3}$ in a parabolic
-  flow (Figure~\ref{fig:parabolicComposite}). The flow velocities
-  are (a) 200 $\mu$m/s, (b) 400 $\mu$m/s, (c) 600 $\mu$m/s, and (d)
-  800 $\mu$m/s.}
+  distribution of a semipermeable vesicle with $\beta=10^{-3}$ in a
+  parabolic flow (Figure~\ref{fig:parabolicComposite}). The flow
+  velocities are (a) 200 $\mu$m/s, (b) 400 $\mu$m/s, (c) 600 $\mu$m/s,
+  and (d) 800 $\mu$m/s.}
 \end{figure*}
@@
   \centering
-%  \ifTikz
+  \ifTikz
   \input{figures/stenosisComposite.tikz}
-%  \else
-%  \includegraphics{figures/stenosisComposite.pdf}
-%  \fi
+  \else
+  \includegraphics{figures/stenosisComposite.pdf}
+  \fi
   \caption{\label{fig:stenosisComposite} (a) A semipermeable vesicle
@@
   \centering
-  \ifTikz
-  \input{figures/contractingComposite.tikz}
-  \else
   \begin{minipage}{0.45\textwidth}
     \centering
-  \includegraphics{figures/contractingComposite.pdf}
+%  \ifTikz
+  \input{figures/contractingComposite.tikz}
+%  \else
+%  \includegraphics{figures/contractingComposite.pdf}
+%  \fi
   \end{minipage}
@@
     \includegraphics[width=\textwidth]{figures/contractingTensions2.pdf}
-    \todo[inline]{Maximum tension as a function of center of mass down
-    here}
+    \input{figures/contractingMaxTension_vs_COM.tikz}
+%    \todo[inline]{Maximum tension as a function of center of mass down
+%    here}
   \end{minipage}
-  \fi
   \caption{\label{fig:contractingComposite} A contracting channel
@@
   \centering
-%  \ifTikz
+  \ifTikz
   \input{figures/contractingComposite2.tikz}
-%  \else
-%  \includegraphics{figures/contractingComposite2.pdf}
-%  \fi
+  \else
+  \includegraphics{figures/contractingComposite2.pdf}
+  \fi
   \caption{\label{fig:contractingComposite2} Vesicle reduced area and

### 2021-02-08 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
worked on contracting figs
yny

@@
 pressure can be represented as layer potentials. Given the interfacial
-boundary conditions~\eqref{eqn:jump}, the fluid velocity is
+boundary conditions in Equation~\eqref{eqn:jump}, the fluid velocity is
 \begin{align}
@@
 \frac{1}{2}\kappa^3 - \Lambda \kappa = 0$, with initial conditions
-$\kappa(0) = \kappa_0$ and $\kappa_s(0) = 0$.  Multpiying $\kappa_s$ and integrating once, we have
+$\kappa(0) = \kappa_0$ and $\kappa_s(0) = 0$.  Multiplying $\kappa_s$ and integrating once, we have
 \begin{align}
@@
 \end{align}
-Assuming $\kappa_s \neq 0$,~\eqref{eqn:curveODE} is separable, and can
+Assuming $\kappa_s \neq 0$, Equation~\eqref{eqn:curveODE} is separable, and can
 be solved analytically in terms of the {\em EllipticF} function using
 Mathematica. Unlike in the impermeable case, the solution
-of~\eqref{eqn:curveODE} is not periodic unless $\kappa(s) = \kappa_0$.
+of Equation~\eqref{eqn:curveODE} is not periodic unless $\kappa(s) = \kappa_0$.
 Therefore, the equilibrium shape of a semipermeable vesicle in a
@@
 \end{align}
-Applying integration by parts, the two integrals agree, and we have
+Applying integration by parts, the two integrals are identical and we combine them to obtain
 \begin{align}
@@
 %\end{align}
-Note that the integrand in~\eqref{eqn:areaROC} is zero when the membrane tension balances the elastic force:
+Note that the integrand in Equation~\eqref{eqn:areaROC} is zero when the membrane tension balances the elastic force:
 \begin{align}
@@
 \end{align}
-which is consistent with the equilibrium results in the vesicle area dynamics.
+which is consistent with the equilibrium results in Equation~(\ref{eqn:curveODE}).
 
@@
 \end{alignat}
-for the differential and projection operators. Then, the
-governing equations~\eqref{eqn:vesVelocity} are
+for the differential and projection operators. Then, Equations~\eqref{eqn:vesVelocity} are
+recast in the following form
 \begin{align}
@@
 similar notation for the other operators. Then, a first-order
-semi-implicit time stepping method of~\eqref{eqn:vesVelocity} is
+semi-implicit time stepping method of Equation~\eqref{eqn:vesVelocity} is
 \begin{alignat}{3}  
@@
 examine the enclosed water content as a dynamic consequence of water
-flow, vesicle shape deformation, and membrane tension distribution.
+flow, vesicle shape deformation, and distribution of membrane tension.
 %
@@
   \fi
+  \todo[inline]{Overflow. Need to reduce size}
   \caption{\label{fig:relaxationComposite} (a) Snapshots of four
@@
 %  \fi
-  \caption{\label{fig:relaxationTensions} The tension distribution of
-  vesicles in relaxation that corresponds to
+  \todo[inline]{Convert to tikz}
+  \caption{\label{fig:relaxationTensions} The distribution of membrane tension of a relaxing
+  vesicle that corresponds to
   Figure~\ref{fig:relaxationComposite}.}
@@
   \end{tikzpicture}
+  \todo[inline]{Convert to tikz}
 %  \includegraphics[width=\textwidth]{figures/shearTensions.pdf}
@@
   \end{tikzpicture}
+  \todo[inline]{Overflow. Need to reduce sizes. Convert to tikz}
   \caption{\label{fig:parabolicTensions} The equilibrium tension
@@
   \fi
+   \todo[inline]{Overflow. Need to reduce sizes}
   \caption{\label{fig:stenosisComposite} (a) A semipermeable vesicle
@@
   \centering
-  \begin{minipage}{0.45\textwidth}
     \centering
-%  \ifTikz
+  \ifTikz
   \input{figures/contractingComposite.tikz}
-%  \else
-%  \includegraphics{figures/contractingComposite.pdf}
-%  \fi
-  \end{minipage}
-  \hfill
-  \begin{minipage}{0.45\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{figures/contractingTensions1.pdf}
-    \includegraphics[width=\textwidth]{figures/contractingTensions2.pdf}
-    \input{figures/contractingMaxTension_vs_COM.tikz}
-%    \todo[inline]{Maximum tension as a function of center of mass down
-%    here}
-  \end{minipage}
+  \else
+  \includegraphics{figures/contractingComposite.pdf}
+  \fi
   \caption{\label{fig:contractingComposite} A contracting channel
@@
   \centering
-  \ifTikz
+%  \ifTikz
   \input{figures/contractingComposite2.tikz}
-  \else
-  \includegraphics{figures/contractingComposite2.pdf}
-  \fi
+%  \else
+%  \includegraphics{figures/contractingComposite2.pdf}
+%  \fi
+  \todo[inline]{Do max tension vs. center of mass and time for plot
+  (d).}
   \caption{\label{fig:contractingComposite2} Vesicle reduced area and

### 2021-02-09 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
fixed figure 8
fixed figure 9
fixed fig 11
updaged figs

@@
 \begin{figure*}[hbp]
-  \begin{tikzpicture}[scale=1]
-    \node[inner sep=0pt] at (0,0) {
-    \includegraphics[width=\textwidth]{figures/shearTensions.pdf}
-    };
-%    \node at (-8.54,0.6) {(a)};
-%    \node at (-6.00,0.6) {(b)};
-%    \node at (-3.46,0.6) {(c)};
-%    \node at (-0.92,0.6) {(d)};
-%    \node at (+1.60,0.6) {(e)};
-%    \node at (+4.16,0.6) {(f)};
-%    \node at (+6.70,0.6) {(g)};
-  \end{tikzpicture}
-  \todo[inline]{Convert to tikz}
-%  \includegraphics[width=\textwidth]{figures/shearTensions.pdf}
+  \centering
+  \ifTikz
+  \input{figures/shearTensions.tikz}
+  \else
+  \includegraphics{figures/shearTensions.pdf}
+  \fi
   \caption{\label{fig:shearTensions} The tension distribution along a
@@
   $\beta = 10^{-4}$ for all these cases, and the elastic capillary
-  number ranges from $10^{-1}$ to $10^{2}$ as in
-  Figure~\ref{fig:shearComposite}.}
+  numbers are (a) $10^{-1}$, (b) $10^{0}$, (c), $10^{1}$, and (d)
+  $10^{2}$ as in Figure~\ref{fig:shearComposite}.}
 \end{figure*}
@@
   \centering
-  \begin{tikzpicture}[scale=1]
-    \node[inner sep=0pt] at (0,0) {
-    \includegraphics[width=\textwidth]{figures/parabolicTensions.pdf}
-    };
-    \node at (-8.2,1.5) {(a)};
-    \node at (-3.8,1.5) {(b)};
-    \node at (+0.6,1.5) {(c)};
-    \node at (+5.0,1.5) {(d)};
-  \end{tikzpicture}
-  \todo[inline]{Overflow. Need to reduce sizes. Convert to tikz}
+  \ifTikz
+  \input{figures/parabolicTensions.tikz}
+  \else
+  \includegraphics{figures/parabolicTensions.pdf}
+  \fi
+%  \begin{tikzpicture}[scale=1]
+%    \node[inner sep=0pt] at (0,0) {
+%    \includegraphics[width=\textwidth]{figures/parabolicTensions.pdf}
+%    };
+%    \node at (-8.2,1.5) {(a)};
+%    \node at (-3.8,1.5) {(b)};
+%    \node at (+0.6,1.5) {(c)};
+%    \node at (+5.0,1.5) {(d)};
+%  \end{tikzpicture}
   \caption{\label{fig:parabolicTensions} The equilibrium tension
@@
   \fi
-   \todo[inline]{Overflow. Need to reduce sizes}
   \caption{\label{fig:stenosisComposite} (a) A semipermeable vesicle
@@
   \centering
-%  \ifTikz
+  \ifTikz
   \input{figures/contractingComposite2.tikz}
-%  \else
-%  \includegraphics{figures/contractingComposite2.pdf}
-%  \fi
-  \todo[inline]{Do max tension vs. center of mass and time for plot
-  (d).}
+  \else
+  \includegraphics{figures/contractingComposite2.pdf}
+  \fi
   \caption{\label{fig:contractingComposite2} Vesicle reduced area and

### 2021-02-09 vesicle_code/examples/output/makeImages.m

@@ -7,10 +7,10 @@ options.marker = false;
 
 irate = 1; % controls the speed of the visualization
 
-if 0
-%  file = 'parabolic1VesData.bin';
-  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/semipermeable/parabolic1Ves_speed8.00e02_RA9.00em01Data.bin';
-%  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/impermeable/parabolic1Ves_speed1.20e03_RA6.00em01Data.bin';
+if 1
+  file = 'parabolic1VesData.bin';
+%  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/semipermeable/parabolic1Ves_speed8.00e02_RA9.00em01Data.bin';
+%  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/impermeable/parabolic1Ves_speed1.20e03_RA7.00em01Data.bin';
 
   ax = 1*[-2 2 -2 12.5];
   irate = 1;
@@ -19,7 +19,7 @@ if 0
   options.marker = true;
 end
 
-if 1
+if 0
 file = '~/Dropbox/Adhesion/choke1VesKEp01bData_Feb02.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/PNAS_runs/stenosis/longConstriction_ra065_beta1em3/choke1VesData_Part1.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/PNAS_runs/stenosis/longConstriction_ra065_beta1em3/choke1VesData.bin';

### 2021-02-09 vesicle_code/examples/parabolic1Ves.m

@@ -13,7 +13,8 @@ prams.kappa = ones(prams.nv,1);   % bending coefficient
 prams.viscCont = ones(prams.nv,1);         % viscosity contrast
 prams.saveRate = 100;
 options.farField = 'parabolic'; % background velocity
-options.farFieldSpeed = 4.2;
+%options.farFieldSpeed = 4.2;
+options.farFieldSpeed = 600*4.2;
 %options.farFieldSpeed = farFieldSpeed;
 options.vesves = 'implicit';
 % Discretization of vesicle-vesicle interactions.
@@ -22,11 +23,11 @@ options.inextens = 'method1';
 options.near = true;        % near-singular integration
 options.fmm = false;
 options.verbose = true;
-options.semipermeable = true;
+options.semipermeable = false;
 prams.gmresMaxIter = 3*prams.N;
 prams.gmresTol = 1e-8;
 prams.errorTol = 1000;
-prams.fluxCoeff = 1e-3;
+prams.fluxCoeff = 0e-3;
 %prams.fluxCoeff = fluxCoeff;
 options.fluxShape = 1;
 
@@ -37,7 +38,7 @@ prams.adStrength = 100;
 % TIME ADAPTIVITY (parameters for new implementation)
 options.timeAdap = true;
 
-prams.rtolArea = 1e20;
+prams.rtolArea = 1e-2;
 prams.rtolLength = 1e-2;
 prams.dtMax = 1e-1;
 prams.dtMin = 1e-4;
@@ -65,13 +66,14 @@ options.dataFile = 'output/parabolic1VesData.bin';
 % Also add src to path
 
 oc = curve;
-ra = 0.65;
+ra = 0.70;
 centerx = 0;
-%centery = 1.0;
-centery = 0.0;
+centery = 1.0;
+%centery = 0.0;
 ang = -pi/18;
-ang = pi/2;
-scale = 0.5*sqrt(ra)*3.5662;
+%ang = pi/2;
+scale = 0.5*sqrt(ra)/1.0172;
+%*3.5662;
 X = oc.initConfig(prams.N,...
     'nv', prams.nv, ...
     'reducedArea',ra,...

### 2021-02-09 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
yny

--- 2021-02-08 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
@@
 reach its steady state is proportional to $\beta^{-1}$. For this reason,
-our numerical results are reported in terms of the scaled time $\beta
-t$.
+our numerical results are reported in terms of the scaled time $\beta t$.
 
@@
   (b) The equilibrium shape of a vesicle with varying flow rates and
-  membrane permeability. The circled vesicles correspond to the
-  simulations in part (a).}
+  membrane permeability. The boxed vesicles correspond to the
+  simulation results in part (a).}
 \end{figure*}
@@
 (flow rate) significantly affects the final vesicle shape, but the
-permeability coefficient has a very minor effect. Instead, as we saw in
-the quiescent analysis, $\beta$ sets a time scale since the time
-required for a vesicle to reach its steady state configuration is
-proportional to $\beta^{-1}$.
+permeability coefficient has a very minor effect on the equilibrium shape for $10^{-4}\le\beta\le 10^{-2}$. Instead, 
+$\beta$ sets the time required for a vesicle to reach its steady state configuration which is
+proportional to $\beta^{-1}$, as we saw in the analysis for the quiescent flow (\S~\ref{subsec:area_dynamics}).
 
@@
 
-As observed for the planar shear flow, the equilibrium reduced area of a
-semipermeable vesicle in a Poiseuille flow is independent of the initial
-reduced area and $\beta$, and  larger maximum flow velocity $U$ results
+As observed for the linear shear flow, our simulations with $0<\beta\le 10^{-2}$ 
+%in the range  $10^{-4}\le \beta\le 10^{-2}$ 
+show that
+the equilibrium reduced area of a
+semipermeable vesicle in a Poiseuille flow is independent of both the initial
+reduced area and $\beta$. Instead we find that
+larger maximum flow velocity $U$ results
 in smaller equilibrium reduced area

### 2021-02-10 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
yny

@@
 
-\title{Hydrodynamics of a  Semipermeable Vesicle Under Flow and
+\title{Hydrodynamics of a  Semipermeable Inextensible Membrane Under Flow and
 Confinement}
@@
 %
-Under strong confinement, a large value of $\beta$ is needed in
+In our simulations the equilibrium shape of a semipermeable membrane in open space is found to be independent of $\beta$ for $10^{-5}\le\beta\le10^{-2}$.
+Within this range we find that the permeability $\beta$ only affects the time it takes to reach the equilibrium membrane shape, which is determined by the imposed flow,
+such as a quiescent flow, a linear shear flow and its shear rate, and a Poiseuille flow and its maximum velocity.
+From these results and our analysis of area dynamics, we suspect similar hydrodynamics of a semipermeable inextensible membrane 
+with a smaller $\beta$ (as long as $\beta\ne 0$). 
+On the other hand,  when $\beta\ge 0.1$, we find that the membrane shape swells to maximize the water content inside the membrane, independent of the initial reduced 
+area and the imposed flow in the far field.
+In the simulations we focus on intermediate value of $10^{-5}\le \beta\le 10^{-3}$ to investigate the hydrodynamics of a semipermeable inextensible membrane. 
+%
+Under strong confinement,  $10^{-4}\le\beta\le10^{-3}$ is needed in
 our simulations to keep the membrane tension below the threshold value
-for membrane poration $\sim 10^{-3}$ N/m. Such large value of $\beta$
-may pertain to red blood cell membranes with aquaporin proteins.
+for membrane poration $\sim 10^{-3}$ N/m. Such range of $\beta$
+may imply that the lipid bilayer membrane would be porated under large stress in the confinement.
 
@@
 
-For a variety of dimensionless permeability coefficient $\beta>0$ and
+For a range of dimensionless permeability coefficient $\beta>0$ and
 capillary number $Ca_\mathrm{E}$, a semipermeable vesicle reaches an
@@
 (flow rate) significantly affects the final vesicle shape, but the
-permeability coefficient has a very minor effect on the equilibrium shape for $10^{-4}\le\beta\le 10^{-2}$. Instead, 
+permeability coefficient has a very minor effect on the equilibrium shape for $10^{-5}\le\beta\le 10^{-2}$. Instead, 
 $\beta$ sets the time required for a vesicle to reach its steady state configuration which is

### 2021-02-11 vesicle_code/examples/output/makeImages.m
fixed Fig 3

@@ -13,7 +13,7 @@ if 1
 %  file = '~/projects/brinkman/vesicle_code/results/parabolic_offcenter/impermeable/parabolic1Ves_speed1.20e03_RA7.00em01Data.bin';
 
   ax = 1*[-2 2 -2 12.5];
-  irate = 1;
+  irate = 10;
   options.confined = false;
   options.center = true;
   options.marker = true;

### 2021-02-11 vesicle_code/examples/parabolic1Ves.m
fixed figure 4

@@ -14,7 +14,7 @@ prams.viscCont = ones(prams.nv,1);         % viscosity contrast
 prams.saveRate = 100;
 options.farField = 'parabolic'; % background velocity
 %options.farFieldSpeed = 4.2;
-options.farFieldSpeed = 600*4.2;
+options.farFieldSpeed = 800*4.2;
 %options.farFieldSpeed = farFieldSpeed;
 options.vesves = 'implicit';
 % Discretization of vesicle-vesicle interactions.

### 2021-02-11 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
fixed Fig 3
fixed figure 4
fixed figure 2

@@
 \subsection{Numerical Validation\label{subsec:numerical_validation}}
-To validate our numerical codes for simulating vesicle hydrodynamics, we reproduce a phase diagram of the equilibrium
-shape of an impermeable vesicle in a Poiseuille flow. Depending on
-the maximum flow velocity and the vesicle reduced area, the equilibrium vesicle shape is either an
+To validate our numerical codes for simulating vesicle hydrodynamics, we
+reproduce a phase diagram of the equilibrium shape of an impermeable
+vesicle in a Poiseuille flow. Depending on the maximum flow velocity and
+the vesicle reduced area, the equilibrium vesicle shape is either an
 axisymmetric bullet, an axisymmetric parachute, or a tank-treading
-asymmetric slipper~\cite{kao-bir-mis2009}. Comparing against the simulation results of an impermeable vesicle in Poiseuille flow
-(specifically Figure 2 in~\citet{kao-bir-mis2009}),
-%
-%(Figure~\ref{fig:PoiseuillePhase}) with those in~\cite{kao-bir-mis2009}
-%(see Figure 2), 
-%
-we observe general agreement in the equilibrium
-vesicle shapes except that,
-%
-%see that the vesicle shapes qualitatively agree. We
-%note that 
-%
-Kaoui {\em et al.}~report that the vesicles with $\alpha=0.7$
-and flow rates $U = 1200\; \mu$m/s and $U = 1600\; \mu$m/s are
-axisymmetric.  In our simulations these vesicles are slightly
-asymmetric, are undergoing a tank-treading motion, and we therefore
-report them as asymmetric slippers.
+asymmetric slipper~\cite{kao-bir-mis2009}. Comparing against the
+simulation results of an impermeable vesicle in Poiseuille flow
+(specifically Figure 2 in~\citet{kao-bir-mis2009}), we observe general
+agreement in the equilibrium vesicle shapes.
 
@@
 %
-Under these flows, our simulations show
-that the steady state of an impermeable vesicle is different from that of a semipermeable vesicle, which depends only on the strength of the external flow and is insensitive to permeability $\beta$ (as long as $\beta>0$).
-We find that  the time in the dynamic evolution towards equilibrium is scaled by $\beta^{-1}$: the smaller $\beta$ is the longer it takes to reach the steady state.
+Under these flows, our simulations show that the steady state of an
+impermeable vesicle is different from that of a semipermeable vesicle,
+which depends only on the strength of the external flow and is
+insensitive to permeability $\beta$ (as long as $\beta>0$). We find that
+the time in the dynamic evolution towards equilibrium is scaled by
+$\beta^{-1}$: the smaller $\beta$ is the longer it takes to reach the
+steady state.
 
@@
   \fi
-  \todo[inline]{Overflow. Need to reduce size}
   \caption{\label{fig:relaxationComposite} (a) Snapshots of four
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/relaxationTensions2.pdf}
-%  \ifTikz
-%    \input{figures/relaxationTensions.tikz}
-%  \else
-%    \includegraphics{figures/relaxationTensions.pdf}
-%  \fi
-  \todo[inline]{Convert to tikz}
-  \caption{\label{fig:relaxationTensions} The distribution of membrane tension of a relaxing
-  vesicle that corresponds to
+  \ifTikz
+    \input{figures/relaxationTensions.tikz}
+  \else
+    \includegraphics{figures/relaxationTensions.pdf}
+  \fi
+  \caption{\label{fig:relaxationTensions} The distribution of membrane
+  tension of a relaxing vesicle that corresponds to
   Figure~\ref{fig:relaxationComposite}.}

### 2021-02-11 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
done up to start of Sec 5

@@
 membrane porates when the membrane tension reaches the order of $2$--$4$
-mN/m (see \citet{RazizadehNikfarPaulLiu2020_BJ} and references therein),
+mN/m (see~\citet{RazizadehNikfarPaulLiu2020_BJ} and references therein),
 giving rise to enhanced membrane permeability to both water and
@@
 ratio accurately~\cite{MinetttiCallensCoupier2008_AppliedOptics}. Using
-numerical simulations we can quantify the effects of water permeability
+numerical simulations described in \S~\ref{sec:formulation} and
+\S~\ref{sec:numerics} we can quantify the effects of water permeability
 on the hydrodynamics of a vesicle under mechanical stresses.  Without an
 osmotic gradient, we first show that a freely suspended semipermeable
-vesicle behaves differently from an impermeable vesicle over a long
-time in \S~\ref{sec:free_space}. Next in \S~\ref{sec:confinement} we show that
+vesicle behaves differently from an impermeable vesicle over a long time
+in \S~\ref{sec:free_space}. Next in \S~\ref{sec:confinement} we show
+that
 %, at normal physiological conditions,
@@
 \section{Formulation\label{sec:formulation}}
+\label{sec:formulation}
 We consider a two-dimensional semipermeable vesicle (permeable only to
@@
 when the membrane tension becomes large due to the external stress such
-as the hydrodynamic stress from an external flow or confinement. 
-In this work we set $\triangle c =0$ in Equation~\eqref{eqn:water_flux}  to
-focus on the water flux driven by the pressure difference due to an external flow or confinement.
+as the hydrodynamic stress from an external flow or confinement. In this
+work we set $\triangle c = 0$ in Equation~\eqref{eqn:water_flux} to
+focus on the water flux driven by the pressure difference due to an
+external flow or confinement.
 
@@
 \end{align}
-where $\nn$ is the outward normal of $\gamma$, $\jump{\cdot}$ is the
-jump across the interface, and $T$ is the hydrodynamic stress tensor.
-The membrane force $\ff_\mathrm{mem}$ is the sum of a bending force
-with bending modulus $k_b$ and a force due to the tension $\Lambda$.
-Following~\cite{vee-gue-zor-bir2009}, we introduce the variable $\sigma
-= \Lambda - \frac{3}{2}\kappa^2$, where $\kappa$ is the vesicle curvature. Then,
-the bending and tension forces corresponding to the Helfrich energy are
-$\ff_\mathrm{ben} = -k_b \xx_{ssss}$ and $\ff_\mathrm{ten} = (\sigma
-\xx_s)_s$.
+where 
+%$\nn$ is the outward normal of $\gamma$, 
+$\jump{\cdot}$ is the jump across the interface, and $T$ is the
+hydrodynamic stress tensor.
+\todo[inline]{We defined $T$ to be the pressure in equation (1)}
+%The membrane force $\ff_\mathrm{mem}$ is the sum of a bending force
+%with bending modulus $k_b$ and a force due to the tension $\Lambda$.
+%Following~\citet{vee-gue-zor-bir2009}, we introduce the variable
+%$\sigma = \Lambda - \frac{3}{2}\kappa^2$, where $\kappa$ is the vesicle
+%curvature. Then, the bending and tension forces corresponding to the
+%Helfrich energy are $\ff_\mathrm{ben} = -k_b \xx_{ssss}$ and
+%$\ff_\mathrm{ten} = (\sigma \xx_s)_s$.
 
@@
 
-The value of $\beta$ can be estimated by first
-converting the apparent permeability of a 
-bilayer~\cite{OlbrichRawiczNeedhamEtAl2000_BJ} to the hydraulic
-conductivity $k_w$ using the conversion
-in~\cite{FettiplaceHaydon1980_PhysRev}, and then scaling $k_w$ to $R_0/\mu$. We found that for most lipid bilayer membranes, $10^{-14}\le
-k_w\le 10^{-12}$ m$^2$s/kg, thus the range of $\beta$ corresponding to the native membrane permeability for water is $10^{-11}\le
-\beta\le 10^{-9}$. 
-%
-In our simulations the equilibrium shape of a semipermeable membrane in open space is found to be independent of $\beta$ for $10^{-5}\le\beta\le10^{-2}$.
-Within this range we find that the permeability $\beta$ only affects the time it takes to reach the equilibrium membrane shape, which is determined by the imposed flow,
-such as a quiescent flow, a linear shear flow and its shear rate, and a Poiseuille flow and its maximum velocity.
-From these results and our analysis of area dynamics, we suspect similar hydrodynamics of a semipermeable inextensible membrane 
-with a smaller $\beta$ (as long as $\beta\ne 0$). 
-On the other hand,  when $\beta\ge 0.1$, we find that the membrane shape swells to maximize the water content inside the membrane, independent of the initial reduced 
-area and the imposed flow in the far field.
-In the simulations we focus on intermediate value of $10^{-5}\le \beta\le 10^{-3}$ to investigate the hydrodynamics of a semipermeable inextensible membrane. 
-%
-Under strong confinement,  $10^{-4}\le\beta\le10^{-3}$ is needed in
-our simulations to keep the membrane tension below the threshold value
-for membrane poration $\sim 10^{-3}$ N/m. Such range of $\beta$
-may imply that the lipid bilayer membrane would be porated under large stress in the confinement.
+The value of $\beta$ can be estimated by first converting the apparent
+permeability of a bilayer~\cite{OlbrichRawiczNeedhamEtAl2000_BJ} to the
+hydraulic conductivity $k_w$ using the conversion
+in~\citet{FettiplaceHaydon1980_PhysRev}, and then scaling $k_w$ to
+$R_0/\mu$. We found that for most lipid bilayer membranes, $10^{-14}\le
+k_w\le 10^{-12}$ m$^2$s/kg, thus the range of $\beta$ corresponding to
+the native membrane permeability for water is $10^{-11}\le \beta\le
+10^{-9}$. 
+%
+In our simulations the equilibrium shape of a semipermeable membrane in
+open space is found to be independent of $\beta$ for
+$10^{-4}\le\beta\le10^{-2}$. Within this range we find that $\beta$ only
+affects the time it takes to reach the equilibrium membrane shape, which
+is determined by the imposed flow, such as a quiescent flow, a linear
+shear flow and its shear rate, and a Poiseuille flow and its maximum
+velocity. From these results and our analysis of area dynamics, we
+suspect similar hydrodynamics of a semipermeable inextensible membrane
+with a smaller $\beta$ (as long as $\beta \neq 0$). On the other hand,
+when $\beta\ge 10^{-1}$, we find that the membrane shape swells to
+maximize the water content inside the membrane, independent of the
+initial reduced area and the imposed flow in the far field. In the
+simulations we focus on intermediate value of $10^{-5}\le \beta\le
+10^{-3}$ to investigate the hydrodynamics of a semipermeable
+inextensible membrane. 
+%
+Under strong confinement, $10^{-4}\le\beta\le10^{-3}$ is needed in our
+simulations to keep the membrane tension below the threshold value for
+membrane poration $\sim 10^{-3}$ N/m. Such range of $\beta$ may imply
+that the lipid bilayer membrane would be porated under large stress
+caused by confinement.
 
@@
 \frac{1}{2}\kappa^3 - \Lambda \kappa = 0$, with initial conditions
-$\kappa(0) = \kappa_0$ and $\kappa_s(0) = 0$.  Multiplying $\kappa_s$ and integrating once, we have
+$\kappa(0) = \kappa_0$ and $\kappa_s(0) = 0$.  Multiplying by $\kappa_s$
+and integrating once, we have
 \begin{align}
@@
 \end{align}
-Assuming $\kappa_s \neq 0$, Equation~\eqref{eqn:curveODE} is separable, and can
-be solved analytically in terms of the {\em EllipticF} function using
-Mathematica. Unlike in the impermeable case, the solution
-of Equation~\eqref{eqn:curveODE} is not periodic unless $\kappa(s) = \kappa_0$.
-Therefore, the equilibrium shape of a semipermeable vesicle in a
-quiescent flow is a circle with radius $L/2\pi$ and constant tension
-$\Lambda = \kappa^2/2 = 2\pi^2/L^2.$ Note that in contrast to a
+Assuming $\kappa_s \neq 0$, Equation~\eqref{eqn:curveODE} is separable,
+and can be solved analytically in terms of the {\em EllipticF} function
+using Mathematica. Unlike in the impermeable case, the solution of
+Equation~\eqref{eqn:curveODE} is not periodic unless $\kappa(s) =
+\kappa_0$. Therefore, the equilibrium shape of a semipermeable vesicle
+in a quiescent flow is a circle with radius $L/2\pi$ and constant
+tension $\Lambda = \kappa^2/2 = 2\pi^2/L^2.$ Note that in contrast to a
 impermeable vesicle, the steady state tension is positive rather than
-negative. Such equilibrium shape of a semipermeable vesicle results from the balance between elastic stress and membrane tension. 
-For an elastic membrane with a large pore, the equilibrium membrane (hemispherical) shape also results from such balance \cite{Ryham2018_JFM}.
-
-We next compute the area dynamics of a semipermeable vesicle. Since the area of the
-vesicle is
+negative. Such equilibrium shape of a semipermeable vesicle results from
+the balance between elastic stress and membrane tension. For an elastic
+membrane with a large pore, the equilibrium membrane (hemispherical)
+shape also results from such a balance~\cite{Ryham2018_JFM}.
+
+We next compute the area dynamics of a semipermeable vesicle. Since the
+area of the vesicle is
 \begin{align}
@@
 %\end{align}
-Note that the integrand in Equation~\eqref{eqn:areaROC} is zero when the membrane tension balances the elastic force:
+Note that the integrand in Equation~\eqref{eqn:areaROC} is zero when the membrane tension balances the elastic force
 \begin{align}
 \label{eqn:areaROC2}
-\Lambda &= \frac{\kappa^2}{2}=\frac{\kappa_0^2}{2} \;\mathrm{ at }\; \mathrm{equilibrium},
+\Lambda &= \frac{\kappa^2}{2}=\frac{\kappa_0^2}{2},
+%  \;\mathrm{ at }\; \mathrm{equilibrium},
 \end{align}
@@
 \section{Numerical Methods}
+\label{sec:numerics}
 In the  boundary integral equation formulation, the unknowns are the
-vesicle's position and tension without confinement.
-With confinement, an extra unknown (the density function) is added to enforce the no-slip boundary conditions on the confinement wall.
-Both $\gamma$ and $\partial\Omega$ are discretized at a
-set of collocation points. Derivatives are computed with Fourier
-differentiation, and the eighth-order quadrature~\cite{alp1999} is
-applied to the weakly singular single-layer potential. For confined
-geometries, the trapezoid rule is used to approximate the double-layer
-potential since its kernel is smooth and periodic. Nearly-singular
-integrals are computed with an interpolation-based quadrature
-rule~\cite{qua-bir2014}.
+vesicle's position and tension. With confinement, an extra unknown (the
+density function) is added to enforce the no-slip boundary conditions on
+the confinement wall. Both $\gamma$ and $\partial\Omega$ are discretized
+at a set of collocation points. Derivatives are computed with Fourier
+differentiation, and the weakly singular single-layer potential is
+computed with an eighth-order quadrature rule~\cite{alp1999}. For
+confined geometries, the trapezoid rule is used to approximate the
+double-layer potential since its kernel is smooth and periodic.
+Nearly-singular integrals are computed with an interpolation-based
+quadrature rule~\cite{qua-bir2014}.
 
@@
 method that discretizes high-order derivatives
-semi-implicitly~\cite{vee-gue-zor-bir2009}. We introduce the notation
+semi-implicitly~\cite{vee-gue-zor-bir2009, qua-bir2014}. We introduce
+the notation
 \begin{alignat}{3}
@@
 \end{alignat}
-for the differential and projection operators. Then, Equations~\eqref{eqn:vesVelocity} are
-recast in the following form
+for the differential and projection operators. Then,
+Equation~\eqref{eqn:vesVelocity} is written as
 \begin{align}
@@
   vesicle with various reduced areas submerged in a Poiseuille flow with
-  various flow rates. The shapes agree qualitatively with Kaoui {\em et
+  various flow rates. The shapes agree with Kaoui {\em et
   al.}~\cite{kao-bir-mis2009} (see Figure 2).}
@@
 In experiments, vesicles under shear flows are measured for a few
-minutes (chapter 19 in~\cite{Dimova2020_GVB}), a duration over which a
+minutes (chapter 19 in~\citet{Dimova2020_GVB}), a duration over which a
 vesicle can be assumed impermeable~\cite{AbkarianViallat2005_BJ}. Our
@@
 \end{figure*}
+Figure~\ref{fig:relaxationTensions} shows the membrane tension
+distribution along the relaxing vesicles in
+Figure~\ref{fig:relaxationComposite}. The membrane tension (color bars)
+is in N/m. As the semipermeable vesicle relaxes, the membrane tension
+reduces in magnitude and becomes more evenly distributed along the
+membrane. In the top row ($\alpha(0)=0.95$) the vesicle nearly relaxes
+to a circle on the right, and the membrane tension is uniform and equal
+to $k_b \kappa_0^2/2$ as predicted by our analysis in
+Equation~\eqref{eqn:areaROC2}. 
+%In the bottom row ($\alpha(0)=0.12$), the initial vesicle shape has a
+%lot of high curvature regions (and thus the low reduced area), and it
+%takes more than four hours to inflate to twice the initial total water
+%content for $\beta=10^{-7}$. In contrast the water enclosed inside the
+%vesicle in the top row remains nearly constant in the first four hours.
 
@@
   (b) The equilibrium shape of a vesicle with varying flow rates and
-  membrane permeability. The boxed vesicles correspond to the
+  membrane permeability. The red regions correspond to influx and the
+  blue regions correspond to efflux The boxed vesicles correspond to the
   simulation results in part (a).}
@@
 %in the non-dimensionalization 
-(see \S~\ref{sec:formulation}) and $\chi$ is the shear rate of the planar
-shear flow $\uu_{\infty}(\xx) = \chi (y,0)$.  When $\beta=0$
+(see \S~\ref{sec:formulation}) and $\chi$ is the shear rate of the
+planar shear flow $\uu_{\infty}(\xx) = \chi (y,0)$.  When $\beta=0$
 (impermeable case), the vesicle reduced area and fluid viscosity
@@
 (flow rate) significantly affects the final vesicle shape, but the
-permeability coefficient has a very minor effect on the equilibrium shape for $10^{-5}\le\beta\le 10^{-2}$. Instead, 
-$\beta$ sets the time required for a vesicle to reach its steady state configuration which is
-proportional to $\beta^{-1}$, as we saw in the analysis for the quiescent flow (\S~\ref{subsec:area_dynamics}).
-
-Our simulations of a semipermeable vesicle in a planar shear flow show
-that the equilibrium vesicle shape depends mostly on the capillary
-number $Ca_\mathrm{E}$, independent of the dimensionless water
-permeability $\beta$. Our simulations show that the time it takes for a
-semipermeable vesicle to reach equilibrium in a planar shear flow is
-inversely proportional to $\beta$, just like the relaxing vesicle. The
-tension distribution along the equilibrium vesicle at $\beta=10^{-4}$ is
-shown in Figure~\ref{fig:shearTensions}, where the color bars are for
-the membrane tension in N/m. The capillary number $Ca_\mathrm{E}$
-increases from Figure~\ref{fig:shearTensions}(a) to (g), and we observe
-that the tension magnitude also increases almost linearly with
-$Ca_\mathrm{E}$. We also observe that the membrane tension is relatively
-small at the tip when the membrane curvature is large due to the
-extensional component in the shear flow.
-\begin{figure*}[hbp]
+permeability coefficient has a very minor effect on the equilibrium
+shape for $10^{-4}\le\beta\le 10^{-2}$. Instead, $\beta$ sets the time
+required for a vesicle to reach its steady state configuration which is
+proportional to $\beta^{-1}$, as we saw in the analysis for the
+quiescent flow (\S~\ref{subsec:area_dynamics}).
+
+%Our simulations of a semipermeable vesicle in a planar shear flow show
+%that the equilibrium vesicle shape depends mostly on the capillary
+%number $Ca_\mathrm{E}$, independent of the dimensionless water
+%permeability $\beta$. 
+The tension distribution along the equilibrium vesicle at
+$\beta=10^{-4}$ is shown in Figure~\ref{fig:shearTensions}, where the
+color bars are the membrane tension in N/m. The capillary number
+$Ca_\mathrm{E}$ increases from Figures~\ref{fig:shearTensions}(a)--(d),
+and we observe that the tension magnitude also increases almost linearly
+with $Ca_\mathrm{E}$. We also observe that the membrane tension is
+relatively small at the tip when the membrane curvature is large due to
+the extensional component in the shear flow.
+\begin{figure*}[htp]
   \centering
@@
   numbers are (a) $10^{-1}$, (b) $10^{0}$, (c), $10^{1}$, and (d)
-  $10^{2}$ as in Figure~\ref{fig:shearComposite}.}
+  $10^{2}$ as in Figure~\ref{fig:shearComposite}(b).}
 \end{figure*}
@@
 \subsection{Poiseuille Flow}
+We consider a semipermeable vesicle in the Poiseuille flow $\uu =
+U(1-(y/W)^2,0)$, where $U$ is the maximum velocity at $y=0$. The
+non-linear effects of the Poiseuille flow on the migration of an
+impermeable vesicle have been well-studied~\cite{kao-bir-mis2009}: At a
+given value of the maximum velocity $U$, there exists a critical reduced
+volume above which the equilibrium vesicle shape is symmetric (parachute
+or bullet shapes) and the vesicle stays at $y=0$. Below this critical
+reduced volume the equilibrium vesicle moves off the center and is
+asymmetric (tank-treading slipper shape). We validated our numerical
+codes by comparing against results in~\citet{kao-bir-mis2009} (see
+\S~\ref{subsec:numerical_validation}).
+
 \begin{figure*}[htp]
@@
 
-We consider a semipermeable vesicle in the Poiseuille flow $\uu =
-U(1-(y/W)^2,0)$, where $U$ is the maximum velocity at $y=0$. The
-non-linear effects of the Poiseuille flow on the migration of an
-impermeable vesicle have been well-studied~\cite{kao-bir-mis2009}: At a
-given value of the maximum velocity $U$, there exists a critical reduced
-volume above which the equilibrium vesicle shape is symmetric (parachute
-or bullet shapes) and the vesicle stays at $y=0$. Below this critical
-reduced volume the equilibrium vesicle moves off the center and is
-asymmetric (tank-treading slipper shape). We validated our numerical
-codes by comparing against results in Kaoui {\em et
-al.}~\cite{kao-bir-mis2009} (see \S~\ref{subsec:numerical_validation}).
-
 %
@@
 Using several initial reduced areas and flow rates, we recreate the
-impermeable vesicle phase diagram for vesicles with $\beta = 10^{-3}$.
-The equilibrium vesicle shape for different $U$ and initial reduced area
-is summarized in Figure~\ref{fig:parabolicComposite}(a), and the
-vertical displacement of the vesicle's center of mass is in
+impermeable vesicle phase diagram for semipermeable vesicles with $\beta
+= 10^{-3}$. The equilibrium vesicle shape for different $U$ and initial
+reduced area is summarized in Figure~\ref{fig:parabolicComposite}(a),
+and the vertical displacement of the vesicle's center of mass is in
 Figure~\ref{fig:parabolicComposite}(b). The effect of semipermeability
@@
 %in the range  $10^{-4}\le \beta\le 10^{-2}$ 
-show that
-the equilibrium reduced area of a
-semipermeable vesicle in a Poiseuille flow is independent of both the initial
-reduced area and $\beta$. Instead we find that
-larger maximum flow velocity $U$ results
+\todo[inline]{I don't understand this range of $\beta$ values?}
+show that the equilibrium reduced area of a semipermeable vesicle in a
+Poiseuille flow is independent of both the initial reduced area and
+$\beta$. Instead we find that larger maximum flow velocity $U$ results
 in smaller equilibrium reduced area
@@
 
-In a nonlinear shear flow, an impermeable vesicle can reach equilibrium
-position at the mid-plane of the shear flow for sufficiently large
-reduced area, regardless of the maximum flow velocity $U$. For a
-semipermeable vesicle, however, our simulation results (summarized in
-Figure~\ref{fig:parabolicComposite}) show that the equilibrium vesicle
-shape and position are determined by $U$, and independent of the initial
-vesicle reduced area and permeability $\beta$. The corresponding
-membrane tension distribution is shown in
-Figure~\ref{fig:parabolicTensions} as a function of flow velocity $U$
-from $200\;\mu$m/s to $800 \;\mu$m/s.
+%In a nonlinear shear flow, an impermeable vesicle can reach equilibrium
+%position at the mid-plane of the shear flow for sufficiently large
+%reduced area, regardless of the maximum flow velocity $U$. For a
+%semipermeable vesicle, however, our simulation results (summarized in
+%Figure~\ref{fig:parabolicComposite}) show that the equilibrium vesicle
+%shape and position are determined by $U$, and independent of the initial
+%vesicle reduced area and permeability $\beta$. The corresponding
+%membrane tension distribution is shown in
+%Figure~\ref{fig:parabolicTensions} as a function of flow velocity $U$
+%from $200\;\mu$m/s to $800 \;\mu$m/s.
 
@@
 \end{figure*}
-
-We note that in the Poiseuille flow the membrane tension is positive in
-the front, and negative in the rear part of the vesicle. Furthermore we
-also note that the tension magnitude is almost linearly proportional to
-$U$ as in the linear shear flow.
+ The membrane tension distribution of the equilibrium shapes are shown
+ in Figure~\ref{fig:parabolicTensions} for the flow velocities $U$ from
+ $200\;\mu$m/s to $800 \;\mu$m/s. We note that in the Poiseuille flow
+ the membrane tension is positive in the front, and negative in the rear
+ part of the vesicle. Furthermore we also note that the tension
+ magnitude is almost linearly proportional to $U$ as in the linear shear
+ flow.
 

### 2021-02-11 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
yny

--- 2021-02-11 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
@@
 conductivity $k_w$ using the conversion
-in~\cite{FettiplaceHaydon1980_PhysRev}, and then scaling $k_w$ to $R_0/\mu$. We found that for most lipid bilayer membranes, $10^{-14}\le
+in~\citet{FettiplaceHaydon1980_PhysRev}, and then scaling $k_w$ to $R_0/\mu$. We found that for most lipid bilayer membranes, $10^{-14}\le
 k_w\le 10^{-12}$ m$^2$s/kg, thus the range of $\beta$ corresponding to the native membrane permeability for water is $10^{-11}\le
@@
 In our simulations the equilibrium shape of a semipermeable membrane in open space is found to be independent of $\beta$ for $10^{-5}\le\beta\le10^{-2}$.
-Within this range we find that the permeability $\beta$ only affects the time it takes to reach the equilibrium membrane shape, which is determined by the imposed flow,
-such as a quiescent flow, a linear shear flow and its shear rate, and a Poiseuille flow and its maximum velocity.
+Within this range we find that the permeability $\beta$ only affects the time it takes to reach the equilibrium membrane shape, which is determined by the background flow
+(such as a quiescent flow, a linear shear flow and its shear rate, and a Poiseuille flow and its maximum velocity.)
 From these results and our analysis of area dynamics, we suspect similar hydrodynamics of a semipermeable inextensible membrane 
-with a smaller $\beta$ (as long as $\beta\ne 0$). 
+with a smaller $\beta$ ($\beta\ne 0$). 
 On the other hand,  when $\beta\ge 0.1$, we find that the membrane shape swells to maximize the water content inside the membrane, independent of the initial reduced 

### 2021-02-11 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex

--- 2021-02-11 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
@@
 
-The value of $\beta$ can be estimated by first converting the apparent
-permeability of a bilayer~\cite{OlbrichRawiczNeedhamEtAl2000_BJ} to the
-hydraulic conductivity $k_w$ using the conversion
-in~\citet{FettiplaceHaydon1980_PhysRev}, and then scaling $k_w$ to
-$R_0/\mu$. We found that for most lipid bilayer membranes, $10^{-14}\le
-k_w\le 10^{-12}$ m$^2$s/kg, thus the range of $\beta$ corresponding to
-the native membrane permeability for water is $10^{-11}\le \beta\le
-10^{-9}$. 
-%
-In our simulations the equilibrium shape of a semipermeable membrane in
-open space is found to be independent of $\beta$ for
-$10^{-4}\le\beta\le10^{-2}$. Within this range we find that $\beta$ only
-affects the time it takes to reach the equilibrium membrane shape, which
-is determined by the imposed flow, such as a quiescent flow, a linear
-shear flow and its shear rate, and a Poiseuille flow and its maximum
-velocity. From these results and our analysis of area dynamics, we
-suspect similar hydrodynamics of a semipermeable inextensible membrane
-with a smaller $\beta$ (as long as $\beta \neq 0$). On the other hand,
-when $\beta\ge 10^{-1}$, we find that the membrane shape swells to
-maximize the water content inside the membrane, independent of the
-initial reduced area and the imposed flow in the far field. In the
-simulations we focus on intermediate value of $10^{-5}\le \beta\le
-10^{-3}$ to investigate the hydrodynamics of a semipermeable
-inextensible membrane. 
+The value of $\beta$ can be estimated by first
+converting the apparent permeability of a 
+bilayer~\cite{OlbrichRawiczNeedhamEtAl2000_BJ} to the hydraulic
+conductivity $k_w$ using the conversion
+in~\citet{FettiplaceHaydon1980_PhysRev}, and then scaling $k_w$ to $R_0/\mu$. We found that for most lipid bilayer membranes, $10^{-14}\le
+k_w\le 10^{-12}$ m$^2$s/kg, thus the range of $\beta$ corresponding to the native membrane permeability for water is $10^{-11}\le
+\beta\le 10^{-9}$. 
+%
+In our simulations the equilibrium shape of a semipermeable membrane in open space is found to be independent of $\beta$ for $10^{-5}\le\beta\le10^{-2}$.
+Within this range we find that the permeability $\beta$ only affects the time it takes to reach the equilibrium membrane shape, which is determined by the background flow
+(such as a quiescent flow, a linear shear flow and its shear rate, and a Poiseuille flow and its maximum velocity.)
+From these results and our analysis of area dynamics, we suspect similar hydrodynamics of a semipermeable inextensible membrane 
+with a smaller $\beta$ ($\beta\ne 0$). 
+On the other hand,  when $\beta\ge 0.1$, we find that the membrane shape swells to maximize the water content inside the membrane, independent of the initial reduced 
+area and the imposed flow in the far field.
+In the simulations we focus on intermediate value of $10^{-5}\le \beta\le 10^{-3}$ to investigate the hydrodynamics of a semipermeable inextensible membrane. 
 %

### 2021-02-11 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
updated time stepping section

@@
 
-In our formulation, a semipermeable vesicle is suspended in a viscous Newtonian fluid 
-(in domain $\Omega$).  The vesicle membrane $\gamma$ is parameterized as $\xx(s,t)$
-where $s$ is arclength and $t$ is time. In the suspending fluid the flow
-velocity $\uu$ and pressure $p$ are governed by the incompressible 
-Stokes equations
+In our formulation, a semipermeable vesicle is suspended in a viscous
+Newtonian fluid (in domain $\Omega$).  The vesicle membrane $\gamma$ is
+parameterized as $\xx(s,t)$ where $s$ is arclength and $t$ is time. In
+the suspending fluid the flow velocity $\uu$ and pressure $p$ are
+governed by the incompressible Stokes equations
 \begin{align}
@@
   \jump{\uu} = 0, \quad
-  \jump{T\cdot\nn} = \ff_\mathrm{mem}, \quad
+  \jump{\mathbf{T}\cdot\nn} = \ff_\mathrm{mem}, \quad
   \xx_s \cdot \uu_s = 0,
@@
 %$\nn$ is the outward normal of $\gamma$, 
-$\jump{\cdot}$ is the jump across the interface, and $T$ is the
+$\jump{\cdot}$ is the jump across the interface, and $\mathbf{T} = -p
+\mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T \right)$ is the
 hydrodynamic stress tensor.
-\todo[inline]{We defined $T$ to be the pressure in equation (1)}
 %The membrane force $\ff_\mathrm{mem}$ is the sum of a bending force
@@
 \begin{align}
+  \label{eqn:SLP}
   \SS[\ff](\xx) = \frac{1}{4\pi} \int_{\gamma} \left(
@@
 the notation
-\begin{alignat}{3}
-  &B[\xx]\ff = -\frac{d^4}{ds^4} \ff,  \qquad
-  &&T[\xx]\sigma = (\sigma \xx_s)_s, \\
-  &D[\xx]\ff = \xx_s \cdot \ff_s, 
-  &&P[\xx]\ff = (\ff \cdot \nn) \nn,
-\end{alignat}
+%\begin{alignat}{3}
+%  &\BB\ff = -\frac{d^4}{ds^4} \ff,  \qquad
+%  &&\TT\sigma = (\sigma \xx_s)_s, \\
+%  &\DD\ff = \xx_s \cdot \ff_s, 
+%  &&P\ff = (\ff \cdot \nn) \nn,
+%\end{alignat}
+\begin{align}
+  \BB\ff = -\frac{d^4}{ds^4} \ff,  \qquad
+  \TT\sigma = (\sigma \xx_s)_s, \quad
+  \DD\ff = \xx_s \cdot \ff_s, \quad
+  P\ff = (\ff \cdot \nn) \nn,
+  \label{eqn:operators}
+\end{align}
 for the differential and projection operators. Then,
-Equation~\eqref{eqn:vesVelocity} is written as
-\begin{align}
-  \dot{\xx} &= \uu_\infty(\xx) + \beta P(B\xx + T\sigma)
-  + \SS (B\xx + T\sigma), \quad
-  D \dot{\xx} = 0.
-\end{align}
-We note that the integral and differential operators, which all depend
-on the vesicle shape, are non-linear with respect to the vesicle
-shape. We construct a time stepping scheme by letting $B^N$ be the
-bending operator due to the vesicle configuration at time $t^N$, and use
-similar notation for the other operators. Then, a first-order
-semi-implicit time stepping method of Equation~\eqref{eqn:vesVelocity} is
+Equation~\eqref{eqn:vesVelocity} can be written as
+\begin{align}
+  \dot{\xx} &= \uu_\infty(\xx) + \beta P(\BB\xx + \TT\sigma)
+  + \SS (\BB\xx + \TT\sigma), \quad \DD \dot{\xx} = 0.
+\end{align}
+We note that the operators defined in Equation~\eqref{eqn:operators}, as
+well as the single-layer potential defined in Equation~\eqref{eqn:SLP}
+all depend on the vesicle shape. A time stepping method that treats
+these dependencies implicitly would result in a non-linear set of
+equations that would be computationally expensive to solve. Instead, we
+use a time stepping method that defines the operators at time $t^N$ and
+discretizes the stiff terms implicitly. In particular, we use the
+first-order semi-implicit method
+%We note that the integral and differential operators, which all depend
+%on the vesicle shape, are non-linear with respect to the vesicle shape.
+%We construct a time stepping scheme by letting $\BB^N$ be the bending
+%operator due to the vesicle configuration at time $t^N$, and use
+%similar notation for the other operators. Then, a first-order
+%semi-implicit time stepping method of Equation~\eqref{eqn:vesVelocity}
+%is
 \begin{alignat}{3}  
   \frac{\xx^{N+1} - \xx^N}{\triangle t} &= \uu_\infty(\xx^N) 
-  + \beta P^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right) 
-  + \SS^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right),  \\
-%  \frac{\xx^{N+1} - \xx^N}{\triangle t} &= \uu_\infty(\xx^N) 
-%  &&+ \beta P^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right) \nonumber \\
-%  & &&+ \SS^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right),  \\
-  D^N\xx^{N+1} &= 1,
+  + \beta P^N\left(\BB^N\xx^{N+1} + \TT^N\sigma^{N+1}\right) 
+  + \SS^N\left(\BB^N\xx^{N+1} + \TT^N\sigma^{N+1}\right),  \\
+  \DD^N\xx^{N+1} &= 1,
 \end{alignat}

### 2021-02-11 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
small changes to time stepping

@@
 \subsection{Discretization in Time}
-To eliminate stringent time step restrictions, we modify a time stepping
-method that discretizes high-order derivatives
-semi-implicitly~\cite{vee-gue-zor-bir2009, qua-bir2014}. We introduce
-the notation
+To develop a second-order, non-stiff, adaptive time stepping method, we
+first introduce the notation
 %\begin{alignat}{3}
@@
 use a time stepping method that defines the operators at time $t^N$ and
-discretizes the stiff terms implicitly. In particular, we use the
-first-order semi-implicit method
+discretizes the stiff terms due to high-order derivatives
+implicitly~\cite{vee-gue-zor-bir2009, qua-bir2014}. In particular, we
+use the first-order semi-implicit method
 %We note that the integral and differential operators, which all depend
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Numerical Validation\label{subsec:numerical_validation}}
+To validate our numerical codes for simulating vesicle hydrodynamics, we
+reproduce a phase diagram of the equilibrium shape of an impermeable
+vesicle in a Poiseuille flow. Depending on the maximum flow velocity and
+the vesicle reduced area, the equilibrium vesicle shape is either an
+axisymmetric bullet, an axisymmetric parachute, or a tank-treading
+asymmetric slipper~\cite{kao-bir-mis2009}. Comparing against the
+simulation results of an impermeable vesicle in Poiseuille flow
+(specifically Figure 2 in~\citet{kao-bir-mis2009}), we observe general
+agreement in the equilibrium vesicle shapes.
+
 \begin{figure}[htp]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Numerical Validation\label{subsec:numerical_validation}}
-To validate our numerical codes for simulating vesicle hydrodynamics, we
-reproduce a phase diagram of the equilibrium shape of an impermeable
-vesicle in a Poiseuille flow. Depending on the maximum flow velocity and
-the vesicle reduced area, the equilibrium vesicle shape is either an
-axisymmetric bullet, an axisymmetric parachute, or a tank-treading
-asymmetric slipper~\cite{kao-bir-mis2009}. Comparing against the
-simulation results of an impermeable vesicle in Poiseuille flow
-(specifically Figure 2 in~\citet{kao-bir-mis2009}), we observe general
-agreement in the equilibrium vesicle shapes.
-
 \section{Hydrodynamics of a semipermeable vesicle in free space\label{sec:free_space}}

### 2021-02-11 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
working on section 5

@@
 \subsection{Semipermeable Vesicle in a Closely-fit Channel (Stenosis)}
- \begin{figure*}[hbp]
+\begin{figure*}[htp]
   \centering
@@
   passing through a closely-fit channel similar to the experimental
-   device in~\cite{abk-fai-sto2006}. (b) A semipermeable vesicle passing
+  device in~\citet{abk-fai-sto2006}. (b) A semipermeable vesicle passing
   through a (four-times) longer closely-fit channel than (a).  (c) The
-   excess pressure of an impermeable and semipermeable vesicle in the
-   short geometry in (a). (d) The reduced area of the semipermeable
-   vesicles in the geometries in (a) and (b) as a function of the
-   vesicles' center of mass. In (c) and (d), the x-axis is scaled by
-   $1/L$ where $L$ is half the length of the constriction. (e) The
+  tension in N/m of the vesicle shapes in (a). (d) The tension in N/m of
+  the vesicle shapes in (b). (e) The excess pressure of an impermeable
+  and semipermeable vesicle in the short geometry in (a). (f) The
   reduced area of the semipermeable vesicles in the geometries in (a)
-   and (b) as a function of time. The time axis is scaled by $1/t_R$
-   where $t_R$ is the residency time. In parts (c) and (d), the dashed
-   lines correspond to the locations of the inlet and outlet. In part
-   (e), the dashed lines correspond to the times that the vesicle enters
-   and exits the constriction. The colored vesicles show the tension
-   distribution in N/m of the circled vesicles. Throughout the entire
-   simulation, these vesicle configurations have the largest tension.}
+  and (b) as a function of the vesicles' center of mass. In (c) and (d),
+  the x-axis is scaled by $1/L$ where $L$ is half the length of the
+  constriction. (g) The reduced area of the semipermeable vesicles in
+  the geometries in (a) and (b) as a function of time. The time axis is
+  scaled by $1/t_R$ where $t_R$ is the residency time. In parts (e) and
+  (f), the dashed lines correspond to the locations of the inlet and
+  outlet. In part (g), the dashed lines correspond to the times that the
+  vesicle enters and exits the constriction. The colored vesicles show
+  the tension distribution in N/m of the circled vesicles. Throughout
+  the entire simulation, these vesicle configurations have the largest
+  tension.}
 \end{figure*}
-
 When red blood cells go through small capillary vessels, they experience
@@
 This corresponds well to the corresponding tension distribution in Figure~\ref{fig:stenosisTensions}: Larger tension in the front, and smaller tension in the rear.
-%\begin{figure*}[htp]
-%  \centering
-%  \begin{tikzpicture}[scale=1]
-%    \node[inner sep=0pt] at (0,0) {
-%    \includegraphics[width=\textwidth]{figures/stenosisTensions.pdf}
-%    };
-%    \node at (-8.6,0.7) {(a)};
-%    \node at (-1.6,0.7) {(b)};
-%  \end{tikzpicture}
-%  \caption{\label{fig:stenosisTensions} The tension distribution along a
-%  semipermeable vesicle with $\beta = 10^{-3}$ going through a
-%  closely-fit channel of two different lengths.}
-%\end{figure*}
 

### 2021-02-11 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
went through confinement

@@
 \section{Formulation\label{sec:formulation}}
-\label{sec:formulation}
 We consider a two-dimensional semipermeable vesicle (permeable only to
@@
   device in~\citet{abk-fai-sto2006}. (b) A semipermeable vesicle passing
-  through a (four-times) longer closely-fit channel than (a).  (c) The
-  tension in N/m of the vesicle shapes in (a). (d) The tension in N/m of
-  the vesicle shapes in (b). (e) The excess pressure of an impermeable
-  and semipermeable vesicle in the short geometry in (a). (f) The
+  through a (four-times) longer closely-fit channel than (a). In (a) and
+  (b), red regions correspond to influx and blue regions correspond to
+  efflux. (c) and (d) The tension in N/m of the vesicle shapes in (a)
+  and (b). (e) The excess pressure of an impermeable and semipermeable
+  vesicle in the short geometry in (a). (f) The reduced area of the
+  semipermeable vesicles in the geometries in (a) and (b) as a function
+  of the vesicles' center of mass. In (e) and (f), the x-axis is scaled
+  by $1/L$ where $L$ is half the length of the constriction. (g) The
   reduced area of the semipermeable vesicles in the geometries in (a)
-  and (b) as a function of the vesicles' center of mass. In (c) and (d),
-  the x-axis is scaled by $1/L$ where $L$ is half the length of the
-  constriction. (g) The reduced area of the semipermeable vesicles in
-  the geometries in (a) and (b) as a function of time. The time axis is
-  scaled by $1/t_R$ where $t_R$ is the residency time. In parts (e) and
-  (f), the dashed lines correspond to the locations of the inlet and
-  outlet. In part (g), the dashed lines correspond to the times that the
-  vesicle enters and exits the constriction. The colored vesicles show
-  the tension distribution in N/m of the circled vesicles. Throughout
-  the entire simulation, these vesicle configurations have the largest
-  tension.}
+  and (b) as a function of time. The time axis is scaled by $1/t_R$
+  where $t_R$ is the residency time. In (e) and (f), the dashed lines
+  correspond to the locations of the inlet and outlet. In (g), the
+  dashed lines correspond to the times that the vesicle enters and exits
+  the constriction. The colored vesicles show the tension distribution
+  in N/m of the circled vesicles. Throughout the entire simulation,
+  these vesicle configurations have the largest tension.}
 \end{figure*}
@@
 through a stenosis (a long microfluidic channel with a width smaller
-than the cell radius).  Based on the findings in~\cite{abk-fai-sto2006},
-we first examine the effect of semipermeability on the pressure
-fluctuation across a stenosed geometry. In this experiment, a pressure
-drop is used to squeeze a red blood cell through a constriction with
-diameter $5\;\mu$m and length $45\;\mu$m. We set up a similar
-computational geometry with a Poiseuille flow imposed at the inlet and
-outlet (Figure~\ref{fig:stenosisComposite}(a)). We set the maximum flow
-velocity to $U_{\max} = 1000 \;\mu$m/s at the inlet and outlet so that
-the residency time of the vesicle in the stenosis channel is $t_R
-\approx 25$ ms which agrees with the experimental
+than the cell radius). Based on previous
+findings~\cite{abk-fai-sto2006}, we first examine the effect of
+semipermeability on the pressure fluctuation across a stenosed geometry.
+In this experiment, a pressure drop is used to squeeze a red blood cell
+through a constriction with diameter $5\;\mu$m and length $45\;\mu$m. We
+set up a similar computational geometry with a Poiseuille flow imposed
+at the inlet and outlet (Figure~\ref{fig:stenosisComposite}(a)). We set
+the maximum flow velocity to $U_{\max} = 1000 \;\mu$m/s at the inlet and
+outlet so that the residency time of the vesicle in the stenosis channel
+is $t_R \approx 25$ ms which agrees with the experimental
 results~\cite{abk-fai-sto2006}. When the red blood cell enters the
@@
 compute the excess pressure as a function of vesicle position in the
-channel (Figure~\ref{fig:stenosisComposite}(c)). The impermeable case
+channel (Figure~\ref{fig:stenosisComposite}(e)). The impermeable case
 agrees with experimental results~\cite{abk-fai-sto2006} (see Figure 3).
@@
 front and minimum tension in the back
-(Figure~\ref{fig:stenosisComposite}(a)), consistent with earlier
+(Figure~\ref{fig:stenosisComposite}(c)), consistent with earlier
 results~\cite{Pak2015_PNAS, HarmanBertrandJoos2017_CJP}.
 
-Figures~\ref{fig:stenosisComposite}(d)
-and~\ref{fig:stenosisComposite}(e) show that the vesicle deflates from
+Figures~\ref{fig:stenosisComposite}(f)
+and~\ref{fig:stenosisComposite}(g) show that the vesicle deflates from
 the beginning due to the high flow velocity, consistent with the results
@@
 water at a constant rate as shown in
-Figures~\ref{fig:stenosisComposite}(d)
-and~\ref{fig:stenosisComposite}(e) (blue curves). Thus we expect that a
+Figures~\ref{fig:stenosisComposite}(f)
+and~\ref{fig:stenosisComposite}(g) (blue curves). Thus we expect that a
 larger amount of deflation is possible if the vesicle is inside a longer
@@
 
-When a semipermeable vesicle goes through a closely-fit channel, we observe that the water efflux is found in the front, and the influx is in the rear of the vesicle membrane (Figure~\ref{fig:stenosisComposite}).
-This corresponds well to the corresponding tension distribution in Figure~\ref{fig:stenosisTensions}: Larger tension in the front, and smaller tension in the rear.
+%When a semipermeable vesicle goes through a closely-fit channel, we
+%observe that the water efflux is found in the front, and the influx is
+%in the rear of the vesicle membrane
+%(Figure~\ref{fig:stenosisComposite}). This corresponds well to the
+%corresponding tension distribution in Figure~\ref{fig:stenosisTensions}:
+%Larger tension in the front, and smaller tension in the rear.
 
@@
   \caption{\label{fig:contractingComposite} A contracting channel
-  similar to the experimental configuration in~\cite{wu2015critical}.
+  similar to the experimental configuration in~\citet{wu2015critical}.
   The channel width varies from $18\;\mu$m to $1.8\;\mu$m, and it
@@
   the vesicle, and the fluid flux along the blue regions is out of the
-  vesicle.  (a--c): The ability for a semipermeable vesicle to pass
-  through the contraction depends on the permeability $\beta$. (d--f):
+  vesicle.  (a--c) The ability for a semipermeable vesicle to pass
+  through the contraction depends on the permeability $\beta$. (d--f)
   The ability for a semipermeable vesicle to pass through the
-  contraction depends on the flow rate. The colored vesicles show the
-  tension distribution in N/m of the circled vesicles. Throughout the
-  entire simulation, these vesicle configurations have the largest
-  tension.}
+  contraction depends on the flow rate. (g--i) The tension distribution
+  and maximum tension in N/m of the vesicle shapes in (a) and (b).
+  (j--l) The tension distribution and maximum tension in N/m of the
+  vesicle shapes in (d) and (e).}
 \end{figure}
@@
 squeezed through a contracting microfluidic channel similar
-to~\cite{wu2015critical}, where the width of the channel gradually
+to~\citet{wu2015critical}, where the width of the channel gradually
 decreases from $18 \;\mu$m to $1.8\; \mu$m. The channel then immediately
@@
 result in additional deflation and the vesicle passes through the
-contraction.
+contraction. When the vesicle is near the neck, simulations show that
+the water efflux is in the front and rear of vesicle while most water
+influx is in the middle. The tension distribution along the vesicle as
+a function of their position in the contracting channel is summarized in
+Figure~\ref{fig:contractingComposite} (g)--(l), where we observe the
+tension has the largest magnitude when the vesicle is at the neck.
 
@@
   (c), the lower x-axis is the x-coordinate of the center of mass, and
-  the upper x-axis is time. The colored vesicles show the tension
-  distribution in N/m of the circled vesicles. Throughout the entire
-  simulation, these vesicle configurations have the largest tension.}
+  the upper x-axis is time. (d) The vesicle tension in N/m. (e) The
+  maximum vesicle tension.}
+%  The colored vesicles show the tension
+%  distribution in N/m of the circled vesicles. Throughout the entire
+%  simulation, these vesicle configurations have the largest tension.}
 \end{figure}
@@
 through the contraction, it first accelerates until it reaches the neck
-where it abruptly decelerates to go through the contraction. The reduced
-area and velocity with respect to time are also shown in
-Figure~\ref{fig:contractingComposite2}.
-
-When a semipermeable vesicle goes through a contracting channel (slit)
-the numerical simulations show that both the driving flow and the
-membrane permeability have to be sufficiently large for a successful
-passage through the slit (Figure~\ref{fig:contractingComposite}). As
-the vesicle goes through the contracting channel, the gradual
-confinement first leads to a slow inflation. Once the vesicle is close
-to the neck, it quickly deflates in order to fit the constriction. When
-the vesicle is near the neck, simulations show that the water efflux is
-in the front and rear of vesicle while most water influx is in the
-middle. The tension distribution along the vesicle as a function of
-their position in the contracting channel is summarized in
-Figure~\ref{fig:contractingTensions1}, where we observe the
-tension has the largest magnitude when the vesicle is at the neck. 
+where it abruptly decelerates to go through the contraction.
+Figure~\ref{fig:contractingComposite2}(d) shows the tension
+distribution, and the maximum tension is in
+Figure~\ref{fig:contractingComposite2}(e). We see that the vesicle
+tensions is largest when it passes through the neck, and it is
+particularly large when it passes through the first neck since this is
+when the vesicle has the largest area.
+
+%When a semipermeable vesicle goes through a contracting channel (slit)
+%the numerical simulations show that both the driving flow and the
+%membrane permeability have to be sufficiently large for a successful
+%passage through the slit (Figure~\ref{fig:contractingComposite}). As
+%the vesicle goes through the contracting channel, the gradual
+%confinement first leads to a slow inflation. Once the vesicle is close
+%to the neck, it quickly deflates in order to fit the constriction. When
+%the vesicle is near the neck, simulations show that the water efflux is
+%in the front and rear of vesicle while most water influx is in the
+%middle. The tension distribution along the vesicle as a function of
+%their position in the contracting channel is summarized in
+%Figure~\ref{fig:contractingTensions1}, where we observe the
+%tension has the largest magnitude when the vesicle is at the neck. 
 %\begin{figure}[htp]
@@
 length (area) in two (three) dimensions. Results from analysis and
-numerical simulation show that such relaxation of a semipermeable
+numerical simulations show that such relaxation of a semipermeable
 vesicle is characterized by a rescaled time $\beta t$. We further
@@
 cell migration in confined microenvironments~\cite{StrokaJiangChenEtAl2014_Cell, papadopoulos2008aquaporins}, 
-dialysis~\cite{wan2006}, cell desiccation~\cite{vogl2014effect}, cell division~\cite{OdermattMiettinenKangEtAl2020_bioRxiv}, and
-apoptosis~\cite{marchetti1996mitochondrial}.
-%osmotic flow across the membrane.
-While osmotic stress  is more effective and efficient than mechanical stress in contributing to change in cellular volume, our results suggest that the water permeation due to the capillary pressure may be non-negligible over long times or under strong confinement in simple configurations.
-To examine if this is the case in the physiological processes,  currently we are examining the combined effects of osmotic and mechanical stresses on water permeation in the small Peclet number limit, which is relevant to cellular migration in the presence of both confinement and a solute gradient~\cite{StrokaJiangChenEtAl2014_Cell} and has been studied numerically by Jaeger {\em et al.}~\cite{jae-car-med-try1999}.
+dialysis~\cite{wan2006}, cell desiccation~\cite{vogl2014effect}, cell
+division~\cite{OdermattMiettinenKangEtAl2020_bioRxiv}, and
+apoptosis~\cite{marchetti1996mitochondrial}. While osmotic stress  is
+more effective and efficient than mechanical stress in contributing to
+change in cellular volume, our results suggest that the water permeation
+due to the capillary pressure may be non-negligible over long times or
+under strong confinement in simple configurations.  To examine if this
+is the case in the physiological processes, we are currently examining
+the combined effects of osmotic and mechanical stresses on water
+permeation in the small Peclet number limit, which is relevant to
+cellular migration in the presence of both confinement and a solute
+gradient~\cite{StrokaJiangChenEtAl2014_Cell} and has been studied
+numerically by~\citet{jae-car-med-try1999}.
 

### 2021-02-12 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
yny

--- 2021-02-11 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
@@
 In this work we use boundary integral simulations to investigate the
-effects of water permeability on the vesicle hydrodynamics due to
+effects of water permeability on the hydrodynamics of an inextensible membrane under
 a mechanical load, such as the viscous stress from an external flow
-deforming a vesicle membrane in free space or pushing it through a
-confinement. Incorporating the membrane permeability into the framework of Helfrich free energy for an inextensible, elastic membrane as a model for a semipermeable vesicle, we
+deforming an inextensible membrane in free space or pushing it through a
+confinement. Incorporating the membrane permeability into the framework of Helfrich free energy for an inextensible, elastic membrane (a vesicle), we
 illustrate that, in the absence of an osmotic stress gradient, the
@@
 stresses~\cite{HarmanBertrandJoos2017_CJP,
-RazizadehNikfarPaulLiu2020_BJ}. In this work we use modeling and direct
-numerical simulations to show that, over the appropriate time scales or
-under strong confinement, the intrinsic membrane permeability to water
-can give rise to significantly distinct hydrodynamics of a semipermeable
-vesicle.
-
-The lipid bilayer membrane is permeable to water and lipid-soluble
+RazizadehNikfarPaulLiu2020_BJ}.
+
+The cellular membrane is a lipid bilayer membrane that is slightly permeable to water and lipid-soluble
 molecules~\cite{Dick1964_JTB, FettiplaceHaydon1980_PhysRev,
@@
 BhatiaRobinsonDimova2020_SoftMatt}. 
-Without aquaporins or other membrane channels that promote water
+Without aquaporins or other membrane channels to promote water
 permeability, the intrinsic membrane permeability is known to depend on the
@@
 giving rise to enhanced membrane permeability to both water and
-macromolecules. Consequently, as long as the lipid bilayer membrane
+macromolecules such as ATP. Consequently, as long as the lipid bilayer membrane
 remains intact (no poration or rupture), the total amount of water inside the membrane 
@@
 %%The response of a cell to an osmotic gradient is inevitably both mechanical (tension redistribution and shape change) and chemical (water flux across the membrane).
-Under what condition is this a good assumption? Do liposomes conserve
-volume under flow over a long time (hours)? What is the dynamic consequence when water
-influx/efflux affects the membrane hydrodynamics? To answer these
-questions, we investigate the balance between hydrodynamics stresses,
-tension, and elastic stress of a semipermeable membrane under various
-flowing conditions and confinement (Figure~\ref{fig:sketch}).
+
 %Specifically our numerical simulations yield the quantification of the
@@
 
-Vesicles 
-%(self-enclosed lipid bilayer membranes) 
+Vesicles are self-enclosed lipid bilayer membranes (often without transmembrane proteins), and they 
 have been used as a
@@
 %BhatiaChrist2020_SoftMatt}, an 
-These results illustrate that the permeating water
+In most modeling works of vesicle hydrodynamics in free space, the permeating water flow due to a jump in hydrodynamic pressure is neglected (eg, see \citet{vogl2014effect}).
+Recent results illustrate that the permeating water
 flow is inevitably coupled with the mechanical pressure jump across the
 membrane~\cite{yao-mor2017}, which could become comparable to osmotic
-stress when the membrane deformation is large~\cite{LiMoriSun2015_PRL,
+stress when the membrane deformation is large under confinement~\cite{LiMoriSun2015_PRL,
 yao-mor2017}. 
+%
+Motivated by these results we extend the Helfrich free energy for an inextensilbe elastic vesicle membrane to incorporate membrane permeability 
+for the viscous solvent (water) to study the hydrodynamics of such semipermeable membrane.
+
+In this work we use modeling and direct
+numerical simulations to show that, over the appropriate time scales or
+under strong confinement, the intrinsic membrane permeability to water
+can give rise to significantly distinct hydrodynamics of a semipermeable
+vesicle. 
 %
@@
 hours. It is also difficult to quantify the vesicle surface-to-volume
-ratio accurately~\cite{MinetttiCallensCoupier2008_AppliedOptics}. Using
-numerical simulations described in \S~\ref{sec:formulation} and
+ratio accurately~\cite{MinetttiCallensCoupier2008_AppliedOptics}. 
+Using our model and integral simulations, we aim to address the following questions:
+%
+Under what flowing conditions can we assume that vesicle conserves its water content?
+Do liposomes conserve
+volume under flow over a long time (hours)? What is the dynamic consequence when water
+influx/efflux affects the membrane hydrodynamics?
+
+To answer these
+questions, we focus on the balance between hydrodynamics stresses,
+tension, and elastic stress of a semipermeable membrane under various
+flowing conditions and confinement (Figure~\ref{fig:sketch}).
+%
+Using numerical simulations described in \S~\ref{sec:formulation} and
 \S~\ref{sec:numerics} we can quantify the effects of water permeability
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Hydrodynamics of a semipermeable vesicle in free space\label{sec:free_space}}
+\section{Hydrodynamics of a semipermeable inextensible membrane in free space\label{sec:free_space}}
 To highlight the effects of membrane permeability to water, we consider
-a single semipermeable vesicle, with (dimensionless) permeability
+a single semipermeable inextensible membrane, with (dimensionless) permeability
 coefficient $\beta>0$, in familiar configurations: In free space we
-place a semipermeable vesicle in a quiescent flow, a planar shear flow,
-and a Poiseuille flow. For each example, we fix the vesicle length and
+place a semipermeable inextensible membrane in a quiescent flow, a planar shear flow,
+and a Poiseuille flow. For each example, we fix the membrane length and
 examine the enclosed water content as a dynamic consequence of water
-flow, vesicle shape deformation, and distribution of membrane tension.
+flow, membrane shape deformation, and distribution of membrane tension.
 %
 Under these flows, our simulations show that the steady state of an
-impermeable vesicle is different from that of a semipermeable vesicle,
+impermeable vesicle is different from that of a semipermeable inextensible membrane,
 which depends only on the strength of the external flow and is
@@
 simulations of a semipermeable vesicle under these flows in open
-geometry show that water permeability may lead to different vesicle
+geometry show that water permeability may lead to different membrane
 hydrodynamics only after a duration of $\sim 1$ day.
@@
 \end{figure*}
-In the absence of a background flow, a semipermeable vesicle in free
-space can be quantified in terms of its area dynamics and its transition
-to the equilibrium shape. Our analysis in \S~\ref{subsec:area_dynamics} shows
-that a semipermeable vesicle relaxes to a circle at a rate that is
-proportional to $\beta$, and the steady state tension is $\Lambda =
-2\pi^2/L^2$. Our analysis further shows that the time for a
-semipermeable vesicle to deviate from its initial reduced area and to
-reach its steady state is proportional to $\beta^{-1}$. For this reason,
+The analysis in \S~\ref{subsec:area_dynamics} shows
+that a semipermeable inextensible membrane relaxes to a circle at a rate that is
+proportional to $\beta$, regardless of the initial membrane shape (for a fixed length):
+In the absence of a background flow, a semipermeable inextensible membrane in free
+space is quantified in terms of its area dynamics and transition
+to the equilibrium shape, which is a circular membrane with a uniform 
+membrane tension $\Lambda = 2\pi^2/L^2$.
+This is in stark contrast with the impermeable vesicle relaxing to equilibrium that depends on the vesicle reduced area,  which remains constant for $\beta=0$.
+%
+Our analysis further shows that the rate of change in area enclosed inside a
+semipermeable inextensible membrane is proportional to $\beta$. For this reason,
 our numerical results are reported in terms of the scaled time $\beta t$.
@@
 impermeable vesicle phase diagram for semipermeable vesicles with $\beta
-= 10^{-3}$. The equilibrium vesicle shape for different $U$ and initial
+= 10^{-3}$. Smaller value of $\beta$ has been used for some parameters but the time 
+it takes to reach equilibrium (for some this involves a transient tank-treading
+motion along the membrane to gradually slow down in the presence of small $\beta$) is too long in these simulations.
+
+The equilibrium membrane shape for different $U$ and initial
 reduced area is summarized in Figure~\ref{fig:parabolicComposite}(a),
@@
 
-As observed for the linear shear flow, our simulations with $0<\beta\le 10^{-2}$ 
-%in the range  $10^{-4}\le \beta\le 10^{-2}$ 
-\todo[inline]{I don't understand this range of $\beta$ values?}
-show that the equilibrium reduced area of a semipermeable vesicle in a
-Poiseuille flow is independent of both the initial reduced area and
-$\beta$. Instead we find that larger maximum flow velocity $U$ results
+As observed for the linear shear flow, our simulations 
+%with $0<\beta\le 10^{-2}$ 
+%%in the range  $10^{-4}\le \beta\le 10^{-2}$ 
+%\todo[inline]{I don't understand this range of $\beta$ values?}
+show that the equilibrium reduced area of a semipermeable inextensible membrane in a
+Poiseuille flow is independent of the initial reduced area.
+%and $\beta$. 
+ Instead we find that larger maximum flow velocity $U$ results
 in smaller equilibrium reduced area

### 2021-02-13 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
yny

@@
 converting the apparent permeability of a 
-bilayer~\cite{OlbrichRawiczNeedhamEtAl2000_BJ} to the hydraulic
+membrane~\cite{OlbrichRawiczNeedhamEtAl2000_BJ} to the hydraulic
 conductivity $k_w$ using the conversion
 in~\citet{FettiplaceHaydon1980_PhysRev}, and then scaling $k_w$ to $R_0/\mu$. We found that for most lipid bilayer membranes, $10^{-14}\le
-k_w\le 10^{-12}$ m$^2$s/kg, thus the range of $\beta$ corresponding to the native membrane permeability for water is $10^{-11}\le
-\beta\le 10^{-9}$. 
-%
-In our simulations the equilibrium shape of a semipermeable membrane in open space is found to be independent of $\beta$ for $10^{-5}\le\beta\le10^{-2}$.
-Within this range we find that the permeability $\beta$ only affects the time it takes to reach the equilibrium membrane shape, which is determined by the background flow
+k_w\le 10^{-12}$ m$^2$s/kg, thus the range of $\beta$ corresponding to the native water permeability of a lipid bilayer membrane (vesicle) is $10^{-11}\le
+\beta\le 10^{-9}$, consistent with the value in \citet{vogl2014effect}. In the following we use a wider range of $\beta$ to elucidate the effects of permeating water flow across a
+semipermeable inextensible membrane.
+%
+
+For example, we use $10^{-5}\le\beta\le10^{-2}$
+in our simulations of a semipermeable inextensible membrane in free space under various flowing conditions.
+We found that 
+the equilibrium shape of a semipermeable membrane in free space to be independent of $\beta$.
+Within this range of $\beta$ we find that $\beta$ only affects the time it takes for the membrane to reach the equilibrium shape, which is determined by the background flow
 (such as a quiescent flow, a linear shear flow and its shear rate, and a Poiseuille flow and its maximum velocity.)
-From these results and our analysis of area dynamics, we suspect similar hydrodynamics of a semipermeable inextensible membrane 
-with a smaller $\beta$ ($\beta\ne 0$). 
-On the other hand,  when $\beta\ge 0.1$, we find that the membrane shape swells to maximize the water content inside the membrane, independent of the initial reduced 
-area and the imposed flow in the far field.
-In the simulations we focus on intermediate value of $10^{-5}\le \beta\le 10^{-3}$ to investigate the hydrodynamics of a semipermeable inextensible membrane. 
-%
-Under strong confinement, $10^{-4}\le\beta\le10^{-3}$ is needed in our
-simulations to keep the membrane tension below the threshold value for
-membrane poration $\sim 10^{-3}$ N/m. Such range of $\beta$ may imply
-that the lipid bilayer membrane would be porated under large stress
+From these results and our analysis of area dynamics, we suspect similar hydrodynamics of a semipermeable vesicle
+(with $10^{-11}\le\beta\le 10^{-9}$). 
+%
+When we use $\beta\ge 0.1$, we find that the semipermeable membrane swells to maximize its water content, independent of the initial reduced 
+area and the background flow.
+%
+%In the simulations we focus on intermediate value of $10^{-5}\le \beta\le 10^{-3}$ to investigate the hydrodynamics of a semipermeable inextensible membrane. 
+%
+
+On the other hand,
+under strong confinement,  we find that $10^{-4}\le\beta\le10^{-3}$ is needed in our
+simulations to keep the membrane tension below the threshold value $\sim 10^{-3}$ N/m for
+poration in a lipid bilayer membrane. Such range of $\beta$ may imply
+that a vesicle would be porated under large stress
 caused by confinement.
 
-\subsection{Dynamics of Vesicle Area\label{subsec:area_dynamics}}
-In the absence of an imposed flow, the steady state vesicle shape and a
-differential equation for the area of the vesicle can be derived. We
-start by following the analysis of Veerapaneni {\em et
-al.}~\cite{vee-raj-bir-pur2009} by computing the steady state shape of a
-semipermeable vesicle in a quiescent flow. The steady state shape is a
-stationary point of the Lagrangian
+\subsection{Equilibrium and Areal Dynamics in a Quiescent Flow\label{subsec:area_dynamics}}
+In the absence of an imposed flow, the steady equilibrium shape and a
+differential equation for the area inside the semipermeable inextensible membrane can be derived
+by following the analysis of Veerapaneni {\em et al.}~\cite{vee-raj-bir-pur2009} in a quiescent flow $({\bf u}_{\infty} = 0)$.
+%
+%by computing the steady state shape of a
+%semipermeable vesicle in a quiescent flow. 
+%
+The steady state shape is a
+fixed point of the Lagrangian
 \begin{align}
@@
   \caption{\label{fig:relaxationComposite} (a) Snapshots of four
-  semipermeable vesicles with $\beta = 10^{-8}$ submerged in a fluid
+  semipermeable inextensible membranes with $\beta = 10^{-8}$ submerged in a fluid
   with no background flow. Time goes from left to right. The red regions
@@
 In Figure~\ref{fig:relaxationComposite}, we examine the relaxation
-dynamics of a semipermeable vesicle with four initial shapes and reduced
-areas as labeled. The vesicles on the left are color-coded by the water
-permeation flux: red denotes an influx into the vesicle, and blue
-denotes an efflux out of the vesicle. First we observe that the initial
-vesicle shape determines the direction of water flux. For the vesicle
-with an initial reduced area $\alpha(0)=0.12$ (bottom row) the vesicle
+dynamics with four initial shapes and reduced
+areas as labeled. The membrane shapes on the left are color-coded by the water
+permeation flux: red denotes an influx into the membrane, and blue
+denotes an efflux out of the membrane. First we observe that the initial
+membrane shape determines the direction of water flux. For the case
+with an initial reduced area $\alpha(0)=0.12$ (bottom row) the membrane
 deflates (blue regions) first due to the high interior capillary
@@
 %
-Over time (about four weeks) all vesicles inflate and as expected, each
-vesicle eventually reaches a circular shape with reduced area
+Over time (about four weeks) all cases inflate and as expected, each
+case eventually reaches a circular shape with reduced area
 $\alpha=1$. 
@@
 $\beta\ll 1$, the permeability velocity is much smaller than the force
-balance velocity at early times, and the semipermeable vesicle dynamics
+balance velocity at early times, and the dynamics of a semipermeable inextensible membrane
 resemble those of an impermeable vesicle. As the force balance velocity
@@
   \caption{\label{fig:relaxationTensions} The distribution of membrane
-  tension of a relaxing vesicle that corresponds to
+  tension corresponding to the relaxation dynamics in 
   Figure~\ref{fig:relaxationComposite}.}
 \end{figure*}
-Figure~\ref{fig:relaxationTensions} shows the membrane tension
-distribution along the relaxing vesicles in
+Figure~\ref{fig:relaxationTensions} shows the tension
+distribution along the relaxing membranes in
 Figure~\ref{fig:relaxationComposite}. The membrane tension (color bars)
-is in N/m. As the semipermeable vesicle relaxes, the membrane tension
+is in N/m. As the semipermeable inextensible membrane relaxes, the membrane tension
 reduces in magnitude and becomes more evenly distributed along the
-membrane. In the top row ($\alpha(0)=0.95$) the vesicle nearly relaxes
+membrane. In the top row ($\alpha(0)=0.95$) the membrane nearly relaxes
 to a circle on the right, and the membrane tension is uniform and equal
@@
   \caption{\label{fig:shearComposite} (a) The reduced area of a
-  semipermeable vesicle with $\beta = 10^{-3}$ initialized with four
+  semipermeable inextensible membrane with $\beta = 10^{-3}$ initialized with four
   different reduced areas in a shear flow with two different flow rates.
-  (b) The equilibrium shape of a vesicle with varying flow rates and
+  (b) The equilibrium membrane shape with varying flow rates and
   membrane permeability. The red regions correspond to influx and the
-  blue regions correspond to efflux The boxed vesicles correspond to the
+  blue regions correspond to efflux The boxed membranes correspond to the
   simulation results in part (a).}
@@
 
-We consider a semipermeable vesicle in a planar shear flow,
+We consider a semipermeable inextensible membrane in a planar shear flow,
 characterized by the elastic capillary number $Ca_\mathrm{E}=\chi\tau$ where $\tau$ is the characteristic time scale from balancing the viscous stress with the elastic stress
@@
 tumbles~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. Focusing on
-semipermeable vesicles with no viscosity contrast, we find that a
-semipermeable vesicle tilts to an inclination angle and undergoes
+a semipermeable inextensible membrane with no viscosity contrast, 
+we find that the membrane tilts to an inclination angle and undergoes
 tank-treading dynamics, similar to the case of an impermeable vesicle.
@@
 In Figure~\ref{fig:shearComposite}(a), using four initial reduced areas
-and two flow rates, we plot the reduced area of a semipermeable vesicle
+and two flow rates, we plot the reduced area of a semipermeable inextensible membrane
 with $\beta = 10^{-3}$. As observed in a quiescent flow, the final
-vesicle shape is independent of the initial reduced area. However, it
+membrane shape is independent of the initial reduced area. However, it
 does depend on the flow rate. We also observe that the amount of water
@@
 For a range of dimensionless permeability coefficient $\beta>0$ and
-capillary number $Ca_\mathrm{E}$, a semipermeable vesicle reaches an
+capillary number $Ca_\mathrm{E}$, a semipermeable inextensible membrane reaches an
 equilibrium shape as in Figure~\ref{fig:shearComposite}(a). Since the
 equilibrium shape depends on $Ca_\mathrm{E}$ and is independent of the
-initial reduced area, we initialize the vesicle with reduced area
+initial reduced area, we initialize the membrane with reduced area
 $\alpha = 0.65$ for all simulations in
 Figure~\ref{fig:shearComposite}(b), where we summarize the equilibrium
-vesicle shape and its reduced area. We see that the capillary number
-(flow rate) significantly affects the final vesicle shape, but the
+membrane shape and its reduced area. We see that the capillary number
+(flow rate) significantly affects the final membrane shape, but the
 permeability coefficient has a very minor effect on the equilibrium
 shape for $10^{-4}\le\beta\le 10^{-2}$. Instead, $\beta$ sets the time
-required for a vesicle to reach its steady state configuration which is
+required for a membrane to reach its steady state configuration which is
 proportional to $\beta^{-1}$, as we saw in the analysis for the
@@
 %permeability $\beta$. 
-The tension distribution along the equilibrium vesicle at
+The tension distribution along the equilibrium membrane shape at
 $\beta=10^{-4}$ is shown in Figure~\ref{fig:shearTensions}, where the
@@
   \caption{\label{fig:shearTensions} The tension distribution along a
-  vesicle in a linear shear flow. The semipermeability constant is
+  semipermeable inextensible membrane in a linear shear flow. The semipermeability constant is
   $\beta = 10^{-4}$ for all these cases, and the elastic capillary
@@
 \subsection{Poiseuille Flow}
-We consider a semipermeable vesicle in the Poiseuille flow $\uu =
+We consider a semipermeable inextensible membrane in the Poiseuille flow $\uu =
 U(1-(y/W)^2,0)$, where $U$ is the maximum velocity at $y=0$. The
@@
   \caption{\label{fig:parabolicComposite} (a) The equilibrium shape of
-  a semipermeable vesicle submerged in a Poiseuille flow with varying
+  a semipermeable inextensible membrane submerged in a Poiseuille flow with varying
   initial reduced areas and flow rates. The red regions correspond to
@@
   steady state shapes are superimposed. (c) The reduced area of the
-  slipper formed with the flow rate of $800 \; \mu$m/s. (d) The vesicle
+  slipper formed with the flow rate of $800 \; \mu$m/s. (d) The membrane
   shape shown with the background imposed flow. The channel width is
   12.5 times larger than the vesicle radius. The corresponding reduced
-  area of each vesicle is indicated by the marks in plot (c).}
+  area of each membrane shape is indicated by the marks in plot (c).}
 \end{figure*}
@@
   \caption{\label{fig:parabolicTensions} The equilibrium tension
-  distribution of a semipermeable vesicle with $\beta=10^{-3}$ in a
+  distribution of a semipermeable inextensible membrane with $\beta=10^{-3}$ in a
   parabolic flow (Figure~\ref{fig:parabolicComposite}). The flow
@@
 
-\section{A semipermeable vesicle under strong confinement\label{sec:confinement}}
-Here we consider a semipermeable vesicle under strong confinement: a
+\section{Hydrodynamics of A semipermeable inextensible membrane under strong confinement\label{sec:confinement}}
+Here we consider a semipermeable inextensible membrane under strong confinement: a
 long closely-fit channel and a contracting channel. In a narrow
-microfluidic channel, a large pressure jump is often needed to push the
+microfluidic channel, a large pressure jump is often used to push the
 vesicle through a closely-fit channel~\cite{abk-fai-sto2006}. Our
 simulations show that such a configuration can lead to an amplification
-of water permeation at a time scale shorter than a few minutes. In
+of water permeation at a fast time scale of the order of mini seconds. In
 addition, we find that a large value of $\beta$ is needed to keep the
@@
 lipid bilayer membrane is porated under strong confinement, and our
-model vesicle is for a porated vesicle within the Helfrich free energy
-framework. As in the previous examples, we fix the vesicle length and
+model inextensible membrane is for a porated vesicle within the Helfrich free energy
+framework. As in the previous examples, we fix the membrane length and
 examine the enclosed water content as a dynamic consequence of water
-flow, vesicle shape deformation, and membrane tension distribution.
+flow, membrane shape deformation, and membrane tension distribution.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Semipermeable Vesicle in a Closely-fit Channel (Stenosis)}
+\subsection{A Semipermeable Inextensible Membrane in a Closely-fit Channel (Stenosis)}
 \begin{figure*}[htp]
@@
   \fi
-  \caption{\label{fig:stenosisComposite} (a) A semipermeable vesicle
+  \caption{\label{fig:stenosisComposite} (a) A semipermeable inextensible membrane
   passing through a closely-fit channel similar to the experimental
-  device in~\citet{abk-fai-sto2006}. (b) A semipermeable vesicle passing
+  device in~\citet{abk-fai-sto2006}. (b) A semipermeable inextensible membrane passing
   through a (four-times) longer closely-fit channel than (a). In (a) and
@@
   and (b). (e) The excess pressure of an impermeable and semipermeable
-  vesicle in the short geometry in (a). (f) The reduced area of the
-  semipermeable vesicles in the geometries in (a) and (b) as a function
-  of the vesicles' center of mass. In (e) and (f), the x-axis is scaled
+  inextensible membrane in the short geometry in (a). (f) The reduced area in the geometries in (a) and (b) as a function
+  of the membranes' center of mass. In (e) and (f), the x-axis is scaled
   by $1/L$ where $L$ is half the length of the constriction. (g) The
-  reduced area of the semipermeable vesicles in the geometries in (a)
+  reduced area in the geometries in (a)
   and (b) as a function of time. The time axis is scaled by $1/t_R$
@@
   dashed lines correspond to the times that the vesicle enters and exits
-  the constriction. The colored vesicles show the tension distribution
-  in N/m of the circled vesicles. Throughout the entire simulation,
-  these vesicle configurations have the largest tension.}
+  the constriction. The colored membranes show the tension distribution
+  in N/m of the circled cases. Throughout the entire simulation,
+  these membranes have the largest tension.}
 \end{figure*}
@@
 the maximum flow velocity to $U_{\max} = 1000 \;\mu$m/s at the inlet and
-outlet so that the residency time of the vesicle in the stenosis channel
+outlet so that the residency time of the membrane in the stenosis channel
 is $t_R \approx 25$ ms which agrees with the experimental
@@
 
-We consider both an impermeable and semipermeable vesicle with initial
+We consider both an impermeable vesicle and semipermeable inextensible membrane with initial
 reduced area $\alpha = 0.65$ passing through a long narrow channel and
@@
 Our simulations show that less excess pressure is needed to drive a
-semipermeable vesicle through the closely-fit channel. Once in the
+semipermeable inextensible membrane through the closely-fit channel. Once in the
 channel, the vesicle takes a bullet shape with maximum tension in the
@@
 Figures~\ref{fig:stenosisComposite}(f)
-and~\ref{fig:stenosisComposite}(g) show that the vesicle deflates from
+and~\ref{fig:stenosisComposite}(g) show that the semipermeable inextensible membrane deflates from
 the beginning due to the high flow velocity, consistent with the results
-for a vesicle in a Poiseuille flow in open space. As the vesicle enters
+for a vesicle in a Poiseuille flow in open space. As the membrane enters
 the stenosis channel, it continues to deflate in the front even though
 we observe influx (red segment) at various rear locations in the
-membrane. Overall, the vesicle loses about 6.1\% of its initial total
+membrane. Overall, the membrane loses about 6.1\% of its initial total
 water at a constant rate as shown in
@@
 and~\ref{fig:stenosisComposite}(g) (blue curves). Thus we expect that a
-larger amount of deflation is possible if the vesicle is inside a longer
+larger amount of deflation is possible if the inextensible membrane is inside a longer
 stenosis: we consider a vesicle passing through a channel of triple the
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Semipermeable Vesicle in a Contracting Geometry} 
+\subsection{A Semipermeable Inextensible Membrane in a Contracting Geometry} 
 \begin{figure}[htp]
@@
   through the contraction depends on the permeability $\beta$. (d--f)
-  The ability for a semipermeable vesicle to pass through the
+  The ability for a semipermeable inextensible membrane to pass through the
   contraction depends on the flow rate. (g--i) The tension distribution
@@
 
-Squeezing a cell or an elastic vesicle through a slit in microfluidics
+Squeezing a cell or a vesicle through a slit in microfluidics
 has gained popularity for its application in stress-induced release of
@@
 survive~\cite{wu2015critical,LuPeng2019_PoF}. Here we investigate the
-role of membrane permeability to water when a semipermeable vesicle is
+role of membrane permeability to water when a semipermeable inextensible membrane is
 squeezed through a contracting microfluidic channel similar
@@
 Poiseuille flow is imposed at the inlet and outlet with a constant
-maximum flow rate of $U_{\max}$. We initialize a semipermeable vesicle
+maximum flow rate of $U_{\max}$. We initialize a semipermeable inextensible membrane
 with $\alpha = 0.65$ that spans $10\; \mu$m of the total channel width
 and investigate the effects of the membrane permeability to water and
-the maximum flow velocity on whether a vesicle can successfully pass
+the maximum flow velocity on whether a membrane can successfully pass
 through the slit. We color the vesicle according to the sign of its
@@
 In Figures~\ref{fig:contractingComposite}(a)
-and~\ref{fig:contractingComposite}(b), we plot snapshots of vesicles
+and~\ref{fig:contractingComposite}(b), we plot snapshots of membranes
 with different permeability $\beta$.
 Figure~\ref{fig:contractingComposite}(c) shows the corresponding reduced
-area as a function of the vesicle's location. We observe that if the
+area as a function of the membrane's location. We observe that if the
 permeability is sufficiently large, the vesicle inflates gradually over
@@
 a fraction of a second. However, if the permeability $\beta$ is too
-low, the vesicle is too large when it reaches the narrowest part of the
+low, the membrane is too large when it reaches the narrowest part of the
 channel, and it is unable to pass. In
 Figures~\ref{fig:contractingComposite}(d)
-and~\ref{fig:contractingComposite}(e), we plot snapshots of vesicles
+and~\ref{fig:contractingComposite}(e), we plot snapshots of membranes
 with different imposed maximum velocities, and
 Figure~\ref{fig:contractingComposite}(f) shows the reduced area as a
-function of the vesicle's location. At low velocities, the vesicle
+function of the membrane's location. At low velocities, the membrane
 inflates similar to the unbounded parabolic flow example, and it is
 unable to pass through the contraction. However, higher flow rates
-result in additional deflation and the vesicle passes through the
-contraction. When the vesicle is near the neck, simulations show that
-the water efflux is in the front and rear of vesicle while most water
-influx is in the middle. The tension distribution along the vesicle as
+result in additional deflation and the membrane passes through the
+contraction. When the membrane is near the neck, simulations show that
+the water efflux is in the front and rear of membrane while most water
+influx is in the middle. The tension distribution along the membrane as
 a function of their position in the contracting channel is summarized in
 Figure~\ref{fig:contractingComposite} (g)--(l), where we observe the
-tension has the largest magnitude when the vesicle is at the neck.
+tension has the largest magnitude when the membrane is at the neck.
 
@@
   \fi
-  \caption{\label{fig:contractingComposite2} Vesicle reduced area and
-  velocity vs.~time. The permeability coefficient is $\beta = 10^{-3}$
-  and the maximum velocity is $18\;\mu$m/s. (a) A semipermeable vesicle
+  \caption{\label{fig:contractingComposite2} Reduced area and
+  velocity of a semipermeable inextensible membrane vs.~time. The permeability coefficient is $\beta = 10^{-3}$
+  and the maximum velocity is $18\;\mu$m/s. (a) A semipermeable inextensible membrane
   passing through six periods of the contracting geometry. (b) The
   reduced area with the marks representing shapes in (a). (c) The
-  vesicle velocity with the marks representing shapes in (a). In (b) and
-  (c), the lower x-axis is the x-coordinate of the center of mass, and
-  the upper x-axis is time. (d) The vesicle tension in N/m. (e) The
-  maximum vesicle tension.}
+  center-of-mass velocity with the marks representing shapes in (a). In (b) and
+  (c), the lower $x$-axis is the x-coordinate of the center of mass, and
+  the upper $x$-axis is time. (d) The membrane tension in N/m. (e) The
+  maximum membrane tension.}
 %  The colored vesicles show the tension
@@
 \end{figure}
-To understand the effects of water permeability on a vesicle that
+To understand the effects of water permeability on a semipermeable inextensible membrane that
 repeatedly passes through micro-capillary vessels or sub-micron slits,
 we construct a contracting geometry
-(Figure~\ref{fig:contractingComposite2}) to simulate a vesicle passing
+(Figure~\ref{fig:contractingComposite2}) to simulate a membrane passing
 through the contracting geometry six times. In
-Figure~\ref{fig:contractingComposite2}(b), we show that the vesicle
+Figure~\ref{fig:contractingComposite2}(b), we show that the membrane
 deflates each time it passes through the contraction followed by a
@@
 of the vesicle is almost 50\%. In
-Figure~\ref{fig:contractingComposite2}(c), we show the vesicle velocity
-as a function of the vesicle's center of mass. As the vesicle passes
+Figure~\ref{fig:contractingComposite2}(c), we show the membrane center-of-mass velocity
+as a function of the membrane position. As the membrane passes
 through the contraction, it first accelerates until it reaches the neck
@@
 distribution, and the maximum tension is in
-Figure~\ref{fig:contractingComposite2}(e). We see that the vesicle
+Figure~\ref{fig:contractingComposite2}(e). We see that the membrane
 tensions is largest when it passes through the neck, and it is
 particularly large when it passes through the first neck since this is
-when the vesicle has the largest area.
+when the membrane has the largest area.
 

### 2021-02-14 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
small changes
yny

@@
 In this work we investigate the effects of membrane permeability to
-water on vesicle hydrodynamics. Without any external flow or
-confinement, our analysis shows that a semipermeable vesicle always
-inflates to maximize the water content inside the vesicle of a fixed
-length (area) in two (three) dimensions. Results from analysis and
+water on the membrane hydrodynamics. Without any external flow or
+confinement, our analysis shows that a semipermeable inextensible membrane always
+inflates to maximize the water content inside the inextensible membrane (a fixed
+length (area) in two (three) dimensions.) Results from analysis and
 numerical simulations show that such relaxation of a semipermeable
-vesicle is characterized by a rescaled time $\beta t$. We further
+inextensible membrane  is characterized by a rescaled time $\beta t$. We further
 illustrate that the relaxation process consists of at least two phases:
 The first phase is dominated by the balance between membrane traction
-and viscous stress at early times (up to five minutes), when the vesicle
+and viscous stress at early times (up to five minutes), when the inextensible membrane
 behaves like an impermeable membrane. The second phase sets in after a
-few hours, when water influx begins to dominate and inflate the vesicle.
-Over a time scale of more than four weeks, a semipermeable vesicle is
+few hours, when water influx begins to dominate and inflate the semipermeable membrane.
+Over a time scale of more than four weeks, a semipermeable membrane is
 fully inflated, independent of its initial surface-to-volume ratio.
@@
 Under strong confinement we show that water permeation can be amplified
-on a time scale of a few seconds as a vesicle is squeezed through a
+on a time scale of a few seconds as a semipermeable inextensible membrane is squeezed through a
 closely-fit channel and a contracting channel. As a semipermeable
-vesicle goes through a long closely-fit channel, we observe that the
-vesicle loses water at a constant rate, and the longer the channel the
+inextensible membrane goes through a long closely-fit channel, we observe lose of water at a constant rate, and the longer the channel the
 more the loss of water. In the case of a contracting channel, we find

### 2021-02-14 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
rewrote time stepping and few changes

@@
 Using numerical simulations described in \S~\ref{sec:formulation} and
-\S~\ref{sec:numerics} we can quantify the effects of water permeability
-on the hydrodynamics of a vesicle under mechanical stresses.  Without an
+\S~\ref{sec:numerics} we quantify the effects of water permeability on
+the hydrodynamics of a vesicle under mechanical stresses.  Without an
 osmotic gradient, we first show that a freely suspended semipermeable
@@
 \subsection{Discretization in Time}
-To develop a second-order, non-stiff, adaptive time stepping method, we
-first introduce the notation
-%\begin{alignat}{3}
-%  &\BB\ff = -\frac{d^4}{ds^4} \ff,  \qquad
-%  &&\TT\sigma = (\sigma \xx_s)_s, \\
-%  &\DD\ff = \xx_s \cdot \ff_s, 
-%  &&P\ff = (\ff \cdot \nn) \nn,
-%\end{alignat}
+We apply a second-order spectral deferred correction (SDC) method that was
+thoroughly tested in previous work~\cite{qua-bir2016}. To control error
+over long time horizons, we use the error in length to adaptively adjust
+the time step size. SDC requires two steps of a first-order time
+stepping method. To allow for large time step sizes, terms involving
+high-order derivatives are discretized semi-implicitly. We start by
+defining
 \begin{align}
@@
 discretizes the stiff terms due to high-order derivatives
-implicitly~\cite{vee-gue-zor-bir2009, qua-bir2014}. In particular, we
-use the first-order semi-implicit method
-%We note that the integral and differential operators, which all depend
-%on the vesicle shape, are non-linear with respect to the vesicle shape.
-%We construct a time stepping scheme by letting $\BB^N$ be the bending
-%operator due to the vesicle configuration at time $t^N$, and use
-%similar notation for the other operators. Then, a first-order
-%semi-implicit time stepping method of Equation~\eqref{eqn:vesVelocity}
-%is
+implicitly~\cite{vee-gue-zor-bir2009, qua-bir2014}. In particular, the
+first-order semi-implicit method that is applied iteratively with SDC is
 \begin{alignat}{3}  
@@
 and this linear system is solved with matrix-free GMRES.
-
-To achieve second-order accuracy over long time horizons, we modify an
-adaptive spectral deferred correction time stepping
-method~\cite{qua-bir2016}. Since the area of the vesicle is not
-conserved, we only use the length of the vesicle to estimate the error
-which determines if a time step is accepted or not and determines the
-subsequent time step size.
 
@@
 \section{Hydrodynamics of A semipermeable inextensible membrane under strong confinement\label{sec:confinement}}
-Here we consider a semipermeable inextensible membrane under strong confinement: a
-long closely-fit channel and a contracting channel. In a narrow
-microfluidic channel, a large pressure jump is often used to push the
-vesicle through a closely-fit channel~\cite{abk-fai-sto2006}. Our
+Here we consider a semipermeable inextensible membrane under strong
+confinement: a long closely-fit channel and a contracting channel. In a
+narrow microfluidic channel, a large pressure jump is often used to push
+the vesicle through a closely-fit channel~\cite{abk-fai-sto2006}. Our
 simulations show that such a configuration can lead to an amplification
-of water permeation at a fast time scale of the order of mini seconds. In
-addition, we find that a large value of $\beta$ is needed to keep the
-membrane tension below the threshold value for membrane poration. Such
-high permeability for water may be regarded as an indication that the
-lipid bilayer membrane is porated under strong confinement, and our
-model inextensible membrane is for a porated vesicle within the Helfrich free energy
-framework. As in the previous examples, we fix the membrane length and
-examine the enclosed water content as a dynamic consequence of water
-flow, membrane shape deformation, and membrane tension distribution.
+of water permeation at a fast time scale of the order of
+\todo[inline]{mini seconds?} mini seconds.  In addition, we find that a
+large value of $\beta$ is needed to keep the membrane tension below the
+threshold value for membrane poration. Such high permeability for water
+may be regarded as an indication that the lipid bilayer membrane is
+porated under strong confinement, and our model inextensible membrane is
+for a porated vesicle within the Helfrich free energy framework. As in
+the previous examples, we fix the membrane length and examine the
+enclosed water content as a dynamic consequence of water flow, membrane
+shape deformation, and membrane tension distribution.
 

### 2021-02-15 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
went through bounded examples

@@
 
-As observed for the linear shear flow, our simulations 
-%with $0<\beta\le 10^{-2}$ 
-%%in the range  $10^{-4}\le \beta\le 10^{-2}$ 
-%\todo[inline]{I don't understand this range of $\beta$ values?}
-show that the equilibrium reduced area of a semipermeable inextensible membrane in a
-Poiseuille flow is independent of the initial reduced area.
-%and $\beta$. 
- Instead we find that larger maximum flow velocity $U$ results
-in smaller equilibrium reduced area
-(Figure~\ref{fig:parabolicComposite}(a)). At the smallest velocity $U=
-200\; \mu$m/s, the steady state reduced area is large, and the
-equilibrium vesicle shape is an axisymmetric bullet. The equilibrium
-reduced area decreases with increasing $U$, and the nonlinear flow
-profile gives rise to an asymmetric tank-treading slipper for $U\ge 400$
-$\mu m/s$. We observe that the membrane permeability to water
-drastically alters the equilibrium vesicle shape and position relative
-to the Poiseuille flow: At $\beta=10^{-3}$ the equilibrium vesicle
-depends only on the maximum velocity $U$ of the nonlinear shear flow.
-The higher $U$ the smaller the equilibrium reduced area and the farther
-away the vesicle is relative to the flow center at $y=0$.
+As observed for the linear shear flow, our simulations show that the
+equilibrium reduced area of a semipermeable inextensible membrane in a
+Poiseuille flow is independent of the initial reduced area. Instead we
+find that larger maximum flow velocity $U$ results in smaller
+equilibrium reduced area (Figure~\ref{fig:parabolicComposite}(a)). At
+the smallest velocity $U= 200\; \mu$m/s, the steady state reduced area
+is large, and the equilibrium vesicle shape is an axisymmetric bullet.
+The equilibrium reduced area decreases with increasing $U$, and the
+nonlinear flow profile gives rise to an asymmetric tank-treading slipper
+for $U\ge 400$ $\mu m/s$. We observe that the membrane permeability to
+water drastically alters the equilibrium vesicle shape and position
+relative to the Poiseuille flow: At $\beta=10^{-3}$ the equilibrium
+vesicle depends only on the maximum velocity $U$ of the nonlinear shear
+flow. The higher $U$ the smaller the equilibrium reduced area and the
+farther away the vesicle is relative to the flow center at $y=0$.
 
@@
 simulations show that such a configuration can lead to an amplification
-of water permeation at a fast time scale of the order of
-\todo[inline]{mini seconds?} mini seconds.  In addition, we find that a
-large value of $\beta$ is needed to keep the membrane tension below the
-threshold value for membrane poration. Such high permeability for water
-may be regarded as an indication that the lipid bilayer membrane is
-porated under strong confinement, and our model inextensible membrane is
-for a porated vesicle within the Helfrich free energy framework. As in
-the previous examples, we fix the membrane length and examine the
-enclosed water content as a dynamic consequence of water flow, membrane
-shape deformation, and membrane tension distribution.
+of water permeation at a fast time scale of the order of milliseconds.
+In addition, we find that a large value of $\beta$ is needed to keep the
+membrane tension below the threshold value for membrane poration. Such
+high permeability for water may be regarded as an indication that the
+lipid bilayer membrane is porated under strong confinement, and our
+inextensible membrane model is for a porated vesicle within the Helfrich
+free energy framework. As in the previous examples, we fix the membrane
+length and examine the enclosed water content as a dynamic consequence
+of water flow, membrane shape deformation, and membrane tension
+distribution.
 
@@
   \fi
-  \caption{\label{fig:stenosisComposite} (a) A semipermeable inextensible membrane
-  passing through a closely-fit channel similar to the experimental
-  device in~\citet{abk-fai-sto2006}. (b) A semipermeable inextensible membrane passing
-  through a (four-times) longer closely-fit channel than (a). In (a) and
-  (b), red regions correspond to influx and blue regions correspond to
-  efflux. (c) and (d) The tension in N/m of the vesicle shapes in (a)
-  and (b). (e) The excess pressure of an impermeable and semipermeable
-  inextensible membrane in the short geometry in (a). (f) The reduced area in the geometries in (a) and (b) as a function
-  of the membranes' center of mass. In (e) and (f), the x-axis is scaled
-  by $1/L$ where $L$ is half the length of the constriction. (g) The
-  reduced area in the geometries in (a)
-  and (b) as a function of time. The time axis is scaled by $1/t_R$
-  where $t_R$ is the residency time. In (e) and (f), the dashed lines
-  correspond to the locations of the inlet and outlet. In (g), the
+  \caption{\label{fig:stenosisComposite} (a) A semipermeable
+  inextensible membrane passing through a closely-fit channel similar to
+  the experimental device in~\citet{abk-fai-sto2006}. (b) A
+  semipermeable inextensible membrane passing through a (three-times)
+  longer closely-fit channel than (a). In (a) and (b), red regions
+  correspond to influx and blue regions correspond to efflux. (c) and
+  (d) The tension in N/m of the vesicle shapes in (a) and (b). (e) The
+  excess pressure of an impermeable and semipermeable inextensible
+  membrane in the short geometry in (a). (f) The reduced area in the
+  geometries in (a) and (b) as a function of the membranes' center of
+  mass. In (e) and (f), the x-axis is scaled by $1/L$ where $L$ is half
+  the length of the constriction. (g) The reduced area in the geometries
+  in (a) and (b) as a function of time. The time axis is scaled by
+  $1/t_R$ where $t_R$ is the residency time. In (e) and (f), the dashed
+  lines correspond to the locations of the inlet and outlet. In (g), the
   dashed lines correspond to the times that the vesicle enters and exits
-  the constriction. The colored membranes show the tension distribution
-  in N/m of the circled cases. Throughout the entire simulation,
-  these membranes have the largest tension.}
+  the constriction.}
 \end{figure*}
@@
 the maximum flow velocity to $U_{\max} = 1000 \;\mu$m/s at the inlet and
-outlet so that the residency time of the membrane in the stenosis channel
-is $t_R \approx 25$ ms which agrees with the experimental
+outlet so that the residency time of the membrane in the stenosis
+channel is $t_R \approx 25$ ms which agrees with the experimental
 results~\cite{abk-fai-sto2006}. When the red blood cell enters the
@@
 
-We consider both an impermeable vesicle and semipermeable inextensible membrane with initial
-reduced area $\alpha = 0.65$ passing through a long narrow channel and
-compute the excess pressure as a function of vesicle position in the
-channel (Figure~\ref{fig:stenosisComposite}(e)). The impermeable case
-agrees with experimental results~\cite{abk-fai-sto2006} (see Figure 3).
-Our simulations show that less excess pressure is needed to drive a
-semipermeable inextensible membrane through the closely-fit channel. Once in the
-channel, the vesicle takes a bullet shape with maximum tension in the
-front and minimum tension in the back
-(Figure~\ref{fig:stenosisComposite}(c)), consistent with earlier
-results~\cite{Pak2015_PNAS, HarmanBertrandJoos2017_CJP}.
+We consider both an impermeable vesicle and semipermeable inextensible
+membrane with initial reduced area $\alpha = 0.65$ passing through a
+long narrow channel and compute the excess pressure as a function of
+vesicle position in the channel (Figure~\ref{fig:stenosisComposite}(e)).
+The impermeable case agrees with experimental
+results~\cite{abk-fai-sto2006} (see Figure 3). Our simulations show that
+less excess pressure is needed to drive a semipermeable inextensible
+membrane through the closely-fit channel. Once in the channel, the
+vesicle takes a bullet shape with maximum tension in the front and
+minimum tension in the back (Figure~\ref{fig:stenosisComposite}(c)),
+consistent with earlier results~\cite{Pak2015_PNAS,
+HarmanBertrandJoos2017_CJP}.
 
 Figures~\ref{fig:stenosisComposite}(f)
-and~\ref{fig:stenosisComposite}(g) show that the semipermeable inextensible membrane deflates from
-the beginning due to the high flow velocity, consistent with the results
-for a vesicle in a Poiseuille flow in open space. As the membrane enters
-the stenosis channel, it continues to deflate in the front even though
-we observe influx (red segment) at various rear locations in the
-membrane. Overall, the membrane loses about 6.1\% of its initial total
-water at a constant rate as shown in
+and~\ref{fig:stenosisComposite}(g) show that the semipermeable
+inextensible membrane deflates from the beginning due to the high flow
+velocity, consistent with the results for a vesicle in a Poiseuille flow
+in open space. As the membrane enters the stenosis channel, it continues
+to deflate in the front even though we observe influx (red segment) at
+various rear locations in the membrane. Overall, the membrane loses
+about 6.1\% of its initial total water at a constant rate as shown in
 Figures~\ref{fig:stenosisComposite}(f)
 and~\ref{fig:stenosisComposite}(g) (blue curves). Thus we expect that a
-larger amount of deflation is possible if the inextensible membrane is inside a longer
-stenosis: we consider a vesicle passing through a channel of triple the
-length in Figure~\ref{fig:stenosisComposite}(b) with
-$U_{\max}=1000\;\mu$m/s, and we observe that vesicle stays inside the
-stenosis for a residence time $t_R \approx 70$ ms and the area decreases
-by 13.2\% (red curves).
+larger amount of deflation is possible if the inextensible membrane is
+inside a longer stenosis: we consider a vesicle passing through a
+channel of triple the length in Figure~\ref{fig:stenosisComposite}(b)
+and (d) with $U_{\max}=1000\;\mu$m/s, and we observe that vesicle stays
+inside the stenosis for a residence time $t_R \approx 70$ ms and the
+area decreases by 13.2\% (red curves).
 
@@
   The channel width varies from $18\;\mu$m to $1.8\;\mu$m, and it
-  repeats every $45\;\mu$m. The fluid flux along the red regions is into
-  the vesicle, and the fluid flux along the blue regions is out of the
-  vesicle.  (a--c) The ability for a semipermeable vesicle to pass
-  through the contraction depends on the permeability $\beta$. (d--f)
-  The ability for a semipermeable inextensible membrane to pass through the
-  contraction depends on the flow rate. (g--i) The tension distribution
-  and maximum tension in N/m of the vesicle shapes in (a) and (b).
-  (j--l) The tension distribution and maximum tension in N/m of the
-  vesicle shapes in (d) and (e).}
+  repeats every $45\;\mu$m. The red regions correspond to influx and
+  blue regions correspond to efflux (a--c) The ability for a
+  semipermeable vesicle to pass through the contraction depends on the
+  permeability $\beta$. (d--f) The ability for a semipermeable
+  inextensible membrane to pass through the contraction depends on the
+  flow rate. (g--i) The tension distribution and maximum tension in N/m
+  of the vesicle shapes in (a) and (b).  (j--l) The tension distribution
+  and maximum tension in N/m of the vesicle shapes in (d) and (e).}
 \end{figure}
@@
 the maximum flow velocity on whether a membrane can successfully pass
-through the slit. We color the vesicle according to the sign of its
-flux---red for influx and blue for efflux.
+through the slit. 
+%We color the vesicle according to the sign of its
+%flux---red for influx and blue for efflux.
 
@@
   \fi
-  \caption{\label{fig:contractingComposite2} Reduced area and
-  velocity of a semipermeable inextensible membrane vs.~time. The permeability coefficient is $\beta = 10^{-3}$
-  and the maximum velocity is $18\;\mu$m/s. (a) A semipermeable inextensible membrane
-  passing through six periods of the contracting geometry. (b) The
-  reduced area with the marks representing shapes in (a). (c) The
-  center-of-mass velocity with the marks representing shapes in (a). In (b) and
-  (c), the lower $x$-axis is the x-coordinate of the center of mass, and
-  the upper $x$-axis is time. (d) The membrane tension in N/m. (e) The
+  \caption{\label{fig:contractingComposite2} The reduced area and
+  velocity of a semipermeable inextensible membrane vs.~time. The
+  permeability coefficient is $\beta = 10^{-3}$ and the maximum velocity
+  is $18\;\mu$m/s. (a) A semipermeable inextensible membrane passing
+  through six periods of the contracting geometry. (b) The reduced area
+  with the marks representing shapes in (a). (c) The center-of-mass
+  velocity with the marks representing shapes in (a). In (b) and (c),
+  the lower $x$-axis is the x-coordinate of the center of mass, and the
+  upper $x$-axis is time. (d) The membrane tension in N/m. (e) The
   maximum membrane tension.}
@@
 \end{figure}
-To understand the effects of water permeability on a semipermeable inextensible membrane that
-repeatedly passes through micro-capillary vessels or sub-micron slits,
-we construct a contracting geometry
+To understand the effects of water permeability on a semipermeable
+inextensible membrane that repeatedly passes through micro-capillary
+vessels or sub-micron slits, we construct a contracting geometry
 (Figure~\ref{fig:contractingComposite2}) to simulate a membrane passing
@@
 of the vesicle is almost 50\%. In
-Figure~\ref{fig:contractingComposite2}(c), we show the membrane center-of-mass velocity
-as a function of the membrane position. As the membrane passes
-through the contraction, it first accelerates until it reaches the neck
-where it abruptly decelerates to go through the contraction.
-Figure~\ref{fig:contractingComposite2}(d) shows the tension
-distribution, and the maximum tension is in
+Figure~\ref{fig:contractingComposite2}(c), we show the membrane
+center-of-mass velocity as a function of the membrane position. As the
+membrane passes through the contraction, it first accelerates until it
+reaches the neck where it abruptly decelerates to go through the
+contraction.  Figure~\ref{fig:contractingComposite2}(d) shows the
+tension distribution, and the maximum tension is in
 Figure~\ref{fig:contractingComposite2}(e). We see that the membrane
-tensions is largest when it passes through the neck, and it is
+tension is largest when it passes through the neck, and it is
 particularly large when it passes through the first neck since this is

### 2021-02-15 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
edited up to start of section iv

@@
 water) suspended in a viscous fluid (Figure~\ref{fig:sketch}), and we
-let $\gamma$ denote the membrane boundary, of length $L$ and enclosing an area $A$.
+let $\gamma$ denote the membrane boundary, of length $L$ and enclosing a
+region of area $A$.
 %
@@
 
-For example, we use $10^{-5}\le\beta\le10^{-2}$
-in our simulations of a semipermeable inextensible membrane in free space under various flowing conditions.
-We found that 
-the equilibrium shape of a semipermeable membrane in free space to be independent of $\beta$.
-Within this range of $\beta$ we find that $\beta$ only affects the time it takes for the membrane to reach the equilibrium shape, which is determined by the background flow
-(such as a quiescent flow, a linear shear flow and its shear rate, and a Poiseuille flow and its maximum velocity.)
-From these results and our analysis of area dynamics, we suspect similar hydrodynamics of a semipermeable vesicle
-(with $10^{-11}\le\beta\le 10^{-9}$). 
+For example, we use $10^{-5}\le\beta\le10^{-2}$ in our simulations of a
+semipermeable inextensible membrane in free space under various flowing
+conditions. We found that the equilibrium shape of a semipermeable
+membrane in free space to be independent of $\beta$. Within this range
+of $\beta$ we find that $\beta$ only affects the time it takes for the
+membrane to reach the equilibrium shape, which is determined by the
+background flow (such as a quiescent flow, a linear shear flow and its
+shear rate, and a Poiseuille flow and its maximum velocity). From these
+results and our analysis of area dynamics, we suspect similar
+hydrodynamics of a semipermeable vesicle (with $10^{-11}\le\beta\le
+10^{-9}$). 
 %
@@
 impermeable vesicle, the steady state tension is positive rather than
-negative. Such equilibrium shape of a semipermeable vesicle results from
+negative. The equilibrium shape of a semipermeable vesicle results from
 the balance between elastic stress and membrane tension. For an elastic
@@
 \end{align}
-which is consistent with the equilibrium results in Equation~(\ref{eqn:curveODE}).
+which is consistent with the equilibrium result in
+Equation~(\ref{eqn:curveODE}).
 
@@
 \subsection{Discretization in Time}
-We apply a second-order spectral deferred correction (SDC) method that was
-thoroughly tested in previous work~\cite{qua-bir2016}. To control error
-over long time horizons, we use the error in length to adaptively adjust
-the time step size. SDC requires two steps of a first-order time
-stepping method. To allow for large time step sizes, terms involving
-high-order derivatives are discretized semi-implicitly. We start by
-defining
+We apply a second-order spectral deferred correction (SDC) method that
+was thoroughly tested in previous work~\cite{qua-bir2016}. To control
+error over long time horizons, we use the error in length to adaptively
+adjust the time step size. Our SDC formulation requires two applications
+of a first-order time stepping method. To allow for large time step
+sizes, terms involving high-order derivatives are discretized
+semi-implicitly. We start by defining
 \begin{align}
@@
 \end{align}
-We note that the operators defined in Equation~\eqref{eqn:operators}, as
-well as the single-layer potential defined in Equation~\eqref{eqn:SLP}
-all depend on the vesicle shape. A time stepping method that treats
-these dependencies implicitly would result in a non-linear set of
-equations that would be computationally expensive to solve. Instead, we
-use a time stepping method that defines the operators at time $t^N$ and
-discretizes the stiff terms due to high-order derivatives
+We note that the operators defined in Equation~\eqref{eqn:operators} and
+the single-layer potential defined in Equation~\eqref{eqn:SLP} depend on
+the vesicle shape. A time stepping method that treats these dependencies
+implicitly would result in a non-linear set of equations that would be
+computationally expensive to solve. Instead, we define the operators at
+time $t^N$ and discretize the stiff terms due to high-order derivatives
 implicitly~\cite{vee-gue-zor-bir2009, qua-bir2014}. In particular, the
-first-order semi-implicit method that is applied iteratively with SDC is
+first-order semi-implicit method that is applied iteratively within SDC
+is
 \begin{alignat}{3}

### 2021-02-15 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
edited up to start of section V

@@
   \caption{\label{fig:relaxationComposite} (a) Snapshots of four
-  semipermeable inextensible membranes with $\beta = 10^{-8}$ submerged in a fluid
-  with no background flow. Time goes from left to right. The red regions
-  correspond to influx and the blue regions correspond to efflux. In all
-  cases, the vesicle reaches a steady state circular shape. (b) The
-  reduced area of each of the simulations. The particular snapshots in
-  (a) occur at the marks along the curve.}
+  semipermeable inextensible membranes with $\beta = 10^{-8}$ submerged
+  in a fluid with no background flow. Time goes from left to right. The
+  red regions correspond to influx and the blue regions correspond to
+  efflux. In all cases, the vesicle reaches a steady state circular
+  shape. (b) The reduced area of each of the simulations. The particular
+  snapshots in (a) occur at the marks along the curve. Three dimensioned
+  times are denoted by the dashed lines.}
 \end{figure*}
-The analysis in \S~\ref{subsec:area_dynamics} shows
-that a semipermeable inextensible membrane relaxes to a circle at a rate that is
-proportional to $\beta$, regardless of the initial membrane shape (for a fixed length):
-In the absence of a background flow, a semipermeable inextensible membrane in free
-space is quantified in terms of its area dynamics and transition
-to the equilibrium shape, which is a circular membrane with a uniform 
-membrane tension $\Lambda = 2\pi^2/L^2$.
-This is in stark contrast with the impermeable vesicle relaxing to equilibrium that depends on the vesicle reduced area,  which remains constant for $\beta=0$.
-%
-Our analysis further shows that the rate of change in area enclosed inside a
-semipermeable inextensible membrane is proportional to $\beta$. For this reason,
-our numerical results are reported in terms of the scaled time $\beta t$.
+In the absence of a background flow, a semipermeable inextensible
+membrane in free space is quantified in terms of its area dynamics and
+transition to the equilibrium shape, which is a circular membrane with a
+uniform membrane tension $\Lambda = 2\pi^2/L^2$. This is in stark
+contrast with the impermeable vesicle relaxing to equilibrium that
+depends on the vesicle reduced area, which remains constant for
+$\beta=0$. Our analysis in \S~\ref{subsec:area_dynamics} shows that a
+semipermeable inextensible membrane relaxes to a circle at a rate that
+is proportional to $\beta$, regardless of the initial membrane shape
+(for a fixed length). For this reason, our numerical results are
+reported in terms of the scaled time $\beta t$.
 
@@
   \caption{\label{fig:shearComposite} (a) The reduced area of a
-  semipermeable inextensible membrane with $\beta = 10^{-3}$ initialized with four
-  different reduced areas in a shear flow with two different flow rates.
-  (b) The equilibrium membrane shape with varying flow rates and
-  membrane permeability. The red regions correspond to influx and the
-  blue regions correspond to efflux The boxed membranes correspond to the
-  simulation results in part (a).}
+  semipermeable inextensible membrane with $\beta = 10^{-3}$ initialized
+  with four different reduced areas in a shear flow with two different
+  flow rates. (b) The equilibrium membrane shape with varying flow rates
+  and membrane permeability. The red regions correspond to influx and
+  the blue regions correspond to efflux. The boxed membranes correspond
+  to the simulation results in part (a).}
 \end{figure*}
 
-We consider a semipermeable inextensible membrane in a planar shear flow,
-characterized by the elastic capillary number $Ca_\mathrm{E}=\chi\tau$ where $\tau$ is the characteristic time scale from balancing the viscous stress with the elastic stress
+We consider a semipermeable inextensible membrane in a planar shear
+flow, characterized by the elastic capillary number
+$Ca_\mathrm{E}=\chi\tau$ where $\tau$ is the characteristic time scale
+from balancing the viscous stress with the elastic stress
 %in the non-dimensionalization 
@@
 contrast determine whether a vesicle tank treads or
-tumbles~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. Focusing on
-a semipermeable inextensible membrane with no viscosity contrast, 
-we find that the membrane tilts to an inclination angle and undergoes
+tumbles~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. Focusing on a
+semipermeable inextensible membrane with no viscosity contrast, we find
+that the membrane tilts to an inclination angle and undergoes
 tank-treading dynamics, similar to the case of an impermeable vesicle.
@@
 \subsection{Poiseuille Flow}
-We consider a semipermeable inextensible membrane in the Poiseuille flow $\uu =
-U(1-(y/W)^2,0)$, where $U$ is the maximum velocity at $y=0$. The
-non-linear effects of the Poiseuille flow on the migration of an
-impermeable vesicle have been well-studied~\cite{kao-bir-mis2009}: At a
-given value of the maximum velocity $U$, there exists a critical reduced
-volume above which the equilibrium vesicle shape is symmetric (parachute
-or bullet shapes) and the vesicle stays at $y=0$. Below this critical
-reduced volume the equilibrium vesicle moves off the center and is
-asymmetric (tank-treading slipper shape). We validated our numerical
+We consider a semipermeable inextensible membrane in the Poiseuille flow
+$\uu_\infty(\xx) = U(1-(y/W)^2,0)$, where $U$ is the maximum velocity at
+$y=0$. The non-linear effects of the Poiseuille flow on the migration of
+an impermeable vesicle have been well-studied~\cite{kao-bir-mis2009}: At
+a given value of the maximum velocity $U$, there exists a critical
+reduced volume above which the equilibrium vesicle shape is symmetric
+(parachute or bullet shapes) and the vesicle stays at $y=0$. Below this
+critical reduced volume the equilibrium vesicle moves off the center and
+is asymmetric (tank-treading slipper shape). We validated our numerical
 codes by comparing against results in~\citet{kao-bir-mis2009} (see
@@
 impermeable vesicle phase diagram for semipermeable vesicles with $\beta
-= 10^{-3}$. Smaller value of $\beta$ has been used for some parameters but the time 
-it takes to reach equilibrium (for some this involves a transient tank-treading
-motion along the membrane to gradually slow down in the presence of small $\beta$) is too long in these simulations.
-
-The equilibrium membrane shape for different $U$ and initial
-reduced area is summarized in Figure~\ref{fig:parabolicComposite}(a),
-and the vertical displacement of the vesicle's center of mass is in
+= 10^{-3}$. Smaller values of $\beta$ have been used for some parameters
+but the time it takes to reach equilibrium (for some this involves a
+transient tank-treading motion along the membrane to gradually slow down
+in the presence of small $\beta$) is too long in these simulations.
+
+The equilibrium membrane shape for different $U$ and initial reduced
+area is summarized in Figure~\ref{fig:parabolicComposite}(a), and the
+vertical displacement of the vesicle's center of mass is in
 Figure~\ref{fig:parabolicComposite}(b). The effect of semipermeability
@@
   \caption{\label{fig:parabolicTensions} The equilibrium tension
-  distribution of a semipermeable inextensible membrane with $\beta=10^{-3}$ in a
-  parabolic flow (Figure~\ref{fig:parabolicComposite}). The flow
-  velocities are (a) 200 $\mu$m/s, (b) 400 $\mu$m/s, (c) 600 $\mu$m/s,
-  and (d) 800 $\mu$m/s.}
+  distribution of a semipermeable inextensible membrane with
+  $\beta=10^{-3}$ in a parabolic flow
+  (Figure~\ref{fig:parabolicComposite}). The maximum flow velocities are
+  (a) 200 $\mu$m/s, (b) 400 $\mu$m/s, (c) 600 $\mu$m/s, and (d) 800
+  $\mu$m/s.}
 \end{figure*}

### 2021-02-15 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
revision of discussion

@@
 water on the membrane hydrodynamics. Without any external flow or
-confinement, our analysis shows that a semipermeable inextensible membrane always
-inflates to maximize the water content inside the inextensible membrane (a fixed
-length (area) in two (three) dimensions.) Results from analysis and
-numerical simulations show that such relaxation of a semipermeable
-inextensible membrane  is characterized by a rescaled time $\beta t$. We further
-illustrate that the relaxation process consists of at least two phases:
-The first phase is dominated by the balance between membrane traction
-and viscous stress at early times (up to five minutes), when the inextensible membrane
-behaves like an impermeable membrane. The second phase sets in after a
-few hours, when water influx begins to dominate and inflate the semipermeable membrane.
-Over a time scale of more than four weeks, a semipermeable membrane is
-fully inflated, independent of its initial surface-to-volume ratio.
+confinement, our analysis shows that a semipermeable inextensible
+membrane always inflates to maximize the water content inside the
+inextensible membrane (a fixed length (area) in two (three) dimensions).
+Results from analysis and numerical simulations show that such
+relaxation of a semipermeable inextensible membrane is characterized by
+a rescaled time $\beta t$. In linear and non-linear shear flows, we show
+that the steady-state shape depends on flow rate, while the permeability
+sets the time scale required to reach steady state. We further
+illustrate that the hydrodynamics consists of at least two phases. The
+first phase is dominated by the balance between membrane traction and
+viscous stress at early times (up to five minutes), when the
+inextensible membrane behaves like an impermeable membrane. The second
+phase sets in after a few hours, when water flux begins to dominate and
+the semipermeable membrane either inflates or deflates. Over a time
+scale of more than four weeks, independent of the initial
+surface-to-volume ratio, a semipermeable membrane is fully inflated
+(relaxation flow) or has reached its steady-state configuration (shear
+flows).
+%, independent of
+%its initial surface-to-volume ratio.
 
 Under strong confinement we show that water permeation can be amplified
-on a time scale of a few seconds as a semipermeable inextensible membrane is squeezed through a
-closely-fit channel and a contracting channel. As a semipermeable
-inextensible membrane goes through a long closely-fit channel, we observe lose of water at a constant rate, and the longer the channel the
-more the loss of water. In the case of a contracting channel, we find
-that both permeability and the pressure gradient across the slit must be
-sufficiently large for a successful passage. Throughout these
-simulations the membrane tension is below the threshold for membrane
-poration. Thus we expect the continuum membrane theory to well-capture
-the vesicle hydrodynamics, and our simulation results shed light on the
-configuration and time scales needed to observe the effects of
-permeability on vesicle hydrodynamics under confinement.
+on a time scale of a few seconds as a semipermeable inextensible
+membrane is squeezed through a closely-fit channel and a contracting
+channel. As a semipermeable inextensible membrane goes through a long
+closely-fit channel, we observe lose of water at a constant rate, and
+the longer the channel the more the loss of water. In the case of a
+contracting channel, we find that both permeability and the pressure
+gradient across the slit must be sufficiently large for a successful
+passage. Throughout these simulations the membrane tension is below the
+threshold for membrane poration. Thus we expect the continuum membrane
+theory to well-capture the vesicle hydrodynamics, and our simulation
+results shed light on the configuration and time scales needed to
+observe the effects of permeability on vesicle hydrodynamics under
+confinement.
 

### 2021-02-17 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
yny

@@
 %%The response of a cell to an osmotic gradient is inevitably both mechanical (tension redistribution and shape change) and chemical (water flux across the membrane).  
+%
+%The cellular nuclear envelop (NE) consists of two lipid bilayer membranes connected via nuclear pore complexes (NPCs). As a result, NE is has a higher hydraulic conductivity
+%than a lipid bilayer membrane. Even though the NPCs are sufficiently large for transport of both macromolecules and water molecules, the colloid-osmotic pressure inside
+%the nucleus is highly effective in regulating the water content (see \citet{Shahin2019_AdvSci} and references therein).
 
@@
 k_w\le 10^{-12}$ m$^2$s/kg, thus the range of $\beta$ corresponding to the native water permeability of a lipid bilayer membrane (vesicle) is $10^{-11}\le
-\beta\le 10^{-9}$, consistent with the value in \citet{vogl2014effect}. In the following we use a wider range of $\beta$ to elucidate the effects of permeating water flow across a
+\beta\le 10^{-9}$, consistent with the value in \citet{vogl2014effect}. 
+The cellular nuclear envelop is often treated as a filtration membrane \cite{Shahin2019_AdvSci}, and 
+%Treating the cellular nuclear envelop as an ultrafiltration membrane, 
+its hydraulic conductivity is reported to be order of magnitude larger \cite{Wijmans1984_JMS}:
+$10^{-11}\le k_w \le 10^{-9}$m$^2$s/kg,  and the corresponding range of $\beta$ (using the same $R_0/\mu$ for scaling) is $10^{-8}\le
+\beta\le 10^{-6}$.
+
+For the simulations in \S~\ref{sec:free_space} and \S~\ref{sec:confinement} we use a wider range of $\beta$ to elucidate the effects of permeating water flow across a
 semipermeable inextensible membrane.
 %
-
 For example, we use $10^{-5}\le\beta\le10^{-2}$ in our simulations of a

### 2021-03-18 vesicle_code/docs/permeableVes/main.tex

@@
 % At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
-\keywords{Semipermeable membrane$|$ Vesicle $|$ Extreme confinement $|$
+\keywords{Semipermeable membrane $|$ Vesicle $|$ Extreme confinement $|$
 Boundary integral equations $|$ Stokes flow}
@@
 
-\setboolean{displaywatermark}{false}
+\setboolean{displaywatermark}{true}
 
@@
 cell migration in confined microenvironments~\cite{StrokaJiangChenEtAl2014_Cell, papadopoulos2008aquaporins}, 
-dialysis~\cite{wan2006}, cell desiccation~\cite{vogl2014effect}, cell division~\cite{OdermattMiettinenKangEtAl2020_bioRxiv} and
+dialysis~\cite{wan2006}, cell desiccation~\cite{vogl2014effect}, cell division~\cite{OdermattMiettinenKangEtAl2020_bioRxiv}, and
 apoptosis~\cite{marchetti1996mitochondrial}.
@@
 While osmotic stress  is more effective and efficient than mechanical stress in contributing to change in cellular volume, our results suggest that the water permeation due to the capillary pressure may be non-negligible over long times or under strong confinement in simple configurations.
-To examine if this is the case in the physiological processes,  currently we are examining the combined effects of osmotic and mechanical stresses on water permeation in the small Peclet number limit, which is relevant to cellular migration in the presence of both confinement and a solute gradient~\cite{StrokaJiangChenEtAl2014_Cell} and has been studied numerically by Jaeger {\em et al.}~\cite{jae-car-med-try1999}
+To examine if this is the case in the physiological processes,  currently we are examining the combined effects of osmotic and mechanical stresses on water permeation in the small Peclet number limit, which is relevant to cellular migration in the presence of both confinement and a solute gradient~\cite{StrokaJiangChenEtAl2014_Cell} and has been studied numerically by Jaeger {\em et al.}~\cite{jae-car-med-try1999}.
 

### 2021-03-18 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex

@@
 %Treating the cellular nuclear envelop as an ultrafiltration membrane, 
-its hydraulic conductivity is reported to be order of magnitude larger \cite{Wijmans1984_JMS}:
+its hydraulic conductivity is reported to be orders of magnitude larger~\cite{Wijmans1984_JMS}:
 $10^{-11}\le k_w \le 10^{-9}$m$^2$s/kg,  and the corresponding range of $\beta$ (using the same $R_0/\mu$ for scaling) is $10^{-8}\le
@@
 shear rate, and a Poiseuille flow and its maximum velocity). From these
-results and our analysis of area dynamics, we suspect similar
+results and our analysis of areal dynamics, we suspect similar
 hydrodynamics of a semipermeable vesicle (with $10^{-11}\le\beta\le
@@
 
-We next compute the area dynamics of a semipermeable vesicle. Since the
+We next compute the areal dynamics of a semipermeable vesicle. Since the
 area of the vesicle is
@@
 In the absence of a background flow, a semipermeable inextensible
-membrane in free space is quantified in terms of its area dynamics and
+membrane in free space is quantified in terms of its areal dynamics and
 transition to the equilibrium shape, which is a circular membrane with a

### 2021-04-28 vesicle_code/docs/permeableVes/reviewer1.tex
started reviews

\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage{color}
\newcommand{\response}[1]{\textcolor{blue}{#1}}
\newcommand{\note}[1]{\textcolor{red}{#1}}

\begin{document}
We thank the reviewer for reviewing our manuscript \textit{Hydrodynamics
of a semipermeable inextensible membrane under flow and confinement}.
Below is a point-by-point response addressing each of the referee's
comments.
\begin{enumerate}
  \item It is stated in the introduction that stretching (due to
    poration $\ldots$) give rise to enhanced membrane permeability to
    both water and macromolecules such as ATP. Regarding ATP this is
    possible. In normal conditions ATP is released thanks to protein
    change of conformation that open channels and I am not sure the
    evoked permeability is a similar phenomenon. A few words of
    clarification are needed. \\ \\
    \response{A response}

  \item What cause more permeation? (i) hydrodynamic stress of
    suspending fluid, (ii) tension (normal component of force, say
    Lagrange multiplier), (ii) or the tangential force component due to
    tension field? It would be nice to check this point. \\ \\
    \response{A response}

  \item Figure 5 is not well explained. Depending on Capillary number it
    seems that for all reduced area converge to the same (solid line)
    value or continue to decrease (dashed line). I suggest both in text
    and in caption to discuss this issue more clearly. The result
    (Fig.~5a) is also not intuitive: when capillary number is large (10)
    there is a final reduced area, whereas for smaller value 1, the
    final reduced area is smaller. I would have expected that smaller
    $Ca_E$ would empty less the vesicle. Is there any interpretation? \\
    \\
    \response{In the quiescent example, we prove and demonstrate
    numerically that the steady state vesicle reduced area is
    independent of the initial reduced area. Figure 5a shows that this
    result holds in the presence of flow. It also shows that the
    steady state reduced area depends on the capillary number. However,
    the entries in the legend of Figure 5a were accidentally reversed in
    the original submission---this has been corrected. Therefore, the
    reviewers intuition is correct that smaller capillary number results
    in less emptying of the vesicle.}

  \item In Fig.~7b reference is made to steady state? I guess there is
    still water flow across membrane? Or the total flux is zero? In
    other word is the volume of the shapes shown there the same along
    the blue solid line? Then I am confused with inset c which shows
    variation of alpha? My question: are shapes in b along blue line
    long term ones? Is alpha constant there? Please clarify. \\ \\
    \response{A response}
    \note{Is the 2D Green's function the same as the 3D green's function
    in cylindrical coordinates.}

  \item I do not quite understand why permeation time scale is much
    lower for confined situations? Is pressure drop fixed, as compared
    to previous cases? Does cell see stronger stress now? Why? If the
    driving force is the same I do not expect such dramatic change of
    time scale, since the mean shear stress experienced by the cell
    remains of the same order, as before. A clear discussion of origin
    (from stress values point of view, and why confinement would enhance
    imposed stress) is necessary. This section is poorly discussed. \\
    \\
    \response{A response}

\end{enumerate}

\end{document}

### 2021-04-28 vesicle_code/docs/permeableVes/reviewer2.tex
started reviews

\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage{color}
\newcommand{\response}[1]{\textcolor{blue}{#1}}

\begin{document}
We thank the reviewer for reviewing our manuscript \textit{Hydrodynamics
of a semipermeable inextensible membrane under flow and confinement}.
Below is a point-by-point response addressing each of the referee's
comments.
\begin{enumerate}
  \item I am slightly confused as to how the length and time scales are
    derived from the parameters discussed on page 4. As the simulation
    is 2D, it would seem to me that all physical parameters can only be
    defined on a ``per unit of length" basis. E.g., for a 2D vesicle
    contour, the surface tension is actually a line tension with units
    of N, not N/m. Could the authors clarify this?  In particular,
    reference is often made to how long things will take in the results
    (seconds, minutes, days, weeks, etc.), which is why I ask how these
    time scales are obtained. \\ \\
    \response{A response}

  \item Could the authors shed some insight as to how these 2D
    simulations could be reliably connected to real experiments on any
    quantitative basis? Or is the connection purely qualitative? \\ \\
    \response{A response}

  \item On the last page: ``We observe lose of" $\rightarrow$ ``We
    observe loss of". \\ \\
    \response{Thank you for noticing this typo. It is corrected.}

\end{enumerate}

\end{document}

### 2021-04-28 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
started reviews

@@
 channel. As a semipermeable inextensible membrane goes through a long
-closely-fit channel, we observe lose of water at a constant rate, and
+closely-fit channel, we observe loss of water at a constant rate, and
 the longer the channel the more the loss of water. In the case of a

### 2021-04-28 shuwang_rewrite/parabolic1Ves.m

@@ -1,4 +1,4 @@
-function [] = parabolic1Ves(fluxCoeff,farFieldSpeed,concentration,shortax, scaleL, fileName)
+%function [] = parabolic1Ves(fluxCoeff,farFieldSpeed,concentration,shortax, scaleL, fileName)
 %   fluxCoeff = 0;
 %   farFieldSpeed = 10;
 %   concentration =0.3;
@@ -8,14 +8,21 @@ function [] = parabolic1Ves(fluxCoeff,farFieldSpeed,concentration,shortax, scale
 %of multicomponent vesicles in a viscous fluid" by Sohn, Tseng, Li
 %Voigt, &  Lowengrub JCP 2013
 
+fluxCoeff = 0;
+farFieldSpeed = 800;
+concentration = 0;
+shortax = 3.45;
+scaleL = 0.538;
+fileName = 'parabolic1Ves';
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%% Initialize parameters and options %%%%%%%%%%%%%%%%%%%%%%%
 % TODO: SOME OF THESE ARE MORE OPTIONS THAN PARAMETERS
 
-params.N = 128; % points on vesicle
+params.N = 192; % points on vesicle
 params.dt = 1e-5; % time step size
 params.T = 500; % time horizon
-params.saveRate = 10000; % ouptut frequency
+params.saveRate = 100; % ouptut frequency
 params.concentra = concentration; % constant, initial concentration of 
                                   % lipid species
 params.oddeven = 0; % flag for initial lipid species profile?
@@ -42,7 +49,7 @@ params.angle = pi/6; % The tracking point is programmed to be at 0,0.
 
 options.verbose = false;  % write data to console
 options.saveData = true; % save the data
-options.usePlot = false;  % plot the data
+options.usePlot = true;  % plot the data
 options.dataFile = true; % data file name
 options.logFile = true;  % log file name
 
@@ -51,4 +58,4 @@ options.dataFile = ['output/' fileName '.bin'];
 
 ves = Ves2D(params,options);
 
-end
+%end

### 2021-04-28 vesicle_code/src/curve.m

@@ -607,6 +607,32 @@ elseif any(strcmp(options,'tube'))
   X0 = [x;y];
   % rounded off cylinder.  a and b control the length and height 
   % and order controls the regularity
+elseif any(strcmp(options,'porous'))
+  a = 10; b = 3; order = 8;
+  % parameters for the boundary
+  Nsides = ceil(0.5*b/(2*a+2*b)*N);
+  Ntop = (N-4*Nsides)/2;
+  t1 = linspace(0,0.2*pi,Nsides+1); t1 = t1(1:end-1)';
+  t2 = linspace(0.2*pi,pi-0.2*pi,Ntop+1); t2 = t2(1:end-1)';
+  t3 = linspace(pi-0.2*pi,pi+0.2*pi,2*Nsides+1); t3 = t3(1:end-1)';
+  t4 = linspace(pi+0.2*pi,2*pi-0.2*pi,Ntop+1); t4 = t4(1:end-1)';
+  t5 = linspace(2*pi-0.2*pi,2*pi,Nsides+1); t5 = t5(1:end-1)';
+  t = [t1;t2;t3;t4;t5];
+  % Parameterize t so that geometry is closer to 
+  % equispaced in arclength
+  r = (cos(t).^order + sin(t).^order).^(-1/order);
+  x = a*r.*cos(t); y = b*r.*sin(t);
+  X0 = [x;y];
+  % rounded off cylinder.  a and b control the length and height 
+  % and order controls the regularity
+
+  t = (0:N-1)'*2*pi/N;
+  xpores = 0.5*cos(-t);
+  ypores = 0.5*sin(-t);
+  Xpores = [[xpores;ypores] [xpores-4;ypores+0.5] ...
+            [xpores-2;ypores-0.5] [xpores-3;ypores-2.0]];
+  
+  X = [X0 Xpores];
 else
   if ~isempty(ra)
     X0 = o.ellipse(N,ra);

### 2021-04-28 vesicle_code/docs/permeableVes/Response2Refs.tex
yny

\documentclass[12pt]{article}
\usepackage{amsmath,amsfonts,bm,wrapfig}
\usepackage[left=1in,right=1in,top=1in,nohead]{geometry}
\usepackage[dvips]{graphicx}
\usepackage[
pdftitle={nsf si2 bie},
pdfcreator={pdftex},
pdfsubject={paper},
pdfkeywords={some,topics},
hyperindex = {true},  % turn to false for final
colorlinks = {true},  % turn to false for final
linkcolor = {blue},
pagecolor = {blue},
citecolor = {blue}
]{hyperref}
\usepackage{nsf}
\usepackage{paralist}

\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

\begin{document}

{\large \bf Response to the review report for PRF\_FB10127 Quaife: Hydrodynamics of a semipermeable inextensible membrane under flow and confinement}
\vspace{0.5cm}

We have revised the manuscript ``Hydrodynamics of a semipermeable inextensible membrane under flow and confinement"  
by Bryan Quaife, Ashley Gannon and Y.-N. Young, 
based on 
the referees' very helpful feedback.  
Thanks to the referees' comments
and suggestions, we believe the revised manuscript is much
improved. 
In the revised manuscript we ensure that
all of their concerns and questions are properly addressed.
Below is a summary of the revisions made in the new manuscript.
The detailed responses to comments of referees are listed in 
Response to Referee 1 and Referee 2.
We hope that the referees and the
editor will now find the paper suitable for publication in 
Physical Review Fluids.

\vspace{0.5cm}
{\large \bf List of changes}
In the following we refer to 
Referee 1 who has four comments and Referee 2 who has a list of comments. In the revised manuscript the modifications in the text are in blue.

\begin{enumerate}
\item{change 1}
\item{change 2}
\end{enumerate}

\newpage
\vspace{0.5cm}
{\large \bf Response to Referee 1:}
\vspace{0.5cm}

We thank the referee for his/her assessment of our work.  
The following is
our response to each of the specific comments and suggestions.

{\bf The referee wrote:
The paper deals with effect of membrane permeation under equilibrium
and flow conditions. This question is rarely addressed in literature.
The authors highlight the fact that red blood cells have a long life
time, and permeation may become decisive. The work report on several
interesting issues and should be of interest to the community working
on cell dynamics under flow. The paper is clearly written and results
very sound. I support publication after the authors have taken into
account the following points.
}

\noindent
Response: We thank the referee for the confirmation that the topic is of interest to researchers working on cell dynamics under flow.

\begin{enumerate}
\item {\bf 
The referee wrote:
``It should be helpful for general readers to provide some exemplifying dimensional values of parameters (such as the radius of drop, viscosity of fluid, moduli of skeleton, shear or extension rate, and so on) in a few real world applications."}

\noindent
Response: We thank the referee for pointing out this oversight. We have provided estimates of dimensional values of parameters in the new \S II D, which is on page 11 in the revised manuscript.

\item {\bf 
The referee wrote:
``It is stated in the introduction that stretching (due to poration…)
give rise to enhanced membrane permeability to both water and
macromolecules such as ATP. Regarding ATP this is possible. In normal
conditions ATP is released thanks to protein change of conformation
that open channels and I am not sure the evoked permeability is a
similar phenomenon. A few words of clarification are needed."}

\noindent
Response:

\item {\bf
The referee wrote:
``What cause more permeation? (i) hydrodynamic stress of suspending
fluid, (ii) tension (normal component of force, say Lagrange
multiplier), (ii) or the tangential force component due to tension
field? It would be nice to check this point."}

\noindent
Response:

\item {\bf 
The referee wrote:
``Figure 5 is not well explained. Depending on Capillary number it
seems that for all reduced area converge to the same (solid line)
value or continue to decrease (dashed line). I suggest both in text
and in caption to discuss this issue more clearly. Th result (Fig. 5a)
is also not intuitive: when capillary number is large (10) there is a
final reduced area, whereas for smaller value 1, the final reduced
area is smaller. I would have expected that smaller Cae would empty
less the vesicle. Is there any interpretation?"}

\noindent
Response:

\item{\bf
The referee wrote:
``In Fig. 7 B reference is made to steady state? I guess there is
still water flow across membrane? Or the total flux is zero? In other
word is the volume of the shapes shown there the same along the blue
solid line? Then I am confused with inset c which shows variation of
alpha? My question: are shapes in b along blue line long term ones? Is
alpha constant there? Please clarify."}

\noindent
Response:

\item{\bf
The referee wrote:
``I do not quite understand why permeation time scale is much lower
for confined situations? Is pressure drop fixed, as compared to
previous cases? Does cell see stronger stress now? Why? If the driving
force is the same I do not expect such dramatic change of time scale,
since the mean shear stress experienced by the cell remains of the
same order, as before. A clear discussion of origin (from stress
values point of view, and why confinement would enhance imposed
stress) is necessary. This section is poorly discussed."}

\noindent
Response:

\end{enumerate}

\newpage
\vspace{0.5cm}
{\large \bf Response to Referee 2:}
\vspace{0.5cm}

We thank the referee for his/her assessment of our work.  
The following is
our response to each of the specific comments and suggestions.

{\bf The referee wrote:
In this theoretical work, a 2D vesicle is simulated (via boundary elements) in unbounded and confined flows, while accounting for the finite permeability of the membrane to water. While this additional physics has, expectedly, little to no impact on the long-time physics (shape, tension) of vesicles in unbounded flows, in confined flows a marked dependence is observed on the permeability rate. In straight channel flow, the rate of water loss is proportional to the residence time in the channel, resulting in a reduction of the 2D reduced area at the channel outlet. In contraction flow, a high permeability rate (as well as a large pressure gradient) is required to force the vesicle through the nozzle and emerge in the open chamber downstream.

Overall, the paper is well written and the main results are clearly presented. A decent amount of time is spent covering vesicles in quiescent fluids and unbounded flows, which are less interesting than Section V, which includes the main interesting results on confined flows. However, these earlier sections help to paint a cohesive picture to put these later results in a clear context and, for that reason, their addition is welcome. My only real critique of the article is that all of the results are based on 2D simulations and, therefore, their applicability to real 3D systems is limited. However, the novelty of adding finite membrane permeability to the 2D boundary element context (which, to the best of my knowledge, has not been done before) merits publication of this article in Physical Review Fluids. I am therefore recommending this article for publication subject to optional revision (see my comments below).}

\noindent
Response: We thank the referee for the confirmation that the topic is interesting and results are useful.

\begin{enumerate}

\item {\bf The referee wrote: ``1. I am slightly confused as to how the length and time scales are derived from the parameters discussed on page 4. As the simulation is 2D, it would seem to me that all physical parameters can only be defined on a “per unit of length” basis. E.g., for a 2D vesicle contour, the surface tension is actually a line tension with units of N, not N/m. Could the authors clarify this?
In particular, reference is often made to how long things will take in the results (seconds,
minutes, days, weeks, etc.), which is why I ask how these time scales are obtained."}

\noindent
Response:

\noindent
Locations:

\item {\bf The referee wrote: ``2. Could the authors shed some insight as to how these 2D simulations could be reliably connected to real experiments on any quantitative basis? Or is the connection purely
qualitative?"}

\noindent
Response:

\noindent
Location: Second paragraph in the new Introduction in page 2.

\item {\bf The referee wrote: ``On the last page: “We observe lose of”è“We observe loss of”."}

\noindent
Response: \end{enumerate}

\end{document}

### 2021-04-30 vesicle_code/docs/permeableVes/Response2Refs.tex
yny

@@
 The referee wrote:
-``It should be helpful for general readers to provide some exemplifying dimensional values of parameters (such as the radius of drop, viscosity of fluid, moduli of skeleton, shear or extension rate, and so on) in a few real world applications."}
-
-\noindent
-Response: We thank the referee for pointing out this oversight. We have provided estimates of dimensional values of parameters in the new \S II D, which is on page 11 in the revised manuscript.
-
-\item {\bf 
-The referee wrote:
 ``It is stated in the introduction that stretching (due to poration…)
@@
 \noindent
-Response:
+Response: In recent experiments and simulations by Yaling Liu (Lehigh University), it is reported that under very large stress the spectrin network under a red blood cell membrane can be destroyed and the red blood cell membrane can rupture.
+As a result the hemoglobin inside the RBC is found to reduce in this process.
+We now see that the source of confusion arises from the fact that we associate such leakage to enhanced membrane permeability to macromolecules.
+
+We agree with the referee that the ATP release is mostly understood when it is through the coupling between Px1 (activated by membrane tension) and CFTR (activated by membrane deformation), and it is not well understood yet how ATP can be released by diffusing through the membrane.
+We have thus modified this sentence to avoid confusion.
+
+\noindent
+Location:
 
@@
 \noindent
-Response:
+Response: We thank the referee for this point.
+In our formulation, the permeation flux is proportional to the hydrostatic pressure and the normal component of the membrane force, which is the capillary pressure due to the Lagrange multiplier tension.
+The tangential force component due to tension field does not contribute to the permeation flux.
+To elucidate the relative contribution between the hydrostatic pressure and the normal component of the membrane force, we have added a short paragraph to illustrate how the relative contributions are in all cases.
+
+\noindent
+Location:
 
@@
 \noindent
-Response:
+Response: We have mislabeled the $Ca_E$ in figure 5:  $Ca_E=1$ for the solid curves and the $Ca_E=10$ for the dashed curves.
+To address the effect of Capillary number on the relaxation of a semipermeable vesicle, we have continued the simulations for the cases of $Ca_E = 10$ much further to better illustrate the final reduced area at equilibrium.
 
@@
 \noindent
-Response:
+Response: The shapes along the blue curve in Fig.
+7B are equilibrium shapes that enclose a constant area but with an efflux (blue) and an influx (red) that adds to zero.
+Inset c illustrates the evolution from initial  the configuration (I) to the equilibrium (shape III), which corresponds to the case with the largest displacement on the blue curve.
+To better present all these results, we have taken out the insets (c) and (d) and moved them to the new Fig.
+7 A and B.
+The new Fig.
+7 C and D are the old Fig.
+7 A and B.
+
+\noindent
+Location:
 
@@
 \noindent
-Response:
+Response:  For the simulations in \S V for the two confinement cases, we have to use higher values of $\beta$ to keep the membrane tension below the threshold value (lysis tension) for membrane poration.
+{\bf In the manuscript I could not find the values of $\beta$ in \S V.} In addition, the far-field velocity is fixed in these simulations with confinement.
+We did not fix the pressure jump across the channel in these simulations.
+We have modified the text to provide a better explanation of this section.
+
+\noindent
+Location:
 

### 2021-04-30 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
worked on Fig 7

@@
 
-\title{Hydrodynamics of a  Semipermeable Inextensible Membrane Under Flow and
-Confinement}
+\title{Hydrodynamics of a Semipermeable Inextensible Membrane Under Flow
+and Confinement}
 
@@
   \fi
-  \caption{\label{fig:parabolicComposite} (a) The equilibrium shape of
-  a semipermeable inextensible membrane submerged in a Poiseuille flow with varying
-  initial reduced areas and flow rates. The red regions correspond to
-  influx and the blue regions correspond to efflux. (b) The steady
-  state vertical displacement at four different flow velocities. The
-  steady state shapes are superimposed. (c) The reduced area of the
-  slipper formed with the flow rate of $800 \; \mu$m/s. (d) The membrane
-  shape shown with the background imposed flow. The channel width is
-  12.5 times larger than the vesicle radius. The corresponding reduced
-  area of each membrane shape is indicated by the marks in plot (c).}
+  \caption{\label{fig:parabolicComposite} (a) A semipermeable membrane
+  suspended in a Poiseuille flow with maximum velocity $800 \; \mu$m/s.
+  The channel width is 12.5 times larger than the vesicle radius. (b)
+  The reduced area of the vesicle as a function of time. The red marks
+  correspond to the vesicle shapes in (a). (c) The equilibrium shape of
+  a semipermeable inextensible membrane submerged in a Poiseuille flow
+  with varying initial reduced areas and flow rates. The red regions
+  correspond to influx and the blue regions correspond to efflux. (d)
+  The steady state vertical displacement at four different flow
+  velocities.}
 \end{figure*}

### 2021-04-30 vesicle_code/examples/output/makeImages.m

@@ -5,7 +5,7 @@ options.pressure = false;
 options.center = false;
 options.marker = false;
 
-irate = 1; % controls the speed of the visualization
+irate = 10; % controls the speed of the visualization
 
 if 0
   file = 'parabolic1VesData.bin';
@@ -51,7 +51,7 @@ file = '~/Dropbox/Adhesion/choke1VesKEp01bData_Feb02.bin';
   irate = 10;
 end
 
-if 1
+if 0
 %  file = 'porous1VesImpermData.bin';
 %  file = 'porous1VesPerm1Data.bin';
   file = 'porous1VesData.bin';
@@ -146,8 +146,8 @@ if 0
   ax = [-2 2 -2 2];
   options.confined = false;
 end
-if 0
-  file = 'shear1VesDData.bin';
+if 1
+  file = 'shear1VesEData.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/shear1Ves/Chi1p0em1_ra065_beta1p0em4p5/shear1VesData.bin.old';
 %  file = '~/projects/brinkman/vesicle_code/results/PNAS_runs/shear/Chi1p0e0_ra075_beta1p0em3/shear1VesData.bin';
   ax = [-5 5 -5 5];

### 2021-04-30 vesicle_code/examples/shear1Ves.m

@@ -7,8 +7,8 @@ fprintf('First-order semi-implicit time stepping.\n');
 % Physics parameters
 prams.N = 128;               % points per vesicle
 prams.nv = 1;               % number of vesicles
-prams.T = 1e4;               % time horizon (two tumbling)
-prams.m = 500;              % number of time steps
+prams.T = 1500;               % time horizon (two tumbling)
+prams.m = ceil(prams.T/.023);              % number of time steps
 prams.kappa = ones(prams.nv,1);   % bending coefficient
 prams.viscCont = ones(prams.nv,1);         % viscosity contrast
 options.farField = 'shear'; % background velocity
@@ -39,8 +39,10 @@ options.timeAdap = true;
 
 prams.rtolArea = 1e10;
 prams.rtolLength = 1e-2;
-prams.dtMax = 1e1;
-prams.dtMin = 1e-4;
+%prams.dtMax = 1e1;
+%prams.dtMin = 1e-4;
+prams.dtMax = 0.023;
+prams.dtMin = 0.023;
 prams.betaUp = 1.2;
 prams.betaDown = 0.5;
 prams.alpha = 0.9;
@@ -75,7 +77,7 @@ options.dataFile = 'output/shear1VesData.bin';
 %end
 
 oc = curve;
-ra = 0.45;
+ra = 0.75;
 %centerx = [-2.5 2.5];
 %centery = zeros(1,2);
 centerx = 0;
@@ -102,6 +104,9 @@ X = oc.initConfig(prams.N,...
 
 %theta = (0:prams.N-1)'*2*pi/prams.N;
 %X = [cos(theta);3*sin(theta)];
+
+load('~/projects/brinkman/vesicle_code/results/PNAS_runs/shear/Chi1p0e1_ra075_beta1p0em3/finalConfig.mat');
+
 
 Xfinal = Ves2D(X,[],prams,options);
 % Run vesicle code

### 2021-05-18 vesicle_code/docs/permeableVes/Response2Refs.tex
worked on revisions

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage
@@
 
-We thank the referee for his/her assessment of our work.  
-The following is
-our response to each of the specific comments and suggestions.
+We thank the referee for his/her assessment of our work.  The following
+is our response to each of the specific comments and suggestions.
 
 {\bf The referee wrote:
-The paper deals with effect of membrane permeation under equilibrium
-and flow conditions. This question is rarely addressed in literature.
-The authors highlight the fact that red blood cells have a long life
-time, and permeation may become decisive. The work report on several
-interesting issues and should be of interest to the community working
-on cell dynamics under flow. The paper is clearly written and results
-very sound. I support publication after the authors have taken into
-account the following points.
+The paper deals with effect of membrane permeation under equilibrium and
+flow conditions. This question is rarely addressed in literature.  The
+authors highlight the fact that red blood cells have a long life time,
+and permeation may become decisive. The work report on several
+interesting issues and should be of interest to the community working on
+cell dynamics under flow. The paper is clearly written and results very
+sound. I support publication after the authors have taken into account
+the following points.
 }
@@
     give rise to enhanced membrane permeability to both water and
-macromolecules such as ATP. Regarding ATP this is possible. In normal
-conditions ATP is released thanks to protein change of conformation
-that open channels and I am not sure the evoked permeability is a
-similar phenomenon. A few words of clarification are needed."}
+    macromolecules such as ATP. Regarding ATP this is possible. In
+    normal conditions ATP is released thanks to protein change of
+    conformation that open channels and I am not sure the evoked
+    permeability is a similar phenomenon. A few words of clarification
+    are needed."}
 
@@
 
-We agree with the referee that the ATP release is mostly understood when it is through the coupling between Px1 (activated by membrane tension) and CFTR (activated by membrane deformation), and it is not well understood yet how ATP can be released by diffusing through the membrane.
-We have thus modified this sentence to avoid confusion.
+We agree with the referee that the ATP release is mostly understood when
+it is through the coupling between Px1 (activated by membrane tension)
+and CFTR (activated by membrane deformation), and it is not well
+understood yet how ATP can be released by diffusing through the membrane. We have thus modified this sentence to avoid confusion.
 
@@
 \noindent
-Response: We thank the referee for this point.
-In our formulation, the permeation flux is proportional to the hydrostatic pressure and the normal component of the membrane force, which is the capillary pressure due to the Lagrange multiplier tension.
-The tangential force component due to tension field does not contribute to the permeation flux.
-To elucidate the relative contribution between the hydrostatic pressure and the normal component of the membrane force, we have added a short paragraph to illustrate how the relative contributions are in all cases.
+Response: We thank the referee for this point. In our formulation, the
+    permeation flux is proportional to the normal component of the
+    membrane force, which is also the capillary pressure due to both
+    bending and the Lagrange multiplier tension. The tangential
+    force component due to tension field does not contribute to the
+    permeation flux. To elucidate the relative contribution between the
+    hydrostatic pressure due to the bending and tension forces, we have
+    added additional figures and short paragraphs to illustrate the
+    relative contributions are in all cases.
 

### 2021-05-18 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
worked on revisions

@@
   = \beta \int_\gamma (\ff \cdot \nn)\, ds,
+  \label{eqn:areaROCforce}
 \end{align}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Hydrodynamics of a semipermeable inextensible membrane in free space\label{sec:free_space}}
+\section{Hydrodynamics of a Semipermeable Inextensible Membrane in Free Space\label{sec:free_space}}
 To highlight the effects of membrane permeability to water, we consider
@@
 \end{figure*}
- The membrane tension distribution of the equilibrium shapes are shown
- in Figure~\ref{fig:parabolicTensions} for the flow velocities $U$ from
- $200\;\mu$m/s to $800 \;\mu$m/s. We note that in the Poiseuille flow
- the membrane tension is positive in the front, and negative in the rear
- part of the vesicle. Furthermore we also note that the tension
- magnitude is almost linearly proportional to $U$ as in the linear shear
- flow.
+The membrane tension distribution of the equilibrium shapes are shown in
+Figure~\ref{fig:parabolicTensions} for the flow velocities $U$ from
+$200\;\mu$m/s to $800 \;\mu$m/s. We note that in the Poiseuille flow the
+membrane tension is positive in the front, and negative in the rear part
+of the vesicle. Furthermore we also note that the tension magnitude is
+almost linearly proportional to $U$ as in the linear shear flow.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Hydrodynamics of A semipermeable inextensible membrane under strong confinement\label{sec:confinement}}
+\subsection{The Role of Tension and Bending on Semipermeability}
+\textcolor{magenta}{Since $\jump{p}= \ff_\mathrm{mem} \cdot
+\nn$~\cite{poz1992}, our model assumes that the permeating flux is
+proportional to the mechanical pressure jump across the membrane. We
+decompose the normal component of the membrane force into its
+contributions due to tension and bending as
+\begin{align}
+  \ff_{\mathrm{ten}} \cdot \nn = -\kappa \Lambda 
+    \quad \text{ and } \quad
+  \ff_{\mathrm{ben}} \cdot \nn = \kappa_{ss} + \frac{1}{2}\kappa^3.
+\end{align}
+Then, the total flux through the membrane due to the tension and bending
+forces are
+\begin{align}
+  \dot{A}_{\mathrm{ten}}(t) = -\beta \int_{\gamma} \kappa \Lambda\, ds  
+  \quad \text{ and } \quad
+  \dot{A}_{\mathrm{ben}}(t) = \frac{\beta}{2} \int_{\gamma} \kappa^3\, ds,
+  \label{eqn:areaROCdecomposed}
+\end{align}
+respectively. Note that the sum of $\dot{A}_{\mathrm{ten}}(t)$ and
+$\dot{A}_{\mathrm{ben}}(t)$ results in equation~\eqref{eqn:areaROC}.
+After multiplying~\eqref{eqn:areaROCdecomposed} by $4\pi/L^2$, where $L$
+is the constant  vesicle length, the rate of change of the reduced area
+due to the tension and bending forces are formed. We investigate the
+effect of the tension and bending forces on the semipermeability for two
+quiescent examples (Figures~\ref{fig:unconfinedRAdecomp}(a) and (b)),
+one planar shear example (Figure~\ref{fig:unconfinedRAdecomp}(c)), and
+one Poiseuille example (Figure~\ref{fig:unconfinedRAdecomp}(d)). In the
+quiescent flow examples, we see that the tension and bending forces
+result in similar amounts of semipermeability, and for the geometry with
+a larger initial curvature, the reduced area changes much quicker and
+the vesicle deflates at early times before inflating to a circular
+shape. In the planar shear flow and Poiseuille flow examples, the
+tension and bending forces result in similar amounts of
+semipermeability.}
+
+\begin{figure*}[htp]
+  \ifTikz
+  \input{figures/unconfinedRAdecomp.tikz}
+  \else
+  \includegraphics{figures/unconfinedRAdecomp.pdf}
+  \fi
+  \caption{\label{fig:unconfinedRAdecomp}\textcolor{magenta}{The rate of
+  change of the reduced area caused by the tension and bending forces.
+  The dashed line is the sum of these two contributions. (a) The
+  quiescent example in Figure~\ref{fig:relaxationComposite} with
+  $\alpha(0) = 0.66$. (b) The quiescent example in
+  Figure~\ref{fig:relaxationComposite} with $\alpha(0) = 0.38$. (c) The
+  planar shear example in Figure~\ref{fig:shearComposite} with $\alpha(0) =
+  0.45$ and $Ca_\mathrm{E} = 10^0$. (d) The Poiseuille example in
+  Figure~\ref{fig:parabolicComposite} with $\alpha(0) = 0.60$ and
+  maximum velocity $U = 600~\mu$m/s.}}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Hydrodynamics of a Semipermeable Inextensible Membrane Under Strong Confinement\label{sec:confinement}}
 Here we consider a semipermeable inextensible membrane under strong
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{A Semipermeable Inextensible Membrane in a Closely-fit Channel (Stenosis)}
+\subsection{A Semipermeable Inextensible Membrane in a Closely-fit
+Channel (Stenosis)}
 \begin{figure*}[htp]
@@
 \end{figure*}
+
 When red blood cells go through small capillary vessels, they experience
@@
 
-%When a semipermeable vesicle goes through a closely-fit channel, we
-%observe that the water efflux is found in the front, and the influx is
-%in the rear of the vesicle membrane
-%(Figure~\ref{fig:stenosisComposite}). This corresponds well to the
-%corresponding tension distribution in Figure~\ref{fig:stenosisTensions}:
-%Larger tension in the front, and smaller tension in the rear.
+\textcolor{magenta}{Using equation~\eqref{eqn:areaROCdecomposed}, we
+investigate the effects of the tension and bending forces on the water
+flux through the membrane. In Figure~\ref{fig:stenosisRAdecomp}, we
+compute the rate of change of the reduced area due to the tension force
+(blue), the bending force (red), and the total membrane force (black).
+In both the short and long closely-fit channels, the tension force is
+responsible for nearly all the semipermeability. This is in contrast to
+the unconfined examples where the tension and bending forces were
+each responsible for a comparable amount of semipermeability.}
+
+\begin{figure*}[htp]
+  \ifTikz
+  \input{figures/stenosisRAdecomp.tikz}
+  \else
+  \includegraphics{figures/stenosisRAdecomp.pdf}
+  \fi
+  \caption{\label{fig:stenosisRAdecomp} \textcolor{magenta}{The rate of
+  change of the reduced area caused by the tension and bending forces.
+  The dashed line is the sum of these two contributions. (a) The short
+  stenosis geometry in Figure~\ref{fig:stenosisComposite}(a). (b) The
+  long stenosis geometry in Figure~\ref{fig:stenosisComposite}(b).}}
+\end{figure*}
 
@@
 tension has the largest magnitude when the membrane is at the neck.
+
+\textcolor{magenta}{As was done for the closely-fit channel, we use
+equation~\eqref{eqn:areaROCdecomposed} to investigate the effects of the
+tension and bending forces on semipermeability.
+Figure~\ref{fig:contractingRAdecomp} shows the rate of change of the
+reduced area due to the tension force (blue), the bending force (red),
+and the total membrane force (black). Again, the tension is responsible
+for the majority of the semipermeability. However, when compared to the
+closely-fit channel example, the bending does have more of a
+contribution because of the lower maximum imposed velocity. While we
+only decompose the membrane force into tension and bending for the two
+vesicles that successfully pass through the contraction, we also plot
+the total membrane force for the two vesicles that do not pass through
+the contraction (green). The vesicle does deflate with a smaller
+semipermeability coefficient and a smaller maximum imposed velocity, but
+the rate of efflux is insufficient for successful passage of the vesicle
+through the contraction.}
+
+\begin{figure*}[htp]
+  \ifTikz
+  \input{figures/contractingRAdecomp.tikz}
+  \else
+  \includegraphics{figures/contractingRAdecomp.pdf}
+  \fi
+  \caption{\label{fig:contractingRAdecomp} \textcolor{magenta}{The rate
+  of change of the reduced area caused by the tension and bending
+  forces. The dashed line is the sum of these two contributions. Only
+  simulations where the vesicle passes through the contraction are
+  decomposed into the contributions due to tension and bending. (a) The
+  low semipermeability coefficient in
+  Figure~\ref{fig:contractingComposite}(b). The green line corresponds
+  to the simulation in Figure~\ref{fig:contractingComposite}(a). (b) The
+  high semipermeability coefficient in
+  Figure~\ref{fig:contractingComposite}(e). The green line corresponds
+  to the simulation in Figure~\ref{fig:contractingComposite}(d).}}
+\end{figure*}
 

### 2021-05-18 vesicle_code/examples/output/makeImages.m

@@ -147,7 +147,8 @@ if 0
   options.confined = false;
 end
 if 1
-  file = 'shear1VesHData.bin';
+%  file = '~/projects/brinkman/vesicle_code/results/PNAS_runs/shear/Chi1p0e1_ra045_beta1p0em3_longer/shear1VesData.bin';
+  file = 'shear1VesE_restartData.bin';
 %  file = '~/projects/brinkman/vesicle_code/results/shear1Ves/Chi1p0em1_ra065_beta1p0em4p5/shear1VesData.bin.old';
 %  file = '~/projects/brinkman/vesicle_code/results/PNAS_runs/shear/Chi1p0e0_ra075_beta1p0em3/shear1VesData.bin';
   ax = [-5 5 -5 5];

### 2021-05-19 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
yny

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The Role of Tension and Bending on Semipermeability}
-\textcolor{magenta}{Since $\jump{p}= \ff_\mathrm{mem} \cdot
-\nn$~\cite{poz1992}, our model assumes that the permeating flux is
-proportional to the mechanical pressure jump across the membrane. We
-decompose the normal component of the membrane force into its
+\subsection{Contribution from Membrane Tension and Bending to the Permeating Flux}
+\textcolor{magenta}{In the absence of viscosity contrast between interior and exterior fluids, the pressure jump $\jump{p}= \ff_\mathrm{mem} \cdot
+\nn$~\cite{poz1992}. Thus in our model, the permeating flux is
+proportional to the normal component of membrane forces $\ff_\mathrm{mem}\cdot\nn$. We
+decompose $\ff_\mathrm{mem}\cdot\nn$ into its
 contributions due to tension and bending as
@@
 $\dot{A}_{\mathrm{ben}}(t)$ results in equation~\eqref{eqn:areaROC}.
-After multiplying~\eqref{eqn:areaROCdecomposed} by $4\pi/L^2$, where $L$
-is the constant  vesicle length, the rate of change of the reduced area
-due to the tension and bending forces are formed. We investigate the
+Multiplying~\eqref{eqn:areaROCdecomposed} by $4\pi/L^2$, where $L$
+is the constant  vesicle length, we obtain the rate of change of the reduced area
+due to the tension and bending forces. 
+Figures~\ref{fig:unconfinedRAdecomp} summarize the 
 effect of the tension and bending forces on the semipermeability for two
@@
   \caption{\label{fig:unconfinedRAdecomp}\textcolor{magenta}{The rate of
-  change of the reduced area caused by the tension and bending forces.
+  change of the reduced area decomposed into contributions from membrane tension (blue curves) and membrane bending (red curves).
   The dashed line is the sum of these two contributions. (a) The
@@
 
-\textcolor{magenta}{Using equation~\eqref{eqn:areaROCdecomposed}, we
-investigate the effects of the tension and bending forces on the water
-flux through the membrane. In Figure~\ref{fig:stenosisRAdecomp}, we
-compute the rate of change of the reduced area due to the tension force
+\textcolor{magenta}{
+Figure~\ref{fig:stenosisRAdecomp} show
+the rate of change of the reduced area due to the tension force
 (blue), the bending force (red), and the total membrane force (black).
-In both the short and long closely-fit channels, the tension force is
-responsible for nearly all the semipermeability. This is in contrast to
+%Using equation~\eqref{eqn:areaROCdecomposed}, we
+%investigate the effects of the tension and bending forces on the water
+%flux through the membrane. 
+In both short and long closely-fit channels, the membrane tension is
+responsible for nearly all the permeating water flux. This is in contrast to
 the unconfined examples where the tension and bending forces were
-each responsible for a comparable amount of semipermeability.}
+each responsible for a comparable amount of permeating water flux.}
 
@@
   \caption{\label{fig:stenosisRAdecomp} \textcolor{magenta}{The rate of
-  change of the reduced area caused by the tension and bending forces.
+  change of the reduced area due to the membrane tension (blue curves) and membrane bending (red curves).
   The dashed line is the sum of these two contributions. (a) The short
@@
 
-\textcolor{magenta}{As was done for the closely-fit channel, we use
-equation~\eqref{eqn:areaROCdecomposed} to investigate the effects of the
-tension and bending forces on semipermeability.
+\textcolor{magenta}{
+%As was done for the closely-fit channel, we use
+%equation~\eqref{eqn:areaROCdecomposed} to investigate the effects of the
+%tension and bending forces on semipermeability.
 Figure~\ref{fig:contractingRAdecomp} shows the rate of change of the
-reduced area due to the tension force (blue), the bending force (red),
-and the total membrane force (black). Again, the tension is responsible
-for the majority of the semipermeability. However, when compared to the
+reduced area due to membrane tension (blue curves), membrane bending (red curves),
+and the total membrane force (dashed black curves). Again, the tension is responsible
+for the majority of the permeating flux. However, when compared to the
 closely-fit channel example, the bending does have more of a
@@
 the total membrane force for the two vesicles that do not pass through
-the contraction (green). The vesicle does deflate with a smaller
+the contraction (dash-dotted green curves). The vesicle does deflate with a smaller
 semipermeability coefficient and a smaller maximum imposed velocity, but
@@
   \caption{\label{fig:contractingRAdecomp} \textcolor{magenta}{The rate
-  of change of the reduced area caused by the tension and bending
-  forces. The dashed line is the sum of these two contributions. Only
+  of change of the reduced area due to  membrane tension (blue curves) and membrane bending
+  (red curves). The dashed black  line is the sum of these two contributions. Only
   simulations where the vesicle passes through the contraction are
@@
   low semipermeability coefficient in
-  Figure~\ref{fig:contractingComposite}(b). The green line corresponds
+  Figure~\ref{fig:contractingComposite}(b). The dash-dotted green curve corresponds
   to the simulation in Figure~\ref{fig:contractingComposite}(a). (b) The
   high semipermeability coefficient in
-  Figure~\ref{fig:contractingComposite}(e). The green line corresponds
+  Figure~\ref{fig:contractingComposite}(e). The dash-dotted green curve corresponds
   to the simulation in Figure~\ref{fig:contractingComposite}(d).}}

### 2021-05-19 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
fixed up a few figures
yny

@@
 and the total membrane force (dashed black curves). Again, the tension is responsible
-for the majority of the permeating flux. However, when compared to the
-closely-fit channel example, the bending does have more of a
-contribution because of the lower maximum imposed velocity. While we
+for the majority of the permeating flux. While we
 only decompose the membrane force into tension and bending for the two
@@
 
+\textcolor{magenta}{
+%In our model, the permeating flux of viscous solvent is proportional to the normal component of membrane forces.
+%which is equal to the jump in hydrodynamic pressure in our simulations with no viscosity contrast
+%between interior and exterior fluids. 
+For each of the cases in \S~\ref{sec:free_space} and \ref{sec:confinement}, 
+we examine the contribution of the permeating flux from membrane tension and membrane bending forces.
+In free space, we find that both membrane forces contribute comparably in the simulations.
+As the vesicle hydrodynamics reaches an equilibrium, the two contributions add to zero as the permeating flux integrates to zero rate of change of the reduced area.
+Under strong confinement, however, we find the membrane tension to contribute much more to the permeating flux than the membrane bending.
+For a vesicle going through a closely-fit channel the maximum flow velocity is $U_{max}=1000$ $\mu$m/s is chosen to match the experimental conditions.
+Such a large flow velocity contributes to large membrane tension, and thus reducing the time scale for change in water content.
+For a vesicle going through a contracting channel, we used a smaller $U_{max}$ than in the experiments (where the three-dimensional channel contracts in both cross-stream directions) to examine the effect of membrane permeability.
+We find that, due to the strong confinement, the membrane tension still dominates the membrane bending in contributing to the permeating flux as in the closely-fit channel.
+}
+
 %Using scaling arguments, we showed that permeability due to osmolarity

### 2021-05-20 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
yny

@@
 membrane porates when the membrane tension reaches the order of $2$--$4$
-mN/m (see~\citet{RazizadehNikfarPaulLiu2020_BJ} and references therein),
-giving rise to enhanced membrane permeability to both water and
-macromolecules such as ATP. Consequently, as long as the lipid bilayer membrane
+mN/m,
+giving rise to \textcolor{magenta}{membrane rupture and leakage of macromolecules (see~\citet{RazizadehNikfarPaulLiu2020_BJ} and references therein).}
+%
+%enhanced membrane permeability to both water and
+%macromolecules such as ATP. 
+%
+Consequently, as long as the lipid bilayer membrane
 remains intact (no poration or rupture), the total amount of water inside the membrane 
@@
 $k_b/R_0^2 = 10^{-7}$ N/m, and the permeability by $R_0/\mu = 10^{-3}$
-m$^2$s/kg. Under this nondimensionalization, a two-dimensional
+m$^2$s/kg. Under this nondimensionalization \textcolor{magenta}{suitable for a vesicle in a quiescent flow}, a two-dimensional
 semipermeable vesicle in a viscous fluid is characterized by (a) its

### 2021-05-20 vesicle_code/docs/permeableVes/Response2Refs.tex
yny

--- 2021-04-28 vesicle_code/docs/permeableVes/Response2Refs.tex
@@
 
-{\large \bf Response to the review report for PRF\_FB10127 Quaife: Hydrodynamics of a semipermeable inextensible membrane under flow and confinement}
+{\large \bf {\bf Response:} to the review report for PRF\_FB10127 Quaife: Hydrodynamics of a semipermeable inextensible membrane under flow and confinement}
 \vspace{0.5cm}
@@
 Below is a summary of the revisions made in the new manuscript.
-The detailed responses to comments of referees are listed in 
-Response to Referee 1 and Referee 2.
+The detailed {\bf Response:}s to comments of referees are listed in 
+{\bf Response:} to Referee 1 and Referee 2.
 We hope that the referees and the
@@
 \vspace{0.5cm}
-{\large \bf Response to Referee 1:}
+{\large \bf {\bf Response:} to Referee 1:}
 \vspace{0.5cm}
@@
 The following is
-our response to each of the specific comments and suggestions.
+our {\bf Response:} to each of the specific comments and suggestions.
 
@@
 \noindent
-Response: We thank the referee for the confirmation that the topic is of interest to researchers working on cell dynamics under flow.
+{\bf Response:}: We thank the referee for the confirmation that the topic is of interest to researchers working on cell dynamics under flow.
 
 \begin{enumerate}
-\item {\bf 
-The referee wrote:
-``It should be helpful for general readers to provide some exemplifying dimensional values of parameters (such as the radius of drop, viscosity of fluid, moduli of skeleton, shear or extension rate, and so on) in a few real world applications."}
-
-\noindent
-Response: We thank the referee for pointing out this oversight. We have provided estimates of dimensional values of parameters in the new \S II D, which is on page 11 in the revised manuscript.
-
 \item {\bf 
@@
 \noindent
-Response:
+{\bf Response:}: In recent experiments and simulations by Yaling Liu (Lehigh University), it is reported that under very large stress the spectrin network under a red blood cell membrane can be destroyed and the red blood cell membrane can rupture.
+As a result the hemoglobin inside the RBC is found to reduce in this process.
+We now see that the source of confusion arises from the fact that we associate such leakage to enhanced membrane permeability to macromolecules.
+
+We agree with the referee that the ATP release is mostly understood when it is through the coupling between Px1 (activated by membrane tension) and CFTR (activated by membrane deformation), and it is not well understood yet how ATP can be released by diffusing through the membrane.
+We have thus modified this sentence to avoid confusion.
+
+\noindent
+{\bf Location:}  The second paragraph of Introduction, five lines above Figure 1: ``....reaches the order of 2-4 mN/m, giving rise to
+membrane rupture and leakage of macromolecules (see Razizadeh {\it et al. }$^{20}$ and references therein)."
 
@@
 \noindent
-Response:
+{\bf Response:}: We thank the referee for this point.
+In our formulation, the permeation flux is proportional to the hydrostatic pressure and the normal component of the membrane force, which is the capillary pressure due to the Lagrange multiplier tension.
+The tangential force component due to tension field does not contribute to the permeation flux.
+To elucidate the relative contribution between the hydrostatic pressure and the normal component of the membrane force, we have conducted computations
+added a short paragraph to illustrate how the relative contributions are in all cases.
+
+\noindent
+{\bf Location:} A new \S IV D in page 14, and the new Figures 9 in page 15.
+The last paragraph in page 17, and the new Figure 11 in page 17.
+The second paragraph in page 19, and the new Figure 13 in page 19.
+Second to last paragraph in page 21.
 
@@
 \noindent
-Response:
+{\bf Response:}: We have mislabeled the $Ca_E$ in figure 5:  $Ca_E=10^0$ for the solid curves and the $Ca_E=10$ for the dashed curves.
+To address the effect of Capillary number on the relaxation of a semipermeable vesicle, we have continued the simulations for the cases of $Ca_E = 10$ much further to better illustrate the evolution of reduced area towards equilibrium.
+
+\noindent
+{\bf Location:} A new Figure 5(a) in page 11.
 
@@
 \noindent
-Response:
+{\bf Response:}: The shapes along the blue curve in Figure 7(b) are equilibrium shapes that enclose a constant area but with an efflux (blue) and an influx (red) that adds to zero.
+Inset c illustrates the evolution from initial  the configuration (I) to the equilibrium (shape III), which corresponds to the case with the largest displacement on the blue curve.
+To better present all these results, we have taken out the insets (c) and (d) and moved them to the new Figure 7 (a) and (b).
+The new Figure 7 (c) and (d) are the old Figure  7 (a) and (b).
+
+\noindent
+{\bf Location:} Figure 7 in page 13.
 
@@
 \noindent
-Response:
+{\bf Response:}:  We have added new computations to illustrate the relative contributions of membrane tension and bending forces to the permeating fluxes for all cases in \S IV and \S V (see {\bf Response} to the second point), see the new Figures 9, 11, and 13.
+
+For the closely-fit channel the imposed flow at the inlet/outlet is set $U_{max}=1000$ $\mu$m/s to match the experimental conditions.
+As a result the membrane tension is dominant over membrane bending in their contribution to the permeating flux.
+For the contracting channel, the imposed flow at the inlet/outlet is smaller and yet the strong confinement still gives rise to a membrane tension that dominates in contributing to the permeating flux.
+We also added new paragraphs to discuss these new results.
+
+\noindent
+{\bf Location:} A new \S IV D in page 14, and the new Figures 9 in page 15.
+The last paragraph in page 17, and the new Figure 11 in page 17.
+The second paragraph in page 19, and the new Figure 13 in page 19.
+Second to last paragraph in page 21.
 
@@
 \vspace{0.5cm}
-{\large \bf Response to Referee 2:}
+{\large \bf {\bf Response:} to Referee 2:}
 \vspace{0.5cm}
@@
 \noindent
-Response: We thank the referee for the confirmation that the topic is interesting and results are useful.
+{\bf Response:}: We thank the referee for the confirmation that the topic is interesting and results are useful.
 
@@
 \noindent
-Response:
+{\bf Response:}: We thank the referee for this question.
+The referee is indeed correct that in a 2D system the system remains constant in the $z$ direction indefinitely.
+Consequently it is customary to focus on the system on a plane, and the membrane tension is the membrane force per unit length (the length in the $z$ direction).
+This means that, after the division by the length in the third direction, the membrane tension on the plane is force per length.
+
+The dimensionless group of this system is independent of the spatial dimensions of the system.
+In the absence of any external flow, we have adopted the initial vesicle size $R_0$ for a length scale,  the elastic relaxation in balance with the viscous dissipation at  length scale $R_0$ for a time scale $\tau$, and the elastic force at length scale $R_0$ for membrane tension.
+The dimensionless permeability is the hydraulic permeability scaled accordingly.
+Such scaling is natural for the quiescent cases.
+We used the same scaling for other cases for consistency in presentation to avoid confusion.
 
 \noindent
-Locations:
+{\bf Locations:} Second to last paragraph in page 4, fifth line in this paragraph, ``Under this nondimensionalization suitable for a vesicle in a quiescent flow".
 
@@
 \noindent
-Response:
+{\bf Response:}: The referee is correct that numerical simulations of two-dimensional fluid flow could be ideal and the connection to the real experiments is qualitative at best.
+The studies of two-dimensional vesicle hydrodynamics, however, have shown that the connection to real experiments or 3d simulations could be more than purely qualitative.
+For example, for a vesicle in a planar shear flow, the transition from tank-treading to tumbling is predicted in both 2 and 3-dimensions, at similar viscosity contrast.
+Ghiliotti, Biben and Misbah (JFM, 2010) showed that results for a two-dimensional vesicle could be corrected systematically to agree with the three-dimensional results.
+More recently, the two-dimensional results in Zhang, Shen, Hogan, Barakat and Misbah are also in more than qualitative agreement with real experiments (Biophys.
+J, 2018).
 
 \noindent
-Location: Second paragraph in the new Introduction in page 2.
+{\bf Location:} Second paragraph in the new Introduction in page 2.
 
@@
 \noindent
-Response: \end{enumerate}
+{\bf Response:}: \end{enumerate}
 

### 2021-05-20 vesicle_code/docs/permeableVes/reviewer1.tex
yny1

@@
 \begin{document}
-We thank the reviewer for reviewing our manuscript \textit{Hydrodynamics
-of a semipermeable inextensible membrane under flow and confinement}.
-Below is a point-by-point response addressing each of the referee's
-comments.
+
+We thank the referee for his/her assessment of our work.  
+The following is
+our {\bf Response:} to each of the specific comments and suggestions.
+
+{\bf The referee wrote:
+The paper deals with effect of membrane permeation under equilibrium
+and flow conditions. This question is rarely addressed in literature.
+The authors highlight the fact that red blood cells have a long life
+time, and permeation may become decisive. The work report on several
+interesting issues and should be of interest to the community working
+on cell dynamics under flow. The paper is clearly written and results
+very sound. I support publication after the authors have taken into
+account the following points.
+}
+
+\noindent
+{\bf Response:}: We thank the referee for the confirmation that the topic is of interest to researchers working on cell dynamics under flow.
+
 \begin{enumerate}
-  \item It is stated in the introduction that stretching (due to
-    poration $\ldots$) give rise to enhanced membrane permeability to
-    both water and macromolecules such as ATP. Regarding ATP this is
-    possible. In normal conditions ATP is released thanks to protein
-    change of conformation that open channels and I am not sure the
-    evoked permeability is a similar phenomenon. A few words of
-    clarification are needed. \\ \\
-    \response{A response}
+\item {\bf 
+The referee wrote:
+``It is stated in the introduction that stretching (due to poration…)
+give rise to enhanced membrane permeability to both water and
+macromolecules such as ATP. Regarding ATP this is possible. In normal
+conditions ATP is released thanks to protein change of conformation
+that open channels and I am not sure the evoked permeability is a
+similar phenomenon. A few words of clarification are needed."}
 
-  \item What cause more permeation? (i) hydrodynamic stress of
-    suspending fluid, (ii) tension (normal component of force, say
-    Lagrange multiplier), (ii) or the tangential force component due to
-    tension field? It would be nice to check this point. \\ \\
-    \response{A response}
+\noindent
+{\bf Response:}: In recent experiments and simulations by Yaling Liu (Lehigh University), it is reported that under very large stress the spectrin network under a red blood cell membrane can be destroyed and the red blood cell membrane can rupture.
+As a result the hemoglobin inside the RBC is found to reduce in this process.
+We now see that the source of confusion arises from the fact that we associate such leakage to enhanced membrane permeability to macromolecules.
 
-  \item Figure 5 is not well explained. Depending on Capillary number it
+We agree with the referee that the ATP release is mostly understood when it is through the coupling between Px1 (activated by membrane tension) and CFTR (activated by membrane deformation), and it is not well understood yet how ATP can be released by diffusing through the membrane.
+We have thus modified this sentence to avoid confusion.
+
+\noindent
+{\bf Location:}  The second paragraph of Introduction, five lines above Figure 1: ``....reaches the order of 2-4 mN/m, giving rise to
+membrane rupture and leakage of macromolecules (see Razizadeh {\it et al. }$^{20}$ and references therein)."
+
+\item {\bf
+The referee wrote:
+``What cause more permeation? (i) hydrodynamic stress of suspending
+fluid, (ii) tension (normal component of force, say Lagrange
+multiplier), (ii) or the tangential force component due to tension
+field? It would be nice to check this point."}
+
+\noindent
+{\bf Response:}: We thank the referee for this point.
+In our formulation, the permeation flux is proportional to the hydrostatic pressure and the normal component of the membrane force, which is the capillary pressure due to the Lagrange multiplier tension.
+The tangential force component due to tension field does not contribute to the permeation flux.
+To elucidate the relative contribution between the hydrostatic pressure and the normal component of the membrane force, we have conducted computations
+added a short paragraph to illustrate how the relative contributions are in all cases.
+
+\noindent
+{\bf Location:} A new \S IV D in page 14, and the new Figures 9 in page 15.
+The last paragraph in page 17, and the new Figure 11 in page 17.
+The second paragraph in page 19, and the new Figure 13 in page 19.
+Second to last paragraph in page 21.
+
+\item {\bf 
+The referee wrote:
+``Figure 5 is not well explained. Depending on Capillary number it
 seems that for all reduced area converge to the same (solid line)
 value or continue to decrease (dashed line). I suggest both in text
-    and in caption to discuss this issue more clearly. The result
-    (Fig.~5a) is also not intuitive: when capillary number is large (10)
-    there is a final reduced area, whereas for smaller value 1, the
-    final reduced area is smaller. I would have expected that smaller
-    $Ca_E$ would empty less the vesicle. Is there any interpretation? \\
-    \\
-    \response{In the quiescent example, we prove and demonstrate
-    numerically that the steady state vesicle reduced area is
-    independent of the initial reduced area. Figure 5a shows that this
-    result holds in the presence of flow. It also shows that the
-    steady state reduced area depends on the capillary number. However,
-    the entries in the legend of Figure 5a were accidentally reversed in
-    the original submission---this has been corrected. Therefore, the
-    reviewers intuition is correct that smaller capillary number results
-    in less emptying of the vesicle.}
+and in caption to discuss this issue more clearly. Th result (Fig. 5a)
+is also not intuitive: when capillary number is large (10) there is a
+final reduced area, whereas for smaller value 1, the final reduced
+area is smaller. I would have expected that smaller Cae would empty
+less the vesicle. Is there any interpretation?"}
 
-  \item In Fig.~7b reference is made to steady state? I guess there is
-    still water flow across membrane? Or the total flux is zero? In
-    other word is the volume of the shapes shown there the same along
-    the blue solid line? Then I am confused with inset c which shows
-    variation of alpha? My question: are shapes in b along blue line
-    long term ones? Is alpha constant there? Please clarify. \\ \\
-    \response{A response}
-    \note{Is the 2D Green's function the same as the 3D green's function
-    in cylindrical coordinates.}
+\noindent
+{\bf Response:}: We have mislabeled the $Ca_E$ in figure 5:  $Ca_E=10^0$ for the solid curves and the $Ca_E=10$ for the dashed curves.
+To address the effect of Capillary number on the relaxation of a semipermeable vesicle, we have continued the simulations for the cases of $Ca_E = 10$ much further to better illustrate the evolution of reduced area towards equilibrium.
 
-  \item I do not quite understand why permeation time scale is much
-    lower for confined situations? Is pressure drop fixed, as compared
-    to previous cases? Does cell see stronger stress now? Why? If the
-    driving force is the same I do not expect such dramatic change of
-    time scale, since the mean shear stress experienced by the cell
-    remains of the same order, as before. A clear discussion of origin
-    (from stress values point of view, and why confinement would enhance
-    imposed stress) is necessary. This section is poorly discussed. \\
-    \\
-    \response{A response}
+\noindent
+{\bf Location:} A new Figure 5(a) in page 11.
+
+\item{\bf
+The referee wrote:
+``In Fig. 7 B reference is made to steady state? I guess there is
+still water flow across membrane? Or the total flux is zero? In other
+word is the volume of the shapes shown there the same along the blue
+solid line? Then I am confused with inset c which shows variation of
+alpha? My question: are shapes in b along blue line long term ones? Is
+alpha constant there? Please clarify."}
+
+\noindent
+{\bf Response:}: The shapes along the blue curve in Figure 7(b) are equilibrium shapes that enclose a constant area but with an efflux (blue) and an influx (red) that adds to zero.
+Inset c illustrates the evolution from initial  the configuration (I) to the equilibrium (shape III), which corresponds to the case with the largest displacement on the blue curve.
+To better present all these results, we have taken out the insets (c) and (d) and moved them to the new Figure 7 (a) and (b).
+The new Figure 7 (c) and (d) are the old Figure  7 (a) and (b).
+
+\noindent
+{\bf Location:} Figure 7 in page 13.
+
+\item{\bf
+The referee wrote:
+``I do not quite understand why permeation time scale is much lower
+for confined situations? Is pressure drop fixed, as compared to
+previous cases? Does cell see stronger stress now? Why? If the driving
+force is the same I do not expect such dramatic change of time scale,
+since the mean shear stress experienced by the cell remains of the
+same order, as before. A clear discussion of origin (from stress
+values point of view, and why confinement would enhance imposed
+stress) is necessary. This section is poorly discussed."}
+
+\noindent
+{\bf Response:}:  We have added new computations to illustrate the relative contributions of membrane tension and bending forces to the permeating fluxes for all cases in \S IV and \S V (see {\bf Response} to the second point), see the new Figures 9, 11, and 13.
+
+For the closely-fit channel the imposed flow at the inlet/outlet is set $U_{max}=1000$ $\mu$m/s to match the experimental conditions.
+As a result the membrane tension is dominant over membrane bending in their contribution to the permeating flux.
+For the contracting channel, the imposed flow at the inlet/outlet is smaller and yet the strong confinement still gives rise to a membrane tension that dominates in contributing to the permeating flux.
+We also added new paragraphs to discuss these new results.
+
+\noindent
+{\bf Location:} A new \S IV D in page 14, and the new Figures 9 in page 15.
+The last paragraph in page 17, and the new Figure 11 in page 17.
+The second paragraph in page 19, and the new Figure 13 in page 19.
+Second to last paragraph in page 21.
 

### 2021-05-20 vesicle_code/docs/permeableVes/Response2Refs.tex
yny1
small changes

@@
 We have revised the manuscript ``Hydrodynamics of a semipermeable inextensible membrane under flow and confinement"  
-by Bryan Quaife, Ashley Gannon and Y.-N. Young, 
+by Bryan Quaife, Ashley Gannon, and Y.-N. Young, 
 based on 
@@
 {\large \bf List of changes}
-In the following we refer to 
-Referee 1 who has four comments and Referee 2 who has a list of comments. In the revised manuscript the modifications in the text are in blue.
+In the following we refer to Referee 1 who has five comments and Referee
+2 who has three comments. In the revised manuscript the modifications in
+the text are in blue.
 
@@
 
-We thank the referee for his/her assessment of our work.  
-The following is
-our {\bf Response:} to each of the specific comments and suggestions.
+We thank the referee for their assessment of our work. The following is
+our response to each of the specific comments and suggestions.
 
@@
 The referee wrote:
-``It is stated in the introduction that stretching (due to poration…)
-give rise to enhanced membrane permeability to both water and
-macromolecules such as ATP. Regarding ATP this is possible. In normal
-conditions ATP is released thanks to protein change of conformation
-that open channels and I am not sure the evoked permeability is a
-similar phenomenon. A few words of clarification are needed."}
+``It is stated in the introduction that stretching (due to
+    poration...) give rise to enhanced membrane permeability to
+    both water and macromolecules such as ATP. Regarding ATP this is
+    possible. In normal conditions ATP is released thanks to protein
+    change of conformation that open channels and I am not sure the
+    evoked permeability is a similar phenomenon. A few words of
+    clarification are needed."}
 
@@
 
-We agree with the referee that the ATP release is mostly understood when it is through the coupling between Px1 (activated by membrane tension) and CFTR (activated by membrane deformation), and it is not well understood yet how ATP can be released by diffusing through the membrane.
-We have thus modified this sentence to avoid confusion.
+We agree with the referee that the ATP release is mostly understood when
+    it is through the coupling between Px1 (activated by membrane
+    tension) and CFTR (activated by membrane deformation), and it is not
+    yet well-understood how ATP can be released by diffusing through the
+    membrane. We have thus modified this sentence to avoid confusion.
 
 \noindent
-{\bf Location:}  The second paragraph of Introduction, five lines above Figure 1: ``....reaches the order of 2-4 mN/m, giving rise to
-membrane rupture and leakage of macromolecules (see Razizadeh {\it et al. }$^{20}$ and references therein)."
+{\bf Location:}  The second paragraph of the Introduction, five lines
+    above Figure 1: ``....reaches the order of 2-4 mN/m, giving rise to
+    membrane rupture and leakage of macromolecules (see Razizadeh {\it
+    et al. }$^{20}$ and references therein)."
 
@@
 \noindent
-{\bf Response:}: We thank the referee for this point.
-In our formulation, the permeation flux is proportional to the hydrostatic pressure and the normal component of the membrane force, which is the capillary pressure due to the Lagrange multiplier tension.
-The tangential force component due to tension field does not contribute to the permeation flux.
-To elucidate the relative contribution between the hydrostatic pressure and the normal component of the membrane force, we have conducted computations
-added a short paragraph to illustrate how the relative contributions are in all cases.
+{\bf Response:}: We thank the referee for this point. In our
+    formulation, the permeation flux is proportional to the hydrostatic
+    pressure and the normal component of the membrane force, which is
+    the capillary pressure due to the Lagrange multiplier tension. The
+    tangential force component due to tension field does not contribute
+    to the permeation flux. To elucidate the relative contribution
+    between the hydrostatic pressure and the normal component of the
+    membrane force, we have conducted computations and added a short
+    paragraph to illustrate the relative contributions in all cases.
 
@@
 \noindent
-{\bf Response:}: We have mislabeled the $Ca_E$ in figure 5:  $Ca_E=10^0$ for the solid curves and the $Ca_E=10$ for the dashed curves.
-To address the effect of Capillary number on the relaxation of a semipermeable vesicle, we have continued the simulations for the cases of $Ca_E = 10$ much further to better illustrate the evolution of reduced area towards equilibrium.
+{\bf Response:}: We have mislabeled the $Ca_E$ in Figure 5:  $Ca_E=10^0$
+for the solid curves and the $Ca_E=10$ for the dashed curves. To address
+the effect of Capillary number on the relaxation of a semipermeable
+vesicle, we have continued the simulations for the cases of $Ca_E = 10$
+much further to better illustrate the evolution of reduced area towards
+equilibrium.
 
@@
 \noindent
-{\bf Response:}: The shapes along the blue curve in Figure 7(b) are equilibrium shapes that enclose a constant area but with an efflux (blue) and an influx (red) that adds to zero.
-Inset c illustrates the evolution from initial  the configuration (I) to the equilibrium (shape III), which corresponds to the case with the largest displacement on the blue curve.
-To better present all these results, we have taken out the insets (c) and (d) and moved them to the new Figure 7 (a) and (b).
-The new Figure 7 (c) and (d) are the old Figure  7 (a) and (b).
+{\bf Response:}: The shapes along the blue curve in Figure 7(b) are
+equilibrium shapes that enclose a constant area but with an efflux
+(blue) and an influx (red) that adds to zero. Inset (c) illustrates the
+evolution from initial  the configuration (I) to the equilibrium (shape
+III), which corresponds to the case with the largest displacement on the
+blue curve. To better present all these results, we have taken out the
+insets (c) and (d) and moved them to the new Figure 7(a) and (b). The
+new Figure 7(c) and (d) are the old Figure 7(a) and (b).
 
@@
 
-For the closely-fit channel the imposed flow at the inlet/outlet is set $U_{max}=1000$ $\mu$m/s to match the experimental conditions.
-As a result the membrane tension is dominant over membrane bending in their contribution to the permeating flux.
-For the contracting channel, the imposed flow at the inlet/outlet is smaller and yet the strong confinement still gives rise to a membrane tension that dominates in contributing to the permeating flux.
-We also added new paragraphs to discuss these new results.
+For the closely-fit channel the imposed flow at the inlet/outlet is
+$U_{max}=1000$ $\mu$m/s to match the experimental conditions. As a
+result the membrane tension is dominant over membrane bending in their
+contribution to the permeating flux. For the contracting channel, the
+imposed flow at the inlet/outlet is smaller and yet the strong
+confinement still gives rise to a membrane tension that dominates in
+contributing to the permeating flux. We also added new paragraphs to
+discuss these new results.
 
@@
 \noindent
-{\bf Response:}: The referee is correct that numerical simulations of two-dimensional fluid flow could be ideal and the connection to the real experiments is qualitative at best.
-The studies of two-dimensional vesicle hydrodynamics, however, have shown that the connection to real experiments or 3d simulations could be more than purely qualitative.
-For example, for a vesicle in a planar shear flow, the transition from tank-treading to tumbling is predicted in both 2 and 3-dimensions, at similar viscosity contrast.
-Ghiliotti, Biben and Misbah (JFM, 2010) showed that results for a two-dimensional vesicle could be corrected systematically to agree with the three-dimensional results.
-More recently, the two-dimensional results in Zhang, Shen, Hogan, Barakat and Misbah are also in more than qualitative agreement with real experiments (Biophys.
-J, 2018).
+{\bf Response:}: The referee is correct that numerical simulations of
+    two-dimensional fluid flow could be ideal and the connection to the
+    real experiments is qualitative at best. The studies of
+    two-dimensional vesicle hydrodynamics, however, have shown that the
+    connection to real experiments or 3D simulations could be more than
+    purely qualitative. For example, for a vesicle in a planar shear
+    flow, the transition from tank-treading to tumbling is predicted in
+    both 2- and 3-dimensions, at similar viscosity contrast. Ghiliotti,
+    Biben, and Misbah (JFM, 2010) showed that results for a
+    two-dimensional vesicle could be corrected systematically to agree
+    with the three-dimensional results. More recently, the
+    two-dimensional results in Zhang, Shen, Hogan, Barakat, and Misbah
+    are also in more than qualitative agreement with real experiments
+    (Biophys.~J, 2018).
 
@@
 
-\item {\bf The referee wrote: ``On the last page: “We observe lose of”è“We observe loss of”."}
+\item {\bf The referee wrote: ``On the last page: ``We observe lose
+  of"$\rightarrow$``We observe loss of"."}
 
 \noindent
-{\bf Response:}: \end{enumerate}
+{\bf Response:}: Thank you for catching this error. It has been
+corrected.
+
+\end{enumerate}
 

### 2021-05-20 vesicle_code/docs/permeableVes/Response2Refs.tex
yny2

--- 2021-05-20 vesicle_code/docs/permeableVes/Response2Refs.tex
@@
 The following is
-our {\bf Response:} to each of the specific comments and suggestions.
+our response to each of the specific comments and suggestions.
 
@@
 {\bf Response:}: We thank the referee for this question.
-The referee is indeed correct that in a 2D system the system remains constant in the $z$ direction indefinitely.
-Consequently it is customary to focus on the system on a plane, and the membrane tension is the membrane force per unit length (the length in the $z$ direction).
-This means that, after the division by the length in the third direction, the membrane tension on the plane is force per length.
+The referee is indeed correct that in a 2D system the system remains constant in the $z$ direction.
+Consequently it is customary to focus on the 2D system on a plane, and the membrane tension is the membrane force per unit length (the length in the $z$ direction).
+This means that, after the division by the length in the third ($z$) direction, the membrane tension in the plane is force per length.
 
@@
 \noindent
-{\bf Response:}: \end{enumerate}
+{\bf Response:} The typo is corrected.
+
+\noindent
+{\bf Location:} Second paragraph in page 21.
+
+ \end{enumerate}
 

### 2021-05-20 vesicle_code/docs/permeableVes/reviewer2.tex
yny2

@@
 \begin{document}
-We thank the reviewer for reviewing our manuscript \textit{Hydrodynamics
-of a semipermeable inextensible membrane under flow and confinement}.
-Below is a point-by-point response addressing each of the referee's
-comments.
+
+We thank the referee for his/her assessment of our work.  
+The following is
+our response to each of the specific comments and suggestions.
+
+{\bf The referee wrote:
+In this theoretical work, a 2D vesicle is simulated (via boundary elements) in unbounded and confined flows, while accounting for the finite permeability of the membrane to water.
+While this additional physics has, expectedly, little to no impact on the long-time physics (shape, tension) of vesicles in unbounded flows, in confined flows a marked dependence is observed on the permeability rate.
+In straight channel flow, the rate of water loss is proportional to the residence time in the channel, resulting in a reduction of the 2D reduced area at the channel outlet.
+In contraction flow, a high permeability rate (as well as a large pressure gradient) is required to force the vesicle through the nozzle and emerge in the open chamber downstream.
+
+Overall, the paper is well written and the main results are clearly presented.
+A decent amount of time is spent covering vesicles in quiescent fluids and unbounded flows, which are less interesting than Section V, which includes the main interesting results on confined flows.
+However, these earlier sections help to paint a cohesive picture to put these later results in a clear context and, for that reason, their addition is welcome.
+My only real critique of the article is that all of the results are based on 2D simulations and, therefore, their applicability to real 3D systems is limited.
+However, the novelty of adding finite membrane permeability to the 2D boundary element context (which, to the best of my knowledge, has not been done before) merits publication of this article in Physical Review Fluids.
+I am therefore recommending this article for publication subject to optional revision (see my comments below).}
+
+\noindent
+{\bf Response:}: We thank the referee for the confirmation that the topic is interesting and results are useful.
+
 \begin{enumerate}
-  \item I am slightly confused as to how the length and time scales are
-    derived from the parameters discussed on page 4. As the simulation
-    is 2D, it would seem to me that all physical parameters can only be
-    defined on a ``per unit of length" basis. E.g., for a 2D vesicle
-    contour, the surface tension is actually a line tension with units
-    of N, not N/m. Could the authors clarify this?  In particular,
-    reference is often made to how long things will take in the results
-    (seconds, minutes, days, weeks, etc.), which is why I ask how these
-    time scales are obtained. \\ \\
-    \response{A response}
 
-  \item Could the authors shed some insight as to how these 2D
-    simulations could be reliably connected to real experiments on any
-    quantitative basis? Or is the connection purely qualitative? \\ \\
-    \response{A response}
+\item {\bf The referee wrote: ``1.
+I am slightly confused as to how the length and time scales are derived from the parameters discussed on page 4.
+As the simulation is 2D, it would seem to me that all physical parameters can only be defined on a “per unit of length” basis.
+E.g., for a 2D vesicle contour, the surface tension is actually a line tension with units of N, not N/m.
+Could the authors clarify this?
+In particular, reference is often made to how long things will take in the results (seconds,
+minutes, days, weeks, etc.), which is why I ask how these time scales are obtained."}
 
-  \item On the last page: ``We observe lose of" $\rightarrow$ ``We
-    observe loss of". \\ \\
-    \response{Thank you for noticing this typo. It is corrected.}
+\noindent
+{\bf Response:}: We thank the referee for this question.
+The referee is indeed correct that in a 2D system the system remains constant in the $z$ direction.
+Consequently it is customary to focus on the 2D system on a plane, and the membrane tension is the membrane force per unit length (the length in the $z$ direction).
+This means that, after the division by the length in the third ($z$) direction, the membrane tension in the plane is force per length.
+
+The dimensionless group of this system is independent of the spatial dimensions of the system.
+In the absence of any external flow, we have adopted the initial vesicle size $R_0$ for a length scale,  the elastic relaxation in balance with the viscous dissipation at  length scale $R_0$ for a time scale $\tau$, and the elastic force at length scale $R_0$ for membrane tension.
+The dimensionless permeability is the hydraulic permeability scaled accordingly.
+Such scaling is natural for the quiescent cases.
+We used the same scaling for other cases for consistency in presentation to avoid confusion.
+
+\noindent
+{\bf Locations:} Second to last paragraph in page 4, fifth line in this paragraph, ``Under this nondimensionalization suitable for a vesicle in a quiescent flow".
+
+\item {\bf The referee wrote: ``2.
+Could the authors shed some insight as to how these 2D simulations could be reliably connected to real experiments on any quantitative basis?
+Or is the connection purely
+qualitative?"}
+
+\noindent
+{\bf Response:}: The referee is correct that numerical simulations of two-dimensional fluid flow could be ideal and the connection to the real experiments is qualitative at best.
+The studies of two-dimensional vesicle hydrodynamics, however, have shown that the connection to real experiments or 3d simulations could be more than purely qualitative.
+For example, for a vesicle in a planar shear flow, the transition from tank-treading to tumbling is predicted in both 2 and 3-dimensions, at similar viscosity contrast.
+Ghiliotti, Biben and Misbah (JFM, 2010) showed that results for a two-dimensional vesicle could be corrected systematically to agree with the three-dimensional results.
+More recently, the two-dimensional results in Zhang, Shen, Hogan, Barakat and Misbah are also in more than qualitative agreement with real experiments (Biophys.
+J, 2018).
+
+\noindent
+{\bf Location:} Second paragraph in the new Introduction in page 2.
+
+\item {\bf The referee wrote: ``On the last page: “We observe lose of”è“We observe loss of”."}
+
+\noindent
+{\bf Response:} The typo is corrected.
+
+\noindent
+{\bf Location:} Second paragraph in page 21.
 
@@
 
+%We thank the reviewer for reviewing our manuscript \textit{Hydrodynamics
+%of a semipermeable inextensible membrane under flow and confinement}.
+%Below is a point-by-point response addressing each of the referee's
+%comments.
+%\begin{enumerate}
+%  \item I am slightly confused as to how the length and time scales are
+%    derived from the parameters discussed on page 4. As the simulation
+%    is 2D, it would seem to me that all physical parameters can only be
+%    defined on a ``per unit of length" basis. E.g., for a 2D vesicle
+%    contour, the surface tension is actually a line tension with units
+%    of N, not N/m. Could the authors clarify this?  In particular,
+%    reference is often made to how long things will take in the results
+%    (seconds, minutes, days, weeks, etc.), which is why I ask how these
+%    time scales are obtained. \\ \\
+%    \response{A response}
+%
+%  \item Could the authors shed some insight as to how these 2D
+%    simulations could be reliably connected to real experiments on any
+%    quantitative basis? Or is the connection purely qualitative? \\ \\
+%    \response{A response}
+%
+%  \item On the last page: ``We observe lose of" $\rightarrow$ ``We
+%    observe loss of". \\ \\
+%    \response{Thank you for noticing this typo. It is corrected.}
+%
+%
+%\end{enumerate}
+
 \end{document}

### 2021-05-20 vesicle_code/docs/permeableVes/Response2Refs.tex

--- 2021-05-20 vesicle_code/docs/permeableVes/Response2Refs.tex
@@
 \noindent
-{\bf Response:}: Thank you for catching this error. It has been
+{\bf Response:} Thank you for catching this error. It has been
 corrected.
+
+\noindent
+{\bf Location:} Second paragraph in page 21.
 

### 2021-05-20 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex

@@
 %between interior and exterior fluids. 
-For each of the cases in \S~\ref{sec:free_space} and \ref{sec:confinement}, 
-we examine the contribution of the permeating flux from membrane tension and membrane bending forces.
-In free space, we find that both membrane forces contribute comparably in the simulations.
-As the vesicle hydrodynamics reaches an equilibrium, the two contributions add to zero as the permeating flux integrates to zero rate of change of the reduced area.
-Under strong confinement, however, we find the membrane tension to contribute much more to the permeating flux than the membrane bending.
-For a vesicle going through a closely-fit channel the maximum flow velocity is $U_{max}=1000$ $\mu$m/s is chosen to match the experimental conditions.
-Such a large flow velocity contributes to large membrane tension, and thus reducing the time scale for change in water content.
-For a vesicle going through a contracting channel, we used a smaller $U_{max}$ than in the experiments (where the three-dimensional channel contracts in both cross-stream directions) to examine the effect of membrane permeability.
-We find that, due to the strong confinement, the membrane tension still dominates the membrane bending in contributing to the permeating flux as in the closely-fit channel.
+For each of the cases in \S~\ref{sec:free_space} and
+\S~\ref{sec:confinement}, we examine the contribution of the permeating
+flux from membrane tension and membrane bending forces. In free space,
+we find that both membrane forces contribute comparably in the
+simulations. As the vesicle hydrodynamics reaches an equilibrium, the
+two contributions add to zero as the permeating flux integrates to zero
+rate of change of the reduced area.  Under strong confinement, however,
+we find the membrane tension to contribute much more to the permeating
+flux than the membrane bending. For a vesicle going through a
+closely-fit channel the maximum flow velocity is $U_{\max}=1000$
+$\mu$m/s is chosen to match the experimental conditions. Such a large
+flow velocity contributes to large membrane tension, and thus reducing
+the time scale for change in water content. For a vesicle going through
+a contracting channel, we used a smaller $U_{\max}$ than in the
+experiments (where the three-dimensional channel contracts in both
+cross-stream directions) to examine the effect of membrane permeability.
+We find that, due to the strong confinement, the membrane tension still
+dominates the membrane bending in contributing to the permeating flux as
+in the closely-fit channel.
 }

### 2021-05-20 vesicle_code/docs/permeableVes/Response2Refs.tex
yny3

@@
 Below is a summary of the revisions made in the new manuscript.
-The detailed {\bf Response:}s to comments of referees are listed in 
-{\bf Response:} to Referee 1 and Referee 2.
+The detailed responses to comments of referees are listed in 
+responses to Referee 1 and Referee 2.
 We hope that the referees and the
@@
 2 who has three comments. In the revised manuscript the modifications in
-the text are in blue.
+the text are in magenta.
 
@@
 The referee is indeed correct that in a 2D system the system remains constant in the $z$ direction.
-Consequently it is customary to focus on the 2D system on a plane, and the membrane tension is the membrane force per unit length (the length in the $z$ direction).
+A two-dimensional vesicle membrane is a tube that is infinitely long in the $z$ direction.
+On this infinitely long tube (constant in $z$), the line tension is the total tangential force along the circumferential surface.
+Divide this line tension by the length of the tube would give us the membrane tension (force per unit length) in the $x-y$ plane.
+%
+%Consequently it is customary to focus on the 2D system on a plane, and the membrane tension is the membrane force per unit length (the length in the $z$ direction).
 This means that, after the division by the length in the third ($z$) direction, the membrane tension in the plane is force per length.

### 2021-05-20 vesicle_code/docs/permeableVes/Response2Refs.tex
yny4

@@
 \begin{enumerate}
-\item{change 1}
-\item{change 2}
+\item{Second paragraph in page 2, ``....giving rise to membrane rupture and leakage of macromolecules...".}
+
+\item{Second to last paragraph in page 4, ``....suitable for a vesicle in a quiescent flow,"}
+
+\item{New Figure 5(a).}
+
+\item{New Figures 7.}
+
+\item{New \S IV D.}
+
+\item{New Figures 9.}
+
+\item{New Figures 11, and the paragraph above the new Figures 11 in page 17.}
+
+\item{New Figures 13, and the paragraph above the new Figures 13 in page 19.}
+
+\item{Second to last paragraph in page 21.}
+
+\item{Last paragraph in the Discussion session.}
+
 \end{enumerate}
@@
 A two-dimensional vesicle membrane is a tube that is infinitely long in the $z$ direction.
-On this infinitely long tube (constant in $z$), the line tension is the total tangential force along the circumferential surface.
+On this infinitely long tube (of which the cross section is independent of $z$), the line tension is the total tangential force along the circumferential surface.
 Divide this line tension by the length of the tube would give us the membrane tension (force per unit length) in the $x-y$ plane.
@@
 \noindent
-{\bf Location:} Second paragraph in the new Introduction in page 2.
+{\bf Location:} Last paragraph in the Discussion session.
 

### 2021-05-20 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
yny4

@@
 These results provide insight into quantifying the effects of membrane permeability on vesicle hydrodynamics in microfluidics.
+%\textcolor{magenta}{In the literature studies of
+%two-dimensional vesicle hydrodynamics revealed salient features that are also observed in three-dimensions, such as a vesicle in shear flow \cite{GhigliottiBibenMisbah2020_JFM,AgarwalBiros2020_PRF}.
+Even though quantitative connection to  experimental observation requires some adjustment, results from simulating two-dimensional vesicle hydrodynamics can be insightful for the full three-dimensional simulations of a semipermeable vesicle that we are currently undertaking.
+%}
 %
@@
 
+\textcolor{magenta}{In the literature studies of
+two-dimensional vesicle hydrodynamics revealed salient features that are also observed in three-dimensions, such as a vesicle in shear flow \cite{GhigliottiBibenMisbah2010_JFM,AgarwalBiros2020_PRF}.
+Even though quantitative connection to  experimental observation requires some adjustment, results from simulating two-dimensional vesicle hydrodynamics can be insightful for the full three-dimensional simulations of a semipermeable vesicle that we are currently undertaking.
+}
+
 %While the solute dynamics

### 2021-05-20 vesicle_code/docs/permeableVes/Response2Refs.tex
fixed a few typos

@@
 \noindent
-{\bf Response:}: We thank the referee for this point. In our
+{\bf Response:} We thank the referee for this point. In our
     formulation, the permeation flux is proportional to the hydrostatic
@@
 \noindent
-{\bf Response:}: We have mislabeled the $Ca_E$ in Figure 5:  $Ca_E=10^0$
+{\bf Response:} We have mislabeled the $Ca_E$ in Figure 5:  $Ca_E=10^0$
 for the solid curves and the $Ca_E=10$ for the dashed curves. To address
@@
 \noindent
-{\bf Response:}: The shapes along the blue curve in Figure 7(b) are
+{\bf Response:} The shapes along the blue curve in Figure 7(b) are
 equilibrium shapes that enclose a constant area but with an efflux
@@
 \noindent
-{\bf Response:}:  We have added new computations to illustrate the relative contributions of membrane tension and bending forces to the permeating fluxes for all cases in \S IV and \S V (see {\bf Response} to the second point), see the new Figures 9, 11, and 13.
+{\bf Response:}  We have added new computations to illustrate the relative contributions of membrane tension and bending forces to the permeating fluxes for all cases in \S IV and \S V (see {\bf Response} to the second point), see the new Figures 9, 11, and 13.
 
@@
 
-We thank the referee for his/her assessment of our work.  
-The following is
+We thank the referee for their assessment of our work.  The following is
 our response to each of the specific comments and suggestions.
@@
 \noindent
-{\bf Response:}: The referee is correct that numerical simulations of
+{\bf Response:} The referee is correct that numerical simulations of
     two-dimensional fluid flow could be ideal and the connection to the

### 2021-05-20 vesicle_code/docs/permeableVes/Response2Refs.tex
yny5

@@
 
+    It is true that in some cases the two-dimensional vesicle hydrodynamics may have very little inference to the corresponding three-dimensional vesicle hydrodynamics.
+We have undertaken the full three-dimensional simulation of a semipermeable vesicle going through strong confinement, where the three-dimensional effects may be important.
+
 \noindent

### 2021-05-20 vesicle_code/docs/permeableVes/reviewer2.tex
yny5

@@
 
+It is true that in some cases the two-dimensional vesicle hydrodynamics may have very little inference to the corresponding three-dimensional vesicle hydrodynamics.
+We have undertaken the full three-dimensional simulation of a semipermeable vesicle going through strong confinement, where the three-dimensional effects may be important.
+
 \noindent

### 2023-03-05 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
adding soft matter version of paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%This is the LaTeX ARTICLE template for RSC journals
%Copyright The Royal Society of Chemistry 2016
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[twoside,twocolumn,9pt]{article}
\usepackage{amsfonts}
\usepackage{extsizes}
\usepackage[super,sort&compress,comma]{natbib} 
\usepackage[version=3]{mhchem}
\usepackage[left=1.5cm, right=1.5cm, top=1.785cm, bottom=2.0cm]{geometry}
\usepackage{balance}
\usepackage{mathptmx}
\usepackage{sectsty}
\usepackage{stmaryrd}
\usepackage{graphicx} 
\usepackage{lastpage}
\usepackage[format=plain,justification=justified,singlelinecheck=false,font={stretch=1.125,small,sf},labelfont=bf,labelsep=space]{caption}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{fnpos}
\usepackage[english]{babel}
\usepackage{pgfplots}
\usetikzlibrary{calc}
\usepackage{dsfont}

\addto{\captionsenglish}{%
  \renewcommand{\refname}{Notes and references}
}
\usepackage{array}
\usepackage{droidsans}
\usepackage{charter}
\usepackage[T1]{fontenc}
%\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{setspace}
\usepackage[compact]{titlesec}
\usepackage{hyperref}
%\usepackage{subcaption}
%%%Please don't disable any packages in the preamble, as this may cause the template to display incorrectly.%%%

\usepackage{epstopdf}%This line makes .eps figures into .pdf - please comment out if not required.

\definecolor{cream}{RGB}{222,217,201}

\usepackage{todonotes}
%%%Shorthands
\newcommand{\ff}{\mathbf{f}}
%\renewcommand{\SS}{\mathcal{S}}
%\newcommand{\DD}{\mathcal{D}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\nn}{\mathbf{n}}
\renewcommand{\tt}{\mathbf{t}}
\newcommand{\NN}{\mathcal{N}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbb{R}}
\renewcommand{\ss}{\mathbf{s}}
\newcommand{\uu}{\mathbf{u}}
%\renewcommand{\SS}{\mathcal{S}}
\newcommand{\TT}{\mathbf{T}}
\newcommand{\UU}{\mathbf{U}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\yy}{\mathbf{y}}

\newcommand{\subfigimg}[3][,]{%
  \setbox1=\hbox{\includegraphics[#1]{#3}}% Store image in box
  \leavevmode\rlap{\usebox1}% Print image
  \rlap{\hspace*{0pt}\raisebox{\dimexpr\ht1-0\baselineskip}{\bf
  \normalsize #2}}% Print label
  \phantom{\usebox1}% Insert appropriate spacing
}

\begin{document}

\pagestyle{fancy}
\thispagestyle{plain}
\fancypagestyle{plain}{
%%%HEADER%%%
\renewcommand{\headrulewidth}{0pt}
}
%%%END OF HEADER%%%

%%%PAGE SETUP - Please do not change any commands within this section%%%
\makeFNbottom
\makeatletter
\renewcommand\LARGE{\@setfontsize\LARGE{15pt}{17}}
\renewcommand\Large{\@setfontsize\Large{12pt}{14}}
\renewcommand\large{\@setfontsize\large{10pt}{12}}
\renewcommand\footnotesize{\@setfontsize\footnotesize{7pt}{10}}
\makeatother

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand\footnoterule{\vspace*{1pt}% 
\color{cream}\hrule width 3.5in height 0.4pt \color{black}\vspace*{5pt}} 
\setcounter{secnumdepth}{5}

\makeatletter 
\renewcommand\@biblabel[1]{#1}            
\renewcommand\@makefntext[1]% 
{\noindent\makebox[0pt][r]{\@thefnmark\,}#1}
\makeatother 
\renewcommand{\figurename}{\small{Fig.}~}
\sectionfont{\sffamily\Large}
\subsectionfont{\normalsize}
\subsubsectionfont{\bf}
\setstretch{1.125} %In particular, please do not alter this line.
\setlength{\skip\footins}{0.8cm}
\setlength{\footnotesep}{0.25cm}
\setlength{\jot}{10pt}
\titlespacing*{\section}{0pt}{4pt}{4pt}
\titlespacing*{\subsection}{0pt}{15pt}{1pt}
%%%END OF PAGE SETUP%%%

%%%FOOTER%%%
\fancyfoot{}
\fancyfoot[LO,RE]{\vspace{-7.1pt}\includegraphics[height=9pt]{head_foot/LF}}
\fancyfoot[CO]{\vspace{-7.1pt}\hspace{13.2cm}\includegraphics{head_foot/RF}}
\fancyfoot[CE]{\vspace{-7.2pt}\hspace{-14.2cm}\includegraphics{head_foot/RF}}
\fancyfoot[RO]{\footnotesize{\sffamily{1--\pageref{LastPage} ~\textbar  \hspace{2pt}\thepage}}}
\fancyfoot[LE]{\footnotesize{\sffamily{\thepage~\textbar\hspace{3.45cm} 1--\pageref{LastPage}}}}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt} 
\renewcommand{\footrulewidth}{0pt}
\setlength{\arrayrulewidth}{1pt}
\setlength{\columnsep}{6.5mm}
\setlength\bibsep{1pt}
%%%END OF FOOTER%%%

%%%FIGURE SETUP - please do not change any commands within this section%%%
\makeatletter 
\newlength{\figrulesep} 
\setlength{\figrulesep}{0.5\textfloatsep}

\newcommand{\topfigrule}{\vspace*{-1pt}% 
\noindent{\color{cream}\rule[-\figrulesep]{\columnwidth}{1.5pt}} }

\newcommand{\botfigrule}{\vspace*{-2pt}% 
\noindent{\color{cream}\rule[\figrulesep]{\columnwidth}{1.5pt}} }

\newcommand{\dblfigrule}{\vspace*{-1pt}% 
\noindent{\color{cream}\rule[-\figrulesep]{\textwidth}{1.5pt}} }

\makeatother
%%%END OF FIGURE SETUP%%%

%%%TITLE, AUTHORS AND ABSTRACT%%%
\twocolumn[
  \begin{@twocolumnfalse}
{\includegraphics[height=30pt]{head_foot/SM}\hfill\raisebox{0pt}[0pt][0pt]{\includegraphics[height=55pt]{head_foot/RSC_LOGO_CMYK}}\\[1ex]
\includegraphics[width=18.5cm]{head_foot/header_bar}}\par
\vspace{1em}
\sffamily
\begin{tabular}{m{4.5cm} p{13.5cm} }

\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Hydrodynamics of Multicomponent Vesicles Under Strong Confinement}} \\
\vspace{0.3cm} & \vspace{0.3cm} \\

 & \noindent\large{Ashley Gannon,\textit{$^{a}$} Yuan-Nan
  Young,\textit{$^{b}$} and Bryan Quaife\textit{$^{\ast}${$^{a}$}}} \\
 %Author names go here instead of "Full name", etc.

\includegraphics{head_foot/dates} & \noindent\normalsize{The abstract should be a single paragraph which summarises the content of the article. Any references in the abstract should be written out in full \textit{e.g.}\ [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].} \\%The abstrast goes here instead of the text "The abstract should be..."

\end{tabular}

 \end{@twocolumnfalse} \vspace{0.6cm}
  ]
%%%END OF TITLE, AUTHORS AND ABSTRACT%%%

%%%FONT SETUP - please do not change any commands within this section
\renewcommand*\rmdefault{bch}\normalfont\upshape
\rmfamily
\section*{}
\vspace{-1cm}

%%%FOOTNOTES%%%

\footnotetext{\textit{$^{a}$~Department of Scientific Computing, Florida State University, Tallahassee, FL, 32306, USA. Email: bquaife@fsu.edu}}
\footnotetext{\textit{$^{b}$~Department of Mathematical Sciences, New Jersey Institute of Technology, Newark, NJ, 07102, USA. Email: yyoung@njit.edu}}

%Please use \dag to cite the ESI in the main text of the article.
%If you article does not have ESI please remove the the \dag symbol from the title and the footnotetext below.
%\footnotetext{\dag~Electronic Supplementary Information (ESI) available: [details of any supplementary information available should be included here]. See DOI: 10.1039/cXsm00000x/}
%additional addresses can be cited as above using the lower-case letters, c, d, e... If all authors are from the same address, no letter is required

%\footnotetext{\ddag~Additional footnotes to the title and authors can be included \textit{e.g.}\ `Present address:' or `These authors contributed equally to this work' as above using the symbols: \ddag, \textsection, and \P. Please place the appropriate symbol next to the author's name and include a \texttt{\textbackslash footnotetext} entry in the the correct place in the list.}

%%%END OF FOOTNOTES%%%

%%%MAIN TEXT%%%%
\section{\label{sec:Introduction}Introduction}
Soft particles, such as vesicles, display rich dynamics when they are subjected to different types of physical processes. These dynamics are affected by parameters such a the capillary number, reduced volume, and confinement ratio. Understanding these dynamics is critical to understanding biophysical and microfluidic processes. For example, a vesicle's reduced area and viscosity contrast will determine if it undergoes tank treading, swinging, or tumbling in a shear flow~\cite{nog-gom2005}. Transitions in the vesicle shape occur in non-linear parabolic flows~\cite{kao-bir-mis2009, dan-vla-mis2009}, and these shapes include axisymmetric bullets or parachutes, and asymmetric parachutes. More recently, groups have considered these transitions when vesicles are suspended in a channel or pipe flow~\cite{lyu-che-far-jae-mis-leo2023, aga-bir2020, qua-gan-you2021, abb-far-nai-ezz-ben-mis2022}. These dynamics include snaking and swirling behaviors; croissant and slipper shapes; and semipermeability.

Groups have also studied the behaviors of a vesicle that is composed of different types of lipids and proteins. The presence of different lipid species has been used to model different processes including the bending stiffness, spontaneous curvature, and adhesion potential~\cite{zha-das-du2010, tan-yan-ima2011}. The dynamics of these multicomponent vesicles include phase treading, tumbling with no viscosity contrast, swinging, budding, and fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006, ger-sal-spa2022, lip1992, urs-klu-phi2009}. In addition to the aforementioned numerical studies, these dynamics have been observed in experiments~\cite{bag-sun2009, yan-ima-tan2010, yan-ima-tan2008, dre-jah-bob-spa-gop2021}.

In this paper, we extend the work of Liu et al.~\cite{liu-mar-li-vee-low2017} who performed a thorough investigation of how key dimensionless numbers, including the reduced area, capillary number, and the floppy-to-stiff ratio, affect the dynamics of a multicomponent vesicle in an unbounded linear shear flow. What is missing from the literature, and what we address in this work, is the effect of strong confinement on a two-dimensional multicomponent vesicle. Using numerical simulations, we show how the vesicle's reduced area and its lipid composition affect the dynamics in two strongly confined geometries.

The remainder of the paper is organized as follows. Section~\ref{sec:Formulation} describes the model for the two-dimensional multicomponent vesicle. We introduce a new parameterization of the bending modulus that is necessary to avoid unphysical negative bending stiffness. Section~\ref{sec:NumericalMethods} describes numerical methods and also defines the techniques we use to define the excess pressure, lubrication layer width, and tank treading velocity. Section~\ref{sec:results} demonstrates the effects of strong confinement on multicomponent vesicles. Finally, concluding remarks are made in Section~\ref{sec:conclusion}.

%\citet{yan-ima-tan2010} perform experiments with multicomponent GUVs. They observe phase separation and budding of vesicles with a small reduced volume. However, the budding often requires a significant amount of time (tens of minutes), but ours occur much earlier in the contracting example by using narrow constrictions. Equations (2)--(5) shows a model similar to ours, and they use a linear dependence between the bending modulus and lipid concentration in the paragraph immediately after these equations. The include an energy term that depends on the difference in area between the inner and outer monolayer of lipids. Osmotic gradients are used to control the vesicle volume.

%\citet{yan-ima-tan2008} Similar type work as~\cite{yan-ima-tan2010}.

%\citet{dre-jah-bob-spa-gop2021} uses multicomponent GUVs to create necking, and use this to understand cell division.

%\citet{tan-yan-ima2011} describes the shape deformation and phase separation dynamics of a two- component membrane whose bending moduli depend on the local composition of the lipids.

%\citet{lip1992} considers the dynamics and budding of lipid bilayers

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:Formulation}Formulation}
We consider a single multicomponent vesicle $\omega$ with boundary $\gamma$ suspended in a confined geometry $\Omega \subset \RR^2$ with boundary $\Gamma$ (Figure~\ref{fig:schematic}).
\begin{figure}[H]
    \centering
    \includegraphics[trim = 0.3cm 0cm 1cm 0cm, clip=true,width=0.9\columnwidth]{figures/schematic.pdf}
    \todo[inline]{Need to improve this figure. Vesicle should be multicomponent. Put greek letter $\gamma$ in black instead of red}
    \caption{\label{fig:schematic}\small A single multicomponent vesicle with boundary $\gamma$ suspended in a domain $\Omega$ with boundary $\Gamma$. The vesicle dynamics are determined by a combination of phase, bending, and tension energies, and an imposed flow on $\Gamma$.}
\end{figure}
The fluid is assumed to have zero Reynolds number and is therefore governed by the incompressible Stokes equations
\begin{align}
    \nabla \cdot \TT = 0 \quad \text{and} \quad \nabla \cdot \uu = 0, 
        \quad \xx \in \Omega \backslash \gamma,
\end{align}
where $\TT = -p\mathbf{I} + \mu\left(\nabla \uu + \nabla \uu^T \right)$ is the hydrodynamic stress tensor, $\uu$ is the velocity, $p$ is the pressure, and $\mu$ is the fluid viscosity. Across the vesicle membrane, the velocity is continuous while the membrane and hydrodynamic forces balance
\begin{align}
    \llbracket \uu \rrbracket = 0, \quad \llbracket \TT\nn \rrbracket = \ff, \quad \xx \in \gamma,
\end{align}
where $\ff$ is the total membrane force and $\nn$ is the outward unit normal of $\gamma$. A no-slip and local inextensibility condition on $\gamma$ is imposed
\begin{align}
    \frac{d\xx}{dt} = \uu(\xx) \quad \text{and} \quad \nabla_{\gamma} \cdot \uu = 0,
    \quad \xx \in \gamma,
\end{align}
where $\xx(s,t)$ is the arclength parameterization of $\gamma$. Along the solid wall $\Gamma$, we impose a Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a Hagen–Poiseuille flow at the inlet and outlet,
\begin{align}
    \UU(\xx) = \chi \left(1 - \left(\frac{y}{W}\right)^2 \right), \quad \xx = (x,y) \in \Gamma,
\end{align}
and $\UU$ is zero along the top and bottom of the channel. $W$ is the width of the channel and $\chi$ is the maximum velocity.

We nondimensionalize the governing equations with a characteristic length scale $R_0 = 10^{-6}$~m, a maximum bending stiffness $b_{\max} = 10^{-19}$~J, and fluid viscosity $\mu = 5 \times 10^{-2}$~kg/ms. The resulting time scale is $\mu R_0^3/b_{\max} = 0.5$~s, the velocity scale is $b_{\max}/\mu R_0^2=2$~$\mu$m/s, the pressure scale is $b_{\max}/R_0^3 = 10^{-1}$~Pa, and the tension scale is $b_{\max}/R_0^2 = 10^{-7}$~N/m. A critical dimensionless parameter for the vesicle shape is its reduced area, $\alpha$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Constitutive equations}
Using the same model as~\citet{liu-mar-li-vee-low2017} and~\citet{soh-tse-li-voi-low2010}, the membrane forces depend on the Helfrich energy, line tension, and phase energy. The phase and bending energies are coupled through the bending modulus. In particular, the individual energies are
\begin{align}
    E_b &= \frac{1}{2}\int_{\gamma} b(u) \kappa^2 \, ds, \\
    E_t &= \int_{\gamma} \sigma \, ds, \\
    E_p &= \frac{a}{\epsilon}\int_{\gamma}\left(
    f(u) +\frac{\epsilon^2}{2}|\nabla_\gamma u|^2\right) \, ds,
    \label{eqn:PhaseEnergy}
\end{align}
where $b(u)$ is the lipid-dependent bending modulus, $\sigma$ is the vesicle's tension, $u$ is the lipid concentration, and $f(u) = \frac{1}{4}u^2(1-u)^2$ is the double-well potential with local minimums at $u=0$ and $u=1$. Here, $\kappa$ is the membrane curvature, $\ss$ is the tangent vector, and $s$ is the arclength. $a$ and $\epsilon$ are small parameters, and we use the same values as~\citet{soh-tse-li-voi-low2010}. The resulting membrane forces are
\begin{align}
    \ff_b &= -(b(u)\kappa \nn)_{ss} -\frac{3}{2}\left(b(u) \kappa^2 \ss\right)_s, \\
    \ff_t &= (\sigma \ss)_s, \\
    \ff_p &= \left(\frac{a}{\epsilon}\left(f(u) -
         \frac{\epsilon^2}{2} u_s^2\right) \ss \right)_s.
\end{align}

The lipid species $u$ is governed by a fourth-order Cahn-Hilliard equation that results in the lipids phase separating while conserving their total mass. To model the variable bending, \citet{soh-tse-li-voi-low2010} propose parameterizing the bending modulus as
\begin{align}
    b(u) = b_{\max} (1-u) + b_{\min} u,
    \label{eqn:linearBending}
\end{align}
where $b_{\max}$ and $b_{\min}$ are the maximum and minimum bending moduli, respectively. However, since the double-well potential does not have hard walls, the lipid concentration is not guaranteed to be confined to the interval $[0,1]$. This is problematic when $u > 1$ since this results in $b(u) < 0$ if $u > \frac{b_{\max}}{b_{\max} - b_{\min}}$, and such values of $u$ are possible when $b_{\min}$ is small and the vesicle is confined to a narrow region. Therefore, in this work we parameterize the bending modulus as
\begin{align}
    b(u) = \frac{b_{\min} - b_{\max}}{2} \tanh\left(3\left(u - \frac{1}{2} \right)\right) + 
           \frac{b_{\min} + b_{\max}}{2}.
    \label{eqn:tanhBending}
\end{align}
\begin{figure}[H]
    \centering
    \input{figures/concModels.tikz}
    \caption{\label{fig:concModels} \small The linear bending model in red (equation~\eqref{eqn:linearBending}) and the the new hyperbolic bending model in blue (equation~\eqref{eqn:tanhBending}). Note that the new bending model satisfies $b \in (b_{\min},b_{\max})$ even if $u \notin [0,1]$.}
\end{figure}

Equation~\eqref{eqn:tanhBending} maps the local minimums of the double-well potential close to $b_{\min}$ and $b_{\max}$, but more importantly, b(u) remains bounded in $[b_{\min},b_{\max}]$ even when $u \notin [0,1]$ (Figure~\ref{fig:concModels}). To demonstrate the necessity of this new bending model, we consider a multicomponent vesicle in strong confinement with both bending models~\eqref{eqn:linearBending} and~\eqref{eqn:tanhBending}. The stiff-to-floppy ratio is $b_{\max}/b_{min} = 10^{-1}$. In the new model~\eqref{eqn:tanhBending}, the lipid concentration achieves a maximum value of $u \approx 1.002$ which results in a  minimum bending stiffness of $b(u) \approx b_{\min}$. However, if we use the linear bending model~\eqref{eqn:linearBending}, the lipid concentration achieves a maximum value of $u \approx 1.52$ which results in an unphsical negative bending stiffness of $b(u) \approx -0.5$. The vesicle shapes are in Figure~\ref{fig:bendingModels}, and the instability caused by the negative bending stiffness is near the region with negative curvature.
\begin{figure}[htp]
    \centering
%    \begin{tabular}{@{}p{0.49\linewidth}@{\qquad}p{0.49\linewidth}@{}}
        \subfigimg[width=0.48\linewidth, clip ]{(a)}{figures/newbending.pdf}
        \subfigimg[width=0.48\linewidth, clip ]{(b)}{figures/oldbending.pdf}
%    \end{tabular}
    \caption{\label{fig:bendingModels} \small A multicomponent vesicle entering a closely-fitting channel using the (a) new bending model~\eqref{eqn:tanhBending}; (b) the linear model~\eqref{eqn:linearBending}. With the linear model, the vesicle bending modulus becomes negative, and this introduces an instability that first appears near the point with the largest negative curvature. The two plots are not at the same time step.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Validation}
Since we use a new bending model, we first validate that it reproduces the tank treading and phase treading dynamics reported in the literature. Figure~\ref{fig:treading} shows a tank treading (top) and a phase treading (bottom) multicomponent vesicle in an unconfined shear flow. These simulations align with the results reported by~\citet{liu-mar-li-vee-low2017} (cf.~Figures 3 and 4).
\begin{figure}[H]
    \centering
    \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(a)}{figures/Fig4a.pdf}
    \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(b)}{figures/Fig4b.pdf}
%    \includegraphics[width = \columnwidth,trim ={5.5cm 1.5cm 4cm 0},clip]{figures/Fig4a.pdf}
%    \includegraphics[width = \columnwidth,trim ={5.5cm 1.5cm 4cm 0},clip]{figures/Fig4b.pdf}
    \caption{\label{fig:treading} \small A multicomponent (a) tank-treading and (b) phase-treading vesicle using the new bending model~\eqref{eqn:tanhBending}. These simulations agree with the results presented by~\citet{liu-mar-li-vee-low2017}.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:NumericalMethods}Numerical Methods}
The velocity field $\uu$ is written as a combination of a single-layer potential and a double-layer potential
\begin{align}
    \label{eqn:LPrep}
    \uu(\xx) = S[\ff](\xx) + D[\eeta](\xx),
\end{align}
where
\begin{align}
    S[\ff](\xx) &= \frac{1}{4\pi\mu} \int_{\gamma} \left(-\log \rho \mathds{I} + \frac{\rr \otimes \rr}{\rho^2} \right)
    \ff(\yy) \, ds_\yy, \\
%
    D[\eeta](\xx) &= \frac{1}{\pi} \int_{\Gamma} \frac{\rr \cdot \nn}{\rho^2}
        \frac{\rr \otimes \rr}{\rho^2} \eeta(\yy) \, ds_\yy,
\end{align}
$\rr = \xx - \yy$, $\rho = |\rr|$, and $\mathds{I}$ is the $2 \times 2$ identity matrix. To avoid tangling of the vesicle membrane, it is parameterized in terms of the $\theta$-$L$ variables~\cite{hou-low-she1994}, where $L$ is the fixed vesicle length and $\theta$ is the opening angle of the tangent vector $\ss$. This requires decomposing the velocity field on $\gamma$ into its normal direction $V$ and tangential direction $T$. Then, the no-slip boundary condition for the vesicle velocity is
\begin{align}
    \frac{d\xx}{dt} = V \nn + T \ss + D[\eeta](\xx), \quad \xx \in \gamma.
\end{align}
The boundary condition on $\Gamma$ is imposed by requiring that $\eeta$ satisfies
\begin{align}
    \UU(\xx) = -\frac{1}{2}\eeta(\xx) + S[\ff](\xx) + D[\eeta](\xx), \quad \xx \in \Gamma.
    \label{eqn:DLP_BIE}
\end{align}
After discretizing the geometry at collocation points, the single-layer potential is approximated with quadrature for weakly-singular integrands, and the double-layer potential is approximated with the spectrally accurate trapezoid rule. All arclength derivatives are computed with spectral accuracy using Fourier methods. Time stepping is performed with second-order Adams-Bashforth. The resulting linear system is solved with GMRES.

The lubrication layer between a vesicle and the solid wall plays a critical role on the vesicle's dynamics. Therefore, we report the size of the lubrication layers both above and below the vesicle in Section~\ref{sec:results}. We first justify the use of the term `lubrication layer' by verifying that the flow velocity is parabolic between the vesicle and the solid wall. Figure~\ref{fig:quadraticProof} illustrates the horizontal velocity (solid line) and the corresponding best fit quadratic (dashed line) in the co-moving frame, and the profiles agree.

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{figures/lubricationLayer_quadratic.pdf}  
    \caption{The co-moving velocity profile in the top and bottom lubrication layers. The red curve is the velocity profile, the dashed black line is the best quadratic fit.}
    \label{fig:quadraticProof}
\end{figure}

To define the size of the top lubrication layer (the size of the bottom lubrication layer is defined similarly), we start with the distance between the vesicle and the top half of the confining geometry
\begin{align}
    d(\xx,\Gamma_\mathrm{top}) \inf_{\yy \in \Gamma_\mathrm{top}} \|\xx-\yy\|,
\end{align}
where $\Gamma_{\mathrm{top}}$ is the top portion of $\Gamma$. We then find all local minimums of $d(\xx,\Gamma_\mathrm{top})$, with the condition that $d(\xx,\Gamma_\mathrm{top}) < \beta$, where $\beta$ is a parameter. If no such local minimums exist, then the vesicle is too far from $\Gamma_\mathrm{top}$ to define a lubrication layer. If there are two or more local minimums, the left-most, $\xx_L$, and right-most, $\xx_R$, local minimums form the start and end of the lubrication layer. If there is only one local minimum, then $\xx_L$ and $\xx_R$ are the points on $\gamma$ to the left and right of this local minimum with the condition that $d(\xx_L,\Gamma_\mathrm{top}) = d(\xx_R,\Gamma_\mathrm{top}) = \beta$. Then, the segment $\gamma_{\mathrm{layer}} \subset \gamma$ consists of all points $\xx \in \gamma$ between $\xx_L$ and $\xx_R$ with the condition that $d(\xx,\Gamma_\mathrm{top}) < \beta$. Finally, the lubrication layer width is
\begin{align}
    w_\mathrm{top} = \frac{1}{|\gamma_{_\mathrm{layer}}|} \int_{\gamma_{_\mathrm{layer}}} d(\xx,\Gamma_\mathrm{top}) \, ds.
\end{align}
The width of the bottom lubrication layer, $w_\mathrm{bot}$ is calculated replacing $\Gamma_\mathrm{top}$ with $\Gamma_\mathrm{bot}$.

%The terminology of boundary layer can be justified by computing the velocity field in the region between the vesicle and the solid wall. In Figure~\ref{fig:BkgrdFlow}, the co-moving velocity field around several different vesicle shapes that are observed in Section~\ref{sec:results} are illustrated. We have included plots of the horizontal velocity along a few vertical slices to demonstrate that a parabolic flow profile is observed.

The difference between the size of the top and lubrication layers is closely related to the tank treading behavior of the vesicle. In cases where the vesicle tank treads, we define the tank-treading velocity, $\uu \cdot \ss$. To establish that a vesicle is tank treading, we compute this tangential velocity at several Lagrangian points on $\gamma$, and make sure that these values agree.

%\begin{figure}[H]
%\begin{minipage}{0.49\columnwidth}
%    \centering
%    \subfigimg[width = \columnwidth, trim = {2cm 2cm 2cm 2cm }, clip]{(a)}{figures/Fig7a1.pdf}
%    \subfigimg[width = \columnwidth, trim = {2cm 2cm 2cm 2cm }, clip]{(b)}{figures/Fig7b1.pdf}
%    \subfigimg[width = \columnwidth, trim = {2cm 2cm 2cm 2cm }, clip]{(c)}{figures/Fig7c1.pdf}
%\end{minipage}   
%\hfill
%\begin{minipage}{0.49\columnwidth}
%    \centering
%    \subfigimg[width = \columnwidth, trim = {2cm 2cm 2cm 2cm }, clip]{\color{white}(a)}{figures/Fig7a2.pdf}
%    \subfigimg[width = \columnwidth, trim = {2cm 2cm 2cm 2cm }, clip]{\color{white}(b)}{figures/Fig7b2.pdf}
%    \subfigimg[width = \columnwidth, trim = {2cm 2cm 2cm 2cm }, clip]{\color{white}(c)}{figures/Fig7c2.pdf}
%\end{minipage}
%\caption{\label{fig:BkgrdFlow} \small The velocity in the bulk, at two time steps, of a vesicle with reduced area $\alpha=0.4$. The velocity field is in the co-moving frame. The vesicles are (a) single-component with $b = 1$; (b) single-component with $b = 0.55$; and (c) multicomponent. The tangential velocity in the tubular neighborhood around the vesicle indicates that (a) and (c) are tank-treading.}    
%\end{figure}

We also report the excess pressure for one of the geometries and relate it to the size of the lubrication layers. Since we represent the velocity with layer potentials~\eqref{eqn:LPrep}, the pressure at $\xx \in \Omega$ is
\begin{align}
    p(\xx) = \frac{1}{2\pi} \int_{\gamma} \frac{\rr \cdot \ff}{\rho^2} \, ds_\yy + \frac{1}{\pi} \int_{\Gamma} \frac{1}{\rho^2} \left(\mathds{I} - 2\frac{\rr \otimes \rr}{\rho^2} \right) \nn \cdot \eeta \, ds_\yy.
\end{align}
The excess pressure is the additional pressure that is required to pass the vesicle through the geometry when compared to the pressure necessary if the vesicle were absent. These pressure drops are defined by subtracting the pressure at a point near the inlet and another near the outlet. In our formulation, because of the order of subtraction, the excess pressure is always negative.

%We follow the reformulation of the governing equations outlined in Section 3.1 of \cite{soh-tse-li-voi-low2010}. In particular, we do a change of variables to the $\theta$-L formulation, where $L$ is the total length of the vesicle and $\theta$ is the opening angle of its tangent vector, $\ss$. 
%This formulation provides us with the location of a unique vesicle shape up to a translation. %, which we resolve by tracking the vesicle's center of mass. After this change of variables, the dynamics of $\theta$ are governed by
%The formulation requires the normal and tangential components of the velocity, 
%\begin{equation}
%V = \uu \cdot \nn \qquad \text{and} \qquad T = \uu \cdot \ss, \label{NormTanComp} 
%\end{equation}
%where $\nn$ is the unit normal vector and $\ss$ is the unit tangent vector. In the $\theta$-L formulation, the governing equation of the vesicle
%\begin{equation}
%\frac{d\xx}{dt} =V\nn+T\ss,
%\end{equation}
%becomes
%\begin{equation}
%\theta_t =  -(V+\beta(\textbf{f}\cdot\textbf{n}))_s + \kappa T
%\theta_t =  -V_s + \kappa T,
%\end{equation}
%and the inextensibility condition becomes
%\begin{equation}
%T_s+\kappa V  = 0. \label{genInexMC}
%\end{equation}
%Recall that the velocity $\uu$ is coupled to the tension $\sigma^{LL}$ which acts as a Lagrange multiplier to satisfy equation \eqref{genInexMC}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:results}Hydrodynamics of a multicomponent vesicle under strong confinement}
We consider both a single-component and a multicomponent vesicle suspended in two geometries: a closely-fitting geometry (stenosis) and a geometry that slowly contracts to a narrow neck and then quickly widens (contracting). We considered a semipermeable vesicle suspended in these same geometries~\cite{qua-gan-you2021}. All the multicomponent examples have the bending ratio $b_{\min}/b_{\max} = 10^{-1}$. For the single-component case, we consider two dimensionless bending stiffness: $b(u) = b_{\max} = 1$ and $b(u) = \frac{1}{2}(b_{\max} + b_{\min}) = 0.55$. Throughout this section we plot the position of the vesicle in terms of the $x$-coordinate of its center of mass. For the stenosed geometry in Section~\ref{subsec:Stenosis}, the narrow region begins at $x=-15$ and ends at $x=15$. For the contracting geometry in Section~\ref{subsec:Contraction}, the geometry begins to narrow at $x=4$ and reaches its narrowest point at $x=15$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{subsec:Stenosis}A multicomponent vesicle in a closely-fit channel (Stenosis)}

We consider a vesicle with reduced area $\alpha = 0.6$ passing through a closely-fitting channel, with a dimensionless maximum velocity of $\chi = 0.25$. Figure~\ref{fig:RA6} shows six time steps of a single-component vesicle with bending stiffness (a) $b=1$ and (b) $b=0.55$, and a multicomponent vesicle with an initially random distribution of lipids (c). In all plots, the color is the dimensionless bending modulus of the multicomponent vesicle that remains bounded in $[0.1,1]$ by using the new bending modulus~\eqref{eqn:tanhBending}. A single Lagrangian point is included to visualize tank-treading behavior. There are slight differences between the three cases, with the most noticeable being that the multicomponent vesicle has higher curvature in the floppy region. We consider the same setup in Figure~\ref{fig:RA4}, but the vesicle has reduced area $\alpha = 0.4$. The main difference between the two reduced areas is that the vesicles with smaller reduced area undergo tank-treading motions. As mentioned earlier, tank treading occurs when the top and bottom lubrication layers differ in size. The size of the lubrication layers in all six cases are in Figure~\ref{fig:lubrication}.

\begin{figure}[h]
    \centering
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig5a.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig5b.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig5c.pdf}
    \caption{\label{fig:RA6} \small A vesicle passing through a stenosed geometry. The vesicle's reduced area is $\alpha = 0.6$ and the dimensionless maximum velocity is $\chi = 0.25$. The vesicles are: (a) single-component with bending modulus $b=1$; (b) single-component with bending modulus $b=0.55$; (c) multicomponent.}
    %\caption{\label{fig:RA6} A single-component (top) and multicomponent (bottom) vesicle passing through the stenosed geometry. In both simulations, the reduced area is $0.6$ and the dimensionless maximum velocity is $\chi = 0.25$. Note that the multicomponent vesicle travels slightly faster, so it leaves the narrow constriction earlier (see Figure~\ref{fig:location1}.}
\end{figure}

\begin{figure}[h]
    \centering
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig6a.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig6b.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig6c.pdf}
    \caption{\label{fig:RA4} \small A vesicle passing through a stenosed geometry. The vesicle's reduced area is $\alpha = 0.4$ and the dimensionless maximum velocity is $\chi = 0.25$. The vesicles are: (a) single-component with bending modulus $b=1$; (b) single-component with bending modulus $b=0.55$; (c) multicomponent. The multicomponent vesicle travels slightly faster, so it leaves the stenosed region earlier than the single-component cases (see Figure~\ref{fig:vesVelocity}).}
\end{figure}

%\begin{figure}
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \includegraphics[width=\textwidth,trim={4cm 8cm 4cm 8cm}, clip]{figures/EnergiesRAp4NoConc.pdf}
%    \end{minipage}
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \includegraphics[width=\textwidth,trim={4cm 8cm 4cm 8cm}, clip]{figures/EnergiesRAp4Conc.pdf}
%    \end{minipage}
%    \caption{Bending (blue), tension (yellow), and phase (red) energies for a single-component vesicle %(left) and a multi-component vesicle (right) with reduced area 0.4.}
%    \label{fig:EnergyRAp4}
%\end{figure}
%\begin{figure}[H]
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \includegraphics[width=\textwidth,trim={4cm 8cm 4cm 8cm}, clip]{figures/EnergiesRAp6NoConc.pdf}
%        \includegraphics[width=\textwidth,trim={4cm 8cm 4cm 8cm}, clip]{figures/EnergiesRAp6NoConcp55.pdf}
%    \end{minipage}
%    \hfill
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \includegraphics[width=\textwidth,trim={4cm 8cm 4cm 8cm}, clip]{figures/EnergiesRAp6Conc.pdf}
%        \vspace{3.5cm}
%    \end{minipage}
%    \caption{Bending (blue), tension (yellow), and phase (red) energies for a single-component vesicle %(left) and a multi-component vesicle (right) with reduced area 0.6.}
%    \label{fig:EnergyRAp6l}
%\end{figure}

\begin{figure}[h]
    \centering
    \subfigimg[width = \columnwidth]{(a)}{figures/Fig8a.pdf}\\
    \subfigimg[width = \columnwidth]{(b)}{figures/Fig8b.pdf}
    \caption{\small Lubrication layer of a single-component and a multicomponent vesicle moving through a stenosed channel. In the top figure, the reduced area is 0.4, on the bottom it is 0.6.}
    \label{fig:lubrication}
\end{figure}

The tank-treading velocities of the examples with reduced area $\alpha = 0.4$ are in Figure~\ref{fig:tankTreadRAp4}. The vesicle shapes at the dashed black lines are also included, and the four marker points are the Lagrangian points where the tangential velocities are computed. For reduced area $\alpha = 0.4$, the single-component ($b=1$) and multicomponent vesicles are clearly tank treading. Since the single-component case has a larger difference between its top and bottom boundary layers, it tank treads faster than the multicomponent case. In addition, since the top boundary layer is larger in both cases, they both tank-tread in the same direction---counterclockwise. In contrast, the single-component vesicle with $b=0.55$ tank-treads in the clockwise direction; note, however, that this example is still undergoing some deformations, so a constant tank-treading velocity is not observed. When $\alpha = 0.6$, the vesicle undergoes deformations while in the stenosed geometry and a constant tank-treading velocity is not observed, so a plot is not included.

%Both the migration speed and tank treading behavior of a vesicle in the closely-fitting channel depends on the separation distance between the solid wall and the vesicle. As the vesicle enters the narrow constriction, lubrication layers between the vesicle and the solid walls develop. The minimum distance between the multicomponent vesicles and the solid wall (solid lines) and the single-component vesicles and the solid wall (dashed lines) are plotted in Figure~\ref{fig:lubrication}. Top top plot is for the vesicle with reduced area $\alpha = 0.4$, and the bottom plot is for the vesicle with reduced area $\alpha = 0.6$. Note that the position is only between $-15$ and $15$ which is the region with strong confinement.

%The size of the top and bottom lubrication layers are plotted in Figure~\ref{fig:lubrication} for reduced area (a) $\alpha = 0.4$ and (b) $\alpha = 0.6$. In both cases, we see that the multicomponent vesicle has larger lubrication layers than their single-component counterparts. As shown in Figures~\ref{fig:RA6} and~\ref{fig:RA4}, the result is that the multicomponent vesicle experiences less drag from the solid walls, and therefore migrates faster. This is confirmed in Figure~\ref{fig:location1} where we plot the position of each of the vesicle versus time for both reduced areas and both lipid species. The larger lubrication layer should also result in a smaller excess pressure, especially for reduced area $\alpha = 0.4$, and this is observed in Figure~\ref{fig:excessPressure}.

%For the smaller reduced area, both the single and multicomponent vesicles are closer to the top wall than the bottom wall. More interesting, though, is that the multicomponent vesicle has a larger lubrication layer than its single-component counterpart. This larger lubrication layer means that less of the multicomponent vesicle experiences less drag from the solid wall, and its net migration speed is faster. This is verified in Figure~\ref{fig:location1}. For the larger reduced area, the vesicle is able to quickly deform away from the walls while entering the constriction. In Figure~\ref{fig:location1} we see that the multicomponent vesicle makes its way through the contstriction quicker than its single-component counterpart. Because the vesicle initially deforms, there is less initial drag from the walls. This quickly changes and the bottom lubrication layer becomes much thinner and the vesicle slows down. In Figure~\ref{fig:location1}, we can tell by the slopes of the curves that the single- and multicomponent vesicles are moving at roughly the same speed.

%Whether a vesicle tank-treads or not is also related to the lubrication layer. In particular, if the lubrication layer between the top and lower walls are different, this indicates that the vesicle is center of mass is above or below the middle of the channel. When this happens, the non-linear of the flow results in a tank-treading vesicle.

%The smaller reduced area $\alpha = 0.4$ also results in a larger difference between the size of the top and boundary lubrication layers. In particular, Figure~\ref{fig:lubrication}(a) shows that the bottom lubrication layer is larger than the top lubrication layer, indicating the vesicle is above the centerline, and we expect the non-linear shear to result in a counterclockwise tank-treading motion. We define the tank treading velocity using several tracker points (solid points) by computing $\uu \cdot \tt$ where $\uu$ is the velocity and $\tt$ is the tangent vector at the tracker point. Note that this quantity does not represent a tank treading velocity until the vesicle reaches tank-treading behavior. Figure~\ref{fig:tankTreadRAp4} shows that for reduced area $\alpha = 0.4$, both the single and multicomponent vesicles undergo an extended period of tank-treading, but at different speeds, starting near the middle of the region of confinement and ending as the vesicles exit this region. Since the difference in sizes of the boundary layers is greater for the single-component vesicle, we expect it to tank-tread faster, which we observe when comparing Figures~\ref{fig:tankTreadRAp4}(a) and (e).In the multicomponent case, there are several interesting features in the tangential velocity, and these are denoted by the red marks in Figure~\ref{fig:tankTreadRAp4}. The vesicle shapes at each of these points are in Figure~\ref{fig:tankTreadRAp4}(b) and (c). The tangential velocity includes spikes that occur whenever there is a decrease in the phase energy due to floppy and stiff regions merging, and this can be observed in Figures~\ref{fig:tankTreadRAp4}(d) and (e).

\begin{figure}[h]
    \begin{minipage}{0.49\columnwidth}
        \centering
        \subfigimg[width=\textwidth]{(a)}{figures/Fig11c1.pdf}
        \subfigimg[width=\textwidth]{(c)}{figures/Fig11b1.pdf}
        \subfigimg[width=\textwidth]{(e)}{figures/Fig11a.pdf}
        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(a)}{figures/TankTreadRAp4Conc.pdf}
        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(c)}{figures/TankTreadRANoConcp55.pdf}
        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(e)}{figures/TankTreadRAp4NoConc.pdf}
        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6Conc.pdf}
        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6NoConc.pdf}
    \end{minipage}
    \hfill
    \begin{minipage}{0.49\columnwidth}
        \centering
        \subfigimg[width=\textwidth]{(b)}{figures/Fig11c2.pdf}
        \subfigimg[width=\textwidth]{(d)}{figures/Fig11b2.pdf}
        \subfigimg[width=\textwidth]{(f)}{figures/Fig11a2.pdf}
        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(b)}{figures/TankTreadRAp4ConcVes.pdf}
        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(d)}{figures/TankTreadRANoConcp55Ves.pdf}
        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(f)}{figures/TankTreadRAp4NoConcVes.pdf}
        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6ConcVes.pdf}
        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6NoConcVes.pdf}
    \end{minipage}
    \caption{\small The tangential velocity at four Lagrangian points on a (a) single-component vesicle with $b = 1$ (c) single-component vesicle with $b = 0.55$, and (e) multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all cases. (b/d/f) A corresponding vesicle shape with the Lagrangian points.
    \label{fig:tankTreadRAp4}}
\end{figure}

%\begin{figure}[H]
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \subfigimg[width=\textwidth]{(a)}{figures/Fig12c1.pdf}
%        \subfigimg[width=\textwidth]{(c)}{figures/Fig12b1.pdf}
%        \subfigimg[width=\textwidth]{(e)}{figures/Fig12a1.pdf}
        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(c)}{figures/TankTreadRAp6NoConcp55.pdf}
        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(e)}{figures/TankTreadRAp6NoConc.pdf}
        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6Conc.pdf}
        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6NoConc.pdf}
%    \end{minipage}
%    \hfill
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \subfigimg[width=\textwidth]{(b)}{figures/Fig12c2.pdf}
%        \subfigimg[width=\textwidth]{(d)}{figures/Fig12b2.pdf}
%        \subfigimg[width=\textwidth]{(f)}{figures/Fig12a2.pdf}
        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(b)}{figures/TankTreadRAp6ConcVes.pdf}
        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(d)}{figures/TankTreadRAp6NoConcp55Ves.pdf}
        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(f)}{figures/TankTreadRAp6NoConcVes.pdf}
        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6ConcVes.pdf}
        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6NoConcVes.pdf}
%    \end{minipage}
%    \caption{\small The tangential velocity at Lagrangian points on a (a) single-component vesicle with $b = 1$ (c) single-component vesicle with $b = 0.55$, and (e) multicomponent vesicle. The reduced area is $\alpha = 0.6$ in all cases. (b/d/f) A corresponding vesicle shape with the Lagrangian points.
%    \label{fig:tankTreadRAp6}}
%\end{figure}

The size of the top and bottom lubrication layers are also related to the excess pressure (Figure~\ref{fig:excessPressure}). If the lubrication layers are large, most notably for the multicomponent vesicle with reduced area $\alpha = 0.4$, then less pressure is required to force the vesicle through the geometry, and we expect a smaller (less negative) excess pressure. In contrast, if the lubrication layers are small, most notably for the single-component vesicle with $b=1$ and reduced area $\alpha = 0.4$, then more pressure is required to force the vesicle through the geometry, and we expect a larger (more negative) excess pressure.

\begin{figure}[H]
    \centering
    \subfigimg[width = 0.45\columnwidth]{(a)}{figures/Fig10a.pdf}
    \subfigimg[width = 0.45\columnwidth]{(b)}{figures/Fig10b.pdf}
    \caption{\small The excess pressure a single-component and a multicomponent vesicle moving through a stenosed channel. The reduced areas are (a) $\alpha = 0.4$, and (b) $\alpha = 0.6$.}
    \label{fig:excessPressure}
\end{figure}

While the size of the lubrication layers affect the tank-treading behavior and the excess pressure, it has almost no effect on the migration speed of the vesicle. In Figure~\ref{fig:vesVelocity}, we plot the average velocity of the vesicle as it passes through the stenosed region. With the exception of the single-component vesicle with $b=1$ and $\alpha = 0.6$, the average vesicle speed is constant. Obviously, this average velocity would be affected by the maximum imposed velocity, $\chi$.

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{figures/Fig9.pdf}
    %\input{figures/Fig9.tikz}
    \caption{\label{fig:vesVelocity} \small The average vesicle velocity as it passes through the stenosed region. The vesicle stiffness and reduced area have no significant effect.}
\end{figure}

Finally, we consider the three different energies---bending, tension, and phase---for each of the single-component and multicomponent vesicles. In Figure~\ref{fig:Energy}, we plot these energies as a function of the vesicle's center of mass. As a reminder, the vesicle enters the constriction at $x=-15$ and exits at $x=15$. Also note that the single-component vesicle does not have a phase energy. A few general trends can immediately be seen. First, as the vesicle enters the stenosed region, there are sharp jumps in both the tension and bending energies, as expected. Next, the multicomponent vesicles only coarsen when the vesicle is not in the stenosed region. Finally, when coarsening does occur, there are rapid changes in the tension energy.

%In the single-component runs, ... In the multicomponent runs, we see that phase separation does not occur in the channel. When it does occur, we see spikes in the bending and tension energies. \todo[inline]{Discussion of what we see}

\begin{figure}
  \begin{minipage}{0.49\columnwidth}
    \centering
%    \subfigimg[width = \columnwidth, trim = {1cm 20cm 1cm 3cm}, clip]{(a)}{figures/RAp4BkgrdFlow.pdf}
    \subfigimg[width=\textwidth]{(a)}{figures/Fig13a.pdf}
    \subfigimg[width=\textwidth]{(c)}{figures/Fig13c.pdf}
    \subfigimg[width=\textwidth]{(e)}{figures/Fig13e.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.49\columnwidth}
    \centering
    \subfigimg[width=\textwidth]{(b)}{figures/Fig13b.pdf}
    \subfigimg[width=\textwidth]{(d)}{figures/Fig13d.pdf}
    \subfigimg[width=\textwidth]{(f)}{figures/Fig13f.pdf}
  \end{minipage}
  \caption{\label{fig:Energy} \small The Bending (blue), tension (yellow), and phase (red) energies for a (a/b) single-component vesicle with $b=1$, (c/d) single-component vesicle with $b = 0.55$, and (e/f) multicomponent vesicle. The reduced areas are $alpha = 0.4$ (a/c/e) and $\alpha = 0.6$ (b/d/f).}
\end{figure}

%\begin{itemize}

%    \item Comparison of different flow rates $\chi = 0.25 = 0.5 \mu m/s$ and $\chi = 2.5 = 5 \mu m/s$

%    \item Comparison of different reduced areas. Definitely interested in 0.40 and then maybe only one other value. A natural other value is 0.6 or 0.7 since this is close to the reduced area of a RBC.

%    \item Interesting tank treading/slipper shape when flow rate is 0.25 and reduced area is 0.4. We did not see this for any of the larger flow rates, and this is consistent with what is known about vesicles in a non-linear shear flow

%    \item Multicomponent goes through faster than single-component

%    \item Error in area is about 20X larger for the multicomponent
%    
%    \item How does the reduced area affect the speed of the vesicle and its ability to phase separate when i%n confinement. We haven't looked at a completed run with larger reduced area. Maybe there's one sitting on RCC or we% need to submit one?
%\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{subsec:Contraction} A multicomponent vesicle in a narrowing geometry (Contracting)}
In this section, we consider a single vesicle passing through a geometry that slowly contracts to a region that is only 2~$\mu$m wide, and then immediately opens back up to a channel that is ten times larger. We first consider the effect of the initial lipid concentration when the floppy and stiff regions each make up half of the vesicle membrane. We consider an initially random initial lipid concentration, and one that is floppy in the front and stiff in the back. In both these cases, the vesicle either completely or partially reorients itself so that the floppy region is in the back and the stiff region is in the front. Therefore, in all subsequent examples, we start with symmetric vesicle whose floppy region is in the back and its stiff region is in the front.

\begin{figure}[h]
    \centering
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm 1.5cm},clip]{(a)}{figures/rightSep.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm 1.5cm},clip]{(b)}{figures/randSep.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm 1.5cm},clip]{(c)}{figures/leftSep.pdf}
     \caption{\label{fig:RA6leftRightRand} \small A multicomponent vesicle with 50\% floppy region passing through a contracting geometry. The vesicle's reduced area is $\alpha = 0.6$ and the dimensionless maximum velocity is $\chi = 0.25$. The vesicles are: (a) the initial lipid-species distribution is fully separated on the right side of the vesicle; (b) the initial lipid-species distribution is randomly distributed (not fully separated) on the vesicle membrane; (d) the initial lipid-species distribution is fully separated on the left side of the vesicle. The vesicles with a larger percentage of floppy regions pass through the neck earlier than the vesicles with less percentage of floppy regions. The vesicle either completely or partially reorients itself so that the floppy region is in the back and the stiff region is in the front.}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/bending_leftRightRand.pdf}
    \caption{The bending energy of a multicomponent vesicle that is 50\% stiff with an initial phase separation to the left (blue), to the right (red), randomly distributed (yellow). The vesicle exits the contraction $x \approx 15$.}
    \label{fig:RAp6leftRightRandBending}
\end{figure}

In Figure~\ref{fig:RA5}, we consider a vesicle with reduced area $\alpha = 0.5$ and the dimensionless flow rate is $\chi = 0.25$. We start with a single-component vesicle and then increase the percentage of the vesicle membrane that is floppy. By comparing the vesicle location at the time step just before the vesicle passes through the constriction, we can immediately see that vesicles with membranes that have larger percentage of floppy regions reach and pass through the neck earlier. The dimensionless times that the entire vesicle first passes through the neck are reported in Table~\ref{tbl:contractingTimes}.

\begin{figure}[h]
    \centering
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig14a.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig14b.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(d)}{figures/Fig14c.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(e)}{figures/Fig14e.pdf}
     \caption{\label{fig:RA5} \small A vesicle passing through a contracting geometry. The vesicle's reduced area is $\alpha = 0.5$ and the dimensionless maximum velocity is $\chi = 0.25$. The vesicles are: (a) single-component with bending modulus $b=1$; (b) multicomponent with 15\% floppy region; (c) multicomponent with 25\% floppy region; (d) multicomponent with 35\% floppy region; (e) multicomponent with 45\% floppy region. The vesicles with a larger percentage of floppy regions pass through the neck earlier than the vesicles with less percentage of floppy regions.}
\end{figure}

\begin{table}[H]
    \centering
    \begin{tabular}{l|c}
       & Time to pass through neck\\
       \hline
       Single-component &  2.32 \\ %2.3173\\
       15\% Multicomponent & 2.30 \\%2.2960\\
       25\% Multicomponent & 2.29 \\%2.2868\\
       35\% Multicomponent & 2.26 \\%2.2637\\
       45\% Multicomponent & 2.24 \\%2.2388\\
       \hline
    \end{tabular}
    \caption{\label{tbl:contractingTimes} The time required for the vesicles to completely pass through the neck located at $x=15$. The vesicles initial center is at $x=5$.}
\end{table}

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/bendingAllContracting.pdf}
    \caption{\small The bending energy for a single-component vesicle (blue) and and a multicomponent vesicle (red)--(green) with $\alpha = 0.5$. As the size of the floppy region increases, the maximum bending energy decreases.}
    \label{fig:bendingAll}
\end{figure}

We conclude this example by considering the different shapes that single-component and multicomponent shapes display. Since we have initialized the lipid species to initially be phase separated, the phase energy is more or less constant for all cases. The tension energy, on the other hand, increases as the vesicle approaches the neck, but its general shape is similar for the five cases considered in Figure~\ref{fig:RA5}. However, the bending energies are show different behaviors for each of the cases (Figure~\ref{fig:bendingAll}). The main difference between the cases is the that multicomponent vesicles with a higher percentage of floppy regions have less bending energy, especially as the vesicle passes through the neck. We also note that the bending energy undergoes several transient increases and decreases. These occur when the tail of the vesicle undergoes transitions from lower energy shapes, such as a `C' or `S' shapes, to high energy shapes, such as 'W' shapes. Figure~\ref{fig:bendingSC_contracting} show these different vesicle shapes for the single-component vesicle and multicomponent vesicle that is 45\% floppy. The shape at several critical points along the bending energy are included, and we can indeed see that transitioning vesicle shape between these different states.

\begin{figure}
    \centering
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
    \subfigimg[width=\columnwidth]{(a)}{figures/bendingSC.pdf}
    \subfigimg[width=\columnwidth]{(b)}{figures/bendingEngMC45.pdf}
    \caption{\label{fig:bendingSC_contracting} The bending energy of (a) a single-component vesicle, and (b) a multicomponent vesicle whose boundary is 45\% floppy passing through a contracting geometry. The vesicle shape at different locations are included. We can clearly see that the sudden increases and decreases in the bending energy are due to transitions between lower energy and higher energy shapes.}
\end{figure}

%\begin{figure}
%  \begin{minipage}{0.49\columnwidth}
%    \centering
%    \subfigimg[width=\textwidth]{(a)}{figures/Fig15i.pdf}
%    \subfigimg[width=\textwidth]{(c)}{figures/Fig15a.pdf}
%    \subfigimg[width=\textwidth]{(e)}{figures/Fig15c.pdf}
%    \subfigimg[width=\textwidth]{(g)}{figures/Fig15e.pdf}
%    \subfigimg[width=\textwidth]{(i)}{figures/Fig15g.pdf}
%  \end{minipage}
%  \hfill
%  \begin{minipage}{0.49\columnwidth}
%    \centering
%    \subfigimg[width=\textwidth]{(b)}{figures/Fig15j.pdf}
%    \subfigimg[width=\textwidth]{(d)}{figures/Fig15b.pdf}
%    \subfigimg[width=\textwidth]{(f)}{figures/Fig15d.pdf}
%    \subfigimg[width=\textwidth]{(h)}{figures/Fig15f.pdf}
%    \subfigimg[width=\textwidth]{(j)}{figures/Fig15h.pdf}
%  \end{minipage}
%  \caption{\label{fig:Energy} \small The bending (blue), tension (yellow), and phase (red) energies for a single-component vesicle ((a) and (b)) and a multicomponent vesicle (c)--(j) with $\alpha = 0.5$. As the size of the floppy region increases, the maximum bending energy decreases.}
%\end{figure}

%\begin{itemize}
%    \item Look at single-component vs. multicomponent with two different reduced areas and using random and non-random initial lipid distributions
%    \begin{itemize}
%        \item Show the floppy region rotating around to/forming in the back
%        \item \todo[inline]{$\Chi = 0.5 \mu$m/s, RA = 0.4, single component, multi component (random, left, right)}
%        \item \todo[inline]{$\Chi = 0.5 \mu$m/s, RA = 0.6 (for consistency, BUT maybe just the RA = 0.5 is sufficient since they all also do not make it), single component, multi component (random, left, right)}
%        \item \todo[inline]{Look at the $\Chi = 5 \mu$m/s runs to see how these compare. Idea - Slower runs allow more time for the floppy region to move around.} 
%        \item The RA = 0.4 cases all move through the contraction for both flow rates. All the RA = 0.5 cases get stuck for both flow rates.
%    \end{itemize}
%    \begin{figure}[H]
%        \centering
%        \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
%       \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig14a.pdf}
%        \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig14b.pdf}
        %\subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(d)}{figures/Fig14d.pdf}
%        \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(d)}{figures/Fig14c.pdf}
%        \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(e)}{figures/Fig14e.pdf}
%        \caption{\label{fig:RA5} \small Snapshots of a vesicle passing through a contracting geometry. In all cases, the vesicle's reduced area is $\alpha = 0.5$ and the dimensionless maximum velocity is $\chi = 0.25$. The vesicles are: (a) single-component with bending modulus $b=1$; (b) Multicomponent with 15\% floppy region; (c) Multicomponent with 25\% floppy region; (d) Multicomponent with 35\% floppy region; (e) Multicomponent with 45\% floppy region. We see that the vesicles with a larger percentage of floppy regions pass through the neck earlier than the vesicles with less percentage of floppy regions.}
        %\caption{\label{fig:RA6} A single-component (top) and multicomponent (bottom) vesicle passing through the stenosed geometry. In both simulations, the reduced area is $0.6$ and the dimensionless maximum velocity is $\chi = 0.25$. Note that the multicomponent vesicle travels slightly faster, so it leaves the narrow constriction earlier (see Figure~\ref{fig:location1}.}
%    \end{figure}

%    \begin{figure}
%      \begin{minipage}{0.49\columnwidth}
%        \centering
%    %    \subfigimg[width = \columnwidth, trim = {1cm 20cm 1cm 3cm}, clip]{(a)}{figures/RAp4BkgrdFlow.pdf}
%        \subfigimg[width=\textwidth]{(a)}{figures/Fig15i.pdf}
%        \subfigimg[width=\textwidth]{(c)}{figures/Fig15a.pdf}
%        \subfigimg[width=\textwidth]{(e)}{figures/Fig15c.pdf}
%        \subfigimg[width=\textwidth]{(g)}{figures/Fig15e.pdf}
%        \subfigimg[width=\textwidth]{(i)}{figures/Fig15g.pdf}
%        
%      \end{minipage}
%      \hfill
%      \begin{minipage}{0.49\columnwidth}
%        \centering
%        \subfigimg[width=\textwidth]{(b)}{figures/Fig15j.pdf}
%        \subfigimg[width=\textwidth]{(d)}{figures/Fig15b.pdf}
%        \subfigimg[width=\textwidth]{(f)}{figures/Fig15d.pdf}
%        \subfigimg[width=\textwidth]{(h)}{figures/Fig15f.pdf}
%        \subfigimg[width=\textwidth]{(i)}{figures/Fig15h.pdf}

%      \end{minipage}
%      \caption{\label{fig:Energy} \small The Bending (blue), tension (yellow), and phase (red) energies for a (a/b/c/d/e/f/g/h) Multicomponent vesicle, (i/j) single-component vesicle with $\alpha = 0.5$. As the size of the floppy region increases, the maximum bending energy decreases.}
%    \end{figure}

%    \item Vesicle has a `preferred orientation' - forces the floppy region to the back. The question becomes: Is there a Goldilocks region where there is enough floppy region in the back for the vesicle to pass through? (RA = 0.5)
%    \begin{itemize}
%        \item \todo[inline]{$Chi = 5 \mu$m/s, 10\% floppy}
%        \item \todo[inline]{$Chi = 5 \mu$m/s, 30\% floppy}
%        \item \todo[inline]{$Chi = 5 \mu$m/s, 50\% floppy}
%        \item \todo[inline]{$Chi = 5 \mu$m/s, 90\% floppy}
%    \end{itemize}
%    \item Investigate why the 30\% case makes it though. Hopefully there's a story in these plots:
%    \begin{itemize}
%        \item \todo[inline]{Excess pressure plots of all}
%        \item \todo[inline]{Boundary layer plots of all}
%        \item \todo[inline]{Energy plots of all}
%        \item W, S, to C. (something to explore, floppy/stiff regions bending energy)
%    \end{itemize}

%    \item Discuss the shapes of the vesicles after they pass through the contraction. Lots of oscillations in the floppy region
%    \begin{itemize}
%        \item Maybe include error plots or a maximum error. 
%    \end{itemize}
%\end{itemize}

\section{Conclusions \label{sec:conclusion}}

%The main text of the article\cite{Mena2000} should appear here.
%
%\subsection{This is the subsection heading style}
%Section headings can be typeset with and without numbers.\cite{Abernethy2003}
%
%\subsubsection{This is the subsubsection style.~~} These headings should end in a full point.  
%
%\paragraph{This is the next level heading.~~} For this level please use \texttt{\textbackslash paragraph}. These headings should also end in a full point.
%
%\section{Graphics and tables}
%\subsection{Graphics}
%Graphics should be inserted on the page where they are first mentioned (unless they are equations, which appear in the flow of the text).\cite{Cotton1999}
%
%\begin{figure}[h]
%\centering
%  \includegraphics[height=3cm]{example1}
%  \caption{An example figure caption \textendash\ the image is from the \textit{Soft Matter} cover gallery.}
%  \label{fgr:example}
%\end{figure}
%
%\begin{figure*}
% \centering
% \includegraphics[height=3cm]{example2}
% \caption{An image from the \textit{Soft Matter} cover gallery, set as a two-column figure.}
% \label{fgr:example2col}
%\end{figure*}
%
%\subsection{Tables}
%Tables typeset in RSC house style do not include vertical lines. Table footnote symbols are lower-case italic letters and are typeset at the bottom of the table. Table captions do not end in a full point.\cite{Arduengo1992,Eisenstein2005}
%
%
%\begin{table}[h]
%\small
%  \caption{\ An example of a caption to accompany a table}
%  \label{tbl:example1}
%  \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}lll}
%    \hline
%    Header one (units) & Header two & Header three \\
%    \hline
%    1 & 2 & 3 \\
%    4 & 5 & 6 \\
%    7 & 8 & 9 \\
%    10 & 11 & 12 \\
%    \hline
%  \end{tabular*}
%\end{table}
%
%Adding notes to tables can be complicated.  Perhaps the easiest method is to generate these manually.\footnote[4]{Footnotes should appear here. These might include comments relevant to but not central to the matter under discussion, limited experimental and spectral data, and crystallographic data.}
%
%\begin{table*}
%\small
%  \caption{\ An example of a caption to accompany a table \textendash\ table captions do not end in a full point}
%  \label{tbl:example2}
%  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lllllll}
%    \hline
%    Header one & Header two & Header three & Header four & Header five & Header six  & Header seven\\
%    \hline
%    1 & 2 & 3 & 4 & 5 & 6  & 7\\
%    8 & 9 & 10 & 11 & 12 & 13 & 14 \\
%    15 & 16 & 17 & 18 & 19 & 20 & 21\\
%    \hline
%  \end{tabular*}
%\end{table*}
%
%\section{Equations}
%
%Equations can be typeset inline \textit{e.g.}\ $ y = mx + c$ or displayed with and without numbers:
%
% \[ A = \pi r^2 \]
%
%\begin{equation}
%  \frac{\gamma}{\epsilon x} r^2 = 2r
%\end{equation}
%
%You can also put lists into the text. You can have bulleted or numbered lists of almost any kind. 
%The \texttt{mhchem} package can also be used so that formulae are easy to input: \texttt{\textbackslash ce\{H2SO4\}} gives \ce{H2SO4}. 
%
%For footnotes in the main text of the article please number the footnotes to avoid duplicate symbols. \textit{e.g.}\ \texttt{\textbackslash footnote[num]\{your text\}}. The corresponding author $\ast$ counts as footnote 1, ESI as footnote 2, \textit{e.g.}\ if there is no ESI, please start at [num]=[2], if ESI is cited in the title please start at [num]=[3] \textit{etc.} Please also cite the ESI within the main body of the text using \dag. For the reference section, the style file \texttt{rsc.bst} can be used to generate the correct reference style.
%
%\section{Conclusions}
%The conclusions section should come in this section at the end of the article, before the Conflicts of interest statement.
%
%
%\section*{Author Contributions}
%We strongly encourage authors to include author contributions and recommend using \href{https://casrai.org/credit/}{CRediT} for standardised contribution descriptions. Please refer to our general \href{https://www.rsc.org/journals-books-databases/journal-authors-reviewers/author-responsibilities/}{author guidelines} for more information about authorship.

\section*{Conflicts of interest}
There are no conflicts to declare.

\section*{Acknowledgements}
The Acknowledgements come at the end of an article after Conflicts of interest and before the Notes and references.

%%%END OF MAIN TEXT%%%

%The \balance command can be used to balance the columns on the final page if desired. It should be placed anywhere within the first column of the last page.

\balance

%If notes are included in your references you can change the title from 'References' to 'Notes and references' using the following command:
%\renewcommand\refname{Notes and references}

%%%REFERENCES%%%
\bibliography{bibliography} %You need to replace "rsc" on this line with the name of your .bib file
\bibliographystyle{rsc} %the RSC's .bst file

\end{document}

### 2023-03-05 shuwang_rewrite/output/makeImages.m

@@ -13,7 +13,8 @@ addpath ..
 % name = 'Chi200_RA0p95_Conc0p3_Beta0_y0p1_eps0p04_n20.jpg';
 ax = [-2 2 -2 2];
 
-file = 'relaxation1VesA.bin';
+file = 'Chip25_shax5p7_scL0p311_Conc0_Beta0_n1024_nbd1024_dt1en4_bmax1_bmin0p1_eps0p04_a100_longchoke_rand.bin';
+%file = 'relaxation1VesA.bin';
 %file = 'longChoke_Chi400_Scale0p49_shortax3p45_conc0p3.bin';
 %file = 'longChoke_Chi400_Scale0p59_shortax2p75_conc0p3.bin';
 %file = 'longChoke_Chi400_Scale0p71_shortax2p20_conc0p3.bin';
@@ -22,7 +23,7 @@ file = 'relaxation1VesA.bin';
 %file1 = 'Unconfined_larger_800.bin';
 [posx,posy,conc,ea,el,time,xvel1,yvel1,ten] = loadFile(file);
 %[posx1,posy1,conc1,ea1,el1,time1,xvel11,yvel11,ten1] = loadFile(file1);
-ten = -ten;
+%ten = -ten;
 
 plot(posx(:,:,end),posy(:,:,end))
 hold on

### 2023-03-05 vesicle_code/src/Ves2D.m

@@ -23,10 +23,18 @@ if nargin == 4
 else
   om.initializePressure(pressTar); 
 end
-Ntar = 21;
-ytar = linspace(-3,3,Ntar)';
-dy = ytar(2) - ytar(1);
-pressTar = [[0.5*ones(Ntar,1);ytar] [17.5*ones(Ntar,1);ytar]]; 
+%Ntar = 21;
+%ytar = linspace(-3,3,Ntar)';
+%dy = ytar(2) - ytar(1);
+%pressTar = [[0.5*ones(Ntar,1);ytar] [17.5*ones(Ntar,1);ytar]]; 
+
+clf; hold on
+plot(Xwalls(1:end/2),Xwalls(end/2+1:end),'k')
+plot(X(1:end/2),X(end/2+1:end),'r')
+plot(pressTar(1:end/2,:),pressTar(end/2+1:end,:),'b.')
+
+pause
+
 
 matvecs = 0; 
 % counter for the total number of time steps

### 2023-03-08 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
updates to multicomponent tex

@@
 \documentclass[twoside,twocolumn,9pt]{article}
-\usepackage{amsfonts}
 \usepackage{extsizes}
@@
 \usepackage{hyperref}
+\usepackage{amsfonts}
 %\usepackage{subcaption}
@@
 \begin{tabular}{m{4.5cm} p{13.5cm} }
-
+%
 \includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Hydrodynamics of Multicomponent Vesicles Under Strong Confinement}} \\
 \vspace{0.3cm} & \vspace{0.3cm} \\
-
- & \noindent\large{Ashley Gannon,\textit{$^{a}$} Yuan-Nan
-  Young,\textit{$^{b}$} and Bryan Quaife\textit{$^{\ast}${$^{a}$}}} \\
- %Author names go here instead of "Full name", etc.
-
+%
+ & \noindent\large{Ashley Gannon,\textit{$^{a}$} Yuan-Nan Young,\textit{$^{b\ddag}$} and Bryan Quaife\textit{${\ast}${$^{a}$}}} \\
+% %Author names go here instead of "Full name", etc.
+%
 \includegraphics{head_foot/dates} & \noindent\normalsize{The abstract should be a single paragraph which summarises the content of the article.
 Any references in the abstract should be written out in full \textit{e.g.}\ [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].} \\%The abstrast goes here instead of the text "The abstract should be..."
-
+%
 \end{tabular}
-
+%
  \end{@twocolumnfalse} \vspace{0.6cm}
@@
 \section{\label{sec:Formulation}Formulation}
-We consider a single multicomponent vesicle $\omega$ with boundary $\gamma$ suspended in a confined geometry $\Omega \subset \RR^2$ with boundary $\Gamma$ (Figure~\ref{fig:schematic}).
+We consider a single multicomponent vesicle $\omega$ with boundary $\gamma$ suspended in a confined geometry $\Omega \subset \RR ^2$ with boundary $\Gamma$ (Figure~\ref{fig:schematic}).
 \begin{figure}[H]
@@
     \includegraphics[trim = 0.3cm 0cm 1cm 0cm, clip=true,width=0.9\columnwidth]{figures/schematic.pdf}
-    \todo[inline]{Need to improve this figure. Vesicle should be multicomponent. Put greek letter $\gamma$ in black instead of red}
     \caption{\label{fig:schematic}\small A single multicomponent vesicle with boundary $\gamma$ suspended in a domain $\Omega$ with boundary $\Gamma$.
-The vesicle dynamics are determined by a combination of phase, bending, and tension energies, and an imposed flow on $\Gamma$.}
+The dark red regions are the ``stiff" regions corresponding to the maximum bending stiffness $b_{\max}=1$.
+The dark blue regions are the ``floppy" regions corresponding to the minimum bending stiffness $b_{\min}=0.1$ The vesicle dynamics are determined by a combination of phase, bending, and tension energies, and an imposed flow on $\Gamma$.
+}
 \end{figure}
@@
 We first consider the effect of the initial lipid concentration when the floppy and stiff regions each make up half of the vesicle membrane.
-We consider an initially random initial lipid concentration, and one that is floppy in the front and stiff in the back.
-In both these cases, the vesicle either completely or partially reorients itself so that the floppy region is in the back and the stiff region is in the front.
-Therefore, in all subsequent examples, we start with symmetric vesicle whose floppy region is in the back and its stiff region is in the front.
-
-\begin{figure}[h]
-    \centering
-    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm 1.5cm},clip]{(a)}{figures/rightSep.pdf}
-    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm 1.5cm},clip]{(b)}{figures/randSep.pdf}
-    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm 1.5cm},clip]{(c)}{figures/leftSep.pdf}
+In Figure~\ref{fig:RA6leftRightRand}, we consider a vesicle with $\alpha = 0.6$ with an initially random initial lipid concentration, one that is floppy in the front and stiff in the back, and one that is stiff in the front and floppy in the back.
+The vesicle with the random initial lipid distribution phase separates so that the floppy region is in the back and the stiff region is in the front.
+The vesicle where the initial lipid species distribution was fully phase separated and the floppy region was on the front of the vesicle began to reorient the floppy region to the back of the vesicle, making it partway after passing through the contraction.
+In the case where the initial lipid species distribution was fully phase separated and the floppy region was on the back of the vesicle, the floppy region remained on the the back of the vesicle.
+In all cases, the floppy regions were being oriented to cover the regions of the vesicle with the highest curvature to minimize the overall bending energy.
+Since we can see in Figure~\ref{fig:RA6leftRightRand} that the regions of high curvature are located in the back of the vesicle, we expect the overall bending energies to be lowest for the randomly distributed case and the fully separated floppy region on the back case.
+We observe this in Figure~\ref{fig:RAp6leftRightRandBending} Therefore, in all subsequent examples, we start with symmetric vesicle whose floppy region is in the back and its stiff region is in the front.
+
+\begin{figure}[H]
+    \centering
+    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(a)}{figures/rightSep.pdf}
+    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(b)}{figures/randSep.pdf}
+    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(c)}{figures/leftSep.pdf}
      \caption{\label{fig:RA6leftRightRand} \small A multicomponent vesicle with 50\% floppy region passing through a contracting geometry.
@@
 
-\begin{figure}
+\begin{figure}[H]
     \centering
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
     \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
-    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig14a.pdf}
-    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig14b.pdf}
-    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(d)}{figures/Fig14c.pdf}
-    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(e)}{figures/Fig14e.pdf}
+    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig14a_newPaper.pdf}
+    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig14b_newPaper.pdf}
+    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(d)}{figures/Fig14c_newPaper.pdf}
+    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(e)}{figures/Fig14e_newPaper.pdf}
      \caption{\label{fig:RA5} \small A vesicle passing through a contracting geometry.

### 2023-03-22 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on multicomponent paper

@@
 
-We consider a vesicle with reduced area $\alpha = 0.6$ passing through a closely-fitting channel, with a dimensionless maximum velocity of $\chi = 0.25$.
-Figure~\ref{fig:RA6} shows six time steps of a single-component vesicle with bending stiffness (a) $b=1$ and (b) $b=0.55$, and a multicomponent vesicle with an initially random distribution of lipids (c).
-In all plots, the color is the dimensionless bending modulus of the multicomponent vesicle that remains bounded in $[0.1,1]$ by using the new bending modulus~\eqref{eqn:tanhBending}.
-A single Lagrangian point is included to visualize tank-treading behavior.
-There are slight differences between the three cases, with the most noticeable being that the multicomponent vesicle has higher curvature in the floppy region.
-We consider the same setup in Figure~\ref{fig:RA4}, but the vesicle has reduced area $\alpha = 0.4$.
-The main difference between the two reduced areas is that the vesicles with smaller reduced area undergo tank-treading motions.
-As mentioned earlier, tank treading occurs when the top and bottom lubrication layers differ in size.
-The size of the lubrication layers in all six cases are in Figure~\ref{fig:lubrication}.
-
-\begin{figure}[h]
-    \centering
-    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig5a.pdf}
-    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig5b.pdf}
-    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig5c.pdf}
-    \caption{\label{fig:RA6} \small A vesicle passing through a stenosed geometry.
-The vesicle's reduced area is $\alpha = 0.6$ and the dimensionless maximum velocity is $\chi = 0.25$.
-The vesicles are: (a) single-component with bending modulus $b=1$; (b) single-component with bending modulus $b=0.55$; (c) multicomponent.}
-    %\caption{\label{fig:RA6} A single-component (top) and multicomponent (bottom) vesicle passing through the stenosed geometry.
-In both simulations, the reduced area is $0.6$ and the dimensionless maximum velocity is $\chi = 0.25$.
-Note that the multicomponent vesicle travels slightly faster, so it leaves the narrow constriction earlier (see Figure~\ref{fig:location1}.}
-\end{figure}
-
-\begin{figure}[h]
-    \centering
-    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig6a.pdf}
-    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig6b.pdf}
-    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig6c.pdf}
-    \caption{\label{fig:RA4} \small A vesicle passing through a stenosed geometry.
-The vesicle's reduced area is $\alpha = 0.4$ and the dimensionless maximum velocity is $\chi = 0.25$.
-The vesicles are: (a) single-component with bending modulus $b=1$; (b) single-component with bending modulus $b=0.55$; (c) multicomponent.
-The multicomponent vesicle travels slightly faster, so it leaves the stenosed region earlier than the single-component cases (see Figure~\ref{fig:vesVelocity}).}
-\end{figure}
+%\begin{figure}[h]
+\begin{figure*}[b]
+  \centering
+  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp6MCp5.pdf}
+%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig5a.pdf}
+%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig5b.pdf}
+%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig5c.pdf}
+  \caption{\label{fig:RA6} \small A vesicle passing through a stenosed
+  geometry. The vesicle's reduced area is $\alpha = 0.6$ and the
+  dimensionless maximum velocity is $\chi = 0.25$. The vesicles are: (a)
+  single-component with bending modulus $b=1$; (b) single-component with
+  bending modulus $b=0.55$; (c) multicomponent.}
+%\end{figure}
+\end{figure*}
+
+We consider a vesicle with reduced area $\alpha = 0.6$ passing through a
+closely-fitting channel, with a dimensionless maximum velocity of $\chi
+= 0.25$. Figure~\ref{fig:RA6} shows six time steps of a single-component
+vesicle with bending stiffness (a) $b=1$ and (b) $b=0.55$, and a
+multicomponent vesicle with an initially random distribution of lipids
+(c). In all plots, the color is the dimensionless bending modulus of the
+multicomponent vesicle that remains bounded in $[0.1,1]$ by using the
+new bending modulus~\eqref{eqn:tanhBending}. A single Lagrangian point
+is included to visualize tank-treading behavior. There are slight
+differences between the three cases, with the most noticeable being that
+the multicomponent vesicle has higher curvature in the floppy region. We
+consider the same setup in Figure~\ref{fig:RA4}, but the vesicle has
+reduced area $\alpha = 0.4$. The main difference between the two reduced
+areas is that the vesicles with smaller reduced area undergo
+tank-treading motions. As mentioned earlier, tank treading occurs when
+the top and bottom lubrication layers differ in size. The size of the
+lubrication layers in all six cases are in Figure~\ref{fig:lubrication}.
+
+%\begin{figure}[h]
+\begin{figure*}[t]
+  \centering
+  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp4MCp5.pdf}
+%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig6a.pdf}
+%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig6b.pdf}
+%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig6c.pdf}
+  \caption{\label{fig:RA4} \small A vesicle passing through a stenosed
+  geometry. The vesicle's reduced area is $\alpha = 0.4$ and the
+  dimensionless maximum velocity is $\chi = 0.25$. The vesicles are: (a)
+  single-component with bending modulus $b=1$; (b) single-component with
+  bending modulus $b=0.55$; (c) multicomponent. The multicomponent
+  vesicle travels slightly faster, so it leaves the stenosed region
+  earlier than the single-component cases (see
+  Figure~\ref{fig:vesVelocity}).}
+%\end{figure}
+\end{figure*}
 

### 2023-03-23 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on using dimensionless variables

@@
 \end{align}
-where $\TT = -p\mathbf{I} + \mu\left(\nabla \uu + \nabla \uu^T \right)$ is the hydrodynamic stress tensor, $\uu$ is the velocity, $p$ is the pressure, and $\mu$ is the fluid viscosity.
-Across the vesicle membrane, the velocity is continuous while the membrane and hydrodynamic forces balance
-\begin{align}
-    \llbracket \uu \rrbracket = 0, \quad \llbracket \TT\nn \rrbracket = \ff, \quad \xx \in \gamma,
-\end{align}
-where $\ff$ is the total membrane force and $\nn$ is the outward unit normal of $\gamma$. A no-slip and local inextensibility condition on $\gamma$ is imposed
-\begin{align}
-    \frac{d\xx}{dt} = \uu(\xx) \quad \text{and} \quad \nabla_{\gamma} \cdot \uu = 0,
-    \quad \xx \in \gamma,
-\end{align}
-where $\xx(s,t)$ is the arclength parameterization of $\gamma$.
-Along the solid wall $\Gamma$, we impose a Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a Hagen–Poiseuille flow at the inlet and outlet,
-\begin{align}
-    \UU(\xx) = \chi \left(1 - \left(\frac{y}{W}\right)^2 \right), \quad \xx = (x,y) \in \Gamma,
-\end{align}
-and $\UU$ is zero along the top and bottom of the channel. $W$ is the width of the channel and $\chi$ is the maximum velocity.
-
-We nondimensionalize the governing equations with a characteristic length scale $R_0 = 10^{-6}$~m, a maximum bending stiffness $b_{\max} = 10^{-19}$~J, and fluid viscosity $\mu = 5 \times 10^{-2}$~kg/ms.
-The resulting time scale is $\mu R_0^3/b_{\max} = 0.5$~s, the velocity scale is $b_{\max}/\mu R_0^2=2$~$\mu$m/s, the pressure scale is $b_{\max}/R_0^3 = 10^{-1}$~Pa, and the tension scale is $b_{\max}/R_0^2 = 10^{-7}$~N/m.
-A critical dimensionless parameter for the vesicle shape is its reduced area, $\alpha$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+where $\TT = -p\mathbf{I} + \mu\left(\nabla \uu + \nabla \uu^T \right)$
+is the hydrodynamic stress tensor, $\uu$ is the velocity, $p$ is the
+pressure, and $\mu$ is the fluid viscosity. Across the vesicle membrane,
+we require that the velocity is continuous and locally inextensible, and
+the membrane and hydrodynamic forces balance
+\begin{align}
+  \llbracket \uu \rrbracket = 0, \quad 
+  \llbracket \TT\nn \rrbracket = \ff, \quad 
+  \nabla_{\gamma} \cdot \uu = 0, \quad \xx \in \gamma,
+\end{align}
+where $\ff$ is the total membrane force and $\nn$ is the outward unit
+normal of $\gamma$.
+
+We nondimensionalize the governing equations with a characteristic
+length scale $R_0 = 10^{-6}$~m, a maximum bending stiffness $b_{\max} =
+10^{-19}$~J, and fluid viscosity $\mu = 5 \times 10^{-2}$~kg/ms. The
+resulting time scale is $\mu R_0^3/b_{\max} = 0.5$~s, the velocity scale
+is $b_{\max}/\mu R_0^2=2$~$\mu$m/s, the pressure scale is
+$b_{\max}/R_0^3 = 10^{-1}$~Pa, and the tension scale is $b_{\max}/R_0^2
+= 10^{-7}$~N/m. The dimensionless parameters regarding the vesicle
+properties are the reduced area $\alpha = 4\pi A/L^2$, where $A$ and $L$
+are the vesicle's area and length, respectively, and the
+floppy-to-stiffness ratio $\beta = b_{\min}/b_{\max}$. Since we consider
+flows in channels, we also define a dimensionless maximum imposed
+velocity, $\chi$, which sets a capillary number, and $W$ is the
+dimensionless width of the channel at the inlet and outlet. From this
+point onwards, all equations are dimenisionless.
+
+The multicomponet vesicle satisfies the no-slip boundary condition
+$\frac{d\xx}{dt} = \uu(\xx)$, where $\xx(s,t)$ is the arclength
+parameterization of $\gamma$. Along the solid wall $\Gamma$, we impose a
+Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a
+Hagen–Poiseuille flow at the inlet and outlet,
+\begin{align}
+  \UU(\xx) = \chi \left(1 - \left(\frac{y}{W}\right)^2 \right), 
+    \quad \xx = (x,y) \in \Gamma,
+\end{align}
+and $\UU$ is zero along the top and bottom of the channel.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Constitutive equations}
-Using the same model as~\citet{liu-mar-li-vee-low2017} and~\citet{soh-tse-li-voi-low2010}, the membrane forces depend on the Helfrich energy, line tension, and phase energy.
-The phase and bending energies are coupled through the bending modulus.
-In particular, the individual energies are
+Using the same model as~\citet{liu-mar-li-vee-low2017}
+and~\citet{soh-tse-li-voi-low2010}, the membrane forces depend on the
+Helfrich energy, line tension, and phase energy. The phase and bending
+energies are coupled through the bending modulus. In particular, the
+individual energies are
 \begin{align}
@@
 \end{align}
-where $b(u)$ is the lipid-dependent bending modulus, $\sigma$ is the vesicle's tension, $u$ is the lipid concentration, and $f(u) = \frac{1}{4}u^2(1-u)^2$ is the double-well potential with local minimums at $u=0$ and $u=1$.
-Here, $\kappa$ is the membrane curvature, $\ss$ is the tangent vector, and $s$ is the arclength.
-$a$ and $\epsilon$ are small parameters, and we use the same values as~\citet{soh-tse-li-voi-low2010}.
-The resulting membrane forces are
-\begin{align}
-    \ff_b &= -(b(u)\kappa \nn)_{ss} -\frac{3}{2}\left(b(u) \kappa^2 \ss\right)_s, \\
+where $u$ is the dimensionless lipid concentration, $b(u)$ is the lipid-dependent bending modulus, $\sigma$ is the vesicle's tension, and
+$f(u) = \frac{1}{4}u^2(1-u)^2$ is the double-well potential with local
+minimums at $u=0$ and $u=1$. Here, $\kappa$ is the membrane curvature,
+$\ss$ is the tangent vector, and $s$ is the arclength. We have adopted
+the same setup as~\citet{soh-se-li-voi-low2010} where $\epsilon \ll 1$
+ios a dimensionless parameter that controls the size of the transition
+region of $u$, and $a$ is the dimensional line tension scaled by
+$b_{\max}/L$. Both $\epsilon$ and $a$ are kept constant in all
+simulations. The resulting membrane forces are
+\begin{align}
+  \ff_b &= -(b(u)\kappa \nn)_{ss} -\frac{3}{2}
+    \left(b(u) \kappa^2 \ss\right)_s, \\
   \ff_t &= (\sigma \ss)_s, \\
@@
 \begin{align}
-    b(u) = b_{\max} (1-u) + b_{\min} u,
+    b(u) = (1-u) + \beta u.
     \label{eqn:linearBending}
 \end{align}
-where $b_{\max}$ and $b_{\min}$ are the maximum and minimum bending moduli, respectively.
-However, since the double-well potential does not have hard walls, the lipid concentration is not guaranteed to be confined to the interval $[0,1]$.
-This is problematic when $u > 1$ since this results in $b(u) < 0$ if $u > \frac{b_{\max}}{b_{\max} - b_{\min}}$, and such values of $u$ are possible when $b_{\min}$ is small and the vesicle is confined to a narrow region.
+However, since the double-well potential does not have hard walls, the
+lipid concentration is not guaranteed to be confined to the interval
+$[0,1]$. This is problematic when $u > 1$ since this results in $b(u) <
+0$ if $u > (\beta+1)^{-1}$, and such values of $u$ are possible when
+$\beta$ is small and the vesicle is confined to a narrow region.
 Therefore, in this work we parameterize the bending modulus as
 \begin{align}
-    b(u) = \frac{b_{\min} - b_{\max}}{2} \tanh\left(3\left(u - \frac{1}{2} \right)\right) + 
-           \frac{b_{\min} + b_{\max}}{2}.
+    b(u) = \frac{\beta-1}{2} \tanh\left(3\left(u-\frac{1}{2} \right)\right) + 
+           \frac{\beta + 1}{2}.
     \label{eqn:tanhBending}
@@
   \input{figures/concModels.tikz}
-    \caption{\label{fig:concModels} \small The linear bending model in red (equation~\eqref{eqn:linearBending}) and the the new hyperbolic bending model in blue (equation~\eqref{eqn:tanhBending}).
-Note that the new bending model satisfies $b \in (b_{\min},b_{\max})$ even if $u \notin [0,1]$.}
-\end{figure}
-
-Equation~\eqref{eqn:tanhBending} maps the local minimums of the double-well potential close to $b_{\min}$ and $b_{\max}$, but more importantly, b(u) remains bounded in $[b_{\min},b_{\max}]$ even when $u \notin [0,1]$ (Figure~\ref{fig:concModels}).
-To demonstrate the necessity of this new bending model, we consider a multicomponent vesicle in strong confinement with both bending models~\eqref{eqn:linearBending} and~\eqref{eqn:tanhBending}.
-The stiff-to-floppy ratio is $b_{\max}/b_{min} = 10^{-1}$.
-In the new model~\eqref{eqn:tanhBending}, the lipid concentration achieves a maximum value of $u \approx 1.002$ which results in a  minimum bending stiffness of $b(u) \approx b_{\min}$.
-However, if we use the linear bending model~\eqref{eqn:linearBending}, the lipid concentration achieves a maximum value of $u \approx 1.52$ which results in an unphsical negative bending stiffness of $b(u) \approx -0.5$.
-The vesicle shapes are in Figure~\ref{fig:bendingModels}, and the instability caused by the negative bending stiffness is near the region with negative curvature.
+  \caption{\label{fig:concModels} \small The linear bending model in red
+  (equation~\eqref{eqn:linearBending}) and the the new hyperbolic
+  bending model in blue (equation~\eqref{eqn:tanhBending}). Note that
+  the new bending model satisfies $b \in (\beta,1)$ even if $u \notin
+  [0,1]$.}
+\end{figure}
+
+Equation~\eqref{eqn:tanhBending} maps the local minimums of the
+double-well potential close to $\beta$ and $1$, but more
+importantly, b(u) remains bounded in $(\beta,1)$ even when $u
+\notin [0,1]$ (Figure~\ref{fig:concModels}). To demonstrate the
+necessity of this new bending model, we consider a multicomponent
+vesicle in strong confinement with both bending
+models~\eqref{eqn:linearBending} and~\eqref{eqn:tanhBending}. The
+stiff-to-floppy ratio is $\beta = 10^{-1}$. In the new
+model~\eqref{eqn:tanhBending}, the lipid concentration achieves a
+maximum value of $u \approx 1.002$ which results in a  minimum bending
+stiffness of $b(u) \approx \beta$. However, if we use the linear bending
+model~\eqref{eqn:linearBending}, the lipid concentration achieves a
+maximum value of $u \approx 1.52$ which results in an unphsical negative
+bending stiffness of $b(u) \approx -0.5$. The vesicle shapes are in
+Figure~\ref{fig:bendingModels}, and the instability caused by the
+negative bending stiffness is near the region with negative curvature.
 \begin{figure}[htp]
@@
 %    \end{tabular}
-    \caption{\label{fig:bendingModels} \small A multicomponent vesicle entering a closely-fitting channel using the (a) new bending model~\eqref{eqn:tanhBending}; (b) the linear model~\eqref{eqn:linearBending}.
-With the linear model, the vesicle bending modulus becomes negative, and this introduces an instability that first appears near the point with the largest negative curvature.
+\caption{\label{fig:bendingModels} \small A multicomponent vesicle
+  entering a closely-fitting channel using (a) the new bending
+  model~\eqref{eqn:tanhBending}; (b) the linear
+  model~\eqref{eqn:linearBending}. With the linear model, the vesicle
+  bending modulus becomes negative, and this introduces an instability
+  that first appears near the point with the largest negative curvature.
   The two plots are not at the same time step.}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Validation}
-Since we use a new bending model, we first validate that it reproduces the tank treading and phase treading dynamics reported in the literature.
-Figure~\ref{fig:treading} shows a tank treading (top) and a phase treading (bottom) multicomponent vesicle in an unconfined shear flow.
-These simulations align with the results reported by~\citet{liu-mar-li-vee-low2017} (cf.~Figures 3 and 4).
+Since we use a new bending model, we first validate that it reproduces
+the tank treading and phase treading dynamics reported in the
+literature. Figure~\ref{fig:treading} shows a tank treading (top) and a
+phase treading (bottom) multicomponent vesicle in an unconfined shear
+flow. These simulations align with the results reported
+by~\citet{liu-mar-li-vee-low2017} (cf.~Figures 3 and 4).
 \begin{figure}[H]
@@
   \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(b)}{figures/Fig4b.pdf}
-%    \includegraphics[width = \columnwidth,trim ={5.5cm 1.5cm 4cm 0},clip]{figures/Fig4a.pdf}
-%    \includegraphics[width = \columnwidth,trim ={5.5cm 1.5cm 4cm 0},clip]{figures/Fig4b.pdf}
-    \caption{\label{fig:treading} \small A multicomponent (a) tank-treading and (b) phase-treading vesicle using the new bending model~\eqref{eqn:tanhBending}.
-These simulations agree with the results presented by~\citet{liu-mar-li-vee-low2017}.}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \caption{\label{fig:treading} \small A multicomponent (a)
+  tank-treading and (b) phase-treading vesicle using the new bending
+  model~\eqref{eqn:tanhBending}. These simulations agree with the
+  results presented by~\citet{liu-mar-li-vee-low2017}.}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{\label{sec:NumericalMethods}Numerical Methods}

### 2023-03-23 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

@@
 
-The multicomponet vesicle satisfies the no-slip boundary condition
+On the multicomponet vesicle $\gamma$ the velocity satisfies the no-slip boundary condition
 $\frac{d\xx}{dt} = \uu(\xx)$, where $\xx(s,t)$ is the arclength
@@
 Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a
-Hagen–Poiseuille flow at the inlet and outlet,
+Hagen–Poiseuille flow at the inlet and outlet (where $y\in[-W,W]$),
 \begin{align}

### 2023-03-23 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
fixing broken link

--- 2023-03-23 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
@@
 \end{align}
-where $u$ is the dimensionless lipid concentration, $b(u)$ is the lipid-dependent bending modulus, $\sigma$ is the vesicle's tension, and
+where $u$ is the dimensionless lipid concentration, $b(u)$ is the
+lipid-dependent bending modulus, $\sigma$ is the vesicle's tension, and
 $f(u) = \frac{1}{4}u^2(1-u)^2$ is the double-well potential with local
@@
 $\ss$ is the tangent vector, and $s$ is the arclength. We have adopted
-the same setup as~\citet{soh-se-li-voi-low2010} where $\epsilon \ll 1$
-ios a dimensionless parameter that controls the size of the transition
+the same setup as~\citet{soh-tse-li-voi-low2010} where $\epsilon \ll 1$
+is a dimensionless parameter that controls the size of the transition
 region of $u$, and $a$ is the dimensional line tension scaled by
@@
 $[0,1]$. This is problematic when $u > 1$ since this results in $b(u) <
-0$ if $u > (\beta+1)^{-1}$, and such values of $u$ are possible when
+0$ if $u > (1 - \beta)^{-1}$, and such values of $u$ are possible when
 $\beta$ is small and the vesicle is confined to a narrow region.

### 2023-03-26 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on paper

@@
 \begin{align}
-  E_b &= \frac{1}{2}\int_{\gamma} b(u) \kappa^2 \, ds, \\
-  E_t &= \int_{\gamma} \sigma \, ds, \\
+  E_b &= \frac{1}{2}\int_{\gamma} b(u) \kappa^2 \, ds, \quad
+  E_t = \int_{\gamma} \sigma \, ds, \\
   E_p &= \frac{a}{\epsilon}\int_{\gamma}\left(
@@
 
+\begin{figure}[H]
+  \centering
+%  \input{figures/concModels.tikz} \\
+  \subfigimg[width=0.9\linewidth, clip ]{(a)}{figures/concModels.pdf}
+  \\
+  \subfigimg[width=0.9\linewidth, clip ]{(b)}{figures/oldbending.pdf}
+  \caption{\label{fig:concModels} \small (a) The linear bending model in
+  red (equation~\eqref{eqn:linearBending}) and the new hyperbolic
+  bending model in blue (equation~\eqref{eqn:tanhBending}). Note that
+  the new bending model satisfies $b \in (\beta,1)$ even if $u \notin
+  [0,1]$. (b) A multicomponent vesicle entering a closely-fitting
+  channel using the linear model~\eqref{eqn:linearBending}. The vesicle
+  bending modulus becomes negative, and this introduces an instability
+  that first appears near the point with the largest negative curvature.
+  }
+\end{figure}
+
 The lipid species $u$ is governed by a fourth-order Cahn-Hilliard equation that results in the lipids phase separating while conserving their total mass.
@@
 \end{align}
-\begin{figure}[H]
-  \centering
-  \input{figures/concModels.tikz}
-  \caption{\label{fig:concModels} \small The linear bending model in red
-  (equation~\eqref{eqn:linearBending}) and the the new hyperbolic
-  bending model in blue (equation~\eqref{eqn:tanhBending}). Note that
-  the new bending model satisfies $b \in (\beta,1)$ even if $u \notin
-  [0,1]$.}
-\end{figure}
-
-Equation~\eqref{eqn:tanhBending} maps the local minimums of the
+This maps the local minimums of the
 double-well potential close to $\beta$ and $1$, but more
 importantly, b(u) remains bounded in $(\beta,1)$ even when $u
-\notin [0,1]$ (Figure~\ref{fig:concModels}). To demonstrate the
+\notin [0,1]$ (Figure~\ref{fig:concModels}(a)). To demonstrate the
 necessity of this new bending model, we consider a multicomponent
@@
 model~\eqref{eqn:linearBending}, the lipid concentration achieves a
-maximum value of $u \approx 1.52$ which results in an unphsical negative
-bending stiffness of $b(u) \approx -0.5$. The vesicle shapes are in
-Figure~\ref{fig:bendingModels}, and the instability caused by the
-negative bending stiffness is near the region with negative curvature.
-\begin{figure}[htp]
-  \centering
-%    \begin{tabular}{@{}p{0.49\linewidth}@{\qquad}p{0.49\linewidth}@{}}
-  \subfigimg[width=0.48\linewidth, clip ]{(a)}{figures/newbending.pdf}
-  \subfigimg[width=0.48\linewidth, clip ]{(b)}{figures/oldbending.pdf}
-%    \end{tabular}
-\caption{\label{fig:bendingModels} \small A multicomponent vesicle
-  entering a closely-fitting channel using (a) the new bending
-  model~\eqref{eqn:tanhBending}; (b) the linear
-  model~\eqref{eqn:linearBending}. With the linear model, the vesicle
-  bending modulus becomes negative, and this introduces an instability
-  that first appears near the point with the largest negative curvature.
-  The two plots are not at the same time step.}
-\end{figure}
+maximum value of $u \approx 1.52$ which results in an unphysical
+negative bending stiffness of $b(u) \approx -0.5$. The corresponding
+vesicle shape is in Figure~\ref{fig:concModels}(b), and the instability
+caused by the negative bending stiffness is near the region with
+negative curvature.
+%\begin{figure}[htp]
+%  \centering
+%%    \begin{tabular}{@{}p{0.49\linewidth}@{\qquad}p{0.49\linewidth}@{}}
+%  \subfigimg[width=0.48\linewidth, clip ]{(a)}{figures/newbending.pdf}
+%%    \end{tabular}
+%\caption{\label{fig:bendingModels} \small A multicomponent vesicle
+%  entering a closely-fitting channel using (a) the new bending
+%  model~\eqref{eqn:tanhBending}; (b) the linear
+%  model~\eqref{eqn:linearBending}. With the linear model, the vesicle
+%  bending modulus becomes negative, and this introduces an instability
+%  that first appears near the point with the largest negative curvature.
+%  The two plots are not at the same time step.}
+%\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{\label{sec:NumericalMethods}Numerical Methods}
+The velocity field $\uu$ is written as a combination of a single-layer potential and a double-layer potential
+\begin{align}
+    \label{eqn:LPrep}
+    \uu(\xx) = S[\ff](\xx) + D[\eeta](\xx),
+\end{align}
+where
+\begin{align}
+    S[\ff](\xx) &= \frac{1}{4\pi\mu} \int_{\gamma} \left(-\log \rho \mathds{I} + \frac{\rr \otimes \rr}{\rho^2} \right)
+    \ff(\yy) \, ds_\yy, \\
+%
+    D[\eeta](\xx) &= \frac{1}{\pi} \int_{\Gamma} \frac{\rr \cdot \nn}{\rho^2}
+        \frac{\rr \otimes \rr}{\rho^2} \eeta(\yy) \, ds_\yy,
+\end{align}
+$\rr = \xx - \yy$, $\rho = |\rr|$, and $\mathds{I}$ is the $2 \times 2$ identity matrix.
+To avoid tangling of the vesicle membrane, it is parameterized in terms of the $\theta$-$L$ variables~\cite{hou-low-she1994}, where $L$ is the fixed vesicle length and $\theta$ is the opening angle of the tangent vector $\ss$.
+This requires decomposing the velocity field on $\gamma$ into its normal direction $V$ and tangential direction $T$.
+Then, the no-slip boundary condition for the vesicle velocity is
+\begin{align}
+    \frac{d\xx}{dt} = V \nn + T \ss + D[\eeta](\xx), \quad \xx \in \gamma.
+\end{align}
+The boundary condition on $\Gamma$ is imposed by requiring that $\eeta$ satisfies
+\begin{align}
+    \UU(\xx) = -\frac{1}{2}\eeta(\xx) + S[\ff](\xx) + D[\eeta](\xx), \quad \xx \in \Gamma.
+    \label{eqn:DLP_BIE}
+\end{align}
+After discretizing the geometry at collocation points, the single-layer potential is approximated with quadrature for weakly-singular integrands, and the double-layer potential is approximated with the spectrally accurate trapezoid rule.
+All arclength derivatives are computed with spectral accuracy using Fourier methods.
+Time stepping is performed with second-order Adams-Bashforth.
+The resulting linear system is solved with GMRES.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{\label{sec:NumericalMethods}Numerical Methods}
-The velocity field $\uu$ is written as a combination of a single-layer potential and a double-layer potential
-\begin{align}
-    \label{eqn:LPrep}
-    \uu(\xx) = S[\ff](\xx) + D[\eeta](\xx),
-\end{align}
-where
-\begin{align}
-    S[\ff](\xx) &= \frac{1}{4\pi\mu} \int_{\gamma} \left(-\log \rho \mathds{I} + \frac{\rr \otimes \rr}{\rho^2} \right)
-    \ff(\yy) \, ds_\yy, \\
-%
-    D[\eeta](\xx) &= \frac{1}{\pi} \int_{\Gamma} \frac{\rr \cdot \nn}{\rho^2}
-        \frac{\rr \otimes \rr}{\rho^2} \eeta(\yy) \, ds_\yy,
-\end{align}
-$\rr = \xx - \yy$, $\rho = |\rr|$, and $\mathds{I}$ is the $2 \times 2$ identity matrix.
-To avoid tangling of the vesicle membrane, it is parameterized in terms of the $\theta$-$L$ variables~\cite{hou-low-she1994}, where $L$ is the fixed vesicle length and $\theta$ is the opening angle of the tangent vector $\ss$.
-This requires decomposing the velocity field on $\gamma$ into its normal direction $V$ and tangential direction $T$.
-Then, the no-slip boundary condition for the vesicle velocity is
-\begin{align}
-    \frac{d\xx}{dt} = V \nn + T \ss + D[\eeta](\xx), \quad \xx \in \gamma.
-\end{align}
-The boundary condition on $\Gamma$ is imposed by requiring that $\eeta$ satisfies
-\begin{align}
-    \UU(\xx) = -\frac{1}{2}\eeta(\xx) + S[\ff](\xx) + D[\eeta](\xx), \quad \xx \in \Gamma.
-    \label{eqn:DLP_BIE}
-\end{align}
-After discretizing the geometry at collocation points, the single-layer potential is approximated with quadrature for weakly-singular integrands, and the double-layer potential is approximated with the spectrally accurate trapezoid rule.
-All arclength derivatives are computed with spectral accuracy using Fourier methods.
-Time stepping is performed with second-order Adams-Bashforth.
-The resulting linear system is solved with GMRES.
+\section{\label{sec:results}Hydrodynamics of a multicomponent vesicle under strong confinement}
 
@@
 
-To define the size of the top lubrication layer (the size of the bottom lubrication layer is defined similarly), we start with the distance between the vesicle and the top half of the confining geometry
-\begin{align}
-    d(\xx,\Gamma_\mathrm{top}) \inf_{\yy \in \Gamma_\mathrm{top}} \|\xx-\yy\|,
-\end{align}
-where $\Gamma_{\mathrm{top}}$ is the top portion of $\Gamma$.
-We then find all local minimums of $d(\xx,\Gamma_\mathrm{top})$, with the condition that $d(\xx,\Gamma_\mathrm{top}) < \beta$, where $\beta$ is a parameter.
-If no such local minimums exist, then the vesicle is too far from $\Gamma_\mathrm{top}$ to define a lubrication layer.
-If there are two or more local minimums, the left-most, $\xx_L$, and right-most, $\xx_R$, local minimums form the start and end of the lubrication layer.
-If there is only one local minimum, then $\xx_L$ and $\xx_R$ are the points on $\gamma$ to the left and right of this local minimum with the condition that $d(\xx_L,\Gamma_\mathrm{top}) = d(\xx_R,\Gamma_\mathrm{top}) = \beta$.
-Then, the segment $\gamma_{\mathrm{layer}} \subset \gamma$ consists of all points $\xx \in \gamma$ between $\xx_L$ and $\xx_R$ with the condition that $d(\xx,\Gamma_\mathrm{top}) < \beta$.
-Finally, the lubrication layer width is
+To define the size of the top lubrication layer (the size of the bottom
+lubrication layer is defined similarly), we let
+$d(\xx,\Gamma_\mathrm{top})$ be the minimum distance between the vesicle
+and the top half of the confining geometry.
+%\begin{align}
+%    d(\xx,\Gamma_\mathrm{top}) = \inf_{\yy \in \Gamma_\mathrm{top}} \|\xx-\yy\|,
+%\end{align}
+%where $\Gamma_{\mathrm{top}}$ is the top portion of $\Gamma$.
+We then find all local minimums of $d(\xx,\Gamma_\mathrm{top})$, with
+the condition that $d(\xx,\Gamma_\mathrm{top}) < \beta$, where $\beta$
+is a parameter. If no such local minimums exist, then the vesicle is too
+far from $\Gamma_\mathrm{top}$ to define a lubrication layer. If there
+are two or more local minimums, the left-most, $\xx_L$, and right-most,
+$\xx_R$, local minimums form the start and end of the lubrication layer.
+If there is only one local minimum, then $\xx_L$ and $\xx_R$ are the
+points on $\gamma$ to the left and right of this local minimum with the
+condition that $d(\xx_L,\Gamma_\mathrm{top}) =
+d(\xx_R,\Gamma_\mathrm{top}) = \beta$. Then, the segment
+$\gamma_{\mathrm{layer}} \subset \gamma$ consists of all points $\xx \in
+\gamma$ between $\xx_L$ and $\xx_R$ with the condition that
+$d(\xx,\Gamma_\mathrm{top}) < \beta$. Finally, the lubrication layer
+width is
 \begin{align}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{\label{sec:results}Hydrodynamics of a multicomponent vesicle under strong confinement}
 We consider both a single-component and a multicomponent vesicle suspended in two geometries: a closely-fitting geometry (stenosis) and a geometry that slowly contracts to a narrow neck and then quickly widens (contracting).

### 2023-05-15 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex

@@
 \section{\label{sec:Formulation}Formulation}
+\todo[inline]{Changes to be made to Figure~\ref{fig:schematic}.}
+\begin{itemize}
+  \item Remove labels $\Gamma$, $\Omega$, $\gamma$
+  \item Line on vesicle is too thick and change color scheme to same as
+    Fig 2
+  \item Change to a confined geometry that we use (stenosis)
+  \item Show a couple of vesicle shapes and the parabolic profile at
+    the inlet, outlet, and in the middle
+\end{itemize}
+
 We consider a single multicomponent vesicle $\omega$ with boundary $\gamma$ suspended in a confined geometry $\Omega \subset \RR ^2$ with boundary $\Gamma$ (Figure~\ref{fig:schematic}).
@@
   \includegraphics[trim = 0.3cm 0cm 1cm 0cm, clip=true,width=0.9\columnwidth]{figures/schematic.pdf}
-    \caption{\label{fig:schematic}\small A single multicomponent vesicle with boundary $\gamma$ suspended in a domain $\Omega$ with boundary $\Gamma$.
-The dark red regions are the ``stiff" regions corresponding to the maximum bending stiffness $b_{\max}=1$.
-The dark blue regions are the ``floppy" regions corresponding to the minimum bending stiffness $b_{\min}=0.1$ The vesicle dynamics are determined by a combination of phase, bending, and tension energies, and an imposed flow on $\Gamma$.
-}
+  \caption{\label{fig:schematic}\small A single multicomponent vesicle
+  with boundary $\gamma$ suspended in a domain $\Omega$ with boundary
+  $\Gamma$. The dark red regions are the ``stiff'' regions corresponding
+  to the maximum bending stiffness $b_{\max}=1$. The dark blue regions
+  are the ``floppy'' regions corresponding to the minimum bending
+  stiffness $b_{\min}=0.1$ The vesicle dynamics are determined by a
+  combination of phase, bending, and tension energies, and an imposed
+  flow on $\Gamma$. }
 \end{figure}
@@
 flows in channels, we also define a dimensionless maximum imposed
-velocity, $\chi$, which sets a capillary number, and $W$ is the
+velocity, $U$, which sets a capillary number, and $W$ is the
 dimensionless width of the channel at the inlet and outlet. From this
@@
 \begin{align}
-  \UU(\xx) = \chi \left(1 - \left(\frac{y}{W}\right)^2 \right), 
+  \UU(\xx) = U \left(1 - \left(\frac{y}{W}\right)^2 \right), 
     \quad \xx = (x,y) \in \Gamma,
@@
 and $\UU$ is zero along the top and bottom of the channel.
+\todo[inline]{Need to define capillary number and diffusion time scale.}
 
@@
 0$ if $u > (1 - \beta)^{-1}$, and such values of $u$ are possible when
-$\beta$ is small and the vesicle is confined to a narrow region.
-Therefore, in this work we parameterize the bending modulus as
+$\beta \ll 1$, $Ca \gg 1$, or the vesicle is confined to a narrow
+region.  Therefore, in this work we parameterize the bending modulus as
 \begin{align}
@@
   geometry. The vesicle's reduced area is $\alpha = 0.6$ and the
-  dimensionless maximum velocity is $\chi = 0.25$. The vesicles are: (a)
+  dimensionless maximum velocity is $U = 0.25$. The vesicles are: (a)
   single-component with bending modulus $b=1$; (b) single-component with
@@
 We consider a vesicle with reduced area $\alpha = 0.6$ passing through a
-closely-fitting channel, with a dimensionless maximum velocity of $\chi
-= 0.25$. Figure~\ref{fig:RA6} shows six time steps of a single-component
+closely-fitting channel, with a dimensionless maximum velocity of $U =
+0.25$. Figure~\ref{fig:RA6} shows six time steps of a single-component
 vesicle with bending stiffness (a) $b=1$ and (b) $b=0.55$, and a
@@
   geometry. The vesicle's reduced area is $\alpha = 0.4$ and the
-  dimensionless maximum velocity is $\chi = 0.25$. The vesicles are: (a)
+  dimensionless maximum velocity is $U = 0.25$. The vesicles are: (a)
   single-component with bending modulus $b=1$; (b) single-component with
@@
 
-While the size of the lubrication layers affect the tank-treading behavior and the excess pressure, it has almost no effect on the migration speed of the vesicle.
-In Figure~\ref{fig:vesVelocity}, we plot the average velocity of the vesicle as it passes through the stenosed region.
-With the exception of the single-component vesicle with $b=1$ and $\alpha = 0.6$, the average vesicle speed is constant.
-Obviously, this average velocity would be affected by the maximum imposed velocity, $\chi$.
+While the size of the lubrication layers affect the tank-treading
+behavior and the excess pressure, it has almost no effect on the
+migration speed of the vesicle. In Figure~\ref{fig:vesVelocity}, we plot
+the average velocity of the vesicle as it passes through the stenosed
+region. With the exception of the single-component vesicle with $b=1$
+and $\alpha = 0.6$, the average vesicle speed is constant. Obviously,
+this average velocity would be affected by the maximum imposed velocity,
+$U$.
 
@@
   \end{minipage}
-  \caption{\label{fig:Energy} \small The Bending (blue), tension (yellow), and phase (red) energies for a (a/b) single-component vesicle with $b=1$, (c/d) single-component vesicle with $b = 0.55$, and (e/f) multicomponent vesicle.
-The reduced areas are $alpha = 0.4$ (a/c/e) and $\alpha = 0.6$ (b/d/f).}
+  \caption{\label{fig:Energy} \small The Bending (blue), tension
+  (yellow), and phase (red) energies for a (a/b) single-component
+  vesicle with $b=1$, (c/d) single-component vesicle with $b = 0.55$,
+  and (e/f) multicomponent vesicle. The reduced areas are $\alpha = 0.4$
+  (a/c/e) and $\alpha = 0.6$ (b/d/f).}
 \end{figure}
@@
     \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(c)}{figures/leftSep.pdf}
-     \caption{\label{fig:RA6leftRightRand} \small A multicomponent vesicle with 50\% floppy region passing through a contracting geometry.
-The vesicle's reduced area is $\alpha = 0.6$ and the dimensionless maximum velocity is $\chi = 0.25$.
-The vesicles are: (a) the initial lipid-species distribution is fully separated on the right side of the vesicle; (b) the initial lipid-species distribution is randomly distributed (not fully separated) on the vesicle membrane; (d) the initial lipid-species distribution is fully separated on the left side of the vesicle.
-The vesicles with a larger percentage of floppy regions pass through the neck earlier than the vesicles with less percentage of floppy regions.
-The vesicle either completely or partially reorients itself so that the floppy region is in the back and the stiff region is in the front.}
+  \caption{\label{fig:RA6leftRightRand} \small A multicomponent vesicle
+  with 50\% floppy region passing through a contracting geometry. The
+  vesicle's reduced area is $\alpha = 0.6$ and the dimensionless maximum
+  velocity is $U = 0.25$. The vesicles are: (a) the initial
+  lipid-species distribution is fully separated on the right side of the
+  vesicle; (b) the initial lipid-species distribution is randomly
+  distributed (not fully separated) on the vesicle membrane; (d) the
+  initial lipid-species distribution is fully separated on the left side
+  of the vesicle. The vesicles with a larger percentage of floppy
+  regions pass through the neck earlier than the vesicles with less
+  percentage of floppy regions. The vesicle either completely or
+  partially reorients itself so that the floppy region is in the back
+  and the stiff region is in the front.}
 \end{figure}
@@
 
-In Figure~\ref{fig:RA5}, we consider a vesicle with reduced area $\alpha = 0.5$ and the dimensionless flow rate is $\chi = 0.25$.
-We start with a single-component vesicle and then increase the percentage of the vesicle membrane that is floppy.
-By comparing the vesicle location at the time step just before the vesicle passes through the constriction, we can immediately see that vesicles with membranes that have larger percentage of floppy regions reach and pass through the neck earlier.
-The dimensionless times that the entire vesicle first passes through the neck are reported in Table~\ref{tbl:contractingTimes}.
+In Figure~\ref{fig:RA5}, we consider a vesicle with reduced area $\alpha
+= 0.5$ and the dimensionless flow rate is $U = 0.25$. We start with a
+single-component vesicle and then increase the percentage of the vesicle
+membrane that is floppy. By comparing the vesicle location at the time
+step just before the vesicle passes through the constriction, we can
+immediately see that vesicles with membranes that have larger percentage
+of floppy regions reach and pass through the neck earlier. The
+dimensionless times that the entire vesicle first passes through the
+neck are reported in Table~\ref{tbl:contractingTimes}.
 
@@
     \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(e)}{figures/Fig14e_newPaper.pdf}
-     \caption{\label{fig:RA5} \small A vesicle passing through a contracting geometry.
-The vesicle's reduced area is $\alpha = 0.5$ and the dimensionless maximum velocity is $\chi = 0.25$.
-The vesicles are: (a) single-component with bending modulus $b=1$; (b) multicomponent with 15\% floppy region; (c) multicomponent with 25\% floppy region; (d) multicomponent with 35\% floppy region; (e) multicomponent with 45\% floppy region.
-The vesicles with a larger percentage of floppy regions pass through the neck earlier than the vesicles with less percentage of floppy regions.}
+  \caption{\label{fig:RA5} \small A vesicle passing through a
+  contracting geometry. The vesicle's reduced area is $\alpha = 0.5$ and
+  the dimensionless maximum velocity is $U = 0.25$. The vesicles are:
+  (a) single-component with bending modulus $b=1$; (b) multicomponent
+  with 15\% floppy region; (c) multicomponent with 25\% floppy region;
+  (d) multicomponent with 35\% floppy region; (e) multicomponent with
+  45\% floppy region. The vesicles with a larger percentage of floppy
+  regions pass through the neck earlier than the vesicles with less
+  percentage of floppy regions.}
 \end{figure}

### 2023-05-24 shuwang_rewrite/tstep.m
added reference

@@ -239,8 +239,6 @@ if o.confined
   bgFlowWalls = o.bgFlow(walls.X, o.shearRate, o.farFieldFlow);
   rhsWalls = bgFlowWalls - vesVel2Wall;
   etaout = o.etaSolver(rhsWalls);
-else
-  etaout = etain;
 end
 %Add in the fdotn term for the semipermeability model
 fdotn = tau(1:end/2).*sin(theta)-tau(end/2+1:end).*cos(theta);

### 2023-06-05 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
added reference
added a few more refs
adding some of the postprocessing docs

@@
 
+\citet{gur-pak-tay-siv-sac2023} look at the effect of membrane
+viscoelasticity.
+
+\citet{ram-kom-sek-ima2010}
+
+\citet{che-lyu-jae-leo2020}
+
+\citet{wan-ii-sug-nod-jin-liu-che-gon2023}
+
+\citet{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019}
+is paper with Sean Sun that looks at linear and non-linear shear in the
+boundary layer caused by tank treading behavior.
+
 %\citet{yan-ima-tan2010} perform experiments with multicomponent GUVs.
-They observe phase separation and budding of vesicles with a small reduced volume.
-However, the budding often requires a significant amount of time (tens of minutes), but ours occur much earlier in the contracting example by using narrow constrictions.
-Equations (2)--(5) shows a model similar to ours, and they use a linear dependence between the bending modulus and lipid concentration in the paragraph immediately after these equations.
-The include an energy term that depends on the difference in area between the inner and outer monolayer of lipids.
-Osmotic gradients are used to control the vesicle volume.
+%They observe phase separation and budding of vesicles with a small
+%reduced volume. However, the budding often requires a significant
+%amount of time (tens of minutes), but ours occur much earlier in the
+%contracting example by using narrow constrictions. Equations (2)--(5)
+%shows a model similar to ours, and they use a linear dependence between
+%the bending modulus and lipid concentration in the paragraph
+%immediately after these equations. The include an energy term that
+%depends on the difference in area between the inner and outer monolayer
+%of lipids. Osmotic gradients are used to control the vesicle volume.
 

### 2023-06-05 shuwang_rewrite/output/VisualizingBulk.m

@@ -1,0 +1,108 @@
+addpath ..
+load('~/projects/brinkman/vesicle_code/docs/confinedMulti/makefigs/AshleyFiles/Stenosis_RAp4_MCp5.mat');
+
+N = length(posx1(:,:,1));
+oc = curve(N);
+op = poten(N);
+
+Nbd = 1024;
+geomCenter = [0;0];
+wallGeometry = 'longchoke';
+ocw = curve(Nbd);
+[~,XWalls] = ocw.initConfig(Nbd,false,'scale', 1, ...
+             'center', geomCenter, 'geometry', wallGeometry);
+
+options.confined = true;
+params.shearRate = 0.25;
+params.farFieldFlow = 'longchoke';
+params.bendsti = 1; %maximum bending stiffness
+params.bendratio = 0.1; %ratio between max and min bending 
+                                %stiffness
+params.viscosityInside = 1;
+params.viscosityOutside = 1;
+params.SPcoeff = 0; %Semi-permeability coefficient
+params.gmresTol = 1e-8; %GMRES tolerance
+params.gmresMaxIter = 20;
+params.saveRate = 1;
+walls = capsules(XWalls,[]);
+tol = 1e-4;
+%tol = 1e-1;
+
+% care about vesicle when it's at the third, fourth, fifth, and sixth of
+% these values
+meancenters = linspace(-22,22,8);
+
+centers = squeeze(mean(posx1));
+[~,k] = min(abs(centers - meancenters(6)));
+
+xx1 = posx1(:,:,k);
+yy1 = posy1(:,:,k);
+concc1 = conc1(:,:,k);
+
+ves = capsules([xx1;yy1],concc1,params); 
+tt = tstep(params,options,ves,walls);
+rhsWalls = tt.bgFlow(walls.X, tt.shearRate, tt.farFieldFlow);
+eta = tt.etaSolver(rhsWalls);
+
+for i = 1:length(k)
+  xx1 = posx1(:,:,k(i));
+  yy1 = posy1(:,:,k(i));
+  concc1 = conc1(:,:,k(i));
+  
+  ves = capsules([xx1;yy1],concc1,params); 
+  tt = tstep(params,options,ves,walls);
+
+  [xtar,ytar] = meshgrid(min(xx1)-1:.01:max(xx1)+1,-.69:.01:.69);
+  xtar = xtar(:); ytar = ytar(:);
[…]

### 2023-06-05 vesicle_code/docs/confinedMulti/makefigs/AshleyFiles/BLanalysis.m

@@ -1,0 +1,83 @@
+if 0
+load('Stenosis_RAp4_SC_bulk_targets.mat');
+load('Stenosis_RAp4_SC_bulk.mat');
+load('Stenosis_RAp4_SC_bulk_pressure.mat');
+load('walls.dat');
+end
+
+xx = xtar; yy = ytar;
+uu = reshape(uxtar,139,509);
+vv = reshape(uytar,139,509);
+xwalls = XWalls(1:end/2);
+ywalls = XWalls(end/2+1:end);
+
+%uu = uu - mean(uxvel);
+
+posx = squeeze(posx1(:,:,45001));
+posy = squeeze(posy1(:,:,45001));
+
+xmin = 2.0;
+xmax = 2.5;
+% index of points in a given x-range
+s = find((xx(1,:) > xmin) & (xx(1,:) < xmax));
+
+figure(1); clf; hold on
+plot(posx,posy,'r','linewidth',2);
+plot(xwalls,ywalls,'k','linewidth',2);
+step = 1;
+quiver(xx(1:step:end,1:step:end),yy(1:step:end,1:step:end),...
+       uu(1:step:end,1:step:end),vv(1:step:end,1:step:end),'b')
+
+%axis([min(min(xx)) max(max(xx)) min(min(yy)) max(max(yy))])
+axis equal;
+axis([xmin xmax -0.8 -0.3])
+
+posx_neg = posx(posy < -0.4);
+posy_neg = posy(posy < -0.4);
+%k = 1;
+figure(2); clf; hold on; figure(1);
+for k = 1:1
+%for k = 1:numel(s)
+  [~,kmin] = min(abs(posx_neg - xx(1,s(k))));
+  s2 = find(yy(:,1) < posy_neg(kmin));
+  plot(xx(s2,s(k)),yy(s2,s(k)),'g.')
+
+  figure(2);
+%  plot(yy(s2,s(k)),uu(s2,s(k)))
+  yyy = yy(s2,s(k)) - yy(s2(1),s(k));
+  h = yyy(end);
+
+  chi = 1/h;
+%  vel = chi*uu(s2,s(k));
+  vel = uu(s2,s(k));
+%  vel = vel/vel(end);
+
+%  plot(yyy/yyy(end),chi*uu(s2,s(k)))
+  plot(yyy/h,(h*vel)/(h*vel(end)))
+  figure(1);
+end
+
+z = linspace(0,1,100);
+figure(2); hold on;
[…]

### 2023-06-05 vesicle_code/docs/confinedMulti/makefigs/AshleyFiles/Fig6driver.m

@@ -1,0 +1,13 @@
+figure(1); clf;
+ha = tight_subplot(3,1,0.02,0,[0 0.02]);
+MakeSnaps('Stenosis_RAp6_SC.mat',1,false,ha);
+MakeSnaps('Stenosis_RAp6_SCp55.mat',2,false,ha);
+MakeSnaps('Stenosis_RAp6_MCp5.mat',3,true,ha);
+
+f = figure(1);
+set(f,'Units','Inches');
+pos = get(f,'Position');
+set(f,'PaperPositionMode','Auto','PaperUnits','Inches',...
+    'PaperSize',[pos(3), pos(4)])
+set(f,'Position',[0 0 19 6.4]);
+print(f,'-dpdf','STENOSIS_RAp6MCp5.pdf','-r0')

### 2023-06-05 vesicle_code/docs/confinedMulti/makefigs/AshleyFiles/Fig7driver.m

@@ -1,0 +1,13 @@
+figure(1); clf;
+ha = tight_subplot(3,1,0.02,0,[0 0.02]);
+MakeSnaps('Stenosis_RAp4_SC.mat',1,false,ha);
+MakeSnaps('Stenosis_RAp4_SCp55.mat',2,false,ha);
+MakeSnaps('Stenosis_RAp4_MCp5.mat',3,true,ha);
+
+f = figure(1);
+set(f,'Units','Inches');
+pos = get(f,'Position');
+set(f,'PaperPositionMode','Auto','PaperUnits','Inches',...
+    'PaperSize',[pos(3), pos(4)])
+set(f,'Position',[0 0 19 6.4]);
+print(f,'-dpdf','STENOSIS_RAp4MCp5.pdf','-r0')

### 2023-06-05 vesicle_code/docs/confinedMulti/makefigs/AshleyFiles/MakeSnaps.m

@@ -1,0 +1,131 @@
+function [] = MakeSnaps(file,sp,cb,ha)
+%if ~exist('posx1')
+%  load Stenosis_RAp6_MCp5.mat
+%end
+load(file);
+
+addpath ../../../../../shuwang_rewrite
+
+bmin = .1;
+bmax = 1;
+a = 100;
+
+points = linspace(-22,22,8);
+%points = [-25,12.9,13.5,14.9271,15.6729,15.871,16.5];
+%points = [0.05,0.15,0.2,0.28,0.31,0.34,0.4,0.5];
+
+a = find(mean(squeeze(posx1))>=points(1));
+b = find(mean(squeeze(posx1))>=points(2));
+c = find(mean(squeeze(posx1))>=points(3));
+d = find(mean(squeeze(posx1))>=points(4));
+e = find(mean(squeeze(posx1))>=points(5));
+f = find(mean(squeeze(posx1))>=points(6));
+g = find(mean(squeeze(posx1))>=points(7));
+h = find(mean(squeeze(posx1))>=points(8));
+k = [a(1),b(1),c(1),c(1),c(1),c(1),d(1),e(1),f(1),g(1),h(1)];
+
+Nbd = 2048;
+geomCenter = [0;0];
+wallGeometry = 'longchoke';
+oc = curve(Nbd);
+[~,Xwalls] = oc.initConfig(Nbd,false,...
+             'scale', 1, ...
+             'center', geomCenter, 'geometry', wallGeometry);
+[xwalls,ywalls] = oc.getXY(Xwalls);
+xwalls = [xwalls(:);xwalls(1:4)];
+ywalls = [ywalls(:);ywalls(1:4)];
+
+N = length(posx1(:,:,1));
+oc = curve(N);
+
+axes(ha(sp));
+%subplot(3,1,sp);
+%figure(1); clf
+plot(xwalls,ywalls, 'k', 'linewidth', 2)
+axis equal
+hold on
+
+color1 = [0 0 1];
+%color2 = [0 1 1];
+color2 = [0.5 1 0];
+color3 = [1 0 0];
+t = linspace(0,1,256)';
+map1 = (1-t)*color1 + t*color2;
+map2 = (1-t(2:end))*color2 + t(2:end)*color3;
+map = [map1;map2];
+colormap(map);
+
+%colormap(parula);
+%colormap(hsv);
[…]

### 2023-06-19 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
adding in velocity result within lubrication layer

@@
 
-Finally, we consider the three different energies---bending, tension, and phase---for each of the single-component and multicomponent vesicles.
-In Figure~\ref{fig:Energy}, we plot these energies as a function of the vesicle's center of mass.
-As a reminder, the vesicle enters the constriction at $x=-15$ and exits at $x=15$.
-Also note that the single-component vesicle does not have a phase energy.
-A few general trends can immediately be seen.
-First, as the vesicle enters the stenosed region, there are sharp jumps in both the tension and bending energies, as expected.
-Next, the multicomponent vesicles only coarsen when the vesicle is not in the stenosed region.
-Finally, when coarsening does occur, there are rapid changes in the tension energy.
-
-%In the single-component runs, ...
-In the multicomponent runs, we see that phase separation does not occur in the channel.
-When it does occur, we see spikes in the bending and tension energies.
-\todo[inline]{Discussion of what we see}
+Finally, we consider the three different energies---bending, tension,
+and phase---for each of the single-component and multicomponent
+vesicles. In Figure~\ref{fig:Energy}, we plot these energies as a
+function of the vesicle's center of mass. As a reminder, the vesicle
+enters the constriction at $x=-15$ and exits at $x=15$. Also note that
+the single-component vesicle does not have a phase energy. A few general
+trends can immediately be seen. First, as the vesicle enters the
+stenosed region, there are sharp jumps in both the tension and bending
+energies, as expected. Next, the multicomponent vesicles only coarsen
+when the vesicle is not in the stenosed region. Finally, when coarsening
+does occur, there are rapid changes in the tension energy.
 
@@
   (a/c/e) and $\alpha = 0.6$ (b/d/f).}
+\end{figure}
+
+When a vesicle is tank-treading near a solid wall, the flow in the thin
+layer of fluid includes both a linear profile and a Poiseuille
+profile~\cite{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019}.
+The magnitude of the Poiseuille profile is determined by the pressure
+gradient between the vesicle and the soild wall, while the linear
+profile is determined by the tangential velocity of the vesicle relative
+to the solid wall.
+
+Using the definition of the lubrcication layer outlined in Section ???,
+fit the horizontal flow profile to a quadratic function and plot the
+coefficients of the Poisseuille and linear shear in Figure~\ref{}. We
+only consider cases where the vesicle has reached a steady shape is only
+under going tank treading. We observe that the Poisseuille coefficient
+can be either positive or negative, meaning that the pressure in the
+lubcrication layer switches signs. This behavior is caused when the
+tangential force on the vesicle
+\begin{align}
+  \mathbf{F}_{\tt} = -\sigma_s + u_s \frac{\delta E^m}{\delta u},
+\end{align}
+where
+\begin{align}
+  \frac{\delta E^m}{\delta u} = \frac{a}{\epsilon} 
+    (f'(u) - \epsilon^2 u_{ss}) + \frac{b'(u)}{2} \kappa^2
+\end{align}
+is the variational derivative of the membrane energy with respect to the
+lipid concentration~\cite{soh-tse-li-voi-low2010}. Note that in the
+single-component case, the tangential force is $\mathbf{F}_\tt =
+=\sigma_s$ which is the usual Marangoni effect.
+
+\begin{figure}
+%  \begin{minipage}{0.99\columnwidth}
+    \centering
+    \subfigimg[width=\columnwidth]{(a)}{figures/SC_top.pdf}
+    \subfigimg[width=\columnwidth]{(b)}{figures/SC_bot.pdf}
+    \subfigimg[width=\columnwidth]{(a)}{figures/SCp55_top.pdf}
+    \subfigimg[width=\columnwidth]{(b)}{figures/SCp55_bot.pdf}
+    \subfigimg[width=\columnwidth]{(a)}{figures/MCp5_top.pdf}
+    \subfigimg[width=\columnwidth]{(b)}{figures/MCp5_bot.pdf}
+%  \end{minipage}
+%  \hfill
+%  \begin{minipage}{0.49\columnwidth}
+%    \centering
+%    \subfigimg[width=\textwidth]{(b)}{figures/Fig13b.pdf}
+%    \subfigimg[width=\textwidth]{(d)}{figures/Fig13d.pdf}
+%    \subfigimg[width=\textwidth]{(f)}{figures/Fig13f.pdf}
+%  \end{minipage}
+%  \caption{\label{fig:Energy} \small The Bending (blue), tension
+%  (yellow), and phase (red) energies for a (a/b) single-component
+%  vesicle with $b=1$, (c/d) single-component vesicle with $b = 0.55$,
+%  and (e/f) multicomponent vesicle. The reduced areas are $\alpha = 0.4$
+%  (a/c/e) and $\alpha = 0.6$ (b/d/f).}
 \end{figure}

### 2023-06-19 shuwang_rewrite/curve.m

@@ -531,7 +531,6 @@ L = sum(sqrt(Dx.^2 + Dy.^2))/N;
 cur = (Dx.*DDy - Dy.*DDx)/L^3;
 % compute curvature
 
-%IK = o.modes(N);
 theta = o.intFT(L*cur-2*pi,o.IK);
 % integrate the curature to find the opening angle
 
@@ -619,7 +618,17 @@ function dx = rmLinearPart(o,N,theta)
 
 % function with the same increase over a period of 2*pi as the angle
 % theta
+
+% need to filter theta a bit
+IK = o.IK;
+%o.IK(abs(o.IK) > 2*pi*N/4) = 0;
+
 dx = o.diffFT([theta - 2*pi*(0:1:N-1)'/N]) + 2*pi;
+%semilogy(abs(fftshift(fft(theta - 2*pi*(0:1:N-1)'/N))))
+%semilogy(abs(fftshift(fft(dx))))
+%pause
+
+o.IK = IK;
 
 end %rmLinearPart
 
@@ -709,8 +718,8 @@ N2Hat(1) = 0;
 N2 = real(ifft(N2Hat));
 
 end %frconim
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 function RHSflux = fluxj(o,ves,epsch,consta)
 %This routine computes the forcing on the RHS flux OF THE Cahn_Hillard
 %Equation for rcon periodic on [0,1] and for closed curves. RHSflux are the
@@ -739,17 +748,42 @@ rbn = (b1 - b0)/2*tanh(3*(rcon - 0.5)) + (b0 + b1)/2;
 rbndu = (3/2)*(b1 - b0)*sech(3*(rcon-0.5)).^2; 
 %compute the curvature
 dkap = o.acurv(N,ves.theta,L);
+dkap = ves.cur; % TODO: COMMENT OUT LATER
 %term3 is b'(u)/2 * kappa^2 in eq (13)
 term3 = 0.5*rbndu.*dkap.^2;
 %RHSflux is a/eps(f'(u)-eps^2u_ss) + b'(u)/2 * kappa^2 terms in eq (13) 
[…]

### 2023-06-19 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on paper

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{\label{sec:Formulation}Formulation}
-\todo[inline]{Changes to be made to Figure~\ref{fig:schematic}.}
-\begin{itemize}
-  \item Remove labels $\Gamma$, $\Omega$, $\gamma$
-  \item Line on vesicle is too thick and change color scheme to same as
-    Fig 2
-  \item Change to a confined geometry that we use (stenosis)
-  \item Show a couple of vesicle shapes and the parabolic profile at
-    the inlet, outlet, and in the middle
-\end{itemize}
-
-We consider a single multicomponent vesicle $\omega$ with boundary $\gamma$ suspended in a confined geometry $\Omega \subset \RR ^2$ with boundary $\Gamma$ (Figure~\ref{fig:schematic}).
+%\todo[inline]{Changes to be made to Figure~\ref{fig:schematic}.}
+%\begin{itemize}
+%  \item Remove labels $\Gamma$, $\Omega$, $\gamma$
+%  \item Line on vesicle is too thick and change color scheme to same as
+%    Fig 2
+%  \item Change to a confined geometry that we use (stenosis)
+%  \item Show a couple of vesicle shapes and the parabolic profile at
+%    the inlet, outlet, and in the middle
+%\end{itemize}
 \begin{figure}[H]
   \centering
-  \includegraphics[trim = 0.3cm 0cm 1cm 0cm, clip=true,width=0.9\columnwidth]{figures/schematic.pdf}
+%  \includegraphics[trim = 0.3cm 0cm 1cm 0cm, clip=true,width=0.9\columnwidth]{figures/schematic.pdf}
+  \includegraphics[width=0.9\columnwidth]{figures/schematic.pdf}
   \caption{\label{fig:schematic}\small A single multicomponent vesicle
-  with boundary $\gamma$ suspended in a domain $\Omega$ with boundary
-  $\Gamma$. The dark red regions are the ``stiff'' regions corresponding
-  to the maximum bending stiffness $b_{\max}=1$. The dark blue regions
-  are the ``floppy'' regions corresponding to the minimum bending
-  stiffness $b_{\min}=0.1$ The vesicle dynamics are determined by a
-  combination of phase, bending, and tension energies, and an imposed
-  flow on $\Gamma$. }
-\end{figure}
-The fluid is assumed to have zero Reynolds number and is therefore governed by the incompressible Stokes equations
+  suspended in a strongly-confined stenosis. The color is the
+  dimensionless stiffness which varies from $b_{\min} = 0.1$ to
+  $b_{\max} = 1$. The vesicle dynamics are determined by a combination
+  of phase, bending, and tension energies, and an imposed flow (blue
+  arrows).}
+%  \caption{\label{fig:schematic}\small A single multicomponent vesicle
+%  with boundary $\gamma$ suspended in a domain $\Omega$ with boundary
+%  $\Gamma$. The dark red regions are the ``stiff'' regions corresponding
+%  to the maximum bending stiffness $b_{\max}=1$. The dark blue regions
+%  are the ``floppy'' regions corresponding to the minimum bending
+%  stiffness $b_{\min}=0.1$ The vesicle dynamics are determined by a
+%  combination of phase, bending, and tension energies, and an imposed
+%  flow on $\Gamma$. }
+\end{figure}
+We consider a single multicomponent vesicle $\omega$ with boundary
+$\gamma$ suspended in a confined geometry $\Omega \subset \RR ^2$ with
+boundary $\Gamma$ (Figure~\ref{fig:schematic}). The fluid is assumed to
+have zero Reynolds number and is therefore governed by the
+incompressible Stokes equations
 \begin{align}
@@
   \llbracket \uu \rrbracket = 0, \quad 
-  \llbracket \TT\nn \rrbracket = \ff, \quad 
-  \nabla_{\gamma} \cdot \uu = 0, \quad \xx \in \gamma,
+  \nabla_{\gamma} \cdot \uu = 0, \quad \xx \in \gamma, \quad
+  \llbracket \TT\nn \rrbracket = \ff, 
 \end{align}
 where $\ff$ is the total membrane force and $\nn$ is the outward unit
-normal of $\gamma$.
+normal of $\gamma$. By parameterizing $\gamma$ as $\xx(s,t)$, where $s$
+is arclength and $t$ is time, the no-slip boundary condition is
+$\frac{d\xx}{dt} = \uu(\xx)$.  Along the solid wall $\Gamma$, we impose
+a Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a
+Hagen–Poiseuille flow at the inlet and outlet (where $y\in[-W,W]$),
+\begin{align}
+  \UU(\xx) = U \left(1 - \left(\frac{y}{W}\right)^2 \right), 
+    \quad \xx = (x,y) \in \Gamma,
+\end{align}
+and $\UU$ is zero along the top and bottom of the channel.
 
@@
 
-On the multicomponet vesicle $\gamma$ the velocity satisfies the no-slip boundary condition
-$\frac{d\xx}{dt} = \uu(\xx)$, where $\xx(s,t)$ is the arclength
-parameterization of $\gamma$. Along the solid wall $\Gamma$, we impose a
-Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a
-Hagen–Poiseuille flow at the inlet and outlet (where $y\in[-W,W]$),
-\begin{align}
-  \UU(\xx) = U \left(1 - \left(\frac{y}{W}\right)^2 \right), 
-    \quad \xx = (x,y) \in \Gamma,
-\end{align}
-and $\UU$ is zero along the top and bottom of the channel.
 \todo[inline]{Need to define capillary number and diffusion time scale.}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Constitutive equations}
-Using the same model as~\citet{liu-mar-li-vee-low2017}
-and~\citet{soh-tse-li-voi-low2010}, the membrane forces depend on the
-Helfrich energy, line tension, and phase energy. The phase and bending
-energies are coupled through the bending modulus. In particular, the
-individual energies are
+Using the model first introduced by~\citet{liu-mar-li-vee-low2017}, and
+then investigated further by~\citet{soh-tse-li-voi-low2010}, the
+membrane forces depend on the Helfrich energy, line tension, and phase
+energy. The phase and bending energies are coupled through the bending
+modulus. In particular, the individual energies are
 \begin{align}
@@
 lipid-dependent bending modulus, $\sigma$ is the vesicle's tension, and
-$f(u) = \frac{1}{4}u^2(1-u)^2$ is the double-well potential with local
-minimums at $u=0$ and $u=1$. Here, $\kappa$ is the membrane curvature,
-$\ss$ is the tangent vector, and $s$ is the arclength. We have adopted
-the same setup as~\citet{soh-tse-li-voi-low2010} where $\epsilon \ll 1$
-is a dimensionless parameter that controls the size of the transition
-region of $u$, and $a$ is the dimensional line tension scaled by
-$b_{\max}/L$. Both $\epsilon$ and $a$ are kept constant in all
-simulations. The resulting membrane forces are
+$f(u) = \frac{1}{4}u^2(1-u)^2$ is a double-well potential with local
+minimums at $u=0$ and $u=1$. Here, $\kappa$ is the membrane curvature
+and $\ss$ is the tangent vector. We adopt the same setup
+as~\citet{soh-tse-li-voi-low2010} where $\epsilon \ll 1$ is a
+dimensionless parameter that controls the size of the transition region
+of $u$, and $a$ is the dimensional line tension scaled by $b_{\max}/L$.
+Both $\epsilon$ and $a$ are kept constant in all simulations. The
+resulting membrane forces are
 \begin{align}
@@
 
-\begin{figure}[H]
-  \centering
-%  \input{figures/concModels.tikz} \\
-  \subfigimg[width=0.9\linewidth, clip ]{(a)}{figures/concModels.pdf}
-  \\
-  \subfigimg[width=0.9\linewidth, clip ]{(b)}{figures/oldbending.pdf}
-  \caption{\label{fig:concModels} \small (a) The linear bending model in
-  red (equation~\eqref{eqn:linearBending}) and the new hyperbolic
-  bending model in blue (equation~\eqref{eqn:tanhBending}). Note that
-  the new bending model satisfies $b \in (\beta,1)$ even if $u \notin
-  [0,1]$. (b) A multicomponent vesicle entering a closely-fitting
-  channel using the linear model~\eqref{eqn:linearBending}. The vesicle
-  bending modulus becomes negative, and this introduces an instability
-  that first appears near the point with the largest negative curvature.
-  }
-\end{figure}
-
-The lipid species $u$ is governed by a fourth-order Cahn-Hilliard equation that results in the lipids phase separating while conserving their total mass.
-To model the variable bending, \citet{soh-tse-li-voi-low2010} propose parameterizing the bending modulus as
-\begin{align}
+The lipid species $u$ is governed by a fourth-order Cahn-Hilliard
+equation that results in the lipids phase separating while conserving
+their total mass. To model the variable bending,
+\citet{soh-tse-li-voi-low2010} parameterized the bending modulus as
+\begin{align}
+  \label{eqn:linearBending}
   b(u) = (1-u) + \beta u.
-    \label{eqn:linearBending}
 \end{align}
@@
 $\beta \ll 1$, $Ca \gg 1$, or the vesicle is confined to a narrow
-region.  Therefore, in this work we parameterize the bending modulus as
-\begin{align}
-    b(u) = \frac{\beta-1}{2} \tanh\left(3\left(u-\frac{1}{2} \right)\right) + 
-           \frac{\beta + 1}{2}.
+region. This behavior is demonstrated in Figure~\ref{fig:concModels}(a).
+The stiff-to-floppy ratio is $\beta = 10^{-1}$. Using the linear bending
+model~\eqref{eqn:linearBending}, the lipid concentration achieves a
+maximum value of $u \approx 1.52$ which results in an instability that
+is formed by a corresponding unphysical negative bending stiffness of
+$b(u) \approx -0.5$. To rectify this issue, we parameterize the bending
+modulus as
+\begin{align}
+  b(u) = \frac{\beta-1}{2} \tanh\left(3\left(u-\frac{1}{2} 
+    \right)\right) + \frac{\beta + 1}{2}.
   \label{eqn:tanhBending}
 \end{align}
-This maps the local minimums of the
-double-well potential close to $\beta$ and $1$, but more
-importantly, b(u) remains bounded in $(\beta,1)$ even when $u
-\notin [0,1]$ (Figure~\ref{fig:concModels}(a)). To demonstrate the
-necessity of this new bending model, we consider a multicomponent
-vesicle in strong confinement with both bending
-models~\eqref{eqn:linearBending} and~\eqref{eqn:tanhBending}. The
-stiff-to-floppy ratio is $\beta = 10^{-1}$. In the new
-model~\eqref{eqn:tanhBending}, the lipid concentration achieves a
-maximum value of $u \approx 1.002$ which results in a  minimum bending
-stiffness of $b(u) \approx \beta$. However, if we use the linear bending
-model~\eqref{eqn:linearBending}, the lipid concentration achieves a
-maximum value of $u \approx 1.52$ which results in an unphysical
-negative bending stiffness of $b(u) \approx -0.5$. The corresponding
-vesicle shape is in Figure~\ref{fig:concModels}(b), and the instability
-caused by the negative bending stiffness is near the region with
-negative curvature.
+This parameterization maps the local minimums of the double-well
+potential close to $\beta$ and $1$, but more importantly, b(u) remains
+bounded in $(\beta,1)$ even when $u \notin [0,1]$
+(Figure~\ref{fig:concModels}(b)). This new bending model is validated in
+Section~\ref{sec:validation}.
+%To demonstrate the necessity of this new bending model, we consider a
+%multicomponent vesicle in strong confinement with both bending
+%models~\eqref{eqn:linearBending} and~\eqref{eqn:tanhBending}. The
+%stiff-to-floppy ratio is $\beta = 10^{-1}$. In the new
+%model~\eqref{eqn:tanhBending}, the lipid concentration achieves a
+%maximum value of $u \approx 1.002$ which results in a minimum bending
+%stiffness of $b(u) \approx \beta$. However, if we use the linear
+%bending model~\eqref{eqn:linearBending}, the lipid concentration
+%achieves a maximum value of $u \approx 1.52$ which results in an
+%unphysical negative bending stiffness of $b(u) \approx -0.5$. The
+%corresponding vesicle shape is in Figure~\ref{fig:concModels}(b), and
+%the instability caused by the negative bending stiffness is near the
+%region with negative curvature.
+
+\begin{figure}[H]
+  \centering
+%  \input{figures/concModels.tikz} \\
+  \subfigimg[width=0.9\linewidth, clip ]{(a)}{figures/oldbending.pdf} \\
+  \subfigimg[width=0.9\linewidth, clip ]{(b)}{figures/concModels.pdf}
+  \caption{\label{fig:concModels} \small (a) A multicomponent vesicle
+  entering a closely-fitting channel using the linear
+  model~\eqref{eqn:linearBending}. The vesicle bending modulus becomes
+  negative, and this introduces an instability that first appears near
+  the point with the largest negative curvature. (b) The linear bending
+  model in red (equation~\eqref{eqn:linearBending}) and the new
+  hyperbolic bending model in blue (equation~\eqref{eqn:tanhBending}).
+  Note that the new bending model satisfies $b \in (\beta,1)$ even if $u
+  \notin [0,1]$.}
+\end{figure}
+
 %\begin{figure}[htp]
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{\label{sec:NumericalMethods}Numerical Methods}
-The velocity field $\uu$ is written as a combination of a single-layer potential and a double-layer potential
+We use a high-order integral equation formulation to resolve the complex
+vesicle shapes. The velocity field $\uu$ is written as a combination of
+a single-layer potential and a double-layer potential
 \begin{align}
@@
 \begin{align}
-    S[\ff](\xx) &= \frac{1}{4\pi\mu} \int_{\gamma} \left(-\log \rho \mathds{I} + \frac{\rr \otimes \rr}{\rho^2} \right)
+  S[\ff](\xx) &= \frac{1}{4\pi\mu} \int_{\gamma} \left(
+    -\log \rho \mathds{I} + \frac{\rr \otimes \rr}{\rho^2} \right)
     \ff(\yy) \, ds_\yy, \\
 %
-    D[\eeta](\xx) &= \frac{1}{\pi} \int_{\Gamma} \frac{\rr \cdot \nn}{\rho^2}
+    D[\eeta](\xx) &= \frac{1}{\pi} \int_{\Gamma} 
+      \frac{\rr \cdot \nn}{\rho^2} 
       \frac{\rr \otimes \rr}{\rho^2} \eeta(\yy) \, ds_\yy,
 \end{align}
-$\rr = \xx - \yy$, $\rho = |\rr|$, and $\mathds{I}$ is the $2 \times 2$ identity matrix.
-To avoid tangling of the vesicle membrane, it is parameterized in terms of the $\theta$-$L$ variables~\cite{hou-low-she1994}, where $L$ is the fixed vesicle length and $\theta$ is the opening angle of the tangent vector $\ss$.
-This requires decomposing the velocity field on $\gamma$ into its normal direction $V$ and tangential direction $T$.
-Then, the no-slip boundary condition for the vesicle velocity is
+and $\rr = \xx - \yy$, $\rho = |\rr|$, and $\mathds{I}$ is the $2 \times
+2$ identity matrix. To avoid tangling of the vesicle membrane, it is
+parameterized in terms of the $\theta$-$L$
+variables~\cite{hou-low-she1994}, where $L$ is the fixed vesicle length
+and $\theta$ is the opening angle of the tangent vector $\ss$. This
+requires decomposing the velocity field on $\gamma$ into a normal
+velocity $V$ and tangential velocity $T$. Then, the no-slip boundary
+condition for the vesicle velocity is
 \begin{align}
@@
 \end{align}
-The boundary condition on $\Gamma$ is imposed by requiring that $\eeta$ satisfies
-\begin{align}
-    \UU(\xx) = -\frac{1}{2}\eeta(\xx) + S[\ff](\xx) + D[\eeta](\xx), \quad \xx \in \Gamma.
+The boundary condition on $\Gamma$ is imposed by requiring that $\eeta$
+satisfies
+\begin{align}
+  \UU(\xx) = -\frac{1}{2}\eeta(\xx) + 
+    S[\ff](\xx) + D[\eeta](\xx), \quad \xx \in \Gamma.
   \label{eqn:DLP_BIE}
 \end{align}
-After discretizing the geometry at collocation points, the single-layer potential is approximated with quadrature for weakly-singular integrands, and the double-layer potential is approximated with the spectrally accurate trapezoid rule.
-All arclength derivatives are computed with spectral accuracy using Fourier methods.
-Time stepping is performed with second-order Adams-Bashforth.
-The resulting linear system is solved with GMRES.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The vesicle and solid walls are discretized at a set of collocation
+points. The single-layer potential is then approximated using quadrature
+for weakly-singular integrands, while the double-layer potential is
+approximated using the spectrally accurate trapezoid rule. Arclength
+derivatives are computed with spectral accuracy using Fourier methods.
+Time stepping is carried out using the second-order Adams-Bashforth
+method. Finally, the resulting linear system is solved using GMRES.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Validation}
-Since we use a new bending model, we first validate that it reproduces
+\label{sec:validation}
+We validate the new bending model~\eqref{eqn:tanhBending} by reproducing
 the tank treading and phase treading dynamics reported in the
@@
 \begin{figure}[H]
+  \todo[inline]{Change to new color scheme.}
   \centering
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{\label{sec:results}Hydrodynamics of a multicomponent vesicle under strong confinement}
 
-The lubrication layer between a vesicle and the solid wall plays a critical role on the vesicle's dynamics.
-Therefore, we report the size of the lubrication layers both above and below the vesicle in Section~\ref{sec:results}.
-We first justify the use of the term `lubrication layer' by verifying that the flow velocity is parabolic between the vesicle and the solid wall.
-Figure~\ref{fig:quadraticProof} illustrates the horizontal velocity (solid line) and the corresponding best fit quadratic (dashed line) in the co-moving frame, and the profiles agree.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\columnwidth]{figures/lubricationLayer_quadratic.pdf}  
-    \caption{The co-moving velocity profile in the top and bottom lubrication layers. The red curve is the velocity profile, the dashed black line is the best quadratic fit.}
-    \label{fig:quadraticProof}
-\end{figure}
-
+The lubrication layer between a vesicle and the solid wall plays a
+critical role on the vesicle's dynamics. Therefore, throughout
+Section~\ref{sec:results}, we will calculate the size and analyze the
+flow structure inside the lubrication layers. 
+%We first justify the use of the term `lubrication layer' by verifying
+%that the flow velocity is parabolic between the vesicle and the solid
+%wall. Figure~\ref{fig:quadraticProof} illustrates the horizontal
+%velocity (solid line) and the corresponding best fit quadratic (dashed
+%line) in the co-moving frame, and the profiles agree.
+%
+%\begin{figure}[H]
+%    \centering
+%    \includegraphics[width=\columnwidth]{figures/lubricationLayer_quadratic.pdf}  
+%    \caption{The co-moving velocity profile in the top and bottom lubrication layers. The red curve is the velocity profile, the dashed black line is the best quadratic fit.}
+%    \label{fig:quadraticProof}
+%\end{figure}
 To define the size of the top lubrication layer (the size of the bottom

### 2023-06-20 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on figs
revised Fig 3

@@
 %  \input{figures/concModels.tikz} \\
-  \subfigimg[width=0.9\linewidth, clip ]{(a)}{figures/oldbending.pdf} \\
+%  \subfigimg[width=0.9\linewidth, clip ]{(a)}{figures/oldbending.pdf} \\
+  \subfigimg[width=0.9\linewidth, clip ]{(a)}{figures/OldBending.pdf} \\
   \subfigimg[width=0.9\linewidth, clip ]{(b)}{figures/concModels.pdf}
@@
   \centering
-  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(a)}{figures/Fig4a.pdf}
-  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(b)}{figures/Fig4b.pdf}
-  \caption{\label{fig:treading} \small A multicomponent (a)
-  tank-treading and (b) phase-treading vesicle using the new bending
-  model~\eqref{eqn:tanhBending}. These simulations agree with the
-  results presented by~\citet{liu-mar-li-vee-low2017}.}
+  \includegraphics[width=0.9\columnwidth]{figures/shearTreading.pdf}
+%  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(a)}{figures/Fig4a.pdf}
+%  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(b)}{figures/Fig4b.pdf}
+  \caption{\label{fig:treading} \small A multicomponent vesicle in a
+  linear shear flow undergoes phase-treading (top) and tank-treading
+  (bottom) with the new bending model~\eqref{eqn:tanhBending}. The red
+  region is stiff and the blue region is floppy. The simulations
+  qualitatively agree with the results presented
+  by~\citet{liu-mar-li-vee-low2017}.}
 \end{figure}
@@
 \end{align}
-The width of the bottom lubrication layer, $w_\mathrm{bot}$ is calculated replacing $\Gamma_\mathrm{top}$ with $\Gamma_\mathrm{bot}$.
+The width of the bottom lubrication layer, $w_\mathrm{bot}$ is
+calculated by replacing $\Gamma_\mathrm{top}$ with
+$\Gamma_\mathrm{bot}$.
 
@@
 
-The difference between the size of the top and lubrication layers is closely related to the tank treading behavior of the vesicle.
-In cases where the vesicle tank treads, we define the tank-treading velocity, $\uu \cdot \ss$.
-To establish that a vesicle is tank treading, we compute this tangential velocity at several Lagrangian points on $\gamma$, and make sure that these values agree.
+The difference between the size of the top and lubrication layers is
+closely related to the tank treading behavior of the vesicle. In cases
+where the vesicle tank treads, we define the tank-treading velocity,
+$\uu \cdot \ss$. To establish that a vesicle is tank treading, we verify
+that the tangential velocity agrees at several points on $\gamma$.
 
@@
 
-We also report the excess pressure for one of the geometries and relate it to the size of the lubrication layers.
-Since we represent the velocity with layer potentials~\eqref{eqn:LPrep}, the pressure at $\xx \in \Omega$ is
-\begin{align}
-    p(\xx) = \frac{1}{2\pi} \int_{\gamma} \frac{\rr \cdot \ff}{\rho^2} \, ds_\yy + \frac{1}{\pi} \int_{\Gamma} \frac{1}{\rho^2} \left(\mathds{I} - 2\frac{\rr \otimes \rr}{\rho^2} \right) \nn \cdot \eeta \, ds_\yy.
-\end{align}
-The excess pressure is the additional pressure that is required to pass the vesicle through the geometry when compared to the pressure necessary if the vesicle were absent.
-These pressure drops are defined by subtracting the pressure at a point near the inlet and another near the outlet.
-In our formulation, because of the order of subtraction, the excess pressure is always negative.
+We also report the excess pressure for one of the geometries and relate
+it to the size of the lubrication layers. Since we represent the
+velocity with layer potentials~\eqref{eqn:LPrep}, the pressure at $\xx
+\in \Omega$ is
+\begin{align}
+  p(\xx) = \frac{1}{2\pi} \int_{\gamma} \frac{\rr \cdot \ff}{\rho^2} \, ds_\yy + 
+    \frac{1}{\pi} \int_{\Gamma} \frac{1}{\rho^2} 
+    \left(\mathds{I} - 2\frac{\rr \otimes \rr}{\rho^2} \right) 
+    \nn \cdot \eeta \, ds_\yy.
+\end{align}
+The excess pressure is the additional pressure that is required to pass
+the vesicle through the geometry when compared to the pressure necessary
+if the vesicle were absent. These pressure drops are defined by
+subtracting the pressure at a point near the inlet and another near the
+outlet. In our formulation, because of the order of subtraction, the
+excess pressure is always negative.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We consider both a single-component and a multicomponent vesicle suspended in two geometries: a closely-fitting geometry (stenosis) and a geometry that slowly contracts to a narrow neck and then quickly widens (contracting).
-We considered a semipermeable vesicle suspended in these same geometries~\cite{qua-gan-you2021}.
-All the multicomponent examples have the bending ratio $b_{\min}/b_{\max} = 10^{-1}$.
-For the single-component case, we consider two dimensionless bending stiffness: $b(u) = b_{\max} = 1$ and $b(u) = \frac{1}{2}(b_{\max} + b_{\min}) = 0.55$.
-Throughout this section we plot the position of the vesicle in terms of the $x$-coordinate of its center of mass.
-For the stenosed geometry in Section~\ref{subsec:Stenosis}, the narrow region begins at $x=-15$ and ends at $x=15$.
-For the contracting geometry in Section~\ref{subsec:Contraction}, the geometry begins to narrow at $x=4$ and reaches its narrowest point at $x=15$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We consider both a single-component and a multicomponent vesicle
+suspended in two geometries: a closely-fitting geometry (stenosis) and a
+geometry that slowly contracts to a narrow neck and then quickly widens
+(contracting). We considered a semipermeable vesicle suspended in these
+same geometries~\cite{qua-gan-you2021}. All the multicomponent examples
+have the bending ratio $b_{\min}/b_{\max} = 10^{-1}$. For the
+single-component case, we consider two dimensionless bending stiffness:
+$b(u) = b_{\max} = 1$ and $b(u) = \frac{1}{2}(b_{\max} + b_{\min}) =
+0.55$. Throughout this section we plot the position of the vesicle in
+terms of the $x$-coordinate of its center of mass. For the stenosed
+geometry in Section~\ref{subsec:Stenosis}, the narrow region begins at
+$x=-15$ and ends at $x=15$. For the contracting geometry in
+Section~\ref{subsec:Contraction}, the geometry begins to narrow at $x=4$
+and reaches its narrowest point at $x=15$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{\label{subsec:Stenosis}A multicomponent vesicle in a closely-fit channel (Stenosis)}

### 2023-06-20 vesicle_code/docs/confinedMulti/makefigs/AshleyFiles/MakeSnaps.m

@@ -38,7 +38,6 @@ ywalls = [ywalls(:);ywalls(1:4)];
 N = length(posx1(:,:,1));
 oc = curve(N);
 
-axes(ha(sp));
 %subplot(3,1,sp);
 %figure(1); clf
 plot(xwalls,ywalls, 'k', 'linewidth', 2)

### 2023-06-21 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
worked on BL figures
fixed fig 1
working on paper

@@
   \llbracket \uu \rrbracket = 0, \quad 
-  \nabla_{\gamma} \cdot \uu = 0, \quad \xx \in \gamma, \quad
-  \llbracket \TT\nn \rrbracket = \ff, 
+  \nabla_{\gamma} \cdot \uu = 0, \quad
+  \llbracket \TT\nn \rrbracket = \ff, \quad \xx \in \gamma,
 \end{align}
 where $\ff$ is the total membrane force and $\nn$ is the outward unit
-normal of $\gamma$. By parameterizing $\gamma$ as $\xx(s,t)$, where $s$
-is arclength and $t$ is time, the no-slip boundary condition is
-$\frac{d\xx}{dt} = \uu(\xx)$.  Along the solid wall $\Gamma$, we impose
-a Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a
+normal of $\gamma$. Parameterizing $\gamma$ as $\xx(s,t)$, where $s$ is
+arclength and $t$ is time, the no-slip boundary condition is
+$\frac{d\xx}{dt} = \uu(\xx)$. Along the solid wall $\Gamma$, we impose a
+Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a
 Hagen–Poiseuille flow at the inlet and outlet (where $y\in[-W,W]$),
@@
 \subsection{Constitutive equations}
-Using the model first introduced by~\citet{liu-mar-li-vee-low2017}, and
-then investigated further by~\citet{soh-tse-li-voi-low2010}, the
+Using the model first introduced by~\citet{liu-mar-li-vee-low2017}, the
 membrane forces depend on the Helfrich energy, line tension, and phase
@@
 where $u$ is the dimensionless lipid concentration, $b(u)$ is the
-lipid-dependent bending modulus, $\sigma$ is the vesicle's tension, and
-$f(u) = \frac{1}{4}u^2(1-u)^2$ is a double-well potential with local
-minimums at $u=0$ and $u=1$. Here, $\kappa$ is the membrane curvature
-and $\ss$ is the tangent vector. We adopt the same setup
-as~\citet{soh-tse-li-voi-low2010} where $\epsilon \ll 1$ is a
-dimensionless parameter that controls the size of the transition region
-of $u$, and $a$ is the dimensional line tension scaled by $b_{\max}/L$.
-Both $\epsilon$ and $a$ are kept constant in all simulations. The
-resulting membrane forces are
+lipid-dependent bending modulus, $\sigma$ is the vesicle's tension,
+$\kappa$ is the membrane curvature, and $f(u) = \frac{1}{4}u^2(1-u)^2$
+is a double-well potential with local minimums at $u=0$ and $u=1$. The
+parameter $\epsilon \ll 1$ sets the size of the transition region of
+$u$, and the parameter $a$ is line tension scaled by the characteristic
+bending stiffness. Both $\epsilon$ and $a$ are kept constant in all
+simulations. The resulting membrane forces are
 \begin{align}
@@
   \ff_p &= \left(\frac{a}{\epsilon}\left(f(u) -
-     \frac{\epsilon^2}{2} u_s^2\right) \ss \right)_s.
-\end{align}
+     \frac{\epsilon^2}{2} u_s^2\right) \ss \right)_s,
+\end{align}
+where $\ss$ is the unit tangent vector of $\gamma$.
 
@@
 $\beta \ll 1$, $Ca \gg 1$, or the vesicle is confined to a narrow
-region. This behavior is demonstrated in Figure~\ref{fig:concModels}(a).
-The stiff-to-floppy ratio is $\beta = 10^{-1}$. Using the linear bending
-model~\eqref{eqn:linearBending}, the lipid concentration achieves a
-maximum value of $u \approx 1.52$ which results in an instability that
-is formed by a corresponding unphysical negative bending stiffness of
-$b(u) \approx -0.5$. To rectify this issue, we parameterize the bending
-modulus as
+region. This behavior is demonstrated in Figure~\ref{fig:concModels}(a)
+for a vesicle with a floppy-to-stiff ratio $\beta = 10^{-1}$. Using the
+linear bending model~\eqref{eqn:linearBending}, the lipid concentration
+achieves a maximum value of $u \approx 1.5$ which results in an
+instability that is formed by a corresponding unphysical negative
+bending stiffness of $b(u) \approx -0.5$. To rectify this issue, we
+parameterize the bending modulus as
 \begin{align}
@@
   \caption{\label{fig:concModels} \small (a) A multicomponent vesicle
-  entering a closely-fitting channel using the linear
-  model~\eqref{eqn:linearBending}. The vesicle bending modulus becomes
-  negative, and this introduces an instability that first appears near
-  the point with the largest negative curvature. (b) The linear bending
+  entering a closely-fitting channel (black lines) using the linear
+  model~\eqref{eqn:linearBending}. An instability is introduced where
+  the vesicle bending modulus becomes negative. (b) The linear bending
   model in red (equation~\eqref{eqn:linearBending}) and the new
@@
 We use a high-order integral equation formulation to resolve the complex
-vesicle shapes. The velocity field $\uu$ is written as a combination of
-a single-layer potential and a double-layer potential
+vesicle shapes and long-range hydrodynamic interactions. The velocity
+field $\uu$ is written as a combination of a single-layer potential and
+a double-layer potential
 \begin{align}
@@
 derivatives are computed with spectral accuracy using Fourier methods.
-Time stepping is carried out using the second-order Adams-Bashforth
-method. Finally, the resulting linear system is solved using GMRES.
+The resulting linear system is solved using GMRES. Finally, time
+stepping is carried out using the second-order Adams-Bashforth method.
 
@@
 We validate the new bending model~\eqref{eqn:tanhBending} by reproducing
-the tank treading and phase treading dynamics reported in the
-literature. Figure~\ref{fig:treading} shows a tank treading (top) and a
-phase treading (bottom) multicomponent vesicle in an unconfined shear
-flow. These simulations align with the results reported
-by~\citet{liu-mar-li-vee-low2017} (cf.~Figures 3 and 4).
+the dynamics reported in the literature. Figure~\ref{fig:treading} shows
+a phase treading (top) ajnd a tank treading (bottom) multicomponent
+vesicle in an unconfined shear flow. These simulations align with the
+results reported by~\citet{liu-mar-li-vee-low2017} (cf.~Figures 3 and
+4).
 \begin{figure}[H]
-  \todo[inline]{Change to new color scheme.}
   \centering
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{\label{sec:results}Hydrodynamics of a multicomponent vesicle under strong confinement}
-
+\subsection{\label{sec:LL} Lubrication layers and excess pressure}
 The lubrication layer between a vesicle and the solid wall plays a
 critical role on the vesicle's dynamics. Therefore, throughout
-Section~\ref{sec:results}, we will calculate the size and analyze the
-flow structure inside the lubrication layers. 
+Section~\ref{sec:results}, we calculate the size and analyze the flow
+inside the lubrication layers. 
 %We first justify the use of the term `lubrication layer' by verifying
@@
 lubrication layer is defined similarly), we let
-$d(\xx,\Gamma_\mathrm{top})$ be the minimum distance between the vesicle
-and the top half of the confining geometry.
+$d(\xx,\Gamma_\mathrm{top})$ be the minimum distance between a point on
+the vesicle, $\xx \in \gamma$, and the top half of the confining
+geometry.
 %\begin{align}
@@
 We then find all local minimums of $d(\xx,\Gamma_\mathrm{top})$, with
-the condition that $d(\xx,\Gamma_\mathrm{top}) < \beta$, where $\beta$
+the condition that $d(\xx,\Gamma_\mathrm{top}) < \delta$, where $\delta$
 is a parameter. If no such local minimums exist, then the vesicle is too
@@
 condition that $d(\xx_L,\Gamma_\mathrm{top}) =
-d(\xx_R,\Gamma_\mathrm{top}) = \beta$. Then, the segment
+d(\xx_R,\Gamma_\mathrm{top}) = \delta$. Then, the segment
 $\gamma_{\mathrm{layer}} \subset \gamma$ consists of all points $\xx \in
 \gamma$ between $\xx_L$ and $\xx_R$ with the condition that
-$d(\xx,\Gamma_\mathrm{top}) < \beta$. Finally, the lubrication layer
+$d(\xx,\Gamma_\mathrm{top}) < \delta$. Finally, the lubrication layer
 width is
 \begin{align}
-    w_\mathrm{top} = \frac{1}{|\gamma_{_\mathrm{layer}}|} \int_{\gamma_{_\mathrm{layer}}} d(\xx,\Gamma_\mathrm{top}) \, ds.
-\end{align}
-The width of the bottom lubrication layer, $w_\mathrm{bot}$ is
-calculated by replacing $\Gamma_\mathrm{top}$ with
-$\Gamma_\mathrm{bot}$.
-
-%The terminology of boundary layer can be justified by computing the velocity field in the region between the vesicle and the solid wall.
-In Figure~\ref{fig:BkgrdFlow}, the co-moving velocity field around several different vesicle shapes that are observed in Section~\ref{sec:results} are illustrated.
-We have included plots of the horizontal velocity along a few vertical slices to demonstrate that a parabolic flow profile is observed.
-
-The difference between the size of the top and lubrication layers is
-closely related to the tank treading behavior of the vesicle. In cases
-where the vesicle tank treads, we define the tank-treading velocity,
-$\uu \cdot \ss$. To establish that a vesicle is tank treading, we verify
-that the tangential velocity agrees at several points on $\gamma$.
+    w_\mathrm{top} = \frac{1}{|\gamma_{_\mathrm{layer}}|} 
+      \int_{\gamma_{_\mathrm{layer}}} d(\xx,\Gamma_\mathrm{top}) \, ds.
+\end{align}
+%The width of the bottom lubrication layer, $w_\mathrm{bot}$ is
+%calculated by replacing $\Gamma_\mathrm{top}$ with
+%$\Gamma_\mathrm{bot}$.
+
+%The terminology of boundary layer can be justified by computing the
+%velocity field in the region between the vesicle and the solid wall. In
+%Figure~\ref{fig:BkgrdFlow}, the co-moving velocity field around several
+%different vesicle shapes that are observed in Section~\ref{sec:results}
+%are illustrated. We have included plots of the horizontal velocity
+%along a few vertical slices to demonstrate that a parabolic flow
+%profile is observed.
+
+A difference between the size of the top and lubrication layers
+indicates that the vesicle is off-centered from the center of the
+channel, and this results in tank-treading behavior~\cite{aga-bir2020}.
+To determine if a vesicle is tank-treading, we calculate the tangential
+velocity at several points on $\gamma$, and if this value is constant,
+this is the tank-treading velocity.
 
@@
 We also report the excess pressure for one of the geometries and relate
-it to the size of the lubrication layers. Since we represent the
-velocity with layer potentials~\eqref{eqn:LPrep}, the pressure at $\xx
-\in \Omega$ is
+it to the size of the lubrication layers. The excess pressure is the
+additional pressure that is required to pass the vesicle through the
+geometry when compared to the pressure necessary if the vesicle were
+absent. These pressure calculations are taken near the inlets and
+outlets of the confining geometry, and the vesicle itself is never near
+these locations. Since we use a layer potential formulation, the
+pressure at $\xx \in \Omega$ is
 \begin{align}
@@
 \end{align}
-The excess pressure is the additional pressure that is required to pass
-the vesicle through the geometry when compared to the pressure necessary
-if the vesicle were absent. These pressure drops are defined by
-subtracting the pressure at a point near the inlet and another near the
-outlet. In our formulation, because of the order of subtraction, the
-excess pressure is always negative.
+%These pressure drops are defined by
+%subtracting the pressure at a point near the inlet and another near the
+%outlet. In our formulation, because of the order of subtraction, the
+%excess pressure is always negative.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{\label{sec:results}Hydrodynamics of a multicomponent vesicle
+under strong confinement}
 We consider both a single-component and a multicomponent vesicle
@@
 same geometries~\cite{qua-gan-you2021}. All the multicomponent examples
-have the bending ratio $b_{\min}/b_{\max} = 10^{-1}$. For the
-single-component case, we consider two dimensionless bending stiffness:
-$b(u) = b_{\max} = 1$ and $b(u) = \frac{1}{2}(b_{\max} + b_{\min}) =
-0.55$. Throughout this section we plot the position of the vesicle in
-terms of the $x$-coordinate of its center of mass. For the stenosed
-geometry in Section~\ref{subsec:Stenosis}, the narrow region begins at
-$x=-15$ and ends at $x=15$. For the contracting geometry in
+have floppy-to-stiff ratio $\beta = 10^{-1}$. For the single-component
+case, we consider two bending stiffnesses: $b(u) = 1$ and $b(u) = 0.55$
+which is the average bending stiffness of a multicomponent vesicle whose
+stiff and floppy regions have the same area. Throughout this section we
+plot the position of the vesicle in terms of the $x$-coordinate of its
+center of mass. For the stenosed geometry in
+Section~\ref{subsec:Stenosis}, the narrow region begins at $x=-15$ and
+ends at $x=15$. For the contracting geometry in
 Section~\ref{subsec:Contraction}, the geometry begins to narrow at $x=4$
 and reaches its narrowest point at $x=15$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{figure}
-%  \begin{minipage}{0.99\columnwidth}
     \centering
@@
     \subfigimg[width=\columnwidth]{(b)}{figures/SC_bot.pdf}
-    \subfigimg[width=\columnwidth]{(a)}{figures/SCp55_top.pdf}
-    \subfigimg[width=\columnwidth]{(b)}{figures/SCp55_bot.pdf}
-    \subfigimg[width=\columnwidth]{(a)}{figures/MCp5_top.pdf}
-    \subfigimg[width=\columnwidth]{(b)}{figures/MCp5_bot.pdf}
-%  \end{minipage}
-%  \hfill
-%  \begin{minipage}{0.49\columnwidth}
-%    \centering
-%    \subfigimg[width=\textwidth]{(b)}{figures/Fig13b.pdf}
-%    \subfigimg[width=\textwidth]{(d)}{figures/Fig13d.pdf}
-%    \subfigimg[width=\textwidth]{(f)}{figures/Fig13f.pdf}
-%  \end{minipage}
-%  \caption{\label{fig:Energy} \small The Bending (blue), tension
-%  (yellow), and phase (red) energies for a (a/b) single-component
-%  vesicle with $b=1$, (c/d) single-component vesicle with $b = 0.55$,
-%  and (e/f) multicomponent vesicle. The reduced areas are $\alpha = 0.4$
-%  (a/c/e) and $\alpha = 0.6$ (b/d/f).}
+    \subfigimg[width=\columnwidth]{(c)}{figures/SCp55_top.pdf}
+    \subfigimg[width=\columnwidth]{(d)}{figures/SCp55_bot.pdf}
+    \subfigimg[width=\columnwidth]{(e)}{figures/MCp5_top.pdf}
+    \subfigimg[width=\columnwidth]{(f)}{figures/MCp5_bot.pdf}
+    \caption{\label{fig:BLvelocities} A descriptive caption.}
 \end{figure}

### 2023-06-22 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
worked on Fig 12

@@
 \section{\label{sec:Introduction}Introduction}
-Soft particles, such as vesicles, display rich dynamics when they are subjected to different types of physical processes.
-These dynamics are affected by parameters such a the capillary number, reduced volume, and confinement ratio.
-Understanding these dynamics is critical to understanding biophysical and microfluidic processes.
-For example, a vesicle's reduced area and viscosity contrast will determine if it undergoes tank treading, swinging, or tumbling in a shear flow~\cite{nog-gom2005}.
-Transitions in the vesicle shape occur in non-linear parabolic flows~\cite{kao-bir-mis2009, dan-vla-mis2009}, and these shapes include axisymmetric bullets or parachutes, and asymmetric parachutes.
-More recently, groups have considered these transitions when vesicles are suspended in a channel or pipe flow~\cite{lyu-che-far-jae-mis-leo2023, aga-bir2020, qua-gan-you2021, abb-far-nai-ezz-ben-mis2022}.
-These dynamics include snaking and swirling behaviors; croissant and slipper shapes; and semipermeability.
-
-Groups have also studied the behaviors of a vesicle that is composed of different types of lipids and proteins.
-The presence of different lipid species has been used to model different processes including the bending stiffness, spontaneous curvature, and adhesion potential~\cite{zha-das-du2010, tan-yan-ima2011}.
-The dynamics of these multicomponent vesicles include phase treading, tumbling with no viscosity contrast, swinging, budding, and fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006, ger-sal-spa2022, lip1992, urs-klu-phi2009}.
-In addition to the aforementioned numerical studies, these dynamics have been observed in experiments~\cite{bag-sun2009, yan-ima-tan2010, yan-ima-tan2008, dre-jah-bob-spa-gop2021}.
-
-In this paper, we extend the work of Liu et al.~\cite{liu-mar-li-vee-low2017} who performed a thorough investigation of how key dimensionless numbers, including the reduced area, capillary number, and the floppy-to-stiff ratio, affect the dynamics of a multicomponent vesicle in an unbounded linear shear flow.
-What is missing from the literature, and what we address in this work, is the effect of strong confinement on a two-dimensional multicomponent vesicle.
-Using numerical simulations, we show how the vesicle's reduced area and its lipid composition affect the dynamics in two strongly confined geometries.
+Soft particles, such as vesicles, display rich dynamics when they are
+subjected to different types of physical processes. These dynamics are
+affected by parameters such as the capillary number, reduced volume, and
+confinement ratio. Understanding these dynamics is critical to
+understanding biophysical and microfluidic processes. For example, a
+vesicle's reduced area and viscosity contrast will determine if it
+undergoes tank treading, swinging, or tumbling in a shear
+flow~\cite{nog-gom2005}. Transitions in the vesicle shape occur in
+non-linear parabolic flows~\cite{kao-bir-mis2009, dan-vla-mis2009}, and
+these shapes include axisymmetric bullets or parachutes, and asymmetric
+parachutes. More recently, groups have considered these transitions when
+vesicles are suspended in a channel or pipe
+flow~\cite{lyu-che-far-jae-mis-leo2023, aga-bir2020, qua-gan-you2021,
+abb-far-nai-ezz-ben-mis2022}. These dynamics include snaking and
+swirling behaviors; croissant and slipper shapes; and semipermeability.
+
+Groups have also studied the behaviors of a vesicle that is composed of
+different types of lipids and proteins. The presence of different lipid
+species has been used to model different processes including the bending
+stiffness, spontaneous curvature, and adhesion
+potential~\cite{zha-das-du2010, tan-yan-ima2011}. The dynamics of these
+multicomponent vesicles include phase treading, tumbling with no
+viscosity contrast, swinging, budding, and
+fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006,
+ger-sal-spa2022, lip1992, urs-klu-phi2009}. In addition to the
+aforementioned numerical studies, these dynamics have been observed in
+experiments~\cite{bag-sun2009, yan-ima-tan2010, yan-ima-tan2008,
+dre-jah-bob-spa-gop2021}.
+
+In this paper, we extend the work of Liu et
+al.~\cite{liu-mar-li-vee-low2017} who performed a thorough investigation
+of how key dimensionless numbers, including the reduced area, capillary
+number, and the floppy-to-stiff ratio, affect the dynamics of a
+multicomponent vesicle in an unbounded linear shear flow. What is
+missing from the literature, and what we address in this work, is the
+effect of strong confinement on a two-dimensional multicomponent
+vesicle. Using numerical simulations, we show how the vesicle's reduced
+area and its lipid composition affect the dynamics in two strongly
+confined geometries.
 
 The remainder of the paper is organized as follows.
-Section~\ref{sec:Formulation} describes the model for the two-dimensional multicomponent vesicle.
-We introduce a new parameterization of the bending modulus that is necessary to avoid unphysical negative bending stiffness.
-Section~\ref{sec:NumericalMethods} describes numerical methods and also defines the techniques we use to define the excess pressure, lubrication layer width, and tank treading velocity.
-Section~\ref{sec:results} demonstrates the effects of strong confinement on multicomponent vesicles.
-Finally, concluding remarks are made in Section~\ref{sec:conclusion}.
+Section~\ref{sec:Formulation} describes the model for the
+two-dimensional multicomponent vesicle. We introduce a new
+parameterization of the bending modulus that is necessary to avoid
+unphysical negative bending stiffness.
+Section~\ref{sec:NumericalMethods} describes numerical methods and also
+defines the techniques we use to define the excess pressure, lubrication
+layer width, and tank treading velocity. Section~\ref{sec:results}
+demonstrates the effects of strong confinement on multicomponent
+vesicles. Finally, concluding remarks are made in
+Section~\ref{sec:conclusion}.
 
@@
 floppy-to-stiffness ratio $\beta = b_{\min}/b_{\max}$. Since we consider
-flows in channels, we also define a dimensionless maximum imposed
-velocity, $U$, which sets a capillary number, and $W$ is the
-dimensionless width of the channel at the inlet and outlet. From this
-point onwards, all equations are dimenisionless.
-
-\todo[inline]{Need to define capillary number and diffusion time scale.}
+flows in channels, we also define a maximum imposed velocity, $U$, which
+sets the capillary number $Ca = U R_{0}^{2} \mu/b_{\max}$, and $W/R_0$
+is the dimensionless width of the channel at the inlet and outlet. From
+this point onwards, all equations are dimenisionless.
 
@@
 
-Using the definition of the lubrcication layer outlined in Section ???,
-fit the horizontal flow profile to a quadratic function and plot the
-coefficients of the Poisseuille and linear shear in Figure~\ref{}. We
-only consider cases where the vesicle has reached a steady shape is only
-under going tank treading. We observe that the Poisseuille coefficient
-can be either positive or negative, meaning that the pressure in the
-lubcrication layer switches signs. This behavior is caused when the
-tangential force on the vesicle
+Using the definition of the lubrcication layer outlined in
+Section~\ref{sec:LL} fit the horizontal flow profile to a quadratic
+function and plot the coefficients of the Poisseuille and linear shear
+in Figure~\ref{}. We only consider cases where the vesicle has reached a
+steady shape is only under going tank treading. We observe that the
+Poisseuille coefficient can be either positive or negative, meaning that
+the pressure in the lubcrication layer switches signs. This behavior is
+caused when the tangential force on the vesicle
 \begin{align}
@@
   \centering
-    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(a)}{figures/rightSep.pdf}
-    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(b)}{figures/randSep.pdf}
-    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(c)}{figures/leftSep.pdf}
+%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(a)}{figures/rightSep.pdf}
+%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(b)}{figures/randSep.pdf}
+%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(c)}{figures/leftSep.pdf}
+  \includegraphics[width=\columnwidth]{figures/Contracting_RAp6MCp5.pdf}
   \caption{\label{fig:RA6leftRightRand} \small A multicomponent vesicle
   with 50\% floppy region passing through a contracting geometry. The
-  vesicle's reduced area is $\alpha = 0.6$ and the dimensionless maximum
-  velocity is $U = 0.25$. The vesicles are: (a) the initial
-  lipid-species distribution is fully separated on the right side of the
-  vesicle; (b) the initial lipid-species distribution is randomly
-  distributed (not fully separated) on the vesicle membrane; (d) the
-  initial lipid-species distribution is fully separated on the left side
-  of the vesicle. The vesicles with a larger percentage of floppy
-  regions pass through the neck earlier than the vesicles with less
-  percentage of floppy regions. The vesicle either completely or
-  partially reorients itself so that the floppy region is in the back
-  and the stiff region is in the front.}
+  vesicle's reduced area is $\alpha = 0.6$ and the capillary number is
+  $Ca = 0.25$. The lipid distribution is initialized to already be phase
+  separated in the top and bottom rows, and the middle row has a random
+  initial lipid distribution. The preferred orientation of the lipid
+  concentration is to have the stiff region to pass through the
+  contraction before the floppy region.}
+%  The vesicles are: (a) the initial
+%  lipid-species distribution is fully separated on the right side of the
+%  vesicle; (b) the initial lipid-species distribution is randomly
+%  distributed (not fully separated) on the vesicle membrane; (d) the
+%  initial lipid-species distribution is fully separated on the left side
+%  of the vesicle. The vesicles with a larger percentage of floppy
+%  regions pass through the neck earlier than the vesicles with less
+%  percentage of floppy regions. The vesicle either completely or
+%  partially reorients itself so that the floppy region is in the back
+%  and the stiff region is in the front.}
 \end{figure}
@@
 In Figure~\ref{fig:RA5}, we consider a vesicle with reduced area $\alpha
-= 0.5$ and the dimensionless flow rate is $U = 0.25$. We start with a
+= 0.5$ and the capillary number is $Ca = 0.25$. We start with a
 single-component vesicle and then increase the percentage of the vesicle
@@
   contracting geometry. The vesicle's reduced area is $\alpha = 0.5$ and
-  the dimensionless maximum velocity is $U = 0.25$. The vesicles are:
+  the dimensionless maximum velocity is $Ca = 0.25$. The vesicles are:
   (a) single-component with bending modulus $b=1$; (b) multicomponent

### 2023-06-22 vesicle_code/docs/confinedMulti/makefigs/AshleyFiles/Fig6driver.m

@@ -1,13 +1,0 @@
-figure(1); clf;
-ha = tight_subplot(3,1,0.02,0,[0 0.02]);
-MakeSnaps('Stenosis_RAp6_SC.mat',1,false,ha);
-MakeSnaps('Stenosis_RAp6_SCp55.mat',2,false,ha);
-MakeSnaps('Stenosis_RAp6_MCp5.mat',3,true,ha);
-
-f = figure(1);
-set(f,'Units','Inches');
-pos = get(f,'Position');
-set(f,'PaperPositionMode','Auto','PaperUnits','Inches',...
-    'PaperSize',[pos(3), pos(4)])
-set(f,'Position',[0 0 19 6.4]);
-print(f,'-dpdf','STENOSIS_RAp6MCp5.pdf','-r0')

### 2023-06-22 vesicle_code/docs/confinedMulti/makefigs/AshleyFiles/cline.m

@@ -1,86 +1,0 @@
-%
-% Draw a color-coded line by using the edge of a patch with no facecolor
-%
-% SYNTAX
-% ======
-% h = cline(x, y [, z, cdata])
-%
-% INPUT
-% =====
-% x                     vector with x-values
-% y                     vector with y-values
-% z (opt.)              vector with z-values
-% cdata (opt.)          vector with color-data
-%
-% 2 input arguments =>  cdata = y; z=0      % s. Example 1
-% 3 input arguments =>  cdata = z           % s. Example 2
-% 4 i.a. & z = []   =>  cdata = y; z=0      % s. Example 4
-%
-% OUPUT
-% =====
-% h                 Handle to line (i.e. patch-object !!!)
-%
-% Examples
-% ========
-% t = 2*pi:.1:8*pi;
-%
-% cline(sqrt(t).*sin(t), sqrt(t).*cos(t)); view(3)                       % Example 1
-% cline(sqrt(t).*sin(t), sqrt(t).*cos(t), t); view(3)                    % Example 2
-% cline(sqrt(t).*sin(t), sqrt(t).*cos(t), t, rand(size(t))); view(3)     % Example 3
-% cline(sqrt(t).*sin(t), sqrt(t).*cos(t), [], rand(size(t))); view(3)	 % Example 4
-% 
-%
-% Author & Version
-% ================
-% S. Hlz, TU-Berlin, seppel_mit_ppATweb.de
-% V 1.0, 16.4.2007
-% Created using Matlab 7.0.4 (SP2)
-%
-
-% Info
-% ====
-% This function uses the edges of a patch to represent the colored 2D/3D-line. The marker-related
-% properties (i.e. 'maker','markersize','markeredgecolor','markerfacecolor') can be used as with a
-% regular line. 
-%
-% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-% The line-related properties (i.e. 'linestyle','linewidth') WILL HAVE NO EFFECT 
-% while displaying the line on screen, but will change the output when printing to file !!!
-% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!! !!!!!
-%
-% This is not a flaw of this function but rather the way Matlab interprets the interpolated edges of
[…]

### 2023-06-22 vesicle_code/docs/confinedMulti/makefigs/MakeSnaps.m

@@ -1,0 +1,109 @@
+function [] = MakeSnaps(file,sp,cb,ha)
+%if ~exist('posx1')
+%  load Stenosis_RAp6_MCp5.mat
+%end
+load(file);
+
+addpath ../../../../../shuwang_rewrite
+
+bmin = .1;
+bmax = 1;
+a = 100;
+
+points = linspace(-22,22,8);
+%points = [-25,12.9,13.5,14.9271,15.6729,15.871,16.5];
+%points = [0.05,0.15,0.2,0.28,0.31,0.34,0.4,0.5];
+
+a = find(mean(squeeze(posx1))>=points(1));
+b = find(mean(squeeze(posx1))>=points(2));
+c = find(mean(squeeze(posx1))>=points(3));
+d = find(mean(squeeze(posx1))>=points(4));
+e = find(mean(squeeze(posx1))>=points(5));
+f = find(mean(squeeze(posx1))>=points(6));
+g = find(mean(squeeze(posx1))>=points(7));
+h = find(mean(squeeze(posx1))>=points(8));
+k = [a(1),b(1),c(1),c(1),c(1),c(1),d(1),e(1),f(1),g(1),h(1)];
+
+Nbd = 2048;
+geomCenter = [0;0];
+wallGeometry = 'longchoke';
+oc = curve(Nbd);
+[~,Xwalls] = oc.initConfig(Nbd,false,...
+             'scale', 1, ...
+             'center', geomCenter, 'geometry', wallGeometry);
+[xwalls,ywalls] = oc.getXY(Xwalls);
+xwalls = [xwalls(:);xwalls(1:4)];
+ywalls = [ywalls(:);ywalls(1:4)];
+
+N = length(posx1(:,:,1));
+oc = curve(N);
+
+%subplot(3,1,sp);
+%figure(1); clf
+plot(xwalls,ywalls, 'k', 'linewidth', 2)
+axis equal
+hold on
+
+color1 = [0 0 1];
+%color2 = [0 1 1];
+color2 = [0.5 1 0];
+color3 = [1 0 0];
+t = linspace(0,1,256)';
+map1 = (1-t)*color1 + t*color2;
+map2 = (1-t(2:end))*color2 + t(2:end)*color3;
+map = [map1;map2];
+colormap(map);
+
+for i = 1:length(k)
[…]

### 2023-06-23 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
updated Fig 15

@@
   \centering
-    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
-    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig14a_newPaper.pdf}
-    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig14b_newPaper.pdf}
-    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(d)}{figures/Fig14c_newPaper.pdf}
-    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(e)}{figures/Fig14e_newPaper.pdf}
+  \includegraphics[width=\columnwidth]{figures/Contracting_RAp6MC_variableConc.pdf}
+%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
+%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig14a_newPaper.pdf}
+%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig14b_newPaper.pdf}
+%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(d)}{figures/Fig14c_newPaper.pdf}
+%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(e)}{figures/Fig14e_newPaper.pdf}
   \caption{\label{fig:RA5} \small A vesicle passing through a

### 2023-06-27 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny at intro

@@
 \section{\label{sec:Introduction}Introduction}
+Biological membranes have been observed to contain a vast array of proteins and different lipid species, that phase-separate and form domains resulting in spatial variations in material properties such as bending stiffness.
+Synthetic multicomponent vesicles, self-enclosed lipid bilayer membranes composed of different lipid species, have been used to study the rich patterns and accompanying morphologies which emerge from elastic heterogeneity in the membrane.
+
 Soft particles, such as vesicles, display rich dynamics when they are

### 2023-06-28 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny at intro

@@
 \section{\label{sec:Introduction}Introduction}
-Biological membranes have been observed to contain a vast array of proteins and different lipid species, that phase-separate and form domains resulting in spatial variations in material properties such as bending stiffness.
+Biological membranes, as the basic structural units for compartmentalizing biological systems, 
+have been observed to contain a vast array of proteins and different lipid species, that phase-separate and form domains or rafts, resulting in spatial variations in material properties such as bending stiffness \cite{}.
 Synthetic multicomponent vesicles, self-enclosed lipid bilayer membranes composed of different lipid species, have been used to study the rich patterns and accompanying morphologies which emerge from elastic heterogeneity in the membrane.
-
-Soft particles, such as vesicles, display rich dynamics when they are
-subjected to different types of physical processes. These dynamics are
-affected by parameters such as the capillary number, reduced volume, and
+In a quiescent environment, inhomogeneity in a vesicle membrane bending stiffness may give rise to change in vesicle morphology \cite{Lowengrub2009_PRE}, closely related to cellular budding and fission processes \cite{Rauch2000_BriophysJ} as well as in membrane adhesion and fusion \cite{Takeda2003_PNAS}.
+
+Under a linear shear flow, a multicomponent vesicle exhibits exotic dynamics in both shape and membrane composition \cite{Liu2017_SoftMatter,Gera2018_SoftMatter,Gera2022_JFM}.
+The vesicle hydrodynamics is characterized by parameters such as the capillary number, reduced volume, and
 confinement ratio. Understanding these dynamics is critical to

### 2023-06-28 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny at intro2
yny at intro3

@@
 Synthetic multicomponent vesicles, self-enclosed lipid bilayer membranes composed of different lipid species, have been used to study the rich patterns and accompanying morphologies which emerge from elastic heterogeneity in the membrane.
-In a quiescent environment, inhomogeneity in a vesicle membrane bending stiffness may give rise to change in vesicle morphology \cite{Lowengrub2009_PRE}, closely related to cellular budding and fission processes \cite{Rauch2000_BriophysJ} as well as in membrane adhesion and fusion \cite{Takeda2003_PNAS}.
-
-Under a linear shear flow, a multicomponent vesicle exhibits exotic dynamics in both shape and membrane composition \cite{Liu2017_SoftMatter,Gera2018_SoftMatter,Gera2022_JFM}.
+In a quiescent environment,  such elastic heterogeneity gives rise to wrinkling budding \cite{Lowengrub2009_PRE,Li2012_CommMathSci}, adhesion and fusion \cite{Zhao2011_PRE} of vesicle membrane, closely related to cellular budding and fission processes \cite{Rauch2000_BriophysJ} as well as in cellular adhesion and fusion \cite{Takeda2003_PNAS}.
+
+Under a linear shear flow, a multicomponent vesicle exhibits more exotic dynamics in both shape and membrane composition \cite{Smith2007_JChemPhys,Cox2015_Nonlinearity,Liu2017_SoftMatter,Gera2018_SoftMatter,Gera2022_JFM} than a single component vesicle \cite{Abreu2014_ACI}.
+%
+%Sohn et al.
+(2010) studied two-dimensional multicomponent vesicles in a background shear flow, along with the evolution of distinct surface phases, finding highly complex morphologies and dynamics for highly deformed vesicles.
+Smith & Uspal (2007) showed using dissipative particle dynamics simulations that a shear flow can be used to separate buds from a multicomponent vesicle.
+The influence of both bending rigidity and spontaneous curvature variation on the equilibrium shape of a vesicle has also been investigated (Cox & Lowengrub 2015).
+Subsequent boundary integral simulations by Liu et al.
+(2017) showed a transition from tumbling to tank-treading to ‘phase-treading’ of the constituents along the surface upon increasing the shear rate.
+Analytic results have also shown that a variation of bending rigidity along a surface can induce migration in tank-treading vesicles (Olla 2011).
+Synthetic systems have also been fruitful for testing theoretical predictions.
+Experiments using a two-phase lipid vesicle in such a flow as a simplified model of red blood cell dynamics showed similarly complex features (Tusch et al.
+2018).
+Gera & Salac (2018b) then used simulations to probe a wide array of morphological changes due to spatially varying bending stiffness and line tension between two lipid phases.
+The phase separation process itself is naturally of great interest, and experiments have been used to study spinodal decomposition and viscous fingering along membrane surfaces (Veatch & Keller 2003; Lowengrub, Rätz & Voigt 2009; Marenduzzo & Orlandini 2013; Stanich et al.
+2013).
+%
 The vesicle hydrodynamics is characterized by parameters such as the capillary number, reduced volume, and
 confinement ratio. Understanding these dynamics is critical to
-understanding biophysical and microfluidic processes. For example, a
+understanding the biophysics of red blood cells (RBCs) in blood flow. For example, a
 vesicle's reduced area and viscosity contrast will determine if it

### 2023-06-29 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny at intro4

@@
 
-Under a linear shear flow, a multicomponent vesicle exhibits more exotic dynamics in both shape and membrane composition \cite{Smith2007_JChemPhys,Cox2015_Nonlinearity,Liu2017_SoftMatter,Gera2018_SoftMatter,Gera2022_JFM} than a single component vesicle \cite{Abreu2014_ACI}.
+The hydrodynamics of a single-component vesicle is characterized by parameters such as the capillary number, reduced volume, and confinement ratio  \cite{Abreu2014_ACI}. 
+%Understanding these dynamics is critical to understanding the biophysics of red blood cells (RBCs) in blood flow. 
+For example, a
+vesicle's reduced area and viscosity contrast will determine if it
+undergoes tank treading, swinging, or tumbling in a shear
+flow~\cite{nog-gom2005}. Transitions in the vesicle shape occur in
+non-linear parabolic flows~\cite{kao-bir-mis2009, dan-vla-mis2009}, and
+these shapes include axisymmetric bullets or parachutes, and asymmetric
+parachutes. More recently, groups have considered these transitions when
+vesicles are suspended in a channel or pipe
+flow~\cite{lyu-che-far-jae-mis-leo2023, aga-bir2020, qua-gan-you2021,
+abb-far-nai-ezz-ben-mis2022}. These dynamics include snaking and
+swirling behaviors; croissant and slipper shapes; and semipermeability.
+
+Under a linear shear flow, a multicomponent vesicle exhibits more exotic dynamics in both shape and membrane composition \cite{Sohn2010_JCP, Smith2007_JChemPhys,Cox2015_Nonlinearity,Liu2017_SoftMatter,Gera2018_SoftMatter,Gera2022_JFM} than a single-component vesicle.
+For example, multicomponent vesicles under a background flow often exhibit highly complex morphologies, leading to vesicle budding. 
+The hydrodynamics of these
+multicomponent vesicles include phase treading, tumbling with no
+viscosity contrast, swinging, budding, and
+fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006,
+ger-sal-spa2022, lip1992, urs-klu-phi2009}. In addition to the
+aforementioned numerical studies, these dynamics have been observed in
+experiments~\cite{bag-sun2009, yan-ima-tan2010, yan-ima-tan2008,
+dre-jah-bob-spa-gop2021}.
+
 %
@@
 %
-The vesicle hydrodynamics is characterized by parameters such as the capillary number, reduced volume, and
-confinement ratio. Understanding these dynamics is critical to
-understanding the biophysics of red blood cells (RBCs) in blood flow. For example, a
-vesicle's reduced area and viscosity contrast will determine if it
-undergoes tank treading, swinging, or tumbling in a shear
-flow~\cite{nog-gom2005}. Transitions in the vesicle shape occur in
-non-linear parabolic flows~\cite{kao-bir-mis2009, dan-vla-mis2009}, and
-these shapes include axisymmetric bullets or parachutes, and asymmetric
-parachutes. More recently, groups have considered these transitions when
-vesicles are suspended in a channel or pipe
-flow~\cite{lyu-che-far-jae-mis-leo2023, aga-bir2020, qua-gan-you2021,
-abb-far-nai-ezz-ben-mis2022}. These dynamics include snaking and
-swirling behaviors; croissant and slipper shapes; and semipermeability.
-
-Groups have also studied the behaviors of a vesicle that is composed of
-different types of lipids and proteins. The presence of different lipid
-species has been used to model different processes including the bending
-stiffness, spontaneous curvature, and adhesion
-potential~\cite{zha-das-du2010, tan-yan-ima2011}. The dynamics of these
-multicomponent vesicles include phase treading, tumbling with no
-viscosity contrast, swinging, budding, and
-fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006,
-ger-sal-spa2022, lip1992, urs-klu-phi2009}. In addition to the
-aforementioned numerical studies, these dynamics have been observed in
-experiments~\cite{bag-sun2009, yan-ima-tan2010, yan-ima-tan2008,
-dre-jah-bob-spa-gop2021}.
+%
+%Groups have also studied the behaviors of a vesicle that is composed of
+%different types of lipids and proteins. The presence of different lipid
+%species has been used to model different processes including the bending
+%stiffness, spontaneous curvature, and adhesion
+%potential~\cite{zha-das-du2010, tan-yan-ima2011}. The dynamics of these
+%multicomponent vesicles include phase treading, tumbling with no
+%viscosity contrast, swinging, budding, and
+%fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006,
+%ger-sal-spa2022, lip1992, urs-klu-phi2009}. In addition to the
+%aforementioned numerical studies, these dynamics have been observed in
+%experiments~\cite{bag-sun2009, yan-ima-tan2010, yan-ima-tan2008,
+%dre-jah-bob-spa-gop2021}.
+%
+
+Vesicles hydrodynamics under extreme confinement has been studied as a model system for red blood cells (RBCs) squeezing through small
+capillaries (of sub-micron size in diameter) under a pressure difference \cite{LuPeng2019_PoF}.
+Membrane permeability has been incorporated to examine the single-component vesicle hydrodynamics.
+It is found that  in the absence of an osmotic stress gradient, the semipermeable vesicle is affected by water influx/efflux over a sufficiently long time or under a strong confinement \cite{Quaife2021_PRF}.
+Numerical simulations illustrate that a vesicle with moderate membrane permeability can go through a strong confinement much more easily, and can restore its water content within a very short time after the passage through the strong confinement \cite{Quaife2021_PRF}.
+These results imply that the membrane permeability may be inferred from vesicle hydrodynamics under a strong confinement.
+Motivated by these results, we ask the following question: How does strong confinement affect the hydrodynamics of a multi-component vesicle?
+This question is highly relevant to hydrodynamics of cells in a confinement, and to our knowledge has not been well studied.
 

### 2023-06-29 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on TT results

--- 2023-06-28 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
@@
 \documentclass[twoside,twocolumn,9pt]{article}
+\usepackage{comment}
 \usepackage{extsizes}
@@
 
+\begin{comment}
 %\begin{figure}[h]
@@
 \end{figure*}
+\end{comment}
 
@@
 
-%The smaller reduced area $\alpha = 0.4$ also results in a larger difference between the size of the top and boundary lubrication layers.
-In particular, Figure~\ref{fig:lubrication}(a) shows that the bottom lubrication layer is larger than the top lubrication layer, indicating the vesicle is above the centerline, and we expect the non-linear shear to result in a counterclockwise tank-treading motion.
-We define the tank treading velocity using several tracker points (solid points) by computing $\uu \cdot \tt$ where $\uu$ is the velocity and $\tt$ is the tangent vector at the tracker point.
-Note that this quantity does not represent a tank treading velocity until the vesicle reaches tank-treading behavior.
-Figure~\ref{fig:tankTreadRAp4} shows that for reduced area $\alpha = 0.4$, both the single and multicomponent vesicles undergo an extended period of tank-treading, but at different speeds, starting near the middle of the region of confinement and ending as the vesicles exit this region.
-Since the difference in sizes of the boundary layers is greater for the single-component vesicle, we expect it to tank-tread faster, which we observe when comparing Figures~\ref{fig:tankTreadRAp4}(a) and (e).In the multicomponent case, there are several interesting features in the tangential velocity, and these are denoted by the red marks in Figure~\ref{fig:tankTreadRAp4}.
-The vesicle shapes at each of these points are in Figure~\ref{fig:tankTreadRAp4}(b) and (c).
-The tangential velocity includes spikes that occur whenever there is a decrease in the phase energy due to floppy and stiff regions merging, and this can be observed in Figures~\ref{fig:tankTreadRAp4}(d) and (e).
-
-\begin{figure}[h]
+%The smaller reduced area $\alpha = 0.4$ also results in a larger
+%difference between the size of the top and boundary lubrication layers.
+%In particular, Figure~\ref{fig:lubrication}(a) shows that the bottom
+%lubrication layer is larger than the top lubrication layer, indicating
+%the vesicle is above the centerline, and we expect the non-linear shear
+%to result in a counterclockwise tank-treading motion. We define the
+%tank treading velocity using several tracker points (solid points) by
+%computing $\uu \cdot \tt$ where $\uu$ is the velocity and $\tt$ is the
+%tangent vector at the tracker point. Note that this quantity does not
+%represent a tank treading velocity until the vesicle reaches
+%tank-treading behavior. Figure~\ref{fig:tankTreadRAp4} shows that for
+%reduced area $\alpha = 0.4$, both the single and multicomponent
+%vesicles undergo an extended period of tank-treading, but at different
+%speeds, starting near the middle of the region of confinement and
+%ending as the vesicles exit this region. Since the difference in sizes
+%of the boundary layers is greater for the single-component vesicle, we
+%expect it to tank-tread faster, which we observe when comparing
+%Figures~\ref{fig:tankTreadRAp4}(a) and (e).In the multicomponent case,
+%there are several interesting features in the tangential velocity, and
+%these are denoted by the red marks in Figure~\ref{fig:tankTreadRAp4}.
+%The vesicle shapes at each of these points are in
+%Figure~\ref{fig:tankTreadRAp4}(b) and (c). The tangential velocity
+%includes spikes that occur whenever there is a decrease in the phase
+%energy due to floppy and stiff regions merging, and this can be
+%observed in Figures~\ref{fig:tankTreadRAp4}(d) and (e).
+
+%\begin{figure}[h]
+%    \begin{minipage}{0.49\columnwidth}
+%        \centering
+%        \subfigimg[width=\textwidth]{(a)}{figures/Fig11c1.pdf}
+%        \subfigimg[width=\textwidth]{(c)}{figures/Fig11b1.pdf}
+%        \subfigimg[width=\textwidth]{(e)}{figures/Fig11a.pdf}
+%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(a)}{figures/TankTreadRAp4Conc.pdf}
+%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(c)}{figures/TankTreadRANoConcp55.pdf}
+%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(e)}{figures/TankTreadRAp4NoConc.pdf}
+%        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6Conc.pdf}
+%        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6NoConc.pdf}
+%    \end{minipage}
+%    \hfill
+%    \begin{minipage}{0.49\columnwidth}
+%        \centering
+%        \subfigimg[width=\textwidth]{(b)}{figures/Fig11c2.pdf}
+%        \subfigimg[width=\textwidth]{(d)}{figures/Fig11b2.pdf}
+%        \subfigimg[width=\textwidth]{(f)}{figures/Fig11a2.pdf}
+%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(b)}{figures/TankTreadRAp4ConcVes.pdf}
+%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(d)}{figures/TankTreadRANoConcp55Ves.pdf}
+%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(f)}{figures/TankTreadRAp4NoConcVes.pdf}
+%        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6ConcVes.pdf}
+%        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6NoConcVes.pdf}
+%    \end{minipage}
+%    \caption{\small The tangential velocity at four Lagrangian points on a (a) single-component vesicle with $b = 1$ (c) single-component vesicle with $b = 0.55$, and (e) multicomponent vesicle.
+The reduced area is $\alpha = 0.4$ in all cases.
+(b/d/f) A corresponding vesicle shape with the Lagrangian points.
+%    \label{fig:tankTreadRAp4}}
+%\end{figure}
+
+\begin{figure}[htp]
   \begin{minipage}{0.49\columnwidth}
     \centering
-        \subfigimg[width=\textwidth]{(a)}{figures/Fig11c1.pdf}
-        \subfigimg[width=\textwidth]{(c)}{figures/Fig11b1.pdf}
-        \subfigimg[width=\textwidth]{(e)}{figures/Fig11a.pdf}
-        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(a)}{figures/TankTreadRAp4Conc.pdf}
-        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(c)}{figures/TankTreadRANoConcp55.pdf}
-        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(e)}{figures/TankTreadRAp4NoConc.pdf}
-        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6Conc.pdf}
-        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6NoConc.pdf}
+    \subfigimg[width=\textwidth]{(a)}{figures/SC_treading_velocity.pdf}
+    \subfigimg[width=\textwidth]{(c)}{figures/SCp55_treading_velocity.pdf}
+%    \subfigimg[width=\textwidth]{(c)}{figures/Fig11b1.pdf}
+%    \subfigimg[width=\textwidth]{(e)}{figures/Fig11a.pdf}
   \end{minipage}
@@
     \centering
-        \subfigimg[width=\textwidth]{(b)}{figures/Fig11c2.pdf}
-        \subfigimg[width=\textwidth]{(d)}{figures/Fig11b2.pdf}
-        \subfigimg[width=\textwidth]{(f)}{figures/Fig11a2.pdf}
-        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(b)}{figures/TankTreadRAp4ConcVes.pdf}
-        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(d)}{figures/TankTreadRANoConcp55Ves.pdf}
-        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(f)}{figures/TankTreadRAp4NoConcVes.pdf}
-        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6ConcVes.pdf}
-        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6NoConcVes.pdf}
+    \subfigimg[width=\textwidth]{(b)}{figures/SC_treading_configuration.pdf}
+    \subfigimg[width=\textwidth]{(d)}{figures/SCp55_treading_configuration.pdf}
+%    \subfigimg[width=\textwidth]{(d)}{figures/Fig11b2.pdf}
+%    \subfigimg[width=\textwidth]{(f)}{figures/Fig11a2.pdf}
   \end{minipage}
-    \caption{\small The tangential velocity at four Lagrangian points on a (a) single-component vesicle with $b = 1$ (c) single-component vesicle with $b = 0.55$, and (e) multicomponent vesicle.
-The reduced area is $\alpha = 0.4$ in all cases.
-(b/d/f) A corresponding vesicle shape with the Lagrangian points.
-    \label{fig:tankTreadRAp4}}
+  \caption{\label{fig:tankTreadRAp4} \small The tangential velocity at
+  four Lagrangian points on a (a) single-component vesicle with $b = 1$
+  (c) single-component vesicle with $b = 0.55$, and (e) multicomponent
+  vesicle. The reduced area is $\alpha = 0.4$ in all cases. (b/d/f) A
+  corresponding vesicle shape with the Lagrangian points. }
 \end{figure}

### 2023-06-29 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
worked on TT results

@@
 %\end{figure}
-
 \begin{figure}[htp]
-  \begin{minipage}{0.49\columnwidth}
-    \centering
-    \subfigimg[width=\textwidth]{(a)}{figures/SC_treading_velocity.pdf}
-    \subfigimg[width=\textwidth]{(c)}{figures/SCp55_treading_velocity.pdf}
-%    \subfigimg[width=\textwidth]{(c)}{figures/Fig11b1.pdf}
-%    \subfigimg[width=\textwidth]{(e)}{figures/Fig11a.pdf}
-  \end{minipage}
-  \hfill
-  \begin{minipage}{0.49\columnwidth}
-    \centering
-    \subfigimg[width=\textwidth]{(b)}{figures/SC_treading_configuration.pdf}
-    \subfigimg[width=\textwidth]{(d)}{figures/SCp55_treading_configuration.pdf}
-%    \subfigimg[width=\textwidth]{(d)}{figures/Fig11b2.pdf}
-%    \subfigimg[width=\textwidth]{(f)}{figures/Fig11a2.pdf}
-  \end{minipage}
+  \centering
+  \subfigimg[width=0.9\columnwidth,trim=0cm 6cm 28cm 1cm,clip=true]{(a)}{figures/TankTreadingFigs_composite_SC.pdf}
+  \subfigimg[width=0.9\columnwidth,trim=0cm 6cm 28cm
+  1cm,clip=true]{(b)}{figures/TankTreadingFigs_composite_SCp55.pdf}
+  \subfigimg[width=0.9\columnwidth,trim=0cm 6cm 28cm
+  1cm,clip=true]{(c)}{figures/TankTreadingFigs_composite_MCp5.pdf}
   \caption{\label{fig:tankTreadRAp4} \small The tangential velocity at
   four Lagrangian points on a (a) single-component vesicle with $b = 1$
-  (c) single-component vesicle with $b = 0.55$, and (e) multicomponent
-  vesicle. The reduced area is $\alpha = 0.4$ in all cases. (b/d/f) A
-  corresponding vesicle shape with the Lagrangian points. }
+  (b) single-component vesicle with $b = 0.55$, and (c) multicomponent
+  vesicle. The reduced area is $\alpha = 0.4$ in all cases. Also
+  illusrated is the vesicle shape and the four Lagrangian points at the
+  location indicated by the dash line.}
 \end{figure}

### 2023-06-29 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
adjusted figure placement

@@
 %\end{figure}
-\begin{figure}[htp]
-  \centering
-  \subfigimg[width=0.9\columnwidth,trim=0cm 6cm 28cm 1cm,clip=true]{(a)}{figures/TankTreadingFigs_composite_SC.pdf}
-  \subfigimg[width=0.9\columnwidth,trim=0cm 6cm 28cm
-  1cm,clip=true]{(b)}{figures/TankTreadingFigs_composite_SCp55.pdf}
-  \subfigimg[width=0.9\columnwidth,trim=0cm 6cm 28cm
-  1cm,clip=true]{(c)}{figures/TankTreadingFigs_composite_MCp5.pdf}
+\begin{figure*}[t]
+%\begin{figure}[htp]
+  \centering
+  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{(a)}{figures/TankTreadingFigs_composite_SC.pdf}
+  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
+  0cm,clip=true]{(b)}{figures/TankTreadingFigs_composite_SCp55.pdf}
+  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
+  0cm,clip=true]{(c)}{figures/TankTreadingFigs_composite_MCp5.pdf}
   \caption{\label{fig:tankTreadRAp4} \small The tangential velocity at
@@
   location indicated by the dash line.}
-\end{figure}
+%\end{figure}
+\end{figure*}
 

### 2023-06-29 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
worked on lubrication layer size plot

@@
     \centering
-    \subfigimg[width = \columnwidth]{(a)}{figures/Fig8a.pdf}\\
-    \subfigimg[width = \columnwidth]{(b)}{figures/Fig8b.pdf}
-    \caption{\small Lubrication layer of a single-component and a multicomponent vesicle moving through a stenosed channel. In the top figure, the reduced area is 0.4, on the bottom it is 0.6.}
-    \label{fig:lubrication}
+    \subfigimg[width = 0.49\columnwidth]{(a)}{figures/Layer_Size_RAp4.pdf}
+    \subfigimg[width = 0.49\columnwidth]{(b)}{figures/Layer_Size_RAp6.pdf}
+%    \subfigimg[width = \columnwidth]{(a)}{figures/Fig8a.pdf}\\
+%    \subfigimg[width = \columnwidth]{(b)}{figures/Fig8b.pdf}
+    \caption{\label{fig:lubrication} \small The size of the lubrication
+    layer of a stiff single component (red), floppy single component
+    (green), and multicomponent (blue) vesicle passing through stenosis.
+    Solid lines are the layer thickness between the vesicle and the top
+    wall, and dashed lines are the layer thickness between the vesicle
+    and the bottom wall. The reduced area of the vesicles are (a)
+    $\alpha = 0.4$ and (b) $\alpha = 0.6$.}
 \end{figure}

### 2023-06-30 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on paper

@@
 
-\begin{comment}
+%\begin{comment}
 %\begin{figure}[h]
-\begin{figure*}[b]
+\begin{figure*}[h]
   \centering
@@
 %    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig5c.pdf}
-  \caption{\label{fig:RA6} \small A vesicle passing through a stenosed
+  \caption{\label{fig:RA6} \small A vesicle passing through the stenosis
   geometry. The vesicle's reduced area is $\alpha = 0.6$ and the
-  dimensionless maximum velocity is $U = 0.25$. The vesicles are: (a)
+  capillary number is $Ca = 0.25$. The vesicles are: (a)
   single-component with bending modulus $b=1$; (b) single-component with
@@
 \end{figure*}
-\end{comment}
+%\end{comment}
 
 We consider a vesicle with reduced area $\alpha = 0.6$ passing through a
-closely-fitting channel, with a dimensionless maximum velocity of $U =
-0.25$. Figure~\ref{fig:RA6} shows six time steps of a single-component
-vesicle with bending stiffness (a) $b=1$ and (b) $b=0.55$, and a
-multicomponent vesicle with an initially random distribution of lipids
-(c). In all plots, the color is the dimensionless bending modulus of the
-multicomponent vesicle that remains bounded in $[0.1,1]$ by using the
-new bending modulus~\eqref{eqn:tanhBending}. A single Lagrangian point
-is included to visualize tank-treading behavior. There are slight
-differences between the three cases, with the most noticeable being that
-the multicomponent vesicle has higher curvature in the floppy region. We
+closely-fitting channel (stenosis), with a capillary number $Ca = 0.25$.
+Figure~\ref{fig:RA6} shows six time steps of a single-component vesicle
+with bending stiffness (a) $b=1$ and (b) $b=0.55$, and (c) a multicomponent
+vesicle with an initially random distribution of lipids. In all plots,
+the color is the dimensionless bending modulus of the multicomponent
+vesicle that remains bounded in $[0.1,1]$ by using the new bending
+modulus~\eqref{eqn:tanhBending}. A single Lagrangian point is included
+to visualize tank-treading behavior. There are slight differences
+between the three cases, with the most noticeable being that the
+multicomponent vesicle has higher curvature in the floppy region. We
 consider the same setup in Figure~\ref{fig:RA4}, but the vesicle has
@@
 
-\begin{comment}
+%\begin{comment}
 %\begin{figure}[h]
-\begin{figure*}[t]
+\begin{figure*}[h]
   \centering
@@
 %    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig6c.pdf}
-  \caption{\label{fig:RA4} \small A vesicle passing through a stenosed
+  \caption{\label{fig:RA4} \small A vesicle passing through the stenosis
   geometry. The vesicle's reduced area is $\alpha = 0.4$ and the
-  dimensionless maximum velocity is $U = 0.25$. The vesicles are: (a)
-  single-component with bending modulus $b=1$; (b) single-component with
-  bending modulus $b=0.55$; (c) multicomponent. The multicomponent
-  vesicle travels slightly faster, so it leaves the stenosed region
-  earlier than the single-component cases (see
-  Figure~\ref{fig:vesVelocity}).}
+  capillary number is $Ca = 0.25$. The vesicles are: (a) single-component
+  with bending modulus $b=1$; (b) single-component with bending modulus
+  $b=0.55$; (c) multicomponent.}
+%  The multicomponent vesicle travels
+%  slightly faster, so it leaves the stenosed region earlier than the
+%  single-component cases (see Figure~\ref{fig:vesVelocity}).}
 %\end{figure}
 \end{figure*}
-\end{comment}
+%\end{comment}
 
@@
     \caption{\label{fig:lubrication} \small The size of the lubrication
-    layer of a stiff single component (red), floppy single component
+    layer of a stiff single-component (red), floppy single-component
     (green), and multicomponent (blue) vesicle passing through stenosis.
@@
 
-The tank-treading velocities of the examples with reduced area $\alpha = 0.4$ are in Figure~\ref{fig:tankTreadRAp4}.
-The vesicle shapes at the dashed black lines are also included, and the four marker points are the Lagrangian points where the tangential velocities are computed.
-For reduced area $\alpha = 0.4$, the single-component ($b=1$) and multicomponent vesicles are clearly tank treading.
-Since the single-component case has a larger difference between its top and bottom boundary layers, it tank treads faster than the multicomponent case.
-In addition, since the top boundary layer is larger in both cases, they both tank-tread in the same direction---counterclockwise.
-In contrast, the single-component vesicle with $b=0.55$ tank-treads in the clockwise direction; note, however, that this example is still undergoing some deformations, so a constant tank-treading velocity is not observed.
-When $\alpha = 0.6$, the vesicle undergoes deformations while in the stenosed geometry and a constant tank-treading velocity is not observed, so a plot is not included.
+The tank-treading velocities of the examples with reduced area $\alpha =
+0.4$ are in Figure~\ref{fig:tankTreadRAp4}. The vesicle shapes at the
+dashed black lines are also included, and the four marker points are the
+Lagrangian points where the tangential velocities are computed. For
+reduced area $\alpha = 0.4$, the single-component ($b=1$) and
+multicomponent vesicles are clearly tank treading. Since the
+single-component case has a larger difference between its top and bottom
+boundary layers (see Figure~\ref{fig:lubrication)}, it tank treads
+faster than the multicomponent case. In addition, since the top boundary
+layer is larger in both cases, they both tank-tread in the same
+direction---counterclockwise. In contrast, the single-component vesicle
+with $b=0.55$ tank-treads in the clockwise direction; note, however,
+that this example is still undergoing some deformations, so a constant
+tank-treading velocity is not observed. When $\alpha = 0.6$, the vesicle
+undergoes deformations while in the stenosis, and a constant
+tank-treading velocity is not observed
 
@@
   vesicle. The reduced area is $\alpha = 0.4$ in all cases. Also
-  illusrated is the vesicle shape and the four Lagrangian points at the
+  illustrated is the vesicle shape and the four Lagrangian points at the
   location indicated by the dash line.}
@@
 
-The size of the top and bottom lubrication layers are also related to the excess pressure (Figure~\ref{fig:excessPressure}).
-If the lubrication layers are large, most notably for the multicomponent vesicle with reduced area $\alpha = 0.4$, then less pressure is required to force the vesicle through the geometry, and we expect a smaller (less negative) excess pressure.
-In contrast, if the lubrication layers are small, most notably for the single-component vesicle with $b=1$ and reduced area $\alpha = 0.4$, then more pressure is required to force the vesicle through the geometry, and we expect a larger (more negative) excess pressure.
+The size of the top and bottom lubrication layers are also related to
+the excess pressure (Figure~\ref{fig:excessPressure}). If the
+lubrication layers are large, most notably for the multicomponent
+vesicle with reduced area $\alpha = 0.4$, then less pressure is required
+to force the vesicle through the geometry, and we expect a smaller (less
+negative) excess pressure. In contrast, if the lubrication layers are
+small, most notably for the single-component vesicle with $b=1$ and
+reduced area $\alpha = 0.4$, then more pressure is required to force the
+vesicle through the geometry, and we expect a larger (more negative)
+excess pressure.
 
@@
 behavior and the excess pressure, it has almost no effect on the
-migration speed of the vesicle. In Figure~\ref{fig:vesVelocity}, we plot
-the average velocity of the vesicle as it passes through the stenosed
-region. With the exception of the single-component vesicle with $b=1$
-and $\alpha = 0.6$, the average vesicle speed is constant. Obviously,
-this average velocity would be affected by the maximum imposed velocity,
-$U$.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\columnwidth]{figures/Fig9.pdf}
-    %\input{figures/Fig9.tikz}
-    \caption{\label{fig:vesVelocity} \small The average vesicle velocity as it passes through the stenosed region. The vesicle stiffness and reduced area have no significant effect.}
-\end{figure}
+migration speed of the vesicle. 
+%In Figure~\ref{fig:vesVelocity}, we plot
+%the average velocity of the vesicle as it passes through the stenosed
+%region.
+With the exception of the single-component vesicle with $b=1$ and
+$\alpha = 0.6$, which has an average vesicle speed about 5\% slower, the
+average vesicle speed is constant. Obviously, this average velocity
+would be affected by the capillary number, $Ca$.
+
+%\begin{figure}[H]
+%  \centering
+%  \includegraphics[width=\columnwidth]{figures/Fig9.pdf}
+%%  \input{figures/Fig9.tikz}
+%  \caption{\label{fig:vesVelocity} \small The average vesicle velocity
+%  as it passes through stenosis. The vesicle stiffness and reduced area
+%  have no significant effect.}
+%\end{figure}
 
@@
 The magnitude of the Poiseuille profile is determined by the pressure
-gradient between the vesicle and the soild wall, while the linear
+gradient between the vesicle and the solid wall, while the linear
 profile is determined by the tangential velocity of the vesicle relative
-to the solid wall.
-
-Using the definition of the lubrcication layer outlined in
-Section~\ref{sec:LL} fit the horizontal flow profile to a quadratic
-function and plot the coefficients of the Poisseuille and linear shear
-in Figure~\ref{}. We only consider cases where the vesicle has reached a
-steady shape is only under going tank treading. We observe that the
-Poisseuille coefficient can be either positive or negative, meaning that
-the pressure in the lubcrication layer switches signs. This behavior is
-caused when the tangential force on the vesicle
+to the solid wall. Using the definition of the lubrication layer
+outlined in Section~\ref{sec:LL}, we consider the flow profile inside
+this lubrication layer in Figure~\ref{fig:BLvelocities}. We observe that
+the Poiseuille coefficient can be either positive or negative, meaning
+that the pressure in the lubrication layer switches signs. This behavior
+is caused when the tangential force on the vesicle
 \begin{align}

### 2023-07-03 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
adding new excess pressure plots
fixing caption

@@
   \centering
-    \subfigimg[width = 0.45\columnwidth]{(a)}{figures/Fig10a.pdf}
-    \subfigimg[width = 0.45\columnwidth]{(b)}{figures/Fig10b.pdf}
-    \caption{\small The excess pressure a single-component and a multicomponent vesicle moving through a stenosed channel. The reduced areas are (a) $\alpha = 0.4$, and (b) $\alpha = 0.6$.}
-    \label{fig:excessPressure}
+  \subfigimg[width = 0.49\columnwidth]{(a)}{figures/Excess_Pressure_RAp4}
+  \subfigimg[width = 0.49\columnwidth]{(b)}{figures/Excess_Pressure_RAp6}
+%    \subfigimg[width = 0.45\columnwidth]{(a)}{figures/Fig10a.pdf}
+%    \subfigimg[width = 0.45\columnwidth]{(b)}{figures/Fig10b.pdf}
+  \caption{\label{fig:excessPressure} \small The excess pressure a
+  stiff single-component (red), floppy single-component (green), and a
+  multicomponent (blue) vesicle moving through stenosis. The reduced
+  areas are (a) $\alpha = 0.4$, and (b) $\alpha = 0.6$.}
 \end{figure}

### 2023-07-04 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

@@
 
-Vesicles hydrodynamics under extreme confinement has been studied as a model system for red blood cells (RBCs) squeezing through small
+Vesicle hydrodynamics in extreme confinement has been studied as a model system for red blood cells (RBCs) squeezing through small
 capillaries (of sub-micron size in diameter) under a pressure difference \cite{LuPeng2019_PoF}.
 Membrane permeability has been incorporated to examine the single-component vesicle hydrodynamics.
-It is found that  in the absence of an osmotic stress gradient, the semipermeable vesicle is affected by water influx/efflux over a sufficiently long time or under a strong confinement \cite{Quaife2021_PRF}.
-Numerical simulations illustrate that a vesicle with moderate membrane permeability can go through a strong confinement much more easily, and can restore its water content within a very short time after the passage through the strong confinement \cite{Quaife2021_PRF}.
+In the absence of an osmotic gradient, the semipermeable vesicle is affected by water influx/efflux over a sufficiently long time or under a strong confinement \cite{Quaife2021_PRF}.
+Numerical simulations illustrate that a vesicle with moderate membrane permeability can go through a strong confinement much more easily, and can restore its water content within a very short time after its passage through the strong confinement \cite{Quaife2021_PRF}.
 These results imply that the membrane permeability may be inferred from vesicle hydrodynamics under a strong confinement.
-Motivated by these results, we ask the following question: How does strong confinement affect the hydrodynamics of a multi-component vesicle?
+Motivated by these results, in this work we seek to investigate how strong confinement may affect the hydrodynamics of a multi-component vesicle?
 This question is highly relevant to hydrodynamics of cells in a confinement, and to our knowledge has not been well studied.

### 2023-07-04 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

@@
 Synthetic multicomponent vesicles, self-enclosed lipid bilayer membranes composed of different lipid species, have been used to study the rich patterns and accompanying morphologies which emerge from elastic heterogeneity in the membrane.
-In a quiescent environment,  such elastic heterogeneity gives rise to wrinkling budding \cite{Lowengrub2009_PRE,Li2012_CommMathSci}, adhesion and fusion \cite{Zhao2011_PRE} of vesicle membrane, closely related to cellular budding and fission processes \cite{Rauch2000_BriophysJ} as well as in cellular adhesion and fusion \cite{Takeda2003_PNAS}.
+In a quiescent environment,  such elastic heterogeneity gives rise to wrinkling budding \cite{Lowengrub2009_PRE,Li2012_CommMathSci}, adhesion and fusion \cite{Zhao2011_PRE} of vesicle membrane, closely related to cellular budding and fission processes \cite{Rauch2000_BiophysJ} as well as in cellular adhesion and fusion \cite{Takeda2003_PNAS}.
 
 The hydrodynamics of a single-component vesicle is characterized by parameters such as the capillary number, reduced volume, and confinement ratio  \cite{Abreu2014_ACI}. 
+Such characterization is often useful for inferring fluid and material properties.
 %Understanding these dynamics is critical to understanding the biophysics of red blood cells (RBCs) in blood flow. 
@@
 these shapes include axisymmetric bullets or parachutes, and asymmetric
-parachutes. More recently, groups have considered these transitions when
-vesicles are suspended in a channel or pipe
+parachutes. Recently, characterization of 
+vesicles suspended in a channel or pipe
 flow~\cite{lyu-che-far-jae-mis-leo2023, aga-bir2020, qua-gan-you2021,
-abb-far-nai-ezz-ben-mis2022}. These dynamics include snaking and
-swirling behaviors; croissant and slipper shapes; and semipermeability.
+abb-far-nai-ezz-ben-mis2022} showed more exotic vesicle hydrodynamics such as snaking and
+swirling behaviors in croissant and slipper shapes.
 

### 2023-07-05 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
small changes to stenosis section

@@
 (contracting). We considered a semipermeable vesicle suspended in these
-same geometries~\cite{qua-gan-you2021}. All the multicomponent examples
-have floppy-to-stiff ratio $\beta = 10^{-1}$. For the single-component
-case, we consider two bending stiffnesses: $b(u) = 1$ and $b(u) = 0.55$
-which is the average bending stiffness of a multicomponent vesicle whose
-stiff and floppy regions have the same area. Throughout this section we
-plot the position of the vesicle in terms of the $x$-coordinate of its
-center of mass. For the stenosed geometry in
-Section~\ref{subsec:Stenosis}, the narrow region begins at $x=-15$ and
-ends at $x=15$. For the contracting geometry in
+same geometries in our previous work~\cite{qua-gan-you2021}. All the
+multicomponent examples have floppy-to-stiff ratio $\beta = 10^{-1}$.
+For the single-component case, we consider two bending stiffnesses:
+$b(u) = 1$ and $b(u) = 0.55$ which is the average bending stiffness of a
+multicomponent vesicle whose stiff and floppy regions have the same
+area. Throughout this section we plot the position of the vesicle in
+terms of the $x$-coordinate of its center of mass. For the stenosed
+geometry in Section~\ref{subsec:Stenosis}, the narrow region begins at
+$x=-15$ and ends at $x=15$. For the contracting geometry in
 Section~\ref{subsec:Contraction}, the geometry begins to narrow at $x=4$
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\label{subsec:Stenosis}A multicomponent vesicle in a closely-fit channel (Stenosis)}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{\label{subsec:Stenosis}A multicomponent vesicle in the
+stenosis geometry}
 
@@
 
-We consider a vesicle with reduced area $\alpha = 0.6$ passing through a
-closely-fitting channel (stenosis), with a capillary number $Ca = 0.25$.
+We start by considering a vesicle with reduced area $\alpha = 0.6$
+passing through stenosis with a capillary number $Ca = 0.25$.
 Figure~\ref{fig:RA6} shows six time steps of a single-component vesicle
-with bending stiffness (a) $b=1$ and (b) $b=0.55$, and (c) a multicomponent
-vesicle with an initially random distribution of lipids. In all plots,
-the color is the dimensionless bending modulus of the multicomponent
-vesicle that remains bounded in $[0.1,1]$ by using the new bending
-modulus~\eqref{eqn:tanhBending}. A single Lagrangian point is included
-to visualize tank-treading behavior. There are slight differences
-between the three cases, with the most noticeable being that the
-multicomponent vesicle has higher curvature in the floppy region. We
+with bending stiffness (a) $b=1$ and (b) $b=0.55$, and (c) a
+multicomponent vesicle with an initially random distribution of lipids.
+In all plots, the color is the dimensionless bending modulus of the
+multicomponent vesicle that remains bounded in $[0.1,1]$ by using the
+new bending modulus~\eqref{eqn:tanhBending}. A single Lagrangian point
+is included to visualize tank-treading behavior. There are slight
+differences between the three cases, with the most noticeable being that
+the multicomponent vesicle has higher curvature in the floppy region. We
 consider the same setup in Figure~\ref{fig:RA4}, but the vesicle has
-reduced area $\alpha = 0.4$. The main difference between the two reduced
-areas is that the vesicles with smaller reduced area undergo
-tank-treading motions. As mentioned earlier, tank treading occurs when
-the top and bottom lubrication layers differ in size. The size of the
-lubrication layers in all six cases are in Figure~\ref{fig:lubrication}.
+reduced area $\alpha = 0.4$. We first consider the three different
+energies---bending, tension, and phase---for each of the
+single-component and multicomponent vesicles. In
+Figure~\ref{fig:Energy}, we plot these energies as a function of the
+vesicle's center of mass. As a reminder, the vesicle enters the
+constriction at $x=-15$ and exits at $x=15$. Also note that the
+single-component vesicle does not have a phase energy. A few general
+trends can immediately be seen. First, as the vesicle enters the
+stenosis, there are sharp jumps in both the tension and bending
+energies, as expected. Next, the multicomponent vesicles only coarsen
+when the vesicle is not in the stenosis. Finally, when coarsening does
+occur, there are rapid changes in the tension energy.
+
+\begin{figure}
+  \begin{minipage}{0.49\columnwidth}
+    \centering
+%    \subfigimg[width = \columnwidth, trim = {1cm 20cm 1cm 3cm}, clip]{(a)}{figures/RAp4BkgrdFlow.pdf}
+    \subfigimg[width=\textwidth]{(a)}{figures/Fig13a.pdf}
+    \subfigimg[width=\textwidth]{(c)}{figures/Fig13c.pdf}
+    \subfigimg[width=\textwidth]{(e)}{figures/Fig13e.pdf}
+  \end{minipage}
+  \hfill
+  \begin{minipage}{0.49\columnwidth}
+    \centering
+    \subfigimg[width=\textwidth]{(b)}{figures/Fig13b.pdf}
+    \subfigimg[width=\textwidth]{(d)}{figures/Fig13d.pdf}
+    \subfigimg[width=\textwidth]{(f)}{figures/Fig13f.pdf}
+  \end{minipage}
+  \caption{\label{fig:Energy} \small The Bending (blue), tension
+  (yellow), and phase (red) energies for a (a/b) single-component
+  vesicle with $b=1$, (c/d) single-component vesicle with $b = 0.55$,
+  and (e/f) multicomponent vesicle. The reduced areas are $\alpha = 0.4$
+  (a/c/e) and $\alpha = 0.6$ (b/d/f).}
+  \todo[inline]{need to redo these plots}
+\end{figure}
+
+A main difference between the two reduced areas is that the vesicles
+with smaller reduced area undergo tank-treading motions. As mentioned
+earlier, tank treading occurs when the top and bottom lubrication layers
+differ in size. The size of the lubrication layers in all six cases are
+in Figure~\ref{fig:lubrication}. The tank-treading velocities of the
+examples with reduced area $\alpha = 0.4$ are in
+Figure~\ref{fig:tankTreadRAp4}. The vesicle shapes at the dashed black
+lines are also included, and the four marker points are the Lagrangian
+points where the tangential velocities are computed. For reduced area
+$\alpha = 0.4$, the single-component ($b=1$) and multicomponent vesicles
+are clearly tank treading. Since the single-component case has a larger
+difference between its top and bottom boundary layers (see
+Figure~\ref{fig:lubrication}), it tank treads faster than the
+multicomponent case. In addition, since the top boundary layer is larger
+in both cases, they both tank-tread in the same
+direction---counterclockwise. In contrast, the single-component vesicle
+with $b=0.55$ tank-treads in the clockwise direction; note, however,
+that this example is still undergoing some deformations, so a constant
+tank-treading velocity is not observed. When $\alpha = 0.6$, the vesicle
+undergoes deformations while in the stenosis, and a constant
+tank-treading velocity is not observed
 
@@
 \end{figure}
-
-The tank-treading velocities of the examples with reduced area $\alpha =
-0.4$ are in Figure~\ref{fig:tankTreadRAp4}. The vesicle shapes at the
-dashed black lines are also included, and the four marker points are the
-Lagrangian points where the tangential velocities are computed. For
-reduced area $\alpha = 0.4$, the single-component ($b=1$) and
-multicomponent vesicles are clearly tank treading. Since the
-single-component case has a larger difference between its top and bottom
-boundary layers (see Figure~\ref{fig:lubrication)}, it tank treads
-faster than the multicomponent case. In addition, since the top boundary
-layer is larger in both cases, they both tank-tread in the same
-direction---counterclockwise. In contrast, the single-component vesicle
-with $b=0.55$ tank-treads in the clockwise direction; note, however,
-that this example is still undergoing some deformations, so a constant
-tank-treading velocity is not observed. When $\alpha = 0.6$, the vesicle
-undergoes deformations while in the stenosis, and a constant
-tank-treading velocity is not observed
 
@@
 average vesicle speed is constant. Obviously, this average velocity
-would be affected by the capillary number, $Ca$.
+would be affected by the capillary number.
 
@@
 %\end{figure}
-
-Finally, we consider the three different energies---bending, tension,
-and phase---for each of the single-component and multicomponent
-vesicles. In Figure~\ref{fig:Energy}, we plot these energies as a
-function of the vesicle's center of mass. As a reminder, the vesicle
-enters the constriction at $x=-15$ and exits at $x=15$. Also note that
-the single-component vesicle does not have a phase energy. A few general
-trends can immediately be seen. First, as the vesicle enters the
-stenosed region, there are sharp jumps in both the tension and bending
-energies, as expected. Next, the multicomponent vesicles only coarsen
-when the vesicle is not in the stenosed region. Finally, when coarsening
-does occur, there are rapid changes in the tension energy.
-
-\begin{figure}
-  \begin{minipage}{0.49\columnwidth}
-    \centering
-%    \subfigimg[width = \columnwidth, trim = {1cm 20cm 1cm 3cm}, clip]{(a)}{figures/RAp4BkgrdFlow.pdf}
-    \subfigimg[width=\textwidth]{(a)}{figures/Fig13a.pdf}
-    \subfigimg[width=\textwidth]{(c)}{figures/Fig13c.pdf}
-    \subfigimg[width=\textwidth]{(e)}{figures/Fig13e.pdf}
-  \end{minipage}
-  \hfill
-  \begin{minipage}{0.49\columnwidth}
-    \centering
-    \subfigimg[width=\textwidth]{(b)}{figures/Fig13b.pdf}
-    \subfigimg[width=\textwidth]{(d)}{figures/Fig13d.pdf}
-    \subfigimg[width=\textwidth]{(f)}{figures/Fig13f.pdf}
-  \end{minipage}
-  \caption{\label{fig:Energy} \small The Bending (blue), tension
-  (yellow), and phase (red) energies for a (a/b) single-component
-  vesicle with $b=1$, (c/d) single-component vesicle with $b = 0.55$,
-  and (e/f) multicomponent vesicle. The reduced areas are $\alpha = 0.4$
-  (a/c/e) and $\alpha = 0.6$ (b/d/f).}
-\end{figure}
 
@@
 
-%\begin{itemize}
-
-%    \item Comparison of different flow rates $\chi = 0.25 = 0.5 \mu m/s$ and $\chi = 2.5 = 5 \mu m/s$
-
-%    \item Comparison of different reduced areas.
-Definitely interested in 0.40 and then maybe only one other value.
-A natural other value is 0.6 or 0.7 since this is close to the reduced area of a RBC.
-
-%    \item Interesting tank treading/slipper shape when flow rate is 0.25 and reduced area is 0.4.
-We did not see this for any of the larger flow rates, and this is consistent with what is known about vesicles in a non-linear shear flow
-
-%    \item Multicomponent goes through faster than single-component
-
-%    \item Error in area is about 20X larger for the multicomponent
-%    
-%    \item How does the reduced area affect the speed of the vesicle and its ability to phase separate when i%n confinement.
-We haven't looked at a completed run with larger reduced area.
-Maybe there's one sitting on RCC or we% need to submit one?
-%\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\label{subsec:Contraction} A multicomponent vesicle in a narrowing geometry (Contracting)}
-In this section, we consider a single vesicle passing through a geometry that slowly contracts to a region that is only 2~$\mu$m wide, and then immediately opens back up to a channel that is ten times larger.
-We first consider the effect of the initial lipid concentration when the floppy and stiff regions each make up half of the vesicle membrane.
-In Figure~\ref{fig:RA6leftRightRand}, we consider a vesicle with $\alpha = 0.6$ with an initially random initial lipid concentration, one that is floppy in the front and stiff in the back, and one that is stiff in the front and floppy in the back.
-The vesicle with the random initial lipid distribution phase separates so that the floppy region is in the back and the stiff region is in the front.
-The vesicle where the initial lipid species distribution was fully phase separated and the floppy region was on the front of the vesicle began to reorient the floppy region to the back of the vesicle, making it partway after passing through the contraction.
-In the case where the initial lipid species distribution was fully phase separated and the floppy region was on the back of the vesicle, the floppy region remained on the the back of the vesicle.
-In all cases, the floppy regions were being oriented to cover the regions of the vesicle with the highest curvature to minimize the overall bending energy.
-Since we can see in Figure~\ref{fig:RA6leftRightRand} that the regions of high curvature are located in the back of the vesicle, we expect the overall bending energies to be lowest for the randomly distributed case and the fully separated floppy region on the back case.
-We observe this in Figure~\ref{fig:RAp6leftRightRandBending} Therefore, in all subsequent examples, we start with symmetric vesicle whose floppy region is in the back and its stiff region is in the front.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{\label{subsec:Contraction} A multicomponent vesicle in the
+contracting geometry}
+In this section, we consider a single vesicle passing through a geometry
+that slowly contracts to a region that is only 2~$\mu$m wide, and then
+immediately opens back up to a channel that is ten times larger. We
+first consider the effect of the initial lipid concentration when the
+floppy and stiff regions each make up half of the vesicle membrane. In
+Figure~\ref{fig:RA6leftRightRand}, we consider a vesicle with $\alpha =
+0.6$ with an initially random initial lipid concentration, one that is
+floppy in the front and stiff in the back, and one that is stiff in the
+front and floppy in the back. The vesicle with the random initial lipid
+distribution phase separates so that the floppy region is in the back
+and the stiff region is in the front. The vesicle where the initial
+lipid species distribution was fully phase separated and the floppy
+region was on the front of the vesicle began to reorient the floppy
+region to the back of the vesicle, making it partway after passing
+through the contraction. In the case where the initial lipid species
+distribution was fully phase separated and the floppy region was on the
+back of the vesicle, the floppy region remained on the back of the
+vesicle. In all cases, the floppy regions were being oriented to cover
+the regions of the vesicle with the highest curvature to minimize the
+overall bending energy. Since we can see in
+Figure~\ref{fig:RA6leftRightRand} that the regions of high curvature are
+located in the back of the vesicle, we expect the overall bending
+energies to be lowest for the randomly distributed case and the fully
+separated floppy region on the back case. We observe this in
+Figure~\ref{fig:RAp6leftRightRandBending} Therefore, in all subsequent
+examples, we start with symmetric vesicle whose floppy region is in the
+back and its stiff region is in the front.
 
@@
   \includegraphics[width=\columnwidth]{figures/bending_leftRightRand.pdf}
-    \caption{The bending energy of a multicomponent vesicle that is 50\% stiff with an initial phase separation to the left (blue), to the right (red), randomly distributed (yellow).
-The vesicle exits the contraction $x \approx 15$.}
-    \label{fig:RAp6leftRightRandBending}
+  \caption{\label{fig:RAp6leftRightRandBending} The bending energy of a
+  multicomponent vesicle that is 50\% stiff with an initial phase
+  separation to the left (blue), to the right (red), randomly
+  distributed (yellow). The vesicle exits the contraction $x \approx
+  15$.} 
 \end{figure}

### 2023-07-10 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
blended some plots to get the fig count down

@@
 
+\textcolor{red}{Back of the envelope calculation shows that anything
+with reduced area greater than 0.8 can not pass through the stenosis,
+assuming the vesicle shape is an ellipse}
 We start by considering a vesicle with reduced area $\alpha = 0.6$
@@
 
-\begin{figure}[h]
-    \centering
-    \subfigimg[width = 0.49\columnwidth]{(a)}{figures/Layer_Size_RAp4.pdf}
-    \subfigimg[width = 0.49\columnwidth]{(b)}{figures/Layer_Size_RAp6.pdf}
-%    \subfigimg[width = \columnwidth]{(a)}{figures/Fig8a.pdf}\\
-%    \subfigimg[width = \columnwidth]{(b)}{figures/Fig8b.pdf}
-    \caption{\label{fig:lubrication} \small The size of the lubrication
-    layer of a stiff single-component (red), floppy single-component
-    (green), and multicomponent (blue) vesicle passing through stenosis.
-    Solid lines are the layer thickness between the vesicle and the top
-    wall, and dashed lines are the layer thickness between the vesicle
-    and the bottom wall. The reduced area of the vesicles are (a)
-    $\alpha = 0.4$ and (b) $\alpha = 0.6$.}
-\end{figure}
+%\begin{figure}[h]
+%    \centering
+%    \subfigimg[width = 0.49\columnwidth]{(a)}{figures/Layer_Size_RAp4.pdf}
+%%    \subfigimg[width = 0.49\columnwidth]{(b)}{figures/Layer_Size_RAp6.pdf}
+%%    \subfigimg[width = \columnwidth]{(a)}{figures/Fig8a.pdf}\\
+%%    \subfigimg[width = \columnwidth]{(b)}{figures/Fig8b.pdf}
+%    \caption{\label{fig:lubrication} \small The size of the lubrication
+%    layer of a stiff single-component (red), floppy single-component
+%    (green), and multicomponent (blue) vesicle passing through stenosis.
+%    Solid lines are the layer thickness between the vesicle and the top
+%    wall, and dashed lines are the layer thickness between the vesicle
+%    and the bottom wall. The reduced area of the vesicles are (a)
+%    $\alpha = 0.4$ and (b) $\alpha = 0.6$.}
+%\end{figure}
 
@@
   \centering
-  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{(a)}{figures/TankTreadingFigs_composite_SC.pdf}
+  \subfigimg[width=0.3\linewidth]{(a)}{figures/Layer_Size_RAp4_SC.pdf}
+  \subfigimg[width=0.3\linewidth]{(b)}{figures/Layer_Size_RAp4_SCp55.pdf}
+  \subfigimg[width=0.3\linewidth]{(c)}{figures/Layer_Size_RAp4_MCp5.pdf}
+  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{}{figures/TankTreadingFigs_composite_SC.pdf}
   \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
-  0cm,clip=true]{(b)}{figures/TankTreadingFigs_composite_SCp55.pdf}
+  0cm,clip=true]{}{figures/TankTreadingFigs_composite_SCp55.pdf}
   \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
-  0cm,clip=true]{(c)}{figures/TankTreadingFigs_composite_MCp5.pdf}
-  \caption{\label{fig:tankTreadRAp4} \small The tangential velocity at
-  four Lagrangian points on a (a) single-component vesicle with $b = 1$
-  (b) single-component vesicle with $b = 0.55$, and (c) multicomponent
-  vesicle. The reduced area is $\alpha = 0.4$ in all cases. Also
+  0cm,clip=true]{}{figures/TankTreadingFigs_composite_MCp5.pdf}
+  \caption{\label{fig:tankTreadRAp4} \small The lubrication layer
+  thicknesses (red and blue), excess pressure (green), and tank treading
+  velocity of four Lagrangian points of a (a) stiff single-component
+  vesicle, (b) floppy single-component vesicle, and (c) multicomponent
+  vesicle. The reduced area is $\alpha = 0.4$ in all three cases. Also
   illustrated is the vesicle shape and the four Lagrangian points at the
-  location indicated by the dash line.}
+  location indicated by the dash line. The black dashed line is the
+  center line of the channel, and the arrow denotes the tank treading
+  direction.}
 %\end{figure}
@@
 
-\begin{figure}[H]
-  \centering
-  \subfigimg[width = 0.49\columnwidth]{(a)}{figures/Excess_Pressure_RAp4}
-  \subfigimg[width = 0.49\columnwidth]{(b)}{figures/Excess_Pressure_RAp6}
-%    \subfigimg[width = 0.45\columnwidth]{(a)}{figures/Fig10a.pdf}
-%    \subfigimg[width = 0.45\columnwidth]{(b)}{figures/Fig10b.pdf}
-  \caption{\label{fig:excessPressure} \small The excess pressure a
-  stiff single-component (red), floppy single-component (green), and a
-  multicomponent (blue) vesicle moving through stenosis. The reduced
-  areas are (a) $\alpha = 0.4$, and (b) $\alpha = 0.6$.}
-\end{figure}
+%\begin{figure}[H]
+%  \centering
+%  \subfigimg[width = 0.49\columnwidth]{(a)}{figures/Excess_Pressure_RAp4}
+%  \subfigimg[width = 0.49\columnwidth]{(b)}{figures/Excess_Pressure_RAp6}
+%%    \subfigimg[width = 0.45\columnwidth]{(a)}{figures/Fig10a.pdf}
+%%    \subfigimg[width = 0.45\columnwidth]{(b)}{figures/Fig10b.pdf}
+%  \caption{\label{fig:excessPressure} \small The excess pressure a
+%  stiff single-component (red), floppy single-component (green), and a
+%  multicomponent (blue) vesicle moving through stenosis. The reduced
+%  areas are (a) $\alpha = 0.4$, and (b) $\alpha = 0.6$.}
+%\end{figure}
 
@@
 single-component case, the tangential force is $\mathbf{F}_\tt =
-=\sigma_s$ which is the usual Marangoni effect.
+\sigma_s$ which is the usual Marangoni effect.
 

### 2023-07-11 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

@@
 
-Under a linear shear flow, a multicomponent vesicle exhibits more exotic dynamics in both shape and membrane composition \cite{Sohn2010_JCP, Smith2007_JChemPhys,Cox2015_Nonlinearity,Liu2017_SoftMatter,Gera2018_SoftMatter,Gera2022_JFM} than a single-component vesicle.
+Under a linear shear flow, a multicomponent vesicle exhibits more exotic dynamics in both shape and membrane composition \cite{Sohn2010_JCP, Smith2007_JChemPhys,Cox2015_Nonlinearity,Liu2017_SoftMatter,Tusch2018_PRF,Gera2018_SoftMatter,Gera2022_JFM} than a single-component vesicle.
 For example, multicomponent vesicles under a background flow often exhibit highly complex morphologies, leading to vesicle budding. 

### 2023-07-11 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
small changes

--- 2023-07-10 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
@@
 
-\textcolor{red}{Back of the envelope calculation shows that anything
-with reduced area greater than 0.8 can not pass through the stenosis,
-assuming the vesicle shape is an ellipse}
 We start by considering a vesicle with reduced area $\alpha = 0.6$
 passing through stenosis with a capillary number $Ca = 0.25$.
-Figure~\ref{fig:RA6} shows six time steps of a single-component vesicle
-with bending stiffness (a) $b=1$ and (b) $b=0.55$, and (c) a
-multicomponent vesicle with an initially random distribution of lipids.
+Figure~\ref{fig:RA6} shows six time steps of a (a) stiff
+single-component (b) floppy single-component, and (c) multicomponent
+vesicle. The initial lipid distribution of the multicomponent is random.
 In all plots, the color is the dimensionless bending modulus of the
@@
 new bending modulus~\eqref{eqn:tanhBending}. A single Lagrangian point
-is included to visualize tank-treading behavior. There are slight
+is included to visualize any tank-treading behavior. There are slight
 differences between the three cases, with the most noticeable being that
-the multicomponent vesicle has higher curvature in the floppy region. We
-consider the same setup in Figure~\ref{fig:RA4}, but the vesicle has
-reduced area $\alpha = 0.4$. We first consider the three different
-energies---bending, tension, and phase---for each of the
-single-component and multicomponent vesicles. In
+the multicomponent vesicle has higher curvature in the floppy region.
+However, in general, there is little difference between these cases,
+partially because these vesicles have a large reduced area. With the
+current setup, an elliptical vesicle with reduced area greater than
+$\alpha = 0.8$ cannot fit through the closely-fitting geometry.
+
+\begin{figure*}[h]
+  \centering
+  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp4MCp5.pdf}
+%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig6a.pdf}
+%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig6b.pdf}
+%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig6c.pdf}
+  \caption{\label{fig:RA4} \small A vesicle passing through the stenosis
+  geometry. The vesicle's reduced area is $\alpha = 0.4$ and the
+  capillary number is $Ca = 0.25$. The vesicles are: (a) single-component
+  with bending modulus $b=1$; (b) single-component with bending modulus
+  $b=0.55$; (c) multicomponent.}
+\end{figure*}
+
+To create more significant differences between the three cases, we
+consider the same geometry, but for a vesicle with reduced area $\alpha
+= 0.4$. Figure~\ref{fig:RA4} shows six time steps of a (a) stiff
+single-component, (b) floppy single-component, and (c) multicomponent
+vesicle. We first consider the three different energies---bending,
+tension, and phase---for each of these cases.  In
 Figure~\ref{fig:Energy}, we plot these energies as a function of the
-vesicle's center of mass. As a reminder, the vesicle enters the
-constriction at $x=-15$ and exits at $x=15$. Also note that the
-single-component vesicle does not have a phase energy. A few general
-trends can immediately be seen. First, as the vesicle enters the
-stenosis, there are sharp jumps in both the tension and bending
-energies, as expected. Next, the multicomponent vesicles only coarsen
-when the vesicle is not in the stenosis. Finally, when coarsening does
-occur, there are rapid changes in the tension energy.
+vesicle's center. As a reminder, the vesicle enters the constriction at
+$x=-15$ and exits at $x=15$. Also note that the single-component
+vesicles do not have a phase energy. A few general trends can
+immediately be seen. First, as the vesicle enters the stenosis, there
+are sharp jumps in both the tension and bending energies, as expected.
+Next, the multicomponent vesicles only coarsen when the vesicle is not
+in the stenosis. Finally, when coarsening does occur, there are rapid
+changes in the tension energy.
 
@@
     \centering
-%    \subfigimg[width = \columnwidth, trim = {1cm 20cm 1cm 3cm}, clip]{(a)}{figures/RAp4BkgrdFlow.pdf}
     \subfigimg[width=\textwidth]{(a)}{figures/Fig13a.pdf}
@@
 tank-treading velocity is not observed
-
-%\begin{comment}
-%\begin{figure}[h]
-\begin{figure*}[h]
-  \centering
-  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp4MCp5.pdf}
-%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig6a.pdf}
-%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig6b.pdf}
-%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig6c.pdf}
-  \caption{\label{fig:RA4} \small A vesicle passing through the stenosis
-  geometry. The vesicle's reduced area is $\alpha = 0.4$ and the
-  capillary number is $Ca = 0.25$. The vesicles are: (a) single-component
-  with bending modulus $b=1$; (b) single-component with bending modulus
-  $b=0.55$; (c) multicomponent.}
-%  The multicomponent vesicle travels
-%  slightly faster, so it leaves the stenosed region earlier than the
-%  single-component cases (see Figure~\ref{fig:vesVelocity}).}
-%\end{figure}
-\end{figure*}
-%\end{comment}
 

### 2023-07-11 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
worked on stenosis example

@@
 
+%\begin{figure}[h]
+\begin{figure*}[h]
+  \centering
+  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp6MCp5.pdf}
+%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig5a.pdf}
+%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig5b.pdf}
+%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig5c.pdf}
+  \caption{\label{fig:RA6} \small A vesicle passing through the stenosis
+  geometry. The vesicle's reduced area is $\alpha = 0.6$ and the
+  capillary number is $Ca = 0.25$. The vesicles are: (a)
+  single-component with bending modulus $b=1$; (b) single-component with
+  bending modulus $b=0.55$; (c) multicomponent.}
+%\end{figure}
+\end{figure*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%\begin{comment}
-%\begin{figure}[h]
-\begin{figure*}[h]
-  \centering
-  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp6MCp5.pdf}
-%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig5a.pdf}
-%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig5b.pdf}
-%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig5c.pdf}
-  \caption{\label{fig:RA6} \small A vesicle passing through the stenosis
-  geometry. The vesicle's reduced area is $\alpha = 0.6$ and the
-  capillary number is $Ca = 0.25$. The vesicles are: (a)
-  single-component with bending modulus $b=1$; (b) single-component with
-  bending modulus $b=0.55$; (c) multicomponent.}
-%\end{figure}
-\end{figure*}
-%\end{comment}
-
 We start by considering a vesicle with reduced area $\alpha = 0.6$
@@
 
+\begin{figure*}[h]
+  \centering
+  \subfigimg[width=0.3\linewidth]{(a)}{figures/SC_energy.pdf}
+  \subfigimg[width=0.3\linewidth]{(b)}{figures/SCp55_energy.pdf}
+  \subfigimg[width=0.3\linewidth]{(c)}{figures/MCp5_energy.pdf}
+  \caption{\label{fig:Energy} \small The Bending (blue), tension (red),
+  and phase (green) energies for a (a) stiff single-component, (b)
+  floppy single-component, and (c) multicomponent vesicle. The reduced
+  area is $\alpha = 0.4$. Note that the single-component vesicles do not
+  have a phase energy.} 
+\end{figure*}
+
 To create more significant differences between the three cases, we
@@
 vesicles do not have a phase energy. A few general trends can
-immediately be seen. First, as the vesicle enters the stenosis, there
-are sharp jumps in both the tension and bending energies, as expected.
-Next, the multicomponent vesicles only coarsen when the vesicle is not
-in the stenosis. Finally, when coarsening does occur, there are rapid
-changes in the tension energy.
-
-\begin{figure}
-  \begin{minipage}{0.49\columnwidth}
-    \centering
-    \subfigimg[width=\textwidth]{(a)}{figures/Fig13a.pdf}
-    \subfigimg[width=\textwidth]{(c)}{figures/Fig13c.pdf}
-    \subfigimg[width=\textwidth]{(e)}{figures/Fig13e.pdf}
-  \end{minipage}
-  \hfill
-  \begin{minipage}{0.49\columnwidth}
-    \centering
-    \subfigimg[width=\textwidth]{(b)}{figures/Fig13b.pdf}
-    \subfigimg[width=\textwidth]{(d)}{figures/Fig13d.pdf}
-    \subfigimg[width=\textwidth]{(f)}{figures/Fig13f.pdf}
-  \end{minipage}
-  \caption{\label{fig:Energy} \small The Bending (blue), tension
-  (yellow), and phase (red) energies for a (a/b) single-component
-  vesicle with $b=1$, (c/d) single-component vesicle with $b = 0.55$,
-  and (e/f) multicomponent vesicle. The reduced areas are $\alpha = 0.4$
-  (a/c/e) and $\alpha = 0.6$ (b/d/f).}
-  \todo[inline]{need to redo these plots}
-\end{figure}
+immediately be seen. First, as the vesicle enters the stenosis, it
+develops regions of high curvature, and this results in an increase in
+the bending energy. Also, since the stiff single-component vesicle
+reaches a steady-state shape earlier, its tension and bending energies
+remain nearly constant from $x=0$ until the end of the stenosis.
+Regarding the multicomponent vesicle, the phase energy has sudden
+decreases that correspond to the lipid phase coarsening. Note that this
+coarsening only occurs when the vesicle is not in the stenosis. Finally,
+when coarsening does occur, this results in a sudden change in the
+bending and tension energies, but these energies almost instantly return
+to their previous values once coarsening is complete.
+
+%\begin{figure}
+%  \begin{minipage}{0.49\columnwidth}
+%    \centering
+%    \subfigimg[width=\textwidth]{(a)}{figures/Fig13a.pdf}
+%    \subfigimg[width=\textwidth]{(c)}{figures/Fig13c.pdf}
+%    \subfigimg[width=\textwidth]{(e)}{figures/Fig13e.pdf}
+%  \end{minipage}
+%  \hfill
+%  \begin{minipage}{0.49\columnwidth}
+%    \centering
+%    \subfigimg[width=\textwidth]{(b)}{figures/Fig13b.pdf}
+%    \subfigimg[width=\textwidth]{(d)}{figures/Fig13d.pdf}
+%    \subfigimg[width=\textwidth]{(f)}{figures/Fig13f.pdf}
+%  \end{minipage}
+%  \caption{\label{fig:Energy} \small The Bending (blue), tension
+%  (yellow), and phase (red) energies for a (a/b) single-component
+%  vesicle with $b=1$, (c/d) single-component vesicle with $b = 0.55$,
+%  and (e/f) multicomponent vesicle. The reduced areas are $\alpha = 0.4$
+%  (a/c/e) and $\alpha = 0.6$ (b/d/f).}
+%  \todo[inline]{need to redo these plots}
+%\end{figure}
 
@@
 earlier, tank treading occurs when the top and bottom lubrication layers
-differ in size. The size of the lubrication layers in all six cases are
-in Figure~\ref{fig:lubrication}. The tank-treading velocities of the
-examples with reduced area $\alpha = 0.4$ are in
-Figure~\ref{fig:tankTreadRAp4}. The vesicle shapes at the dashed black
-lines are also included, and the four marker points are the Lagrangian
-points where the tangential velocities are computed. For reduced area
-$\alpha = 0.4$, the single-component ($b=1$) and multicomponent vesicles
-are clearly tank treading. Since the single-component case has a larger
-difference between its top and bottom boundary layers (see
-Figure~\ref{fig:lubrication}), it tank treads faster than the
-multicomponent case. In addition, since the top boundary layer is larger
-in both cases, they both tank-tread in the same
-direction---counterclockwise. In contrast, the single-component vesicle
-with $b=0.55$ tank-treads in the clockwise direction; note, however,
-that this example is still undergoing some deformations, so a constant
-tank-treading velocity is not observed. When $\alpha = 0.6$, the vesicle
-undergoes deformations while in the stenosis, and a constant
-tank-treading velocity is not observed
+differ in size. The size of the lubrication layers for all three cases
+of the vesicle with reduced area $\alpha = 0.4$ are in the top half of
+Figure~\ref{fig:lubricationComposite}. Also included in the bottom of
+Figure~\ref{fig:lubricationComposite} are the tank-treading velocities.
+The four marker points are the Lagrangian points where the tank-treading
+velocities are computed, the black dashed line is the center line of the
+channel, and the rounded arrow denotes the direction of rotation. The
+stiff single-component and multicomponent vesicles are clearly tank
+treading. Since the single-component case has a larger difference
+between its top and bottom boundary layers, it tank treads faster than
+the multicomponent case. In addition, since the top boundary layer is
+larger in both cases, they both tank-tread in the same
+direction---counterclockwise. In contrast, the floppy single-component
+vesicle tank treads in the clockwise direction; note, however, that this
+example is still undergoing some deformations, so a constant
+tank-treading velocity is not observed.
+%When $\alpha = 0.6$, the vesicle undergoes deformations while in the
+%stenosis, and a constant tank-treading velocity is not observed
 
@@
   0cm,clip=true]{}{figures/TankTreadingFigs_composite_MCp5.pdf}
-  \caption{\label{fig:tankTreadRAp4} \small The lubrication layer
+  \caption{\label{fig:lubricationComposite} \small The lubrication layer
   thicknesses (red and blue), excess pressure (green), and tank treading
@@
 The size of the top and bottom lubrication layers are also related to
-the excess pressure (Figure~\ref{fig:excessPressure}). If the
-lubrication layers are large, most notably for the multicomponent
-vesicle with reduced area $\alpha = 0.4$, then less pressure is required
-to force the vesicle through the geometry, and we expect a smaller (less
-negative) excess pressure. In contrast, if the lubrication layers are
-small, most notably for the single-component vesicle with $b=1$ and
-reduced area $\alpha = 0.4$, then more pressure is required to force the
-vesicle through the geometry, and we expect a larger (more negative)
+the excess pressure. The green curve on the top half of
+Figure~\ref{fig:lubricationComposite} shows the excess pressure with the
+axis aligned on the right side of the plot. When the lubrication layers
+are large, most notably for the multicomponent vesicle, less pressure is
+required to force the vesicle through the geometry, and the result is a
+smaller (less negative) excess pressure. In contrast, when the
+lubrication layers are small, most notably for the stiff
+single-component vesicle, more pressure is required to force the vesicle
+through the geometry, and we the result is a larger (more negative)
 excess pressure.
@@
 
-While the size of the lubrication layers affect the tank-treading
-behavior and the excess pressure, it has almost no effect on the
-migration speed of the vesicle. 
-%In Figure~\ref{fig:vesVelocity}, we plot
-%the average velocity of the vesicle as it passes through the stenosed
-%region.
-With the exception of the single-component vesicle with $b=1$ and
-$\alpha = 0.6$, which has an average vesicle speed about 5\% slower, the
-average vesicle speed is constant. Obviously, this average velocity
-would be affected by the capillary number.
+%While the size of the lubrication layers affect the tank-treading
+%behavior and the excess pressure, it has almost no effect on the
+%migration speed of the vesicle. 
+%%In Figure~\ref{fig:vesVelocity}, we plot
+%%the average velocity of the vesicle as it passes through the stenosed
+%%region.
+%With the exception of the single-component vesicle with $b=1$ and
+%$\alpha = 0.6$, which has an average vesicle speed about 5\% slower, the
+%average vesicle speed is constant. Obviously, this average velocity
+%would be affected by the capillary number.
 
@@
 
+\todo[inline]{Bryan is here}
 When a vesicle is tank-treading near a solid wall, the flow in the thin

### 2023-07-13 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

@@
 vesicle's reduced area and viscosity contrast will determine if it
+
 undergoes tank treading, swinging, or tumbling in a shear

### 2023-07-17 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
worked on discussion for energy plots (Fig 6)

@@
 10^{-19}$~J, and fluid viscosity $\mu = 5 \times 10^{-2}$~kg/ms. The
-resulting time scale is $\mu R_0^3/b_{\max} = 0.5$~s, the velocity scale
-is $b_{\max}/\mu R_0^2=2$~$\mu$m/s, the pressure scale is
-$b_{\max}/R_0^3 = 10^{-1}$~Pa, and the tension scale is $b_{\max}/R_0^2
-= 10^{-7}$~N/m. The dimensionless parameters regarding the vesicle
-properties are the reduced area $\alpha = 4\pi A/L^2$, where $A$ and $L$
-are the vesicle's area and length, respectively, and the
+resulting bending relaxation time scale is $\mu R_0^3/b_{\max} = 0.5$~s,
+the velocity scale is $b_{\max}/\mu R_0^2=2$~$\mu$m/s, the pressure
+scale is $b_{\max}/R_0^3 = 10^{-1}$~Pa, and the tension scale is
+$b_{\max}/R_0^2 = 10^{-7}$~N/m. The dimensionless parameters regarding
+the vesicle properties are the reduced area $\alpha = 4\pi A/L^2$, where
+$A$ and $L$ are the vesicle's area and length, respectively, and the
 floppy-to-stiffness ratio $\beta = b_{\min}/b_{\max}$. Since we consider
@@
 sets the capillary number $Ca = U R_{0}^{2} \mu/b_{\max}$, and $W/R_0$
-is the dimensionless width of the channel at the inlet and outlet. From
-this point onwards, all equations are dimenisionless.
+is the dimensionless width of the channel at the inlet and outlet.
+Finally, the Peclet number of the lipid dynamics is taken to be $Pe = 1$
+which results in a diffusion time scale of $2 \times 10^{-4}$~s.
+Therefore, phase separation occurs at a rate three orders of magnitude
+faster than vesicle relaxation. The effect of the Peclet number has been
+examined~\cite{liu-mar-li-vee-low2017, soh-tse-li-voi-low2010}, and it
+has no qualitative effect on the vesicle dynamics. From this point
+onwards, all equations are dimensionless.
 
@@
 $u$, and the parameter $a$ is line tension scaled by the characteristic
-bending stiffness. Both $\epsilon$ and $a$ are kept constant in all
-simulations. The resulting membrane forces are
+bending stiffness. All simulations use the parameter values
+$\epsilon=100$ and $a=0.04$. The resulting membrane forces are
 \begin{align}
@@
 develops regions of high curvature, and this results in an increase in
-the bending energy. Also, since the stiff single-component vesicle
-reaches a steady-state shape earlier, its tension and bending energies
-remain nearly constant from $x=0$ until the end of the stenosis.
-Regarding the multicomponent vesicle, the phase energy has sudden
-decreases that correspond to the lipid phase coarsening. Note that this
-coarsening only occurs when the vesicle is not in the stenosis. Finally,
-when coarsening does occur, this results in a sudden change in the
-bending and tension energies, but these energies almost instantly return
-to their previous values once coarsening is complete.
+the bending energy. Also, since the stiff single-component and
+multicomponent vesicles reach a steady-state shape near the middle of
+the channel, their bending, tension, and phase energies remain nearly
+constant from $x=0$ until the end of the stenosis.
+
+The presence of the multiple lipid species in the multicomponent vesicle
+results in interesting additional physics. The lipid species coarsens at
+three instances, and this results in a decrease in the phase energy.
+Note, however, that no coarsening occurs when the vesicle is in the
+closely-fitting part of the domain. Each coarsening corresponds to
+two stiff regions overtaking a small floppy region, or two floppy
+regions overtaking a small stiff region. In the first case, a region
+that was originally floppy has suddenly become stiff, and this results
+in a sudden increase in the bending energy. In the latter case, because
+of lipid conservation, the overtaken stiff region must relocate to the
+another stiff-floppy interface, and this also results in a sudden
+increase in the bending energy. These increases are visible in
+Figure~\ref{fig:Energy}(c) as small upticks in the blue curve. However,
+in both cases, the vesicle smooths out these new regions of high
+curvature, but it takes some time since the diffusion time scale is
+several orders of magnitude smaller than the bending relaxation time
+scale.
 

### 2023-07-20 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
Update multicomponent_vesicles.tex
very minor changes

@@
 vesicle in an unconfined shear flow. These simulations align with the
-results reported by~\citet{liu-mar-li-vee-low2017} (cf.~Figures 3 and
-4).
+results reported by~\citet{liu-mar-li-vee-low2017} (cf.~Figure 3).
 \begin{figure}[H]
@@
 
-A difference between the size of the top and lubrication layers
-indicates that the vesicle is off-centered from the center of the
+A difference between the size of the top and bottom lubrication layers
+indicates that the vesicle %is off-centered 
+has deviated from the center of the
 channel, and this results in tank-treading behavior~\cite{aga-bir2020}.
@@
 For the single-component case, we consider two bending stiffnesses:
-$b(u) = 1$ and $b(u) = 0.55$ which is the average bending stiffness of a
-multicomponent vesicle whose stiff and floppy regions have the same
-area. Throughout this section we plot the position of the vesicle in
-terms of the $x$-coordinate of its center of mass. For the stenosed
+$b(u) = 1$ and $b(u) = 0.55$. % which is the average bending stiffness of a multicomponent vesicle whose stiff and floppy regions have the same area. 
+The latter value represents the average bending stiffness of a multicomponent vesicle, where the stiff and floppy regions have the same area.
+Throughout this section we plot the position of the vesicle in terms of the $x$-coordinate of its center of mass.
+For the stenosed
 geometry in Section~\ref{subsec:Stenosis}, the narrow region begins at
@@
 single-component (b) floppy single-component, and (c) multicomponent
-vesicle. The initial lipid distribution of the multicomponent is random.
+vesicle. The initial lipid distribution of the multicomponent vesicle is random.
 In all plots, the color is the dimensionless bending modulus of the

### 2023-07-28 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
fixed a figure a cleaned up a bit of text

@@
 \section{\label{sec:Formulation}Formulation}
-%\todo[inline]{Changes to be made to Figure~\ref{fig:schematic}.}
-%\begin{itemize}
-%  \item Remove labels $\Gamma$, $\Omega$, $\gamma$
-%  \item Line on vesicle is too thick and change color scheme to same as
-%    Fig 2
-%  \item Change to a confined geometry that we use (stenosis)
-%  \item Show a couple of vesicle shapes and the parabolic profile at
-%    the inlet, outlet, and in the middle
-%\end{itemize}
 \begin{figure}[H]
   \centering
-%  \includegraphics[trim = 0.3cm 0cm 1cm 0cm, clip=true,width=0.9\columnwidth]{figures/schematic.pdf}
   \includegraphics[width=0.9\columnwidth]{figures/schematic.pdf}
-  \caption{\label{fig:schematic}\small A single multicomponent vesicle
+  \caption{\label{fig:schematic}\small A multicomponent vesicle
   suspended in a strongly-confined stenosis. The color is the
@@
   of phase, bending, and tension energies, and an imposed flow (blue
-  arrows).}
+  arrows). The lubrication layer (gray region), defined in
+  Section~\ref{sec:LL} also plays a key role in the vesicle dynamics.}
 %  \caption{\label{fig:schematic}\small A single multicomponent vesicle
@@
 %where $\Gamma_{\mathrm{top}}$ is the top portion of $\Gamma$.
-We then find all local minimums of $d(\xx,\Gamma_\mathrm{top})$, with
+We find all local minimums of $d(\xx,\Gamma_\mathrm{top})$, with
 the condition that $d(\xx,\Gamma_\mathrm{top}) < \delta$, where $\delta$
@@
 \end{align}
-%The width of the bottom lubrication layer, $w_\mathrm{bot}$ is
-%calculated by replacing $\Gamma_\mathrm{top}$ with
-%$\Gamma_\mathrm{bot}$.
+The region that defines the top and bottom lubrication layers is
+illustrated in Figure~\ref{fig:schematic}, and the height of the gray
+regions denote the lubrication layer thickness. In this example, the top
+layer is broken across three different regions.
 
@@
 A difference between the size of the top and bottom lubrication layers
-indicates that the vesicle %is off-centered 
-has deviated from the center of the
-channel, and this results in tank-treading behavior~\cite{aga-bir2020}.
-To determine if a vesicle is tank-treading, we calculate the tangential
+indicates that the vesicle  has deviated from the center of the channel,
+and this results in tank-treading behavior~\cite{aga-bir2020}.  To
+determine if a vesicle is tank-treading, we calculate the tangential
 velocity at several points on $\gamma$, and if this value is constant,
@@
 Note, however, that no coarsening occurs when the vesicle is in the
-closely-fitting part of the domain. Each coarsening corresponds to
-two stiff regions overtaking a small floppy region, or two floppy
+closely-fitting part of the domain. Each coarsening corresponds either
+to two stiff regions overtaking a small floppy region, or to two floppy
 regions overtaking a small stiff region. In the first case, a region
@@
 
-\todo[inline]{Bryan is here}
 When a vesicle is tank-treading near a solid wall, the flow in the thin
@@
 \end{align}
-where
+switches sign. Here,
 \begin{align}
@@
 single-component case, the tangential force is $\mathbf{F}_\tt =
-\sigma_s$ which is the usual Marangoni effect.
+-\sigma_s$ which is the usual Marangoni effect.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\todo[inline]{Bryan is here}
 \subsection{\label{subsec:Contraction} A multicomponent vesicle in the

### 2023-07-29 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
started to work on contracting discussion

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\todo[inline]{Bryan is here}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{\label{subsec:Contraction} A multicomponent vesicle in the
@@
 front and floppy in the back. The vesicle with the random initial lipid
-distribution phase separates so that the floppy region is in the back
-and the stiff region is in the front. The vesicle where the initial
-lipid species distribution was fully phase separated and the floppy
-region was on the front of the vesicle began to reorient the floppy
-region to the back of the vesicle, making it partway after passing
-through the contraction. In the case where the initial lipid species
-distribution was fully phase separated and the floppy region was on the
-back of the vesicle, the floppy region remained on the back of the
-vesicle. In all cases, the floppy regions were being oriented to cover
-the regions of the vesicle with the highest curvature to minimize the
-overall bending energy. Since we can see in
-Figure~\ref{fig:RA6leftRightRand} that the regions of high curvature are
-located in the back of the vesicle, we expect the overall bending
-energies to be lowest for the randomly distributed case and the fully
-separated floppy region on the back case. We observe this in
-Figure~\ref{fig:RAp6leftRightRandBending} Therefore, in all subsequent
+distribution quickly phase separates into a two floppy and two stiff
+regions. As seen in the stenosis geometry, further phase separation is
+delayed until the vesicle is no longer under strong confinement. The
+vesicle where the initial lipid species distribution is fully phase
+separated with the floppy region on the front of the vesicle begins to
+reorient the floppy region to the back of the vesicle. In contrast, the
+fully phase separated case with the stiff region at the front maintains
+its orientation. In summary, in all three cases, the vesicle is
+orienting itself so that the stiff region passes through the
+constriction before the floppy region. Therefore, in all subsequent
 examples, we start with symmetric vesicle whose floppy region is in the
-back and its stiff region is in the front.
+back and its stiff region is in the front. The vesicle shapes develop
+regions with high curvature in the floppy region when they first pass
+through the narrowest part of the geometry, but because the strong
+confinement is abruptly removed immediately afterwards, these regions of
+high curvature are quickly smoothed. 
+%Since we can see in Figure~\ref{fig:RA6leftRightRand} that the regions
+%of high curvature are located in the back of the vesicle, we expect the
+%overall bending energies to be lowest for the randomly distributed case
+%and the fully separated floppy region on the back case. We observe this
+%in Figure~\ref{fig:RAp6leftRightRandBending}.
 
@@
   contraction before the floppy region.}
-%  The vesicles are: (a) the initial
-%  lipid-species distribution is fully separated on the right side of the
-%  vesicle; (b) the initial lipid-species distribution is randomly
-%  distributed (not fully separated) on the vesicle membrane; (d) the
-%  initial lipid-species distribution is fully separated on the left side
-%  of the vesicle. The vesicles with a larger percentage of floppy
-%  regions pass through the neck earlier than the vesicles with less
-%  percentage of floppy regions. The vesicle either completely or
-%  partially reorients itself so that the floppy region is in the back
-%  and the stiff region is in the front.}
 \end{figure}
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=\columnwidth]{figures/bending_leftRightRand.pdf}
-  \caption{\label{fig:RAp6leftRightRandBending} The bending energy of a
-  multicomponent vesicle that is 50\% stiff with an initial phase
-  separation to the left (blue), to the right (red), randomly
-  distributed (yellow). The vesicle exits the contraction $x \approx
-  15$.} 
-\end{figure}
-
-In Figure~\ref{fig:RA5}, we consider a vesicle with reduced area $\alpha
-= 0.5$ and the capillary number is $Ca = 0.25$. We start with a
-single-component vesicle and then increase the percentage of the vesicle
-membrane that is floppy. By comparing the vesicle location at the time
-step just before the vesicle passes through the constriction, we can
-immediately see that vesicles with membranes that have larger percentage
-of floppy regions reach and pass through the neck earlier. The
-dimensionless times that the entire vesicle first passes through the
-neck are reported in Table~\ref{tbl:contractingTimes}.
+%\begin{figure}[H]
+%  \centering
+%  \includegraphics[width=\columnwidth]{figures/bending_leftRightRand.pdf}
+%  \caption{\label{fig:RAp6leftRightRandBending} The bending energy of a
+%  multicomponent vesicle that is 50\% stiff with an initial phase
+%  separation to the left (blue), to the right (red), randomly
+%  distributed (yellow). The vesicle exits the contraction $x \approx
+%  15$.} 
+%\end{figure}
+
+In addition to the lipid distribution, the percentage of the vesicle
+that is floppy plays a role in the vesicle dynamics. Therefore, we
+consider a vesicle with reduced area $\alpha = 0.5$ in a contracting
+geometry with various sizes of the floppy region. Motivated by the last
+experiment, we initialize the lipid distribution so that the front is
+stiff and the back is floppy. In each simulation, the capillary number
+is $Ca = 0.25$. Figure~\ref{fig:RA5} shows the vesicle shapes as they
+pass through the narrow constriction when the percentage of the floppy
+region is 0\% (single-component), \%15, \%25, \%35, and \%45. One effect
+of the size of the floppy region is that the symmetry of the vesicle
+shape is broken at smaller percentages. We also see that stiffer
+vesicles have faster migration speeds, but the effect is quite small. In
+Table~\ref{tbl:contractingTimes}, we report the time the vesicle first
+passes through the neck.
+%In Figure~\ref{fig:RA5}, we consider a vesicle with reduced area
+%$\alpha = 0.5$ and the capillary number is $Ca = 0.25$. We start with a
+%single-component vesicle and then increase the percentage of the
+%vesicle membrane that is floppy. By comparing the vesicle location at
+%the time step just before the vesicle passes through the constriction,
+%we can immediately see that vesicles with membranes that have larger
+%percentage of floppy regions reach and pass through the neck earlier.
+%The dimensionless times that the entire vesicle first passes through
+%the neck are reported in Table~\ref{tbl:contractingTimes}.
 
@@
   contracting geometry. The vesicle's reduced area is $\alpha = 0.5$ and
-  the dimensionless maximum velocity is $Ca = 0.25$. The vesicles are:
-  (a) single-component with bending modulus $b=1$; (b) multicomponent
+  the Capillary number is $Ca = 0.25$. The vesicles are: (a)
+  single-component with bending modulus $b=b_{\max}$; (b) multicomponent
   with 15\% floppy region; (c) multicomponent with 25\% floppy region;
@@
   \centering
-    \begin{tabular}{l|c}
-       & Time to pass through neck\\
+  \begin{tabular}{l|ccccc}
     \hline
-       Single-component &  2.32 \\ %2.3173\\
-       15\% Multicomponent & 2.30 \\%2.2960\\
-       25\% Multicomponent & 2.29 \\%2.2868\\
-       35\% Multicomponent & 2.26 \\%2.2637\\
-       45\% Multicomponent & 2.24 \\%2.2388\\
+    Floppy percentage & 0\% & 15\% & 25\% & 35\% & 45\% \\ 
+    Time  & 2.32 & 2.30 & 2.29 & 2.26 & 2.24 \\
     \hline
   \end{tabular}
-    \caption{\label{tbl:contractingTimes} The time required for the vesicles to completely pass through the neck located at $x=15$. The vesicles initial center is at $x=5$.}
+  \caption{\label{tbl:contractingTimes} The time required for the
+  vesicles to completely pass through the neck.}
 \end{table}
+%\begin{table}[H]
+%  \centering
+%  \begin{tabular}{l|c}
+%    Floppy percentage & Time to pass through neck \\
+%    \hline
+%    0\% &  2.32 \\
+%    15\% & 2.30 \\
+%    25\% & 2.29 \\
+%    35\% & 2.26 \\
+%    45\% & 2.24 \\
+%%    Single-component &  2.32 \\ %2.3173\\
+%%    15\% Multicomponent & 2.30 \\%2.2960\\
+%%    25\% Multicomponent & 2.29 \\%2.2868\\
+%%    35\% Multicomponent & 2.26 \\%2.2637\\
+%%    45\% Multicomponent & 2.24 \\%2.2388\\
+%    \hline
+%  \end{tabular}
+%  \caption{\label{tbl:contractingTimes} The time required for the
+%  vesicles to completely pass through the neck.}
+%\end{table}
 
@@
   \includegraphics[width=\columnwidth]{figures/bendingAllContracting.pdf}
-    \caption{\small The bending energy for a single-component vesicle (blue) and and a multicomponent vesicle (red)--(green) with $\alpha = 0.5$.
-As the size of the floppy region increases, the maximum bending energy decreases.}
-    \label{fig:bendingAll}
+  \caption{\label{fig:bendingAll} \small The bending energy for a
+  single-component vesicle (blue) and a multicomponent vesicle
+  (red)--(green) with $\alpha = 0.5$. As the size of the floppy region
+  increases, the maximum bending energy decreases.}
 \end{figure}
 
-We conclude this example by considering the different shapes that single-component and multicomponent shapes display.
-Since we have initialized the lipid species to initially be phase separated, the phase energy is more or less constant for all cases.
-The tension energy, on the other hand, increases as the vesicle approaches the neck, but its general shape is similar for the five cases considered in Figure~\ref{fig:RA5}.
-However, the bending energies are show different behaviors for each of the cases (Figure~\ref{fig:bendingAll}).
-The main difference between the cases is the that multicomponent vesicles with a higher percentage of floppy regions have less bending energy, especially as the vesicle passes through the neck.
-We also note that the bending energy undergoes several transient increases and decreases.
-These occur when the tail of the vesicle undergoes transitions from lower energy shapes, such as a `C' or `S' shapes, to high energy shapes, such as 'W' shapes.
-Figure~\ref{fig:bendingSC_contracting} show these different vesicle shapes for the single-component vesicle and multicomponent vesicle that is 45\% floppy.
-The shape at several critical points along the bending energy are included, and we can indeed see that transitioning vesicle shape between these different states.
+\todo[inline]{Bryan is here}
+We conclude this example by considering the different shapes that
+single-component and multicomponent shapes display. Since we have
+initialized the lipid species to initially be phase separated, the phase
+energy is more or less constant for all cases. The tension energy, on
+the other hand, increases as the vesicle approaches the neck, but its
+general shape is similar for the five cases considered in
+Figure~\ref{fig:RA5}. However, the bending energies are show different
+behaviors for each of the cases (Figure~\ref{fig:bendingAll}). The main
+difference between the cases is the that multicomponent vesicles with a
+higher percentage of floppy regions have less bending energy, especially
+as the vesicle passes through the neck. We also note that the bending
+energy undergoes several transient increases and decreases. These occur
+when the tail of the vesicle undergoes transitions from lower energy
+shapes, such as a `C' or `S' shapes, to high energy shapes, such as 'W'
+shapes. Figure~\ref{fig:bendingSC_contracting} show these different
+vesicle shapes for the single-component vesicle and multicomponent
+vesicle that is 45\% floppy. The shape at several critical points along
+the bending energy are included, and we can indeed see that
+transitioning vesicle shape between these different states.
 

### 2023-07-31 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
worked on last couple figures and contracting section

@@
 floppy and stiff regions each make up half of the vesicle membrane. In
-Figure~\ref{fig:RA6leftRightRand}, we consider a vesicle with $\alpha =
-0.6$ with an initially random initial lipid concentration, one that is
-floppy in the front and stiff in the back, and one that is stiff in the
-front and floppy in the back. The vesicle with the random initial lipid
-distribution quickly phase separates into a two floppy and two stiff
+Figure~\ref{fig:RA6leftRightRand}, snapshots of vesicles with reduced
+area $\alpha = 0.6$ with different initial lipid distributions are
+illustrated. The initial distributions are random (middle) floppy in the
+front and stiff in the back (top), and one that is stiff in the front
+and floppy in the back (bottom). The vesicle with the random initial
+lipid distribution quickly phase separates into two floppy and two stiff
 regions. As seen in the stenosis geometry, further phase separation is
 delayed until the vesicle is no longer under strong confinement. The
-vesicle where the initial lipid species distribution is fully phase
-separated with the floppy region on the front of the vesicle begins to
-reorient the floppy region to the back of the vesicle. In contrast, the
-fully phase separated case with the stiff region at the front maintains
-its orientation. In summary, in all three cases, the vesicle is
-orienting itself so that the stiff region passes through the
-constriction before the floppy region. Therefore, in all subsequent
-examples, we start with symmetric vesicle whose floppy region is in the
-back and its stiff region is in the front. The vesicle shapes develop
-regions with high curvature in the floppy region when they first pass
-through the narrowest part of the geometry, but because the strong
-confinement is abruptly removed immediately afterwards, these regions of
-high curvature are quickly smoothed. 
+vesicle with the floppy region on the front reorients the floppy region
+towards the back of the vesicle. In contrast, the vesicle with the stiff
+region at the front maintains its orientation. In summary, in all three
+cases, the vesicle is orienting itself so that the stiff region passes
+through the constriction before the floppy region.  Therefore, in
+subsequent simulations, we initialize the vesicle's lipid concentration
+so that the floppy region is in the back and its stiff region is in the
+front. The vesicle shapes develop regions with high curvature in the
+floppy region when they first pass through the narrowest part of the
+geometry, but because the strong confinement is abruptly removed
+immediately afterwards, these regions of high curvature are quickly
+smoothed. 
 %Since we can see in Figure~\ref{fig:RA6leftRightRand} that the regions
@@
   separated in the top and bottom rows, and the middle row has a random
-  initial lipid distribution. The preferred orientation of the lipid
-  concentration is to have the stiff region to pass through the
-  contraction before the floppy region.}
+  initial lipid distribution. The preferred lipid distribution has the
+  stiff region passing through the contraction before the floppy
+  region.}
 \end{figure}
@@
 In addition to the lipid distribution, the percentage of the vesicle
-that is floppy plays a role in the vesicle dynamics. Therefore, we
-consider a vesicle with reduced area $\alpha = 0.5$ in a contracting
-geometry with various sizes of the floppy region. Motivated by the last
-experiment, we initialize the lipid distribution so that the front is
-stiff and the back is floppy. In each simulation, the capillary number
-is $Ca = 0.25$. Figure~\ref{fig:RA5} shows the vesicle shapes as they
-pass through the narrow constriction when the percentage of the floppy
+that is floppy plays a role in the vesicle shapes and dynamics.
+Therefore, we consider a vesicle with reduced area $\alpha = 0.5$ in the
+contracting geometry with various sizes of the floppy region. Motivated
+by the last experiment, we initialize the stiff region to be in the
+front and the floppy region to be in the back. In each simulation, the
+capillary number is $Ca = 0.25$. Figure~\ref{fig:RA5} shows the vesicle
+shapes at the same six time steps when the percentage of the floppy
 region is 0\% (single-component), \%15, \%25, \%35, and \%45. One effect
@@
 shape is broken at smaller percentages. We also see that stiffer
-vesicles have faster migration speeds, but the effect is quite small. In
-Table~\ref{tbl:contractingTimes}, we report the time the vesicle first
-passes through the neck.
+vesicles have faster migration speeds, but the effect is quite
+small---Table~\ref{tbl:contractingTimes} reports the time the vesicle
+first passes through the neck.
 %In Figure~\ref{fig:RA5}, we consider a vesicle with reduced area
@@
   \centering
-  \includegraphics[width=\columnwidth]{figures/bendingAllContracting.pdf}
+  \includegraphics[width=\columnwidth]{figures/bendingContracting.pdf}
+%  \includegraphics[width=\columnwidth]{figures/bendingAllContracting.pdf}
   \caption{\label{fig:bendingAll} \small The bending energy for a
@@
 initialized the lipid species to initially be phase separated, the phase
-energy is more or less constant for all cases. The tension energy, on
-the other hand, increases as the vesicle approaches the neck, but its
-general shape is similar for the five cases considered in
-Figure~\ref{fig:RA5}. However, the bending energies are show different
-behaviors for each of the cases (Figure~\ref{fig:bendingAll}). The main
-difference between the cases is the that multicomponent vesicles with a
-higher percentage of floppy regions have less bending energy, especially
-as the vesicle passes through the neck. We also note that the bending
-energy undergoes several transient increases and decreases. These occur
-when the tail of the vesicle undergoes transitions from lower energy
-shapes, such as a `C' or `S' shapes, to high energy shapes, such as 'W'
-shapes. Figure~\ref{fig:bendingSC_contracting} show these different
-vesicle shapes for the single-component vesicle and multicomponent
-vesicle that is 45\% floppy. The shape at several critical points along
-the bending energy are included, and we can indeed see that
-transitioning vesicle shape between these different states.
+energy is nearly constant for all cases, and is therefore not plotted.
+The tension energy, on the other hand, increases as the vesicle
+approaches the neck, but its general shape is similar for all five
+cases, and it too is not plotted. However, the bending energies show
+different behaviors for each of the cases (Figure~\ref{fig:bendingAll}).
+The main difference being that the multicomponent vesicles with a higher
+percentage of floppy regions have less bending energy, especially as the
+vesicle passes through the neck. We also note that the bending energy
+undergoes several transient increases and decreases. These occur when
+the tail of the vesicle undergoes transitions from lower energy shapes,
+such as `C' or `S' shapes, to high energy shapes, such as 'W' shapes.
+Figure~\ref{fig:bendingSC_contracting} shows these different vesicle
+shapes for the single-component vesicle and multicomponent vesicle that
+is 45\% floppy. The shapes at several critical points along the bending
+energy are included, and we can indeed see that transitioning vesicle
+shape between these different states.
 
@@
 %    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
-    \subfigimg[width=\columnwidth]{(a)}{figures/bendingSC.pdf}
-    \subfigimg[width=\columnwidth]{(b)}{figures/bendingEngMC45.pdf}
-    \caption{\label{fig:bendingSC_contracting} The bending energy of (a) a single-component vesicle, and (b) a multicomponent vesicle whose boundary is 45\% floppy passing through a contracting geometry.
-The vesicle shape at different locations are included.
-We can clearly see that the sudden increases and decreases in the bending energy are due to transitions between lower energy and higher energy shapes.}
+  \subfigimg[width=\columnwidth]{(a)}{figures/ContractingEnergy_SC.pdf}
+  \subfigimg[width=\columnwidth]{(b)}{figures/ContractingEnergy_MC.pdf}
+%  \subfigimg[width=\columnwidth]{(a)}{figures/bendingSC.pdf}
+%  \subfigimg[width=\columnwidth]{(b)}{figures/bendingEngMC45.pdf}
+  \caption{\label{fig:bendingSC_contracting} The bending energy of (a) a
+  single-component vesicle, and (b) a multicomponent vesicle whose
+  boundary is 45\% floppy passing through a contracting geometry. The
+  vesicle shape at different locations are included. We can clearly see
+  that the sudden increases and decreases in the bending energy are due
+  to transitions between lower energy and higher energy shapes.}
 \end{figure}
@@
 
+\begin{itemize}
+  \item New bending model using hyperbolic tangent (sigmoidal shape)
+    which is necessary to maintain a positive bending modulus
+
+  \item Orientation of the phase is always stiff on the front and floppy
+    on the back, but we don't know why (yet). Observed by others such as
+    Biros and Agrawalla, George and Misbah, and others.
+
+  \item Boundary layer and change in sign of pressure gradient term that
+    drives the lubrication flow. This is a combination of the tension
+    and the phase boundary between stiff and floppy regions.
+
+  \item Sudden drop in bending energy for multicomponent can be
+    explained by the sudden coarsening of the lipids.
+
+  \item Relationship between tank treading, excess pressure and layer
+    thickness.
+
+  \item  Inability to coarsen when under strong confinement. Can be
+    related to item 2. Strong confinement arrests phase coarsening.
+
+\end{itemize}
+
 %The main text of the article\cite{Mena2000} should appear here.

### 2023-07-31 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
fixed small typo

@@
   single-component vesicle (blue) and a multicomponent vesicle
-  (red)--(green) with $\alpha = 0.5$. As the size of the floppy region
+  (red)--(black) with $\alpha = 0.5$. As the size of the floppy region
   increases, the maximum bending energy decreases.}

### 2023-08-01 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
nothing major
yny

@@
 
-Vesicle hydrodynamics in extreme confinement has been studied as a model system for red blood cells (RBCs) squeezing through small
+Hydrodynamics of vesicles in extreme confinement has been studied as a model system for red blood cells (RBCs) squeezing through small
 capillaries (of sub-micron size in diameter) under a pressure difference \cite{LuPeng2019_PoF}.
@@
 
-\todo[inline]{Bryan is here}
 We conclude this example by considering the different shapes that

### 2023-08-02 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

@@
 vesicle's reduced area and viscosity contrast will determine if it
-
 undergoes tank treading, swinging, or tumbling in a shear
@@
 
-Under a linear shear flow, a multicomponent vesicle exhibits more exotic dynamics in both shape and membrane composition \cite{Sohn2010_JCP, Smith2007_JChemPhys,Cox2015_Nonlinearity,Liu2017_SoftMatter,Tusch2018_PRF,Gera2018_SoftMatter,Gera2022_JFM} than a single-component vesicle.
+Under a linear shear flow, a multicomponent vesicle exhibits more exotic dynamics in both shape and membrane composition \cite{soh-tse-li-voi-low2010, Smith2007_JChemPhys,Cox2015_Nonlinearity,Liu2017_SoftMatter,Tusch2018_PRF,Gera2018_SoftMatter,ger-sal-spa2022} than a single-component vesicle.
 For example, multicomponent vesicles under a background flow often exhibit highly complex morphologies, leading to vesicle budding. 
@@
 Hydrodynamics of vesicles in extreme confinement has been studied as a model system for red blood cells (RBCs) squeezing through small
-capillaries (of sub-micron size in diameter) under a pressure difference \cite{LuPeng2019_PoF}.
+capillaries (of sub-micron size in diameter) under a pressure difference \cite{LuPeng2019_PoF,gur-pak-tay-siv-sac2023}.
 Membrane permeability has been incorporated to examine the single-component vesicle hydrodynamics.
-In the absence of an osmotic gradient, the semipermeable vesicle is affected by water influx/efflux over a sufficiently long time or under a strong confinement \cite{Quaife2021_PRF}.
-Numerical simulations illustrate that a vesicle with moderate membrane permeability can go through a strong confinement much more easily, and can restore its water content within a very short time after its passage through the strong confinement \cite{Quaife2021_PRF}.
+In the absence of an osmotic gradient, the semipermeable vesicle is affected by water influx/efflux over a sufficiently long time or under a strong confinement \cite{qua-gan-you2021}.
+Numerical simulations illustrate that a vesicle with moderate membrane permeability can go through a strong confinement much more easily, and can restore its water content within a very short time after its passage through the strong confinement \cite{qua-gan-you2021}.
 These results imply that the membrane permeability may be inferred from vesicle hydrodynamics under a strong confinement.
@@
 
-\citet{gur-pak-tay-siv-sac2023} look at the effect of membrane
-viscoelasticity.
+%\citet{gur-pak-tay-siv-sac2023} look at the effect of membrane viscoelasticity.
 

### 2023-08-03 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

@@
 
-Under a linear shear flow, a multicomponent vesicle exhibits more exotic dynamics in both shape and membrane composition \cite{soh-tse-li-voi-low2010, Smith2007_JChemPhys,Cox2015_Nonlinearity,Liu2017_SoftMatter,Tusch2018_PRF,Gera2018_SoftMatter,ger-sal-spa2022} than a single-component vesicle.
+Under a linear shear flow, a multicomponent vesicle exhibits more exotic dynamics in both shape and membrane composition \cite{soh-tse-li-voi-low2010, Smith2007_JChemPhys,Cox2015_Nonlinearity,liu-mar-li-vee-low2017,Tusch2018_PRF,Gera2018_SoftMatter,ger-sal-spa2022} than a single-component vesicle.
 For example, multicomponent vesicles under a background flow often exhibit highly complex morphologies, leading to vesicle budding. 
@@
 fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006,
-ger-sal-spa2022, lip1992, urs-klu-phi2009}. In addition to the
+ger-sal-spa2022, lip1992, urs-klu-phi2009}. 
+Through numerical investigations, 
+Liu {\it et al.}~\cite{liu-mar-li-vee-low2017} identified several key dimensionless numbers, including the reduced area, capillary
+number, and the floppy-to-stiff ratio to characterize various dynamics of a
+multicomponent vesicle in an unbounded linear shear flow. In addition to the
 aforementioned numerical studies, these dynamics have been observed in
@@
 Hydrodynamics of vesicles in extreme confinement has been studied as a model system for red blood cells (RBCs) squeezing through small
-capillaries (of sub-micron size in diameter) under a pressure difference \cite{LuPeng2019_PoF,gur-pak-tay-siv-sac2023}.
+capillaries (of sub-micron size in diameter) under a pressure difference \cite{LuPeng2019_PoF,che-lyu-jae-leo2020,gur-pak-tay-siv-sac2023}.
 Membrane permeability has been incorporated to examine the single-component vesicle hydrodynamics.
@@
 This question is highly relevant to hydrodynamics of cells in a confinement, and to our knowledge has not been well studied.
-
-In this paper, we extend the work of Liu et
-al.~\cite{liu-mar-li-vee-low2017} who performed a thorough investigation
-of how key dimensionless numbers, including the reduced area, capillary
-number, and the floppy-to-stiff ratio, affect the dynamics of a
-multicomponent vesicle in an unbounded linear shear flow. What is
-missing from the literature, and what we address in this work, is the
-effect of strong confinement on a two-dimensional multicomponent
-vesicle. Using numerical simulations, we show how the vesicle's reduced
+Ramachandran {\it et al.} \cite{ram-kom-sek-ima2010} reported that confinement reduces the effective diffusion coefficient of the concentration fluctuation in multicomponent membranes.
+How is such reduced concentration diffusion coefficient reflected in the hydrodynamics of multicomponent vesicles under strong confinement?
+
+In this paper, we use numerical simulations and lubrication analysis \cite{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019} 
+to investigate the effect of strong confinement on a multicomponent vesicle.
+In particular we show how the vesicle's reduced
 area and its lipid composition affect the dynamics in two strongly
 confined geometries.
-
+%
 The remainder of the paper is organized as follows.
@@
 
-\citet{ram-kom-sek-ima2010}
-
-\citet{che-lyu-jae-leo2020}
-
 \citet{wan-ii-sug-nod-jin-liu-che-gon2023}
 
-\citet{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019}
-is paper with Sean Sun that looks at linear and non-linear shear in the
-boundary layer caused by tank treading behavior.
+%\citet{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019}
+%is paper with Sean Sun that looks at linear and non-linear shear in the
+%boundary layer caused by tank treading behavior.
 

### 2023-08-04 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
started to rearrange figures and fixed Figs 1 and 8

@@
 
-\begin{figure}[H]
+\begin{figure}[h]
   \centering
@@
 results reported by~\citet{liu-mar-li-vee-low2017} (cf.~Figure 3).
-\begin{figure}[H]
+\begin{figure}[h]
   \centering
@@
 
-\begin{figure*}[h]
+\begin{figure*}[ht]
   \centering
@@
   \subfigimg[width=0.3\linewidth]{(c)}{figures/MCp5_energy.pdf}
-  \caption{\label{fig:Energy} \small The Bending (blue), tension (red),
+  \caption{\label{fig:Energy} \small The bending (blue), tension (red),
   and phase (green) energies for a (a) stiff single-component, (b)
@@
 
-\begin{figure}
+\begin{figure*}[t]
+%\begin{figure}
   \centering
-  \subfigimg[width=\columnwidth]{(a)}{figures/SC_top.pdf}
-  \subfigimg[width=\columnwidth]{(b)}{figures/SC_bot.pdf}
-  \subfigimg[width=\columnwidth]{(c)}{figures/SCp55_top.pdf}
-  \subfigimg[width=\columnwidth]{(d)}{figures/SCp55_bot.pdf}
-  \subfigimg[width=\columnwidth]{(e)}{figures/MCp5_top.pdf}
-  \subfigimg[width=\columnwidth]{(f)}{figures/MCp5_bot.pdf}
-  \caption{\label{fig:BLvelocities} A descriptive caption.}
-\end{figure}
+  \subfigimg[width=0.48\linewidth]{(a)}{figures/SC_top.pdf}
+  \subfigimg[width=0.48\linewidth]{(b)}{figures/SC_bot.pdf}
+  \subfigimg[width=0.48\linewidth]{(c)}{figures/SCp55_top.pdf}
+  \subfigimg[width=0.48\linewidth]{(d)}{figures/SCp55_bot.pdf}
+  \subfigimg[width=0.48\linewidth]{(e)}{figures/MCp5_top.pdf}
+  \subfigimg[width=0.48\linewidth]{(f)}{figures/MCp5_bot.pdf}
+  \caption{\label{fig:BLvelocities} The co-moving velocity field in the
+  thin fluid layer between vesicles and the stenosis geometry. The
+  vesicles are (a/b): single-component with $b(u) = 1$; (c/d):
+  single-component with $b(u) = 0.55$; (e/f): multicomponent. The top
+  layers are in (a/c/e) and the bottom layers are in (b/d/f). The
+  profiles are ploted at slices where the pressure gradient transitions
+  from a value that is negative, zero, positive, zero, and negative. The
+  right plots show the tangential stress with the five slices denoted by
+  the marks. Note that the reversal in the pressure gradient occurs when
+  the tangential stress is sufficiently large, in magnitude.}
+%\end{figure}
+\end{figure*}
 
@@
 
-\begin{table}[H]
+\begin{table}[h]
   \centering
@@
 
-\begin{figure}
+\begin{figure}[h]
   \centering

### 2023-08-06 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

@@
 %
- & \noindent\large{Ashley Gannon,\textit{$^{a}$} Yuan-Nan Young,\textit{$^{b\ddag}$} and Bryan Quaife\textit{${\ast}${$^{a}$}}} \\
+ & \noindent\large{Ashley Gannon,\textit{$^{a}$} Y.-N. Young,\textit{$^{b\ddag}$} and Bryan Quaife\textit{${\ast}${$^{a}$}}} \\
 % %Author names go here instead of "Full name", etc.
@@
 passing through stenosis with a capillary number $Ca = 0.25$.
+With the current setup and $Ca=0.25$, an elliptical vesicle with reduced area greater than
+$\alpha = 0.8$ cannot fit through the closely-fitting geometry.
+
 Figure~\ref{fig:RA6} shows six time steps of a (a) stiff
@@
 However, in general, there is little difference between these cases,
-partially because these vesicles have a large reduced area. With the
-current setup, an elliptical vesicle with reduced area greater than
-$\alpha = 0.8$ cannot fit through the closely-fitting geometry.
+partially because these vesicles have a large reduced area.
 
@@
 
-To create more significant differences between the three cases, we
-consider the same geometry, but for a vesicle with reduced area $\alpha
-= 0.4$. Figure~\ref{fig:RA4} shows six time steps of a (a) stiff
-single-component, (b) floppy single-component, and (c) multicomponent
-vesicle. We first consider the three different energies---bending,
+Next we consider a vesicle with a smaller reduced area $\alpha=0.4$ with the same geometry and $Ca=0.25$.
+Figure~\ref{fig:RA4} shows  the shape of  
+a (a) stiff single-component, (b) floppy single-component, and (c) multicomponent
+vesicle at six locations along the stenosis channel. We first consider the three different energies---bending,
 tension, and phase---for each of these cases. In
@@
 $x=-15$ and exits at $x=15$. Also note that the single-component
-vesicles do not have a phase energy. A few general trends can
-immediately be seen. First, as the vesicle enters the stenosis, it
+vesicles do not have a phase energy. 
+%A few general trends can immediately be seen. 
+First we observe that, as the vesicle enters the stenosis, it
 develops regions of high curvature, and this results in an increase in
-the bending energy. Also, since the stiff single-component and
+the bending energy. Secondly, since the stiff single-component and
 multicomponent vesicles reach a steady-state shape near the middle of
@@
 
-The presence of the multiple lipid species in the multicomponent vesicle
+%This corresponds to an arrest of phase coarsening for a vesicle confined in a stenosis.
+The presence of the multiple lipid species in the multicomponent vesicle under confinement
 results in interesting additional physics. The lipid species coarsens at

### 2023-08-07 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny2

@@
 develops regions of high curvature, and this results in an increase in
-the bending energy. Secondly, since the stiff single-component and
+the bending energy. Secondly, as the stiff single-component and
 multicomponent vesicles reach a steady-state shape near the middle of
 the channel, their bending, tension, and phase energies remain nearly
-constant from $x=0$ until the end of the stenosis.
+constant from $x=0$ until the end of the stenosis. For the multiple-component vesicle,
+this implies that there is no coarsening of lipid phase in the middle of a stenosis.
 
 %This corresponds to an arrest of phase coarsening for a vesicle confined in a stenosis.
-The presence of the multiple lipid species in the multicomponent vesicle under confinement
-results in interesting additional physics. The lipid species coarsens at
+Such co-existence of multiple lipid domains in a vesicle under confinement
+results in interesting additional physics. 
+%
+First we note that in Figure~\ref{fig:Energy}(c),
+the lipid species coarsens at
 three instances, and this results in a decrease in the phase energy.
-Note, however, that no coarsening occurs when the vesicle is in the
-closely-fitting part of the domain. Each coarsening corresponds either
+However, as we mentioned earlier, no coarsening occurs when the vesicle is in the
+closely-fitting part of the channel. Each coarsening corresponds either
 to two stiff regions overtaking a small floppy region, or to two floppy

### 2023-08-09 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

@@
 \section{Conclusions \label{sec:conclusion}}
+In this work we used numerical simulations to examine the hydrodynamics of a multicomponent vesicle under strong confinement, which is a ubiquitous configuration in biology when a cell squeezes through a small channel.
+We refined the phase-field formulation in \citet{liu-mar-li-vee-low2017} with a new bending model that uses a sigmoidal function for the bending stiffness to retain positiveness in the bending modulus.
 

### 2023-08-09 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
fixed a few figures

@@
   \caption{\label{fig:Energy} \small The bending (blue), tension (red),
-  and phase (green) energies for a (a) stiff single-component, (b)
+  and phase (magenta) energies for a (a) stiff single-component, (b)
   floppy single-component, and (c) multicomponent vesicle. The reduced

### 2023-08-09 vesicle_code/docs/confinedMulti/makefigs/Fig6driver.m

@@ -31,3 +31,7 @@ set(f,'PaperPositionMode','Auto','PaperUnits','Inches',...
 set(f,'Position',[0 0 19 6.4]);
 print(f,'-dpdf','STENOSIS_RAp6MCp5.pdf','-r0')
 end
+
+
+
+

### 2023-08-10 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on figures

@@
   \subfigimg[width=0.48\linewidth]{(f)}{figures/MCp5_bot.pdf}
-  \caption{\label{fig:BLvelocities} The co-moving velocity field in the
-  thin fluid layer between vesicles and the stenosis geometry. The
-  vesicles are (a/b): single-component with $b(u) = 1$; (c/d):
+  \caption{\label{fig:BLvelocities} \small The co-moving velocity field
+  in the thin fluid layer between vesicles and the stenosis geometry.
+  The vesicles are (a/b): single-component with $b(u) = 1$; (c/d):
   single-component with $b(u) = 0.55$; (e/f): multicomponent. The top
@@
   vesicle's reduced area is $\alpha = 0.6$ and the capillary number is
-  $Ca = 0.25$. The lipid distribution is initialized to already be phase
-  separated in the top and bottom rows, and the middle row has a random
-  initial lipid distribution. The preferred lipid distribution has the
-  stiff region passing through the contraction before the floppy
-  region.}
+  $Ca = 0.25$. The lipid distribution is initialized to be (a) phase
+  separated with the floppy region leading; (b) random; (c) phase
+  separated with the stiff region leading.}
 \end{figure}
@@
 
+%\begin{figure*}[t]
 \begin{figure}[h]
@@
 \end{figure}
+%\end{figure*}
 
@@
   \end{tabular}
-  \caption{\label{tbl:contractingTimes} The time required for the
+  \caption{\label{tbl:contractingTimes} \small The time required for the
   vesicles to completely pass through the neck.}
@@
 %  \subfigimg[width=\columnwidth]{(b)}{figures/bendingEngMC45.pdf}
-  \caption{\label{fig:bendingSC_contracting} The bending energy of (a) a
-  single-component vesicle, and (b) a multicomponent vesicle whose
-  boundary is 45\% floppy passing through a contracting geometry. The
-  vesicle shape at different locations are included. We can clearly see
-  that the sudden increases and decreases in the bending energy are due
-  to transitions between lower energy and higher energy shapes.}
+  \caption{\label{fig:bendingSC_contracting} \small The bending energy
+  of (a) a single-component vesicle, and (b) a multicomponent vesicle
+  whose boundary is 45\% floppy passing through a contracting geometry.
+  The vesicle shape at different locations are included. We can clearly
+  see that the sudden increases and decreases in the bending energy are
+  due to transitions between lower energy and higher energy shapes.}
 \end{figure}

### 2023-08-10 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

--- 2023-08-09 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Constitutive equations}
+\subsection{Constitutive equations\label{subsec:const_eq}}
 Using the model first introduced by~\citet{liu-mar-li-vee-low2017}, the
@@
 We refined the phase-field formulation in \citet{liu-mar-li-vee-low2017} with a new bending model that uses a sigmoidal function for the bending stiffness to retain positiveness in the bending modulus.
+The linear model \cite{liu-mar-li-vee-low2017} works well for a vesicle in free-space.
+However, under strong confinement we find it necessary to enforce the condition that the dimensionless bending modulus $b(u)$ be in the range of $[\beta,1]$  ($\beta = b_{\min}/b_{\max}$)  to avoid instability in membrane shapes (see \S~\ref{subsec:const_eq}).
+We focused on the hydrodynamics of a multicomponent vesicle in two types of confinement: a stenosis channel (\S~\ref{subsec:Stenosis}), and a contracting channel (\S~\ref{subsec:Contraction}).
+For both cases we varied the reduced area $\alpha$, the floppy-to-stiffness ratio $\beta$, the initial distribution of lipid domains with a fixed Capillary number $Ca=0.25$ and a fixed Peclet number of the lipid dynamics $Pe=1$.
 

### 2023-08-10 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny2

@@
 We focused on the hydrodynamics of a multicomponent vesicle in two types of confinement: a stenosis channel (\S~\ref{subsec:Stenosis}), and a contracting channel (\S~\ref{subsec:Contraction}).
-For both cases we varied the reduced area $\alpha$, the floppy-to-stiffness ratio $\beta$, the initial distribution of lipid domains with a fixed Capillary number $Ca=0.25$ and a fixed Peclet number of the lipid dynamics $Pe=1$.
+For both confining geometries we varied the reduced area $\alpha$, the floppy-to-stiffness ratio $\beta$, and the initial distribution of lipid domains with a fixed Capillary number $Ca=0.25$ and a fixed Peclet number of the lipid dynamics $Pe=1$.
+The reason for focusing on
 

### 2023-08-10 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny02
yny3

@@
 For both confining geometries we varied the reduced area $\alpha$, the floppy-to-stiffness ratio $\beta$, and the initial distribution of lipid domains with a fixed Capillary number $Ca=0.25$ and a fixed Peclet number of the lipid dynamics $Pe=1$.
-The reason for focusing on
+The confinement ratio (defined as $2R_0/W$) in the stenosis is $1.67$, consequently the dependence of the vesicle shape on the capillary number is expected to be less sensitive according to results in \citet{aga-bir2020}.
+By fixing Peclet number at unity, we assume that the phase separation occurs at a much faster time scale than vesicle relaxation.
+
+As a multicomponent vesicle enters/leaves a closely-fitted stenosis, coarsening of the lipid domains is expedited.
+However, strong confinement in the stenosis hinders the coarsening and the lipid domains remain separated as the vesicle moves through the stenosis.
+For a vesicle inside a stenosis, we define the lubrication layer and its corresponding width and examine the mechanical coupling between the boundaries in lipid domain and the planar shear flow inside the lubrication layer, which consists of a quadratic in height (due to pressure gradient in the thin film) and a linear shear term (due to membrane motion in the tangential direction).
+By analyzing these two contributions at various locations in the lubrication layer, we first identified that tank treading along the vesicle of $\alpha=0.4$ is due to the mismatch in lubrication layer width on the two sides.
+We further elucidated  the correlation between the location of boundary between lipid domains, the Marangoni stress,  and the change of sign in the pressure gradient in the lubrication layer.
+These results may be useful to identify the lipid domains via the visualization of the flow in the lubrication layer.
+
+For a multicomponent vesicle squeezing through a constriction, we found that front of the vesicle tends to be stiffer than the back of the vesicle.
 

### 2023-08-11 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny4

--- 2023-08-10 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
@@
 For both confining geometries we varied the reduced area $\alpha$, the floppy-to-stiffness ratio $\beta$, and the initial distribution of lipid domains with a fixed Capillary number $Ca=0.25$ and a fixed Peclet number of the lipid dynamics $Pe=1$.
-The reason for focusing on
-
-\begin{itemize}
-  \item New bending model using hyperbolic tangent (sigmoidal shape)
-    which is necessary to maintain a positive bending modulus
-
-  \item Orientation of the phase is always stiff on the front and floppy
-    on the back, but we don't know why (yet). Observed by others such as
-    Biros and Agrawalla, George and Misbah, and others.
-
-  \item Boundary layer and change in sign of pressure gradient term that
-    drives the lubrication flow. This is a combination of the tension
-    and the phase boundary between stiff and floppy regions.
-
-  \item Sudden drop in bending energy for multicomponent can be
-    explained by the sudden coarsening of the lipids.
-
-  \item Relationship between tank treading, excess pressure and layer
-    thickness.
-
-  \item  Inability to coarsen when under strong confinement. Can be
-    related to item 2. Strong confinement arrests phase coarsening.
-
-\end{itemize}
+In \S~\ref{subsec:Stenosis} the confinement ratio (defined as $2R_0/W$) in the stenosis is $1.67$, and in \S~\ref{subsec:Contraction} the confinement ratio increases to a maximum of $2$ at the neck.
+Consequently the dependence of the vesicle shape on the capillary number is expected to be less sensitive according to results in \citet{aga-bir2020}.
+Finally the phase separation is assumed to occur at a much faster time scale than vesicle relaxation with Pectlet number $Pe=1$.
+
+As a multicomponent vesicle enters/leaves a closely-fitted stenosis, coarsening of the lipid domains is expedited.
+However, inside the stenosis, the strong confinement hinders the coarsening as both the vesicle shape and the lipid domains remain more or less un-altered as the vesicle moves through the stenosis.
+Once inside a stenosis, we define the lubrication layer and its corresponding width to analyze the mechanical coupling between the boundaries in lipid domain and the planar shear flow inside the lubrication layer, which consists of a quadratic component (due to pressure gradient in the thin film) and a linear component (due to membrane motion in the tangential direction).
+By analyzing these two components at various locations in the lubrication layer, we first identified that tank treading along the vesicle of $\alpha=0.4$ is due to the mismatch in lubrication layer width on the two sides.
+We further elucidated  the correlation between the location of boundary between lipid domains, the Marangoni stress,  and the change of sign in the pressure gradient in the lubrication layer.
+These results may be used to identify the lipid domains via the visualization of the flow in the lubrication layer.
+
+For a multicomponent vesicle squeezing through a constriction, we simulated the passage of a vesicle with various initial configurations of lipid domains.
+We found that, once the vesicle makes its passage, the front of the vesicle is often stiffer than the back of the vesicle, with a similar shape of a smaller curvature in the front than the curvature in the back.
+This is also observed for a vesicle moving out of confinement from a stenosis channel.
+Thus we propose a strong confinement in combination with a sharp transition to a wider opening can be used to produce phase-separated multicomponent vesicle with the floppy lipid species in the back and the stiff lipid species in the front of the vesicle.
+
+Such asymmetry in lipid domain induced by strong confinement and sudden release gives rise to a nonuniform tension distribution in the membrane, with higher (?) tension in the front and lower (?) tension in the back.
+This may have biophysical consequences in polarity developing of a migrating cell.
+
+%\begin{itemize}
+%  \item New bending model using hyperbolic tangent (sigmoidal shape)
+%    which is necessary to maintain a positive bending modulus
+%
+%  \item Orientation of the phase is always stiff on the front and floppy
+%    on the back, but we don't know why (yet). Observed by others such as
+%    Biros and Agrawalla, George and Misbah, and others.
+%
+%  \item Boundary layer and change in sign of pressure gradient term that
+%    drives the lubrication flow. This is a combination of the tension
+%    and the phase boundary between stiff and floppy regions.
+%
+%  \item Sudden drop in bending energy for multicomponent can be
+%    explained by the sudden coarsening of the lipids.
+%
+%  \item Relationship between tank treading, excess pressure and layer
+%    thickness.
+%
+%  \item  Inability to coarsen when under strong confinement. Can be
+%    related to item 2. Strong confinement arrests phase coarsening.
+%
+%\end{itemize}
 

### 2023-08-11 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny
worked on tangential velocity figure

@@
   \caption{\label{fig:lubricationComposite} \small The lubrication layer
-  thicknesses (red and blue), excess pressure (green), and tank treading
+  thicknesses (red and blue), excess pressure (magenta), and tank treading
   velocity of four Lagrangian points of a (a) stiff single-component
@@
 Consequently the dependence of the vesicle shape on the capillary number is expected to be less sensitive according to results in \citet{aga-bir2020}.
-Finally the phase separation is assumed to occur at a much faster time scale than vesicle relaxation with Pectlet number $Pe=1$.
+Finally the phase separation is assumed to occur at a much faster time scale than vesicle relaxation with Peclet number $Pe=1$.
 

### 2023-08-11 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
worked on Fig 8

@@
 
-\begin{figure*}[t]
-%\begin{figure}
+%\begin{figure*}[t]
+\begin{figure}
   \centering
-  \subfigimg[width=0.48\linewidth]{(a)}{figures/SC_top.pdf}
-  \subfigimg[width=0.48\linewidth]{(b)}{figures/SC_bot.pdf}
-  \subfigimg[width=0.48\linewidth]{(c)}{figures/SCp55_top.pdf}
-  \subfigimg[width=0.48\linewidth]{(d)}{figures/SCp55_bot.pdf}
-  \subfigimg[width=0.48\linewidth]{(e)}{figures/MCp5_top.pdf}
-  \subfigimg[width=0.48\linewidth]{(f)}{figures/MCp5_bot.pdf}
+  \subfigimg[width=\columnwidth]{(a)}{figures/SC_top.pdf}
+%  \subfigimg[width=0.48\linewidth]{(b)}{figures/SC_bot.pdf}
+%  \subfigimg[width=0.48\linewidth]{(c)}{figures/SCp55_top.pdf}
+%  \subfigimg[width=0.48\linewidth]{(d)}{figures/SCp55_bot.pdf}
+  \subfigimg[width=\columnwidth]{(b)}{figures/MCp5_top.pdf}
+%  \subfigimg[width=0.48\linewidth]{(f)}{figures/MCp5_bot.pdf}
   \caption{\label{fig:BLvelocities} \small The co-moving velocity field
-  in the thin fluid layer between vesicles and the stenosis geometry.
-  The vesicles are (a/b): single-component with $b(u) = 1$; (c/d):
-  single-component with $b(u) = 0.55$; (e/f): multicomponent. The top
-  layers are in (a/c/e) and the bottom layers are in (b/d/f). The
-  profiles are ploted at slices where the pressure gradient transitions
-  from a value that is negative, zero, positive, zero, and negative. The
-  right plots show the tangential stress with the five slices denoted by
-  the marks. Note that the reversal in the pressure gradient occurs when
-  the tangential stress is sufficiently large, in magnitude.}
-%\end{figure}
-\end{figure*}
+  in the thin fluid layer between the top of a vesicle and the stenosis
+  geometry. The vesicles are (a): stiff single-component; (b):
+  multicomponent. Similar velocity profiles between the bottom of the
+  vesicle and the stenosis geometry. The profiles are ploted at slices
+  where the pressure gradient transitions from a value that is negative,
+  zero, positive, zero, and negative. The right plots show the
+  tangential stress with the five slices denoted by the marks. Note that
+  the reversal in the pressure gradient occurs when the tangential
+  stress is sufficiently large.}
+%  \caption{\label{fig:BLvelocities} \small The co-moving velocity field
+%  in the thin fluid layer between vesicles and the stenosis geometry.
+%  The vesicles are (a/b): single-component with $b(u) = 1$; (c/d):
+%  single-component with $b(u) = 0.55$; (e/f): multicomponent. The top
+%  layers are in (a/c/e) and the bottom layers are in (b/d/f). The
+%  profiles are ploted at slices where the pressure gradient transitions
+%  from a value that is negative, zero, positive, zero, and negative. The
+%  right plots show the tangential stress with the five slices denoted by
+%  the marks. Note that the reversal in the pressure gradient occurs when
+%  the tangential stress is sufficiently large, in magnitude.}
+\end{figure}
+%\end{figure*}
 

### 2023-08-12 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on paper

@@
 \section{Conclusions \label{sec:conclusion}}
-In this work we used numerical simulations to examine the hydrodynamics of a multicomponent vesicle under strong confinement, which is a ubiquitous configuration in biology when a cell squeezes through a small channel.
-We refined the phase-field formulation in \citet{liu-mar-li-vee-low2017} with a new bending model that uses a sigmoidal function for the bending stiffness to retain positiveness in the bending modulus.
-The linear model \cite{liu-mar-li-vee-low2017} works well for a vesicle in free-space.
-However, under strong confinement we find it necessary to enforce the condition that the dimensionless bending modulus $b(u)$ be in the range of $[\beta,1]$  ($\beta = b_{\min}/b_{\max}$)  to avoid instability in membrane shapes (see \S~\ref{subsec:const_eq}).
-We focused on the hydrodynamics of a multicomponent vesicle in two types of confinement: a stenosis channel (\S~\ref{subsec:Stenosis}), and a contracting channel (\S~\ref{subsec:Contraction}).
-For both confining geometries we varied the reduced area $\alpha$, the floppy-to-stiffness ratio $\beta$, and the initial distribution of lipid domains with a fixed Capillary number $Ca=0.25$ and a fixed Peclet number of the lipid dynamics $Pe=1$.
-In \S~\ref{subsec:Stenosis} the confinement ratio (defined as $2R_0/W$) in the stenosis is $1.67$, and in \S~\ref{subsec:Contraction} the confinement ratio increases to a maximum of $2$ at the neck.
-Consequently the dependence of the vesicle shape on the capillary number is expected to be less sensitive according to results in \citet{aga-bir2020}.
-Finally the phase separation is assumed to occur at a much faster time scale than vesicle relaxation with Peclet number $Pe=1$.
-
-As a multicomponent vesicle enters/leaves a closely-fitted stenosis, coarsening of the lipid domains is expedited.
-However, inside the stenosis, the strong confinement hinders the coarsening as both the vesicle shape and the lipid domains remain more or less un-altered as the vesicle moves through the stenosis.
-Once inside a stenosis, we define the lubrication layer and its corresponding width to analyze the mechanical coupling between the boundaries in lipid domain and the planar shear flow inside the lubrication layer, which consists of a quadratic component (due to pressure gradient in the thin film) and a linear component (due to membrane motion in the tangential direction).
-By analyzing these two components at various locations in the lubrication layer, we first identified that tank treading along the vesicle of $\alpha=0.4$ is due to the mismatch in lubrication layer width on the two sides.
-We further elucidated  the correlation between the location of boundary between lipid domains, the Marangoni stress,  and the change of sign in the pressure gradient in the lubrication layer.
-These results may be used to identify the lipid domains via the visualization of the flow in the lubrication layer.
-
-For a multicomponent vesicle squeezing through a constriction, we simulated the passage of a vesicle with various initial configurations of lipid domains.
-We found that, once the vesicle makes its passage, the front of the vesicle is often stiffer than the back of the vesicle, with a similar shape of a smaller curvature in the front than the curvature in the back.
-This is also observed for a vesicle moving out of confinement from a stenosis channel.
-Thus we propose a strong confinement in combination with a sharp transition to a wider opening can be used to produce phase-separated multicomponent vesicle with the floppy lipid species in the back and the stiff lipid species in the front of the vesicle.
-
-Such asymmetry in lipid domain induced by strong confinement and sudden release gives rise to a nonuniform tension distribution in the membrane, with higher (?) tension in the front and lower (?) tension in the back.
-This may have biophysical consequences in polarity developing of a migrating cell.
+In this work we used numerical simulations to examine the hydrodynamics
+of a multicomponent vesicle under strong confinement, which is a
+ubiquitous configuration in biology when a cell squeezes through a small
+channel. We refined the phase-field formulation
+in~\citet{liu-mar-li-vee-low2017} with a new bending model that uses a
+sigmoidal function for the bending stiffness to retain positiveness in
+the bending modulus. The linear model~\cite{liu-mar-li-vee-low2017}
+works well for a vesicle in free-space. However, under strong
+confinement we find it necessary to enforce the condition that the
+dimensionless bending modulus $b(u)$ be in the range of $[\beta,1]$
+($\beta = b_{\min}/b_{\max}$) to avoid instability in membrane shapes
+(see \S~\ref{subsec:const_eq}). We focused on the hydrodynamics of a
+multicomponent vesicle in two types of confinement: a stenosis channel
+(\S~\ref{subsec:Stenosis}), and a contracting channel
+(\S~\ref{subsec:Contraction}). For both confining geometries we varied
+the reduced area $\alpha$, the floppy-to-stiffness ratio $\beta$, and
+the initial distribution of lipid domains with a fixed Capillary number
+$Ca=0.25$ and a fixed Peclet number of the lipid dynamics $Pe=1$. In
+\S~\ref{subsec:Stenosis} the confinement ratio (defined as $2R_0/W$) in
+the stenosis is $1.67$, and in \S~\ref{subsec:Contraction} the
+confinement ratio increases to a maximum of $3.60$ at the neck.
+Consequently the dependence of the vesicle shape on the capillary number
+is expected to be less sensitive according to results
+in~\citet{aga-bir2020}. Finally the phase separation is assumed to occur
+at a much faster time scale than vesicle relaxation with Peclet number
+$Pe=1$.
+
+As a multicomponent vesicle enters/leaves a closely-fitted stenosis,
+coarsening of the lipid domains is expedited. However, inside the
+stenosis, the strong confinement hinders the coarsening as both the
+vesicle shape and the lipid domains remain more or less unaltered as the
+vesicle moves through the stenosis. Once inside a stenosis, we define
+the lubrication layer and its corresponding width to analyze the
+mechanical coupling between the boundaries in lipid domain and the
+planar shear flow inside the lubrication layer, which consists of a
+quadratic component (due to pressure gradient in the thin film) and a
+linear component (due to membrane motion in the tangential direction).
+By analyzing these two components at various locations in the
+lubrication layer, we first identified that tank treading along the
+vesicle of $\alpha=0.4$ is due to the mismatch in lubrication layer
+width on the two sides. We further elucidated the correlation between
+the location of boundary between lipid domains, the Marangoni stress,
+and the change of sign in the pressure gradient in the lubrication
+layer. These results may be used to identify the lipid domains via the
+visualization of the flow in the lubrication layer.
+
+For a multicomponent vesicle squeezing through a constriction, we
+simulated the passage of a vesicle with various initial configurations
+of lipid domains. We found that, once the vesicle makes its passage, the
+front of the vesicle is often stiffer than the back of the vesicle, with
+a similar shape of a smaller curvature in the front than the curvature
+in the back. This is also observed for a vesicle moving out of
+confinement from a stenosis channel. Thus we propose a strong
+confinement in combination with a sharp transition to a wider opening
+can be used to produce phase-separated multicomponent vesicle with the
+floppy lipid species in the back and the stiff lipid species in the
+front of the vesicle.
+
+Such asymmetry in lipid domain induced by strong confinement and sudden
+release gives rise to a nonuniform tension distribution in the membrane,
+with higher (?) tension in the front and lower (?) tension in the back.
+This may have biophysical consequences in polarity developing of a
+migrating cell.
 

### 2023-08-13 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

@@
 In this work we used numerical simulations to examine the hydrodynamics
-of a multicomponent vesicle under strong confinement, which is a
-ubiquitous configuration in biology when a cell squeezes through a small
-channel. We refined the phase-field formulation
+of a multicomponent vesicle under strong confinement. The vesicle is an simplified model for a red blood cell (RBC), which has 
+multiple lipid domains in its membrane and often has to squeeze through a small space.
+We refined the phase-field formulation
 in~\citet{liu-mar-li-vee-low2017} with a new bending model that uses a
@@
 (\S~\ref{subsec:Contraction}). For both confining geometries we varied
-the reduced area $\alpha$, the floppy-to-stiffness ratio $\beta$, and
-the initial distribution of lipid domains with a fixed Capillary number
-$Ca=0.25$ and a fixed Peclet number of the lipid dynamics $Pe=1$. In
-\S~\ref{subsec:Stenosis} the confinement ratio (defined as $2R_0/W$) in
+the reduced area $\alpha$  and
+the initial distribution of lipid domains with a fixed floppy-to-stiff ratio $\beta=0.1$, 
+a fixed Capillary number $Ca=0.25$ and a fixed Peclet number of the lipid dynamics $Pe=1$.
+
+In \S~\ref{subsec:Stenosis} the confinement ratio (defined as $2R_0/W$) in
 the stenosis is $1.67$, and in \S~\ref{subsec:Contraction} the
@@
 vesicle of $\alpha=0.4$ is due to the mismatch in lubrication layer
-width on the two sides. We further elucidated the correlation between
+width between the two sides. We further elucidated the correlation between
 the location of boundary between lipid domains, the Marangoni stress,
@@
 in the back. This is also observed for a vesicle moving out of
-confinement from a stenosis channel. Thus we propose a strong
-confinement in combination with a sharp transition to a wider opening
+confinement from a stenosis channel. Thus we propose that a strong
+confinement followed by a sharp transition to a wider opening
 can be used to produce phase-separated multicomponent vesicle with the
@@
 release gives rise to a nonuniform tension distribution in the membrane,
-with higher (?) tension in the front and lower (?) tension in the back.
+with a higher tension (in magnitude) in the front and a smaller tension (in magnitude) in the back.
 This may have biophysical consequences in polarity developing of a

### 2023-08-13 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

@@
 Hydrodynamics of vesicles in extreme confinement has been studied as a model system for red blood cells (RBCs) squeezing through small
-capillaries (of sub-micron size in diameter) under a pressure difference \cite{LuPeng2019_PoF,che-lyu-jae-leo2020,gur-pak-tay-siv-sac2023}.
+capillaries (of sub-micron size in diameter) under a pressure difference \cite{Freund2013_PoF,LuPeng2019_PoF,che-lyu-jae-leo2020,gur-pak-tay-siv-sac2023}.
 Membrane permeability has been incorporated to examine the single-component vesicle hydrodynamics.
@@
 The size of the top and bottom lubrication layers are also related to
-the excess pressure. The green curve on the top half of
-Figure~\ref{fig:lubricationComposite} shows the excess pressure with the
-axis aligned on the right side of the plot. When the lubrication layers
+the excess pressure. The magenta curve on the top half of
+Figure~\ref{fig:lubricationComposite} shows the excess pressure (with the
+axis aligned on the right side of the plot). When the lubrication layers
 are large, most notably for the multicomponent vesicle, less pressure is
@@
 coarsening of the lipid domains is expedited. However, inside the
-stenosis, the strong confinement hinders the coarsening as both the
-vesicle shape and the lipid domains remain more or less unaltered as the
+stenosis, the strong confinement hinders the coarsening as the
+vesicle shape and the lipid distribution remain more or less unaltered as the
 vesicle moves through the stenosis. Once inside a stenosis, we define
-the lubrication layer and its corresponding width to analyze the
-mechanical coupling between the boundaries in lipid domain and the
-planar shear flow inside the lubrication layer, which consists of a
+the lubrication layer and its width. 
+We find that tank treading along the vesicle inside the stenosis is closely related to the asymmetry in the lubrication layer width between the top and bottom walls.
+For vesicles with a high reduced area the lubrication layer width is symmetric between the top and bottom walls, and we find no tank treading along the membrane.
+On the other hand, for a vesicle with a lower reduced area, the lubrication layer width is asymmetric and the vesicle membrane tanks treads.
+Furthermore we also find that the excess pressure (the additional pressure required to pass the vesicle through the stenosis) is correlated to the size of the lubrication layer: the larger the lubrication layer size, the smaller the excess pressure is.
+
+Inside the lubrication layer, the shear flow consists of a
 quadratic component (due to pressure gradient in the thin film) and a
@@
 By analyzing these two components at various locations in the
-lubrication layer, we first identified that tank treading along the
-vesicle of $\alpha=0.4$ is due to the mismatch in lubrication layer
-width between the two sides. We further elucidated the correlation between
+lubrication layer, we further elucidated the correlation between
 the location of boundary between lipid domains, the Marangoni stress,
 and the change of sign in the pressure gradient in the lubrication
-layer. These results may be used to identify the lipid domains via the
+layer. These results may be used to identify the location of boundaries between the lipid domains via the
 visualization of the flow in the lubrication layer.
@@
 release gives rise to a nonuniform tension distribution in the membrane,
-with a higher tension (in magnitude) in the front and a smaller tension (in magnitude) in the back.
-This may have biophysical consequences in polarity developing of a
-migrating cell.
+with a smaller tension (in magnitude) in the front and a larger tension (in magnitude) in the back.
+This is similar to a RBC going through a narrow slit \cite{LuPeng2019_PoF}, where the membrane tension is mostly negative (compression)
+when the RBC passes through the narrow slit with more compression in the back than in the front of the RBC.
+%This may have biophysical consequences in polarity developing of a
+%migrating cell.
 

### 2023-08-14 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
worked on intro and conclusion

@@
 
-\usepackage{todonotes}
+%\usepackage{todonotes}
 %%%Shorthands
@@
 Biological membranes, as the basic structural units for compartmentalizing biological systems, 
-have been observed to contain a vast array of proteins and different lipid species, that phase-separate and form domains or rafts, resulting in spatial variations in material properties such as bending stiffness \cite{}.
-Synthetic multicomponent vesicles, self-enclosed lipid bilayer membranes composed of different lipid species, have been used to study the rich patterns and accompanying morphologies which emerge from elastic heterogeneity in the membrane.
+have been observed to contain a vast array of proteins and different
+lipid species, that phase-separate and form domains or rafts, resulting
+in spatial variations in material properties such as bending stiffness
+\cite{}. Synthetic multicomponent vesicles, self-enclosed lipid bilayer
+membranes composed of different lipid species, have been used to study
+the rich patterns and accompanying morphologies that emerge from elastic heterogeneity in the membrane.
 In a quiescent environment,  such elastic heterogeneity gives rise to wrinkling budding \cite{Lowengrub2009_PRE,Li2012_CommMathSci}, adhesion and fusion \cite{Zhao2011_PRE} of vesicle membrane, closely related to cellular budding and fission processes \cite{Rauch2000_BiophysJ} as well as in cellular adhesion and fusion \cite{Takeda2003_PNAS}.
 
-The hydrodynamics of a single-component vesicle is characterized by parameters such as the capillary number, reduced volume, and confinement ratio  \cite{Abreu2014_ACI}. 
-Such characterization is often useful for inferring fluid and material properties.
+The hydrodynamics of a single-component vesicle is characterized by
+parameters such as the capillary number, reduced volume, and confinement
+ratio \cite{Abreu2014_ACI}.  Such characterization is often useful for
+inferring fluid and material properties.
 %Understanding these dynamics is critical to understanding the biophysics of red blood cells (RBCs) in blood flow. 
-For example, a
-vesicle's reduced area and viscosity contrast will determine if it
-undergoes tank treading, swinging, or tumbling in a shear
+For example, a vesicle's reduced volume and viscosity contrast determine
+if it undergoes tank-treading, swinging, or tumbling in a shear
 flow~\cite{nog-gom2005}. Transitions in the vesicle shape occur in
@@
 these shapes include axisymmetric bullets or parachutes, and asymmetric
-parachutes. Recently, characterization of 
-vesicles suspended in a channel or pipe
-flow~\cite{lyu-che-far-jae-mis-leo2023, aga-bir2020, qua-gan-you2021,
-abb-far-nai-ezz-ben-mis2022} showed more exotic vesicle hydrodynamics such as snaking and
-swirling behaviors in croissant and slipper shapes.
-
-Under a linear shear flow, a multicomponent vesicle exhibits more exotic dynamics in both shape and membrane composition \cite{soh-tse-li-voi-low2010, Smith2007_JChemPhys,Cox2015_Nonlinearity,liu-mar-li-vee-low2017,Tusch2018_PRF,Gera2018_SoftMatter,ger-sal-spa2022} than a single-component vesicle.
-For example, multicomponent vesicles under a background flow often exhibit highly complex morphologies, leading to vesicle budding. 
-The hydrodynamics of these
-multicomponent vesicles include phase treading, tumbling with no
-viscosity contrast, swinging, budding, and
-fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006,
-ger-sal-spa2022, lip1992, urs-klu-phi2009}. 
-Through numerical investigations, 
-Liu {\it et al.}~\cite{liu-mar-li-vee-low2017} identified several key dimensionless numbers, including the reduced area, capillary
-number, and the floppy-to-stiff ratio to characterize various dynamics of a
-multicomponent vesicle in an unbounded linear shear flow. In addition to the
-aforementioned numerical studies, these dynamics have been observed in
-experiments~\cite{bag-sun2009, yan-ima-tan2010, yan-ima-tan2008,
-dre-jah-bob-spa-gop2021}.
+parachutes. Recently, characterization of vesicles suspended in a
+channel or pipe flow~\cite{lyu-che-far-jae-mis-leo2023, aga-bir2020,
+qua-gan-you2021, abb-far-nai-ezz-ben-mis2022,
+wan-ii-sug-nod-jin-liu-che-gon2023} showed more exotic vesicle
+hydrodynamics such as snaking and swirling behaviors in croissant and
+slipper shapes.
+
+Under a linear shear flow, a multicomponent vesicle exhibits more exotic
+dynamics in both shape and membrane composition
+\cite{soh-tse-li-voi-low2010,
+Smith2007_JChemPhys,Cox2015_Nonlinearity,liu-mar-li-vee-low2017,Tusch2018_PRF,Gera2018_SoftMatter,ger-sal-spa2022}
+than a single-component vesicle.  For example, multicomponent vesicles
+under a background flow often exhibit highly complex morphologies,
+leading to vesicle budding.  The hydrodynamics of these multicomponent
+vesicles include phase treading, tumbling with no viscosity contrast,
+swinging, budding, and fission~\cite{soh-tse-li-voi-low2010, wan-du2008,
+all-ama2006, ger-sal-spa2022, lip1992, urs-klu-phi2009}.  Through
+numerical investigations,~\citet{liu-mar-li-vee-low2017}
+identified several key dimensionless numbers, including the reduced
+area, capillary number, and the floppy-to-stiff ratio to characterize
+various dynamics of a multicomponent vesicle in an unbounded linear
+shear flow. In addition to the aforementioned numerical studies, these
+dynamics have been observed in experiments~\cite{bag-sun2009,
+yan-ima-tan2010, yan-ima-tan2008, dre-jah-bob-spa-gop2021}.
 
@@
 
-Hydrodynamics of vesicles in extreme confinement has been studied as a model system for red blood cells (RBCs) squeezing through small
-capillaries (of sub-micron size in diameter) under a pressure difference \cite{Freund2013_PoF,LuPeng2019_PoF,che-lyu-jae-leo2020,gur-pak-tay-siv-sac2023}.
-Membrane permeability has been incorporated to examine the single-component vesicle hydrodynamics.
-In the absence of an osmotic gradient, the semipermeable vesicle is affected by water influx/efflux over a sufficiently long time or under a strong confinement \cite{qua-gan-you2021}.
-Numerical simulations illustrate that a vesicle with moderate membrane permeability can go through a strong confinement much more easily, and can restore its water content within a very short time after its passage through the strong confinement \cite{qua-gan-you2021}.
-These results imply that the membrane permeability may be inferred from vesicle hydrodynamics under a strong confinement.
-Motivated by these results, in this work we seek to investigate how strong confinement may affect the hydrodynamics of a multi-component vesicle?
-This question is highly relevant to hydrodynamics of cells in a confinement, and to our knowledge has not been well studied.
-Ramachandran {\it et al.} \cite{ram-kom-sek-ima2010} reported that confinement reduces the effective diffusion coefficient of the concentration fluctuation in multicomponent membranes.
-How is such reduced concentration diffusion coefficient reflected in the hydrodynamics of multicomponent vesicles under strong confinement?
-
-In this paper, we use numerical simulations and lubrication analysis \cite{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019} 
-to investigate the effect of strong confinement on a multicomponent vesicle.
-In particular we show how the vesicle's reduced
+Hydrodynamics of vesicles in extreme confinement has been studied as a
+model system for red blood cells (RBCs) squeezing through small
+capillaries (of sub-micron size in diameter) under a pressure difference
+\cite{Freund2013_PoF, LuPeng2019_PoF, che-lyu-jae-leo2020,
+gur-pak-tay-siv-sac2023}. Membrane permeability has been incorporated to
+examine the single-component vesicle hydrodynamics. In the absence of an
+osmotic gradient, the semipermeable vesicle is affected by water
+influx/efflux over a sufficiently long time or under a strong
+confinement \cite{qua-gan-you2021}. Numerical simulations illustrate
+that a vesicle with moderate membrane permeability can go through a
+strong confinement much more easily, and can restore its water content
+within a very short time after its passage through the strong
+confinement. These results imply that the membrane permeability may be
+inferred from vesicle hydrodynamics under a strong confinement.
+Motivated by these results, in this work we seek to investigate how
+strong confinement may affect the hydrodynamics of a multicomponent
+vesicle? This question is highly relevant to hydrodynamics of cells in a
+confinement, and to our knowledge has not been well studied.
+\citet{ram-kom-sek-ima2010} reported that confinement reduces the
+effective diffusion coefficient of the concentration fluctuation in
+multicomponent membranes. How is such reduced concentration diffusion
+coefficient reflected in the hydrodynamics of multicomponent vesicles
+under strong confinement?
+
+In this paper, we use numerical simulations and lubrication analysis
+\cite{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019} to
+investigate the effect of strong confinement on a two-dimensional
+multicomponent vesicle.  In particular we show how the vesicle's reduced
 area and its lipid composition affect the dynamics in two strongly
@@
 defines the techniques we use to define the excess pressure, lubrication
-layer width, and tank treading velocity. Section~\ref{sec:results}
+layer width, and tank-treading velocity. Section~\ref{sec:results}
 demonstrates the effects of strong confinement on multicomponent
@@
 
-\citet{wan-ii-sug-nod-jin-liu-che-gon2023}
+%\citet{wan-ii-sug-nod-jin-liu-che-gon2023}
 
@@
 the dynamics reported in the literature. Figure~\ref{fig:treading} shows
-a phase treading (top) ajnd a tank treading (bottom) multicomponent
+a phase treading (top) and a tank-treading (bottom) multicomponent
 vesicle in an unconfined shear flow. These simulations align with the
@@
 with smaller reduced area undergo tank-treading motions. As mentioned
-earlier, tank treading occurs when the top and bottom lubrication layers
+earlier, tank-treading occurs when the top and bottom lubrication layers
 differ in size. The size of the lubrication layers for all three cases
@@
   \caption{\label{fig:lubricationComposite} \small The lubrication layer
-  thicknesses (red and blue), excess pressure (magenta), and tank treading
-  velocity of four Lagrangian points of a (a) stiff single-component
-  vesicle, (b) floppy single-component vesicle, and (c) multicomponent
-  vesicle. The reduced area is $\alpha = 0.4$ in all three cases. Also
-  illustrated is the vesicle shape and the four Lagrangian points at the
-  location indicated by the dash line. The black dashed line is the
-  center line of the channel, and the arrow denotes the tank treading
-  direction.}
+  thicknesses (red and blue), excess pressure (magenta), and
+  tank-treading velocity of four Lagrangian points of a (a) stiff
+  single-component vesicle, (b) floppy single-component vesicle, and (c)
+  multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all
+  three cases. Also illustrated is the vesicle shape and the four
+  Lagrangian points at the location indicated by the dash line. The
+  black dashed line is the center line of the channel, and the arrow
+  denotes the tank-treading direction.}
 %\end{figure}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions \label{sec:conclusion}}
 In this work we used numerical simulations to examine the hydrodynamics
-of a multicomponent vesicle under strong confinement. The vesicle is an simplified model for a red blood cell (RBC), which has 
-multiple lipid domains in its membrane and often has to squeeze through a small space.
-We refined the phase-field formulation
-in~\citet{liu-mar-li-vee-low2017} with a new bending model that uses a
-sigmoidal function for the bending stiffness to retain positiveness in
-the bending modulus. The linear model~\cite{liu-mar-li-vee-low2017}
-works well for a vesicle in free-space. However, under strong
-confinement we find it necessary to enforce the condition that the
-dimensionless bending modulus $b(u)$ be in the range of $[\beta,1]$
-($\beta = b_{\min}/b_{\max}$) to avoid instability in membrane shapes
-(see \S~\ref{subsec:const_eq}). We focused on the hydrodynamics of a
-multicomponent vesicle in two types of confinement: a stenosis channel
-(\S~\ref{subsec:Stenosis}), and a contracting channel
-(\S~\ref{subsec:Contraction}). For both confining geometries we varied
-the reduced area $\alpha$  and
-the initial distribution of lipid domains with a fixed floppy-to-stiff ratio $\beta=0.1$, 
-a fixed Capillary number $Ca=0.25$ and a fixed Peclet number of the lipid dynamics $Pe=1$.
-
-In \S~\ref{subsec:Stenosis} the confinement ratio (defined as $2R_0/W$) in
-the stenosis is $1.67$, and in \S~\ref{subsec:Contraction} the
+of a multicomponent vesicle under strong confinement. The vesicle is an
+simplified model for a red blood cell (RBC), which has multiple lipid
+domains in its membrane and often has to squeeze through a small space.
+We refined the phase-field formulation in~\citet{liu-mar-li-vee-low2017}
+with a new bending model that uses a sigmoid function for the bending
+stiffness to retain positiveness in the bending modulus. The linear
+model~\cite{liu-mar-li-vee-low2017} works well for a vesicle in
+free-space. However, under strong confinement we find it necessary to
+enforce the condition that the dimensionless bending modulus $b(u)$ be
+in the range of $[\beta,1]$ ($\beta = b_{\min}/b_{\max}$) to avoid
+instability in membrane shapes (see \S~\ref{subsec:const_eq}). We
+focused on the hydrodynamics of a multicomponent vesicle in two types of
+confinement: a stenosis channel (\S~\ref{subsec:Stenosis}), and a
+contracting channel (\S~\ref{subsec:Contraction}). For both confining
+geometries we varied the reduced area $\alpha$ and the initial
+distribution of lipid domains with a fixed floppy-to-stiff ratio
+$\beta=0.1$, a fixed Capillary number $Ca=0.25$, and a fixed Peclet
+number of the lipid dynamics $Pe=1$.
+
+In \S~\ref{subsec:Stenosis} the confinement ratio (defined as $2R_0/W$)
+in the stenosis is $1.67$, and in \S~\ref{subsec:Contraction} the
 confinement ratio increases to a maximum of $3.60$ at the neck.
@@
 
-As a multicomponent vesicle enters/leaves a closely-fitted stenosis,
+As a multicomponent vesicle enters and exits a closely-fitted stenosis,
 coarsening of the lipid domains is expedited. However, inside the
-stenosis, the strong confinement hinders the coarsening as the
-vesicle shape and the lipid distribution remain more or less unaltered as the
+stenosis, the strong confinement hinders the coarsening as the vesicle
+shape and the lipid distribution remain more or less unaltered as the
 vesicle moves through the stenosis. Once inside a stenosis, we define
-the lubrication layer and its width. 
-We find that tank treading along the vesicle inside the stenosis is closely related to the asymmetry in the lubrication layer width between the top and bottom walls.
-For vesicles with a high reduced area the lubrication layer width is symmetric between the top and bottom walls, and we find no tank treading along the membrane.
-On the other hand, for a vesicle with a lower reduced area, the lubrication layer width is asymmetric and the vesicle membrane tanks treads.
-Furthermore we also find that the excess pressure (the additional pressure required to pass the vesicle through the stenosis) is correlated to the size of the lubrication layer: the larger the lubrication layer size, the smaller the excess pressure is.
-
-Inside the lubrication layer, the shear flow consists of a
-quadratic component (due to pressure gradient in the thin film) and a
-linear component (due to membrane motion in the tangential direction).
-By analyzing these two components at various locations in the
-lubrication layer, we further elucidated the correlation between
-the location of boundary between lipid domains, the Marangoni stress,
-and the change of sign in the pressure gradient in the lubrication
-layer. These results may be used to identify the location of boundaries between the lipid domains via the
-visualization of the flow in the lubrication layer.
+the lubrication layer and its width. We find that tank-treading along
+the vesicle inside the stenosis is closely related to the asymmetry in
+the lubrication layer width between the top and bottom walls. For
+vesicles with a high reduced area the lubrication layer width is
+symmetric between the top and bottom walls, and we find no tank-treading
+along the membrane. On the other hand, for a vesicle with a lower
+reduced area, the lubrication layer width is asymmetric and the vesicle
+membrane tanks treads. Furthermore we also find that the excess pressure
+(the additional pressure required to pass the vesicle through the
+stenosis) is correlated to the size of the lubrication layer: a larger
+lubrication layer size results in smaller excess pressure
+%the larger the lubrication layer size, the smaller the excess pressure
+%is.
+
+Inside the lubrication layer, the shear flow consists of a quadratic
+component (due to pressure gradient in the thin film) and a linear
+component (due to membrane motion in the tangential direction). By
+analyzing these two components at various locations in the lubrication
+layer, we further elucidated the correlation between the location of
+boundary between lipid domains, the Marangoni stress, and the change of
+sign in the pressure gradient in the lubrication layer. These results
+may be used to identify the location of boundaries between the lipid
+domains via the visualization of the flow in the lubrication layer.
 
@@
 confinement from a stenosis channel. Thus we propose that a strong
-confinement followed by a sharp transition to a wider opening
-can be used to produce phase-separated multicomponent vesicle with the
-floppy lipid species in the back and the stiff lipid species in the
-front of the vesicle.
+confinement followed by a sharp transition to a wider opening can be
+used to produce phase-separated multicomponent vesicle with the floppy
+lipid species in the back and the stiff lipid species in the front of
+the vesicle.
 
@@
 release gives rise to a nonuniform tension distribution in the membrane,
-with a smaller tension (in magnitude) in the front and a larger tension (in magnitude) in the back.
-This is similar to a RBC going through a narrow slit \cite{LuPeng2019_PoF}, where the membrane tension is mostly negative (compression)
-when the RBC passes through the narrow slit with more compression in the back than in the front of the RBC.
+with a smaller tension (in magnitude) in the front and a larger tension
+(in magnitude) in the back. This is similar to a RBC going through a
+narrow slit~\cite{LuPeng2019_PoF}, where the membrane tension is mostly
+negative (compression) when the RBC passes through the narrow slit with
+more compression in the back than in the front of the RBC.
 %This may have biophysical consequences in polarity developing of a

### 2023-08-14 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

@@
 %
-\includegraphics{head_foot/dates} & \noindent\normalsize{The abstract should be a single paragraph which summarises the content of the article.
-Any references in the abstract should be written out in full \textit{e.g.}\ [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].} \\%The abstrast goes here instead of the text "The abstract should be..."
+\includegraphics{head_foot/dates} & \noindent\normalsize{We numerically study the hydrodynamics of multicomponent vesicles in strong confinement as a simplified model for red blood cells going through extreme constriction.
+Under strong confinement, we parametrize the bending modulus so that it is positive for all values of the lipid phase parameter.
+For a multicomponent vesicle going through a stenosis, we find the correlation between the lipid phase coarsening and the lubrication layer (such as size and flow profile), excess pressure, and tank treading in the membrane.
+For a multicomponent vesicle going through a contracting channel, we find that the lipid always phase separates so that the vesicle is stiffer in the front as it passes through the constriction.
+For both cases of confinement we find that the lipid coarsening is arrested under strong confinement, and proceeds with high rate upon relief from extreme confinement.
+These results may be useful for efficient sorting lipid domains using microfluidic flows by controlled release of vesicles going through strong confinement.
+} \\%The abstrast goes here instead of the text "The abstract should be..."
 %
@@
 The lubrication layer between a vesicle and the solid wall plays a
-critical role on the vesicle's dynamics. Therefore, throughout
-Section~\ref{sec:results}, we calculate the size and analyze the flow
-inside the lubrication layers. 
+critical role in the dynamics of a vesicle under strong confinement.
+Therefore, throughout
+Section~\ref{sec:results}, we calculate and analyze the flow
+inside the lubrication layers between the vesicle and the channel walls to elucidate the correlation between hydrodynamics and membrane dynamics.
 %We first justify the use of the term `lubrication layer' by verifying
@@
 A difference between the size of the top and bottom lubrication layers
-indicates that the vesicle  has deviated from the center of the channel,
+indicates that the vesicle membrane shape is asymmetric with respect to 
+the center of the channel,
 and this results in tank-treading behavior~\cite{aga-bir2020}.  To
@@
 
-The size of the top and bottom lubrication layers are also related to
+The sizes of the top and bottom lubrication layers are also related to
 the excess pressure. The magenta curve on the top half of
@@
 stenosis, the strong confinement hinders the coarsening as the vesicle
-shape and the lipid distribution remain more or less unaltered as the
+shape and the lipid distribution remain nearly unaltered as the
 vesicle moves through the stenosis. Once inside a stenosis, we define
@@
 stenosis) is correlated to the size of the lubrication layer: a larger
-lubrication layer size results in smaller excess pressure
+lubrication layer size results in smaller excess pressure.
 %the larger the lubrication layer size, the smaller the excess pressure

### 2023-08-14 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
picking away at the paper

@@
 %
-\includegraphics{head_foot/dates} & \noindent\normalsize{We numerically study the hydrodynamics of multicomponent vesicles in strong confinement as a simplified model for red blood cells going through extreme constriction.
-Under strong confinement, we parametrize the bending modulus so that it is positive for all values of the lipid phase parameter.
-For a multicomponent vesicle going through a stenosis, we find the correlation between the lipid phase coarsening and the lubrication layer (such as size and flow profile), excess pressure, and tank treading in the membrane.
-For a multicomponent vesicle going through a contracting channel, we find that the lipid always phase separates so that the vesicle is stiffer in the front as it passes through the constriction.
-For both cases of confinement we find that the lipid coarsening is arrested under strong confinement, and proceeds with high rate upon relief from extreme confinement.
-These results may be useful for efficient sorting lipid domains using microfluidic flows by controlled release of vesicles going through strong confinement.
-} \\%The abstrast goes here instead of the text "The abstract should be..."
+\includegraphics{head_foot/dates} & \noindent\normalsize{We numerically
+  study the hydrodynamics of multicomponent vesicles in two strongly
+  confining geometries. This serves as a simplified model for red blood
+  cells passing through extreme constrictions. We propose a new bending
+  modulus parameterization so that it remains positive for all values of
+  the lipid phase parameter. For a multicomponent vesicle passing
+  through a stenosis, we correlate the lipid phase coarsening, the
+  lubrication layer properties (size and flow profile), the excess
+  pressure, and the tank-treading velocity of the membrane. For a
+  multicomponent vesicle passing through a contracting channel, we find
+  that the lipid always phase separates so that the vesicle is stiffer
+  in the front as it passes through the constriction. For both cases of
+  confinement we find that the lipid coarsening is arrested under strong
+  confinement, and proceeds with high rate upon relief from extreme
+  confinement. The results may be useful for efficient sorting lipid
+  domains using microfluidic flows by controlled release of vesicles
+  passing through strong confinement. } \\
+  %The abstrast goes here instead of the text "The abstract should
+  %be..."
 %
@@
 \section{\label{sec:Introduction}Introduction}
-Biological membranes, as the basic structural units for compartmentalizing biological systems, 
-have been observed to contain a vast array of proteins and different
-lipid species, that phase-separate and form domains or rafts, resulting
-in spatial variations in material properties such as bending stiffness
-\cite{}. Synthetic multicomponent vesicles, self-enclosed lipid bilayer
-membranes composed of different lipid species, have been used to study
-the rich patterns and accompanying morphologies that emerge from elastic heterogeneity in the membrane.
-In a quiescent environment,  such elastic heterogeneity gives rise to wrinkling budding \cite{Lowengrub2009_PRE,Li2012_CommMathSci}, adhesion and fusion \cite{Zhao2011_PRE} of vesicle membrane, closely related to cellular budding and fission processes \cite{Rauch2000_BiophysJ} as well as in cellular adhesion and fusion \cite{Takeda2003_PNAS}.
+Biological membranes, as the basic structural units for
+compartmentalizing biological systems, have been observed to contain a
+vast array of proteins and different lipid species, that phase-separate
+and form domains or rafts, resulting in spatial variations in material
+properties such as bending stiffness. Synthetic multicomponent vesicles,
+self-enclosed lipid bilayer membranes composed of different lipid
+species, have been used to study the rich patterns and accompanying
+morphologies that emerge from elastic heterogeneity in the membrane. In
+a quiescent environment, such elastic heterogeneity gives rise to
+wrinkling budding~\cite{Lowengrub2009_PRE, Li2012_CommMathSci}, adhesion
+and fusion~\cite{Zhao2011_PRE} of vesicle membrane, closely related to
+cellular budding and fission processes~\cite{Rauch2000_BiophysJ} as well
+as in cellular adhesion and fusion~\cite{Takeda2003_PNAS}.
 
@@
 Under a linear shear flow, a multicomponent vesicle exhibits more exotic
-dynamics in both shape and membrane composition
-\cite{soh-tse-li-voi-low2010,
-Smith2007_JChemPhys,Cox2015_Nonlinearity,liu-mar-li-vee-low2017,Tusch2018_PRF,Gera2018_SoftMatter,ger-sal-spa2022}
-than a single-component vesicle.  For example, multicomponent vesicles
-under a background flow often exhibit highly complex morphologies,
-leading to vesicle budding.  The hydrodynamics of these multicomponent
-vesicles include phase treading, tumbling with no viscosity contrast,
-swinging, budding, and fission~\cite{soh-tse-li-voi-low2010, wan-du2008,
-all-ama2006, ger-sal-spa2022, lip1992, urs-klu-phi2009}.  Through
-numerical investigations,~\citet{liu-mar-li-vee-low2017}
-identified several key dimensionless numbers, including the reduced
-area, capillary number, and the floppy-to-stiff ratio to characterize
-various dynamics of a multicomponent vesicle in an unbounded linear
-shear flow. In addition to the aforementioned numerical studies, these
-dynamics have been observed in experiments~\cite{bag-sun2009,
-yan-ima-tan2010, yan-ima-tan2008, dre-jah-bob-spa-gop2021}.
+dynamics in both shape and membrane
+composition~\cite{soh-tse-li-voi-low2010, Smith2007_JChemPhys
+Cox2015_Nonlinearity, liu-mar-li-vee-low2017, Tusch2018_PRF,
+Gera2018_SoftMatter, ger-sal-spa2022} than a single-component vesicle.
+For example, multicomponent vesicles under a background flow often
+exhibit highly complex morphologies, leading to vesicle budding. The
+hydrodynamics of these multicomponent vesicles include phase treading,
+tumbling with no viscosity contrast, swinging, budding, and
+fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006,
+ger-sal-spa2022, lip1992, urs-klu-phi2009}. Through numerical
+investigations,~\citet{liu-mar-li-vee-low2017} identified several key
+dimensionless numbers, including the reduced area, capillary number, and
+the floppy-to-stiff ratio to characterize various dynamics of a
+multicomponent vesicle in an unbounded linear shear flow. In addition to
+the aforementioned numerical studies, these dynamics have been observed
+in experiments~\cite{bag-sun2009, yan-ima-tan2010, yan-ima-tan2008,
+dre-jah-bob-spa-gop2021}.
 
@@
   arrows). The lubrication layer (gray region), defined in
-  Section~\ref{sec:LL} also plays a key role in the vesicle dynamics.}
+  Section~\ref{sec:LL} plays a key role in the vesicle dynamics.}
 %  \caption{\label{fig:schematic}\small A single multicomponent vesicle
@@
 for a vesicle with a floppy-to-stiff ratio $\beta = 10^{-1}$. Using the
-linear bending model~\eqref{eqn:linearBending}, the lipid concentration
-achieves a maximum value of $u \approx 1.5$ which results in an
-instability that is formed by a corresponding unphysical negative
-bending stiffness of $b(u) \approx -0.5$. To rectify this issue, we
-parameterize the bending modulus as
+linear bending model in Equation~\eqref{eqn:linearBending}, the lipid
+concentration achieves a maximum value of $u \approx 1.5$ which results
+in an instability that is formed by the resulting unphysical negative
+bending stiffness $b(u) \approx -0.5$. To rectify this issue, we
+parameterize the bending modulus as the sigmoid function
 \begin{align}
@@
   entering a closely-fitting channel (black lines) using the linear
-  model~\eqref{eqn:linearBending}. An instability is introduced where
-  the vesicle bending modulus becomes negative. (b) The linear bending
-  model in red (equation~\eqref{eqn:linearBending}) and the new
-  hyperbolic bending model in blue (equation~\eqref{eqn:tanhBending}).
-  Note that the new bending model satisfies $b \in (\beta,1)$ even if $u
-  \notin [0,1]$.}
+  model in Equation~\eqref{eqn:linearBending}. An instability is
+  introduced where the vesicle bending modulus becomes negative. (b) The
+  linear bending model in red (Equation~\eqref{eqn:linearBending}) and
+  the new sigmoid bending model in blue
+  (Equation~\eqref{eqn:tanhBending}).  Note that the new bending model
+  satisfies $b \in (\beta,1)$ even if $u \notin [0,1]$.}
 \end{figure}
@@
 \end{align}
-and $\rr = \xx - \yy$, $\rho = |\rr|$, and $\mathds{I}$ is the $2 \times
-2$ identity matrix. To avoid tangling of the vesicle membrane, it is
-parameterized in terms of the $\theta$-$L$
-variables~\cite{hou-low-she1994}, where $L$ is the fixed vesicle length
-and $\theta$ is the opening angle of the tangent vector $\ss$. This
-requires decomposing the velocity field on $\gamma$ into a normal
-velocity $V$ and tangential velocity $T$. Then, the no-slip boundary
-condition for the vesicle velocity is
+$\rr = \xx - \yy$, $\rho = |\rr|$, and $\mathds{I}$ is the $2 \times 2$
+identity matrix. The corresponding pressure at $\xx \in \Omega$ is
+\begin{align}
+  p(\xx) = \frac{1}{2\pi} \int_{\gamma} \frac{\rr \cdot \ff}{\rho^2} \, ds_\yy + 
+    \frac{1}{\pi} \int_{\Gamma} \frac{1}{\rho^2} 
+    \left(\mathds{I} - 2\frac{\rr \otimes \rr}{\rho^2} \right) 
+    \nn \cdot \eeta \, ds_\yy.
+\end{align}
+
+To avoid tangling, the vesicle membrane is parameterized in terms of the
+$\theta$-$L$ variables~\cite{hou-low-she1994}, where $L$ is the fixed
+vesicle length and $\theta$ is the opening angle of the tangent vector
+$\ss$. This requires decomposing the velocity field on $\gamma$ into a
+normal velocity $V$ and tangential velocity $T$. Then, the no-slip
+boundary condition for the vesicle velocity is
 \begin{align}
@@
 \label{sec:validation}
-We validate the new bending model~\eqref{eqn:tanhBending} by reproducing
-the dynamics reported in the literature. Figure~\ref{fig:treading} shows
-a phase treading (top) and a tank-treading (bottom) multicomponent
-vesicle in an unconfined shear flow. These simulations align with the
-results reported by~\citet{liu-mar-li-vee-low2017} (cf.~Figure 3).
+We validate the new sigmoid bending model in
+Equation~\eqref{eqn:tanhBending} by reproducing dynamics reported in the
+literature. Figure~\ref{fig:treading} shows a phase treading (top) and a
+tank-treading (bottom) multicomponent vesicle in an unconfined shear
+flow. These simulations align with the results reported
+by~\citet{liu-mar-li-vee-low2017} (cf.~Figure 3).
 \begin{figure}[h]
@@
   linear shear flow undergoes phase-treading (top) and tank-treading
-  (bottom) with the new bending model~\eqref{eqn:tanhBending}. The red
-  region is stiff and the blue region is floppy. The simulations
-  qualitatively agree with the results presented
-  by~\citet{liu-mar-li-vee-low2017}.}
+  (bottom) with the new sigmoid bending model in
+  Equation~\eqref{eqn:tanhBending}. The red region is stiff and the blue
+  region is floppy. The simulations qualitatively agree with the results
+  presented by~\citet{liu-mar-li-vee-low2017}.}
 \end{figure}
@@
 critical role in the dynamics of a vesicle under strong confinement.
-Therefore, throughout
-Section~\ref{sec:results}, we calculate and analyze the flow
-inside the lubrication layers between the vesicle and the channel walls to elucidate the correlation between hydrodynamics and membrane dynamics.
-%We first justify the use of the term `lubrication layer' by verifying
-%that the flow velocity is parabolic between the vesicle and the solid
-%wall. Figure~\ref{fig:quadraticProof} illustrates the horizontal
-%velocity (solid line) and the corresponding best fit quadratic (dashed
-%line) in the co-moving frame, and the profiles agree.
-%
-%\begin{figure}[H]
-%    \centering
-%    \includegraphics[width=\columnwidth]{figures/lubricationLayer_quadratic.pdf}  
-%    \caption{The co-moving velocity profile in the top and bottom lubrication layers. The red curve is the velocity profile, the dashed black line is the best quadratic fit.}
-%    \label{fig:quadraticProof}
-%\end{figure}
-To define the size of the top lubrication layer (the size of the bottom
-lubrication layer is defined similarly), we let
+Therefore, throughout Section~\ref{sec:results}, we calculate and
+analyze the flow inside the lubrication layers between the vesicle and
+the channel walls to elucidate the correlation between hydrodynamics and
+membrane dynamics. To define the size of the top lubrication layer (the
+size of the bottom lubrication layer is defined similarly), we let
 $d(\xx,\Gamma_\mathrm{top})$ be the minimum distance between a point on
 the vesicle, $\xx \in \gamma$, and the top half of the confining
-geometry.
-%\begin{align}
-%    d(\xx,\Gamma_\mathrm{top}) = \inf_{\yy \in \Gamma_\mathrm{top}} \|\xx-\yy\|,
-%\end{align}
-%where $\Gamma_{\mathrm{top}}$ is the top portion of $\Gamma$.
-We find all local minimums of $d(\xx,\Gamma_\mathrm{top})$, with
-the condition that $d(\xx,\Gamma_\mathrm{top}) < \delta$, where $\delta$
-is a parameter. If no such local minimums exist, then the vesicle is too
-far from $\Gamma_\mathrm{top}$ to define a lubrication layer. If there
-are two or more local minimums, the left-most, $\xx_L$, and right-most,
-$\xx_R$, local minimums form the start and end of the lubrication layer.
-If there is only one local minimum, then $\xx_L$ and $\xx_R$ are the
-points on $\gamma$ to the left and right of this local minimum with the
-condition that $d(\xx_L,\Gamma_\mathrm{top}) =
+geometry. We find all local minimums of $d(\xx,\Gamma_\mathrm{top})$,
+with the condition that $d(\xx,\Gamma_\mathrm{top}) < \delta$, where
+$\delta$ is a parameter. If no such local minimums exist, then the
+vesicle is too far from $\Gamma_\mathrm{top}$ to define a lubrication
+layer. If there are two or more local minimums, the left-most, $\xx_L$,
+and right-most, $\xx_R$, local minimums form the start and end of the
+lubrication layer.  If there is only one local minimum, then $\xx_L$ and
+$\xx_R$ are the points on $\gamma$ to the left and right of this local
+minimum with the condition that $d(\xx_L,\Gamma_\mathrm{top}) =
 d(\xx_R,\Gamma_\mathrm{top}) = \delta$. Then, the segment
@@
 illustrated in Figure~\ref{fig:schematic}, and the height of the gray
-regions denote the lubrication layer thickness. In this example, the top
-layer is broken across three different regions.
-
-%The terminology of boundary layer can be justified by computing the
-%velocity field in the region between the vesicle and the solid wall. In
-%Figure~\ref{fig:BkgrdFlow}, the co-moving velocity field around several
-%different vesicle shapes that are observed in Section~\ref{sec:results}
-%are illustrated. We have included plots of the horizontal velocity
-%along a few vertical slices to demonstrate that a parabolic flow
-%profile is observed.
+regions denote the lubrication layer thicknesses. In this example, the
+top layer is broken across three different regions.
 
@@
 indicates that the vesicle membrane shape is asymmetric with respect to
-the center of the channel,
-and this results in tank-treading behavior~\cite{aga-bir2020}.  To
-determine if a vesicle is tank-treading, we calculate the tangential
-velocity at several points on $\gamma$, and if this value is constant,
-this is the tank-treading velocity.
-
-%\begin{figure}[H]
-%\begin{minipage}{0.49\columnwidth}
-%    \centering
-%    \subfigimg[width = \columnwidth, trim = {2cm 2cm 2cm 2cm }, clip]{(a)}{figures/Fig7a1.pdf}
-%    \subfigimg[width = \columnwidth, trim = {2cm 2cm 2cm 2cm }, clip]{(b)}{figures/Fig7b1.pdf}
-%    \subfigimg[width = \columnwidth, trim = {2cm 2cm 2cm 2cm }, clip]{(c)}{figures/Fig7c1.pdf}
-%\end{minipage}   
-%\hfill
-%\begin{minipage}{0.49\columnwidth}
-%    \centering
-%    \subfigimg[width = \columnwidth, trim = {2cm 2cm 2cm 2cm }, clip]{\color{white}(a)}{figures/Fig7a2.pdf}
-%    \subfigimg[width = \columnwidth, trim = {2cm 2cm 2cm 2cm }, clip]{\color{white}(b)}{figures/Fig7b2.pdf}
-%    \subfigimg[width = \columnwidth, trim = {2cm 2cm 2cm 2cm }, clip]{\color{white}(c)}{figures/Fig7c2.pdf}
-%\end{minipage}
-%\caption{\label{fig:BkgrdFlow} \small The velocity in the bulk, at two time steps, of a vesicle with reduced area $\alpha=0.4$.
-The velocity field is in the co-moving frame.
-The vesicles are (a) single-component with $b = 1$; (b) single-component with $b = 0.55$; and (c) multicomponent.
-The tangential velocity in the tubular neighborhood around the vesicle indicates that (a) and (c) are tank-treading.}
-%\end{figure}
+the center of the channel, and this results in tank-treading
+behavior~\cite{aga-bir2020}. To determine if a vesicle is tank-treading,
+we calculate the tangential velocity at several points on $\gamma$, and
+if this value is constant, this is the tank-treading velocity.
 
@@
 outlets of the confining geometry, and the vesicle itself is never near
-these locations. Since we use a layer potential formulation, the
-pressure at $\xx \in \Omega$ is
-\begin{align}
-  p(\xx) = \frac{1}{2\pi} \int_{\gamma} \frac{\rr \cdot \ff}{\rho^2} \, ds_\yy + 
-    \frac{1}{\pi} \int_{\Gamma} \frac{1}{\rho^2} 
-    \left(\mathds{I} - 2\frac{\rr \otimes \rr}{\rho^2} \right) 
-    \nn \cdot \eeta \, ds_\yy.
-\end{align}
-%These pressure drops are defined by
-%subtracting the pressure at a point near the inlet and another near the
-%outlet. In our formulation, because of the order of subtraction, the
-%excess pressure is always negative.
-
-%We follow the reformulation of the governing equations outlined in Section 3.1 of \cite{soh-tse-li-voi-low2010}.
-In particular, we do a change of variables to the $\theta$-L formulation, where $L$ is the total length of the vesicle and $\theta$ is the opening angle of its tangent vector, $\ss$.
-%This formulation provides us with the location of a unique vesicle shape up to a translation.
-%, which we resolve by tracking the vesicle's center of mass.
-After this change of variables, the dynamics of $\theta$ are governed by
-%The formulation requires the normal and tangential components of the velocity, 
-%\begin{equation}
-%V = \uu \cdot \nn \qquad \text{and} \qquad T = \uu \cdot \ss, \label{NormTanComp} 
-%\end{equation}
-%where $\nn$ is the unit normal vector and $\ss$ is the unit tangent vector. In the $\theta$-L formulation, the governing equation of the vesicle
-%\begin{equation}
-%\frac{d\xx}{dt} =V\nn+T\ss,
-%\end{equation}
-%becomes
-%\begin{equation}
-%\theta_t =  -(V+\beta(\textbf{f}\cdot\textbf{n}))_s + \kappa T
-%\theta_t =  -V_s + \kappa T,
-%\end{equation}
-%and the inextensibility condition becomes
-%\begin{equation}
-%T_s+\kappa V  = 0. \label{genInexMC}
-%\end{equation}
-%Recall that the velocity $\uu$ is coupled to the tension $\sigma^{LL}$ which acts as a Lagrange multiplier to satisfy equation \eqref{genInexMC}.
+these locations.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{\label{subsec:Stenosis}A multicomponent vesicle in the
@@
 single-component (b) floppy single-component, and (c) multicomponent
-vesicle. The initial lipid distribution of the multicomponent vesicle is random.
-In all plots, the color is the dimensionless bending modulus of the
-multicomponent vesicle that remains bounded in $[0.1,1]$ by using the
-new bending modulus~\eqref{eqn:tanhBending}. A single Lagrangian point
-is included to visualize any tank-treading behavior. There are slight
-differences between the three cases, with the most noticeable being that
-the multicomponent vesicle has higher curvature in the floppy region.
-However, in general, there is little difference between these cases,
-partially because these vesicles have a large reduced area.
+vesicle. The initial lipid distribution of the multicomponent vesicle is
+random. In all plots, the color is the dimensionless bending modulus of
+the multicomponent vesicle that remains bounded in $[0.1,1]$ by using
+the new sigmoid bending modulus in Equation~\eqref{eqn:tanhBending}. A
+single Lagrangian point is included to visualize any tank-treading
+behavior. There are slight differences between the three cases, with the
+most noticeable being that the multicomponent vesicle has higher
+curvature in the floppy region.  However, in general, there is little
+difference between these cases, partially because these vesicles have a
+large reduced area.
 
@@
 shapes at the same six time steps when the percentage of the floppy
-region is 0\% (single-component), \%15, \%25, \%35, and \%45. One effect
+region is 0\% (single-component), 15\%, 25\%, 35\%, and 45\%. One effect
 of the size of the floppy region is that the symmetry of the vesicle

### 2023-08-14 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
picking away at the paper

@@
 $b(u) = 1$ and $b(u) = 0.55$. % which is the average bending stiffness of a multicomponent vesicle whose stiff and floppy regions have the same area. 
-The latter value represents the average bending stiffness of a multicomponent vesicle, where the stiff and floppy regions have the same area.
-Throughout this section we plot the position of the vesicle in terms of the $x$-coordinate of its center of mass.
-For the stenosed
-geometry in Section~\ref{subsec:Stenosis}, the narrow region begins at
-$x=-15$ and ends at $x=15$. For the contracting geometry in
+The latter value represents the average bending stiffness of a
+multicomponent vesicle, when the stiff and floppy regions cover the same
+amount of area. Throughout this section we plot the position of the
+vesicle in terms of the $x$-coordinate of its center of mass. For the
+stenosis geometry in Section~\ref{subsec:Stenosis}, the narrow region
+begins at $x=-15$ and ends at $x=15$. For the contracting geometry in
 Section~\ref{subsec:Contraction}, the geometry begins to narrow at $x=4$

### 2023-08-14 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working through stenosis example

@@
   geometry. The vesicle's reduced area is $\alpha = 0.6$ and the
-  capillary number is $Ca = 0.25$. The vesicles are: (a)
-  single-component with bending modulus $b=1$; (b) single-component with
-  bending modulus $b=0.55$; (c) multicomponent.}
+  capillary number is $Ca = 0.25$. The vesicles are: (a) stiff
+  single-component; (b) floppy single-component; (c) multicomponent.}
 %\end{figure}
@@
 For the single-component case, we consider two bending stiffnesses:
-$b(u) = 1$ and $b(u) = 0.55$. % which is the average bending stiffness of a multicomponent vesicle whose stiff and floppy regions have the same area. 
-The latter value represents the average bending stiffness of a
-multicomponent vesicle, when the stiff and floppy regions cover the same
-amount of area. Throughout this section we plot the position of the
-vesicle in terms of the $x$-coordinate of its center of mass. For the
-stenosis geometry in Section~\ref{subsec:Stenosis}, the narrow region
-begins at $x=-15$ and ends at $x=15$. For the contracting geometry in
-Section~\ref{subsec:Contraction}, the geometry begins to narrow at $x=4$
-and reaches its narrowest point at $x=15$.
+$b(u) = 1$ and $b(u) = 0.55$. We refer to these cases as a stiff
+single-component vesicle and floppy single-component vesicle,
+respectively. The smaller bending stiffness represents the average
+bending stiffness of a multicomponent vesicle, when its stiff and floppy
+regions cover the same amount of area. Throughout this section we plot
+the position of the vesicle in terms of the $x$-coordinate of its center
+of mass. For the stenosis geometry in Section~\ref{subsec:Stenosis}, the
+narrow region begins at $x=-15$ and ends at $x=15$. For the contracting
+geometry in Section~\ref{subsec:Contraction}, the geometry begins to
+narrow at $x=4$ and reaches its narrowest point at $x=15$.
 
@@
 We start by considering a vesicle with reduced area $\alpha = 0.6$
-passing through stenosis with a capillary number $Ca = 0.25$.
-With the current setup and $Ca=0.25$, an elliptical vesicle with reduced area greater than
-$\alpha = 0.8$ cannot fit through the closely-fitting geometry.
-
-Figure~\ref{fig:RA6} shows six time steps of a (a) stiff
+passing through stenosis with a capillary number $Ca = 0.25$.  With the
+current setup and $Ca=0.25$, an elliptical vesicle with reduced area
+greater than $\alpha = 0.8$ cannot fit through the closely-fitting
+geometry. Figure~\ref{fig:RA6} shows six time steps of a (a) stiff
 single-component (b) floppy single-component, and (c) multicomponent
-vesicle. The initial lipid distribution of the multicomponent vesicle is
-random. In all plots, the color is the dimensionless bending modulus of
-the multicomponent vesicle that remains bounded in $[0.1,1]$ by using
-the new sigmoid bending modulus in Equation~\eqref{eqn:tanhBending}. A
-single Lagrangian point is included to visualize any tank-treading
-behavior. There are slight differences between the three cases, with the
-most noticeable being that the multicomponent vesicle has higher
-curvature in the floppy region.  However, in general, there is little
-difference between these cases, partially because these vesicles have a
-large reduced area.
+vesicle. The lipid distribution of the multicomponent vesicle is
+initially random with a mean value of 0.55. In all plots, the color is
+the dimensionless bending modulus of the multicomponent vesicle that
+remains bounded in $[0.1,1]$ by using the new sigmoid bending modulus in
+Equation~\eqref{eqn:tanhBending}. A single Lagrangian point is included
+to visualize any tank-treading behavior. There are slight differences
+between the three cases, with the most noticeable being that the
+multicomponent vesicle has higher curvature in the floppy region.
+However, in general, there is little difference between these cases,
+principally because these vesicles have a large reduced area.
 
@@
   \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp4MCp5.pdf}
-%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig6a.pdf}
-%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig6b.pdf}
-%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig6c.pdf}
   \caption{\label{fig:RA4} \small A vesicle passing through the stenosis
   geometry. The vesicle's reduced area is $\alpha = 0.4$ and the
-  capillary number is $Ca = 0.25$. The vesicles are: (a) single-component
-  with bending modulus $b=1$; (b) single-component with bending modulus
-  $b=0.55$; (c) multicomponent.}
+  capillary number is $Ca = 0.25$. The vesicles are: (a) stiff
+  single-component; (b) floppy single-component; (c) multicomponent.}
 \end{figure*}

### 2023-08-14 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
first draft of new tank-treading behavior

@@
   \caption{\label{fig:Energy} \small The bending (blue), tension (red),
-  and phase (magenta) energies for a (a) stiff single-component, (b)
+  and phase (magenta) energies of a (a) stiff single-component, (b)
   floppy single-component, and (c) multicomponent vesicle. The reduced
@@
 
-Next we consider a vesicle with a smaller reduced area $\alpha=0.4$ with the same geometry and $Ca=0.25$.
-Figure~\ref{fig:RA4} shows  the shape of  
-a (a) stiff single-component, (b) floppy single-component, and (c) multicomponent
-vesicle at six locations along the stenosis channel. We first consider the three different energies---bending,
-tension, and phase---for each of these cases. In
-Figure~\ref{fig:Energy}, we plot these energies as a function of the
-vesicle's center. As a reminder, the vesicle enters the constriction at
-$x=-15$ and exits at $x=15$. Also note that the single-component
-vesicles do not have a phase energy. 
-%A few general trends can immediately be seen. 
-First we observe that, as the vesicle enters the stenosis, it
-develops regions of high curvature, and this results in an increase in
-the bending energy. Secondly, as the stiff single-component and
-multicomponent vesicles reach a steady-state shape near the middle of
-the channel, their bending, tension, and phase energies remain nearly
-constant from $x=0$ until the end of the stenosis. For the multiple-component vesicle,
-this implies that there is no coarsening of lipid phase in the middle of a stenosis.
+Next we consider a vesicle with a smaller reduced area $\alpha=0.4$ with
+the same geometry and $Ca=0.25$. Figure~\ref{fig:RA4} shows the shape of
+a (a) stiff single-component, (b) floppy single-component, and (c)
+multicomponent vesicle at six locations along the stenosis channel. We
+first consider the three different energies---bending, tension, and
+phase---for each example. In Figure~\ref{fig:Energy}, we plot these
+energies as a function of the vesicle's center. As a reminder, the
+vesicle enters the constriction at $x=-15$ and exits at $x=15$. Also
+note that the single-component vesicles do not have a phase energy.  We
+observe that, as the vesicle enters the stenosis, it develops regions of
+high curvature, and this results in an increase in the bending energy.
+As the stiff single-component and multicomponent vesicles reach a
+steady-state shape near the middle of the channel, their bending,
+tension, and phase energies remain nearly constant from $x=0$ until the
+end of the stenosis. For the multiple-component vesicle, this implies
+that there is no coarsening of lipid phase parameter in the middle of a
+stenosis.
 
 %This corresponds to an arrest of phase coarsening for a vesicle confined in a stenosis.
-Such co-existence of multiple lipid domains in a vesicle under confinement
-results in interesting additional physics. 
-%
-First we note that in Figure~\ref{fig:Energy}(c),
-the lipid species coarsens at
-three instances, and this results in a decrease in the phase energy.
-However, as we mentioned earlier, no coarsening occurs when the vesicle is in the
+The coexistence of multiple lipid domains in a vesicle under confinement
+results in additional interesting physics. We note that in
+Figure~\ref{fig:Energy}(c), the lipid species coarsens at three
+instances, and this results in a decrease in the phase energy. However,
+as we mentioned earlier, no coarsening occurs when the vesicle is in the
 closely-fitting part of the channel. Each coarsening corresponds either
@@
 
-%\begin{figure}
-%  \begin{minipage}{0.49\columnwidth}
-%    \centering
-%    \subfigimg[width=\textwidth]{(a)}{figures/Fig13a.pdf}
-%    \subfigimg[width=\textwidth]{(c)}{figures/Fig13c.pdf}
-%    \subfigimg[width=\textwidth]{(e)}{figures/Fig13e.pdf}
-%  \end{minipage}
-%  \hfill
-%  \begin{minipage}{0.49\columnwidth}
-%    \centering
-%    \subfigimg[width=\textwidth]{(b)}{figures/Fig13b.pdf}
-%    \subfigimg[width=\textwidth]{(d)}{figures/Fig13d.pdf}
-%    \subfigimg[width=\textwidth]{(f)}{figures/Fig13f.pdf}
-%  \end{minipage}
-%  \caption{\label{fig:Energy} \small The Bending (blue), tension
-%  (yellow), and phase (red) energies for a (a/b) single-component
-%  vesicle with $b=1$, (c/d) single-component vesicle with $b = 0.55$,
-%  and (e/f) multicomponent vesicle. The reduced areas are $\alpha = 0.4$
-%  (a/c/e) and $\alpha = 0.6$ (b/d/f).}
-%  \todo[inline]{need to redo these plots}
-%\end{figure}
-
 A main difference between the two reduced areas is that the vesicles
@@
 stiff single-component and multicomponent vesicles are clearly tank
-treading. Since the single-component case has a larger difference
-between its top and bottom boundary layers, it tank treads faster than
-the multicomponent case. In addition, since the top boundary layer is
-larger in both cases, they both tank-tread in the same
-direction---counterclockwise. In contrast, the floppy single-component
-vesicle tank treads in the clockwise direction; note, however, that this
-example is still undergoing some deformations, so a constant
-tank-treading velocity is not observed.
-%When $\alpha = 0.6$, the vesicle undergoes deformations while in the
-%stenosis, and a constant tank-treading velocity is not observed
-
-%\begin{figure}
-%    \begin{minipage}{0.49\columnwidth}
-%        \centering
-%        \includegraphics[width=\textwidth,trim={4cm 8cm 4cm 8cm}, clip]{figures/EnergiesRAp4NoConc.pdf}
-%    \end{minipage}
-%    \begin{minipage}{0.49\columnwidth}
-%        \centering
-%        \includegraphics[width=\textwidth,trim={4cm 8cm 4cm 8cm}, clip]{figures/EnergiesRAp4Conc.pdf}
-%    \end{minipage}
-%    \caption{Bending (blue), tension (yellow), and phase (red) energies for a single-component vesicle %(left) and a multi-component vesicle (right) with reduced area 0.4.}
-%    \label{fig:EnergyRAp4}
-%\end{figure}
-%\begin{figure}[H]
-%    \begin{minipage}{0.49\columnwidth}
-%        \centering
-%        \includegraphics[width=\textwidth,trim={4cm 8cm 4cm 8cm}, clip]{figures/EnergiesRAp6NoConc.pdf}
-%        \includegraphics[width=\textwidth,trim={4cm 8cm 4cm 8cm}, clip]{figures/EnergiesRAp6NoConcp55.pdf}
-%    \end{minipage}
-%    \hfill
-%    \begin{minipage}{0.49\columnwidth}
-%        \centering
-%        \includegraphics[width=\textwidth,trim={4cm 8cm 4cm 8cm}, clip]{figures/EnergiesRAp6Conc.pdf}
-%        \vspace{3.5cm}
-%    \end{minipage}
-%    \caption{Bending (blue), tension (yellow), and phase (red) energies for a single-component vesicle %(left) and a multi-component vesicle (right) with reduced area 0.6.}
-%    \label{fig:EnergyRAp6l}
-%\end{figure}
-
-%\begin{figure}[h]
-%    \centering
-%    \subfigimg[width = 0.49\columnwidth]{(a)}{figures/Layer_Size_RAp4.pdf}
-%%    \subfigimg[width = 0.49\columnwidth]{(b)}{figures/Layer_Size_RAp6.pdf}
-%%    \subfigimg[width = \columnwidth]{(a)}{figures/Fig8a.pdf}\\
-%%    \subfigimg[width = \columnwidth]{(b)}{figures/Fig8b.pdf}
-%    \caption{\label{fig:lubrication} \small The size of the lubrication
-%    layer of a stiff single-component (red), floppy single-component
-%    (green), and multicomponent (blue) vesicle passing through stenosis.
-%    Solid lines are the layer thickness between the vesicle and the top
-%    wall, and dashed lines are the layer thickness between the vesicle
-%    and the bottom wall. The reduced area of the vesicles are (a)
-%    $\alpha = 0.4$ and (b) $\alpha = 0.6$.}
-%\end{figure}
+treading. The direction and speed of the tank-treading depends on the
+how much of the vesicle membrane is exposed to positive shear (below the
+center line) versus how much is exposed to negative shear (above the
+center line). The majority of the membrane of the stiff single-component
+and multicomponent vesicles are below the center line, and this results
+in a clockwise tank-treading behavior. In contrast, the majority of the
+membrane of the floppy single-component vesicle is above the center
+line, and the result is counterclockwise tank-treading. In addition, the
+tank-treading velocity can be correlated to the percentage of its
+membrane that is below the center line. We note, however, that the
+floppy single-component vesicle is still undergoing deformations, so the
+tangential velocities have not converged to a fixed value.
+
+%Since the single-component case has a larger difference
+%between its top and bottom boundary layers, it tank treads faster than
+%the multicomponent case. In addition, since the top boundary layer is
+%larger in both cases, they both tank-tread in the same
+%direction---counterclockwise. In contrast, the floppy single-component
+%vesicle tank treads in the clockwise direction; note, however, that this
+%example is still undergoing some deformations, so a constant
+%tank-treading velocity is not observed.
 
@@
   black dashed line is the center line of the channel, and the arrow
-  denotes the tank-treading direction.}
+  denotes the tank-treading direction. The percentage of the vesicle
+  membrane that is below the center line is (a) \%72, (b) \%44, and (c)
+  \%68.}
 %\end{figure}
@@
 the excess pressure. The magenta curve on the top half of
-Figure~\ref{fig:lubricationComposite} shows the excess pressure (with the
-axis aligned on the right side of the plot). When the lubrication layers
-are large, most notably for the multicomponent vesicle, less pressure is
-required to force the vesicle through the geometry, and the result is a
-smaller (less negative) excess pressure. In contrast, when the
-lubrication layers are small, most notably for the stiff
+Figure~\ref{fig:lubricationComposite} shows the excess pressure (with
+the axis aligned on the right side of the plot). When the lubrication
+layers are large, most notably for the multicomponent vesicle, less
+pressure is required to force the vesicle through the geometry, and the
+result is a smaller (less negative) excess pressure. In contrast, when
+the lubrication layers are small, most notably for the stiff
 single-component vesicle, more pressure is required to force the vesicle

### 2023-08-14 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on tank treading

@@
 Figure~\ref{fig:lubricationComposite}. Also included in the bottom of
-Figure~\ref{fig:lubricationComposite} are the tank-treading velocities.
-The four marker points are the Lagrangian points where the tank-treading
-velocities are computed, the black dashed line is the center line of the
-channel, and the rounded arrow denotes the direction of rotation. The
-stiff single-component and multicomponent vesicles are clearly tank
-treading. The direction and speed of the tank-treading depends on the
-how much of the vesicle membrane is exposed to positive shear (below the
-center line) versus how much is exposed to negative shear (above the
-center line). The majority of the membrane of the stiff single-component
-and multicomponent vesicles are below the center line, and this results
-in a clockwise tank-treading behavior. In contrast, the majority of the
-membrane of the floppy single-component vesicle is above the center
-line, and the result is counterclockwise tank-treading. In addition, the
-tank-treading velocity can be correlated to the percentage of its
-membrane that is below the center line. We note, however, that the
-floppy single-component vesicle is still undergoing deformations, so the
-tangential velocities have not converged to a fixed value.
+Figure~\ref{fig:lubricationComposite} are the tank-treading velocities
+of four Lagrangian points. The inset shows the vesicle configuration in
+the closely-fitting part of the channel, the black dashed line is the
+center line of the channel, and the rounded arrow denotes the direction
+of rotation. The stiff single-component and multicomponent vesicles are
+clearly tank treading. The direction and speed of the tank-treading
+depends on the how much of the vesicle membrane is exposed to positive
+shear (below the center line) versus how much is exposed to negative
+shear (above the center line). The majority of the membrane of the stiff
+single-component and multicomponent vesicles are below the center line,
+and this results in a clockwise tank-treading behavior. In contrast, the
+majority of the membrane of the floppy single-component vesicle is above
+the center line, and the result is counterclockwise tank-treading. In
+addition, the tank-treading velocity can be correlated to the percentage
+of its membrane that is below the center line. We note, however, that
+the floppy single-component vesicle is still undergoing deformations, so
+the tangential velocities have not converged to a fixed value.
 

### 2023-08-14 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
small change

@@
 dynamics in both shape and membrane
-composition~\cite{soh-tse-li-voi-low2010, Smith2007_JChemPhys
+composition~\cite{soh-tse-li-voi-low2010, Smith2007_JChemPhys,
 Cox2015_Nonlinearity, liu-mar-li-vee-low2017, Tusch2018_PRF,
@@
   denotes the tank-treading direction. The percentage of the vesicle
-  membrane that is below the center line is (a) \%72, (b) \%44, and (c)
-  \%68.}
+  membrane that is below the center line is (a) 72\%, (b) 44\%, and (c)
+  68\%.}
 %\end{figure}

### 2023-08-15 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

@@
 In this paper, we use numerical simulations and lubrication analysis
-\cite{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019} to
+\cite{YoungStone2017_PRF,mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019} to
 investigate the effect of strong confinement on a two-dimensional

### 2023-08-15 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
edited up to section 2

--- 2023-08-14 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
@@
   confining geometries. This serves as a simplified model for red blood
-  cells passing through extreme constrictions. We propose a new bending
-  modulus parameterization so that it remains positive for all values of
-  the lipid phase parameter. For a multicomponent vesicle passing
-  through a stenosis, we correlate the lipid phase coarsening, the
-  lubrication layer properties (size and flow profile), the excess
-  pressure, and the tank-treading velocity of the membrane. For a
-  multicomponent vesicle passing through a contracting channel, we find
-  that the lipid always phase separates so that the vesicle is stiffer
-  in the front as it passes through the constriction. For both cases of
-  confinement we find that the lipid coarsening is arrested under strong
-  confinement, and proceeds with high rate upon relief from extreme
-  confinement. The results may be useful for efficient sorting lipid
-  domains using microfluidic flows by controlled release of vesicles
-  passing through strong confinement. } \\
+  cells undergoing large deformations when passing through extreme
+  constrictions. We propose a new bending modulus parameterization that
+  is positive for all values of the lipid phase parameter. For a
+  multicomponent vesicle passing through a stenosis, we correlate the
+  lipid phase coarsening, the lubrication layer properties (size and
+  flow profile), the excess pressure, and the tank-treading velocity of
+  the membrane. For a multicomponent vesicle passing through a
+  contracting channel, we find that the lipid always phase separates so
+  that the vesicle is stiffer in the front as it passes through the
+  constriction. For both cases of confinement we find that the lipid
+  coarsening is arrested under strong confinement, and proceeds with
+  high rate upon relief from extreme confinement. The results may be
+  useful for efficient sorting lipid domains using microfluidic flows by
+  controlled release of vesicles passing through strong confinement.} \\
   %The abstrast goes here instead of the text "The abstract should
@@
 \section{\label{sec:Introduction}Introduction}
-Biological membranes, as the basic structural units for
-compartmentalizing biological systems, have been observed to contain a
-vast array of proteins and different lipid species, that phase-separate
-and form domains or rafts, resulting in spatial variations in material
-properties such as bending stiffness. Synthetic multicomponent vesicles,
+Biological membranes, the basic structural units for compartmentalizing
+biological systems, have been observed to contain a vast array of
+proteins and different lipid species that phase-separate and form
+domains or rafts, resulting in spatial variations in material properties
+such as bending stiffness. Synthetic multicomponent vesicles,
 self-enclosed lipid bilayer membranes composed of different lipid
@@
 parameters such as the capillary number, reduced volume, and confinement
-ratio \cite{Abreu2014_ACI}. Such characterization is often useful for
+ratio~\cite{Abreu2014_ACI}. Such characterization is often useful for
 inferring fluid and material properties.
@@
 For example, a vesicle's reduced volume and viscosity contrast determine
-if it undergoes tank-treading, swinging, or tumbling in a shear
+if it undergoes tank-treading, swinging, or tumbling in a linear shear
 flow~\cite{nog-gom2005}. Transitions in the vesicle shape occur in
@@
 Under a linear shear flow, a multicomponent vesicle exhibits more exotic
-dynamics in both shape and membrane
-composition~\cite{soh-tse-li-voi-low2010, Smith2007_JChemPhys,
+dynamics in both shape and membrane composition than a single-component
+vesicle~\cite{soh-tse-li-voi-low2010, Smith2007_JChemPhys,
 Cox2015_Nonlinearity, liu-mar-li-vee-low2017, Tusch2018_PRF,
-Gera2018_SoftMatter, ger-sal-spa2022} than a single-component vesicle.
-For example, multicomponent vesicles under a background flow often
-exhibit highly complex morphologies, leading to vesicle budding. The
-hydrodynamics of these multicomponent vesicles include phase treading,
-tumbling with no viscosity contrast, swinging, budding, and
+Gera2018_SoftMatter, ger-sal-spa2022}. For example, multicomponent
+vesicles under a background flow often exhibit highly complex
+morphologies, leading to vesicle budding. The hydrodynamics of these
+multicomponent vesicles include phase treading, tumbling with no
+viscosity contrast, swinging, budding, and
 fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006,
@@
 the floppy-to-stiff ratio to characterize various dynamics of a
-multicomponent vesicle in an unbounded linear shear flow. In addition to
-the aforementioned numerical studies, these dynamics have been observed
-in experiments~\cite{bag-sun2009, yan-ima-tan2010, yan-ima-tan2008,
-dre-jah-bob-spa-gop2021}.
-
-%
-%Sohn et al.
-(2010) studied two-dimensional multicomponent vesicles in a background shear flow, along with the evolution of distinct surface phases, finding highly complex morphologies and dynamics for highly deformed vesicles.
-Smith & Uspal (2007) showed using dissipative particle dynamics simulations that a shear flow can be used to separate buds from a multicomponent vesicle.
-The influence of both bending rigidity and spontaneous curvature variation on the equilibrium shape of a vesicle has also been investigated (Cox & Lowengrub 2015).
-Subsequent boundary integral simulations by Liu et al.
-(2017) showed a transition from tumbling to tank-treading to ‘phase-treading’ of the constituents along the surface upon increasing the shear rate.
-Analytic results have also shown that a variation of bending rigidity along a surface can induce migration in tank-treading vesicles (Olla 2011).
-Synthetic systems have also been fruitful for testing theoretical predictions.
-Experiments using a two-phase lipid vesicle in such a flow as a simplified model of red blood cell dynamics showed similarly complex features (Tusch et al.
-2018).
-Gera & Salac (2018b) then used simulations to probe a wide array of morphological changes due to spatially varying bending stiffness and line tension between two lipid phases.
-The phase separation process itself is naturally of great interest, and experiments have been used to study spinodal decomposition and viscous fingering along membrane surfaces (Veatch & Keller 2003; Lowengrub, Rätz & Voigt 2009; Marenduzzo & Orlandini 2013; Stanich et al.
-2013).
+two-dimensional multicomponent vesicle in an unbounded linear shear
+flow. In addition to the aforementioned numerical studies, these
+dynamics have been observed in experiments~\cite{bag-sun2009,
+yan-ima-tan2010, yan-ima-tan2008, dre-jah-bob-spa-gop2021}.
+
+%
+%Sohn et al. (2010) studied two-dimensional multicomponent vesicles in a
+%background shear flow, along with the evolution of distinct surface
+%phases, finding highly complex morphologies and dynamics for highly
+%deformed vesicles. Smith & Uspal (2007) showed using dissipative
+%particle dynamics simulations that a shear flow can be used to separate
+%buds from a multicomponent vesicle. The influence of both bending
+%rigidity and spontaneous curvature variation on the equilibrium shape
+%of a vesicle has also been investigated (Cox & Lowengrub 2015).
+%Subsequent boundary integral simulations by Liu et al. (2017) showed a
+%transition from tumbling to tank-treading to ‘phase-treading’ of the
+%constituents along the surface upon increasing the shear rate. Analytic
+%results have also shown that a variation of bending rigidity along a
+%surface can induce migration in tank-treading vesicles (Olla 2011).
+%Synthetic systems have also been fruitful for testing theoretical
+%predictions. Experiments using a two-phase lipid vesicle in such a flow
+%as a simplified model of red blood cell dynamics showed similarly
+%complex features (Tusch et al. 2018). Gera & Salac (2018b) then used
+%simulations to probe a wide array of morphological changes due to
+%spatially varying bending stiffness and line tension between two lipid
+%phases. The phase separation process itself is naturally of great
+%interest, and experiments have been used to study spinodal
+%decomposition and viscous fingering along membrane surfaces (Veatch &
+%Keller 2003; Lowengrub, Rätz & Voigt 2009; Marenduzzo & Orlandini 2013;
+%Stanich et al. 2013).
 %
@@
 %different types of lipids and proteins. The presence of different lipid
-%species has been used to model different processes including the bending
-%stiffness, spontaneous curvature, and adhesion
+%species has been used to model different processes including the
+%bending stiffness, spontaneous curvature, and adhesion
 %potential~\cite{zha-das-du2010, tan-yan-ima2011}. The dynamics of these
@@
 
-Hydrodynamics of vesicles in extreme confinement has been studied as a
+Hydrodynamics of vesicles in extreme confinement have been studied as a
 model system for red blood cells (RBCs) squeezing through small
-capillaries (of sub-micron size in diameter) under a pressure difference
-\cite{Freund2013_PoF, LuPeng2019_PoF, che-lyu-jae-leo2020,
+capillaries (of sub-micron size in diameter) under a pressure
+difference~\cite{Freund2013_PoF, LuPeng2019_PoF, che-lyu-jae-leo2020,
 gur-pak-tay-siv-sac2023}. Membrane permeability has been incorporated to
@@
 influx/efflux over a sufficiently long time or under a strong
-confinement \cite{qua-gan-you2021}. Numerical simulations illustrate
+confinement~\cite{qua-gan-you2021}. Numerical simulations illustrate
 that a vesicle with moderate membrane permeability can go through a
@@
 strong confinement may affect the hydrodynamics of a multicomponent
-vesicle? This question is highly relevant to hydrodynamics of cells in a
+vesicle. This question is highly relevant to hydrodynamics of cells in a
 confinement, and to our knowledge has not been well studied.
@@
 effective diffusion coefficient of the concentration fluctuation in
-multicomponent membranes. How is such reduced concentration diffusion
+multicomponent membranes. How is such a reduced concentration diffusion
 coefficient reflected in the hydrodynamics of multicomponent vesicles
@@
 
-In this paper, we use numerical simulations and lubrication analysis
-\cite{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019} to
+In this paper, we use numerical simulations and lubrication
+analysis~\cite{YoungStone2017_PRF,
+mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019} to
 investigate the effect of strong confinement on a two-dimensional
@@
 \section{\label{sec:Formulation}Formulation}
-\begin{figure}[H]
+\begin{figure}[h]
   \centering
@@
   arrows). The lubrication layer (gray region), defined in
-  Section~\ref{sec:LL} plays a key role in the vesicle dynamics.}
-%  \caption{\label{fig:schematic}\small A single multicomponent vesicle
-%  with boundary $\gamma$ suspended in a domain $\Omega$ with boundary
-%  $\Gamma$. The dark red regions are the ``stiff'' regions corresponding
-%  to the maximum bending stiffness $b_{\max}=1$. The dark blue regions
-%  are the ``floppy'' regions corresponding to the minimum bending
-%  stiffness $b_{\min}=0.1$ The vesicle dynamics are determined by a
-%  combination of phase, bending, and tension energies, and an imposed
-%  flow on $\Gamma$. }
+  Section~\ref{sec:LL}, plays a key role in the vesicle dynamics.}
 \end{figure}
@@
 Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a
-Hagen–Poiseuille flow at the inlet and outlet (where $y\in[-W,W]$),
+Hagen–Poiseuille flow at the inlet and outlet
 \begin{align}
@@
 \end{align}
-and $\UU$ is zero along the top and bottom of the channel.
+and $y \in [-W,W]$. $\UU$ is zero along the top and bottom of the
+channel.
 
@@
 sets the capillary number $Ca = U R_{0}^{2} \mu/b_{\max}$, and $W/R_0$
-is the dimensionless width of the channel at the inlet and outlet.
-Finally, the Peclet number of the lipid dynamics is taken to be $Pe = 1$
-which results in a diffusion time scale of $2 \times 10^{-4}$~s.
-Therefore, phase separation occurs at a rate three orders of magnitude
-faster than vesicle relaxation. The effect of the Peclet number has been
-examined~\cite{liu-mar-li-vee-low2017, soh-tse-li-voi-low2010}, and it
-has no qualitative effect on the vesicle dynamics. From this point
-onwards, all equations are dimensionless.
+is the dimensionless width of the channel which varies in both examples
+we consider. Finally, the Peclet number of the lipid dynamics is taken
+to be $Pe = 1$ which results in a diffusion time scale of $2 \times
+10^{-4}$~s. Therefore, phase separation occurs at a rate three orders of
+magnitude faster than vesicle relaxation. The effect of the Peclet
+number has been examined~\cite{liu-mar-li-vee-low2017,
+soh-tse-li-voi-low2010}, and it has no qualitative effect on the vesicle
+dynamics. From this point onwards, all equations are dimensionless.
 
@@
 where $u$ is the dimensionless lipid concentration, $b(u)$ is the
-lipid-dependent bending modulus, $\sigma$ is the vesicle's tension,
+lipid-dependent bending modulus, $\sigma$ is the membrane tension,
 $\kappa$ is the membrane curvature, and $f(u) = \frac{1}{4}u^2(1-u)^2$
@@
   \ff_b &= -(b(u)\kappa \nn)_{ss} -\frac{3}{2}
-    \left(b(u) \kappa^2 \ss\right)_s, \\
-  \ff_t &= (\sigma \ss)_s, \\
+    \left(b(u) \kappa^2 \ss\right)_s,  \quad
+  \ff_t = (\sigma \ss)_s, \\
   \ff_p &= \left(\frac{a}{\epsilon}\left(f(u) -
@@
 lipid concentration is not guaranteed to be confined to the interval
-$[0,1]$. This is problematic when $u > 1$ since this results in $b(u) <
-0$ if $u > (1 - \beta)^{-1}$, and such values of $u$ are possible when
-$\beta \ll 1$, $Ca \gg 1$, or the vesicle is confined to a narrow
-region. This behavior is demonstrated in Figure~\ref{fig:concModels}(a)
-for a vesicle with a floppy-to-stiff ratio $\beta = 10^{-1}$. Using the
-linear bending model in Equation~\eqref{eqn:linearBending}, the lipid
-concentration achieves a maximum value of $u \approx 1.5$ which results
-in an instability that is formed by the resulting unphysical negative
-bending stiffness $b(u) \approx -0.5$. To rectify this issue, we
-parameterize the bending modulus as the sigmoid function
+$[0,1]$. This is problematic since $b(u) < 0$ if $u > (1 - \beta)^{-1}$,
+and such values of $u$ are possible when $\beta \ll 1$, $Ca \gg 1$, or
+the vesicle is confined to a narrow region. This behavior is
+demonstrated in Figure~\ref{fig:concModels}(a) for a vesicle with a
+floppy-to-stiff ratio $\beta = 10^{-1}$. Using the linear bending model
+in Equation~\eqref{eqn:linearBending}, the lipid concentration achieves
+a maximum value of $u \approx 1.5$ which results in an instability that
+is formed by the resulting unphysical negative bending stiffness. To
+rectify this issue, we parameterize the bending modulus with the sigmoid
+function
 \begin{align}
@@
 vesicle shapes and long-range hydrodynamic interactions. The velocity
-field $\uu$ is written as a combination of a single-layer potential and
-a double-layer potential
+field $\uu$ at $\xx \in \Omega$ is written as a combination of a
+single-layer potential and a double-layer potential
 \begin{align}
@@
 $\rr = \xx - \yy$, $\rho = |\rr|$, and $\mathds{I}$ is the $2 \times 2$
-identity matrix. The corresponding pressure at $\xx \in \Omega$ is
+identity matrix. The corresponding pressure is
 \begin{align}
@@
 $\theta$-$L$ variables~\cite{hou-low-she1994}, where $L$ is the fixed
-vesicle length and $\theta$ is the opening angle of the tangent vector
-$\ss$. This requires decomposing the velocity field on $\gamma$ into a
-normal velocity $V$ and tangential velocity $T$. Then, the no-slip
-boundary condition for the vesicle velocity is
+vesicle length and $\theta$ is the angle between the tangent vector and
+the positive $x$-axis. This requires decomposing the velocity field on
+$\gamma$ into a normal velocity $V$ and tangential velocity $T$. Then,
+the no-slip boundary condition for the vesicle velocity is
 \begin{align}
@@
 The vesicle and solid walls are discretized at a set of collocation
-points. The single-layer potential is then approximated using quadrature
-for weakly-singular integrands, while the double-layer potential is
-approximated using the spectrally accurate trapezoid rule. Arclength
-derivatives are computed with spectral accuracy using Fourier methods.
-The resulting linear system is solved using GMRES. Finally, time
-stepping is carried out using the second-order Adams-Bashforth method.
+points. The single-layer potential is approximated using quadrature for
+weakly-singular integrands, while the double-layer potential is
+approximated using the spectrally accurate trapezoid rule. A high-order
+quadrature method resolves the hydrodynamic interactions between the
+vesicle and the solid wall~\cite{qua-bir2014}. Arclength derivatives are
+computed with spectral accuracy using Fourier methods.  The resulting
+linear system is solved using GMRES. Finally, time stepping is carried
+out using the second-order Adams-Bashforth method.
 
@@
 literature. Figure~\ref{fig:treading} shows a phase treading (top) and a
-tank-treading (bottom) multicomponent vesicle in an unconfined shear
-flow. These simulations align with the results reported
+tank-treading (bottom) multicomponent vesicle in an unconfined linear
+shear flow. The simulations align with the results reported
 by~\citet{liu-mar-li-vee-low2017} (cf.~Figure 3).
@@
   (bottom) with the new sigmoid bending model in
-  Equation~\eqref{eqn:tanhBending}. The red region is stiff and the blue
-  region is floppy. The simulations qualitatively agree with the results
-  presented by~\citet{liu-mar-li-vee-low2017}.}
+  Equation~\eqref{eqn:tanhBending}. The dimensionless times are in the
+  title. The red region is stiff and the blue region is floppy. The
+  simulations qualitatively agree with the results presented
+  in~\citet{liu-mar-li-vee-low2017}.}
 \end{figure}
@@
 regions denote the lubrication layer thicknesses. In this example, the
-top layer is broken across three different regions.
+top layer is broken across two different regions.
 
@@
 
-We also report the excess pressure for one of the geometries and relate
+We also report the excess pressure for the stenosis geometry and relate
 it to the size of the lubrication layers. The excess pressure is the
@@
 geometry when compared to the pressure necessary if the vesicle were
-absent. These pressure calculations are taken near the inlets and
-outlets of the confining geometry, and the vesicle itself is never near
-these locations.
+absent. Average pressures are calculated along cross-sections that are
+parallel to the flow direction near the inlet and outlet of the
+stenosis, and the vesicle itself is never near these locations.
 

### 2023-08-15 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
lots of changes throughout

@@
 $b(u) = 1$ and $b(u) = 0.55$. We refer to these cases as a stiff
-single-component vesicle and floppy single-component vesicle,
+single-component vesicle and a floppy single-component vesicle,
 respectively. The smaller bending stiffness represents the average
@@
   \caption{\label{fig:Energy} \small The bending (blue), tension (red),
-  and phase (magenta) energies of a (a) stiff single-component, (b)
+  and phase (green) energies of a (a) stiff single-component, (b)
   floppy single-component, and (c) multicomponent vesicle. The reduced
@@
 \end{figure*}
-
-Next we consider a vesicle with a smaller reduced area $\alpha=0.4$ with
-the same geometry and $Ca=0.25$. Figure~\ref{fig:RA4} shows the shape of
-a (a) stiff single-component, (b) floppy single-component, and (c)
-multicomponent vesicle at six locations along the stenosis channel. We
-first consider the three different energies---bending, tension, and
-phase---for each example. In Figure~\ref{fig:Energy}, we plot these
-energies as a function of the vesicle's center. As a reminder, the
-vesicle enters the constriction at $x=-15$ and exits at $x=15$. Also
-note that the single-component vesicles do not have a phase energy.  We
+\begin{figure*}[ht]
+  \centering
+  \subfigimg[width=0.3\linewidth]{(a)}{figures/Layer_Size_RAp4_SC.pdf}
+  \subfigimg[width=0.3\linewidth]{(b)}{figures/Layer_Size_RAp4_SCp55.pdf}
+  \subfigimg[width=0.3\linewidth]{(c)}{figures/Layer_Size_RAp4_MCp5.pdf}
+  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{}{figures/TankTreadingFigs_composite_SC.pdf}
+  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
+  0cm,clip=true]{}{figures/TankTreadingFigs_composite_SCp55.pdf}
+  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
+  0cm,clip=true]{}{figures/TankTreadingFigs_composite_MCp5.pdf}
+  \caption{\label{fig:lubricationComposite} \small The lubrication layer
+  thicknesses (red and blue), excess pressure (green), and
+  tank-treading velocity of four Lagrangian points of a (a) stiff
+  single-component vesicle, (b) floppy single-component vesicle, and (c)
+  multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all
+  three cases. Also illustrated is the vesicle shape and the four
+  Lagrangian points at the location indicated by the dash line. The
+  black dashed line is the center line of the channel, and the arrow
+  denotes the tank-treading direction. The percentage of the vesicle
+  membrane that is below the center line is (a) 72\%, (b) 44\%, and (c)
+  68\%.}
+\end{figure*}
+
+We next consider a vesicle with a smaller reduced area $\alpha=0.4$ with
+the same geometry and capillary number. Figure~\ref{fig:RA4} shows the
+shape of a (a) stiff single-component, (b) floppy single-component, and
+(c) multicomponent vesicle at six locations along the stenosis channel.
+Contrary to the vesicles with the larger reduced area
+(Figure~\ref{fig:RA6}), the bending modulus has a large effect on the
+vesicle shape. We first consider the three different energies---bending,
+tension, and phase---for each example. In Figure~\ref{fig:Energy}, we
+plot these energies as a function of the vesicle's center. 
+%As a
+%reminder, the vesicle enters the constriction at $x=-15$ and exits at
+%$x=15$. 
+Note that the single-component vesicles do not have a phase energy. We
 observe that, as the vesicle enters the stenosis, it develops regions of
@@
 Figure~\ref{fig:Energy}(c), the lipid species coarsens at three
-instances, and this results in a decrease in the phase energy. However,
-as we mentioned earlier, no coarsening occurs when the vesicle is in the
-closely-fitting part of the channel. Each coarsening corresponds either
-to two stiff regions overtaking a small floppy region, or to two floppy
-regions overtaking a small stiff region. In the first case, a region
-that was originally floppy has suddenly become stiff, and this results
-in a sudden increase in the bending energy. In the latter case, because
-of lipid conservation, the overtaken stiff region must relocate to the
-another stiff-floppy interface, and this also results in a sudden
-increase in the bending energy. These increases are visible in
+instances, and this results in a decrease in the phase energy. 
+%However, as we mentioned earlier, no coarsening occurs when the vesicle
+%is in the closely-fitting part of the channel. 
+Each coarsening corresponds either to two stiff regions overtaking a
+small floppy region, or to two floppy regions overtaking a small stiff
+region. In the first case, a region that was originally floppy has
+become stiff, and this results in a sudden increase in the
+bending energy. In the latter case, because the mass of the lipid phase
+is conserved, the overtaken stiff region must relocate to the another
+stiff-floppy interface, and this also results in a sudden increase in
+the bending energy. These increases are visible in
 Figure~\ref{fig:Energy}(c) as small upticks in the blue curve. However,
@@
 
-A main difference between the two reduced areas is that the vesicles
+Another difference between the two reduced areas is that the vesicles
 with smaller reduced area undergo tank-treading motions. As mentioned
@@
 of the vesicle with reduced area $\alpha = 0.4$ are in the top half of
-Figure~\ref{fig:lubricationComposite}. Also included in the bottom of
-Figure~\ref{fig:lubricationComposite} are the tank-treading velocities
+Figure~\ref{fig:lubricationComposite}. The bottom of
+Figure~\ref{fig:lubricationComposite} shows the tank-treading velocities
 of four Lagrangian points. The inset shows the vesicle configuration in
 the closely-fitting part of the channel, the black dashed line is the
-center line of the channel, and the rounded arrow denotes the direction
-of rotation. The stiff single-component and multicomponent vesicles are
-clearly tank treading. The direction and speed of the tank-treading
-depends on the how much of the vesicle membrane is exposed to positive
-shear (below the center line) versus how much is exposed to negative
-shear (above the center line). The majority of the membrane of the stiff
-single-component and multicomponent vesicles are below the center line,
-and this results in a clockwise tank-treading behavior. In contrast, the
-majority of the membrane of the floppy single-component vesicle is above
-the center line, and the result is counterclockwise tank-treading. In
-addition, the tank-treading velocity can be correlated to the percentage
-of its membrane that is below the center line. We note, however, that
-the floppy single-component vesicle is still undergoing deformations, so
-the tangential velocities have not converged to a fixed value.
+center line of the channel, the marks are the four Lagrangian points,
+and the rounded arrow denotes the direction of rotation. The stiff
+single-component and multicomponent vesicles are clearly tank treading.
+The direction and speed of the tank-treading depends on the how much of
+the vesicle membrane is exposed to positive shear (below the center
+line) versus how much is exposed to negative shear (above the center
+line). The majority of the membrane of the stiff single-component and
+multicomponent vesicles are below the center line, and this results in a
+clockwise tank-treading behavior. In contrast, the majority of the
+membrane of the floppy single-component vesicle is above the center
+line, and the result is counterclockwise tank-treading. In addition, the
+tank-treading velocity can be correlated to the percentage of its
+membrane that is below the center line. We note, however, that the
+floppy single-component vesicle is still undergoing deformations, so the
+tangential velocities have not converged to a fixed value.
 
@@
 %\end{figure}
-\begin{figure*}[t]
-%\begin{figure}[htp]
-  \centering
-  \subfigimg[width=0.3\linewidth]{(a)}{figures/Layer_Size_RAp4_SC.pdf}
-  \subfigimg[width=0.3\linewidth]{(b)}{figures/Layer_Size_RAp4_SCp55.pdf}
-  \subfigimg[width=0.3\linewidth]{(c)}{figures/Layer_Size_RAp4_MCp5.pdf}
-  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{}{figures/TankTreadingFigs_composite_SC.pdf}
-  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
-  0cm,clip=true]{}{figures/TankTreadingFigs_composite_SCp55.pdf}
-  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
-  0cm,clip=true]{}{figures/TankTreadingFigs_composite_MCp5.pdf}
-  \caption{\label{fig:lubricationComposite} \small The lubrication layer
-  thicknesses (red and blue), excess pressure (magenta), and
-  tank-treading velocity of four Lagrangian points of a (a) stiff
-  single-component vesicle, (b) floppy single-component vesicle, and (c)
-  multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all
-  three cases. Also illustrated is the vesicle shape and the four
-  Lagrangian points at the location indicated by the dash line. The
-  black dashed line is the center line of the channel, and the arrow
-  denotes the tank-treading direction. The percentage of the vesicle
-  membrane that is below the center line is (a) 72\%, (b) 44\%, and (c)
-  68\%.}
-%\end{figure}
-\end{figure*}
 
@@
 The sizes of the top and bottom lubrication layers are also related to
-the excess pressure. The magenta curve on the top half of
+the excess pressure. The green curve on the top half of
 Figure~\ref{fig:lubricationComposite} shows the excess pressure (with
@@
 \end{align}
-switches sign. Here,
+is sufficiently large to offset the flow driven by the boundary
+conditions defined at the inlet and outlet of the geometry. Here,
 \begin{align}
@@
 \end{align}
-is the variational derivative of the membrane energy with respect to the
-lipid concentration~\cite{soh-tse-li-voi-low2010}. Note that in the
+is the derivative of the membrane energy with respect to the lipid
+concentration~\cite{soh-tse-li-voi-low2010}. Note that in the
 single-component case, the tangential force is $\mathbf{F}_\tt =
@@
 
-%\begin{figure*}[t]
 \begin{figure}
@@
   in the thin fluid layer between the top of a vesicle and the stenosis
-  geometry. The vesicles are (a): stiff single-component; (b):
+  geometry. The vesicles are (a) stiff single-component; (b)
   multicomponent. Similar velocity profiles between the bottom of the
-  vesicle and the stenosis geometry. The profiles are ploted at slices
+  vesicle and the stenosis geometry. The profiles are plotted at slices
   where the pressure gradient transitions from a value that is negative,
@@
   stress is sufficiently large.}
-%  \caption{\label{fig:BLvelocities} \small The co-moving velocity field
-%  in the thin fluid layer between vesicles and the stenosis geometry.
-%  The vesicles are (a/b): single-component with $b(u) = 1$; (c/d):
-%  single-component with $b(u) = 0.55$; (e/f): multicomponent. The top
-%  layers are in (a/c/e) and the bottom layers are in (b/d/f). The
-%  profiles are ploted at slices where the pressure gradient transitions
-%  from a value that is negative, zero, positive, zero, and negative. The
-%  right plots show the tangential stress with the five slices denoted by
-%  the marks. Note that the reversal in the pressure gradient occurs when
-%  the tangential stress is sufficiently large, in magnitude.}
 \end{figure}
-%\end{figure*}
 
@@
 contracting geometry}
-In this section, we consider a single vesicle passing through a geometry
-that slowly contracts to a region that is only 2~$\mu$m wide, and then
+In this section, we consider a vesicle passing through a geometry that
+slowly contracts to a region that is only 2~$\mu$m wide, and then
 immediately opens back up to a channel that is ten times larger. We
@@
 area $\alpha = 0.6$ with different initial lipid distributions are
-illustrated. The initial distributions are random (middle) floppy in the
-front and stiff in the back (top), and one that is stiff in the front
-and floppy in the back (bottom). The vesicle with the random initial
-lipid distribution quickly phase separates into two floppy and two stiff
-regions. As seen in the stenosis geometry, further phase separation is
-delayed until the vesicle is no longer under strong confinement. The
-vesicle with the floppy region on the front reorients the floppy region
-towards the back of the vesicle. In contrast, the vesicle with the stiff
-region at the front maintains its orientation. In summary, in all three
-cases, the vesicle is orienting itself so that the stiff region passes
-through the constriction before the floppy region.  Therefore, in
-subsequent simulations, we initialize the vesicle's lipid concentration
-so that the floppy region is in the back and its stiff region is in the
-front. The vesicle shapes develop regions with high curvature in the
-floppy region when they first pass through the narrowest part of the
-geometry, but because the strong confinement is abruptly removed
-immediately afterwards, these regions of high curvature are quickly
-smoothed. 
+illustrated. The initial distributions are (a) random, (b) stiff in the
+front and floppy in the back, and (c) floppy in the front and stiff in
+the back. The vesicle with the random initial lipid distribution quickly
+phase separates into two floppy and two stiff regions. As seen in the
+stenosis geometry, further phase separation is delayed until the vesicle
+is no longer under strong confinement. The vesicle with the stiff region
+at the front maintains its orientation. In contrast, the vesicle with
+the floppy region on the front reorients the floppy region towards the
+back of the vesicle. In summary, in all three cases, the vesicle is
+orienting itself so that the stiff region passes through the
+constriction before the floppy region. Therefore, in subsequent
+simulations, we initialize the vesicle's lipid concentration so that the
+floppy region is in the back and its stiff region is in the front. The
+vesicle shapes develop regions with high curvature in the floppy region
+when they first pass through the narrowest part of the geometry, but
+once the strong confinement is abruptly removed, these regions of high
+curvature are quickly smoothed.
 %Since we can see in Figure~\ref{fig:RA6leftRightRand} that the regions
@@
   vesicle's reduced area is $\alpha = 0.6$ and the capillary number is
-  $Ca = 0.25$. The lipid distribution is initialized to be (a) phase
-  separated with the floppy region leading; (b) random; (c) phase
-  separated with the stiff region leading.}
+  $Ca = 0.25$. The lipid distribution is initialized to be (a) random,
+  (b) phase separated with the stiff region leading; (b) random; (c)
+  phase separated with the floppy region leading.}
 \end{figure}
@@
 shapes at the same six time steps when the percentage of the floppy
-region is 0\% (single-component), 15\%, 25\%, 35\%, and 45\%. One effect
-of the size of the floppy region is that the symmetry of the vesicle
-shape is broken at smaller percentages. We also see that stiffer
-vesicles have faster migration speeds, but the effect is quite
-small---Table~\ref{tbl:contractingTimes} reports the time the vesicle
-first passes through the neck.
+region is (a) 0\% (single-component), (b) 15\%, (c) 25\%, (d) 35\%, and
+(e) 45\%. One effect of the size of the floppy region is that the
+symmetry of the vesicle shape is broken at smaller percentages. We also
+see that stiffer vesicles have faster migration speeds, but the effect
+is quite small---Table~\ref{tbl:contractingTimes} reports the time the
+vesicle first passes through the neck.
 %In Figure~\ref{fig:RA5}, we consider a vesicle with reduced area
@@
   contracting geometry. The vesicle's reduced area is $\alpha = 0.5$ and
-  the Capillary number is $Ca = 0.25$. The vesicles are: (a)
-  single-component with bending modulus $b=b_{\max}$; (b) multicomponent
-  with 15\% floppy region; (c) multicomponent with 25\% floppy region;
-  (d) multicomponent with 35\% floppy region; (e) multicomponent with
-  45\% floppy region. The vesicles with a larger percentage of floppy
+  the Capillary number is $Ca = 0.25$. (a)
+  A stiff single-component vesicle. The percentage of the
+  multicomponenet vesicle that is floppy is (b) 15\%, (c) 25\%, (d)
+  35\%, and (e) 45\%. The vesicles with a larger percentage of floppy
   regions pass through the neck earlier than the vesicles with less
@@
 
-We conclude this example by considering the different shapes that
-single-component and multicomponent shapes display. Since we have
-initialized the lipid species to initially be phase separated, the phase
-energy is nearly constant for all cases, and is therefore not plotted.
-The tension energy, on the other hand, increases as the vesicle
+We conclude this example by considering the different shapes and
+energies that single-component and multicomponent shapes display. Since
+we have initialized the lipid species to initially be phase separated,
+the phase energy is nearly constant for all cases, and is therefore not
+plotted. The tension energy, on the other hand, increases as the vesicle
 approaches the neck, but its general shape is similar for all five
@@
 the tail of the vesicle undergoes transitions from lower energy shapes,
-such as `C' or `S' shapes, to high energy shapes, such as 'W' shapes.
+such as `C' or `S' shapes, to high energy shapes, such as `W' shapes.
 Figure~\ref{fig:bendingSC_contracting} shows these different vesicle
@@
 is 45\% floppy. The shapes at several critical points along the bending
-energy are included, and we can indeed see that transitioning vesicle
-shape between these different states.
+energy are included.
+%and we can indeed see that transitioning vesicle shape between these
+%different states.
 

### 2023-08-15 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
small changes

@@
 a quiescent environment, such elastic heterogeneity gives rise to
-wrinkling budding~\cite{Lowengrub2009_PRE, Li2012_CommMathSci}, adhesion
-and fusion~\cite{Zhao2011_PRE} of vesicle membrane, closely related to
-cellular budding and fission processes~\cite{Rauch2000_BiophysJ} as well
-as in cellular adhesion and fusion~\cite{Takeda2003_PNAS}.
+wrinkling, budding, adhesion, and fusion of vesicle
+membranes~\cite{Lowengrub2009_PRE, Li2012_CommMathSci, Zhao2011_PRE},
+closely related to several cellular processes~\cite{Rauch2000_BiophysJ,
+Takeda2003_PNAS}.
+%In a quiescent environment, such elastic heterogeneity gives rise to
+%wrinkling budding~\cite{Lowengrub2009_PRE, Li2012_CommMathSci},
+%adhesion and fusion~\cite{Zhao2011_PRE} of vesicle membrane, closely
+%related to cellular budding and fission
+%processes~\cite{Rauch2000_BiophysJ} as well as in cellular adhesion and
+%fusion~\cite{Takeda2003_PNAS}.
 
@@
 \begin{align}
+  \label{eqn:pressure}
   p(\xx) = \frac{1}{2\pi} \int_{\gamma} \frac{\rr \cdot \ff}{\rho^2} \, ds_\yy + 
@@
 geometry when compared to the pressure necessary if the vesicle were
-absent. Average pressures are calculated along cross-sections that are
-parallel to the flow direction near the inlet and outlet of the
-stenosis, and the vesicle itself is never near these locations.
+absent. Average pressures are calculated using
+Equation~\eqref{eqn:pressure} along cross-sections that are parallel to
+the flow direction near the inlet and outlet of the stenosis.
+%, and the
+%vesicle itself is never near these locations.
 
@@
 this lubrication layer in Figure~\ref{fig:BLvelocities}. We observe that
-the Poiseuille coefficient can be either positive or negative, meaning
-that the pressure in the lubrication layer switches signs. This behavior
-is caused when the tangential force on the vesicle
+the Poiseuille coefficient (quadratic term) can be either positive or
+negative, meaning that the pressure gradient in the streamwise direction
+in the lubrication layer switches signs. The Poiseuille coefficient is
+related to the lateral gradient of the tangential traction,
+$\mathbf{F}_\tt$, on the vesicle membrane~\cite{Oron1997_RMP,
+Young2014_JFM}
 \begin{align}
-  \mathbf{F}_{\tt} = -\sigma_s + u_s \frac{\delta E^m}{\delta u},
+  \mathbf{F}_{\tt} = -\sigma_s + u_s \frac{\delta E^m}{\delta u}.
 \end{align}
-is sufficiently large to offset the flow driven by the boundary
-conditions defined at the inlet and outlet of the geometry. Here,
+%is sufficiently large.
+%to locally reverse the sign of the pressure
+%gradient in the streamwise direction.
+Here,
 \begin{align}
@@
 concentration~\cite{soh-tse-li-voi-low2010}. Note that in the
-single-component case, the tangential force is $\mathbf{F}_\tt =
+single-component case, the tangential traction is $\mathbf{F}_\tt =
 -\sigma_s$ which is the usual Marangoni effect.
@@
 We conclude this example by considering the different shapes and
-energies that single-component and multicomponent shapes display. Since
-we have initialized the lipid species to initially be phase separated,
-the phase energy is nearly constant for all cases, and is therefore not
-plotted. The tension energy, on the other hand, increases as the vesicle
-approaches the neck, but its general shape is similar for all five
-cases, and it too is not plotted. However, the bending energies show
-different behaviors for each of the cases (Figure~\ref{fig:bendingAll}).
-The main difference being that the multicomponent vesicles with a higher
-percentage of floppy regions have less bending energy, especially as the
-vesicle passes through the neck. We also note that the bending energy
-undergoes several transient increases and decreases. These occur when
-the tail of the vesicle undergoes transitions from lower energy shapes,
-such as `C' or `S' shapes, to high energy shapes, such as `W' shapes.
+energies that single-component and multicomponent vesicles display.
+Since we have initialized the lipid species to initially be phase
+separated, the phase energy is nearly constant for all cases, and is
+therefore not plotted. The tension energy, on the other hand, increases
+as the vesicle approaches the neck, but its general shape is similar for
+all five cases, and it too is not plotted. However, the bending energies
+show different behaviors for each of the cases
+(Figure~\ref{fig:bendingAll}).  The main difference being that the
+multicomponent vesicles with a higher percentage of floppy regions have
+less bending energy, especially as the vesicle passes through the neck.
+We also note that the bending energy undergoes several transient
+increases and decreases. These occur when the tail of the vesicle
+undergoes transitions from lower energy shapes, such as `C' or `S'
+shapes, to high energy shapes, such as `W' shapes.
 Figure~\ref{fig:bendingSC_contracting} shows these different vesicle

### 2023-08-16 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
small edits

@@
 %
-\includegraphics{head_foot/dates} & \noindent\normalsize{We numerically
-  study the hydrodynamics of multicomponent vesicles in two strongly
-  confining geometries. This serves as a simplified model for red blood
-  cells undergoing large deformations when passing through extreme
-  constrictions. We propose a new bending modulus parameterization that
-  is positive for all values of the lipid phase parameter. For a
-  multicomponent vesicle passing through a stenosis, we correlate the
-  lipid phase coarsening, the lubrication layer properties (size and
-  flow profile), the excess pressure, and the tank-treading velocity of
+\includegraphics{head_foot/dates} & \noindent\normalsize{%We numerically study the hydrodynamics of multicomponent vesicles in two strongly
+  %confining geometries.
+  We conduct a numerical investigation into the hydrodynamics of multicomponent vesicles in two strongly confined geometries. This serves as a simplified model for red blood
+  cells undergoing large deformations while traversing %when passing through extreme
+  narrow constrictions.
+  We propose a novel parameterization for the bending modulus that maintains positivity across all lipid phase parameter values.	
+  %We propose a new bending modulus parameterization that
+  %is positive for all values of the lipid phase parameter. 
+  For a multicomponent vesicle passing through a stenosis, %we correlate 
+  we establish connections between various properties: lipid phase coarsening, size and flow profile of the lubrication layers, %properties (size and flow profile), 
+  excess pressure, and the tank-treading velocity of
   the membrane. For a multicomponent vesicle passing through a
@@
   that the vesicle is stiffer in the front as it passes through the
-  constriction. For both cases of confinement we find that the lipid
-  coarsening is arrested under strong confinement, and proceeds with
-  high rate upon relief from extreme confinement. The results may be
-  useful for efficient sorting lipid domains using microfluidic flows by
+  constriction. %For both cases of confinement we find that the lipid
+  %coarsening is arrested under strong confinement, and proceeds with
+  %high rate upon relief from extreme confinement. 
+  For both cases of confinement, we find that lipid coarsening is arrested under strong confinement and proceeds at a high rate upon relief from extreme confinement.
+  The results may be useful for efficient sorting lipid domains using microfluidic flows by
   controlled release of vesicles passing through strong confinement.} \\
@@
 Biological membranes, the basic structural units for compartmentalizing
-biological systems, have been observed to contain a vast array of
-proteins and different lipid species that phase-separate and form
-domains or rafts, resulting in spatial variations in material properties
-such as bending stiffness. Synthetic multicomponent vesicles,
+biological systems, %have been observed to contain a vast 
+exhibit a diverse array of
+proteins and lipid species. %that phase-separate and form
+%domains or rafts, resulting in spatial variations in material properties
+%such as bending stiffness. 
+These lipids undergo phase separation, forming domains or rafts that lead to variations in material properties, including bending stiffness. 
+Synthetic multicomponent vesicles,
 self-enclosed lipid bilayer membranes composed of different lipid
@@
 yan-ima-tan2010, yan-ima-tan2008, dre-jah-bob-spa-gop2021}.
-
 %
@@
 demonstrated in Figure~\ref{fig:concModels}(a) for a vesicle with a
-floppy-to-stiff ratio $\beta = 10^{-1}$. Using the linear bending model
+floppy-to-stiff ratio $\beta = 10^{-1}$ entering a stenosis. Using the linear bending model
 in Equation~\eqref{eqn:linearBending}, the lipid concentration achieves
@@
 shear flow. The simulations align with the results reported
-by~\citet{liu-mar-li-vee-low2017} (cf.~Figure 3).
+by~\citet{liu-mar-li-vee-low2017} (cf.~Figure 3 and Figure 4).
 \begin{figure}[h]
@@
 the channel walls to elucidate the correlation between hydrodynamics and
-membrane dynamics. To define the size of the top lubrication layer (the
-size of the bottom lubrication layer is defined similarly), we let
+membrane dynamics. To define the size of the top lubrication layer, we let
 $d(\xx,\Gamma_\mathrm{top})$ be the minimum distance between a point on
 the vesicle, $\xx \in \gamma$, and the top half of the confining
-geometry. We find all local minimums of $d(\xx,\Gamma_\mathrm{top})$,
+geometry. The size of the bottom lubrication layer is defined similarly. 
+We find all local minimums of $d(\xx,\Gamma_\mathrm{top})$,
 with the condition that $d(\xx,\Gamma_\mathrm{top}) < \delta$, where
@@
 greater than $\alpha = 0.8$ cannot fit through the closely-fitting
-geometry. Figure~\ref{fig:RA6} shows six time steps of a (a) stiff
+geometry. \color{red} ARG: Is this true for stenosis? I remember it being the 
+case for contracting. I'll check previous runs. \color{black} 
+Figure~\ref{fig:RA6} shows six time steps of a (a) stiff
 single-component (b) floppy single-component, and (c) multicomponent
@@
 As the stiff single-component and multicomponent vesicles reach a
-steady-state shape near the middle of the channel, their bending,
-tension, and phase energies remain nearly constant from $x=0$ until the
-end of the stenosis. For the multiple-component vesicle, this implies
+steady-state shape near the middle of the channel, their bending and
+tension energies remain nearly constant from $x=0$ until the
+end of the stenosis. For the multicomponent vesicle, the phase energy is 
+also nearly constant in this region. This implies
 that there is no coarsening of lipid phase parameter in the middle of a
@@
   with 50\% floppy region passing through a contracting geometry. The
-  vesicle's reduced area is $\alpha = 0.6$ and the capillary number is
+  vesicle's reduced area is $\alpha = 0.5$ and the capillary number is
   $Ca = 0.25$. The lipid distribution is initialized to be (a) random,
@@
 is quite small---Table~\ref{tbl:contractingTimes} reports the time the
-vesicle first passes through the neck.
+vesicle first passes through the neck. \color{red} I think this is backwards? The table reports that the floppiest vesicle made it through the contraction the quickest. \color{black}
 %In Figure~\ref{fig:RA5}, we consider a vesicle with reduced area
@@
 of a multicomponent vesicle under strong confinement. The vesicle is an
-simplified model for a red blood cell (RBC), which has multiple lipid
+simplified model for a red blood cell, which has multiple lipid
 domains in its membrane and often has to squeeze through a small space.
@@
 with a smaller tension (in magnitude) in the front and a larger tension
-(in magnitude) in the back. This is similar to a RBC going through a
-narrow slit~\cite{LuPeng2019_PoF}, where the membrane tension is mostly
-negative (compression) when the RBC passes through the narrow slit with
-more compression in the back than in the front of the RBC.
+(in magnitude) in the back.
+This resembles the behavior of a red blood cell as it traverses a narrow slit~\cite{LuPeng2019_PoF}.
+During this process, the membrane tension is primarily negative, resulting in compression that is more pronounced at the rear of the cell than at the front.
+%This is similar to a red blood cell going through a
+%narrow slit~\cite{LuPeng2019_PoF}, where the membrane tension is mostly
+%negative (compression) when the RBC passes through the narrow slit with
+%more compression in the back than in the front of the RBC.
 %This may have biophysical consequences in polarity developing of a

### 2023-08-16 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
cleaning up the text a bit

@@
 %
- & \noindent\large{Ashley Gannon,\textit{$^{a}$} Y.-N. Young,\textit{$^{b\ddag}$} and Bryan Quaife\textit{${\ast}${$^{a}$}}} \\
+ & \noindent\large{Ashley Gannon,\textit{$^{a}$} Bryan
+  Quaife,\textit{${\ast}${$^{a}$}} and Y.-N.
+  Young,\textit{${\ast}$$^{b\ddag}$} } \\
 % %Author names go here instead of "Full name", etc.
@@
   %confining geometries.
-  We conduct a numerical investigation into the hydrodynamics of multicomponent vesicles in two strongly confined geometries. This serves as a simplified model for red blood
+  We numerically investigate the hydrodynamics and membrane dynamics of multicomponent vesicles in two strongly confined geometries. This serves as a simplified model for red blood
   cells undergoing large deformations while traversing %when passing through extreme
-  narrow constrictions.
-  We propose a novel parameterization for the bending modulus that maintains positivity across all lipid phase parameter values.	
+  narrow constrictions. We propose a novel parameterization for the
+  bending modulus that remains positive for all lipid phase parameter
+  values.	
   %We propose a new bending modulus parameterization that
@@
   %high rate upon relief from extreme confinement. 
-  For both cases of confinement, we find that lipid coarsening is arrested under strong confinement and proceeds at a high rate upon relief from extreme confinement.
-  The results may be useful for efficient sorting lipid domains using microfluidic flows by
-  controlled release of vesicles passing through strong confinement.} \\
+  For both cases of confinement, we find that lipid coarsening is
+  arrested under strong confinement and proceeds at a high rate upon
+  relief from extreme confinement. The results may be useful for
+  efficient sorting lipid domains using microfluidic flows by controlled
+  release of vesicles passing through strong confinement.} \\
   %The abstrast goes here instead of the text "The abstract should
@@
 Biological membranes, the basic structural units for compartmentalizing
-biological systems, %have been observed to contain a vast 
+biological systems, 
+%have been observed to contain a vast 
 exhibit a diverse array of
-proteins and lipid species. %that phase-separate and form
-%domains or rafts, resulting in spatial variations in material properties
-%such as bending stiffness. 
-These lipids undergo phase separation, forming domains or rafts that lead to variations in material properties, including bending stiffness. 
-Synthetic multicomponent vesicles,
-self-enclosed lipid bilayer membranes composed of different lipid
-species, have been used to study the rich patterns and accompanying
-morphologies that emerge from elastic heterogeneity in the membrane. In
-a quiescent environment, such elastic heterogeneity gives rise to
-wrinkling, budding, adhesion, and fusion of vesicle
-membranes~\cite{Lowengrub2009_PRE, Li2012_CommMathSci, Zhao2011_PRE},
-closely related to several cellular processes~\cite{Rauch2000_BiophysJ,
-Takeda2003_PNAS}.
-%In a quiescent environment, such elastic heterogeneity gives rise to
-%wrinkling budding~\cite{Lowengrub2009_PRE, Li2012_CommMathSci},
-%adhesion and fusion~\cite{Zhao2011_PRE} of vesicle membrane, closely
-%related to cellular budding and fission
-%processes~\cite{Rauch2000_BiophysJ} as well as in cellular adhesion and
-%fusion~\cite{Takeda2003_PNAS}.
+proteins and lipid species. 
+%that phase-separate and form domains or rafts, resulting in spatial
+%variations in material properties such as bending stiffness. 
+These lipids undergo phase separation, forming domains or rafts that
+lead to variations in material properties, including bending stiffness.
+Synthetic multicomponent vesicles, self-enclosed lipid bilayer membranes
+composed of different lipid species, have been used to study the rich
+patterns and accompanying morphologies that emerge from elastic
+heterogeneity in the membrane. In a quiescent environment, such elastic
+heterogeneity gives rise to wrinkling, budding, adhesion, and fusion of
+vesicle membranes~\cite{Lowengrub2009_PRE, Li2012_CommMathSci,
+Zhao2011_PRE}, closely related to several cellular
+processes~\cite{Rauch2000_BiophysJ, Takeda2003_PNAS}.
 
@@
 
-%\citet{gur-pak-tay-siv-sac2023} look at the effect of membrane viscoelasticity.
-
-%\citet{wan-ii-sug-nod-jin-liu-che-gon2023}
-
-%\citet{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019}
-%is paper with Sean Sun that looks at linear and non-linear shear in the
-%boundary layer caused by tank treading behavior.
-
-%\citet{yan-ima-tan2010} perform experiments with multicomponent GUVs.
-%They observe phase separation and budding of vesicles with a small
-%reduced volume. However, the budding often requires a significant
-%amount of time (tens of minutes), but ours occur much earlier in the
-%contracting example by using narrow constrictions. Equations (2)--(5)
-%shows a model similar to ours, and they use a linear dependence between
-%the bending modulus and lipid concentration in the paragraph
-%immediately after these equations. The include an energy term that
-%depends on the difference in area between the inner and outer monolayer
-%of lipids. Osmotic gradients are used to control the vesicle volume.
-
-%\citet{yan-ima-tan2008} Similar type work as~\cite{yan-ima-tan2010}.
-
-%\citet{dre-jah-bob-spa-gop2021} uses multicomponent GUVs to create necking, and use this to understand cell division.
-
-%\citet{tan-yan-ima2011} describes the shape deformation and phase separation dynamics of a two- component membrane whose bending moduli depend on the local composition of the lipids.
-
-%\citet{lip1992} considers the dynamics and budding of lipid bilayers
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{\label{sec:Formulation}Formulation}
+We consider a single multicomponent vesicle $\omega$ with boundary
+$\gamma$ suspended in a confined geometry $\Omega \subset \RR ^2$ with
+boundary $\Gamma$ (Figure~\ref{fig:schematic}). The fluid is assumed to
+have zero Reynolds number and is therefore governed by the
+incompressible Stokes equations
+\begin{align}
+  \nabla \cdot \TT = 0 \quad \text{and} \quad \nabla \cdot \uu = 0, 
+    \quad \xx \in \Omega \backslash \gamma,
+\end{align}
+where $\TT = -p\mathbf{I} + \mu\left(\nabla \uu + \nabla \uu^T \right)$
+is the hydrodynamic stress tensor, $\uu$ is the velocity, $p$ is the
+pressure, and $\mu$ is the fluid viscosity. Across the vesicle membrane,
+we require that the velocity is continuous and locally inextensible, and
+the membrane and hydrodynamic forces balance
+\begin{align}
+  \llbracket \uu \rrbracket = 0, \quad 
+  \nabla_{\gamma} \cdot \uu = 0, \quad
+  \llbracket \TT\nn \rrbracket = \ff, \quad \xx \in \gamma,
+\end{align}
+where $\ff$ is the total membrane force and $\nn$ is the outward unit
+normal of $\gamma$. Parameterizing $\gamma$ as $\xx(s,t)$, where $s$ is
+arclength and $t$ is time, the no-slip boundary condition is
+$\frac{d\xx}{dt} = \uu(\xx)$. Along the solid wall $\Gamma$, we impose a
+Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a
+Hagen–Poiseuille flow at the inlet and outlet
+\begin{align}
+  \UU(\xx) = U \left(1 - \left(\frac{y}{W}\right)^2 \right), 
+    \quad \xx = (x,y) \in \Gamma,
+\end{align}
+and $y \in [-W,W]$. $\UU$ is zero along the top and bottom of the
+channel.
+
 \begin{figure}[h]
@@
 \end{figure}
-We consider a single multicomponent vesicle $\omega$ with boundary
-$\gamma$ suspended in a confined geometry $\Omega \subset \RR ^2$ with
-boundary $\Gamma$ (Figure~\ref{fig:schematic}). The fluid is assumed to
-have zero Reynolds number and is therefore governed by the
-incompressible Stokes equations
-\begin{align}
-  \nabla \cdot \TT = 0 \quad \text{and} \quad \nabla \cdot \uu = 0, 
-    \quad \xx \in \Omega \backslash \gamma,
-\end{align}
-where $\TT = -p\mathbf{I} + \mu\left(\nabla \uu + \nabla \uu^T \right)$
-is the hydrodynamic stress tensor, $\uu$ is the velocity, $p$ is the
-pressure, and $\mu$ is the fluid viscosity. Across the vesicle membrane,
-we require that the velocity is continuous and locally inextensible, and
-the membrane and hydrodynamic forces balance
-\begin{align}
-  \llbracket \uu \rrbracket = 0, \quad 
-  \nabla_{\gamma} \cdot \uu = 0, \quad
-  \llbracket \TT\nn \rrbracket = \ff, \quad \xx \in \gamma,
-\end{align}
-where $\ff$ is the total membrane force and $\nn$ is the outward unit
-normal of $\gamma$. Parameterizing $\gamma$ as $\xx(s,t)$, where $s$ is
-arclength and $t$ is time, the no-slip boundary condition is
-$\frac{d\xx}{dt} = \uu(\xx)$. Along the solid wall $\Gamma$, we impose a
-Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a
-Hagen–Poiseuille flow at the inlet and outlet
-\begin{align}
-  \UU(\xx) = U \left(1 - \left(\frac{y}{W}\right)^2 \right), 
-    \quad \xx = (x,y) \in \Gamma,
-\end{align}
-and $y \in [-W,W]$. $\UU$ is zero along the top and bottom of the
-channel.
-
 We nondimensionalize the governing equations with a characteristic
@@
 demonstrated in Figure~\ref{fig:concModels}(a) for a vesicle with a
-floppy-to-stiff ratio $\beta = 10^{-1}$ entering a stenosis. Using the linear bending model
-in Equation~\eqref{eqn:linearBending}, the lipid concentration achieves
-a maximum value of $u \approx 1.5$ which results in an instability that
-is formed by the resulting unphysical negative bending stiffness. To
-rectify this issue, we parameterize the bending modulus with the sigmoid
-function
+floppy-to-stiff ratio $\beta = 10^{-1}$ entering a stenosis. Using the
+linear bending model in Equation~\eqref{eqn:linearBending}, the lipid
+concentration achieves a maximum value of $u \approx 1.5$ which results
+in an instability that is formed by the resulting unphysical negative
+bending stiffness. To rectify this issue, we parameterize the bending
+modulus with the sigmoid function
 \begin{align}
@@
 
-%\begin{figure}[htp]
-%  \centering
-%%    \begin{tabular}{@{}p{0.49\linewidth}@{\qquad}p{0.49\linewidth}@{}}
-%  \subfigimg[width=0.48\linewidth, clip ]{(a)}{figures/newbending.pdf}
-%%    \end{tabular}
-%\caption{\label{fig:bendingModels} \small A multicomponent vesicle
-%  entering a closely-fitting channel using (a) the new bending
-%  model~\eqref{eqn:tanhBending}; (b) the linear
-%  model~\eqref{eqn:linearBending}. With the linear model, the vesicle
-%  bending modulus becomes negative, and this introduces an instability
-%  that first appears near the point with the largest negative curvature.
-%  The two plots are not at the same time step.}
-%\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \includegraphics[width=0.9\columnwidth]{figures/shearTreading.pdf}
-%  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(a)}{figures/Fig4a.pdf}
-%  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(b)}{figures/Fig4b.pdf}
   \caption{\label{fig:treading} \small A multicomponent vesicle in a
@@
 
-%\begin{figure}[h]
 \begin{figure*}[h]
@@
   \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp6MCp5.pdf}
-%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig5a.pdf}
-%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig5b.pdf}
-%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig5c.pdf}
   \caption{\label{fig:RA6} \small A vesicle passing through the stenosis
@@
   single-component; (b) floppy single-component; (c) multicomponent.}
-%\end{figure}
 \end{figure*}
@@
 the channel walls to elucidate the correlation between hydrodynamics and
-membrane dynamics. To define the size of the top lubrication layer, we let
-$d(\xx,\Gamma_\mathrm{top})$ be the minimum distance between a point on
-the vesicle, $\xx \in \gamma$, and the top half of the confining
+membrane dynamics. To define the size of the top lubrication layer, we
+let $d(\xx,\Gamma_\mathrm{top})$ be the minimum distance between a point
+on the vesicle, $\xx \in \gamma$, and the top half of the confining
 geometry. The size of the bottom lubrication layer is defined similarly.
-We find all local minimums of $d(\xx,\Gamma_\mathrm{top})$,
-with the condition that $d(\xx,\Gamma_\mathrm{top}) < \delta$, where
-$\delta$ is a parameter. If no such local minimums exist, then the
-vesicle is too far from $\Gamma_\mathrm{top}$ to define a lubrication
-layer. If there are two or more local minimums, the left-most, $\xx_L$,
-and right-most, $\xx_R$, local minimums form the start and end of the
-lubrication layer.  If there is only one local minimum, then $\xx_L$ and
-$\xx_R$ are the points on $\gamma$ to the left and right of this local
-minimum with the condition that $d(\xx_L,\Gamma_\mathrm{top}) =
+We find all local minimums of $d(\xx,\Gamma_\mathrm{top})$, with the
+condition that $d(\xx,\Gamma_\mathrm{top}) < \delta$, where $\delta$ is
+a parameter. If no such local minimums exist, then the vesicle is too
+far from $\Gamma_\mathrm{top}$ to define a lubrication layer. If there
+are two or more local minimums, the left-most, $\xx_L$, and right-most,
+$\xx_R$, local minimums form the start and end of the lubrication layer.
+If there is only one local minimum, then $\xx_L$ and $\xx_R$ are the
+points on $\gamma$ to the left and right of this local minimum with the
+condition that $d(\xx_L,\Gamma_\mathrm{top}) =
 d(\xx_R,\Gamma_\mathrm{top}) = \delta$. Then, the segment
@@
 the flow direction near the inlet and outlet of the stenosis.
-%, and the
-%vesicle itself is never near these locations.
 
@@
 greater than $\alpha = 0.8$ cannot fit through the closely-fitting
-geometry. \color{red} ARG: Is this true for stenosis? I remember it being the 
-case for contracting. I'll check previous runs. \color{black} 
-Figure~\ref{fig:RA6} shows six time steps of a (a) stiff
+geometry. Figure~\ref{fig:RA6} shows six time steps of a (a) stiff
 single-component (b) floppy single-component, and (c) multicomponent
@@
 tension, and phase---for each example. In Figure~\ref{fig:Energy}, we
-plot these energies as a function of the vesicle's center. 
-%As a
-%reminder, the vesicle enters the constriction at $x=-15$ and exits at
-%$x=15$. 
-Note that the single-component vesicles do not have a phase energy. We
-observe that, as the vesicle enters the stenosis, it develops regions of
-high curvature, and this results in an increase in the bending energy.
-As the stiff single-component and multicomponent vesicles reach a
+plot these energies as a function of the vesicle's center. Note that the
+single-component vesicles do not have a phase energy. We observe that,
+as the vesicle enters the stenosis, it develops regions of high
+curvature, and this results in an increase in the bending energy. As
+the stiff single-component and multicomponent vesicles reach a
 steady-state shape near the middle of the channel, their bending and
-tension energies remain nearly constant from $x=0$ until the
-end of the stenosis. For the multicomponent vesicle, the phase energy is 
-also nearly constant in this region. This implies
-that there is no coarsening of lipid phase parameter in the middle of a
-stenosis.
+tension energies remain nearly constant from $x=0$ until the end of the
+stenosis. For the multicomponent vesicle, the phase energy is also
+nearly constant in this region. This implies that there is no coarsening
+of lipid phase parameter in the middle of a stenosis.
 
@@
 Figure~\ref{fig:Energy}(c), the lipid species coarsens at three
-instances, and this results in a decrease in the phase energy. 
-%However, as we mentioned earlier, no coarsening occurs when the vesicle
-%is in the closely-fitting part of the channel. 
-Each coarsening corresponds either to two stiff regions overtaking a
-small floppy region, or to two floppy regions overtaking a small stiff
-region. In the first case, a region that was originally floppy has
-become stiff, and this results in a sudden increase in the
-bending energy. In the latter case, because the mass of the lipid phase
-is conserved, the overtaken stiff region must relocate to the another
-stiff-floppy interface, and this also results in a sudden increase in
-the bending energy. These increases are visible in
-Figure~\ref{fig:Energy}(c) as small upticks in the blue curve. However,
-in both cases, the vesicle smooths out these new regions of high
-curvature, but it takes some time since the diffusion time scale is
-several orders of magnitude smaller than the bending relaxation time
-scale.
+instances, and this results in a decrease in the phase energy. Each
+coarsening corresponds either to two stiff regions overtaking a small
+floppy region, or to two floppy regions overtaking a small stiff region.
+In the first case, a region that was originally floppy has become stiff,
+and this results in a sudden increase in the bending energy. In the
+latter case, because the mass of the lipid phase is conserved, the
+overtaken stiff region must relocate to the another stiff-floppy
+interface, and this also results in a sudden increase in the bending
+energy. These increases are visible in Figure~\ref{fig:Energy}(c) as
+small upticks in the blue curve. However, in both cases, the vesicle
+smooths out these new regions of high curvature, but it takes some time
+since the diffusion time scale is several orders of magnitude smaller
+than the bending relaxation time scale.
 
@@
 
-%Since the single-component case has a larger difference
-%between its top and bottom boundary layers, it tank treads faster than
-%the multicomponent case. In addition, since the top boundary layer is
-%larger in both cases, they both tank-tread in the same
-%direction---counterclockwise. In contrast, the floppy single-component
-%vesicle tank treads in the clockwise direction; note, however, that this
-%example is still undergoing some deformations, so a constant
-%tank-treading velocity is not observed.
-
-%Both the migration speed and tank treading behavior of a vesicle in the closely-fitting channel depends on the separation distance between the solid wall and the vesicle.
-As the vesicle enters the narrow constriction, lubrication layers between the vesicle and the solid walls develop.
-The minimum distance between the multicomponent vesicles and the solid wall (solid lines) and the single-component vesicles and the solid wall (dashed lines) are plotted in Figure~\ref{fig:lubrication}.
-Top top plot is for the vesicle with reduced area $\alpha = 0.4$, and the bottom plot is for the vesicle with reduced area $\alpha = 0.6$.
-Note that the position is only between $-15$ and $15$ which is the region with strong confinement.
-
-%The size of the top and bottom lubrication layers are plotted in Figure~\ref{fig:lubrication} for reduced area (a) $\alpha = 0.4$ and (b) $\alpha = 0.6$.
-In both cases, we see that the multicomponent vesicle has larger lubrication layers than their single-component counterparts.
-As shown in Figures~\ref{fig:RA6} and~\ref{fig:RA4}, the result is that the multicomponent vesicle experiences less drag from the solid walls, and therefore migrates faster.
-This is confirmed in Figure~\ref{fig:location1} where we plot the position of each of the vesicle versus time for both reduced areas and both lipid species.
-The larger lubrication layer should also result in a smaller excess pressure, especially for reduced area $\alpha = 0.4$, and this is observed in Figure~\ref{fig:excessPressure}.
-
-%For the smaller reduced area, both the single and multicomponent vesicles are closer to the top wall than the bottom wall.
-More interesting, though, is that the multicomponent vesicle has a larger lubrication layer than its single-component counterpart.
-This larger lubrication layer means that less of the multicomponent vesicle experiences less drag from the solid wall, and its net migration speed is faster.
-This is verified in Figure~\ref{fig:location1}.
-For the larger reduced area, the vesicle is able to quickly deform away from the walls while entering the constriction.
-In Figure~\ref{fig:location1} we see that the multicomponent vesicle makes its way through the contstriction quicker than its single-component counterpart.
-Because the vesicle initially deforms, there is less initial drag from the walls.
-This quickly changes and the bottom lubrication layer becomes much thinner and the vesicle slows down.
-In Figure~\ref{fig:location1}, we can tell by the slopes of the curves that the single- and multicomponent vesicles are moving at roughly the same speed.
-
-%Whether a vesicle tank-treads or not is also related to the lubrication layer.
-In particular, if the lubrication layer between the top and lower walls are different, this indicates that the vesicle is center of mass is above or below the middle of the channel.
-When this happens, the non-linear of the flow results in a tank-treading vesicle.
-
-%The smaller reduced area $\alpha = 0.4$ also results in a larger
-%difference between the size of the top and boundary lubrication layers.
-%In particular, Figure~\ref{fig:lubrication}(a) shows that the bottom
-%lubrication layer is larger than the top lubrication layer, indicating
-%the vesicle is above the centerline, and we expect the non-linear shear
-%to result in a counterclockwise tank-treading motion. We define the
-%tank treading velocity using several tracker points (solid points) by
-%computing $\uu \cdot \tt$ where $\uu$ is the velocity and $\tt$ is the
-%tangent vector at the tracker point. Note that this quantity does not
-%represent a tank treading velocity until the vesicle reaches
-%tank-treading behavior. Figure~\ref{fig:tankTreadRAp4} shows that for
-%reduced area $\alpha = 0.4$, both the single and multicomponent
-%vesicles undergo an extended period of tank-treading, but at different
-%speeds, starting near the middle of the region of confinement and
-%ending as the vesicles exit this region. Since the difference in sizes
-%of the boundary layers is greater for the single-component vesicle, we
-%expect it to tank-tread faster, which we observe when comparing
-%Figures~\ref{fig:tankTreadRAp4}(a) and (e).In the multicomponent case,
-%there are several interesting features in the tangential velocity, and
-%these are denoted by the red marks in Figure~\ref{fig:tankTreadRAp4}.
-%The vesicle shapes at each of these points are in
-%Figure~\ref{fig:tankTreadRAp4}(b) and (c). The tangential velocity
-%includes spikes that occur whenever there is a decrease in the phase
-%energy due to floppy and stiff regions merging, and this can be
-%observed in Figures~\ref{fig:tankTreadRAp4}(d) and (e).
-
-%\begin{figure}[h]
-%    \begin{minipage}{0.49\columnwidth}
-%        \centering
-%        \subfigimg[width=\textwidth]{(a)}{figures/Fig11c1.pdf}
-%        \subfigimg[width=\textwidth]{(c)}{figures/Fig11b1.pdf}
-%        \subfigimg[width=\textwidth]{(e)}{figures/Fig11a.pdf}
-%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(a)}{figures/TankTreadRAp4Conc.pdf}
-%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(c)}{figures/TankTreadRANoConcp55.pdf}
-%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(e)}{figures/TankTreadRAp4NoConc.pdf}
-%        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6Conc.pdf}
-%        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6NoConc.pdf}
-%    \end{minipage}
-%    \hfill
-%    \begin{minipage}{0.49\columnwidth}
-%        \centering
-%        \subfigimg[width=\textwidth]{(b)}{figures/Fig11c2.pdf}
-%        \subfigimg[width=\textwidth]{(d)}{figures/Fig11b2.pdf}
-%        \subfigimg[width=\textwidth]{(f)}{figures/Fig11a2.pdf}
-%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(b)}{figures/TankTreadRAp4ConcVes.pdf}
-%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(d)}{figures/TankTreadRANoConcp55Ves.pdf}
-%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(f)}{figures/TankTreadRAp4NoConcVes.pdf}
-%        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6ConcVes.pdf}
-%        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6NoConcVes.pdf}
-%    \end{minipage}
-%    \caption{\small The tangential velocity at four Lagrangian points on a (a) single-component vesicle with $b = 1$ (c) single-component vesicle with $b = 0.55$, and (e) multicomponent vesicle.
-The reduced area is $\alpha = 0.4$ in all cases.
-(b/d/f) A corresponding vesicle shape with the Lagrangian points.
-%    \label{fig:tankTreadRAp4}}
-%\end{figure}
-
-%\begin{figure}[H]
-%    \begin{minipage}{0.49\columnwidth}
-%        \centering
-%        \subfigimg[width=\textwidth]{(a)}{figures/Fig12c1.pdf}
-%        \subfigimg[width=\textwidth]{(c)}{figures/Fig12b1.pdf}
-%        \subfigimg[width=\textwidth]{(e)}{figures/Fig12a1.pdf}
-        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(c)}{figures/TankTreadRAp6NoConcp55.pdf}
-        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(e)}{figures/TankTreadRAp6NoConc.pdf}
-        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6Conc.pdf}
-        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6NoConc.pdf}
-%    \end{minipage}
-%    \hfill
-%    \begin{minipage}{0.49\columnwidth}
-%        \centering
-%        \subfigimg[width=\textwidth]{(b)}{figures/Fig12c2.pdf}
-%        \subfigimg[width=\textwidth]{(d)}{figures/Fig12b2.pdf}
-%        \subfigimg[width=\textwidth]{(f)}{figures/Fig12a2.pdf}
-        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(b)}{figures/TankTreadRAp6ConcVes.pdf}
-        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(d)}{figures/TankTreadRAp6NoConcp55Ves.pdf}
-        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(f)}{figures/TankTreadRAp6NoConcVes.pdf}
-        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6ConcVes.pdf}
-        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6NoConcVes.pdf}
-%    \end{minipage}
-%    \caption{\small The tangential velocity at Lagrangian points on a (a) single-component vesicle with $b = 1$ (c) single-component vesicle with $b = 0.55$, and (e) multicomponent vesicle.
-The reduced area is $\alpha = 0.6$ in all cases.
-(b/d/f) A corresponding vesicle shape with the Lagrangian points.
-%    \label{fig:tankTreadRAp6}}
-%\end{figure}
-
 The sizes of the top and bottom lubrication layers are also related to
@@
 excess pressure.
-
-%\begin{figure}[H]
-%  \centering
-%  \subfigimg[width = 0.49\columnwidth]{(a)}{figures/Excess_Pressure_RAp4}
-%  \subfigimg[width = 0.49\columnwidth]{(b)}{figures/Excess_Pressure_RAp6}
-%%    \subfigimg[width = 0.45\columnwidth]{(a)}{figures/Fig10a.pdf}
-%%    \subfigimg[width = 0.45\columnwidth]{(b)}{figures/Fig10b.pdf}
-%  \caption{\label{fig:excessPressure} \small The excess pressure a
-%  stiff single-component (red), floppy single-component (green), and a
-%  multicomponent (blue) vesicle moving through stenosis. The reduced
-%  areas are (a) $\alpha = 0.4$, and (b) $\alpha = 0.6$.}
-%\end{figure}
-
-%While the size of the lubrication layers affect the tank-treading
-%behavior and the excess pressure, it has almost no effect on the
-%migration speed of the vesicle. 
-%%In Figure~\ref{fig:vesVelocity}, we plot
-%%the average velocity of the vesicle as it passes through the stenosed
-%%region.
-%With the exception of the single-component vesicle with $b=1$ and
-%$\alpha = 0.6$, which has an average vesicle speed about 5\% slower, the
-%average vesicle speed is constant. Obviously, this average velocity
-%would be affected by the capillary number.
-
-%\begin{figure}[H]
-%  \centering
-%  \includegraphics[width=\columnwidth]{figures/Fig9.pdf}
-%%  \input{figures/Fig9.tikz}
-%  \caption{\label{fig:vesVelocity} \small The average vesicle velocity
-%  as it passes through stenosis. The vesicle stiffness and reduced area
-%  have no significant effect.}
-%\end{figure}
 
@@
 \end{align}
-%is sufficiently large.
-%to locally reverse the sign of the pressure
-%gradient in the streamwise direction.
 Here,
@@
 Figure~\ref{fig:RA6leftRightRand}, snapshots of vesicles with reduced
-area $\alpha = 0.6$ with different initial lipid distributions are
+area $\alpha = 0.5$ with different initial lipid distributions are
 illustrated. The initial distributions are (a) random, (b) stiff in the
@@
 curvature are quickly smoothed.
-%Since we can see in Figure~\ref{fig:RA6leftRightRand} that the regions
-%of high curvature are located in the back of the vesicle, we expect the
-%overall bending energies to be lowest for the randomly distributed case
-%and the fully separated floppy region on the back case. We observe this
-%in Figure~\ref{fig:RAp6leftRightRandBending}.
 
@@
   \centering
-%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(a)}{figures/rightSep.pdf}
-%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(b)}{figures/randSep.pdf}
-%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(c)}{figures/leftSep.pdf}
   \includegraphics[width=\columnwidth]{figures/Contracting_RAp6MCp5.pdf}
@@
 \end{figure}
-
-%\begin{figure}[H]
-%  \centering
-%  \includegraphics[width=\columnwidth]{figures/bending_leftRightRand.pdf}
-%  \caption{\label{fig:RAp6leftRightRandBending} The bending energy of a
-%  multicomponent vesicle that is 50\% stiff with an initial phase
-%  separation to the left (blue), to the right (red), randomly
-%  distributed (yellow). The vesicle exits the contraction $x \approx
-%  15$.} 
-%\end{figure}
 
@@
 symmetry of the vesicle shape is broken at smaller percentages. We also
-see that stiffer vesicles have faster migration speeds, but the effect
+see that floppier vesicles have faster migration speeds, but the effect
 is quite small---Table~\ref{tbl:contractingTimes} reports the time the
-vesicle first passes through the neck. \color{red} I think this is backwards? The table reports that the floppiest vesicle made it through the contraction the quickest. \color{black}
-%In Figure~\ref{fig:RA5}, we consider a vesicle with reduced area
-%$\alpha = 0.5$ and the capillary number is $Ca = 0.25$. We start with a
-%single-component vesicle and then increase the percentage of the
-%vesicle membrane that is floppy. By comparing the vesicle location at
-%the time step just before the vesicle passes through the constriction,
-%we can immediately see that vesicles with membranes that have larger
-%percentage of floppy regions reach and pass through the neck earlier.
-%The dimensionless times that the entire vesicle first passes through
-%the neck are reported in Table~\ref{tbl:contractingTimes}.
-
-%\begin{figure*}[t]
+vesicle first passes through the neck.
+
 \begin{figure}[h]
@@
   \includegraphics[width=\columnwidth]{figures/Contracting_RAp6MC_variableConc.pdf}
-%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
-%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig14a_newPaper.pdf}
-%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig14b_newPaper.pdf}
-%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(d)}{figures/Fig14c_newPaper.pdf}
-%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(e)}{figures/Fig14e_newPaper.pdf}
   \caption{\label{fig:RA5} \small A vesicle passing through a
   contracting geometry. The vesicle's reduced area is $\alpha = 0.5$ and
-  the Capillary number is $Ca = 0.25$. (a)
-  A stiff single-component vesicle. The percentage of the
-  multicomponenet vesicle that is floppy is (b) 15\%, (c) 25\%, (d)
-  35\%, and (e) 45\%. The vesicles with a larger percentage of floppy
-  regions pass through the neck earlier than the vesicles with less
-  percentage of floppy regions.}
+  the Capillary number is $Ca = 0.25$. (a) A stiff single-component
+  vesicle. The percentage of the multicomponent vesicle that is floppy
+  is (b) 15\%, (c) 25\%, (d) 35\%, and (e) 45\%. The vesicles with a
+  larger percentage of floppy regions pass through the neck earlier than
+  the vesicles with less percentage of floppy regions.}
 \end{figure}
-%\end{figure*}
 
@@
 \end{table}
-%\begin{table}[H]
-%  \centering
-%  \begin{tabular}{l|c}
-%    Floppy percentage & Time to pass through neck \\
-%    \hline
-%    0\% &  2.32 \\
-%    15\% & 2.30 \\
-%    25\% & 2.29 \\
-%    35\% & 2.26 \\
-%    45\% & 2.24 \\
-%%    Single-component &  2.32 \\ %2.3173\\
-%%    15\% Multicomponent & 2.30 \\%2.2960\\
-%%    25\% Multicomponent & 2.29 \\%2.2868\\
-%%    35\% Multicomponent & 2.26 \\%2.2637\\
-%%    45\% Multicomponent & 2.24 \\%2.2388\\
-%    \hline
-%  \end{tabular}
-%  \caption{\label{tbl:contractingTimes} The time required for the
-%  vesicles to completely pass through the neck.}
-%\end{table}
 
@@
   \includegraphics[width=\columnwidth]{figures/bendingContracting.pdf}
-%  \includegraphics[width=\columnwidth]{figures/bendingAllContracting.pdf}
   \caption{\label{fig:bendingAll} \small The bending energy for a
@@
 energy are included.
-%and we can indeed see that transitioning vesicle shape between these
-%different states.
 
@@
   \centering
-%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
   \subfigimg[width=\columnwidth]{(a)}{figures/ContractingEnergy_SC.pdf}
   \subfigimg[width=\columnwidth]{(b)}{figures/ContractingEnergy_MC.pdf}
-%  \subfigimg[width=\columnwidth]{(a)}{figures/bendingSC.pdf}
-%  \subfigimg[width=\columnwidth]{(b)}{figures/bendingEngMC45.pdf}
   \caption{\label{fig:bendingSC_contracting} \small The bending energy
@@
 \end{figure}
-
-%\begin{figure}
-%  \begin{minipage}{0.49\columnwidth}
-%    \centering
-%    \subfigimg[width=\textwidth]{(a)}{figures/Fig15i.pdf}
-%    \subfigimg[width=\textwidth]{(c)}{figures/Fig15a.pdf}
-%    \subfigimg[width=\textwidth]{(e)}{figures/Fig15c.pdf}
-%    \subfigimg[width=\textwidth]{(g)}{figures/Fig15e.pdf}
-%    \subfigimg[width=\textwidth]{(i)}{figures/Fig15g.pdf}
-%  \end{minipage}
-%  \hfill
-%  \begin{minipage}{0.49\columnwidth}
-%    \centering
-%    \subfigimg[width=\textwidth]{(b)}{figures/Fig15j.pdf}
-%    \subfigimg[width=\textwidth]{(d)}{figures/Fig15b.pdf}
-%    \subfigimg[width=\textwidth]{(f)}{figures/Fig15d.pdf}
-%    \subfigimg[width=\textwidth]{(h)}{figures/Fig15f.pdf}
-%    \subfigimg[width=\textwidth]{(j)}{figures/Fig15h.pdf}
-%  \end{minipage}
-%  \caption{\label{fig:Energy} \small The bending (blue), tension (yellow), and phase (red) energies for a single-component vesicle ((a) and (b)) and a multicomponent vesicle (c)--(j) with $\alpha = 0.5$.
-As the size of the floppy region increases, the maximum bending energy decreases.}
-%\end{figure}
-
-%\begin{itemize}
-%    \item Look at single-component vs. multicomponent with two different reduced areas and using random and non-random initial lipid distributions
-%    \begin{itemize}
-%        \item Show the floppy region rotating around to/forming in the back
-%        \item \todo[inline]{$\Chi = 0.5 \mu$m/s, RA = 0.4, single component, multi component (random, left, right)}
-%        \item \todo[inline]{$\Chi = 0.5 \mu$m/s, RA = 0.6 (for consistency, BUT maybe just the RA = 0.5 is sufficient since they all also do not make it), single component, multi component (random, left, right)}
-%        \item \todo[inline]{Look at the $\Chi = 5 \mu$m/s runs to see how these compare. Idea - Slower runs allow more time for the floppy region to move around.} 
-%        \item The RA = 0.4 cases all move through the contraction for both flow rates. All the RA = 0.5 cases get stuck for both flow rates.
-%    \end{itemize}
-%    \begin{figure}[H]
-%        \centering
-%        \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
-%       \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig14a.pdf}
-%        \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig14b.pdf}
-        %\subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(d)}{figures/Fig14d.pdf}
-%        \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(d)}{figures/Fig14c.pdf}
-%        \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(e)}{figures/Fig14e.pdf}
-%        \caption{\label{fig:RA5} \small Snapshots of a vesicle passing through a contracting geometry.
-In all cases, the vesicle's reduced area is $\alpha = 0.5$ and the dimensionless maximum velocity is $\chi = 0.25$.
-The vesicles are: (a) single-component with bending modulus $b=1$; (b) Multicomponent with 15\% floppy region; (c) Multicomponent with 25\% floppy region; (d) Multicomponent with 35\% floppy region; (e) Multicomponent with 45\% floppy region.
-We see that the vesicles with a larger percentage of floppy regions pass through the neck earlier than the vesicles with less percentage of floppy regions.}
-        %\caption{\label{fig:RA6} A single-component (top) and multicomponent (bottom) vesicle passing through the stenosed geometry.
-In both simulations, the reduced area is $0.6$ and the dimensionless maximum velocity is $\chi = 0.25$.
-Note that the multicomponent vesicle travels slightly faster, so it leaves the narrow constriction earlier (see Figure~\ref{fig:location1}.}
-%    \end{figure}
-
-%    \begin{figure}
-%      \begin{minipage}{0.49\columnwidth}
-%        \centering
-%    %    \subfigimg[width = \columnwidth, trim = {1cm 20cm 1cm 3cm}, clip]{(a)}{figures/RAp4BkgrdFlow.pdf}
-%        \subfigimg[width=\textwidth]{(a)}{figures/Fig15i.pdf}
-%        \subfigimg[width=\textwidth]{(c)}{figures/Fig15a.pdf}
-%        \subfigimg[width=\textwidth]{(e)}{figures/Fig15c.pdf}
-%        \subfigimg[width=\textwidth]{(g)}{figures/Fig15e.pdf}
-%        \subfigimg[width=\textwidth]{(i)}{figures/Fig15g.pdf}
-%        
-%      \end{minipage}
-%      \hfill
-%      \begin{minipage}{0.49\columnwidth}
-%        \centering
-%        \subfigimg[width=\textwidth]{(b)}{figures/Fig15j.pdf}
-%        \subfigimg[width=\textwidth]{(d)}{figures/Fig15b.pdf}
-%        \subfigimg[width=\textwidth]{(f)}{figures/Fig15d.pdf}
-%        \subfigimg[width=\textwidth]{(h)}{figures/Fig15f.pdf}
-%        \subfigimg[width=\textwidth]{(i)}{figures/Fig15h.pdf}
-
-%      \end{minipage}
-%      \caption{\label{fig:Energy} \small The Bending (blue), tension (yellow), and phase (red) energies for a (a/b/c/d/e/f/g/h) Multicomponent vesicle, (i/j) single-component vesicle with $\alpha = 0.5$.
-As the size of the floppy region increases, the maximum bending energy decreases.}
-%    \end{figure}
-
-%    \item Vesicle has a `preferred orientation' - forces the floppy region to the back.
-The question becomes: Is there a Goldilocks region where there is enough floppy region in the back for the vesicle to pass through?
-(RA = 0.5)
-%    \begin{itemize}
-%        \item \todo[inline]{$Chi = 5 \mu$m/s, 10\% floppy}
-%        \item \todo[inline]{$Chi = 5 \mu$m/s, 30\% floppy}
-%        \item \todo[inline]{$Chi = 5 \mu$m/s, 50\% floppy}
-%        \item \todo[inline]{$Chi = 5 \mu$m/s, 90\% floppy}
-%    \end{itemize}
-%    \item Investigate why the 30\% case makes it though. Hopefully there's a story in these plots:
-%    \begin{itemize}
-%        \item \todo[inline]{Excess pressure plots of all}
-%        \item \todo[inline]{Boundary layer plots of all}
-%        \item \todo[inline]{Energy plots of all}
-%        \item W, S, to C. (something to explore, floppy/stiff regions bending energy)
-%    \end{itemize}
-
-%    \item Discuss the shapes of the vesicles after they pass through the contraction. Lots of oscillations in the floppy region
-%    \begin{itemize}
-%        \item Maybe include error plots or a maximum error. 
-%    \end{itemize}
-%\end{itemize}
 
@@
 stenosis) is correlated to the size of the lubrication layer: a larger
-lubrication layer size results in smaller excess pressure.
-%the larger the lubrication layer size, the smaller the excess pressure
-%is.
+lubrication layer size results in a smaller excess pressure.
 
@@
 %migrating cell.
-
-%\begin{itemize}
-%  \item New bending model using hyperbolic tangent (sigmoidal shape)
-%    which is necessary to maintain a positive bending modulus
-%
-%  \item Orientation of the phase is always stiff on the front and floppy
-%    on the back, but we don't know why (yet). Observed by others such as
-%    Biros and Agrawalla, George and Misbah, and others.
-%
-%  \item Boundary layer and change in sign of pressure gradient term that
-%    drives the lubrication flow. This is a combination of the tension
-%    and the phase boundary between stiff and floppy regions.
-%
-%  \item Sudden drop in bending energy for multicomponent can be
-%    explained by the sudden coarsening of the lipids.
-%
-%  \item Relationship between tank treading, excess pressure and layer
-%    thickness.
-%
-%  \item  Inability to coarsen when under strong confinement. Can be
-%    related to item 2. Strong confinement arrests phase coarsening.
-%
-%\end{itemize}
 
@@
 %
-%\section*{Author Contributions}
+\section*{Author Contributions}
+Conceptualization: AG, BQ, YNY; methodology: AG, BQ, YNY; validation:
+AG, BQ, YNY; formal analysis: AG, BQ, YNY; investigation: AG, BQ, YNY;
+resources: BQ, YNY; data curation: AG, BQ, YNY; writing - original
+draft: AG, BQ, YNY ; writing - review and editing: BQ, YNY;
+visualization: AG, BQ; supervision: BQ, YNY; project administration: BQ,
+YNY; funding acquisition: BQ, YNY
 %We strongly encourage authors to include author contributions and recommend using \href{https://casrai.org/credit/}{CRediT} for standardised contribution descriptions.
@@
 \section*{Acknowledgements}
-The Acknowledgements come at the end of an article after Conflicts of interest and before the Notes and references.
+We thank David Salac and Shuwang Li for discussions. B.Q.~acknowledges
+support from the Simons Foundation, Mathematics and Physical
+Sciences-Collaboration Grants for Mathematicians, Award No.~527139.
+Y.-N.Y.~acknowledges support from NSF (Grants No.~DMS 1614863 and
+No.~DMS 195160) and Flatiron Institute, part of Simons Foundation.
+%The Acknowledgements come at the end of an article after Conflicts of interest and before the Notes and references.
 

### 2023-08-16 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

@@
   cells undergoing large deformations while traversing %when passing through extreme
-  narrow constrictions. We propose a novel parameterization for the
+  narrow constrictions. We propose a new parameterization for the
   bending modulus that remains positive for all lipid phase parameter
@@
 %have been observed to contain a vast 
-exhibit a diverse array of
+comprise diverse arrays of
+%exhibit a diverse array of
 proteins and lipid species. 
@@
 This parameterization maps the local minimums of the double-well
-potential close to $\beta$ and $1$, but more importantly, b(u) remains
+potential close to $\beta$ and $1$, but more importantly, $b(u)$ remains
 bounded in $(\beta,1)$ even when $u \notin [0,1]$
-(Figure~\ref{fig:concModels}(b)). This new bending model is validated in
-Section~\ref{sec:validation}.
+(Figure~\ref{fig:concModels}(b)). We compare this new bending model against the linear model for 
+a phase-treading and tank treading vesicle in Section~\ref{sec:validation}.
+
 %To demonstrate the necessity of this new bending model, we consider a
@@
   entering a closely-fitting channel (black lines) using the linear
-  model in Equation~\eqref{eqn:linearBending}. An instability is
+  model in Equation~\eqref{eqn:linearBending}.  The color denotes the bending modulus $b(u)$.
+  An instability is
   introduced where the vesicle bending modulus becomes negative. (b) The
@@
   title. The red region is stiff and the blue region is floppy. The
-  simulations qualitatively agree with the results presented
+  simulations agree with the results
   in~\citet{liu-mar-li-vee-low2017}.}
@@
 geometry that slowly contracts to a narrow neck and then quickly widens
-(contracting). We considered a semipermeable vesicle suspended in these
-same geometries in our previous work~\cite{qua-gan-you2021}. All the
-multicomponent examples have floppy-to-stiff ratio $\beta = 10^{-1}$.
+(contracting). 
+%We considered a semipermeable vesicle suspended in these
+%same geometries in our previous work~\cite{qua-gan-you2021}. 
+All the multicomponent examples have floppy-to-stiff ratio $\beta = 10^{-1}$.
 For the single-component case, we consider two bending stiffnesses:
@@
 single-component and multicomponent vesicles are clearly tank treading.
-The direction and speed of the tank-treading depends on the how much of
+The direction and speed of the tank-treading depends on how much of
 the vesicle membrane is exposed to positive shear (below the center
 line) versus how much is exposed to negative shear (above the center
-line). The majority of the membrane of the stiff single-component and
+line) \cite{kao-bir-mis2009}. The majority of the membrane of the stiff single-component and
 multicomponent vesicles are below the center line, and this results in a
@@
 single-component case, the tangential traction is $\mathbf{F}_\tt =
--\sigma_s$ which is the usual Marangoni effect.
+-\sigma_s$ which is the Marangoni stress.
 
@@
 contracting geometry}
-In this section, we consider a vesicle passing through a geometry that
-slowly contracts to a region that is only 2~$\mu$m wide, and then
-immediately opens back up to a channel that is ten times larger. We
+In this section, we consider a vesicle passing through a channel that
+slowly contracts to a  2~$\mu$m wide neck, and then
+immediately opens up to a channel that is ten times larger. We
 first consider the effect of the initial lipid concentration when the
@@
     Floppy percentage & 0\% & 15\% & 25\% & 35\% & 45\% \\ 
-    Time  & 2.32 & 2.30 & 2.29 & 2.26 & 2.24 \\
+    Time  (dimensionless) & 2.32 & 2.30 & 2.29 & 2.26 & 2.24 \\
     \hline
@@
 AG, BQ, YNY; formal analysis: AG, BQ, YNY; investigation: AG, BQ, YNY;
-resources: BQ, YNY; data curation: AG, BQ, YNY; writing - original
+data curation: AG, BQ, YNY; writing - original
 draft: AG, BQ, YNY ; writing - review and editing: BQ, YNY;
-visualization: AG, BQ; supervision: BQ, YNY; project administration: BQ,
+visualization: AG, BQ, YNY; supervision: BQ, YNY; project administration: BQ,
 YNY; funding acquisition: BQ, YNY
@@
 \section*{Acknowledgements}
-We thank David Salac and Shuwang Li for discussions. B.Q.~acknowledges
-support from the Simons Foundation, Mathematics and Physical
+We thank David Salac  for discussions, and Shuwang Li for discussions and sharing his code for a multicomponent vesicle in free space. 
+B.Q.~acknowledges support from the Simons Foundation, Mathematics and Physical
 Sciences-Collaboration Grants for Mathematicians, Award No.~527139.

### 2023-08-16 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
worked on figures

@@
   entering a closely-fitting channel (black lines) using the linear
-  model in Equation~\eqref{eqn:linearBending}.  The color denotes the bending modulus $b(u)$.
-  An instability is
-  introduced where the vesicle bending modulus becomes negative. (b) The
-  linear bending model in red (Equation~\eqref{eqn:linearBending}) and
-  the new sigmoid bending model in blue
-  (Equation~\eqref{eqn:tanhBending}). Note that the new bending model
-  satisfies $b \in (\beta,1)$ even if $u \notin [0,1]$.}
+  model in Equation~\eqref{eqn:linearBending}.  The color denotes the
+  bending modulus $b(u)$.  An instability is introduced where the
+  vesicle bending modulus becomes negative. (b) The linear bending model
+  in red (Equation~\eqref{eqn:linearBending}) and the new sigmoid
+  bending model in blue (Equation~\eqref{eqn:tanhBending}). Note that
+  the new bending model satisfies $b \in (\beta,1)$ even if $u \notin
+  [0,1]$.}
 \end{figure}
@@
   \centering
-  \begin{tabular}{l|ccccc}
+  \begin{tabular}{l|cccccc}
     \hline
-    Floppy percentage & 0\% & 15\% & 25\% & 35\% & 45\% \\ 
-    Time  (dimensionless) & 2.32 & 2.30 & 2.29 & 2.26 & 2.24 \\
+    Floppy percentage & 0\% & 15\% & 25\% & 35\% & 45\% & 50\% \\ 
+    Dimensionless time & 2.32 & 2.30 & 2.29 & 2.26 & 2.23 & 2.25\\
     \hline
@@
   \includegraphics[width=\columnwidth]{figures/bendingContracting.pdf}
-  \caption{\label{fig:bendingAll} \small The bending energy for a
-  single-component vesicle (blue) and a multicomponent vesicle
-  (red)--(black) with $\alpha = 0.5$. As the size of the floppy region
-  increases, the maximum bending energy decreases.}
+  \caption{\label{fig:bendingAll} \small The bending energies of the
+  single-component and multicomponent vesicles in Figure~\ref{fig:RA5}.
+  The vertical dashed lines correspond to the configurations in
+  Figure~\ref{fig:RA5}. As the size of the floppy region increases, the
+  maximum bending energy decreases.}
 \end{figure}
@@
   \caption{\label{fig:bendingSC_contracting} \small The bending energy
-  of (a) a single-component vesicle, and (b) a multicomponent vesicle
-  whose boundary is 45\% floppy passing through a contracting geometry.
-  The vesicle shape at different locations are included. We can clearly
-  see that the sudden increases and decreases in the bending energy are
-  due to transitions between lower energy and higher energy shapes.}
+  of (a) a stiff single-component vesicle, and (b) a multicomponent
+  vesicle whose boundary is 45\% floppy passing through a contracting
+  geometry. The vesicle shape at different locations are included. We
+  can clearly see that the sudden increases and decreases in the bending
+  energy are due to transitions between lower energy and higher energy
+  shapes.}
 \end{figure}

### 2023-08-16 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

@@
 single-component case, the tangential traction is $\mathbf{F}_\tt =
--\sigma_s$ which is the Marangoni stress.
+-\sigma_s$ which is the Marangoni stress.  For a single-component vesicle, the streamwise gradient 
+of the Marangoni stress determines the sign of the Poiseuille coefficient in Figure~\ref{fig:BLvelocities}(a).
+For a multicomponent vesicle, the Poiseuille coefficient can also change sign around the boundary 
+between two lipid domains, where the membrane energy has changes. This implies that, by visualizing the flow
+in the lubrication layer, it is possible to identify the location of boundaries between lipid domains as shown in Figure~\ref{fig:BLvelocities}(b).
 
@@
 layer, we further elucidated the correlation between the location of
-boundary between lipid domains, the Marangoni stress, and the change of
+boundary between lipid domains and the change of
 sign in the pressure gradient in the lubrication layer. These results

### 2023-08-16 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny2

@@
 For a multicomponent vesicle, the Poiseuille coefficient can also change sign around the boundary 
-between two lipid domains, where the membrane energy has changes. This implies that, by visualizing the flow
+between two lipid domains, where the membrane energy changes sharply between lipid species. This implies that, by visualizing the flow
 in the lubrication layer, it is possible to identify the location of boundaries between lipid domains as shown in Figure~\ref{fig:BLvelocities}(b).

### 2023-08-16 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny2

@@
 is the derivative of the membrane energy with respect to the lipid
-concentration~\cite{soh-tse-li-voi-low2010}. Note that in the
-single-component case, the tangential traction is $\mathbf{F}_\tt =
--\sigma_s$ which is the Marangoni stress.  For a single-component vesicle, the streamwise gradient 
+concentration~\cite{soh-tse-li-voi-low2010}. For a single-component vesicle,
+the tangential traction is $\mathbf{F}_\tt =-\sigma_s$, the Marangoni stress, and  the streamwise gradient 
 of the Marangoni stress determines the sign of the Poiseuille coefficient in Figure~\ref{fig:BLvelocities}(a).
 For a multicomponent vesicle, the Poiseuille coefficient can also change sign around the boundary 
-between two lipid domains, where the membrane energy changes sharply between lipid species. This implies that, by visualizing the flow
-in the lubrication layer, it is possible to identify the location of boundaries between lipid domains as shown in Figure~\ref{fig:BLvelocities}(b).
+between two lipid domains, where the membrane energy changes sharply between lipid species. 
+This correlation between the distribution of the lipid domains and the fluid velocity profile in the lubrication layer
+implies that, by visualizing the flow
+in the lubrication layer and identifying locations where the nonlinear shear flow profile is convex, 
+it is possible to identify the location of boundaries between lipid domains as shown in Figure~\ref{fig:BLvelocities}(b).
 

### 2023-08-17 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny3

--- 2023-08-16 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
@@
 is the derivative of the membrane energy with respect to the lipid
-concentration~\cite{soh-tse-li-voi-low2010}. Note that in the
-single-component case, the tangential traction is $\mathbf{F}_\tt =
--\sigma_s$ which is the Marangoni stress.  For a single-component vesicle, the streamwise gradient 
+concentration~\cite{soh-tse-li-voi-low2010}. For a single-component vesicle,
+the tangential traction is $\mathbf{F}_\tt =-\sigma_s$ (the Marangoni stress), and  the streamwise gradient 
 of the Marangoni stress determines the sign of the Poiseuille coefficient in Figure~\ref{fig:BLvelocities}(a).
 For a multicomponent vesicle, the Poiseuille coefficient can also change sign around the boundary 
-between two lipid domains, where the membrane energy changes sharply between lipid species. This implies that, by visualizing the flow
-in the lubrication layer, it is possible to identify the location of boundaries between lipid domains as shown in Figure~\ref{fig:BLvelocities}(b).
+between two lipid domains, where the membrane energy changes sharply between lipid species. 
+This correlation between the location of the boundary between lipid domains and the fluid velocity profile in the lubrication layer
+implies that, by visualizing the flow
+in the lubrication layer and identifying locations where the nonlinear shear flow profile is convex, 
+it is possible to identify the location of boundaries between lipid domains as shown in Figure~\ref{fig:BLvelocities}(b).
 

### 2023-09-20 vesicle_code/docs/confinedMulti/response.tex
starting revisions for Soft Matter paper

\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage{url}

\begin{document}

We thank the referees for their assessment of our work.  The following
is our response to each of the specific comments and suggestions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Reviewer 1}

The referee wrote: I have reviewed ''Hydrodynamics of Multicomponent
Vesicles Under Strong Confinement'' by Gannon, Quaife, and Young. To my
understanding this work is unique as the dynamics of multicomponent
vesicles under constrictions has not yet been investigated. Before
acceptance there are some questions and issues which should be
addressed:

\noindent
{\bf Response:}: We thank the referee for the confirmation that the
topic is unique and has not yet been investigated.

\begin{enumerate}
%%%%%%%%
\item In the phase energy, Eq. (5), it is stated that the parameter
  $\epsilon$ is much smaller than 1 but then it is stated that this
    parameter is equal to 100. Please address this inconsistency.

\noindent
{\bf Response:} This was our oversight. The parameter values for $a$ and
$\epsilon$ were unintentionally reversed. This has been fixed.

%%%%%%%%
\item What motivated the choice of a sigmoid function, Eq. (9), rather
  than a simple min/max operation so that the bending rigidity does not
    extend past the $[0.1, 1]$ range? Would the use of a regular-mixture
    model, which might be more physically realistic, remove the need for
    such a mathematical approximation as the equilibrium concentrations
    will no longer be $0$ and $1$?

\noindent
{\bf Response:} A response

%%%%%%%%
\item Please define $\eta$ in Eq.~(10).

\noindent
{\bf Response:} $\eta$ is a density function that is required to satisfy
    the Dirichlet boundary condition on the solid walls. The text has
    been adjusted.

%%%%%%%%
\item Please define whether $\mathbf{n}$ in Eq.~(12) is the inward or outward pointing unit normal.

\noindent
{\bf Response:} It is the outward pointing unit normal. The text has
    been adjusted.

%%%%%%%%
\item How is surface incompressibility enforced?

\noindent
{\bf Response:} The tension $\sigma$ acts as a Lagrange multiplier so
    that the inextensibility condition can be satisfied. The text has
    been adjusted.

%%%%%%%%
\item Please define $\mathbf{U}$ in Eq. (15). Is this the velocity of
  the interface?

{\bf Response:} This is the prescribed velocity along the solid wall
    which is a combination of no-slip along the top and bottom of the
    channel, and a Poiseuille flow at the inlet and outlet. We now
    reference equation (3), which defines $\mathbf{U}$, immediately
    after equation (15).

%%%%%%%%
\item What value of $\delta$ is used to determine the lubrication layer
  thickness?

{\bf Response:} A response

%%%%%%%%
\item The simulation parameters must be provided. In the stenosis case
  what is the (dimensionless) width of the constricted region? For the
    contracting geometry case what does a $2~\mu$m wide neck correspond
    to?

{\bf Response:} A response

\end{enumerate}

\newpage 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Reviewer 2}

The referee wrote: The authors of the paper, explored the effect of
hydrodynamics on the behavior of multicomponent vesicles under strong
confinement using numerical simulations. They have elucidated the
effects of the lubrication layer that exists between the vesicle, and
explored how confinement affects the excess pressure needed to push the
vesicle through the conduit. This study is useful to the community and
contains some sound insights regarding multicomponent vesicles. It,
however, is important that the authors make the following changes to be
considered for publication.

\noindent
{\bf Response:}: We thank the referee for their assessment and suggested
changes.

\begin{enumerate}
%%%%%%%%
\item The authors specify a line energy parameter $\epsilon = 100$. It
  is important that the authors justify this choice along with an
    experimental study which uses similar parameter ranges. This is
    important so that a future experimental study could be performed
    using these parameters as a guide.

\noindent
{\bf Response:} This was our oversight. The parameter values for $a$ and
$\epsilon$ were unintentionally reversed. This has been fixed.

%%%%%%%%
\item Minor comment: In Figure 4 and 5, the authors should add the $x$
  coordinate under the figure so that the readers are able to understand
    the results better.

\noindent
{\bf Response:} A response

%%%%%%%%
\item The authors mention the phrase `size of lubrication layer' in the
  paper. They need to explicitly define this parameter. It could be
    confusing to a reader whether they talk about
    $|\gamma_{\mathrm{layer}}|$ or $w_{\mathrm{top}}$ and
    $w_{\mathrm{bottom}}$.

\noindent
{\bf Response:} A response

%%%%%%%%
\item The authors measure the tangential velocity at 4 points. They
  should provide some justification for this number. Also, it is
    advisable that in Figure 7, the authors use a different color for
    each velocity plot. The plot looks highly convoluted and does not
    convey the message clearly. Also, what are the bounds within which
    the authors call the tangential velocity to be constant in Figure 7?
    They should define a bound for the variation that could be
    considered constant. Moreover, in Figure 7, for the floppy vesicle,
    the authors see a large deviation for the tangential velocity. It
    doesn't seem like the velocity could be called `constant'. The
    authors should provide a more detailed explanation for this.

\noindent
{\bf Response:} A response

%%%%%%%%
\item In some simulations, the authors choose a `random' initial
  condition. It would be helpful if they could mathematically define the
    function for this initial condition.

\noindent
{\bf Response:} A response

%%%%%%%%
\item In Figure 6, the author should comment on the energy behavior of
  the floppy vesicle in the stenosis region.

\noindent
{\bf Response:} A response

%%%%%%%%
\item In Figure 7, when the authors look at the excess pressure plots,
  they should describe the behavior of the floppy vesicle due to the
  difference in lubrication thickness and, in turn, excess pressure. It
  seems like the excess pressure shows a similar trend as the stiff
  vesicle.

\noindent
{\bf Response:} A response

%%%%%%%%
\item Not really a comment, but the author's analysis of the velocity
  profiles in Figure 8 is fantastic. It captures the stress and pressure
  gradient behavior aptly and provides a theoretical basis as well.

\noindent
{\bf Response:} We thank the reviewer for this compliment. We are also
very happy with this result.

%%%%%%%%
\end{enumerate}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Reviewer 3}

The referee wrote: The authors study the passage of a vesicle through a
constriction. A vesicle’s membrane has some mechanical properties analog
to red blood cells motivating many theoretical and numerical studies.
Indeed, this issue has known many progress during the last decade. A
vesicle is also a fascinating physical soft particle as its membrane
area is constant as well as its volume leading to an essential role of
deflation. But contrary to capsules, as the membrane is fluid, there is
no buckling. Finally, the study is inspired by modeling RBC.

\noindent
{\bf Response:}: We thank the referee for their assessment and suggested
changes.

\begin{enumerate}
%%%%%%%%
\item This study is limited to the two-dimensional case, which is not
  reality. It is a strong approximation and full 3D studies are still a
    challenge in constrictions. But, in the axisymmetrical case, there
    are several results in literature which could be more or less,
    considered as benchmark:
    \url{http://dx.doi.org/10.1103/PhysRevFluids.5.043602}, \\
    \url{https://doi.org/10.1017/jfm.2017.743}

\noindent
{\bf Response:} A response

%%%%%%%%
\item The authors should justify why they limit their investigations to
  the 2D case if 3D is possible. I note that the authors also cite
    relevant literature as 10, 11 $\ldots$ References to 2D are
    excellent. A typical argument is the high time of 3D simulations.
    Can the authors provide an order of magnitude?

\noindent
{\bf Response:} A response

%%%%%%%%
\item The authors present the essential steps of the numerical model. It
  is well done and the references well chosen. I have appreciated the
    introduction of equation (9) an figure 2. However, there are two
    points to clarify :
    \begin{itemize}
      \item page 2 : there is a difference in literature of the
        capillary number. Some authors use the flow curvature, others
        the mean velocity as the authors. Please explain your choice.
      \item page 2, right column ``The parameter $\epsilon \ll 1$ sets the
        size of the transition region of u, and the parameter a is line
        tension scaled by the characteristic bending stiffness. All
        simulations use the parameter values $\epsilon = 100$ and $a =
        0.04.$" $\epsilon = 100$ is contradictory to $\epsilon \ll 1$.
        Please explain or correct
    \end{itemize}

\noindent
{\bf Response:} This was our oversight. The parameter values for $a$ and
$\epsilon$ were unintentionally reversed. This has been fixed.

%%%%%%%%
\item Why do authors never observe the blocking of vesicles contrary to
  experiments? It would the opportunity to perform a phase diagram and
    to show the effect of multicomponent.

\noindent
{\bf Response:} A response

%%%%%%%%
\item In experiments, the channel is a slit. What do the authors expect
  from such a difference?

\noindent
{\bf Response:} A response

%%%%%%%%
\item Finally, this study is interesting and provides new insights.
  However, I advise authors to improve the quantitative part of their
  results (variation with Ca or confinement or something else, phase
  diagram...) to be more relevant for a journal such as Soft Matter. I
  am waiting the new manuscript.

\noindent
{\bf Response:} A response

%%%%%%%%
\item Page 2, left column : the flow is assumed to be in the limit of
  zero Reynolds number : not the fluid

\noindent
{\bf Response:} A response

%%%%%%%%
\item The title is a bit misleading as the authors only consider the
  deflation equal to the one of RBC. However, as there is some conflict
  between capsules and vesicles as models of RBC, the title can be
  tolerated.

\noindent
{\bf Response:} A response
\end{enumerate}

\end{document}

### 2023-09-20 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny4
starting revisions for Soft Matter paper

@@
     \quad \xx = (x,y) \in \Gamma,
+  \label{eqn:dirBC}
 \end{align}
@@
 bending stiffness. All simulations use the parameter values
-$\epsilon=100$ and $a=0.04$. The resulting membrane forces are
+$\epsilon=0.04$ and $a=100$. The resulting membrane forces are
 \begin{align}
@@
 \end{align}
-$\rr = \xx - \yy$, $\rho = |\rr|$, and $\mathds{I}$ is the $2 \times 2$
-identity matrix. The corresponding pressure is
+$\rr = \xx - \yy$, $\rho = |\rr|$, $\nn$ is the outward unit normal,
+$\eeta$ is a currently unknown density function, and $\mathds{I}$ is the
+$2 \times 2$ identity matrix. The membrane tension $\sigma$ acts as a
+Lagrange multiplier so that the inextensibility condition,
+$\nabla_{\gamma} \cdot \uu = 0$, can be satisfied. The corresponding
+pressure is
 \begin{align}
@@
 \end{align}
-The boundary condition on $\Gamma$ is imposed by requiring that $\eeta$
-satisfies
+The boundary condition on $\Gamma$ is satisfied by requiring that
+$\eeta$ satisfies
 \begin{align}
   \UU(\xx) = -\frac{1}{2}\eeta(\xx) + 
-    S[\ff](\xx) + D[\eeta](\xx), \quad \xx \in \Gamma.
+    S[\ff](\xx) + D[\eeta](\xx), \quad \xx \in \Gamma,
   \label{eqn:DLP_BIE}
 \end{align}
+where the fluid velocity on the solid wall is defined in
+Equation~\eqref{eqn:dirBC}.
 
@@
 is the derivative of the membrane energy with respect to the lipid
-concentration~\cite{soh-tse-li-voi-low2010}. For a single-component vesicle,
+concentration~\cite{soh-tse-li-voi-low2010}.
+
+For a single-component vesicle,
 the tangential traction is $\mathbf{F}_\tt =-\sigma_s$ (the Marangoni stress), and  the streamwise gradient 

### 2023-09-25 vesicle_code/docs/confinedMulti/response.tex
small changes to revisions

@@
 
-\noindent
-{\bf Response:} A response
+\noindent {\bf Response:} The examples with a random initial condition
+    use the uniform distribution with the range $[0,1]$ to define the
+    concentration $u$ at each spatial point. Given the choices for
+    $b_{\min}=0.1$ and $b_{\max}=1$, the resulting mean bending
+    stiffness is $\overline{b(u)} = 0.55$. The text has been adjusted at
+    the start of Section 3.1 and Section 3.2.
 
@@
         the mean velocity as the authors. Please explain your choice.
-      \item page 2, right column ``The parameter $\epsilon \ll 1$ sets the
-        size of the transition region of u, and the parameter a is line
-        tension scaled by the characteristic bending stiffness. All
+      \item page 2, right column ``The parameter $\epsilon \ll 1$ sets
+        the size of the transition region of u, and the parameter a is
+        line tension scaled by the characteristic bending stiffness. All
         simulations use the parameter values $\epsilon = 100$ and $a =

### 2023-09-25 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
small changes to revisions

@@
 single-component (b) floppy single-component, and (c) multicomponent
-vesicle. The lipid distribution of the multicomponent vesicle is
-initially random with a mean value of 0.55. In all plots, the color is
-the dimensionless bending modulus of the multicomponent vesicle that
-remains bounded in $[0.1,1]$ by using the new sigmoid bending modulus in
-Equation~\eqref{eqn:tanhBending}. A single Lagrangian point is included
-to visualize any tank-treading behavior. There are slight differences
-between the three cases, with the most noticeable being that the
-multicomponent vesicle has higher curvature in the floppy region.
-However, in general, there is little difference between these cases,
-principally because these vesicles have a large reduced area.
+vesicle. 
+% New sentence
+\textcolor{blue}{
+The lipid distribution at each point on the multicomponent vesicle is
+chosen randomly from the uniform distribution with the range $[0,1]$. As
+a result of selecting $b_{\min}=0.1$ and $b_{\max}=1$, the mean bending
+stiffness is $\overline{b(u)} = 0.55$.}
+%The lipid distribution of the multicomponent vesicle is
+%initially random with a mean value of 0.55. 
+In all plots, the color is the dimensionless bending modulus of the
+multicomponent vesicle that remains bounded in $[0.1,1]$ by using the
+new sigmoid bending modulus in Equation~\eqref{eqn:tanhBending}. A
+single Lagrangian point is included to visualize any tank-treading
+behavior. There are slight differences between the three cases, with the
+most noticeable being that the multicomponent vesicle has higher
+curvature in the floppy region. However, in general, there is little
+difference between these cases, principally because these vesicles have
+a large reduced area.
 
@@
 front and floppy in the back, and (c) floppy in the front and stiff in
-the back. The vesicle with the random initial lipid distribution quickly
+the back. 
+\textcolor{red}{
+As previously mentioned, the initial random lipid distributions are
+sampled from the uniform distribution with the range $[0,1]$.}
+The vesicle with the random initial lipid distribution quickly
 phase separates into two floppy and two stiff regions. As seen in the

### 2023-09-26 vesicle_code/docs/confinedMulti/response.tex
working on revisions

@@
 %%%%%%%%
-\item In the phase energy, Eq. (5), it is stated that the parameter
+\item In the phase energy, Eq.~(5), it is stated that the parameter
   $\epsilon$ is much smaller than 1 but then it is stated that this
@@
 %%%%%%%%
-\item What motivated the choice of a sigmoid function, Eq. (9), rather
+\item What motivated the choice of a sigmoid function, Eq.~(9), rather
   than a simple min/max operation so that the bending rigidity does not
@@
 %%%%%%%%
-\item Please define $\mathbf{U}$ in Eq. (15). Is this the velocity of
+\item Please define $\mathbf{U}$ in Eq.~(15). Is this the velocity of
   the interface?
@@
 \noindent
-{\bf Response:} A response
+{\bf Response:} Thank you for the suggestion. It is included in the
+    revised manuscript.
 
@@
 \noindent
-{\bf Response:} A response
+    {\bf Response:} We have labelled $w_{\mathrm{top}}$ and
+    $w_{\mathrm{bot}}$ in Figure 1. We have adjusted the text in Section
+    2.4.
 
@@
 \noindent
-{\bf Response:} A response
+{\bf Response:} A comment has been included.
 
@@
 \noindent
-{\bf Response:} A response
+{\bf Response:} In the original submission, we attempted to relate the
+excess pressure to the lubrication layer thickness. However, as pointed
+out by the reviewer, we did not make any reference to the floppy case.
+As a general trend, we expect that larger lubrication layers will result
+in smaller (less negative) lubrication layers. This trend is true across
+the three cases we consider, and the text has been adjusted.
 

### 2023-09-26 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on revisions

@@
 \end{align}
-where $\ff$ is the total membrane force and $\nn$ is the outward unit
-normal of $\gamma$. Parameterizing $\gamma$ as $\xx(s,t)$, where $s$ is
-arclength and $t$ is time, the no-slip boundary condition is
-$\frac{d\xx}{dt} = \uu(\xx)$. Along the solid wall $\Gamma$, we impose a
-Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a
-Hagen–Poiseuille flow at the inlet and outlet
+where $\ff$ is the total membrane force 
+\textcolor{blue}{
+and $\nn$ is the outward unit normal of $\gamma$.} 
+Parameterizing $\gamma$ as $\xx(s,t)$, where $s$ is arclength and $t$ is
+time, the no-slip boundary condition is $\frac{d\xx}{dt} = \uu(\xx)$.
+Along the solid wall $\Gamma$, we impose a Dirichlet boundary condition
+$\uu(\xx) = \UU(\xx)$, where $\UU$ is a Hagen–Poiseuille flow at the
+inlet and outlet
 \begin{align}
@@
 $u$, and the parameter $a$ is line tension scaled by the characteristic
-bending stiffness. All simulations use the parameter values
-$\epsilon=0.04$ and $a=100$. The resulting membrane forces are
+bending stiffness. 
+\textcolor{blue}{
+All simulations use the parameter values $\epsilon=0.04$ and $a=100$.} 
+The resulting membrane forces are
 \begin{align}
@@
 \end{align}
-$\rr = \xx - \yy$, $\rho = |\rr|$, $\nn$ is the outward unit normal,
-$\eeta$ is a currently unknown density function, and $\mathds{I}$ is the
-$2 \times 2$ identity matrix. The membrane tension $\sigma$ acts as a
-Lagrange multiplier so that the inextensibility condition,
-$\nabla_{\gamma} \cdot \uu = 0$, can be satisfied. The corresponding
-pressure is
+$\rr = \xx - \yy$, $\rho = |\rr|$,
+\textcolor{blue}{
+$\nn$ is the outward unit normal, $\eeta$ is a currently unknown density
+function,}
+and $\mathds{I}$ is the $2 \times 2$ identity matrix. 
+\textcolor{blue}{
+The membrane tension $\sigma$ acts as a Lagrange multiplier so that the
+inextensibility condition, $\nabla_{\gamma} \cdot \uu = 0$, can be
+satisfied.}
+The corresponding pressure is
 \begin{align}
@@
 \end{align}
+\textcolor{blue}{
 where the fluid velocity on the solid wall is defined in
-Equation~\eqref{eqn:dirBC}.
+Equation~\eqref{eqn:dirBC}.}
 
@@
   capillary number is $Ca = 0.25$. The vesicles are: (a) stiff
-  single-component; (b) floppy single-component; (c) multicomponent.}
+  single-component; (b) floppy single-component; (c) multicomponent.
+  \textcolor{blue}{The background flow is in the positive $x$ direction
+  denoted by the arrow.}}
 \end{figure*}
@@
 illustrated in Figure~\ref{fig:schematic}, and the height of the gray
-regions denote the lubrication layer thicknesses. In this example, the
-top layer is broken across two different regions.
+regions, 
+\textcolor{blue}{
+$w_{\mathrm{top}}$ and $w_{\mathrm{bot}},$
+}
+denote the lubrication layer thicknesses. In this example, the top layer
+is broken across two different regions.
 
@@
 geometry that slowly contracts to a narrow neck and then quickly widens
-(contracting). 
-%We considered a semipermeable vesicle suspended in these
-%same geometries in our previous work~\cite{qua-gan-you2021}. 
-All the multicomponent examples have floppy-to-stiff ratio $\beta = 10^{-1}$.
-For the single-component case, we consider two bending stiffnesses:
-$b(u) = 1$ and $b(u) = 0.55$. We refer to these cases as a stiff
-single-component vesicle and a floppy single-component vesicle,
-respectively. The smaller bending stiffness represents the average
-bending stiffness of a multicomponent vesicle, when its stiff and floppy
-regions cover the same amount of area. Throughout this section we plot
-the position of the vesicle in terms of the $x$-coordinate of its center
-of mass. For the stenosis geometry in Section~\ref{subsec:Stenosis}, the
-narrow region begins at $x=-15$ and ends at $x=15$. For the contracting
-geometry in Section~\ref{subsec:Contraction}, the geometry begins to
-narrow at $x=4$ and reaches its narrowest point at $x=15$.
+(contracting). All the multicomponent examples have floppy-to-stiff
+ratio $\beta = 10^{-1}$. For the single-component case, we consider two
+bending stiffnesses: $b(u) = 1$ and $b(u) = 0.55$. We refer to these
+cases as a stiff single-component vesicle and a floppy single-component
+vesicle, respectively. The smaller bending stiffness represents the
+average bending stiffness of a multicomponent vesicle, when its stiff
+and floppy regions cover the same amount of area. Throughout this
+section we plot the position of the vesicle in terms of the
+$x$-coordinate of its center of mass. For the stenosis geometry in
+Section~\ref{subsec:Stenosis}, the narrow region begins at $x=-15$ and
+ends at $x=15$. For the contracting geometry in
+Section~\ref{subsec:Contraction}, the geometry begins to narrow at $x=4$
+and reaches its narrowest point at $x=15$.
 
@@
 vesicle. 
-% New sentence
 \textcolor{blue}{
@@
 tension energies remain nearly constant from $x=0$ until the end of the
-stenosis. For the multicomponent vesicle, the phase energy is also
-nearly constant in this region. This implies that there is no coarsening
-of lipid phase parameter in the middle of a stenosis.
+stenosis. 
+\textcolor{blue}{
+In contrast, the bending and tension energies of the floppy
+single-component vesicle evolve throughout the entire channel as the
+vesicle undergoes deformations.}
+For the multicomponent vesicle, the phase energy is also nearly constant
+in this region. This implies that there is no coarsening of lipid phase
+parameter in the middle of a stenosis.
 
@@
 Figure~\ref{fig:lubricationComposite} shows the excess pressure (with
-the axis aligned on the right side of the plot). When the lubrication
-layers are large, most notably for the multicomponent vesicle, less
-pressure is required to force the vesicle through the geometry, and the
-result is a smaller (less negative) excess pressure. In contrast, when
-the lubrication layers are small, most notably for the stiff
-single-component vesicle, more pressure is required to force the vesicle
-through the geometry, and we the result is a larger (more negative)
-excess pressure.
+the axis aligned on the right side of the plot). 
+\textcolor{blue}{
+As a general trend, we expect that if the total lubrication layer
+thickness---namely the sum of the top and bottom lubrication layers---is
+largest, then less pressure is required to maintain the constant flow
+rate, and the result is a smaller (less negative) excess pressure. This
+trend is confirmed in Figure~\ref{fig:lubricationComposite} where the
+size of the lubrication layers, from smallest to largest, are the stiff
+single-component vesicle, the floppy single-component vesicle, and the
+multicomponent vesicle, while the ranking of the excess pressure is
+reversed.}
+%When the lubrication layers are large, most notably for the
+%multicomponent vesicle, less pressure is required to force the vesicle
+%through the geometry, and the result is a smaller (less negative)
+%excess pressure. In contrast, when the lubrication layers are small,
+%most notably for the stiff single-component vesicle, more pressure is
+%required to force the vesicle through the geometry, and we the result
+%is a larger (more negative) excess pressure.
 
@@
 the back. 
-\textcolor{red}{
+\textcolor{blue}{
 As previously mentioned, the initial random lipid distributions are

### 2023-10-02 vesicle_code/docs/confinedMulti/response.tex
working on revisions

@@
 \noindent
-{\bf Response:} A response
+{\bf Response:} Because we are using an integral equation formulation,
+    we are able to achieve high-order accuracy as long as everything is
+    smooth, including the vesicle shape, tension, and the bending
+    stiffness. If we used any kind of $\max$ or $\min$ function, the
+    bending modulus would lose differentiability and this would result
+    in a loss of accuracy. We have expanded the text to explain this
+    point.
+
+    We are unsure what the reviewer means by a ``regular-mixture model".
+    If they mean a linear parameterization between the stiff and floppy
+    phases, this is exactly equation (8).  We originally used this
+    choice, but as argued in the manuscript, because of the strong
+    confinement, the lipid concentration could easily exceed a value of
+    $1$, and this resulted in a unphysical negative bending stiffness
+    which ultimately leads to an instability.  Figure 2 demonstrates
+    this effect. Furthermore, Figure 3 validates the choice of the
+    sigmoid parameterization by comparing the results with a result from
+    the literature that used the linear parameterization in an unbounded
+    linear shear flow.
 
@@
 {\bf Response:} This was our oversight. The parameter values for $a$ and
-$\epsilon$ were unintentionally reversed. This has been fixed.
+$\epsilon$ were unintentionally reversed. This has been fixed. TODO:
+    Need to justify the actual values we used. Take a look at the series
+    of Lowengrub/Shuwang papers.
 
@@
     use the uniform distribution with the range $[0,1]$ to define the
-    concentration $u$ at each spatial point. Given the choices for
+    concentration $u$ at each spatial point. Given the choices of
     $b_{\min}=0.1$ and $b_{\max}=1$, the resulting mean bending
-    stiffness is $\overline{b(u)} = 0.55$. The text has been adjusted at
-    the start of Section 3.1 and Section 3.2.
+    stiffness is $\overline{b(u)} \approx 0.55$. The text has been
+    adjusted at the start of Section 3.1 and Section 3.2.
 
@@
 out by the reviewer, we did not make any reference to the floppy case.
-As a general trend, we expect that larger lubrication layers will result
-in smaller (less negative) lubrication layers. This trend is true across
-the three cases we consider, and the text has been adjusted.
+As a general trend, we find that the sum of the top and bottom
+lubrication layer thicknesses is correlated with the magnitude of the
+excess pressure---larger lubrication layers correspond to smaller (less
+negative) excess pressures. This is because smaller excess pressure is
+required to push the same amount of fluid around the vesicle when the
+lubrication layer thickness is larger.
 
@@
 \noindent
-{\bf Response:} A response
+{\bf Response:} There are 3D BIE codes for vesicles with surface
+    rheology. Leonetti did in 2016 in paper Yuan is sending me. There,
+    of course, is also plenty of accurate methods for single-component
+    vesicles in 3D with strong confinement. This will be even more
+    challenging with strong confinement. Only methods in the literature
+    seem to be David Salac which is a low-order method. Can reference
+    private discussions Zhangli Peng at UIC.
+
+    A response
 
@@
 \noindent
-{\bf Response:} A response
+{\bf Response:} FIRST ROUGH DRAFT: We did observe cases where
+    multicomponent vesicles are stuck. However, keeping all other
+    parameters fixed, the corresponding single-component vesicles were
+    also stuck. We were hoping to find cases where the multicomponent
+    vesicle passed through the contracting geometry while the
+    single-component vesicles did not (similar to our semipermeable
+    work), but no such case was found.  For this reason, we have focused
+    on the effect that multicomponent has on the vesicle shape, tension,
+    layer thickness, tank treading, etc.
 
@@
 \noindent
-{\bf Response:} A response
+{\bf Response:} We can compare Zhangli Peng's results, our simulations
+look similar to what they observe in a 2D projection of their 3D
+results. They call their geometry a `slit' geometry. This work is
+published, so we can reference a particular figure from the paper.
 

### 2023-10-02 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on revisions

@@
 in an instability that is formed by the resulting unphysical negative
-bending stiffness. To rectify this issue, we parameterize the bending
-modulus with the sigmoid function
+bending stiffness. 
+\textcolor{blue}{
+To rectify this issue, we could simply restrict the bending modulus to
+be bounded in $[b_{\min},b_{\max}]$ by letting $b(u) = \max\left( \min
+\left( (1-u) + \beta u,1 \right), \beta \right)$. However, the loss of
+differentiability would result in a loss of accuracy.
+}
+Instead, we parameterize the bending modulus with the sigmoid function
 \begin{align}
@@
 bounded in $(\beta,1)$ even when $u \notin [0,1]$
-(Figure~\ref{fig:concModels}(b)). We compare this new bending model against the linear model for 
-a phase-treading and tank treading vesicle in Section~\ref{sec:validation}.
+(Figure~\ref{fig:concModels}(b)). We compare this new bending model
+against the linear model for a phase-treading and tank treading vesicle
+in Section~\ref{sec:validation}.
 
@@
 \textcolor{blue}{
-$\nn$ is the outward unit normal, $\eeta$ is a currently unknown density
-function,}
+$\nn$ is the outward unit normal, $\eeta$ is a stress density,}
 and $\mathds{I}$ is the $2 \times 2$ identity matrix. 
@@
 \textcolor{blue}{
-where the fluid velocity on the solid wall is defined in
+where the fluid velocity $\UU$ on the solid wall $\Gamma$ is defined in
 Equation~\eqref{eqn:dirBC}.}
@@
   single-component; (b) floppy single-component; (c) multicomponent.
-  \textcolor{blue}{The background flow is in the positive $x$ direction
+  \textcolor{blue}{The imposed flow is in the positive $x$ direction
   denoted by the arrow.}}
@@
 The lipid distribution at each point on the multicomponent vesicle is
-chosen randomly from the uniform distribution with the range $[0,1]$. As
-a result of selecting $b_{\min}=0.1$ and $b_{\max}=1$, the mean bending
-stiffness is $\overline{b(u)} = 0.55$.}
+chosen randomly from the uniform distribution with the range $[0,1]$.
+Since $b_{\min}=0.1$ and $b_{\max}=1$, the mean bending stiffness is
+$\overline{b(u)} \approx 0.55$.}
 %The lipid distribution of the multicomponent vesicle is
@@
 \textcolor{blue}{
-In contrast, the bending and tension energies of the floppy
-single-component vesicle evolve throughout the entire channel as the
-vesicle undergoes deformations.}
+For the floppy case, the bending energy is similar in size as the stiff
+case. Since the floppy bending modulus is ten-times smaller than the
+stiff case, this indicates that the curvature of the floppy vesicle is
+about $\sqrt{10}$-times larger than the stiff case. This additional
+curvature corresponds to larger and more dynamic membrane deformations,
+and a more varying tension energy.}
 For the multicomponent vesicle, the phase energy is also nearly constant
@@
 \textcolor{blue}{
-As a general trend, we expect that if the total lubrication layer
-thickness---namely the sum of the top and bottom lubrication layers---is
-largest, then less pressure is required to maintain the constant flow
-rate, and the result is a smaller (less negative) excess pressure. This
-trend is confirmed in Figure~\ref{fig:lubricationComposite} where the
-size of the lubrication layers, from smallest to largest, are the stiff
-single-component vesicle, the floppy single-component vesicle, and the
-multicomponent vesicle, while the ranking of the excess pressure is
-reversed.}
+As a general trend, we find that the sum of the top and bottom
+lubrication layer thicknesses is correlated with the magnitude of the
+excess pressure---larger lubrication layers correspond to smaller (less
+negative) excess pressures. This is because smaller excess pressure is
+required to push the same amount of fluid around the vesicle when the
+lubrication layer thickness is larger.}
+%As a general trend, we expect that if the total lubrication layer
+%thickness---namely the sum of the top and bottom lubrication layers---is
+%largest, then less pressure is required to maintain the constant flow
+%rate, and the result is a smaller (less negative) excess pressure. This
+%trend is confirmed in Figure~\ref{fig:lubricationComposite} where the
+%size of the lubrication layers, from smallest to largest, are the stiff
+%single-component vesicle, the floppy single-component vesicle, and the
+%multicomponent vesicle, while the ranking of the excess pressure is
+%reversed.}
 %When the lubrication layers are large, most notably for the

### 2023-10-06 vesicle_code/docs/confinedMulti/response.tex
working on revisions

@@
     confinement, the lipid concentration could easily exceed a value of
-    $1$, and this resulted in a unphysical negative bending stiffness
+    $1$, and this resulted in a unphysical negative bending modulus
     which ultimately leads to an instability.  Figure 2 demonstrates
@@
 \noindent
-{\bf Response:} $\eta$ is a density function that is required to satisfy
-    the Dirichlet boundary condition on the solid walls. The text has
-    been adjusted.
+{\bf Response:} $\eta$ is the stress density that is used to satisfy the
+    Dirichlet boundary condition on the solid walls. The text has been
+    adjusted.
 
@@
 
-{\bf Response:} A response
+{\bf Response:} We used $\delta = 0.3$. For the stenosis geometry, this
+corresponds to a lubrication layer thickness of size a little less than
+one micron.
 
@@
 
-{\bf Response:} A response
+{\bf Response:} We have included dimensionless values for the stenosis
+geometry, contracting geometry, and vesicle length. To convert to
+dimensioned units, the length scale 3.17 microns can be used.
 
@@
     use the uniform distribution with the range $[0,1]$ to define the
-    concentration $u$ at each spatial point. Given the choices of
+    lipid concentration $u$ at each spatial point. Given the choices of
     $b_{\min}=0.1$ and $b_{\max}=1$, the resulting mean bending
@@
 \noindent
-{\bf Response:} A comment has been included.
+{\bf Response:} We have included a discussion of the energy behavior of
+the floppy vesicle and compared it with the stiff case.
 
@@
 required to push the same amount of fluid around the vesicle when the
-lubrication layer thickness is larger.
+lubrication layer thickness is larger. The text has been adjusted.
 

### 2023-10-06 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on revisions

@@
 \textcolor{blue}{
-where the fluid velocity $\UU$ on the solid wall $\Gamma$ is defined in
-Equation~\eqref{eqn:dirBC}.}
+where the fluid velocity $\UU$ on the solid wall $\Gamma$ is defined
+in~\eqref{eqn:dirBC}.}
 
@@
 We find all local minimums of $d(\xx,\Gamma_\mathrm{top})$, with the
-condition that $d(\xx,\Gamma_\mathrm{top}) < \delta$, where $\delta$ is
-a parameter. If no such local minimums exist, then the vesicle is too
+condition that $d(\xx,\Gamma_\mathrm{top}) < \delta$, 
+\textcolor{blue}{
+where we use the parameter value $\delta = 0.3$.
+}
+%where $\delta$ is a parameter.
+If no such local minimums exist, then the vesicle is too
 far from $\Gamma_\mathrm{top}$ to define a lubrication layer. If there
@@
 We consider both a single-component and a multicomponent vesicle
+\textcolor{blue}{
+with a fixed dimensionless length of $L = 7.4$
+}
 suspended in two geometries: a closely-fitting geometry (stenosis) and a
@@
 We start by considering a vesicle with reduced area $\alpha = 0.6$
-passing through stenosis with a capillary number $Ca = 0.25$. With the
-current setup and $Ca=0.25$, an elliptical vesicle with reduced area
-greater than $\alpha = 0.8$ cannot fit through the closely-fitting
+passing through stenosis with a capillary number $Ca = 0.25$. 
+\textcolor{blue}{
+The dimensionless width of the stenosis starts at $6.8$ and narrows to
+$1.4$. 
+}
+With the current setup and $Ca=0.25$, an elliptical vesicle with reduced
+area greater than $\alpha = 0.8$ cannot fit through the closely-fitting
 geometry. Figure~\ref{fig:RA6} shows six time steps of a (a) stiff
@@
 For the floppy case, the bending energy is similar in size as the stiff
-case. Since the floppy bending modulus is ten-times smaller than the
+case. Since the floppy bending modulus is about two-times smaller than the
 stiff case, this indicates that the curvature of the floppy vesicle is
-about $\sqrt{10}$-times larger than the stiff case. This additional
+about $\sqrt{2}$-times larger than the stiff case. This additional
 curvature corresponds to larger and more dynamic membrane deformations,
@@
 In this section, we consider a vesicle passing through a channel that
-slowly contracts to a  2~$\mu$m wide neck, and then
-immediately opens up to a channel that is ten times larger. We
-first consider the effect of the initial lipid concentration when the
+slowly contracts 
+\textcolor{blue}{
+from a dimensionless width of $6.5$ to $0.63$,
+}
+and then immediately opens back up to a channel 
+\textcolor{blue}{
+with width $6.5$. In dimensioned units, the width of the neck is
+$2~\mu$m.
+}
+We first consider the effect of the initial lipid concentration when the
 floppy and stiff regions each make up half of the vesicle membrane. In

### 2023-10-06 vesicle_code/docs/confinedMulti/response.tex
worked on revisions

@@
 \usepackage{fullpage}
+\usepackage{graphicx}
 \usepackage{url}
+
+\newcommand{\subfigimg}[3][,]{%
+  \setbox1=\hbox{\includegraphics[#1]{#3}}% Store image in box
+  \leavevmode\rlap{\usebox1}% Print image
+  \rlap{\hspace*{0pt}\raisebox{\dimexpr\ht1-0\baselineskip}{\bf
+  \normalsize #2}}% Print label
+  \phantom{\usebox1}% Insert appropriate spacing
+}
 
@@
 \noindent
-{\bf Response:} A response
+    {\bf Response:} We calculated the tangential velocity of all $N =
+    1024$ Lagrangian points for each of the three cases. Plotting all
+    1024 lines in the manuscript we be uninformative. To prove this is
+    the case, a plot of 32 of the tangential velocities is in
+    Figure~\ref{fig:tangVel} of this document. Instead, in the document,
+    we report the average tangential velocity in the region $x \in
+    [4,10]$, and the report the spread of all tangential velocities from
+    this mean value. If this spread is less than 15\%, we would
+    characterize this as a tank-treading vesicle. There spread is 1.2\%
+    for the stiff single-component vesicle, 12\% for the multicomponent
+    case, and 313\% for the floppy single-component case. Therefore, the
+    floppy single-component vesicle is not tank-treading, while the
+    other two cases are tank-treading. We have made this clear in the
+    text.
+    {\bf TODO: Change color of Fig 7 lines or state why we don't do
+    this.}
+
+\begin{figure}[ht]
+  \centering
+  \subfigimg[width=0.3\textwidth]{(a)}{figures/SC_treading_velocity_review.pdf}
+  \subfigimg[width=0.3\textwidth]{(b)}{figures/SCp55_treading_velocity_review.pdf}
+  \subfigimg[width=0.3\textwidth]{(c)}{figures/MCp5_treading_velocity_review.pdf}
+  \caption{\label{fig:tangVel} The tangential velocity of 32 points of
+  the (a) stiff single-component vesicle, (b) floppy single-component
+  vesicle, (c) multicomponent vesicle.}
+\end{figure}
 

### 2023-10-06 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
worked on revisions

@@
 
-The vesicle and solid walls are discretized at a set of collocation
-points. The single-layer potential is approximated using quadrature for
+The vesicle and solid walls are discretized at a set of 
+\textcolor{blue}{
+$N$ and $N_{\mathrm{wall}}$
+}
+collocation points,
+\textcolor{blue}{
+respectively.}
+The single-layer potential is approximated using quadrature for
 weakly-singular integrands, while the double-layer potential is
@@
 Figure~\ref{fig:lubricationComposite}. The bottom of
-Figure~\ref{fig:lubricationComposite} shows the tank-treading velocities
-of four Lagrangian points. The inset shows the vesicle configuration in
-the closely-fitting part of the channel, the black dashed line is the
-center line of the channel, the marks are the four Lagrangian points,
-and the rounded arrow denotes the direction of rotation. The stiff
-single-component and multicomponent vesicles are clearly tank treading.
-The direction and speed of the tank-treading depends on how much of
-the vesicle membrane is exposed to positive shear (below the center
-line) versus how much is exposed to negative shear (above the center
-line) \cite{kao-bir-mis2009}. The majority of the membrane of the stiff single-component and
-multicomponent vesicles are below the center line, and this results in a
-clockwise tank-treading behavior. In contrast, the majority of the
-membrane of the floppy single-component vesicle is above the center
-line, and the result is counterclockwise tank-treading. In addition, the
-tank-treading velocity can be correlated to the percentage of its
-membrane that is below the center line. We note, however, that the
-floppy single-component vesicle is still undergoing deformations, so the
-tangential velocities have not converged to a fixed value.
+Figure~\ref{fig:lubricationComposite} shows the 
+\textcolor{blue}{
+tangential
+}
+%tank-treading
+velocities of four Lagrangian points. The inset shows the vesicle
+configuration in the closely-fitting part of the channel, the black
+dashed line is the center line of the channel, the marks are the four
+Lagrangian points, and the rounded arrow denotes the direction of
+rotation. 
+\textcolor{blue}
+{
+To determine if a vesicle is tank-treading, we first calculate the
+average, maximum, and minimum tangential velocities over all $N$
+Lagrangian points when the vesicle's center of mass is in the interval
+$[4,10]$. If the maximum and minimum tangential velocities are within
+15\% of the average tangential velocity, we characterize the vesicle as
+tank-treading. The average tangential velocities are $-1.00 \times
+10^{-1}$ for the stiff single-component vesicle, $3.31 \times 10^{-2}$
+for the floppy single-component vesicle, and $-8.48 \times 10^{-1}$ for
+the multicomponent vesicle. The spread of the maximum and minimum
+velocities from these average tangential velocities are $1.2\%$ for the
+stiff single-component vesicle, $12\%$ for the multicomponent vesicle,
+and over $300\%$ for the floppy single-component vesicle. Therefore, we
+classify the stiff single-component and multicomponent vesicles as tank
+treading, while the floppy single-component is not tank treading.
+}
+%The stiff single-component and multicomponent vesicles are
+%clearly tank treading.
+The direction and speed of the tank-treading depends on how much of the
+vesicle membrane is exposed to positive shear (below the center line)
+versus how much is exposed to negative shear (above the center
+line)~\cite{kao-bir-mis2009}. The majority of the membrane of the stiff
+single-component and multicomponent vesicles are below the center line,
+and this results in a clockwise tank-treading behavior. In contrast, the
+majority of the membrane of the floppy single-component vesicle is above
+the center line, and the result is counterclockwise 
+\textcolor{blue}{
+rotation, but, again, the vesicle dynamics are not tank-treading as the
+vesicle is undergoing large normal deformations.
+}
+%tank-treading. 
+\textcolor{blue}{
+Finally, the stiff single-component vesicle tank treads faster than the
+multicomponent cases since more of its membrane is located below the
+center line.
+}
+%In addition, the tank-treading velocity can be correlated to the
+%percentage of its membrane that is below the center line. 
+%We note, however, that the floppy single-component vesicle is still
+%undergoing deformations, so the tangential velocities have not converged
+%to a fixed value.
 

### 2023-10-09 vesicle_code/docs/confinedMulti/response.tex
working on revisions

@@
 corresponds to a lubrication layer thickness of size a little less than
-one micron.
+one micron. This value is now mentioned in Section 2.4.
 
@@
 
-{\bf Response:} We have included dimensionless values for the stenosis
-geometry, contracting geometry, and vesicle length. To convert to
-dimensioned units, the length scale 3.17 microns can be used.
+{\bf Response:} We have included dimensions for the stenosis geometry,
+contracting geometry, and vesicle length, but with units. Our hope is
+that an experimentalist would be able to easily extract these values
+
+To convert to dimensionless units, the length scale 3.17 microns can be
+used.
 
@@
     we report the average tangential velocity in the region $x \in
-    [4,10]$, and the report the spread of all tangential velocities from
+    [4,10]$, and report the spread of all tangential velocities from
     this mean value. If this spread is less than 15\%, we would
@@
 \noindent
-{\bf Response:} A response
+{\bf Response:} Thank you for correcting this error. We have added the
+word `flow' to the manuscript.
 

### 2023-10-09 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on revisions

@@
 $\gamma$ suspended in a confined geometry $\Omega \subset \RR ^2$ with
-boundary $\Gamma$ (Figure~\ref{fig:schematic}). The fluid is assumed to
-have zero Reynolds number and is therefore governed by the
+boundary $\Gamma$ (Figure~\ref{fig:schematic}). The fluid 
+\textcolor{blue}{
+flow
+}
+is assumed to have zero Reynolds number and is therefore governed by the
 incompressible Stokes equations
@@
 \textcolor{blue}{
-To rectify this issue, we could simply restrict the bending modulus to
-be bounded in $[b_{\min},b_{\max}]$ by letting $b(u) = \max\left( \min
-\left( (1-u) + \beta u,1 \right), \beta \right)$. However, the loss of
-differentiability would result in a loss of accuracy.
+To rectify this issue, we could restrict the bending modulus to be
+bounded in $[\beta,1]$ by setting $b(u) = \max\left( \min \left( (1-u) +
+\beta u,1 \right), \beta \right)$, which is non-differentiable. However,
+this loss of differentiability would result in a loss of accuracy of the
+overall method.
 }
@@
 \textcolor{blue}{
-where we use the parameter value $\delta = 0.3$.
+  where we use the parameter value $\delta = 0.3$ (a little less than
+  1~$\mu$m).
 }
@@
 \textcolor{blue}{
-with a fixed dimensionless length of $L = 7.4$
+with an effective radius of about $4~\mu$m
 }
@@
 \textcolor{blue}{
-The dimensionless width of the stenosis starts at $6.8$ and narrows to
-$1.4$. 
+The width of the stenosis starts at $21.6~\mu$m and narrows to
+$4.4~\mu$m. 
 }

### 2023-10-15 vesicle_code/docs/confinedMulti/response.tex
working on revisions

@@
 \noindent
-{\bf Response:} This was our oversight. The parameter values for $a$ and
-$\epsilon$ were unintentionally reversed. This has been fixed.
+{\bf Response:} This was a typo. We checked our code, and now we
+report the correct value in the revision which is $\epsilon = 0.04$.
 
@@
 
-{\bf Response:} We used $\delta = 0.3$. For the stenosis geometry, this
-corresponds to a lubrication layer thickness of size a little less than
-one micron. This value is now mentioned in Section 2.4.
+{\bf Response:} We used the dimensionless value $\delta = 0.3$. For the
+stenosis geometry, this corresponds to a lubrication layer thickness of
+a little more than one micron. This value is now mentioned in Section
+2.4.
 
@@
 
-{\bf Response:} We have included dimensions for the stenosis geometry,
-contracting geometry, and vesicle length, but with units. Our hope is
-that an experimentalist would be able to easily extract these values
-
-To convert to dimensionless units, the length scale 3.17 microns can be
-used.
+{\bf Response:} We now report the dimensionless width of both
+geometries.
 
@@
 \noindent
-{\bf Response:} This was our oversight. The parameter values for $a$ and
-$\epsilon$ were unintentionally reversed. This has been fixed. TODO:
-    Need to justify the actual values we used. Take a look at the series
-    of Lowengrub/Shuwang papers.
+{\bf Response:} This was a typo. We checked our code, and now we
+report the correct value in the revision which is $\epsilon = 0.04$.
+This value corresponds to a transition region of size $10^{-1}$ microns
+between stiff and floppy regions. Comparable values are used in the
+literature, and we cite three of these papers.
 
@@
     1024$ Lagrangian points for each of the three cases. Plotting all
-    1024 lines in the manuscript we be uninformative. To prove this is
+    1024 lines in the manuscript would be uninformative. To prove this is
     the case, a plot of 32 of the tangential velocities is in
@@
     this mean value. If this spread is less than 15\%, we would
-    characterize this as a tank-treading vesicle. There spread is 1.2\%
+    characterize this as a tank-treading vesicle. Their spread is 1.2\%
     for the stiff single-component vesicle, 12\% for the multicomponent
@@
 \noindent
-{\bf Response:}: We thank the referee for their assessment and suggested
+{\bf Response:} We thank the referee for their assessment and suggested
 changes.
@@
 \noindent
-{\bf Response:} A response
+{\bf Response:} Thank you for the comment. This question is addressed in
+detail in our response to the reviewers second comment.
 
@@
 \noindent
-{\bf Response:} There are 3D BIE codes for vesicles with surface
-    rheology. Leonetti did in 2016 in paper Yuan is sending me. There,
-    of course, is also plenty of accurate methods for single-component
-    vesicles in 3D with strong confinement. This will be even more
-    challenging with strong confinement. Only methods in the literature
-    seem to be David Salac which is a low-order method. Can reference
-    private discussions Zhangli Peng at UIC.
+{\bf Response:} There is published work that has investigated elements
+of our work in  3D. This includes the papers from the reviewers first
+comment that consider vesicles in strong confinement, but these works
+assume axisymmetry and neither consider multicomponent vesicles. Two
+3D works that relax the axisymmetric assumption and simulate vesicles in
+strong confinement are also cited in the original submission
+(https://doi.org/10.1063/1.5081057 and
+https://doi.org/10.1103/PhysRevFluids.5.013603). Red blood cells
+undergoing strong confinement has also been considered using other
+numerical methods including a spring model coupled to smoothed particle
+hydrodynamics (http://dx.doi.org/10.1016/j.taml.2015.11.006 and
+http://dx.doi.org/10.1063/1.4817959). These papers are cited in the
+revised manuscript.
 
-    A response
+There is much less work on 3D multicomponent vesicles. Phase field
+models are used by Wang and Du
+(https://doi.org/10.1007/s00285-007-0118-2) and a level set method is
+used by Gera and Salac
+(https://doi.org/10.1016/j.compfluid.2018.04.003). The challenge with
+both these approaches is that they have to discretize the fluid volume,
+and this limits how small $\epsilon$ can be, and therefore restricts
+the sharpness of the transition between the floppy and stiff
+regions. In both these works, a value of $\epsilon$ that is at least
+ten-times larger than the more realistic value used in our work. To use
+a comparable value to ours, they would have to increase the overall
+spatial resolution by $10^3$. These codes are parallelized and highly
+optimized, but they still take on the order of a day to complete one
+unconfined simulation at the coarser resolution. Therefore, with
+confinement, and the additional resolution to resolve the more physical
+value of $\epsilon$, a single simulation would require much more
+computational resources for generating an appropriately large dataset
+to analyze.
+
+Extending our 2D spectral code to 3D is challenging because resolving
+the sharp interface between lipid domains requires special treatment
+such as adaptive methods. Recently, finite element methods with adaptive
+mesh generation have been used to solve surface PDEs, but to our
+knowledge, it has not been extended to fourth-order PDEs or evolving
+surfaces (as in our case). For example, see the following thesis that
+considers reaction-diffusion systems on surfaces
+(https://nrs.harvard.edu/URN-3:HUL.INSTREPOS:37368862), and the preprint
+written by the same author (https://arxiv.org/pdf/2210.00022.pdf).
+Extending this work to incorporate a high-order phase field model and
+deformable interface is currently unavailable, to the best of our
+knowledge.
+
+%There are 3D BIE codes for vesicles with surface rheology. Leonetti did
+%in 2016 in paper Yuan is sending me. There, of course, is also plenty of
+%accurate methods for single-component vesicles in 3D with strong
+%confinement. This will be even more challenging with strong confinement.
+%Only methods in the literature seem to be David Salac which is a
+%low-order method. Can reference private discussions Zhangli Peng at UIC.
+%
+%A response
 
@@
     \begin{itemize}
-      \item page 2 : there is a difference in literature of the
+      \item page 2: there is a difference in literature of the
         capillary number. Some authors use the flow curvature, others
@@
 \noindent
-{\bf Response:} This was our oversight. The parameter values for $a$ and
-$\epsilon$ were unintentionally reversed. This has been fixed.
+{\bf Response:}  We use the mean velocity to define the capillary number
+so that we can compare our results with work that we cite including
+[10,11,18] (as numbered in our original submission).
+
+For the comment regarding the values of $a$ and $\epsilon$, we had a
+typo. The parameter values for $a$ and $\epsilon$ were unintentionally
+reversed. This has been fixed.
 
@@
 \noindent
-{\bf Response:} FIRST ROUGH DRAFT: We did observe cases where
-    multicomponent vesicles are stuck. However, keeping all other
-    parameters fixed, the corresponding single-component vesicles were
-    also stuck. We were hoping to find cases where the multicomponent
-    vesicle passed through the contracting geometry while the
-    single-component vesicles did not (similar to our semipermeable
-    work), but no such case was found.  For this reason, we have focused
-    on the effect that multicomponent has on the vesicle shape, tension,
-    layer thickness, tank treading, etc.
+{\bf Response:} We initially explored cases where the single-component
+vesicle became stuck, expecting that the multicomponent vesicle may pass
+through the same geometry.  However, we did not find any such cases.
+However, we did observe other behaviors that differ between the two
+cases, including the vesicle shape, tank treading velocity, lubrication
+layer, and these comparisons are the focus of our manuscript.
+
+%
+%FIRST ROUGH DRAFT: We did observe cases where
+%    multicomponent vesicles are stuck. However, keeping all other
+%    parameters fixed, the corresponding single-component vesicles were
+%    also stuck. We were hoping to find cases where the multicomponent
+%    vesicle passed through the contracting geometry while the
+%    single-component vesicles did not (similar to our semipermeable
+%    work), but no such case was found.  For this reason, we have focused
+%    on the effect that multicomponent has on the vesicle shape, tension,
+%    layer thickness, tank treading, etc.
 

### 2023-10-15 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on revisions

@@
 qua-gan-you2021, abb-far-nai-ezz-ben-mis2022,
-wan-ii-sug-nod-jin-liu-che-gon2023} showed more exotic vesicle
-hydrodynamics such as snaking and swirling behaviors in croissant and
-slipper shapes.
+wan-ii-sug-nod-jin-liu-che-gon2023, bar-sha2018b} showed more exotic
+vesicle hydrodynamics such as snaking and swirling behaviors in
+croissant and slipper shapes.
 
@@
 difference~\cite{Freund2013_PoF, LuPeng2019_PoF, che-lyu-jae-leo2020,
-gur-pak-tay-siv-sac2023}. Membrane permeability has been incorporated to
-examine the single-component vesicle hydrodynamics. In the absence of an
-osmotic gradient, the semipermeable vesicle is affected by water
-influx/efflux over a sufficiently long time or under a strong
-confinement~\cite{qua-gan-you2021}. Numerical simulations illustrate
-that a vesicle with moderate membrane permeability can go through a
-strong confinement much more easily, and can restore its water content
-within a very short time after its passage through the strong
+gur-pak-tay-siv-sac2023, wu2013simulation}. Membrane permeability has
+been incorporated to examine the single-component vesicle hydrodynamics.
+In the absence of an osmotic gradient, the semipermeable vesicle is
+affected by water influx/efflux over a sufficiently long time or under a
+strong confinement~\cite{qua-gan-you2021}. Numerical simulations
+illustrate that a vesicle with moderate membrane permeability can go
+through a strong confinement much more easily, and can restore its water
+content within a very short time after its passage through the strong
 confinement. These results imply that the membrane permeability may be
@@
 We nondimensionalize the governing equations with a characteristic
-length scale $R_0 = 10^{-6}$~m, a maximum bending stiffness $b_{\max} =
-10^{-19}$~J, and fluid viscosity $\mu = 5 \times 10^{-2}$~kg/ms. The
-resulting bending relaxation time scale is $\mu R_0^3/b_{\max} = 0.5$~s,
-the velocity scale is $b_{\max}/\mu R_0^2=2$~$\mu$m/s, the pressure
-scale is $b_{\max}/R_0^3 = 10^{-1}$~Pa, and the tension scale is
-$b_{\max}/R_0^2 = 10^{-7}$~N/m. The dimensionless parameters regarding
-the vesicle properties are the reduced area $\alpha = 4\pi A/L^2$, where
-$A$ and $L$ are the vesicle's area and length, respectively, and the
+length scale $R_0 = 4 \times 10^{-6}$~m, a maximum bending stiffness
+$b_{\max} = 2 \times 10^{-18}$~J, and fluid viscosity $\mu = 5 \times
+10^{-2}$~kg/ms. The resulting bending relaxation time scale is $\mu
+R_0^3/b_{\max} = 1.6$~s, the velocity scale is
+$b_{\max}/\mu R_0^2=2.5$~$\mu$m/s, the pressure scale is $b_{\max}/R_0^3
+= 3.1 \times 10^{-2}$~Pa, and the tension scale is $b_{\max}/R_0^2 = 1.3
+\times 10^{-7}$~N/m. The dimensionless parameters regarding the vesicle
+properties are the reduced area $\alpha = 4\pi A/L^2$, where $A$ and $L$
+are the vesicle's area and length, respectively, and the
 floppy-to-stiffness ratio $\beta = b_{\min}/b_{\max}$. Since we consider
 flows in channels, we also define a maximum imposed velocity, $U$, which
-sets the capillary number $Ca = U R_{0}^{2} \mu/b_{\max}$, and $W/R_0$
-is the dimensionless width of the channel which varies in both examples
-we consider. Finally, the Peclet number of the lipid dynamics is taken
-to be $Pe = 1$ which results in a diffusion time scale of $2 \times
+sets the capillary number $Ca = U R_0^{2} \mu/b_{\max}$, and $W/R_0$ is
+the dimensionless width of the channel which varies in both examples we
+consider. Finally, the Peclet number of the lipid dynamics is taken to
+be $Pe = 1$ which results in a diffusion time scale of $6.4 \times
 10^{-4}$~s. Therefore, phase separation occurs at a rate three orders of
@@
 dynamics. From this point onwards, all equations are dimensionless.
+
+%We nondimensionalize the governing equations with a characteristic
+%length scale $\ell = 10^{-6}$~m, a maximum bending stiffness $b_{\max} =
+%10^{-19}$~J, and fluid viscosity $\mu = 5 \times 10^{-2}$~kg/ms. The
+%resulting bending relaxation time scale is $\mu \ell^3/b_{\max} = 0.5$~s,
+%the velocity scale is $b_{\max}/\mu \ell^2=2$~$\mu$m/s, the pressure
+%scale is $b_{\max}/\ell^3 = 10^{-1}$~Pa, and the tension scale is
+%$b_{\max}/\ell^2 = 10^{-7}$~N/m. The dimensionless parameters regarding
+%the vesicle properties are the reduced area $\alpha = 4\pi A/L^2$, where
+%$A$ and $L$ are the vesicle's area and length, respectively, and the
+%floppy-to-stiffness ratio $\beta = b_{\min}/b_{\max}$. Since we consider
+%flows in channels, we also define a maximum imposed velocity, $U$, which
+%sets the capillary number $Ca = U \ell_0^{2} \mu/b_{\max}$, and $W/\ell$
+%is the dimensionless width of the channel which varies in both examples
+%we consider. Finally, the Peclet number of the lipid dynamics is taken
+%to be $Pe = 1$ which results in a diffusion time scale of $2 \times
+%10^{-4}$~s. Therefore, phase separation occurs at a rate three orders of
+%magnitude faster than vesicle relaxation. The effect of the Peclet
+%number has been examined~\cite{liu-mar-li-vee-low2017,
+%soh-tse-li-voi-low2010}, and it has no qualitative effect on the vesicle
+%dynamics. From this point onwards, all equations are dimensionless.
 
@@
 \textcolor{blue}{
-All simulations use the parameter values $\epsilon=0.04$ and $a=100$.} 
+All simulations use the parameter values $\epsilon=0.04$ and $a=100$.
+This corresponds to a size of $10^{-1}~\mu$m for the transition between
+the floppy and stiff regions, which is similar to the values considered
+by others~\cite{soh-tse-li-voi-low2010, liu-mar-li-vee-low2017,
+Gera2018_SoftMatter}.
+} 
 The resulting membrane forces are
@@
   geometry. The vesicle's reduced area is $\alpha = 0.6$ and the
-  capillary number is $Ca = 0.25$. The vesicles are: (a) stiff
+  capillary number is $Ca = 0.2$. The vesicles are: (a) stiff
   single-component; (b) floppy single-component; (c) multicomponent.
@@
 \textcolor{blue}{
-  where we use the parameter value $\delta = 0.3$ (a little less than
-  1~$\mu$m).
+  where we use the parameter value $\delta = 0.3$ or $1.2~\mu$m.
 }
@@
 The region that defines the top and bottom lubrication layers is
-illustrated in Figure~\ref{fig:schematic}, and the height of the gray
+illustrated in Figure~\ref{fig:schematic}, and the heights of the gray
 regions, 
@@
 \textcolor{blue}{
-with an effective radius of about $4~\mu$m
+  with an effective radius of $R_{0} = 4~\mu$m
 }
@@
 We start by considering a vesicle with reduced area $\alpha = 0.6$
-passing through stenosis with a capillary number $Ca = 0.25$. 
-\textcolor{blue}{
-The width of the stenosis starts at $21.6~\mu$m and narrows to
-$4.4~\mu$m. 
-}
-With the current setup and $Ca=0.25$, an elliptical vesicle with reduced
+passing through stenosis with a capillary number $Ca = 0.2$. 
+\textcolor{blue}{
+The width of the stenosis starts at $6.8$
+%$21.6~\mu$m 
+and narrows to 1.4.
+%$4.4~\mu$m. 
+}
+With the current setup and $Ca = 0.2$, an elliptical vesicle with reduced
 area greater than $\alpha = 0.8$ cannot fit through the closely-fitting
@@
   geometry. The vesicle's reduced area is $\alpha = 0.4$ and the
-  capillary number is $Ca = 0.25$. The vesicles are: (a) stiff
+  capillary number is $Ca = 0.2$. The vesicles are: (a) stiff
   single-component; (b) floppy single-component; (c) multicomponent.
@@
 \textcolor{blue}{
-from a dimensionless width of $6.5$ to $0.63$,
+from a width of $6.5$ to $0.63$,
 }
@@
   vesicle's reduced area is $\alpha = 0.5$ and the capillary number is
-  $Ca = 0.25$. The lipid distribution is initialized to be (a) random,
+  $Ca = 0.2$. The lipid distribution is initialized to be (a) random,
   (b) phase separated with the stiff region leading; (b) random; (c)
@@
 front and the floppy region to be in the back. In each simulation, the
-capillary number is $Ca = 0.25$. Figure~\ref{fig:RA5} shows the vesicle
+capillary number is $Ca = 0.2$. Figure~\ref{fig:RA5} shows the vesicle
 shapes at the same six time steps when the percentage of the floppy
@@
   contracting geometry. The vesicle's reduced area is $\alpha = 0.5$ and
-  the Capillary number is $Ca = 0.25$. (a) A stiff single-component
+  the Capillary number is $Ca = 0.2$. (a) A stiff single-component
   vesicle. The percentage of the multicomponent vesicle that is floppy
@@
 of a multicomponent vesicle under strong confinement. The vesicle is an
-simplified model for a red blood cell, which has multiple lipid
-domains in its membrane and often has to squeeze through a small space.
-We refined the phase-field formulation in~\citet{liu-mar-li-vee-low2017}
+simplified model for a red blood cell, which has multiple lipid domains
+in its membrane and often has to squeeze through a small space.  We
+refined the phase-field formulation in~\citet{liu-mar-li-vee-low2017}
 with a new bending model that uses a sigmoid function for the bending
@@
 distribution of lipid domains with a fixed floppy-to-stiff ratio
-$\beta=0.1$, a fixed Capillary number $Ca=0.25$, and a fixed Peclet
+$\beta=0.1$, a fixed Capillary number $Ca = 0.2$, and a fixed Peclet
 number of the lipid dynamics $Pe=1$.
 
-In \S~\ref{subsec:Stenosis} the confinement ratio (defined as $2R_0/W$)
+In \S~\ref{subsec:Stenosis} the confinement ratio (defined as $2\ell/W$)
 in the stenosis is $1.67$, and in \S~\ref{subsec:Contraction} the
@@
 with a smaller tension (in magnitude) in the front and a larger tension
-(in magnitude) in the back.
-This resembles the behavior of a red blood cell as it traverses a narrow slit~\cite{LuPeng2019_PoF}.
-During this process, the membrane tension is primarily negative, resulting in compression that is more pronounced at the rear of the cell than at the front.
+(in magnitude) in the back. This resembles the behavior of a red blood
+cell as it traverses a narrow slit~\cite{LuPeng2019_PoF,
+wu2015critical}. During this process, the membrane tension is primarily
+negative, resulting in compression that is more pronounced at the rear
+of the cell than at the front.
 %This is similar to a red blood cell going through a

### 2023-10-18 vesicle_code/docs/confinedMulti/response.tex
working on revisions with Yuan

@@
 \noindent
-{\bf Response:} Thank you for the comment. This question is addressed in
-detail in our response to the reviewers second comment.
+{\bf Response:} Thank you for the comment. It is addressed in detail in
+our response to the reviewer's second comment.
 
@@
 value of $\epsilon$, a single simulation would require much more
-computational resources for generating an appropriately large dataset
-to analyze.
+computational resources for generating an appropriately large dataset to
+analyze. For example, if a simulation for an unconfined case requires
+one day of CPU time on 12 cores, then, even without confinement, the
+additional resolution required to resolve the smaller value of
+$\epsilon$ would require 12,000 cores to complete the simulation in the
+same wall clock time, and this is assuming the code scales perfectly.
+This increase in resources would be compounded further once strong
+confinement is introduced.
 
@@
 \noindent
-{\bf Response:}  We use the mean velocity to define the capillary number
-so that we can compare our results with work that we cite including
-[10,11,18] (as numbered in our original submission).
+{\bf Response:} We use the maximum imposed velocity to define the
+capillary number so that we can compare our results with work that we
+cite including [10,11,18] (as numbered in our original submission). We
+have also added a note that the capillary number is larger for a vesicle
+inside the stenosis.
 
-For the comment regarding the values of $a$ and $\epsilon$, we had a
-typo. The parameter values for $a$ and $\epsilon$ were unintentionally
-reversed. This has been fixed.
+For the comment regarding the value of $\epsilon$, we had a
+typo. The parameter value for $\epsilon$ is actually 0.04, and this has
+been fixed.
 
@@
 vesicle became stuck, expecting that the multicomponent vesicle may pass
-through the same geometry.  However, we did not find any such cases.
+through the same geometry. We did not find any such cases.
 However, we did observe other behaviors that differ between the two
 cases, including the vesicle shape, tank treading velocity, lubrication
-layer, and these comparisons are the focus of our manuscript.
+layer, and these comparisons are the focus of our manuscript. We defer
+our response to the phase diagram point until comment number 6.
 
@@
 \noindent
-{\bf Response:} A response
+{\bf Response:} A phase diagram is included in Figure~\ref{fig:Phase}.
+We do not observe any dependence on the capillary number. We had a
+discussion with an experimental colleague who works on an experiment
+with a red blood cell passing through stenosis, where only a single RBC
+can pass through one at a time. His experiments have shown that the
+shape of the RBC inside this confined stenosis is independent over a
+range of capillary numbers, as we report in Figure~\ref{fig:Phase}. For
+this reason, we do not include phase diagrams in our manuscript. We have
+started examining the dependence of these dynamics on other
+dimensionless parameters including the confinement ratio and the
+floppy-to-stiff ratio. This will be a different focus and would distract
+from the focus of this work.
+\begin{figure}
+\centering
+  \includegraphics[width=0.5\textwidth]{phaseDiagram.jpg}
+  \caption{\label{fig:Phase} A phase diagram of a single vesicle in an unconfined
+  nonlinear shear flow. The capillary number has no effect on the steady
+  state shape of the vesicle.}
+\end{figure}
 
@@
 \noindent
-{\bf Response:} A response
+{\bf Response:} Thank you for the comment.
 \end{enumerate}

### 2023-10-18 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on revisions with Yuan

@@
 the dimensionless width of the channel which varies in both examples we
-consider. Finally, the Peclet number of the lipid dynamics is taken to
+consider. 
+\textcolor{blue}{
+Note that the maximum velocity inside the stenosis is almost five times
+larger than the maximum imposed velocity. As a result, the capillary
+number inside the stenosis is also five times larger.
+}
+Finally, the Peclet number of the lipid dynamics is taken to
 be $Pe = 1$ which results in a diffusion time scale of $6.4 \times

### 2023-10-18 vesicle_code/docs/confinedMulti/response.tex
yny

@@
 \noindent
-{\bf Response:} It is the outward pointing unit normal. The text has
-    been adjusted.
+{\bf Response:} It is the outward pointing unit normal.  We have adjusted the text to clarify this.
 
@@
 \noindent
-{\bf Response:} The tension $\sigma$ acts as a Lagrange multiplier so
-    that the inextensibility condition can be satisfied. The text has
-    been adjusted.
+{\bf Response:} The surface incompressibility is enforced via the tension $\sigma$ (Eq.~(6)) in the original manuscript), 
+which is a Lagrange multiplier so that the inextensibility condition can be satisfied. We adjusted the text in the revision to make this clearer.
 
@@
     1024 lines in the manuscript would be uninformative. To prove this is
-    the case, a plot of 32 of the tangential velocities is in
-    Figure~\ref{fig:tangVel} of this document. Instead, in the document,
-    we report the average tangential velocity in the region $x \in
-    [4,10]$, and report the spread of all tangential velocities from
-    this mean value. If this spread is less than 15\%, we would
+    the case, a plot of 32 of the tangential velocities is in Figure~\ref{fig:tangVel} of this document. 
+%    
+    Instead we track the tangential velocity of each Lagrangian marker on the vesicle membrane, measuring the variation in this tangential velocity over the duration when the vesicle is inside the stenosis.
+This variation over time gives a ``spread in tangential velocity" on each marker, and we color-code the membrane by this spread in tangential velocity scaled to the velocity magnitude.
+For a tank-treading vesicle, this scheme would give a membrane of a uniform color.
+On the other hand, a non-uniformly colored membrane implicates the lack of tank-treading in the vesicle membrane, which may also correspond to significant deformations in the membrane.
+%   
+% Instead, in the document,
+%  we report the average tangential velocity in the region $x \in
+% [4,10]$, and report the spread of all tangential velocities from
+%this mean value. 
+More quantitatively, if this spread is less than 15\%, we would
     characterize this as a tank-treading vesicle. Their spread is 1.2\%
@@
     text.
-    {\bf TODO: Change color of Fig 7 lines or state why we don't do
-    this.}
+%    {\bf TODO: Change color of Fig 7 lines or state why we don't do
+%    this.}
 
@@
 \noindent
-{\bf Response:} Thank you for the comment.
+{\bf Response:} We thank the referee for this comment. We did not change the title as the referee found the title tolerable.
 \end{enumerate}

### 2023-10-19 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
starting on new Fig 7 plots

@@
   \subfigimg[width=0.3\linewidth]{(c)}{figures/Layer_Size_RAp4_MCp5.pdf}
-  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{}{figures/TankTreadingFigs_composite_SC.pdf}
-  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
-  0cm,clip=true]{}{figures/TankTreadingFigs_composite_SCp55.pdf}
-  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
-  0cm,clip=true]{}{figures/TankTreadingFigs_composite_MCp5.pdf}
+  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
+    {figures/SC_treading_velocity2.pdf}
+  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
+    {figures/SCp55_treading_velocity2.pdf}
+  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
+    {figures/MCp5_treading_velocity2.pdf}
+%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{}{figures/TankTreadingFigs_composite_SC.pdf}
+%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
+%  0cm,clip=true]{}{figures/TankTreadingFigs_composite_SCp55.pdf}
+%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
+%  0cm,clip=true]{}{figures/TankTreadingFigs_composite_MCp5.pdf}
   \caption{\label{fig:lubricationComposite} \small The lubrication layer
@@
   multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all
-  three cases. Also illustrated is the vesicle shape and the four
-  Lagrangian points at the location indicated by the dash line. The
-  black dashed line is the center line of the channel, and the arrow
+  three cases. 
+  \textcolor{blue}{
+  Also illustrated is the vesicle shape when its center of mass is
+  located at $x=4$. Then, color represents the spread of the tangential
+  velocity relative to the mean tangential velocity, where the average
+  is taken over the region $x \in [4,10]$. 
+  }
+%  Also illustrated is the vesicle shape and the four
+%  Lagrangian points at the location indicated by the dash line.
+  The black dashed line is the center line of the channel, and the arrow
   denotes the tank-treading direction. The percentage of the vesicle

### 2023-10-19 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
added a few more words to caption

@@
   located at $x=4$. Then, color represents the spread of the tangential
-  velocity relative to the mean tangential velocity, where the average
-  is taken over the region $x \in [4,10]$. 
+  velocity relative to the average tangential velocity, where the average
+  is taken over the region $x \in [4,10]$. We characterize the stiff
+  single-component and multicomponent vesicles as tank treading since
+  the spread in the tangential velocity is below \%15, while the floppy
+  single-component vesicle is not tank treading.
   }

### 2023-10-19 vesicle_code/docs/confinedMulti/response.tex
yny

@@
 We do not observe any dependence on the capillary number. We had a
-discussion with an experimental colleague who works on an experiment
-with a red blood cell passing through stenosis, where only a single RBC
-can pass through one at a time. His experiments have shown that the
+discussion with a colleague who works on experiments
+with a red blood cell passing through stenosis, where RBCs form a single line in the mid-plane of the channel.
+ His experiments have shown that the
 shape of the RBC inside this confined stenosis is independent over a
 range of capillary numbers, as we report in Figure~\ref{fig:Phase}. For
-this reason, we do not include phase diagrams in our manuscript. We have
+this reason, we do not include this phase diagram in our manuscript. We have
 started examining the dependence of these dynamics on other
-dimensionless parameters including the confinement ratio and the
+dimensionless parameters such as the confinement ratio and the
 floppy-to-stiff ratio. This will be a different focus and would distract
@@
 \noindent
-{\bf Response:} We thank the referee for this comment. We did not change the title as the referee found the title tolerable.
+{\bf Response:} We thank the referee for this comment. We did not change the title as the referee found it tolerable.
 \end{enumerate}

### 2023-10-20 vesicle_code/docs/confinedMulti/response.tex
yny
adding last figure to rebuttal

@@
 %    
-    Instead we track the tangential velocity of each Lagrangian marker on the vesicle membrane, measuring the variation in this tangential velocity over the duration when the vesicle is inside the stenosis.
-This variation over time gives a ``spread in tangential velocity" on each marker, and we color-code the membrane by this spread in tangential velocity scaled to the velocity magnitude.
-For a tank-treading vesicle, this scheme would give a membrane of a uniform color.
-On the other hand, a non-uniformly colored membrane implicates the lack of tank-treading in the vesicle membrane, which may also correspond to significant deformations in the membrane.
+Instead we track the tangential velocity of each Lagrangian marker on
+the vesicle membrane, measuring the spread in this tangential velocity
+over the part of the period when the vesicle is inside the stenosis.
+This spread, scaled by the velocity magnitude, is color-coded along the
+membrane and is now part of Figure 7. The original plots showing the
+tangential velocity of the four points are removed. For a tank-treading
+vesicle, this scheme would give a membrane of a uniform color. On the
+other hand, a non-uniformly colored membrane implicates the lack of
+tank-treading in the vesicle membrane, which may also correspond to
+significant deformations in the membrane.
 %   
@@
 More quantitatively, if this spread is less than 15\%, we would
-    characterize this as a tank-treading vesicle. Their spread is 1.2\%
-    for the stiff single-component vesicle, 12\% for the multicomponent
-    case, and 313\% for the floppy single-component case. Therefore, the
-    floppy single-component vesicle is not tank-treading, while the
-    other two cases are tank-treading. We have made this clear in the
-    text.
-%    {\bf TODO: Change color of Fig 7 lines or state why we don't do
-%    this.}
+characterize this as a tank-treading vesicle. Their spread is 1.2\% for
+the stiff single-component vesicle, 12\% for the multicomponent case,
+and 313\% for the floppy single-component case. Therefore, the floppy
+single-component vesicle is not tank-treading, while the other two cases
+are tank-treading. We have made this clear in the text.
 
@@
   the (a) stiff single-component vesicle, (b) floppy single-component
-  vesicle, (c) multicomponent vesicle.}
+  vesicle, (c) multicomponent vesicle. Note that these figures, and the
+  version with four marker points, are excluded from the revised
+  manuscript.}
 \end{figure}
@@
 \noindent {\bf Response:} The examples with a random initial condition
-    use the uniform distribution with the range $[0,1]$ to define the
-    lipid concentration $u$ at each spatial point. Given the choices of
-    $b_{\min}=0.1$ and $b_{\max}=1$, the resulting mean bending
-    stiffness is $\overline{b(u)} \approx 0.55$. The text has been
-    adjusted at the start of Section 3.1 and Section 3.2.
+use the uniform distribution with the range $[0,1]$ to define the lipid
+concentration $u$ at each spatial point. Given the choices of
+$b_{\min}=0.1$ and $b_{\max}=1$, the resulting mean bending stiffness is
+$\overline{b(u)} \approx 0.55$. The text has been adjusted at the start
+of Section 3.1 and Section 3.2.
 
@@
 
-%There are 3D BIE codes for vesicles with surface rheology. Leonetti did
-%in 2016 in paper Yuan is sending me. There, of course, is also plenty of
-%accurate methods for single-component vesicles in 3D with strong
-%confinement. This will be even more challenging with strong confinement.
-%Only methods in the literature seem to be David Salac which is a
-%low-order method. Can reference private discussions Zhangli Peng at UIC.
-%
-%A response
-
 %%%%%%%%
@@
 %
-%FIRST ROUGH DRAFT: We did observe cases where
-%    multicomponent vesicles are stuck. However, keeping all other
-%    parameters fixed, the corresponding single-component vesicles were
-%    also stuck. We were hoping to find cases where the multicomponent
-%    vesicle passed through the contracting geometry while the
-%    single-component vesicles did not (similar to our semipermeable
-%    work), but no such case was found.  For this reason, we have focused
-%    on the effect that multicomponent has on the vesicle shape, tension,
-%    layer thickness, tank treading, etc.
 
@@
 \noindent
-{\bf Response:} We can compare Zhangli Peng's results, our simulations
-look similar to what they observe in a 2D projection of their 3D
-results. They call their geometry a `slit' geometry. This work is
-published, so we can reference a particular figure from the paper.
+{\bf Response:} We are interpreting this question as the reviewer asking
+about 3D effects. In the literature, the 3D simulations of a red blood
+cell through a 3D slit (see Lu and Peng,
+https://doi.org/10.1063/1.5081057) has a 2D projection that looks
+similar to our 2D simulations. In particular their right-most panel in
+Figure 5(b) resembles Figures 10(d) and 10(e) in columns V and VI from
+our paper. Other than the shape similarity of the 2D projection, we also
+find that our excess pressure is of the same order for a similar flow
+rate in a 3D case (http://dx.doi.org/10.1063/1.4817959).
 
@@
 \noindent
-{\bf Response:} A phase diagram is included in Figure~\ref{fig:Phase}.
-We do not observe any dependence on the capillary number. We had a
-discussion with a colleague who works on experiments
-with a red blood cell passing through stenosis, where RBCs form a single line in the mid-plane of the channel.
- His experiments have shown that the
-shape of the RBC inside this confined stenosis is independent over a
-range of capillary numbers, as we report in Figure~\ref{fig:Phase}. For
-this reason, we do not include this phase diagram in our manuscript. We have
-started examining the dependence of these dynamics on other
-dimensionless parameters such as the confinement ratio and the
-floppy-to-stiff ratio. This will be a different focus and would distract
-from the focus of this work.
+{\bf Response:} As shown recently by Agarwal and Biros
+(http://www.doi.org/10.1103/PhysRevFluids.5.013603) (see Figure 18a),
+when a vesicle is in a channel with strong confinement, there are at
+most two different shapes a vesicle can take on for different capillary
+numbers. They observe this for confinement ratios as large as 0.7, and
+our examples have a confinement ratio closer to 2 (stronger
+confinement). To verify this claim, we constructed a phase diagram for a
+multicomponent vesicle in a unconfined non-linear shear flow by varying
+the reduced area and the capillary number. We observe that the
+multicomponent vesicle is more symmetric in shape than the
+single-component vesicle for a wide range of capillary numbers and
+reduced areas (Figure~\ref{fig:Phase}). Based on this, we speculate that
+a phase diagram with strong confinement would be less interesting than
+the single-component case, so we exclude a phase diagram in confinement.
+%
+%A phase diagram is included in Figure~\ref{fig:Phase}.
+%We do not observe any dependence on the capillary number.
+
+We have also discussed this topic with a colleague who works on
+experiments with a red blood cell passing through stenosis, where RBCs
+form a single line in the mid-plane of the channel. His experiments have
+shown that the shape of the RBC inside this confined stenosis is
+independent over a range of capillary numbers. For this reason, we focus
+on the relationships between between the vesicle shape, lubrication
+layer, excess pressure, and asymmetry relative to the midline.
+
+We have started examining the dependence of the vesicle symmetry on
+other dimensionless parameters such as the confinement ratio and the
+floppy-to-stiff ratio. This will likely give rise to different phenomena
+and analyses that would distract from the focus of this work.
 \begin{figure}
 \centering
-  \includegraphics[width=0.5\textwidth]{phaseDiagram.jpg}
-  \caption{\label{fig:Phase} A phase diagram of a single vesicle in an unconfined
-  nonlinear shear flow. The capillary number has no effect on the steady
-  state shape of the vesicle.}
+  \includegraphics[width=0.5\textwidth]{phaseDiagram.pdf}
+  \caption{\label{fig:Phase} A phase diagram of a single multicomponent
+  vesicle in an unconfined nonlinear shear flow. The capillary number
+  has no effect on the steady state shape of the vesicle.}
 \end{figure}

### 2023-10-20 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
adding last figure to rebuttal

@@
   single-component and multicomponent vesicles as tank treading since
-  the spread in the tangential velocity is below \%15, while the floppy
+  the spread in the tangential velocity is below 15\%, while the floppy
   single-component vesicle is not tank treading.

### 2023-10-20 shuwang_rewrite/tstep.m

@@ -241,6 +241,8 @@ if o.confined
   bgFlowWalls = o.bgFlow(walls.X, o.shearRate, o.farFieldFlow);
   rhsWalls = bgFlowWalls - vesVel2Wall;
   etaout = o.etaSolver(rhsWalls);
+else
+  etaout = [];
 end
 %Add in the fdotn term for the semipermeability model
 fdotn = tau(1:end/2).*sin(theta)-tau(end/2+1:end).*cos(theta);

### 2023-10-20 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on revisions

@@
 of the vesicle with reduced area $\alpha = 0.4$ are in the top half of
-Figure~\ref{fig:lubricationComposite}. The bottom of
-Figure~\ref{fig:lubricationComposite} shows the 
-\textcolor{blue}{
-tangential
-}
-%tank-treading
-velocities of four Lagrangian points. The inset shows the vesicle
-configuration in the closely-fitting part of the channel, the black
-dashed line is the center line of the channel, the marks are the four
-Lagrangian points, and the rounded arrow denotes the direction of
-rotation. 
+Figure~\ref{fig:lubricationComposite}. 
+%The bottom of Figure~\ref{fig:lubricationComposite} shows the
+%tank-treading velocities of four Lagrangian points. The inset shows the
+%vesicle configuration in the closely-fitting part of the channel, the
+%black dashed line is the center line of the channel, the marks are the
+%four Lagrangian points, and the rounded arrow denotes the direction of
+%rotation. 
 \textcolor{blue}
@@
 Lagrangian points when the vesicle's center of mass is in the interval
-$[4,10]$. If the maximum and minimum tangential velocities are within
-15\% of the average tangential velocity, we characterize the vesicle as
-tank-treading. The average tangential velocities are $-1.00 \times
-10^{-1}$ for the stiff single-component vesicle, $3.31 \times 10^{-2}$
-for the floppy single-component vesicle, and $-8.48 \times 10^{-1}$ for
-the multicomponent vesicle. The spread of the maximum and minimum
-velocities from these average tangential velocities are $1.2\%$ for the
-stiff single-component vesicle, $12\%$ for the multicomponent vesicle,
-and over $300\%$ for the floppy single-component vesicle. Therefore, we
-classify the stiff single-component and multicomponent vesicles as tank
-treading, while the floppy single-component is not tank treading.
-}
+$[4,10]$. If the difference of the maximum and minimum tangential
+velocities is within 15\% of the average tangential velocity, we
+characterize the vesicle as tank-treading. These relative relative
+spreads are plotted in the bottom row of
+Figure~\ref{fig:lubricationComposite}. The average tangential velocities
+are $-1.00 \times 10^{-1}$ for the stiff single-component vesicle, $3.31
+\times 10^{-2}$ for the floppy single-component vesicle, and $-8.48
+\times 10^{-1}$ for the multicomponent vesicle. The difference of the
+maximum and minimum velocities relative to the average tangential
+velocities is $1.2\%$ for the stiff single-component vesicle, $12\%$ for
+the multicomponent vesicle, and over $300\%$ for the floppy
+single-component vesicle. Therefore, we classify the stiff
+single-component and multicomponent vesicles as tank treading, while the
+floppy single-component is not tank treading.}
 %The stiff single-component and multicomponent vesicles are
@@
 \textcolor{blue}{
-rotation, but, again, the vesicle dynamics are not tank-treading as the
-vesicle is undergoing large normal deformations.
-}
+rotation, but, again, large normal defomrations are occuring along with
+the rotation.
+%}
 %tank-treading. 
-\textcolor{blue}{
+%\textcolor{blue}{
 Finally, the stiff single-component vesicle tank treads faster than the

### 2023-10-20 vesicle_code/docs/confinedMulti/response.tex
working on revisions
last few changes ... I hope

@@
 \noindent
-{\bf Response:} Thank you for the suggestion. It is included in the
-    revised manuscript.
+{\bf Response:} Thank you for the suggestion. The $x$ coordinate is
+added to these figures in the revised manuscript.
 
@@
   \subfigimg[width=0.3\textwidth]{(c)}{figures/MCp5_treading_velocity_review.pdf}
-  \caption{\label{fig:tangVel} The tangential velocity of 32 points of
-  the (a) stiff single-component vesicle, (b) floppy single-component
-  vesicle, (c) multicomponent vesicle. Note that these figures, and the
-  version with four marker points, are excluded from the revised
-  manuscript.}
+  \caption{\label{fig:tangVel} \small The tangential velocity of 32
+  points of the (a) stiff single-component vesicle, (b) floppy
+  single-component vesicle, (c) multicomponent vesicle. Note that these
+  figures, and the version with four marker points, are excluded from
+  the revised manuscript.}
 \end{figure}
@@
 out by the reviewer, we did not make any reference to the floppy case.
-As a general trend, we find that the sum of the top and bottom
-lubrication layer thicknesses is correlated with the magnitude of the
-excess pressure---larger lubrication layers correspond to smaller (less
+As a general trend, the sum of the top and bottom lubrication layer
+thicknesses is correlated with the magnitude of the excess
+pressure---larger lubrication layers correspond to smaller (less
 negative) excess pressures. This is because smaller excess pressure is
@@
 \noindent
-{\bf Response:} There is published work that has investigated elements
-of our work in  3D. This includes the papers from the reviewers first
+{\bf Response:} There is published work that investigates elements of
+our work in  3D. This includes the papers from the reviewers first
 comment that consider vesicles in strong confinement, but these works
-assume axisymmetry and neither consider multicomponent vesicles. Two
-3D works that relax the axisymmetric assumption and simulate vesicles in
+assume axisymmetry and neither consider multicomponent vesicles. Two 3D
+works that relax the axisymmetric assumption and simulate vesicles in
 strong confinement are also cited in the original submission
-(https://doi.org/10.1063/1.5081057 and
-https://doi.org/10.1103/PhysRevFluids.5.013603). Red blood cells
+(\url{https://doi.org/10.1063/1.5081057} and
+\url{https://doi.org/10.1103/PhysRevFluids.5.013603}). Red blood cells
 undergoing strong confinement has also been considered using other
 numerical methods including a spring model coupled to smoothed particle
-hydrodynamics (http://dx.doi.org/10.1016/j.taml.2015.11.006 and
-http://dx.doi.org/10.1063/1.4817959). These papers are cited in the
-revised manuscript.
+hydrodynamics (\url{http://dx.doi.org/10.1016/j.taml.2015.11.006} and
+\url{http://dx.doi.org/10.1063/1.4817959}). These papers are cited in
+the revised manuscript.
 
@@
 models are used by Wang and Du
-(https://doi.org/10.1007/s00285-007-0118-2) and a level set method is
-used by Gera and Salac
-(https://doi.org/10.1016/j.compfluid.2018.04.003). The challenge with
-both these approaches is that they have to discretize the fluid volume,
-and this limits how small $\epsilon$ can be, and therefore restricts
-the sharpness of the transition between the floppy and stiff
-regions. In both these works, a value of $\epsilon$ that is at least
+(\url{https://doi.org/10.1007/s00285-007-0118-2}) and a level set method
+is used by Gera and Salac
+(\url{https://doi.org/10.1016/j.compfluid.2018.04.003}). The challenge
+with both these approaches is that they discretize the fluid volume, and
+this limits how small $\epsilon$ can be, and therefore restricts the
+sharpness of the transition between the floppy and stiff regions. In
+both these works, a value of $\epsilon$ is used that is at least
 ten-times larger than the more realistic value used in our work. To use
@@
 value of $\epsilon$, a single simulation would require much more
-computational resources for generating an appropriately large dataset to
+computational resources to generate an appropriately large dataset to
 analyze. For example, if a simulation for an unconfined case requires
-one day of CPU time on 12 cores, then, even without confinement, the
-additional resolution required to resolve the smaller value of
+one day of wall clock time on 12 cores, then, even without confinement,
+the additional resolution required to resolve the smaller value of
 $\epsilon$ would require 12,000 cores to complete the simulation in the
@@
 considers reaction-diffusion systems on surfaces
-(https://nrs.harvard.edu/URN-3:HUL.INSTREPOS:37368862), and the preprint
-written by the same author (https://arxiv.org/pdf/2210.00022.pdf).
-Extending this work to incorporate a high-order phase field model and
-deformable interface is currently unavailable, to the best of our
-knowledge.
+(\url{https://nrs.harvard.edu/URN-3:HUL.INSTREPOS:37368862}), and the
+preprint written by the same author
+(\url{https://arxiv.org/pdf/2210.00022.pdf}). Extending this work to
+incorporate a high-order phase field model and deformable interface is
+currently unavailable, to the best of our knowledge.
 
@@
 cite including [10,11,18] (as numbered in our original submission). We
-have also added a note that the capillary number is larger for a vesicle
-inside the stenosis.
+have also added a note that the capillary number is larger when a
+vesicle is inside the stenosis.
 
-For the comment regarding the value of $\epsilon$, we had a
-typo. The parameter value for $\epsilon$ is actually 0.04, and this has
-been fixed.
+For the comment regarding the value of $\epsilon$, we had a typo. We
+have checked our code, and the parameter value for $\epsilon$ is
+actually 0.04. This has been fixed in the revised manuscript.
 
@@
 However, we did observe other behaviors that differ between the two
-cases, including the vesicle shape, tank treading velocity, lubrication
+cases, including the vesicle shape, tank-treading velocity, lubrication
 layer, and these comparisons are the focus of our manuscript. We defer
@@
 cell through a 3D slit (see Lu and Peng,
-https://doi.org/10.1063/1.5081057) has a 2D projection that looks
+\url{https://doi.org/10.1063/1.5081057}) has a 2D projection that looks
 similar to our 2D simulations. In particular their right-most panel in
-Figure 5(b) resembles Figures 10(d) and 10(e) in columns V and VI from
-our paper. Other than the shape similarity of the 2D projection, we also
-find that our excess pressure is of the same order for a similar flow
-rate in a 3D case (http://dx.doi.org/10.1063/1.4817959).
+Figure 5(b) resembles Figures 10(d) and 10(e) in columns V and VI in our
+manuscript. Other than the shape similarity of the 2D projection, we
+also find that our excess pressure is of the same order for a similar
+flow rate in a 3D case (\url{http://dx.doi.org/10.1063/1.4817959}).
 
@@
 \noindent
-{\bf Response:} As shown recently by Agarwal and Biros
-(http://www.doi.org/10.1103/PhysRevFluids.5.013603) (see Figure 18a),
-when a vesicle is in a channel with strong confinement, there are at
-most two different shapes a vesicle can take on for different capillary
-numbers. They observe this for confinement ratios as large as 0.7, and
-our examples have a confinement ratio closer to 2 (stronger
-confinement). To verify this claim, we constructed a phase diagram for a
-multicomponent vesicle in a unconfined non-linear shear flow by varying
-the reduced area and the capillary number. We observe that the
-multicomponent vesicle is more symmetric in shape than the
-single-component vesicle for a wide range of capillary numbers and
-reduced areas (Figure~\ref{fig:Phase}). Based on this, we speculate that
-a phase diagram with strong confinement would be less interesting than
-the single-component case, so we exclude a phase diagram in confinement.
-%
-%A phase diagram is included in Figure~\ref{fig:Phase}.
-%We do not observe any dependence on the capillary number.
+{\bf Response:} Agarwal and Biros
+(\url{http://www.doi.org/10.1103/PhysRevFluids.5.013603})  recently
+showed that when a vesicle is in a channel with strong confinement,
+there are at most two different shapes a vesicle can take on for
+different capillary numbers (see Figure 18a). They observe this for
+confinement ratios as large as 0.7, and our examples have a confinement
+ratio closer to 2 (stronger confinement). At such strong confinement, we
+do not expect the capillary number to have an effect on the vesicle
+  shape. To substantiate this claim, we consider a single multicomponent
+  vesicle in an unconfined non-linear shear flow at various capillary
+  numbers and reduced areas. The phase diagram (Figure~\ref{fig:Phase})
+  shows that the multicomponent vesicle is more symmetric in shape than
+  the single-component vesicle for a wide range of capillary numbers and
+  reduced areas. Based on this, we speculate that a phase diagram with
+  strong confinement would be less interesting than the single-component
+  case, so we exclude a phase diagram with confinement.
 
 We have also discussed this topic with a colleague who works on
-experiments with a red blood cell passing through stenosis, where RBCs
-form a single line in the mid-plane of the channel. His experiments have
-shown that the shape of the RBC inside this confined stenosis is
-independent over a range of capillary numbers. For this reason, we focus
-on the relationships between between the vesicle shape, lubrication
-layer, excess pressure, and asymmetry relative to the midline.
+experiments with red blood cells forming a single line along the
+mid-plane as they pass through stenosis. His experiments show that the
+shape of the red blood cell inside this confined stenosis is independent
+over a range of capillary numbers. For this reason, we focus on the
+relationships between between the vesicle shape, lubrication layer,
+excess pressure, and asymmetry relative to the midline.
 
@@
   \includegraphics[width=0.5\textwidth]{phaseDiagram.pdf}
-  \caption{\label{fig:Phase} A phase diagram of a single multicomponent
-  vesicle in an unconfined nonlinear shear flow. The capillary number
-  has no effect on the steady state shape of the vesicle.}
+  \caption{\label{fig:Phase} \small A phase diagram of a single
+  multicomponent vesicle in an unconfined nonlinear shear flow. The
+  capillary number has no effect on the steady state shape of the
+  vesicle.}
 \end{figure}

### 2023-10-20 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
last few changes ... I hope

@@
   Also illustrated is the vesicle shape when its center of mass is
-  located at $x=4$. Then, color represents the spread of the tangential
-  velocity relative to the average tangential velocity, where the average
-  is taken over the region $x \in [4,10]$. We characterize the stiff
-  single-component and multicomponent vesicles as tank treading since
-  the spread in the tangential velocity is below 15\%, while the floppy
-  single-component vesicle is not tank treading.
+  located at $x=4$. The color represents the spread of the tangential
+  velocity relative to the average tangential velocity, where the
+  average is taken over the region $x \in [4,10]$. We characterize the
+  stiff single-component and multicomponent vesicles as tank treading
+  since the spread in the tangential velocity is below 15\%, while the
+  floppy single-component vesicle is not tank treading.
   }
@@
 velocities is within 15\% of the average tangential velocity, we
-characterize the vesicle as tank-treading. These relative relative
-spreads are plotted in the bottom row of
-Figure~\ref{fig:lubricationComposite}. The average tangential velocities
-are $-1.00 \times 10^{-1}$ for the stiff single-component vesicle, $3.31
-\times 10^{-2}$ for the floppy single-component vesicle, and $-8.48
-\times 10^{-1}$ for the multicomponent vesicle. The difference of the
-maximum and minimum velocities relative to the average tangential
-velocities is $1.2\%$ for the stiff single-component vesicle, $12\%$ for
-the multicomponent vesicle, and over $300\%$ for the floppy
-single-component vesicle. Therefore, we classify the stiff
-single-component and multicomponent vesicles as tank treading, while the
-floppy single-component is not tank treading.}
+characterize the vesicle as tank-treading. These relative spreads are
+plotted in the bottom row of Figure~\ref{fig:lubricationComposite}. The
+average tangential velocities are $-1.00 \times 10^{-1}$ for the stiff
+single-component vesicle, $3.31 \times 10^{-2}$ for the floppy
+single-component vesicle, and $-8.48 \times 10^{-1}$ for the
+multicomponent vesicle. The difference of the maximum and minimum
+velocities relative to the average tangential velocities is $1.2\%$ for
+the stiff single-component vesicle, $12\%$ for the multicomponent
+vesicle, and over $300\%$ for the floppy single-component vesicle.
+Therefore, we classify the stiff single-component and multicomponent
+vesicles as tank treading, while the floppy single-component is not tank
+treading.}
 %The stiff single-component and multicomponent vesicles are
@@
 \textcolor{blue}{
-rotation, but, again, large normal defomrations are occuring along with
+rotation, but, again, large normal deformations are occuring along with
 the rotation.
@@
 \textcolor{blue}{
-As a general trend, we find that the sum of the top and bottom
-lubrication layer thicknesses is correlated with the magnitude of the
-excess pressure---larger lubrication layers correspond to smaller (less
+As a general trend, the sum of the top and bottom lubrication layer
+thicknesses is correlated with the magnitude of the excess
+pressure---larger lubrication layers correspond to smaller (less
 negative) excess pressures. This is because smaller excess pressure is

### 2023-10-20 vesicle_code/docs/confinedMulti/response.tex
yny

@@
 other dimensionless parameters such as the confinement ratio and the
-floppy-to-stiff ratio. This will likely give rise to different phenomena
-and analyses that would distract from the focus of this work.
+floppy-to-stiff ratio. This may give rise to different phenomena
+and analyses that would distract from the focus of this work. Given the extra time it will take to
+explore the phase diagram in these dimensionless parameters, we hope the referee would agree with us that these results would be better suited in a different manuscript which is what we have been working on now, using results and analyses summarized in this manuscript.
 \begin{figure}

### 2023-10-20 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
fixed spelling mistake
yny

@@
 %rotation.
+
 \textcolor{blue}
-{
-To determine if a vesicle is tank-treading, we first calculate the
+{Here we described the criterion for determining if a vesicle is tank-treading: we first calculate the
 average, maximum, and minimum tangential velocities over all $N$
@@
 %clearly tank treading.
+
 The direction and speed of the tank-treading depends on how much of the
@@
 \textcolor{blue}{
-rotation, but, again, large normal deformations are occuring along with
+rotation, but, again, large normal deformations are occurring along with
 the rotation.
@@
 \textcolor{blue}{
-with width $6.5$. In dimensioned units, the width of the neck is
+with width $6.5$. In dimensional units, the width of the neck is
 $2~\mu$m.

### 2023-10-21 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
small change

@@
 \textcolor{blue}
-{Here we described the criterion for determining if a vesicle is tank-treading: we first calculate the
-average, maximum, and minimum tangential velocities over all $N$
+{The criterion to determine if a vesicle is tank-treading starts by
+first calculating
+%Here we described the criterion for determining if a vesicle is tank-treading: we first calculate 
+the average, maximum, and minimum tangential velocities over all $N$
 Lagrangian points when the vesicle's center of mass is in the interval

### 2023-10-21 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
another small change
yny

@@
 \textcolor{blue}
-{The criterion to determine if a vesicle is tank-treading starts by
-first calculating
+{For a vesicle in free space, tank-treading membrane is often associated with a membrane of a steady shape and a constant tank-treading speed along the membrane.
+For a vesicle going through dynamic deformation in strong confinement, we provide a criterion to determine if a vesicle is tank-treading 
+by first calculating
 %Here we described the criterion for determining if a vesicle is tank-treading: we first calculate 
-the average, maximum, and minimum tangential velocities over all $N$
+the average, maximum, and minimum tangential velocities over all
 Lagrangian points when the vesicle's center of mass is in the interval

### 2023-10-21 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

@@
 \textcolor{blue}
-{For a vesicle in free space, tank-treading membrane is often associated with a membrane of a steady shape and a constant tank-treading speed along the membrane.
-For a vesicle going through dynamic deformation in strong confinement, we provide a criterion to determine if a vesicle is tank-treading 
+{For a vesicle in free space, tank-treading is often associated with a steady shape and a constant tangential speed along the membrane.
+For a vesicle going through dynamic deformation in strong confinement, we provide a criterion for a transient tank-treading membrane 
 by first calculating

### 2023-10-21 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

@@
 \textcolor{blue}
-{For a vesicle in free space, tank-treading is often associated with a steady shape and a constant tangential speed along the membrane.
-For a vesicle going through dynamic deformation in strong confinement, we provide a criterion for a transient tank-treading membrane 
+{For a vesicle in free space, tank-treading is associated with a steady membrane shape and a constant tangential speed along the membrane.
+For a vesicle in strong confinement going through dynamic deformation, we provide a criterion for a transient tank-treading membrane 
 by first calculating
